### 2016-07-06 Complex Geometry - index of notations by taper.tex
Initial drafts.

\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

\usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols

\title{Complex Geometry - Index of Notations and ideas}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
Obviously.

\end{abstract}

\section{Book}
	\subsection{1. Local Theory}
		\subsubsection{1.1 Holomorphic Functions of Several Variables}
		\label{sec:1.1_book}
		\textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.

		\textcolor{blue}{holomorphic}: pp.1. pp4. Def 1.1.1. pp.10(Def.1.1.8).

		\textcolor{blue}{Cauchy-Riemann equations}: pp.2

		\textcolor{blue}{$\frac{\partial}{\partial z}$,$\frac{\partial}{\partial \bar{z}}$}:
		$\frac{\partial}{\partial z}:= \frac{1}{2}
				(\frac{\partial}{\partial x} 
				-i \frac{\partial}{\partial y})
				$
		,
		$\frac{\partial}{\partial \bar{z}}:= \frac{1}{2}
		(\frac{\partial}{\partial x} 
		+ i \frac{\partial}{\partial y})
		$

		\textcolor{blue}{Maximum principle}: pp.3.

		\textcolor{blue}{Identity theorem}: pp.3.

		\textcolor{blue}{Riemann extension theorem}: pp.3. pp.9 (Prop. 1.1.7).

		\textcolor{blue}{Riemann mapping theorem}: pp.3.

		\textcolor{blue}{Liouville theorem}: pp.4.

		\textcolor{blue}{Residue theorem}: pp.4.

		\textcolor{blue}{polydiscs $B_\epsilon(\omega)$}: $\{z| |z_i-\omega_i| <\epsilon\} $.  pp.4.

		\textcolor{blue}{Hartogs' theorem}: Prop. 1.1.4. pp.6.

		\textcolor{blue}{Weierstrass preparation theorem (WPT)}:
		Prop. 1.1.6. pp.8.

		\textcolor{blue}{Weierstrass polynomial}: Def. 1.1.5. pp.7.

		\textcolor{blue}{$Z(f)$}: zero set of $f$. pp.9.

		\textcolor{blue}{biholomorphic}: pp.10.

		\textcolor{blue}{(complex) Jacobian, regular, regular value}: Def. 1.1.9. pp.10.

		\textcolor{blue}{IFT. Inverse function theorem}: Prop 1.1.10 pp.11.

		\textcolor{blue}{IFT. Implicit function theorem}: Prop 1.1.11. pp.10.

		\textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n}$}:
		sheaf of holomorphic functions on $\mathbb{C}^n$. Def. 1.1.14. pp.14.

		\textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n,z}$}: Def. 1.1.14. pp.14.

		\textcolor{blue}{$\mathcal{O}^*_{\mathbb{C}^n,0}$}:
		units of $\mathcal{O}_{\mathbb{C}^n,0}$. pp.14.

		\textcolor{blue}{UFD, unique factorization domain, irreducible}: 
		Def. 1.1.16. pp.14.

		\textcolor{blue}{Gauss Lemma}: pp.14.

		\textcolor{blue}{Weierstrass division theorem}: Prop. 1.1.17. pp.15.

		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:

	\subsection{2.Complex Manifolds}

		\subsubsection{2.2 Holomorphic Vector Bundles}

		\textcolor{blue}{$\tau_X$}: holomorphic tangent bundle of a complex manifold $X$ (Def 2.2.14 at pp. 71).

		\textcolor{blue}{$\varOmega_X$, $\varOmega^p_X$}: holomorphic cotangent bundle and holomorphic $p$-forms. (Def 2.2.14 at pp. 71)

		\textcolor{blue}{$K_X$}:=det($\varOmega_X$) = $\varOmega_X^n$, the canonical bundle of $X$. (Def 2.2.14 at pp. 71)

		\subsubsection{2.6 Differential Calculus on Complex Manifolds}

		\textcolor{blue}{$\wedge^k_{\mathbb{C}}X$}:=$\wedge^k(T_{\mathbb{C}}X)^*$. (Def 2.6.7 at pp. 105)

		\textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
							\bigotimes_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)

		\textcolor{blue}{$\mathcal{A}^k_{X,\mathbb{C}}$,$\mathcal{A}^{p,q}_X$}: sheaves of section of the above correspond items. (Def 2.6.7 at pp. 105)

		\textcolor{blue}{$\mathcal{A}^{p,q}(E)$}: the sheaf of $p,q$-forms with values in $E$, a complex vector bundle. (Def 2.6.22 at pp.109). Note that in particular, $\mathcal{A}^0(E)$ is the sheaf of sections of $E$.

	\subsection{Appendix B: Sheaf Cohomology}

	\begin{itemize}
		\item
		\textcolor{blue}{pre-sheaf}: Def B.0.19, pp. 287.

		\item
		\textcolor{blue}{$\mathcal{C^0_M}$}: the pre-sheaf of continuous functions on $M$. Example B.0.20, pp. 287.

		\item
		\textcolor{blue}{sheaf}: Def B.0.21, at pp.288.

		\item
		\textcolor{blue}{\underline{$\mathbb{R}$},\underline{$\mathbb{Z}$}}: constant sheaves, Sometimes written simply as \textcolor{blue}{$\mathbb{R}$}, \textcolor{blue}{$\mathbb{Z}$} respectively. pp. 288.
		\item
		\textcolor{blue}{$\mathcal{E}$}: actually a $\mathcal{C}^0_M$-modules. Sometimes identified as $E$. pp.288.
		\item
		\textcolor{blue}{(pre)-sheaf homomorphism}: Def B.0.23.  pp.288.
		\item
		\textcolor{blue}{Ker($\phi$),Im($\phi$),Coker($\phi$)}: as pre-sheaves in pp.288. sheaves in pp.289, Def B.0.26.
		\item
		\textcolor{blue}{injective, surjective of sheaf-homomorphism}:pp.289.
		\item
		\textcolor{blue}{complex, exact complex}: Def B.0.27. pp.289
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:
		\item
		\textcolor{blue}{text}:	
	\end{itemize}

\section{My lecture Notes}

	\subsection{Lecture 2016 Lecture 1}
	The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.

	\subsection{Lecture 4 (20160307) Complex Manifold}

	\textbf{Note}: we use abbrevation \textit{mnfd} for \textit{manifold}.

	pp. A:
		\begin{itemize}
			\item \textcolor{blue}{Holomorphic Atlas}
			\item \textcolor{blue}{Holmorphic chart}
			\item \textcolor{blue}{Complex mnfd}
		\end{itemize}

	pp. B:
		\begin{itemize}
			\item \textcolor{blue}{Holomorphic function}
			\item \textcolor{blue}{$\mathcal{O}_X$}: sheaf of holomorhic functions on a complex mnfd $X$.
		\end{itemize}
	pp. C:
		\begin{itemize}
			\item \textcolor{blue}{Hartdogs' theorem}: on complex mnfd.
			\item \textcolor{blue}{Holomorphic functions on complex mnfd}:
		\end{itemize}
	pp. D:
		\begin{itemize}
			\item \textcolor{blue}{Complex Lie group}
			\item \textcolor{blue}{Complex Projective Space, $\mathbb{CP}^n$, or just $\mathbb{P}^n$}.
		\end{itemize}
	pp. E:
		\begin{itemize}
			\item \textcolor{blue}{Topology in $\mathbb{P}^n$}
			\item \textcolor{blue}{Mnfd structure on $\mathbb{P}^n$, atlas, and the \textbf{canonical covering}}
		\end{itemize}
	pp. F
		\begin{itemize}
			\item Grassmannian mnfd.
		\end{itemize}

	\subsection{Lecture 5 Submanifolds (20160308)}

	pp. A:
		\begin{itemize}
			\item Affine Hypersurface (actually this is not quite different from the usual $\mathbb{C}^n$.)
		\end{itemize}

	Part 2. \textbf{Sheaf Theory}

	pp. A:
		\begin{itemize}
			\item pre-sheaf
			\item $\mathcal{O}_X(U)$
			\item $\mathcal{O}^*_X(U)$
		\end{itemize}
	pp. B:
		\begin{itemize}
			\item $C^{\infty}$
			\item $\mathbb{\underline{Z}}$, sometimes simply denoted as $\mathbb{Z}$: sheaf of localy constant $\mathbb{Z}$-valued functions.
			\item Sheaf
		\end{itemize}
	pp. D:
		\begin{itemize}
			\item sheaf-morphisms
		\end{itemize}
	pp. E:
		\begin{itemize}
			\item Section
			\item Ker($\phi$) - sheaf of kernals.
		\end{itemize}
	pp. F:
		\begin{itemize}
			\item Im($\phi$) is a presheaf, but not a sheaf.
			\item Im($\phi$): the sheafification of Im($\phi$) above. Note that we use the same notation to denote both.
		\end{itemize}

	\subsection{Lecture 6 Sheaf \& Cohomology (20160315)}
	pp. A:
		\begin{itemize}
			\item Stalk $\mathcal{F}_x$.
			\item germ
			\item Directed partial order set
			\item Directed System
		\end{itemize}
	pp. B:
		\begin{itemize}
			\item Directed limit
		\end{itemize}
	pp. C:
	\begin{itemize}
		\item Exact Complex/ Exact Sequence.
		\item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
		\item
	\end{itemize}
	pp. D:
	\begin{itemize}
		\item Čech cohomology
	\end{itemize}
	pp. E:
	\begin{itemize}
		\item q-cochain
		\item coboundary operator. $\delta$.
		\item $Z^p(U,\mathcal{F})$ = Ker.
		\item $B^p(U,\mathcal{F})$ = Im.
		\item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
	\end{itemize}
		\subsubsection{Notes of Čech Cohomology with Coeficients in a Sheaf}
		pp.1:
		\begin{itemize}
			\item q-simplex $\sigma$.
			\item support $|\sigma|$.
			\item q-cocain
			\item $C^q(U,\mathcal{F})$
			\item Coboundary Operator $\delta$.
		\end{itemize}
		pp.2,3,4:
		\begin{itemize}
			\item Cochain Complex
			\item Čech cohomology
			\item cocycle
			\item cochain
			\item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
			\item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
		\end{itemize}

	\subsection{Lecture 7 Vector Bundle (20160321)}
	pp.1,2:
	\begin{itemize}
		\item Vector Bundle
		\item Trivializing covering, $\{(U_i,\tau_i)\}$.
		\item trivializing maps, trivializes.
		\item VB-equivalent of trivializing maps.
		\item E: total space, X: base space.
	\end{itemize}
	pp. 3,5:
	\begin{itemize}
		\item transition maps.
		\item fibre.
		\item $\mathcal{O}(-1)$
		\item cocycle condition.
		\item $\mathcal{T}_X$, Holomorphic tangent bundle.
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item s: section of a holomorphic vector bundle.
		\item $\mathcal{E}$: sheaf of sections of holomorphic vector bundle. $\mathcal{E}(U)$.
	\end{itemize}

	\subsection{Lecture 8 Almost Complex Structures (20160322)}
	pp. 1,2:
	\begin{itemize}
		\item $I$: Almost Complex Structure. $I^2=-1$. Sometime $J$ is used in place of $I$.
		\item $V_{\mathbb{C}}$ := $V\otimes \mathbb{C}$.
		\item $I_\mathbb{C}$: $I$ extending to $V_{\mathbb{C}}$. Usually abbreviated simply as $I$.
		\item $V^{1,0}$:= ker$(I+i)$.
		\item $V^{0,1}$:= ker$(I-i)$.
	\end{itemize}

	\subsection{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}

	pp.1,2:
	\begin{itemize}
		\item $V^*$: dual of $V$.
		\item $\{dx^i,dy^i\}$.
		\item $J^*$: $J$ extending to dual space.
		\item $dz^i,d\bar{z}^i$.
	\end{itemize}
	pp. 3:
	\begin{itemize}
		\item $S^k(V)$, $\Lambda^k(V)$.
		\item $s$ and $a$, symmetrization and anti-symmetrization of a tensor.
		\item $\Lambda^* V$.
	\end{itemize}
	pp. 4:
	\begin{itemize}
		\item $\Lambda^n T^*_{\mathcal{C}}X$.
		\item $\Lambda^* T^*_{\mathcal{C}}X$.
		\item $\Lambda^{p,q} T^*_{\mathcal{C}}X$.
	\end{itemize}
	pp. 5,6:
	\begin{itemize}
		\item $\mathcal{A}$: sheaf of section of cotangent bundle.
		\item $\mathcal{A}^n(U)$, $\mathcal{A}^{p,q}(U)$.
		\item $\Lambda$ on $\mathcal{A}$.
		\item $d$: de Rham differential.
		\item $\partial, \bar{\partial}$.
	\end{itemize}

	\subsection{Lecture 10 Debeault Cohomology (20160406)}

	pp. 1:
	\begin{itemize}
		\item $\mathcal{H}^{p,q}(X)$.
		\item $f^*$: pull-back. Various defintion from pp.1 to pp.4.
	\end{itemize}
	pp. 5,6,7:
	\begin{itemize}
		\item $\mathcal{A}^{p,q}(U,E):=\Gamma(U,\Lambda^{p,q}T_{\mathbb{C}}^* X \otimes E)$.
		\item $\bar{\partial}_E$
		\item $\mathcal{H}^{p,q}(X,E)$.
		\item $\bar{\partial}$-Poincaré lemma in one variable.
	\end{itemize}

	\subsection{Lecture 11 (20160412)}
	pp.1,2,3: 
	\begin{itemize}
		\item $\bar{\partial}$-Poincaré lemma in n-dimension
		\item $\Omega_X^p$: holomorphic p-forms. On pp.2.
		\item $\check{H}^q(X,\Omega^p)\text{(Čech)}\cong \mathcal{H}_{\bar{\partial}}^{p,q}(X)$(Dolbeault). On pp.3.
	\end{itemize}
	pp. 6,7:
	\begin{itemize}
		\item Analytic Subvarity.
		\item Analytic Hybersurface.
		\item Cousin's Problem.
	\end{itemize}

	\subsection{Lecture 12 Hermitan Structure on Manifold  Manifold (20160418)}
	pp. 1,2,3:
	\begin{itemize}
		\item $I$ compatible with $<-,->$.
		\item $\omega$: Fundamental form associated with $<,>$ and $I$. $\omega(v,w):= <I(v),w>$.
		\item Conformal Equivalence.
		\item $<,>$: Hermitian Inner Product.
	\end{itemize}
	pp. 4:
	\begin{itemize}
		\item $( , )$: s.t. $(v,w):=<v,w>-i\omega(v,w) = <v,w> - i <I(v),w>$
	\end{itemize}
	pp. 5:
	\begin{itemize}
		\item $<,>_{\mathbb{C}}$ be s.t.$<v\otimes \alpha, w\otimes \beta>:= \alpha \bar{\beta} <v,w>$.
	\end{itemize}
	pp. 6:
	\begin{itemize}
		\item $\frac{1}{2}(,) = <,>_{\mathbb{C}} \arrowvert_{V^{1,0}}$
	\end{itemize}
	pp. 7,8:
	\begin{itemize}
		\item Local computations: $z_i$,$h_{ij}$,
		\item $\omega = (...dx^i...dy^i)$
		\item $\omega$, Fundamental form on Riemannian Mnfd.
		\item Kähler mnfd: $d\omega \equiv 0$.
	\end{itemize}

	\subsection{Lecture 13 Kähler Manifold (20160419)}
	pp.1:
	\begin{itemize}
		\item Local computation: $\omega = (...dz^i...d\bar{z}^i)$
	\end{itemize}
	pp.4:
	\begin{itemize}
		\item Fubini-Study Metric on $\mathbb{CP}^n$.
	\end{itemize}

	\subsection{Lecture 14 Hodge Theory (20160425)}
	pp.1:
	\begin{itemize}
		\item $<,>$ on $\Lambda^k V$
		\item vol: volumn element.
		\item $*$: Hodge Star Operator.
	\end{itemize}
	pp.4:
	\begin{itemize}
		\item $L$: Lefschetz Operator
		\item $\Lambda$: adjoint of $L$. $\Lambda = *^{-1}\circ L\circ *$.
	\end{itemize}
	pp.5 :
	\begin{itemize}
		\item $*,L,\Lambda$ on Kähler mnfd.
		\item $d^*:= (-1)^{m*(k+1)+1}*\circ d\circ*$, adjoint of $d$. On a Kähler mnfd, $d^*= -*\circ d\circ*$
		\item $\Delta:=d^*\circ d + d\circ d^*$.
	\end{itemize}
	pp. 6:
	\begin{itemize}
		\item $\bar{\partial}^*, \partial^*$: Similar to the above for $d$.
		\item $\Delta_\partial, \Delta_{\bar{\partial}}$: Similar to the above for $d$.
	\end{itemize}

	\subsection{Lecture 15 Hodge Theory on Manifold (20160426)}
	pp.1:
	\begin{itemize}
		\item $(,)$ on $\mathcal{A}^*(X)$. $(\alpha,\beta):=\int_X g_\mathbb{C}(\alpha,\beta) vol$
	\end{itemize}
	pp.3:
	\begin{itemize}
		\item $\mathcal{H}^k(X,g)$: d-harmonic forms. Sometimes we replace $\mathcal{H}$ with $\mathscr{H}$ for harmonic forms, so is for symbols below.
		\item $\mathcal{H}^k_{\bar{\partial}}(X,g)$: $\bar{\partial}$-harmonic forms. 
		(Be careful to distinguish this with Dolbeault Cohomology groups).
		\item $\mathcal{H}^k_{\partial}(X,g)$: $\partial$-harmonic forms.
	\end{itemize}
	pp. 5:
	\begin{itemize}
		\item $\mathcal{H}^k_d(X,g) \cong \mathcal{H}^{2n-k}_d(X,g)$, Poincar\'{e} duality
		\item $\mathcal{H}^{p,q}_{\bar{\partial}}(X,g) \cong 
		\left( \mathcal{H}^{n-p,n-q}_{\bar{\partial}}(X,g)\right)^*$, both are harmonic forms, called Serre Duality. 
	\end{itemize}
	pp. 6,7:
	\begin{itemize}
		\item 
		$\mathcal{A}^{p,q} = 
		\bar{\partial}\mathcal{A}^{p,q-1}(X)\oplus
		\bar{\partial}^* \mathcal{A}^{p,q+1}(X) \oplus
		\mathcal{H}^{p,q}_{\bar{\partial}}(X,g)$:

		 Hodge decomposition

		\item $\mathcal{H}^{p,q}_{\bar{\partial}}
			\text{(harmonic forms)}
			\cong
			\mathcal{H}^{p,q}_{\bar{\partial}}(X)
			\text{(Dolbeault Cohomology group)}$
		\item $\mathcal{H}^{p,q}_{d}
			\text{(harmonic forms)}
			\cong
			\mathcal{H}^{p,q}_{dR}(X)
			\text{(de Rham Cohomology group)}$
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item A lot of isomorphisms between \textit{de Rham}, \textit{Dolbeault} and \textit{harmonic forms}.
	\end{itemize}

	\subsection{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}

	pp.1:
	\begin{itemize}
		\item $\Delta_\partial = \Delta_{\bar{\partial}} = 
			\frac{1}{2}\Delta_d$, for K\"{a}hler mnfd.
	\end{itemize}

	\subsection{Lecture 17 Hermitian Vector Bundle (20160510)}
	pp.1,3:
	\begin{itemize}
		\item Hermitian Vector Bundle. pp.1
		\item Antilinear map. pp.3.
		\item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
		\item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
		\item $\bar{\partial}_E^*$
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item Kadaira-Serre Duality.
	\end{itemize}

	\subsection{Lecture 18 Connection (20160516)}
	\begin{itemize}
		\item $\bigtriangledown$: connection. pp.1.
		\item Trivial connections. pp.2
		\item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
		\item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
		\item $\Delta = d+A$. pp.4.
		\item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
		\item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
		\item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
	\end{itemize}

	\subsection{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
	\begin{itemize}
		\item Holomorphic Connecction. pp.1.
		\item $At(E)$: Atiyah class of $E$. pp.2.
		\item $\Delta^k$. pp.4.
		\item $F_\Delta$: curvature associated with $\Delta$. pp.5.
		\item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
		\item First Chern class of complex line bundle.
	\end{itemize}

	\subsection{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
	\begin{itemize}
		\item Analytic Subvariety. pp.1.
		\item Regular/Smooth Point. pp.1.
		\item Singular Point. pp.2.
		\item Irreducible analytic subvariety. pp.2.
		\item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
		\item Affine algebraic varieties. pp.3.
		\item Projective algebraic varieties. pp.3.
		\item Hypersurface. pp.4.
		\item Divisor, $Div(X)$:=group of all divisors. pp.5.
		\item Effective divisor. pp.6.
		\item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
		\item Meromorphic function on complex mnfd.
		\item $(f)$: divisor given by a global meromorphic function.
		\item Principal divisor. pp.8.
	\end{itemize}

	\subsection{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
	\begin{itemize}
		\item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
		\item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
		\item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
		\item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
		\item Linear equivalent of divisors.
		\item $*$: used only in this section to denoted the map:
		$$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
		pp.6.
		\item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
	\end{itemize}

	\subsection{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
	\begin{itemize}
		\item Base point of a line bundle. pp.4.
		\item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
		\item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
	\end{itemize}

\begin{thebibliography}{1}

	\bibitem{blog} Complex Geometry

\end{thebibliography}
\end{document}

### 2016-07-06 Useful (anit)Commutative relationships.tex
Initial drafts.

\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters

\title{Useful (anti)Commutation Relation}
\date{\today}
\author{\begin{CJK}{UTF8}{gbsn}
陈鸿翔
\end{CJK}(Taper)}

\begin{document}

\maketitle

\abstract{
none
}

\tableofcontents

\section{General}
\begin{align}
[A,B]:=AB-BA \\
\{A,B\}:=AB+BA\\
[AB,C] &= A [B,C] + [A,C]B\\
		&= A\{B,C\} - \{A,C\} B\\
[C,AB] &= -[AB,C]\\
		&=A [C,B] + [C,A]B \\
       &=\{C,A\} B - A\{C,B\}
\end{align}

\section{2nd Quantization}

\subsection{Boson}

\begin{align}
n_{\alpha} := a_{\alpha}^{\dagger}a_{\alpha}\\
[a_{\alpha},a_{\beta}]=[a^{\dagger}_{\alpha},a^{\dagger}_{\beta}]=0\\
[a_{\alpha},a^{\dagger}_{\beta}]=\delta_{\alpha\beta}
\end{align}

\subsection{Fermion}
\begin{align}
n_{\alpha} := c_{\alpha}^{\dagger}c_{\alpha}\\
\{c_{\alpha},c_{\beta}\} = \{c_{\alpha}^{\dagger},c_{\beta}^{\dagger}\} = 0\\
\{c_{\alpha},c^{\dagger}_{\beta}\}=\delta_{\alpha\beta} \\
\{n_{\alpha},c_{\alpha}\} = c_{\alpha} \\
\{n_{\alpha},c^{\dagger}_{\alpha}\} = c^{\dagger}_{\alpha}
\end{align}

\begin{thebibliography}{1}
	\bibitem
	{wiki:Matrix} Wikipedia contributors, "Matrix mechanics," 
	Wikipedia, The Free Encyclopedia, 
	\url{https://en.wikipedia.org/wiki/Matrix_mechanics}
	(accessed July 2, 2015).
	\bibitem
	{Green} Green, H.S. 1965. Matrix Mechanics. Groningen, 
	The Netherlands: P. Noordhoff Ltd.
	\bibitem{Wrong}
	H. Fritzsch. You Are Wrong, Mr Einstein! World Scientific Publishing Company.
	\bibitem{Griff}
	D.J Griffiths. Introduction to Quantum Mechanics, 3rd edition.
	Pearson Prentice Hall.
	\bibitem{S-L_theory}
	Sturm-Liouville theory. Encyclopedia of Mathematics. 
	\url{http://www.encyclopediaofmath.org/index.php?title=Sturm-Liouville_theory&oldid=23061}
	(Accessed July 14, 2015)
\end{thebibliography}
\end{document}

### 2016-07-06 draft.tex
Initial drafts.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters
%\usepackage{ dsfont } % For double struck fonts
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\title{Topological Insulators and Topological Superconductors}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    This is a draft.
}
\tableofcontents

\section{Lectures on the Frontiers of Physics}
\textbf{Given by professor of physics in SUSTC}
    \subsection{By JQ. He.}
    \textbf{Thermal electrics}

    \subsection{By Lang. Chen}
    \label{sec:c.l}
    Grow thin films.
    \begin{itemize}
	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
	\item 
	orbital contral of electrons -> 
	orbitronics -> Control of Spin orbital coupling.
	\item
	Multiferroics -> multiple order parameters, and the interaction
	between them. E.g. $BiFeO_3$.
	\item
	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
	symmetries simultaneous broken.
	\item
	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
	exactly in theoretical physics?
	\item
	$H_2S$: 200K superconductor?
	\item
	The Double Exchange effect of oxygem -> Half-metal, phase transition.
    \end{itemize}

    \subsection{By Alan}
    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
    the keys.

    \subsection{By Li, Huang}
    \begin{itemize}
            \item Computational Physics
            \item Surface Dynamics
            \item Structural factor from 2D to 3D.
            \item Finding Order Amid the Chaos. amorphous -> spatially
                    resolved distributed function.
            \item ?: What is genetically algorithm.
    \end{itemize}
    \textbf{Computational and theoretical studies of Surface dynamics}

    \begin{itemize}
            \item Surface atoms is immersed in a very different environment
                    compared with the bulk atoms.
            \item First-principle calculations
            \item DFT + LDA -> Conser equation
            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
                    Conser equation
            \item Continumm method ?
    \end{itemize}

    \subsection{By Junfen, Liu}
    \begin{itemize}
            \item electronic transport in mesoscopic systems:
            \item Spintronics
            \item Graphene eletronics
            \item Superconductors etc.
    \end{itemize}
    \textbf{Quantum wire conductiing}
    The conduction channel in quantum wire is quantized, with discrete value
    of conductance.
    \begin{itemize}
            \item $\lambda_F$ Fermi wavelength
            \item $L_m$ Momuntum relaxation length <-- impurities.
            \item $L_\phi$ Phase relaxation length <-- memory of phase,
                    related to energy $\omega = E/\hbar$.
            \item $L$ Sample length
    \end{itemize}
    \begin{itemize}
            \item Ballistic transport: $L << L_m$ No scattering.
            \item Diffusive $L>L_m$, scattering, reduced transmission.
            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
            \item Classical. (Omitted)
    \end{itemize}
    \textbf{Conductance}
    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
    accounting for the back scattering, perhaps the transmission
    probability.
    In reality, $G=\sum_{\text{Different channels}}G_i$,

    We can turn the $G$ into resisivity: 
    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
    $R+T=1$

    \paragraph{Resonate Transmission} (Omitted)

    \paragraph{Spintronics} Use the extra freedom of Spin.

    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)

    GMR: 2007 Nobel prize in Physics.

    Hall Effect (Omitted)
    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);

    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)

    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
    \textbf{Klein Paradox}

    \paragraph{Josephson Junction} A phase difference could conduct
    electricity in Superconductors.

    \subsection{By Haizhou, Lu}
    \paragraph{Quantum Anomalous Hall Effect}
    Requires strong magnetic field: $\approx 10$ Tesla.

    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
    where $M$ is the magnetic susceptibility.
    Two-factors: SO coupling. Spin-dependent Hall Effect.

    An excellent illustrations is found in \cite{Arxiv-Xiao}:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/1}
        \caption{Illustration}
        \label{fig:Xiao Illustration}
    \end{figure}

    \subsection{By Kedong Wang}
    Tunneling current $I\propto V e^{-2kz}$, where 
    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
    $I$ is very sensitive to the distance $z$.

    \paragraph{Work function} $\phi$ characterize the obstruction
    that prevents electron from escaping the sample.

\section{Problems in Bernevig's Topological ...}

    \subsection{Chapter 2}
    \paragraph{Non-Abelian Berry Transport}
    Derive Berry curvature to the adiabatic transport of a degenerate
    multiplet of states separated by a gap from the excited states.
    (Cautious about rotation within degenerate states).

    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$

    Approach:
    Assuming that the those degenerate states are labeled by $1\cdots N$. 
    Thus we have naturally:
	\begin{align}
            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
        \phi = \sum_n A_n \psi_n
    \end{align}

    Then we have:
    \begin{align}
    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
	\sum_n E A_n \psi_n&=i\hbar\sum_n
		\left(
		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
		\right) \nonumber\\
	E A_m &=i\hbar
		\frac{\partial A_m(t)}{\partial t}
		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
    \end{align}
    Put in another form:
    $$
    \sum_n \left(\delta^n_m E
        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
        =
    i\hbar \frac{\partial A_m(t)}{\partial t}
    $$
    In matrix form:
    \begin{align}
            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
    \end{align}
    where:
    \begin{align}
        E &= \left(
        \begin{array}{ccc}
         \cdots   &     &   \\
              & E &   \\
             &    & \text{...} \\
        \end{array}
        \right) \\
        P &= (P^m_n) = \left(
        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
        A &= \left(\begin{array}{c}
            A_1(t) \\
            A_2(t) \\
            \cdots \\
        \end{array}\right)
    \end{align}

    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.

    Notice that
    \begin{align}
            0= \frac{\partial}{\partial t} \braket{m|n} &=
        \braket{\frac{\partial}{\partial t}m|n} +
        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
    \end{align}
    temporary mathematica code:

% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
%         {y1[x], y2[x]}, x]
% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]

\section{Miscellnaneous Notes}
    \subsection{Super conductor}
    Mean-field approach to deal with a four operator diagonalization.

    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:

    	$$ \delta^2 \approx 0 $$
    i.e.:

    \begin{align}
    	( (CD)^* - avg ) ( CD - avg ) = 0\\
    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
    \end{align}
    Hence a four operator is reduced into a few of two operators.
    Such method could be naturally extended to treat the operator
    $\sum_{i,j} D^*_i C^*_i C_j D_j$.

    A copper pair has the energy of:
    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$

    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$

    This will require an additional enegy of $2\Delta$.

    The exact meaning of "equivalent to" is as follows:
    \begin{align}
        & \text{break a copper pair} \longrightarrow 
        \text{scatter two electrons consecutively} 
        \nonumber\\ & \longrightarrow 
        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
    \end{align}

    \subsection{Why 0/0 is undefined?}
    If we suppose
    $$ \frac{0}{0}= \triangle $$
    Consider the following derivation:
    \begin{align}
	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
	    0 \cdot \frac{1}{0} &= \triangle\\
	    \Rightarrow \triangle &= 0
    \end{align}
    This is already bad enough. And we are forced to define $\frac{1}{0}$.
    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
    This is disastrous.

    Alternatively, we could let
    \begin{enumerate}
	    \item Let $\frac{1}{0}$ be undefined.
	    \item Or let $\frac{1}{0} =
		    \infty$.
	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
		    true when $b=0$.
    \end{enumerate}
    The third idea is disastrous for algebraic manipulation. \footnote{
    Or more speicifically, it is a disaster for field theory.
    }
    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
    out to be very useful in both mathematics and physics. Actully, in
    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
    any nonzero number $a$, where the sign of $\infty$ is determined by 
    the sign of $a$.
    The second idea is okey. But then we are faced with a serious problem.
    We have to define $\triangle \equiv 0 \cdot \infty$

    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?

    \subsection{Preface of BSCS}
        \label{sec:Preface_of_Bosonization_and_Strongly 
        Correlated_Systems}
    BSCS: see \cite{BSCS}.
    Parallism between theories in condensed matter physics and those in
    particle physics.
    \begin{itemize}
            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
                    (C.M.P.)
            \item 'inflation' in Cosmology, first order phase transition
            \item 'cosmic strings', magnetic field vortex lines in type
                    II superconductors
            \item Hadron-meson interaction, Ginzburg-Landau theory of
                    superfluid $He^3$.
    \end{itemize}
    Same ideas on different space-time scales, different hierachical
    'layers'.
    Strong parallism: \textbf{strongly correlated low dimensional system}

    E.g.:

    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.

    Approaches:
    \begin{enumerate}
            \item Exact solutions
            \item Reformulate complicated interacting models in such a way
                    that they become weekly interacting. -> Bosonization.

                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
                    Model of interacting

                    fermions.
                    (Jordan and Wigner, 1928)
    \end{enumerate}
    Bosonization: transformation from fermions to a scalar massless bosonic
    field.

    \subsection{System of Differential Equations}
    This is a small note of \cite{DETA}.

    pp. 266.

    \begin{defi}
        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
    \end{defi}

    pp. 291.

    \begin{thm}[Existence-uniqueness theorem]
        There exists one, and only one, solution of the initial-value
        problem

        \begin{align}
            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
                \mathbf{x}(t_0) = \mathbf{x}^0 = 
                \left(
                \begin{array}{c}
		            x^0_1\\
                    x^0_2\\
                    \cdots
                \end{array} 
                    \right)
        \end{align}

        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
    \end{thm}
    \begin{remark}
        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
        time $t$. Also notice that the elements of $\mathbf{A}$ are just
        numbers.
    \end{remark}

    \begin{thm}
        The dimension of the space $\mathbf{V}$ of all solutions of the
        homogeneous linear system of differential equations:
        \begin{align}
            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
        \end{align}
        is $n$, i.e. the dimension of vector $\mathbf{x}$.
    \end{thm} 
    \subsection{ODE by Arnold}
    sec. 14
    \begin{defi}
        \begin{align}
            \label{eq:e^A}
            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
            \text{or}& \nonumber \\
            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
        \end{align}
        where $I$ is the identity matrix.
    \end{defi}
    Equivalance of the two definition will be addressed in the Theorem on
    pp. 165.

    Important theorems:
    \begin{thm}[pp. 158]
        The series $e^A$ converges for any $A$ uniformly on each set
        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
    \end{thm}
    \begin{thm}[pp. 160]
        $$e^{At} = H^t$$
        where $H^t$ is the translation operator which sends every polynomial
        $p(x)$ into $p(x+t)$.
    \end{thm}
    \begin{thm}[pp. 163]
        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
    \end{thm}
    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
        Constant Coefficients]
        The solution of:
        \begin{align}
            \label{eq:fund_thm_of_linear_eqs_const_coef}
            \dot{\mathbf{x}} = A\mathbf{x}
        \end{align}
        with initial condition $\phi(0) = \mathbf{x}_0$ is
        \begin{align}
            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
        \end{align}
    \end{thm}

    Practically solution to
    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
    (pp. 173, Sec 17)
    (Assuming $A$ is diagonalizable.)
    \begin{itemize}
        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
        \item Expand the initial condition in the new basis.
            \begin{align}
                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
            \end{align}
        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
    \end{itemize}
    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}

    \begin{align}
        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
            (\eta_b,U_{ac}\dot{\psi}_c
    \end{align}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\end{document}

### 2016-07-08 Photosynthesis Course Note.tex
Adding notes for Q.S.M., and Photosynthesis course. Adding content index for readme file.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters
%\usepackage{ dsfont } % For double struck fonts
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\title{Photosynthesis Course Note}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle

\tableofcontents

\section{8th, July}
\label{sec:8th_July}
\paragraph{pp.2 of PPT}
In the last lecture, the \textit{master equation} for density matrix
\footnote{Reference not found.}
could lead to problematic result. As the density matrix propagates
as described by the master equation, the eigenvalues for it might
involved into negative values. This is because the added terms
are not rigorously derived, but just an approximation.

\textbf{Digression}:  PRE 65 056120, something about entanglement between
oscillators.

\paragraph{pp.3 of PPT}
\textbf{Lindblad equations} This equation ensures that the
density matrix $\rho \geq 0$ (i.e. having all positive
eigenvalues). However, this operator sometimes breaks down
the symmetries of the system. That is, a system started with
translation symmetry at $t_0$ might not have translation
symmetry at $t > t_0$.

An Example for Lindblad equation:

Considering the case of a harmonic oscillator.
$$ H = w_0 a^\dagger a $$
If we add interaction of oscillator and other excitons:
$$ A^\dagger A (a^\dagger + a) = \text{extra} + \text{bath}$$
Then $A^\dagger A$ is $V_m$ in ppt.

\paragraph{Digression} Two Spin system. One way to judge
whether the two particles are entangled or not, is to do partial
transpose: transposing only part of the density
matrix corresponding to only one particle of the system.

\paragraph{Energy Transfer}

\textbf{Note}: This section's materail could be found in
\textit{Excitonic energy transfer in light-harvesting complexes 
in purple bacteria. JChemPhys\_136\_245104.pdf}

% TODO what is exciton?
\paragraph{pp.5 of PPT}
Exciton transport process. External
influence to the system includes trapping, decaying and disspation.

The $k_t$ characterizes the trapping rate. And $k_d$ characterizes
the decay rate.

\paragraph{pp.6 of PPT}
Life time $\tau_n = \int_0^\infty \rho(t)_n dt$, where
$\rho_n \equiv \rho_{nn}$. We hope the $\braket{t} = \sum \tau_n$
to be small, because the shorter an exciton is fixed on a state,
the more random the system is and the more likely that the exciton
is trapped.

Quantum yeild $q= \text{On PPT} 
            = \frac{\text{trapped}}{\text{trapp} + \text{died}}$.

\paragraph{pp.8 of PPT}
Showcase of calculating the $\rho(t)$ using the Haken-Strobl model
A simple Ring.
% TODO try to calculate the example.

\paragraph{pp.9 of PPT}
Complex models with more and more elements in the ring.

\paragraph{pp.10 of PPT}
\footnote{Could be found on \textit{Efficient energy transfer in 
light-harvesting systems. Cao and Silbey et al New J Phys (2010)}}
The 16 sites ring shows that there is always 
a peek in the opposite site(See upper-left plot). This is
because there is always
two channels of equal length for it to get to the opposite side.

\paragraph{pp.11 of PPT}
A two ring case, with 8 sites on each ring. The initial configuration
is evenly excited in the left ring. The right ring comprised of
trapping sites.

\paragraph{pp.12 of PPT}
Another two ring case, with a change in the right ring's number
of trapping sites. It shows that a asymmetric design would somehow
imporve the efficiency, since the right side plot has a maximum region.

\paragraph{pp.15 of PPT}

Start with a reduced single-electron density matrix. Consider an
external interruption caused by Laser, and apply the 
\textit{Principle of the nearsightedness of equilibrium systems} to
reduce the computation difficulties. This principle is related 
R.P.A. in condensed matter physics.

\textbf{Caution:} I am quite confused by the following content,
from pp.16 to the end of PPT. Erogo the
following notes are note well organized. It is advised that one should
look at the original paper
\paragraph{pp.16 of PPT}
\footnote{
\url{http://journals.aps.org/pre/pdf/10.1103/PhysRevE.69.032902}} 
instead.

% TODO unclear picture about this slide.
Calculating the absorption spectrum, with the result that only one level
is acceptable.
$A\propto amplitude$ characterize the behavior of laser input. 
$M_{mn}:$ the angle between oscillation angles.

\paragraph{pp.17 of PPT}
Changing the bahavior of lasers could result (in generally) more
different acceptable levels. However, the laser configuration
is not practical.

\paragraph{pp.19 of PPT}
Using Frankel-Exciton Model and find very good fit, balabala.
% TODO transition dipole, dimerization.

\end{document}

### 2016-07-08 draft.tex
Adding notes for Q.S.M., and Photosynthesis course. Adding content index for readme file.

@@
 
-\title{Topological Insulators and Topological Superconductors}
+\title{Draft}
 \date{\today}
@@
     that prevents electron from escaping the sample.
+
+    \subsection{By Mingyuan Hunag}
+    Too boring.
+
+    \subsection{By Wenkang Wong}
+    \paragraph{Non-clone Theorem} We can easily see that there is no universal
+    copy operators in Quantum Mechanics.
+
+    \begin{proof}
+    We proove it by contradiction. Let $U$ be the copy operator. By definition,
+    we have
+    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
+    For any $\ket{\psi}$.
+    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
+    \begin{align*}
+        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
+        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
+        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
+    \end{align*}
+    This is a contradiction.
+    \end{proof}
+    \begin{remark}
+        We assume that the copyer is universal. This might seems to be too
+        strong. However, if we assume that the copyer only
+        works for certain states $\ket{\phi}$, then with the knowledge
+        of these certain states, we could in principle create an exact copy
+        of these states. This copy ,in the sense of another instance of the
+        same object, of original state should not be considered to be an
+        copied version of the original state.
+    \end{remark}
 
@@
     \end{align}
+    \subsection{Quantum Statistical Mechanics}
+    \label{sec:Quantum Statistical Mechanics}
+    \begin{defi}[Time Evolution Operator]
+        The time evolution operator $U(t,t_0)$ is defined such that
+        \begin{align}
+            \label{eq:def_time_evo_op}
+            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
+        \end{align}
+    \end{defi}
+    It satisfy the relationship:
+    \begin{align}
+        \label{eq:def_time_evo_op 2}
+        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
+    \end{align}
+    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
+    Equations.
+
+    \paragraph{Quantum Macrostates}
+    Macrostates of the system depend on only a few the thermodynamic
+    functions. We can form an ensemble of a large number $\mathcal{N}$ of
+    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
+    The different microstates occur with probability $p_\alpha$.
+    When wen no longer have exact knowledge of the microstate of a
+    system the system is said to be in a \textit{mixed state}.
+    The ensemble average of the quantum mechanical expectation
+    value is given by:
+    \begin{align}
+        \label{eq:quantum_macrostates_ensemble_avg}
+        \bar{\braket{O}} &= 
+            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
+            = \sum_{\alpha,m,n} p_\alpha
+                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
+                \nonumber\\
+            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
+                = \text{tr}(\rho O)
+    \end{align}
+    where we have introduced the density matrix:
+    \begin{defi}[Density Matrix]
+        The density matrix $\rho(t)$ is defined as
+        \begin{align}
+            \label{eq:density_matrix_def}
+        \braket{n|\rho(t)|m} \equiv
+        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
+        \end{align}
+        or
+        \begin{align}
+            \label{eq:density_matrix_def_2}
+            \rho(t) \equiv \sum_\alpha p_\alpha
+                \ket{\psi_\alpha}\bra{\psi_\alpha}
+        \end{align}
+    \end{defi}
+    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
+    P.D.F, since $\rho$ often represents density.
+
+    Density matrix satisfies several good properties:
+    \begin{itemize}
+        \item Normalized
+        \item Hermiticity
+        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
+    \end{itemize}
 \section{Anchor}
@@
     \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
+    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
 \end{thebibliography}

### 2016-07-08 feynman diagram/Feynman_diagram.tex
Adding notes for Q.S.M., and Photosynthesis course. Adding content index for readme file.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

\title{%
	Feynman Diagram \\
	\large Part I - Interaction Picture}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
In this article, we introduces the basic Interaction Picture in quantum mechanics, then introduce the idea of "adiabatic turn on", which is supported by Gell-Mann and Low theorem (proved in appendix).

% Next we define the Green function and provide three reasons for studying Green functions. Finally, we provide a few remarks on other types of Green functions, and on how Green functions, combined with Wick's theorem, lead to the development of Feynman Diagrams.

\end{abstract}

\section{Note}
This note is intended for learning Feynman Diagram techniques in many-body physics. However, due to the limited time and the growing size of this document, I have to split it into small parts. This first part provides one foundational material for the beginning of Feynman Diagrams, i.e. Interaction Picture of quantum mechanics. Further updates will be found on my blog\cite{blog} within this summer vocation.

The style of the article might be fastidious. Yet I have try to maintain some physical viewpoints. Also, I will provide readers with reference to original materials whenever possible.

\section{Natural Units}

For convenience, I will use the unit system s.t. $\hbar=1$. An example of such unit systems is Plank units. 
\footnote{Readers could refer to \cite{wiki:Plank_units} for details.} Usually, calculation down in such unit systems are carried out mathematically first, then those normalized (being set to $1$) units, such as $\hbar$ here, are inserted back to the equations by dimensional analysis. For example, in this article when one sees the imaginary unit $i$, one should replace it with $\frac{i}{\hbar}$ or sometimes $i\hbar$ to get back to S.I. units.

\section{Interaction Picture}

The Interaction Picture
    \footnote{This part follows much of section 6 of \cite{fetter}. Similar material could also be found on section 2.1 of \cite{mahan}.}
is a very important way to view physical systems as interacting systems growing from the underlying ground state systems. In Interaction Picture,
both the wave functions and the operators are time dependent. The Hamiltonian is separated into the ground state part and the interaction part:
	$$H=H_0+V$$
where
	\begin{itemize}
		\item 		$H_0:$
		is taken to be an exactly solvable Hamiltonian. Note that $H_0$ should be bilinear in $C^{\dagger}\text{ and } C$ for Wick's theoren to be applicable.
		\footnote{See page 79, Sec 2.4 of \cite{mahan}}
	\end{itemize}

The operators and states are related to Schrödinger's Picture by

\begin{align}
	\ket{\Psi_I} &=  e^{iH_0t} \ket{\Psi_s}= e^{iH_0t}e^{-iHt} \ket{ \Psi_H} \label{eq:def_Psi}  	\\
	\hat{O}_1 &= e^{iH_0t}\hat{O}_Se^{-iH_0t}
\end{align}

where subscripts denoting:
	\begin{itemize}
		\item 		I:Interaction Picture
		\item		S: Schrödinger Picture
		\item		H: Heisenberg Picture
	\end{itemize}

Remark: we see that the "inner product" value is unaltered by this:
	$$\braket{\Psi_I|\hat{O}_S|\Psi_S} 
	= \braket{\Psi_S|e^{-iH_0t} \cdot (e^{iH_0t}\Hat{O}e^{-iH_0t}) \cdot e^{iH_0t}|\Psi_S }
	=\braket{\Psi_S|\Hat{O}_S|\Psi_S}$$
Physically, this leaves the probabilities (the only important value) unchanged.

The evolution of states is governed by equation of motion. In Schrödinger Picture, it is the Schrödinger's equation. In Interaction Picture, we will mainly deal the evolution operator.

	\subsection{Equation of Motion for Observables}

	Before we talk about evolution operator, we mention two useful results. The first is a equation of motion for observables in Interaction Picture.

	Since: $\hat{O}_I(t) = e^{i\hat{H_0}t}\hat{O}_S e^{-i\hat{H}_0t}$, we have:
	\begin{align}
		& i\cdot \frac{\partial \hat{O}_I(t)}{\partial t}\nonumber\\
		&= i\left[  i\hat{H}_0 e^{i\hat{H_0}t} \hat{O}_S e^{-i\hat{H_0}t}] + e^{i\hat{H_0}t} \hat{O}_S(-i\hat{H}_0) e^{-i\hat{H_0}t} \right]\nonumber\\
		&= -\hat{H}_0 (e^{i\hat{H_0}t} \hat{O}_S e^{-i\hat{H_0}t})
			+ e^{i\hat{H_0}t}\hat{O}_Se^{-i\hat{H_0}t} \hat{H}_0 \nonumber\\
		&= [\hat{O}_I(t),\hat{H}_0]
	\end{align}
	This looks very similar to the Heisenberg's equation, which is reasonable since in both pictures the operators is time-dependent.

	\subsection{Equation of Motion for wave function}

	Another important result is the following equation:

	\begin{align}
	i \frac{\partial}{\partial t} \ket{\Psi_I(t)} 
	=& i \frac{\partial}{\partial t} (e^{i\hat{H}_0t} \ket{\Psi_S(t)})
	\\
	=& i (i\hat{H}_0)\cdot \ket{\Psi_I(t)} + e^{i\hat{H}_0t} \cdot \frac{\partial}{\partial t} \ket{\Psi_S(t)}
	\\
	=& -\hat{H}_0 \ket{\Psi_I(t)} + e^{i\hat{H}_0t} (H_0+V) \ket{\Psi_S(t)}
	\\
	=& [-\hat{H}_0 + e^{iH_0t} (\hat{H}_0 +V) e^{-i\hat{H}_0t}] \ket{\Psi_I(t)}
	\\
	\label{eq:motion} =& \hat{V}_I \ket{\Psi_I(t)}		
	\end{align}

	However, in Interaction Picture, there is one operator which is even more important than the above equations. It is the evolution operator to be defined below.

	\subsection{The evolution operator in Interaction picture}

	\textbf{Note:} From now on, we work mostly in Interaction Picture. Hence the subscript $I$ will be neglected, when it is convenient, for operators or states in Interaction Picture.

	The evolution operator $\hat{U}(t,t_0)$ is defined s.t. 
	\begin{align}\ket{\Psi(t)}= \hat{U}(t,t_0) \ket{\Psi (t_0)}\end{align}

	We observe that $\hat{U}$ behaves just like the time-evolution operator in Schrödinger Picture: it brings a state at time $t_0$ to a later time $t$. For finite time, it can be given a formal expression as follows:

	By \fref{eq:def_Psi} we have
	\begin{align}
    	\ket{\Psi_I(t)} &= e^{iH_0t} \ket{\Psi_S(t)}
    	\\
    	&= e^{iH_0t}\cdot e^{iH(t-t_0)} \ket{\Psi_S(t_0)} &\text{    (by Schrödinger equation)}
    	\\
    	&= e^{iH_0t}\cdot e^{-iH(t-t_0)} \cdot e^{iH_0t_0} \ket{\Psi_I(t_0)} &\text{   (by \ref{eq:def_Psi})}
	\end{align}	
	so:
	\begin{align}\hat{U}(t,t_0)= e^{iH_0t} e^{-iH(t-t_0)} e^{iH_0t_0}\end{align}

	The evolution operator has following properties:

	\begin{enumerate}
		\item	$\hat{U}(t_0,t_0)=1$
		Physically, this means that a state is not evolving.

		\item	$\hat{U}(t_2,t_1) \hat{U}(t_1,t_0) =\hat{U}(t_2,t_0):$

    	Physically, an evolving state should obviously be continuous in time, hence this property. It can also be demonstrated mathematically:
    	\begin{align}
        	\hat{U}(t_0,t_1) \hat{U}(t_1,t_0) =& e^{iH_0t_2} e^{-iH(t_2-t_1)} e^{-iH_0t_1} 
        	\cdot  e^{iH_0t_1} e^{-iH(t_1-t_0)} e^{-iH_0t_0} 
        	\nonumber\\
        	=&  e^{iH_0t_2} e^{-iH(t_2-t_0)} e^{-iH_0t_0} \nonumber
    	\end{align}

		\item $\hat{U}(t,t_0) \cdot \hat{U}(t_0,t) = 1$
		This is a result of 2.

		\item $\hat{U}(t,t_0)$ is unitary:
		Because $U(t,t_0)$ is a transformation of basis that brings all basis at time $t_0$ to time $t$.

		Also, one can easily see that mathematically: $\hat{U}(t,t_0) \cdot \hat{U}^{\dagger}(t,t_0) = 1$

		\item  $U^{-1}(t,t_0) = U^{\dagger}(t,t_0) = U(t_0,t)$
		This means that "inverse" = "dagger" for $\hat{U}$. This is result of 4.
	\end{enumerate}

	\subsection{Perturbative Solution for the evolution operator}

	The operator $\hat{U}$ has another more useful form which is the basis for perturbative analysis of complex interacting systems. To obtain such form, we first derive an integral equation for $\hat{U}$
	By \fref{eq:motion}:
	\begin{align}
		&&	i\frac{\partial}{\partial t} \cdot \hat{U}(t,t_0) \ket{\Psi_I(t_0)} &= (\hat{V})_I \hat{U}(t,t_0) \ket{\Psi_I(t_0)} 
		\\
		\rightarrow& 	&i\frac{\partial}{\partial t} \hat{U}(t,t_0) &= -i \hat{V}_I U(t,t_0)
		\\
		\rightarrow& 	&\hat{U}(t,t_0) - \hat{U}(t_0,t_0) &= -i \cdot \int_{t_0}^{t}\hat{V_I} U(t,t_0) dt
		\\
		or&		
		\label{eq:int_eq_4U} &\hat{U}(t,t_0) &= 1- i \int_{t_0}^{t} \hat{V_I} U(t_1,t_0) dt_1		
	\end{align}

	The integral equation is solved by an iterative method.
	% \marginpar{(5.7.6) of Sakurai P356 = (2.18) of Makan P68}
	We first start with a primitive guess:
	$$\hat{U}^{(1)}(t,t_0) = 1- \int_{t_0}^{t} \hat{V}(t')dt'$$

	Here, $\hat{U}^{(1)}$ is the first order solution.

	Then one improves on this with
	\begin{align}
		\hat{U}^{(2)} (t,t_0) =& 1- \int_{t_0}^{t} \hat{V}(t') \hat{U}^{(1)}(t',t_0) dt'
		\\
		=& 1- \int_{t_0}^{t} \hat{V}(t_2)  (1-\int_{t_0}^{t_2} \hat{V}(t_1)dt_1) dt_2
	\end{align}

	This is called it the second order solution.

	And one improves again:

	\begin{align}
	    U^{(3)}	=& 1- \int_{t_0}^{t} dt_3 \cdot \hat{V}(t_3) \cdot \hat{U}^{(2)}(t_3, t_0)
	    \\
	    =& 1- \int_{t_0}^{t} dt_3 \hat{V}(t_3) \cdot [ 1- \int_{t_0}^{t_3} dt_2 \hat{V}(t_2) \cdot
	    (1- \int_{t_0}^{t_2}dt_1 \hat{V}(t_1))dt_1]	
	\end{align}

    Inductively we get the expression:
    \begin{align}
    	\hat{U}(t,t_0) = \sum_{n=0}^{\infty}
    		(-i)^n
    		\int_{t_0}^{t} dt_1 \int_{t_0}^{t_1} dt_2
    		\dotsb \int_{t_0}^{t_{n-1}} dt_n
    		\hat{V}(t_1)\dotsb\hat{V}(t_{n})
    \end{align}
    %\marginpar{Express the result in the form of exp(...)(2.27) on pp.69 of Makan.}

    We remark that we have already obtain U in the form of %\marginpar{delete this?}
    $$U=\Sigma_1 (-i)^n a_n$$

    If we can find another value $b_n=n!a_n$, then
    $$U= \sum_i \frac{(-i)^n}{n!}b_n= \text{ (Formally writing as) }e^{-ib}$$

    This is related to other forms of Wick's theorem, which we will not discuss until the subsequent parts of this series.

    Now we change the expression for $\hat{U}$ a little bit. Let us take the case of $n=2$ as an example. The main part is the integral:

    \begin{align} \label{eq:n_is_21} \int_{t_0}^{t}dt_2 \int_{t_0}^{t_2} dt_1 \hat{V}_I(t_2) \hat{V}_I(t_1)
    \end{align}

    The integration is taken diagrammatically:

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\textwidth]{figures/1.jpg}
		\caption{$t_2>t_1$}
	\end{figure}

    If we relabel $t_1$ to $t_2$, $t_2$ to $t_1$, we get:
    \begin{align} \label{eq:n_is_22} \int_{t_0}^{t}dt_1 \int_{t_0}^{t_1}dt_2 \cdot \hat{V}_I(t_1) \hat{V}_I(t_2)  
    \end{align}

    Then the integration is changed into:

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\textwidth]{figures/2.jpg}
		\caption{$t_1>t_2$}
	\end{figure}

    We observe that doing the two integration is equivalent to doing a full integral over the region marked by ($t_0 \leqslant t_1 \leqslant t $ and $t_0 \leqslant t_2 \leqslant t$),

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.6\textwidth]{figures/3.jpg}
		\caption{Whole region}
	\end{figure}

    while restricting the value of integration in the proper region and putting the operators in correct order.

    For example:

    \fref{eq:n_is_21} is: $\int_{t_0}^{t}dt_2 \cdot \int_{t_0}^{t_2} dt_1 \theta(t_1-t_2) \hat{V}_I(t_2) \hat{V}_I(t_1)$

    \fref{eq:n_is_22} is: $\int_{t_0}^{t}dt_1 \int_{t_0}^{t_1}dt_2 \cdot \theta(t_1-t_2) \hat{V}_I(t_2) \hat{V}_I(t_1)$

    where $\theta(t_1-t_2)$ is restricting the to region $t_2>t_1$. Also, I put the latest time in the front.

    \subsubsection{Time Ordering Operator T}

    We introduce a time ordering operator $T$ to signify the process we described above. When $T$ acts on a set of operators, it automatically sorts them in descending time order.

    For example, if $t_3>t_2>t_1$, then

    $$T(A(t_1)B(t_3)C(t_2)) = B(t_3)C(t_2)A(t_1)$$

    Then

    \begin{align}
        \int_{t_0}^{t}dt_1 \int_{t_0}^{t}dt_2 =& T (\hat{V}(t_1) \hat{V}(t_2))
        \\
        = (\text{integration of } &\hat{V}_I(t_1) \hat{V}_I(t_2) \text{ when } t_1>t_2 ) \nonumber\\
         +(\text{integration of } &\hat{V}(t_2)\hat{V}(t_1) \text{ when } t_2>t_1)
        \nonumber\\
        = (\int_{t_0}^{t}dt_1 \int_{t_0}^{t_1}dt_2 & \hat{V}_I(t_1) \hat{V}_I(t_2)  \nonumber\\
        + (\int_{t_0}^{t}dt_2 \int_{t_0}^{t_2} dt_1 &\hat{V}_I(t_2) \hat{V}_I(t_1))
    \end{align}

    But \fref{eq:n_is_22} is equal to \fref{eq:n_is_21}, because $ \int_{t_0}^{t}dt_2 \cdot \int_{t_0}^{t_2} dt_1 \hat{V}_I(t_2) \hat{V}_I(t_1)= \frac{1}{2} \cdot \int_{t_0}^{t}dt_1 \int_{t_0}^{t}dt_2 \cdot T[\hat{V}_2(t_1) \hat{V}_2(t_2)]  $

    Similarly, for arbitrary n, we have
    $$ \int_{t_0}^{t}dt_n \int_{t_0}^{t_n}dt_(n-1) \cdots \int_{t_0}^{t}dt_1 \cdot 
    \hat{V}_I(t_n) \cdots \hat{V}_I(t_1)
    =\frac{1}{n!} \cdot \int_{t_0}^{t}dt_n \cdots \int_{t_0}^{t}dt_1 \cdot 
    T(\hat{V}_I(t_n) \cdots \hat{V}_I(t_1))
    $$

    The factor $n!$ is that we have in total $n!$ different ways to rearrange {$t_1,\cdots, t_n$}. And each arrangement {$t_{i_1}, \cdots,t_{i_n}$} corresponds to a region in ${[t_0, t_0]}^n$ where $t_0 \leqslant t_{i_1} < \cdots < t_{i_n} \leqslant t$.

    Thus we the most useful expression for operator $\hat{U}$:

   	\begin{align}
    	\hat{U}(t,t_0) = \sum_{n=0}^{\infty}
    	\frac{(-i)^n}{n!}
    	\int_{t_0}^{t} dt_1 \int_{t_0}^{t} dt_2
    	\dotsb \int_{t_0}^{t} dt_n
    	T[\hat{V}(t_1)\dotsb\hat{V}(t_{n})]
   	\end{align}

    \subsection{Adiabatic Switch on}

    The next idea for interacting many-body system is to use the notion of adiabatic switch on. In the Interaction Picture, we assume our Hamiltonian is:

    $$ H=H_0 +V $$

    We wish to extract the eigenstate of $H$ from that of $H_0$. Hence we imagine that we have

    $$ H' = H_0 + e^{-\epsilon |t|}V  $$

    So we have $\lim_{t\to\infty} H'= \lim_{t\to\infty} H'=H_0 $.

    In this scenario, we have

    $$ \ket{\Psi(t=\pm\infty)} = \ket{\Phi_0}   $$

    where $\ket{\Phi_0}$ can be exactly solved.

    Then using the evolution operator $U$, we can bring up the states from $-\infty$ to now $t=0$.

    \begin{align}
        \ket{\Psi(t=0)} =& U_\epsilon (0,-\infty) \ket{\Psi(t=-\infty}
        \\
        =& U_\epsilon (0,-\infty) \ket{\Psi(\infty)}
    \end{align}

    This is the solution to $H=H_0+V$, since $e^{-\epsilon \cdot 0}=0$.

    %\marginpar Note How $e^{-\epsilon (t)}=0$

    However, there is a problem with this. Because the real physical system is in the Hamiltonian $H=H_0+V$ all the time. And our system dives in the Hamiltonian $H$ only at one instant of time. If the result of over calculation is to be meaningful, it must be independent on $\epsilon$.
    How
    In addition, we have a Gell-Mann and Low theorem, which requires a length proof provided in appendix \ref{appendix:Proof_of_G-M_Low}. It states that:

    If the following quantity exists to all orders in perturbation theory, (denoting $\ket{\Psi_0} :\equiv U_{\epsilon} (0, -\infty) \ket{\Phi_0}$. )

    	$$ \frac{\hat{U}_\epsilon(0,-\infty)\ket{\Phi_0}}{\bra{\Phi_0}\hat{U}_\epsilon(0,-\infty)\ket{\Phi_0}}
    	\equiv
    	\frac{\ket{\Psi_0}}{\braket{\Phi_0|\Psi_0}}
    	$$
    	then $\ket{\Psi_0}$ is an eigenstate of $\hat{H}$ in the following sense:
    	$$\hat{H}\frac{\ket{\Phi_0}}{\braket{\Phi_0|\Psi_0}}
    	=
    	E \frac{\ket{\Psi_0}}{\braket{\Phi_0 |\Psi_0}}
    	$$

    %If the following .....(pp. 61) of Fetter.

    The equation (6.44) could be recast into a new form.

    $$\bra{\Phi_0} \hat{H} \frac{\ket{\Psi_0}}{\braket{\Phi_0|\Psi_0}}
    = E \cdot \frac{\braket{\Phi_0|\Psi_0}}{\braket{\Phi_0|\Psi_0}}
    $$

    Since $H=H_0+V$ and $\braket{\Phi_0|H_0|\Psi_0} = E_0 \cdot {\braket{\Phi_0|\Psi_0}}$, we have

    \begin{align} \frac{\braket{\Phi_0|V|\Psi_0}}{\braket{\Phi_0|\Psi_0}}= E-E_0   \label{eq:6.45}
    \end{align}

    Thus, in the limit $\epsilon \rightarrow 0$ we have a way to calculate the energy of our physical system's $E$ by \ref{eq:6.45}. This is also intuitively satisfying, since when $\epsilon$ is small, $\hat{H}'$ approximates $\hat{H}$ in a long enough time. If we imagine that we turn on $H'$ from $t=-\infty$ very slowly, then we are confident that our calculation is giving us the real wave function and its energy.

\section{Green Function}
\label{sec:Green Function}

\section{Todo}

Here lists I want to add to this article.

First I will define Green functions
\footnote{could be found on \cite{fetter} or \cite{mahan}},
which are related to a variety of physical phenomenons. Then the above idea of adiabatic switch on will allow me to give a formula for Green functions. I will show that this formula, combined with perturbative solution to $\hat{U}$ and the Wick's thoerem
\footnote{Proof of Wick's theorem could be found on \cite{fetter}},
gives us a systematical way of calculating Green functions. I will then explain Feynman Diagrams
\footnote{Both \cite{fetter} and \cite{mahan} explains Feynman Diagrams, though \cite{fetter} explains in more detail.}
, which will give a graphical representation of each Green functions. I will try to understand the new path integral way of calculating Feynman Diagrams\footnote{Could be found on \cite{Negele}.}.

%% ----------------------------------------------------------
%%                       TODO 
%% ----------------------------------------------------------
% 1. Change the bibligraphy into a modern style.
% 2. Improve the identation of source file
% 3. put \ref into \fref.
% 4. Explain for the g in the proof of \ref{appendix:Proof_of_G-M_Low}
% 5. Also in \ref{appendix:Proof_of_G-M_Low}, I think we should call it $\lim_{\epsilon\to 0^+} is finite!
% 6. Give a Mindmap for this article.
% 7. Solve those problems in \marginpar
%\section{Def. Single Particle Green function}
%%Sec 7. (ch3. Sec 3.7) Green Function
%
%$G_{\alpha \beta}$ be s.t.
%$$ iG_{\alpha \beta} (xt,x't')= 
%\frac{\braket{\Psi_0|T[\hat{\psi}_{H\alpha}(x,t)\psi_{H\beta}^{\dagger}(x',t)|\Psi_0}}
%{\braket{\Psi_0|\Psi_0}}  \text{  (7.1)of Fetter  }
%$$
%
%Here, $\ket{\Psi_0}$ and $\psi_H$ are in Heisenberg picture. $\alpha$ and $\beta$ index the spin.
%
%$T$ is defined differently as:
%
%% (7.4) of Fetter.
%
%But this is consistent with previous example, because
%% (under 7.4 of Fetter)
%
%\section{Reason for Green function}
%
%The usefulness of Green function could be demonstrated in several aspects. Although I will not go into the details, I will list three points.
%
%\begin{enumerate}
%	\item Green functions are related to a wide range of observations. To list a few, we have
%	$$(7.7), (7.8)(7.9)(7.10)(7.22)(7.32)
%	$$
%	\item Green functions can be interpreted as a Gredantoer experiment. For example, when $t>t'$, 
%	$$ iG_{\alpha \beta} (xt,x't')= 
%	\braket{\Psi_0|\hat{\psi}_{H\alpha}(x,t)\psi_{H\beta}^{\dagger}(x',t')|\Psi_0}
%	$$
%	%(6.31) of Fetter @ 59
%	
%	\begin{align}
%	\braket{\Psi_I(t)
%		|\hat{\psi}_{I\alpha}(x,t) \hat{U}(t,t') \psi_{I\beta}^{\dagger}(x',t')|
%		\Psi_I(t')}
%	=& \braket{\Phi_0|
%		\hat{U}(-\infty,t) \cdot \hat{U}(t,0) \psi_{H\alpha}(x,t) \hat{U}(0,t) \cdot \hat{U}(t,t') 
%		\times \hat{U}(t',0) \hat{\psi}_{H\beta}^{\dagger}(x',t') \hat{U}(0,t') \cdot \hat{U}(t',-\infty)
%		|\Phi_0}
%	\\
%	=& \braket{\Phi_0
%		|\hat{U}(-\infty,0) \hat{\psi}_{H\alpha}(x,t) \psi_{H\beta}^{\dagger}(x,t') \hat{U}(0,-\infty) |
%		\Phi_0}
%	\end{align}
%	
%	Thus the Green Function could be viewed as 
%	%pp.96 of Jrshi. Sec 6.2.
%	
%	\item There is particularly useful technique to calculate the Green function perturbatively, which is what we are going to illustrate in the next section, i.e. Feymann Diagram.
%\end{enumerate}
%
%\section{Feynman's Diagram and Wick's Theorem}
%
%%(Sec8 of Fetter)
%
%\subsection{alsdkfjlsdkjfal}
%{From \text{$\braket{\hat{O}_H}$} to \text{$\braket{\hat{O}_S}$|}
%	
%	Before applying perturbative analysis, we first need to transform the Green's function defined in Heisenberg picture into a more convenience form.
%	
%	\subsubsection{Theorem}
%	$$ \frac{\braket{\Psi_0 | \hat{O}_H(t) | \Psi_0}}
%	{\braket{\Psi_0 | \Psi_0}} 
%	=
%	\frac{1}{\cdots} 
%	%(8.1) of Fetter
%	$$
%	
%	where $S= \hat{U}_\epsilon (\infty,-\infty)$.
%	
%	$S$ is called the S-Matrix, because it relates the initial state and final state of the system.

% Eki finishes!
\appendix %See: http://www.tex.ac.uk/FAQ-appendix.html

\section{Proof of Gell-Mann and Low Theorem}
\label{appendix:Proof_of_G-M_Low}
The theorem states:

\begin{thm}
	If the following quantity exists to all orders in perturbation theory:

	$$ \frac{\hat{U}_\epsilon(0,-\infty)\ket{\Phi_0}}{\bra{\Phi_0}\hat{U}_\epsilon(0,-\infty)\ket{\Phi_0}}
	\equiv
	\frac{\ket{\Psi_0}}{\braket{\Phi_0|\Psi_0}}
	$$
	then $\ket{\Psi_0}$ is an eigenstate of $\hat{H}$ in the following sense:
	$$\hat{H}\frac{\ket{\Phi_0}}{\braket{\Phi_0|\Psi_0}}
	=
	E \frac{\ket{\Psi_0}}{\braket{\Phi_0 |\Psi_0}}
	$$
\end{thm}

Proof:

Here and afterwards, we will set $\ket{\Psi_0(\epsilon)} \equiv \hat{U}_\epsilon(0,-\infty) \ket{\Phi_0}$.

Consider the following:

\begin{align}
(\hat{H}_0-E_0) \ket{\Psi_0(\epsilon)} =& (\hat{H}_0 - E_0)\hat{U}_\epsilon(0,-\infty)\ket{\Psi_0} \\		
=& \left( \hat{H}_0 \hat{U}_\epsilon(0,-\infty) - \hat{U}_\epsilon(0,-\infty)E_0\right)  \ket{\Psi_0} \\
=& \left( \hat{H}_0\hat{U}_\epsilon(0,-\infty) - \hat{U}_\epsilon(0,-\infty) \hat{H}_0\right) \ket{\Psi_0} \\
=& [\hat{H}_0, \hat{U}_\epsilon(0,-\infty)] \ket{\Psi_0}
\label{eq:6.46}
\end{align}

The expression for $\hat{U}_\epsilon(0,-\infty)$ is explicitly:

\begin{align}
\hat{U}_\epsilon(0,-\infty) =& \nonumber\\
\sum_{n=0}^{\infty} \frac{(-i)^n}{n!} &\int_{-\infty}^{0} dt_1 \dotsb \int_{-\infty}^{0} dt_n e^{\epsilon(t_1+\dotsb+t_n)} T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]
\end{align}

So we need $[\hat{H_0}, \hat{V}(t_1)\dotsb\hat{{V}(t_n)}]$ to get $[\hat{H}_0, \hat{U}_\epsilon(0,-\infty)]$.

\begin{lemma}
	$[H,ABC\dotsb] = \left( [H,A] BC\dotsb\right)  + \left( A[H,B]C\dotsb\right)  + \dotsb$
\end{lemma}

Proof:

Obviously we have: 
\begin{align}[H,AB] = [H,A]B + A[H,B] \label{eq:HAB}\end{align}
Then for more terms we can, for example:
\begin{align}
[H,ABC] =& [H,AB] C + AB[H,C] \nonumber\\
=& [H,A]BC + A[H,B]C + AB[H,C] \nonumber
\end{align}

Thus one may obviously obtain the lemma by using \fref{eq:HAB} recursively.

Using above lemma, one has:

\begin{align}
[\hat{H}_0,\hat{V}(t_1)\dotsb\hat{V}(t_n)] &= [\hat{H}_0,\hat{V}(t_1)]\hat{V}(t_2)\dotsb \nonumber\\
&+ \dotsb \nonumber \\
&+ \hat{V}(t_1)\dotsb\hat{V}(t_{n-1})[\hat{H}_0,\hat{V}(t_n)] 
\end{align}

Also, in Interaction Picture, one has:
$$ i\frac{\partial \hat{V}(t)}{\partial t} = [\hat{V}(t),\hat{H}_0]$$
or:
$$ \frac{1}{i} \frac{\partial \hat{V}(t)}{\partial t} = [\hat{H}_0,\hat{V}(t)]$$
Hence the above commutators are turned into partial derivatives:

\begin{align}
[\hat{H}_0,\hat{V}(t_1)\dotsb\hat{V}(t_n)] &= \frac{1}{i} \left( \frac{\partial}{\partial t_1} + \dotsb + \frac{\partial}{\partial t_n}  \right)  \hat{V}(t_1)\dotsb\hat{V}(t_{n})
\label{eq:eq_of_HVVV}
\end{align}

We need an additional fact:
\begin{align}
T[\left( \frac{\partial}{\partial t_1} + \dotsb + \frac{\partial}{\partial t_n}  \right)  \hat{V}(t_1)\dotsb\hat{V}(t_{n})] &= \left( \frac{\partial}{\partial t_1} + \dotsb + \frac{\partial}{\partial t_n}  \right)  T [\hat{V}(t_1)\dotsb\hat{V}(t_{n})]
\label{eq:partial_T}
\end{align}
This can be seen on an example. Notice that 
$T[\hat{V}(t_1)\hat{V}(t_2)] = \theta(t_1-t_2)\hat{V}(t_1)\hat{V}(t_2) + \theta(t_2-t_1)\hat{V}(t_2)\hat{V}(t_1)$, where $\theta(t)$ is Heaviside step function. We also have: $\frac{\partial}{\partial t}\theta(t) = \delta(t) $. So when $t_1\neq t_2$, $T\frac{\partial}{\partial t_1} = \frac{\partial}{\partial t_1} T$, i.e. it commutes with $T$. When $t_1 = t_2$, this is obviously also correct as well. Hence:
$$
T[ \frac{\partial}{\partial t_1} \hat{V}(t_1) \hat{V}(t_{2})] = 
\frac{\partial}{\partial t_1} T[  \hat{V}(t_1) \hat{V}(t_{2})]
$$
Similar arguments will give us \fref{eq:partial_T}, since $T$ is essentially a series of $\theta(t)$ functions.

Using the above fact and \ref*{eq:eq_of_HVVV}, one turns \ref*{eq:6.46} into (Denote $\int_{-\infty}^{0} dt_1\dotsb \int_{-\infty}^{0} dt_n$ as \textit{(Integrate)}):
\begin{align}
(\hat{H}_0-E_0)\ket{\Psi_0(\epsilon)} =& \nonumber\\
\Bigl[ 
\hat{H}_0, 1+\sum_{n=0}^{\infty} \frac{(-i)^n}{n!} 
&\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)} T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]
\Bigr] \nonumber\\
=& \sum_{n=1}^{\infty} \frac{(-i)^n}{i\cdot n!} 
\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)} 
\left( \frac{\partial}{\partial t_1} + \dotsb + \frac{\partial}{\partial t_n}  \right) 
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] \nonumber\\
=& \sum_{n=1}^{\infty} - \frac{(-i)^{n-1}}{n!} 
\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)}
\left( \frac{\partial}{\partial t_1} + \dotsb + \frac{\partial}{\partial t_n}  \right)
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]
\label{eq:6.46_2}
\end{align}

Integration by parts gives us, for example:

$$\int_{-\infty}^{0} dt_1 e^{\epsilon t_1} \frac{\partial}{\partial t_1} T[\hat{V}(t_1)] 
= 
e^{\epsilon t_1} T[\hat{V}(t_1)] \bigg|_{\infty}^0 - \epsilon\int_{\infty}^{0} dt_1 e^{\epsilon t_1}T[\hat{V}(t_1)]$$

Similarly:
\begin{align}
&\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)}
\frac{\partial}{\partial t_1}
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] \nonumber \\
&= \hat{V}(0) \text{\textit{ (Integrate without $t_1$) }} 	e^{\epsilon(t_2+\dotsb+t_n)}
T[\hat{V}(t_2)\dotsb \hat{V}(t_n)] \nonumber \\
&- \epsilon \text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)}
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]
\end{align}

For other "$\frac{\partial}{\partial t_i}$", the procedure is essentially the same, and they all contribute to the same value, as can be seen by relabeling the dummy indices "$t_1 \dotsb t_n$". Hence \ref{eq:6.46_2} is:

\begin{align}
(\hat{H}_0-E_0)\ket{\Psi_0} &= 
\sum_{n=1}^{\infty} - \frac{(-i)^{n-1}}{n!} \cdot n \times \nonumber \\
&\bigg\{
\hat{V}(0) \text{\textit{ (Integrate without $t_1$) }}
e^{\epsilon(t_2+\dotsb+t_n)}
T[\hat{V}(t_2)\dotsb \hat{V}(t_n)] \nonumber\\
&-
\epsilon
\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)}
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]	
\bigg\}
\ket{\Phi_0}  \nonumber \\
&\text{($n$ for $n$ same contributions from 
	$\int_{-\infty}^{0} dt_1 \dotsb \int_{-\infty}^{0} dt_n$.)} \nonumber\\
&= -\hat{V}(0)\hat{U}_\epsilon(0,-\infty) \ket{\Phi_0}
\text{(the first term)} \nonumber\\
&+ \epsilon \sum_{n=1}^{\infty} \frac{(-i)^{n-}}{(n-1)!}
\text{\textit{ (Integrate) }}
e^{\epsilon(t_1+\dotsb+t_n)}
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] \ket{\Phi_0} \nonumber
\end{align}
The second term is dealt with as follows:
\begin{align}
\frac{(-i)^{n-1}}{(n-1)!} \text{\textit{ (Integrate) }} 
T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] & 
\text{(assuming $\hat{V} = g\cdot \hat{V}')$} \nonumber\\
= \frac{(-i)^{n-1}}{(n-1)!} &\text{\textit{ (Integrate) }}
g^n T[\hat{V}'(t_1)\dotsb \hat{V}'(t_n)] \nonumber \\
=ig\frac{\partial}{\partial g} \frac{(-i)^n}{n!}g^n
&\text{\textit{ (Integrate) }} T[\hat{V}'(t_1)\dotsb \hat{V}'(t_n)]
\nonumber \\
=ig\frac{\partial}{\partial g} \frac{(-i)^n}{n!}g^n
&\text{\textit{ (Integrate) }} T[\hat{V}(t_1)\dotsb \hat{V}(t_n)]\nonumber
\end{align}
Hence:
\begin{align}
\text{second term} &= \epsilon
\sum_{n=1}^{\infty}ig \frac{\partial}{\partial g}
\frac{(-i)^n}{n!}
\text{\textit{ (Integrate) }} T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] \ket{\Phi_0} \nonumber\\
&= i\epsilon g \frac{\partial}{\partial g}
\sum_{n=0}^{\infty}
\frac{(-i)^n}{n!}
\text{\textit{ (Integrate) }} T[\hat{V}(t_1)\dotsb \hat{V}(t_n)] \ket{\Phi_0} \nonumber\\
&\text{\quad(since $\frac{\partial}{\partial g}
	\text{(zeroth term)}=0$)} \nonumber\\
&=i\epsilon g \frac{\partial}{\partial g}
\hat{U}_\epsilon(0,-\infty) \ket{\Phi_0} \nonumber\\
&= i\epsilon g \frac{\partial}{\partial g} \ket{\Psi_0(\epsilon)}
\nonumber
\end{align}
Together we have (noting that $\hat{V}(0)$ is actually the interacting part of real Hamiltonian $\hat{V}$):
\begin{align}
(\hat{H}_0-E_0)\ket{\Psi_0(\epsilon)} = -\hat{V}\ket{\Psi_0(\epsilon)} + i\epsilon \frac{\partial}{\partial g} \ket{\Psi_0(\epsilon)}
\end{align}
Write it in another way:
\begin{align}
(\hat{H}_0+\hat{V}-E_0) \ket{\Psi_0(\epsilon)} &= (\hat{H} -E_0)\ket{\Psi_0(\epsilon)} \nonumber\\
&= i\epsilon g \frac{\partial}{\partial g} \ket{\Psi_0(\epsilon)}
\label{eq:6.50}
\end{align}
Multiplying left with
$\frac{\bra{\Phi_0}}{\braket{\Phi_0|\Psi_0(\epsilon)}}$,
we have:
\begin{align}
RHS &= i\epsilon g
\frac{
	\braket{\Phi_0|\frac{\partial}{\partial g} |\Psi_0(\epsilon)}
}
{\braket{\Phi_0|\Psi_0(\epsilon)}
}\nonumber\\
&\text{\quad(since 
	$\frac{\partial}{\partial g} \bra{\Phi_0}=0$)}\nonumber\\
&= i\epsilon g
\frac{
	\frac{\partial}{\partial g}\braket{\Phi_0|\Psi_0(\epsilon)}
}
{
	\braket{\Phi_0|\Psi_0(\epsilon)}
}\nonumber\\
&=i \epsilon g \frac{\partial}{\partial g}
\ln\braket{\Phi_0|\Psi_0(\epsilon)}
\end{align}
while:
\begin{align}
LHS = \frac{
	\braket{\Phi_0|\hat{H} | \Psi_0(\epsilon)}
}{
\braket{\Phi_0|\Psi_0(\epsilon)}
}
= E-E_0
\end{align}
So we have:
\begin{align} i \epsilon g \frac{\partial}{\partial g}
\ln\braket{\Phi_0|\Psi_0(\epsilon)} = E-E_0 
\label{eq:6.51}
\end{align}
From above expression, we notice that 
$\lim_{\epsilon\to 0^+} \epsilon \ln\braket{\Phi_0|\Psi_0(\epsilon)}$ is finite, otherwise we would have $E=E_0$ when $\epsilon\to 0^+$, which is absurd. Hence, $ln \braket{\Phi_0| \Psi_0(\epsilon)} \propto \frac{1}{\epsilon}$, or $\braket{\Phi_0| \Psi_0(\epsilon)} \propto e^{1/\epsilon}$.

Now we calculate

\begin{align}
&(H-E_0 - i\epsilon g \frac{\partial}{\partial g}) \frac{\ket{\Psi_0(\epsilon)}}
{\braket{\Phi_0|\Psi_0(t)}} \nonumber\\
&= \frac{
	(\hat{H}-E_0-i \epsilon g \frac{\partial}{\partial g})
	\ket{\Psi_0(\epsilon)}
}{
\braket{\Phi_0|\Psi_0(\epsilon)}
}
+ i\epsilon g
\frac{
	\ket{\Psi_0(\epsilon)}\frac{\partial}{\partial g}
	\braket{\Phi_0|\Psi_0(\epsilon)}
}{
\braket{\Phi_0|\Psi_0(\epsilon)}^2
} \nonumber\\
&= \text{(by \ref{eq:6.50} the first term vanishes)\quad} 0
+ \frac{\ket{\Psi_0(\epsilon)}}
{\braket{\Phi_0|\Psi_0(\epsilon)}}
\cdot
i \epsilon g \frac{\partial}{\partial g}
\ln\braket{\Phi_0|\Psi_0(\epsilon)} \nonumber\\
&= \text{(by \ref{eq:6.51})\quad}
\frac{\ket{\Psi_0(\epsilon)}}
{\braket{\Phi_0|\Psi_0(\epsilon)}}
\cdot
(E-E_0)
\end{align}
That is:
\begin{align}
\left( \hat{H} - E - i \epsilon g \frac{\partial}{\partial g}\right) 
\frac{\ket{\Psi_0(\epsilon)}}
{\braket{\Phi_0|\Psi_0(\epsilon)}}
= 0
\end{align}
Now by assumption 
$\frac{\ket{\Psi_0(\epsilon)}}
{\braket{\Phi_0|\Psi_0(\epsilon)}}$ is finite when 
$\epsilon\to 0^+$,
we have:
\begin{align}
\hat{H}\frac{\ket{\Phi_0}}{\braket{\Phi_0|\Psi_0}}
=
E \frac{\ket{\Psi_0}}{\braket{\Phi_0 |\Psi_0}}
\end{align}

\textbf{Q.E.D.}

\begin{thebibliography}{1}

	\bibitem{blog} \url{http://we-taper.github.io/}

	\bibitem{fetter} Alexander L. Fetter, John Dirk Walecka, Quantum Theory of Many-Particle Systems

	\bibitem{mahan}  Gerald D. Mahan, Many-Particle Physics (3rd)

	\bibitem{wiki:Plank_units} \url{https://en.wikipedia.org/wiki/Planck_units}
	(accessed June 1, 2016).

	\bibitem{Negele} Negele \& Orland, Quantum Many-particle Systems.

\end{thebibliography}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\end{document}

### 2016-07-10 draft.tex
Notes on The Mathematical Theory of Communication by Shannon. Very interesting article.

@@
     \end{itemize}
+    \subsection{The Mathematical Theory of Communication}
+    \label{sec:The_Mathematical_Theory_of_Communication}
+    \subsubsection{Introduction}
+
+    \paragraph{What is information}
+    In this part, it is implied that \textit{information} in this work
+    does not carry the usual sense in people's daily life. The semantic
+    aspect of a message is considered to be irrelavant, for purpose
+    of generality of the design of communication systems.
+
+    \paragraph{Measure of information} 
+    % TODO Read the paper of Hartley to understand what is information:
+    % Hartley, R. V. L., "Transmission of Information," Bell System Technical
+    % Journal, July 1928, p. 535
+
+    Then it refers to a paper by Hartley to substantiate the use of
+    \begin{align}
+        \label{eq:measure_of_information}
+        S = \log(M)
+    \end{align}
+    as a measure of information. More specifically, we assume we have a
+    set of possible messages. Then $M$ is the cardinality of this set.
+    Then $S$ is a measure of the information produced when one message
+    is chosen from the set. Once again, we regard all choices 
+    being equally possible.
+
+    Note that the base of logrithm in \ref{eq:measure_of_information}
+    is undefined. Choosing a base constituting choosing a unit of
+    the measure. Two such measures, when calculated in different units,
+    are related by a simple constant.
+
+    Conventionally, a base $2$ is chosen. The resulted unit is called
+    bits. If the base $10$ is chosen, then the units may be called
+    decimal digits. If the base $e$ is chosen, then the units is
+    called natural units.
+
+    Also, the author lists several points to illustrate the
+    convenience of this measure.
+
+    \paragraph{Communication systems}
+    Next the author defines the necessary components of a \textit{
+    communication system}, and categorizes it into discrete systems,
+    continuous systems and mixed systems.
+
+    \subsubsection{Discrete Noiseless Systems}
+
+    \paragraph{Discrete Noiseless Channel}
+    \label{sec:Discrete Noiseless Channel}
+    This part deals with another measure, the measure of the capacity
+    of a channel to transmit information. It defines the capacity of a
+    discrete channel as:
+    \begin{align}
+        \label{eq:capacity_of_disc_chan}
+        C\equiv \lim_{T\to \infty} \frac{\log N(T)}{T}
+    \end{align}
+    where $N(T)$ is the number of allowed signals of duration $T$.
+    Several examples are given with formula for $C$ in each particular
+    example.
+
+    \paragraph{Discrete Source of Information}
+    Next, it proceeds to discuss the statistical property of the source
+    of information. Pointing out that a statistical knowledge of the
+    source of information can help peopole craft special protocals to
+    reduce the required capacity of the channel, the article gradually
+    focuses on the statistical property of sourcs. It profess that while a
+    discrete source could be represented by a statistical source, a
+    statistical process can also be considered a discrete source. The
+    second claim is substatiated by several exmaples.
+
+    In one example of natural language, the article defines a 
+    \textit{n-gram} case to produce natural language from statistical
+    information.
+
+    \paragraph{Series of Approximations to English}
+    As the title suggests, this part illustrate two serial levels of
+    steps to approximate the English language using statistical knowledge
+    of appearance of alphabets (the first method) and words (the second
+    example). The article claims that "a sufficiently complex stochastic 
+    process will give a satisfactory representation of a discrete source".
+    Although I am largely against this juvenile view.
+
+    \paragraph{Graphical Representation of a Markoff Process}
+    Then the article mentions a graphical way to represent the aforementioned
+    approximation process, and gives three examples on page 46.
+
+    \paragraph{Ergodic and Mixed Sources}
+    Now the article comes to a special type of stochastic process, ergodic
+    processes. A rough idea of "ergodic" is given in page 45. The idea is
+    so important that I felt compeled to present it here:
+
+    "In an ergodic process every sequence produced by
+    the process is the same in statistical properties. Thus the letter
+    frequencies, digram frequencies, etc., obtained from particular
+    sequences, will, as the lengths of the sequences increase, approach
+    definite limits independent of the particular sequence.
+    Actually
+    this is not true of every sequence but the set for which it is false
+    has probability zero. Roughly the ergodic property means 
+    \textbf{statistical homogeneity}."
+
+    Next, the article claims that artificial languages given in previous
+    examples are ergodic, because the corresponding graph does not
+    have two properties: they does not comprise two or more \textit{isolated
+    parts}, and they $gcd$ of the lengths of all \textit{circuits }is one.
+    The precise meaning is listed in page 47. Roughly, an analogy made by
+    myself helps to
+    catch the points. If we picture an stochastic process as a connected 
+    area, then isolated parts are its connected components, whereas the
+    circuit are the recurrent pattterns.
+
+    Naturally , a stochastic process may exhibit a mixed behavir, in which
+    there are several different sources $L_1,L_2,L_3,\cdots$, which are
+    each of homogeneous, i.e. ergodic, statistical structure. This is
+    discussed following the introduction of ergodicity in page 48.
+
+    Then the article declare that except in special cases, ergodicity is
+    always assumed. This purpose is analogous to that of in statistical
+    physics, to "identify averages along a sequence with averages over 
+    the ensemble of possible sequences", with "the probability of a
+    discrepancy being zero".
+
+    Lastly, the article mentions a fact regarding the equilibrium of
+    the system. A process is called stationary, if it satisfies a
+    equilibrium condition:
+    \begin{align}
+        \label{eq:Ergodic_and_Mixed_States:equil_condition}
+        P_j = \sum_i P_i \cdot P_i(j)
+    \end{align}
+    where $P_j$ is the probability of being in state $j$, and $P_i(j)$ is
+    the transition probability from $i$ to $j$.
+    The fact is that ergodic process is, in a sense, always stationary.
+
+    \paragraph{The Entropy of an Information Source}
+    This part first defines the entropy of a discrete source of finite state
+    to be:
+    \begin{align}
+        \label{eq:entropy_of_discrete_infor_source}
+        H \equiv& \sum_i P_i H_i\\
+        =& -\sum_{i,j} P_i p_i(j) \log(p_i(j)) \nonumber
+    \end{align}
+    It is "the entropy of the source per symbol of text". Another
+    definition for entropy per second is also listed.
+
+    Following this definition are some theorems, which I consider to be
+    the most essential and influential part of the whole book (although
+    I have not yet read the whole book). They are:
+
+    \begin{thm}[Theorem 3 on page 55]
+        Given any $\epsilon >0$ and $\delta >0$, we can find an $N_0$
+        such that the sequences of any legnth $N\geq N_0$ fall into
+        two class:
+        \begin{itemize}
+            \item A set whose total probability is less than $\epsilon$.
+            \item The remainder, all of whose members have probabilities
+                satisfying the inequality
+                \begin{align}
+                    \label{eq:Entropy_of_info_source:thm3}
+                    \left| \frac{\log p^{-1}}{N}-H\right| < \delta
+                \end{align}
+        \end{itemize}
+    \end{thm}
+    "In other words we are almost certain to have 
+    $\frac{\log p^{-1}}{N}$ very close to $H$ when $N$ is large."
+    For me, this reads quite like the \textit{second law of
+    thermaldynamics}.
+
+    % TODO having trouble understanding the Theorem 4 on page 55.
+
 \section{Anchor}

### 2016-07-11 Photosynthesis Course Note.tex
Update light-harvesting system (Photosynthesis) notes.

@@
 
-\section{8th, July}
-\label{sec:8th_July}
+\abstract{
+    This is a note of the course \textit{An Introduction
+    to Light Harvesting in Bacteria and Plants}. The course is more
+    of a academic than of a pedagodic nature: ideas and
+    methods are only mentioned, with reference to the published paper
+    available in the corresponding PDF page.
+    Therefore, this note aims to provide a guidance to read the PDFs.
+    Note that the page numbers in this note are the page numbers of
+    each individual PDFs, not necessarily the page numbers displayed
+    on the bottom-right corner inside the PDFs.
+}
+\section{June 29th}
+\label{sec:June_29th}
+
+In this lecture, the teacher presents backgroud for light-harvesting
+mechanism in biology systems:
+\begin{itemize}
+    \item \textbf{pp.1 to 9 of PPT} 
+        General backgroud to Biophysics.
+    \item \textbf{pp.10 to 18 of PPT}
+        Review of several mechanisms of light harvesting in different 
+        species.
+    \item \textbf{pp.19 to 20 of PPT}
+        The central topics of this course
+        \begin{itemize}
+            \item The natrual of exciton in biological ligth harvesting 
+                system.
+                Is it of Frenkel (short-ranged) of Wannier (long-ranged) type?
+            \item The transfer mechanism. (pp.20) It was mentioned that
+                the transfer is much more efficient than predicted
+                by a classical diffusion model.
+            \item How is active self-regulation archieved. (pp.20)
+        \end{itemize}
+\end{itemize}
+%\paragraph{pp.21 of PPT} Omitted.
+% TODO what is point of this slide?
+Then after a review of Quantum Mechanics (\textbf{pp. 22 to 32} )\footnote{
+    Interestingly, the teacher mentioned Bohmian Mechanics, an alternative
+    model of Quantum Mechanics that features determinism and nonlocality.
+    A comprehensive discussion of this model could be found here:
+    \url{http://plato.stanford.edu/entries/qm-bohm/}
+}, the teacher illustrated a model to calculate
+the excitation energy of a dimer.(\textbf{pp.33 to 36})
+Note that here it is expected that only one of the
+dimer is excited, becuase this energetically eaiser to achieve.
+Note also that the
+symble "$\dagger$" denotes neither conjugation nor creation operator,
+but simply a label for an excited state's wavefunction.
+
+Afterwards, the result on \textbf{page 36} expressed the excitation energy 
+as a function of
+transition dipole moment and the speration length of two molecules.
+
+\section{July 1th}
+\label{sec:July_1th}
+\paragraph{pp.1 of PPT} It begins with a review of two modes of excitons
+in organic biology.
 \paragraph{pp.2 of PPT}
-In the last lecture, the \textit{master equation} for density matrix
+\section{July 8th}
+\label{sec:July_8th}
+In the previous lecture, the \textit{master equation} for density matrix
 \footnote{Reference not found.}
-could lead to problematic result. As the density matrix propagates
+could lead to problematic result. When the density matrix propagates
 as described by the master equation, the eigenvalues for it might
-involved into negative values. This is because the added terms
-are not rigorously derived, but just an approximation.
-
-\textbf{Digression}:  PRE 65 056120, something about entanglement between
-oscillators.
-
-\paragraph{pp.3 of PPT}
-\textbf{Lindblad equations} This equation ensures that the
+evolve into comprising negative values. This is because the added terms
+are not rigorously derived, but just an approximation. On \textbf{page 2} the
+teacher mentioned a specific case.\footnote{
+    Digression: in the article PRE 65 056120, we can find
+    something about the entanglement between two oscillators.
+}
+Therefore, one introduces the \textbf{Lindblad equations}
+(\textbf{pp.3}). This equation ensures that the 
 density matrix $\rho \geq 0$ (i.e. having all positive
@@
 
-An Example for Lindblad equation:
+The teacher wrote an example for the $V_m$ term on ppt on blackboard:
 
@@
 $$ H = w_0 a^\dagger a $$
-If we add interaction of oscillator and other excitons:
-$$ A^\dagger A (a^\dagger + a) = \text{extra} + \text{bath}$$
+If we add an interaction between the oscillator and other excitons:
+$$ A^\dagger A (a^\dagger + a) = \text{extra} \otimes \text{bath}$$
 Then $A^\dagger A$ is $V_m$ in ppt.
 
-\paragraph{Digression} Two Spin system. One way to judge
+\paragraph{Digression} In two Spin system. One way to judge
 whether the two particles are entangled or not, is to do partial
@@
 matrix corresponding to only one particle of the system.
+% TODO and then?
 
-\paragraph{Energy Transfer}
-
-\textbf{Note}: This section's materail could be found in
+Next, the author provided a specific model of energy transfer.
+\footnote{
+\textbf{Note}: This section's material could be found in
 \textit{Excitonic energy transfer in light-harvesting complexes 
 in purple bacteria. JChemPhys\_136\_245104.pdf}
+}
 
 % TODO what is exciton?
-\paragraph{pp.5 of PPT}
-Exciton transport process. External
-influence to the system includes trapping, decaying and disspation.
-
-The $k_t$ characterizes the trapping rate. And $k_d$ characterizes
+\paragraph{pp.5} shows diagramatically the exciton transport process.
+External influence to the system includes trapping, decaying and disspation.
+Here $k_t$ characterizes the trapping rate. And $k_d$ characterizes
 the decay rate.
 
-\paragraph{pp.6 of PPT}
-Life time $\tau_n = \int_0^\infty \rho(t)_n dt$, where
-$\rho_n \equiv \rho_{nn}$. We hope the $\braket{t} = \sum \tau_n$
-to be small, because the shorter an exciton is fixed on a state,
+\paragraph{pp.6 of PPT} explains some notations.
+Here $\tau_n$ characterize the life time 
+of exciton in on state $n$. \footnote{ Here
+$\rho_n \equiv \rho_{nn}$.} We hope that the total life time
+$\braket{t} = \sum \tau_n$
+is small, because the shorter an exciton is fixed on a state,
 the more random the system is and the more likely that the exciton
@@
 
-Quantum yeild $q= \text{On PPT} 
-            = \frac{\text{trapped}}{\text{trapp} + \text{died}}$.
+Following are a series of toycases that has been calculated.
 
-\paragraph{pp.8 of PPT}
-Showcase of calculating the $\rho(t)$ using the Haken-Strobl model
-A simple Ring.
+\paragraph{pp.8 to 9} are the $\rho(t)$ for these simple cases.
 % TODO try to calculate the example.
-
-\paragraph{pp.9 of PPT}
-Complex models with more and more elements in the ring.
 
@@
 light-harvesting systems. Cao and Silbey et al New J Phys (2010)}}
-The 16 sites ring shows that there is always 
-a peek in the opposite site(See upper-left plot). This is
+This ring with 16 sites shows that there is always 
+a peek Max population in the opposite site(See upper-right plot). This is
 because there is always
-two channels of equal length for it to get to the opposite side.
+two channels of equal length for excitons to get to the opposite site.
 
-\paragraph{pp.11 of PPT}
-A two ring case, with 8 sites on each ring. The initial configuration
-is evenly excited in the left ring. The right ring comprised of
-trapping sites.
+\paragraph{pp.11 of PPT} is 
+a two ring case, with 8 sites on each ring. The initial configuration
+is that excitons are evenly excited in the left ring. 
+The right ring comprised of trapping sites.
 
-\paragraph{pp.12 of PPT}
-Another two ring case, with a change in the right ring's number
+\paragraph{pp.12 of PPT} is 
+another two ring case, with a change in the right ring's number
 of trapping sites. It shows that a asymmetric design would somehow
-imporve the efficiency, since the right side plot has a maximum region.
-
-\paragraph{pp.15 of PPT}
-
-Start with a reduced single-electron density matrix. Consider an
-external interruption caused by Laser, and apply the 
-\textit{Principle of the nearsightedness of equilibrium systems} to
-reduce the computation difficulties. This principle is related 
-R.P.A. in condensed matter physics.
+imporve the efficiency, since the plot on the right has a maximum region
+while the left one has none. The next slide shows similar result.
 
@@
 following notes are note well organized. It is advised that one should
-look at the original paper
-\paragraph{pp.16 of PPT}
-\footnote{
-\url{http://journals.aps.org/pre/pdf/10.1103/PhysRevE.69.032902}} 
-instead.
+look at the original literature instead.
 
-% TODO unclear picture about this slide.
-Calculating the absorption spectrum, with the result that only one level
-is acceptable.
-$A\propto amplitude$ characterize the behavior of laser input. 
-$M_{mn}:$ the angle between oscillation angles.
+\paragraph{pp.15 to 16} shows a more advanced calculation of excited
+states.
+
+\paragraph{pp.16 of PPT} Calculating the absorption spectrum, 
+showing that only one level is acceptable.
 
 \paragraph{pp.17 of PPT}
-Changing the bahavior of lasers could result (in generally) more
-different acceptable levels. However, the laser configuration
-is not practical.
+Changing the configuration of laser could result (in generally) more
+acceptable levels. However, these laser configurations are not practically
+achievable.
 
@@
 Using Frankel-Exciton Model and find very good fit, balabala.
-% TODO transition dipole, dimerization.
 

### 2016-07-11 Photosynthesis Course Note.tex
The photosynthesis notes is now up-to-date.

@@
     to Light Harvesting in Bacteria and Plants}. The course is more
-    of a academic than of a pedagodic nature: ideas and
+    of a research than of a pedagodic taste: ideas and
     methods are only mentioned, with reference to the published paper
-    available in the corresponding PDF page.
-    Therefore, this note aims to provide a guidance to read the PDFs.
+    available in the corresponding slides.
+    Therefore, this note aims to provide a guidance to read those slides.
     Note that the page numbers in this note are the page numbers of
-    each individual PDFs, not necessarily the page numbers displayed
+    each individual PDF, not necessarily the page numbers displayed
     on the bottom-right corner inside the PDFs.
@@
 \end{itemize}
-%\paragraph{pp.21 of PPT} Omitted.
-% TODO what is point of this slide?
-Then after a review of Quantum Mechanics (\textbf{pp. 22 to 32} )\footnote{
+\textbf{pp.21} displays a observed long-range transport of excitation
+    energy in a biomimetic light-harvesting system.
+Then, after a review of Quantum Mechanics (\textbf{pp. 22 to 32} )\footnote{
     Interestingly, the teacher mentioned Bohmian Mechanics, an alternative
@@
 
-Afterwards, the result on \textbf{page 36} expressed the excitation energy 
-as a function of
-transition dipole moment and the speration length of two molecules.
+The calculated excited state energys on page 35 are splitted into
+two levels. the difference between them, denoted by $\mathcal{E}$,
+is expressed as a function of the two
+transition dipole moments and the speration length of two molecules.
+Details about the interaction potential $V_{uv}$ can be found on
+the next lecture.
 
@@
 \label{sec:July_1th}
-\paragraph{pp.1 of PPT} It begins with a review of two modes of excitons
-in organic biology.
-\paragraph{pp.2 of PPT}
+Begin with a review of two modes of excitons in organic system
+\textbf{pp.1}, this
+lecture proceeds to explain in detail the dipole interaction potential
+(\textbf{pp.2 to 3})
+$V_{uv}$ mentioned in previous lecture. \textbf{Page 4} digresses on
+the difference between the transition dipole moment and the
+permanent dipole moment. The picture shows the transition dipole
+moment for a Bacteriacholorophyll (the photosynthetic pigments that 
+occur in various phototrophic bacteria). The right side plot illustrates
+the absorption spectra for Bacteriacholorophyll.
+\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
+strength.
+
+The following slide comes back to the excitation energy. It states two
+forms of dimer: the J aggregation ( \textbf{pp.9 to 10}, and the H
+aggregation ( \textbf{pp.11}). The accessible energy level for absorption
+is determined by conservation of moment. As the result, the J aggregated
+dimer absorbs less energy than the monomer case, and a red shift will be
+observed when comparing the absorption spectra. The case of H aggregation
+is similar. \textbf{Page 12 to 13 } mentions the transition dipole in
+more complicated cases. \footnote{Reference could be found in \textit{
+J. Phys. Chem. B, Vol. 107, No. 35, 2003}.}
+
+\section{July 6th}
+\label{sec:July_6th}
+This lecture begins with a note on the unbelievable efficiency of biological
+system. Then it proceeds to review some concepts in quantum statistical 
+mechanics ( \textbf{page 2 to 21}). Since we are quite familar with this
+subject, it will be omitted from this note. The last page mentioned an
+important equation for the evolvement of density matrix in an open system,
+called the "master equation".
+% TODO reference required!
+
 \section{July 8th}
@@
 
-\paragraph{Digression} In two Spin system. One way to judge
-whether the two particles are entangled or not, is to do partial
-transpose: transposing only part of the density
-matrix corresponding to only one particle of the system.
-% TODO and then?
-
 Next, the author provided a specific model of energy transfer.
@@
 
-% TODO what is exciton?
 \paragraph{pp.5} shows diagramatically the exciton transport process.

### 2016-07-11 Complex Geometry - index of notations by taper.tex
Addint license notes too all documents.

@@
+% The entire content of this work (including the source code
+% for TeX files and the generated PDF documents) by 
+% Hongxiang Chen (nicknamed we.taper, or just Taper) is
+% licensed under a 
+% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
+% International License (Link to the complete license text:
+% http://creativecommons.org/licenses/by-nc-sa/4.0/).
 \documentclass{article}
@@
 \usepackage{cite} % need for bibligraphy.
-\usepackage{hyperref}  % make every cite a link
+\usepackage[unicode]{hyperref}  % make every cite a link
 \usepackage{CJKutf8} % For Chinese characters
@@
 	\end{itemize}
-		\subsubsection{Notes of Čech Cohomology with Coeficients in a Sheaf}
+    \subsubsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
 		pp.1:
@@
 \end{thebibliography}
+\section{License}
+The entire content of this work (including the source code
+for TeX files and the generated PDF documents) by 
+Hongxiang Chen (nicknamed we.taper, or just Taper) is
+licensed under a 
+\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
+Commons Attribution-NonCommercial-ShareAlike 4.0 International 
+License}. Permissions beyond the scope of this 
+license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
 \end{document}

### 2016-07-11 Photosynthesis Course Note.tex
Addint license notes too all documents.

@@
 
+\section{License}
+The entire content of this work (including the source code
+for TeX files and the generated PDF documents) by 
+Hongxiang Chen (nicknamed we.taper, or just Taper) is
+licensed under a 
+\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
+Commons Attribution-NonCommercial-ShareAlike 4.0 International 
+License}. Permissions beyond the scope of this 
+license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
+
 \end{document}

### 2016-07-16 Photosynthesis Course Note.tex
Update light-harvesting notes to the new course. Add notes for Q.F.T.

@@
 (\textbf{pp.2 to 3})
-$V_{uv}$ mentioned in previous lecture. \textbf{Page 4} digresses on
+$V_{uv}$ mentioned in previous lecture. \textbf{Page 4 to 5} digresses on
 the difference between the transition dipole moment and the
-permanent dipole moment. The picture shows the transition dipole
+permanent dipole moment. On page 4, the picture shows the transition dipole
 moment for a Bacteriacholorophyll (the photosynthetic pigments that 
 occur in various phototrophic bacteria). The right side plot illustrates
-the absorption spectra for Bacteriacholorophyll.
+the absorption spectra for Bacteriacholorophyll. Page 5 originally
+contains an animated display, which is lost in this PDF file, although
+the content is not important.
 \textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
@@
 The following slide comes back to the excitation energy. It states two
-forms of dimer: the J aggregation ( \textbf{pp.9 to 10}, and the H
-aggregation ( \textbf{pp.11}). The accessible energy level for absorption
+forms of dimer: the J aggregation (\textbf{pp.9 to 10}), and the H
+aggregation (\textbf{pp.11}). The accessible energy level for absorption
 is determined by conservation of moment. As the result, the J aggregated
@@
 
+\section{July 13th}
+\label{sec:July_13th}
+
+In this lecture, we start with a review of simple harmonic
+oscillators in quantum mechanics (\textbf{pp.1 to 8}).
+Then turn to the introduction of Glauber coherent states.
+
+\paragraph{Glauber Coherent States} (defined on \textbf{pp.9})
+is the eigenstate of the annilation 
+operator:
+    \begin{align}
+        A \ket{\alpha} = a \ket{\alpha}
+    \end{align}
+These states maintain their coherence usually longer those number
+eigenstates. There are other features of the Glauber coherent state,
+mentioned in \textbf{pp.9 to 10}.
+
+The next few deductions will give us a very physical picture of Glauber
+coherent states. First, express Glauber coherent state as a linear
+combination of number eigenstates (\textbf{pp.11 to 14}). 
+(It is also found that different coherent states are note 
+orthogonal (\textbf{pp.15}). Also, the overlap of
+two coherent state decays expoentially as the difference 
+of the eigenvalues $|\alpha-\beta|$.
+
+\textbf{Digression}: usualy, the coherent state representation is
+much more numerical efficient in computer simulation
+than the number representation.
+
+Next, we explore several interesting properties of these coherent
+states:
+\begin{itemize}
+    \item \textbf{Expectations}
+        (\textbf{pp.16 to 17}) It is found that 
+        $\braket{X}=\sqrt{2}\lambda \text{Re}(\alpha)$,
+        and $\braket{P} = \frac{\sqrt{2}\hbar}{\lambda} \text{Im}(\alpha)$. Or:
+        $\alpha$ is related to $\braket{\alpha|X|\alpha}$
+        and $\braket{\alpha|P|\alpha}$. Hence a real $\alpha$ means the state
+        $\ket{\alpha}$ is a static state with $\braket{P}=0$. Moreover, this 
+        state
+        is the lowest energy eigenstate of a simple harmonic oscillator with
+        the origin shifted from $0$ to $\alpha$. 
+        % todo substantiate this point!
+    \item \textbf{Variance}
+        (\textbf{pp.18 to 20})
+        It is also found that the variance 
+        $(\Delta X)^2 = \frac{\lambda^2}{2}$,
+        this is exactly the same as the variance of the gound state of simple
+        harmonic oscillator.
+        And $(\Delta P)^2 = \frac{\hbar^2}{2\lambda^2}$. 
+        From the two expression,
+        we see that any coherent states have the same minimal uncertainty:
+        $\Delta X \cdot \Delta P = \frac{\hbar}{2}$.
+    \item \textbf{Time Evolution}
+        (\textbf{pp.21})
+        Using the energy eigenstate of simple harmonic oscillator, we can find 
+        the time evolution of coherent state as 
+        $\alpha(t) = e^{-i\omega t} \alpha_0$. It shows that $\alpha$ is really
+        like a \textit{classical oscillator} and the norm $|\alpha|^2$ is conserved. 
+        This is so cool!
+\end{itemize}
+
+The next slide (\textbf{pp.22}) summarizes the classical feature of Glauber coherent state.
+
+Then we turn to its application in biophysics.
+\paragraph{Polaron dynamics in LH1/LH2} We first introduces polaron
+(\textbf{pp.24 to 25}). The \textbf{polaron model}: Polaron
+is short for polarized electron. In a polarized crystal, an moving electron
+will deform the lattice. Then polaron is the electron and those deformed
+part put it together. This seems quite like the copper pair picture in
+BCS theory. In the light-harvesting system, since only a very small
+amount of light is captured, the exciton concentration is low. And we can
+use the polaron picture for electrons.
+
+Next we write out the Hamiltonian for the LH1/2. (\textbf{pp.26})
+The phonon $H_{ph}$ term 
+contains 16 phonons for 16 pigments in LH1. The exciton term $H_{ex}$
+assumes that the interaction is only nearst neighbour interaction.
+The exciton-phonon interaction $H_{\text{ex-ph}}$ is essentially
+the usual electron-phonon interaction term in solid state physics.
+\section{July 15}
+\label{sec:July_15}
+
+% $q$ represent the phonon vibration. Since $\Omega(Q) = \Omega(0) = 
+% \frac{\partial}{\partial q}q + ...$, the linear-diagonal coupling
+% is just the first.
+% $\gamma_{mn}^l$, $\gamma_0$ is the energy for the phonon on the same
+% site. 
+Here we first introduces a new term in the Hamiltonian, 
+$H_{\text{ex-ph}}^{\text{off-diagonal}}$.
+
+Taking a linear approximation of the phonon band. We will find
+a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.
+
+We will use a time-dependent variational calculation. Then
+we introduces a Davydov ansatz. Note that
+\begin{align*}
+    e^{A+B} = e^A e^B e^{\frac{1}{2}[A,B]}
+\end{align*}
+% todo check this
+And using this relationship, it could be found that the $\ket{\beta}$
+is actually a Glauber coherent state.
+
+note that the Davydov ansatz is not translational invariant.
+
+Next we project the Davydov ansatz into bloch states, and get
+the Toyozawa's ansatz. This Toyozawa ansatz has a central
+position. Using thise, we get the energy band.
+
+Explain for the energy band.
+% todo level repulsion
+
+Shows a Holstein polaron's phase diagram. Outside the thin region,
+there is always a unique solution (global minimum for the variational
+parameters). Below the region, large polaron. Above, small polaron.
+% todo what is a large polaron.
+Inside the solid region, there will be two solutions coexisting.
+The the solution obatined depeands on the initial configuration.
+The physical picture is that, changing the value of $J$ and $g$,
+the size of polaron will change sharply when one transverse the
+dashed line.
+
+Shows some variational parameters calculated. The strange wedge
+in the picture, is the mode of $q=0$ mode ($\beta_{q=0} = g$). It is
+called the Goldston mode, decoupled from the system. This explains
+that the constant value inside these plots, when $q=0$.
+
+When we calculate the off-diagonal coupling. There will be two
+wedges
+
+Then freqency plot. The labels are $(J,g,\phi)$, where $\phi$
+is the off-diagonal strength.
+
+Another approach, called the Munn-Silbey Method,
+in which one first do a strange transformation
+and 
 \section{License}

### 2016-07-16 draft.tex
Update light-harvesting system (Photosynthesis) notes.
Update light-harvesting notes to the new course. Add notes for Q.F.T.

@@
     \subsection{By Mingyuan Hunag}
-    Too boring.
+    Not insterested.
 
@@
 
+    \subsection{By Liyuan Zhang}
+    Not insterested.
 \section{Problems in Bernevig's Topological ...}
@@
         \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
+        i\hbar \partial_t U(t,t_0)= H U(t,t_0)
     \end{align}
@@
     \end{itemize}
+    The time evolution of density matrix, directly obtained from Schrodinger's
+    equation, is
+    \begin{align}
+        \label{eq:quantum_macrostates:density_matrix:evolution}
+        i\hbar \frac{\partial}{\partial t}\rho = [H,\rho]
+    \end{align}
+
     \subsection{The Mathematical Theory of Communication}
@@
 
+\section{Quantum Field Theory}
+\label{sec:Quantum_Field_Theory}
+    \subsection{Relatvistic Quantum Mechanics}
+    \label{sec:Relatvistic_Quantum_Mechanics}
+
+    \subsubsection{2.1 Quantum Mechanics}
+    \label{sec:2.1_Quantum_Mechanics}
+    This part sumarize the axioms of quantum mechanics. (Omitted)
+    However, one class of important but seldom mentioned operator,
+    the antilinear operators and the antiunitary operators are not
+    discussed here but postponed to the next part.
+
+    \subsubsection{2.2 Symmetries}
+    \label{sec:2.2_Symmetries}
+    This part discribe some important theorems concerning the symmetries
+    in quantum mechanics.
+
+    Firstly, symmetries in quantum mechanics some times requires the use
+    of antilinear and antiunitary operators.
+
+    \paragraph{Antilinear and Antiunitary}
+    Antilinear operators: $U (\lambda A + \upsilon B)
+                            = \lambda^* UA + \upsilon^* UB$.
+
+    Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$
+
+    The adjoint operator of an antilinear operator requires special
+    attention:
+    $$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
+    (The usual definition will become troublesome since the LHS will
+    be antilinear in $\phi$, whereas the RHS is linear.)
+
+    Thankfully, the criterion for unitarity or antiunitarity is the same:
+    $$U^\dagger = U^{-1}$$
+
+    An important example is those symmetries which can be infinitesimally
+    close to identity. In the vincinity of unity, it is:
+    $$ U =1+i\epsilon t $$
+    where $t$ is Hermitian and linear.
+    % TODO why is it Hermitian?
+
+    \paragraph{Symmetry Group and its Representation} The set of all
+    symmetries transformations obviously can have a group structure.
+    By giving each symmetry transformation a unitary or antiunitary
+    operator, a representation of such group is obtained. However,
+    such a representation can be projective (projective as in
+    projective geometry, or $\mathbb{CP}^n$), since operators acts
+    on ket spaces, which is already projective (within a freedom of
+    phase).
+
+    If the phase is taken into consideration, it is found that this
+    phase is independent of the ket that the operator acts on:
+    \begin{align}
+        \label{eq:2.2_symmetries_projective_phase}
+        U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
+    \end{align}
+    Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
+    transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
+    on $T_1 T_2$.
+
+    Howver, there is one exception to this rule. It exists when the
+    state $\Psi$ is not the linear some of some other wave functions.
+    That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
+    This seems incomprehesible to me.
+    % TODO Understand this!
+    There are some link on page 53
+    between the structure of Lie group associated
+    with this symmetry and whether the representation can be projective.
+    \footnote{Though not state, it can be infered that a representation
+    can be made not-projective by a good choice of $U(T)$, so that
+    $\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }
+
+    \paragraph{Connected Lie group} is of special importance in physics.
+    However, the books description obfuscate the mathematical description
+    of this structure. I will update this note later to remedy such
+    % TODO update this part.
+    discussion. The message I understand is that the representation is
+    tightly bound to the Lie algebra. An important example is that when
+    $$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
+    $$ [t_b,t_c] = 0$$
+    then
+    $$ U(T(\theta)) = \exp(it_a \theta^a) $$
+
+    \subsubsection{2.3 Quantum Lorentz Transformations}
+    \label{sec:2.3_Quantum_Lorentz_Transformations}
+    \textbf{Note}: although the title suggests "quantum", this part is
+    mostly classical.
+
+    Starting with the invariance of interval:
+    \begin{align}
+        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
+        \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
+    \end{align}
+    or equivalently % TODO why equivalently?
+    \begin{align}
+        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+        \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
+            \frac{\partial x'^\nu}{\partial x^\sigma}
+            =
+        \eta_{\rho\sigma}
+    \end{align}
+    It claims that any coordinate transformation satisfying 
+    \ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+    must be linear.
+
+    Such linear Lorentz transformations satisfy:
+    \begin{align}
+        T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
+            T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
+    \end{align}
+    where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
+    transformations.
+
+    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
+    equations that relate it with $\eta_{\mu\nu}$. Note that:
+    $$ \Lambda^{\rho}_{ \nu} \neq \Lambda^{ \rho}_\nu$$
 \section{Anchor}

### 2016-07-16 Draft/draft.tex
Adding notes for sheaf cohomology. Updating the notes for "light harvesting system". Updating notes for Q.F.T.

--- 2016-07-16 draft.tex
@@
 \newtheorem{ex}{Example}[section]
+
+\usepackage{tensor}  % For tensor indices
+\usepackage[all]{xy} % For drawing category diagrams
+\usepackage{mathrsfs}
 
@@
     The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
-    equations that relate it with $\eta_{\mu\nu}$. Note that:
-    $$ \Lambda^{\rho}_{ \nu} \neq \Lambda^{ \rho}_\nu$$
+    equations that relate it with $\eta_{\mu\nu}$.
+
+    Note that:
+    \[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
+    And:
+    \begin{equation}
+        \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
+        (\Lambda^{-1})\indices{^\rho_\nu} = 
+            \Lambda\indices{_\nu^\rho} = 
+            \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
+    \end{equation}
+
+    The only part about quantum mechanics here, is that the operators
+    corresponding to the Lorentz transformations, have the property that:
+    \begin{equation}
+        U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
+            U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
+    \end{equation}
+    where $a$ represents the translation.
+
+    The group of Lorentz transformations is very important. There is:
+        %\text{sssssss} & B
+    \[
+        \xymatrix{ 
+        \text{Poincar\'e Group}  \\
+        \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
+        \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
+        }
+    \]
+    The important \textit{proper orthochronous Lorentz group} consists
+    of those $\Lambda$ with $\det \Lambda = 1$ and 
+    $\Lambda\indices{^0_0} \geq 1$.
+
+    We have also $ \mathscr{P}$, the space inversion matrix. And
+    \(\mathscr{T}\), the time-reversal matrix. The definition for
+    both can be easily written.
+
+    A important rule is that all homogeneous Lorentz transformations can
+    are generated by 
+    \(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
+    However this property is not proved
+
+    \paragraph{Digression about tensor notation} It seems that phsysicists
+    have not settled down on their notation for tensors. Weinberg using
+    the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
+    so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
+    tangent vector. I see that this notation helps to distinguish the
+    type of arguments. This is unnecessary, since the upper and lower
+    indices already fulfill this function. Another benefit is that it
+    conveies the process of lowering of raising a index.
+
+    However, this idea that each slot in tensor indices are distinct
+    and can be lowered and raised seperatly, is not even mentioned
+    in some modern mathematical physics book.
+
+    Helpful link:
+    \href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
+    \href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.
+
 \section{Anchor}

### 2016-07-16 Light harvesting/Photosynthesis Course Note.tex
Adding notes for sheaf cohomology. Updating the notes for "light harvesting system". Updating notes for Q.F.T.

--- 2016-07-16 Photosynthesis Course Note.tex
@@
 }
-\section{June 29th}
+\section{June 29th Wed}
 \label{sec:June_29th}
@@
 
-\section{July 1th}
+\section{July 1th Fri}
 \label{sec:July_1th}
@@
 
-\section{July 6th}
+\section{July 6th Wed}
 \label{sec:July_6th}
@@
 
-\section{July 8th}
+\section{July 8th Fri}
 \label{sec:July_8th}
@@
 
-\section{July 13th}
+\section{July 13th Wed}
 \label{sec:July_13th}
@@
 the usual electron-phonon interaction term in solid state physics.
-\section{July 15}
+\section{July 15, Friday}
 \label{sec:July_15}
 
-% $q$ represent the phonon vibration. Since $\Omega(Q) = \Omega(0) = 
-% \frac{\partial}{\partial q}q + ...$, the linear-diagonal coupling
-% is just the first.
-% $\gamma_{mn}^l$, $\gamma_0$ is the energy for the phonon on the same
-% site. 
-Here we first introduces a new term in the Hamiltonian, 
-$H_{\text{ex-ph}}^{\text{off-diagonal}}$.
+\textbf{Note}: In general, the difficulty in assimilation of ideas is
+greater in Friday than in Wednesday's speech. I was lost again today.
 
-Taking a linear approximation of the phonon band. We will find
+Teacher first explains the Hamiltonian for off-diagonal coupling
+(\textbf{pp.1 to 2}). (The off-diagonal represents phonon-exciton
+interaction between different sites.)
+
+Then he toke a linear approximation of the phonon band. He mentioned
 a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.
 
-We will use a time-dependent variational calculation. Then
-we introduces a Davydov ansatz. Note that
+\textbf{pp.4 to 7} reviews the traditional variational approach.
+
+\textbf{pp.8} introduces the Davydov's ansatz.
+Note that
 \begin{align*}
@@
 
-note that the Davydov ansatz is not translational invariant.
+Note also that the Davydov ansatz is not translational invariant.
 
-Next we project the Davydov ansatz into bloch states, and get
+\textbf{pp.9} projects the Davydov ansatz into bloch states, and get
 the Toyozawa's ansatz. This Toyozawa ansatz has a central
-position. Using thise, we get the energy band.
+position. Using this, we get the energy band.
 
@@
 
-Shows a Holstein polaron's phase diagram. Outside the thin region,
+\textbf{pp.10 }shows a Holstein polaron's phase diagram. 
+\footnote{Could be found in pdf file "nonlocal.pdf".}
+The region enclosed by the pointed solid line is of particular
+interests. Outside this thin region,
 there is always a unique solution (global minimum for the variational
-parameters). Below the region, large polaron. Above, small polaron.
+parameters). 
+% Below the region, large polaron. Above, small polaron.
 % todo what is a large polaron.
-Inside the solid region, there will be two solutions coexisting.
+Outside the region, there will be two solutions coexisting.
 The the solution obatined depeands on the initial configuration.
@@
 
-Shows some variational parameters calculated. The strange wedge
-in the picture, is the mode of $q=0$ mode ($\beta_{q=0} = g$). It is
-called the Goldston mode, decoupled from the system. This explains
+\textbf{pp.11} shows some results when only diagonal term
+is considered.
+\footnote{Could be found on "Toyozawa Ansat.pdf".}
+The strange wedge
+in the picture, is the mode of $q=0$ 
+(in which case it could be found that $\beta_{q=0} = g$). 
+It is
+called the Goldstone mode. This mode is actually decoupled from 
+the system, as can be found directly in the Hamiltonian. This explains
 that the constant value inside these plots, when $q=0$.
 
-When we calculate the off-diagonal coupling. There will be two
-wedges
+\textbf{pp.13} is the result of off-diagonal coupling. 
+% TODO reference not found
+There will be two regions enclosed by solid line.
 
-Then freqency plot. The labels are $(J,g,\phi)$, where $\phi$
-is the off-diagonal strength.
-
-Another approach, called the Munn-Silbey Method,
-in which one first do a strange transformation
-and 
+The remaining slides re not be included in this note,
+since they follow the pattern of applying models developed
+by condensed matter physicsists and showing the result.
+Detailed results could be found in the papers provided by
+the teacher.
 \section{License}

### 2016-07-16 Note of Sheaf Theory/temp.tex
Adding notes for sheaf cohomology. Updating the notes for "light harvesting system". Updating notes for Q.F.T.

\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters
%\usepackage{ dsfont } % For double struck fonts
% For theorems. https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage[all]{xy} % For diagrams: https://en.wikibooks.org/wiki/LaTeX/Xy-pic
\usepackage{CJKutf8}

\title{Sheaf Cohomology}
\date{\today}
\author{
\begin{CJK}{UTF8}{gbsn}
	陈鸿翔，吴獬，金鹏荣，石一凡
\end{CJK}
}
\begin{document}

\maketitle
\abstract{
	Sheaf theory is a powerful tool developed in the 40's of last century and widely used in the area of algebraic geometry and complex geometry . By sheaves and cohomology of sheaves, we can express clearly the obstructions to the problems of going from local solutions to global solutions. This small essay is intended to give a brief outline to the basic sheaf theory presented in the book \cite{voisin}.
}
\tableofcontents

% \section{Definitions and Examples}
% \begin{defi}
% 	A \textbf{pre-sheaf} $ \mathcal{F} $ of abelian groups on a topological space $ M $ consists of an abelian group $ \Gamma(U, \mathcal{F}) = \mathcal{F} $
% 	for every open set $ U\in M $ and a group homomorphism $r^V_U: \mathcal{F}(V)\rightarrow \mathcal{F}(F)$ for any two open sets $U,V$ such that $U\in V$. The map $r$ should satisfy the following relations:
% 	\begin{enumerate}
% 		\item $r^U_U=id_{ \mathcal{F}(U) }$.
% 		\item For open subsets $U \subset V \subset W$, one has 
% 			$r^V_U \circ r^W_V = r^W_V$
% 	\end{enumerate}
% \end{defi}
%  The defition of sheaf is to add the following two conditions to the above:
% \begin{defi}
% 	let $\{U_i\}$ be an open covering of $M$. Let $ \mathcal{F}$ be a presheaf on $M$, then $ \mathcal{F}$ is called a \textbf{sheaf} if and only if it satisfies the following condition:
% 	\begin{enumerate}
% 		\item If $f,g\in \mathcal{F}(M)$ with $r^M_{U_i}(f) = r^M_{U_i}(g)$ for all $i$, then $f=g$.
% 		\item If $f_i\in \mathcal{F}(U_i)$ for all $i$ such that $r^M_{U_i\cap U_j}(f_i)=r^M_{U_i\cap U_j}(f_j)$ for any $j$, then there exists an element $f \in \mathcal{F}(M)$ such that $r^M_{U_i} = f_i$ for all $i$.
% 	\end{enumerate}
% \end{defi}
% 
% The morphism of presheaf is:
% \begin{defi}
% 	Let $ \mathcal{F} $ and $ \mathcal{G}$ be two presheaves, a \textbf{presheaf homomorphism} $\phi :\mathcal{F}\to \mathcal{G}$ is given by group homomorphisms $\phi _U: \mathcal{F}(U)\to \mathcal{G} (U)$ such that the following diagram commutes:
% 	$$ \xymatrix{
% 	\mathcal{F}(V) \ar[r]^{\phi_V}\ar[d]^{r^{ \mathcal{F}}} & \mathcal{G}(V) \ar[d]^{r^{ \mathcal{G}}} \\
% 	\mathcal{F}(U) \ar[r]^{\phi_U} & \mathcal{G}(V)
% 	}
% 	$$
% 	
% 	A \textbf{sheaf homomorphism} is given by a presheaf homomorphism of the underlying presheaves.
% \end{defi}

% \begin{defi}
%     Let $ \mathcal{A}$ be a sheaf of rings over $X$. A \textbf{sheaf of $ \mathcal{A}$-modules }over $X$ is a sheaf $\mathcal{F}$ such
%     that each $\mathcal{F}(U)$ is equipped with the structure of an
%     $ \mathcal{A}(U)-module$ compatible with its group structure. The
%     restriction map are morphisms of $ \mathcal{A}(U)-modules$, where $\mathcal{F}(V)$ is equipped with the structure of an $ \mathcal{A}(U)-modules$ via the restriction morphism
%     $$ \mathcal{A}(U) \to \mathcal{A}(V) $$
% \end{defi}

% ------------------------------------------------------------------------
\section{Sheafification}
For every presheaf $ \mathcal{F}$ one can always form a sheaf associated to it. This sheaf is unique up to an sheaf isomorphism. The procedure is presented below. Throughout this section, $X$ is our topological space.

\begin{defi}
	The sheaf $\prod\mathcal{F}$ of a presheaf $\mathcal{F}$ is defined as the sheaf that gives, for any open set $U \subset X$ 
	$$
	\Pi(U) = \prod\nolimits_{x \in U} \mathcal{F}_x.
	$$
	The restriction map is obvious and the abelian group
	structure is point-wise. This obvious constitutes
	a sheaf.
\end{defi}

\begin{defi}
	The sheaf \textbf{associated} with a presheaf $ \mathcal{F}$, denoted
	by $\mathcal{F^+}$, called the \text{\textbf{sheafification}} of $\mathcal{F}$, is the sheaf such that,
	$$
	\mathcal{F}^{+}(U)
	=
	\{
	(s_u) \in \prod\nolimits_{u \in U} \mathcal{F}_u
	\text{ such that }(*)
	\}
	$$
	where $(*)$ is the property:
	\begin{itemize}
		\item[$(*)$] For every $x \in U$, there exists an open neighbourhood
		$x \in V \subset U$, and a section $t \in \mathcal{F}(V)$
		such that for all $y \in V$ we have $s(y) = t_y$.
	\end{itemize}
\end{defi}

$\mathcal{F^+}$ is clearly a subset of $\mathcal{\prod F}$. It becomes a sheaf because it naturally inherts the sheaf structure of $\mathcal{\prod F}$, and its definition allows us to look at a section only locally. These meanings are best illustrate in the following example.
\begin{ex}
	Let $ \mathbb{R}$ denotes the pre-sheaf of constant real-valued functions. It is not a sheaf because the any sections $f,g$ of $ \mathbb{R}$ on disjoint sets $U,V$ agrees on their intersectin, the empty set. Yet they can not be glued. But the sheafification of it is the sheaf of locally constant functions. In the new sheaf $f,g$ can be glued freely because we only need to look at them locally.
\end{ex}

The sheaf $\mathcal{F^+}$ is better than the crude idea $\prod \mathcal{F}$ because of the following lemmata:
\begin{lemma}
	\label{lemma:f_x=f+_x}
	$\mathcal{F}_x \cong \mathcal{F}_x^+$
\end{lemma}
\begin{proof}
	Observe that an element of $(\prod \mathcal{F})_x$ is 
	characterized by being the same in some local region. 
	An element of $\mathcal{F}_x^+$ is the same as
	some $t\in \mathcal{F}(V)$ or possibly another $t'\in \mathcal{F}(V')$
	. Such an ambiguity is removed by $t\sim t'$ in $\mathcal{F}_x$.
\end{proof}

% Tag 0080 of Stacks Project.
%\marginpar{Uniqueness is not proved!}
\begin{lemma}
	\label{lemma:f_f+_factor}
	Let $\mathcal{F}$ be a presheaf and $\mathcal{G}$ be a sheaf. Any map $\phi:\mathcal{F}\to \mathcal{G}$ factors uniquely as $\mathcal{F}\to \mathcal{F}^+\to \mathcal{G}$.
\end{lemma}
\begin{proof}
	We first construct a diagram:
	$$\xymatrix{
	\mathcal{F} \ar[r]^{f_1}\ar[d]^{\phi} & \mathcal{F^+} \ar[d]^{j}\ar[r]^{f_2} & \prod(\mathcal{F}) \ar[d]^{f_3}\\
	\mathcal{G} \ar[r]^{f_4} & \mathcal{G^+} \ar[r]^{f_5} & \prod( \mathcal{G})
	}$$
	The maps ${f_2}$ and ${f_3}$ are inclusions. ${f_3}$ is the map induced by
	$\phi_x$. $j$ is the map defined by ${f_2}$ and ${f_3}$ and ${f_5}$, with the
	inverse of ${f_5}$ defined by projection. ${f_1}$ and ${f_4}$ are naturally defined. Notice that by lemma \ref{lemma:iso_of_x} and lemma
	\ref{lemma:f_x=f+_x}, we have $ \mathcal{G} = \mathcal{G^+}$. Hence
	${f_4}$ is actually an isomorphism. To prove that $j$ is the
	required map, we need to show that the left part of the
	above diagram commutes. This is obvious if we careful tract the image
	of a section $s\in \mathcal{F}(U)$, and notice the fact
	$(\phi_U(s))_x= \phi_x(s_x)$.
\end{proof}
\textbf{Note}: There are other means of sheafification, which can be found in lemma 4.4 of \cite{voisin}. The above lemma ensures that all such sheafifications are equivalent.

\section{Morphisms of sheaves}

\begin{lemma}
\label{lemma:iso_of_x}
    Let $\phi: \mathcal{F} \to \mathcal{G} $ be a sheaf homomorphism. Then $\phi$ is a isomorphism
    if and only if for any $x\in X$, we have $\phi _x:\mathcal{F}_x\to 
    \mathcal{G}_x$ is an 
    isomorphism.
\end{lemma}
\begin{proof}
    The necessity is clear.

    Conversely, if $\phi_x$ is an isomorphism for all $x\in X$, $U\subset X$ is open. We proof,

    $\phi_U: \mathcal{F}(U)\to \mathcal{G}(U)$ is injective: For $s\in \mathcal{F}(U)$, if $\phi_U(s)=0$. Then $\left(\phi _U(s)\right)_x=\phi _x\left(s_x\right)=0$, i.e. $s_x=0$. Hence $s=0$ by the uniqueness of gluing. Thus the kernal is $0$ and the map is injective.

    $\phi_U: \mathcal{F}(U)\to \mathcal{G}(U)$ is surjective: For $t\in \mathcal{G}(U)$, we can use the representative elements of $t_x$ to find an open covering $\{U_i\}$ of $U$ and $s_i\in F(U_i)$ such that $\phi(s_i) = t|_{U_i}$. Then $\phi(s_i)_{U_i\cap U_j}
    - \phi(s_j)_{U_i\cap U_j} = 0$. By injective we have $s_i|_{U_i\cap U_j}
    = s_j|_{U_i\cap U_j}$, hence $s_i$ can be glued into $s\in F(U)$, whose
    image is clearly $t$. So $\phi_U$ is surjective.
\end{proof}

% Def 4.10 of \ref{voisin}
\begin{defi}
	Let $\phi :\mathcal{F}\to \mathcal{G}$ be a morphism of sheaves. Then $\phi$ is injective (resp. surjective) if for every $x\in X$, the morphism $\phi_x$ is injective (resp. surjective).
\end{defi}
\begin{remark}
	This definition of injectivity is compatible with lemma \ref{lemma:iso_of_x}. However, a sheaf morphism $\phi$ being surjective, does not guarantee that the induced morphism $\phi_U$ is surjective, as can be seen in the proof of lemma \ref{lemma:iso_of_x}.
\end{remark}

% lemma 4.11 of \ref{voisin}
\begin{lemma}
    Let $\phi :\mathcal{F}\to \mathcal{G}$ be a sheaf morphism. Then the presheaf
    $$U\mapsto \text{Ker}\left(\phi _U:\mathcal{F}(U)\to \mathcal{G}(U)\right)$$
    is a sheaf, written $Ker(\phi)$. $Ker(\phi)=0$ if and only if $\phi$ is injective.
\end{lemma}
\begin{proof}
	That $Ker(\phi)$ is a sheaf has already been proved in class.

	The sufficiency for the second assumption is already proved in the
	proof of lemma \ref{lemma:iso_of_x}. The necessity for the second assumption follows from the observation that $\phi _x\left(s_x\right)=\left(\phi _U(s)\right)_x$.
\end{proof}

On the other hand, the image presheaf $Im(\phi)$ is not necessarily a sheaf. Usualy one has to deal with its sheafification, as in the following lemma.
\begin{lemma}
    Let $\phi :\mathcal{F}\to \mathcal{G}$ be a morphism of sheaves, then the sheaf associated to the presheaf
    $$U\mapsto \text{Im}\left(\phi _U:\mathcal{F}(U)\to \mathcal{G}(U)\right)$$
    also written as $Im(\phi)$, is equal to $ \mathcal{G}$ if and only if $\phi$ is surjective.
\end{lemma}
\begin{proof}
	The necessity is obvious by lemma \ref{lemma:f_x=f+_x} 
	and lemma \ref{lemma:iso_of_x}.

	Conversely, if $\phi$ is surjective, By lemma \ref{lemma:f_f+_factor},
	there is a unique map $j:Im(\phi) \to \mathcal{G}$.
	Since $j$ is already injective
	on the presheaf, $j$ is injective. Now since $\phi_x$ is
	surjective, $j_x$ is surjective. If $s$ is a section of 
	$ \mathcal{G}$ on $U$, there
	thus exists a covering of $U$ by open sets $V$ , and sections $t_V$ of 
	$Im(\phi)$, such that
	$j(t_V) = s|_V$ . As $j$ is injective, the $t_V$ coincide on the
	intersections, so there
	exists a section $t$ of $Im(\phi)$ such that $t_V=t_U$ . Then
	$s=j(t)$ and
	$$j:Im(\phi)(U)\to \mathcal{G}(U)$$
	is surjective. Therefore $j$ is an isomorphism. 
\end{proof}

% ------------------------------------------------------------------------
\section{Resolution}

\begin{defi}
A resolution of a sheaf $\mathcal{F}$ is a complex $0\to \mathcal{F}^0 \to \mathcal{F}^1 \to \dots$ together with a homomorphism $\mathcal{F} \to \mathcal{F}^0$ such that
\[
0\longrightarrow \mathcal{F}\longrightarrow \mathcal{F}^0\longrightarrow \mathcal{F}^1\longrightarrow \mathcal{F}^2\longrightarrow \cdots
\]
is an exact complex of sheaves.
\end{defi}

\paragraph{The \v{C}ech resolution}
Let $\mathcal{F}$ be a sheaf over X, and let $U_i$, $i\in \mathbb{N}$ be a countable covering by open
sets of X. For each finite set $I \subset N$, set
\[
U_I=\bigcap_{i\in I}U_i.
\]
If $V\overset{j}{\to}X$is the inclusion of an open set, then whenever G is a sheaf over V,
we define the sheaf $j_\ast \mathcal G$ by the formula
\[
j_\ast \mathcal G(U)=\mathcal G(V\bigcap U).
\]
We also introduce the sheaf $j_\ast \mathcal F$, sometimes written $\mathcal F_V$; it is called the restriction
of $\mathcal F$ to V. To an open set $U \subset V$, this sheaf associates $\mathcal F(U)$. For every
open set $U_I$ of X, let $j_I$ be the inclusion of $U_I$ in X, and let
\[
\mathcal F_I := j_{I_\ast}\mathcal F_{U_I}.
\]
We then define
\[
\mathcal F^k =\bigoplus \limits_{|I|=k+1}\mathcal F_I
\]
and $d : \mathcal F^k \to \mathcal F^{k+1}$ by the formula
\[
(d\sigma)_{j_0,\dots,j_{k+1}}=\sum \limits_ i (-1)^i \sigma_{j_0,\dots,\check{j}_i,\dots,j_{k+1}|U\bigcap U_{j_0,\dots,j_{k+1}}},j_0,<\dots<j_{k+1}
\]
which is valid for $\sigma=(\sigma _I)$,$\sigma _I\in \mathcal F_I(U)=\mathcal F(U \bigcap U_I)$.We easily check
that $d \circ d = 0$. Let us also define $j : \mathcal F \to \mathcal F^0$ by $j(\sigma)_i = \sigma_{|U\bigcap U_i}$ for $\sigma \in \mathcal F(U)$.

\begin{prop}
	The complex
	\begin{align}
	\label{eq1}
		0 \to \mathcal F^0 \overset{d}{\to} \mathcal F^1 \overset{d}{\to} \cdots \overset{d}{\to} \mathcal F^n \overset{d}{\to} \mathcal F^{n+1} \cdots
	\end{align}
	is a resolution of $\mathcal F$.
\end{prop}
We call this resolution the \v{C}ech resolution of $\mathcal F$ associated to the covering $U_i$
of X. The functorial nature of this resolution renders it very useful.
\begin{proof} 
	The injectivity of $j$ is due to the property of uniqueness of the sections
	of $F$ having given restriction to the $U_i$. The fact that Im $j$ can be identified with
	the kernel of $d$ on $\mathcal F^0$ is exactly equivalent to the fact that sections of $F$ on
	$U \bigcap U_i$ which coincide on the intersections glue together to form a section of
	$\mathcal F$ on $U$. The exactness in general can be checked stalk by stalk, as follows. Let
	$x \in X$, and let $i$ be such that $x \in U_i$. We then define
	\[
	\delta : \mathcal F^k_x \to \mathcal F^{k-1}_x 
	\]
	for $k \ge 1$ by the following formula. An element $\sigma \in \mathcal F^k_x$ is represented by a
	series of germs $\sigma _I \in \mathcal F(V_I \bigcap U_I)$ for $|I|= k + 1$, where $V_I$ is an open set
	containing $x$ which we can assume is contained in $U_i$. We then define $\delta \sigma$ by
	\begin{align}
	\label{eq2}
	(\delta \sigma)_{i_0,\dots,i_{k-1}}=\epsilon \sigma_{i,i_0,\dots,i_{k-1}}, i_0<\dots<i_{k-1}
	\end{align}
	where $\epsilon$ is the signature of the permutation reordering
	the set

	\noindent
	$\{i,i_0,\dots,i_{k-1}\}$.
	We use the convention that $\sigma_{i,i_0,\dots,i_{k-1}}=0$ if $i\in \{i,i_0,\dots,i_{k-1}\}$. To see that equation \ref{eq2} makes sense, we need to see that the right-hand term defines a germ of a section
	of $j_{i_0,\dots,i_{k-1}\ast}\mathcal F$ on the neighbourhood of $x$. But as each $V_I$ is contained in $U_i$,
	we have $V_{i,i_0,\dots,i_{k-1}}\bigcap U_{i_0,\dots,i_{k-1}}=V_{i,i_0,\dots,i_{k-1}}\bigcap U_{i,i_0,\dots,i_{k-1}}$, so that $\sigma_{i,i_0,\dots,i_{k-1}}$ can be seen as a section of $j_{i_0,\dots,i_{k-1}\ast}\mathcal F$ on $V_{i,i_0,\dots,i_{k-1}}$. We immediately check that
	$d\circ \delta + \delta \circ d=Id$ on $\mathcal F^k_x$ for $k \ge 1$. This implies the exactness of the complex
	\ref{eq1} at the point $x$.
\end{proof}

\paragraph{de Rham resolution}

Let $X$ be a $ \mathcal{C}^{\infty}$ differentiable manifold.
$ \mathcal{A}^k$ be the sheaf of $ \mathcal{C}^{\infty}$ differential
forms, i.e. the sheaf of sections of the bundle $\Omega^k_{X,\mathbb{R}}$. 
The exterior differential $d$ is a morphism of sheaves $ \mathcal{A}^k$.
Notice that the constant sheaf $ \mathbb{R}$ is natually included in
$ \mathcal{A}^0$, and the kernal of $d:\mathcal{A}^0\to \mathcal{A}^1$
consist precisely of the locally constant functions. Thus we have the
following theorem:

\begin{prop}
    The complex
    $$ 0\to \mathcal{A}^0\to \mathcal{A}^1\to \text{...}\to \mathcal{A}^n\to 0$$
    where $n=\text{dim}X$ is a resolution of the constant sheaf $ \mathbb{R}$.
\end{prop}

\paragraph{The Dolbeault resolution}

Let $X$ be a complex manifold and $E\to X$ be a holomorphic vector bundle.
Let $ \mathcal{E}$ be the associated sheaf of free $ \mathcal{O}_X$-module.
Let $ \mathcal{A}^{0,q}(E)$ be the sheaf of $ \mathcal{C}^{\infty}$ sections
of $\Omega^{p,q} \otimes E$. Then the $\bar{\partial}$ operator defines
morphisms $ \mathcal{A}^{0,q}\to \mathcal{A}^{0,q}$. Note that the kernal
$ \bar{\partial} :\mathcal{A}^{0,0}\to \mathcal{A}^{0,1}$
is $ \mathcal{E}$. Note also that by $\bar{\partial}$-Poinc\`{a}re lemma,
sections in above is $\bar{\partial}$-closed if and only if it is
$\bar{\partial}$-exact. Hence we have

\begin{prop}
    The complex
    $$ 0\to \mathcal{A}^{0,0}(E)\to \mathcal{A}^{0,1}(E)\to \text{...}\to \mathcal{A}^{0,n}(E)\to 0 $$
    where $n=\text{dim}_{ \mathbb{C}} X$ is a resolution of the sheaf $ \mathcal{E}$.
\end{prop}

\section{Abelian Categories}

\begin{defi}
    An abelian category $\mathcal{C}$ is a category satisfying the following
    conditions:
\end{defi}

\begin{itemize}
	\item
	For every pair of objects $A, B$ of $\mathcal{C}$ , Hom$(A, B)$
	is an abelian group, and the composition of morphisms
	$$ \text{Hom} (A, B) \times \text{Hom} (B, C) \to \text{Hom} (A, C) $$
	is bilinear for these abelian groupstructures.

	\item
	Every morphism $\phi : A\to B$ admits a kernel and a cokernel;
	the kernel of
	$\phi$ is an object $\mathcal{C}$ written Ker$\phi$, 
	equipped with a morphism $\chi: C \to A$, such
	that for every object $M$ of $\mathcal{C}$, left composition with $\chi$
	induces an isomorphism
	$$\text{Hom}(M,C)\cong \{\psi\in\text{Hom}(M,A)|\phi\circ\psi = 0\}. $$
	Diagramatically:
	$\xymatrix{
	A \ar[r]^\phi & B \\
	\text{Ker}\phi=C \ar[u]^\chi & M \ar[l]\ar[ul]^\psi
	}$

	Similarly, the cokernel of $\phi$ is an object $D$, written Coker$\phi$,
	equipped with a
	morphism $\chi:B\to D$, such that for every object M of C, right composition
	with $\chi$ induces an isomorphism
	$$\text{Hom}(D,M)\cong \{\psi\in \text{Hom}(B,M)|\psi\circ\phi=0\}$$
	Diagramatically:
	$\xymatrix{
	A \ar[d]^\phi 			& M \\
	B \ar[ur]^\psi 	& D=\text{Coker}\phi \ar[l]^\chi \ar[u]
	}$

	\item
	A morphism $\phi: A\to B$ is said to be \textbf{injective} if $\text{Hom}(\text{Ker}\phi,A) = \{0\}$.
	\item
	The image of a morphism $\phi$ can be defined as the cokernel of
	its kernel or as the kernel of its cokernel. ( \textit{image} in
	the sense of isomorphism.)

	\item
	Direct sums exist; the direct sum $A\otimes B$ is such that for
	every object $M$ of $\mathcal{C}$, we have
	$$ \text{Hom}(M,A\otimes B)=\text{Hom}(M,A)\otimes \text{Hom}(M,B)$$
	$$ \text{Hom}(A\otimes B,M)=\text{Hom}(A,M)\otimes \text{Hom}(B,M)$$
\end{itemize}

The standard examples of abelian categories are the category of abelian groups
and their morphisms, and the category of modules over a given ring. If $X$ is
a topological space, the category of sheaves of abelian groups or sheaves of
$\mathcal{A}$-modules, where $\mathcal{A}$ is a sheaf of rings over $X$, 
is also abelian

\begin{ex}
Let $X$ be a topological space. The functor $\Gamma$ from the category
of sheaves of abelian groups over $X$ to the category of abelian groups, which to
a sheaf $F$ of abelian groups over $X$ associates the group of its global sections
$\mathcal F(X)$, is left-exact.
\end{ex}
Let $A, B,C$ be three objects of $\mathcal{C}$ , and let $\phi : A \to B,\psi : B \to C$ be morphisms.

\begin{defi}
	We say that the sequence
	\[
	0 \to A \overset{\phi}{\to} B\overset{\psi}{\to} C \to 0
	\]
	is a short exact sequence if $A \overset{\phi}{\to} B$ is isomorphic to the kernel of $\psi$ and
	$B\overset{\psi}{\to} C$ is isomorphic to the cokernel of $\phi$. 
\end{defi}
\textbf{Note}:The kernel Ker $\psi$ of $\psi$ is an object
of $\mathcal C$ equipped with a morphism $\chi:Ker \psi \to B$. The isomorphism above is an
isomorphism $i : A \cong Ker \psi$ such that $\chi \circ i =\phi$. The analogous notion holds
for the cokernel, i.e.
$$ A \overset{i}{\cong} \text{Ker}\psi \overset{\chi}{\to} B.$$

\begin{defi}
	An object $I$ of an abelian category is called injective if for
	every injective morphism $A\overset{j}{\to}B$ and for every morphism $\phi : A \to I$, there
	exists a morphism $\psi : B \to I$ such that $\psi \circ j =\phi$.
\end{defi}
$$ \xymatrix{
	A\ar[d]^\phi \ar[r]^j & B\ar[dl]^\psi \\
	I
}$$
\begin{ex}
	The injective objects in the category of abelian groups are the divisible groups $G$,
	i.e. those such that for every $g \in G$ and every $n \in \mathbb N^\ast$, there exists $g' \in G$ such
that $ng' = g$.
\end{ex}
%\marginpar{Question!}
% Def 4.24, pp.97 of \ref{voisin}
\begin{defi}
	The degree $i$ cohomology of a complex $(M^\cdot,d_M)$ is the object
	$$ H^i(M^\cdot):= \text{Coker}\left(d^{i-1}_M: M^{i-1}\to 
	\text{Ker}d^i_M \right)$$
\end{defi}

% P 97 of \ref{voisin}
\begin{defi}
	A homotopy $H$ between two morphisms of complexes $\phi^\cdot:(M^\cdot,d_M)\to(N^\cdot,d_N)$ and $\psi^\cdot:(M^\cdot,d_M)\to(N^\cdot,d_N)$ is a collection of morphisms
	\[
	H^\cdot:M^\cdot \to N^{\cdot -1}
	\]
	satisfying
	\begin{align}
	\label{eq4.6}
	H^{i+1}\circ d^i_M+d^{i-1}_N\circ H^i=\phi^i-\psi^i, \forall i\ge 0.
	\end{align}
\end{defi}

If there exists a homotopy between two morphisms of complexes $\phi^\cdot:(M^\cdot,d_M)\to(N^\cdot,d_N)$ and $\psi^\cdot:(M^\cdot,d_M)\to(N^\cdot,d_N)$, then the induced morphisms
$H^i(\phi^\cdot)$ and $H^i(\psi^\cdot)$ are equal. Indeed, relation \ref{eq4.6} shows that $\phi^i \to \psi^i : Ker d^i_M \to N^i$ factors through $d^{i-1}_N$, and thus induces 0 in Hom(Ker $d^i_M$,Coker $d^{i-1}_N$).

\begin{defi}
    A complex $M^i, i\geq 0$ is called a resolution of an object $A$ of 
    $\mathcal{C}$ if $\text{Im }d^i = \text{Ker }d^{i+1}$, and there exist an 
    injective morphism $j:A\to M^0$ such that $j:A\to M^0$ is isomorphic to
    $\text{Ker }d^0$.
\end{defi}

\begin{defi}
    An abelian category $\mathcal{C}$  has sufficently many injective objects
    if every object $A$ of $\mathcal{C}$  admits an injective morphism
    $j:A\to I$, where $I$ is injective.
\end{defi}

\begin{lemma}
    If $\mathcal{C}$ has sufficently many injective objects, then every
    object of $\mathcal{C}$ admits an injective resolution, i.e. a
    resolution $I^\cdot$ by a complex all of whose objects are injective
    objects.
\end{lemma}
\begin{proof}
	See Lemma 4.26 of book \cite{voisin}.
\end{proof}

\begin{prop}
	Let $I^\cdot$, $A\overset{i}{\to} I^0$, and $J^\cdot$, 
	$B\overset{j}{\to}J^0$ be resolutions of $A,B$ respectively,
	and let $\phi:A\to B$ be a morphism. Then if the second
	resolution is injective, there exists a morphism of complexes
	$\phi^\cdot : I^\cdot \to J^\cdot$ satisfying
	$\phi^0 \circ i=j\circ \phi$. Moreover, if we have two
	such morphisms $\phi^\cdot$ and $\psi^\cdot$, there exists
	a homotopy $H^\cdot$ between $\phi^\cdot$ and $\psi^\cdot$.
\end{prop}
Diagramatically:
$$ \xymatrix{
A \ar[r]^i\ar[d]^\phi	& I^0\ar[r]^i\ar[d]^{\phi^0} & I^1 \ar[r]\ar[d] &...\\
	B \ar[r]^j 	& J^0\ar[r]^j 	& J^1 \ar[r] &...\\
}$$
\begin{proof}
	See Proposition 4.27 of book \cite{voisin}.
\end{proof}

In particular, appying this proposition to the case where $I^\cdot$ and
$J^\cdot$ are two injective resolution of $A$, we obtain morphism
$\phi^\cdot: I^\cdot \to J^\cdot$ and $\psi^\cdot: J^\cdot \to I^\cdot$ 
such that $\psi^\cdot\circ \phi^\cdot$ and $\phi^\cdot\circ \psi^\cdot$
are morphisms of complexes (from $I^\cdot$ to itself and from $J^\cdot$
to itself respectively), which are both homotopic to the identity.
We then say that $\phi^\cdot$ is a homotopy equivalence. Thus, we see that
an injective resolution is unique up to homotopy equivalence.

\section{Derived functors}
Let $\mathcal{C}$  and $\mathcal{C'}$  be two abelian categories, and let
$F$ be a left-exact functor from $\mathcal{C}$ 
to $\mathcal{C'}$ . Assume that $\mathcal{C}$  has sufficiently many injective objects.

\begin{thm}
	For every object $M$ of $\mathcal{C}$, there exist objects 
	$R^i F(M)$, $i\geq 0$ in $\mathcal{C'}$, determined up to isomorphism
	, satisfying the following conditions
	\begin{itemize}
		\item We have $R^0 F(M) = F(M)$.
		\item For every short exact sequence
			$$ 0\to A\overset{\phi}{\to} B\overset{\psi}{\to}
			C \to 0$$
		in $\mathcal{C}$ , we can construct a long exact sequence
		(i.e. an exact complex) in $\mathcal{C'}$:
		$$ 0\to F(A) \overset{\phi}{\to} F(B) \overset{\psi}{\to}
		F(C) \to R^1 F(A) \to R^1 F(B) \to R^1F(C) \to \cdots.$$
		\item
		For every injective object $I$ of $\mathcal{C}$, we
		have $R^iF(I)=0$, $i>0$.
	\end{itemize}
\end{thm}
\begin{proof}
	See Theorem 4.28 of book \cite{voisin}.
\end{proof}

\begin{lemma}
    If
    $$ 0\to A \overset{\phi}{\to} B \overset{\psi}{\to} C\to 0 $$
    is a short exact sequence in $\mathcal{C}$ , then there exist injective
    resolutions $I^\cdot$, $J^\cdot$, $K^\cdot$ of $A,B,C$ respectively,
    and an exact sequence of complexes
    $$ 0\to I^\cdot \overset{\phi^\cdot}{\to} J^\cdot \overset{\psi^\cdot}{\to} 
    K^\cdot\to 0$$
    with $\phi^0 \circ i = j\circ \phi$, $\psi^0\circ j=k\circ\psi$.
\end{lemma}
\begin{proof}
	See Lemma 4.29 of book \cite{voisin}.
\end{proof}

%P101 prop 4.30
\begin{prop}
If $\phi:A\to B$ is a morphism in $\mathcal{C}$ , and $I^.$, $J^.$ are injective resolutions of A and B respectively, then there exists a canonical morphism induced by $\phi$,
$$R^iF(\phi):R^iF(A)\to R^iF(B)$$
where the derived objects are computed using the chosen resolutions.
\end{prop}
\begin{proof}
	See Proposition 4.30 of book \cite{voisin}.
\end{proof}
In practice, injective resolutions are difficult to manipulate. The following
result shows how to replace injective resolutions by resolutions satisfying a
weaker condition.

\begin{defi}[F-acyclic object]
We say that an object $M$ of $\mathcal{C}$ is acyclic for the functor F (or F-acyclic) if we have $R^iF(M)=0$ for all $i>0$.
\end{defi}

\begin{prop}
	Let $M^.$, $i: A\to M^0$ be a resolution of A, where the $M^i$ are acyclic for the functor F. Then $R^i F(A)$ is equal to the cohomology $H^i(F(M^.))$ of the complex $F(M^.)$ .
\end{prop}
\begin{proof}
	See Proposition 4.32 of book \cite{voisin}.
\end{proof}
\section{Sheaf cohomology}
 From now on, we consider the category of sheaves of abelian groups over a topological space $X$, and the functor $\Gamma$ of “global sections” which to $\mathcal{F}$ associates$\Gamma (X,\mathcal{F})=\mathcal{F}(X)$, with values in the category of abelian groups.

\begin{lemma}
The category of sheaves of abelian groups has sufficiently many injective objects.
\end{lemma}
\begin{proof}
	See section 4.3 of book \cite{voisin}.
\end{proof}

\begin{defi}[flasque sheaf]
A sheaf $\mathcal{F}$ is said to be flasque if for every pair of open sets $V\subset U$ , the restriction map $\rho _{UV} : \mathcal{F}(U) \to \mathcal{F}(V)$ is surjective.
\end{defi}

\begin{prop}
Flasque sheaves are acyclic for the functor $\Gamma$ .
\end{prop}
\begin{proof}
	See Proposition 4.34 of book \cite{voisin}.
\end{proof}
\begin{lemma}[Godement resolution]
The Godement resolution of $\mathcal{F}$ is constructed by considering the inclusion of $\mathcal{F}$ into the sheaf $\mathcal{F}_{God}$

$$ U\mapsto \mathcal{F}_{God}(U)=\bigoplus_{x\in U} \mathcal{F}_x$$
where the sum is actually the infinite direct product. This sheaf is obviously flasque. We then inject the quotient $\mathcal{F}_{God} /F$ into the flasque sheaf $(\mathcal{F}_{God}/\mathcal{F})_{God}$ , and so on.
\end{lemma}

\begin{proof}
	See page 103 of book \cite{voisin}.
\end{proof}
\begin{defi}[fine sheaf]
A fine sheaf $\mathcal{F}$ over $X$ is a sheaf of $\mathcal{A}$-modules, where $\mathcal{A}$ is a sheaf of rings over $X$ satisfying the property:
For every open cover $U_i$
,$i\in I$ of $X$ , there exists a partition of unity $f_i$
,$i\in I$ , $\Sigma f_i=1$ (where the sum is locally finite), subordinate to this covering.
\end{defi}

\begin{prop}
	If $\mathcal{F}$ is a fine sheaf , we have $H^i(X,\mathcal{F})=0$ , $\forall i>0$.
\end{prop}
\begin{proof}
	See Proposition 4.36 of book \cite{voisin}.
\end{proof}

\begin{coro}
Let $X$ be a $\mathcal{C}^{\infty}$ manifold. Then
$$H^k(X,\mathbb{R})=Ker(d:A^k(X)\to A^{k+1}(X))/Im(d:A^{k-1}(X)\to A^k(X))$$
where $A^i(X)$ is the real vector space of differential forms of degree i. A similar statement holds for the complex cohomology.
\end{coro}
\begin{proof}
	See Corollary 4.37 of book \cite{voisin}.
\end{proof}

\begin{coro}
Let $E$ be a holomorphic vector bundle over a complex manifold $X$, and let $\mathcal{E}$ be the sheaf of holomorphic sections of $E$. Then
$$H^q(X,\mathcal{E})=Ker(\bar{\partial}:A^{0,q}(E)\to A^{0,q+1}(E))/Im(\bar{\partial}:A^{0,q-1}(E)\to A^{0,q}(E))$$
\end{coro}
\begin{proof}
	See Corollary 4.38 of book \cite{voisin}.
\end{proof}

\begin{coro}
If $E$ is as above , we have $H^q(X,E)=0$ for $q>n=dim X$.
\end{coro}
\begin{proof}
	See Corollary 4.39 of book \cite{voisin}.
\end{proof}
We will now introduce the \v{C}ech cohomology, which is extremely useful in 
practice, since it gives a uniform way of computing cohomology groups, unlike
the de Rham type resolutions, which specifically concern constant sheaves over
manifolds. Let $\mathcal{F}$  be a sheaf of abelian groups over a topological space $X$. Let $U=(U_i)_{i\in \mathbb{N}}$ be a countable ordered open covering of X.

\begin{defi}
Define $\check{H}^q(\mathcal{U} ,\mathcal{F})$ to be the qth cohomology group of the complex of global sections
$$C^q(\mathcal{U} ,\mathcal{F})=\bigoplus_{|I|=q+1} \mathcal{F}(U_I)$$
of the $\check{C}ech$ complex associated to the covering $\mathcal{U}$.
\end{defi}

\begin{thm}
If the open sets $U_I=\bigcap_{i\in I} U_i$ satisfy $H^q(U_I,\mathcal{F})=0$ for all $q>0$, then
$$H^q(X,\mathcal{F})=\check{H}^q(\mathcal{U},\mathcal{F}) , \forall q\ge 0$$
\end{thm}
\begin{proof}
	See Theorem 4.41 of book \cite{voisin}.
\end{proof}

\begin{thm}
If X is separable, then by passage to the direct limit, the morphisms
$$\check{H}^q(\mathcal{U},\mathcal{F})\to H^q(X,\mathcal{F})$$
induce an isomorphism
$$\underset{  \overset{\to}{\mathcal{U}}   }{lim}\check{H}^q(\mathcal{U},\mathcal{F})\cong H^q(X,\mathcal{F})$$
\end{thm}
\begin{proof}
	See Theorem 4.44 of book \cite{voisin}.
\end{proof}
% ------------------------------------------------------------------------
% \section{unknown}
% 
% \begin{thm}
% If the open sets $U_I=\bigcap \limits_{i\in I}U_i$ satisfies $H^q(U_I,\mathcal{F})=0$,for all $q>0$,then $H^q(X,\mathcal{F})=\check{H}^q(\{U_i\},\mathcal{F}) ~\forall q\ge 0$.
% 
% \end{thm} 
% 
% 
% \begin{defi}
% A double complex in an abelian category A is given by a collection of objects $K^{p,q}(p,q)\in \mathbb{Z}^2$,together with morphisms(called differentials)$D_1:K^{p,q} \rightarrow K^{p,q+1}$,$D_2:K^{p,q} \rightarrow K^{p,q+1}$ satisfying the relations $D_1\circ D_1=0,D_2\circ D_2=0,D_1\circ D_2=D_2\circ D_1$.
% \end{defi}
% 
% Suppose the double complex $K$ satisfies the following finiteness condition: $\exists p_0,q_0\in \mathbb{Z}$ such that $K^{p,q}=0$ for $p\ge p_0$ or $q\ge q_0$.We then construct the following complex:
% $K^n=\bigoplus \limits_{p+q=n}K^{p,q},D=D_1+(-1)^p D_2$ over $K^{p,q}\subset K^n$.
% The finiteness condition ensures that the direct sum is finite. There is an element of arbitrariness in the choice of the signs of the differential $D$. The sign $(-1)^p$ is placed here in order to ensure that $D\circ D=0$ . There is a variation on this construction,in the case where the differentials $D_i$ anticommute instead of commuting:we then set
% $D=D_1+D_2$.
% 
% 
% \begin{defi}
% The complex $(K^\bullet,D)$ is the simple complex associated to the double complex$(K^{\bullet,\bullet},D_1,D_2)$
% \end{defi}
% 
% \begin{proof}
%     Take a flasque resolution $I^\bullet$ of $\mathbb{F}$. For each $I^l(l\ge 0)$,we can consider the Cech resolution $I^{l,\bullet}$ of $I^l$ associated to the covering $\{U_i\}$. By the functoriality of the Cech resolution,the $I^{\bullet,\bullet}$ form a double complex. Moreover,the $I^{l,\bullet}$ are acyclic,since we have $I^{l,k}=\bigoplus \limits{|J|=k+1}j_{J_\ast}(I_{U_J}^l)$ ,so that $I^{l,k}$ is flasque,and thus acyclic (Flaque sheaves are acyclic for the functor $\Gamma$ ).
% \end{proof}

\begin{thebibliography}{1}
	\bibitem{voisin} C. Voisin. Hodge Theory and Complex Algebraic
	Geometry I, Cambridge University Press.
	\bibitem{huybrechts} Daniel Huybrechts. Complex Geometry - An
	Introduction, Springer.
\end{thebibliography}

\end{document}

### 2016-07-24 Draft/draft.tex
Adding notes for A.Zee's QFT in a Nutshell

@@
 \usepackage{fancyref} % For lazy reference \fref
-\usepackage{hyperref} % For hyperlink everything.
+\usepackage[unicode]{hyperref} % For hyperlink everything.
 \usepackage{CJKutf8} % For Chinese characters
@@
 % In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
+
+\section{Quantum Field Theory}
+\label{sec:Quantum_Field_Theory}
+    \subsection{Relatvistic Quantum Mechanics}
+    \label{sec:Relatvistic_Quantum_Mechanics}
+
+    \subsubsection{2.1 Quantum Mechanics}
+    \label{sec:2.1_Quantum_Mechanics}
+    This part sumarize the axioms of quantum mechanics. (Omitted)
+    However, one class of important but seldom mentioned operator,
+    the antilinear operators and the antiunitary operators are not
+    discussed here but postponed to the next part.
+
+    \subsubsection{2.2 Symmetries}
+    \label{sec:2.2_Symmetries}
+    This part discribe some important theorems concerning the symmetries
+    in quantum mechanics.
+
+    Firstly, symmetries in quantum mechanics some times requires the use
+    of antilinear and antiunitary operators.
+
+    \paragraph{Antilinear and Antiunitary}
+    Antilinear operators: $U (\lambda A + \upsilon B)
+                            = \lambda^* UA + \upsilon^* UB$.
+
+    Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$
+
+    The adjoint operator of an antilinear operator requires special
+    attention:
+    $$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
+    (The usual definition will become troublesome since the LHS will
+    be antilinear in $\phi$, whereas the RHS is linear.)
+
+    Thankfully, the criterion for unitarity or antiunitarity is the same:
+    $$U^\dagger = U^{-1}$$
+
+    An important example is those symmetries which can be infinitesimally
+    close to identity. In the vincinity of unity, it is:
+    $$ U =1+i\epsilon t $$
+    where $t$ is Hermitian and linear.
+    % TODO why is it Hermitian?
+
+    \paragraph{Symmetry Group and its Representation} The set of all
+    symmetries transformations obviously can have a group structure.
+    By giving each symmetry transformation a unitary or antiunitary
+    operator, a representation of such group is obtained. However,
+    such a representation can be projective (projective as in
+    projective geometry, or $\mathbb{CP}^n$), since operators acts
+    on ket spaces, which is already projective (within a freedom of
+    phase).
+
+    If the phase is taken into consideration, it is found that this
+    phase is independent of the ket that the operator acts on:
+    \begin{align}
+        \label{eq:2.2_symmetries_projective_phase}
+        U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
+    \end{align}
+    Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
+    transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
+    on $T_1 T_2$.
+
+    Howver, there is one exception to this rule. It exists when the
+    state $\Psi$ is not the linear some of some other wave functions.
+    That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
+    This seems incomprehesible to me.
+    % TODO Understand this!
+    There are some link on page 53
+    between the structure of Lie group associated
+    with this symmetry and whether the representation can be projective.
+    \footnote{Though not state, it can be infered that a representation
+    can be made not-projective by a good choice of $U(T)$, so that
+    $\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }
+
+    \paragraph{Connected Lie group} is of special importance in physics.
+    However, the books description obfuscate the mathematical description
+    of this structure. I will update this note later to remedy such
+    % TODO update this part.
+    discussion. The message I understand is that the representation is
+    tightly bound to the Lie algebra. An important example is that when
+    $$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
+    $$ [t_b,t_c] = 0$$
+    then
+    $$ U(T(\theta)) = \exp(it_a \theta^a) $$
+
+    \subsubsection{2.3 Quantum Lorentz Transformations}
+    \label{sec:2.3_Quantum_Lorentz_Transformations}
+    \textbf{Note}: although the title suggests "quantum", this part is
+    mostly classical.
+
+    Starting with the invariance of interval:
+    \begin{align}
+        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
+        \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
+    \end{align}
+    or equivalently % TODO why equivalently?
+    \begin{align}
+        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+        \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
+            \frac{\partial x'^\nu}{\partial x^\sigma}
+            =
+        \eta_{\rho\sigma}
+    \end{align}
+    It claims that any coordinate transformation satisfying 
+    \ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+    must be linear.
+
+    Such linear Lorentz transformations satisfy:
+    \begin{align}
+        T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
+            T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
+    \end{align}
+    where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
+    transformations.
+
+    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
+    equations that relate it with $\eta_{\mu\nu}$.
+
+    Note that:
+    \[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
+    And:
+    \begin{equation}
+        \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
+        (\Lambda^{-1})\indices{^\rho_\nu} = 
+            \Lambda\indices{_\nu^\rho} = 
+            \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
+    \end{equation}
+
+    The only part about quantum mechanics here, is that the operators
+    corresponding to the Lorentz transformations, have the property that:
+    \begin{equation}
+        U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
+            U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
+    \end{equation}
+    where $a$ represents the translation.
+
+    The group of Lorentz transformations is very important. There is:
+        %\text{sssssss} & B
+    \[
+        \xymatrix{ 
+        \text{Poincar\'e Group}  \\
+        \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
+        \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
+        }
+    \]
+    The important \textit{proper orthochronous Lorentz group} consists
+    of those $\Lambda$ with $\det \Lambda = 1$ and 
+    $\Lambda\indices{^0_0} \geq 1$.
+
+    We have also $ \mathscr{P}$, the space inversion matrix. And
+    \(\mathscr{T}\), the time-reversal matrix. The definition for
+    both can be easily written.
+
+    A important rule is that all homogeneous Lorentz transformations can
+    are generated by 
+    \(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
+    However this property is not proved
+
+    \paragraph{Digression about tensor notation} It seems that phsysicists
+    have not settled down on their notation for tensors. Weinberg using
+    the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
+    so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
+    tangent vector. I see that this notation helps to distinguish the
+    type of arguments. This is unnecessary, since the upper and lower
+    indices already fulfill this function. Another benefit is that it
+    conveies the process of lowering of raising a index.
+
+    However, this idea that each slot in tensor indices are distinct
+    and can be lowered and raised seperatly, is not even mentioned
+    in some modern mathematical physics book.
+
+    Helpful link:
+    \href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
+    \href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.
+
+    \subsubsection{2.4 The Poincar\'{e} Algebra}
+    \label{sec:2.4_The_Poincare_Algebra}
+    \textbf{I am lost in this part.} The general idea seems to develop, in a 
+    infinitesimal sense, the property of a Lorentz transformation.
+    For a infinitesimal Lorentz transformation:
+    \begin{align}
+        U(1+\omega, \epsilon) = 
+            1+ \frac{1}{2} i\omega_{\rho\sigma}J^{\rho\sigma}
+            -i\epsilon_\rho P^\rho + \cdots
+    \end{align}
+    where $J$ and $P$ are independent of the infinitesimal value
+    $\omega$ and $\epsilon$.
+
+    Later $P$ is identified as the energy-momentum operator (with
+    $P^0$ being the energy operator), and $J^{23}$, $J^{31}$,
+    \(J^{12}\) are identified with the angular momentum operator.
+    However, the reason for this identification is not provided. 
+    % TODO why P is energy momentum, and J is angular momentum
+
+    Later, it was eatablished that $J$ and $P$ satisfy:
+    \begin{align}
+        i[J^{\mu\nu},J^{\rho\sigma}] &=
+            \eta^{\nu\rho}J^{\mu\sigma} - \eta^{\mu\rho}J^{\nu\sigma}
+            -\eta^{\sigma\mu}J^{\rho\nu} + \eta^{\sigma\nu}J^{\rho\mu}
+        \\
+        i[P^\mu,J^{\rho\sigma} &=
+            \eta^{\mu\rho}P^\sigma - \eta^{\mu\sigma}P^{\rho}
+        \\
+        [P^\mu,P^\rho] &= 0
+    \end{align}
+    This is called the \textit{Lie Algebra} of the Poincar\'{e}
+    group.
+    The relation \([P^\mu,P^\rho] = 0\) is particular interesting.
+
+    With this, the finite translation and a rotation by angle
+    $\theta$ are expressed as:
+    \begin{align}
+        U(1,a) = \exp(-iP^\mu a_\mu) \\
+        U(\theta,0) = \exp(i \mathbf{J}\cdot \theta)
+    \end{align}
+
+    This part ends with a discussion on the low-velocity limit
+    of the Lie Algebra obtained above, i.e. the Galilean algebra.
+
+    \subsection{Note}
+    \label{sec:Note}
+    I will now change to another book: Q.F.T. in a Nutshell by A. Zee.
+
+\section{Quantum Field Theory in a Nutshell}
+\label{sec:Quantum_Field_Theory_in_a_Nutshell}
+    \subsection{Part I: Motivition and Foundations}
+    \label{sec:QFT_in_a_Nutshell.Part_I}
+        \subsubsection{I:2 Path Integral Formulation of Quantum Physics}
+        \label{sec:QFT_in_a_Nutshell_Part_I.2}
+        Here the path integral formulation of quantum mechanics is introduced.
+        The intuition comes from a limiting case of the traditional double 
+        slit electron interference experiment. (\textbf{pp.7 to 10}) Then 
+        it calculates the transition probability $\braket{q_F|e^{-iHT}|q_I}$
+        by divide it into a infinite of steps:
+        \begin{align}
+            \braket{q_F|e^{-iHT}|q_I} = \lim_{N\to \infty}
+            \braket{q_F|e^{iH\delta t}e^{iH\delta t}\cdots e^{iH\delta t}|q_I}
+            (\text{with }N\delta t = T)
+        \end{align}
+
+        For illustration, it calculates this value when 
+        $H=\frac{\hat{p}^2}{2m}$. The result is that:
+        \begin{align*}
+            \braket{q_F|e^{-iHT}|q_I} = \int Dq(t) 
+                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 }
+        \end{align*}
+
+        where:
+        \begin{align}
+            \int Dq(t) \equiv \lim_{N\to \infty} 
+            \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
+            \left( \prod_{k=1}^{N-1} \int dq_k \right)
+        \end{align}
+        It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
+        would have been:
+        \begin{align}
+            \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
+            \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
+                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
+                \nonumber \\
+                &= e^{i \int_0^T dt L(\dot{q}, q)}
+        \end{align}
+        where $L$ is the Lagrangian of the system.
+
+        The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
+        mentions that one often effect a change of coordinate
+        $t \to -it$, called \textit{Wick rotation}, to obtain:
+        \begin{align}
+            Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
+        \end{align}
+        where $H$ is the Hamiltonian of the system.
+        The mathematical rigorious aspect is often ignored.
+
+        It also discuss how this formulation could explain the classical
+        limit of quantum mechanics, i.e. classical mechanics, in a
+        very direct manner. This is related to the saddle point
+        approximation to the integral 
+        \ref{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}.
+
+        \paragraph{Unclear point}
+        Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
+        \ket{p}\bra{p} = 1$. What does it mean by saying
+        "to see that the normalization is correct" (pp. 10 and 11).
+
+        \paragraph{Corresponding pages in draft} pp. 1 to 3.
+
+\section{Miscellnaneous Math}
+\label{sec:Miscellnaneous_Math}
+\subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
+From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. By Aryabhata (http://math.stackexchange.com/users/1102/aryabhata).
+
+I believe this can also be solved using double integrals.
+
+It is possible (if I remember correctly) to justify switching the order of integration to give the equality:
+
+$$\int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dy \Bigg)\, dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
+Notice that
+$$\int_{0}^{\infty} e^{-xy} \sin x\,dy = \frac{\sin x}{x}$$
+
+This leads us to
+
+$$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
+Now the right hand side can be found easily, using integration by parts.
+
+\begin{align*}
+I &= \int e^{-xy} \sin x \,dx = -e^{-xy}{\cos x} - y \int e^{-xy} \cos x \, dx\\
+&= -e^{-xy}{\cos x} - y \Big(e^{-xy}\sin x + y \int e^{-xy} \sin x \,dx \Big)\\
+&= \frac{-ye^{-xy}\sin x - e^{-xy}\cos x}{1+y^2}.
+\end{align*}
+Thus $$\int_{0}^{\infty} e^{-xy} \sin x \,dx = \frac{1}{1+y^2}$$
+Thus $$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty}\frac{1}{1+y^2}\,dy = \frac{\pi}{2}.$$
 
@@
 
-\section{Quantum Field Theory}
-\label{sec:Quantum_Field_Theory}
-    \subsection{Relatvistic Quantum Mechanics}
-    \label{sec:Relatvistic_Quantum_Mechanics}
-
-    \subsubsection{2.1 Quantum Mechanics}
-    \label{sec:2.1_Quantum_Mechanics}
-    This part sumarize the axioms of quantum mechanics. (Omitted)
-    However, one class of important but seldom mentioned operator,
-    the antilinear operators and the antiunitary operators are not
-    discussed here but postponed to the next part.
-
-    \subsubsection{2.2 Symmetries}
-    \label{sec:2.2_Symmetries}
-    This part discribe some important theorems concerning the symmetries
-    in quantum mechanics.
-
-    Firstly, symmetries in quantum mechanics some times requires the use
-    of antilinear and antiunitary operators.
-
-    \paragraph{Antilinear and Antiunitary}
-    Antilinear operators: $U (\lambda A + \upsilon B)
-                            = \lambda^* UA + \upsilon^* UB$.
-
-    Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$
-
-    The adjoint operator of an antilinear operator requires special
-    attention:
-    $$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
-    (The usual definition will become troublesome since the LHS will
-    be antilinear in $\phi$, whereas the RHS is linear.)
-
-    Thankfully, the criterion for unitarity or antiunitarity is the same:
-    $$U^\dagger = U^{-1}$$
-
-    An important example is those symmetries which can be infinitesimally
-    close to identity. In the vincinity of unity, it is:
-    $$ U =1+i\epsilon t $$
-    where $t$ is Hermitian and linear.
-    % TODO why is it Hermitian?
-
-    \paragraph{Symmetry Group and its Representation} The set of all
-    symmetries transformations obviously can have a group structure.
-    By giving each symmetry transformation a unitary or antiunitary
-    operator, a representation of such group is obtained. However,
-    such a representation can be projective (projective as in
-    projective geometry, or $\mathbb{CP}^n$), since operators acts
-    on ket spaces, which is already projective (within a freedom of
-    phase).
-
-    If the phase is taken into consideration, it is found that this
-    phase is independent of the ket that the operator acts on:
-    \begin{align}
-        \label{eq:2.2_symmetries_projective_phase}
-        U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
-    \end{align}
-    Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
-    transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
-    on $T_1 T_2$.
-
-    Howver, there is one exception to this rule. It exists when the
-    state $\Psi$ is not the linear some of some other wave functions.
-    That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
-    This seems incomprehesible to me.
-    % TODO Understand this!
-    There are some link on page 53
-    between the structure of Lie group associated
-    with this symmetry and whether the representation can be projective.
-    \footnote{Though not state, it can be infered that a representation
-    can be made not-projective by a good choice of $U(T)$, so that
-    $\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }
-
-    \paragraph{Connected Lie group} is of special importance in physics.
-    However, the books description obfuscate the mathematical description
-    of this structure. I will update this note later to remedy such
-    % TODO update this part.
-    discussion. The message I understand is that the representation is
-    tightly bound to the Lie algebra. An important example is that when
-    $$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
-    $$ [t_b,t_c] = 0$$
-    then
-    $$ U(T(\theta)) = \exp(it_a \theta^a) $$
-
-    \subsubsection{2.3 Quantum Lorentz Transformations}
-    \label{sec:2.3_Quantum_Lorentz_Transformations}
-    \textbf{Note}: although the title suggests "quantum", this part is
-    mostly classical.
-
-    Starting with the invariance of interval:
-    \begin{align}
-        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
-        \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
-    \end{align}
-    or equivalently % TODO why equivalently?
-    \begin{align}
-        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
-        \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
-            \frac{\partial x'^\nu}{\partial x^\sigma}
-            =
-        \eta_{\rho\sigma}
-    \end{align}
-    It claims that any coordinate transformation satisfying 
-    \ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
-    must be linear.
-
-    Such linear Lorentz transformations satisfy:
-    \begin{align}
-        T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
-            T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
-    \end{align}
-    where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
-    transformations.
-
-    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
-    equations that relate it with $\eta_{\mu\nu}$.
-
-    Note that:
-    \[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
-    And:
-    \begin{equation}
-        \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
-        (\Lambda^{-1})\indices{^\rho_\nu} = 
-            \Lambda\indices{_\nu^\rho} = 
-            \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
-    \end{equation}
-
-    The only part about quantum mechanics here, is that the operators
-    corresponding to the Lorentz transformations, have the property that:
-    \begin{equation}
-        U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
-            U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
-    \end{equation}
-    where $a$ represents the translation.
-
-    The group of Lorentz transformations is very important. There is:
-        %\text{sssssss} & B
-    \[
-        \xymatrix{ 
-        \text{Poincar\'e Group}  \\
-        \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
-        \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
-        }
-    \]
-    The important \textit{proper orthochronous Lorentz group} consists
-    of those $\Lambda$ with $\det \Lambda = 1$ and 
-    $\Lambda\indices{^0_0} \geq 1$.
-
-    We have also $ \mathscr{P}$, the space inversion matrix. And
-    \(\mathscr{T}\), the time-reversal matrix. The definition for
-    both can be easily written.
-
-    A important rule is that all homogeneous Lorentz transformations can
-    are generated by 
-    \(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
-    However this property is not proved
-
-    \paragraph{Digression about tensor notation} It seems that phsysicists
-    have not settled down on their notation for tensors. Weinberg using
-    the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
-    so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
-    tangent vector. I see that this notation helps to distinguish the
-    type of arguments. This is unnecessary, since the upper and lower
-    indices already fulfill this function. Another benefit is that it
-    conveies the process of lowering of raising a index.
-
-    However, this idea that each slot in tensor indices are distinct
-    and can be lowered and raised seperatly, is not even mentioned
-    in some modern mathematical physics book.
-
-    Helpful link:
-    \href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
-    \href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.
-
 \section{Anchor}

### 2016-07-24 Light harvesting/Photosynthesis Course Note.tex
Adding notes for A.Zee's QFT in a Nutshell

@@
 important equation for the evolvement of density matrix in an open system,
-called the "master equation".
-% TODO reference required!
+called the "master equation".\footnote{Suggested reading: 
+PhysRevA.62.033821}
 
@@
         the origin shifted from $0$ to $\alpha$. 
-        % todo substantiate this point!
+        % TODO substantiate this point!
     \item \textbf{Variance}
@@
 the usual electron-phonon interaction term in solid state physics.
-\section{July 15, Friday}
+\section{July 15th, Friday}
 \label{sec:July_15}
@@
 \end{align*}
-% todo check this
+% TODO check this
 And using this relationship, it could be found that the $\ket{\beta}$
@@
 
-Explain for the energy band.
-% todo level repulsion
-
 \textbf{pp.10 }shows a Holstein polaron's phase diagram. 
@@
 % Below the region, large polaron. Above, small polaron.
-% todo what is a large polaron.
+% TODO what is a large polaron.
 Outside the region, there will be two solutions coexisting.
@@
 
-The remaining slides re not be included in this note,
-since they follow the pattern of applying models developed
-by condensed matter physicsists and showing the result.
-Detailed results could be found in the papers provided by
-the teacher.
+The remaining slides are not included in this note,
+because I felt sleepy at that moment. Thankfully the
+attached papers have all the interesting information.
+\section{July 20th, Wed}
+\label{sec:July_20th_Wed}
+In this lecture, the author first explains that the $q=0$ mode is
+de-coupled into a simple Hamiltonian. Then he uses the time-dependent
+variation method developed by Dirac, Frenkel and McLachlan. This method
+solves the equation:
+\begin{align}
+    \label{eq:}
+    \braket{\delta \Psi| i\hbar \dot{\Psi} - H\Psi} = 0
+\end{align}
+with the constraint of $\Psi$ being normalized.
+
+It is also established (by McLachlan) that minimize the following
+value:
+\begin{align}
+    \label{eq:July_20th_Wed}
+    ||i\dot{\Psi}-H\Psi||
+\end{align}
+is an alternative option.
+
+Next we introduces three different Ansatzes: $D_1$ (\textbf{pp.3})
+$D_2$ and $\tilda{D}$ (\textbf{pp.4}). The $D_1$ ansatz is most
+numerical demanding. It accouts for the difference of phonons in
+different site of the 
 \section{License}

### 2016-07-27 Algebra/Noetherian Ring.tex
Update QFT in a Nutshell. Move this note outside "Draft.tex".

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage[unicode]{hyperref} % For hyperlink everything.
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage[all]{xy} % For drawing category diagrams
\usepackage{mathrsfs}
\usepackage{nomencl} % For a index of symbols.
\makenomenclature % For a index of symbols.
\title{Noetherian Ring}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    About Noetherian Ring.
}
\tableofcontents

\section{Module}
\label{sec:Module}
(\textbf{pp.117 to 118 of \cite{lang}})
\begin{defi}[Module]
    \nomenclature{$M$ Module}{A left module\nomrefpage.}
Let $A$: ring. $M$ is a nomen left $A$-module if and only if 
\begin{enumerate}
    \item $M$ is an abelian group, usually written additively.
    \item there exists an operation of $A$ on $M$, written as a
        multiplicative monoid, such that, for any $a,b\in A$, any
        $x,y \in M$, we have:
        \begin{align}
            (a+b) x = ax + bx\\
            a(x+y) = ax + ay
        \end{align}
\end{enumerate}
\end{defi}

By definition of an operation, we have $1x = x$. Also, it can be easily
derived that $a(-x) = -ax$, and $0x=0$.

\begin{ex}{Examples of modules}
    \begin{enumerate}
        \item $A$ is a module over itself.
        \item Any commutative group is a $\mathbb{Z}$-module.
        \item Any left ideal of $A$ is a module over $A$, i.e. a left
            $A$-module.
        \item A vector space $V$ over $K$, is basically a $K$-module,
            with the additional structure of $K$ being a field.
        \item Let $V$ be a vector space. 
            Let $R$ be the ring of all linear maps of $V$ into itself.
            Then $V$ is also a module over $R$.
    \end{enumerate}
\end{ex}

\begin{defi}[Submodule]
\nomenclature{Submodule}{\nomrefpage.}
    A submodule $M$ is an additive subgroup such that 
    $AN\subset N$
\end{defi}

\begin{defi}[factor module]
\nomenclature{factor module}{\nomrefpage.}
    Let $M$ be an $A$-module, and $N$ a submodule. 
    A factor module $M/N$ is the factor group $M/N$ (for the
    additive group structure) equipped with a module structure.
    The action of $A$ on $M/N$ is defined by $a(x+N) = ax+N$.
    This is well defined, since if $y$ is in the same coset as
    $x$, then $ay$ is in the same coset as $ax$.
\end{defi}
(\textbf{pp.119 of \cite{lang}})

\section{Noetherian}
\label{sec:Noetherian}
\begin{defi}[Noetherian Module]
    \nomenclature{Noetherian Module}{\nomrefpage.}
    Let $A$: a ring. $M$: a left $A$-module. $M$ is called Noetherian
    if $M$ satisfies any of the following conditions:
    \begin{enumerate}
        \item Every submodule of $M$ is finitely generated.
        \item Every ascending sequences of submodules of $M$
            \[ M_1 \subset M_2 \subset \cdots \]
            such that $M_i \neq M_{i+1}$, is fininte.
        \item Every non-empty set $S$ of submodules of $M$ has a maximal
            element.
    \end{enumerate}
\end{defi}

The equivalence of the above conditions are proved in page 413 to 414 of 
\cite{lang}.

\begin{defi}[Noetherian Ring]
\nomenclature{Noetherian Ring}{\nomrefpage.}
    A ring $A$ is Noetherian if and only if it is Noetherian when
    viewed as a left module over itself.
\end{defi}
(\textbf{pp.415 of \cite{lang}})

The structure of being Noetherian is consistent between a module
and its submodules, factor modules, in the sense of the 
following two propositions.

\begin{prop}
    Let $M$ be a Noetherian $A$-module, then every submodule and
    every factor module of $M$ is Noetherian.
\end{prop}
(\textbf{pp.414 of \cite{lang}})

\begin{prop}
    Let $M$ be a module, $N$ be a submodule. If $N$ and $M/N$ are
    Noetherian, then $M$ is Noetherian.
\end{prop}
(\textbf{pp.414 of \cite{lang}})

The above statements could be summarized by saying that, given an
exact sequence:
\begin{align*}
    \xymatrix{
    0\ar[r] & M'\ar[r]^f & M\ar[r]^g & M''\ar[r] & 0
    }
\end{align*}
$M$ is Noetherian if and only if $M'$ and $M''$ are Noetherian.
This could be seen by two immediate fact of an exact sequence:
\[
    M'\cong \text{Im}f, \text{ } M/\text{Ker}g \cong M''
\]
\printnomenclature

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
    \bibitem{lang} S. Lang. Algebra. 3rd. Springer.
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\end{document}

### 2016-07-27 Draft/draft.tex
Update QFT in a Nutshell. Move this note outside "Draft.tex".

@@
 
-\section{Quantum Field Theory in a Nutshell}
-\label{sec:Quantum_Field_Theory_in_a_Nutshell}
-    \subsection{Part I: Motivition and Foundations}
-    \label{sec:QFT_in_a_Nutshell.Part_I}
-        \subsubsection{I:2 Path Integral Formulation of Quantum Physics}
-        \label{sec:QFT_in_a_Nutshell_Part_I.2}
-        Here the path integral formulation of quantum mechanics is introduced.
-        The intuition comes from a limiting case of the traditional double 
-        slit electron interference experiment. (\textbf{pp.7 to 10}) Then 
-        it calculates the transition probability $\braket{q_F|e^{-iHT}|q_I}$
-        by divide it into a infinite of steps:
-        \begin{align}
-            \braket{q_F|e^{-iHT}|q_I} = \lim_{N\to \infty}
-            \braket{q_F|e^{iH\delta t}e^{iH\delta t}\cdots e^{iH\delta t}|q_I}
-            (\text{with }N\delta t = T)
-        \end{align}
-
-        For illustration, it calculates this value when 
-        $H=\frac{\hat{p}^2}{2m}$. The result is that:
-        \begin{align*}
-            \braket{q_F|e^{-iHT}|q_I} = \int Dq(t) 
-                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 }
-        \end{align*}
-
-        where:
-        \begin{align}
-            \int Dq(t) \equiv \lim_{N\to \infty} 
-            \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
-            \left( \prod_{k=1}^{N-1} \int dq_k \right)
-        \end{align}
-        It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
-        would have been:
-        \begin{align}
-            \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
-            \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
-                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
-                \nonumber \\
-                &= e^{i \int_0^T dt L(\dot{q}, q)}
-        \end{align}
-        where $L$ is the Lagrangian of the system.
-
-        The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
-        mentions that one often effect a change of coordinate
-        $t \to -it$, called \textit{Wick rotation}, to obtain:
-        \begin{align}
-            Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
-        \end{align}
-        where $H$ is the Hamiltonian of the system.
-        The mathematical rigorious aspect is often ignored.
-
-        It also discuss how this formulation could explain the classical
-        limit of quantum mechanics, i.e. classical mechanics, in a
-        very direct manner. This is related to the saddle point
-        approximation to the integral 
-        \ref{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}.
-
-        \paragraph{Unclear point}
-        Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
-        \ket{p}\bra{p} = 1$. What does it mean by saying
-        "to see that the normalization is correct" (pp. 10 and 11).
-
-        \paragraph{Corresponding pages in draft} pp. 1 to 3.
-
 \section{Miscellnaneous Math}
@@
 \subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
-From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. By Aryabhata (http://math.stackexchange.com/users/1102/aryabhata).
+From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. 
+By \href{http://math.stackexchange.com/users/1102/aryabhata}{Aryabhata}.
 

### 2016-07-27 Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update QFT in a Nutshell. Move this note outside "Draft.tex".

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{book}

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage[unicode]{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters
%\usepackage{ dsfont } % For double struck fonts
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage{tensor}  % For tensor indices
\usepackage[all]{xy} % For drawing category diagrams
\usepackage{mathrsfs}

\title{Notes of Quantum Field Theory in a Nutshell}
\date{\today}
\author{we.taper}
\begin{document}
	\maketitle
	\tableofcontents

\chapter{Part I: Motivation and Foundations}
\label{sec:QFT_in_a_Nutshell.Part_I}
\section{I:2 Path Integral Formulation of Quantum Physics}
\label{sec:QFT_in_a_Nutshell_Part_I.2}
Here the path integral formulation of quantum mechanics is introduced.
The intuition comes from a limiting case of the traditional double 
slit electron interference experiment. (\textbf{pp.7 to 10}) Then 
it calculates the transition probability $\braket{q_F|e^{-iHT}|q_I}$
by divide it into a infinite of steps:
\begin{align}
    \braket{q_F|e^{-iHT}|q_I} = \lim_{N\to \infty}
    \braket{q_F|e^{iH\delta t}e^{iH\delta t}\cdots e^{iH\delta t}|q_I}
    (\text{with }N\delta t = T)
\end{align}

For illustration, it calculates this value when 
$H=\frac{\hat{p}^2}{2m}$. The result is that:
\begin{align*}
    \braket{q_F|e^{-iHT}|q_I} = \int Dq(t) 
        e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 }
\end{align*}

where:
\begin{align}
    \int Dq(t) \equiv \lim_{N\to \infty} 
    \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
    \left( \prod_{k=1}^{N-1} \int dq_k \right)
\end{align}
It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
would have been:
\begin{align}
    \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
    \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
        e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
        \nonumber \\
        &=\int Dq(t) e^{i \int_0^T dt L(\dot{q}, q)}
\end{align}
where $L$ is the Lagrangian of the system.

Often, the value we need to calculate is $\braket{F|e^{-iHT}|I}$.
Using $\int \ket{q}\bra{q} dq=1$, we have:
\begin{align}
    \braket{F|e^{-iHT}|I} = \int dq_F \int dq_I
        \braket{F|q_F} \braket{q_F|e^{-iHT}|q_I}\braket{q_I|I}
\end{align}

The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
mentions that one often effect a change of coordinate
$t \to -it$, called \textit{Wick rotation}, to obtain:
\begin{align}
    Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
\end{align}
where $H$ is the Hamiltonian of the system.
The mathematical rigorous aspect is often ignored.

It also discuss how this formulation could explain the classical
limit of quantum mechanics, i.e. classical mechanics, in a
very direct manner. This is related to the saddle point
approximation to the integral 
\ref{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}.

\textbf{Unclear point}
Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
\ket{p}\bra{p} = 1$. What does it mean by saying
"to see that the normalization is correct" (pp. 10 and 11).
Why is effecting the Wick rotation is "somewhat rigorous"?

\textbf{Corresponding pages in draft} pp. 1 to 3.

    \subsection{Appendix 1 - Dirac Delta function and
        \texorpdfstring{$\varepsilon$}{} as infinitesimal
        small value}

    Here the Dirac Delta function is defined as the limit of another
    function $d_K(x)$. Since:
    \begin{align}
        d_K(x) \equiv \int_{-K/2}^{K/2} \frac{dk}{2\pi} e^{ikx} = 
            \frac{1}{\pi x}\sin\frac{Kx}{2}\\
        \int_{-\infty}^{\infty} dx\text{ } d_K(x) = 1
    \end{align}
    Hence we de fine $\delta(x) = \lim_{K\to \infty}d_K(x)$.
    Other important formula include:
    \begin{align}
        \delta(x) = \int_{-\infty}^{\infty} \frac{dk}{2\pi}e^{ikx} \\
        \frac{1}{x+i\varepsilon} = \mathcal{P}\frac{1}{x}-i\pi \delta(x)\\
        \delta(x) = \frac{1}{\pi}\frac{\varepsilon}{x^2+\varepsilon^2}
    \end{align}
    Here $\varepsilon$ is a infinitesimal value. $\mathcal{P}$ denotes the
    principal value integral, defined by:
    \begin{align}
        \int dx \mathcal{P}\frac{1}{x}f(x) = \lim_{\varepsilon\to 0}
            \int dx \frac{x}{x^2+\varepsilon^2}f(x)
    \end{align}
    \subsection{Appendix 2 - Wick theorem in Gaussian 
    Integral}

    This part introduces some very important formulae, listed 
    below:

    (It is very important that $A$ is a real symmetric matrix.)

    \begin{align}
        &\int_{-\infty}^{+\infty} dx
            e^{-\frac{1}{2}ax^2+Jx} =
            \left(\frac{2\pi}{a}\right)^{\frac{1}{2}}
            e^{\frac{J^2}{2a}} 
        \\
        &\int_{-\infty}^{+\infty} \int_{-\infty}^{+\infty} \cdots
        \int_{-\infty}^{+\infty} dx_1 dx_2 \cdots dx_N
            e^{-\frac{1}{2} x^T A x + J^T x} =
            \left( \frac{(2\pi)^N}{\text{det}A} \right)^{\frac{1}{2}}
            e^{\frac{1}{2}J^T A^{-1}J}
        \\
        &\braket{x_i x_j \cdots x_k x_l}
        \equiv
            \frac{
                \int_{-\infty}^{+\infty}\int_{-\infty}^{+\infty}\cdots
                \int_{-\infty}^{+\infty} dx_1 dx_2\cdots dx_N
                e^{-\frac{1}{2}x^T Ax} x_i x_j \cdots x_k x_l}
                {
                \int_{-\infty}^{+\infty}\int_{-\infty}^{+\infty}\cdots
                \int_{-\infty}^{+\infty} dx_1 dx_2\cdots dx_N
                e^{-\frac{1}{2}x^T Ax} }
            \nonumber \\
        &= \sum_{\text{Wick}} 
            (A^{-1})_{ab}\cdots(A^{-1})_{cd}
    \end{align}
    For exmaple:
    \begin{align*}
        &\braket{x^{2n}} \equiv 
            \frac{\int_{-\infty}^{+\infty}dx
            e^{-\frac{1}{2}ax^2} x^{2n}}
            {\int_{-\infty}^{\infty} dx e^{-\frac{1}{2}ax^2}
            }
        = \frac{1}{a^n}(2n-1)!! \\
        &\braket{x_ix_jx_kx_l} = 
        (A^{-1})_{ij}(A^{-1})_{kl}+(A^{-1})_{ik}(A^{-1})_{jl}
        +(A^{-1})_{il}(A^{-1})_{jk}
    \end{align*}
    \textbf{Corresponding pages in draft} pp. 4 to 6.

\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\end{document}

### 2016-07-28 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
New note about QFT in a nutshell. Add some related resource about QFT.

--- 2016-07-27 Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
@@
     \begin{align}
-        &\int_{-\infty}^{+\infty} dx
-            e^{-\frac{1}{2}ax^2+Jx} =
-            \left(\frac{2\pi}{a}\right)^{\frac{1}{2}}
-            e^{\frac{J^2}{2a}} 
-        \\
         &\int_{-\infty}^{+\infty} \int_{-\infty}^{+\infty} \cdots
@@
             e^{\frac{1}{2}J^T A^{-1}J}
+   		\label{eq:QFT_in_a_Nutshell_Part_I.2.appdx1.1}
+		\\
+        &\int_{-\infty}^{+\infty} dx
+        e^{-\frac{1}{2}ax^2+Jx} =
+        \left(\frac{2\pi}{a}\right)^{\frac{1}{2}}
+        e^{\frac{J^2}{2a}} 
         \\
@@
     \end{align}
-    For exmaple:
+    For example:
     \begin{align*}
@@
 
+\section{I:3 From Mattress to Field}
+\label{sec:QFT_in_a_Nutshell_Part_I.3}
+\paragraph{Note} After reading this section and several comments online,
+I realize that this book put more emphasize on physical
+intuition than on mathematical rigor. To illustrate this point, I
+quote a sentence from A. Zee's homepage at UCSB, which comes from
+a review of this book (QFT in a Nutshell):
+
+\begin{quote}
+    "It is often deeper to know why something is true rather than to have a proof that it is true."
+\end{quote}
+
+By above reason, I gave up tracking the calculations done in this
+book.
+
+\paragraph{Mattress in continuum limit} It start with taking the
+limit of lattice spacing $l\to 0$, aiming to write down the field
+equation from the mattress perspective. The process is transparant
+and neatly summarized in the "promotion table" on page 19:
+
+\begin{center}
+\begin{tabular}{| c | c |}
+    \hline
+    function  & $q\to \phi$  \\
+    \hline
+    atom position  & \(a\to x\)  \\
+    \hline
+    dynamic function  & \(q_a(t) \to \phi(t,\mathbf{x})=\phi(x)\)  \\
+    \hline
+    summation  & \(\sum_a \to \int d^D x\)  \\
+    \hline
+\end{tabular}
+\end{center}
+
+In detail, $\sum_a \frac{1}{2} m_a\dot{q}_a^2$ becomes 
+$\int d^2x \frac{1}{2} \sigma (\partial \phi/\partial t)^2$.,
+$\sum_{ab} k_{ab} \frac{1}{2} (q_a-q_b)^2$ becomes
+$\int d^2x \rho( \frac{\partial^2 \phi}{\partial x^2}
+    + \frac{\partial^2 \phi}{\partial y^2})$, and
+
+\begin{align}
+    S(q) &\to S(\phi) \equiv \int_0^T dt \int d^2x \mathcal{L}(\phi)
+    \nonumber \\
+    &= \int_0^T dt \int d^2x \frac{1}{2}
+    \left\lbrace \sigma ( \frac{\partial \phi}{\partial t})^2
+    -\rho \left[ ( \frac{\partial \phi}{\partial x})^2 +
+        \frac{\partial \phi}{\partial x})^2 \right]
+    -\tau\phi^2 -\xi\phi^4 +\cdots \right\rbrace
+\end{align}
+
+% TODO why not odd terms
+Then he notes about the Landau-Ginzburg view:
+
+\begin{quote}
+    we start with the desired symmetry, say Lorentz invariance if we
+    want to do particle physics, decide on the fields we want by 
+    specifying how they transform
+    under the symmetry (in this case we decided on a scalar field 
+    $\phi$), and then write down
+    the action involving no more than two time derivatives 
+    (because we don’t know how to
+    quantize actions with more than two time derivatives)
+\end{quote}
+
+Also it is customary to write $d = D + 1$ and speak of a 
+$(D + 1)$-dimensional spacetime. When $D=0$, quantum
+field theory reduces to normal quantum mechanics,
+which deal with only a point (in the mattress
+sense, we have only one particle).
+
+Then he also notes that the Lagrangian can only have the form
+$\mathcal{L}=\frac{1}{2}(\partial\phi)^2-V(\phi)$.\footnote{
+    in a footnote, he also mentions a possible additional
+    term $U(\phi)(\partial \phi)^2$. It is related to a
+    particle whose mass depends on position. This will be
+considered later}.
+
+The classical limit of this formulation can be obtained by
+method similar to previous section. A saddle point approximation
+to the integral:
+\begin{align}
+    Z = \int D\phi e^{i/\hbar \int d^4x \mathcal{L}(phi)}
+\end{align}
+will find the classical field equation:
+\begin{align}
+    \label{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}
+    \partial_\mu \frac{\delta \mathcal{L}}{\delta(\partial_\mu\phi)}
+    -\frac{\delta\mathcal{L}}{\delta\phi} =0
+\end{align}
+
+\textbf{Corresponding pages in draft} pp. 7 to 8.
+
+\paragraph{Vacuum and Response}
+
+It is said that the vacuum in quantum field theory is a
+stormy sea of quantum fluctuations.
+
+Then, it discuss a process, very similar to the idea in linear
+response theory in condensed matter physics. The idea is to
+set up a source and a sink in which particles are created and
+annihilated. It correspondes to adding a term $sum_a J_a(t)q_a$ to
+the potential, or in the continuum limit, a term $\int d^DxJ(x)\phi(x)$.
+
+\paragraph{Free field theory}
+
+Here he centers at the the Lagrangian
+\begin{align}
+    \mathcal{L}(\phi)=\frac{1}{2}\left( (\partial\phi)^2-m^2\phi^2\right)
+\end{align}
+The corresponding theory is called the \textbf{free} or 
+\textbf{Guassian theory}. Using 
+% TODO why is it called free
+\ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
+obtain the Klein-Gorden equation:
+\begin{align}
+    (\partial^2+m^2)\phi=0
+\end{align}
+The plain wave solution is of the form:
+\begin{align}
+    \omega^2=\vec{k}^2+m^2
+\end{align}
+He notes that by transfer back to the SI unit, one will
+recognize above equations the same as the $E=mc^2$ identity.
+
+Next, we evaluate the disturbed case of free field theory:
+\begin{align}
+    Z = \int D\phi e^{i\int d^4x \left( \frac{1}{2} 
+        [(\partial\phi)^2-m^2\phi^2]+J\phi \right)
+        }
+\end{align}
+The integration is rather lengthy. It involves a trick called
+"to imagine discretizing spacetime". In my opinion, such a trick
+is to the best, a fancy intuition. There maybe mathematical proof,
+but is neglected by the author. However, the result is surprisingly
+rich in intuition and analogy. It start with the discretized
+analogy with \eqref{eq:QFT_in_a_Nutshell_Part_I.2.appdx1.1}. One
+is gradually lead to believe that the result of:
+\begin{align}
+    Z = \int D\phi e^{ i\int d^4x 
+        \left(-\frac{1}{2}(\partial^2+m^2)\phi+J\phi \right)}
+\end{align}
+is:
+\begin{align}
+    Z(J) = \mathcal{C}e^{-(i/2) \int\int d^4xd^4y J(x)D(x-y)J(y)}
+\end{align}
+where $\mathcal{C}$ is just some factor which will proven to be
+unimportant. $D(x-y)$ is the solution of:
+\begin{align}
+    \label{eq:QFT_in_a_Nutshell_Part_I.3.2}
+    -(\partial^2+m^2)D(x-y)=\delta^{(4)}(x-y)
+\end{align}
+
+The following is devoted to the function $D(x)$.
+
+One check by direct substitution that:
+\begin{align}
+    D(x-y) = \int \frac{d^4k}{(2\pi)^4} 
+        \frac{e^{ik(x-y)}}{k^2-m^2+i\varepsilon}
+\end{align}
+is the solution to \ref{eq:QFT_in_a_Nutshell_Part_I.3.2}.
+
+Then the author tries to explain how to evaluate $D(x)$, which
+I fail to reproduce. The final result is equation (23) on page 
+24. He notes that
+\begin{quote}
+    Physically, $D(x)$ describes the amplitude for a disturbance 
+    in the field to propagate from the origin to $x$. 
+\end{quote}
+In different region of spacetime, the value of $D(x)$ varies greatly.
+When $x$ is in timelink region, $D(x)$ is the superposition of
+plane waves, while the phase is opposite between $x^0=t<0$ and
+$x^0=t>0$. When $x$ is in the spacelike region, the $D(x)$ exhibits
+a strange behavior that the particle can leak outside lightcone,
+over a distance of order $m^{-1}$. This is consistent with the
+Heisenberg's uncertainty principle.
+
+\textbf{Corresponding pages in draft} pp. 9 to 11.
+
+\textbf{Unclear points}: I cannot follow all the calculation for 
+$D(x)$, because my result is different from the book's. Also, the
+physics picture about $D(x)$ on page 24, is badly reasoned. The
+argument is tenuous, in my opinion.
+\chapter{Bibliography}
 \begin{thebibliography}{1}
@@
 \end{thebibliography}
-
-\section{License}
+\chapter{License}
 The entire content of this work (including the source code

### 2016-08-01 Algebra/Noetherian Ring.tex
Update notes about: Noetherian Ring, QFT in a Nutshell, Complex Geometry.

@@
 \abstract{
-    About Noetherian Ring.
+    A note about Noetherian Ring, majorly from the book \cite{lang}.
 }
@@
 
+\paragraph{Some theorems}
+
+Here are some theorems mentioned in Chapter X,
+section 2 of \cite{lang}.
+
+The propositions \ref{prop:Noetherian.1.1},
+\ref{prop:Noetherian.1.2}, \ref{coro:Noetherian.1.3} expresses the
+"Noetherian relation" between $M$ and its submodules. The proposition
+\ref{prop:Noetherian.1.4} relates a Noetherian ring $A$ and the
+$A$-modules. The proposition \ref{prop:Noetherian.1.5} relates two
+rings. The proposition \ref{prop:Noetherian.1.6} relates a commutative
+Noetherian ring and its multiplicative subset. The following diagram
+summarized these relations.
+$$ \xymatrix{
+S^{-1}A & A
+            \ar[d]^{\text{prop.} \ref{prop:Noetherian.1.5}}
+            \ar[l]^{\text{prop.} \ref{prop:Noetherian.1.6}}
+            \ar[r]^{\text{prop.} \ref{prop:Noetherian.1.4}}
+        & M\ar[d]^{\text{prop.}:
+            \ref{prop:Noetherian.1.1},
+            \ref{prop:Noetherian.1.2},
+            \text{coro.} \ref{coro:Noetherian.1.3}} \\
+            & B       & \text{submodules}\ar[u]
+} $$
+($A,B$: ring, $S$: $A$'s multiplicative subset. $M$: a $A$-module.)
+
 The structure of being Noetherian is consistent between a module
@@
 \begin{prop}
+    \label{prop:Noetherian.1.1}
     Let $M$ be a Noetherian $A$-module, then every submodule and
@@
 \begin{prop}
+    \label{prop:Noetherian.1.2}
     Let $M$ be a module, $N$ be a submodule. If $N$ and $M/N$ are
@@
 \]
-\printnomenclature
 
+\begin{coro}
+    \label{coro:Noetherian.1.3}
+    A finite direct sum of Noetherian modules is Noetherian. Specifically,
+    let $M$ be a module, let $N,N'$ be two submodules. If $M=N+N'$ and if
+    both $N,N'$ are Noetherian, then $M$ is Noetherian.
+\end{coro}
+(\textbf{pp.415 of \cite{lang}})
+\begin{prop}
+    \label{prop:Noetherian.1.4}
+    Let $A$ be a Noetherian ring, and let $M$ be a finitely generated
+    $A$-module. Then $M$ is Noetherian.
+\end{prop}
+(\textbf{pp.415 of \cite{lang}})
+\begin{prop}
+    \label{prop:Noetherian.1.5}
+    Let $A$ be a ring which is Noetherian, and let $\phi:A\to B$ be
+    a surjective ring-homomorphism. Then $B$ is Noetherian.
+\end{prop}
+(\textbf{pp.415 of \cite{lang}})
+In colloquial term, a surjective homomorphism induces a Noetherian ring.
+\begin{prop}
+    \label{prop:Noetherian.1.6}
+    Let $A$ be a commutative Noetherian ring, and let $S$ be a
+    multiplicative subset of $A$. Then $S^{-1}A$ is Noetherian.
+\end{prop}
+(\textbf{pp.415 of \cite{lang}})
+\section{Examples}
+\label{sec:Examples}
+\begin{itemize}
+    \item The polynomial Ring
+    \item The ring of power series
+    \item The ring of formal power series is \textbf{NOT} Noetherian.
+        See this \href{http://math.stackexchange.com/questions/281597/an-example-of-a-non-noetherian-ufd}{post}
+        \begin{quote}
+        The essential point is that the polynomial ring in infinitely many variables is the ascending union of subrings $K[x_1,\ldots,x_n]$, since any polynomial can involve only finitely-many indeterminates.
+Each of these rings is a UFD, and it is easy to see that a polynomial in which $x_N$ does not appear has only factorizations in which $x_N$ does not appear, again because everything takes place inside some polynomial ring in finitely-many variables.
+But the ring is not Noetherian, because the ideal generated by all the indeterminates is certainly not finitely-generated.
+        \end{quote}
+\end{itemize}
 \section{Anchor}
 % This is just an anchor for seperating thebibliography from above contents.
+\printnomenclature
 \begin{thebibliography}{1}

### 2016-08-03 Complex Geometry - index/Complex Geometry - index.tex
New complex geometry note.

--- 2016-07-11 Complex Geometry - index of notations by taper.tex
@@
 % http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\documentclass{book}
 
@@
 \usepackage{amsthm}
-\newtheorem{thm}{Theorem}
-\newtheorem{lemma}{Lemma}
+\newtheorem{defi}{Definition}[section]
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{remark}{Remark}[section]
+\newtheorem{prop}{Proposition}[section]
+\newtheorem{coro}{Corollary}[section]
+\theoremstyle{definition}
+\newtheorem{ex}{Example}[section]
 
@@
 
-\begin{abstract}
-Obviously.
+\part{Indices of Notation}
 
-\end{abstract}
-
-\section{Book}
-	\subsection{1. Local Theory}
-		\subsubsection{1.1 Holomorphic Functions of Several Variables}
+\chapter{Book}
+\section{1. Local Theory}
+    \subsection{1.1 Holomorphic Functions of Several Variables}
     \label{sec:1.1_book}
@@
 
-		\textcolor{blue}{1}: 
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}: 
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
+    \textcolor{blue}{germ of set}: (\textbf{pp.18})
 
-	\subsection{2.Complex Manifolds}
+    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})
 
-		\subsubsection{2.2 Holomorphic Vector Bundles}
+    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})
+
+    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})
+
+    \textcolor{blue}{$I(X)$}: the set of all $f\in
+    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
+    % TODO bookmark
+    \subsection{1.2 Complex and Hermitian Structures}
+    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
+    (\textbf{pp.25})
+
+    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
+    of $I$.
+    (\textbf{pp.25})
+
+    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
+    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
+    (\textbf{pp.27})
+
+    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{compatible}:an almost complex structure $I$ is
+    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{Conformal equivalence}(between scalar product):
+    (\textbf{pp.29})
+
+    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
+    (\textbf{pp.29})
+    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
+    \quad(Local calculation could be found on \textbf{pp.31})
+
+    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
+    (\textbf{pp.30})
+\section{2.Complex Manifolds}
+
+    \subsection{2.1 Complex and Hermitian Structures}
+    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
+	\subsection{2.2 Holomorphic Vector Bundles}
 
@@
 
-		\subsubsection{2.6 Differential Calculus on Complex Manifolds}
+    \subsection{2.6 Differential Calculus on Complex Manifolds}
 
@@
     \textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
-							\bigotimes_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)
+                        \bigoplus_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)
 
@@
 
-\section{My lecture Notes}
+\chapter{My lecture Notes}
 
-	\subsection{Lecture 2016 Lecture 1}
+\section{Lecture 2016 Lecture 1}
 The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.
 
-	\subsection{Lecture 4 (20160307) Complex Manifold}
+\section{Lecture 4 (20160307) Complex Manifold}
 
@@
 
-	\subsection{Lecture 5 Submanifolds (20160308)}
+\section{Lecture 5 Submanifolds (20160308)}
 
@@
 
-	\subsection{Lecture 6 Sheaf \& Cohomology (20160315)}
-	pp. A:
+\section{Lecture 6 Sheaf \& Cohomology (20160315)} pp. A:
     \begin{itemize}
@@
 \end{itemize}
-    \subsubsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
+
+    \subsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
     pp.1:
@@
 
-	\subsection{Lecture 7 Vector Bundle (20160321)}
+\section{Lecture 7 Vector Bundle (20160321)}
 pp.1,2:
@@
 
-	\subsection{Lecture 8 Almost Complex Structures (20160322)}
+\section{Lecture 8 Almost Complex Structures (20160322)}
 pp. 1,2:
@@
 
-	\subsection{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}
+\section{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}
 
@@
 
-	\subsection{Lecture 10 Debeault Cohomology (20160406)}
+\section{Lecture 10 Debeault Cohomology (20160406)}
 
@@
 
-	\subsection{Lecture 11 (20160412)}
+\section{Lecture 11 (20160412)}
 pp.1,2,3: 
@@
 
-	\subsection{Lecture 12 Hermitan Structure on Manifold  Manifold (20160418)}
+\section{Lecture 12 Hermitian Structure on Manifold  Manifold (20160418)}
 pp. 1,2,3:
@@
 
-	\subsection{Lecture 13 Kähler Manifold (20160419)}
+\section{Lecture 13 Kähler Manifold (20160419)}
 pp.1:
@@
 
-	\subsection{Lecture 14 Hodge Theory (20160425)}
+\section{Lecture 14 Hodge Theory (20160425)}
 pp.1:
@@
 
-	\subsection{Lecture 15 Hodge Theory on Manifold (20160426)}
+\section{Lecture 15 Hodge Theory on Manifold (20160426)}
 pp.1:
@@
 
-	\subsection{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}
+\section{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}
 
@@
 
-	\subsection{Lecture 17 Hermitian Vector Bundle (20160510)}
+\section{Lecture 17 Hermitian Vector Bundle (20160510)}
 pp.1,3:
@@
 
-	\subsection{Lecture 18 Connection (20160516)}
+\section{Lecture 18 Connection (20160516)}
 \begin{itemize}
@@
 
-	\subsection{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
+\section{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
 \begin{itemize}
@@
 
-	\subsection{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
+\section{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
 \begin{itemize}
@@
 
-	\subsection{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
+\section{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
 \begin{itemize}
@@
 
-	\subsection{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
+\section{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
 \begin{itemize}
@@
 
+\part{Indices of Results}
+
+{Theorems, Remarks, etc.}
+\chapter{Local Theory}
+\label{chap:Local Theory}
+
+\section{1.1 Holomorphic Functions of Several Variables}
+\label{sec:book_1.1}
+
+\begin{prop}
+    The local ring $\mathcal{O}_{\mathbb{C}^n,0}$ is a UFD.
+\end{prop}
+(\textbf{pp.14 of \cite{book}})
+
+\begin{prop}{Weierstrass division theorem}
+    Let $f\in \mathcal{O}_{\mathbb{C}^n,0}$ and $g\in
+    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ be a Weierstrass
+    polynomial of degree $d$. Then there exist $r\in
+    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ of degree $<d$
+    and $h\in \mathcal{O}_{\mathbb{C}^n,0}$ such that $f=g\cdot h+r$.
+    The functions $h$ and $r$ are uniquely determined.
+\end{prop}
+(\textbf{pp.15 of \cite{book}})
+
+\begin{prop}
+    The local UFT $\mathcal{O}_{\mathbb{C}^n,0}$ is Noetherian.
+\end{prop}
+(\textbf{pp.16 of \cite{book}})
+
+\begin{coro}
+    Let $g\in \mathcal{O}_{\mathbb{C}^n,0}$ be an irreducible function.
+    If $f\in\mathcal{O}_{\mathbb{C}^n,0}$ vanishes on $Z(g)$, then
+    $g$ divides $f$.
+\end{coro}
+(\textbf{pp.16 of \cite{book}})
+
+\begin{lemma}
+    For any germ $X\subset \mathbb{C}^n$ the set $I(X)\subset
+    \mathcal{O}_{\mathbb{C}^n,0}$ is an ideal.
+    If $(A)\subset \mathcal{O}_{\mathbb{C}^n,0}$ denotes the ideal
+    generated by the subset $A\subset \mathcal{O}_{\mathbb{C}^n,0}$,
+    then $Z(A)=Z((A))$ and $Z(A)$ is analytic.
+\end{lemma}
+(\textbf{pp.18 of \cite{book}})
+
+\begin{lemma}
+    If $X_1\subset X_2$, then $I(X_2)\subset I(X_1)$. If $I_1\subset I_2$,
+    then $Z(I_2)\subset Z(I_1)4$. For any analytic germ $X$ one has
+    $Z(I(X))=X$. For any ideal $I\subset \mathcal{O}_{\mathbb{C}^n,0}$,
+    one has $I\subset I(Z(I))$.
+\end{lemma}
+(\textbf{pp.18 of \cite{book}})
+% TODO bookmark this chapter stops at page 18.
+
+\section{1.2 Complex and Hermitian Structures}
+\begin{lemma}
+    If $I$ is an almost complex structure on a real vector space $V$,
+    then $V$ admits in a natural way the structure of a complex vector
+    space
+\end{lemma}
+(\textbf{pp.25 of \cite{book}})
+
+\begin{remark}
+    An almost complex structure can only exist on an even dimensional
+    real vector space.
+\end{remark}
+
+\begin{coro}
+    Any almost complex structure on $V$ induces a natural orientation
+    on $V$.
+\end{coro}
+(\textbf{pp.25 of \cite{book}})
+
+\begin{lemma}
+    Let $V$ be a real vector space endowed with an almost complex
+    structure $I$. Then
+    $$ V_{\mathbb{C}} = V^{1,0}\oplus V^{0,1}$$
+    Complex conjugation on $V_{\mathbb{C}}$ induces an $\mathbb{R}$-linear
+    isomorphism $V^{1,0}\cong V^{0,1}$.
+\end{lemma}
+(\textbf{pp.26 of \cite{book}})
+
+\begin{remark}
+    Two almost complex structures on $V_{\mathbb{C}}$: $I$ and $i$,
+    coincide on the subspace $V^{1,0}$ but differ by a sign on
+    $V^{0,1}$.
+\end{remark}
+
+\begin{lemma}
+    Let $V$ be a real vector space endowed with an almost complex
+    structure $I$. Then the dual space 
+    $V^*=\text{Hom}_{\mathbb{R}}(V,\mathbb{R})$ has a natural almost
+    complex structure given by $I(f)(v)=f(I(v))$. The induced 
+    decomposition on 
+    $(V^*)_{\mathbb{C}}=\text{Hom}_{\mathbb{R}}(V,\mathbb{C})
+    = (V_{\mathbb{C}})^*$ is given by
+    $$ (V^*)^{1,0} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
+        f(I(v)) = i f(v) \} = (V^{1,0})^*$$
+    $$ (V^*)^{0,1} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
+        f(I(v)) = -i f(v) \} = (V^{0,1})^*$$
+    Also note that $(V^*)^{1,0} = 
+        \text{Hom}_{\mathbb{C}}((V,I),\mathbb{C})$.
+\end{lemma}
+
+\begin{prop}
+    For a real vector space $V$ endowed with an almost complex
+    structure $I$, one has:
+    \begin{enumerate}
+        \item $\bigwedge^{p,q}V$ is in a canonical way a subsapce
+            of $\bigwedge^{p+q} V_{\mathbb{C}}$.
+        \item $\bigwedge^k V_{\mathbb{C}}
+            = \bigoplus_{p+q=k}\bigwedge^{p,q}V$.
+        \item Complex conjugation on $\bigwedge^* V_{\mathbb{C}}$ defines
+            a ($\mathbb{C}$-linear) isomorphism
+            $\bigwedge^{p,q}V\cong \bigwedge^{q,p}V$, i.e.
+            $\bar{\bigwedge^{p,q}V}=\bigwedge^{q,p}V$.
+        \item The exterior prodoct is of bidegree $(0,0)$.
+    \end{enumerate}
+\end{prop}
+(\textbf{pp.27 of \cite{book}})
+\begin{remark}{Local calculation of $V^{1,0}$,$(V^*)^{1,0}$}
+    $$z_i=\frac{1}{2}(x_i-y_i)\text{, }\bar{z}_i=\frac{1}{2}(x_i+iy_i)$$
+    $$z^i=x^i+iy^i\text{, }\bar{z}^i=x^i-iy^i$$
+    $$I(z_i)=i z_i\text{, }I(z^i)=i z^i$$
+\end{remark}
+(\textbf{pp.27 to 28 of \cite{book}})
+
+\begin{lemma}
+    For any $m\leq \text{dim}_{\mathbb{C}}V^{1,0}$, one has
+    $$(-2i)^m (z_1\wedge\bar{z}_1)\wedge\cdots\wedge(z_m\wedge\bar{z}_m)=
+        (x_1\wedge y_1)\wedge\cdots\wedge(x_m\wedge y_m).$$
+    For $m=\text{dim}_\mathbb{C} V^{1,0}$, this defines a positive
+    oriented volume form for the natural orientation of $V$.
+
+    Also
+    $$\left(\frac{i}{2}\right)^m
+      (z^1\wedge\bar{z}^1)\wedge\cdots\wedge(z^m\wedge\bar{z}^m)=
+      (x^1\wedge y^1)\wedge\cdots\wedge(x^m\wedge y^m).$$
+\end{lemma}
+
 \begin{thebibliography}{1}
-
-	\bibitem{blog} Complex Geometry
-
+	\bibitem{book} Complex Geometry
 \end{thebibliography}
-\section{License}
+\part{License}
 The entire content of this work (including the source code

### 2016-08-09 Finished/Light harvesting/Light Harvesting Course Note.tex
Finished notes of light harvesting.

--- 2016-07-24 Light harvesting/Photosynthesis Course Note.tex
@@
 
-\title{Photosynthesis Course Note}
+\title{Light Harvesting Course Note}
 \date{\today}
@@
     to Light Harvesting in Bacteria and Plants}. The course is more
-    of a research than of a pedagodic taste: ideas and
-    methods are only mentioned, with reference to the published paper
+    of a research than of a pedagogic taste: ideas and
+    methods are outlined, with reference to the published paper
     available in the corresponding slides.
-    Therefore, this note aims to provide a guidance to read those slides.
-    Note that the page numbers in this note are the page numbers of
+
+    This note only aims to provide a guidance to read those slides.  
+    The page numbers in this note are the page numbers of
     each individual PDF, not necessarily the page numbers displayed
-    on the bottom-right corner inside the PDFs.
+    on the bottom-right corner on those slides.
 }
@@
 
-In this lecture, the teacher presents backgroud for light-harvesting
+In this lecture, the teacher presents background for light-harvesting
 mechanism in biology systems:
 \begin{itemize}
-    \item \textbf{pp.1 to 9 of PPT} 
-        General backgroud to Biophysics.
-    \item \textbf{pp.10 to 18 of PPT}
+    \item 
+        General background to Biophysics.
+        \textbf{(pp.1 to 9)} 
+    \item 
         Review of several mechanisms of light harvesting in different 
         species.
-    \item \textbf{pp.19 to 20 of PPT}
+        \textbf{(pp.10 to 18)}
+    \item 
         The central topics of this course
+        \textbf{(pp.19 to 20)}
         \begin{itemize}
-            \item The natrual of exciton in biological ligth harvesting 
+            \item The natural of exciton in biological ligth harvesting 
                 system.
@@
                 by a classical diffusion model.
-            \item How is active self-regulation archieved. (pp.20)
+            \item How is active self-regulation archived. (pp.20)
         \end{itemize}
@@
     energy in a biomimetic light-harvesting system.
-Then, after a review of Quantum Mechanics (\textbf{pp. 22 to 32} )\footnote{
+Then, after a review of Quantum Mechanics (\textbf{pp.22 to 32} )\footnote{
     Interestingly, the teacher mentioned Bohmian Mechanics, an alternative
@@
 Note that here it is expected that only one of the
-dimer is excited, becuase this energetically eaiser to achieve.
+dimer is excited, because this energetically easier to achieve.
 Note also that the
-symble "$\dagger$" denotes neither conjugation nor creation operator,
+symbol "$\dagger$" here denotes neither conjugation nor creation operator,
 but simply a label for an excited state's wavefunction.
 
-The calculated excited state energys on page 35 are splitted into
+The calculated excited state energys on page 35 are split into
 two levels. the difference between them, denoted by $\mathcal{E}$,
 is expressed as a function of the two
-transition dipole moments and the speration length of two molecules.
+transition dipole moments and the separation length of two molecules.
 Details about the interaction potential $V_{uv}$ can be found on
@@
 Begin with a review of two modes of excitons in organic system
-\textbf{pp.1}, this
+(\textbf{pp.1}), this
 lecture proceeds to explain in detail the dipole interaction potential
 (\textbf{pp.2 to 3})
-$V_{uv}$ mentioned in previous lecture. \textbf{Page 4 to 5} digresses on
+$V_{uv}$ mentioned in previous lecture. (\textbf{pp.4 to 5}) digresses on
 the difference between the transition dipole moment and the
@@
 the content is not important.
-\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
+(\textbf{pp.6 and 7}) also digresses on electronic momenta and oscillator
 strength.
@@
 observed when comparing the absorption spectra. The case of H aggregation
-is similar. \textbf{Page 12 to 13 } mentions the transition dipole in
+is similar. (\textbf{pp.12 to 13 }) mentions the transition dipole in
 more complicated cases. \footnote{Reference could be found in \textit{
@@
 system. Then it proceeds to review some concepts in quantum statistical 
-mechanics ( \textbf{page 2 to 21}). Since we are quite familar with this
+mechanics (\textbf{page 2 to 21}). Since we are quite familiar with this
 subject, it will be omitted from this note. The last page mentioned an
-important equation for the evolvement of density matrix in an open system,
+important equation for the evolution of density matrix in an open system,
 called the "master equation".\footnote{Suggested reading: 
@@
 evolve into comprising negative values. This is because the added terms
-are not rigorously derived, but just an approximation. On \textbf{page 2} the
+are not rigorously derived, but just an approximation. On (\textbf{page 2}) the
 teacher mentioned a specific case.\footnote{
@@
 
-The teacher wrote an example for the $V_m$ term on ppt on blackboard:
+The teacher wrote an example for the $V_m$ term on PPT on blackboard:
 
@@
 $$ A^\dagger A (a^\dagger + a) = \text{extra} \otimes \text{bath}$$
-Then $A^\dagger A$ is $V_m$ in ppt.
+Then $A^\dagger A$ is $V_m$ in PPT
 
@@
 
-\paragraph{pp.5} shows diagramatically the exciton transport process.
-External influence to the system includes trapping, decaying and disspation.
+\paragraph{pp.5} shows diagrammatically the exciton transport process.
+External influence to the system includes trapping, decaying and dissipation
 Here $k_t$ characterizes the trapping rate. And $k_d$ characterizes
@@
 
-\paragraph{pp.6 of PPT} explains some notations.
+\paragraph{pp.6} explains some notations.
 Here $\tau_n$ characterize the life time 
@@
 
-Following are a series of toycases that has been calculated.
+Following are a series of toy cases that has been calculated.
 
@@
 
-\paragraph{pp.10 of PPT}
+\paragraph{pp.10}
 \footnote{Could be found on \textit{Efficient energy transfer in 
@@
 
-\paragraph{pp.11 of PPT} is 
+\paragraph{pp.11} is 
 a two ring case, with 8 sites on each ring. The initial configuration
@@
 
-\paragraph{pp.12 of PPT} is 
+\paragraph{pp.12} is 
 another two ring case, with a change in the right ring's number
 of trapping sites. It shows that a asymmetric design would somehow
-imporve the efficiency, since the plot on the right has a maximum region
+improve the efficiency, since the plot on the right has a maximum region
 while the left one has none. The next slide shows similar result.
@@
 \textbf{Caution:} I am quite confused by the following content,
-from pp.16 to the end of PPT. Erogo the
-following notes are note well organized. It is advised that one should
+from pp.16 to the end of PPT. Ergo the following notes for this lecture
+are note well organized. It is advised that one should
 look at the original literature instead.
@@
 
-\paragraph{pp.16 of PPT} Calculating the absorption spectrum, 
+\paragraph{pp.16} Calculating the absorption spectrum, 
 showing that only one level is acceptable.
 
-\paragraph{pp.17 of PPT}
+\paragraph{pp.17}
 Changing the configuration of laser could result (in generally) more
@@
 
-\paragraph{pp.19 of PPT}
+\paragraph{pp.19}
 Using Frankel-Exciton Model and find very good fit, balabala.
@@
 \paragraph{Glauber Coherent States} (defined on \textbf{pp.9})
-is the eigenstate of the annilation 
+is the eigenstate of the annihilation 
 operator:
@@
 orthogonal (\textbf{pp.15}). Also, the overlap of
-two coherent state decays expoentially as the difference 
+two coherent state decays exponentially as the difference 
 of the eigenvalues $|\alpha-\beta|$.
 
-\textbf{Digression}: usualy, the coherent state representation is
+\textbf{Digression}: usually, the coherent state representation is
 much more numerical efficient in computer simulation
@@
         $(\Delta X)^2 = \frac{\lambda^2}{2}$,
-        this is exactly the same as the variance of the gound state of simple
+        this is exactly the same as the variance of the ground state of simple
         harmonic oscillator.
@@
 contains 16 phonons for 16 pigments in LH1. The exciton term $H_{ex}$
-assumes that the interaction is only nearst neighbour interaction.
+assumes that the interaction is only nearest neighbour interaction.
 The exciton-phonon interaction $H_{\text{ex-ph}}$ is essentially
@@
 
-Then he toke a linear approximation of the phonon band. He mentioned
+Then he took a linear approximation of the phonon band. He mentioned
 a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.
@@
 
-\textbf{pp.8} introduces the Davydov's ansatz.
+\textbf{pp.8} introduces the Davydov's Ansatz
 Note that
@@
 
-Note also that the Davydov ansatz is not translational invariant.
+Note also that the Davydov Ansatz is not translational invariant.
 
-\textbf{pp.9} projects the Davydov ansatz into bloch states, and get
-the Toyozawa's ansatz. This Toyozawa ansatz has a central
+\textbf{pp.9} projects the Davydov Ansatz into Bloch states, and get
+the Toyozawa's Ansatz This Toyozawa Ansatz has a central
 position. Using this, we get the energy band.
@@
 Outside the region, there will be two solutions coexisting.
-The the solution obatined depeands on the initial configuration.
+The the solution obtained depends on the initial configuration.
 The physical picture is that, changing the value of $J$ and $g$,
@@
 is considered.
-\footnote{Could be found on "Toyozawa Ansat.pdf".}
+\footnote{Could be found on "Toyozawa Ansatzpdf".}
 The strange wedge
@@
 In this lecture, the author first explains that the $q=0$ mode is
-de-coupled into a simple Hamiltonian. Then he uses the time-dependent
+de-coupled into a simple Hamiltonian.(\textbf{pp.1})
+Then he uses the time-dependent
 variation method developed by Dirac, Frenkel and McLachlan. This method
@@
 Next we introduces three different Ansatzes: $D_1$ (\textbf{pp.3})
-$D_2$ and $\tilda{D}$ (\textbf{pp.4}). The $D_1$ ansatz is most
-numerical demanding. It accouts for the difference of phonons in
-different site of the 
+$D_2$ and $\widetilde{D}$ (\textbf{pp.4}). The $D_1$ Ansatz is most
+general and numerically demanding. It accounts for the difference 
+of phonons in different sites of the ring. The second point is ignored
+in $D_2$ to reduce the numerical complexity. $\widetilde{D}$ tries to
+strike a balance between the numerical demand and accuracy by including
+the factor $\beta(t)e^{-inq}$, which "can be viewed as an Ansatz for 
+the spatial variation of $\lambda_{qn}$ around this mean value."
+Details of the following calculation could be found on 
+\textit{Sun J et al PRB 2010}(attached).
+
+The rest of the lecture explores the numerical result. Regretfully, I
+was distrait by the malfunction in my computer. Details could be found
+on the aforementioned paper.
+
+\section{July 22nd, Friday}
+\label{sec:July_22ed_Friday}
+
+I did not attend this lecture because I was preparing for travel.
+home.
+
 \section{License}

### 2016-08-13 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
New complex geometry note.
Update QFT in nutshell's notes.

@@
 \label{sec:QFT_in_a_Nutshell.Part_I}
-\section{I:2 Path Integral Formulation of Quantum Physics}
+\section{I.2 Path Integral Formulation of Quantum Physics}
 \label{sec:QFT_in_a_Nutshell_Part_I.2}
@@
 
-\section{I:3 From Mattress to Field}
+\section{I.3 From Mattress to Field}
 \label{sec:QFT_in_a_Nutshell_Part_I.3}
@@
 \begin{align}
+    \label{eq:QFT_in_a_Nutshell_Part_I.3.3}
     Z(J) = \mathcal{C}e^{-(i/2) \int\int d^4xd^4y J(x)D(x-y)J(y)}
@@
 
-One check by direct substitution that:
+One checks by direct substitution that:
 \begin{align}
@@
 
+We also denote the exponent in \ref{eq:QFT_in_a_Nutshell_Part_I.3.3}
+as $W(J)$. So:
+\begin{align}
+    \label{eq:}
+    W(J) = -\frac{1}{2} \int\int d^4x d^4y J(x)D(x-y)J(y) \\
+    Z= \mathcal{C}e^{iW(J)}
+\end{align}
+
+\paragraph{Free propagator}
+
+The function $D(x)$ is also called a propagator. It "plays an 
+essential role in quantum field theory. As the inverse of a
+differential operator it is clearly closely related to the Green’s
+function you encountered in a course on electromagnetism".
+
 Then the author tries to explain how to evaluate $D(x)$, which
 I fail to reproduce. The final result is equation (23) on page 
-24. He notes that
+24:
+\begin{align}
+    D(x)= -i\int \frac{d^3k}{(2\pi)^3 2\omega_k}
+    \left( e^{-i(w_k t-\vec{k}\cdot\vec{x})} \theta(x^0)
+        + e^{i(w_k t-\vec{k}\cdot\vec{x})} \theta(-x^0)
+    \right)
+\end{align}
+
+He notes that
 \begin{quote}
@@
 argument is tenuous, in my opinion.
+
+\section{I.4 From Field to Particle to Force}
+\label{sec:I.4 From Field to Particle to Force}
+
+\textbf{Note}: discussion in this section is based on the \textit{free
+field theory}.
+
+\paragraph{From field to particle}
+
+With the Fourier transformation, several physical properties
+could be extrated from $W(J)$. The Fourier transformed $W(J)$ is:
+\begin{align}
+    W(J) = -\frac{1}{2}\int \frac{d^4}{(2\pi)^4}J(k)^*
+        \frac{1}{k^2-m^2+i\epsilon}J(k)
+\end{align}
+If separating $J$ into $J(x)=J_1(x)+J_2(x)$, then naturally, the
+Fourier transformed calculation will include terms of the form:
+$J^*_1J_1,J^*_1J_2,J^*_2J_1,J^*_2J_2$. We see that the denominator
+in $W(J)$ contains $k^2-m^2$. Somehow the author wants to argue that
+the term $J^*_2J_1$ describes the influence of a particle of mass $m$
+propagating from the source $1$ to the sink $2$. But his language is loose.
+
+This part also introduces the jargon \textit{on mass shell} and the
+language of "virtual particles" moving in $k$-space.
+
+\paragraph{From particle to force}
+With two delta source $J_a(x)=\delta^(3)(\vec{x}-\vec{x}_a)$, one can
+describe two massive lumps setting on $\vec{x}_1$ and $\vec{x}_2$ and
+not moving at all. These two lumps, coupled with the free field $\phi$,
+will attract each other. To show the attraction, the author calculates
+explicitly the $W(J)$, and identifies $iW(J) \equiv -iET$ (the
+identification is substantiate by $e^{-iET} = Z = e^{iW(J)}$).
+Finally, it shows:
+\begin{align}
+    E= -\frac{1}{4\pi r}e^{-mr}
+\end{align}
+This is actually the Yukawa model for the attraction between nucleons
+in the atomic nucleus. A plot is in due:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/Yukawa-potential.pdf}
+    \caption{Plot of Yukawa potential $-\frac{e^{-r}}{4 \pi  r}$}
+\end{figure}
+
+It shows us several information:
+\begin{itemize}
+    \item In the long distance, the potential drops off over the
+        distance scale of $1/m$.
+    \item In the short range, the force is $1/r^2$.
+    \item The energy gets smaller when the two sources come closer.
+        It tends to $-\infty$ as $r\to 0$.
+\end{itemize}
+
+\paragraph{Origin of force}
+% TODO stops here.
 \chapter{Bibliography}

### 2016-08-14 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update QFT in a nutshell.

@@
 
-\textbf{Unclear point}
+\paragraph{Unclear point}
 Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
@@
 
-\textbf{Unclear points}: I cannot follow all the calculation for 
+\paragraph{Unclear points}: I cannot follow all the calculation for 
 $D(x)$, because my result is different from the book's. Also, the
@@
 \paragraph{From particle to force}
-With two delta source $J_a(x)=\delta^(3)(\vec{x}-\vec{x}_a)$, one can
+With two delta source $J_a(x)=\delta^{(3)}(\vec{x}-\vec{x}_a)$, one can
 describe two massive lumps setting on $\vec{x}_1$ and $\vec{x}_2$ and
@@
 will attract each other. To show the attraction, the author calculates
-explicitly the $W(J)$, and identifies $iW(J) \equiv -iET$ (the
-identification is substantiate by $e^{-iET} = Z = e^{iW(J)}$).
+explicitly the $W(J)$\footnote{
+    Specifically, he calculates the $J^*_1J_2$ and $J^*_2J_1$ terms,
+    ignoring the $J^*_1J_1$ and $J^*_2J_2$ terms, because the latter
+    appears in $W(J)$ regardless of the existance of the other particle.
+}, and identifies $iW(J) \equiv -iET$ (the
+identification is substantiate by $\braket{0|e^{-iET}|0} = Z = e^{iW(J)}$).
 Finally, it shows:
@@
 \paragraph{Origin of force}
-% TODO stops here.
+The energy calculated above, and the previous \textit{sink and source}
+interpretation, lead us to believe that force is the result of an
+exchange of particles.
+
+\paragraph{Connected versus disconnected}
+Here the author notes the Feynman's heuristic language to discribe
+the integral related to $J(x)D(x-y)J(y)$ as a graph:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/J(x)D(x-y)J(y).png}
+    \caption{$J(x)D(x-y)J(y)$}
+\end{figure}
+It also introduces the concept of connectedness or disconnectedness
+in the graph (omitted here).
+
+\paragraph{Unclear Points} Marked in the text.
+
+\section{I.5 Coulomb an Newton: Repulsion and Attraction}
+This section tries to replicate the previous section's procedure to
+produce a repulsive force. It starts with the Maxwell's Lagrangian for
+electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
+However, the authors adds an additional mass term and let the mass
+$m\to 0$ in the end. This is declared to be avoiding the complication of
+gauge invariance. The result is surprisingly simple. We have:
+\begin{align}
+    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
+        {k^2-m^2}
+    \nonumber\\
+    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
+        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
+    \nonumber\\
+    E&=\frac{1}{4\pi r}e^{-mr} 
+\end{align}
+
+This clearly represent the idea of repulsive Coulomb force.
 \chapter{Bibliography}

### 2016-08-16 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Daily update. New resource for QFT.

@@
 
-% TODO why not odd terms
 Then he notes about the Landau-Ginzburg view:
@@
 set up a source and a sink in which particles are created and
-annihilated. It correspondes to adding a term $sum_a J_a(t)q_a$ to
+annihilated. It correspondes to adding a term $\sum_a J_a(t)q_a$ to
 the potential, or in the continuum limit, a term $\int d^DxJ(x)\phi(x)$.
@@
 \textbf{Guassian theory}. Using 
-% TODO why is it called free
 \ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
@@
 \section{I.5 Coulomb an Newton: Repulsion and Attraction}
+\paragraph{Why like charges repel}
+
 This section tries to replicate the previous section's procedure to
@@
 This clearly represent the idea of repulsive Coulomb force.
+
+\paragraph{Bypassing Maxwell}
+% TODO stopped here.
+I am not sure what to write here, since I lost grip of which field
+the author is trying to calculate: meson of spin 1? or phonton?.
 \chapter{Bibliography}

### 2016-08-16 Complex Geometry - index/Complex Geometry - index.tex
Update QFT in nutshell's notes.
Daily update. New resource for QFT.
Update QFT in a nutshell, Complex Geometry notes. Improved git-push.bat script for visual echo.

@@
     (\textbf{pp.30})
+
+    \textcolor{blue}{Lefschetz operator $L$}:
+        $\bigwedge^* V^*_{\mathbb{C}}\to
+    \wedge^* V_{\mathbb{C}}^*$, given by $\alpha\to\omega\wedge\alpha$.
+    (\textbf{pp.31})
+
+    \textcolor{blue}{Hodge star $*$-operator}: $\alpha\wedge *\beta=
+        \langle\alpha,\beta\rangle \cdot \text{vol}$.
+    (\textbf{pp.33})
+
+    \textcolor{blue}{dual Lefschetz operator $\Lambda$}:
+        $\langle\Lambda\alpha,\beta\rangle =\langle\alpha,L\beta\rangle$,
+        degree $-2$, bidegree $(-1,-1)$, $\Lambda=*^{-1}\circ L\circ *$.
+    (\textbf{pp.33 to 34})
+
+    \textcolor{blue}{Counting operator $H$}:
+        $H=\sum_{k=0}^{2n}(k-n)\cdot\prod^k$, 
+        where $\text{dim}_{\mathbb{R}}=2n$.
+    (\textbf{pp.34})
+
+    \textcolor{blue}{commutator [A,B]}:$=A\circ B-B\circ A$.
+    (\textbf{pp.34})
+
+\paragraph{Commutators}
+$$[H,L]=2L,\text{ } [H,\Lambda]=-2\Lambda,\text{ } [L,\Lambda]=H.$$
+(\textbf{pp.34})
+
+$$[L^i,\Lambda](\alpha)= i(k-n+i-1)L^{i-1}(\alpha),\text{for all}
+    \alpha\in\bigwedge^k V^*$$
+(\textbf{pp.35})
+
+    \textcolor{blue}{primitive element} in $\bigwedge^kV^*$:
+        $\alpha$ is primitive if and only if $\Lambda\alpha=0$.
+    (\textbf{pp.36})
+
+    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
+    of all primitive elements.
+    (\textbf{pp.36})
 \section{2.Complex Manifolds}
@@
 
+\begin{prop}[Lefschetz decomposition]
+    There exists a direct sum decomposition of the form:
+    \begin{align}
+        \bigwedge^kV^* = \bigoplus_{i\geq 0} L^i(P^{k-2i})
+    \end{align}
+    Also, $P^k={\alpha\in \bigwedge^k V^*|L^{n-k+1}\alpha=0}$, for
+    $k\leq n$. Naturally $P^k=0$ for $k>0$.
+
+    We also have several morphisms induced by $L$, which is illustrated
+    in the following graph adapted from the book:
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=1.3\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
+        \caption{Morphisms}
+    \end{figure}
+\end{prop}
+(\textbf{pp.36 of \cite{book}})
 \begin{thebibliography}{1}

### 2016-08-16 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update QFT in a nutshell, Complex Geometry notes. Improved git-push.bat script for visual echo.

@@
 
+\usepackage{nomencl} % For a index of symbols.
+\makenomenclature % For a index of symbols.
+
 \title{Notes of Quantum Field Theory in a Nutshell}
@@
 \end{align}
+\nomenclature{$\int Dq(t)$}{\nomrefpage}
 It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
@@
 
-The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
-mentions that one often effect a change of coordinate
+We define:
+\begin{align}
+    Z\equiv \braket{0|e^{-iHT}|0}
+\end{align}
+\nomenclature{$Z$}{\nomrefpage}
+
+This part mentions that one often effect a change of coordinate
 $t \to -it$, called \textit{Wick rotation}, to obtain:
@@
 
-\paragraph{Mattress in continuum limit} It start with taking the
+\paragraph{Mattress in continuum limit}
+
+\footnote{
+    \textbf{Note}: Here and afterwards, the author suppresses the factor 
+    $\braket{0|q_f} \braket{q_I|0}$.
+}
+
+It start with taking the
 limit of lattice spacing $l\to 0$, aiming to write down the field
@@
 Also it is customary to write $d = D + 1$ and speak of a 
-$(D + 1)$-dimensional spacetime. When $D=0$, quantum
-field theory reduces to normal quantum mechanics,
+$(D + 1)$-dimensional spacetime
+\nomenclature{$(D + 1)$-dimensional spacetime}{\nomrefpage}. 
+When $D=0$, quantum field theory reduces to normal quantum mechanics,
 which deal with only a point (in the mattress
@@
 
-\paragraph{Vacuum and Response}
+\paragraph{Vacuum and (Linear) Response}
 
@@
 \end{align}
-The plain wave solution is of the form:
+The plain wave solution 
+    $\phi(\vec{x},t)=e^{i(\omega t-\vec{k}\cdot\vec{x})}$ 
+has the property:
 \begin{align}
@@
 We also denote the exponent in \ref{eq:QFT_in_a_Nutshell_Part_I.3.3}
-as $W(J)$. So:
+as $W(J)$ \nomenclature{$W(J)$}{\nomrefpage}. So:
 \begin{align}
@@
 With the Fourier transformation, several physical properties
-could be extrated from $W(J)$. The Fourier transformed $W(J)$ is:
+could be extrated from $W(J)$. The Fourier transformed $W(J)$
+\nomenclature{Fourier transformed $W(J)$}{\nomrefpage} is:
 \begin{align}
@@
 
+\textbf{Note} that the field $\phi$ used here is like the field used
+by Yukawa. The Yukawa model correctly describes the field of
+$\pi$ meson, also called pion.
+\nomenclature{$\pi$ meson}{ also called pion\nomrefpage}
 \paragraph{Origin of force}
@@
 % TODO stopped here.
-I am not sure what to write here, since I lost grip of which field
-the author is trying to calculate: meson of spin 1? or phonton?.
+
+\paragraph{Unclear Points} Marked in the book. Especially, where
+in the calculatioin above shows that the field is of a spin $1$
+or a spin $2$ meson?
+
 \chapter{Bibliography}
@@
 
+% For a list of symbols.
+\printnomenclature
 \end{document}

### 2016-08-17 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update notes about QFT in a nutshell.

@@
 
+\nomenclature{$D(x)$}{propagator for the free field theory\nomrefpage}
 The function $D(x)$ is also called a propagator. It "plays an 
@@
         {k^2-m^2}
+        = \frac{-G_{\nu\lambda}}{k^2-m^2}
+        \nomenclature{$D_{\nu\lambda}$}
+            {Propagator for massive spin $1$ field\nomrefpage}
     \nonumber\\
@@
 \end{align}
-
+where he defines 
+$G_{\nu\lambda}\equiv g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$.
 This clearly represent the idea of repulsive Coulomb force.
@@
 \paragraph{Bypassing Maxwell}
+
+Here he re-evaluates the propagator for massive spin $1$ particle
+(photon) using another approach, without the use of Maxwell's Lagrangian.
+\footnote{
+    In the appendix $1$, the author also provides a derivation of
+    Maxwell's Lagrangian.
+}
+The calculation depends on that:
+\begin{quote}
+   The amplitude for a particle with momentum $k$ and polarization $a$
+   to be created at the source is proportional to 
+   $\varepsilon^{(a)}_\lambda(k)$, and the amplitude for it to be absorbed 
+   at the sink is proportional to $\varepsilon^{(a)}_\lambda(k)$. We 
+   multiply the amplitudes together to get the amplitude for
+   propagation from source to sink, and then sum over the three 
+   possible polarizations
+\end{quote}
+This should give the propagator. In the end, it is found that:
+\begin{align}
+    \sum_a \varepsilon^{(a)}_\nu(k) \varepsilon^{(a)}_\lambda(k)
+    = - G_{\nu\lambda}(k) 
+    \equiv - \left(g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}\right)
+\end{align}
+
+\paragraph{Bypassing Einstein}
 % TODO stopped here.
-
 \paragraph{Unclear Points} Marked in the book. Especially, where

### 2016-08-18 Complex Geometry - index/Complex Geometry - index.tex
Daily update. Complex Geometry notes.

@@
 \usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols
+
+% To include PDF in higher version format.
+\pdfoptionpdfminorversion=6
 
@@
     (\textbf{pp.36})
+
+    \textcolor{blue}{Hodge-Riemann pairing $Q$}:
+    $$\bigwedge^kV^*\times\bigwedge^kV^*\to \mathbb{R}\text{, }
+     (\alpha,\beta)\mapsto (-1)^{k(k-1)}{2}\alpha\wedge\beta\wedge w^{n-k}$$
+
+    Note: here we identify $\bigwedge^{2n}V^*$ with $\mathbb{R}$ 
+    by the volumn form $\text{vol}$. Also the $\mathbb{C}$-linear 
+    extension of this is still denoted $Q$.
+
 \section{2.Complex Manifolds}
@@
         \centering
-        \includegraphics[width=1.3\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
+        \includegraphics[width=0.9\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
         \caption{Morphisms}
@@
 (\textbf{pp.36 of \cite{book}})
+
+As shown in the theorem, the map $\Lambda^{n-k}$ is produce a mirror
+effect in $\bigwedge^*V^*$, very similar to the Hodge $*$.
+The next proposition relates the two:
+
+\begin{prop}
+    For all $\alpha\in P^k$, we have:
+    \begin{align}
+        *L^j \alpha = (-1)^{\frac{k(k+2)}{2}}
+            \frac{j!}{(n-k-j)!}\cdot L^{n-k-j}I(\alpha).
+    \end{align}
+\end{prop}
+Particularly, when $j=k=0$, we have $*1=\text{vol} = \frac{\omega^n}{n!}$,
+or,
+\begin{align}
+    n!\text{vol} = \omega^n
+\end{align}
+(\textbf{pp.37 of \cite{book}})
+
+\begin{coro}[Hodge—Riemann bilinear relation]
+    \begin{align}
+        Q(\bigwedge^{p,q}V^*, \bigwedge^{p',q'}V^*)=0
+    \end{align}
+    for $(p,q)\neq (p',q')$, and
+    \begin{align}
+        i^{p-q}Q(\alpha,\bar\alpha)=(n-(p+q))! \cdot
+        \langle\alpha,\alpha\rangle_{\mathbb{C}}>0
+    \end{align}
+    for $0\neq\alpha\in P^{p,q}$, with $p+q\leq n$.
+\end{coro}
+(\textbf{pp.39 of \cite{book}})
 \begin{thebibliography}{1}

### 2016-08-30 Green function/green-f.tex
Inaugurating the new green function file, marking my first attempt at research level physics.

--- 2016-08-03 Complex Geometry - index/Complex Geometry - index.tex
@@
 
-\title{Complex Geometry - Index of Notations and ideas}
+% To include PDF in higher version format.
+\pdfoptionpdfminorversion=6
+
+\title{(Tentative) Calculating Green Function}
+% TODO give it a better name.
 \date{\today}
@@
 \maketitle
+\abstract{
+    This is a note for reading the paper \cite{1}, and for understanding
+    the code produced from that file.
+}
 \tableofcontents
-
-\part{Indices of Notation}
-
-\chapter{Book}
-\section{1. Local Theory}
-    \subsection{1.1 Holomorphic Functions of Several Variables}
-    \label{sec:1.1_book}
-    \textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.
-
-    \textcolor{blue}{holomorphic}: pp.1. pp4. Def 1.1.1. pp.10(Def.1.1.8).
-
-    \textcolor{blue}{Cauchy-Riemann equations}: pp.2
-
-    \textcolor{blue}{$\frac{\partial}{\partial z}$,$\frac{\partial}{\partial \bar{z}}$}:
-    $\frac{\partial}{\partial z}:= \frac{1}{2}
-            (\frac{\partial}{\partial x} 
-            -i \frac{\partial}{\partial y})
-            $
-    ,
-    $\frac{\partial}{\partial \bar{z}}:= \frac{1}{2}
-    (\frac{\partial}{\partial x} 
-    + i \frac{\partial}{\partial y})
-    $
-
-    \textcolor{blue}{Maximum principle}: pp.3.
-
-    \textcolor{blue}{Identity theorem}: pp.3.
-
-    \textcolor{blue}{Riemann extension theorem}: pp.3. pp.9 (Prop. 1.1.7).
-
-    \textcolor{blue}{Riemann mapping theorem}: pp.3.
-
-    \textcolor{blue}{Liouville theorem}: pp.4.
-
-    \textcolor{blue}{Residue theorem}: pp.4.
-
-    \textcolor{blue}{polydiscs $B_\epsilon(\omega)$}: $\{z| |z_i-\omega_i| <\epsilon\} $.  pp.4.
-
-    \textcolor{blue}{Hartogs' theorem}: Prop. 1.1.4. pp.6.
-
-    \textcolor{blue}{Weierstrass preparation theorem (WPT)}:
-    Prop. 1.1.6. pp.8.
-
-    \textcolor{blue}{Weierstrass polynomial}: Def. 1.1.5. pp.7.
-
-    \textcolor{blue}{$Z(f)$}: zero set of $f$. pp.9.
-
-    \textcolor{blue}{biholomorphic}: pp.10.
-
-    \textcolor{blue}{(complex) Jacobian, regular, regular value}: Def. 1.1.9. pp.10.
-
-    \textcolor{blue}{IFT. Inverse function theorem}: Prop 1.1.10 pp.11.
-
-    \textcolor{blue}{IFT. Implicit function theorem}: Prop 1.1.11. pp.10.
-
-    \textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n}$}:
-    sheaf of holomorphic functions on $\mathbb{C}^n$. Def. 1.1.14. pp.14.
-
-    \textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n,z}$}: Def. 1.1.14. pp.14.
-
-    \textcolor{blue}{$\mathcal{O}^*_{\mathbb{C}^n,0}$}:
-    units of $\mathcal{O}_{\mathbb{C}^n,0}$. pp.14.
-
-    \textcolor{blue}{UFD, unique factorization domain, irreducible}: 
-    Def. 1.1.16. pp.14.
-
-    \textcolor{blue}{Gauss Lemma}: pp.14.
-
-    \textcolor{blue}{Weierstrass division theorem}: Prop. 1.1.17. pp.15.
-
-    \textcolor{blue}{germ of set}: (\textbf{pp.18})
-
-    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})
-
-    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})
-
-    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})
-
-    \textcolor{blue}{$I(X)$}: the set of all $f\in
-    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
-    % TODO bookmark
-    \subsection{1.2 Complex and Hermitian Structures}
-    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
-    (\textbf{pp.25})
-
-    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
-    of $I$.
-    (\textbf{pp.25})
-
-    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
-    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
-    (\textbf{pp.27})
-
-    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{compatible}:an almost complex structure $I$ is
-    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{Conformal equivalence}(between scalar product):
-    (\textbf{pp.29})
-
-    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
-    (\textbf{pp.29})
-    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
-    \quad(Local calculation could be found on \textbf{pp.31})
-
-    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
-    (\textbf{pp.30})
-\section{2.Complex Manifolds}
-
-    \subsection{2.1 Complex and Hermitian Structures}
-    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
-	\subsection{2.2 Holomorphic Vector Bundles}
-
-    \textcolor{blue}{$\tau_X$}: holomorphic tangent bundle of a complex manifold $X$ (Def 2.2.14 at pp. 71).
-
-    \textcolor{blue}{$\varOmega_X$, $\varOmega^p_X$}: holomorphic cotangent bundle and holomorphic $p$-forms. (Def 2.2.14 at pp. 71)
-
-    \textcolor{blue}{$K_X$}:=det($\varOmega_X$) = $\varOmega_X^n$, the canonical bundle of $X$. (Def 2.2.14 at pp. 71)
-
-    \subsection{2.6 Differential Calculus on Complex Manifolds}
-
-    \textcolor{blue}{$\wedge^k_{\mathbb{C}}X$}:=$\wedge^k(T_{\mathbb{C}}X)^*$. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
-                        \bigoplus_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\mathcal{A}^k_{X,\mathbb{C}}$,$\mathcal{A}^{p,q}_X$}: sheaves of section of the above correspond items. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\mathcal{A}^{p,q}(E)$}: the sheaf of $p,q$-forms with values in $E$, a complex vector bundle.
-(Def 2.6.22 at pp.109).
-Note that in particular, $\mathcal{A}^0(E)$ is the sheaf of sections of $E$.
-
-	\subsection{Appendix B: Sheaf Cohomology}
-
-	\begin{itemize}
-		\item
-		\textcolor{blue}{pre-sheaf}: Def B.0.19, pp. 287.
-
-		\item
-		\textcolor{blue}{$\mathcal{C^0_M}$}: the pre-sheaf of continuous functions on $M$. Example B.0.20, pp. 287.
-
-		\item
-		\textcolor{blue}{sheaf}: Def B.0.21, at pp.288.
-
-		\item
-		\textcolor{blue}{\underline{$\mathbb{R}$},\underline{$\mathbb{Z}$}}: constant sheaves, Sometimes written simply as \textcolor{blue}{$\mathbb{R}$}, \textcolor{blue}{$\mathbb{Z}$} respectively.
-pp.
-288.
-		\item
-		\textcolor{blue}{$\mathcal{E}$}: actually a $\mathcal{C}^0_M$-modules. Sometimes identified as $E$. pp.288.
-		\item
-		\textcolor{blue}{(pre)-sheaf homomorphism}: Def B.0.23.  pp.288.
-		\item
-		\textcolor{blue}{Ker($\phi$),Im($\phi$),Coker($\phi$)}: as pre-sheaves in pp.288. sheaves in pp.289, Def B.0.26.
-		\item
-		\textcolor{blue}{injective, surjective of sheaf-homomorphism}:pp.289.
-		\item
-		\textcolor{blue}{complex, exact complex}: Def B.0.27. pp.289
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:	
-	\end{itemize}
-
-\chapter{My lecture Notes}
-
-\section{Lecture 2016 Lecture 1}
-The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.
-
-\section{Lecture 4 (20160307) Complex Manifold}
-
-\textbf{Note}: we use abbrevation \textit{mnfd} for \textit{manifold}.
-
-pp. A:
-    \begin{itemize}
-        \item \textcolor{blue}{Holomorphic Atlas}
-        \item \textcolor{blue}{Holmorphic chart}
-        \item \textcolor{blue}{Complex mnfd}
-    \end{itemize}
-
-pp. B:
-    \begin{itemize}
-        \item \textcolor{blue}{Holomorphic function}
-        \item \textcolor{blue}{$\mathcal{O}_X$}: sheaf of holomorhic functions on a complex mnfd $X$.
-    \end{itemize}
-pp. C:
-    \begin{itemize}
-        \item \textcolor{blue}{Hartdogs' theorem}: on complex mnfd.
-        \item \textcolor{blue}{Holomorphic functions on complex mnfd}:
-    \end{itemize}
-pp. D:
-    \begin{itemize}
-        \item \textcolor{blue}{Complex Lie group}
-        \item \textcolor{blue}{Complex Projective Space, $\mathbb{CP}^n$, or just $\mathbb{P}^n$}.
-    \end{itemize}
-pp. E:
-    \begin{itemize}
-        \item \textcolor{blue}{Topology in $\mathbb{P}^n$}
-        \item \textcolor{blue}{Mnfd structure on $\mathbb{P}^n$, atlas, and the \textbf{canonical covering}}
-    \end{itemize}
-pp. F
-    \begin{itemize}
-        \item Grassmannian mnfd.
-    \end{itemize}
-
-\section{Lecture 5 Submanifolds (20160308)}
-
-pp. A:
-    \begin{itemize}
-        \item Affine Hypersurface (actually this is not quite different from the usual $\mathbb{C}^n$.)
-    \end{itemize}
-
-Part 2. \textbf{Sheaf Theory}
-
-pp. A:
-	\begin{itemize}
-		\item pre-sheaf
-		\item $\mathcal{O}_X(U)$
-		\item $\mathcal{O}^*_X(U)$
-	\end{itemize}
-pp. B:
-	\begin{itemize}
-		\item $C^{\infty}$
-		\item $\mathbb{\underline{Z}}$, sometimes simply denoted as $\mathbb{Z}$: sheaf of localy constant $\mathbb{Z}$-valued functions.
-		\item Sheaf
-	\end{itemize}
-pp. D:
-	\begin{itemize}
-		\item sheaf-morphisms
-	\end{itemize}
-pp. E:
-	\begin{itemize}
-		\item Section
-		\item Ker($\phi$) - sheaf of kernals.
-	\end{itemize}
-pp. F:
-	\begin{itemize}
-		\item Im($\phi$) is a presheaf, but not a sheaf.
-		\item Im($\phi$): the sheafification of Im($\phi$) above. Note that we use the same notation to denote both.
-	\end{itemize}
-
-\section{Lecture 6 Sheaf \& Cohomology (20160315)} pp. A:
-    \begin{itemize}
-        \item Stalk $\mathcal{F}_x$.
-        \item germ
-        \item Directed partial order set
-        \item Directed System
-    \end{itemize}
-pp. B:
-    \begin{itemize}
-        \item Directed limit
-    \end{itemize}
-pp. C:
-\begin{itemize}
-    \item Exact Complex/ Exact Sequence.
-    \item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
-    \item
-\end{itemize}
-pp. D:
-\begin{itemize}
-    \item Čech cohomology
-\end{itemize}
-pp. E:
-\begin{itemize}
-    \item q-cochain
-    \item coboundary operator. $\delta$.
-    \item $Z^p(U,\mathcal{F})$ = Ker.
-    \item $B^p(U,\mathcal{F})$ = Im.
-    \item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
-\end{itemize}
-
-    \subsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
-    pp.1:
-    \begin{itemize}
-        \item q-simplex $\sigma$.
-        \item support $|\sigma|$.
-        \item q-cocain
-        \item $C^q(U,\mathcal{F})$
-        \item Coboundary Operator $\delta$.
-    \end{itemize}
-    pp.2,3,4:
-    \begin{itemize}
-        \item Cochain Complex
-        \item Čech cohomology
-        \item cocycle
-        \item cochain
-        \item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
-        \item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
-    \end{itemize}
-
-\section{Lecture 7 Vector Bundle (20160321)}
-pp.1,2:
-\begin{itemize}
-    \item Vector Bundle
-    \item Trivializing covering, $\{(U_i,\tau_i)\}$.
-    \item trivializing maps, trivializes.
-    \item VB-equivalent of trivializing maps.
-    \item E: total space, X: base space.
-\end{itemize}
-pp. 3,5:
-\begin{itemize}
-    \item transition maps.
-    \item fibre.
-    \item $\mathcal{O}(-1)$
-    \item cocycle condition.
-    \item $\mathcal{T}_X$, Holomorphic tangent bundle.
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item s: section of a holomorphic vector bundle.
-    \item $\mathcal{E}$: sheaf of sections of holomorphic vector bundle. $\mathcal{E}(U)$.
-\end{itemize}
-
-\section{Lecture 8 Almost Complex Structures (20160322)}
-pp. 1,2:
-\begin{itemize}
-    \item $I$: Almost Complex Structure. $I^2=-1$. Sometime $J$ is used in place of $I$.
-    \item $V_{\mathbb{C}}$ := $V\otimes \mathbb{C}$.
-    \item $I_\mathbb{C}$: $I$ extending to $V_{\mathbb{C}}$. Usually abbreviated simply as $I$.
-    \item $V^{1,0}$:= ker$(I+i)$.
-    \item $V^{0,1}$:= ker$(I-i)$.
-\end{itemize}
-
-\section{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}
-
-pp.1,2:
-\begin{itemize}
-    \item $V^*$: dual of $V$.
-    \item $\{dx^i,dy^i\}$.
-    \item $J^*$: $J$ extending to dual space.
-    \item $dz^i,d\bar{z}^i$.
-\end{itemize}
-pp. 3:
-\begin{itemize}
-    \item $S^k(V)$, $\Lambda^k(V)$.
-    \item $s$ and $a$, symmetrization and anti-symmetrization of a tensor.
-    \item $\Lambda^* V$.
-\end{itemize}
-pp. 4:
-\begin{itemize}
-    \item $\Lambda^n T^*_{\mathcal{C}}X$.
-    \item $\Lambda^* T^*_{\mathcal{C}}X$.
-    \item $\Lambda^{p,q} T^*_{\mathcal{C}}X$.
-\end{itemize}
-pp. 5,6:
-\begin{itemize}
-    \item $\mathcal{A}$: sheaf of section of cotangent bundle.
-    \item $\mathcal{A}^n(U)$, $\mathcal{A}^{p,q}(U)$.
-    \item $\Lambda$ on $\mathcal{A}$.
-    \item $d$: de Rham differential.
-    \item $\partial, \bar{\partial}$.
-\end{itemize}
-
-\section{Lecture 10 Debeault Cohomology (20160406)}
-
-pp. 1:
-\begin{itemize}
-    \item $\mathcal{H}^{p,q}(X)$.
-    \item $f^*$: pull-back. Various defintion from pp.1 to pp.4.
-\end{itemize}
-pp. 5,6,7:
-\begin{itemize}
-    \item $\mathcal{A}^{p,q}(U,E):=\Gamma(U,\Lambda^{p,q}T_{\mathbb{C}}^* X \otimes E)$.
-    \item $\bar{\partial}_E$
-    \item $\mathcal{H}^{p,q}(X,E)$.
-    \item $\bar{\partial}$-Poincaré lemma in one variable.
-\end{itemize}
-
-\section{Lecture 11 (20160412)}
-pp.1,2,3: 
-\begin{itemize}
-    \item $\bar{\partial}$-Poincaré lemma in n-dimension
-    \item $\Omega_X^p$: holomorphic p-forms. On pp.2.
-    \item $\check{H}^q(X,\Omega^p)\text{(Čech)}\cong \mathcal{H}_{\bar{\partial}}^{p,q}(X)$(Dolbeault). On pp.3.
-\end{itemize}
-pp. 6,7:
-\begin{itemize}
-    \item Analytic Subvarity.
-    \item Analytic Hybersurface.
-    \item Cousin's Problem.
-\end{itemize}
-
-\section{Lecture 12 Hermitian Structure on Manifold  Manifold (20160418)}
-pp. 1,2,3:
-\begin{itemize}
-    \item $I$ compatible with $<-,->$.
-    \item $\omega$: Fundamental form associated with $<,>$ and $I$. $\omega(v,w):= <I(v),w>$.
-    \item Conformal Equivalence.
-    \item $<,>$: Hermitian Inner Product.
-\end{itemize}
-pp. 4:
-\begin{itemize}
-    \item $( , )$: s.t. $(v,w):=<v,w>-i\omega(v,w) = <v,w> - i <I(v),w>$
-\end{itemize}
-pp. 5:
-\begin{itemize}
-    \item $<,>_{\mathbb{C}}$ be s.t.$<v\otimes \alpha, w\otimes \beta>:= \alpha \bar{\beta} <v,w>$.
-\end{itemize}
-pp. 6:
-\begin{itemize}
-    \item $\frac{1}{2}(,) = <,>_{\mathbb{C}} \arrowvert_{V^{1,0}}$
-\end{itemize}
-pp. 7,8:
-\begin{itemize}
-    \item Local computations: $z_i$,$h_{ij}$,
-    \item $\omega = (...dx^i...dy^i)$
-    \item $\omega$, Fundamental form on Riemannian Mnfd.
-    \item Kähler mnfd: $d\omega \equiv 0$.
-\end{itemize}
-
-\section{Lecture 13 Kähler Manifold (20160419)}
-pp.1:
-\begin{itemize}
-    \item Local computation: $\omega = (...dz^i...d\bar{z}^i)$
-\end{itemize}
-pp.4:
-\begin{itemize}
-    \item Fubini-Study Metric on $\mathbb{CP}^n$.
-\end{itemize}
-
-\section{Lecture 14 Hodge Theory (20160425)}
-pp.1:
-\begin{itemize}
-    \item $<,>$ on $\Lambda^k V$
-    \item vol: volumn element.
-    \item $*$: Hodge Star Operator.
-\end{itemize}
-pp.4:
-\begin{itemize}
-    \item $L$: Lefschetz Operator
-    \item $\Lambda$: adjoint of $L$. $\Lambda = *^{-1}\circ L\circ *$.
-\end{itemize}
-pp.5 :
-\begin{itemize}
-    \item $*,L,\Lambda$ on Kähler mnfd.
-    \item $d^*:= (-1)^{m*(k+1)+1}*\circ d\circ*$, adjoint of $d$. On a Kähler mnfd, $d^*= -*\circ d\circ*$
-    \item $\Delta:=d^*\circ d + d\circ d^*$.
-\end{itemize}
-pp. 6:
-\begin{itemize}
-    \item $\bar{\partial}^*, \partial^*$: Similar to the above for $d$.
-    \item $\Delta_\partial, \Delta_{\bar{\partial}}$: Similar to the above for $d$.
-\end{itemize}
-
-\section{Lecture 15 Hodge Theory on Manifold (20160426)}
-pp.1:
-\begin{itemize}
-    \item $(,)$ on $\mathcal{A}^*(X)$. $(\alpha,\beta):=\int_X g_\mathbb{C}(\alpha,\beta) vol$
-\end{itemize}
-pp.3:
-\begin{itemize}
-    \item $\mathcal{H}^k(X,g)$: d-harmonic forms. Sometimes we replace $\mathcal{H}$ with $\mathscr{H}$ for harmonic forms, so is for symbols below.
-    \item $\mathcal{H}^k_{\bar{\partial}}(X,g)$: $\bar{\partial}$-harmonic forms. 
-    (Be careful to distinguish this with Dolbeault Cohomology groups).
-    \item $\mathcal{H}^k_{\partial}(X,g)$: $\partial$-harmonic forms.
-\end{itemize}
-pp. 5:
-\begin{itemize}
-    \item $\mathcal{H}^k_d(X,g) \cong \mathcal{H}^{2n-k}_d(X,g)$, Poincar\'{e} duality
-    \item $\mathcal{H}^{p,q}_{\bar{\partial}}(X,g) \cong 
-    \left( \mathcal{H}^{n-p,n-q}_{\bar{\partial}}(X,g)\right)^*$, both are harmonic forms, called Serre Duality. 
-\end{itemize}
-pp. 6,7:
-\begin{itemize}
-    \item 
-    $\mathcal{A}^{p,q} = 
-    \bar{\partial}\mathcal{A}^{p,q-1}(X)\oplus
-    \bar{\partial}^* \mathcal{A}^{p,q+1}(X) \oplus
-    \mathcal{H}^{p,q}_{\bar{\partial}}(X,g)$:
-
-     Hodge decomposition
-
-    \item $\mathcal{H}^{p,q}_{\bar{\partial}}
-        \text{(harmonic forms)}
-        \cong
-        \mathcal{H}^{p,q}_{\bar{\partial}}(X)
-        \text{(Dolbeault Cohomology group)}$
-    \item $\mathcal{H}^{p,q}_{d}
-        \text{(harmonic forms)}
-        \cong
-        \mathcal{H}^{p,q}_{dR}(X)
-        \text{(de Rham Cohomology group)}$
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item A lot of isomorphisms between \textit{de Rham}, \textit{Dolbeault} and \textit{harmonic forms}.
-\end{itemize}
-
-\section{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}
-
-pp.1:
-\begin{itemize}
-    \item $\Delta_\partial = \Delta_{\bar{\partial}} = 
-        \frac{1}{2}\Delta_d$, for K\"{a}hler mnfd.
-\end{itemize}
-
-\section{Lecture 17 Hermitian Vector Bundle (20160510)}
-pp.1,3:
-\begin{itemize}
-    \item Hermitian Vector Bundle. pp.1
-    \item Antilinear map. pp.3.
-    \item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
-    \item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
-    \item $\bar{\partial}_E^*$
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item Kadaira-Serre Duality.
-\end{itemize}
-
-\section{Lecture 18 Connection (20160516)}
-\begin{itemize}
-    \item $\bigtriangledown$: connection. pp.1.
-    \item Trivial connections. pp.2
-    \item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
-    \item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
-    \item $\Delta = d+A$. pp.4.
-    \item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
-    \item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
-    \item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
-\end{itemize}
-
-\section{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
-\begin{itemize}
-    \item Holomorphic Connecction. pp.1.
-    \item $At(E)$: Atiyah class of $E$. pp.2.
-    \item $\Delta^k$. pp.4.
-    \item $F_\Delta$: curvature associated with $\Delta$. pp.5.
-    \item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
-    \item First Chern class of complex line bundle.
-\end{itemize}
-
-\section{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
-\begin{itemize}
-    \item Analytic Subvariety. pp.1.
-    \item Regular/Smooth Point. pp.1.
-    \item Singular Point. pp.2.
-    \item Irreducible analytic subvariety. pp.2.
-    \item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
-    \item Affine algebraic varieties. pp.3.
-    \item Projective algebraic varieties. pp.3.
-    \item Hypersurface. pp.4.
-    \item Divisor, $Div(X)$:=group of all divisors. pp.5.
-    \item Effective divisor. pp.6.
-    \item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
-    \item Meromorphic function on complex mnfd.
-    \item $(f)$: divisor given by a global meromorphic function.
-    \item Principal divisor. pp.8.
-\end{itemize}
-
-\section{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
-\begin{itemize}
-    \item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
-    \item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
-    \item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
-    \item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
-    \item Linear equivalent of divisors.
-    \item $*$: used only in this section to denoted the map:
-    $$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
-    pp.6.
-    \item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
-\end{itemize}
-
-\section{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
-\begin{itemize}
-    \item Base point of a line bundle. pp.4.
-    \item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
-    \item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
-\end{itemize}
-
-\part{Indices of Results}
-
-{Theorems, Remarks, etc.}
-\chapter{Local Theory}
-\label{chap:Local Theory}
-
-\section{1.1 Holomorphic Functions of Several Variables}
-\label{sec:book_1.1}
-
-\begin{prop}
-    The local ring $\mathcal{O}_{\mathbb{C}^n,0}$ is a UFD.
-\end{prop}
-(\textbf{pp.14 of \cite{book}})
-
-\begin{prop}{Weierstrass division theorem}
-    Let $f\in \mathcal{O}_{\mathbb{C}^n,0}$ and $g\in
-    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ be a Weierstrass
-    polynomial of degree $d$. Then there exist $r\in
-    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ of degree $<d$
-    and $h\in \mathcal{O}_{\mathbb{C}^n,0}$ such that $f=g\cdot h+r$.
-    The functions $h$ and $r$ are uniquely determined.
-\end{prop}
-(\textbf{pp.15 of \cite{book}})
-
-\begin{prop}
-    The local UFT $\mathcal{O}_{\mathbb{C}^n,0}$ is Noetherian.
-\end{prop}
-(\textbf{pp.16 of \cite{book}})
-
-\begin{coro}
-    Let $g\in \mathcal{O}_{\mathbb{C}^n,0}$ be an irreducible function.
-    If $f\in\mathcal{O}_{\mathbb{C}^n,0}$ vanishes on $Z(g)$, then
-    $g$ divides $f$.
-\end{coro}
-(\textbf{pp.16 of \cite{book}})
-
-\begin{lemma}
-    For any germ $X\subset \mathbb{C}^n$ the set $I(X)\subset
-    \mathcal{O}_{\mathbb{C}^n,0}$ is an ideal.
-    If $(A)\subset \mathcal{O}_{\mathbb{C}^n,0}$ denotes the ideal
-    generated by the subset $A\subset \mathcal{O}_{\mathbb{C}^n,0}$,
-    then $Z(A)=Z((A))$ and $Z(A)$ is analytic.
-\end{lemma}
-(\textbf{pp.18 of \cite{book}})
-
-\begin{lemma}
-    If $X_1\subset X_2$, then $I(X_2)\subset I(X_1)$. If $I_1\subset I_2$,
-    then $Z(I_2)\subset Z(I_1)4$. For any analytic germ $X$ one has
-    $Z(I(X))=X$. For any ideal $I\subset \mathcal{O}_{\mathbb{C}^n,0}$,
-    one has $I\subset I(Z(I))$.
-\end{lemma}
-(\textbf{pp.18 of \cite{book}})
-% TODO bookmark this chapter stops at page 18.
-
-\section{1.2 Complex and Hermitian Structures}
-\begin{lemma}
-    If $I$ is an almost complex structure on a real vector space $V$,
-    then $V$ admits in a natural way the structure of a complex vector
-    space
-\end{lemma}
-(\textbf{pp.25 of \cite{book}})
-
-\begin{remark}
-    An almost complex structure can only exist on an even dimensional
-    real vector space.
-\end{remark}
-
-\begin{coro}
-    Any almost complex structure on $V$ induces a natural orientation
-    on $V$.
-\end{coro}
-(\textbf{pp.25 of \cite{book}})
-
-\begin{lemma}
-    Let $V$ be a real vector space endowed with an almost complex
-    structure $I$. Then
-    $$ V_{\mathbb{C}} = V^{1,0}\oplus V^{0,1}$$
-    Complex conjugation on $V_{\mathbb{C}}$ induces an $\mathbb{R}$-linear
-    isomorphism $V^{1,0}\cong V^{0,1}$.
-\end{lemma}
-(\textbf{pp.26 of \cite{book}})
-
-\begin{remark}
-    Two almost complex structures on $V_{\mathbb{C}}$: $I$ and $i$,
-    coincide on the subspace $V^{1,0}$ but differ by a sign on
-    $V^{0,1}$.
-\end{remark}
-
-\begin{lemma}
-    Let $V$ be a real vector space endowed with an almost complex
-    structure $I$. Then the dual space 
-    $V^*=\text{Hom}_{\mathbb{R}}(V,\mathbb{R})$ has a natural almost
-    complex structure given by $I(f)(v)=f(I(v))$. The induced 
-    decomposition on 
-    $(V^*)_{\mathbb{C}}=\text{Hom}_{\mathbb{R}}(V,\mathbb{C})
-    = (V_{\mathbb{C}})^*$ is given by
-    $$ (V^*)^{1,0} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
-        f(I(v)) = i f(v) \} = (V^{1,0})^*$$
-    $$ (V^*)^{0,1} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
-        f(I(v)) = -i f(v) \} = (V^{0,1})^*$$
-    Also note that $(V^*)^{1,0} = 
-        \text{Hom}_{\mathbb{C}}((V,I),\mathbb{C})$.
-\end{lemma}
-
-\begin{prop}
-    For a real vector space $V$ endowed with an almost complex
-    structure $I$, one has:
-    \begin{enumerate}
-        \item $\bigwedge^{p,q}V$ is in a canonical way a subsapce
-            of $\bigwedge^{p+q} V_{\mathbb{C}}$.
-        \item $\bigwedge^k V_{\mathbb{C}}
-            = \bigoplus_{p+q=k}\bigwedge^{p,q}V$.
-        \item Complex conjugation on $\bigwedge^* V_{\mathbb{C}}$ defines
-            a ($\mathbb{C}$-linear) isomorphism
-            $\bigwedge^{p,q}V\cong \bigwedge^{q,p}V$, i.e.
-            $\bar{\bigwedge^{p,q}V}=\bigwedge^{q,p}V$.
-        \item The exterior prodoct is of bidegree $(0,0)$.
-    \end{enumerate}
-\end{prop}
-(\textbf{pp.27 of \cite{book}})
-\begin{remark}{Local calculation of $V^{1,0}$,$(V^*)^{1,0}$}
-    $$z_i=\frac{1}{2}(x_i-y_i)\text{, }\bar{z}_i=\frac{1}{2}(x_i+iy_i)$$
-    $$z^i=x^i+iy^i\text{, }\bar{z}^i=x^i-iy^i$$
-    $$I(z_i)=i z_i\text{, }I(z^i)=i z^i$$
-\end{remark}
-(\textbf{pp.27 to 28 of \cite{book}})
-
-\begin{lemma}
-    For any $m\leq \text{dim}_{\mathbb{C}}V^{1,0}$, one has
-    $$(-2i)^m (z_1\wedge\bar{z}_1)\wedge\cdots\wedge(z_m\wedge\bar{z}_m)=
-        (x_1\wedge y_1)\wedge\cdots\wedge(x_m\wedge y_m).$$
-    For $m=\text{dim}_\mathbb{C} V^{1,0}$, this defines a positive
-    oriented volume form for the natural orientation of $V$.
-
-    Also
-    $$\left(\frac{i}{2}\right)^m
-      (z^1\wedge\bar{z}^1)\wedge\cdots\wedge(z^m\wedge\bar{z}^m)=
-      (x^1\wedge y^1)\wedge\cdots\wedge(x^m\wedge y^m).$$
-\end{lemma}
 
@@
 \end{thebibliography}
-\part{License}
+\chapter{License}
 The entire content of this work (including the source code

### 2016-08-30 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Inaugurating the new green function file, marking my first attempt at research level physics.

@@
 $G_{\nu\lambda}\equiv g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$.
+\nomenclature{$G_{\nu\lambda}$}
+    {$g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$\nomrefpage}
 This clearly represent the idea of repulsive Coulomb force.
@@
 \paragraph{Bypassing Einstein}
-% TODO stopped here.
-\paragraph{Unclear Points} Marked in the book. Especially, where
-in the calculatioin above shows that the field is of a spin $1$
-or a spin $2$ meson?
+
+The producedure here is almost identical to that of the previous chapter.
+Here, two equations are sued to obtain the final result:
+\begin{align}
+    k^\mu \varepsilon^{(a)}{\mu\nu} &= 0\\
+    g^{\mu\nu}\varepsilon^{(a)}{\mu\nu}&=0 \text{(traceless)}\\
+\end{align}
+result:
+\begin{align}
+    \sum_a \varepsilon^{(a)}_{\mu\nu}(k) \varepsilon^{(a)}(k)
+        \varepsilon^{(a)}_{\lambda\sigma}(k)=
+        (G_{\mu\lambda}G_{\nu\sigma}+G_{\mu\sigma}G_{\nu\lambda})
+        -\frac{3}{2}G_{\mu\nu} G_{\lambda\sigma}
+\end{align}
+so that the propagator for a massive spin $2$ particle 
+\nomenclature{$D_{\mu\nu,\lambda\sigma}(k)$}
+{propagator for a massive spin $2$ particle\nomrefpage}
+is:
+\begin{align}
+    D_{\mu\nu,\lambda\sigma}(k)=
+    \frac{ (G_{\mu\lambda}G_{\nu\sigma}+G_{\mu\sigma}G_{\nu\lambda})
+        -\frac{3}{2}G_{\mu\nu} G_{\lambda\sigma} }
+        {k^2-m^2}
+\end{align}
+
+\paragraph{ Why we fall}
+
+\paragraph{Unclear Points} Marked in the book.
 

### 2016-08-31 Green function/green-f.tex
Chapter one of the new green-func

@@
 % http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{book}
+\documentclass{article}
 
@@
 \abstract{
-    This is a note for reading the paper \cite{1}, and for understanding
+    This is a note for reading the paper \cite{dissertation}, and for understanding
     the code produced from that file.
@@
 
+\section{Chapter 1 - Introductions}
+\label{sec:Chapter 1 - Introductions}
+This chapter is really a nice introduction to the current fields of mesoscopic physics.
+The writing is clear and it traces the develpment of this field. It gives me a lucid
+and holistic historical account of both the important discoveries and motives behind
+them. I should find those marked regions on pdf inside this part very useful.
+
 \begin{thebibliography}{1}
-    \bibitem{book} Complex Geometry
+    \bibitem{dissertation} 
+        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
+        by von Georgo Metalidis. (Link found via Google)
 \end{thebibliography}
-\chapter{License}
+\section{License}
 The entire content of this work (including the source code

### 2016-09-01 Green function/green-f.tex
Uodated notes of green function.

@@
 
+% Following is for the special character: differential "d".
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
+\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
 % Following is for theorems etc environments
@@
 
+% A list of nomenclatures.
+\usepackage{nomencl}
+\makenomenclature
+
 \title{(Tentative) Calculating Green Function}
@@
 \abstract{
-    This is a note for reading the paper \cite{dissertation}, and for understanding
-    the code produced from that file.
+    This is a note for reading the paper \cite{dissertation}, and for 
+    understanding the code produced from that file.
 }
@@
 \section{Chapter 1 - Introductions}
-\label{sec:Chapter 1 - Introductions}
+\label{sec:Chapter_1_-_Introductions}
 This chapter is really a nice introduction to the current fields of mesoscopic physics.
@@
 \end{thebibliography}
+\section{Chapter 2 - 2 Landauer-Büttiker formalism}
+\label{sec:Chapter_2_-_2_Landauer-Buttiker_formalism}
+
+This chapter introduces the Landauer-Büttiker formalism for calculating the
+transport properties. The typical setup is illustrated below:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{ch2.setup_for_L-B_formalism}.png}
+    \caption{Setup for the Landauer-Büttiker formalism}
+    %\label{fig:}
+\end{figure}
+
+In that formalism, the currents following through the leads have the following
+expression:
+\begin{align}
+    I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
+\end{align}
+where $T_{pq}$ is the transmission coefficients for electrons to go from
+lead $q$ to lead $p$. This formula can be simplified/linearized into:
+\begin{align}
+    I_p = \frac{e^2}{h}\sum_q T_{pq}(E_F)(V_p-V_q)
+\end{align}
+An obvious advantage of Landauer-Büttiker formalism is that it makes the
+dependence of $I_p$ on experimental setup explicit in the formula.
+
+This chapter continue to discuss some time reversal symmetry (TR) properties 
+of this formula, centring/centering around the coefficient $T_{pq}$.
+But I am perplexed by that he, while discussing TR, mentions the
+magnetic field $B$ and formulae like:
+\begin{align}
+    T_{12}(+B)= T_{12}(-B)
+\end{align}
+\nomenclature{confusion: TR and $B$}{\nomrefpage}
+
+\section{Chapter 3 Tight-binding model}
+\label{sec:Chapter_3_Tight-binding_model}
+
+\printnomenclature
 \section{License}

### 2016-09-03 Draft/draft.tex
1. Seperate the old note "Lectures on the Frontiers of Physics" from general    "Draft". Archive it inside the "Finished". 2. Initial commit to MH Wong's dissertation.

@@
 
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
-    \textbf{Thermal electrics}
-
-    \subsection{By Lang. Chen}
-    \label{sec:c.l}
-    Grow thin films.
-    \begin{itemize}
-	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
-	\item 
-	orbital contral of electrons -> 
-	orbitronics -> Control of Spin orbital coupling.
-	\item
-	Multiferroics -> multiple order parameters, and the interaction
-	between them. E.g. $BiFeO_3$.
-	\item
-	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
-	symmetries simultaneous broken.
-	\item
-	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
-	exactly in theoretical physics?
-	\item
-	$H_2S$: 200K superconductor?
-	\item
-	The Double Exchange effect of oxygem -> Half-metal, phase transition.
-    \end{itemize}
-
-    \subsection{By Alan}
-    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
-    the keys.
-
-    \subsection{By Li, Huang}
-    \begin{itemize}
-            \item Computational Physics
-            \item Surface Dynamics
-            \item Structural factor from 2D to 3D.
-            \item Finding Order Amid the Chaos. amorphous -> spatially
-                    resolved distributed function.
-            \item ?: What is genetically algorithm.
-    \end{itemize}
-    \textbf{Computational and theoretical studies of Surface dynamics}
-
-    \begin{itemize}
-            \item Surface atoms is immersed in a very different environment
-                    compared with the bulk atoms.
-            \item First-principle calculations
-            \item DFT + LDA -> Conser equation
-            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
-                    Conser equation
-            \item Continumm method ?
-    \end{itemize}
-
-    \subsection{By Junfen, Liu}
-    \begin{itemize}
-            \item electronic transport in mesoscopic systems:
-            \item Spintronics
-            \item Graphene eletronics
-            \item Superconductors etc.
-    \end{itemize}
-    \textbf{Quantum wire conductiing}
-    The conduction channel in quantum wire is quantized, with discrete value
-    of conductance.
-    \begin{itemize}
-            \item $\lambda_F$ Fermi wavelength
-            \item $L_m$ Momuntum relaxation length <-- impurities.
-            \item $L_\phi$ Phase relaxation length <-- memory of phase,
-                    related to energy $\omega = E/\hbar$.
-            \item $L$ Sample length
-    \end{itemize}
-    \begin{itemize}
-            \item Ballistic transport: $L << L_m$ No scattering.
-            \item Diffusive $L>L_m$, scattering, reduced transmission.
-            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
-            \item Classical. (Omitted)
-    \end{itemize}
-    \textbf{Conductance}
-    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
-    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
-    accounting for the back scattering, perhaps the transmission
-    probability.
-    In reality, $G=\sum_{\text{Different channels}}G_i$,
-
-    We can turn the $G$ into resisivity: 
-    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
-    $R+T=1$
-
-    \paragraph{Resonate Transmission} (Omitted)
-
-    \paragraph{Spintronics} Use the extra freedom of Spin.
-
-    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)
-
-    GMR: 2007 Nobel prize in Physics.
-
-    Hall Effect (Omitted)
-    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);
-
-    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)
-
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
-    \textbf{Klein Paradox}
-
-    \paragraph{Josephson Junction} A phase difference could conduct
-    electricity in Superconductors.
-
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
-    Requires strong magnetic field: $\approx 10$ Tesla.
-
-    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
-    where $M$ is the magnetic susceptibility.
-    Two-factors: SO coupling. Spin-dependent Hall Effect.
-
-    An excellent illustrations is found in \cite{Arxiv-Xiao}:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/1}
-        \caption{Illustration}
-        \label{fig:Xiao Illustration}
-    \end{figure}
-
-    \subsection{By Kedong Wang}
-    Tunneling current $I\propto V e^{-2kz}$, where 
-    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
-    $I$ is very sensitive to the distance $z$.
-
-    \paragraph{Work function} $\phi$ characterize the obstruction
-    that prevents electron from escaping the sample.
-
-    \subsection{By Mingyuan Hunag}
-    Not insterested.
-
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
-    copy operators in Quantum Mechanics.
-
-    \begin{proof}
-    We proove it by contradiction. Let $U$ be the copy operator. By definition,
-    we have
-    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
-    For any $\ket{\psi}$.
-    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
-    \begin{align*}
-        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
-        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
-        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
-    \end{align*}
-    This is a contradiction.
-    \end{proof}
-    \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
-        strong. However, if we assume that the copyer only
-        works for certain states $\ket{\phi}$, then with the knowledge
-        of these certain states, we could in principle create an exact copy
-        of these states. This copy ,in the sense of another instance of the
-        same object, of original state should not be considered to be an
-        copied version of the original state.
-    \end{remark}
-
-    \subsection{By Liyuan Zhang}
-    Not insterested.
 \section{Problems in Bernevig's Topological ...}
@@
     Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
     \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)

### 2016-09-03 Finished/Lectures on the Frontiers of Physics/Lectures on the Frontiers of Physics.tex
1. Seperate the old note "Lectures on the Frontiers of Physics" from general    "Draft". Archive it inside the "Finished". 2. Initial commit to MH Wong's dissertation.

--- 2016-07-08 draft.tex
@@
 
-\title{Draft}
-\date{\today}
+\usepackage{tensor}  % For tensor indices
+\usepackage[all]{xy} % For drawing category diagrams
+\usepackage{mathrsfs}
+
+\title{Lectures on the Frontiers of Physics}
+\date{2016-07-22}
 \author{we.taper}
@@
 \abstract{
-    This is a draft.
+    This is notes of lectures given by (assistant/)professors of physics in SUSTC,
+    each talking about their own researches. Since they are generally boring
+    (targeted at first/second year students), I omitted many of them.
 }
@@
 
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
+\section{By JQ. He.}
 \textbf{Thermal electrics}
 
-    \subsection{By Lang. Chen}
+\section{By Lang. Chen}
 \label{sec:c.l}
@@
 
-    \subsection{By Alan}
+\section{By Alan}
 \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
@@
 
-    \subsection{By Li, Huang}
+\section{By Li, Huang}
 \begin{itemize}
@@
 
-    \subsection{By Junfen, Liu}
+\section{By Junfen, Liu}
 \begin{itemize}
@@
 
-    \paragraph{Resonate Transmission} (Omitted)
+\subsection{Resonate Transmission} (Omitted)
 
-    \paragraph{Spintronics} Use the extra freedom of Spin.
+\subsection{Spintronics} Use the extra freedom of Spin.
 
@@
 
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
+\subsection{Graphene} Carrier -> Relativistic Dirac fermions.
 \textbf{Klein Paradox}
 
-    \paragraph{Josephson Junction} A phase difference could conduct
+\subsection{Josephson Junction} A phase difference could conduct
 electricity in Superconductors.
 
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
+\section{By Haizhou, Lu}
+\subsection{Quantum Anomalous Hall Effect}
 Requires strong magnetic field: $\approx 10$ Tesla.
@@
 
-    \subsection{By Kedong Wang}
+\section{By Kedong Wang}
 Tunneling current $I\propto V e^{-2kz}$, where 
@@
 
-    \paragraph{Work function} $\phi$ characterize the obstruction
+\subsection{Work function} $\phi$ characterize the obstruction
 that prevents electron from escaping the sample.
 
-    \subsection{By Mingyuan Hunag}
-    Too boring.
+\section{By Mingyuan Hunag}
+Not insterested.
 
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
+\section{By Wenkang Wong}
+\subsection{Non-clone Theorem} We can easily see that there is no universal
 copy operators in Quantum Mechanics.
@@
 \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
+    We assume that the copier is universal. This might seems to be too
     strong. However, if we assume that the copyer only
@@
 
-\section{Problems in Bernevig's Topological ...}
-
-    \subsection{Chapter 2}
-    \paragraph{Non-Abelian Berry Transport}
-    Derive Berry curvature to the adiabatic transport of a degenerate
-    multiplet of states separated by a gap from the excited states.
-    (Cautious about rotation within degenerate states).
-
-    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$
-
-    Approach:
-    Assuming that the those degenerate states are labeled by $1\cdots N$. 
-    Thus we have naturally:
-	\begin{align}
-            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
-        \phi = \sum_n A_n \psi_n
-    \end{align}
-
-    Then we have:
-    \begin{align}
-    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
-	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
-	\sum_n E A_n \psi_n&=i\hbar\sum_n
-		\left(
-		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
-		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
-		\right) \nonumber\\
-	E A_m &=i\hbar
-		\frac{\partial A_m(t)}{\partial t}
-		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
-    \end{align}
-    Put in another form:
-    $$
-    \sum_n \left(\delta^n_m E
-        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
-        =
-    i\hbar \frac{\partial A_m(t)}{\partial t}
-    $$
-    In matrix form:
-    \begin{align}
-            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
-    \end{align}
-    where:
-    \begin{align}
-        E &= \left(
-        \begin{array}{ccc}
-         \cdots   &     &   \\
-              & E &   \\
-             &    & \text{...} \\
-        \end{array}
-        \right) \\
-        P &= (P^m_n) = \left(
-        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
-        A &= \left(\begin{array}{c}
-            A_1(t) \\
-            A_2(t) \\
-            \cdots \\
-        \end{array}\right)
-    \end{align}
-
-    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
-    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
-    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.
-
-    Notice that
-    \begin{align}
-            0= \frac{\partial}{\partial t} \braket{m|n} &=
-        \braket{\frac{\partial}{\partial t}m|n} +
-        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
-    \end{align}
-    temporary mathematica code:
-
-% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
-%         {y1[x], y2[x]}, x]
-% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
-% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
-% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
-
-\section{Miscellnaneous Notes}
-    \subsection{Super conductor}
-    Mean-field approach to deal with a four operator diagonalization.
-
-    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
-    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:
-
-    	$$ \delta^2 \approx 0 $$
-    i.e.:
-
-    \begin{align}
-    	( (CD)^* - avg ) ( CD - avg ) = 0\\
-    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
-    \end{align}
-    Hence a four operator is reduced into a few of two operators.
-    Such method could be naturally extended to treat the operator
-    $\sum_{i,j} D^*_i C^*_i C_j D_j$.
-
-    A copper pair has the energy of:
-    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$
-
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
-    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
-
-    This will require an additional enegy of $2\Delta$.
-
-    The exact meaning of "equivalent to" is as follows:
-    \begin{align}
-        & \text{break a copper pair} \longrightarrow 
-        \text{scatter two electrons consecutively} 
-        \nonumber\\ & \longrightarrow 
-        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
-    \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
-
-    \subsection{Preface of BSCS}
-        \label{sec:Preface_of_Bosonization_and_Strongly 
-        Correlated_Systems}
-    BSCS: see \cite{BSCS}.
-    Parallism between theories in condensed matter physics and those in
-    particle physics.
-    \begin{itemize}
-            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
-                    (C.M.P.)
-            \item 'inflation' in Cosmology, first order phase transition
-            \item 'cosmic strings', magnetic field vortex lines in type
-                    II superconductors
-            \item Hadron-meson interaction, Ginzburg-Landau theory of
-                    superfluid $He^3$.
-    \end{itemize}
-    Same ideas on different space-time scales, different hierachical
-    'layers'.
-    Strong parallism: \textbf{strongly correlated low dimensional system}
-
-    E.g.:
-
-    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.
-
-    Approaches:
-    \begin{enumerate}
-            \item Exact solutions
-            \item Reformulate complicated interacting models in such a way
-                    that they become weekly interacting. -> Bosonization.
-
-                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
-                    Model of interacting
-
-                    fermions.
-                    (Jordan and Wigner, 1928)
-    \end{enumerate}
-    Bosonization: transformation from fermions to a scalar massless bosonic
-    field.
-
-    \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
-
-    pp. 266.
-
-    \begin{defi}
-        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
-        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
-        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
-    \end{defi}
-
-    pp. 291.
-
-    \begin{thm}[Existence-uniqueness theorem]
-        There exists one, and only one, solution of the initial-value
-        problem
-
-        \begin{align}
-            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
-                \mathbf{x}(t_0) = \mathbf{x}^0 = 
-                \left(
-                \begin{array}{c}
-		            x^0_1\\
-                    x^0_2\\
-                    \cdots
-                \end{array} 
-                    \right)
-        \end{align}
-
-        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
-    \end{thm}
-    \begin{remark}
-        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
-        time $t$. Also notice that the elements of $\mathbf{A}$ are just
-        numbers.
-    \end{remark}
-
-    \begin{thm}
-        The dimension of the space $\mathbf{V}$ of all solutions of the
-        homogeneous linear system of differential equations:
-        \begin{align}
-            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
-        \end{align}
-        is $n$, i.e. the dimension of vector $\mathbf{x}$.
-    \end{thm} 
-    \subsection{ODE by Arnold}
-    sec. 14
-    \begin{defi}
-        \begin{align}
-            \label{eq:e^A}
-            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
-            \text{or}& \nonumber \\
-            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
-        \end{align}
-        where $I$ is the identity matrix.
-    \end{defi}
-    Equivalance of the two definition will be addressed in the Theorem on
-    pp. 165.
-
-    Important theorems:
-    \begin{thm}[pp. 158]
-        The series $e^A$ converges for any $A$ uniformly on each set
-        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
-    \end{thm}
-    \begin{thm}[pp. 160]
-        $$e^{At} = H^t$$
-        where $H^t$ is the translation operator which sends every polynomial
-        $p(x)$ into $p(x+t)$.
-    \end{thm}
-    \begin{thm}[pp. 163]
-        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
-    \end{thm}
-    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
-        Constant Coefficients]
-        The solution of:
-        \begin{align}
-            \label{eq:fund_thm_of_linear_eqs_const_coef}
-            \dot{\mathbf{x}} = A\mathbf{x}
-        \end{align}
-        with initial condition $\phi(0) = \mathbf{x}_0$ is
-        \begin{align}
-            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
-        \end{align}
-    \end{thm}
-
-    Practically solution to
-    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
-    (pp. 173, Sec 17)
-    (Assuming $A$ is diagonalizable.)
-    \begin{itemize}
-        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
-            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
-        \item Expand the initial condition in the new basis.
-            \begin{align}
-                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
-            \end{align}
-        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
-    \end{itemize}
-    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
-
-    \begin{align}
-        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
-            (\eta_b,U_{ac}\dot{\psi}_c
-    \end{align}
-    \subsection{Quantum Statistical Mechanics}
-    \label{sec:Quantum Statistical Mechanics}
-    \begin{defi}[Time Evolution Operator]
-        The time evolution operator $U(t,t_0)$ is defined such that
-        \begin{align}
-            \label{eq:def_time_evo_op}
-            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
-        \end{align}
-    \end{defi}
-    It satisfy the relationship:
-    \begin{align}
-        \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
-    \end{align}
-    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
-    Equations.
-
-    \paragraph{Quantum Macrostates}
-    Macrostates of the system depend on only a few the thermodynamic
-    functions. We can form an ensemble of a large number $\mathcal{N}$ of
-    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
-    The different microstates occur with probability $p_\alpha$.
-    When wen no longer have exact knowledge of the microstate of a
-    system the system is said to be in a \textit{mixed state}.
-    The ensemble average of the quantum mechanical expectation
-    value is given by:
-    \begin{align}
-        \label{eq:quantum_macrostates_ensemble_avg}
-        \bar{\braket{O}} &= 
-            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
-            = \sum_{\alpha,m,n} p_\alpha
-                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
-                \nonumber\\
-            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
-                = \text{tr}(\rho O)
-    \end{align}
-    where we have introduced the density matrix:
-    \begin{defi}[Density Matrix]
-        The density matrix $\rho(t)$ is defined as
-        \begin{align}
-            \label{eq:density_matrix_def}
-        \braket{n|\rho(t)|m} \equiv
-        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
-        \end{align}
-        or
-        \begin{align}
-            \label{eq:density_matrix_def_2}
-            \rho(t) \equiv \sum_\alpha p_\alpha
-                \ket{\psi_\alpha}\bra{\psi_\alpha}
-        \end{align}
-    \end{defi}
-    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
-    P.D.F, since $\rho$ often represents density.
-
-    Density matrix satisfies several good properties:
-    \begin{itemize}
-        \item Normalized
-        \item Hermiticity
-        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
-    \end{itemize}
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
-
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
-
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-\end{thebibliography}
+\section{By Liyuan Zhang}
+Not insterested.
 \section{License}
@@
 
+\begin{thebibliography}{1}
+    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
+\end{thebibliography}
 \end{document}

### 2016-09-04 Green function/green-f.tex
Updating Chapter 3 of Green function.

@@
 
-\begin{thebibliography}{1}
-    \bibitem{dissertation} 
-        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
-        by von Georgo Metalidis. (Link found via Google)
-\end{thebibliography}
 \section{Chapter 2 - 2 Landauer-Büttiker formalism}
@@
 
+Here in this chapter the author presents the fundamental Hamiltonian of
+the system under consideration.
+\marginpar{
+    Given the formula mentioned in previous chapter, the Hamiltonian
+    presented here seemed extraneous. Maybe the author wants to examine
+    the physics in more detail.
+}
+
+The process to obtain the Hamiltonian is discretization the Hamiltonian
+in continuous case, quite the reverse of the first few chapters of
+A. Zee's QFT in a Nutshell. It should be noted that "a site may represent 
+a region containing many atoms", although "this region should be small 
+compared to physically relevant quantities such as the Fermi wavelength".
+
+    \subsection{3.1 Spin-degenerate system}
+    \label{sec:3.1_Spin-degenerate_system}
+    Here the general Hamiltonian, using tight-binding model, is
+    mentioned:
+    \begin{align}
+        H = &\sum_{n,m} 
+            \left( t^x_{nm}\ket{n+1,m}\bra{n,m}
+                +t^y_{nm}\ket{n,m+1}\bra{n,m}+h.c.\right)\nonumber\\
+            &+\sum_{n,m} \epsilon_{nm}\ket{n,m}\bra{n,m}
+    \end{align}
+
+    The important thing is to determine the coefficient $t$.
+    In the absence of magnetic field, $t$ is give by:
+    \begin{align}
+        t^x_{nm}=t^y_{nm}=-t=-\frac{\hbar^2}{2m^* a^2}
+    \end{align}
+    When magnetic field is present, we effect a so called Peierls
+    substitution to get $t$.
+    \marginpar{
+        The author points to a paper, saying that it contains a
+        "lucid discussion on the physics" of Peierls substitution.
+        This might be something worth reading.
+    }
+    The result is, using Landau gauge in one dimensional under a
+    homogeneous magnetic field.
+    \begin{align}
+        t^x_{nm} =& -t e^{i2\pi (m-1) \Phi/\Phi_0} \\
+        t^y_{nm} =& -t
+    \end{align}
+
+    When the magnetic field is inhomogeneous, it is generally difficult
+    to choose a gauge to calculate analytically. The author uses a
+    very intuitive discretization process to approach this problem.
+    The process is best illustrated by just the following picture:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{ch3.not-uniform_magnetic_field}.png}
+        \caption{Not uniform magnetic field}
+        \label{fig:ch3-uniform_magnetic_field.png}
+    \end{figure}
+
+    Therefore, the result is something like:
+    \begin{align}
+        t^x_{nm}=-t e^{i2\pi\sum_{m'<m}\Phi_{nm'}/\Phi_0}
+    \end{align}
 \printnomenclature
+    \subsection{3.2 Including spin degrees of freedom}
+    \label{sec:3.2_Including_spin_degrees_of_freedom}
+
+    When the spin is taken into consideration, the formulation should
+    be modified accordingly.
+
+    If Zeeman/exchange splitting is considered, then:
+    \begin{align}
+        H_S = -\frac{1}{2}g^* \mu_B
+            \sum_{nm}\ket{n,m}\bra{n,m}\otimes (B^{eff}_{nm}\cdot\sigma)
+    \end{align}
+    Not that the magnetic field strength here is only "effective".
+
+    If Spin-orbit coupling is taken into consideration,
+    \footnote{
+        In my opinion, this is essentially all about Spin-Magnetic 
+        field coupling, not just Spin-Orbital coupling.
+    }
+    the following Hamiltonian should be considered:
+    \begin{align}
+        H_{SO}= \lambda P\cdot (\bigtriangledown V \times \sigma)
+        \label{eq:ch3.SO_coupling}
+    \end{align}
+    Here $P$ is the mechanical momentum operator, $\sigma$ is the
+    three pauli spin matrix $(\sigma_x, \sigma_y, \sigma_z)$.
+
+    The tight-binding version of this is too complicated to be presented
+    here, it is on page 16, equation (3.20).
+
+    One additional consideration is the Rashba spin-orbit coupling.
+    This is the peculiar result of electrons trapped in a two
+    dimensional surface. In the $Z$ direction, with $Z$ perpendicular
+    to the 2 dimensional plane, the potential looks like something
+    below, called a triangular potential:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/{ch3.rashba_spin-orbit_effect}.png}
+        \caption{Conduction band at the interface of a semiconductor 
+            heterostructure. Band bending creates a potential well 
+            $V(z)$ confining the electrons to the XY plane. The asymmetry 
+            of this well leads to Rashba spin-orbit coupling.}
+        \label{fig:ch3-orbit_effect.png}
+    \end{figure}
+    It is pretty obvious, by equation \ref{eq:ch3.SO_coupling}, that
+    this potential is going into our Hamiltonian.
+    The result in tight-binding model is yet another complicated
+    Hamiltonian, not to be presented here, numbered equation (3.23)
+    on page 18.
+
+\section{Anchor}
+
+\begin{thebibliography}{1}
+    \bibitem{dissertation} 
+        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
+        by von Georgo Metalidis. (Link found via Google)
+\end{thebibliography}
 \section{License}

### 2016-09-05 Green function/green-f.tex
Updated Green function.

@@
 \label{sec:Chapter_1_-_Introductions}
-This chapter is really a nice introduction to the current fields of mesoscopic physics.
-The writing is clear and it traces the develpment of this field. It gives me a lucid
-and holistic historical account of both the important discoveries and motives behind
-them. I should find those marked regions on pdf inside this part very useful.
+This chapter is really a nice introduction to the current fields of 
+mesoscopic physics. The writing is clear and it traces the develpment 
+of this field. It gives me a lucid and holistic historical account of 
+both the important discoveries and motives behind them. I should 
+find those marked regions on pdf inside this part very useful.
 
@@
 \begin{align}
+    \label{eq:ch1.Landauer-Buttiker_formula}
     I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
@@
 
-\section{Chapter 3 Tight-binding model}
+\section{Chapter 3 - Tight-binding model}
 \label{sec:Chapter_3_Tight-binding_model}
@@
     Given the formula mentioned in previous chapter, the Hamiltonian
-    presented here seemed extraneous. Maybe the author wants to examine
-    the physics in more detail.
+    presented here seemed seemingly extraneous. Read the introduction
+    here in chapter 4 to understand the underlying logic.
 }
@@
 
+\section{Chapter 4 - Green’s function formalism}
+\label{sec:Chapter_4-Greens_function_formalism}
+
+In this section we finally circled back to the Landauer-Büttiker
+formalism. Here a breif summary of chapter 3 and 4 is opportune.
+The purpose of chapter 3 and 4 as a whole, is to calculate the 
+transmission coefficient $T_{qp}$ in equation
+\ref{eq:ch1.Landauer-Buttiker_formula}. Here, chapter 3 establish the
+Hamiltonian, and chapter 4 uses the Green function to calculate
+transmission coefficient out of the Hamiltonian.
+
+    \subsection{4.1 Green’s functions: The basics}
+    \label{sec:4.1_Greens_functions_The_basics}
+
+    The author takes the definition of Green's function as inverse
+    of Hamiltonian, more specifically:
+    \begin{align}
+        [E-\hat{H}]\hat{G}(E) = 1
+    \end{align}
+    or, in the position-spin representation:
+    \begin{align}
+        [E-H(\vec{x})]G(\vec{x},\vec{x'},E)=\delta(\vec{x}-\vec{x'})
+    \end{align}
+    where $\vec{x}=(\vec{r},\sigma)$, containing in addition to the
+    usual spatial part, the spin part.
+
+    The physical meaning is also explained, although I learnt this
+    better in A. Zee's QFT in a Nutshell. However, he notes that
+    to disguish between the source and sink, i.e. to tell whether
+    the Green's function calculated represents a wavefunction
+    resulted from a unit excitation (the sink), or a source for such
+    an excitation, we should incorporate boundary conditions. This is
+    done by adding "an infinitesimal imaginary variable into the energy",
+    "leading to the following definitions":
+    \begin{align}
+        G^{\pm}(\vec{x},\vec{x'},E)\equiv \lim_{\eta\to 0^{+}}
+            G(\vec{x},\vec{x'},E\pm i\eta)
+    \end{align}
+    and $G^{\pm}$ satisfies:
+    \begin{align}
+        [E\pm i\eta - H(\vec{x})] G^{\pm}(\vec{x},\vec{x'},E)=
+            \sigma(\vec{x}-\vec{x'})
+    \end{align}
+    The functions $G^+$ and $G^-$ are called respectively the
+    \textbf{retarded and advanced Green's function}. The author
+    mentions that, "when Fourier transforming the functions $G^\pm$ to
+    the time domain using a closed contour integration in the complex 
+    plane, they would correspond to causal and anticausal solutions".
+
+    Though seemingly extraneous, the operator definition for above
+    Green functions is also mentioned:
+    \begin{align}
+        \hat{G}^{\pm}(E)\equiv \lim_{\eta\to 0^+}
+            \frac{1}{E\pm i\eta-\hat{H}}
+    \end{align}
+    \subsection{4.2 Transmission coefficients and the Green’s function}
+    \label{sec:4.2_Transmission_coefficients_and_the_Greens_function}
+
+    Here it is mentioned than the transmission coefficient is related
+    Green's funciton in the following way:
+    \begin{align}
+        T_{pq} = \text{Tr}\left[\Gamma_p G_{pq}\Gamma_q G^{\dagger}_{pq}
+                \right]
+    \end{align}
+    Here $G_{pq}$ is, to borrow the language of matrix mechanics,
+    a submatrix of the Green's function. $\Gamma_p$ is a abbreviation
+    for the following counting:
+    \marginpar{I am not sure about this peculiar thing.}
+    \begin{align}
+        \label{eq:}
+        \Gamma_p \equiv i(\sum_p-\sum^\dagger_p)
+    \end{align}
+    Here $\sum_p$ is named "self-energy of the lead", something I
+    don't quite understand.
 \section{Anchor}

### 2016-09-06 G.R/G.R.tex
Initiating new fields: general relativity and quantum gravity.

--- 2016-09-01 Green function/green-f.tex
@@
 \usepackage{mathrsfs}
+% Followings are for the special character: differential "d".
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
+\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
 \numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
@@
 
-% Following is for the special character: differential "d".
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
 % Following is for theorems etc environments
@@
 
-\usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols
-
-% To include PDF in higher version format.
-\pdfoptionpdfminorversion=6
-
 % A list of nomenclatures.
@@
 
-\title{(Tentative) Calculating Green Function}
-% TODO give it a better name.
+\title{Notes for General Relativity}
 \date{\today}
@@
 \abstract{
-    This is a note for reading the paper \cite{dissertation}, and for 
-    understanding the code produced from that file.
+    (None)
 }
 \tableofcontents
+\section{The Principle of Relativity}
+\label{sec:Principle_of_Relativity}
+Landau's book \cite{landau} describes the speed of light, as a speed of the
+maximum velocity of propagation of interaction. He perceives velocity as
+describing the propagation of interaction.
 
-\section{Chapter 1 - Introductions}
-\label{sec:Chapter_1_-_Introductions}
-This chapter is really a nice introduction to the current fields of mesoscopic physics.
-The writing is clear and it traces the develpment of this field. It gives me a lucid
-and holistic historical account of both the important discoveries and motives behind
-them. I should find those marked regions on pdf inside this part very useful.
+In another aspect, I think that time does not exist. I perceive time as
+a agent of the environmental effect, communicating information and 
+coordinating movement between the system under consideration and its 
+envrionment. Therefore, a single existance is eternal by nature. Perhaps 
+before the universe originates, time is a meaningless concept. In my 
+view, the light is the only reliable tool to serve function of
+communication and coordination.
+
+Fram either perspective, the speed of light is inherently constent.
+However, from my view, it is not clear why this speed should be a maximum.
+
+\subsection{Invariance of Interval}
+\label{sec:Invariance of Interval}
+
+The Landau's book\cite{landau}, introduces a
 
 \begin{thebibliography}{1}
-    \bibitem{dissertation} 
-        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
-        by von Georgo Metalidis. (Link found via Google)
+    \bibitem{landau} The Classical Theory of Fields
 \end{thebibliography}
-\section{Chapter 2 - 2 Landauer-Büttiker formalism}
-\label{sec:Chapter_2_-_2_Landauer-Buttiker_formalism}
-
-This chapter introduces the Landauer-Büttiker formalism for calculating the
-transport properties. The typical setup is illustrated below:
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/{ch2.setup_for_L-B_formalism}.png}
-    \caption{Setup for the Landauer-Büttiker formalism}
-    %\label{fig:}
-\end{figure}
-
-In that formalism, the currents following through the leads have the following
-expression:
-\begin{align}
-    I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
-\end{align}
-where $T_{pq}$ is the transmission coefficients for electrons to go from
-lead $q$ to lead $p$. This formula can be simplified/linearized into:
-\begin{align}
-    I_p = \frac{e^2}{h}\sum_q T_{pq}(E_F)(V_p-V_q)
-\end{align}
-An obvious advantage of Landauer-Büttiker formalism is that it makes the
-dependence of $I_p$ on experimental setup explicit in the formula.
-
-This chapter continue to discuss some time reversal symmetry (TR) properties 
-of this formula, centring/centering around the coefficient $T_{pq}$.
-But I am perplexed by that he, while discussing TR, mentions the
-magnetic field $B$ and formulae like:
-\begin{align}
-    T_{12}(+B)= T_{12}(-B)
-\end{align}
-\nomenclature{confusion: TR and $B$}{\nomrefpage}
-
-\section{Chapter 3 Tight-binding model}
-\label{sec:Chapter_3_Tight-binding_model}
-
 \printnomenclature

### 2016-09-06 Gravity and Entanglement/gravity_n_entanglement.tex
Initiating new fields: general relativity and quantum gravity.

--- 2016-09-06 G.R/G.R.tex
@@
 
-\title{Notes for General Relativity}
+\title{Notes of Gravity and Entanglement}
 \date{\today}
@@
 \abstract{
-    (None)
+This is my notes to \cite{utube_video}, a video lecture given by
+professor Mark Van Raamsdonk. Also, it seems that this lecture is
+unrelated to another paper of the same title, written by the same
+author, on arXiv \cite{arxiv_paper}.
 }
 \tableofcontents
-\section{The Principle of Relativity}
-\label{sec:Principle_of_Relativity}
-Landau's book \cite{landau} describes the speed of light, as a speed of the
-maximum velocity of propagation of interaction. He perceives velocity as
-describing the propagation of interaction.
 
-In another aspect, I think that time does not exist. I perceive time as
-a agent of the environmental effect, communicating information and 
-coordinating movement between the system under consideration and its 
-envrionment. Therefore, a single existance is eternal by nature. Perhaps 
-before the universe originates, time is a meaningless concept. In my 
-view, the light is the only reliable tool to serve function of
-communication and coordination.
+\section{Lecture}
+\label{sec:Lecture}
 
-Fram either perspective, the speed of light is inherently constent.
-However, from my view, it is not clear why this speed should be a maximum.
+We have reviewed ads/CFT, entanglement, some interesting connections
+between entanglement structure of the CFT states, and the geometry
+structure of the space time due to this state. If this is true, a natural
+question is whether we can understand spacetime dynamics, i.e. gravitation,
+from some physics related to entanglement.
 
-\subsection{Invariance of Interval}
-\label{sec:Invariance of Interval}
+Consider some CFT theory, assumning to satisfy the xxxxx (1'50) conjectur 
+entanglement entropies are computed via:
+xxxxx conjecture
+2'17
 
-The Landau's book\cite{landau}, introduces a
+\begin{align}
+    S(A) = \frac{\text{Area}(\title{A})}{4G_N}
+\end{align}
 
+Some propertries that entanglement entropy must satisfy:
+\begin{enumerate}
+    \item sub-aditivity: $S(A and B)-S(A)-S(B) \geq 0$
+\end{enumerate}
+If there is some geometry due to the original states, will their entropy
+statisfy the above constraints. Hence: \textbf{what do those constraints imply about
+the spacetime geometry?}
+
+Start with small perturbations to (?). 
 \begin{thebibliography}{1}
-    \bibitem{landau} The Classical Theory of Fields
+    \bibitem{utube_video} Availalble on Youtube: \href{https://www.youtube.com/watch?v=ABJvMg5d9OY}{Mark Van Raamsdonk -Gravity and Entanglement}.
+    \bibitem{arxiv_paper} \href{http://arxiv.org/abs/1609.00026v1}{arXiv:1609.00026v1}
 \end{thebibliography}

### 2016-09-08 Finished/Physical Challenges of Quantum Computation/Physical_CoQC.tex
Daily update. Too many things to be covered.

--- 2016-09-06 G.R/G.R.tex
@@
 
-\title{Notes for General Relativity}
+\title{Notes of Physical Challenges of Quantum Computation}
 \date{\today}
@@
 \abstract{
-    (None)
+    This is a note to the dissertation \cite{dissertation} by professor MH Wong in SUSTC.
 }
 \tableofcontents
-\section{The Principle of Relativity}
-\label{sec:Principle_of_Relativity}
-Landau's book \cite{landau} describes the speed of light, as a speed of the
-maximum velocity of propagation of interaction. He perceives velocity as
-describing the propagation of interaction.
+\section{Chapter 1 Overview}
+\label{sec:Chapter_1_Overview}
 
-In another aspect, I think that time does not exist. I perceive time as
-a agent of the environmental effect, communicating information and 
-coordinating movement between the system under consideration and its 
-envrionment. Therefore, a single existance is eternal by nature. Perhaps 
-before the universe originates, time is a meaningless concept. In my 
-view, the light is the only reliable tool to serve function of
-communication and coordination.
+    \subsection{1.1 Introduction to quantum computing}
+    \label{sec:1.1_Introduction_to_quantum_computing}
+    Here he presents some differences between the classical and quantum
+    computers. Keywords: \textbf{quantum parallelism}, \textbf{reversible
+    computation process}, \textbf{simulation of quantum dynamics}.
 
-Fram either perspective, the speed of light is inherently constent.
-However, from my view, it is not clear why this speed should be a maximum.
+    \subsection{1.2~1.3 Physical implementations and challenges 
+    of quantum computing}
 
-\subsection{Invariance of Interval}
-\label{sec:Invariance of Interval}
+    These two parts do as the title suggests. The methods are summarized
+    in the following table:
 
-The Landau's book\cite{landau}, introduces a
+    \begin{table}[H]
+    \centering
+    \caption{Different Quantum Computing Approaches}
+    %\label{my-label}
 
+    \begin{tabular}
+        {|p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
+         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
+         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
+        }
+        %{lll}
+    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Error Prevention} \\ \hline
+        gate model 
+            & $U\ket{\text{Input}}=\ket{\text{Output}}$ 
+            & quantum error correction, 
+              analogous to its classical counterparts. \\ \hline
+        adiabatic model 
+            & Keep the quantum states of qbits in ground state. 
+            & Prevent thermalization. \\ \hline
+        one-way quantum computing/measurement-based quantum computing 
+            & Initialized in cluster state. Computation achived via 
+              a series of adaptive measurements. 
+            & High quality cluster state. Precision in measurement.
+        \\ \hline
+    \end{tabular}
+
+    \end{table}
+
+    It should be noted that the above classification is not exclusive,
+    there are certainly overlap between the three approaches. 
 \begin{thebibliography}{1}
-    \bibitem{landau} The Classical Theory of Fields
+    \bibitem{dissertation} From UIUC:
+    \url{https://www.ideals.illinois.edu/bitstream/handle/2142/14565/yung_manhong.pdf?sequence=1&isAllowed=y}
 \end{thebibliography}

### 2016-09-08 G.R/G.R.tex
Daily update. Too many things to be covered.

@@
 
-The Landau's book\cite{landau}, introduces a
+    To do dynamics, we necessarily need a measure of distance. 
+    Here introduces the distance in spacetime - interval. It is:
+    \begin{align}
+        \diff s^2 = \diff t^2 - \diff x^2 - \diff y^2 - \diff z^2
+    \end{align}
+    \textbf{Note} that from now on, I will try to use natural units
+    as often as possible.
 
+    Such a measure should be invariant in different Lorentz frames.
+    Landau proves it by postulating a priori that:
+    \begin{align}
+        \diff s^2 = a \diff s'^2
+    \end{align}
+    This is suggested by $\diff s=0$ is invariant (invariance of the
+    speed of light), and $\diff s$ and $\diff s'$ should be 
+    infinitesimals of the same order. From this postulation, it is
+    straightforward to argue that $a$ should be a constant and is
+    equal to $1$.
+
+    Using this property, one can classify interval between events
+    as being \textit{timelike, spacelike,} and \textit{lightlike},
+    by whether $ds>0$, $ds<0$ or $ds=0$. A mnemonic tip is that
+    for timelike intervals, the "time difference" is dominant,
+    and for spacelike intervals, the spatial difference is
+    dominant.
+
+    The following figure gives an indication of how the timelike,
+    spacelike, lightlike classification is related to causality:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/{ch1.spacetime_regions}.png}
+        \caption{Spacetime regions}
+    \end{figure}
+
+    Only those events in the absolute future and in the absolute past
+    regions can have a causal link with the people at $O$, due to the 
+    limit of speed of propagation. And the future and past combined
+    together as the timelike region.
+
+    Another difference of timelike and spacelike regions lies in the
+    prefix "absoluate". All events in timelike region cannot be
+    simultaneous with $O$ in any reference frame, since the interval
+    must have a nonzero time component. Similarly all events in
+    spacelike region must happen in different place with the $O$.
+    An additional requirement, which comes naturally from law of
+    causality, is that all events in the future must remain absolutely
+    in the future in any reference frame. Similarly we have an
+    absolute past.
+
+    Interestingly, the concept of being simultaneous with $O$, 
+    being before or after $O$ in time, are relative for events in
+    spacelike region. However, since there can be no causal link
+    between $O$ and those events, this relativity does not pose
+    a challenge to causality.
+
+    Lastly, the cone formed by all events with $ds=0$ is called the
+    \textit{light cone}. Events in it is very special that it deserve
+    to devote a separate section to discuss it, which will be done
+    later in this note.
+
+    \subsection{Proper Time}
+    \label{sec:Proper_Time}
+
+    By
+    \begin{align*}
+        dt'^2 = dt^2-dx^2 = dt^2-(v\diff t)^2
+    \end{align*}
+    we have 
+    \begin{align}
+        \label{eq:}
+        \Delta t' = \int_{t_1}^{t_2} \diff t \sqrt{1-v^2}
+    \end{align}
+
+    This shows the time dilation effect of a moving clock.
+    Also, by this we can always calculate the time experienced by a clock
+    by $t=\frac{1}{c}\int\diff s$ (SI unit).
+
+    The Landau's book \cite{landau} explains a classical paradox about
+    time dilation, which is omitted here.
+
+    Interestingly, we have the property that, for all lines between two
+    events, the longest one (i.e. the path that has the longest interval),
+    is the straight line, contrary to the classical case. To see this,
+    we note that any two events (assumed to be causally linked) can be
+    connected by a flying clock with uniform speed.
+
+    \subsection{Light's life}
+    \label{sec:Lights_life}
+    The life of a proton must be miserable.
+
+    Possible sources: \href{http://physics.stackexchange.com/questions/16018/does-a-photon-in-vacuum-have-a-rest-frame}{1},
+    \href{http://physics.stackexchange.com/questions/29082/would-time-freeze-if-you-could-travel-at-the-speed-of-light}{2}.
+    \href{https://www.quora.com/What-does-the-frame-of-reference-of-a-photon-look-like}{3}.
 \begin{thebibliography}{1}

### 2016-09-08 Green function/green-f.tex
Daily update. Too many things to be covered.

@@
   \end{align}
-\printnomenclature
   \subsection{3.2 Including spin degrees of freedom}
@@
       \label{eq:}
-        \Gamma_p \equiv i(\sum_p-\sum^\dagger_p)
+      \Gamma_p \equiv i(\textstyle\sum_p-\textstyle\sum^\dagger_p)
   \end{align}
@@
   don't quite understand.
+  \subsection{4.3 Lattice Green’s function method}
+  \label{sec:4.3_Lattice_Greens_function_method}
+  In this section, the author builds up a recursive method to calculate
+  the Green's function. The difficulty in calculating Green's function
+  is that the Hamiltonian matrix might be infinite, hence impossible
+  to invert numerically, or the inversion is numercially expensive.
+  Hence a recursive method is more preferable.
+
+  We define a notation for one particular submatrix of Green's funciton.
+  $G_{nn'}$ is such that:
+  \begin{align}
+      \braket{m,\sigma|G_{nn'}(E)|m',\sigma'} 
+          \equiv \braket{nm\sigma |G(E)|n'm'\sigma'}
+          = G_{nm\sigma,n'm'\sigma'}(E)
+  \end{align}
+  where $(m,n)$ labels columns in the tight-binding lattice, 
+  and $\sigma$ is the spin index.
+
+    \subsubsection{4.3.1 Semiinfinite leads: Self-energy description}
+    \label{sec:4.3.1_Semiinfinite_leads_Self-energy_description}
+    We have the following Hamiltonian from Landauer-Büttiker 
+    formalism,
+    \begin{align}
+        H= H_{cd} + \sum_i (H^i_l + V^i_{ld} + V^i_{dl})
+        \label{eq:ch4.1.3_H_general}
+    \end{align}
+
+    where $H_{cd}$ is the Hamiltonian for the central device, and 
+    $H_{li}$ the Hamiltonian for lead $i$. The coupling between 
+    lead and device is described by $V_{ld}^i$ (and its hermitian
+    conjugate $V_{dl}^i$ ).
+
+    Here is a improvement on that. 
+    It is shown that the central device, including the influence of
+    leads on it, is described by a \textit{finite-dimensional}
+    Hamiltonian:
+    \begin{align}
+        \mathcal{H}_{cd} = H_{cd} + \sum_i \textstyle\sum^i
+    \end{align}
+    where $\sum^i$ is called the retarted self-energy of lead $i$:
+    \begin{align}
+        \textstyle\sum^i = V^i_{dl}g^i_l V^i_{ld}
+    \end{align}
+    Here $g^i_l$ is the Green's function of the isolated 
+    semi-infinite lead: $g^i_l= [E+i\eta -H^i_l]^{-1}$.
+
+    At this point, the problem of computation is finally solve 
+    because we are using nearest neighbour model here. Hence the 
+    dimension of some matrix is significantly cut down.
+    \marginpar{
+        Actually, I don't see why the dimension of matrix is infinite
+        in the above \ref{eq:ch4.1.3_H_general}, while here the
+        matrix suddenly become fininte.
+    }
+    Also, author mentions that several methods are available to
+    calculate this Green's funciton: analytical solution when the
+    magnetic field is absent; numerical methods when there is a
+    magnetic field.
+
+    \subsubsection{4.3.2 Recursive technique: Standard method}
+    \label{sec:4.3.2_Recursive_technique_Standard_method}
+    Recursive method is based on the Dyson's equation:
+    \begin{align}
+      \label{eq:4.3.2.Dyson_Equaton}
+      \hat{G}=\hat{g}+ \hat{g} \hat{V}\hat{G}
+    \end{align}
+    (Note that this is an equation of operators!)
+
+    Here $g$ is the Green's function of two disconnected subsystems,
+    $G$ is the Green's funciton of the connected system,
+    comprising two previously disconnected subsystems; $V$ describes
+    the hopping between the subsystems. One may already see the
+    spirit of recursive method, by that $G$ appears on both side
+    of the equation.
+
+    It should be noted that, strictly speaking, in Dyson's equation
+    there should be two part: the self-energy part and everything
+    else (categorized as external potential). But I am not confident
+    about this.
+    % TODO improve Dyson's equation.
+
+    After this, the author illustrate one simple example of using
+    Dyson's equation to calculate $G$.
 \section{Anchor}
@@
 \end{thebibliography}
+\printnomenclature
 \section{License}

### 2016-09-08 Quantum Information/preskill.tex
Daily update. Too many things to be covered.

--- 2016-09-06 G.R/G.R.tex
@@
 
-\title{Notes for General Relativity}
+\title{Notes of Preskill's Quantum Information Theory}
 \date{\today}
@@
 \abstract{
-    (None)
+This is a note taken when I read the course notes of Preskill's
+course on quantum computation.
 }
 \tableofcontents
-\section{The Principle of Relativity}
-\label{sec:Principle_of_Relativity}
-Landau's book \cite{landau} describes the speed of light, as a speed of the
-maximum velocity of propagation of interaction. He perceives velocity as
-describing the propagation of interaction.
+\section{Chapter 2 Foundations I: States and Ensembles}
+\label{sec:Chapter_2_Foundations_I_States_and_Ensembles}
 
-In another aspect, I think that time does not exist. I perceive time as
-a agent of the environmental effect, communicating information and 
-coordinating movement between the system under consideration and its 
-envrionment. Therefore, a single existance is eternal by nature. Perhaps 
-before the universe originates, time is a meaningless concept. In my 
-view, the light is the only reliable tool to serve function of
-communication and coordination.
+    \subsection{2.2 The Qubit}
+    \label{sec:2.2_The_Qubit}
+    Here the concept of qubit is defined:
+    \begin{defi}[Qubit]
+    \nomenclature{Qubit}{\nomrefpage.}
+        A qubit is a quantum system described by a two-dimensional 
+        Hilbert space.
+    \end{defi}
+    However, since measurement collapse the superposition state of quantum
+    mechanics, there seems to be not difference between a qubit and a 
+    classical bit whose initial state is only known probabilistically.
+    More important distinction should be and will be pointed out in the
+    next few sections.
 
-Fram either perspective, the speed of light is inherently constent.
-However, from my view, it is not clear why this speed should be a maximum.
-
-\subsection{Invariance of Interval}
-\label{sec:Invariance of Interval}
-
-The Landau's book\cite{landau}, introduces a
+    \paragraph{Spin-$\frac{1}{2}$}
 
 \begin{thebibliography}{1}
-    \bibitem{landau} The Classical Theory of Fields
+    %\bibitem{book} 
 \end{thebibliography}

### 2016-09-08 Green function/1D QAHI Conductance/GreenF.m

@@ -1,0 +1,56 @@
+function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gamma,dis)
+% Obtain the GF with recursive method for twoo-lead with same material
+% tc is coupling between S and N
+
+w=1.*10^-3;                     % the resolution of energy
+
+I=eye(4);
+gL=g11(E,muL,ts,tsoL,w);   
+Tc1=V_dl(tc1);        
+SE1=Tc1*gL*Tc1';               % self energy for the L-L interfaces of lead-1
+%HnS=H_sample(1,muS,ts,tso,delta,Gamma,0);
+HnS=H_sample(1,muS,ts,tso,delta,Gamma,0);
+
+
+HeS1=HnS+SE1+dis(1)*diag([-1,-1,1,1]);               
+Tc2=V_dl(tc2);        
+SE2=Tc2*gL*Tc2';               % self energy for the L-L interfaces of lead-2         
+HeS2=HnS+SE2+dis(L)*diag([-1,-1,1,1]); 
+
+%% from left to right ( lead 1 to lead 2)
+Gnn=I/(((E+1i*w)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component
+G1n=Gnn;                        %|
+Gn1=Gnn;                        %|
+V1=V_sample(ts,tso);
+V2=V1';
+for i=2:L-1
+    %i
+    gnn=I/(((E+1i*w)*I-HnS+dis(i)*diag([-1,-1,1,1]))); % isolated GF for 2 ~ N-1 componets
+	Gnn=(I-gnn*V2*Gnn*V1)\gnn;
+	Gn1=Gnn*V2*Gn1;
+	G1n=G1n*V1*Gnn;    
+end
+
+gnn=I/(((E+1i*w)*I-HeS2));      % isolated GF for the last component at lead-2
+GNN=(I-gnn*V2*Gnn*V1)\gnn;
+GN1=GNN*V2*Gn1;
+G1N=G1n*V1*GNN; 
+
+%% from right to left
+Gnn=I/(((E+1i*w)*I-HeS2));      %| initial values of the first recursion, i.e. the isolated GF for the first component
+GNn=Gnn;                        %|
[…]

### 2016-09-08 Green function/1D QAHI Conductance/H_lead.m

@@ -1,0 +1,89 @@
+function y=H_lead(L,mu,ts,tso)
+y=zeros(4*L);
+Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
+condition=1.0; % =1 for spin independent hoping ts
+%tso=0.0; tso=0 or not, the results are quite different!
+m_y=00.0;
+m_x=0.0;
+
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    %y(i,i+L)=I*m_y;
+    %y(i+L,i)=-I*m_y;
+    %y(i+2*L,i+3*L)=-I*m_y;
+    %y(i+3*L,i+2*L)=I*m_y;
+    
+    %=====================================================================
+    
+    
+    
+
+
+for i=1:L-1
+    
+    y(i,i)=Gamma-mu;
+    y(i+L,i+L)=-Gamma-mu;
+    y(i+2*L,i+2*L)=Gamma-mu;
+    y(i+3*L,i+3*L)=-Gamma-mu;
+
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    y(i,i+L)=m_x+I*m_y;
+    y(i+L,i)=m_x-I*m_y;
+    y(i+2*L,i+3*L)=m_x-I*m_y;
+    y(i+3*L,i+2*L)=m_x+I*m_y;
+    
+    %=====================================================================
+    
+    
+    
+    if condition==1
+    y(i,i+1)=-ts;
+    y(i+L,i+L+1)=-ts;
+    y(i+2*L,i+2*L+1)=-ts;
+    y(i+3*L,i+3*L+1)=-ts;
+    
+    y(i+1,i)=-ts;
+    y(i+L+1,i+L)=-ts;
+    y(i+2*L+1,i+2*L)=-ts;
+    y(i+3*L+1,i+3*L)=-ts; 
+     
+    else
+    y(i,i+1)=-ts;
+    y(i+L,i+L+1)=ts;
[…]

### 2016-09-08 Green function/1D QAHI Conductance/H_sample.m

@@ -1,0 +1,131 @@
+%% without normal t
+%% Modified program to calculate AIII topological insulator as 
+%% spin transistor
+
+% i electron up
+% i electron down
+
+
+function y=H_sample(L,mu,ts,tso,delta,Gamma,dis)
+y=zeros(4*L);
+
+m_y=0.0;
+m_x=00.0;
+%Gamma=2.0;
+
+for i=1:L-1
+    mu=mu+dis*(rand-0.5);
+    y(i,i)=Gamma-mu;
+    y(i+L,i+L)=-Gamma-mu;
+    y(i+2*L,i+2*L)=Gamma-mu;
+    y(i+3*L,i+3*L)=-Gamma-mu;
+    
+    %y(i,i)=-mu;
+    %y(i+L,i+L)=-mu;
+    %y(i+2*L,i+2*L)=-mu;
+    %y(i+3*L,i+3*L)=-mu;
+    
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    y(i,i+L)=j*m_y;
+    y(i+L,i)=-j*m_y;
+    y(i+2*L,i+3*L)=-j*m_y;
+    y(i+3*L,i+2*L)=j*m_y;
+    
+    %=====================================================================
+    
+    
+    
+    y(i,i+1)=-ts;
+    y(i+L,i+L+1)=ts;
+    y(i+2*L,i+2*L+1)=-ts;
+    y(i+3*L,i+3*L+1)=ts;
+    
+    y(i+1,i)=-ts;
+    y(i+L+1,i+L)=ts;
+    y(i+2*L+1,i+2*L)=-ts;
+    y(i+3*L+1,i+3*L)=ts;
+    
+    y(i,i+L+1)=tso;
+    y(i+1,i+L)=-tso;
+    y(i+2*L,i+L+1+2*L)=tso;
+    y(i+1+2*L,i+L+2*L)=-tso;
+   
+    y(i+L+1,i)=tso;
+    y(i+L,i+1)=-tso;
+    y(i+L+1+2*L,i+2*L)=tso;
[…]

### 2016-09-08 Green function/1D QAHI Conductance/ScatteringM.m

@@ -1,0 +1,49 @@
+%function y=ScatteringM(1,Ly,W,E,Vy,u,t,a,tc,Ds,Dp,periodx)
+function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+    y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
+%SCateringMatix calculates the scatering matrix from lattice Green function
+%based on the formula: S=-1+i*sqrt(Gammaa)*GF*sqrt(Gammaa')
+
+[G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
+Gamma1=(1i*(SE1-SE1'));
+A1=my_sqrt(Gamma1);
+Gamma2=(1i*(SE2-SE2'));
+A2=my_sqrt(Gamma2);
+y11=-eye(4)+1i*A1*G11*A1;
+y12=1i*A1*G1N*A2;
+y21=1i*A2*GN1*A1;
+y22=-eye(4)+1i*A2*GNN*A2;
+%y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
+                        % e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
+y11ee=y11(1:2*1,1:2*1);
+y12ee=y12(1:2*1,1:2*1);
+y11eh=y11(1:2*1,2*1+1:4*1);
+y12eh=y12(1:2*1,2*1+1:4*1);
+y21ee=y21(1:2*1,1:2*1);
+y22ee=y22(1:2*1,1:2*1);
+y21eh=y21(1:2*1,2*1+1:4*1);
+y22eh=y22(1:2*1,2*1+1:4*1);
+y11he=y11(2*1+1:4*1,1:2*1);
+y12he=y12(2*1+1:4*1,1:2*1);
+y11hh=y11(2*1+1:4*1,2*1+1:4*1);
+y12hh=y12(2*1+1:4*1,2*1+1:4*1);
+y21he=y21(2*1+1:4*1,1:2*1);
[…]

### 2016-09-08 Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -1,0 +1,200 @@
+%% ============= T vs E =========================================
+clear
+cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
+
+L=20;          % number of sites
+ts=10;           % hoping 
+tso=1.0;          % spin orbital coupling
+tsoL=0;         % spin orbital coupling of the leads    
+tc1=0.2*ts;     % coupling between lead 1 and the sample
+tc2=0.2*ts;     % coupling between lead 2 and the sample
+muL=5.0;          % chemical potential of the leads
+muS=0;          % chemical potential of the sample
+disorder=0;     % local disorder
+delta=0.0;         % superconducting pairing
+
+M=200;   % gamma
+N=200;   % E
+
+if cont==1
+    gamma=3*(-ts:2.0*ts/M:ts);          % Zeeman energy Gammz_z as a variable
+    %E=-15:30/N:15;
+    E=(-muL:2*muL/N:1*muL);
+else
+    gamma=3.0;                % Zeeman energy Gammz_z as a constant
+    gap=min(abs(2*ts-abs(gamma)),2*abs(tso));
+  %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
+     E=(-muL:2*muL/N:1*muL);
+  %pause(0.5)
+end
+
+M=length(gamma);N=length(E)
+pause(0.5)
+
+TCee=zeros(N,M);
+TChe=zeros(N,M);
+TLee=zeros(N,M);
+TLhe=zeros(N,M);
+dis=disorder*(rand(1,L)-0.5);  
+for i=1:N
+    i
+    for j=1:M
+        [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+            y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM(E(i),L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,gamma(j),dis);
+        %yup=T_up(y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+        %    y11hh,y12hh,y21he,y22he,y21hh,y22hh);
+        %ydown=T_down(y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+        %    y11hh,y12hh,y21he,y22he,y21hh,y22hh);
[…]

### 2016-09-08 Green function/1D QAHI Conductance/V_dl.m

@@ -1,0 +1,5 @@
+function y=V_dl(tc)
+% Vdl: The coupling between the sample and the lead. Vld=Vdl'
+% T: the coupling amplitude 
+y=tc*diag([-1,-1,-1,-1]); 
+end

### 2016-09-08 Green function/1D QAHI Conductance/V_lead.m

@@ -1,0 +1,15 @@
+function y=V_lead(ts,tso)
+%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
+%tso: SOC
+y=zeros(4);
+for i=1:1
+    y(i,i)=-ts;
+    y(i+1,i+1)=-ts;
+    y(i+2*1,i+2*1)=ts;
+    y(i+3*1,i+3*1)=ts;
+    
+    y(i,i+1)=tso;
+    y(i+2*1,i+1+2*1)=-tso;
+    y(i+1,i)=-tso;
+    y(i+1+2*1,i+2*1)=tso; 
+end

### 2016-09-08 Green function/1D QAHI Conductance/V_sample.m

@@ -1,0 +1,15 @@
+function y=V_sample(ts,tso)
+%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
+%tso: SOC
+% electron and hole section are the same in topological insulator case.
+y=zeros(4);
+for i=1:1
+    y(i,i)=-ts;
+    y(i+1,i+1)=ts;
+    y(i+2*1,i+2*1)=-ts;
+    y(i+3*1,i+3*1)=ts;
+    y(i,i+1)=tso;
+    y(i+2*1,i+1+2*1)=tso;
+    y(i+1,i)=-tso;
+    y(i+1+2*1,i+2*1)=-tso; 
+end

### 2016-09-08 Green function/1D QAHI Conductance/g11.m

@@ -1,0 +1,22 @@
+function y=g11(E,mu,ts,tso,w)
+%g11 The submatrix of the Green function of the LEAD
+% Obtained by N times of recursion
+D=(E+1i*w)*eye(4)-H_lead(1,mu,ts,tso);
+A=V_lead(ts,tso);
+B=A';
+d=D;
+for i=1:1000 %maximum number of recursive times
+	d1=d-A/D*B;
+	D1=D-A/D*B-B/D*A;
+	A1=A/D*A;
+	B1=B/D*B;
+    if max(max(abs(d1-d)))<1e-99
+        %i
+        break
+    end
+	d=d1;
+	D=D1;
+	A=A1;
+	B=B1;
+end
+y=eye(4)/d1;

### 2016-09-08 Green function/1D QAHI Conductance/my_sqrt.m

@@ -1,0 +1,8 @@
+function y=my_sqrt(A)
+% this function calculates the squre root of a sparse complex matrix 
+% 
+%A=round(A*10^5)/10^5;
+[V,D]=eig(full(A));
+d=sqrt(D);
+y=V*d/V;
+end

### 2016-09-09 Complex Geometry - index/misc/complex geometry-misc.tex
New miscellaneous notes about complex geometry.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                  % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

\title{Miscellaneous notes for D. Huybrechts's Complex Geometry}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
Miscellaneous notes for D. Huybrechts's book \textit{Introduction
to Complex Geometry}, include some homeworks done.
}
\tableofcontents
\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{2n}$}{}}
\label{sec:The_structure_of_almost_complex_structures_on_R2n}
In exercise 1.2.1, it says that the set of all compatible almost complex
structures on a euclidean space of dimension $2n$, is two copies of $S^2$.

To show it, I tried first a straight calculation. Assuming the almost
complex structure $I= (a_{ij})$. Then we have:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.70]{pdfs/draft_20160908.pdf}
  \caption{Draft}
\end{figure}

Then I discover this too hard to work, because too many equations are
involed, and none of them could be eliminiated by other. Meanwhile, I
found a post in Math.SE about this:
\href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.

To understand that post, I read this:
\href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}. However, the proof inside is not perfect:
\begin{quote}
    The claim is: If $V$ is an $n$-dimensional complex vector space with underlying $2n$-dimensional real vector space $W$, then the canonical group monomorphism $\mathrm{GL}(V) \to \mathrm{GL}(W)$ lands inside $\mathrm{GL}^+(W)=\{f \in \mathrm{GL}(W) : \det(f)>0\}$.  The purpose of this abstract reformulation is that we may use operations on vector spaces in order to simplify the problem: If $V'$ is another finite-dimensional complex vector space with underlying real vector space $W'$, the diagram

    \begin{align}
      \begin{array}{ccc} 
        \mathrm{GL}(V) \times \mathrm{GL}(V') & \rightarrow & \mathrm{GL}(W) \times \mathrm{GL}(W') \\
        \downarrow & & \downarrow \\ 
        \mathrm{GL}(V \oplus V') & \rightarrow & \mathrm{GL}(W \oplus W') 
      \end{array}
    \end{align}

    commutes, and the image of $\mathrm{GL}^+(W) \times \mathrm{GL}^+(W')$  is contained in $\mathrm{GL}^+(W \oplus W')$. Therefore, if some element in $\mathrm{GL}(V \oplus V')$ lies in the image of $\mathrm{GL}(V) \times \mathrm{GL}(V')$, it suffices to consider the components. Combining this with the fact that $\mathrm{GL}(V)$ is generated by \href{https://en.wikipedia.org/wiki/Elementary_matrix}{elementary matrices} (after chosing a basis of $V$), we may reduce the whole problem to the following three types of matrices:

  - the $1 \times 1$-matrices $(\lambda)$,

  - the $2 \times 2$-matrices $\begin{pmatrix} 1 & 0 \\ \lambda & 1 \end{pmatrix}$,

  - and the $2 \times 2$-matrix $\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}$.

  Write $\lambda=a+ib$ with $(a,b) \in \mathbb{R}^2 \setminus \{(0,0)\}$. Then, the complex $1 \times 1$-matrix $(\lambda)$ becomes the real $2 \times 2$-matrix $\begin{pmatrix} a & -b \\ b & a \end{pmatrix}$, which has determinant $a^2+b^2 > 0$. The complex $2 \times 2$-matrix $\begin{pmatrix} 1 & 0 \\ \lambda & 1 \end{pmatrix}$ becomes the real $4 \times 4$-matrix
  $\begin{pmatrix}
  1 & 0 & 0 & 0 \\
  0 & 1 & 0 & 0 \\
  a & -b & 1 & 0 \\
  b & a & 0 & 1 \end{pmatrix}$, which has determinant $1$. Finally, the complex $2 \times 2$-matrix  $\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}$ becomes the real $4 \times 4$-matrix $\begin{pmatrix} 0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1\\ 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \end{pmatrix}$, which has determinant $1$.

\end{quote}

This proof is not complete because, to build the proof from 
$\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument, that
any element in $\mathrm{GL}(V\oplus V)$ is in the image of
$\mathrm{GL}(V)\times \mathrm{GL}(V')$, which is not the case.

On the other hand, it seems that this property can be proved directly
by calculation. % TODO Start here and learn that paper.
\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry. Springer.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-09 Quantum Information/preskill.tex
Learns about symmetry in Q.M.

@@
 
-    \paragraph{Spin-$\frac{1}{2}$}
+    \subsubsection{Spin-\texorpdfstring{$\frac{1}{2}$}{}} 
+    In this part, the author in fact discusses the symmetry and its role
+    in quantum mechanis, albeit roughly.
+
+    \paragraph{Symmetry}
+    \begin{defi}[Symmetry]
+    \nomenclature{Symmetry}{\nomrefpage.}
+    A symmetry is a \textit{transformation} that acts on a state of a
+    system, yet leaves all observable properties of the system unchanged.
+    \end{defi}
+    Hence a symmetry must leaves any $|\braket{\psi|\phi}|^2$ 
+    (probability) unchanged. This leads Wigner to derive a famous theorem
+    stating that:
+    \begin{thm}
+        Any symmetry transformation, by adopting suitable phase conventions,
+        can always chosen to be either unitary or antiunitary.
+    \end{thm}
+
+    He mentions that symmetry transformations formes a group. (Omitted here)
+
+    Here the author focuses on unitary ones, since "The antiunitary
+    alternative, while important for discrete symmetries, can be 
+    excluded for continuous symmetries".
+
+    Also, he demands that symmetry "respect the dynamical evolution of 
+    the system", thus deducing:
+    \begin{align}
+        [\hat{U}(R),\hat{H}] = 0 \\
+        [\hat{Q},\hat{H}] = 0,\text{ }\hat{Q} = \hat{Q}^\dagger \\
+        \hat{U} = \hat{I} - i\varepsilon \hat{Q} \\
+    \end{align}
+    Here $\hat{U}$ is the symmetry transformation corresponding to the
+    symmetry $R$. $Q$ is an observable (since $\hat{Q}$ is hermitian)
+    related to this symmetry by above formula, and $\varepsilon$ as
+    expected is an infinitesimal number. We also finds that this
+    observable is conserved by above formula.
+
+    $\hat{Q}$ is said to be the generator
+    \nomenclature{$\hat{Q}$, generator}{\nomrefpage}
+    of the symmetry by the following formula:
+    \begin{align}
+        \label{eq:}
+        \hat{U}(R) = 
+          \lim_{N\to \infty}(\hat{I}+i\frac{\theta}{N}\hat{Q})^N
+          = e^{i\theta \hat{Q}}
+    \end{align}
 
 \begin{thebibliography}{1}
-    %\bibitem{book} 
+    \bibitem{book} Preskill's notes are available through his Caltech
+    course website, Phy219.
 \end{thebibliography}

### 2016-09-10 G.R/G.R.tex
Daily update.

@@
 
+    \subsection{Lorentz Transformation}
+    \label{sec:Lorentz_Transformation}
+
+    Next we have to consider the coordinate transformations in
+    four-dimensional spacetime. The formula can be obtained solely by
+    the restricting transformation to be an isometry.
+
+    These transformations are categorize into two groups: parallel
+    displacement and rotation. Only formula for rotation is worth
+    consideration. Rotation in spacetime, simiilar to their
+    counterparts in $\mathbb{R}^3$, can be decomposed according to
+    six axes of rotation, each representing rotation in plane
+    $xy,xz,yz,xt,yt,zt$. The first of this is only ordinary spatial
+    rotation. The rest are called \textit{Lorentz Transformations}.
+    And there is really only one important formula, one for 
+    rotation around $xt$ plane:
+    \begin{align}
+        x = x'\cosh\psi + t \sinh\psi\text{, }
+        t = x'\sinh\psi + t \cosh\psi
+    \end{align}
+    where $\psi$ is the "angle of rotation". However, this "angle"
+    do not have much physical interpretation. Instead, the following
+    formula is more useful, which relates the coordinate in frame
+    $K$, to anther fram $K'$ moving in uniform velocity $v$ w.r.t
+    $K$:
+    \begin{align}
+        x = \frac{x'+vt'}{\sqrt{1-v^2}}\nonumber\\
+        y = y'\text{, }z = z' \nonumber\\
+        t = \frac{t'+v x'}{\sqrt{1-v^2}}
+    \end{align}
+
+    Aided with this formula, Landau discusses the \textit{Lorentz
+    contraction} phenomenon in special relativity and defines
+    the proper length\nomenclature{proper length}{\nomrefpage}
+    $l_0$, defined as the length in its rest frame. It is related
+    to its length measured in another frame $K'$ by:
+    \begin{align}
+        l' = l_0 \sqrt{1-v^2}
+    \end{align}
+
+    Finally he mentions that, since Lorentz transformations are
+    in fact rotations, they naturally do not commute, unless the
+    rotation is fixed in only one plane.
+
     \subsection{Light's life}

### 2016-09-13 Complex Geometry - index/misc/complex geometry-misc.tex
Learns about symmetry in Q.M.
I AM NOT ROBOT.  daily update.

@@
 
+% For better indices
+\usepackage{tensor}
+% ANCHOR
 \title{Miscellaneous notes for D. Huybrechts's Complex Geometry}
@@
 involed, and none of them could be eliminiated by other. Meanwhile, I
-found a post in Math.SE about this:
-\href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
+found a post in Math.SE about this \cite{math.se_1}.
 
-To understand that post, I read this:
-\href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}.
-However, the proof inside is not perfect:
+    \subsection{Understand \texorpdfstring{ 
+                    $\frac{GL(2n,\mathbb{R})}
+                        {GL(n,\mathbb{C})}$
+                            }{}
+                }
+    \label{sec:Understand_GL(2n,R)/GL(n,C)}
+
+    \marginpar{Here I digressed to another problem. I will come back later.}
+    To understand that post, I read this\cite{math.se_2}. However, the answer
+    in the second post is not perfect:
+
     \begin{quote}
@@
         a & -b & 1 & 0 \\
-  b & a & 0 & 1 \end{pmatrix}$, which has determinant $1$.
+        b & a & 0 & 1 \end{pmatrix}$, 
+        which has determinant $1$.
 Finally, the complex $2 \times 2$-matrix  $\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}$ becomes the real $4 \times 4$-matrix $\begin{pmatrix} 0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1\\ 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \end{pmatrix}$, which has determinant $1$.
@@
     On the other hand, it seems that this property can be proved directly
-by calculation. % TODO Start here and learn that paper.
+    by calculation. The following will be a notes of a paper 
+    \cite{determinants_of_block_m}, which one comment mentions 
+    in the Math.SE post \cite{math.se_2}.
+
+        \subsubsection{Determinants of Block Matrices}
+        \label{sec:Determinants of Block Matrices}
+
+        This paper tries to prove the theorem:
+
+        \begin{thm}
+            %\label{thm:determinant_of_block_m}
+            Let $R$ be a commutative subring of $\tensor[^n]{F}{^n}$,
+            where $F$ is a field (or a commutative ring), and let 
+            $M\in \tensor[^m]{R}{^m}$. Then 
+            \begin{align}
+                \text{det}_F \mathbf{M} = 
+                    \text{det}_F( \text{det}_R \mathbf{M})
+            \end{align}
+        \end{thm}
+
+        In particular, we have:
+        \begin{align}
+            \text{det}_F \left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{B} \\
+                \mathbf{C} & \mathbf{D} \\
+                \end{array}
+                \right)
+                = \text{det}_F (AD-BC)
+        \end{align}
+        Note that, that the ring being is commutative excludes some
+        ambiguity. For example, when the ring $4$ is not commutative,
+        then the quantity:
+
+        \begin{align}
+            \text{det}_F \left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{B} \\
+                \mathbf{C} & \mathbf{D} \\
+                \end{array}
+                \right)
+        \end{align}
+        is not well-defined. It can be $AD-BC$, or $DA-CB$, etc.
+
+        Before the proof of the main theorem, it establishes several
+        facts:
+        \begin{align}
+            \label{eq:sec1.1.1_fact_5}
+            \text{det}_F  \left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{0} \\
+                \mathbf{C} & \mathbf{D} \\
+                \end{array}
+                \right)
+                =& \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
+            \\
+            \label{eq:sec1.1.1_fact_6}
+            \text{det}_F  \left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{B} \\
+                \mathbf{0} & \mathbf{D} \\
+                \end{array}
+                \right)
+                =& \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
+            \\
+            \label{eq:sec1.1.1_fact_8}
+            \text{det}_F  \left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{B} \\
+                \mathbf{C} & \mathbf{0} \\
+                \end{array}
+                \right)
+                =& \text{det}_F \mathbf{-C} \text{det}_F \mathbf{B}
+            \\
+            \label{eq:sec1.1.1_fact_88}
+            \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
+            =& \text{det}_F \mathbf{I}_n \text{det}_F (\mathbf{AD})
+        \end{align}
+
+        He first builds up a seemingly simplified, but is actually
+        different version of the main theorem:
+        \begin{thm}
+            \label{thm:sec_1.1.1_thm3}
+            Let $\mathbf{A,B,C,D}\in \tensor[^n]{F}{^n}$. 
+            Let $\mathbf{M}=\left(
+                \begin{array}{cc}
+                \mathbf{A} & \mathbf{B} \\
+                \mathbf{C} & \mathbf{D} \\
+                \end{array}
+                \right)$.
+
+            If
+            $\mathbf{CD=DC}$, then,
+            \begin{align}
+                \text{det}_F \mathbf{M}= 
+                \text{det}_F (\mathbf{AD-BC})
+            \end{align}
+        \end{thm}
+        and similar results:
+        \begin{align}
+            \label{eq:sec1.1.1_thm3_similar}
+            \text{if } \mathbf{AC=CA} &\text{then, }
+                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{AD-CB})
+            \\
+            \text{if } \mathbf{BD=DB} &\text{then, }
+                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{DA-BC})
+            \\
+            \text{if } \mathbf{AB=BA} &\text{then, }
+                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{DA-CB})
+        \end{align}
+        These equalities can be proved easily by the following:
+        \begin{align*}
+            \left(
+                \begin{array}{cc}
+                 D & 0 \\
+                 -C & i \\
+                \end{array}
+            \right) \left(
+                \begin{array}{cc}
+                 A & B \\
+                 C & D \\
+                \end{array}
+            \right) &= \left(
+                \begin{array}{cc}
+                 \text{AD}-\text{BC} & B \\
+                 \text{CD}-\text{DC} & D \\
+                \end{array}
+            \right)=\left(
+                \begin{array}{cc}
+                 \text{AD}-\text{BC} & B \\
+                 0 & D \\
+                \end{array}
+            \right) \text{ when $C,D$ commutes}
+            \\
+            \left(
+                \begin{array}{cc}
+                 D & -B \\
+                 0 & i \\
+                \end{array}
+            \right) \left(
+                \begin{array}{cc}
+                 A & B \\
+                 C & D \\
+                \end{array}
+            \right) &= \left(
+                \begin{array}{cc}
+                 \text{DA}-\text{BC} & \text{DB}-\text{BD} \\
+                 C & D \\
+                \end{array}
+            \right)=\left(
+                \begin{array}{cc}
+                 \text{DA}-\text{BC} & 0 \\
+                 C & D \\
+                \end{array}
+            \right) \text{ when $D,B$ commutes.}
+        \end{align*}
+
+        The author also gives an illuminative explanation for why
+        $$ \left( \text{det}_F \mathbf{M}- \text{det}_F (\mathbf{AD-BC}) 
+            \right) \text{det}_F \mathbf{D} =0 $$
+        necessarily implies:
+        $$ \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{AD-BC}) $$
+
+% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures
+
+\section{Anchor}
+\label{sec:Anchor}
+
 \begin{thebibliography}{1}
-  \bibitem{book} D Huybrechts's Introduction to Complex Geometry. Springer.
+  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
+  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
+  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
+  \bibitem{determinants_of_block_m} John R. Silvester, 
+      Determinants of Block Matrices. Available in WebArchive link:
+      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
 \end{thebibliography}
 \printnomenclature
+
 \section{License}

### 2016-09-13 G.R/G.R.tex
I AM NOT ROBOT.  daily update.

@@
 
+    \subsection{Transformation of velocities}
+    \label{sec:Transformation_of_velocities}
+
+    Note that for convenience, I will adopt the popular Lorentz factor
+    $\gamma$, defined as:
+    \begin{align}
+        \gamma \equiv \frac{1}{\sqrt{1-V^2}}
+    \end{align}
+
+    To get the similar transofmrations for velocities is quite easy,
+    and the result is:
+    \begin{align}
+        v_x &= \frac{v'_x + V}{1+ v'_x V}\\
+        v_y &= \frac{v'_y}{\gamma \left(1+v'x V\right)}\\
+        v_z &= \frac{v'_z}{\gamma \left(1+v'x V\right)}\\
+    \end{align}
+
+    In the special case when the motion is parallel to the $x$-axis,
+    we have (let $v_x$ just be $v$):
+    \begin{align}
+        v = \frac{v'+V}{1+v' V}
+    \end{align}
+
+    Landau mentions that when $V$ is significantly smaller than the
+    velocity of light, we have the following approximate formula:
+    \begin{align}
+        \vec{v} = \vec{v'} + \vec{V} - (\vec{V}\cdot\vec{v'}) \vec{v'}
+    \end{align}
+
     \subsection{Light's life}

### 2016-09-16 Complex Geometry - index/misc/complex geometry-misc.tex
Solve one minor problem in landau's book. Solved one major step in one problem in complex geometry.

@@
 
+        However, I am dubious about this conclusion, since I think it
+        needs in addition that the polynomial ring $F[x]$ has not
+        nonzero zero divisor.
+
+        Having demonstrated the above simple case, the author continues to
+        prove the main theorem. He proves by induction. He first uses:
+        \begin{align}
+            \left(
+                \begin{array}{cc}
+                 A & b \\
+                 c & d \\
+                \end{array}
+            \right)  \left(
+                \begin{array}{cc}
+                 \text{dI} & 0 \\
+                 -c & 1 \\
+                \end{array}
+            \right)=\left(
+                \begin{array}{cc}
+                 A_0 & b \\
+                 0 & d \\
+                \end{array}
+            \right)
+        \end{align}
+        where $A,A_0\in \tensor[^{m-1}]{R}{^{m-1}}, 
+        b\in \tensor[^{m-1}]{R}{}, c\in \tensor{R}{^{m-1}}, d\in R$. 
+        Therefore, (let $M=
+            \left(
+            \begin{array}{cc}
+             A & b \\
+             c & d \\
+            \end{array}
+            \right)$)
+        with similar reason mentioned before, he shows if:
+        \begin{align}
+            \text{det}_F \mathbf{A_0} =
+              \text{det}_F \mathbf{( \text{det}_R \mathbf{A_0})}
+        \end{align}
+        (which is true by induction) then:
+        \begin{align}
+            \text{det}_F \mathbf{M} =
+              \text{det}_F \mathbf{( \text{det}_R \mathbf{M})}
+        \end{align}
+        Proof completes.
+
+        He also mentions a corollary:
+        \begin{coro}
+            Let $\mathbf{P}\in \tensor[^n]{F}{^n}$ and $\mathbf{Q}\in
+            \tensor[^m]{F}{^m}$, then
+            \begin{align}
+                \text{det}_F (\mathbf{P\otimes Q}) =
+                (\text{det}_F \mathbf{P}) ^m (\text{det}_F \mathbf{Q})^n
+            \end{align}
+        \end{coro}
+
+        The proof is quite straightforward and is omitted.
+        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
+            {GL(n,\mathbb{C})}$}{} (continued)}
+
+        Coming back to my point. This is a note of my question on
+        Math.SE\cite{math.se_3}
+
+        First, I try to do it when $n=1$. I inject a complex number 
+        $a+bi$ by
+        identify it with $a\mathbb{I}+b\mathbb{J}$, where $\mathbb{I}$ 
+        is the identify matrix and $\mathbb{J}$ is
+        $ \left(
+        \begin{array}{cc}
+         0 & -1 \\
+         1 & 0 \\
+        \end{array}
+        \right) $. I take one set of basis of 
+        $\mathrm{GL}(2,\mathbb{R})$ as:
+        $$
+        \left(
+        \begin{array}{cc}
+         1 & 0 \\
+         0 & 1 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & -1 \\
+         1 & 0 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & 0 \\
+         1 & 0 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & 0 \\
+         0 & 1 \\
+        \end{array}
+        \right)
+        $$
+
+        (I think this is a basis because the following matrix is 
+        non-singular:
+        $$
+        \left(
+        \begin{array}{cccc}
+         1 & 0 & 0 & 0 \\
+         0 & -1 & 0 & 0 \\
+         0 & 1 & 1 & 0 \\
+         1 & 0 & 0 & 1 \\
+        \end{array}
+        \right)
+        $$)
+        Then the $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}
+        (n,\mathbb{C})}$ becomes equivalent classes represented by 
+        $$
+        \left(
+        \begin{array}{cc}
+         0 & 0 \\
+         c & d \\
+        \end{array}
+        \right)
+        $$
+
+        However, I don't know how to link this with an almost complex 
+        structure.
+
+        I have a feeling that I might have been in the wrong direction. 
+        It was pointed out that $\mathrm{GL}(2n,\mathbb{R})$ is not
+        even a vector space. So what I did is in fact nonsense.
+
+        Below is one correct answer I got:
+
+        An almost-complex structure is a matrix $J$ such that $J^2 = -I$
+        is the negative identity. As you said, one example of such a 
+        matrix $J$ is $$\begin{pmatrix} 0 & I \\ -I & 0 \end{pmatrix}.$$
+
+        Interpreting $GL(n,\mathbb{C})$ as a subgroup of 
+        $GL(2n;\mathbb{R})$ depends on having fixed such an 
+        almost-complex structure. Once we have a matrix $J$, we can call 
+        a matrix $A \in GL(2n;\mathbb{R})$ complex-linear if it commutes 
+        with $J$, i.e. $AJA^{-1} = J.$
+
+        (The idea is that $\mathbb{C}$-linear maps $T$ are just real 
+        linear maps with the additional property that $T(iv) = i T(v)$
+        for all vectors $v$)
+
+        Given any matrix $A \in GL(2n;\mathbb{R})$, we get another 
+        almost-complex structure $AJA^{-1}$. This is the same 
+        almost-complex structure $J$ if and only if 
+        $A \in GL(n;\mathbb{C}).$ On the other hand, all almost-complex 
+        structures are similar (although it may take some work to be 
+        convincing that they are similar over $\mathbb{R}$ and not 
+        only $\mathbb{C}$) since they are diagonalizable with the same 
+        eigenvalues $\pm i$. That gives you a bijection 
+        $$
+            GL(2n;\mathbb{R}) / GL(n;\mathbb{C}) \longrightarrow 
+            \{\mathrm{almost}-\mathrm{complex}\; 
+            \mathrm{structures}\}
+        $$ 
+        under which a class $A \cdot GL(n;\mathbb{C})$ corresponds 
+        to the almost-complex structure $AJA^{-1}.$
+
+        I questioned him:
+        \begin{enumerate}
+            \item Why $AJA^{-1}$ is the same almost-complex structure 
+                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
+            \item Why all almost-complex structures are similar over 
+                $\mathbb{R}$.
+        \end{enumerate}
+        He responsed that:
+        \begin{enumerate}
+            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
+                as matrices $A$ with $AJA^{-1}=J$.
+            \item comes from the fact that any real matrices that are 
+                similar over $\mathbb{C}$ are already similar over 
+                $\mathbb{R}$. This isn't trivial but it has been asked 
+                and answered many times on this site: here is one 
+                reference \url{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
+        \end{enumerate}
+
+        Inside the reference, the following theorem is proved:
+
+        \begin{thm}
+            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
+            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
+            $B$ are similar over $E$, they are similar over $F$.
+        \end{thm}
 % TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures
@@
       \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
+  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
 \end{thebibliography}

### 2016-09-16 G.R/G.R.tex
Solve one minor problem in landau's book. Solved one major step in one problem in complex geometry.

@@
 \makenomenclature
+
+\usepackage{tensor}
 
@@
 
+    \subsection{Four-vectors}
+    \label{sec:Four-vectors}
+
+    This section is basically an recapitulation of important definitions
+    and results in tensor analysis in spacetime. Since I am quite
+    familiar with this topic, I will only cover something I felt new.
+
+    \paragraph{Complete antisymmetric tensor $e^{iklm}$}
+    It is defined such that any interchange of indices gives a minus
+    sign. We requires that:
+    \begin{align}
+        e^{0123}= +1
+    \end{align}
+    Therefore:
+    \begin{align*}
+        e_{0123}= -1\;, e^{iklm}e_{iklm}= -24
+    \end{align*}
+    Also, $e^{iklm}$ is only a pseudotensor:
+    \begin{proof}
+        Under transformation (let $\Lambda$ be the transformation matrix)
+        we have:
+        $\tilde{e}^{0123}=
+          \Lambda^{0}_{i}\Lambda^{1}_{k}\Lambda^{2}_{l}\Lambda^{3}_{m}
+          e^{iklm}$
+        Notice that $e^{iklm}=\mathrm{sgn}(iklm)$ by our definition.
+        Therefore, the right hand side above is exactly the definition
+        of determinant. Hence $\tilde{e}^{0123}=\mathrm{det}(\Lambda)$.
+
+        Also, one can easily show that $\tilde{e}^{nqpr}$ is also
+        totally antisymmetric, since $e^{iklm}$ is totally antisymmetric.
+
+        With these we have:
+        $$
+            \tilde{e}^{nqpr}=\mathrm{det}(\Lambda)e^{nqpr}
+        $$
+        But $e^{iklm}$ is defined without reference to basis, therefore
+        we have actually:
+        \begin{align}
+            \tilde{e}^{nqpr} \equiv e^{npqr}
+        \end{align}
+        Note that since $\Lambda$ must be orthonormal, we have 
+        $\mathrm{det}(\Lambda)=\pm 1$. Therefore when
+        $\mathrm{det}(\Lambda)=1$, the two requirement coincide and
+        $e^{iklm}$ behaves like a tensor, and when 
+        $\mathrm{det}(\Lambda)=-1$, it behaves like a pseudotensor.
+    \end{proof}
+
     \subsection{Light's life}

### 2016-09-18 Complex Geometry - index/misc/complex geometry-misc.tex
Solved one problem in "complex geometry". Start to learn the code for green functions.

@@
 \tableofcontents
-\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{2n}$}{}}
+\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{4}$}{}
+  (exercise 1.2.1)}
 \label{sec:The_structure_of_almost_complex_structures_on_R2n}
@@
 involed, and none of them could be eliminiated by other. Meanwhile, I
-found a post in Math.SE about this \cite{math.se_1}.
+found a post in Math.SE about this \cite{math.se_1}. Here are several
+important concepts for understanding that post.
 
@@
 
-    \marginpar{Here I digressed to another problem. I will come back later.}
-    To understand that post, I read this\cite{math.se_2}. However, the answer
-    in the second post is not perfect:
+        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
+            {GL(n,\mathbb{C})}$}{}}
+
+        This is a note of my question on Math.SE\cite{math.se_3}, which
+        explains that we can identify the set of almost complex structures
+        with $\frac{GL(2n,\mathbb{R})}{GL(n,\mathbb{C})}$.
+
+        First, I try to do it when $n=1$. I inject a complex number 
+        $a+bi$ by
+        identify it with $a\mathbb{I}+b\mathbb{J}$, where $\mathbb{I}$ 
+        is the identify matrix and $\mathbb{J}$ is
+        $ \left(
+        \begin{array}{cc}
+         0 & -1 \\
+         1 & 0 \\
+        \end{array}
+        \right) $. I take one set of basis of 
+        $\mathrm{GL}(2,\mathbb{R})$ as:
+        $$
+        \left(
+        \begin{array}{cc}
+         1 & 0 \\
+         0 & 1 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & -1 \\
+         1 & 0 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & 0 \\
+         1 & 0 \\
+        \end{array}
+        \right),\left(
+        \begin{array}{cc}
+         0 & 0 \\
+         0 & 1 \\
+        \end{array}
+        \right)
+        $$
+
+        (I think this is a basis because the following matrix is 
+        non-singular:
+        $$
+        \left(
+        \begin{array}{cccc}
+         1 & 0 & 0 & 0 \\
+         0 & -1 & 0 & 0 \\
+         0 & 1 & 1 & 0 \\
+         1 & 0 & 0 & 1 \\
+        \end{array}
+        \right)
+        $$)
+        Then the $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}
+        (n,\mathbb{C})}$ becomes equivalent classes represented by 
+        $$
+        \left(
+        \begin{array}{cc}
+         0 & 0 \\
+         c & d \\
+        \end{array}
+        \right)
+        $$
+
+        However, I don't know how to link this with an almost complex 
+        structure.
+
+        I have a feeling that I might have been in the wrong direction. 
+        It was pointed out that $\mathrm{GL}(2n,\mathbb{R})$ is not
+        even a vector space. So what I did is in fact nonsense.
+
+        Below is one correct answer I got:
+
+        An almost-complex structure is a matrix $J$ such that $J^2 = -I$
+        is the negative identity. As you said, one example of such a 
+        matrix $J$ is $$\begin{pmatrix} 0 & I \\ -I & 0 \end{pmatrix}.$$
+
+        Interpreting $GL(n,\mathbb{C})$ as a subgroup of 
+        $GL(2n;\mathbb{R})$ depends on having fixed such an 
+        almost-complex structure. Once we have a matrix $J$, we can call 
+        a matrix $A \in GL(2n;\mathbb{R})$ complex-linear if it commutes 
+        with $J$, i.e. $AJA^{-1} = J.$
+
+        (The idea is that $\mathbb{C}$-linear maps $T$ are just real 
+        linear maps with the additional property that $T(iv) = i T(v)$
+        for all vectors $v$)
+
+        Given any matrix $A \in GL(2n;\mathbb{R})$, we get another 
+        almost-complex structure $AJA^{-1}$. This is the same 
+        almost-complex structure $J$ if and only if 
+        $A \in GL(n;\mathbb{C}).$ On the other hand, all almost-complex 
+        structures are similar (although it may take some work to be 
+        convincing that they are similar over $\mathbb{R}$ and not 
+        only $\mathbb{C}$) since they are diagonalizable with the same 
+        eigenvalues $\pm i$. That gives you a bijection 
+        $$
+            GL(2n;\mathbb{R}) / GL(n;\mathbb{C}) \longrightarrow 
+            \{\mathrm{almost}-\mathrm{complex}\; 
+            \mathrm{structures}\}
+        $$ 
+        under which a class $A \cdot GL(n;\mathbb{C})$ corresponds 
+        to the almost-complex structure $AJA^{-1}.$
+
+        I questioned him:
+        \begin{enumerate}
+            \item Why $AJA^{-1}$ is the same almost-complex structure 
+                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
+            \item Why all almost-complex structures are similar over 
+                $\mathbb{R}$.
+        \end{enumerate}
+        He responsed that:
+        \begin{enumerate}
+            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
+                as matrices $A$ with $AJA^{-1}=J$.
+            \item comes from the fact that any real matrices that are 
+                similar over $\mathbb{C}$ are already similar over 
+                $\mathbb{R}$. This isn't trivial but it has been asked 
+                and answered many times on this site: here is one 
+                reference \cite{math.se_4}.
+        \end{enumerate}
+
+        Inside that reference, the following theorem is proved:
+
+        \begin{thm}
+            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
+            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
+            $B$ are similar over $E$, they are similar over $F$.
+        \end{thm}
+
+        However, I still have doubts about the following question:
+        For $A\in \mathrm{GL}(2n,\mathbb{R})$, if $AJA^{-1}=J$, can we
+        conlude that $A$ is inside $\mathrm{GL}(n,\mathbb{C})$?
+        % TODO resolve this double.
+        \subsubsection{Why \texorpdfstring{
+                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
+                }{}
+            }
+
+        To understand that post \cite{math.se_1}, I also read this
+        \cite{math.se_2}. In it, it asks how to prove that 
+        \begin{align}
+            \label{eq:sec.1.1.2_why_glnc_injectInto_positive_comp}
+            GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})
+        \end{align}
+        for any $n$. The questioner gives the intuition for this fact:
+        \begin{quote}
+            how about since as Lie groups, $GL(n,\mathbb{C}) 
+            \subset GL(2n, \mathbb{R})$ and $GL(n,\mathbb{C})$ is connected 
+            but $GL(2n, \mathbb{R})$ has two connected components, one for 
+            positive determinant and one for negative determinant? And the 
+            identity has positive determinant, so it must lie in that 
+            component.
+        \end{quote}
+
+        Someone answered that question:
 
@@
 
-    This proof is not complete because, to build the proof from 
+        However, this proof is not complete because, to build the proof from 
         $\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument, that
@@
         in the Math.SE post \cite{math.se_2}.
+
+% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures
 
@@
         The proof is quite straightforward and is omitted.
-        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
-            {GL(n,\mathbb{C})}$}{} (continued)}
 
-        Coming back to my point. This is a note of my question on
-        Math.SE\cite{math.se_3}
-
-        First, I try to do it when $n=1$. I inject a complex number 
-        $a+bi$ by
-        identify it with $a\mathbb{I}+b\mathbb{J}$, where $\mathbb{I}$ 
-        is the identify matrix and $\mathbb{J}$ is
-        $ \left(
-        \begin{array}{cc}
-         0 & -1 \\
-         1 & 0 \\
-        \end{array}
-        \right) $. I take one set of basis of 
-        $\mathrm{GL}(2,\mathbb{R})$ as:
-        $$
-        \left(
-        \begin{array}{cc}
-         1 & 0 \\
-         0 & 1 \\
-        \end{array}
-        \right),\left(
-        \begin{array}{cc}
-         0 & -1 \\
-         1 & 0 \\
-        \end{array}
-        \right),\left(
-        \begin{array}{cc}
-         0 & 0 \\
-         1 & 0 \\
-        \end{array}
-        \right),\left(
-        \begin{array}{cc}
-         0 & 0 \\
-         0 & 1 \\
-        \end{array}
-        \right)
-        $$
-
-        (I think this is a basis because the following matrix is 
-        non-singular:
-        $$
-        \left(
-        \begin{array}{cccc}
-         1 & 0 & 0 & 0 \\
-         0 & -1 & 0 & 0 \\
-         0 & 1 & 1 & 0 \\
-         1 & 0 & 0 & 1 \\
-        \end{array}
-        \right)
-        $$)
-        Then the $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}
-        (n,\mathbb{C})}$ becomes equivalent classes represented by 
-        $$
-        \left(
-        \begin{array}{cc}
-         0 & 0 \\
-         c & d \\
-        \end{array}
-        \right)
-        $$
-
-        However, I don't know how to link this with an almost complex 
-        structure.
-
-        I have a feeling that I might have been in the wrong direction. 
-        It was pointed out that $\mathrm{GL}(2n,\mathbb{R})$ is not
-        even a vector space. So what I did is in fact nonsense.
-
-        Below is one correct answer I got:
-
-        An almost-complex structure is a matrix $J$ such that $J^2 = -I$
-        is the negative identity. As you said, one example of such a 
-        matrix $J$ is $$\begin{pmatrix} 0 & I \\ -I & 0 \end{pmatrix}.$$
-
-        Interpreting $GL(n,\mathbb{C})$ as a subgroup of 
-        $GL(2n;\mathbb{R})$ depends on having fixed such an 
-        almost-complex structure. Once we have a matrix $J$, we can call 
-        a matrix $A \in GL(2n;\mathbb{R})$ complex-linear if it commutes 
-        with $J$, i.e. $AJA^{-1} = J.$
-
-        (The idea is that $\mathbb{C}$-linear maps $T$ are just real 
-        linear maps with the additional property that $T(iv) = i T(v)$
-        for all vectors $v$)
-
-        Given any matrix $A \in GL(2n;\mathbb{R})$, we get another 
-        almost-complex structure $AJA^{-1}$. This is the same 
-        almost-complex structure $J$ if and only if 
-        $A \in GL(n;\mathbb{C}).$ On the other hand, all almost-complex 
-        structures are similar (although it may take some work to be 
-        convincing that they are similar over $\mathbb{R}$ and not 
-        only $\mathbb{C}$) since they are diagonalizable with the same 
-        eigenvalues $\pm i$. That gives you a bijection 
-        $$
-            GL(2n;\mathbb{R}) / GL(n;\mathbb{C}) \longrightarrow 
-            \{\mathrm{almost}-\mathrm{complex}\; 
-            \mathrm{structures}\}
-        $$ 
-        under which a class $A \cdot GL(n;\mathbb{C})$ corresponds 
-        to the almost-complex structure $AJA^{-1}.$
-
-        I questioned him:
-        \begin{enumerate}
-            \item Why $AJA^{-1}$ is the same almost-complex structure 
-                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
-            \item Why all almost-complex structures are similar over 
-                $\mathbb{R}$.
-        \end{enumerate}
-        He responsed that:
-        \begin{enumerate}
-            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
-                as matrices $A$ with $AJA^{-1}=J$.
-            \item comes from the fact that any real matrices that are 
-                similar over $\mathbb{C}$ are already similar over 
-                $\mathbb{R}$. This isn't trivial but it has been asked 
-                and answered many times on this site: here is one 
-                reference \url{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
-        \end{enumerate}
-
-        Inside the reference, the following theorem is proved:
-
-        \begin{thm}
-            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
-            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
-            $B$ are similar over $E$, they are similar over $F$.
-        \end{thm}
-% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures
-
+        \subsubsection{Why \texorpdfstring{
+                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
+                }{}(continued)
+            }
+        With above theorem, the proof of equation 
+        \ref{eq:sec.1.1.2_why_glnc_injectInto_positive_comp} 
+        is straight forward. Since for 
+        $(a_{ij})= A\in \mathrm{GL}(n,\mathbb{C})$, it injects into
+        $\mathrm{GL}(2n,\mathbb{R})$ as matrices of the form:
+        \begin{align*}
+            \left( \begin{array}{ccc}
+             \text{...} & \text{...} & \text{...} \\
+             \text{...} & H a_{\text{ij}} & \text{...} \\
+             \text{...} & \text{...} & \text{...} \\
+            \end{array} \right)
+        \end{align*}
+        where:
+        \begin{align*}
+            H(z\equiv x+iy)=\left( \begin{array}{cc}
+                    x & -y \\
+                    y & x \\
+            \end{array}\right)
+        \end{align*}
+        Since $H(a_{ij})$ commutes with each other (proved by calculation),
+        we can use the theorem in previous part to show that:
+        \begin{align*}
+            \mathrm{det_\mathbb{R}}(A) =
+            \mathrm{det_\mathbb{R}}  (\mathrm{det_\mathbb{C}}(A))
+            = |\mathrm{det_\mathbb{C}}(A) |^2 \geq 0
+        \end{align*}
+        Notice that I have been sloopy in language, but the meaning should
+        be clear.
 \section{Anchor}
@@
   \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
+  \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
+  {Similar matrices and field extensions}
 \end{thebibliography}

### 2016-09-18 Green function/1D QAHI Conductance/GreenF.m

@@ -2,52 +2,49 @@ function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso
 % Obtain the GF with recursive method for twoo-lead with same material
 % tc is coupling between S and N
 
-w=1.*10^-3;                     % the resolution of energy
+w_energy_resol=1.*10^-3;                     % the resolution of energy
 
 I=eye(4);
-gL=g11(E,muL,ts,tsoL,w);   
-Tc1=V_dl(tc1);        
+gL=g11(E,muL,ts,tsoL,w_energy_resol);
+Tc1=V_dl(tc1);
 SE1=Tc1*gL*Tc1';               % self energy for the L-L interfaces of lead-1
-%HnS=H_sample(1,muS,ts,tso,delta,Gamma,0);
 HnS=H_sample(1,muS,ts,tso,delta,Gamma,0);
-
-
-HeS1=HnS+SE1+dis(1)*diag([-1,-1,1,1]);               
-Tc2=V_dl(tc2);        
-SE2=Tc2*gL*Tc2';               % self energy for the L-L interfaces of lead-2         
-HeS2=HnS+SE2+dis(L)*diag([-1,-1,1,1]); 
+HeS1=HnS+SE1+dis(1)*diag([-1,-1,1,1]);
+Tc2=V_dl(tc2);
+SE2=Tc2*gL*Tc2';               % self energy for the L-L interfaces of lead-2
+HeS2=HnS+SE2+dis(L)*diag([-1,-1,1,1]);
 
 %% from left to right ( lead 1 to lead 2)
-Gnn=I/(((E+1i*w)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component
+Gnn=I/(((E+1i*w_energy_resol)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component
 G1n=Gnn;                        %|
 Gn1=Gnn;                        %|
 V1=V_sample(ts,tso);
 V2=V1';
 for i=2:L-1
     %i
-    gnn=I/(((E+1i*w)*I-HnS+dis(i)*diag([-1,-1,1,1]))); % isolated GF for 2 ~ N-1 componets
[…]

### 2016-09-18 Green function/1D QAHI Conductance/H_lead(deceased).m

@@ -6,27 +6,22 @@ condition=1.0; % =1 for spin independent hoping ts
 m_y=00.0;
 m_x=0.0;
 
-    %=====================================================================
-    % Additional term which break C2,T2 symmetry but preserve C1 and T1
-    % symmetry. To test the influence of C1 and T1 symmetry.
-    %y(i,i+L)=I*m_y;
-    %y(i+L,i)=-I*m_y;
-    %y(i+2*L,i+3*L)=-I*m_y;
-    %y(i+3*L,i+2*L)=I*m_y;
-    
-    %=====================================================================
-    
-    
-    
+%=====================================================================
+% Additional term which break C2,T2 symmetry but preserve C1 and T1
+% symmetry. To test the influence of C1 and T1 symmetry.
+%y(i,i+L)=I*m_y;
+%y(i+L,i)=-I*m_y;
+%y(i+2*L,i+3*L)=-I*m_y;
+%y(i+3*L,i+2*L)=I*m_y;
 
+%=====================================================================
 
 for i=1:L-1
-    
     y(i,i)=Gamma-mu;
     y(i+L,i+L)=-Gamma-mu;
     y(i+2*L,i+2*L)=Gamma-mu;
     y(i+3*L,i+3*L)=-Gamma-mu;
-
+    
     %=====================================================================
     % Additional term which break C2,T2 symmetry but preserve C1 and T1
     % symmetry. To test the influence of C1 and T1 symmetry.
@@ -40,33 +35,33 @@ for i=1:L-1
     
     
     if condition==1
-    y(i,i+1)=-ts;
-    y(i+L,i+L+1)=-ts;
-    y(i+2*L,i+2*L+1)=-ts;
-    y(i+3*L,i+3*L+1)=-ts;
-    
-    y(i+1,i)=-ts;
-    y(i+L+1,i+L)=-ts;
-    y(i+2*L+1,i+2*L)=-ts;
-    y(i+3*L+1,i+3*L)=-ts; 
-     
+        y(i,i+1)=-ts;
[…]

### 2016-09-18 Green function/1D QAHI Conductance/H_sample.m

@@ -1,5 +1,5 @@
 %% without normal t
-%% Modified program to calculate AIII topological insulator as 
+%% Modified program to calculate AIII topological insulator as
 %% spin transistor
 
 % i electron up
@@ -51,7 +51,7 @@ for i=1:L-1
     y(i+1,i+L)=-tso;
     y(i+2*L,i+L+1+2*L)=tso;
     y(i+1+2*L,i+L+2*L)=-tso;
-   
+    
     y(i+L+1,i)=tso;
     y(i+L,i+1)=-tso;
     y(i+L+1+2*L,i+2*L)=tso;
@@ -60,7 +60,7 @@ for i=1:L-1
     y(i,i+3*L)=delta;
     y(i+L,i+2*L)=-delta;
     y(i+3*L,i)=delta;
-    y(i+2*L,i+L)=-delta;  
+    y(i+2*L,i+L)=-delta;
 end
 mu=mu+dis*(rand-0.5);
 y(L,L)=Gamma-mu;
@@ -71,7 +71,7 @@ y(4*L,4*L)=Gamma+mu;
 y(L,L+3*L)=delta;
 y(L+L,L+2*L)=-delta;
 y(L+3*L,L)=delta;
-y(L+2*L,L+L)=-delta;  
+y(L+2*L,L+L)=-delta;
 y=sparse(y);
 end
 %}
@@ -111,7 +111,7 @@ for i=1:L-1
     y(i,i+3*L)=delta;
     y(i+L,i+2*L)=-delta;
     y(i+3*L,i)=delta;
-    y(i+2*L,i+L)=-delta;  
+    y(i+2*L,i+L)=-delta;
 end
 mu=mu+dis*(rand-0.5);
 y(L,L)=Gamma-mu;
@@ -122,7 +122,7 @@ y(4*L,4*L)=Gamma+mu;
 y(L,L+3*L)=delta;
 y(L+L,L+2*L)=-delta;
 y(L+3*L,L)=delta;
-y(L+2*L,L+L)=-delta;  
+y(L+2*L,L+L)=-delta;
 y=sparse(y);
 end
 %}

### 2016-09-18 Green function/1D QAHI Conductance/ScatteringM.m

@@ -1,6 +1,6 @@
 %function y=ScatteringM(1,Ly,W,E,Vy,u,t,a,tc,Ds,Dp,periodx)
 function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
-    y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
+  y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
 %SCateringMatix calculates the scatering matrix from lattice Green function
 %based on the formula: S=-1+i*sqrt(Gammaa)*GF*sqrt(Gammaa')
 
@@ -14,7 +14,7 @@ y12=1i*A1*G1N*A2;
 y21=1i*A2*GN1*A1;
 y22=-eye(4)+1i*A2*GNN*A2;
 %y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
-                        % e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
+% e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
 y11ee=y11(1:2*1,1:2*1);
 y12ee=y12(1:2*1,1:2*1);
 y11eh=y11(1:2*1,2*1+1:4*1);
@@ -39,11 +39,11 @@ y11ee=Rd*y11ee*R;
 y12ee=Rd*y12ee*R;
 
 %{
-% change the basis to [e1u,e1d,e2u,e2d,h1u,h1d,h2u,h2d] to obtain the whole S-matrix,  
+% change the basis to [e1u,e1d,e2u,e2d,h1u,h1d,h2u,h2d] to obtain the whole S-matrix,
 
 y=[y11ee,y12ee,y11eh,y12eh;
     y21ee,y22ee,y21eh,y22eh;
     y11he,y12he,y11hh,y12hh;
-    y21he,y22he,y21hh,y22hh]; 
+    y21he,y22he,y21hh,y22hh];
 %}
 end

### 2016-09-18 Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -1,11 +1,11 @@
-%% ============= T vs E =========================================
+% ============= T vs E =========================================
 clear
 cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
 
 L=20;          % number of sites
-ts=10;           % hoping 
+ts=10;           % hoping
 tso=1.0;          % spin orbital coupling
-tsoL=0;         % spin orbital coupling of the leads    
+tsoL=0;         % spin orbital coupling of the leads
 tc1=0.2*ts;     % coupling between lead 1 and the sample
 tc2=0.2*ts;     % coupling between lead 2 and the sample
 muL=5.0;          % chemical potential of the leads
@@ -13,188 +13,182 @@ muS=0;          % chemical potential of the sample
 disorder=0;     % local disorder
 delta=0.0;         % superconducting pairing
 
-M=200;   % gamma
-N=200;   % E
+% M_gamma=200;   % gamma
+% N_E=200;   % E
+M_gamma=10;   % gamma
+N_E=10;   % E
 
 if cont==1
-    gamma=3*(-ts:2.0*ts/M:ts);          % Zeeman energy Gammz_z as a variable
+    gamma=3*(-ts:2.0*ts/M_gamma:ts);          % Zeeman energy Gammz_z as a variable
     %E=-15:30/N:15;
-    E=(-muL:2*muL/N:1*muL);
+    E=(-muL:2*muL/N_E:1*muL);
 else
     gamma=3.0;                % Zeeman energy Gammz_z as a constant
     gap=min(abs(2*ts-abs(gamma)),2*abs(tso));
-  %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
-     E=(-muL:2*muL/N:1*muL);
-  %pause(0.5)
+    %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
+    E=(-muL:2*muL/N_E:1*muL);
+    %pause(0.5)
 end
 
-M=length(gamma);N=length(E)
+M_gamma=length(gamma);N_E=length(E)
 pause(0.5)
 
-TCee=zeros(N,M);
-TChe=zeros(N,M);
-TLee=zeros(N,M);
[…]

### 2016-09-18 Green function/1D QAHI Conductance/V_dl.m

@@ -1,5 +1,5 @@
 function y=V_dl(tc)
 % Vdl: The coupling between the sample and the lead. Vld=Vdl'
-% T: the coupling amplitude 
-y=tc*diag([-1,-1,-1,-1]); 
+% T: the coupling amplitude
+y=tc*diag([-1,-1,-1,-1]);
 end

### 2016-09-18 Green function/1D QAHI Conductance/V_lead(deceased).m

@@ -11,5 +11,5 @@ for i=1:1
     y(i,i+1)=tso;
     y(i+2*1,i+1+2*1)=-tso;
     y(i+1,i)=-tso;
-    y(i+1+2*1,i+2*1)=tso; 
+    y(i+1+2*1,i+2*1)=tso;
 end

### 2016-09-18 Green function/1D QAHI Conductance/V_sample.m

@@ -11,5 +11,5 @@ for i=1:1
     y(i,i+1)=tso;
     y(i+2*1,i+1+2*1)=tso;
     y(i+1,i)=-tso;
-    y(i+1+2*1,i+2*1)=-tso; 
+    y(i+1+2*1,i+2*1)=-tso;
 end

### 2016-09-18 Green function/1D QAHI Conductance/g11.m

@@ -1,22 +1,112 @@
-function y=g11(E,mu,ts,tso,w)
-%g11 The submatrix of the Green function of the LEAD
-% Obtained by N times of recursion
-D=(E+1i*w)*eye(4)-H_lead(1,mu,ts,tso);
-A=V_lead(ts,tso);
-B=A';
-d=D;
-for i=1:1000 %maximum number of recursive times
-	d1=d-A/D*B;
-	D1=D-A/D*B-B/D*A;
-	A1=A/D*A;
-	B1=B/D*B;
-    if max(max(abs(d1-d)))<1e-99
-        %i
-        break
+function y=g11(E,mu,ts,tso,w_energy_resol)
+    %g11 The submatrix of the Green function of the LEAD
+    % Obtained by N times of recursion
+    D=(E+1i*w_energy_resol)*eye(4)-H_lead(1,mu,ts,tso);
+    A=V_lead(ts,tso);
+    B=A';
+    d=D;
+    for i=1:1000 %maximum number of recursive times
+        d1=d-A/D*B;
+        D1=D-A/D*B-B/D*A;
+        A1=A/D*A;
+        B1=B/D*B;
+        if max(max(abs(d1-d)))<1e-99
+            %i
+            break
+        end
+        d=d1;
+        D=D1;
+        A=A1;
+        B=B1;
     end
-	d=d1;
-	D=D1;
-	A=A1;
-	B=B1;
+    y=eye(4)/d1;
+
+function y=H_lead(L,mu,ts,tso)
+    y=zeros(4*L);
+    Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
+    condition=1.0; % =1 for spin independent hoping ts
+    %tso=0.0; tso=0 or not, the results are quite different!
+    m_y=00.0;
+    m_x=0.0;
+
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    %y(i,i+L)=I*m_y;
+    %y(i+L,i)=-I*m_y;
+    %y(i+2*L,i+3*L)=-I*m_y;
+    %y(i+3*L,i+2*L)=I*m_y;
+    %=====================================================================
+    for i=1:L-1
+        y(i,i)=Gamma-mu;
[…]

### 2016-09-18 Green function/1D QAHI Conductance/my_sqrt.m

@@ -1,6 +1,6 @@
 function y=my_sqrt(A)
-% this function calculates the squre root of a sparse complex matrix 
-% 
+% this function calculates the squre root of a sparse complex matrix
+%
 %A=round(A*10^5)/10^5;
 [V,D]=eig(full(A));
 d=sqrt(D);

### 2016-09-19 G.R/G.R.tex
New course note: Group theory in Physics. Modifying G.R. and green function program.

@@
 
+    By similar arguments, we see that $e^{iklm}e^{npqr}$ forms a true
+    tensor, so does $e^{iklm}e_{prst}$, etc.
+
+    Also, Landau says that the only tensor that is invariant in all 
+    corrdinate system is the unit tensor $\sigma^i_k$. So all the 
+    above tensor should be able to be expressed in terms of this.
+    The author then provides the following formulae (they are too
+    complicated to type that I just paste the screenshot here):
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{ch1.four_vectors_formulae_4_ee}.png}
+        \caption{Formulae for ee}
+        \label{fig:Formulae-for-ee}
+    \end{figure}
+
+    And:
+    \begin{align}
+        e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= -A e_{iklm} \\
+        e^{iklm}e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= 24 \;\mathrm{det}(A)
+    \end{align}
+    Next the autho introduces the dual tensors. Since this is important
+    and the case of Lorentzian spacetime is somewhat different from
+    the usual case, this topic deserves a separate treatment in the
+    following section.
+
+    \subsection{Dual Tensors}
+    \label{sec:Dual_Tensors}
+    % TODO See this post:http://physics.stackexchange.com/questions/37577/what-does-the-dual-of-a-tensor-mean-e-g-dual-stress-tensor-in-relativistic-ed
     \subsection{Light's life}

### 2016-09-19 Group Theory in Physics/group theory in physics.tex
New course note: Group theory in Physics. Modifying G.R. and green function program.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

% For highlighting
\usepackage{xcolor,soul}
\newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}

\title{Group Theory in Physics (Course Note)}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
This is our course note for the course about group theoy, with its
application in physics.
}
\tableofcontents
\begin{enumerate}
    \item Combine group theory with you research.
    \item Mid-term and final.
    \item No homework, cause it is already graduate level.
    \item Professor Fei Ye. (Phone: 88018229, 228 in Research building 2), 
        T.A. Zhe Zhang. (110 Research building 2).
\end{enumerate}

\section{20160919}
\label{sec:20160919}

He first introduces several common examples of symmetries in our life and
physics. Omitted, with one exception:

He mentions that there is one more symmetry in the Hydrogen 
Hamiltonian: the Laplace-Runge-Lenz symmetry. (So its symmetry 
group is not just $SO(3)$, but two copies of $SO(3)$ that forms a $SO(4)$.
And using the representation of $SO(4)$, the complete spectrum of
Hydrogen Hamiltonian is solved. Hence this $SO(4)$ is the largest
symmetry of Hydrogen Hamiltonian.

    \subsection{Digression about Lenz vector}
    \label{sec:Digression_about_Lenz_vector}
    Since the class is too boring, I checked about the Lenz vector via
    Google and found this Math.SE question \cite{math.se_1_lenz_vector}

    The first answer to that post is:

    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

    \begin{quote}
        1) \textbf{Problem}. The \href{http://en.wikipedia.org/wiki/Kepler_problem}{Kepler Problem} has Hamiltonian

        $$ H~:=~ \frac{p^2}{2m}- \frac{k}{q},  $$

        where $m$ is the 2-body reduced mass. The [Laplace–Runge–Lenz vector](http://en.wikipedia.org/wiki/Laplace%E2%80%93Runge%E2%80%93Lenz_vector) is (up to an irrelevant normalization)

        $$ A^j ~:=~a^j  + km\frac{q^j}{q}, \qquad a^j~:=~({\bf L} \times {\bf p})^j~=~{\bf q}\cdot{\bf p}~p^j- p^2~q^j,\qquad {\bf L}~:=~ {\bf q} \times {\bf p}.$$

        2) \textbf{Action}. The Hamiltonian Lagrangian is

        $$  L_H~:=~ \dot{\bf q}\cdot{\bf p} - H, $$

        and the action is

        $$ S[{\bf q},{\bf p}]~=~ \int {\rm d}t~L_H .$$

        The non-zero fundamental canonical Poisson brackets are

        $$ \{ q^i , p^j\}~=~ \delta^{ij}. $$

        3) \textbf{Inverse Noether's Theorem}. Quite generally in the Hamiltonian formulation, given a constant of motion $Q$, then the infinitesimal variation

        $$\delta~=~ \varepsilon \{Q,\cdot\}$$

        is a global off-shell symmetry of the action $S$ (modulo boundary terms). Here $\varepsilon$ is an infinitesimal global parameter, and $X_Q=\{Q,\cdot\}$ is a Hamiltonian vector field with Hamiltonian generator $Q$. The full Noether current is (minus) $Q$, see e.g. my answer to [this question](http://physics.stackexchange.com/q/8626/2451). \hl{(The words \textbf{on-shell}. and \textbf{off-shell}. refer to whether the equations of motion are satisfied or not.)}

        4) \textbf{Variation}. Let us check that the three Laplace–Runge–Lenz components $A^j$ are Hamiltonian generators of three continuous global off-shell symmetries of the action $S$. In detail, the infinitesimal variations $\delta= \varepsilon_j \{A^j,\cdot\}$ read

        $$ \delta  q^i ~=~  \varepsilon_j  \{A^j,q^i\}   , \qquad 
         \{A^j,q^i\} ~ =~ 2 p^i q^j - q^i p^j - {\bf q}\cdot{\bf p}~\delta^{ij}, $$
        $$ \delta  p^i ~=~  \varepsilon_j  \{A^j,p^i\}   , \qquad  
        \{A^j,p^i\}~ =~ p^i p^j - p^2~\delta^{ij} +km\left(\frac{\delta^{ij}}{q}- \frac{q^i q^j}{q^3}\right), $$
        $$ \delta  t ~=~0,$$

        where $\varepsilon_j$ are three infinitesimal parameters.

        5) Notice for later that

        $$ {\bf q}\cdot\delta {\bf q}~=~\varepsilon_j({\bf q}\cdot{\bf p}~q^j - q^2~p^j),  $$

        $$ {\bf p}\cdot\delta {\bf p}
        ~=~\varepsilon_j km(\frac{p^j}{q}-\frac{{\bf q}\cdot{\bf p}~q^j}{q^3})~=~- \frac{km}{q^3}{\bf q}\cdot\delta {\bf q},  $$

        $$ {\bf q}\cdot\delta {\bf p}~=~\varepsilon_j({\bf q}\cdot{\bf p}~p^j - p^2~q^j )~=~\varepsilon_j a^j,  $$

        $$ {\bf p}\cdot\delta {\bf q}~=~2\varepsilon_j( p^2~q^j - {\bf q}\cdot{\bf p}~p^j)~=~-2\varepsilon_j a^j~.  $$

        6) The Hamiltonian is invariant

        $$ \delta  H ~=~ \frac{1}{m}{\bf p}\cdot\delta {\bf p} + \frac{k}{q^3}{\bf q}\cdot\delta {\bf q}~=~0, $$

        showing that the Laplace–Runge–Lenz vector $A^j$ is classically a constant of motion

        $$\frac{dA^j}{dt} ~\approx~ \{ A^j, H\}+\frac{\partial A^j}{\partial t} ~=~  0.$$

        (We will use the $\approx$ sign to stress that an equation is an on-shell equation.)

        7) The variation of the Hamiltonian Lagrangian $L_H$ is a total time derivative

        $$ \delta L_H~=~ \delta  (\dot{\bf q}\cdot{\bf p})~=~ \dot{\bf q}\cdot\delta {\bf p} - \dot{\bf p}\cdot\delta {\bf q} + \frac{d({\bf p}\cdot\delta {\bf q})}{dt} $$
        $$  =~ \varepsilon_j\left( \dot{\bf q}\cdot{\bf p}~p^j - p^2~\dot{q}^j +  km\left( \frac{\dot{q}^j}{q} -  \frac{{\bf q} \cdot \dot{\bf q}~q^j}{q^3}\right)\right)    $$
        $$- \varepsilon_j\left(2 \dot{\bf p}\cdot{\bf p}~q^j - \dot{\bf p}\cdot{\bf q}~p^j- {\bf p}\cdot{\bf q}~\dot{p}^j  \right) - 2\varepsilon_j\frac{da^j}{dt}$$
        $$ =~\varepsilon_j\frac{df^j}{dt}, \qquad f^j ~:=~ A^j-2a^j, $$

        and hence the action $S$ is invariant off-shell up to boundary terms.

        8) \textbf{Noether current}. The bare \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether current} $j^k$ is

        $$j^k~:=~ \frac{\partial L_H}{\partial \dot{q}^i}  \{A^k,q^i\}+\frac{\partial L_H}{\partial \dot{p}^i}  \{A^k,p^i\}
        ~=~ p^i\{A^k,q^i\}~=~ -2a^k. $$

        The full Noether current $J^k$ (which takes the total time-derivative into account) becomes (minus) the Laplace–Runge–Lenz vector

        $$ J^k~:=~j^k-f^k~=~ -2a^k-(A^k-2a^k)~=~ -A^k.$$

        $J^k$ is conserved on-shell

        $$\frac{dJ^k}{dt} ~\approx~  0,$$

        due to \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether's first Theorem}. Here $k$ is an index that labels the three symmetries.
    \end{quote}

    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

    However, I don't really understand the content inside. I asked professor
    Ye whether we can find some physics about this conserved quantity, and
    he answered with no.

    The next answer is also interesting:

    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

    \begin{quote}
        While Kepler second law is simply a statement of the conservation of angular momentum (and as such it holds for all systems described by central forces), \hl{the first and the third laws are special and are linked with the unique form of the newtonian potential $-k/r$.} In particular, \hl{Bertrand theorem assures that *only* the newtonian potential and the harmonic potential $kr^2$ give rise to closed orbits (no precession).} It is natural to think that this must be due to some kind of symmetry of the problem. In fact, the particular symmetry of the newtonian potential is described exactly by the conservation of the RL vector (\hl{it can be shown that the RL vector is conserved iff the potential is central and newtonian}). This, in turn, is due to a more general symmetry: \hl{if conservation of angular momentum is linked to the group of special orthogonal transformations in 3-dimensional space $SO(3)$, conservation of the RL vector must be linked to a 6-dimensional group of symmetries}, since in this case there are apparently six conserved quantities (3 components of $L$ and 3 components of $\mathcal A$). In the case of bound orbits, this group is $SO(4)$, the group of rotations in 4-dimensional space.

        Just to fix the notation, the RL vector is:

        \begin{equation} \mathcal{A}=\textbf{p}\times\textbf{L}-\frac{km}{r}\textbf{x} \end{equation}

        Calculate its total derivative:

        \begin{equation}\frac{d\mathcal{A}}{dt}=-\nabla U\times(\textbf{x}\times\textbf{p})+\textbf{p}\times\frac{d\textbf{L}}{dt}-\frac{k\textbf{p}}{r}+\frac{km(\textbf{p}\cdot \textbf{x})}{r^3}\textbf{x} \end{equation}

        Make use of Levi-Civita symbol to develop the cross terms:

        \begin{equation}\epsilon_{sjk}\epsilon_{sil}=\delta_{ji}\delta_{kl}-\delta_{jl}\delta_{ki}   \end{equation}

        Finally:

        \begin{equation}
        \frac{d\mathcal{A}}{dt}=\left(\textbf{x}\cdot\nabla U-\frac{k}{r}\right)\textbf{p}+\left[(\textbf{p}\cdot\textbf{x})\frac{k}{r^3}-2\textbf{p}\cdot\nabla U\right]\textbf{x}+(\textbf{p}\cdot\textbf{x})\nabla U
        \end{equation}

        Now, if the potential $U=U(r)$ is central:

        \begin{equation}
        (\nabla U)_j=\frac{\partial U}{\partial x_j}=\frac{dU}{dr}\frac{\partial r}{\partial x_j}=\frac{dU}{dr}\frac{x_j}{r}
        \end{equation}

        so

        \begin{equation} \nabla U=\frac{dU}{dr}\frac{\textbf{x}}{r}\end{equation}

        Substituting back:

        \begin{equation}
            \hlMath{\frac{d\mathcal A}{dt}=\frac{1}{r}\left(\frac{dU}{dr}-\frac{k}{r^2}\right)[r^2\textbf{p}-(\textbf{x}\cdot\textbf{p})\textbf{x}]}
        \end{equation}

        Now, you see that if $U$ has \textit{exactly} the newtonian form then the first parenthesis is zero and so the RL vector is conserved.

        Maybe there's some slicker way to see it (Poisson brackets?), but this works anyway.
    \end{quote}
    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

    % TODO Study in detail about this example.

    \subsection{Coming back to the course}

After mentioning the Poinc\'{a}re group, he produces to review some
concepts about linear algebra:
\begin{enumerate}
    \item The axioms of linear space, using quantum mechanics
        as basic example (Omitted).
    \item Some common concepts of linear space: linear-independence,
        subspace, direct sum, linear operators, its matrix representation. (Omitted)
    \item Introducing the complete antisymmetric tensor 
        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
        \begin{align}
            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
            \\
            &= \sum_{p_1,\cdots,p_n} 
            \epsilon_{p_1,\cdots,p_n} 
                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
                \\
            \epsilon_{ab}\epsilon_{rs} &=
                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
                \\
            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
        \end{align}
    \item Some special matrices.
    \item Fact: If $R\Gamma = \Gamma R$, and 
        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
        On the other hand, if $R_{\mu\nu}\neq 0$, then
        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
        This is obviously from:
        \begin{align*}
            R^{i}_{j}\Gamma^{j}_{k}=\Gamma^{i}_{j} R^{j}_k
            \Longrightarrow
            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
        \end{align*}
        where the first is automatically summed, and the second is not.

    \item A linear functional is closed w.r.t. a vector space. (Omitted)
    \item ... then this linear functional can be expressed as a
        matrix w.r.t to a basis of this vector space. (Omitted)
    \item Invariant subspace. (Omitted)
    \item Transformation of basis. (Omitted)
    \item Direct sum of operators:

        Let vector spaces $L=L_1\oplus L_2$, with $L=\braket{e_i}$,
        $L_1=\braket{e'_1,\cdots e'_n}$,$L_2=\braket{e'_{n+1},\cdots,e'_m}$,
        $e'_\nu=\sum_\mu e_\mu  S_{\mu\nu}$. 
        Assume that $L_1,L_2$ are invariant w.r.t $A$, an linear operator. If:
        \begin{align}
            A e'_\mu = \sum_{\nu=1}^{m} e'_\nu R'_{\nu\mu}
        \end{align}
        we have obviously:
        \begin{align}
            A e'_\mu = \sum_{\nu=1}^{n} e'_\nu R'_{\nu\mu} \text{for }
                \mu\in \{1\cdots n\}
                \\
            A e'_\mu = \sum_{\nu=n}^{m} e'_\nu R'_{\nu\mu} \text{for }
                \mu\in \{n\cdots m\}
        \end{align}
        i.e., $A$'s matrix representation has two diagonal blocks.
        Using this fact, $A$ after a linear transformation (by $S$),
        could be written as $R_1\oplus R_2$, where the meaning of $R_1/R_2$
        is obvious.
    \item Eigenvalues and the characteristic equation. (Omitted)
        Some properties:
        \begin{enumerate}
            \item Trace = $\sum_i \lambda_i$
            \item Determinant = $\prod_i \lambda_i$
            \item Geometric multiplicity $\leq$ Algebraic multiplicity, or
                $$\mathrm{dim}V_{\lambda_1} \leq n_1$$.
        \end{enumerate}
    \item Inner product and orthonormal basis. (Omitted) Here we define
        matrix $\Omega$ to be, when a basis $\{e_i\}$is given:
        \begin{defi}[]
        \nomenclature{}{\nomrefpage.}
            \begin{align}
                \Omega_{ij} \equiv \braket{e_i,e_j}
            \end{align}
        \end{defi}
    \item Adjoint operator:

        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
        $(R^T)^* \Omega = \Omega A$, so:
        \begin{align}
            R^\dagger = \Omega^{-1} A^\dagger \Omega
        \end{align}
        where we have used the fact that $\Omega^\dagger=\Omega$.

        Note that $(R^{k}_j)^* \Omega_{ki}$ is not $\Omega^T R^*$.
        (Be careful and you will find out why.)

        This is very different from my previous naive concept
        when $\Omega$ is not identity matrix, i.e. when the basis
        is not orthonormal.
\end{enumerate}

\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    %\bibitem{book} 
    \bibitem{book_1} Zhongqi Ma, Group Theory in Physics
    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-20 Draft/draft.tex
New notes about adjoint operator of antilinear operators.

@@
 \usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
+\usepackage{bbm} % for numbers with mathbb
 \numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
@@
 
+    \subsection{Adjoint of antilinear operator}
+    \label{sec:Adjoint_of_antilinear_operator}
+
+    If we were to define adjoint of an antilinear operator, we might
+    run into troubles with traditional definition. For example, suppose
+    $A$ is antilinear, let multiply it with $c\mathbbm{1}$, where $c$
+    is just some nonzero constant.
+
+    We have:
+    \begin{align}
+        \braket{\phi|cA \psi} = c\braket{\phi|A\psi}
+    \end{align}
+    on the other hand:
+    \begin{align}
+        &\braket{\phi|cA \psi} = \braket{cA\psi|\phi}^*
+            = \braket{\psi|A^\dagger c^* \phi}^* \nonumber\\
+        &=(c\braket{\psi|A^\dagger \phi})^* = c^* \braket{A\psi|\phi}^*
+            = c^* \braket{\phi|A\psi}
+    \end{align}
+    A contracdiction. Then, it was proposed, in the first answer to
+    this Math.SE post, that we define the adjoint operator differently 
+    for antilinear operator $A$:
+    \begin{align}
+        \braket{A^\dagger v|w} = \braket{v| Aw}^*
+    \end{align}
+    Then the above discrepancy will not exist anymore (easily confirmed).
+
+    Here I also include the complete answer for reference:
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+    \begin{quote}
+        I) First of all, one should never use the [Dirac bra-ket notation](http://en.wikipedia.org/wiki/Bra-ket\_notation) (in its ultimate version where an operator acts to the right on kets and to the left on bras) to consider the definition of [adjointness](http://en.wikipedia.org/wiki/Adjoint\_operator), since the notation was designed to make the adjointness property look like a mathematical triviality, which it is not.
+See also [this](http://physics.stackexchange.com/q/43069/2451) Phys.SE post.
+
+        II) OP's question(v1) about the existence of the adjoint of an [antilinear](http://en.wikipedia.org/wiki/Antilinear\_map) operator is an interesting mathematical question, which is rarely treated in textbooks, because they usually start by assuming that operators are $\mathbb{C}$-linear.
+
+        III) Let us next recall the mathematical definition of the adjoint of a linear operator.
+Let there be a [Hilbert space](http://en.wikipedia.org/wiki/Hilbert\_space) $H$ over a [field](http://en.wikipedia.org/wiki/Field\_\%28mathematics\%29) $\mathbb{F}$, which in principle could be either real or complex numbers, $\mathbb{F}=\mathbb{R}$ or $\mathbb{F}=\mathbb{C}$.
+Of course in quantum mechanics, $\mathbb{F}=\mathbb{C}$.
+In the complex case, we will use the standard physicist's convention that the [inner product/sequilinear form](http://en.wikipedia.org/wiki/Sesquilinear\_form) $\langle \cdot | \cdot \rangle$ is conjugated $\mathbb{C}$-linear in the first entry, and $\mathbb{C}$-linear in the second entry.
+
+        Recall [Riesz' representation theorem](http://en.wikipedia.org/wiki/Riesz\_representation\_theorem): For each continuous $\mathbb{F}$-linear functional $f: H \to \mathbb{F}$ there exists a unique vector $u\in H$ such that
+        $$\text{tag\{1\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
+
+        Let $A:H\to H$ be a continuous$^1$ $\mathbb{F}$-linear operator. Let $v\in H$ be a vector. Consider the continuous $\mathbb{F}$-linear functional
+
+        $$\text{tag\{2\}} f(\cdot)~=~\langle v | A(\cdot) \rangle.$$
+
+        The value $A^{\dagger}v\in H$ of the adjoint operator $A^{\dagger}$ at the vector $v\in H$ is by definition the unique vector $u\in H$, guaranteed by Riesz' representation theorem, such that 
+        $$\text{tag\{3\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
+
+        In other words, 
+        $$\text{tag\{4\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\langle v | Aw \rangle. $$
+
+        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an $\mathbb{F}$-linear operator as well.
+
+        IV) Finally, let us return to OP's question and consider the definition of the adjoint of an antilinear operator.
+The definition will rely on the complex version of Riesz' representation theorem.
+Let $H$ be given a complex Hilbert space, and let  $A:H\to H$ be an antilinear continuous operator.
+In this case, the above equations (2) and (4) should be replaced with
+
+        $$\text{tag\{2'\}} f(\cdot)~=~\overline{\langle v | A(\cdot) \rangle},$$
+
+        and
+
+        $$\text{tag\{4'\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\overline{\langle v | Aw \rangle}, $$
+
+        respectively. Note that $f$ is a $\mathbb{C}$-linear functional.
+
+        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an antilinear operator as well.
+
+        --
+
+        $^{1}$We will ignore subtleties with [discontinuous/unbounded operators](http://en.wikipedia.org/wiki/Unbounded\_operator), domains, [selfadjoint extensions](http://en.wikipedia.org/wiki/Extensions\_of\_symmetric\_operators), etc., in this answer.
+    \end{quote}
+
 \section{Anchor}
@@
 	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
-
+	\bibitem{BSCS} 
+        Bosonization and Strongly Correlated Systems. Cambridge.
         \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
@@
     \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
+    \bibitem{math.SE-adjoint-of-antilinear}\href{http://physics.stackexchange.com/questions/45227/existence-of-adjoint-of-an-antilinear-operator-time-reversal}{Existence of adjoint of an antilinear operator, time reversal}
 \end{thebibliography}

### 2016-09-20 Complex Geometry - index/misc/complex geometry-misc.tex
Finished one problem of complex geometry! Oh yeah.

@@
         conlude that $A$ is inside $\mathrm{GL}(n,\mathbb{C})$?
-        % TODO resolve this double.
+
+        The following is my solution:
+        \begin{lemma}
+            There exists a injection $\phi$ of $\mathrm{GL}(n,\mathbb{C})
+            \hookrightarrow \mathrm{GL}(2n,\mathbb{R})$ such that:
+            \begin{align}
+                \phi(i B)= \phi(i)\phi(B)
+            \end{align}
+            for any $B\in \mathrm{GL}(n,\mathbb{C})$. Also, for any
+            $A\in \mathrm{GL}(2n,\mathbb{R})$ we have $AJA^{-1}=J$
+            if and only if $A\in \mathrm{Im}(\phi)$, where $J\equiv\phi(i)$.
+        \end{lemma}
+
+        \begin{proof}
+            The $\phi$ is construct as follows. Let 
+            $J_0=\left( \begin{array}{cc}
+                 0 & -1 \\
+            1 & 0 \\ \end{array} \right)$, define $H(x+iy)$ for
+            $x,y\in \mathbb{R}$ as
+            \begin{align}
+                H(x+iy) = x I + y J
+            \end{align}
+            Then:
+            \begin{align}
+                \phi(A)_{ij} \equiv H(a_{ij})
+            \end{align}
+            Then:
+            \begin{align}
+                \phi(i) = \left( \begin{array}{ccc}
+                     J & 0 & 0 \\
+                     0 & \text{...} & 0 \\
+                     0 & 0 & J \\
+                    \end{array} \right)
+            \end{align}
+            By direct simple calculation (remember to use the technique
+            of block multiplication), we have:
+            $\phi(i B)= \phi(i)\phi(B)$.
+            for any $B\in \mathrm{GL}(n,\mathbb{C}$. This shows also
+            $BJB^{-1}=J$, since $iB=Bi$.
+
+            To prove the converse, we see that the following matrices forms
+            a basis of $2x2$ real matrices:
+            $$ \left( \begin{array}{cc}
+             1 & 0 \\
+             0 & 1 \\ \end{array}
+            \right),\left( \begin{array}{cc}
+             0 & -1 \\
+             1 & 0 \\ \end{array}
+            \right),\left( \begin{array}{cc}
+             0 & 0 \\
+             1 & 0 \\ \end{array}
+            \right),\left( \begin{array}{cc}
+             0 & 0 \\
+             0 & 1 \\ \end{array} \right) $$
+            They are denoted, from left to right as $I,J_0,K,L$.
+            \marginpar{Fun fact: $[K,J_0]=\sigma_z\;,[L,J_0]=\sigma_x$, the
+            pauli matrices!}
+            Let any $A\in \mathrm{GL}(2n,\mathbb{R})$, we can partition $A$
+            into a matrix of $2x2$ matrices $(a_{ij})$. Each matrix can
+            the be expressed as $a_{ij}=x_{ij}I+y_{ij}J_0+z_{ij}K+t_{ij}L$.
+            Then if $AJA^{-1}=J$, by direct calculation we find:
+            $$ (z_{ij}K+t_{ij}L)J_0=J_0(z_{ij}K+t_{ij}L)$$
+            then also by direct calculation, it can be easily found that
+            $z_{ij}=t_{ij}=0$. Hence $A\in \mathrm{Im}(\phi)$.
+        \end{proof}
+
         \subsubsection{Why \texorpdfstring{

### 2016-09-20 matlab home/Commutator.m

@@ -1,0 +1,3 @@
+function T=Commutator(A,B)
+    T = A*B-B*A;
+end

### 2016-09-20 matlab home/H_matrix.m

@@ -1,0 +1,6 @@
+function H=H_matrix(z)
+    I=eye(2);
+    J=[0,-1;1,0];
+    x=real(z);y=imag(z);
+    H=x*I+y*J;
+end

### 2016-09-22 Complex Geometry - index/misc/complex geometry-misc.tex
1. Begin really tackling the first problem in Complex Geometry. 2. Editing some green function code. 3. New course notes about Advanced Quantum Mechanics.

@@
 % ANCHOR
+
+% For highlighting
+\usepackage{xcolor,soul}
+
 \title{Miscellaneous notes for D. Huybrechts's Complex Geometry}
@@
         be clear.
+
+    \subsection{Math.SE answer in \texorpdfstring{$M_2$}{} is two copies of \texorpdfstring{$S^2$}{}}
+
+    Following is an answer\cite{math.se_set-of-almost}
+    in Math.SE about this question:
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+    \begin{quote}
+        As you noted, $M$ is *not* diffeomorphic to $S^2\coprod S^2$ for
+        dimension reasons.
+
+        On the other hand, what is true is $M$ is homotopy equivalent to $S^2
+        \coprod S^2$.
+
+        (The following argument is partly adapted from a [paper][1] of
+        Montgomery)
+
+        To see this, it's enough to show that
+        $Gl^+(4,\mathbb{R})/Gl(2,\mathbb{C})$ is homotopy equivalent to $S^2$,
+        where $Gl^+$ denotes those matrices of positive determinant.
+
+        Now, consider the subgroups $U(2)\subseteq Gl(2,\mathbb{C})$ and
+        $SO(4)\subseteq Gl^+(4,\mathbb{R})$.
+
+        It's relatively well known that $Gl(2,\mathbb{C})$ is diffeomorphic to
+        $U(2)\times \mathbb{R}^4$ and that $Gl^+(4,\mathbb{R})$ is diffeomorphic
+        to $SO(4)\times \mathbb{R}^{10}$.  Further, in the usual inclusion
+        $Gl(2,\mathbb{C})\rightarrow Gl^+(4,\mathbb{R})$, $U(2)$ becomes a
+        subgroup of $SO(4)$.
+
+        Now, the chain of subgroups $U(2)\subseteq SO(4)\subseteq
+        Gl^+(4,\mathbb{R})$ gives rise to a homogeneous fibration
+        $$SO(4)/U(2)\rightarrow Gl^+(4,\mathbb{R})/U(2)\rightarrow
+        Gl^+(4,\mathbb{R})/SO(4).$$  \hl{In light of the above diffeomorphisms,
+        $Gl^+(4,\mathbb{R})/SO(4)$ is diffeomorphic to $\mathbb{R}^{10}$.}
+        Since Euclidean spaces are \hl{contractible, it follows that the
+        fibration is trivial}, so $Gl^+(4,\mathbb{R})/U(2)$ is diffeomorphic to
+        $SO(4)/U(2)\times \mathbb{R}^{10}$.  In particular, $SO(4)/U(2)$ is
+        homotopy equivalent to $Gl^+(4,\mathbb{R})/U(2)$.
+
+        Now, consider the chain of subgroups $U(2)\subseteq
+        Gl(2,\mathbb{C})\subseteq Gl^+(4,\mathbb{R})$.  This gives rise to a
+        homogeneous fibration $$Gl(2,\mathbb{C})/U(2)\rightarrow
+        Gl^+(4,\mathbb{R})/U(2) \rightarrow
+        Gl^+(4,\mathbb{R})/Gl(2,\mathbb{C}).$$  In this case, the fiber is
+        diffeomoprhic to $\mathbb{R}^4$, which immediately implies that
+        $Gl^+(4,\mathbb{R})/U(2)$ is homotopy equivalent to
+        $Gl^+(4,\mathbb{R})/Gl(2,\mathbb{C})$.
+        \begin{center}\noindent\rule{8cm}{0.4pt}
+            (Paused reading here)
+        \end{center}
+
+        Putting the last two paragraphs together, we now know that $SO(4)/U(2)$
+        is homotopy equivalent to $Gl^+(4,\mathbb{R})/Gl(2,\mathbb{C})$.
+
+        To finish off the argument, we need to show that $SO(4)/U(2)$ is
+        diffeomorphic to $S^2$.  To see this, first note that $U(2)$ intersects
+        the center $Z(SO(4)) = \{\pm I\}$ of $SO(4)$.  It follows that
+        $$SO(4)/U(2) \cong [SO(4)/Z(SO(4)]/[U(2)/(Z(SO(4))\cap U(2))].$$
+
+        But $SO(4)/Z(SO(4))\cong SO(3)\times SO(3)$ and $U(2)/(Z(SO(4))\cap
+        U(2)) \cong SO(3)\times S^1$.  So, $SO(4)/U(2)\cong (SO(3)\times
+        SO(3))/(SO(3)\times S^1)\cong SO(3)/S^1$.
+
+        But the standard action of $SO(3)$ on $S^2$ is transitive with
+        stabilizer $S^1$, so $SO(3)/S^1 \cong S^2$.
+
+        [1]:
+        \url{http://www.ams.org/journals/proc/1950-001-04/S0002-9939-1950-0037311-6/S0002-9939-1950-0037311-6.pdf}
+    \end{quote}
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
+    I honestly know almost nothing about the concepts this response mentioned.
+    Therefore, I try to dismantle the response into several parts:
+
+    Facts he mentioned that I am not familiar
+    \begin{enumerate}
+        \item $Gl(2,\mathbb{C})$ is diffeomorphic to $U(2)\times\mathbb{R}^4$.
+        \item $Gl^+(4,\mathbb{R})$ is diffeomoprhic to $SO(4)\times
+            \mathbb{R}^10$
+        \item In the usual inclusion $Gl(2,\mathbb{C})\rightarrow
+            Gl^+(4,\mathbb{R})$, $U(2)$ becomes a subgroup of $SO(4)$.
+    \end{enumerate}
+    Concepts to be learnt:
+    \begin{enumerate}
+        \item fibration of above Lie groups
+        \item Hightlight area 1: can fibration kill a subgroup?
+        \item Hightlight area 2: contractible and fibration?
+        \item And the following sentence.
+        \item then the next sentence: diffeomoprhism and homotopy?
+        \item How does a "chain of subgroups" gives rise to a fibration.
+    \end{enumerate}
 \section{Anchor}
@@
   {Similar matrices and field extensions}
+  \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
 \end{thebibliography}

### 2016-09-22 Draft/draft.tex
1. Begin really tackling the first problem in Complex Geometry. 2. Editing some green function code. 3. New course notes about Advanced Quantum Mechanics.

@@
 
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
+    \subsection{Bayes' theorem}
+    \label{sec:Bayes-theorem}
+    I am quite unfamiliar with this formula, so I decided to make a note
+    here for future reference.
+
+    This formula starts from the definition of conditional probability:
+    \begin{align}
+        P(A|B)\equiv \frac{P(A\&B)}{P(B)}
+    \end{align}
+    this definition if quite intuitively pleasing if $P(B)$ is multiplied
+    to the left side. Then one easily deduce that:
+    \begin{thm}[Bayes' theorem] \begin{align}
+        P(A|B)=\frac{P(B|A)P(A)}{P(B)}
+    \end{align} \end{thm}
+
+    We have also an extended form. Suppose the event space is partitioned
+    into $\{A_i\}$, then we have (also easily proved):
+    \begin{align}
+        P(A_i|B)=\frac{P(B|A_i)P(A_i)}{\sum_j P(B|A_j)P(A_j)}
+    \end{align}
+    Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
 \section{Anchor}

### 2016-09-22 Notes of Advanced Quantum Mechanics/Notes of Advanced Quantum Mechanics.tex
1. Begin really tackling the first problem in Complex Geometry. 2. Editing some green function code. 3. New course notes about Advanced Quantum Mechanics.

--- 2016-09-19 Group Theory in Physics/group theory in physics.tex
@@
 \usepackage{amssymb}
-\usepackage{mathrsfs}
+\usepackage{bbm} % for numbers within mathbb
+\usepackage{mathrsfs} % For \mathscr{ABC}
 % Followings are for the special character: differential "d".
@@
 
-% For highlighting
-\usepackage{xcolor,soul}
-\newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}
-
-\title{Group Theory in Physics (Course Note)}
+\title{Notes of Advanced Quantum Mechanics}
 \date{\today}
@@
 \abstract{
-This is our course note for the course about group theoy, with its
-application in physics.
+Notes of the course Advanced Quantum Mechanics, told by professor
+MH. Wang.
 }
 \tableofcontents
+
+Evaluation
 \begin{enumerate}
-    \item Combine group theory with you research.
-    \item Mid-term and final.
-    \item No homework, cause it is already graduate level.
-    \item Professor Fei Ye. (Phone: 88018229, 228 in Research building 2), 
-        T.A. Zhe Zhang. (110 Research building 2).
+    \item Homework 20\%
+
+        5\% bonus for solution based on \LaTeX, other bonus available.
+    \item Mid-term 30\%
+    \item Final 50 \%
 \end{enumerate}
 
-\section{20160919}
-\label{sec:20160919}
-
-He first introduces several common examples of symmetries in our life and
-physics. Omitted, with one exception:
-
-He mentions that there is one more symmetry in the Hydrogen 
-Hamiltonian: the Laplace-Runge-Lenz symmetry. (So its symmetry 
-group is not just $SO(3)$, but two copies of $SO(3)$ that forms a $SO(4)$.
-And using the representation of $SO(4)$, the complete spectrum of
-Hydrogen Hamiltonian is solved. Hence this $SO(4)$ is the largest
-symmetry of Hydrogen Hamiltonian.
-
-    \subsection{Digression about Lenz vector}
-    \label{sec:Digression_about_Lenz_vector}
-    Since the class is too boring, I checked about the Lenz vector via
-    Google and found this Math.SE question \cite{math.se_1_lenz_vector}
-
-    The first answer to that post is:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        1) \textbf{Problem}. The \href{http://en.wikipedia.org/wiki/Kepler_problem}{Kepler Problem} has Hamiltonian
-
-        $$ H~:=~ \frac{p^2}{2m}- \frac{k}{q},  $$
-
-        where $m$ is the 2-body reduced mass. The [Laplace–Runge–Lenz vector](http://en.wikipedia.org/wiki/Laplace%E2%80%93Runge%E2%80%93Lenz_vector) is (up to an irrelevant normalization)
-
-        $$ A^j ~:=~a^j  + km\frac{q^j}{q}, \qquad a^j~:=~({\bf L} \times {\bf p})^j~=~{\bf q}\cdot{\bf p}~p^j- p^2~q^j,\qquad {\bf L}~:=~ {\bf q} \times {\bf p}.$$
-
-        2) \textbf{Action}. The Hamiltonian Lagrangian is
-
-        $$  L_H~:=~ \dot{\bf q}\cdot{\bf p} - H, $$
-
-        and the action is
-
-        $$ S[{\bf q},{\bf p}]~=~ \int {\rm d}t~L_H .$$
-
-        The non-zero fundamental canonical Poisson brackets are
-
-        $$ \{ q^i , p^j\}~=~ \delta^{ij}. $$
-
-        3) \textbf{Inverse Noether's Theorem}. Quite generally in the Hamiltonian formulation, given a constant of motion $Q$, then the infinitesimal variation
-
-        $$\delta~=~ \varepsilon \{Q,\cdot\}$$
-
-        is a global off-shell symmetry of the action $S$ (modulo boundary terms).
-Here $\varepsilon$ is an infinitesimal global parameter, and $X_Q=\{Q,\cdot\}$ is a Hamiltonian vector field with Hamiltonian generator $Q$.
-The full Noether current is (minus) $Q$, see e.g.
-my answer to [this question](http://physics.stackexchange.com/q/8626/2451).
-\hl{(The words \textbf{on-shell}.
-and \textbf{off-shell}.
-refer to whether the equations of motion are satisfied or not.)}
-
-        4) \textbf{Variation}.
-Let us check that the three Laplace–Runge–Lenz components $A^j$ are Hamiltonian generators of three continuous global off-shell symmetries of the action $S$.
-In detail, the infinitesimal variations $\delta= \varepsilon_j \{A^j,\cdot\}$ read
-
-        $$ \delta  q^i ~=~  \varepsilon_j  \{A^j,q^i\}   , \qquad 
-         \{A^j,q^i\} ~ =~ 2 p^i q^j - q^i p^j - {\bf q}\cdot{\bf p}~\delta^{ij}, $$
-        $$ \delta  p^i ~=~  \varepsilon_j  \{A^j,p^i\}   , \qquad  
-        \{A^j,p^i\}~ =~ p^i p^j - p^2~\delta^{ij} +km\left(\frac{\delta^{ij}}{q}- \frac{q^i q^j}{q^3}\right), $$
-        $$ \delta  t ~=~0,$$
-
-        where $\varepsilon_j$ are three infinitesimal parameters.
-
-        5) Notice for later that
-
-        $$ {\bf q}\cdot\delta {\bf q}~=~\varepsilon_j({\bf q}\cdot{\bf p}~q^j - q^2~p^j),  $$
-
-        $$ {\bf p}\cdot\delta {\bf p}
-        ~=~\varepsilon_j km(\frac{p^j}{q}-\frac{{\bf q}\cdot{\bf p}~q^j}{q^3})~=~- \frac{km}{q^3}{\bf q}\cdot\delta {\bf q},  $$
-
-        $$ {\bf q}\cdot\delta {\bf p}~=~\varepsilon_j({\bf q}\cdot{\bf p}~p^j - p^2~q^j )~=~\varepsilon_j a^j,  $$
-
-        $$ {\bf p}\cdot\delta {\bf q}~=~2\varepsilon_j( p^2~q^j - {\bf q}\cdot{\bf p}~p^j)~=~-2\varepsilon_j a^j~.  $$
-
-        6) The Hamiltonian is invariant
-
-        $$ \delta  H ~=~ \frac{1}{m}{\bf p}\cdot\delta {\bf p} + \frac{k}{q^3}{\bf q}\cdot\delta {\bf q}~=~0, $$
-
-        showing that the Laplace–Runge–Lenz vector $A^j$ is classically a constant of motion
-
-        $$\frac{dA^j}{dt} ~\approx~ \{ A^j, H\}+\frac{\partial A^j}{\partial t} ~=~  0.$$
-
-        (We will use the $\approx$ sign to stress that an equation is an on-shell equation.)
-
-        7) The variation of the Hamiltonian Lagrangian $L_H$ is a total time derivative
-
-        $$ \delta L_H~=~ \delta  (\dot{\bf q}\cdot{\bf p})~=~ \dot{\bf q}\cdot\delta {\bf p} - \dot{\bf p}\cdot\delta {\bf q} + \frac{d({\bf p}\cdot\delta {\bf q})}{dt} $$
-        $$  =~ \varepsilon_j\left( \dot{\bf q}\cdot{\bf p}~p^j - p^2~\dot{q}^j +  km\left( \frac{\dot{q}^j}{q} -  \frac{{\bf q} \cdot \dot{\bf q}~q^j}{q^3}\right)\right)    $$
-        $$- \varepsilon_j\left(2 \dot{\bf p}\cdot{\bf p}~q^j - \dot{\bf p}\cdot{\bf q}~p^j- {\bf p}\cdot{\bf q}~\dot{p}^j  \right) - 2\varepsilon_j\frac{da^j}{dt}$$
-        $$ =~\varepsilon_j\frac{df^j}{dt}, \qquad f^j ~:=~ A^j-2a^j, $$
-
-        and hence the action $S$ is invariant off-shell up to boundary terms.
-
-        8) \textbf{Noether current}. The bare \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether current} $j^k$ is
-
-        $$j^k~:=~ \frac{\partial L_H}{\partial \dot{q}^i}  \{A^k,q^i\}+\frac{\partial L_H}{\partial \dot{p}^i}  \{A^k,p^i\}
-        ~=~ p^i\{A^k,q^i\}~=~ -2a^k. $$
-
-        The full Noether current $J^k$ (which takes the total time-derivative into account) becomes (minus) the Laplace–Runge–Lenz vector
-
-        $$ J^k~:=~j^k-f^k~=~ -2a^k-(A^k-2a^k)~=~ -A^k.$$
-
-        $J^k$ is conserved on-shell
-
-        $$\frac{dJ^k}{dt} ~\approx~  0,$$
-
-        due to \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether's first Theorem}. Here $k$ is an index that labels the three symmetries.
-    \end{quote}
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    However, I don't really understand the content inside. I asked professor
-    Ye whether we can find some physics about this conserved quantity, and
-    he answered with no.
-
-    The next answer is also interesting:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        While Kepler second law is simply a statement of the conservation of angular momentum (and as such it holds for all systems described by central forces), \hl{the first and the third laws are special and are linked with the unique form of the newtonian potential $-k/r$.} In particular, \hl{Bertrand theorem assures that *only* the newtonian potential and the harmonic potential $kr^2$ give rise to closed orbits (no precession).} It is natural to think that this must be due to some kind of symmetry of the problem.
-In fact, the particular symmetry of the newtonian potential is described exactly by the conservation of the RL vector (\hl{it can be shown that the RL vector is conserved iff the potential is central and newtonian}).
-This, in turn, is due to a more general symmetry: \hl{if conservation of angular momentum is linked to the group of special orthogonal transformations in 3-dimensional space $SO(3)$, conservation of the RL vector must be linked to a 6-dimensional group of symmetries}, since in this case there are apparently six conserved quantities (3 components of $L$ and 3 components of $\mathcal A$).
-In the case of bound orbits, this group is $SO(4)$, the group of rotations in 4-dimensional space.
-
-        Just to fix the notation, the RL vector is:
-
-        \begin{equation} \mathcal{A}=\textbf{p}\times\textbf{L}-\frac{km}{r}\textbf{x} \end{equation}
-
-        Calculate its total derivative:
-
-        \begin{equation}\frac{d\mathcal{A}}{dt}=-\nabla U\times(\textbf{x}\times\textbf{p})+\textbf{p}\times\frac{d\textbf{L}}{dt}-\frac{k\textbf{p}}{r}+\frac{km(\textbf{p}\cdot \textbf{x})}{r^3}\textbf{x} \end{equation}
-
-        Make use of Levi-Civita symbol to develop the cross terms:
-
-        \begin{equation}\epsilon_{sjk}\epsilon_{sil}=\delta_{ji}\delta_{kl}-\delta_{jl}\delta_{ki}   \end{equation}
-
-        Finally:
-
-        \begin{equation}
-        \frac{d\mathcal{A}}{dt}=\left(\textbf{x}\cdot\nabla U-\frac{k}{r}\right)\textbf{p}+\left[(\textbf{p}\cdot\textbf{x})\frac{k}{r^3}-2\textbf{p}\cdot\nabla U\right]\textbf{x}+(\textbf{p}\cdot\textbf{x})\nabla U
-        \end{equation}
-
-        Now, if the potential $U=U(r)$ is central:
-
-        \begin{equation}
-        (\nabla U)_j=\frac{\partial U}{\partial x_j}=\frac{dU}{dr}\frac{\partial r}{\partial x_j}=\frac{dU}{dr}\frac{x_j}{r}
-        \end{equation}
-
-        so
-
-        \begin{equation} \nabla U=\frac{dU}{dr}\frac{\textbf{x}}{r}\end{equation}
-
-        Substituting back:
-
-        \begin{equation}
-            \hlMath{\frac{d\mathcal A}{dt}=\frac{1}{r}\left(\frac{dU}{dr}-\frac{k}{r^2}\right)[r^2\textbf{p}-(\textbf{x}\cdot\textbf{p})\textbf{x}]}
-        \end{equation}
-
-        Now, you see that if $U$ has \textit{exactly} the newtonian form then the first parenthesis is zero and so the RL vector is conserved.
-
-        Maybe there's some slicker way to see it (Poisson brackets?), but this works anyway.
-    \end{quote}
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    % TODO Study in detail about this example.
-
-    \subsection{Coming back to the course}
-
-After mentioning the Poinc\'{a}re group, he produces to review some
-concepts about linear algebra:
-\begin{enumerate}
-    \item The axioms of linear space, using quantum mechanics
-        as basic example (Omitted).
-    \item Some common concepts of linear space: linear-independence,
-        subspace, direct sum, linear operators, its matrix representation. (Omitted)
-    \item Introducing the complete antisymmetric tensor 
-        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
-        \begin{align}
-            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
-            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
-            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
-            \\
-            &= \sum_{p_1,\cdots,p_n} 
-            \epsilon_{p_1,\cdots,p_n} 
-                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
-                \\
-            \epsilon_{ab}\epsilon_{rs} &=
-                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
-                \\
-            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
-                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
-        \end{align}
-    \item Some special matrices.
-    \item Fact: If $R\Gamma = \Gamma R$, and 
-        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
-        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
-        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
-        On the other hand, if $R_{\mu\nu}\neq 0$, then
-        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
-        This is obviously from:
-        \begin{align*}
-            R^{i}_{j}\Gamma^{j}_{k}=\Gamma^{i}_{j} R^{j}_k
-            \Longrightarrow
-            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
-        \end{align*}
-        where the first is automatically summed, and the second is not.
-
-    \item A linear functional is closed w.r.t. a vector space. (Omitted)
-    \item ... then this linear functional can be expressed as a
-        matrix w.r.t to a basis of this vector space. (Omitted)
-    \item Invariant subspace. (Omitted)
-    \item Transformation of basis. (Omitted)
-    \item Direct sum of operators:
-
-        Let vector spaces $L=L_1\oplus L_2$, with $L=\braket{e_i}$,
-        $L_1=\braket{e'_1,\cdots e'_n}$,$L_2=\braket{e'_{n+1},\cdots,e'_m}$,
-        $e'_\nu=\sum_\mu e_\mu  S_{\mu\nu}$. 
-        Assume that $L_1,L_2$ are invariant w.r.t $A$, an linear operator. If:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{m} e'_\nu R'_{\nu\mu}
-        \end{align}
-        we have obviously:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{n} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{1\cdots n\}
-                \\
-            A e'_\mu = \sum_{\nu=n}^{m} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{n\cdots m\}
-        \end{align}
-        i.e., $A$'s matrix representation has two diagonal blocks.
-        Using this fact, $A$ after a linear transformation (by $S$),
-        could be written as $R_1\oplus R_2$, where the meaning of $R_1/R_2$
-        is obvious.
-    \item Eigenvalues and the characteristic equation. (Omitted)
-        Some properties:
-        \begin{enumerate}
-            \item Trace = $\sum_i \lambda_i$
-            \item Determinant = $\prod_i \lambda_i$
-            \item Geometric multiplicity $\leq$ Algebraic multiplicity, or
-                $$\mathrm{dim}V_{\lambda_1} \leq n_1$$.
-        \end{enumerate}
-    \item Inner product and orthonormal basis. (Omitted) Here we define
-        matrix $\Omega$ to be, when a basis $\{e_i\}$is given:
-        \begin{defi}[]
-        \nomenclature{}{\nomrefpage.}
-            \begin{align}
-                \Omega_{ij} \equiv \braket{e_i,e_j}
-            \end{align}
-        \end{defi}
-    \item Adjoint operator:
-
-        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
-        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
-        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
-        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
-        $(R^T)^* \Omega = \Omega A$, so:
-        \begin{align}
-            R^\dagger = \Omega^{-1} A^\dagger \Omega
-        \end{align}
-        where we have used the fact that $\Omega^\dagger=\Omega$.
-
-        Note that $(R^{k}_j)^* \Omega_{ki}$ is not $\Omega^T R^*$.
-        (Be careful and you will find out why.)
-
-        This is very different from my previous naive concept
-        when $\Omega$ is not identity matrix, i.e. when the basis
-        is not orthonormal.
-\end{enumerate}
+Textbook: Griffiths or Sakurai. As a reference, this course will cover
+chapter 1, 2, 4, and 7 of Sakurai's book. And if time permits, chapter 8
+about the Relativistic Quantum Mechanics in chapter 8. Since the average
+level of the course is not high, He seems to hold negative view towards
+this goal.
 
@@
     %\bibitem{book} 
-    \bibitem{book_1} Zhongqi Ma, Group Theory in Physics
-    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
 \end{thebibliography}

### 2016-09-22 Green function/1D QAHI Conductance/GreenF.m

@@ -4,15 +4,17 @@ function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso
 
 w_energy_resol=1.*10^-3;                     % the resolution of energy
 
-I=eye(4);
-gL=g11(E,muL,ts,tsoL,w_energy_resol);
-Tc1=V_dl(tc1);
-SE1=Tc1*gL*Tc1';               % self energy for the L-L interfaces of lead-1
-HnS=H_sample(1,muS,ts,tso,delta,Gamma,0);
-HeS1=HnS+SE1+dis(1)*diag([-1,-1,1,1]);
-Tc2=V_dl(tc2);
-SE2=Tc2*gL*Tc2';               % self energy for the L-L interfaces of lead-2
-HeS2=HnS+SE2+dis(L)*diag([-1,-1,1,1]);
+% tc1 coupling between lead 1 and the sample
+% tc2 coupling between lead 2 and the sample
+I    = eye(4);
+gL   = g11(E,muL,ts,tsoL,w_energy_resol);
+Tc1  = V_dl(tc1);
+SE1  = Tc1*gL*Tc1';          % self energy for the L-L interfaces of lead-1
+HnS  = H_sample(1,muS,ts,tso,delta,Gamma,0);
+HeS1 = HnS+SE1+dis(1)*diag([-1,-1,1,1]);
+Tc2  = V_dl(tc2);
+SE2  = Tc2*gL*Tc2';       % self energy for the L-L interfaces of lead-2
+HeS2 = HnS+SE2+dis(L)*diag([-1,-1,1,1]);
 
 %% from left to right ( lead 1 to lead 2)
 Gnn=I/(((E+1i*w_energy_resol)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component

### 2016-09-22 Green function/1D QAHI Conductance/ScatteringM.m

@@ -1,49 +1,52 @@
 %function y=ScatteringM(1,Ly,W,E,Vy,u,t,a,tc,Ds,Dp,periodx)
 function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
   y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
-%SCateringMatix calculates the scatering matrix from lattice Green function
-%based on the formula: S=-1+i*sqrt(Gammaa)*GF*sqrt(Gammaa')
+%SCateringMatrix calculates the scatering matrix from lattice Green function
+%based on the formula: S=-1+i*sqrt(Gamma)*GF*sqrt(Gamma')
 
 [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
-Gamma1=(1i*(SE1-SE1'));
-A1=my_sqrt(Gamma1);
-Gamma2=(1i*(SE2-SE2'));
-A2=my_sqrt(Gamma2);
-y11=-eye(4)+1i*A1*G11*A1;
-y12=1i*A1*G1N*A2;
-y21=1i*A2*GN1*A1;
-y22=-eye(4)+1i*A2*GNN*A2;
+Gamma1 = (1i*(SE1-SE1'));
+A1     = my_sqrt(Gamma1);
+Gamma2 = (1i*(SE2-SE2'));
+A2     = my_sqrt(Gamma2);
+y11    = -eye(4)+1i*A1*G11*A1;
+y12    = 1i*A1*G1N*A2;
+y21    = 1i*A2*GN1*A1;
+y22    = -eye(4)+1i*A2*GNN*A2;
 %y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
 % e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
-y11ee=y11(1:2*1,1:2*1);
-y12ee=y12(1:2*1,1:2*1);
-y11eh=y11(1:2*1,2*1+1:4*1);
[…]

### 2016-09-22 Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -2,28 +2,28 @@
 clear
 cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
 
-L=20;          % number of sites
-ts=10;           % hoping
-tso=1.0;          % spin orbital coupling
-tsoL=0;         % spin orbital coupling of the leads
-tc1=0.2*ts;     % coupling between lead 1 and the sample
-tc2=0.2*ts;     % coupling between lead 2 and the sample
-muL=5.0;          % chemical potential of the leads
-muS=0;          % chemical potential of the sample
-disorder=0;     % local disorder
-delta=0.0;         % superconducting pairing
+% Here we use ts as a reference for other energies.
+L=20;        % number of sites
+ts=10;       % hoping
+tso=1.0;     % spin orbital coupling
+tsoL=0;      % spin orbital coupling of the leads
+tc1=0.2*ts;  % coupling between lead 1 and the sample
+tc2=0.2*ts;  % coupling between lead 2 and the sample
+muL=5.0;     % chemical potential of the leads
+muS=0;       % chemical potential of the sample
+disorder=0;  % local disorder
+delta=0.0;   % superconducting pairing
 
-% M_gamma=200;   % gamma
-% N_E=200;   % E
-M_gamma=10;   % gamma
-N_E=10;   % E
+M_gamma=200; % gamma
+N_E=200;     % E
 
 if cont==1
-    gamma=3*(-ts:2.0*ts/M_gamma:ts);          % Zeeman energy Gammz_z as a variable
-    %E=-15:30/N:15;
+    % For cont=1, we try to plot G as a function of gamma
+    % and E.
+    gamma=3*(-ts:2.0*ts/M_gamma:ts);  % Zeeman energy
     E=(-muL:2*muL/N_E:1*muL);
 else
-    gamma=3.0;                % Zeeman energy Gammz_z as a constant
+    gamma=3.0;      % Zeeman energy Gammz_z as a constant
     gap=min(abs(2*ts-abs(gamma)),2*abs(tso));
     %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
[…]

### 2016-09-22 Green function/1D QAHI Conductance/g11.m

@@ -6,6 +6,8 @@ function y=g11(E,mu,ts,tso,w_energy_resol)
     B=A';
     d=D;
     for i=1:1000 %maximum number of recursive times
+        % The following 4 lines of code seems to come from:
+        % Appendix B of the dissertation
         d1=d-A/D*B;
         D1=D-A/D*B-B/D*A;
         A1=A/D*A;
@@ -20,6 +22,7 @@ function y=g11(E,mu,ts,tso,w_energy_resol)
         B=B1;
     end
     y=eye(4)/d1;
+end
 
 function y=H_lead(L,mu,ts,tso)
     y=zeros(4*L);
@@ -38,18 +41,18 @@ function y=H_lead(L,mu,ts,tso)
     %y(i+3*L,i+2*L)=I*m_y;
     %=====================================================================
     for i=1:L-1
-        y(i,i)=Gamma-mu;
-        y(i+L,i+L)=-Gamma-mu;
-        y(i+2*L,i+2*L)=Gamma-mu;
-        y(i+3*L,i+3*L)=-Gamma-mu;
+        y(i,i)         = Gamma-mu;
+        y(i+L,i+L)     = -Gamma-mu;
+        y(i+2*L,i+2*L) = Gamma-mu;
+        y(i+3*L,i+3*L) = -Gamma-mu;
         
         %=====================================================================
         % Additional term which break C2,T2 symmetry but preserve C1 and T1
         % symmetry. To test the influence of C1 and T1 symmetry.
-        y(i,i+L)=m_x+I*m_y;
-        y(i+L,i)=m_x-I*m_y;
-        y(i+2*L,i+3*L)=m_x-I*m_y;
-        y(i+3*L,i+2*L)=m_x+I*m_y;
+        y(i,i+L)       = m_x+I*m_y;
+        y(i+L,i)       = m_x-I*m_y;
+        y(i+2*L,i+3*L) = m_x-I*m_y;
+        y(i+3*L,i+2*L) = m_x+I*m_y;
         
         %=====================================================================
         if condition==1
@@ -109,4 +112,6 @@ function y=V_lead(ts,tso)
         y(i+2*1,i+1+2*1)=-tso;
         y(i+1,i)=-tso;
         y(i+1+2*1,i+2*1)=tso;
+    end
 end
+    

### 2016-09-22 Green function/1D QAHI Conductance/my_sqrt.m

@@ -2,7 +2,8 @@ function y=my_sqrt(A)
 % this function calculates the squre root of a sparse complex matrix
 %
 %A=round(A*10^5)/10^5;
-[V,D]=eig(full(A));
+[V,D]=eig(full(A)); % full: sparse matrix -> full matrix
 d=sqrt(D);
+% What is the point of doing "/V" here? TODO
 y=V*d/V;
 end

### 2016-09-25 Complex Geometry - index/misc/complex geometry-misc.tex
Daily update.

@@
 \usepackage{xcolor,soul}
+
+% For category graphs
+\usepackage[all]{xy}
 
@@
     \end{enumerate}
+
+    The following notes are aim at understanding the above sentences.
+
+    \subsection{Lifting Property}
+    \label{sec:Lifting-Property}
+    \paragraph{Lift of morphisms}
+    \begin{defi}[Lift of morphisms]
+    \nomenclature{Lift of morphisms}{\nomrefpage.}
+        The \textbf{lift} of a morphism $f: Y\to B$ along an epimorphism
+        \footnote{Epimorphism is the category analogy of surjective
+        functions in set theory}. (or more general map) $p:X\to B$ is a
+        morphism $\tilde{f}: Y\to X$ such that $f = p\circ\tilde{f}$.
+    \end{defi}
+    $$
+    \xymatrix{
+        X\ar[r]^p                    & B \\
+        Y\ar[ur]^f\ar[u]^{\tilde{f}} & \\
+    }
+    $$
+    \begin{defi}[Lift property]
+    \nomenclature{Lift property}{\nomrefpage.}
+        We say that $f$ has a \textbf{left lifting property} w.r.t $g$, or
+        equivalently that $g$ has a \textbf{right lifting property} w.r.t
+        $f$, if and only if for every commutative diagram below:
+        $$
+        \xymatrix{
+        a\ar[r]^u\ar[d]^f & c\ar[d]^g \\
+        b\ar[r]^v         & d
+        }
+        $$
+        there is an arrow $\gamma$, s.t. both triangles in the followinng
+        diagram commutes.
+        $$ \xymatrix{
+        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
+        b\ar[r]^v\ar[ru]^{\gamma} & d
+        }$$
+        Such an arrow $\gamma$ is called a \textbf{lift} or a 
+        \textbf{solution} to the lifting problem $(u,v)$.
+        If such $\gamma$ is unique, i.e. we have:
+        $$ \xymatrix{
+        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
+        b\ar[r]^v\ar@{.>}[ru]^{\gamma} & d
+        }$$
+        Then we say $f$ is \textbf{orthogonal} to $g$, denoted $f \perp g$.
+    \end{defi}
+    ref \cite{nlab-lift}.
+
+    % Resources: https://ncatlab.org/nlab/show/fibration
+    %            https://ncatlab.org/nlab/show/homotopy+lifting+property
+    %            https://en.wikipedia.org/wiki/Homotopy_lifting_property
+    %            https://en.wikipedia.org/wiki/Fibration
 \section{Anchor}
@@
   \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
+  \bibitem{nlab-lift}\href{https://ncatlab.org/nlab/show/lift}{nLab Lift}
 \end{thebibliography}

### 2016-09-25 Draft/draft.tex
Daily update.

@@
 
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
+    To resist the flow of current carried by Copper Pair, is equivalent to destroying a pair of Copper Pair:
     $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
@@
     Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
+    \subsection{About Matlab}
+    \label{sec:About-Matlab}
+    \paragraph{On using $A/B$ or $A\\B$}
+    Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
+    , abbrevated $A/B$ and $A\\B$, are different and should be used with
+    caution. One can check that:
+    \begin{center}
+        $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
+        equivalent to $D\backslash A$.
+    \end{center}
+    Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.
 \section{Anchor}

### 2016-09-25 G.R/G.R.tex
Daily update.

@@
 
+    Note that in matrix form, (using the popular notations
+    $\tensor[]{\Lambda}{^\nu_\mu},\gamma, \text{and }\beta$):
+    \begin{align}
+        \tensor[]{\Lambda}{^\nu_\mu} =
+        \left( \begin{array}{cccc}
+         \gamma        & -\gamma \beta & 0 & 0 \\
+         -\gamma \beta & \gamma        & 0 & 0 \\
+         0             & 0             & 0 & 0 \\
+         0             & 0             & 0 & 0 \\
+        \end{array} \right)
+    \end{align}
     Aided with this formula, Landau discusses the \textit{Lorentz
@@
     \end{align}
-    Next the autho introduces the dual tensors. Since this is important
+    Next Landau introduces the dual tensors. Since this is important
     and the case of Lorentzian spacetime is somewhat different from
@@
 
+    \subsection{Digression: inverse of \texorpdfstring{$\Lambda$}{}}
+    Here's a simple formula to get the inverse of Lorentz transformation.
+    \begin{align}
+        \tensor[]{(\Lambda^{-1})}{^\nu_\mu}=\tensor[]{\Lambda}{_\mu^\nu}
+    \end{align}
+    i.e., we drag down the first index and raise the second index, using
+    of course the metric $g$.
+    To put it more precise, we have:
+    \begin{align}
+        \Lambda\indices{^i_\sigma}\Lambda\indices{_j^\sigma}&=\delta^i_j
+        \nonumber\\
+        \Lambda\indices{_\sigma^i}\Lambda\indices{^\sigma_j}&=\delta^i_j
+    \end{align}
+    \begin{proof}
+    This can be proved by noting
+    $(\Lambda V, \Lambda W)=(V,W)$, i.e.
+    $$
+    \Lambda\indices{^\mu_\nu} V^\nu g_{\mu\mu'}
+        \Lambda\indices{^{\mu'}_{\nu'}} W^{\nu'} =  
+        V^\mu g_{\mu\mu'} W^{\mu'}$$
+    By choosing $V$ and $W$ to have appropriate components, one can prove
+    that $\Lambda\indices{^\mu_i} g_{\mu\mu'}\Lambda\indices{^{\mu'}_j}=
+    g_{ij}$. Also notice that $g^2=I$. Then by multiply $g^{ik}$ to the
+    left, we can get:
+    \begin{align}
+        g^{ik} \Lambda\indices{^\mu_k}g_{\mu\mu'}
+            \Lambda\indices{^{\mu'}_j} = \delta^i_j
+    \end{align}
+    \end{proof}
+    Actually, the above proof shows that this relation is much general,
+    can be applied in all space transformations that preserve any metric.
+    It only requires that the matric is idempotent.
+
     \subsection{Dual Tensors}
-    \label{sec:Dual_Tensors}
+    \label{secinDual_Tensors}
     % TODO See this post:http://physics.stackexchange.com/questions/37577/what-does-the-dual-of-a-tensor-mean-e-g-dual-stress-tensor-in-relativistic-ed

### 2016-09-25 Green function/1D QAHI Conductance/GreenF.m

@@ -1,6 +1,7 @@
 function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gamma,dis)
 % Obtain the GF with recursive method for twoo-lead with same material
 % tc is coupling between S and N
+% TODO: I think I should check this with the PDF.
 
 w_energy_resol=1.*10^-3;                     % the resolution of energy
 

### 2016-09-25 Green function/1D QAHI Conductance/H_sample.m

@@ -1,13 +1,14 @@
-%% without normal t
-%% Modified program to calculate AIII topological insulator as
-%% spin transistor
+% without normal t
+% Modified program to calculate AIII topological insulator as
+% spin transistor
 
 % i electron up
 % i electron down
 
 
 function y=H_sample(L,mu,ts,tso,delta,Gamma,dis)
-y=zeros(4*L);
+% TODO Find reference for this code
+%y=zeros(4*L);
 
 m_y=0.0;
 m_x=00.0;
@@ -65,6 +66,7 @@ end
 mu=mu+dis*(rand-0.5);
 y(L,L)=Gamma-mu;
 y(2*L,2*L)=-Gamma-mu;
+% TODO the following code might be wrong!
 y(3*L,3*L)=-Gamma+mu;
 y(4*L,4*L)=Gamma+mu;
 
@@ -76,7 +78,24 @@ y=sparse(y);
 end
 %}
 
-%% with normal
+% % A sample output of the above code:
+% [ gamma - mu - dis*(rand - 0.5),                             -ts,                         zero1_3,                          m_y*1i,                               tso,                           zero1_6,                       zero1_7,                         zero1_8,                         zero1_9,                           delta,                          zero1_11,                        zero1_12]
+% [                           -ts, gamma - mu - 2*dis*(rand - 0.5),                             -ts,                            -tso,                            m_y*1i,                               tso,                       zero2_7,                         zero2_8,                         zero2_9,                        zero2_10,                             delta,                        zero2_12]
+% [                       zero3_1,                             -ts, gamma - mu - 3*dis*(rand - 0.5),                         zero3_4,                              -tso,                           zero3_6,                       zero3_7,                         zero3_8,                         zero3_9,                        zero3_10,                          zero3_11,                           delta]
+% [                       -m_y*1i,                            -tso,                         zero4_3, - gamma - mu - dis*(rand - 0.5),                                ts,                           zero4_6,                        -delta,                         zero4_8,                         zero4_9,                        zero4_10,                          zero4_11,                        zero4_12]
+% [                           tso,                         -m_y*1i,                            -tso,                              ts, - gamma - mu - 2*dis*(rand - 0.5),                                ts,                       zero5_7,                          -delta,                         zero5_9,                        zero5_10,                          zero5_11,                        zero5_12]
[…]

### 2016-09-25 Green function/1D QAHI Conductance/ScatteringM.m

@@ -3,50 +3,51 @@ function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
   y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
 %SCateringMatrix calculates the scatering matrix from lattice Green function
 %based on the formula: S=-1+i*sqrt(Gamma)*GF*sqrt(Gamma')
+% TODO I think I should find reference for this file.
 
-[G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
-Gamma1 = (1i*(SE1-SE1'));
-A1     = my_sqrt(Gamma1);
-Gamma2 = (1i*(SE2-SE2'));
-A2     = my_sqrt(Gamma2);
-y11    = -eye(4)+1i*A1*G11*A1;
-y12    = 1i*A1*G1N*A2;
-y21    = 1i*A2*GN1*A1;
-y22    = -eye(4)+1i*A2*GNN*A2;
-%y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
-% e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
-y11ee=y11(1:2*1     , 1:2*1);
-y12ee=y12(1:2*1     , 1:2*1);
-y11eh=y11(1:2*1     , 2*1+1:4*1);
-y12eh=y12(1:2*1     , 2*1+1:4*1);
+    [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
+    Gamma1 = (1i*(SE1-SE1'));
+    A1     = my_sqrt(Gamma1);
+    Gamma2 = (1i*(SE2-SE2'));
+    A2     = my_sqrt(Gamma2);
+    y11    = -eye(4)+1i*A1*G11*A1;
+    y12    = 1i*A1*G1N*A2;
+    y21    = 1i*A2*GN1*A1;
+    y22    = -eye(4)+1i*A2*GNN*A2;
[…]

### 2016-09-25 Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -1,4 +1,5 @@
 % ============= T vs E =========================================
+% TODO Find reference for this code
 clear
 cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
 

### 2016-09-25 Green function/1D QAHI Conductance/V_dl.m

@@ -1,5 +1,6 @@
 function y=V_dl(tc)
 % Vdl: The coupling between the sample and the lead. Vld=Vdl'
 % T: the coupling amplitude
+% TODO I think I should ask the R.A. about this.
 y=tc*diag([-1,-1,-1,-1]);
 end

### 2016-09-25 Green function/1D QAHI Conductance/V_sample.m

@@ -2,6 +2,14 @@ function y=V_sample(ts,tso)
 %V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
 %tso: SOC
 % electron and hole section are the same in topological insulator case.
+
+% ---- A exmaple output ------
+% [     -ts,     tso, zero1_3, zero1_4]
+% [    -tso,      ts, zero2_3, zero2_4]
+% [ zero3_1, zero3_2,     -ts,     tso]
+% [ zero4_1, zero4_2,    -tso,      ts]
+% -------------------------------
+% TODO find reference for this
 y=zeros(4);
 for i=1:1
     y(i,i)=-ts;

### 2016-09-25 Green function/1D QAHI Conductance/g11.m

@@ -1,19 +1,22 @@
 function y=g11(E,mu,ts,tso,w_energy_resol)
-    %g11 The submatrix of the Green function of the LEAD
-    % Obtained by N times of recursion
+%g11 The submatrix of the Green function of the LEAD
+% Obtained by N times of recursion
+% Checkpoint: I think I understand this code now.
+% For derivation pls refer: Appendix B of the dissertation
+    % TODO find reference for following line of code
     D=(E+1i*w_energy_resol)*eye(4)-H_lead(1,mu,ts,tso);
+    % TODO find reference for following line of code
     A=V_lead(ts,tso);
     B=A';
     d=D;
     for i=1:1000 %maximum number of recursive times
         % The following 4 lines of code seems to come from:
-        % Appendix B of the dissertation
         d1=d-A/D*B;
         D1=D-A/D*B-B/D*A;
         A1=A/D*A;
         B1=B/D*B;
         if max(max(abs(d1-d)))<1e-99
-            %i
+            % TODO 1e-99 might be too small...
             break
         end
         d=d1;
@@ -25,6 +28,7 @@ function y=g11(E,mu,ts,tso,w_energy_resol)
 end
 
 function y=H_lead(L,mu,ts,tso)
+% TODO I should find reference for this.
     y=zeros(4*L);
     Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
     condition=1.0; % =1 for spin independent hoping ts
@@ -40,6 +44,9 @@ function y=H_lead(L,mu,ts,tso)
     %y(i+2*L,i+3*L)=-I*m_y;
     %y(i+3*L,i+2*L)=I*m_y;
     %=====================================================================
+    % TODO what is the point of the following line? It is never used in
+    % actually usage.
+    % TODO Also, the variable I is not defined!
     for i=1:L-1
         y(i,i)         = Gamma-mu;
         y(i+L,i+L)     = -Gamma-mu;
@@ -99,8 +106,14 @@ function y=H_lead(L,mu,ts,tso)
 end
 
 function y=V_lead(ts,tso)
-    %V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
-    %tso: SOC
+%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
+%tso: SOC
+% TODO I should find reference for this.
[…]

### 2016-09-27 Complex Geometry - index/misc/complex geometry-misc.tex
Yesterday's note for class about group theory. And new complex geometry notes.

@@
             \mathrm{det_\mathbb{R}}  (\mathrm{det_\mathbb{C}}(A))
-            = |\mathrm{det_\mathbb{C}}(A) |^2 \geq 0
+            = \mathrm{det}_\mathbb{R}(aI+bJ)
+            =\mathrm{det}\left(\begin{array}{cc}
+                    a & -b\\
+                    b & a\\
+            \end{array}\right) \geq 0
         \end{align*}
@@
 
-    \subsection{Lifting Property}
-    \label{sec:Lifting-Property}
+    \subsection{Fibration}
+    \label{sec:Fibration}
     \paragraph{Lift of morphisms}
@@
 
+    \begin{defi}[Homotopy lifting property]
+    \nomenclature{Homotopy lifting property}{\nomrefpage.}
+    Let $C$ be a category with \textbf{products} and with \textbf{interval
+    object} $I$. A morphism $E\to B$ has the homotopy lifting property if it
+    has the right lifting property w.r.t all morphisms of the form
+    $(\text{Id},0):Y \to Y\times I$.
+    \end{defi}
+    $$ \xymatrix{
+        Y\ar[r]^f\ar[d]                 & E\ar[d]^p \\
+        Y\times I\ar[r]^F\ar[ru]^\sigma & B
+    }$$
+    Note: the term \textbf{products} and \textbf{interval object} mentioned
+    above are category analogy of cartisian products and unit interval $[0,1]$
+    in our daily mathematics. Since I will be concentrated in the case of a
+    topological space, I will simply regard them just as topological products
+    and the unit interval.
+
+    \paragraph{Fibrations}
+    \begin{defi}[Hurewicz fibration]
+    \nomenclature{Hurewicz fibration}{\nomrefpage.}
+        A map $p$ is called a Hurewicz fibration if it satisfies the homotopy
+        lifting property w.r.t to all spaces $X$.
+    \end{defi}
+    \begin{defi}[Serre fibration]
+    \nomenclature{Serre fibration}{\nomrefpage.}
+        A map $p$ is called a Serre fibration if it satisfies the homotopy
+        lifting property w.r.t to all discs $X$.
+    \end{defi}
+    Notes: by discs, I think he means closed discs, or closed balls, because he
+    also mentioned "equivalently" closed cubes.
+
+    Ref \cite{nlab-homotopy-lifting-property}.
     % Resources: https://ncatlab.org/nlab/show/fibration
@@
     \bibitem{nlab-lift}\href{https://ncatlab.org/nlab/show/lift}{nLab Lift}
+    \bibitem{nlab-homotopy-lifting-property}\href{https://ncatlab.org/nlab/show/homotopy+lifting+property}{nLab Homotopy lifting property}, \href{https://ncatlab.org/nlab/show/cartesian+product}{nLab Cartesian product}, \href{https://ncatlab.org/nlab/show/interval+object}{nLab Interval object}.
 \end{thebibliography}

### 2016-09-27 Group Theory in Physics/group theory in physics.tex
New notes about adjoint operator of antilinear operators.
1. Begin really tackling the first problem in Complex Geometry. 2. Editing some green function code. 3. New course notes about Advanced Quantum Mechanics.
Yesterday's note for class about group theory. And new complex geometry notes.

@@
         \begin{align*}
-            R^{i}_{j}\Gamma^{j}_{k}=\Gamma^{i}_{j} R^{j}_k
+            \sum_j R^{i}_{j}\Gamma^{j}_{k}=\sum_j\Gamma^{i}_{j} R^{j}_k
             \Longrightarrow
@@
         \begin{align}
-            R^\dagger = \Omega^{-1} A^\dagger \Omega
+            R = \Omega^{-1} A^\dagger \Omega
         \end{align}
@@
 
+\section{20160926}
+\label{sec:20160926}
+
+He first introduces some important matrices:
+
+\paragraph{Unitary matrix} Eigenvalues of Unitary matrices has modulus $1$,
+i.e. $|\lambda|=1$. This can be proved directly. Also, Unitary matrices are unitarily diagonalizable. This is a result of the following Spectral Theorem:
+\begin{thm}[Spectral Theorem]
+    A matrix $A$, which is normal (i.e. $A^\dagger A= AA^\dagger$), if and only if it is unitarily diagonalizable.
+\end{thm}
+\begin{proof}
+    If $A$ is normal, then by Schur decomposition, we can write
+    $A=UTU^\dagger$, here $U$ is unitary and $T$ is upper-triangular. 
+    Using the condition of being normal, one can show directly that $T$ 
+    is in fact also normal. Now we show that any triangular matrix that 
+    is normal must be diagonal. Observe that we have 
+    $\braket{e_i,T^\dagger T e_i}=\braket{e_i,TT^\dagger e_i}$, 
+    i.e. $\braket{T^\dagger e_i, T^\dagger e_i}=\braket{T e_i, T e_i}$. 
+    This is sayin g that the norm of the first column of $A^\dagger$ 
+    is equal to the norm of the first column of $A$. Obviously 
+    $A$ has to be diagonal.
+
+    The converse is obvious.
+\end{proof}
+
+Also, unitary matrix's eigenvector corresponding to different eigenvalues 
+are orthogonal. This is a direct result of fact mentioned above.
+
+\paragraph{Hermitian matrices} They have real eigenvalues and orthogonal
+eigenvectors (proof omitted). Also, if $\text{det}(R^\dagger R)\neq 0$,
+then $R^\dagger R >0$, i.e. it is positive-definite.
+
+\textbf{This is wong:} An example is that
+the matrix $\Omega$ introduced in the previous lecture has
+$\text{det}(\Omega^\dagger \Omega)=\text{det}(\Omega)$, hence
+$\text{det}(\Omega)=1$ (it cannot be $0$), hence it is positive definite.
+
+\textbf{Actually} 
+$\text{det}(\Omega^\dagger \Omega)\neq\text{det}(\Omega)$, because
+\begin{align}
+    \sum_\rho \ket{e_\rho}\bra{e_\rho} \neq 1 \text{(unless the basis is
+        orthonormal)}
+    % TODO think about this in depth
+\end{align}
+Therefore we need anthoer argument for $\Omega$ being positive-definite.
+It is provided in page 11 of \cite{book}.
+
+\paragraph{Orthogonal matrix} For an orthogonal matrix over $\mathbb{C}$,
+it is quite troublesome. For example, if $Ra=\lambda a$ and
+$\lambda \neq \pm 1$, then we have $a^T a=0$, which is quite bad because
+this force $a$ to have complex components.
+
+\paragraph{Orthogonal matrix over $\mathbb{R}$} In this case, we have
+similar result. But it is easy to show that for an orthogonal matrix
+$R$ having only real elements, then its eigenvalues $\lambda= \pm 1$.
+
+Then he proceeds to direct product.
+\paragraph{Direct product} and also the Kronecker Product of two
+matrices. Properties (let $T=R\otimes S$):
+\begin{enumerate}
+    \item $\mathrm{dim}T = \mathrm{dim}R \times \mathrm{dim}S$
+    \item $\mathrm{tr}(T)=\mathrm{tr}(R)\mathrm{tr}(S)$
+    \item $\otimes$ commutes with the operation of inverse, transpose,
+        and transpose conjugation.
+    \item \begin{align}
+            \frac{d}{d\alpha} (R(\alpha)\otimes S(\alpha)) =
+            R'(\alpha)\otimes S(\alpha) + R(\alpha)\otimes S'(\alpha)
+    \end{align}
+    \item when the dimentions are the same:
+        \begin{enumerate}
+            \item 
+            $(R_1\otimes S_1)(R_2\otimes S_2) = (R_1R_2)\otimes (S_1S_2)$
+        \end{enumerate}
+\end{enumerate}
+
+Finally we arrived in the group theory.
+\paragraph{Symmetry examples} Dipole transition. 
+$\braket{\phi_f|\hat{P}|\phi_i}$, must happen when the parity of $\phi_i$
+and $\phi_f$ is of opposite parity. (pp.18 of \cite{book})
+
+\paragraph{Group}
+\begin{defi}[Group]
+\nomenclature{Group}{\nomrefpage.}
+    Omitted.
+\end{defi}
+Some basic properties (Omitted).
+\begin{defi}[Abel Group]
+\nomenclature{Abel Group}{\nomrefpage.}
+    Omitted.
+\end{defi}
+\begin{defi}[Cardinality of group $\# A$]
+\nomenclature{Cardinality of group $#$}{\nomrefpage.}
+    Omitted.
+\end{defi}
+
+\paragraph{Multiplication table}
+
+Facts: group of order $1,2,$ and $3$ are unique up to an isomorphism.
+
+\begin{defi}[Cyclic group, generators]
+\nomenclature{Cyclic group, generators}{\nomrefpage.}
+    Omitted.
+\end{defi}
+
+\begin{defi}[$C_N,\bar{C}_N$]
+\nomenclature{$C_N,\bar{C}_N$}{\nomrefpage.}
+    $\bar{C}_N=C_N*\sigma$
+\end{defi}
 \section{Anchor}
@@
     %\bibitem{book} 
-    \bibitem{book_1} Zhongqi Ma, Group Theory in Physics
+    \bibitem{book} Zhongqi Ma, Group Theory in Physics
     \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}

### 2016-09-29 Complex Geometry - index/misc/complex geometry-misc.tex
Correcting error in complex geometry-misc. Initiating new notes on a conference: connecting few and many body pictures of FQH.

@@
 In exercise 1.2.1, it says that the set of all compatible almost complex
-structures on a euclidean space of dimension $2n$, is two copies of $S^2$.
+structures on a euclidean space of dimension $4$, is two copies of $S^2$.
 
@@
 
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
         An almost-complex structure is a matrix $J$ such that $J^2 = -I$
@@
         to the almost-complex structure $AJA^{-1}.$
+
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
 
@@
             $\phi(i B)= \phi(i)\phi(B)$.
-            for any $B\in \mathrm{GL}(n,\mathbb{C}$. This shows also
+            for any $B\in \mathrm{GL}(n,\mathbb{C})$. This also shows 
             $BJB^{-1}=J$, since $iB=Bi$.
@@
         for any $n$. The questioner gives the intuition for this fact:
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
         \begin{quote}
@@
         \end{quote}
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
 
         Someone answered that question:
+
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
 
@@
         \end{quote}
+        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
 
         However, this proof is not complete because, to build the proof from 
-        $\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument, that
-        any element in $\mathrm{GL}(V\oplus V)$ is in the image of
+        $\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument,
+        that any element in $\mathrm{GL}(V\oplus V)$ is in the image of
         $\mathrm{GL}(V)\times \mathrm{GL}(V')$, which is not the case.

### 2016-09-29 Notes of Connecting Few-body and Many-body Pictures of Fractional Quantum Hall Physics/Notes of Connect Few-Many FQH.tex
Correcting error in complex geometry-misc. Initiating new notes on a conference: connecting few and many body pictures of FQH.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{bbm} % for numbers within mathbb
\usepackage{mathrsfs} % For \mathscr{ABC}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

\usepackage[all]{xy} % For drawing diagrams with arrows
\title{Notes of Connecting Few-body and Many-body Pictures of Fractional Quantum Hall Physics}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    YouTube link\cite{utube-lecture}.
    Note that, although I have the video on hand, the lecturers are
    speaking somehow too fast and it would be too time-consuming to replay
    these lectures. So the content is..... quite unorgnised and bare.
    Therefore, this note could be viewed just as a collection of key
    words.
}
\tableofcontents
\section{Using Optical Emission to Study Competing Phase in the Second
Landau Level}
\label{sec:Using-Optical-Emission-to-Study-Competing-Phase-in-the-Second-Landau-Level}

By:

Antonio Levy, Aron Pinczuk, Yuliya Kuznetsova (Columbia University),
Ursula Wurstbauer (Technische Uni. Munchen), Ken. W. West, Loren N.
Pfeiffer (Princeton), Michael J. Manfra, Geoff C. Gardner, John D. Watson
(Purdue University).

\paragraph{Overview} Second Landau Level displays
\begin{enumerate}
    \item FQHS
    \item Ordered phases (partially). RIQHE $ \overset{from}{\Leftarrow}$
        Electron stalids.
    \item Competition \& Coexistance

        Anisotropic FQHS arise from coorelation when anisotropic
        $\overset{from}{\Leftarrow}$ magneti field
\end{enumerate}
\paragraph{Advanage of Optial}
\begin{enumerate}
    \item Direct probes bulk
    \item Distinguish between charge and spin modes
\end{enumerate}
\paragraph{Sample} Omitted.
\paragraph{RRS}
$ $ % Go to the next line.

$ \xymatrix{
    \text{light}\ar[r] &
    \bullet\ar@/^/[r]^{\text{quasiparticle}}
                \ar@/_/@{<.}[r]_{\text{quasihole}} & 
    \bullet & \text{scattered photon}
}$

$\bullet$ Easy to probe Single Partical excitation and collective
excitation.

... (Skipped)

\section{Hyperspherical Adiabatic Approximation}
\label{sec:Hyperspherical-adiabatic-Approximation}

By: Rachel Wooten (Purdue University)

\paragraph{Outline}
\begin{enumerate}
    \item QHS
    \item Motivation
    \item Hyperspherical adiabatic approximation (\textbf{HAA})
    \item The role of degeneracy
    \item Hyperradial breathing mode
    \item Results and Discussion
\end{enumerate}

\paragraph{QHS}
\begin{table}[H]
    \caption{Two Schemes}
    \centering
    \begin{tabular}{|ccc|}
        \hline
        Conventional     & $\approx$ & Neutral Atom gass \\
        \hline
        2D Landau levels &           & 2D Rotation($\Omega$) \\
        $\omega_c$       &           & $\omega= 2\Omega$ \\
        \hline
    \end{tabular}
\end{table}

(Other schemes are also available, not treated).

\paragraph{Motivation}
\begin{itemize}
    \item QHS: prototype of \textit{Strongly correlated systems}
    \item Nature of few-body states
    \item insights from collectively coordinates
    \item use ... ?
\end{itemize}

\paragraph{Few body, adiabatic hypershperical approach\textbf{(AHA)}}

\begin{itemize}
    \item intrinsic collective coordinates
    \item length scale $R$ $\overset{\text{from}}{ \Leftarrow}$ geometry
    \item $E$ potential $ \Leftarrow$ length scale
    \item introduce Grand Angular momentum $K$ - quantum number
\end{itemize}

\paragraph{AHA background} Joe Macek, 1968 JPB.

\paragraph{Scheme} Sch-Ep $\overset{recast}{ \Rightarrow}$ relative
coordinates $ \overset{diagonalize}{ \Rightarrow}$ solve.

\paragraph{Hyperspherical Coordinates} $ $

$2N-2$ Jacobi coordinates $\Rightarrow$ $2N-3$ angular coordinates
$\Omega$ + 1 length coordinates Hyperradial $R$.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/rachel-wooten-purdue.png}
\end{figure}

\paragraph{Hyperradius}
$$\rho = \left( \frac{\pi\mu\braket{R^2}}{N(N-1)} \right)$$
$$\mathscr{H}_\text{rel} = (R, \Omega, \cdots)
    +\text{Colomb} V(R)=\frac{1}{R}
    +\text{Polarized dipoles}V(R)=\frac{1}{R^3}
$$
\paragraph{AHA (Non-interacting case)} Omitted.
\paragraph{AHA (Interacting case)}$ $

Treat $R$ as an adiabatic parameter.

Interaction $\overset{\text{introduct}}{\Rightarrow}$ degeneracies
\paragraph{Accuracy check} Omitted.
\paragraph{Exceptional degeneracy}

\section{? (Wick Haxton)}
\label{sec:Wick-Haxton}

(1995) Algebraic classification of general 4 fermion problem (Joe
Ginocchio) $\Rightarrow$ has FQHE implications

Jain \& Laughlin work (numerically succesful)

(No audio available for this lecture recording!, Skipped)

\section{Perspectives on the half-fill Landau Level}
\label{sec:Perspectives-on-the-half-fill-Landau-Level}

By B.I. Halperin, N. Copper, Chong Wong, Adey Stern.

\paragraph{Question}: What ahppens to half-filled Landau Level when there
is \textbf{NO} magnetic field.

\paragraph{Motivation}
\begin{itemize}
    \item New research on half-filled Landau level
    \item Describe system by "Dirac Fermion" is simpler, generated
        different theories $\Rightarrow$ doubt whether they are
        equivalent.
    \item Particle-hole symmetry in explicit in "Dirac Fermion", not
        explicit in HLR framwork.
\end{itemize}
\paragraph{Physical Setup} $ $

Half-filled Landau level: in a semiconductor.
$$ H_0 = \sum_i \frac{ |P_i - A(r_i)|^2}{2m} + V_2 \text{(interactions)}
$$
Units: $e=\hbar=1$.
\paragraph{PH Symmetry} $ $

\begin{itemize}
    \item $m\to 0$, e-e interactions are fixed -> exact PH symmetry
    \item For $v=1/2$, PHS requires that $\sigma_{xy}(\sigma)=(1/2) e^2/h$
\end{itemize}

\paragraph{HLR Approach}
(Halperin, Lee, Read. PRB 1993)

\begin{itemize}
    \item Singular gauge transformation $\Rightarrow$ Chern-Simons Gauge
        Field
    \item Transformed Hamiltonian will have fermion terms, interactions,
        gauge field (chern-simons interaction in it). Also the curl of a
        fact vector is constrained.
\end{itemize}
\paragraph{Antecednets}
\begin{itemize}
    \item Fractional Quantized Hall states by Jain; Lopez and Fradkin;
        others.
    \item Simultaneous work by Kalmeyer and Zhang had some features of
        HLR.
\end{itemize}

\paragraph{HLR Hypothesis}
\begin{itemize}
    \item Do mean field theory on this problem: the ground state and low
        energy properties of quantum hall system at $v=1/2$. And use
        perturbation theory and take into account of fluctuations in gauge
        field and Coulomb interactions
    \item ...
\end{itemize}
\paragraph{HLR consequences}
\begin{itemize}
    \item with $1/r$ interactions, the ground state is a "marginal fermi
        liquid". With mass diverges $log$ at fermi serface, eue to
        infrared divergence.
    \item assume interactions that fall off slower than $1/r$.
\end{itemize}
\paragraph{HLR-RPA predications}
\begin{itemize}
    \item ground state at $v=1/2$ should be compressible
    \item energy gaps, FQH states, occur at Jain fractions $v=p/(2p+2)$.
    \item relative sizes of energy gaps close to $1/2$
    \item transport in absence of impurities: DC hall conductance
    \item Longitudianl conductivity at finite $q,\omega\to 0$:
        $$\sigma_{xx}(q)=q/(8\pi k_f) $$
        in the presence impurities: formula holds for $q>l_{cf}$.
\end{itemize}

Related work: Kalmeyer \& Zhang.

\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    \bibitem{utube-lecture}\url{https://www.youtube.com/playlist?list=PLCoSh1h28ieLIaD-HGi5aUQzunOTtxHTC}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-29 Notes of Connecting Few-body and Many-body Pictures of Fractional Quantum Hall Physics/Notes of Connect Few-Many FQH.tex
Almost done with the conference: connecting few-many pictures of FQH

@@
 \abstract{
-    YouTube link\cite{utube-lecture}.
+    I wrote this with the aim of finding some interesting topics for
+    research. This conference has its lecture recorded and published
+    in YouTube (link\cite{utube-lecture}).
     Note that, although I have the video on hand, the lecturers are
     speaking somehow too fast and it would be too time-consuming to replay
-    these lectures. So the content is..... quite unorgnised and bare.
-    Therefore, this note could be viewed just as a collection of key
-    words.
+    these lectures. So the content is..... quite un-organised and bare.
+    In addition, after typing for several hours, my fingers are getting
+    tired. So... I could be very lazy.
+
+    Therefore, this note could be viewed just as a collection of keywords.
 }
@@
 \end{itemize}
+\paragraph{HLR-RPA problems}
+\begin{itemize}
+    \item most important error: ignores renormalization of fermian
+        effective mass. gives wrong energy scale, wrong value for specific
+        heat at $1/2$, wrong scale for FQHE gaps.
+    \item correct effective mass is set by the e-e interaction, not by the
+        bare mass, when $m$ is small.
+\end{itemize}
+\paragraph{Naive renormalizaed RPA}
+\begin{itemize}
+    \item simply replace $m$ by $m^*$.
+    \item however: iolates Kohn's theorem for $\omega=\neq 0$.
+    \item and many many....
+\end{itemize}
+\paragraph{Landau interaction parameters}
+\begin{itemize}
+    \item energy cost of a ditortion of fermi surface, independent of
+        position.
+    \item (several formulae)
+\end{itemize}
+\paragraph{DC conductitivity in presence of impurties}
+\begin{itemize}
+    \item Kivelson (1997): naive HLR leads to deviations
+    \item ... continued of problems of HLR-RPA
+\end{itemize}
+\paragraph{Side-jump contribution} ......
+\paragraph{Commensurability oscillations: $v\neq 1/2$, with finite $q$}
+and this result is symmetric w.r.t $\Delta B$, different from HLR.
 
-Related work: Kalmeyer \& Zhang.
+\section{Composite fermi liquids in the lowest Landau level}
+\label{sec:Composite-fermi-liquids-in-the-lowest-Landau-level}
+By: T. Senthil (MIT), Chong Wang (MIT -> Harvord)
 
+\paragraph{2d electrons in the QH regime}
+\footnote{This is the first time that I find a correct usage of the word
+"regime", without suspicion that it should be replaced by "region".}.
+\paragraph{Unquantized region}
+
+\begin{itemize}
+    \item Incompressible FQHE states: fill certain rational fractions of a
+        Landau level
+    \item Large degeneracy is split by e-e interactions to give a gapped
+        ground state
+    \item compressible metallic states: "unquantized
+        quantum Hall effect"
+    \item \textbf{How do interactions manage to produce a metal}
+\end{itemize}
+
+\paragraph{Standard theory} HLR theory, idea of composite fermions
+
+\paragraph{Some experimental verification of composite fermions}
+
+\paragraph{Unsatisfactory aspects of the theory}
+\begin{itemize}
+    \item HLR not suited to projecting to Lowest Landau Level (LLL)
+    \item mean field effective mass = bare electron mass
+    \item LLL limit: take $m$ to zero: what happens?
+    \item LLL theory has an extra symmetry that HLR is blind to. the PH
+        symmetry.
+\end{itemize}
+\paragraph{PH symmetry: formal implementation} ways to exam the
+particle-hole symmetry.
+
+Numerical work: shows metallic ground state $v=1/2$ preserves the C
+symmetry.
+
+HLR theory: not in LLL, therefore it does not address the problem of p/h
+within its scope.
+
+\paragraph{Related theoretical problems}
+\begin{itemize}
+    \item electrons at $v=1/4,1/6,\cdots$ No p/h. But issue of nature of a
+        LLL theory remains
+    \item useful to consider problem of bosons in the quantum Hall regime.
+        Fate of such a state in LLL. For bosons, microscopically there is
+        no p/h.
+\end{itemize}
+\paragraph{Progress old and new}
+\begin{itemize}
+    \item Bosons at $v=1$: LLL theory of metallic Composite Fermi Liquid
+        (\textbf{CFL}) state (Read 1998)
+    \item PH symmetric theory for electronc CFL at $v=1/2$.
+        by Son (2016): Is the composite fermion at $v=1/2$ a dirac
+        particle?
+        \begin{itemize}
+            \item field theoretic justification: connection to the surface
+                of 3d topological insulators (C. Wang. TS ...)
+            \item Simple physical picture of the PH symmetric composite
+                fermion (C. Wang. ...)
+            \item Numerical calculations (...)
+        \end{itemize}
+\end{itemize}
+\paragraph{Talk outline}
+\begin{itemize}
+    \item Understanding the p/h symmetric composite fermi liquid of
+        electrons at $v=1/2$ (physical picture, field theoretic
+        derivation)
+    \item Composite Fermi Liquid of bosons at $v=1$:
+        \begin{itemize}
+            \item review of Read's Lowest Landau Level theory
+            \item comparison with electrons at $v=1/2$.
+        \end{itemize}
+    \item Composite Fermi Liquids in LLL at generic $v$:
+\end{itemize}
+\paragraph{Old physical picture Composite Fermion in LLL}
+LLL wave function: (Rezayi-Read 94)
+$$ \psi= P_{LLL} \mathrm{det}(e^{ik_i r_j})\prod_{i<j} (z_i-z_j)^2 $$
+Composite fermion = electron bound to $4\pi$-vortex which has charge
+depletion $-e$. They are neutral but carry a dipole moment.
+
+Howeer this picture misses some physics and further is not PH symmetric.
+
+\paragraph{New picture of composite fermion in LLL}
+by Wang. TS.
+$$\psi=\prod_{i<j} (z_i-z_j)f(z_1,\cdots,z_N)$$
+where $f$ is symmetric.
+
+One vortex is exactly on electron due to Pauli. Each vortex has charge
+$-e/2$ => single vortex exactly on electron has charge $+e/2$ and the
+displaced vortex has chare $-e/2$.
+
+\paragraph{Internal structure of composite fermion in LLL}
+Two ends have mutual statistics of $\pi$. Solve Quantum Mechanics of just
+relative motion. $\cdots$
+
+\paragraph{1/2-filled LL and correlated 3 dimentional Topological
+Insulator surface} Derivation of and more
+insidght into PH symmetric composite fermi liquid theory.
+
+Skipped.
+
+\section{Nematic order in fractional quantum Hall liquids}
+\label{sec:Nematic-order-in-fractional-quantum-Hall-liquids}
+By Joseph Maciejko (University of Alberta).
+
+\paragraph{FQH nematic}
+\begin{itemize}
+    \item A proposed novel state of matter where (topological) FQH order
+        coexists with (conventional) nematic order
+    \item Intrinsic topological order (blobal) is insensitive to symmetry
+        considerations (local); Can imaagine many possible broken
+        symmetries.
+    \item ...
+\end{itemize}
+\paragraph{FQH nematic at $v=7/3$} Xia et al., Nat. Phys. 2011.
+
+\paragraph{FQH nematic at $v=5/2$} Samkharadze et al., Nat. Phys. 2015.
+
+No symmetry breaking field, but not clear if there is a Hall plateau or
+not
+
+\paragraph{FQH nematic at $v=5/2$} Liu et al., PRB 2013 No Hall plateu
+reported, but longitudinal resistances appear to vanish as $T\to 0$.
+
+\paragraph{Disclaimer}
+\begin{itemize}
+    \item Some of these experiements may or may not be explained by a FQH
+        nematic
+    \item will focus on FQH nematic
+    \item theoretical: Haldane's geometrical perspective on the FQHE.
+\end{itemize}
+\paragraph{FQH isotropic-nematic transition}
+\begin{itemize}
+    \item Main questions
+        \begin{itemize} 
+            \item Generic mechanism for a transition from
+            isoropic FQHE to FQH nematic 
+            \item effective field theory of
+            the transition?  
+            \item can we realize this transition in a
+            microscopic model of interacting electrons?  
+        \end{itemize}
+    \item isotropic FQH liquid is naturally proximate to a FQH nematic
+    \item Girvin-MacDonald-Platzman (GMP) mode in the $q=0$ limit
+        corresponds to gapped nematic fluctuations wich condense at a
+        putaative isotropic-nematic QCP (JM et al., PRB 2013).
+\end{itemize}
+
+\paragraph{GMP mode} "Intra-LL" neutral collective mode in the FQHE (by
+contrast with "inter-LL" Kohn/magnetoplasmon mode). G. M. P., Prl 1985.
+
+$q=0$ limit of GMP mode has quadrupolar symmetry
+\paragraph{GMP mode as a quadrupole}
+
+\begin{itemize}
+    \item numerical studies $\cdots \cdots$.
+    \item heuristic argument.
+\end{itemize}
+\paragraph{geometrical theory of the FQHE}
+\begin{itemize}
+    \item $q=0$ limit of the GMP = fluctuating intrinsic "metric"
+        $g_{ab}(r,t)$ (Haldane PRL 2011; ....)
+    \item Metric is unimodular ($\mathrm{det} g = 1$): set of ellipses of
+        fixed area, i.e., quedrupolar deformations of the circle.
+\end{itemize}
+....
+\paragraph{Intrinsic metric and nematicity}
+\begin{itemize}
+    \item Unimodular metric equivalent to nematic order parameter
+        $Q_{ab}$.
+\end{itemize}
+$$ g = \mathrm{exp}Q$$
+$\cdots$
+
+\paragraph{FQH isotropic-nematic transition} $\cdots$
+Skipped.
+
+\section{Rotational properties of multi-species Bose gases}
+\label{sec:Rotational-properties-of-multi-species-Bose-gases}
+
+By Suasanne Viefers, University of Osio.
+\marginpar{A good one for those not familiar with this field.}
+\paragraph{Outline}
+\begin{itemize}
+    \item Review of rotating bosons in the LLL quantum Hall connection
+    \item Two- and three- species Bose gases
+    \item Composite fermion approach: results and puzzles
+    \item outlook
+\end{itemize}
+
+\paragraph{Rotating Bose condensates}
+\begin{itemize}
+    \item 1995: first atomic Bose condensate
+    \item 1999: first vortex in rotating BEC (JILA, Paris)
+    \item 2004: Abrikosov lattice in Lowest Landau Level (200 vortices)
+
+        Increasing rotation: cloud flattens out, density decreases, weaker
+        interaction, lowest Landau level.
+
+        Eventually: Vortex lattice predicted to melt, so system enters
+        quantum Hall regime
+    \item Recent reports of small systems ($N<10$) reaching FQH regime in
+        novel type of optical lattice with local rotation of each site.
+\end{itemize}
+
+\paragraph{LLL wave functions}
+\begin{itemize}
+    \item Historical motivation: Quantum Hall effect
+    \item 2-dimensional electron gas in a strong perpendicular magnetic
+        field at low T
+    \item Electrons residing mainly in the LLL
+\end{itemize}
+
+Construction of explicit trial wave function by various schemes (in
+partular) Laughlin, hierarchy/composite fermions) has proven very
+successful in exploring QH physics. Not exact, but o capture essential
+properties (topological order).
+
+\paragraph{Bose condensate in the LLL}
+Mathematical equivalence in 2D between rotation (harmonic oscillator) and
+perpendicular magnetic field.
+
+In the absence of interaction: Lowest N-body state with give $L$ is highly
+degenerate. The interaction lifts this degeneracy and selects the lowest
+("yrast") state. (Yrast= "most dizzy"). \footnote{Here is one anecdote.}
+
+\begin{itemize}
+    \item N-particle state: symmetric homogeneous polynomials.
+    \item Total angular momentum = deree of polynomial
+\end{itemize}
+
+Composite fermion scheme modified and shown to work successfully for the
+entire yrast line, including low angular momenta.
+
+\paragraph{Multi-component systems} ...
+\paragraph{Two component systems: QH regime}
+\begin{itemize}
+    \item Two species Bose gases in the quantum Hall regime: several
+        theoretical studies.
+    \item Proposed (under discussion): NASS state at $v=4/3$.
+    \item Fundamentl quasiholes: charge $e/3$ non-Abelian anyons
+    \item Bosonic IQH states with topologically protected edge states.
+\end{itemize}
+
+\paragraph{Two-component systems: Slow rotation}
+\begin{itemize}
+    \item Study 2-species Bose gas in LLL with homogeneous contact
+        interaction.
+    \item Recent work identified a class analytically exact many-body
+        eigenstates for low angular momenta
+    \item Beyond papenbrock? Study low $L$ regime in terms of composite
+        fermions, exploiting (pesudo) spin analogy for homogeneous
+        interaction. Not a priori expected to work
+    \item Choice of Slater determinants in general not unique, i.e.
+        several $CF$ candidates -- may or may not be lineary dependent.
+\end{itemize}
+\paragraph{Simple example}...
+
+\paragraph{Selection criteria for Slaters}...
+\paragraph{Full CF diagonalization}
+\paragraph{Sample states}...
+\paragraph{Puzzles: linear dependencies}
+
+\begin{itemize}
+    \item the number of apparent CF condidates is generally too large,
+        after projection.
+    \item This is true even when restricting to simple states.
+    \item Similar problems were recently discussed in the context of
+        higher bands for electronic FQH states. without fully succeeding
+        to reveal the underlying mathematical structures
+    \item ...
+    \item Wish: identify linear dependdencies before projection (for
+        numerical concern).
+\end{itemize}
+\paragraph{Linear dependencies (simple states): Ingredients} ...
+\begin{itemize}
+    \item More direct understanding of linear dependencies in the CF
+        formalism?
+    \item Go beyond homogeneous interaction, study vortex structures,
+        anyonic quasiparticles in QH regime
+    \item Future experiments in this regime?
+    \item Spin-I
+    \item NORDITA program "topological phases in cold atom systems" Aug
+        2017.
+\end{itemize}
+
+\section{Artificial gauge fields with ultracold bosonic atoms in optical
+lattices}
+\label{sec:Artificial-gauge-fields-with-ultracold-bosonic-atoms-in-optical
+lattices}
+By Monika Aidelsburger (LMU Munich, MP institute of Quantum Optics).
+
+\paragraph{Outline}
+\begin{itemize}
+    \item Realization of artificial magnetic fields using laser-assisted
+        tunneling
+    \item Experimental results
+    \item Chern-number measurement
+    \item Summary and prospects
+\end{itemize}
+Skipped. May contain a good introduction to topological Insulator
+concepts. But I have really limited amount of time now.
+
+\section{Generalized Topological Forces}
+\label{sec:Generalized-Topological-Forces}
+By I.B. Spielman (JQI - Maryland).
+
+\paragraph{Topology in CMP}
+How the underlying topology gives rise to the forces.
+\paragraph{Outline}
+\begin{itemize}
+    \item Geometric charge pumping
+
+        From abelian Berry's curvature related to the 1st chern
+        number/class.
+    \item 2nd Chern number/class
+
+        From non-abelian Berry's curvature.
+\end{itemize}
+\paragraph{Pumps throughout history} From archimedean to NIST single
+electron pump.
+
+\paragraph{Questions from simple 1D lattice}
+A force "just" causes Bloch oscillations.
+\begin{itemize}
+    \item Gives motion in topological/geometric pumps 
+    \item Deflects trajectories in Bloch oscillations
+    \item Force underlying quantum Hall effect
+\end{itemize}
+
+\paragraph{Topology in parameter space}
+\paragraph{Monopole - topological defects}
+
+He seems to want to create some concepts of force in CMP system. And I
+decided to skip him for the moment.
 \section{Anchor}

### 2016-10-05 Draft/draft.tex
Daily update. Not too much new things.
New drafts: something calculation about spin operators. Plans on new notes about TR symmetry for condensed matter physics.

@@
 
+\subsection{About \texorpdfstring{$e^{-i\pi S_y/\hbar}$}{}}
+\label{sec:About-exp(-i*pi S_y/hbar)}
+
+    (Related: Sakurai's Q.M., about (4.4.65)).
+
+    Since 
+    $$S_y=\frac{\hbar}{2}\sigma_y=\frac{\hbar}{2}
+        \left( \begin{array}{cc}
+         0 & -i \\
+         i & 0 \\
+        \end{array} \right)$$
+    It is easy to check that $\sigma_y^2 = \mathbb{I}$. So:
+    \begin{align*}
+        e^{-i\phi S_y/\hbar}=
+        e^{-i\frac{\phi}{2}\sigma_y}&=\sum_{n=0}^{\infty}
+         \frac{(-i\frac{\phi}{2})^n(\sigma_y)^n}{n!}\nonumber\\
+         &=\sum_{\text{odd }n}-\frac{i(\frac{\phi}{2})^n}{n!}\sigma_y
+           + \sum_{\text{even }n}\frac{(i\frac{\phi}{2})^n}{n!}\mathbb{I}
+    \end{align*}
+    Using the taylor expansions:
+    \begin{align}
+        \sinh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n+1}}{(2n+1)!}
+        \text{ (odd terms)}\\
+        \cosh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n}}{(2n)!}
+        \text{ (even terms)}
+    \end{align}
+    We see that:
+    \begin{align}
+        e^{-i\phi S_y/\hbar}=e^{-i\frac{\phi}{2}\sigma_y}&=
+         - \sigma_y\sinh{i\frac{\phi}{2}}+ \mathbb{I}\cosh{i\frac{\phi}{2}}
+         \nonumber\\
+         &=
+         -i\sigma_y \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+         &=-i\frac{2}{\hbar}S_y\sin{\frac{\phi}{2}}
+            +\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+         &=\left( \begin{array}{cc}
+            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
+            \sin (\frac{\phi }{2}) & \cos (\frac{\phi }{2}) \\
+         \end{array}\right)
+    \end{align}
+    So
+    $$e^{-i\pi S_y/\hbar} = -i\frac{2S_y}{\hbar}$$
+    By exactly the same argument, or simply by the symmetry
+    ($x\leftrightarrow y$), we
+    have:
+    \begin{align}
+        e^{-i\phi S_x/\hbar}=e^{-i\frac{\phi}{2}\sigma_x}&=
+         -i\sigma_x \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+        &=-i\frac{2}{\hbar}S_x\sin{\frac{\phi}{2}}
+            +\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+        &=\left(\begin{array}{cc}
+            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
+            \sin (\frac{\phi }{2}) & \cos(\frac{\phi }{2}) \\
+         \end{array}\right)
+    \end{align}
+    Also, one can easily find that:
+    \begin{align}
+        e^{-i\phi S_z/\hbar}=e^{-i\frac{\phi}{2}\sigma_z}&=
+          \left(\begin{array}{cc}
+              e^{-i\frac{\phi }{2}} & 0 \\
+              0                     & e^{i\frac{\phi }{2}} \\
+         \end{array}\right)
+    \end{align}
+    Here a formula that encompass all the above relationship:
+    \begin{align}
+        \exp(\frac{-i\vec{\sigma}\cdot\hat{\vec{n}}\phi}{2})
+        =
+        \cos(\frac{\phi}{2})\mathbb{I}-i\vec\sigma\cdot\hat{\vec{n}}
+        \sin(\frac{\phi}{2})
+    \end{align}
+    where $\vec\sigma=(\sigma_x,\sigma_y,\sigma_z)$, and 
+    $\hat{\vec{n}}$ is any unit vector.
 \section{Miscellnaneous Notes}

### 2016-10-05 Notes about TR symmetry/Notes about TR symmetry.tex
New drafts: something calculation about spin operators. Plans on new notes about TR symmetry for condensed matter physics.

--- 2016-09-29 Notes of Connecting Few-body and Many-body Pictures of Fractional Quantum Hall Physics/Notes of Connect Few-Many FQH.tex
@@
 
-\usepackage[all]{xy} % For drawing diagrams with arrows
-\title{Notes of Connecting Few-body and Many-body Pictures of Fractional Quantum Hall Physics}
+% For drawing diagrams with arrows
+\usepackage[all]{xy}
+
+\title{Notes about TR Symmetry}
 \date{\today}
@@
 \abstract{
-    YouTube link\cite{utube-lecture}.
-    Note that, although I have the video on hand, the lecturers are
-    speaking somehow too fast and it would be too time-consuming to replay
-    these lectures. So the content is..... quite unorgnised and bare.
-    Therefore, this note could be viewed just as a collection of key
-    words.
+This is a note about TR symmetry, with its application in the theory of
+condensed matter physics. The two reference book are the classic by
+Sakurai \cite{sakurai}, and the other by Bernevig \cite{bernevig}.
 }
 \tableofcontents
-\section{Using Optical Emission to Study Competing Phase in the Second
-Landau Level}
-\label{sec:Using-Optical-Emission-to-Study-Competing-Phase-in-the-Second-Landau-Level}
 
-By:
-
-Antonio Levy, Aron Pinczuk, Yuliya Kuznetsova (Columbia University),
-Ursula Wurstbauer (Technische Uni. Munchen), Ken. W. West, Loren N.
-Pfeiffer (Princeton), Michael J. Manfra, Geoff C. Gardner, John D. Watson
-(Purdue University).
-
-\paragraph{Overview} Second Landau Level displays
+\section{Review of Spin theory}
+\label{sec:Review-of-Spin-theory}
+Outline:
 \begin{enumerate}
-    \item FQHS
-    \item Ordered phases (partially). RIQHE $ \overset{from}{\Leftarrow}$
-        Electron stalids.
-    \item Competition \& Coexistance
-
-        Anisotropic FQHS arise from coorelation when anisotropic
-        $\overset{from}{\Leftarrow}$ magneti field
-\end{enumerate}
-\paragraph{Advanage of Optial}
-\begin{enumerate}
-    \item Direct probes bulk
-    \item Distinguish between charge and spin modes
-\end{enumerate}
-\paragraph{Sample} Omitted.
-\paragraph{RRS}
-$ $ % Go to the next line.
-
-$ \xymatrix{
-    \text{light}\ar[r] &
-    \bullet\ar@/^/[r]^{\text{quasiparticle}}
-                \ar@/_/@{<.}[r]_{\text{quasihole}} & 
-    \bullet & \text{scattered photon}
-}$
-
-$\bullet$ Easy to probe Single Partical excitation and collective
-excitation.
-
-... (Skipped)
-
-\section{Hyperspherical Adiabatic Approximation}
-\label{sec:Hyperspherical-adiabatic-Approximation}
-
-By: Rachel Wooten (Purdue University)
-
-\paragraph{Outline}
-\begin{enumerate}
-    \item QHS
-    \item Motivation
-    \item Hyperspherical adiabatic approximation (\textbf{HAA})
-    \item The role of degeneracy
-    \item Hyperradial breathing mode
-    \item Results and Discussion
+    \item The representation of infinitesimal operator.
+    \item From traditional rotational operators to commutation
+        relationship
+    \item From commutators to their eigenvalues.
+    \item Summarize some further results regarding the matrix
+        representation of those operators.
 \end{enumerate}
 
-\paragraph{QHS}
-\begin{table}[H]
-    \caption{Two Schemes}
-    \centering
-    \begin{tabular}{|ccc|}
-        \hline
-        Conventional     & $\approx$ & Neutral Atom gass \\
-        \hline
-        2D Landau levels &           & 2D Rotation($\Omega$) \\
-        $\omega_c$       &           & $\omega= 2\Omega$ \\
-        \hline
-    \end{tabular}
-\end{table}
+\section{Review of Symmetry Operator}
+\label{sec:Review-of-Symmetry-Operator}
+\begin{enumerate}
+    \item The invariance of probability and Wigner's theorem
+    \item The values of measurement before and after transformation
+\end{enumerate}
 
-(Other schemes are also available, not treated).
+\section{Derive some properties of TR operator}
 
-\paragraph{Motivation}
-\begin{itemize}
-    \item QHS: prototype of \textit{Strongly correlated systems}
-    \item Nature of few-body states
-    \item insights from collectively coordinates
-    \item use ... ?
-\end{itemize}
-
-\paragraph{Few body, adiabatic hypershperical approach\textbf{(AHA)}}
-
-\begin{itemize}
-    \item intrinsic collective coordinates
-    \item length scale $R$ $\overset{\text{from}}{ \Leftarrow}$ geometry
-    \item $E$ potential $ \Leftarrow$ length scale
-    \item introduce Grand Angular momentum $K$ - quantum number
-\end{itemize}
-
-\paragraph{AHA background} Joe Macek, 1968 JPB.
-
-\paragraph{Scheme} Sch-Ep $\overset{recast}{ \Rightarrow}$ relative
-coordinates $ \overset{diagonalize}{ \Rightarrow}$ solve.
-
-\paragraph{Hyperspherical Coordinates} $ $
-
-$2N-2$ Jacobi coordinates $\Rightarrow$ $2N-3$ angular coordinates
-$\Omega$ + 1 length coordinates Hyperradial $R$.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/rachel-wooten-purdue.png}
-\end{figure}
-
-\paragraph{Hyperradius}
-$$\rho = \left( \frac{\pi\mu\braket{R^2}}{N(N-1)} \right)$$
-$$\mathscr{H}_\text{rel} = (R, \Omega, \cdots)
-    +\text{Colomb} V(R)=\frac{1}{R}
-    +\text{Polarized dipoles}V(R)=\frac{1}{R^3}
-$$
-\paragraph{AHA (Non-interacting case)} Omitted.
-\paragraph{AHA (Interacting case)}$ $
-
-Treat $R$ as an adiabatic parameter.
-
-Interaction $\overset{\text{introduct}}{\Rightarrow}$ degeneracies
-\paragraph{Accuracy check} Omitted.
-\paragraph{Exceptional degeneracy}
-
-\section{? (Wick Haxton)}
-\label{sec:Wick-Haxton}
-
-(1995) Algebraic classification of general 4 fermion problem (Joe
-Ginocchio) $\Rightarrow$ has FQHE implications
-
-Jain \& Laughlin work (numerically succesful)
-
-(No audio available for this lecture recording!, Skipped)
-
-\section{Perspectives on the half-fill Landau Level}
-\label{sec:Perspectives-on-the-half-fill-Landau-Level}
-
-By B.I. Halperin, N. Copper, Chong Wong, Adey Stern.
-
-\paragraph{Question}: What ahppens to half-filled Landau Level when there
-is \textbf{NO} magnetic field.
-
-\paragraph{Motivation}
-\begin{itemize}
-    \item New research on half-filled Landau level
-    \item Describe system by "Dirac Fermion" is simpler, generated
-        different theories $\Rightarrow$ doubt whether they are
-        equivalent.
-    \item Particle-hole symmetry in explicit in "Dirac Fermion", not
-        explicit in HLR framwork.
-\end{itemize}
-\paragraph{Physical Setup} $ $
-
-Half-filled Landau level: in a semiconductor.
-$$ H_0 = \sum_i \frac{ |P_i - A(r_i)|^2}{2m} + V_2 \text{(interactions)}
-$$
-Units: $e=\hbar=1$.
-\paragraph{PH Symmetry} $ $
-
-\begin{itemize}
-    \item $m\to 0$, e-e interactions are fixed -> exact PH symmetry
-    \item For $v=1/2$, PHS requires that $\sigma_{xy}(\sigma)=(1/2) e^2/h$
-\end{itemize}
-
-\paragraph{HLR Approach}
-(Halperin, Lee, Read. PRB 1993)
-
-\begin{itemize}
-    \item Singular gauge transformation $\Rightarrow$ Chern-Simons Gauge
-        Field
-    \item Transformed Hamiltonian will have fermion terms, interactions,
-        gauge field (chern-simons interaction in it). Also the curl of a
-        fact vector is constrained.
-\end{itemize}
-\paragraph{Antecednets}
-\begin{itemize}
-    \item Fractional Quantized Hall states by Jain; Lopez and Fradkin;
-        others.
-    \item Simultaneous work by Kalmeyer and Zhang had some features of
-        HLR.
-\end{itemize}
-
-\paragraph{HLR Hypothesis}
-\begin{itemize}
-    \item Do mean field theory on this problem: the ground state and low
-        energy properties of quantum hall system at $v=1/2$. And use
-        perturbation theory and take into account of fluctuations in gauge
-        field and Coulomb interactions
-    \item ...
-\end{itemize}
-\paragraph{HLR consequences}
-\begin{itemize}
-    \item with $1/r$ interactions, the ground state is a "marginal fermi
-        liquid". With mass diverges $log$ at fermi serface, eue to
-        infrared divergence.
-    \item assume interactions that fall off slower than $1/r$.
-\end{itemize}
-\paragraph{HLR-RPA predications}
-\begin{itemize}
-    \item ground state at $v=1/2$ should be compressible
-    \item energy gaps, FQH states, occur at Jain fractions $v=p/(2p+2)$.
-    \item relative sizes of energy gaps close to $1/2$
-    \item transport in absence of impurities: DC hall conductance
-    \item Longitudianl conductivity at finite $q,\omega\to 0$:
-        $$\sigma_{xx}(q)=q/(8\pi k_f) $$
-        in the presence impurities: formula holds for $q>l_{cf}$.
-\end{itemize}
-
-Related work: Kalmeyer \& Zhang.
+\section{Kramer's theorem and the lifting of degenracy}
 
@@
 \begin{thebibliography}{1}
-    \bibitem{utube-lecture}\url{https://www.youtube.com/playlist?list=PLCoSh1h28ieLIaD-HGi5aUQzunOTtxHTC}
+    \bibitem{sakurai} Modern Quantum Mechanics. J.J. Sakurai.
+    \bibitem{bernevig} Introduction to Topological Insulators. Bernevig.
 \end{thebibliography}

### 2016-10-06 Draft/draft.tex
Huge updates to TR operator notes.

@@
     projective geometry, or $\mathbb{CP}^n$), since operators acts
-    on ket spaces, which is already projective (within a freedom of
+    on ket spaces, which is already projective (i.e. within a freedom of
     phase).
@@
 
-    \subsection{Adjoint of antilinear operator}
-    \label{sec:Adjoint_of_antilinear_operator}
-
-    If we were to define adjoint of an antilinear operator, we might
-    run into troubles with traditional definition. For example, suppose
-    $A$ is antilinear, let multiply it with $c\mathbbm{1}$, where $c$
-    is just some nonzero constant.
-
-    We have:
-    \begin{align}
-        \braket{\phi|cA \psi} = c\braket{\phi|A\psi}
-    \end{align}
-    on the other hand:
-    \begin{align}
-        &\braket{\phi|cA \psi} = \braket{cA\psi|\phi}^*
-            = \braket{\psi|A^\dagger c^* \phi}^* \nonumber\\
-        &=(c\braket{\psi|A^\dagger \phi})^* = c^* \braket{A\psi|\phi}^*
-            = c^* \braket{\phi|A\psi}
-    \end{align}
-    A contracdiction. Then, it was proposed, in the first answer to
-    this Math.SE post, that we define the adjoint operator differently 
-    for antilinear operator $A$:
-    \begin{align}
-        \braket{A^\dagger v|w} = \braket{v| Aw}^*
-    \end{align}
-    Then the above discrepancy will not exist anymore (easily confirmed).
-
-    Here I also include the complete answer for reference:
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-    \begin{quote}
-        I) First of all, one should never use the [Dirac bra-ket notation](http://en.wikipedia.org/wiki/Bra-ket\_notation) (in its ultimate version where an operator acts to the right on kets and to the left on bras) to consider the definition of [adjointness](http://en.wikipedia.org/wiki/Adjoint\_operator), since the notation was designed to make the adjointness property look like a mathematical triviality, which it is not.
-See also [this](http://physics.stackexchange.com/q/43069/2451) Phys.SE post.
-
-        II) OP's question(v1) about the existence of the adjoint of an [antilinear](http://en.wikipedia.org/wiki/Antilinear\_map) operator is an interesting mathematical question, which is rarely treated in textbooks, because they usually start by assuming that operators are $\mathbb{C}$-linear.
-
-        III) Let us next recall the mathematical definition of the adjoint of a linear operator.
-Let there be a [Hilbert space](http://en.wikipedia.org/wiki/Hilbert\_space) $H$ over a [field](http://en.wikipedia.org/wiki/Field\_\%28mathematics\%29) $\mathbb{F}$, which in principle could be either real or complex numbers, $\mathbb{F}=\mathbb{R}$ or $\mathbb{F}=\mathbb{C}$.
-Of course in quantum mechanics, $\mathbb{F}=\mathbb{C}$.
-In the complex case, we will use the standard physicist's convention that the [inner product/sequilinear form](http://en.wikipedia.org/wiki/Sesquilinear\_form) $\langle \cdot | \cdot \rangle$ is conjugated $\mathbb{C}$-linear in the first entry, and $\mathbb{C}$-linear in the second entry.
-
-        Recall [Riesz' representation theorem](http://en.wikipedia.org/wiki/Riesz\_representation\_theorem): For each continuous $\mathbb{F}$-linear functional $f: H \to \mathbb{F}$ there exists a unique vector $u\in H$ such that
-        $$\text{tag\{1\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
-
-        Let $A:H\to H$ be a continuous$^1$ $\mathbb{F}$-linear operator. Let $v\in H$ be a vector. Consider the continuous $\mathbb{F}$-linear functional
-
-        $$\text{tag\{2\}} f(\cdot)~=~\langle v | A(\cdot) \rangle.$$
-
-        The value $A^{\dagger}v\in H$ of the adjoint operator $A^{\dagger}$ at the vector $v\in H$ is by definition the unique vector $u\in H$, guaranteed by Riesz' representation theorem, such that 
-        $$\text{tag\{3\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
-
-        In other words, 
-        $$\text{tag\{4\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\langle v | Aw \rangle. $$
-
-        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an $\mathbb{F}$-linear operator as well.
-
-        IV) Finally, let us return to OP's question and consider the definition of the adjoint of an antilinear operator.
-The definition will rely on the complex version of Riesz' representation theorem.
-Let $H$ be given a complex Hilbert space, and let  $A:H\to H$ be an antilinear continuous operator.
-In this case, the above equations (2) and (4) should be replaced with
-
-        $$\text{tag\{2'\}} f(\cdot)~=~\overline{\langle v | A(\cdot) \rangle},$$
-
-        and
-
-        $$\text{tag\{4'\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\overline{\langle v | Aw \rangle}, $$
-
-        respectively. Note that $f$ is a $\mathbb{C}$-linear functional.
-
-        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an antilinear operator as well.
-
-        --
-
-        $^{1}$We will ignore subtleties with [discontinuous/unbounded operators](http://en.wikipedia.org/wiki/Unbounded\_operator), domains, [selfadjoint extensions](http://en.wikipedia.org/wiki/Extensions\_of\_symmetric\_operators), etc., in this answer.
-    \end{quote}
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
     \subsection{Bayes' theorem}
@@
     \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-    \bibitem{math.SE-adjoint-of-antilinear}\href{http://physics.stackexchange.com/questions/45227/existence-of-adjoint-of-an-antilinear-operator-time-reversal}{Existence of adjoint of an antilinear operator, time reversal}
 \end{thebibliography}

### 2016-10-06 Notes about TR symmetry/Notes about TR symmetry.tex
Huge updates to TR operator notes.

@@
 
-\title{Notes about TR Symmetry}
+\title{Notes about Spin and TR Symmetry}
 \date{\today}
@@
 Sakurai \cite{sakurai}, and the other by Bernevig \cite{bernevig}.
+It contains a summary of treatment of Spin (actually, rotation) in
+quantum mechanics, which is needed to discuss the TR symmetry operator.
 }
@@
 
+\subsection{The representation of transformation}
+\label{sec:The-representation-of-transformation}
+
+To find an operator for a physical transformation, we naturally encounters
+the theory of representation of groups. Why groups? See the following
+notes for an bird view. (The note is an excerpt from my notes about
+Quantum Field Theory by Weinberg, which is still in its infancy because
+the book is so hard to read)
+\begin{quote}
+    The set of all symmetries transformations obviously can have a group
+    structure. By giving each symmetry transformation a unitary or
+    antiunitary operator, a representation of such group is obtained.
+    However, such a representation can be projective (projective as in
+    projective geometry, or $\mathbb{CP}^n$), since operators acts on ket
+    spaces, which is already projective (i.e. within a freedom of phase). 
+\end{quote}
+
+Here I outlined one general procedure to obtain such representation from
+infinitesimal transformations. This procedure is discussed in chapter 1
+and 2 of \cite{sakurai}.
+% TODO update more specific location inside that book.
+We first needs two thing to characterize a tranformation: a Hermitian
+operator $G$ and an infinitesimal change $\varepsilon$. I am not sure about
+how to choose $G$, but I think the choice for $\varepsilon$ should be
+% TODO how to choose G, and what is G
+clear. Here are three typical examples.
+
+For displacement in $x$ direction:
+\begin{align}
+    G \rightarrow \frac{p_x}{\hbar},\, \varepsilon \rightarrow \diff x
+\end{align}
+For an infinitesimal time evolution:
+\begin{align}
+    G \rightarrow \frac{H}{\hbar},\, \varepsilon \rightarrow \diff t
+\end{align}
+For infinitesimal rotation around $k$ th axis:
+\begin{align}
+    G \rightarrow \frac{J_k}{\hbar},\, \varepsilon \rightarrow \diff \phi
+    \label{eq:revSpin.repreTrans.angulalMomGen}
+\end{align}
+Or more general (let the rotation be characterized by $\mathbf{J}\cdot
+\hat{\mathbf{n}}$, where $\hat{\mathbf{n}}$ is a unit vector), we have:
+\begin{align}
+    G \rightarrow \frac{\mathbf{J}\cdot \hat{\mathbf{n}} }{\hbar},\,
+    \varepsilon \rightarrow \diff \phi
+\end{align}
+
+Here $\mathbf{J}=(J_x,J_y,J_z)$ is defined such that the substitution
+\ref{eq:revSpin.repreTrans.angulalMomGen} indeed produces a rotation.
+What do we mean by "indeed" here? This will be explained in section
+\ref{sec:From-classical-mechanic-to-commutators}.
+\label{page:question-def_of_J}
+
+Then the operator corresponding to the infinitesimal transformation is
+\begin{align}
+    U_\varepsilon= 1-i\, G\varepsilon
+\end{align}
+And for a finite transformation (let $\Delta$ denotes the finite
+transformation):
+\begin{align}
+    \lim_{N\to \infty}\left[ 1-iG\frac{\Delta}{N}\right]^N =
+    \exp(-iG\Delta)
+\end{align}
+For example, in the case of rotation we have (using $\mathscr{D}$ to
+denote the operator):
+\begin{align}
+    \mathscr{D}(\hat{\mathbf{n}},\diff \phi) =
+    1-i\frac{\mathbf{J}\cdot\hat{\mathbf{n}}}{\hbar}\diff\phi
+    \\
+    \mathscr{D}(z,\phi)=\exp(\frac{-iJ_z \phi}{\hbar})
+    \label{eq:revSpin.repreTrans.repreFiniteRot}
+\end{align}
+
+Note that, here $G$ is regarded as a generator of physical transformation:
+\begin{table}[H]
+    \centering
+    \caption{Generators}
+    \begin{tabular}{|c|c|}
+    \hline
+    Generator                     & Physically generated transformation \\
+    \hline
+    Momentum $p_x$                & Translation $\diff x$ \\
+    \hline
+    Energy $H$                    & Time evolution: $\diff t$ \\
+    \hline
+    Angular momentum $J_x$ & Rotation about $x$ axis \\
+    \hline
+    \end{tabular}
+\end{table}
+\subsection{From classical mechanics to commutators in quantum mechanics}
+\label{sec:From-classical-mechanic-to-commutators}
+
+This part is discussed in secion 3.1 of \cite{sakurai}.
+
+The commutation relationship is obtained by considering infinitesimal
+transformation. In general, classical rotation can be decomposed into
+rotation about three axes. We can use linear transformation to express
+them. For example, rotation about $z$ axis is:
+\begin{align}
+    R_z(\phi) = \left( \begin{array}{ccc}
+         \cos (\phi ) & -\sin (\phi ) & 0 \\
+         \sin (\phi ) & \cos (\phi ) & 0 \\
+         0 & 0 & 1 \\ \end{array} \right)
+\end{align}
+Put it into infinitesimal amount, one has:
+\begin{align} 
+    R_z(\varepsilon)=\left( \begin{array}{ccc}
+     1-\frac{\varepsilon ^2}{2} & -\varepsilon               & 0 \\
+     \varepsilon                & 1-\frac{\varepsilon ^2}{2} & 0 \\
+     0                          & 0                          & 1 \\
+\end{array} \right) \end{align}
+Similar procedure could be done for other axes (see equation 3.1.4 and
+3.1.5 in \cite{sakurai}). By calculation one finds that
+$$ R_x(\varepsilon)R_y(\varepsilon)=R_y(\varepsilon)R_x(\varepsilon)$$
+if terms higher than $\varepsilon$ is ignored. This means that
+infinitesimal rotation $\diff \mathbf{\omega}$ can be safely considered as
+vectors.
+
+However if only terms of order equal and lower than $\varepsilon^2$ is kept
+(note especially that $\varepsilon^4$ is ignored), one finds:
+\begin{align}
+    \label{eq:revSpin.fromCM2QM.classicalRotComu}
+    R_x(\varepsilon)R_y(\varepsilon)-R_y(\varepsilon)R_x(\varepsilon)=
+    R_z(\varepsilon^2)-\mathbb{I}
+\end{align}
+
+Expand equation \ref{eq:revSpin.repreTrans.repreFiniteRot} in orders of
+$\phi$ and keep only terms with order $leq \phi^2$, we have:
+$$
+\mathscr{D}(x,\varepsilon)=
+1-\frac{iJ_x \varepsilon}{\hbar}-\frac{J_x^2 \varepsilon^2}{2\hbar^2}
+$$
+and so on for other axes.
+
+Plug these results into the classical commutation relationship
+\ref{eq:revSpin.fromCM2QM.classicalRotComu}, and with some calculation,
+one will find:
+\begin{align}
+    \label{eq:revSpin.fromCM2QM.comuOfAngularM}
+    [J_i,J_j]=i\hbar \varepsilon_{ijk}J_k
+\end{align}
+here $\varepsilon_{ijk}$ is the Levi-Civita notation in $3$ dimension.
+This relation also ensures that the operator $\mathbf{J}$ we defined
+indeed corresponds to a physical rotation, which answers the question is
+mentioned in page \pageref{page:question-def_of_J}.
+
+\subsection{From commutators to eigenvalues}
+\label{sec:From-commutators-to-eigenvalues}
+Now one may use the commutation relation
+\ref{eq:revSpin.fromCM2QM.comuOfAngularM} to get the eigenvalues of these
+operators. The procedure is quite standard and can be found in section 3.5
+of \cite{sakurai}. There the author defines the ladder operators:
+\begin{defi}[Ladder operator]
+\nomenclature{Ladder operator}{\nomrefpage.}
+    \begin{align}
+        J_{\pm}\equiv J_x \pm i J_y
+    \end{align}
+\end{defi}
+Then he derives the cummutation relationship:
+\begin{align}
+    [\mathbf{J}^2,J_k] &= 0\\
+    [J_+,J_-] &=2\hbar J_z \\
+    [J_z,J_\pm] &= \pm \hbar J_\pm \\
+    [\mathbf{J}^2,J_\pm] &=0 \\
+\end{align}
+Chossing the $z$ direction as eigenstate. Denote the simultaneous
+eigenstates of $\mathbf{J}^2$ and $J_z$ as $\ket{j,m}$, such that:
+\begin{align}
+    \mathbf{J}^2\ket{j,m} &= j(j+1)\hbar^2 \ket{j,m} \\
+    J_z \ket{j,m} &= m \hbar\ket{j,m}
+\end{align}
+(such a strange choice is conventional in the case of spin).
+
+As usual, one finds that
+\begin{itemize}
+    \item For $J_z$, $J_\pm$ will pull up/lower its eigenvalue for
+        eigenstate in units of $\hbar$.
+    \item For $\mathbf{J}^2$, $J_\pm$ will not alter its eigenvectors,
+        since it commutes with $\mathbf{J}^2$.
+\end{itemize} 
+By above relationships, one can derive the following facts (for
+convenience let $a$ be the eigenvalue for $\mathbf{J}^2$, and $b$ be the
+eigenvalue for $J_z$.):
+\begin{itemize}
+    \item $a\geq b^2$, i.e $b$ is bounded by $a$. More specifically,
+    \item $a=b_{\text{max}}(b_{\text{max}}+\hbar)$.
+    \item Also, $-b_{\text{max}}\leq b \leq b_{\text{max}}$.
+    \item Using $b_{\text{max}}=b_{\text{min}}+n\hbar$ ($n$ is some
+        integer), one gets
+    \item $b_{\text{max}}= \frac{n\hbar}{2}$. This, by identifying
+        $j=\frac{n}{2}$, one has
+\end{itemize}
+\begin{align}
+    a &= j(j+1)\hbar^2 \\
+    b &= m\hbar\\
+    (m &= -j, -j+1,\cdots, j-1,j;\, j=\frac{n}{2}) \nonumber
+\end{align}
+\subsection{Getting the matrix of rotation operators}
+\label{sec:Using-Euler-angles-to-get-matrix-of-rotation-operators}
+
+Simply by commutation relationships above, one can easy get:
+\begin{align}
+    \bra{j',m'}\mathbf{J}^2\ket{j,m} &= 
+        j(j+1)\hbar^2 \delta_{j'j}\delta_{m'm} \\
+    \bra{j',m'}J_z\ket{j,m} &= 
+        m\hbar \delta_{j'j}\delta_{m'm} \\
+    \bra{j',m'}J_\pm\ket{j,m} &= 
+        \sqrt{(j\mp m)(j\pm m+1)} \hbar \delta_{j'j}\delta_{m',m\pm 1}
+        \label{eq:revSpin.getMatRot.J_pm}
+\end{align}
+
+To get matrix element for
+$\exp(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar})$, one needs to
+use Euler angles.
+
+    \subsubsection{Eulerian Angles}
+    \label{sec:Eulerian-Angles}
+    The Euler angles is discussed in section 3.3 of \cite{sakurai}.
+    However, Sakurai's usage in his book \cite{sakurai} is a bit different
+    from the usual one. But the following graph taken from that section
+    should explains all:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=1.2\linewidth]{pics/{fig3.4in-Sakurai-Euler-angles}.png}
+        \caption{Euler Angles (fig 3.4 in that book)}
+        \label{fig:fig3.4-Sakurai-Euler-angles}
+    \end{figure}
+
+    One can find that a Euler rotaion characterized by
+    $(\alpha,\beta,\gamma)$ could be decomposed into:
+    \begin{align}
+        R(\alpha,\beta,\gamma)=R_z(\alpha)R_y(\beta)R_z(\gamma)
+    \end{align}
+
+    \subsubsection{Using Euler angles to get matrix for rotation operator}
+    \label{sec:Using Euler angles to get matrix for rotation operator}
+
+    As the title suggests, in section 3.5 of \cite{sakurai}, we have
+    $$
+    \exp\left(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar}\right)
+    =
+    \exp\left(\frac{-i J_z\alpha}{\hbar}\right)
+    \exp\left(\frac{-i J_y\beta}{\hbar}\right)
+    \exp\left(\frac{-i J_z\gamma}{\hbar}\right)
+    $$,
+    define 
+    \begin{align}
+        \nomenclature{
+            Wigner function $\mathscr{D}^{(j)_{m'm}}$}{\nomrefpage.}
+        \mathscr{D}^{(j)}_{m'm}\equiv
+        \bra{j,m'}
+            \exp\left(\frac{-i J_z\alpha}{\hbar}\right)
+            \exp\left(\frac{-i J_y\beta}{\hbar}\right)
+            \exp\left(\frac{-i J_z\gamma}{\hbar}\right)
+        \ket{j,m}
+    \end{align}
+    This $\mathscr{D}$ is sometimes called the \textbf{Wigner function}.
+    Note that we have implicitly assumed that the rotation in 
+    $\exp\left(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar}\right)$
+    does not alter the eigenstate of length $\mathbf{J}^2$. This is
+    physically satisfying, and can also be proved (equation 3.5.43 in
+    \cite{sakurai}).
+
+    % TODO I thin we should distinguish of two concepts of rotation:
+    % J and exp(-iJ/h).
+
+    Since we have diagonalize using the eigenstate of $J_z$, we have:
+    \begin{align}
+        \mathscr{D}^{(j)}_{m'm} =
+            e^{-i(m'\alpha+m\gamma)}\bra{j,m'}
+                \exp\left(\frac{-i J_y\beta}{\hbar}\right)
+            \ket{j,m}
+    \end{align}
+    The remaining part can only be calculated case by case. Denote it as 
+    $d^{(j)}_{m'm}$\nomenclature{ $d^{(j)}_{m'm}$}{\nomrefpage.}, i.e.:
+    \begin{align}
+        d^{(j)}_{m'm}\equiv \bra{j,m'}
+                \exp\left(\frac{-i J_y\beta}{\hbar}\right)
+            \ket{j,m}
+    \end{align}
+
+    Detailed calculation could start from equation
+    \ref{eq:revSpin.getMatRot.J_pm}.
+    In case of $j=\frac{1}{2}$, as is familiar for use, it is:
+    \begin{align}
+        d^{\frac{1}{2}}=\left( \begin{array}{cc}
+            \cos \left(\frac{\beta }{2}\right) 
+                & -\sin \left(\frac{\beta}{2}\right) \\
+            \sin \left(\frac{\beta }{2}\right) 
+                & \cos \left(\frac{\beta}{2}\right) \\
+            \end{array} \right)
+    \end{align}
+    Footnote \footnote{This can also be obtained using the Pauli matrices,
+    which can be found in my miscellaneous notes.}
+
+    \subsubsection{Pauli matrices in half-spin: about \texorpdfstring{$e^{-i\pi S_y/\hbar}$}{}}
+    \label{sec:About-exp(-i*pi-S_y/hbar)}
+
+    Since everyone is familiar with the Pauli matrices in spin $1/2$
+    system, I here only shows a useful result. This result is related to
+    equation (4.4.65) in \cite{sakurai}.
+
+    Since 
+    $$S_y=\frac{\hbar}{2}\sigma_y=\frac{\hbar}{2}
+        \left( \begin{array}{cc}
+         0 & -i \\
+         i & 0 \\
+        \end{array} \right)$$
+    It is easy to check that $\sigma_y^2 = \mathbb{I}$. So:
+    \begin{align*}
+        e^{-i\phi S_y/\hbar}=
+        e^{-i\frac{\phi}{2}\sigma_y}&=\sum_{n=0}^{\infty}
+         \frac{(-i\frac{\phi}{2})^n(\sigma_y)^n}{n!}\nonumber\\
+         &=\sum_{\text{odd }n}-\frac{i(\frac{\phi}{2})^n}{n!}\sigma_y
+           + \sum_{\text{even }n}\frac{(i\frac{\phi}{2})^n}{n!}\mathbb{I}
+    \end{align*}
+    Using the taylor expansions:
+    \begin{align}
+        \sinh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n+1}}{(2n+1)!}
+        \text{ (odd terms)}\\
+        \cosh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n}}{(2n)!}
+        \text{ (even terms)}
+    \end{align}
+    We see that:
+    \begin{align}
+        e^{-i\phi S_y/\hbar}=e^{-i\frac{\phi}{2}\sigma_y}&=
+         - \sigma_y\sinh{i\frac{\phi}{2}}+ \mathbb{I}\cosh{i\frac{\phi}{2}}
+         \nonumber\\
+         &=
+         -i\sigma_y \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+         &=-i\frac{2}{\hbar}S_y\sin{\frac{\phi}{2}}
+            +\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+         &=\left( \begin{array}{cc}
+            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
+            \sin (\frac{\phi }{2}) & \cos (\frac{\phi }{2}) \\
+         \end{array}\right)
+    \end{align}
+    So
+    $$e^{-i\pi S_y/\hbar} = -i\frac{2S_y}{\hbar}$$
+    By exactly the same argument, or simply by the symmetry
+    ($x\leftrightarrow y$), we
+    have:
+    \begin{align}
+        e^{-i\phi S_x/\hbar}=e^{-i\frac{\phi}{2}\sigma_x}&=
+         -i\sigma_x \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+        &=-i\frac{2}{\hbar}S_x\sin{\frac{\phi}{2}}
+            +\mathbb{I}\cos{\frac{\phi}{2}}
+        \\
+        &=\left(\begin{array}{cc}
+            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
+            \sin (\frac{\phi }{2}) & \cos(\frac{\phi }{2}) \\
+         \end{array}\right)
+    \end{align}
+    Also, one can easily find that:
+    \begin{align}
+        e^{-i\phi S_z/\hbar}=e^{-i\frac{\phi}{2}\sigma_z}&=
+          \left(\begin{array}{cc}
+              e^{-i\frac{\phi }{2}} & 0 \\
+              0                     & e^{i\frac{\phi }{2}} \\
+         \end{array}\right)
+    \end{align}
+    Also, we have a formula that encompass all the above relationship
+    (proved in page 170, section 3.2 of \cite{sakurai}):
+    \begin{align}
+        \exp(\frac{-i\vec{\sigma}\cdot\hat{\vec{n}}\phi}{2})
+        =
+        \cos(\frac{\phi}{2})\mathbb{I}-i\vec\sigma\cdot\hat{\vec{n}}
+        \sin(\frac{\phi}{2})
+    \end{align}
+    where $\vec\sigma=(\sigma_x,\sigma_y,\sigma_z)$, and 
+    $\hat{\vec{n}}$ is any unit vector.
+
+    \subsubsection{Eigenstate for \texorpdfstring{$\mathbf{S}\cdot
+    \hat{\mathbf{n}}$}{}}
+    \label{sec:Eigenstate_for_Sn}
+    Here is a physical arguemnt to construct an eigenstate for the
+    operator $\mathbf{S}\cdot \hat{\mathbf{n}}$. It mimics what was done
+    in page 172 of \cite{sakurai}. This is certainly correct when
+    $j=\frac{1}{2}$. However, I am not sure about its validity in case of
+    higher spin.
+    % TODO check this!
+
+    Suppose we have a state of the highest eigenvalue for $J_z$, i.e.
+    a state labeled by $\ket{j,j}$, then in principle any state can
+    be obtained from this state after a rotatation and a scale. But since
+    $\ket{\mathbf{n}}$ is unit vector, it can be characterized by two
+    angle: the polar angle $\beta$ and the azimuthal angles $\alpha$.
+    As shown in the following picture:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{fig3.3in-Sakurai-polar-n-azimuthal}.png}
+        \caption{Polar and azimuthal angle (fig 3.3 in \cite{sakurai})}
+    \end{figure}
+
+    So I think the eigenstate should be:
+    \begin{align}
+        \label{eq:revSpin.getMatRot.Sn.Snket}
+        \ket{\hat{\mathbf{n}};+}= e^{-iS_z \alpha/\hbar}
+        e^{-iS_y \beta/\hbar} \ket{+}
+    \end{align}
+    here $\ket{+}$ denotes the state $\ket{j,j}$. The eigenvalue is of
+    course $j\hbar$.
+
+    This is confirmed when $j=\frac{1}{2}$ in page 171 of \cite{sakurai},
+    but not in other cases.
+
 \section{Review of Symmetry Operator}
 \label{sec:Review-of-Symmetry-Operator}
+
+This part is discussed in section 4.4 of \cite{sakurai}.
+
+Outline:
 \begin{enumerate}
+    \item A note about antilinear operator, and we should treat it with
+        care.
     \item The invariance of probability and Wigner's theorem
@@
 
-\section{Derive some properties of TR operator}
+\subsection{A note about antiunitary operator}
+\label{sec:A-note-about-antiunitary-operator}
+Please note that the Dirac bra-ket notation is only convenient when we are
+dealing with unitary operators. When antiunitary operators, or arbitrary
+operators are considered, the situation can get tricky. Here are two
+examples.
 
-\section{Kramer's theorem and the lifting of degenracy}
+    \subsubsection{Formula for base transformation}
+    \label{sec:Formula-for-base-transformation}
+
+    Suppose we transform the basis
+    $\ket{e_i}$ by an operator $\mathcal{O}$, what is the formula for the
+    corresponding basis for the dual space? The requirement of dual basis
+    requires that:
+    $$ \bra{\widetilde{e}_i} = \bra{\widetilde{e}_i}U^{-1}$$
+    But by the "dual-correspondance" in Dirac notation, we expect:
+    $$ \bra{\widetilde{e}_i} = \bra{\widetilde{e}_i}U^{\dagger}$$
+    The two notion coincide only when $U$ is unitary.
+
+    Similarly, consider the operator $\ket{e_i}\bra{e_i}$, if we perform a
+    scale of the basis $\ket{e_i}\to \lambda\ket{e_i}$, then how will the
+    above operator transform? Is it
+    $$ \ket{\lambda e_i}\bra{\lambda e_i}$$
+    or is it:
+    $$ \ket{\lambda^{-1} e_i}\bra{\lambda e_i}$$
+    Of course, when the transformation is unitary, the two notion
+    coincide, because $\lambda^*=\lambda^{-1}$ implies
+    $\lambda=\lambda^{-1}$.
+    \subsubsection{The adjoint of antilinear operator}
+    label{sec:The-adjoint-of-antilinear-operator}
+
+    If we were to define adjoint of an antilinear operator, we might
+    run into troubles with traditional definition. For example, suppose
+    $A$ is antilinear, let us multiply it with $c\mathbbm{1}$, where $c$
+    is just some nonzero constant.
+
+    We have:
+    \begin{align}
+        \braket{\phi|cA \psi} = c\braket{\phi|A\psi}
+    \end{align}
+    on the other hand:
+    \begin{align}
+        &\braket{\phi|cA \psi} = \braket{cA\psi|\phi}^*
+            = \braket{\psi|A^\dagger c^* \phi}^* 
+            =(c\braket{\psi|A^\dagger \phi})^* \nonumber\\
+            =& c^* \braket{A\psi|\phi}^* 
+            = c^* \braket{\phi|A\psi}
+    \end{align}
+    A contracdiction. Then, it was proposed, in the first answer to
+    this Math.SE post\cite{math.SE-adjoint-of-antilinear}, that we define
+    the adjoint operator differently for antilinear operator $A$:
+    \begin{align}
+        \braket{A^\dagger v|w} = \braket{v| Aw}^*
+    \end{align}
+    Then the above discrepancy will not exist anymore (easily confirmed).
+
+    Here I also include the complete answer for reference:
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+    \begin{quote}
+        I) First of all, one should never use the [Dirac bra-ket notation](http://en.wikipedia.org/wiki/Bra-ket\_notation) (in its ultimate version where an operator acts to the right on kets and to the left on bras) to consider the definition of [adjointness](http://en.wikipedia.org/wiki/Adjoint\_operator), since the notation was designed to make the adjointness property look like a mathematical triviality, which it is not.
+See also [this](http://physics.stackexchange.com/q/43069/2451) Phys.SE post.
+
+        II) OP's question(v1) about the existence of the adjoint of an [antilinear](http://en.wikipedia.org/wiki/Antilinear\_map) operator is an interesting mathematical question, which is rarely treated in textbooks, because they usually start by assuming that operators are $\mathbb{C}$-linear.
+
+        III) Let us next recall the mathematical definition of the adjoint of a linear operator.
+Let there be a [Hilbert space](http://en.wikipedia.org/wiki/Hilbert\_space) $H$ over a [field](http://en.wikipedia.org/wiki/Field\_\%28mathematics\%29) $\mathbb{F}$, which in principle could be either real or complex numbers, $\mathbb{F}=\mathbb{R}$ or $\mathbb{F}=\mathbb{C}$.
+Of course in quantum mechanics, $\mathbb{F}=\mathbb{C}$.
+In the complex case, we will use the standard physicist's convention that the [inner product/sequilinear form](http://en.wikipedia.org/wiki/Sesquilinear\_form) $\langle \cdot | \cdot \rangle$ is conjugated $\mathbb{C}$-linear in the first entry, and $\mathbb{C}$-linear in the second entry.
+
+        Recall [Riesz' representation theorem](http://en.wikipedia.org/wiki/Riesz\_representation\_theorem): For each continuous $\mathbb{F}$-linear functional $f: H \to \mathbb{F}$ there exists a unique vector $u\in H$ such that
+        $$\text{tag\{1\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
+
+        Let $A:H\to H$ be a continuous$^1$ $\mathbb{F}$-linear operator. Let $v\in H$ be a vector. Consider the continuous $\mathbb{F}$-linear functional
+
+        $$\text{tag\{2\}} f(\cdot)~=~\langle v | A(\cdot) \rangle.$$
+
+        The value $A^{\dagger}v\in H$ of the adjoint operator $A^{\dagger}$ at the vector $v\in H$ is by definition the unique vector $u\in H$, guaranteed by Riesz' representation theorem, such that 
+        $$\text{tag\{3\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
+
+        In other words, 
+        $$\text{tag\{4\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\langle v | Aw \rangle. $$
+
+        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an $\mathbb{F}$-linear operator as well.
+
+        IV) Finally, let us return to OP's question and consider the definition of the adjoint of an antilinear operator.
+The definition will rely on the complex version of Riesz' representation theorem.
+Let $H$ be given a complex Hilbert space, and let  $A:H\to H$ be an antilinear continuous operator.
+In this case, the above equations (2) and (4) should be replaced with
+
+        $$\text{tag\{2'\}} f(\cdot)~=~\overline{\langle v | A(\cdot) \rangle},$$
+
+        and
+
+        $$\text{tag\{4'\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\overline{\langle v | Aw \rangle}, $$
+
+        respectively. Note that $f$ is a $\mathbb{C}$-linear functional.
+
+        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an antilinear operator as well.
+
+        --
+
+        $^{1}$We will ignore subtleties with [discontinuous/unbounded operators](http://en.wikipedia.org/wiki/Unbounded\_operator), domains, [selfadjoint extensions](http://en.wikipedia.org/wiki/Extensions\_of\_symmetric\_operators), etc., in this answer.
+    \end{quote}
+
+    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
+    \subsubsection{Conclusion}
+    \label{sec:Conclusion}
+    For antilinear operators, we should always working with it acting on
+    the kets. See page 289 in section 4.4 of \cite{sakurai}.
+
+\subsection{Property of a symmetry operator}
+\label{sec:Property-of-symmetry-operator}
+Consider a symmetry operation acting on states such that:
+\begin{align}
+    \ket{\alpha}\to \ket{\widetilde{\alpha}}\,\,
+    \ket{\beta}\to \ket{\widetilde{\beta}}
+\end{align}
+We require that the probability, the most important thing in quantum
+mechanics, is unchaged:
+\begin{align}
+    |\braket{\widetilde{\beta}|\widetilde{\alpha}}| =
+        |\braket{\beta|\alpha}|
+\end{align}
+Wigner has proved that\footnote{
+Though it was only mentioned in page 289 of \cite{sakurai}.},
+all such symmetry transformations can be characterized either by an unitary
+or an antiunitary operator. Also, any antiunitary operator $\theta$ can be
+expressed as
+\begin{align}
+    \theta = U K
+\end{align}
+where $U$ is unitary, and $K$ is complex conjugation. Three facts about
+$K$:
+\begin{itemize}
+    \item \textit{"acts only on any coefficient that multiplies a ket
+        (and stands on the right of K)."} 
+    \item $K$ also does not act on the base ket, i.e. $K\ket{e}=\ket{e}$.
+    \item $K$'s action depends heavily the base ket. This is obvious from
+        the above two points. Of course, this is not important when every
+        physical state is only projective. However, I still doubt whether
+        this will call additional problem.
+        \footnote{Consider $K\ket{e}=\ket{e}$, but when
+        $\ket{e}=i\ket{e'}$, then $K\ket{e}=-i\ket{e'}=-\ket{e}$.}
+\end{itemize}
+
+\subsection{States and Operators after transformation}
+\label{sec:States-and-Operators-after-transformation}
+Let $U$ be an unitary operator and $A$ be an antiunitary operator. Suppose
+we have $\ket{\alpha}$ and $\ket{\beta}$, and regard both to be
+transformed under $U$ and $A$. Let:
+\begin{align}
+    \ket{\alpha_u}=U\ket{\alpha},\, \ket{\alpha_a}=A\ket{\alpha} \\
+    \ket{\beta_u}=U\ket{\beta},\, \ket{\beta_a}=A\ket{\beta}
+\end{align}
+Then by defintion of unitary and antiunitary, we have:
+\begin{align}
+    \braket{\beta_u|\alpha_u} &=\braket{\beta|\alpha} \\
+    \braket{\beta_a|\alpha_a}^* &=\braket{\beta|\alpha}
+\end{align}
+
+For any operator $\mathcal{O}$, we have, after transformation:
+\begin{align}
+    \mathcal{O}_u &= U\mathcal{O}U^\dagger \\
+    \mathcal{O}_a &= A \mathcal{O}^\dagger A^{-1}
+\end{align}
+The two equation are mean to expresses the following idea:
+\begin{align}
+    \bra{\alpha}\mathcal{O}\ket{\beta} &=
+    \braket{\widetilde{\alpha}|\mathcal{O}_u |\widetilde{\beta}} \\
+    \bra{\alpha}\mathcal{O}\ket{\beta} &=
+    \braket{\widetilde{\beta}|\mathcal{O}_a |\widetilde{\alpha}}
+\end{align}
+
+Proof may be found on page 292 of \cite{sakurai}.
+\section{TR operator}
+
+Finally I can turn to the TR operator. But before the formal discussion of
+time reversal, I should first note that the name \textbf{time reversal} is
+actually a misnomer. As mentioned in page 284, section 4.4 in 
+\cite{sakurai}:
+\begin{quote}
+    What we do in this section can be more appropriately characterized by
+    the term \textbf{reversal of motion}. Indeed, that is the phrase used
+    by E.  Wigner, who formulated time reversal in a very fundamental
+    paper written in 1932.
+\end{quote}
+This section can be found in section 4.4 of \cite{sakurai}.
+
+Outline:
+\begin{enumerate}
+    \item Deduce the property of TR symmetry operator from classical
+        picture.
+    \item The problem of degenracy and how a breaking of TR symmetry lifts
+        this degenracy.
+\end{enumerate}
+
+    \subsection{From classical notion to property of TR symmetry}
+    \label{sec:From-classical-notion-to-property-of-TR-symmetry}
+    To get the time reversal operator, we can first look at the following
+    equality (let $\Theta$ dentoes the time reversal operator):
+    \begin{align}
+        \left(1-\frac{iH}{\hbar}\delta t\right) \Theta \ket{\alpha}
+        = \Theta\left(1-\frac{iH}{\hbar}(-\delta t)\right)\ket{\alpha}
+        \label{eq:TRoper.fromClas2Quam.phyPic}
+    \end{align}
+    This follows from the following notion: a time reversed state is
+    equivalent to the original state at an earlier time. Recall that
+    $\left(1-\frac{iH}{\hbar}\delta t\right)$ produces an infinitesimal
+    time translation.
+
+    From equality \ref{eq:TRoper.fromClas2Quam.phyPic}, one finds:
+    \begin{align}
+        -iH\Theta = \Theta i H
+    \end{align}
+
+    One can show that \textbf{$\Theta$ must be antilinear}. Because if one
+    assumes that $\Theta$ is linear, one will find that the energy
+    spectrum for time reversal symmetric system will always has symmetric
+    energy spectrum (i.e. with both and symmetric positive and negative
+    energy), which is not true.
+
+    So we have:
+    \begin{itemize}
+        \item $\Theta$ is antiunitary.
+        \item $\Theta H=H\Theta$.
+    \end{itemize}
+
+    Recall that $\Theta= UK$, and $K$ is highly dependent on the basis
+    chosen. So $U$ will depend on the basis too. To get $\Theta$ in a
+    basis $\ket{e_i}$, obviously we only need to consider the result of
+    $K\ket{e_i}$. This however, is hard to determine. However we can argue
+    that in case when the basis has some classical connection, then by the
+    Correspondance Principle we have, for example:
+    \begin{align}
+        \Theta \hat{p} \Theta^{-1}&= -\hat{p} \\
+        \Theta \hat{x} \Theta^{-1}&= \hat{x} \\
+        \Theta \mathbf{J} \Theta^{-1}&= -\mathbf{J}
+    \end{align}
+    with these one can easily find:
+    \begin{align}
+        \Theta \ket{p} &= \ket{-p} \\
+        \Theta \ket{x} &= \ket{x} \\
+        [x_i, p_j]\Theta \ket{} &= i\hbar \delta_{ij} \Theta\ket{}
+    \end{align}
+    where $\ket{}$ stands for any ket. Then clearly, $\Theta$ is just
+    complex conjugation for wave function $\Psi(x)$. But $\Theta$ acts on
+    $\Psi(p)$ will produces $\Psi^*(-p)$. The case for eigenstate of
+    spin is a little complicated, which will be discussed in section
+    \ref{sec:Time-reversal-operator-in-spin-j}.
+
+    Following is a useful theorem, which is easy to proof (proof can be
+    found on page 294 of \cite{sakurai}):
+    \begin{thm}
+        When Hamiltonian is invariant under time reversal and the energy
+        eigenket is nondegenerate; then the corresponding energy
+        eigenfunction is real (or, more generally, a real function times a
+        phase factor independent of $x$)
+    \end{thm}
+    Therefore, a complex eigenfunction almost means a degenrate state, or
+    the system is not invariant under time reversal.
+
+    \subsection{Time reversal operator in spin \texorpdfstring{$j$}{}}
+    \label{sec:Time-reversal-operator-in-spin-j}
+    Using my guess \ref{eq:revSpin.getMatRot.Sn.Snket}:
+    \begin{align*}
+        \ket{\hat{\mathbf{n}};+}= e^{-iS_z \alpha/\hbar}
+        e^{-iS_y \beta/\hbar} \ket{+}
+    \end{align*}
+    and by similar argument in that section \ref{sec:Eigenstate_for_Sn},
+    we can argue that the state with opposite direction is
+    \begin{align}
+        \ket{\hat{\mathbf{n}};-}= e^{-iS_z \alpha/\hbar}
+        e^{-iS_y (\beta+\pi)/\hbar} \ket{+}
+    \end{align}
+    Again, I am using notation $\ket{-}$ to denotes $\ket{j,-j}$.
+
+    Since time reversal reverses the angular momentum, I expects:
+    \begin{align}
+        \Theta \ket{\hat{\mathbf{n}};+} = \eta \ket{\hat{\mathbf{n}};-}
+    \end{align}
+    where $\eta$ is just some unnecessay factor.
+
+    With above relationship, one can easily see that:
+    \begin{align}
+        \Theta = \eta e^{-i\pi J_y/\hbar}K
+    \end{align}
+    The proof is trivial for $j=\frac{1}{2}$, but I cannot find a proof
+    for other values of $j$.
+
+    It is also interesting to note that in general:
+    \begin{align}
+        \Theta^2 &= -1 \text{ if $j$ is a half-integer} \\
+        \Theta^2 &= 1 \text{ if $j$ is an integer}
+    \end{align}
+    However, this can only be proved when $j=\frac{1}{2}$, in which case
+    the proof is also straightforward if we use the formula mentioned in
+    section \ref{sec:About-exp(-i*pi-S_y/hbar)}.
+
+    However, if we imagine a spin $j$ system as composed all just of
+    electrons of spin $\frac{1}{2}$, then we have a strong argument that
+    the above formula is true.
+    \subsection{Kramer's theorem and the lifting of degenracy}
 
@@
     \bibitem{bernevig} Introduction to Topological Insulators. Bernevig.
+    \bibitem{math.SE-adjoint-of-antilinear}\href{http://physics.stackexchange.com/questions/45227/existence-of-adjoint-of-an-antilinear-operator-time-reversal}{Existence of adjoint of an antilinear operator, time reversal}
 \end{thebibliography}

### 2016-10-06 Draft/draft.tex
Small fixes

@@
 
-\subsection{About \texorpdfstring{$e^{-i\pi S_y/\hbar}$}{}}
-\label{sec:About-exp(-i*pi S_y/hbar)}
-
-    (Related: Sakurai's Q.M., about (4.4.65)).
-
-    Since 
-    $$S_y=\frac{\hbar}{2}\sigma_y=\frac{\hbar}{2}
-        \left( \begin{array}{cc}
-         0 & -i \\
-         i & 0 \\
-        \end{array} \right)$$
-    It is easy to check that $\sigma_y^2 = \mathbb{I}$. So:
-    \begin{align*}
-        e^{-i\phi S_y/\hbar}=
-        e^{-i\frac{\phi}{2}\sigma_y}&=\sum_{n=0}^{\infty}
-         \frac{(-i\frac{\phi}{2})^n(\sigma_y)^n}{n!}\nonumber\\
-         &=\sum_{\text{odd }n}-\frac{i(\frac{\phi}{2})^n}{n!}\sigma_y
-           + \sum_{\text{even }n}\frac{(i\frac{\phi}{2})^n}{n!}\mathbb{I}
-    \end{align*}
-    Using the taylor expansions:
-    \begin{align}
-        \sinh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n+1}}{(2n+1)!}
-        \text{ (odd terms)}\\
-        \cosh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n}}{(2n)!}
-        \text{ (even terms)}
-    \end{align}
-    We see that:
-    \begin{align}
-        e^{-i\phi S_y/\hbar}=e^{-i\frac{\phi}{2}\sigma_y}&=
-         - \sigma_y\sinh{i\frac{\phi}{2}}+ \mathbb{I}\cosh{i\frac{\phi}{2}}
-         \nonumber\\
-         &=
-         -i\sigma_y \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-         &=-i\frac{2}{\hbar}S_y\sin{\frac{\phi}{2}}
-            +\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-         &=\left( \begin{array}{cc}
-            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
-            \sin (\frac{\phi }{2}) & \cos (\frac{\phi }{2}) \\
-         \end{array}\right)
-    \end{align}
-    So
-    $$e^{-i\pi S_y/\hbar} = -i\frac{2S_y}{\hbar}$$
-    By exactly the same argument, or simply by the symmetry
-    ($x\leftrightarrow y$), we
-    have:
-    \begin{align}
-        e^{-i\phi S_x/\hbar}=e^{-i\frac{\phi}{2}\sigma_x}&=
-         -i\sigma_x \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-        &=-i\frac{2}{\hbar}S_x\sin{\frac{\phi}{2}}
-            +\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-        &=\left(\begin{array}{cc}
-            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
-            \sin (\frac{\phi }{2}) & \cos(\frac{\phi }{2}) \\
-         \end{array}\right)
-    \end{align}
-    Also, one can easily find that:
-    \begin{align}
-        e^{-i\phi S_z/\hbar}=e^{-i\frac{\phi}{2}\sigma_z}&=
-          \left(\begin{array}{cc}
-              e^{-i\frac{\phi }{2}} & 0 \\
-              0                     & e^{i\frac{\phi }{2}} \\
-         \end{array}\right)
-    \end{align}
-    Here a formula that encompass all the above relationship:
-    \begin{align}
-        \exp(\frac{-i\vec{\sigma}\cdot\hat{\vec{n}}\phi}{2})
-        =
-        \cos(\frac{\phi}{2})\mathbb{I}-i\vec\sigma\cdot\hat{\vec{n}}
-        \sin(\frac{\phi}{2})
-    \end{align}
-    where $\vec\sigma=(\sigma_x,\sigma_y,\sigma_z)$, and 
-    $\hat{\vec{n}}$ is any unit vector.
 \section{Miscellnaneous Notes}

### 2016-10-08 Notes about TR symmetry/Notes about TR symmetry.tex
Small fixes
Daily upate: correct error in homework. New notes about TR symmetry - kramer's theorem.

@@
 
-\subsection{Property of a symmetry operator}
+\subsection{Properties of a symmetry operator}
 \label{sec:Property-of-symmetry-operator}
@@
 
-    \subsection{From classical notion to property of TR symmetry}
+    \subsection{From classical notion to properties of TR symmetry}
     \label{sec:From-classical-notion-to-property-of-TR-symmetry}
@@
     \begin{align}
+        \label{eq:TRoper.TRoper.square_minus}
         \Theta^2 &= -1 \text{ if $j$ is a half-integer} \\
         \Theta^2 &= 1 \text{ if $j$ is an integer}
+        \label{eq:TRoper.TRoper.square_plus}
     \end{align}
@@
     \subsection{Kramer's theorem and the lifting of degenracy}
+    When one is concerned with the energy spectrum, one encounters the
+    Kramer's theorem, which says:
+    \begin{thm}[Kramer's theorem]
+        For a system with halt-integer $j$ spin, the degree of degeneracy
+        is at least two.
+    \end{thm}
+    \begin{proof}
+        Let $\ket{n}$ be an energy eigenstate. If the system is time
+        reversal symmetric, i.e. $[H,\Theta]=0$, then $\Theta \ket{n}$ is
+        another energy eigenstate with the same energy. Supposing there is
+        no degeneracy, then we have
+        $$ \ket{n} = e^{i\eta}\Theta\ket{n}$$
+        for some $\eta\in \mathbb{R}$. Apply $\Theta$ on both sides, then
+        we have
+        \begin{align*}
+            e^{-i\eta} \Theta^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
+            &= \Theta \ket{n} = e^{i\eta} \ket{n}
+        \end{align*}
+        Clearly this is a contracdiction unless $\Theta^2=1$, which is
+        true only for interger spin system by equation
+        \ref{eq:TRoper.TRoper.square_plus} and
+        \ref{eq:TRoper.TRoper.square_minus}.
+    \end{proof}
+    Another way to show this is presented in page 37 of
+    \cite{bernevig}. That method is too troublesome and basis dependent 
+    \footnote{Borrowing the jargon of mathematicians, not canonical,
+        geometric, or intrinsic.}
+    to be shown here.
+    But it shows an interesting fact that $\Theta^2=-1$, actually
+    implies that $U$, its unitary component mentioned in section
+    \ref{sec:Property-of-symmetry-operator}, is antisymmetric. This is
+    obvious when one juxtapose the following two facts:
+    $$ U (U^*)^T = \mathbbm{1}$$
+    $$ \Theta^2 = UKUK = U U^* = -\mathbbm{1} $$
 
+    By Kramer's theorem, one also says that for system with half-integer
+    spin, one \textit{lift the degenracy by breaking the time reversal
+    symmetry of the system.}
+
+    An additional point by Bernevig is about the transition probability
+    $\bra{\Theta \psi}H\ket{\psi}$ from a state to its time reversed
+    state.
+
+    \begin{align*}
+        & \braket{\Theta\psi|H|\psi} = (U_{mp}K\psi_p)^*H_{mn}\psi_n 
+        =U_{mp}^* \psi_p H_{mn} \psi_n = (U^\dagger)_pm\psi_p H_{mn}\psi_n
+        = (U^\dagger)_{pm}\psi_p (THT^{-1})_{mn} \psi_n
+        \\
+        &= (U^\dagger)_{pm}\psi_p \left(U_{mr}KH_{rq}(-U_{qn}K)\right)\psi_n\\
+        &= - (U^\dagger)_{pm}\psi_p \left(U_{mr}H^*_{rq}U^*_{qn}\right)\psi_n\\
+        &= - \psi_p \left((U^\dagger)_{pm}
+            U_{mr}\right)H^*_{rq}U^*_{qn}\psi_n\\
+        &= - \psi_p H^*_{pq}U^*_{qn}\psi_n\\
+            \overset{\text{by ...}}{=}& - \psi_p U^*_{pq}H_{qn}\psi_n \\
+        &= U^*_{qp}\psi_p H_{qn} \psi_n
+    \end{align*}
+    Either there is a mistake in Bernevig's derivation or I am wrong...
 \section{Anchor}

### 2016-10-09 Notes about TR symmetry/Notes about TR symmetry.tex
Updating TR Symmetry.

--- 2016-10-06 Notes about TR symmetry/Notes about TR symmetry.tex
@@
 \newtheorem{coro}{Corollary}[section]
+\newtheorem{fact}{Fact}[section]
 \theoremstyle{definition}
 \newtheorem{ex}{Example}[section]
+\newtheorem{argument}{Argument}[section]
 
@@
 
-    \subsection{From classical notion to property of TR symmetry}
+    \subsection{From classical notion to properties of TR symmetry}
     \label{sec:From-classical-notion-to-property-of-TR-symmetry}
     To get the time reversal operator, we can first look at the following
-    equality (let $\Theta$ dentoes the time reversal operator):
+    equality (let $T$ dentoes the time reversal operator):
     \begin{align}
-        \left(1-\frac{iH}{\hbar}\delta t\right) \Theta \ket{\alpha}
-        = \Theta\left(1-\frac{iH}{\hbar}(-\delta t)\right)\ket{\alpha}
+        \left(1-\frac{iH}{\hbar}\delta t\right) T \ket{\alpha}
+        = T\left(1-\frac{iH}{\hbar}(-\delta t)\right)\ket{\alpha}
         \label{eq:TRoper.fromClas2Quam.phyPic}
@@
     \begin{align}
-        -iH\Theta = \Theta i H
+        -iHT = T i H
     \end{align}
 
-    One can show that \textbf{$\Theta$ must be antilinear}. Because if one
-    assumes that $\Theta$ is linear, one will find that the energy
+    One can show that \textbf{$T$ must be antilinear}. Because if one
+    assumes that $T$ is linear, one will find that the energy
     spectrum for time reversal symmetric system will always has symmetric
@@
     \begin{itemize}
-        \item $\Theta$ is antiunitary.
-        \item $\Theta H=H\Theta$.
+        \item $T$ is antiunitary.
+        \item $T H=HT$ for a time reversal symmetric state.
     \end{itemize}
 
-    Recall that $\Theta= UK$, and $K$ is highly dependent on the basis
-    chosen. So $U$ will depend on the basis too. To get $\Theta$ in a
+    Recall that $T= UK$, and $K$ is highly dependent on the basis
+    chosen. So $U$ will depend on the basis too. To get $T$ in a
     basis $\ket{e_i}$, obviously we only need to consider the result of
@@
     \begin{align}
-        \Theta \hat{p} \Theta^{-1}&= -\hat{p} \\
-        \Theta \hat{x} \Theta^{-1}&= \hat{x} \\
-        \Theta \mathbf{J} \Theta^{-1}&= -\mathbf{J}
+        T \hat{p} T^{-1}&= -\hat{p} \\
+        T \hat{x} T^{-1}&= \hat{x} \\
+        T \mathbf{J} T^{-1}&= -\mathbf{J}
     \end{align}
@@
     \begin{align}
-        \Theta \ket{p} &= \ket{-p} \\
-        \Theta \ket{x} &= \ket{x} \\
-        [x_i, p_j]\Theta \ket{} &= i\hbar \delta_{ij} \Theta\ket{}
+        T \ket{p} &= \ket{-p} \\
+        T \ket{x} &= \ket{x} \\
+        [x_i, p_j]T \ket{} &= i\hbar \delta_{ij} T\ket{}
     \end{align}
-    where $\ket{}$ stands for any ket. Then clearly, $\Theta$ is just
-    complex conjugation for wave function $\Psi(x)$. But $\Theta$ acts on
+    where $\ket{}$ stands for any ket. Then clearly, $T$ is just
+    complex conjugation for wave function $\Psi(x)$. But $T$ acts on
     $\Psi(p)$ will produces $\Psi^*(-p)$. The case for eigenstate of
@@
 
+    \subsection{Properties of TR operator}
+    \label{sec:Properties-of-TR-operator}
+
     Following is a useful theorem, which is easy to proof (proof can be
@@
     \begin{thm}
+        \label{thm:TRoper.fromCM2QM.TR_nondegen_real}
         When Hamiltonian is invariant under time reversal and the energy
@@
 
-    \subsection{Time reversal operator in spin \texorpdfstring{$j$}{}}
+    The next theorem is about $T^2$. Classically, since there is only
+    two directions in time, we expect $T^2=1$. But quantum states are
+    rays, so there is the freedom of phase. Then $T^2 = \phi$ for
+    some $|\phi|^2=1$. But better, we have:
+
+    \begin{lemma}
+        $T^2 = \pm \mathbbm{1}$
+    \end{lemma}
+    \begin{proof}
+        Proof can be found on page 34 of \cite{bernevig}. But the proof is
+        so clever that I want to include it here. First observe that 
+        $U U^\dagger = \mathbbm{1}$, implies that $U^* U^T = \mathbbm{1}$
+        by transposing both sides. Next one use the expression $T=UK$ to
+        expand $T^2$, only to find that $U=\phi U^T$, this means that
+        $\phi^2=1$. Hence $\phi=\pm 1$.
+    \end{proof}
+
+    We then have the useful fact:
+    \begin{fact}
+        For any kets $\ket{\alpha},\ket{\beta}$, we have
+        \begin{align}
+            \pm \braket{\alpha|T\beta} = 
+                \braket{\beta|T\alpha}
+        \end{align}
+        The sign is the same as in $T^2=\pm 1$. Specifically, one has
+        \begin{align}
+            \braket{\alpha |T \alpha} = 0
+        \end{align}
+        when $T^2= -\mathbbm{1}$.
+    \end{fact}
+    \begin{proof}
+        This is simple by using 
+        $\braket{T\alpha|T\beta} = \braket{\beta|\alpha}$, 
+        and replacing $\ket{\alpha}$ with $\ket{T \alpha}$.
+    \end{proof}
+
+    \subsection{Time reversal operator in system with spin 
+    \texorpdfstring{$j$}{}}
     \label{sec:Time-reversal-operator-in-spin-j}
@@
     \begin{align}
-        \Theta \ket{\hat{\mathbf{n}};+} = \eta \ket{\hat{\mathbf{n}};-}
+        T \ket{\hat{\mathbf{n}};+} = \eta \ket{\hat{\mathbf{n}};-}
     \end{align}
@@
     \begin{align}
-        \Theta = \eta e^{-i\pi J_y/\hbar}K
+        T = \eta e^{-i\pi J_y/\hbar}K
     \end{align}
@@
     It is also interesting to note that in general:
-    \begin{align}
-        \Theta^2 &= -1 \text{ if $j$ is a half-integer} \\
-        \Theta^2 &= 1 \text{ if $j$ is an integer}
-    \end{align}
+    \begin{thm} \begin{align}
+        \label{eq:TRoper.TRoper.square_minus}
+        T^2 &= -1 \text{ if $j$ is a half-integer} \\
+        T^2 &= 1 \text{ if $j$ is an integer}
+        \label{eq:TRoper.TRoper.square_plus}
+    \end{align} \end{thm}
     However, this can only be proved when $j=\frac{1}{2}$, in which case
@@
     \subsection{Kramer's theorem and the lifting of degenracy}
+    \label{sec:Kramers-theorem-and-the-lifting-of-degenracy}
+    When one is concerned with the energy spectrum, one encounters the
+    Kramer's theorem, which says:
+    \begin{thm}[Kramer's theorem]
+        For a system with halt-integer $j$ spin, the degree of degeneracy
+        is at least two.
+    \end{thm}
+    \begin{proof}
+        Let $\ket{n}$ be an energy eigenstate. If the system is time
+        reversal symmetric, i.e. $[H,T]=0$, then $T \ket{n}$ is
+        another energy eigenstate with the same energy. Supposing there is
+        no degeneracy, then we have
+        $$ \ket{n} = e^{i\eta}T\ket{n}$$
+        for some $\eta\in \mathbb{R}$. Apply $T$ on both sides, then
+        we have
+        \begin{align*}
+            e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
+            &= T \ket{n} = e^{i\eta} \ket{n}
+        \end{align*}
+        Clearly this is a contracdiction unless $T^2=1$, which is
+        true only for interger spin system by equation
+        \ref{eq:TRoper.TRoper.square_plus} and
+        \ref{eq:TRoper.TRoper.square_minus}.
+    \end{proof}
+    Another way to show this is presented in page 37 of
+    \cite{bernevig}. That method is too troublesome and basis dependent 
+    \footnote{Borrowing the jargon of mathematicians, not canonical,
+        geometric, or intrinsic.}
+    to be shown here.
+    But it shows an interesting fact that $T^2=-1$, actually
+    implies that $U$, its unitary component mentioned in section
+    \ref{sec:Property-of-symmetry-operator}, is antisymmetric. This is
+    obvious when one juxtapose the following two facts:
+    $$ U (U^*)^T = \mathbbm{1}$$
+    $$ T^2 = UKUK = U U^* = -\mathbbm{1} $$
+
+    By Kramer's theorem, one also says that for system with half-integer
+    spin, one \textit{lift the degenracy by breaking the time reversal
+    symmetry of the system.}
+
+        \subsubsection{Argument against Bernevig's result}
+        \label{sec:Argument again Bernevig's result}
+
+        An additional point by Bernevig is about the transition probability
+        $\bra{T \psi}H\ket{\psi}$ from a state to its time reversed
+        state.
+
+        Here I first mention two points:
+        \begin{enumerate}
+            \item When $T H=HT$, and $T=UK$, one can deduce
+                $UH^* = HU$, or $U^*H=H^*U^*$, i.e.
+                $(U^*)_{mp}H_{pn}=(H^*)_{mp}(U^*)_{pn}$.
+            \item As mentioned before in section
+                \ref{sec:Kramers-theorem-and-the-lifting-of-degenracy},
+                $U$ is antisymmetric, so $U^*$ is antisymmetric too.
+        \end{enumerate}
+
+        Then begin Bernevig's wrong calculation (Summation implied when
+        index is repeated twice):
+        \begin{align}
+            & \braket{T\psi|H|\psi} = (U_{mp}K\psi_p)^*H_{mn}\psi_n 
+            \nonumber\\
+            =& U_{mp}^* \psi_p H_{mn} \psi_n 
+            \nonumber\\
+            =& (U^\dagger)_{pm}\psi_p H_{mn}\psi_n 
+            \label{eq:TRoper.Kramer.bernevig1}
+            \\
+            =& (U^\dagger)_{pm}\psi_p (THT^{-1})_{mn} \psi_n 
+            \nonumber\\       
+            =& (U^\dagger)_{pm}\psi_p \left(U_{mr}KH_{rq}(-U_{qn}K)\right)
+                \psi_n
+            \nonumber\\       
+            =& - (U^\dagger)_{pm}\psi_p \left(U_{mr}H^*_{rq}U^*_{qn}\right)
+                \psi_n
+            \nonumber\\       
+            =& - \psi_p \left((U^\dagger)_{pm}
+                U_{mr}\right)H^*_{rq}U^*_{qn}\psi_n
+            \nonumber\\       
+            =& - \psi_p H^*_{pq}U^*_{qn}\psi_n
+            \nonumber\\       
+            \text{(by point 1)}=& - \psi_p U^*_{pq}H_{qn}\psi_n 
+            \nonumber\\       
+            \text{(by point 2)}=& U^*_{qp}\psi_p H_{qn} \psi_n 
+            \nonumber\\       
+            \text{(by the first line)}=& \braket{T\psi|H|\psi}
+        \end{align}
+        So I see that he just circles back to the origin...
+
+        No I give an argument that statement in page 37 of
+        \cite{bernevig} cannot be true.
+        \begin{argument}
+            Suppose we can prove that $\braket{T \psi|H|\psi}=0$.
+            Then $\braket{\psi|HT |\psi}=0$, notice that $H=T
+            HT^{-1}$, and $T^{2}=-1$, one can see that
+            $\braket{\psi|H|\psi}=0$. Such is too strong an result. For
+            example, if $\ket{\psi}$ is any eigenket of $H$, then our
+            argument shows that its eigenvalue is zero. Does this means
+            that $H$ is just the trivial operator $0$? Of course not!
+            Therefore the Bernevig's result is wrong.
+        \end{argument}
+
+    \subsection{Time reversal symmetry in crystal}
+    \label{sec:Time-reversal-symmetry-in-crystal}
+
+        \subsubsection{Time reversal symmetry in spinless crystal}
+        \label{sec:Time-reversal-symmetry-in-spinless-}
+        Since there is not spin, time reversal symmetry does not alter a
+        creation/annihilation of a particle. Then:
+        \begin{align}
+            Tc_j T^{-1} = c_j
+        \end{align}
+        Then, in the fourier expansion of $c_j$:
+        \begin{align}
+            c_j = \sum_k e^{ikR_j} c_k
+        \end{align}
+        Since $T$ acting on the left, will change $e^{ikR_j}$ into
+        $e^{-ikR_j}$, then naturally:
+        \begin{align}
+            Tc_k T^{-1} = c_{-k}
+        \end{align}
+        Then, for a time reversal symmetric system, let 
+        $H = \sum_k h(k)c_k^\dagger c_k$. Since $T H T^{-1}=H$,
+        $T$ has to flip the sign of $k$ again, so:
+        \begin{align}
+            T h(k) T^{-1} = h(-k) \,\text{(For TR symmetric
+            state)}
+            \label{eq:TRoper.trInCry.trInSpinless.hk}
+        \end{align}
+
+        \paragraph{Implications for crystal systems} The above result has
+        profound implications for crystal with zero spin.
+        \begin{thm}
+            For crystal with zero spin, one has in crystal momentum space,
+            always at least a double degeneracy, except for certain point
+            symmetric to $k$ and $-k$.
+        \end{thm}
+        \begin{proof}
+            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
+            $\phi(k)$ and $T\phi(k)$ corresponding to eigenstate in
+            $k$ and $-k$. When $T$ acts on a wavefunction, its
+            creation operator is affected and its ... (paused here).
+        \end{proof}
 
@@
 \label{sec:Anchor}
-
 \begin{thebibliography}{1}

### 2016-10-10 Complex Geometry - index/misc/complex geometry-misc.tex
New class notes. A fews new lines in fibration (Complex Geometry)

@@
     \end{defi}
-    ref \cite{nlab-lift}.
+    Ref \cite{nlab-lift}.
 
@@
 
+    \begin{remark}
+        (From page 355, Fibration in chapter 11.)
+
+        If one defines the relationship as above, then one will find
+        something interesting out of these relations.
+
+        If one defines $h_1:Y\to B$ by $h_1(x)=F(x,0)$, then $f$ is a
+        lifting of $h_1$; if one defines $h_2:Y\to B$ by $h_2(x)=F(x,1)$,
+        then one sees $F$ actually induces homotopy $h_1\simeq h_2$.
+        Similarly, $\sigma$ is also a homotopy $f\simeq \widetilde f$,
+        where $\widetilde f=\sigma(x,1)$ is a lifting of 
+    \end{remark}
     \paragraph{Fibrations}
@@
     %            https://en.wikipedia.org/wiki/Fibration
+
 \section{Anchor}
@@
     \bibitem{nlab-homotopy-lifting-property}\href{https://ncatlab.org/nlab/show/homotopy+lifting+property}{nLab Homotopy lifting property}, \href{https://ncatlab.org/nlab/show/cartesian+product}{nLab Cartesian product}, \href{https://ncatlab.org/nlab/show/interval+object}{nLab Interval object}.
+    \bibitem{GTM119} Jossph J. Rotman. An Introduction to Algebraic
+    Topology. First Edition. GTM 119. Springer.
 \end{thebibliography}

### 2016-10-10 Lecture note - Group Theory in Physics/group theory in physics.tex
New class notes. A fews new lines in fibration (Complex Geometry)

--- 2016-09-27 Group Theory in Physics/group theory in physics.tex
@@
 \newtheorem{ex}{Example}[section]
+\newtheorem{fact}{Fact}[section]
 
+\usepackage{CJKutf8} % For chinese characters.
 % A list of nomenclatures.
@@
 
+\begin{CJK}{UTF8}{gbsn}
+固有转动是指的那些 $det(M)>0$ 的转动. 用$C_n$来表示他们.
+
+Also, 周期 of $R$ is just $\braket{R}$.
+\end{CJK}
+
+Let $\sigma$\nomenclature{$\sigma$}{\nomrefpage.} for spatial reflection.
 \begin{defi}[$C_N,\bar{C}_N$]
@@
 \end{defi}
+\section{20161010}
+\label{sec:20161010}
+Introducing to various groups:$S_4, V_4$, $D_3$, all omited.
+(\textbf{pp.22-23 of \cite{book}})
+
+$D_n$ group. See pp. 25-26 of the book \cite{book}.
+Note that here the $n$ refers to the $n$-polygon, not that the group is
+of order $n$. For the mathematicians, they might be comfortable with
+$D_n$ means the dihedral group of order $n$, but is actually the group of
+symmetries of $n/2$-polygon.
+
+\begin{defi}[Subgroup]
+\nomenclature{Subgroup}{\nomrefpage.}
+    Omitted.
+\end{defi}
+\begin{fact}
+    One only has to check the closeness for determining a subgroup, if it
+    is of finite order.
+
+    However, for group of infinite order, one has to check the existance
+    of unit and inverse elements.
+\end{fact}
+Examples of subgroup (\textbf{pp.26 of \cite{book}})
+
+Noteworth:$C_6$ has three copies of $D_2$, this can be intuitively 
+guessed by the fact that a hexago has three rectanle in it.
+
+\begin{defi}[Coset]
+\nomenclature{Coset}{\nomrefpage.}
+    Omitted.
+\end{defi}
+Properties of coset (omitted).
+
+\begin{defi}[Index of subgroup]
+\nomenclature{Index of subgroup}{\nomrefpage.}
+    Omitted.
+\end{defi}
+
+\begin{prop}
+    Two elements $R$ and $T$ belongs to the same coset $kH$, if and only
+    if $R^{-1}T\in H$.
+\end{prop}
+\begin{proof}
+    Omitted.
+\end{proof}
+\begin{defi}[Normal/Invariant subgroup]
+\nomenclature{Normal/Invariant subgroup}{\nomrefpage.}
+    A subgroupNormal/Invariant subgrouproup(also invariant), if and only
+    if for any $x\in G$, we have $xH = Hx$.
+\end{defi}
+\begin{fact}
+    If $H$ has index 2, then it must be normal/invariant. This is
+    obvious.
+\end{fact}
+\begin{defi}[Quotient]
+\nomenclature{Quotient}{\nomrefpage.}
+    Omitted.
+\end{defi}
+Note that quotient group (a.k.a. factor group) is only defined for a normal subgroup.
+
+\begin{ex}
+    $D_3$ (Using the multiplication table). Omitted because it is too
+    complex to be typed down here.
+\end{ex}
+
+\begin{defi}[Conjugate]
+\nomenclature{Conjugate}{\nomrefpage.}
+    If exists $S\in G$, s.t. $R' = S^{-1}RS$, then we say $R'$ is
+    conjugate to $R$.
+\end{defi}
+see (\textbf{pp.28-30 of \cite{book}})
+This is clearly an equivalence relationship. By this we can define
+conjugate class, denoted by $C=\{R_1,\cdots\}$, then we have the
+characterization $C = \{ s^{-1} R_i s|\forall s\in G\}$, for any
+$R_i$. We then have the following facts (all are obvious):
+\begin{fact}$ $
+
+    \begin{enumerate}
+        \item The unit class formed just by the unit element.
+        \item The inverse class formed by just all the inverse element.
+            $C^{-1} = \{ R_i^{-1}\}$. If $C=C^{-1}$, then $C$ is called
+            self-inverse.
+        \item The order of elements in a class is just the same.
+        \item For $\forall T,S\in G$, $TS$ and $ST$ are conjugate to each
+            other. This means that all elements symmetric on the
+            multiplication table is conjugate to each other.
+        \item For two elements $R$, $R'$ conjugate to each other, both
+            can be expressed by the products of two elements in two
+            different way. (Isn't this too obvious to mention.)
+        \item Let $G$ be a rotation group. Suppose it has an axis of the
+            order of $n$, with its operation denoted as $R$,, we can get
+            a new axis by the following steps. (Supose we have another
+            rotation $S$),
+
+            \begin{enumerate}
+                \item  $S^{-1}$, rotate $m$ back to $n$.
+                \item  $R$, rotate about n around $2\pi/n$,
+                \item  $S$ rotate $n$ to $m$
+            \end{enumerate}
+
+            Result: $S^{-1}RS$ rotate around a new axis $m$ about
+            $2\pi/n$. So $R'=S^{-1}RS$ and $R$ is calle the equivalent
+            axis.
+
+            Also, if $m=-n$, then they are called polar axis to each
+            other.
+
+        \item $C_n$, which is an abel group, every element form a
+            conjugate class by itself. Specifically, $e$ and $R^{n/2}$
+            are self inverse, if $n$ is even.
+    \end{enumerate}
+\end{fact}
+\begin{prop}
+    \label{prop:20161010.conjugate_subgroup}
+    For an invariant subgroup, then every conjugate element is also
+    inside the same invariant subgroup. This shows that an invariant
+    subgroup can be decomposed into a series of sum of conjugate classes.
+\end{prop}
+\begin{proof}
+    If $R\in H$, then we show that $S^{-1}RS\in H$, this is obviously
+    since it belongs to $S^{-1}HS$.
+\end{proof}
+
+\begin{ex}
+    For $D_3: E,D,F,A,B,C$, their orders are respetively
+    $1,3,3,2,2,2$. We have the following conjugate classes:
+    \begin{enumerate}
+        \item $\{ E\}$. Is self inverse.
+        \item $\{ D,F\}$. $D$ is conjugate to $F$. We can see
+            this physically by looking at rotation from the front
+            or the below. This class is also self-inverse.
+        \item $\{A,B,C\}$, is clearly a self-inverse conjugate
+            class.
+    \end{enumerate}
+\end{ex}
+\begin{ex}[$D_6$]
+    Ramiliarize one with the formulae for $D_n$. Hint: use the order of
+    elements to find classes of conjugate. Then use the proposition
+    \ref{prop:20161010.conjugate_subgroup} to find the subgroups.
+    % TODO maybe I can try this when I am free.
+\end{ex}
+
 \section{Anchor}
 \label{sec:Anchor}
-
 \begin{thebibliography}{1}

### 2016-10-19 Notes of Advanced Quantum Mechanics/Homeworks/161012/HW2_sol. 11310075.tex
Make up update.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{bbm} % for numbers within mathbb
\usepackage{mathrsfs} % For \mathscr{ABC}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage{CJKutf8}

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

% For drawing diagrams with arrows
\usepackage[all]{xy}

\title{Solution for HW2 20161013}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
\begin{CJK}{UTF8}{gbsn}陈鸿翔（11310075）\end{CJK}
}
%\tableofcontents
\section{Describe wave function}
Wave functgion is a function that is assumed to be describing the
physical system. It is assumed that all physical information can be
extracted from it, which is saying that a wave function is the
complete description of the physical system it is complete. And we
calculate any observable $A$ by calculating its expectation value
using the wave function.

As for the probability wave, I thick this is kind of a misnomer. It is
the wave function that propagates in the form of waves, as can be seen
by the following formal solution to the schrodinger equation:

\begin{align}
    i\hbar \frac{\partial}{\partial t} \Psi = H \Psi \nonumber\\
    \Rightarrow \Psi(t) = e^{-i\hbar H} \Psi(t=t_0)
\end{align}

However, the probability is determined by the absolute value of
wavefunction, so it does not exactly propagate like a wave.

\section{Eigensystems}

$\bullet e^x$: $\frac{\diff^2}{\diff x^2} e^x = e^x$, so it IS an
eigenfunction, with eigenvalue $1$.

$\bullet \sin(x)$: $\frac{\diff^2}{\diff x^2} \sin(x) = -\sin(x)$, so
it IS an eigenfunction, with eigenvalue $-1$.

$\bullet 2\cos(x)$: $\frac{\diff^2}{\diff x^2} 2\cos(x) = 2
(-\cos(x)) = - (2\cos(x))$, so it IS an eigenfunction, with eigenvalue
$-1$.

$\bullet \sin^2(x)$: $\frac{\diff^2}{\diff x^2} \sin^2(x) =
\frac{\diff}{\diff x}2 \cos(x) = -2 \sin(x)$, so it is NOT an
eigenfunction.

$\bullet x^3$: $\frac{\diff^2}{\diff x^2} x^3 = 6x$, so it is NOT an
eigenfunction.

$\bullet \sin(x)+\cos(x)$: the combination of two eigenfunction with
the same eigenvalue is of course an eigenfunction, with eigenvalue
$-1$.

\section{1D infinite potential well}
The time-independent Schrodinger equation inside the wall is:
$$ -\frac{\hbar^2}{2m} \frac{\diff^2}{\diff x^2} \psi = E\psi$$,
so clearly
$$\psi = A \sin(kx) + B\cos(kx)$$
inside the wall. Here $k=\sqrt{\frac{2mE}{\hbar^2}}$.

Outside the wall the potential is infinite, not suitable for
wavefunction to live. So $\psi=0$ outside. Connecting the wave
function in the boundary will clearly leads to dicretized wavelength.
But the give coordinate is not convenient to determine the parameters
$A,B$. So I shift the origin leftwards for $\frac{a}{2}$. Then the
potential becomes:
$$
U = \begin{cases}
    0& 0\leq x\leq a \\
    \infty& \text{otherwise}
\end{cases}
$$
Then we have $\psi(0)=0$, hence $B=0$. And $\psi(a)=0$, hence
$$ \sqrt{\frac{2mE}{\hbar^2}} a = n\pi \Rightarrow$$
$$ E = \frac{n^2\pi^2\hbar^2}{2ma^2}$$
where $n=1,2,\cdots$. $A$ is determined by normalization, but I don't
have to calculate because the next exercise has already given the
answer: $A = \sqrt{\frac{2}{a}}$. Now shift the coordinate back, I
have
\begin{align}
    \psi(x) &= \sqrt{\frac{2}{a}}\sin\left(k(x-\frac{a}{2})\right)
            =\sqrt{\frac{2}{a}}
                \sin\left(\frac{n\pi}{a}(x-\frac{a}{2})\right)\\
    k       &= \sqrt{\frac{2mE}{\hbar^2}}\\
    E       &= \frac{n^2\pi^2\hbar^2}{2ma^2}
\end{align}

\section{Prove the orthogonality}
This is simple:
\begin{align*}
    &\int_{0}^{l} \sin(\frac{n\pi x}{l}) \sin(\frac{m\pi x}{l})\\
    =& \int_{0}^{l} \frac{ 
        \cos(\frac{(n-m)\pi x}{l}) - \cos(\frac{(n-m)\pi x}{l})
        } {2}
\end{align*}
Notice that when $n\neq m$, both $\cos(\frac{(n-m)\pi x}{l})$ and
$\cos(\frac{(n-m)\pi x}{l})$ oscillate with the period of $l$. That
means the integration is taken over a whole peroid. So the result is
$0$, i.e.:
\begin{align}
    \int_{0}^{l} \sin(\frac{n\pi x}{l}) \sin(\frac{m\pi x}{l})=0
\end{align}
for $m\neq n$.
\end{document}

### 2016-10-19 GRE Physics Prep/General Physics Formula.tex
Preparing for GRE Physics test.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{bbm} % for numbers within mathbb
\usepackage{mathrsfs} % For \mathscr{ABC}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\newtheorem{fact}{Fact}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]
\newtheorem{argument}{Argument}[section]

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

% For drawing diagrams with arrows
\usepackage[all]{xy}

% For highlighting
\usepackage{color,soul}

\title{General Physics Formula}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
This is a collection of important formulae in Fundamentals of Physics
Extended Version by Halliday and Resnick.
}
\tableofcontents

\section{Classical mechanics}
\label{sec:Classical-mechanics}

\paragraph{Constant Accleration}
These five equations in Table 2-1 describe the motion of a particle with constant acceleration:
\begin{align}
    v           &= v_0 + at \\
    x-x_0       &= v_0 t + \frac{1}{2} at^2\\
    x-x_0       &= vt - \frac{1}{2} at^2\\
    v^2 - v_0^2 &= 2a(x-x_0)\\
    x-x_0       &= \frac{1}{2} (v_0+v) t
\end{align}

\paragraph{Projectile Motion} Projectile motion is the motion of a
particle that is launched with an initial velocity $\vec v_0$. During
its flight, the particle’s horizontal acceleration is zero and its
vertical acceleration is the free-fall acceleration $-g$. (Upward is
taken to be a positive direction.) If $\vec v_0$ is expressed as a
magnitude (the speed $v_0$) and an angle $\theta_0$ (measured from the
horizontal), the particle’s equations of motion along the horizontal x
axis and vertical y axis are
\begin{align}
    x-x_0 &= (v_0 \cos(\theta_0) ) t \\
    y-y_0 &= (v_0 \sin(\theta_0) ) t - \frac{1}{2} gt^2 \\
    v_y   &= v_0 \sin{\theta_0} - gt \\
    v_y^2 &= (v_0 \sin{\theta_0})^2 - 2g (y-y_0)
\end{align}
The \textbf{trajectory} (path) of a particle in projectile motion is
parabolic and is given by
\begin{align}
    y &= (\tan{\theta_0}) x - \frac{gx^2}{2(v_0 \cos{\theta_0})^2} 
\end{align}

\paragraph{Uniform Circular Motion} If a particle travels along a circle
or circular arc of radius $r$ at constant speed $v$, it is said to be in
\textit{uniform circular motion} and has an acceleration of constant
magnitude
\begin{align}
    a = \frac{v^2}{r}
\end{align}
The direction of is toward the center of the circle or circular arc,
and is said to be centripetal. The time for the particle to complete
a circle is
\begin{align}
    T=\frac{2\pi r}{v}
\end{align}
$T$ is called the period of revolution, or simply the period, of the
motion.

This acceleration is due to a net centripetal force on the particle,
with magnitude given by
\begin{align}
    F = \frac{mv^2}{R}
\end{align}
where $m$ is the particle’s mass. The vector quantities $\vec a$ and
$\vec F$ are directed toward the center of curvature of the particle’s
path
\begin{defi}[Normal force]
\nomenclature{Normal force}{\nomrefpage.}
A \textbf{normal force} is the force on a body from a surface against
which the body presses.The normal force is always perpendicular to the
surface.
\end{defi}

\paragraph{Drag Force} When there is relative motion between air (or
some other fluid) and a body, the body experiences a drag force $\vec
D$
that opposes the relative motion and points in the direction in
which the fluid flows relative to the body. The magnitude of $\vec D$is
related to the relative speed $v$ by an experimentally determined
drag coefficient $C$ according to
\begin{align}
    D=\frac{1}{2} C\rho A v^2
\end{align}
where $\rho$ is the fluid density (mass per unit volume) and $A$ is
the effective cross-sectional area of the body (the area of a cross
section taken perpendicular to the relative velocity $\vec v$)

Power The power due to a force is the rate at which that force
does work on an object. For a force $\vec F$ at an angle $\phi$ to the
direction of travel of the instantaneous velocity $\vec v$, the
instantaneous power is
\begin{align}
    P = Fv \cos{\phi} = \vec{F} \cdot \vec{v}
\end{align}

\paragraph{Collision and Impulse} Applying Newton’s second law in
momentum form to a particle-like body involved in a collision
leads to the impulse–linear momentum theorem:
\begin{align}
    \vec{p}_f - \vec{p}_i = \int_{t_i}^{t_f} \vec{F} \diff t
\end{align}
where the LHS is the change in the body’s linear
momentum, and RHS is defined as the impulse $\vec{J}$ due to the force
exerted on the body by the other body in the collision.

\paragraph{Elastic Collisions in One Dimension} An elastic collision
is a special type of collision in which the kinetic energy of a system
of colliding bodies is conserved. If the system is closed and
isolated, its linear momentum is also conserved. For a one-dimensional
collision in which body $2$ is a target and body $1$ is an incoming
projectile, conservation of kinetic energy and linear momentum yield
the following expressions for the velocities immediately after the
collision:
\begin{align}
    v_{1f} &= \frac{m_1-m_2}{m_1+m_2} v_{1i} \\
    v_{2f} &= \frac{2m_1}{m_1+m_2} v_{1i}
\end{align}

Variable-Mass Systems In the absence of external forces a rocket
accelerates at an instantaneous rate given by
\begin{align}
    R v_{\text{rel}} = Ma \text{(first rocket equation)}
\end{align}
in which $M$ is the rocket’s instantaneous mass (including
unexpended fuel), $R$ is the fuel consumption rate, and $v_{\text{rel}}$ is the fuel’s
exhaust speed relative to the rocket. The term $R v_{\text{rel}}$ is the thrust of
the rocket engine. For a rocket with constant R and $v_{\text{rel}}$, whose speed
changes from $v_i$ to $v_f$ when its mass changes from $M_i$ to $M_f$,
\begin{align}
    v_f - v_i = v_{\text{rel}} \ln\frac{M_i}{M_f} \text{(second rocket
    equation)}
\end{align}
($R\equiv |\frac{\diff M}{\diff t}|$)

\paragraph{The Kinematic Equations for Constant Angular Acceleration}
Constant angular acceleration ($\alpha =$a constant) is an important
special case of rotational motion. The appropriate kinematic
equations, given in Table 10-1, are
\begin{align}
    \sigma &= \sigma_0 + \alpha t \\
    \theta - \theta_0 &= \omega_0 t + \frac{1}{2} \alpha t^2 \\
    \theta - \theta_0 &= \omega t - \frac{1}{2} \alpha t^2 \\
    \omega^2 - \omega_0^2 &= 2\alpha (\theta - \theta_0) \\
    \theta - \theta_0 &= \frac{1}{2}(\omega_0 + \omega) t
\end{align}

\paragraph{Linear and Angular Variables Related} A point in a rigid
rotating body, at a perpendicular distance $r$ from the rotation axis,
moves in a circle with radius $r$.

The linear acceleration $\vec{a}$ of the point \hl{has both tangential and
radial components}.The tangential component is
\begin{align}
    a_t = \alpha r
\end{align}
where $\alpha$ is the magnitude of the angular acceleration (in radians
per second-squared) of the body.The radial component of $\vec{a}$ is
\begin{align}
    a_r = \frac{v^2}{r} = \omega^2 r
\end{align}
If the point moves in uniform circular motion, the period $T$ of
the motion for the point and the body is
\begin{align}
    T = \frac{2\pi r}{v} = \frac{2\pi}{\omega}
\end{align}
\paragraph{Rotational Kinetic Energy and Rotational Inertia} The
kinetic energy $K$ of a rigid body rotating about a fixed axis is
given by
\begin{align}
    K=\frac{1}{2} I\omega^2
\end{align}
in which $I$ is the rotational inertia of the body, defined as
\begin{align}
    I \equiv \int r^2 \diff m
\end{align}
\paragraph{The Parallel-Axis Theorem} 265
\begin{align}
    I = I_{\text{com}} + M h^2
\end{align}

\paragraph{Work and Rotational Kinetic Energy} 265
\begin{align}
    W = \int_{\theta_i}^{\theta_f} \tau \diff \theta \\
    P = \frac{\diff W}{\diff t} = \tau \omega
\end{align}

\paragraph{Rolling Bodies}
[295]
\begin{align}
    v_\text{com} &= \omega R\\
    K  &= \frac{1}{2}I_\text{com}\omega^2 + \frac{1}{2}Mv_\text{com}^2
    \\
    a_\text{com} = \alpha R
\end{align}
\paragraph{Precession of a Gyroscope}
\begin{align}
    \Omega = \frac{Mgr}{I\omega}
\end{align}

\paragraph{Elastic Moduli} [319]
\begin{center}
    stress $=$ modulus $\times$ strain
\end{center}

Young's modulus:
\begin{align}
    \frac{F}{A} = E \frac{\Delta L}{L}
\end{align}

Shear's modulus:
\begin{align}
    \frac{F}{A} = G \frac{\Delta x}{L}
\end{align}

Hydraulic bulk modulus:
\begin{align}
    p = B \frac{\Delta V}{V}
\end{align}

\paragraph{Gravitational Potential Energy} [349]
\begin{align}
    U = -\frac{GMm}{r}
\end{align}

\textbf{Escape speed}
\begin{align}
    v = \sqrt{ \frac{2GM}{R} }
\end{align}

\textbf{Kepler's Laws}
\begin{enumerate}
    \item The law of orbits. All planets move in elliptical orbits
        with the Sun at one focus.
    \item The law of areas. A line joining any planet to the Sun
        sweeps out equal areas in equal time intervals. (This
        statement is equivalent to conservation of angular momentum.)
    \item The law of periods. The square of the period $T$ of any
        planet is proportional to the cube of the semimajor axis a of
        its orbit. For circular orbits with radius $r$,
    \begin{align}
        T^2 = \left(\frac{4\pi^2}{GM}\right) r^3
    \end{align}
        where $M$ is the mass of the attracting body—the Sun in the
        case of the solar system. For elliptical planetary orbits, the
        semimajor axis $a$ is substituted for $r$.
\end{enumerate}

\textbf{Energy in Planetary Motion}
\begin{align}
    U &= -\frac{GMm}{r} \\
    K &= \frac{GMm}{2r} \\
    E &= -\frac{GMm}{2r} \,\text{ or} \\
    E &= -\frac{GMm}{2a} 
\end{align}

\paragraph{Flow of Ideal Fluids}[377]
\begin{defi}[Apparent weight]
\nomenclature{Apparent weight}{\nomrefpage.}
    Omited
\end{defi}

\textbf{Equation of continuity}
\begin{align}
    R_v \equiv Av = \text{ a constant}
\end{align}
\textbf{Bernoulli's Equation}
\begin{align}
    p + \frac{1}{2}\rho v^2 + \rho gh = \text{ a constant}
\end{align}

\paragraph{Oscillation} (\textbf{pp.403 of \cite{book}})
\begin{align}
    \omega &= \frac{2\pi}{T} = 2\pi f
\end{align}
\textbf{Linear Oscillator}
\begin{align}
    & \omega = \sqrt{\frac{k}{m}} \\
    & T = 2\pi \sqrt{\frac{m}{k}} 
\end{align}
\textbf{Pendulums}
\begin{align}
    & T = 2\pi \sqrt{I/\kappa} \\
    & T = 2\pi \sqrt{L/g} \\
    & T = 2\pi \sqrt{I/mgh}
\end{align}
\textbf{Damped Harmonic Motion}
\begin{align}
    & x(t) = x_m e^{-bt/2m} \cos\left( \omega' t+\phi\right) \\
    & \omega' = \sqrt{ \frac{k}{m} - \frac{b^2}{4m^2} } \\
    & E(t)\approx \frac{1}{2} kx_m^2 e^{-bt/m}
\end{align}
\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
\begin{align}
    & y(x,t) = y_m \sin(kx-\omega t) \\
    & k = \frac{2\pi}{\lambda} \\
    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
\end{align}
\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

\paragraph{Conduction} (\textbf{pp.498 ch18 of \cite{book}})
\textbf{Thermal expansion}
\begin{align}
    & \Delta L = L \alpha \Delta T \\
    & \Delta V = V \beta \Delta T \\
    & \beta = 3 \alpha \\
    & Q = C \Delta T = cm \Delta T
\end{align}
\begin{defi}[Convection]
\nomenclature{Convection}{\nomrefpage.}
    Convection occurs when temperature differences cause an energy
    transfer by motion within a fluid
\end{defi}
\textbf{Radiation}
\begin{align}
    & P_\text{rad} = \sigma \varepsilon AT^4 \\
    & P_\text{abs} = \sigma \varepsilon AT_\text{evn}^4
\end{align}
\textbf{Conduction}
\begin{align}
    P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L} 
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond}.png}
\end{figure}

\paragraph{Thermal Process} (\textbf{pp.529 ch19 of \cite{book}})
Thermal process:
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        No. & Constant Quaility            & Process Type & Special Results  \\
        \hline
        1   & $p$                          & Isobaric     & $Q = nC_p\Delta T;W=p\Delta V$ \\
        2   & $V$                          & Isothermal   & $Q=W=nRT\ln(V_f/V_i); \Delta E_\text{int}=0$  \\
        3   & $pV^\gamma$, $TV^{\gamma-1}$ & Adiabatic    & $W=-\Delta E_\text{int}$ \\
        4   & $V$                          & Isochoric    & $Q=\Delta E_\text{int}=nC_V \Delta T;W=0$ \\
        \hline
    \end{tabular}
\end{table}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.therm_pro}.png}
\end{figure}
Isothermal Process:
\begin{align}
    W = Nk T \ln\frac{V_f}{V_i}
\end{align}
\textbf{Temperature and Kinetic Energy}
\begin{align}
    & K_\text{avg} = \frac{3}{2}kT \text{, per molecule} \\
    & \lambda = \frac{1}{\sqrt{2} \pi d^2 N/V} 
\end{align}
\paragraph{Molar Specific Heats}
\begin{align}
    & C_V = \frac{3}{2} R \\
    & C_P = C_V + R \\
    & \Delta E_\text{int} = N C_V \Delta T \\
    & C_V = \frac{f}{2} k \\
    & \gamma \equiv \frac{C_P}{C_V}
\end{align}

\paragraph{Entropy} (\textbf{pp.554 ch20 of \cite{book}})

\begin{align}
    & \diff S = \frac{\diff Q}{T} \\
    & \Delta S = nR \ln{\frac{V_f}{V_i}} + nC_V \ln{\frac{T_f}{T_i}}
    \\
    & \varepsilon = 1-\frac{T_L}{T_H}  \text{ (Carnot engine)} \\
    & K = \frac{T_L}{T_H-T_L} \text{ (Carnot refrigerator)}  \\
    & \ln{N!} \approx N\ln{N} - N
\end{align}

\paragraph{Electric field} (\textbf{pp.596 ch22 of \cite{book}})
\begin{align}
    & E = \frac{1}{4\pi \varepsilon_0} \frac{q}{r^2} \\
    & E = \frac{1}{2\pi \varepsilon_0} \frac{p}{z^3} \\
    & U = - \vec{p}\cdot \vec{E} 
\end{align}

\paragraph{Gauss's Law} (\textbf{pp.620 ch23 of \cite{book}})

\begin{align}
    & E = \frac{\sigma}{\varepsilon_0}\text{ ,charged conductor} \\
    & E = \frac{\sigma}{2\varepsilon_0}\text{ ,infinite sheet} \\
    & E = \frac{\lambda}{2\pi\varepsilon_0 r} \\
    & E = 0 \text{ , inside charged shell} \\
    & E = \left(\frac{q}{4\pi\varepsilon_0 R^3}\right) r
\end{align}

\paragraph{Electric Potential} (\textbf{pp.646 ch24 of \cite{book}})

\begin{align}
    & V = \frac{1}{4\pi\varepsilon_0}\frac{q}{r} \\
    & V = \frac{1}{4\pi\varepsilon_0}\frac{p\cos\theta}{r^2} \\
    & U = \frac{1}{4\pi\varepsilon_0}\frac{q_1 q_2}{r}
\end{align}

\paragraph{Capacitor} (\textbf{pp.675 ch25 of \cite{book}})

\begin{align}
    & C \equiv \frac{q}{V} \\
    & C = \frac{\varepsilon_0 A}{d} \text{ (parallel-plate)} \\
    & C = 2\pi \varepsilon_0 \frac{L}{\ln{b/a}} 
            \text{ (cylindrical)}\\
    & C = 4\pi \varepsilon_0 \frac{ab}{b-a} \text{ (spherical)}\\
    & C = 4\pi \varepsilon_0 R \text{ (isolated spherical)} \\
    & C = \sum_j C_j \text{ (parallel)} \\
    & \frac{1}{C} = \sum_j \frac{1}{C_j} \text{ (series)}  \\
    & U = \frac{1}{2}\frac{q^2}{C} = \frac{1}{2}CV^2 \\
    & u = \frac{1}{2}\varepsilon_0 E^2
\end{align}

\paragraph{Current} (\textbf{pp.698 ch26 of \cite{book}})

\begin{align}
    & \vec{J} = ne \vec{v}_d \\
    & \rho \equiv \frac{1}{\sigma} = \frac{E}{J} \\
    & \vec{E} = \rho \vec{J} \\
    & R = \rho \frac{L}{A} \\
    & \rho - \rho_0 = \rho_0 \alpha (T-T_0) \\
    & \rho = \frac{m}{e^2 n\tau }
\end{align}

\paragraph{Electro motive force} (\textbf{pp.724 ch27 of \cite{book}})

\begin{align}
    & \mathcal{E} = \frac{\diff W}{\diff q}
\end{align}

\textbf{Circuit Rule}
\begin{itemize}
    \item \textbf{Loop Rule}. The algebraic sum of the changes in
        potential encountered in a complete traversal of any loop of a
        circuit must be zero.
    \item \textbf{Junction Rule}. The sum of the currents entering any
        junction must be equal to the sum of the currents leaving that
        junction
\end{itemize}

\begin{align}
    & R = \sum_j R_j \text{ , series} \\
    & \frac{1}{R} = \sum_j \frac{1}{R_j} \text{ , parallel}
\end{align}

\paragraph{Magnetic Field} (\textbf{pp.755 ch28 of \cite{book}})

\begin{align}
    & qvB = \frac{mv^2}{r} \\
    & T = \frac{2\pi r}{ rqB / m} = \frac{2\pi m}{qB} \\
    & \vec\tau = \vec{\mu} \times \vec{B} \\
    & U(\theta) = -\vec\mu \cdot \vec B
\end{align}

\paragraph{Magnetic -> Electricity} (\textbf{pp.781 ch29 of
\cite{book}})

\begin{align}
    & \diff \vec{B} = \frac{\mu_0}{4\pi}
        \frac{i\diff \vec{s}\times\hat{r}}{r^2} \\
    & B = \frac{\mu_0 i}{2\pi R} \\
    & B = \frac{\mu_0 i \phi}{4\pi R} \\
    & B = \mu_0 i N/L \\
    & B = \frac{\mu_i i N}{2\pi}\frac{1}{r} \\
    & \vec{B}(z) = \frac{\mu_0}{2\pi}\frac{\vec{\mu}}{z^3}
\end{align}

\paragraph{Faraday's Law} (\textbf{pp.816 ch30 of \cite{book}})

\begin{align}
    \mathcal{E} = \int \vec{E} \diff \vec{s} \\
\end{align}
\textbf{Inductance}
\begin{align}
    & L \equiv \frac{N\Phi_B}{i} \\
    & \frac{L}{l} = \mu_n n^2 A \\
    & \mathcal{E}_L = - L\frac{\diff i}{\diff t} \\
    & U_B = \frac{1}{2} L i^2 \\
    & u_B = \frac{1}{2} \frac{B^2}{\mu_0} 
\end{align}
\section{Anchor}
\label{sec:anchor}
\begin{thebibliography}{1}
    \bibitem{book} Fundamentals of Physics, Extended Edition. Halliday
    \& Resnick.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-10-20 GRE Physics Prep/General Physics Formula.tex
New GRE physics prepare.

@@
 
+\section{Fluid}
+\label{sec:Fluid}
+
 \paragraph{Flow of Ideal Fluids}[377]
@@
 \end{align}
+
+\section{Wave}
+\label{sec:Wave}
 
@@
 \end{align}
+
 \paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
@@
 \end{align}
+
+\section{Thermal Physics}
+\label{sec:Thermal-Physics}
 
@@
 \end{align}
+
+\section{Electrodynamics}
+\label{sec:Electrodynamics}
 
@@
 \begin{align}
-    \mathcal{E} = \int \vec{E} \diff \vec{s} \\
+    \mathcal{E} = \oint \vec{E} \diff \vec{s} \\
 \end{align}
@@
 \end{align}
+
+\paragraph{LC Circuit} (\textbf{pp.853 ch31 of \cite{book}})
+
+\begin{align}
+    & U_E = \frac{q^2}{2C} \\
+    & U_B = \frac{L i^2}{2} \\
+    & \omega = \frac{1}{\sqrt{LC}}
+\end{align}
+Predicting RLC current (\textbf{pp.843 of \cite{book}})
+
+\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})
+
+\begin{align}
+    & \oint \vec{E} \cdot \diff \vec{A} = q_\text{enc}/\varepsilon_0
+    \\
+    & \oint \vec{B} \cdot\diff\vec{A} = 0 \\
+    & \oint \vec{E}\cdot\diff\vec{s} = -\frac{\diff\Phi_B}{\diff t} \\
+    & \oint \vec{B}\cdot\diff\vec{s} = 
+    \mu_0\varepsilon_0 \frac{\diff\Phi_E}{\diff t} +\mu_0 i_\text{enc}
+    \nonumber\\
+    & \,= \mu_0 i_d + \mu_0 i_\text{enc}
+\end{align}
+
+(\textbf{pp.882 ch32 of \cite{book}})
+
+\textbf{Spin}
+\begin{align}
+    & \mu_s = -\frac{e}{m} S \\
+    & \mu_B = \frac{e\hbar}{2m} = 9.27\times 10^{-24} \text{J/T} \\
+    & \mu_\text{orb} = -\frac{e}{2m} L_\text{orb}
+\end{align}
+\textbf{Curie's law} 
+\begin{align}
+    M = C\frac{B_\text{ext}}{T}
+\end{align}
+
+\paragraph{Optics} (\textbf{pp.913 ch33 of \cite{book}})
+\begin{align}
+    & \vec{S} = \frac{1}{\mu_0} \vec{E}\times\vec{B} \\
+    & F = \frac{IA}{c} \text{ (total absorption)} \\
+    & F = \frac{2IA}{c} \text{ (total reflection)} \\
+    & I = I_0 \cos^2{\theta} \\
+    & n_1 \sin{\theta_1} = n_2 \sin{\theta_2} \\
+    & \theta_c = \sin^{-1}\frac{n_2}{n_1} \\
+    & \theta_B = \tan^{-1}\frac{n_2}{n_1}
+\end{align}
+
+\paragraph{Optics 2} (\textbf{pp.948 ch34 of \cite{book}})
+\begin{align}
+    \text{Omitted}
+\end{align}
+
+\paragraph{Interference} (\textbf{pp.981 ch35 of \cite{book}})
+
+\begin{align}
+    & \lambda_n = \frac{\lambda}{n} \\
+    & 2L = (m+\frac{1}{2})\frac{\lambda}{n_2} \text{ (thin film, max)}
+    \\
+    & d\sin{\theta} = m\lambda \text{ (Young's, max)}
+\end{align}
+
+\paragraph{Diffraction} (\textbf{pp.1013 ch36 of \cite{book}})
+
+\begin{align}
+    a\sin{\theta} &= m \lambda \text{, $m=1,2,\cdots$ (single-slit
+    minima)} \\
+    \theta_R &= 1.22\frac{\lambda}{d} \text{ (Rayleigh's criterion)}
+    \\
+    I(\theta) &=  I_m
+      (\cos^2\beta)\left(\frac{\sin{\alpha}}{\alpha}\right)^2 \\
+    \beta &= (\pi d/\lambda),\, \alpha = (\pi a/\lambda)\sin\theta \\
+    d\sin{\theta} &= m\lambda \text{, $m=0,1,2\cdots$ (diffraction
+      grating maxima)} \\
+    2d\sin{\theta} &= m\lambda \text{, $m=1,2,\cdots$ (Bragg's law)}
+\end{align}
+
+\paragraph{Relativity} (\textbf{pp.1048 ch37 of \cite{book}})
+\begin{align}
+    \Delta t &= \gamma \Delta t_0 \\
+    L &= L_0/\gamma \\
+    x' &= \gamma(x-vt) \\
+    t' &= \gamma(t-vx/c^2) \\
+    u &= \frac{u'+v}{1+u'v/c^2} \\
+    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}} \\
+    f &= f_0 \sqrt{1-\beta^2} \\
+    \vec{p} &= \gamma m \vec{v} \\
+    E &= mc^2 + K = \gamma mc^2 \\
+    E^2 &= (pc)^2 + (mc^2)^r
+\end{align}
+
+\paragraph{Photon} (\textbf{pp.1077 ch38 of \cite{book}})
+\begin{align}
+    & E = h f \\
+    & p= \frac{hf}{c} = \frac{h}{\lambda} \\
+    & hf = K_\text{max} + \Phi_\text{work function} \\
+    & \Delta\lambda = \frac{h}{mc}(1-\cos{\phi})
+\end{align}
+
+\paragraph{Conductions} (\textbf{pp.1160 ch41 of \cite{book}})
+\begin{align}
+    P(E) &= \frac{1}{e^{(E-E_F)/kT} +1} 
+\end{align}
+
 \section{Anchor}

### 2016-10-20 Notes about TR symmetry/Notes about TR symmetry.tex
My C.V..

@@
 
-        \paragraph{Implications for crystal systems} The above result has
-        profound implications for crystal with zero spin.
+        \begin{remark}[Implications for crystal systems]
+            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
+            $\phi(k)$ and $T\phi(k)$ corresponding to two eigenstate in
+            $k$ and $-k$. But since $\bra{\alpha}\ket{T\alpha}$ is not
+            necessarily $0$ for $T^2= \mathbbm{1}$, We cannot prove
+            that we have a double generacy because the two candidate
+            $h(k)$ and $h(-k)$ might be the same wave function.
+        \end{remark}
+
+        Another important implication is that
         \begin{thm}
-            For crystal with zero spin, one has in crystal momentum space,
-            always at least a double degeneracy, except for certain point
-            symmetric to $k$ and $-k$.
+            Hall Conductance vanishes for Spinless time
+            symmetric system.  
         \end{thm}
         \begin{proof}
-            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
-            $\phi(k)$ and $T\phi(k)$ corresponding to eigenstate in
-            $k$ and $-k$. When $T$ acts on a wavefunction, its
-            creation operator is affected and its ... (paused here).
+            Recall for 
         \end{proof}

### 2016-10-21 Lattice Green function/green-f.tex
New notes about Berry phase.

--- 2016-09-08 Green function/green-f.tex
@@
 
-    After this, the author illustrate one simple example of using
-    Dyson's equation to calculate $G$.
+    After this, the author illustrates one simple example of using
+    Dyson's equation to calculate $G$. This process is essentially
+    the same as the standard recursive technique. Therefore I will
+    only mention the standard technique below.
+
+    The standard technique is best illustrated with the following
+    diagram:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{ch4.3.standard_recursive_technique}.png}
+        \caption{Standard recursive technique}
+        %\label{fig:pics/ch4.standard_recursive_technique.png}
+    \end{figure}
+
+    And these equations:
+    \begin{align}
+        G^L_{n+1,n+1}=&
+          \left(1-
+            G^{isol}_{n+1,n+1}V_{n+1,n}G^L_{n,n}V_{n,n+1}\right)^{-1}
+          G^{isol}_{n+1,n+1}
+        \\
+        G^L_{n+1,1}=& G^L_{n+1,n+1}V_{n+1,n}G^L_{n,1}
+        \\
+        G^L_{1,n+1} =& G^L_{1n} V_{n,n+1} G^L_{n+1,n+1}
+    \end{align}
+
+    \subsubsection{4.3.3 Recursive technique: An extension}
+    \label{sec:4.3.3_Recursive_technique_An_extension}
+
+    The author utilizes a simple bisection method to calculate,
+    best illustrated by the diagram:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{ch4.3.extended_recursive_technique}.png}
+        \caption{Extended recursive technique}
+        %\label{fig:pics/ch4.extended_recursive_technique.png}
+    \end{figure}
+    There is, obviously, one final step that requires different formula
+    than the previous steps:
+    \begin{align}
+        G_{n1}=&
+          \left( 1-G^L_{nn}V_{n,n+1}G^R_{n+1,n+1}V_{n+1,n}\right)^{-1}
+          \cdot G^L_{n1}
+        \\
+        G_{1n}=&
+          G^L_{1n}+G^L_{1n}V_{n,n+1}G^R_{n+1,n+1}V_{n+1,n}G_{nn}
+        \\
+        G_{nn}=&
+          \left(1-G^L_{nn}V_{n,n+1}G^R_{n+1,n+1}V_{n+1,n}\right)^{-1}
+          \cdot G^L_{nn}
+        \\
+        G_{Nn}=& G^R_{N,n+1}V_{n+1,n}G_{nn}
+        \\
+        G_{nN}=& G_{nn}V_{n,n+1}G^R_{n+1,N}
+    \end{align}
 \section{Anchor}

### 2016-10-21 Notes of Bernvig's Book/Ch2 Berry Phase/Ch2 Berry Phase.tex
New notes about Berry phase.

--- 2016-10-19 GRE Physics Prep/General Physics Formula.tex
@@
 
+% For highlighting
+\usepackage{color,soul}
+
 % Following is for theorems etc environments
@@
 
-% For highlighting
-\usepackage{color,soul}
-
-\title{General Physics Formula}
+\title{Notes of Chapter 2 of Bernevig's Book}
 \date{\today}
@@
 \abstract{
-This is a collection of important formulae in Fundamentals of Physics
-Extended Version by Halliday and Resnick.
+Since I have already made a written one, this note is only an outline
+of the written script, in the hope of makeing it eaiser to read.
 }
@@
 
-\section{Classical mechanics}
-\label{sec:Classical-mechanics}
+\section{Deriving Berry Phase}
+\label{sec:Deriving-Berry-Phase}
+From page 1 to page 2 (equation 2.7), one derives the expression for
+the phase $e^{i\gamma_m}$ using instaneous energy eigenstate for
+$E_m$:
+\begin{align}
+    & H(\vec{R})\ket{n(\vec{R})} = E_m(\vec{R})\ket{n(\vec{R})} \\
+    & \gamma_m = i\int_0^t
+    \braket{
+        m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
+        m\left(\vec{R}(t')\right) \diff t' }
+\end{align}
+Then I writes about different ways to get the $\gamma_m$:
+\begin{align}
+    \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
+    \diff \vec{R}
+\end{align}
+(equation 2.8) 
+Also, one defines
+\begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
+\nomenclature{Berry Connection, Berry Vector Potential
+$\vec{A}$}{\nomrefpage.}
+    \begin{align}
+        \vec{A}_n \equiv i \braket{n|\nabla_{\vec{R}}\, n }
+    \end{align}
+\end{defi}
+Then I proves several facts:
+\begin{fact}
+    \label{fact:gamma_is_real}
+    $  $
+    \begin{center}
+        $\gamma_n$ is real
+    \end{center}
+\end{fact}
+\begin{fact}
+    $ $
+    \begin{center}
+        Berry connection $\vec{A}_n$ is gauge-dependent 
+    \end{center}
+    The dependence is: If 
+    $$\ket{n}\to \ket{n'}= e^{i\xi(\vec{R})}\ket{n}$$
+    then
+    \begin{align}
+        \vec{A}_n \to \vec{A}_n - \nabla_{\vec{R}}\,\xi(\vec{R})
+    \end{align}
+\end{fact}
+Therefore we have
+\begin{fact}
+    $  $
+    \begin{center}
+        $\gamma_n$ is gauge-dependent, unless the path tranverses a
+        closed loop.
+    \end{center}
+    Since 
+    $$ \gamma_n \to \gamma_n - \left(\xi(\vec{R}(T))-
+    \xi(\vec{R}(0)) \right) $$
+    It is unchanged unless the integration curve is a closed loop. In
+    which case
+    $$\xi(\vec{R}(T)) - \xi(\vec{R}(0)) = 2\pi m
+    \overset{\text{mod }2\pi}{=} 0 $$
+\end{fact}
+\begin{ex}
+    There is a simple example on page 3 to show that the Berry phase
+    can be actually detected.
+\end{ex}
+By virtue of fact \ref{fact:gamma_is_real}, we have
+\section{Anchor}
+\label{sec:Anchor}
 
-\paragraph{Constant Accleration}
-These five equations in Table 2-1 describe the motion of a particle with constant acceleration:
-\begin{align}
-    v           &= v_0 + at \\
-    x-x_0       &= v_0 t + \frac{1}{2} at^2\\
-    x-x_0       &= vt - \frac{1}{2} at^2\\
-    v^2 - v_0^2 &= 2a(x-x_0)\\
-    x-x_0       &= \frac{1}{2} (v_0+v) t
-\end{align}
-
-\paragraph{Projectile Motion} Projectile motion is the motion of a
-particle that is launched with an initial velocity $\vec v_0$. During
-its flight, the particle’s horizontal acceleration is zero and its
-vertical acceleration is the free-fall acceleration $-g$. (Upward is
-taken to be a positive direction.) If $\vec v_0$ is expressed as a
-magnitude (the speed $v_0$) and an angle $\theta_0$ (measured from the
-horizontal), the particle’s equations of motion along the horizontal x
-axis and vertical y axis are
-\begin{align}
-    x-x_0 &= (v_0 \cos(\theta_0) ) t \\
-    y-y_0 &= (v_0 \sin(\theta_0) ) t - \frac{1}{2} gt^2 \\
-    v_y   &= v_0 \sin{\theta_0} - gt \\
-    v_y^2 &= (v_0 \sin{\theta_0})^2 - 2g (y-y_0)
-\end{align}
-The \textbf{trajectory} (path) of a particle in projectile motion is
-parabolic and is given by
-\begin{align}
-    y &= (\tan{\theta_0}) x - \frac{gx^2}{2(v_0 \cos{\theta_0})^2} 
-\end{align}
-
-\paragraph{Uniform Circular Motion} If a particle travels along a circle
-or circular arc of radius $r$ at constant speed $v$, it is said to be in
-\textit{uniform circular motion} and has an acceleration of constant
-magnitude
-\begin{align}
-    a = \frac{v^2}{r}
-\end{align}
-The direction of is toward the center of the circle or circular arc,
-and is said to be centripetal. The time for the particle to complete
-a circle is
-\begin{align}
-    T=\frac{2\pi r}{v}
-\end{align}
-$T$ is called the period of revolution, or simply the period, of the
-motion.
-
-This acceleration is due to a net centripetal force on the particle,
-with magnitude given by
-\begin{align}
-    F = \frac{mv^2}{R}
-\end{align}
-where $m$ is the particle’s mass. The vector quantities $\vec a$ and
-$\vec F$ are directed toward the center of curvature of the particle’s
-path
-\begin{defi}[Normal force]
-\nomenclature{Normal force}{\nomrefpage.}
-A \textbf{normal force} is the force on a body from a surface against
-which the body presses.The normal force is always perpendicular to the
-surface.
-\end{defi}
-
-\paragraph{Drag Force} When there is relative motion between air (or
-some other fluid) and a body, the body experiences a drag force $\vec
-D$
-that opposes the relative motion and points in the direction in
-which the fluid flows relative to the body. The magnitude of $\vec D$is
-related to the relative speed $v$ by an experimentally determined
-drag coefficient $C$ according to
-\begin{align}
-    D=\frac{1}{2} C\rho A v^2
-\end{align}
-where $\rho$ is the fluid density (mass per unit volume) and $A$ is
-the effective cross-sectional area of the body (the area of a cross
-section taken perpendicular to the relative velocity $\vec v$)
-
-Power The power due to a force is the rate at which that force
-does work on an object. For a force $\vec F$ at an angle $\phi$ to the
-direction of travel of the instantaneous velocity $\vec v$, the
-instantaneous power is
-\begin{align}
-    P = Fv \cos{\phi} = \vec{F} \cdot \vec{v}
-\end{align}
-
-\paragraph{Collision and Impulse} Applying Newton’s second law in
-momentum form to a particle-like body involved in a collision
-leads to the impulse–linear momentum theorem:
-\begin{align}
-    \vec{p}_f - \vec{p}_i = \int_{t_i}^{t_f} \vec{F} \diff t
-\end{align}
-where the LHS is the change in the body’s linear
-momentum, and RHS is defined as the impulse $\vec{J}$ due to the force
-exerted on the body by the other body in the collision.
-
-\paragraph{Elastic Collisions in One Dimension} An elastic collision
-is a special type of collision in which the kinetic energy of a system
-of colliding bodies is conserved. If the system is closed and
-isolated, its linear momentum is also conserved. For a one-dimensional
-collision in which body $2$ is a target and body $1$ is an incoming
-projectile, conservation of kinetic energy and linear momentum yield
-the following expressions for the velocities immediately after the
-collision:
-\begin{align}
-    v_{1f} &= \frac{m_1-m_2}{m_1+m_2} v_{1i} \\
-    v_{2f} &= \frac{2m_1}{m_1+m_2} v_{1i}
-\end{align}
-
-Variable-Mass Systems In the absence of external forces a rocket
-accelerates at an instantaneous rate given by
-\begin{align}
-    R v_{\text{rel}} = Ma \text{(first rocket equation)}
-\end{align}
-in which $M$ is the rocket’s instantaneous mass (including
-unexpended fuel), $R$ is the fuel consumption rate, and $v_{\text{rel}}$ is the fuel’s
-exhaust speed relative to the rocket. The term $R v_{\text{rel}}$ is the thrust of
-the rocket engine. For a rocket with constant R and $v_{\text{rel}}$, whose speed
-changes from $v_i$ to $v_f$ when its mass changes from $M_i$ to $M_f$,
-\begin{align}
-    v_f - v_i = v_{\text{rel}} \ln\frac{M_i}{M_f} \text{(second rocket
-    equation)}
-\end{align}
-($R\equiv |\frac{\diff M}{\diff t}|$)
-
-\paragraph{The Kinematic Equations for Constant Angular Acceleration}
-Constant angular acceleration ($\alpha =$a constant) is an important
-special case of rotational motion. The appropriate kinematic
-equations, given in Table 10-1, are
-\begin{align}
-    \sigma &= \sigma_0 + \alpha t \\
-    \theta - \theta_0 &= \omega_0 t + \frac{1}{2} \alpha t^2 \\
-    \theta - \theta_0 &= \omega t - \frac{1}{2} \alpha t^2 \\
-    \omega^2 - \omega_0^2 &= 2\alpha (\theta - \theta_0) \\
-    \theta - \theta_0 &= \frac{1}{2}(\omega_0 + \omega) t
-\end{align}
-
-\paragraph{Linear and Angular Variables Related} A point in a rigid
-rotating body, at a perpendicular distance $r$ from the rotation axis,
-moves in a circle with radius $r$.
-
-The linear acceleration $\vec{a}$ of the point \hl{has both tangential and
-radial components}.The tangential component is
-\begin{align}
-    a_t = \alpha r
-\end{align}
-where $\alpha$ is the magnitude of the angular acceleration (in radians
-per second-squared) of the body.The radial component of $\vec{a}$ is
-\begin{align}
-    a_r = \frac{v^2}{r} = \omega^2 r
-\end{align}
-If the point moves in uniform circular motion, the period $T$ of
-the motion for the point and the body is
-\begin{align}
-    T = \frac{2\pi r}{v} = \frac{2\pi}{\omega}
-\end{align}
-\paragraph{Rotational Kinetic Energy and Rotational Inertia} The
-kinetic energy $K$ of a rigid body rotating about a fixed axis is
-given by
-\begin{align}
-    K=\frac{1}{2} I\omega^2
-\end{align}
-in which $I$ is the rotational inertia of the body, defined as
-\begin{align}
-    I \equiv \int r^2 \diff m
-\end{align}
-\paragraph{The Parallel-Axis Theorem} 265
-\begin{align}
-    I = I_{\text{com}} + M h^2
-\end{align}
-
-\paragraph{Work and Rotational Kinetic Energy} 265
-\begin{align}
-    W = \int_{\theta_i}^{\theta_f} \tau \diff \theta \\
-    P = \frac{\diff W}{\diff t} = \tau \omega
-\end{align}
-
-\paragraph{Rolling Bodies}
-[295]
-\begin{align}
-    v_\text{com} &= \omega R\\
-    K  &= \frac{1}{2}I_\text{com}\omega^2 + \frac{1}{2}Mv_\text{com}^2
-    \\
-    a_\text{com} = \alpha R
-\end{align}
-\paragraph{Precession of a Gyroscope}
-\begin{align}
-    \Omega = \frac{Mgr}{I\omega}
-\end{align}
-
-\paragraph{Elastic Moduli} [319]
-\begin{center}
-    stress $=$ modulus $\times$ strain
-\end{center}
-
-Young's modulus:
-\begin{align}
-    \frac{F}{A} = E \frac{\Delta L}{L}
-\end{align}
-
-Shear's modulus:
-\begin{align}
-    \frac{F}{A} = G \frac{\Delta x}{L}
-\end{align}
-
-Hydraulic bulk modulus:
-\begin{align}
-    p = B \frac{\Delta V}{V}
-\end{align}
-
-\paragraph{Gravitational Potential Energy} [349]
-\begin{align}
-    U = -\frac{GMm}{r}
-\end{align}
-
-\textbf{Escape speed}
-\begin{align}
-    v = \sqrt{ \frac{2GM}{R} }
-\end{align}
-
-\textbf{Kepler's Laws}
-\begin{enumerate}
-    \item The law of orbits. All planets move in elliptical orbits
-        with the Sun at one focus.
-    \item The law of areas. A line joining any planet to the Sun
-        sweeps out equal areas in equal time intervals. (This
-        statement is equivalent to conservation of angular momentum.)
-    \item The law of periods. The square of the period $T$ of any
-        planet is proportional to the cube of the semimajor axis a of
-        its orbit. For circular orbits with radius $r$,
-    \begin{align}
-        T^2 = \left(\frac{4\pi^2}{GM}\right) r^3
-    \end{align}
-        where $M$ is the mass of the attracting body—the Sun in the
-        case of the solar system. For elliptical planetary orbits, the
-        semimajor axis $a$ is substituted for $r$.
-\end{enumerate}
-
-\textbf{Energy in Planetary Motion}
-\begin{align}
-    U &= -\frac{GMm}{r} \\
-    K &= \frac{GMm}{2r} \\
-    E &= -\frac{GMm}{2r} \,\text{ or} \\
-    E &= -\frac{GMm}{2a} 
-\end{align}
-
-\paragraph{Flow of Ideal Fluids}[377]
-\begin{defi}[Apparent weight]
-\nomenclature{Apparent weight}{\nomrefpage.}
-    Omited
-\end{defi}
-
-\textbf{Equation of continuity}
-\begin{align}
-    R_v \equiv Av = \text{ a constant}
-\end{align}
-\textbf{Bernoulli's Equation}
-\begin{align}
-    p + \frac{1}{2}\rho v^2 + \rho gh = \text{ a constant}
-\end{align}
-
-\paragraph{Oscillation} (\textbf{pp.403 of \cite{book}})
-\begin{align}
-    \omega &= \frac{2\pi}{T} = 2\pi f
-\end{align}
-\textbf{Linear Oscillator}
-\begin{align}
-    & \omega = \sqrt{\frac{k}{m}} \\
-    & T = 2\pi \sqrt{\frac{m}{k}} 
-\end{align}
-\textbf{Pendulums}
-\begin{align}
-    & T = 2\pi \sqrt{I/\kappa} \\
-    & T = 2\pi \sqrt{L/g} \\
-    & T = 2\pi \sqrt{I/mgh}
-\end{align}
-\textbf{Damped Harmonic Motion}
-\begin{align}
-    & x(t) = x_m e^{-bt/2m} \cos\left( \omega' t+\phi\right) \\
-    & \omega' = \sqrt{ \frac{k}{m} - \frac{b^2}{4m^2} } \\
-    & E(t)\approx \frac{1}{2} kx_m^2 e^{-bt/m}
-\end{align}
-\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
-\begin{align}
-    & y(x,t) = y_m \sin(kx-\omega t) \\
-    & k = \frac{2\pi}{\lambda} \\
-    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
-    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
-\end{align}
-\textbf{String}
-\begin{align}
-    & v = \frac{\tau}{\mu} \\
-    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
-\end{align}
-\textbf{Resonance}
-\begin{align}
-    n \lambda = 2L
-\end{align}
-\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
-\begin{align}
-    & v = \sqrt{\frac{B}{\rho}} \\
-    & s = s_m \cos(kx-\omega t) \\
-    & \Delta p = \Delta p_m sin(kx-\omega r) \\
-    & \Delta p_m = (v\rho \omega) s_m
-\end{align}
-\textbf{Sound Intensity}
-\begin{align}
-    & I = \frac{P}{A} \\
-    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
-    & I = \frac{P_s}{4\pi r^2} \\
-\end{align}
-\textbf{Standing Wave Patterns in Pipes}
-\begin{align}
-    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
-    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
-\end{align}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
-\end{figure}
-\textbf{Beat}
-\begin{align}
-    f_\text{beat} = f_1 - f_2
-\end{align}
-\textbf{The Doppler Effect}
-\begin{align}
-    f' = f \frac{ v \pm v_D}{ v\pm v_s}
-\end{align}
-The signs are chosen such that $f'$ tends to be \textit{greater} for
-motion toward and \textit{less} for motion away.
-\textbf{Shock wave}
-\begin{align}
-    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
-\end{align}
-
-\paragraph{Conduction} (\textbf{pp.498 ch18 of \cite{book}})
-\textbf{Thermal expansion}
-\begin{align}
-    & \Delta L = L \alpha \Delta T \\
-    & \Delta V = V \beta \Delta T \\
-    & \beta = 3 \alpha \\
-    & Q = C \Delta T = cm \Delta T
-\end{align}
-\begin{defi}[Convection]
-\nomenclature{Convection}{\nomrefpage.}
-    Convection occurs when temperature differences cause an energy
-    transfer by motion within a fluid
-\end{defi}
-\textbf{Radiation}
-\begin{align}
-    & P_\text{rad} = \sigma \varepsilon AT^4 \\
-    & P_\text{abs} = \sigma \varepsilon AT_\text{evn}^4
-\end{align}
-\textbf{Conduction}
-\begin{align}
-    P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L} 
-\end{align}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond}.png}
-\end{figure}
-
-\paragraph{Thermal Process} (\textbf{pp.529 ch19 of \cite{book}})
-Thermal process:
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|c|c|c|c|}
-        \hline
-        No. & Constant Quaility            & Process Type & Special Results  \\
-        \hline
-        1   & $p$                          & Isobaric     & $Q = nC_p\Delta T;W=p\Delta V$ \\
-        2   & $V$                          & Isothermal   & $Q=W=nRT\ln(V_f/V_i); \Delta E_\text{int}=0$  \\
-        3   & $pV^\gamma$, $TV^{\gamma-1}$ & Adiabatic    & $W=-\Delta E_\text{int}$ \\
-        4   & $V$                          & Isochoric    & $Q=\Delta E_\text{int}=nC_V \Delta T;W=0$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/{ch18.therm_pro}.png}
-\end{figure}
-Isothermal Process:
-\begin{align}
-    W = Nk T \ln\frac{V_f}{V_i}
-\end{align}
-\textbf{Temperature and Kinetic Energy}
-\begin{align}
-    & K_\text{avg} = \frac{3}{2}kT \text{, per molecule} \\
-    & \lambda = \frac{1}{\sqrt{2} \pi d^2 N/V} 
-\end{align}
-\paragraph{Molar Specific Heats}
-\begin{align}
-    & C_V = \frac{3}{2} R \\
-    & C_P = C_V + R \\
-    & \Delta E_\text{int} = N C_V \Delta T \\
-    & C_V = \frac{f}{2} k \\
-    & \gamma \equiv \frac{C_P}{C_V}
-\end{align}
-
-\paragraph{Entropy} (\textbf{pp.554 ch20 of \cite{book}})
-
-\begin{align}
-    & \diff S = \frac{\diff Q}{T} \\
-    & \Delta S = nR \ln{\frac{V_f}{V_i}} + nC_V \ln{\frac{T_f}{T_i}}
-    \\
-    & \varepsilon = 1-\frac{T_L}{T_H}  \text{ (Carnot engine)} \\
-    & K = \frac{T_L}{T_H-T_L} \text{ (Carnot refrigerator)}  \\
-    & \ln{N!} \approx N\ln{N} - N
-\end{align}
-
-\paragraph{Electric field} (\textbf{pp.596 ch22 of \cite{book}})
-\begin{align}
-    & E = \frac{1}{4\pi \varepsilon_0} \frac{q}{r^2} \\
-    & E = \frac{1}{2\pi \varepsilon_0} \frac{p}{z^3} \\
-    & U = - \vec{p}\cdot \vec{E} 
-\end{align}
-
-\paragraph{Gauss's Law} (\textbf{pp.620 ch23 of \cite{book}})
-
-\begin{align}
-    & E = \frac{\sigma}{\varepsilon_0}\text{ ,charged conductor} \\
-    & E = \frac{\sigma}{2\varepsilon_0}\text{ ,infinite sheet} \\
-    & E = \frac{\lambda}{2\pi\varepsilon_0 r} \\
-    & E = 0 \text{ , inside charged shell} \\
-    & E = \left(\frac{q}{4\pi\varepsilon_0 R^3}\right) r
-\end{align}
-
-\paragraph{Electric Potential} (\textbf{pp.646 ch24 of \cite{book}})
-
-\begin{align}
-    & V = \frac{1}{4\pi\varepsilon_0}\frac{q}{r} \\
-    & V = \frac{1}{4\pi\varepsilon_0}\frac{p\cos\theta}{r^2} \\
-    & U = \frac{1}{4\pi\varepsilon_0}\frac{q_1 q_2}{r}
-\end{align}
-
-\paragraph{Capacitor} (\textbf{pp.675 ch25 of \cite{book}})
-
-\begin{align}
-    & C \equiv \frac{q}{V} \\
-    & C = \frac{\varepsilon_0 A}{d} \text{ (parallel-plate)} \\
-    & C = 2\pi \varepsilon_0 \frac{L}{\ln{b/a}} 
-            \text{ (cylindrical)}\\
-    & C = 4\pi \varepsilon_0 \frac{ab}{b-a} \text{ (spherical)}\\
-    & C = 4\pi \varepsilon_0 R \text{ (isolated spherical)} \\
-    & C = \sum_j C_j \text{ (parallel)} \\
-    & \frac{1}{C} = \sum_j \frac{1}{C_j} \text{ (series)}  \\
-    & U = \frac{1}{2}\frac{q^2}{C} = \frac{1}{2}CV^2 \\
-    & u = \frac{1}{2}\varepsilon_0 E^2
-\end{align}
-
-\paragraph{Current} (\textbf{pp.698 ch26 of \cite{book}})
-
-\begin{align}
-    & \vec{J} = ne \vec{v}_d \\
-    & \rho \equiv \frac{1}{\sigma} = \frac{E}{J} \\
-    & \vec{E} = \rho \vec{J} \\
-    & R = \rho \frac{L}{A} \\
-    & \rho - \rho_0 = \rho_0 \alpha (T-T_0) \\
-    & \rho = \frac{m}{e^2 n\tau }
-\end{align}
-
-\paragraph{Electro motive force} (\textbf{pp.724 ch27 of \cite{book}})
-
-\begin{align}
-    & \mathcal{E} = \frac{\diff W}{\diff q}
-\end{align}
-
-\textbf{Circuit Rule}
-\begin{itemize}
-    \item \textbf{Loop Rule}. The algebraic sum of the changes in
-        potential encountered in a complete traversal of any loop of a
-        circuit must be zero.
-    \item \textbf{Junction Rule}. The sum of the currents entering any
-        junction must be equal to the sum of the currents leaving that
-        junction
-\end{itemize}
-
-\begin{align}
-    & R = \sum_j R_j \text{ , series} \\
-    & \frac{1}{R} = \sum_j \frac{1}{R_j} \text{ , parallel}
-\end{align}
-
-\paragraph{Magnetic Field} (\textbf{pp.755 ch28 of \cite{book}})
-
-\begin{align}
-    & qvB = \frac{mv^2}{r} \\
-    & T = \frac{2\pi r}{ rqB / m} = \frac{2\pi m}{qB} \\
-    & \vec\tau = \vec{\mu} \times \vec{B} \\
-    & U(\theta) = -\vec\mu \cdot \vec B
-\end{align}
-
-\paragraph{Magnetic -> Electricity} (\textbf{pp.781 ch29 of
-\cite{book}})
-
-\begin{align}
-    & \diff \vec{B} = \frac{\mu_0}{4\pi}
-        \frac{i\diff \vec{s}\times\hat{r}}{r^2} \\
-    & B = \frac{\mu_0 i}{2\pi R} \\
-    & B = \frac{\mu_0 i \phi}{4\pi R} \\
-    & B = \mu_0 i N/L \\
-    & B = \frac{\mu_i i N}{2\pi}\frac{1}{r} \\
-    & \vec{B}(z) = \frac{\mu_0}{2\pi}\frac{\vec{\mu}}{z^3}
-\end{align}
-
-\paragraph{Faraday's Law} (\textbf{pp.816 ch30 of \cite{book}})
-
-\begin{align}
-    \mathcal{E} = \int \vec{E} \diff \vec{s} \\
-\end{align}
-\textbf{Inductance}
-\begin{align}
-    & L \equiv \frac{N\Phi_B}{i} \\
-    & \frac{L}{l} = \mu_n n^2 A \\
-    & \mathcal{E}_L = - L\frac{\diff i}{\diff t} \\
-    & U_B = \frac{1}{2} L i^2 \\
-    & u_B = \frac{1}{2} \frac{B^2}{\mu_0} 
-\end{align}
-\section{Anchor}
-\label{sec:anchor}
 \begin{thebibliography}{1}
-    \bibitem{book} Fundamentals of Physics, Extended Edition. Halliday
-    \& Resnick.
+    \bibitem{book} Bernevig's Topological Insulators and
+    Superconductors
 \end{thebibliography}

### 2016-10-21 Green function/1D QAHI Conductance/GreenF.m

@@ -1,56 +1,0 @@
-function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gamma,dis)
-% Obtain the GF with recursive method for twoo-lead with same material
-% tc is coupling between S and N
-% TODO: I think I should check this with the PDF.
-
-w_energy_resol=1.*10^-3;                     % the resolution of energy
-
-% tc1 coupling between lead 1 and the sample
-% tc2 coupling between lead 2 and the sample
-I    = eye(4);
-gL   = g11(E,muL,ts,tsoL,w_energy_resol);
-Tc1  = V_dl(tc1);
-SE1  = Tc1*gL*Tc1';          % self energy for the L-L interfaces of lead-1
-HnS  = H_sample(1,muS,ts,tso,delta,Gamma,0);
-HeS1 = HnS+SE1+dis(1)*diag([-1,-1,1,1]);
-Tc2  = V_dl(tc2);
-SE2  = Tc2*gL*Tc2';       % self energy for the L-L interfaces of lead-2
-HeS2 = HnS+SE2+dis(L)*diag([-1,-1,1,1]);
-
-%% from left to right ( lead 1 to lead 2)
-Gnn=I/(((E+1i*w_energy_resol)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component
-G1n=Gnn;                        %|
-Gn1=Gnn;                        %|
-V1=V_sample(ts,tso);
-V2=V1';
-for i=2:L-1
-    %i
-    gnn=I/(((E+1i*w_energy_resol)*I-HnS+dis(i)*diag([-1,-1,1,1]))); % isolated GF for 2 ~ N-1 componets
-    Gnn=(I-gnn*V2*Gnn*V1)\gnn;
-    Gn1=Gnn*V2*Gn1;
-    G1n=G1n*V1*Gnn;
-end
-
-gnn=I/(((E+1i*w_energy_resol)*I-HeS2));      % isolated GF for the last component at lead-2
-GNN=(I-gnn*V2*Gnn*V1)\gnn;
-GN1=GNN*V2*Gn1;
-G1N=G1n*V1*GNN;
-
-%% from right to left
[…]

### 2016-10-21 Green function/1D QAHI Conductance/H_lead(deceased).m

@@ -1,84 +1,0 @@
-function y=H_lead(L,mu,ts,tso)
-y=zeros(4*L);
-Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
-condition=1.0; % =1 for spin independent hoping ts
-%tso=0.0; tso=0 or not, the results are quite different!
-m_y=00.0;
-m_x=0.0;
-
-%=====================================================================
-% Additional term which break C2,T2 symmetry but preserve C1 and T1
-% symmetry. To test the influence of C1 and T1 symmetry.
-%y(i,i+L)=I*m_y;
-%y(i+L,i)=-I*m_y;
-%y(i+2*L,i+3*L)=-I*m_y;
-%y(i+3*L,i+2*L)=I*m_y;
-
-%=====================================================================
-
-for i=1:L-1
-    y(i,i)=Gamma-mu;
-    y(i+L,i+L)=-Gamma-mu;
-    y(i+2*L,i+2*L)=Gamma-mu;
-    y(i+3*L,i+3*L)=-Gamma-mu;
-    
-    %=====================================================================
-    % Additional term which break C2,T2 symmetry but preserve C1 and T1
-    % symmetry. To test the influence of C1 and T1 symmetry.
-    y(i,i+L)=m_x+I*m_y;
-    y(i+L,i)=m_x-I*m_y;
-    y(i+2*L,i+3*L)=m_x-I*m_y;
-    y(i+3*L,i+2*L)=m_x+I*m_y;
-    
-    %=====================================================================
-    
-    
-    
-    if condition==1
-        y(i,i+1)=-ts;
-        y(i+L,i+L+1)=-ts;
-        y(i+2*L,i+2*L+1)=-ts;
-        y(i+3*L,i+3*L+1)=-ts;
-        
-        y(i+1,i)=-ts;
-        y(i+L+1,i+L)=-ts;
-        y(i+2*L+1,i+2*L)=-ts;
-        y(i+3*L+1,i+3*L)=-ts;
-        
-    else
-        y(i,i+1)=-ts;
-        y(i+L,i+L+1)=ts;
-        y(i+2*L,i+2*L+1)=-ts;
[…]

### 2016-10-21 Green function/1D QAHI Conductance/H_sample.m

@@ -1,150 +1,0 @@
-% without normal t
-% Modified program to calculate AIII topological insulator as
-% spin transistor
-
-% i electron up
-% i electron down
-
-
-function y=H_sample(L,mu,ts,tso,delta,Gamma,dis)
-% TODO Find reference for this code
-%y=zeros(4*L);
-
-m_y=0.0;
-m_x=00.0;
-%Gamma=2.0;
-
-for i=1:L-1
-    mu=mu+dis*(rand-0.5);
-    y(i,i)=Gamma-mu;
-    y(i+L,i+L)=-Gamma-mu;
-    y(i+2*L,i+2*L)=Gamma-mu;
-    y(i+3*L,i+3*L)=-Gamma-mu;
-    
-    %y(i,i)=-mu;
-    %y(i+L,i+L)=-mu;
-    %y(i+2*L,i+2*L)=-mu;
-    %y(i+3*L,i+3*L)=-mu;
-    
-    %=====================================================================
-    % Additional term which break C2,T2 symmetry but preserve C1 and T1
-    % symmetry. To test the influence of C1 and T1 symmetry.
-    y(i,i+L)=j*m_y;
-    y(i+L,i)=-j*m_y;
-    y(i+2*L,i+3*L)=-j*m_y;
-    y(i+3*L,i+2*L)=j*m_y;
-    
-    %=====================================================================
-    
-    
-    
-    y(i,i+1)=-ts;
-    y(i+L,i+L+1)=ts;
-    y(i+2*L,i+2*L+1)=-ts;
-    y(i+3*L,i+3*L+1)=ts;
-    
-    y(i+1,i)=-ts;
-    y(i+L+1,i+L)=ts;
-    y(i+2*L+1,i+2*L)=-ts;
-    y(i+3*L+1,i+3*L)=ts;
-    
-    y(i,i+L+1)=tso;
-    y(i+1,i+L)=-tso;
-    y(i+2*L,i+L+1+2*L)=tso;
-    y(i+1+2*L,i+L+2*L)=-tso;
-    
-    y(i+L+1,i)=tso;
-    y(i+L,i+1)=-tso;
-    y(i+L+1+2*L,i+2*L)=tso;
-    y(i+L+2*L,i+1+2*L)=-tso;
-    
-    y(i,i+3*L)=delta;
-    y(i+L,i+2*L)=-delta;
-    y(i+3*L,i)=delta;
[…]

### 2016-10-21 Green function/1D QAHI Conductance/ScatteringM.m

@@ -1,53 +1,0 @@
-%function y=ScatteringM(1,Ly,W,E,Vy,u,t,a,tc,Ds,Dp,periodx)
-function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
-  y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
-%SCateringMatrix calculates the scatering matrix from lattice Green function
-%based on the formula: S=-1+i*sqrt(Gamma)*GF*sqrt(Gamma')
-% TODO I think I should find reference for this file.
-
-    [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
-    Gamma1 = (1i*(SE1-SE1'));
-    A1     = my_sqrt(Gamma1);
-    Gamma2 = (1i*(SE2-SE2'));
-    A2     = my_sqrt(Gamma2);
-    y11    = -eye(4)+1i*A1*G11*A1;
-    y12    = 1i*A1*G1N*A2;
-    y21    = 1i*A2*GN1*A1;
-    y22    = -eye(4)+1i*A2*GNN*A2;
-    %y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
-    % e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
-    y11ee=y11(1:2*1     , 1:2*1);
-    y12ee=y12(1:2*1     , 1:2*1);
-    y11eh=y11(1:2*1     , 2*1+1:4*1);
-    y12eh=y12(1:2*1     , 2*1+1:4*1);
-
-    y21ee=y21(1:2*1     , 1:2*1);
-    y22ee=y22(1:2*1     , 1:2*1);
-    y21eh=y21(1:2*1     , 2*1+1:4*1);
-    y22eh=y22(1:2*1     , 2*1+1:4*1);
-
-    y11he=y11(2*1+1:4*1 , 1:2*1);
-    y12he=y12(2*1+1:4*1 , 1:2*1);
-    y11hh=y11(2*1+1:4*1 , 2*1+1:4*1);
[…]

### 2016-10-21 Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -1,199 +1,0 @@
-% ============= T vs E =========================================
-% TODO Find reference for this code
-clear
-cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
-
-% Here we use ts as a reference for other energies.
-L=20;        % number of sites
-ts=10;       % hoping
-tso=1.0;     % spin orbital coupling
-tsoL=0;      % spin orbital coupling of the leads
-tc1=0.2*ts;  % coupling between lead 1 and the sample
-tc2=0.2*ts;  % coupling between lead 2 and the sample
-muL=5.0;     % chemical potential of the leads
-muS=0;       % chemical potential of the sample
-disorder=0;  % local disorder
-delta=0.0;   % superconducting pairing
-
-M_gamma=200; % gamma
-N_E=200;     % E
-
-if cont==1
-    % For cont=1, we try to plot G as a function of gamma
-    % and E.
-    gamma=3*(-ts:2.0*ts/M_gamma:ts);  % Zeeman energy
-    E=(-muL:2*muL/N_E:1*muL);
-else
-    gamma=3.0;      % Zeeman energy Gammz_z as a constant
-    gap=min(abs(2*ts-abs(gamma)),2*abs(tso));
-    %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
-    E=(-muL:2*muL/N_E:1*muL);
-    %pause(0.5)
-end
-
-M_gamma=length(gamma);N_E=length(E)
-pause(0.5)
-
-% TC: Transmission Coefficient.
-% TL: what? TODO
-TCee=zeros(N_E,M_gamma);
-TChe=zeros(N_E,M_gamma);
-TLee=zeros(N_E,M_gamma);
-TLhe=zeros(N_E,M_gamma);
-dis=disorder*(rand(1,L)-0.5);
-
-for i=1:N_E
-    i % Indicating the progress of this script
-    for j=1:M_gamma
-        [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
-          y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM(E(i),L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,gamma(j),dis);
[…]

### 2016-10-21 Green function/1D QAHI Conductance/V_dl.m

@@ -1,6 +1,0 @@
-function y=V_dl(tc)
-% Vdl: The coupling between the sample and the lead. Vld=Vdl'
-% T: the coupling amplitude
-% TODO I think I should ask the R.A. about this.
-y=tc*diag([-1,-1,-1,-1]);
-end

### 2016-10-21 Green function/1D QAHI Conductance/V_lead(deceased).m

@@ -1,15 +1,0 @@
-function y=V_lead(ts,tso)
-%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
-%tso: SOC
-y=zeros(4);
-for i=1:1
-    y(i,i)=-ts;
-    y(i+1,i+1)=-ts;
-    y(i+2*1,i+2*1)=ts;
-    y(i+3*1,i+3*1)=ts;
-    
-    y(i,i+1)=tso;
-    y(i+2*1,i+1+2*1)=-tso;
-    y(i+1,i)=-tso;
-    y(i+1+2*1,i+2*1)=tso;
-end

### 2016-10-21 Green function/1D QAHI Conductance/V_sample.m

@@ -1,23 +1,0 @@
-function y=V_sample(ts,tso)
-%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
-%tso: SOC
-% electron and hole section are the same in topological insulator case.
-
-% ---- A exmaple output ------
-% [     -ts,     tso, zero1_3, zero1_4]
-% [    -tso,      ts, zero2_3, zero2_4]
-% [ zero3_1, zero3_2,     -ts,     tso]
-% [ zero4_1, zero4_2,    -tso,      ts]
-% -------------------------------
-% TODO find reference for this
-y=zeros(4);
-for i=1:1
-    y(i,i)=-ts;
-    y(i+1,i+1)=ts;
-    y(i+2*1,i+2*1)=-ts;
-    y(i+3*1,i+3*1)=ts;
-    y(i,i+1)=tso;
-    y(i+2*1,i+1+2*1)=tso;
-    y(i+1,i)=-tso;
-    y(i+1+2*1,i+2*1)=-tso;
-end

### 2016-10-21 Green function/1D QAHI Conductance/g11.m

@@ -1,130 +1,0 @@
-function y=g11(E,mu,ts,tso,w_energy_resol)
-%g11 The submatrix of the Green function of the LEAD
-% Obtained by N times of recursion
-% Checkpoint: I think I understand this code now.
-% For derivation pls refer: Appendix B of the dissertation
-    % TODO find reference for following line of code
-    D=(E+1i*w_energy_resol)*eye(4)-H_lead(1,mu,ts,tso);
-    % TODO find reference for following line of code
-    A=V_lead(ts,tso);
-    B=A';
-    d=D;
-    for i=1:1000 %maximum number of recursive times
-        % The following 4 lines of code seems to come from:
-        d1=d-A/D*B;
-        D1=D-A/D*B-B/D*A;
-        A1=A/D*A;
-        B1=B/D*B;
-        if max(max(abs(d1-d)))<1e-99
-            % TODO 1e-99 might be too small...
-            break
-        end
-        d=d1;
-        D=D1;
-        A=A1;
-        B=B1;
-    end
-    y=eye(4)/d1;
-end
-
-function y=H_lead(L,mu,ts,tso)
-% TODO I should find reference for this.
-    y=zeros(4*L);
-    Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
-    condition=1.0; % =1 for spin independent hoping ts
-    %tso=0.0; tso=0 or not, the results are quite different!
-    m_y=00.0;
-    m_x=0.0;
-
-    %=====================================================================
-    % Additional term which break C2,T2 symmetry but preserve C1 and T1
-    % symmetry. To test the influence of C1 and T1 symmetry.
-    %y(i,i+L)=I*m_y;
-    %y(i+L,i)=-I*m_y;
-    %y(i+2*L,i+3*L)=-I*m_y;
-    %y(i+3*L,i+2*L)=I*m_y;
-    %=====================================================================
-    % TODO what is the point of the following line? It is never used in
-    % actually usage.
-    % TODO Also, the variable I is not defined!
-    for i=1:L-1
-        y(i,i)         = Gamma-mu;
-        y(i+L,i+L)     = -Gamma-mu;
[…]

### 2016-10-21 Green function/1D QAHI Conductance/my_sqrt.m

@@ -1,9 +1,0 @@
-function y=my_sqrt(A)
-% this function calculates the squre root of a sparse complex matrix
-%
-%A=round(A*10^5)/10^5;
-[V,D]=eig(full(A)); % full: sparse matrix -> full matrix
-d=sqrt(D);
-% What is the point of doing "/V" here? TODO
-y=V*d/V;
-end

### 2016-10-21 Lattice Green function/1D QAHI Conductance/GreenF.m

@@ -1,0 +1,56 @@
+function [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gamma,dis)
+% Obtain the GF with recursive method for twoo-lead with same material
+% tc is coupling between S and N
+% TODO: I think I should check this with the PDF.
+
+w_energy_resol=1.*10^-3;                     % the resolution of energy
+
+% tc1 coupling between lead 1 and the sample
+% tc2 coupling between lead 2 and the sample
+I    = eye(4);
+gL   = g11(E,muL,ts,tsoL,w_energy_resol);
+Tc1  = V_dl(tc1);
+SE1  = Tc1*gL*Tc1';          % self energy for the L-L interfaces of lead-1
+HnS  = H_sample(1,muS,ts,tso,delta,Gamma,0);
+HeS1 = HnS+SE1+dis(1)*diag([-1,-1,1,1]);
+Tc2  = V_dl(tc2);
+SE2  = Tc2*gL*Tc2';       % self energy for the L-L interfaces of lead-2
+HeS2 = HnS+SE2+dis(L)*diag([-1,-1,1,1]);
+
+%% from left to right ( lead 1 to lead 2)
+Gnn=I/(((E+1i*w_energy_resol)*I-HeS1));      %| initial values of the first recursion, i.e. the isolated GF for the first component
+G1n=Gnn;                        %|
+Gn1=Gnn;                        %|
+V1=V_sample(ts,tso);
+V2=V1';
+for i=2:L-1
+    %i
+    gnn=I/(((E+1i*w_energy_resol)*I-HnS+dis(i)*diag([-1,-1,1,1]))); % isolated GF for 2 ~ N-1 componets
+    Gnn=(I-gnn*V2*Gnn*V1)\gnn;
+    Gn1=Gnn*V2*Gn1;
+    G1n=G1n*V1*Gnn;
+end
+
+gnn=I/(((E+1i*w_energy_resol)*I-HeS2));      % isolated GF for the last component at lead-2
+GNN=(I-gnn*V2*Gnn*V1)\gnn;
+GN1=GNN*V2*Gn1;
+G1N=G1n*V1*GNN;
+
+%% from right to left
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/H_lead(deceased).m

@@ -1,0 +1,84 @@
+function y=H_lead(L,mu,ts,tso)
+y=zeros(4*L);
+Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
+condition=1.0; % =1 for spin independent hoping ts
+%tso=0.0; tso=0 or not, the results are quite different!
+m_y=00.0;
+m_x=0.0;
+
+%=====================================================================
+% Additional term which break C2,T2 symmetry but preserve C1 and T1
+% symmetry. To test the influence of C1 and T1 symmetry.
+%y(i,i+L)=I*m_y;
+%y(i+L,i)=-I*m_y;
+%y(i+2*L,i+3*L)=-I*m_y;
+%y(i+3*L,i+2*L)=I*m_y;
+
+%=====================================================================
+
+for i=1:L-1
+    y(i,i)=Gamma-mu;
+    y(i+L,i+L)=-Gamma-mu;
+    y(i+2*L,i+2*L)=Gamma-mu;
+    y(i+3*L,i+3*L)=-Gamma-mu;
+    
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    y(i,i+L)=m_x+I*m_y;
+    y(i+L,i)=m_x-I*m_y;
+    y(i+2*L,i+3*L)=m_x-I*m_y;
+    y(i+3*L,i+2*L)=m_x+I*m_y;
+    
+    %=====================================================================
+    
+    
+    
+    if condition==1
+        y(i,i+1)=-ts;
+        y(i+L,i+L+1)=-ts;
+        y(i+2*L,i+2*L+1)=-ts;
+        y(i+3*L,i+3*L+1)=-ts;
+        
+        y(i+1,i)=-ts;
+        y(i+L+1,i+L)=-ts;
+        y(i+2*L+1,i+2*L)=-ts;
+        y(i+3*L+1,i+3*L)=-ts;
+        
+    else
+        y(i,i+1)=-ts;
+        y(i+L,i+L+1)=ts;
+        y(i+2*L,i+2*L+1)=-ts;
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/H_sample.m

@@ -1,0 +1,150 @@
+% without normal t
+% Modified program to calculate AIII topological insulator as
+% spin transistor
+
+% i electron up
+% i electron down
+
+
+function y=H_sample(L,mu,ts,tso,delta,Gamma,dis)
+% TODO Find reference for this code
+%y=zeros(4*L);
+
+m_y=0.0;
+m_x=00.0;
+%Gamma=2.0;
+
+for i=1:L-1
+    mu=mu+dis*(rand-0.5);
+    y(i,i)=Gamma-mu;
+    y(i+L,i+L)=-Gamma-mu;
+    y(i+2*L,i+2*L)=Gamma-mu;
+    y(i+3*L,i+3*L)=-Gamma-mu;
+    
+    %y(i,i)=-mu;
+    %y(i+L,i+L)=-mu;
+    %y(i+2*L,i+2*L)=-mu;
+    %y(i+3*L,i+3*L)=-mu;
+    
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    y(i,i+L)=j*m_y;
+    y(i+L,i)=-j*m_y;
+    y(i+2*L,i+3*L)=-j*m_y;
+    y(i+3*L,i+2*L)=j*m_y;
+    
+    %=====================================================================
+    
+    
+    
+    y(i,i+1)=-ts;
+    y(i+L,i+L+1)=ts;
+    y(i+2*L,i+2*L+1)=-ts;
+    y(i+3*L,i+3*L+1)=ts;
+    
+    y(i+1,i)=-ts;
+    y(i+L+1,i+L)=ts;
+    y(i+2*L+1,i+2*L)=-ts;
+    y(i+3*L+1,i+3*L)=ts;
+    
+    y(i,i+L+1)=tso;
+    y(i+1,i+L)=-tso;
+    y(i+2*L,i+L+1+2*L)=tso;
+    y(i+1+2*L,i+L+2*L)=-tso;
+    
+    y(i+L+1,i)=tso;
+    y(i+L,i+1)=-tso;
+    y(i+L+1+2*L,i+2*L)=tso;
+    y(i+L+2*L,i+1+2*L)=-tso;
+    
+    y(i,i+3*L)=delta;
+    y(i+L,i+2*L)=-delta;
+    y(i+3*L,i)=delta;
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/ScatteringM.m

@@ -1,0 +1,53 @@
+%function y=ScatteringM(1,Ly,W,E,Vy,u,t,a,tc,Ds,Dp,periodx)
+function [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+  y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM_x(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis)
+%SCateringMatrix calculates the scatering matrix from lattice Green function
+%based on the formula: S=-1+i*sqrt(Gamma)*GF*sqrt(Gamma')
+% TODO I think I should find reference for this file.
+
+    [G11,G1N,GN1,GNN,G1N_R,GN1_R,SE1,SE2]=GreenF(E,L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,Gammaz,dis);
+    Gamma1 = (1i*(SE1-SE1'));
+    A1     = my_sqrt(Gamma1);
+    Gamma2 = (1i*(SE2-SE2'));
+    A2     = my_sqrt(Gamma2);
+    y11    = -eye(4)+1i*A1*G11*A1;
+    y12    = 1i*A1*G1N*A2;
+    y21    = 1i*A2*GN1*A1;
+    y22    = -eye(4)+1i*A2*GNN*A2;
+    %y=[y11,y12;y21,y22];   %the basis here is [e1u,e1d,h1u,h1d,e2u,e2d,h2u,h2d]
+    % e/h for electron/hole, 1/2 for lead 1/2, u/d for spin up/down
+    y11ee=y11(1:2*1     , 1:2*1);
+    y12ee=y12(1:2*1     , 1:2*1);
+    y11eh=y11(1:2*1     , 2*1+1:4*1);
+    y12eh=y12(1:2*1     , 2*1+1:4*1);
+
+    y21ee=y21(1:2*1     , 1:2*1);
+    y22ee=y22(1:2*1     , 1:2*1);
+    y21eh=y21(1:2*1     , 2*1+1:4*1);
+    y22eh=y22(1:2*1     , 2*1+1:4*1);
+
+    y11he=y11(2*1+1:4*1 , 1:2*1);
+    y12he=y12(2*1+1:4*1 , 1:2*1);
+    y11hh=y11(2*1+1:4*1 , 2*1+1:4*1);
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/T_vs_E_and_Gammaz_SpinSx_1DQAHI.m

@@ -1,0 +1,199 @@
+% ============= T vs E =========================================
+% TODO Find reference for this code
+clear
+cont=1.0;   % =1 for 2D countour plot, otherwise for 1D plot
+
+% Here we use ts as a reference for other energies.
+L=20;        % number of sites
+ts=10;       % hoping
+tso=1.0;     % spin orbital coupling
+tsoL=0;      % spin orbital coupling of the leads
+tc1=0.2*ts;  % coupling between lead 1 and the sample
+tc2=0.2*ts;  % coupling between lead 2 and the sample
+muL=5.0;     % chemical potential of the leads
+muS=0;       % chemical potential of the sample
+disorder=0;  % local disorder
+delta=0.0;   % superconducting pairing
+
+M_gamma=200; % gamma
+N_E=200;     % E
+
+if cont==1
+    % For cont=1, we try to plot G as a function of gamma
+    % and E.
+    gamma=3*(-ts:2.0*ts/M_gamma:ts);  % Zeeman energy
+    E=(-muL:2*muL/N_E:1*muL);
+else
+    gamma=3.0;      % Zeeman energy Gammz_z as a constant
+    gap=min(abs(2*ts-abs(gamma)),2*abs(tso));
+    %  E=(-1*gap:2*gap/N:1*gap);                                 % bias energy eV
+    E=(-muL:2*muL/N_E:1*muL);
+    %pause(0.5)
+end
+
+M_gamma=length(gamma);N_E=length(E)
+pause(0.5)
+
+% TC: Transmission Coefficient.
+% TL: what? TODO
+TCee=zeros(N_E,M_gamma);
+TChe=zeros(N_E,M_gamma);
+TLee=zeros(N_E,M_gamma);
+TLhe=zeros(N_E,M_gamma);
+dis=disorder*(rand(1,L)-0.5);
+
+for i=1:N_E
+    i % Indicating the progress of this script
+    for j=1:M_gamma
+        [y11ee,y12ee,y11eh,y12eh,y21ee,y22ee,y21eh,y22eh,y11he,y12he,...
+          y11hh,y12hh,y21he,y22he,y21hh,y22hh]=ScatteringM(E(i),L,muS,muL,ts,tc1,tc2,tso,tsoL,delta,gamma(j),dis);
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/V_dl.m

@@ -1,0 +1,6 @@
+function y=V_dl(tc)
+% Vdl: The coupling between the sample and the lead. Vld=Vdl'
+% T: the coupling amplitude
+% TODO I think I should ask the R.A. about this.
+y=tc*diag([-1,-1,-1,-1]);
+end

### 2016-10-21 Lattice Green function/1D QAHI Conductance/V_lead(deceased).m

@@ -1,0 +1,15 @@
+function y=V_lead(ts,tso)
+%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
+%tso: SOC
+y=zeros(4);
+for i=1:1
+    y(i,i)=-ts;
+    y(i+1,i+1)=-ts;
+    y(i+2*1,i+2*1)=ts;
+    y(i+3*1,i+3*1)=ts;
+    
+    y(i,i+1)=tso;
+    y(i+2*1,i+1+2*1)=-tso;
+    y(i+1,i)=-tso;
+    y(i+1+2*1,i+2*1)=tso;
+end

### 2016-10-21 Lattice Green function/1D QAHI Conductance/V_sample.m

@@ -1,0 +1,23 @@
+function y=V_sample(ts,tso)
+%V: the inside coupling term of the sample between two wires: Vn,n+1; Vn+1,n=conj(Vn,n+1).
+%tso: SOC
+% electron and hole section are the same in topological insulator case.
+
+% ---- A exmaple output ------
+% [     -ts,     tso, zero1_3, zero1_4]
+% [    -tso,      ts, zero2_3, zero2_4]
+% [ zero3_1, zero3_2,     -ts,     tso]
+% [ zero4_1, zero4_2,    -tso,      ts]
+% -------------------------------
+% TODO find reference for this
+y=zeros(4);
+for i=1:1
+    y(i,i)=-ts;
+    y(i+1,i+1)=ts;
+    y(i+2*1,i+2*1)=-ts;
+    y(i+3*1,i+3*1)=ts;
+    y(i,i+1)=tso;
+    y(i+2*1,i+1+2*1)=tso;
+    y(i+1,i)=-tso;
+    y(i+1+2*1,i+2*1)=-tso;
+end

### 2016-10-21 Lattice Green function/1D QAHI Conductance/g11.m

@@ -1,0 +1,130 @@
+function y=g11(E,mu,ts,tso,w_energy_resol)
+%g11 The submatrix of the Green function of the LEAD
+% Obtained by N times of recursion
+% Checkpoint: I think I understand this code now.
+% For derivation pls refer: Appendix B of the dissertation
+    % TODO find reference for following line of code
+    D=(E+1i*w_energy_resol)*eye(4)-H_lead(1,mu,ts,tso);
+    % TODO find reference for following line of code
+    A=V_lead(ts,tso);
+    B=A';
+    d=D;
+    for i=1:1000 %maximum number of recursive times
+        % The following 4 lines of code seems to come from:
+        d1=d-A/D*B;
+        D1=D-A/D*B-B/D*A;
+        A1=A/D*A;
+        B1=B/D*B;
+        if max(max(abs(d1-d)))<1e-99
+            % TODO 1e-99 might be too small...
+            break
+        end
+        d=d1;
+        D=D1;
+        A=A1;
+        B=B1;
+    end
+    y=eye(4)/d1;
+end
+
+function y=H_lead(L,mu,ts,tso)
+% TODO I should find reference for this.
+    y=zeros(4*L);
+    Gamma=00.0;  % Gamma: the Zeeman energy in the leads.
+    condition=1.0; % =1 for spin independent hoping ts
+    %tso=0.0; tso=0 or not, the results are quite different!
+    m_y=00.0;
+    m_x=0.0;
+
+    %=====================================================================
+    % Additional term which break C2,T2 symmetry but preserve C1 and T1
+    % symmetry. To test the influence of C1 and T1 symmetry.
+    %y(i,i+L)=I*m_y;
+    %y(i+L,i)=-I*m_y;
+    %y(i+2*L,i+3*L)=-I*m_y;
+    %y(i+3*L,i+2*L)=I*m_y;
+    %=====================================================================
+    % TODO what is the point of the following line? It is never used in
+    % actually usage.
+    % TODO Also, the variable I is not defined!
+    for i=1:L-1
+        y(i,i)         = Gamma-mu;
+        y(i+L,i+L)     = -Gamma-mu;
[…]

### 2016-10-21 Lattice Green function/1D QAHI Conductance/my_sqrt.m

@@ -1,0 +1,9 @@
+function y=my_sqrt(A)
+% this function calculates the squre root of a sparse complex matrix
+%
+%A=round(A*10^5)/10^5;
+[V,D]=eig(full(A)); % full: sparse matrix -> full matrix
+d=sqrt(D);
+% What is the point of doing "/V" here? TODO
+y=V*d/V;
+end

### 2016-10-22 Notes of Bernvig's Book/Ch2 Berry Phase/Ch2 Berry Phase.tex
New notes to Bernevig's book. New physics LaTeX package.

@@
 \usepackage{mathrsfs} % For \mathscr{ABC}
-% Followings are for the special character: differential "d".
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
 \numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
@@
 \usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex
 
@@
 
+% -=---------------- My Own New commands ---------------
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physics-taper}
+% Referenced package: \usepackage{physics}
+
+%  Vector notation ---------------------
+% \DeclareDocumentCommand\vectorbold{ s m }{
+%     \IfBooleanTF{#1}
+%     {\boldsymbol{#2}}
+%     {\mathbf{#2}}
+% } % Vector bold [star for Greek and italic Roman]
+% \DeclareDocumentCommand\vb{}{\vectorbold} % Shorthand for \vectorbold
+% 
+% \DeclareDocumentCommand\vectorunit{ s m }{
+%     \IfBooleanTF{#1}
+%     {\boldsymbol{\hat{#2}}}
+%     {\mathbf{\hat{#2}}}
+% } % Unit vector [star for Greek and italic Roman]
+% \DeclareDocumentCommand\vu{}{\vectorunit} % Shorthand for \vectorunit
+% 
+% \DeclareDocumentCommand\vdot{}{\boldsymbol\cdot} % Vector dot product symbol
+% \DeclareDocumentCommand\cross{}{\boldsymbol\times} % Vector cross product symbol
+% \DeclareDocumentCommand\vnabla{}{\boldsymbol\nabla} % Vector bold \nabla symbol
+% \DeclareDocumentCommand\grad{}{\vnabla} 
+% \DeclareDocumentCommand\dive{}{\vnabla\vdot} 
+% \DeclareDocumentCommand\curl{}{\vnabla\cross}
+% \DeclareDocumentCommand\laplacian{}{\nabla^2} 
+% 
+% % Operators ----------------------------
+% \let\imaginary\Im
+% \RenewDocumentCommand\Im{g}{
+%     \IfNoValueTF{#1}
+%     {\operatorname{Im}}
+%     {\operatorname{Im}\left\{ #1 \right\}}
+% }
+% \let\real\Re
+% \DeclareDocumentCommand\Re{g}{
+%     \IfNoValueTF{#1}
+%     {\operatorname{Re}}
+%     {\operatorname{Re} \left\{ #1 \right\} }
+% }
 \title{Notes of Chapter 2 of Bernevig's Book}
@@
         m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
-        m\left(\vec{R}(t')\right) \diff t' }
+        m\left(\vec{R}(t')\right) \dd t' }
 \end{align}
@@
     \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
-    \diff \vec{R}
+    \dd \vec{R}
+    = \int_{\text{curve}} \vec{A}_n \vdot\dd \vec{R}
 \end{align}
 (equation 2.8) 
-Also, one defines
+where one defines
 \begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
@@
     \label{fact:gamma_is_real}
-    $  $
-    \begin{center}
         $\gamma_n$ is real
-    \end{center}
 \end{fact}
+By virtue of fact \ref{fact:gamma_is_real}, we have
+\begin{align}
+    \gamma_n = -\Im \int_\text{curve} \braket{ n|\nabla_{\vec{R}}\,n}
+    \vdot \dd \vec{R} 
+\end{align}
 \begin{fact}
-    $ $
-    \begin{center}
-        Berry connection $\vec{A}_n$ is gauge-dependent 
-    \end{center}
+    Berry connection $\vec{A}_n$ is gauge-dependent.
     The dependence is: If 
@@
 \begin{fact}
-    $  $
-    \begin{center}
-        $\gamma_n$ is gauge-dependent, unless the path tranverses a
+    $\gamma_n$ is gauge-dependent, unless the path transverses a
     closed loop.
-    \end{center}
     Since 
@@
 \end{ex}
-By virtue of fact \ref{fact:gamma_is_real}, we have
+
+When the parameter space is $\mathbb{R}^3$, we have a simpler
+expression for berry phase. It is derived on page 4 (equation 2.12)
+that
+\begin{align}
+    \gamma_n = -\Im \oint \braket{\grad_{\vb{R}}
+    n|\cross|\grad_{\vb{R}} n} \vdot \dd \vb{s}
+    = -\Im \oint \mathcal{A}^n \vdot \dd\vb{s}
+\end{align}
+where we have defined:
+\begin{defi}[Berry Curvature $\mathcal{A}^n$]
+\nomenclature{Berry Curvature $\mathcal{A}^n$}{\nomrefpage.}
+    \begin{align}
+        \mathcal{A}^n = \braket{\grad_{\vb{R}} n|\cross|\grad_{\vb{R}} n}
+    \end{align}
+    In components (repeated index automatically summed):
+    \begin{align}
+        \mathcal{A}_i^n = \varepsilon_{ijk} \braket{\partial_j n |
+        \partial_k n}
+    \end{align}
+\end{defi}
+By analogy with the theory of electromagnetic fields, this is also
+called Berry field, dentoed by $F_{jk}$ in Bernevig's book.
+\nomenclature{Berry field $F_{jk}$}{\nomrefpage}. More specifically:
+$F_{jk} = \braket{\partial_j n(\vb{R})|\partial_j n(\vb{R})} - (j
+    \leftrightarrow k) $.
+
+\section{Gauge-independent calculation of Berry Curvature}
+\label{sec:Gauge-independent-calculation-of-Berry-Curvature}
+For numerical considerations, we Bernevig gives a new way to calculate
+the Berry curvature. I shows in page 5 to 6 that:
+\begin{align}
+    \gamma_n = -\Im \oint \dd\vb{s} \sum_{m\neq n}
+    \frac{\bra{n(\vb{R})}\grad_{\vb{R}} H \ket{m(\vb{R})}
+        \cross \bra{m(\vb{R})}\grad_{\vb{R}} H \ket{n(\vb{R})} }
+        {(E_n-E_m)^2}
+\end{align}
+There are two advantages of this formula:
+\begin{enumerate}
+    \item It is intrinsically gauge-independent (see page 6 for
+        explanation).
+    \item It is nolonger necessary to pick $\ket{n}$ to be smooth \&
+        single-valued. \marginpar{Don't know why}
+\end{enumerate}
+There are several remarks about this formula on page 7. One important
+remark is that:
+\begin{fact}
+    \begin{align}
+        \sum_n \gamma_n = 0
+    \end{align}
+\end{fact}
+
+\section{Degeneracy and level-crossing}
+\label{sec:Degeneracy-and-level-crossing}
+Page 7 has a discussion about the serious problems posed by the
+degenracy points. Then we turn our attention to two-level system.
+
+    \subsection{Two-level system and Berry connection
+    \texorpdfstring{$\vb{A}_n$}{}}
+    \label{sec:Two-level-system-and-Berry-connection}
+    Here Bernevig considers a system with Hamiltonian
+    \begin{equation}
+        H = \epsilon(\vb{R}) I + \vb{d}(\vb{R})\vdot\vb{\sigma}
+    \end{equation}
+
+    He first calculate in a general setting and concludes that the Berry
+    field is
+    \begin{equation}
+        \vb{V}_{-} = \frac{1}{2}\frac{\vb{d}}{d^3}
+    \end{equation}
+    However, I don't think it is a good calculation, explained in page 8.
+    On the other hand, Bernevig also gives an alternative calculation in
+    the following.
+
+        \subsubsection{Two-level system using Hamiltonian approach}
+        \label{sec:Two-level-system-using-Hamiltonian-approach}
+        On page 8 to 10, I gives the calculation of Berry phase of
+        Spin in a varying magnetic environment. Consider the
+        Hamiltonian:
+        \begin{equation}
+            H(\vb{B}) = \vb{B}\vdot \vb{S} 
+        \end{equation}
+        with
+        \begin{equation}
+            n = -s, -s+1,\cdots, s
+        \end{equation}
+        One finds:
+        \begin{align}
+            \gamma_n = - n\oint \frac{\vb{B}}{B^3} \dd\vb{s}
+        \end{align}
+        (equation 2.31)
+        If the integration is taken on the surface of a sphere, then
+        we have (noting that the solid angle $\dd
+        \Omega=\sin(\theta)\dd\theta\dd\phi$. Use $\Omega$ to denote
+        the solid angle of the integration area)
+        \begin{equation}
+            e^{i\gamma_n} = e^{-i n \Omega}
+        \end{equation}
+
+        There are several remarks on page 10. The important ones are
+        \begin{remark}
+            If we integrate in a whole sphere, and the sphere contains
+            several "poles" - the degeneracy point, we have
+            \begin{align}
+                |\gamma_i| = 4\pi n \times \text{(number of poles
+                inside)}
+            \end{align}
+            Similary, if the paremeter space in 2 dimensional, then
+            \begin{align}
+                |\gamma_i| = 2\pi n \times \text{(number of poles
+                inside)}
+            \end{align}
+            Specifically, for electrons
+            \begin{align}
+                |\gamma_i| = \pi \times \text{(number of poles
+                inside)}
+            \end{align}
+            Therefore, an electron transversing a circle will
+            accumulate a phase of $e^{i\pi}=-1$.
+        \end{remark}
 \section{Anchor}

### 2016-10-22 Notes of Bernvig's Book/Ch4 TR symmetry/Notes about TR symmetry.tex
New notes about Berry phase.
New notes to Bernevig's book. New physics LaTeX package.

--- 2016-10-20 Notes about TR symmetry/Notes about TR symmetry.tex
@@
 \usepackage[all]{xy}
+
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physics-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physics-taper}
 
@@
         \begin{proof}
-            Recall for 
+            Recall we have:
+            \begin{align}
+                \sigma_{ij} = \int \frac{\diff k_x\diff k_y}{(2\pi)^2}
+                \sum_{a=1}^{m} (-i) F_{jk}^a(\vb{k})
+                = \frac{1}{(2\pi)^2} \sum_{a=1}^m \gamma_a
+            \end{align}
+            i.e., The Hall conductivity is an integral over the filled
+            bands of the Berry curvature. (See (3.79) of\cite{bernevig})
+
+            Here 
+            $$F_{ij}(\vb{k}) = -i \left( \braket{\partial_i
+            u(k)|\partial_j u(k)} - (i\leftrightarrow j) \right)$$
+            is the Berry field strength.
+            For system with TR symmetry, we have
+            $$ u(k) = T u(-k)$$
+            (Note that $T$ flips the sign of $k$) Since $T$ is
+            antiunitary, we have $ u(-k) = u(k)^*$. Therefore
+            $\braket{\partial_i u(-k)|\partial_j u(-k)} = 
+              \braket{\partial_j u(k)|\partial_i u(k)}$
+            So:
+            \begin{equation}
+                F_{ij}(\vb{-k}) = - F_{ij}(\vb{k})
+            \end{equation}
+            Therefore $F_{ij}$ is a odd function. So its integration
+            over the whole BZ is zero, i.e. $\sigma_{ij}$ is zero.
         \end{proof}

### 2016-10-22 Notes of Bernvig's Book/Ch4 TR symmetry/Notes about TR symmetry.tex
New notes about TR symmetry

@@
     \begin{fact}
+        \label{fact:TROperator_TRInSpin_InnerProdTUandU}
         For any kets $\ket{\alpha},\ket{\beta}$, we have
@@
         \end{proof}
+        \subsubsection{Time reversal symmetry in electron bands}
+        \label{sec:Time-reversal-symmetry-in-electron-bands}
+        Natually operator $T$ flips the sign of the
+        creation/annihilation operator of an electron. We now proves:
+        \begin{thm}
+            We have, up to a phase,
+            \begin{align}
+                & T c_\sigma T^{-1} =
+                i(\sigma_y)_{\sigma\sigma'}c_{\sigma'} \\
+                & T c_\sigma^\dagger T^{-1} = 
+                ic_{\sigma'}^\dagger(\sigma_y)^T_{\sigma'\sigma}
+            \end{align}
+            Where $\sigma_y = \left( \begin{array}{cc}
+                         0 & -i \\
+                         i & 0 \\ \end{array} \right)$.
+            and $\sigma$ label spin $\uparrow$ and spin
+            $\downarrow$.
+        \end{thm}
+        \begin{proof}
+            Assuming
+            \begin{align}
+                & Tc_\uparrow T^{-1} = A c_\downarrow \\
+                & Tc_\downarrow T^{-1} = B c_\uparrow
+            \end{align}
+            Then we need only to prove $AB^* = -1$. Since up to a
+            phase change, we can let
+            \begin{equation}
+                A = 1\,, B = -1
+            \end{equation}
+            This is what the theorem says.
+
+            Let's consider the following
+            $$T c_\uparrow c_\uparrow^\dagger \ket{0}$$
+            First, it is equal to $T\ket{0}$. On the other hand, we
+            can let the $T$ jumps over one creation operator:
+            $$A c_\downarrow T c_\uparrow^\dagger \ket{0}$$
+            Now insert $T^{-1}T$ between $A$ and $c_\downarrow$. And
+            makes the new $T$ one jump to the right:\
+            $$ A T^{-1} B c_\uparrow T^2 c_\uparrow^\dagger \ket{0}$$
+            Now be careful to notice that the first $T^{-1}$ is $T$,
+            whereas the second $T^2$ is $- \mathbbm{1}$ (watch the
+            Spin!). With simple calculation one finds it is equal to
+            $$ -AB^* T\ket{0}$$
+            Hence $-AB^* = 1$. The case for the creation operatros is
+            similar.
+        \end{proof}
+        \begin{thm}
+            For the creation and annihilation in the momentum space,
+            we have:
+            \begin{align}
+                & Tc^\dagger_{\vb{k}\sigma} T^{-1} =
+                    c^\dagger_{\vb{-k}\sigma'}
+                    i(\sigma_y)^T_{\sigma\sigma'} \\
+                & Tc_{\vb{k}\sigma} T^{-1} =
+                    c_{\vb{-k}\sigma'}
+                    i(\sigma_y)_{\sigma\sigma'}
+            \end{align}
+        \end{thm}
+        \begin{proof}
+            This is quite obvious since $T$ changes the coefficient of
+            fourier expansion: $e^{-i \vb{k}\vdot\vb{R}_j} \to 
+            e^{i \vb{k}\vdot\vb{R}_j}$
+        \end{proof}
+        Then directly apply $T$ and $T^{-1}$ to both sides of
+        $$H = \sum_{\vb{k}} c^\dagger_{\vb{k}\sigma}
+            h^{\sigma\sigma'}(\vb{k})
+            c_{\vb{k}\sigma'}$$
+
+            gives (noticing $h(k)$ is just a number that $T$ turns it
+            into its conjugate number):
+        \begin{equation}
+            h^{\sigma\sigma'}(\vb{k}) \mapsto
+            i(\sigma_y)^T_{\sigma_1\sigma} (h^{\sigma,\sigma'})^*
+            i(\sigma_y)_{\sigma'\sigma_2}
+        \end{equation}
+        If one carefully examine the cases, one finds that when
+        $\sigma_1\neq\sigma_2$, the above should obviously be $0$. And
+        when $\sigma_1=\sigma_2$, the RHS above is surprisingly just
+        $(h^{\{\cdot,\cdot\}})^*$, with appropriate spin.
+        So we have compactly:
+        \begin{thm}
+            For electron bands,
+            \begin{equation}
+                Th(\vb{k})T^{-1} = h(-\vb{k})
+            \end{equation}
+            with spin inverted.
+        \end{thm}
+
+        Then we have the following fact:
+        \begin{fact}
+            For Time reversal symmetric electron bands, there is
+            always at least two degenerate state
+        \end{fact}
+        This is obvious since:
+        $$h(-\vb{k}) T\ket{u(\vb{k})} = Th(\vb{k})\ket{u(\vb{k})}
+        = TE(\vb{k})\ket{u(\vb{k})} = E(\vb{k})T\ket{u(\vb{k})} $$
+        Also, by fact \ref{fact:TROperator_TRInSpin_InnerProdTUandU},
+        one sees that the time reversed state $T\ket{u(\vb{k})}$ is
+        distinct from the orginal state. Hence the double degeneracy.
 

### 2016-10-24 GRE Physics Prep/General Physics Formula.tex
A lot of review notes for physics GRE.

@@
 \usepackage{color,soul}
+
+% Resolving pdf version warning
+\pdfoptionpdfminorversion=7
+
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physics-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physics-taper}
 
@@
 path
+
+\paragraph{First, Second Speed}
+
+\textbf{Circular}: $v = \sqrt{gR}$.
+
+\textbf{Escape Speed} $\frac{1}{2}mv^2 = \frac{GMm}{R}$, so
+$v=\sqrt{2GM/R}$.
 \begin{defi}[Normal force]
@@
 \end{align}
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{some-rotational-inertias}.png}
+    \caption{Some Rotational Inertias (p. 255 of\cite{book}) }
+    \label{fig:some-rotational-inertias}
+\end{figure}
 \paragraph{Work and Rotational Kinetic Energy} 265
@@
 \begin{align}
-    P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L} 
+    & P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L}  \\
+    & P_\text{cond} = A \frac{T_H-T_C}{\sum(L_i/K_i)}
 \end{align}
@@
     \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond}.png}
+    \caption{pp.494 of \cite{book}}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond_series}.png}
+    \caption{pp.495 of \cite{book}}
 \end{figure}
@@
         1   & $p$                          & Isobaric     & $Q = nC_p\Delta T;W=p\Delta V$ \\
-        2   & $V$                          & Isothermal   & $Q=W=nRT\ln(V_f/V_i); \Delta E_\text{int}=0$  \\
+        2   & $T$                          & Isothermal   & $Q=W=nRT\ln(V_f/V_i); \Delta E_\text{int}=0$  \\
         3   & $pV^\gamma$, $TV^{\gamma-1}$ & Adiabatic    & $W=-\Delta E_\text{int}$ \\
@@
 \end{table}
+In particular, for Adiabatic process (let $K\equiv pV^\gamma$):
+\begin{equation}
+    W = \int_i^f \frac{K}{V^\gamma}\dd V =
+    \frac{p_fV_f-p_iV_i}{1-\gamma}
+\end{equation}
 \begin{figure}[H]
@@
 \end{align}
+
+Even more accurate formulae found in pp. 158 Kardar's book \cite{kardar}:
+\begin{align}
+    & C_V = \frac{6n-3-r}{2}k_B \\
+    & C_p = C_V + k_B
+\end{align}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{kardar-C_v-formulae}.PNG}
+    \caption{Examples of $n,r,$ and $\gamma$.}
+\end{figure}
+But these are \hl{\textbf{classical results}}, only valid at high
+temperature! (See the refered page for details).
 
@@
 \end{align}
+Cutting Magnetic field lines:
+\begin{equation}
+    \mathcal{E} = BLv 
+\end{equation}
+Cutting Magnetic field lines in circular motion:
+\begin{equation}
+    \mathcal{E} = B(\frac{1}{2}\omega R) R = \frac{1}{2}B\omega R^2
+\end{equation}
 
@@
 
+\paragraph{Radiation} $ $
+
+Electric dipole:
+\begin{equation}
+    \braket{P} = \frac{\mu_0 p_0^2 \omega^4}{12\pi c}
+\end{equation}
+where $p_0 = q_0 d$.
+Electric quadrupole: $\braket{P} \propto \omega^6$.
+
+(The cases for Magnetic dipole is similarly $\propto \omega^4$)
+
+\textbf{Lienard's generalization of the Larmor formula}
+\begin{align}
+    P &= \frac{\mu_0 q^2 \gamma^6}{6\pi c}
+    \left( a^2- \abs{\frac{\vb{v}\cross\vb{a}}{c}}^2\right) \\
+    &\approx \frac{\mu_0q^2}{6\pi c} a^2
+\end{align}
+(\textbf{pp.448 of \cite{Griffiths_electrod}}).
+
+\begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+
 (\textbf{pp.882 ch32 of \cite{book}})
@@
 
+\hl{Light waves change phase by $\pi/2$ when they reflect from the surface of
+a medium with higher refractive index than that of the medium in which
+they are travelling.}
+
 \paragraph{Interference} (\textbf{pp.981 ch35 of \cite{book}})
@@
 
+\section{Relativity}
+\label{sec:Relativity}
+
 \paragraph{Relativity} (\textbf{pp.1048 ch37 of \cite{book}})
 \begin{align}
+    \gamma &= \frac{1}{\sqrt{1-\beta^2}} \\
     \Delta t &= \gamma \Delta t_0 \\
@@
     E &= mc^2 + K = \gamma mc^2 \\
-    E^2 &= (pc)^2 + (mc^2)^r
+    E^2 &= (pc)^2 + (mc^2)^2
 \end{align}
+
+\paragraph{Electrodynamics with Relativity} (\textbf{pp.526-531 of
+\cite{Griffiths_electrod}})
+\begin{equation}
+    E = \gamma_0 E_0
+\end{equation}
+    (Only in the direction perpendicular to
+    the motion, without $B$ field)
+\begin{align}
+    & \bar{E}_x = E_x \\
+    & \bar{E}_y = \gamma(E_y - v B_z) \\
+    & \bar{E}_z = \gamma(E_z + v B_y) \\
+    & \bar{B}_x = B_x \\
+    & \bar{B}_y = \gamma(B_y + \frac{v}{c^2} E_z) \\
+    & \bar{B}_z = \gamma(B_z - \frac{v}{c^2} E_y)
+\end{align}
+
+\section{Quantum Mechanics}
+\label{sec:Quantum-Mechanics}
 
@@
 
+\paragraph{Infinite Square Well} (\textbf{pp.32 of \cite{Griffiths_QM}})
+
+\begin{align}
+    & k_n = \frac{n\pi}{a} \\
+    & E_n = \frac{\hbar^2 k_n^2}{2m} \\
+    & \psi_n = \sqrt{\frac{2}{a}} \sin(k_n x)
+\end{align}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/qm_infinite_square_well.PNG}
+    \caption{Wave functions}
+\end{figure}
 \paragraph{Conductions} (\textbf{pp.1160 ch41 of \cite{book}})
@@
     P(E) &= \frac{1}{e^{(E-E_F)/kT} +1} 
+\end{align}
+
+\section{Atomic Physics}
+\label{sec:Atomic-Physics}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{electron-state}.PNG}
+    \caption{Electron State (from pp.162 of \cite{book_atomic})}
+\end{figure}
+
+\paragraph{Standard Model}
+Read page 1244 of \cite{book}.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{Standard-Model-of-Elementary-Particles}.pdf}
+    \caption{Standard Model of Elementary Particles (from Wikipedia)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{Elementary_particle_interactions_in_the_Standard_Model}.png}
+    \caption{Elementary particle interactions in the Standard Model
+    (from Wikipedia)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{Comprehensive-standard-model-particle-chart}.jpg}
+    \caption{Comprehensive standard model particle Chart }
+\end{figure}
+(from \href{http://electron6.phys.utk.edu/phys250/modules/module%206/images/particle_chart.jpg}{Link})
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.0\linewidth]{pics/{Elementary-Particles-concept-map}.pdf}
+    \caption{Elementary Particles concept Map}
+\end{figure}
+\section{Positronium}
+\label{sec:Positronium}
+
+\href{https://en.wikipedia.org/wiki/Positronium}{Wiki Positronium}.
+
+Energy:
+\begin{equation}
+    E_n = -\frac{6.8 \text{eV}}{n^2}
+\end{equation}
+\section{Common Mathematical Formulae}
+\label{sec:Common-Mathematical-Formulae}
+\begin{align}
+    & \frac{1}{1-x} = 1 + x + x^2 + x^3 + \cdots
 \end{align}
@@
     \& Resnick.
+    \bibitem{book_atomic} Atomic Physics. Fujia, Yang. (Chinese)
+    \bibitem{Griffiths_electrod} Introduction to Electrodynamics, 3rd,
+    Griffiths.
+    \bibitem{Griffiths_QM} Introduction to Quantum Mechanics, 2nd,
+    Griffiths.
+    \bibitem{kardar} Kardar. Statistical Physics of Particles. (2007)
 \end{thebibliography}

### 2016-10-25 Complex Geometry - index/Complex Geometry - index.tex
Yesterday's note for class about group theory. And new complex geometry notes.
1.New physics GRE prep. 2. Learn to organize tex into small subfiles.

--- 2016-08-03 Complex Geometry - index/Complex Geometry - index.tex
@@
 
+% To include PDF in higher version format.
+\pdfoptionpdfminorversion=6
+
 \title{Complex Geometry - Index of Notations and ideas}
@@
 
+\section{Note}
+\label{sec:Note}
+This notes aims to provide an index of symbols, definitions of the book
+\cite{book}. It is very useful, especially when there are so many
+wildly different concepts introduced!
+
 \part{Indices of Notation}
 
-\chapter{Book}
-\section{1. Local Theory}
-    \subsection{1.1 Holomorphic Functions of Several Variables}
-    \label{sec:1.1_book}
-    \textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.
-
-    \textcolor{blue}{holomorphic}: pp.1. pp4. Def 1.1.1. pp.10(Def.1.1.8).
-
-    \textcolor{blue}{Cauchy-Riemann equations}: pp.2
-
-    \textcolor{blue}{$\frac{\partial}{\partial z}$,$\frac{\partial}{\partial \bar{z}}$}:
-    $\frac{\partial}{\partial z}:= \frac{1}{2}
-            (\frac{\partial}{\partial x} 
-            -i \frac{\partial}{\partial y})
-            $
-    ,
-    $\frac{\partial}{\partial \bar{z}}:= \frac{1}{2}
-    (\frac{\partial}{\partial x} 
-    + i \frac{\partial}{\partial y})
-    $
-
-    \textcolor{blue}{Maximum principle}: pp.3.
-
-    \textcolor{blue}{Identity theorem}: pp.3.
-
-    \textcolor{blue}{Riemann extension theorem}: pp.3. pp.9 (Prop. 1.1.7).
-
-    \textcolor{blue}{Riemann mapping theorem}: pp.3.
-
-    \textcolor{blue}{Liouville theorem}: pp.4.
-
-    \textcolor{blue}{Residue theorem}: pp.4.
-
-    \textcolor{blue}{polydiscs $B_\epsilon(\omega)$}: $\{z| |z_i-\omega_i| <\epsilon\} $.  pp.4.
-
-    \textcolor{blue}{Hartogs' theorem}: Prop. 1.1.4. pp.6.
-
-    \textcolor{blue}{Weierstrass preparation theorem (WPT)}:
-    Prop. 1.1.6. pp.8.
-
-    \textcolor{blue}{Weierstrass polynomial}: Def. 1.1.5. pp.7.
-
-    \textcolor{blue}{$Z(f)$}: zero set of $f$. pp.9.
-
-    \textcolor{blue}{biholomorphic}: pp.10.
-
-    \textcolor{blue}{(complex) Jacobian, regular, regular value}: Def. 1.1.9. pp.10.
-
-    \textcolor{blue}{IFT. Inverse function theorem}: Prop 1.1.10 pp.11.
-
-    \textcolor{blue}{IFT. Implicit function theorem}: Prop 1.1.11. pp.10.
-
-    \textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n}$}:
-    sheaf of holomorphic functions on $\mathbb{C}^n$. Def. 1.1.14. pp.14.
-
-    \textcolor{blue}{$\mathcal{O}_{\mathbb{C}^n,z}$}: Def. 1.1.14. pp.14.
-
-    \textcolor{blue}{$\mathcal{O}^*_{\mathbb{C}^n,0}$}:
-    units of $\mathcal{O}_{\mathbb{C}^n,0}$. pp.14.
-
-    \textcolor{blue}{UFD, unique factorization domain, irreducible}: 
-    Def. 1.1.16. pp.14.
-
-    \textcolor{blue}{Gauss Lemma}: pp.14.
-
-    \textcolor{blue}{Weierstrass division theorem}: Prop. 1.1.17. pp.15.
-
-    \textcolor{blue}{germ of set}: (\textbf{pp.18})
-
-    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})
-
-    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})
-
-    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})
-
-    \textcolor{blue}{$I(X)$}: the set of all $f\in
-    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
-    % TODO bookmark
-    \subsection{1.2 Complex and Hermitian Structures}
-    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
-    (\textbf{pp.25})
-
-    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
-    of $I$.
-    (\textbf{pp.25})
-
-    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
-    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
-    (\textbf{pp.27})
-
-    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{compatible}:an almost complex structure $I$ is
-    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
-    (\textbf{pp.28})
-
-    \textcolor{blue}{Conformal equivalence}(between scalar product):
-    (\textbf{pp.29})
-
-    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
-    (\textbf{pp.29})
-    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
-    \quad(Local calculation could be found on \textbf{pp.31})
-
-    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
-    (\textbf{pp.30})
-\section{2.Complex Manifolds}
-
-    \subsection{2.1 Complex and Hermitian Structures}
-    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
-	\subsection{2.2 Holomorphic Vector Bundles}
-
-    \textcolor{blue}{$\tau_X$}: holomorphic tangent bundle of a complex manifold $X$ (Def 2.2.14 at pp. 71).
-
-    \textcolor{blue}{$\varOmega_X$, $\varOmega^p_X$}: holomorphic cotangent bundle and holomorphic $p$-forms. (Def 2.2.14 at pp. 71)
-
-    \textcolor{blue}{$K_X$}:=det($\varOmega_X$) = $\varOmega_X^n$, the canonical bundle of $X$. (Def 2.2.14 at pp. 71)
-
-    \subsection{2.6 Differential Calculus on Complex Manifolds}
-
-    \textcolor{blue}{$\wedge^k_{\mathbb{C}}X$}:=$\wedge^k(T_{\mathbb{C}}X)^*$. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
-                        \bigoplus_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\mathcal{A}^k_{X,\mathbb{C}}$,$\mathcal{A}^{p,q}_X$}: sheaves of section of the above correspond items. (Def 2.6.7 at pp. 105)
-
-    \textcolor{blue}{$\mathcal{A}^{p,q}(E)$}: the sheaf of $p,q$-forms with values in $E$, a complex vector bundle.
-(Def 2.6.22 at pp.109).
-Note that in particular, $\mathcal{A}^0(E)$ is the sheaf of sections of $E$.
-
-	\subsection{Appendix B: Sheaf Cohomology}
-
-	\begin{itemize}
-		\item
-		\textcolor{blue}{pre-sheaf}: Def B.0.19, pp. 287.
-
-		\item
-		\textcolor{blue}{$\mathcal{C^0_M}$}: the pre-sheaf of continuous functions on $M$. Example B.0.20, pp. 287.
-
-		\item
-		\textcolor{blue}{sheaf}: Def B.0.21, at pp.288.
-
-		\item
-		\textcolor{blue}{\underline{$\mathbb{R}$},\underline{$\mathbb{Z}$}}: constant sheaves, Sometimes written simply as \textcolor{blue}{$\mathbb{R}$}, \textcolor{blue}{$\mathbb{Z}$} respectively.
-pp.
-288.
-		\item
-		\textcolor{blue}{$\mathcal{E}$}: actually a $\mathcal{C}^0_M$-modules. Sometimes identified as $E$. pp.288.
-		\item
-		\textcolor{blue}{(pre)-sheaf homomorphism}: Def B.0.23.  pp.288.
-		\item
-		\textcolor{blue}{Ker($\phi$),Im($\phi$),Coker($\phi$)}: as pre-sheaves in pp.288. sheaves in pp.289, Def B.0.26.
-		\item
-		\textcolor{blue}{injective, surjective of sheaf-homomorphism}:pp.289.
-		\item
-		\textcolor{blue}{complex, exact complex}: Def B.0.27. pp.289
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:
-		\item
-		\textcolor{blue}{text}:	
-	\end{itemize}
-
-\chapter{My lecture Notes}
-
-\section{Lecture 2016 Lecture 1}
-The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.
-
-\section{Lecture 4 (20160307) Complex Manifold}
-
-\textbf{Note}: we use abbrevation \textit{mnfd} for \textit{manifold}.
-
-pp. A:
-    \begin{itemize}
-        \item \textcolor{blue}{Holomorphic Atlas}
-        \item \textcolor{blue}{Holmorphic chart}
-        \item \textcolor{blue}{Complex mnfd}
-    \end{itemize}
-
-pp. B:
-    \begin{itemize}
-        \item \textcolor{blue}{Holomorphic function}
-        \item \textcolor{blue}{$\mathcal{O}_X$}: sheaf of holomorhic functions on a complex mnfd $X$.
-    \end{itemize}
-pp. C:
-    \begin{itemize}
-        \item \textcolor{blue}{Hartdogs' theorem}: on complex mnfd.
-        \item \textcolor{blue}{Holomorphic functions on complex mnfd}:
-    \end{itemize}
-pp. D:
-    \begin{itemize}
-        \item \textcolor{blue}{Complex Lie group}
-        \item \textcolor{blue}{Complex Projective Space, $\mathbb{CP}^n$, or just $\mathbb{P}^n$}.
-    \end{itemize}
-pp. E:
-    \begin{itemize}
-        \item \textcolor{blue}{Topology in $\mathbb{P}^n$}
-        \item \textcolor{blue}{Mnfd structure on $\mathbb{P}^n$, atlas, and the \textbf{canonical covering}}
-    \end{itemize}
-pp. F
-    \begin{itemize}
-        \item Grassmannian mnfd.
-    \end{itemize}
-
-\section{Lecture 5 Submanifolds (20160308)}
-
-pp. A:
-    \begin{itemize}
-        \item Affine Hypersurface (actually this is not quite different from the usual $\mathbb{C}^n$.)
-    \end{itemize}
-
-Part 2. \textbf{Sheaf Theory}
-
-pp. A:
-	\begin{itemize}
-		\item pre-sheaf
-		\item $\mathcal{O}_X(U)$
-		\item $\mathcal{O}^*_X(U)$
-	\end{itemize}
-pp. B:
-	\begin{itemize}
-		\item $C^{\infty}$
-		\item $\mathbb{\underline{Z}}$, sometimes simply denoted as $\mathbb{Z}$: sheaf of localy constant $\mathbb{Z}$-valued functions.
-		\item Sheaf
-	\end{itemize}
-pp. D:
-	\begin{itemize}
-		\item sheaf-morphisms
-	\end{itemize}
-pp. E:
-	\begin{itemize}
-		\item Section
-		\item Ker($\phi$) - sheaf of kernals.
-	\end{itemize}
-pp. F:
-	\begin{itemize}
-		\item Im($\phi$) is a presheaf, but not a sheaf.
-		\item Im($\phi$): the sheafification of Im($\phi$) above. Note that we use the same notation to denote both.
-	\end{itemize}
-
-\section{Lecture 6 Sheaf \& Cohomology (20160315)} pp. A:
-    \begin{itemize}
-        \item Stalk $\mathcal{F}_x$.
-        \item germ
-        \item Directed partial order set
-        \item Directed System
-    \end{itemize}
-pp. B:
-    \begin{itemize}
-        \item Directed limit
-    \end{itemize}
-pp. C:
-\begin{itemize}
-    \item Exact Complex/ Exact Sequence.
-    \item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
-    \item
-\end{itemize}
-pp. D:
-\begin{itemize}
-    \item Čech cohomology
-\end{itemize}
-pp. E:
-\begin{itemize}
-    \item q-cochain
-    \item coboundary operator. $\delta$.
-    \item $Z^p(U,\mathcal{F})$ = Ker.
-    \item $B^p(U,\mathcal{F})$ = Im.
-    \item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
-\end{itemize}
-
-    \subsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
-    pp.1:
-    \begin{itemize}
-        \item q-simplex $\sigma$.
-        \item support $|\sigma|$.
-        \item q-cocain
-        \item $C^q(U,\mathcal{F})$
-        \item Coboundary Operator $\delta$.
-    \end{itemize}
-    pp.2,3,4:
-    \begin{itemize}
-        \item Cochain Complex
-        \item Čech cohomology
-        \item cocycle
-        \item cochain
-        \item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
-        \item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
-    \end{itemize}
-
-\section{Lecture 7 Vector Bundle (20160321)}
-pp.1,2:
-\begin{itemize}
-    \item Vector Bundle
-    \item Trivializing covering, $\{(U_i,\tau_i)\}$.
-    \item trivializing maps, trivializes.
-    \item VB-equivalent of trivializing maps.
-    \item E: total space, X: base space.
-\end{itemize}
-pp. 3,5:
-\begin{itemize}
-    \item transition maps.
-    \item fibre.
-    \item $\mathcal{O}(-1)$
-    \item cocycle condition.
-    \item $\mathcal{T}_X$, Holomorphic tangent bundle.
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item s: section of a holomorphic vector bundle.
-    \item $\mathcal{E}$: sheaf of sections of holomorphic vector bundle. $\mathcal{E}(U)$.
-\end{itemize}
-
-\section{Lecture 8 Almost Complex Structures (20160322)}
-pp. 1,2:
-\begin{itemize}
-    \item $I$: Almost Complex Structure. $I^2=-1$. Sometime $J$ is used in place of $I$.
-    \item $V_{\mathbb{C}}$ := $V\otimes \mathbb{C}$.
-    \item $I_\mathbb{C}$: $I$ extending to $V_{\mathbb{C}}$. Usually abbreviated simply as $I$.
-    \item $V^{1,0}$:= ker$(I+i)$.
-    \item $V^{0,1}$:= ker$(I-i)$.
-\end{itemize}
-
-\section{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}
-
-pp.1,2:
-\begin{itemize}
-    \item $V^*$: dual of $V$.
-    \item $\{dx^i,dy^i\}$.
-    \item $J^*$: $J$ extending to dual space.
-    \item $dz^i,d\bar{z}^i$.
-\end{itemize}
-pp. 3:
-\begin{itemize}
-    \item $S^k(V)$, $\Lambda^k(V)$.
-    \item $s$ and $a$, symmetrization and anti-symmetrization of a tensor.
-    \item $\Lambda^* V$.
-\end{itemize}
-pp. 4:
-\begin{itemize}
-    \item $\Lambda^n T^*_{\mathcal{C}}X$.
-    \item $\Lambda^* T^*_{\mathcal{C}}X$.
-    \item $\Lambda^{p,q} T^*_{\mathcal{C}}X$.
-\end{itemize}
-pp. 5,6:
-\begin{itemize}
-    \item $\mathcal{A}$: sheaf of section of cotangent bundle.
-    \item $\mathcal{A}^n(U)$, $\mathcal{A}^{p,q}(U)$.
-    \item $\Lambda$ on $\mathcal{A}$.
-    \item $d$: de Rham differential.
-    \item $\partial, \bar{\partial}$.
-\end{itemize}
-
-\section{Lecture 10 Debeault Cohomology (20160406)}
-
-pp. 1:
-\begin{itemize}
-    \item $\mathcal{H}^{p,q}(X)$.
-    \item $f^*$: pull-back. Various defintion from pp.1 to pp.4.
-\end{itemize}
-pp. 5,6,7:
-\begin{itemize}
-    \item $\mathcal{A}^{p,q}(U,E):=\Gamma(U,\Lambda^{p,q}T_{\mathbb{C}}^* X \otimes E)$.
-    \item $\bar{\partial}_E$
-    \item $\mathcal{H}^{p,q}(X,E)$.
-    \item $\bar{\partial}$-Poincaré lemma in one variable.
-\end{itemize}
-
-\section{Lecture 11 (20160412)}
-pp.1,2,3: 
-\begin{itemize}
-    \item $\bar{\partial}$-Poincaré lemma in n-dimension
-    \item $\Omega_X^p$: holomorphic p-forms. On pp.2.
-    \item $\check{H}^q(X,\Omega^p)\text{(Čech)}\cong \mathcal{H}_{\bar{\partial}}^{p,q}(X)$(Dolbeault). On pp.3.
-\end{itemize}
-pp. 6,7:
-\begin{itemize}
-    \item Analytic Subvarity.
-    \item Analytic Hybersurface.
-    \item Cousin's Problem.
-\end{itemize}
-
-\section{Lecture 12 Hermitian Structure on Manifold  Manifold (20160418)}
-pp. 1,2,3:
-\begin{itemize}
-    \item $I$ compatible with $<-,->$.
-    \item $\omega$: Fundamental form associated with $<,>$ and $I$. $\omega(v,w):= <I(v),w>$.
-    \item Conformal Equivalence.
-    \item $<,>$: Hermitian Inner Product.
-\end{itemize}
-pp. 4:
-\begin{itemize}
-    \item $( , )$: s.t. $(v,w):=<v,w>-i\omega(v,w) = <v,w> - i <I(v),w>$
-\end{itemize}
-pp. 5:
-\begin{itemize}
-    \item $<,>_{\mathbb{C}}$ be s.t.$<v\otimes \alpha, w\otimes \beta>:= \alpha \bar{\beta} <v,w>$.
-\end{itemize}
-pp. 6:
-\begin{itemize}
-    \item $\frac{1}{2}(,) = <,>_{\mathbb{C}} \arrowvert_{V^{1,0}}$
-\end{itemize}
-pp. 7,8:
-\begin{itemize}
-    \item Local computations: $z_i$,$h_{ij}$,
-    \item $\omega = (...dx^i...dy^i)$
-    \item $\omega$, Fundamental form on Riemannian Mnfd.
-    \item Kähler mnfd: $d\omega \equiv 0$.
-\end{itemize}
-
-\section{Lecture 13 Kähler Manifold (20160419)}
-pp.1:
-\begin{itemize}
-    \item Local computation: $\omega = (...dz^i...d\bar{z}^i)$
-\end{itemize}
-pp.4:
-\begin{itemize}
-    \item Fubini-Study Metric on $\mathbb{CP}^n$.
-\end{itemize}
-
-\section{Lecture 14 Hodge Theory (20160425)}
-pp.1:
-\begin{itemize}
-    \item $<,>$ on $\Lambda^k V$
-    \item vol: volumn element.
-    \item $*$: Hodge Star Operator.
-\end{itemize}
-pp.4:
-\begin{itemize}
-    \item $L$: Lefschetz Operator
-    \item $\Lambda$: adjoint of $L$. $\Lambda = *^{-1}\circ L\circ *$.
-\end{itemize}
-pp.5 :
-\begin{itemize}
-    \item $*,L,\Lambda$ on Kähler mnfd.
-    \item $d^*:= (-1)^{m*(k+1)+1}*\circ d\circ*$, adjoint of $d$. On a Kähler mnfd, $d^*= -*\circ d\circ*$
-    \item $\Delta:=d^*\circ d + d\circ d^*$.
-\end{itemize}
-pp. 6:
-\begin{itemize}
-    \item $\bar{\partial}^*, \partial^*$: Similar to the above for $d$.
-    \item $\Delta_\partial, \Delta_{\bar{\partial}}$: Similar to the above for $d$.
-\end{itemize}
-
-\section{Lecture 15 Hodge Theory on Manifold (20160426)}
-pp.1:
-\begin{itemize}
-    \item $(,)$ on $\mathcal{A}^*(X)$. $(\alpha,\beta):=\int_X g_\mathbb{C}(\alpha,\beta) vol$
-\end{itemize}
-pp.3:
-\begin{itemize}
-    \item $\mathcal{H}^k(X,g)$: d-harmonic forms. Sometimes we replace $\mathcal{H}$ with $\mathscr{H}$ for harmonic forms, so is for symbols below.
-    \item $\mathcal{H}^k_{\bar{\partial}}(X,g)$: $\bar{\partial}$-harmonic forms. 
-    (Be careful to distinguish this with Dolbeault Cohomology groups).
-    \item $\mathcal{H}^k_{\partial}(X,g)$: $\partial$-harmonic forms.
-\end{itemize}
-pp. 5:
-\begin{itemize}
-    \item $\mathcal{H}^k_d(X,g) \cong \mathcal{H}^{2n-k}_d(X,g)$, Poincar\'{e} duality
-    \item $\mathcal{H}^{p,q}_{\bar{\partial}}(X,g) \cong 
-    \left( \mathcal{H}^{n-p,n-q}_{\bar{\partial}}(X,g)\right)^*$, both are harmonic forms, called Serre Duality. 
-\end{itemize}
-pp. 6,7:
-\begin{itemize}
-    \item 
-    $\mathcal{A}^{p,q} = 
-    \bar{\partial}\mathcal{A}^{p,q-1}(X)\oplus
-    \bar{\partial}^* \mathcal{A}^{p,q+1}(X) \oplus
-    \mathcal{H}^{p,q}_{\bar{\partial}}(X,g)$:
-
-     Hodge decomposition
-
-    \item $\mathcal{H}^{p,q}_{\bar{\partial}}
-        \text{(harmonic forms)}
-        \cong
-        \mathcal{H}^{p,q}_{\bar{\partial}}(X)
-        \text{(Dolbeault Cohomology group)}$
-    \item $\mathcal{H}^{p,q}_{d}
-        \text{(harmonic forms)}
-        \cong
-        \mathcal{H}^{p,q}_{dR}(X)
-        \text{(de Rham Cohomology group)}$
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item A lot of isomorphisms between \textit{de Rham}, \textit{Dolbeault} and \textit{harmonic forms}.
-\end{itemize}
-
-\section{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}
-
-pp.1:
-\begin{itemize}
-    \item $\Delta_\partial = \Delta_{\bar{\partial}} = 
-        \frac{1}{2}\Delta_d$, for K\"{a}hler mnfd.
-\end{itemize}
-
-\section{Lecture 17 Hermitian Vector Bundle (20160510)}
-pp.1,3:
-\begin{itemize}
-    \item Hermitian Vector Bundle. pp.1
-    \item Antilinear map. pp.3.
-    \item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
-    \item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
-    \item $\bar{\partial}_E^*$
-\end{itemize}
-pp. 8:
-\begin{itemize}
-    \item Kadaira-Serre Duality.
-\end{itemize}
-
-\section{Lecture 18 Connection (20160516)}
-\begin{itemize}
-    \item $\bigtriangledown$: connection. pp.1.
-    \item Trivial connections. pp.2
-    \item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
-    \item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
-    \item $\Delta = d+A$. pp.4.
-    \item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
-    \item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
-    \item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
-\end{itemize}
-
-\section{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
-\begin{itemize}
-    \item Holomorphic Connecction. pp.1.
-    \item $At(E)$: Atiyah class of $E$. pp.2.
-    \item $\Delta^k$. pp.4.
-    \item $F_\Delta$: curvature associated with $\Delta$. pp.5.
-    \item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
-    \item First Chern class of complex line bundle.
-\end{itemize}
-
-\section{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
-\begin{itemize}
-    \item Analytic Subvariety. pp.1.
-    \item Regular/Smooth Point. pp.1.
-    \item Singular Point. pp.2.
-    \item Irreducible analytic subvariety. pp.2.
-    \item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
-    \item Affine algebraic varieties. pp.3.
-    \item Projective algebraic varieties. pp.3.
-    \item Hypersurface. pp.4.
-    \item Divisor, $Div(X)$:=group of all divisors. pp.5.
-    \item Effective divisor. pp.6.
-    \item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
-    \item Meromorphic function on complex mnfd.
-    \item $(f)$: divisor given by a global meromorphic function.
-    \item Principal divisor. pp.8.
-\end{itemize}
-
-\section{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
-\begin{itemize}
-    \item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
-    \item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
-    \item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
-    \item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
-    \item Linear equivalent of divisors.
-    \item $*$: used only in this section to denoted the map:
-    $$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
-    pp.6.
-    \item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
-\end{itemize}
-
-\section{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
-\begin{itemize}
-    \item Base point of a line bundle. pp.4.
-    \item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
-    \item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
-\end{itemize}
+\include{./"part\space 1"/Notations}
 
@@
 {Theorems, Remarks, etc.}
-\chapter{Local Theory}
-\label{chap:Local Theory}
 
-\section{1.1 Holomorphic Functions of Several Variables}
-\label{sec:book_1.1}
+\include{./"part\space 2"/results}
 
-\begin{prop}
-    The local ring $\mathcal{O}_{\mathbb{C}^n,0}$ is a UFD.
-\end{prop}
-(\textbf{pp.14 of \cite{book}})
+\part{Misc}
 
-\begin{prop}{Weierstrass division theorem}
-    Let $f\in \mathcal{O}_{\mathbb{C}^n,0}$ and $g\in
-    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ be a Weierstrass
-    polynomial of degree $d$. Then there exist $r\in
-    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ of degree $<d$
-    and $h\in \mathcal{O}_{\mathbb{C}^n,0}$ such that $f=g\cdot h+r$.
-    The functions $h$ and $r$ are uniquely determined.
-\end{prop}
-(\textbf{pp.15 of \cite{book}})
-
-\begin{prop}
-    The local UFT $\mathcal{O}_{\mathbb{C}^n,0}$ is Noetherian.
-\end{prop}
-(\textbf{pp.16 of \cite{book}})
-
-\begin{coro}
-    Let $g\in \mathcal{O}_{\mathbb{C}^n,0}$ be an irreducible function.
-    If $f\in\mathcal{O}_{\mathbb{C}^n,0}$ vanishes on $Z(g)$, then
-    $g$ divides $f$.
-\end{coro}
-(\textbf{pp.16 of \cite{book}})
-
-\begin{lemma}
-    For any germ $X\subset \mathbb{C}^n$ the set $I(X)\subset
-    \mathcal{O}_{\mathbb{C}^n,0}$ is an ideal.
-    If $(A)\subset \mathcal{O}_{\mathbb{C}^n,0}$ denotes the ideal
-    generated by the subset $A\subset \mathcal{O}_{\mathbb{C}^n,0}$,
-    then $Z(A)=Z((A))$ and $Z(A)$ is analytic.
-\end{lemma}
-(\textbf{pp.18 of \cite{book}})
-
-\begin{lemma}
-    If $X_1\subset X_2$, then $I(X_2)\subset I(X_1)$. If $I_1\subset I_2$,
-    then $Z(I_2)\subset Z(I_1)4$. For any analytic germ $X$ one has
-    $Z(I(X))=X$. For any ideal $I\subset \mathcal{O}_{\mathbb{C}^n,0}$,
-    one has $I\subset I(Z(I))$.
-\end{lemma}
-(\textbf{pp.18 of \cite{book}})
-% TODO bookmark this chapter stops at page 18.
-
-\section{1.2 Complex and Hermitian Structures}
-\begin{lemma}
-    If $I$ is an almost complex structure on a real vector space $V$,
-    then $V$ admits in a natural way the structure of a complex vector
-    space
-\end{lemma}
-(\textbf{pp.25 of \cite{book}})
-
-\begin{remark}
-    An almost complex structure can only exist on an even dimensional
-    real vector space.
-\end{remark}
-
-\begin{coro}
-    Any almost complex structure on $V$ induces a natural orientation
-    on $V$.
-\end{coro}
-(\textbf{pp.25 of \cite{book}})
-
-\begin{lemma}
-    Let $V$ be a real vector space endowed with an almost complex
-    structure $I$. Then
-    $$ V_{\mathbb{C}} = V^{1,0}\oplus V^{0,1}$$
-    Complex conjugation on $V_{\mathbb{C}}$ induces an $\mathbb{R}$-linear
-    isomorphism $V^{1,0}\cong V^{0,1}$.
-\end{lemma}
-(\textbf{pp.26 of \cite{book}})
-
-\begin{remark}
-    Two almost complex structures on $V_{\mathbb{C}}$: $I$ and $i$,
-    coincide on the subspace $V^{1,0}$ but differ by a sign on
-    $V^{0,1}$.
-\end{remark}
-
-\begin{lemma}
-    Let $V$ be a real vector space endowed with an almost complex
-    structure $I$. Then the dual space 
-    $V^*=\text{Hom}_{\mathbb{R}}(V,\mathbb{R})$ has a natural almost
-    complex structure given by $I(f)(v)=f(I(v))$. The induced 
-    decomposition on 
-    $(V^*)_{\mathbb{C}}=\text{Hom}_{\mathbb{R}}(V,\mathbb{C})
-    = (V_{\mathbb{C}})^*$ is given by
-    $$ (V^*)^{1,0} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
-        f(I(v)) = i f(v) \} = (V^{1,0})^*$$
-    $$ (V^*)^{0,1} = \{f\in \text{Hom}_{\mathbb{R}}(V,\mathbb{C}) |
-        f(I(v)) = -i f(v) \} = (V^{0,1})^*$$
-    Also note that $(V^*)^{1,0} = 
-        \text{Hom}_{\mathbb{C}}((V,I),\mathbb{C})$.
-\end{lemma}
-
-\begin{prop}
-    For a real vector space $V$ endowed with an almost complex
-    structure $I$, one has:
-    \begin{enumerate}
-        \item $\bigwedge^{p,q}V$ is in a canonical way a subsapce
-            of $\bigwedge^{p+q} V_{\mathbb{C}}$.
-        \item $\bigwedge^k V_{\mathbb{C}}
-            = \bigoplus_{p+q=k}\bigwedge^{p,q}V$.
-        \item Complex conjugation on $\bigwedge^* V_{\mathbb{C}}$ defines
-            a ($\mathbb{C}$-linear) isomorphism
-            $\bigwedge^{p,q}V\cong \bigwedge^{q,p}V$, i.e.
-            $\bar{\bigwedge^{p,q}V}=\bigwedge^{q,p}V$.
-        \item The exterior prodoct is of bidegree $(0,0)$.
-    \end{enumerate}
-\end{prop}
-(\textbf{pp.27 of \cite{book}})
-\begin{remark}{Local calculation of $V^{1,0}$,$(V^*)^{1,0}$}
-    $$z_i=\frac{1}{2}(x_i-y_i)\text{, }\bar{z}_i=\frac{1}{2}(x_i+iy_i)$$
-    $$z^i=x^i+iy^i\text{, }\bar{z}^i=x^i-iy^i$$
-    $$I(z_i)=i z_i\text{, }I(z^i)=i z^i$$
-\end{remark}
-(\textbf{pp.27 to 28 of \cite{book}})
-
-\begin{lemma}
-    For any $m\leq \text{dim}_{\mathbb{C}}V^{1,0}$, one has
-    $$(-2i)^m (z_1\wedge\bar{z}_1)\wedge\cdots\wedge(z_m\wedge\bar{z}_m)=
-        (x_1\wedge y_1)\wedge\cdots\wedge(x_m\wedge y_m).$$
-    For $m=\text{dim}_\mathbb{C} V^{1,0}$, this defines a positive
-    oriented volume form for the natural orientation of $V$.
-
-    Also
-    $$\left(\frac{i}{2}\right)^m
-      (z^1\wedge\bar{z}^1)\wedge\cdots\wedge(z^m\wedge\bar{z}^m)=
-      (x^1\wedge y^1)\wedge\cdots\wedge(x^m\wedge y^m).$$
-\end{lemma}
+\chapter{Anchor}
+\label{sec:Anchor}
 
@@
 \end{thebibliography}
-\part{License}
+
+\chapter{License}
+\label{sec:License}
+
 The entire content of this work (including the source code

### 2016-10-25 Complex Geometry - index/part 1/Notations.tex
1.New physics GRE prep. 2. Learn to organize tex into small subfiles.

--- 2016-07-06 Complex Geometry - index of notations by taper.tex
@@
-\documentclass{article}
-
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{thm}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols
-
-\title{Complex Geometry - Index of Notations and ideas}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\tableofcontents
-
-\begin{abstract}
-Obviously.
-
-\end{abstract}
-
-\section{Book}
-	\subsection{1. Local Theory}
-		\subsubsection{1.1 Holomorphic Functions of Several Variables}
+\chapter{Book}
+\section{1. Local Theory}
+    \subsection{1.1 Holomorphic Functions of Several Variables}
     \label{sec:1.1_book}
@@
 
-		\textcolor{blue}{1}: 
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}: 
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
-		\textcolor{blue}{1}:
+    \textcolor{blue}{germ of set}: (\textbf{pp.18})
 
-	\subsection{2.Complex Manifolds}
+    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})
 
-		\subsubsection{2.2 Holomorphic Vector Bundles}
+    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})
+
+    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})
+
+    \textcolor{blue}{$I(X)$}: the set of all $f\in
+    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
+    % TODO bookmark
+    \subsection{1.2 Complex and Hermitian Structures}
+    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
+    (\textbf{pp.25})
+
+    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
+    of $I$.
+    (\textbf{pp.25})
+
+    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
+    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
+    (\textbf{pp.27})
+
+    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{compatible}:an almost complex structure $I$ is
+    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
+    (\textbf{pp.28})
+
+    \textcolor{blue}{Conformal equivalence}(between scalar product):
+    (\textbf{pp.29})
+
+    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
+    (\textbf{pp.29})
+    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
+    \quad(Local calculation could be found on \textbf{pp.31})
+
+    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
+    (\textbf{pp.30})
+
+    \textcolor{blue}{Lefschetz operator $L$}:
+        $\bigwedge^* V^*_{\mathbb{C}}\to
+    \wedge^* V_{\mathbb{C}}^*$, given by $\alpha\to\omega\wedge\alpha$.
+    (\textbf{pp.31})
+
+    \textcolor{blue}{Hodge star $*$-operator}: $\alpha\wedge *\beta=
+        \langle\alpha,\beta\rangle \cdot \text{vol}$.
+    (\textbf{pp.33})
+
+    \textcolor{blue}{dual Lefschetz operator $\Lambda$}:
+        $\langle\Lambda\alpha,\beta\rangle =\langle\alpha,L\beta\rangle$,
+        degree $-2$, bidegree $(-1,-1)$, $\Lambda=*^{-1}\circ L\circ *$.
+    (\textbf{pp.33 to 34})
+
+    \textcolor{blue}{Counting operator $H$}:
+        $H=\sum_{k=0}^{2n}(k-n)\cdot\prod^k$, 
+        where $\text{dim}_{\mathbb{R}}=2n$.
+    (\textbf{pp.34})
+
+    \textcolor{blue}{commutator [A,B]}:$=A\circ B-B\circ A$.
+    (\textbf{pp.34})
+
+\paragraph{Commutators}
+$$[H,L]=2L,\text{ } [H,\Lambda]=-2\Lambda,\text{ } [L,\Lambda]=H.$$
+(\textbf{pp.34})
+
+$$[L^i,\Lambda](\alpha)= i(k-n+i-1)L^{i-1}(\alpha),\text{for all}
+    \alpha\in\bigwedge^k V^*$$
+(\textbf{pp.35})
+
+    \textcolor{blue}{primitive element} in $\bigwedge^kV^*$:
+        $\alpha$ is primitive if and only if $\Lambda\alpha=0$.
+    (\textbf{pp.36})
+
+    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
+    of all primitive elements.
+    (\textbf{pp.36})
+
+    \textcolor{blue}{Hodge-Riemann pairing $Q$}:
+    $$\bigwedge^kV^*\times\bigwedge^kV^*\to \mathbb{R}\text{, }
+     (\alpha,\beta)\mapsto (-1)^{k(k-1)}{2}\alpha\wedge\beta\wedge w^{n-k}$$
+
+    Note: here we identify $\bigwedge^{2n}V^*$ with $\mathbb{R}$ 
+    by the volumn form $\text{vol}$. Also the $\mathbb{C}$-linear 
+    extension of this is still denoted $Q$.
+
+\section{2.Complex Manifolds}
+
+    \subsection{2.1 Complex and Hermitian Structures}
+    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
+	\subsection{2.2 Holomorphic Vector Bundles}
 
@@
 \end{itemize}
-		\subsubsection{Notes of Čech Cohomology with Coeficients in a Sheaf}
+
+    \subsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
     pp.1:
@@
 \end{itemize}
-
-\begin{thebibliography}{1}
-
-	\bibitem{blog} Complex Geometry
-
-\end{thebibliography}
-\end{document}

### 2016-10-25 GRE Physics Prep/General Physics Formula.tex
1.New physics GRE prep. 2. Learn to organize tex into small subfiles.

@@
 \end{align}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/{wave-and-reflection}.PNG}
+    \caption{wave and Reflection}
+\end{figure}
+$(a)$ A pulse incident from the right is reflected at the left end of
+the string, which is tied to a wall. Note that the reflected pulse is
+inverted from the incident pulse. $(b)$ Here the left end of the string
+is tied to a ring that can slide without friction up and down the rod.
+Now the pulse is not inverted by the reflection
+
 \textbf{String}
@@
 
+\paragraph{Lorentz Force Law}
+\begin{equation}
+    \vb{F} = q\left(\vb{E} +\vb{v}\cross\vb{B}\right)
+\end{equation}
 \paragraph{Electric field} (\textbf{pp.596 ch22 of \cite{book}})
@@
 
-\paragraph{Magnetic -> Electricity} (\textbf{pp.781 ch29 of
+\paragraph{Magnetic $\to$ Electricity} (\textbf{pp.781 ch29 of
 \cite{book}})

### 2016-10-26 Draft/draft.tex
Updates physics GRE prepare notes.

@@
 \label{sec:Quantum_Field_Theory}
-    \subsection{Relatvistic Quantum Mechanics}
-    \label{sec:Relatvistic_Quantum_Mechanics}
+\input{./sections/QFT-by-Weinberg}
 
-    \subsubsection{2.1 Quantum Mechanics}
-    \label{sec:2.1_Quantum_Mechanics}
-    This part sumarize the axioms of quantum mechanics. (Omitted)
-    However, one class of important but seldom mentioned operator,
-    the antilinear operators and the antiunitary operators are not
-    discussed here but postponed to the next part.
+\section{Miscellaneous Math}
+\label{sec:Miscellnaneous_Math}
+\input{./sections/misc-math}
 
-    \subsubsection{2.2 Symmetries}
-    \label{sec:2.2_Symmetries}
-    This part discribe some important theorems concerning the symmetries
-    in quantum mechanics.
+\section{Miscellaneous Physics}
+\label{sec:Miscellnaneous_Physics}
+\input{./sections/misc-physics}
 
-    Firstly, symmetries in quantum mechanics some times requires the use
-    of antilinear and antiunitary operators.
+\section{Miscellaneous Other}
+\label{sec:Miscellaneous_Other}
+\input{./sections/misc-other}
 
-    \paragraph{Antilinear and Antiunitary}
-    Antilinear operators: $U (\lambda A + \upsilon B)
-                            = \lambda^* UA + \upsilon^* UB$.
-
-    Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$
-
-    The adjoint operator of an antilinear operator requires special
-    attention:
-    $$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
-    (The usual definition will become troublesome since the LHS will
-    be antilinear in $\phi$, whereas the RHS is linear.)
-
-    Thankfully, the criterion for unitarity or antiunitarity is the same:
-    $$U^\dagger = U^{-1}$$
-
-    An important example is those symmetries which can be infinitesimally
-    close to identity. In the vincinity of unity, it is:
-    $$ U =1+i\epsilon t $$
-    where $t$ is Hermitian and linear.
-    % TODO why is it Hermitian?
-
-    \paragraph{Symmetry Group and its Representation} The set of all
-    symmetries transformations obviously can have a group structure.
-    By giving each symmetry transformation a unitary or antiunitary
-    operator, a representation of such group is obtained. However,
-    such a representation can be projective (projective as in
-    projective geometry, or $\mathbb{CP}^n$), since operators acts
-    on ket spaces, which is already projective (i.e. within a freedom of
-    phase).
-
-    If the phase is taken into consideration, it is found that this
-    phase is independent of the ket that the operator acts on:
-    \begin{align}
-        \label{eq:2.2_symmetries_projective_phase}
-        U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
-    \end{align}
-    Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
-    transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
-    on $T_1 T_2$.
-
-    Howver, there is one exception to this rule. It exists when the
-    state $\Psi$ is not the linear some of some other wave functions.
-    That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
-    This seems incomprehesible to me.
-    % TODO Understand this!
-    There are some link on page 53
-    between the structure of Lie group associated
-    with this symmetry and whether the representation can be projective.
-    \footnote{Though not state, it can be infered that a representation
-    can be made not-projective by a good choice of $U(T)$, so that
-    $\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }
-
-    \paragraph{Connected Lie group} is of special importance in physics.
-    However, the books description obfuscate the mathematical description
-    of this structure. I will update this note later to remedy such
-    % TODO update this part.
-    discussion. The message I understand is that the representation is
-    tightly bound to the Lie algebra. An important example is that when
-    $$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
-    $$ [t_b,t_c] = 0$$
-    then
-    $$ U(T(\theta)) = \exp(it_a \theta^a) $$
-
-    \subsubsection{2.3 Quantum Lorentz Transformations}
-    \label{sec:2.3_Quantum_Lorentz_Transformations}
-    \textbf{Note}: although the title suggests "quantum", this part is
-    mostly classical.
-
-    Starting with the invariance of interval:
-    \begin{align}
-        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
-        \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
-    \end{align}
-    or equivalently % TODO why equivalently?
-    \begin{align}
-        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
-        \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
-            \frac{\partial x'^\nu}{\partial x^\sigma}
-            =
-        \eta_{\rho\sigma}
-    \end{align}
-    It claims that any coordinate transformation satisfying 
-    \ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
-    must be linear.
-
-    Such linear Lorentz transformations satisfy:
-    \begin{align}
-        T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
-            T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
-    \end{align}
-    where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
-    transformations.
-
-    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
-    equations that relate it with $\eta_{\mu\nu}$.
-
-    Note that:
-    \[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
-    And:
-    \begin{equation}
-        \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
-        (\Lambda^{-1})\indices{^\rho_\nu} = 
-            \Lambda\indices{_\nu^\rho} = 
-            \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
-    \end{equation}
-
-    The only part about quantum mechanics here, is that the operators
-    corresponding to the Lorentz transformations, have the property that:
-    \begin{equation}
-        U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
-            U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
-    \end{equation}
-    where $a$ represents the translation.
-
-    The group of Lorentz transformations is very important. There is:
-        %\text{sssssss} & B
-    \[
-        \xymatrix{ 
-        \text{Poincar\'e Group}  \\
-        \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
-        \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
-        }
-    \]
-    The important \textit{proper orthochronous Lorentz group} consists
-    of those $\Lambda$ with $\det \Lambda = 1$ and 
-    $\Lambda\indices{^0_0} \geq 1$.
-
-    We have also $ \mathscr{P}$, the space inversion matrix. And
-    \(\mathscr{T}\), the time-reversal matrix. The definition for
-    both can be easily written.
-
-    A important rule is that all homogeneous Lorentz transformations can
-    are generated by 
-    \(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
-    However this property is not proved
-
-    \paragraph{Digression about tensor notation} It seems that phsysicists
-    have not settled down on their notation for tensors. Weinberg using
-    the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
-    so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
-    tangent vector. I see that this notation helps to distinguish the
-    type of arguments. This is unnecessary, since the upper and lower
-    indices already fulfill this function. Another benefit is that it
-    conveies the process of lowering of raising a index.
-
-    However, this idea that each slot in tensor indices are distinct
-    and can be lowered and raised seperatly, is not even mentioned
-    in some modern mathematical physics book.
-
-    Helpful link:
-    \href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
-    \href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.
-
-    \subsubsection{2.4 The Poincar\'{e} Algebra}
-    \label{sec:2.4_The_Poincare_Algebra}
-    \textbf{I am lost in this part.} The general idea seems to develop, in a 
-    infinitesimal sense, the property of a Lorentz transformation.
-    For a infinitesimal Lorentz transformation:
-    \begin{align}
-        U(1+\omega, \epsilon) = 
-            1+ \frac{1}{2} i\omega_{\rho\sigma}J^{\rho\sigma}
-            -i\epsilon_\rho P^\rho + \cdots
-    \end{align}
-    where $J$ and $P$ are independent of the infinitesimal value
-    $\omega$ and $\epsilon$.
-
-    Later $P$ is identified as the energy-momentum operator (with
-    $P^0$ being the energy operator), and $J^{23}$, $J^{31}$,
-    \(J^{12}\) are identified with the angular momentum operator.
-    However, the reason for this identification is not provided. 
-    % TODO why P is energy momentum, and J is angular momentum
-
-    Later, it was eatablished that $J$ and $P$ satisfy:
-    \begin{align}
-        i[J^{\mu\nu},J^{\rho\sigma}] &=
-            \eta^{\nu\rho}J^{\mu\sigma} - \eta^{\mu\rho}J^{\nu\sigma}
-            -\eta^{\sigma\mu}J^{\rho\nu} + \eta^{\sigma\nu}J^{\rho\mu}
-        \\
-        i[P^\mu,J^{\rho\sigma} &=
-            \eta^{\mu\rho}P^\sigma - \eta^{\mu\sigma}P^{\rho}
-        \\
-        [P^\mu,P^\rho] &= 0
-    \end{align}
-    This is called the \textit{Lie Algebra} of the Poincar\'{e}
-    group.
-    The relation \([P^\mu,P^\rho] = 0\) is particular interesting.
-
-    With this, the finite translation and a rotation by angle
-    $\theta$ are expressed as:
-    \begin{align}
-        U(1,a) = \exp(-iP^\mu a_\mu) \\
-        U(\theta,0) = \exp(i \mathbf{J}\cdot \theta)
-    \end{align}
-
-    This part ends with a discussion on the low-velocity limit
-    of the Lie Algebra obtained above, i.e. the Galilean algebra.
-
-    \subsection{Note}
-    \label{sec:Note}
-    I will now change to another book: Q.F.T. in a Nutshell by A. Zee.
-
-\section{Miscellnaneous Math}
-\label{sec:Miscellnaneous_Math}
-\subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
-From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. 
-By \href{http://math.stackexchange.com/users/1102/aryabhata}{Aryabhata}.
-
-I believe this can also be solved using double integrals.
-
-It is possible (if I remember correctly) to justify switching the order of integration to give the equality:
-
-$$\int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dy \Bigg)\, dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
-Notice that
-$$\int_{0}^{\infty} e^{-xy} \sin x\,dy = \frac{\sin x}{x}$$
-
-This leads us to
-
-$$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
-Now the right hand side can be found easily, using integration by parts.
-
-\begin{align*}
-I &= \int e^{-xy} \sin x \,dx = -e^{-xy}{\cos x} - y \int e^{-xy} \cos x \, dx\\
-&= -e^{-xy}{\cos x} - y \Big(e^{-xy}\sin x + y \int e^{-xy} \sin x \,dx \Big)\\
-&= \frac{-ye^{-xy}\sin x - e^{-xy}\cos x}{1+y^2}.
-\end{align*}
-Thus $$\int_{0}^{\infty} e^{-xy} \sin x \,dx = \frac{1}{1+y^2}$$
-Thus $$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty}\frac{1}{1+y^2}\,dy = \frac{\pi}{2}.$$
-
-\section{Miscellnaneous Notes}
-    \subsection{Super conductor}
-    Mean-field approach to deal with a four operator diagonalization.
-
-    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
-    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:
-
-    	$$ \delta^2 \approx 0 $$
-    i.e.:
-
-    \begin{align}
-    	( (CD)^* - avg ) ( CD - avg ) = 0\\
-    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
-    \end{align}
-    Hence a four operator is reduced into a few of two operators.
-    Such method could be naturally extended to treat the operator
-    $\sum_{i,j} D^*_i C^*_i C_j D_j$.
-
-    A copper pair has the energy of:
-    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$
-
-    To resist the flow of current carried by Copper Pair, is equivalent to destroying a pair of Copper Pair:
-    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
-
-    This will require an additional enegy of $2\Delta$.
-
-    The exact meaning of "equivalent to" is as follows:
-    \begin{align}
-        & \text{break a copper pair} \longrightarrow 
-        \text{scatter two electrons consecutively} 
-        \nonumber\\ & \longrightarrow 
-        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
-    \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
-
-    \subsection{Preface of BSCS}
-        \label{sec:Preface_of_Bosonization_and_Strongly 
-        Correlated_Systems}
-    BSCS: see \cite{BSCS}.
-    Parallism between theories in condensed matter physics and those in
-    particle physics.
-    \begin{itemize}
-            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
-                    (C.M.P.)
-            \item 'inflation' in Cosmology, first order phase transition
-            \item 'cosmic strings', magnetic field vortex lines in type
-                    II superconductors
-            \item Hadron-meson interaction, Ginzburg-Landau theory of
-                    superfluid $He^3$.
-    \end{itemize}
-    Same ideas on different space-time scales, different hierachical
-    'layers'.
-    Strong parallism: \textbf{strongly correlated low dimensional system}
-
-    E.g.:
-
-    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.
-
-    Approaches:
-    \begin{enumerate}
-            \item Exact solutions
-            \item Reformulate complicated interacting models in such a way
-                    that they become weekly interacting. -> Bosonization.
-
-                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
-                    Model of interacting
-
-                    fermions.
-                    (Jordan and Wigner, 1928)
-    \end{enumerate}
-    Bosonization: transformation from fermions to a scalar massless bosonic
-    field.
-
-    \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
-
-    pp. 266.
-
-    \begin{defi}
-        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
-        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
-        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
-    \end{defi}
-
-    pp. 291.
-
-    \begin{thm}[Existence-uniqueness theorem]
-        There exists one, and only one, solution of the initial-value
-        problem
-
-        \begin{align}
-            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
-                \mathbf{x}(t_0) = \mathbf{x}^0 = 
-                \left(
-                \begin{array}{c}
-		            x^0_1\\
-                    x^0_2\\
-                    \cdots
-                \end{array} 
-                    \right)
-        \end{align}
-
-        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
-    \end{thm}
-    \begin{remark}
-        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
-        time $t$. Also notice that the elements of $\mathbf{A}$ are just
-        numbers.
-    \end{remark}
-
-    \begin{thm}
-        The dimension of the space $\mathbf{V}$ of all solutions of the
-        homogeneous linear system of differential equations:
-        \begin{align}
-            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
-        \end{align}
-        is $n$, i.e. the dimension of vector $\mathbf{x}$.
-    \end{thm} 
-    \subsection{ODE by Arnold}
-    sec. 14
-    \begin{defi}
-        \begin{align}
-            \label{eq:e^A}
-            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
-            \text{or}& \nonumber \\
-            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
-        \end{align}
-        where $I$ is the identity matrix.
-    \end{defi}
-    Equivalance of the two definition will be addressed in the Theorem on
-    pp. 165.
-
-    Important theorems:
-    \begin{thm}[pp. 158]
-        The series $e^A$ converges for any $A$ uniformly on each set
-        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
-    \end{thm}
-    \begin{thm}[pp. 160]
-        $$e^{At} = H^t$$
-        where $H^t$ is the translation operator which sends every polynomial
-        $p(x)$ into $p(x+t)$.
-    \end{thm}
-    \begin{thm}[pp. 163]
-        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
-    \end{thm}
-    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
-        Constant Coefficients]
-        The solution of:
-        \begin{align}
-            \label{eq:fund_thm_of_linear_eqs_const_coef}
-            \dot{\mathbf{x}} = A\mathbf{x}
-        \end{align}
-        with initial condition $\phi(0) = \mathbf{x}_0$ is
-        \begin{align}
-            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
-        \end{align}
-    \end{thm}
-
-    Practically solution to
-    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
-    (pp. 173, Sec 17)
-    (Assuming $A$ is diagonalizable.)
-    \begin{itemize}
-        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
-            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
-        \item Expand the initial condition in the new basis.
-            \begin{align}
-                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
-            \end{align}
-        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
-    \end{itemize}
-    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
-
-    \begin{align}
-        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
-            (\eta_b,U_{ac}\dot{\psi}_c
-    \end{align}
-    \subsection{Quantum Statistical Mechanics}
-    \label{sec:Quantum Statistical Mechanics}
-    \begin{defi}[Time Evolution Operator]
-        The time evolution operator $U(t,t_0)$ is defined such that
-        \begin{align}
-            \label{eq:def_time_evo_op}
-            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
-        \end{align}
-    \end{defi}
-    It satisfy the relationship:
-    \begin{align}
-        \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= H U(t,t_0)
-    \end{align}
-    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
-    Equations.
-
-    \paragraph{Quantum Macrostates}
-    Macrostates of the system depend on only a few the thermodynamic
-    functions. We can form an ensemble of a large number $\mathcal{N}$ of
-    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
-    The different microstates occur with probability $p_\alpha$.
-    When wen no longer have exact knowledge of the microstate of a
-    system the system is said to be in a \textit{mixed state}.
-    The ensemble average of the quantum mechanical expectation
-    value is given by:
-    \begin{align}
-        \label{eq:quantum_macrostates_ensemble_avg}
-        \bar{\braket{O}} &= 
-            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
-            = \sum_{\alpha,m,n} p_\alpha
-                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
-                \nonumber\\
-            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
-                = \text{tr}(\rho O)
-    \end{align}
-    where we have introduced the density matrix:
-    \begin{defi}[Density Matrix]
-        The density matrix $\rho(t)$ is defined as
-        \begin{align}
-            \label{eq:density_matrix_def}
-        \braket{n|\rho(t)|m} \equiv
-        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
-        \end{align}
-        or
-        \begin{align}
-            \label{eq:density_matrix_def_2}
-            \rho(t) \equiv \sum_\alpha p_\alpha
-                \ket{\psi_\alpha}\bra{\psi_\alpha}
-        \end{align}
-    \end{defi}
-    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
-    P.D.F, since $\rho$ often represents density.
-
-    Density matrix satisfies several good properties:
-    \begin{itemize}
-        \item Normalized
-        \item Hermiticity
-        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
-    \end{itemize}
-    The time evolution of density matrix, directly obtained from Schrodinger's
-    equation, is
-    \begin{align}
-        \label{eq:quantum_macrostates:density_matrix:evolution}
-        i\hbar \frac{\partial}{\partial t}\rho = [H,\rho]
-    \end{align}
-
-    \subsection{The Mathematical Theory of Communication}
-    \label{sec:The_Mathematical_Theory_of_Communication}
-    \subsubsection{Introduction}
-
-    \paragraph{What is information}
-    In this part, it is implied that \textit{information} in this work
-    does not carry the usual sense in people's daily life. The semantic
-    aspect of a message is considered to be irrelavant, for purpose
-    of generality of the design of communication systems.
-
-    \paragraph{Measure of information} 
-    % TODO Read the paper of Hartley to understand what is information:
-    % Hartley, R. V. L., "Transmission of Information," Bell System Technical
-    % Journal, July 1928, p. 535
-
-    Then it refers to a paper by Hartley to substantiate the use of
-    \begin{align}
-        \label{eq:measure_of_information}
-        S = \log(M)
-    \end{align}
-    as a measure of information. More specifically, we assume we have a
-    set of possible messages. Then $M$ is the cardinality of this set.
-    Then $S$ is a measure of the information produced when one message
-    is chosen from the set. Once again, we regard all choices 
-    being equally possible.
-
-    Note that the base of logrithm in \ref{eq:measure_of_information}
-    is undefined. Choosing a base constituting choosing a unit of
-    the measure. Two such measures, when calculated in different units,
-    are related by a simple constant.
-
-    Conventionally, a base $2$ is chosen. The resulted unit is called
-    bits. If the base $10$ is chosen, then the units may be called
-    decimal digits. If the base $e$ is chosen, then the units is
-    called natural units.
-
-    Also, the author lists several points to illustrate the
-    convenience of this measure.
-
-    \paragraph{Communication systems}
-    Next the author defines the necessary components of a \textit{
-    communication system}, and categorizes it into discrete systems,
-    continuous systems and mixed systems.
-
-    \subsubsection{Discrete Noiseless Systems}
-
-    \paragraph{Discrete Noiseless Channel}
-    \label{sec:Discrete Noiseless Channel}
-    This part deals with another measure, the measure of the capacity
-    of a channel to transmit information. It defines the capacity of a
-    discrete channel as:
-    \begin{align}
-        \label{eq:capacity_of_disc_chan}
-        C\equiv \lim_{T\to \infty} \frac{\log N(T)}{T}
-    \end{align}
-    where $N(T)$ is the number of allowed signals of duration $T$.
-    Several examples are given with formula for $C$ in each particular
-    example.
-
-    \paragraph{Discrete Source of Information}
-    Next, it proceeds to discuss the statistical property of the source
-    of information. Pointing out that a statistical knowledge of the
-    source of information can help peopole craft special protocals to
-    reduce the required capacity of the channel, the article gradually
-    focuses on the statistical property of sourcs. It profess that while a
-    discrete source could be represented by a statistical source, a
-    statistical process can also be considered a discrete source. The
-    second claim is substatiated by several exmaples.
-
-    In one example of natural language, the article defines a 
-    \textit{n-gram} case to produce natural language from statistical
-    information.
-
-    \paragraph{Series of Approximations to English}
-    As the title suggests, this part illustrate two serial levels of
-    steps to approximate the English language using statistical knowledge
-    of appearance of alphabets (the first method) and words (the second
-    example). The article claims that "a sufficiently complex stochastic 
-    process will give a satisfactory representation of a discrete source".
-    Although I am largely against this juvenile view.
-
-    \paragraph{Graphical Representation of a Markoff Process}
-    Then the article mentions a graphical way to represent the aforementioned
-    approximation process, and gives three examples on page 46.
-
-    \paragraph{Ergodic and Mixed Sources}
-    Now the article comes to a special type of stochastic process, ergodic
-    processes. A rough idea of "ergodic" is given in page 45. The idea is
-    so important that I felt compeled to present it here:
-
-    "In an ergodic process every sequence produced by
-    the process is the same in statistical properties. Thus the letter
-    frequencies, digram frequencies, etc., obtained from particular
-    sequences, will, as the lengths of the sequences increase, approach
-    definite limits independent of the particular sequence.
-    Actually
-    this is not true of every sequence but the set for which it is false
-    has probability zero. Roughly the ergodic property means 
-    \textbf{statistical homogeneity}."
-
-    Next, the article claims that artificial languages given in previous
-    examples are ergodic, because the corresponding graph does not
-    have two properties: they does not comprise two or more \textit{isolated
-    parts}, and they $gcd$ of the lengths of all \textit{circuits }is one.
-    The precise meaning is listed in page 47. Roughly, an analogy made by
-    myself helps to
-    catch the points. If we picture an stochastic process as a connected 
-    area, then isolated parts are its connected components, whereas the
-    circuit are the recurrent pattterns.
-
-    Naturally , a stochastic process may exhibit a mixed behavir, in which
-    there are several different sources $L_1,L_2,L_3,\cdots$, which are
-    each of homogeneous, i.e. ergodic, statistical structure. This is
-    discussed following the introduction of ergodicity in page 48.
-
-    Then the article declare that except in special cases, ergodicity is
-    always assumed. This purpose is analogous to that of in statistical
-    physics, to "identify averages along a sequence with averages over 
-    the ensemble of possible sequences", with "the probability of a
-    discrepancy being zero".
-
-    Lastly, the article mentions a fact regarding the equilibrium of
-    the system. A process is called stationary, if it satisfies a
-    equilibrium condition:
-    \begin{align}
-        \label{eq:Ergodic_and_Mixed_States:equil_condition}
-        P_j = \sum_i P_i \cdot P_i(j)
-    \end{align}
-    where $P_j$ is the probability of being in state $j$, and $P_i(j)$ is
-    the transition probability from $i$ to $j$.
-    The fact is that ergodic process is, in a sense, always stationary.
-
-    \paragraph{The Entropy of an Information Source}
-    This part first defines the entropy of a discrete source of finite state
-    to be:
-    \begin{align}
-        \label{eq:entropy_of_discrete_infor_source}
-        H \equiv& \sum_i P_i H_i\\
-        =& -\sum_{i,j} P_i p_i(j) \log(p_i(j)) \nonumber
-    \end{align}
-    It is "the entropy of the source per symbol of text". Another
-    definition for entropy per second is also listed.
-
-    Following this definition are some theorems, which I consider to be
-    the most essential and influential part of the whole book (although
-    I have not yet read the whole book). They are:
-
-    \begin{thm}[Theorem 3 on page 55]
-        Given any $\epsilon >0$ and $\delta >0$, we can find an $N_0$
-        such that the sequences of any legnth $N\geq N_0$ fall into
-        two class:
-        \begin{itemize}
-            \item A set whose total probability is less than $\epsilon$.
-            \item The remainder, all of whose members have probabilities
-                satisfying the inequality
-                \begin{align}
-                    \label{eq:Entropy_of_info_source:thm3}
-                    \left| \frac{\log p^{-1}}{N}-H\right| < \delta
-                \end{align}
-        \end{itemize}
-    \end{thm}
-    "In other words we are almost certain to have 
-    $\frac{\log p^{-1}}{N}$ very close to $H$ when $N$ is large."
-    For me, this reads quite like the \textit{second law of
-    thermaldynamics}.
-
-    % TODO having trouble understanding the Theorem 4 on page 55.
-
-    \subsection{Bayes' theorem}
-    \label{sec:Bayes-theorem}
-    I am quite unfamiliar with this formula, so I decided to make a note
-    here for future reference.
-
-    This formula starts from the definition of conditional probability:
-    \begin{align}
-        P(A|B)\equiv \frac{P(A\&B)}{P(B)}
-    \end{align}
-    this definition if quite intuitively pleasing if $P(B)$ is multiplied
-    to the left side. Then one easily deduce that:
-    \begin{thm}[Bayes' theorem] \begin{align}
-        P(A|B)=\frac{P(B|A)P(A)}{P(B)}
-    \end{align} \end{thm}
-
-    We have also an extended form. Suppose the event space is partitioned
-    into $\{A_i\}$, then we have (also easily proved):
-    \begin{align}
-        P(A_i|B)=\frac{P(B|A_i)P(A_i)}{\sum_j P(B|A_j)P(A_j)}
-    \end{align}
-    Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
-    \subsection{About Matlab}
-    \label{sec:About-Matlab}
-    \paragraph{On using $A/B$ or $A\\B$}
-    Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
-    , abbrevated $A/B$ and $A\\B$, are different and should be used with
-    caution. One can check that:
-    \begin{center}
-        $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
-        equivalent to $D\backslash A$.
-    \end{center}
-    Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.
 \section{Anchor}
@@
     \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
+    \bibitem{griffiths-EM} Introduction to Electrodynamics, 3rd,
+    Griffiths
 \end{thebibliography}

### 2016-10-26 Draft/sections/QFT-by-Weinberg.tex
Updates physics GRE prepare notes.

--- 2016-07-08 draft.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\subsection{Relativistic Quantum Mechanics}
+\label{sec:Relatvistic_Quantum_Mechanics}
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage{hyperref} % For hyperlink everything.
-\usepackage{CJKutf8} % For Chinese characters
-%\usepackage{ dsfont } % For double struck fonts
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
+\subsubsection{2.1 Quantum Mechanics}
+\label{sec:2.1_Quantum_Mechanics}
+This part sumarize the axioms of quantum mechanics. (Omitted)
+However, one class of important but seldom mentioned operator,
+the antilinear operators and the antiunitary operators are not
+discussed here but postponed to the next part.
 
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
+\subsubsection{2.2 Symmetries}
+\label{sec:2.2_Symmetries}
+This part discribe some important theorems concerning the symmetries
+in quantum mechanics.
 
-\title{Draft}
-\date{\today}
-\author{we.taper}
-\begin{document}
-\maketitle
-\abstract{
-    This is a draft.
+Firstly, symmetries in quantum mechanics some times requires the use
+of antilinear and antiunitary operators.
+
+\paragraph{Antilinear and Antiunitary}
+Antilinear operators: $U (\lambda A + \upsilon B)
+                        = \lambda^* UA + \upsilon^* UB$.
+
+Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$
+
+The adjoint operator of an antilinear operator requires special
+attention:
+$$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
+(The usual definition will become troublesome since the LHS will
+be antilinear in $\phi$, whereas the RHS is linear.)
+
+Thankfully, the criterion for unitarity or antiunitarity is the same:
+$$U^\dagger = U^{-1}$$
+
+An important example is those symmetries which can be infinitesimally
+close to identity. In the vincinity of unity, it is:
+$$ U =1+i\epsilon t $$
+where $t$ is Hermitian and linear.
+% TODO why is it Hermitian?
+
+\paragraph{Symmetry Group and its Representation} The set of all
+symmetries transformations obviously can have a group structure.
+By giving each symmetry transformation a unitary or antiunitary
+operator, a representation of such group is obtained. However,
+such a representation can be projective (projective as in
+projective geometry, or $\mathbb{CP}^n$), since operators acts
+on ket spaces, which is already projective (i.e. within a freedom of
+phase).
+
+If the phase is taken into consideration, it is found that this
+phase is independent of the ket that the operator acts on:
+\begin{align}
+    \label{eq:2.2_symmetries_projective_phase}
+    U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
+\end{align}
+Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
+transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
+on $T_1 T_2$.
+
+Howver, there is one exception to this rule. It exists when the
+state $\Psi$ is not the linear some of some other wave functions.
+That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
+This seems incomprehesible to me.
+% TODO Understand this!
+There are some link on page 53
+between the structure of Lie group associated
+with this symmetry and whether the representation can be projective.
+\footnote{Though not state, it can be infered that a representation
+can be made not-projective by a good choice of $U(T)$, so that
+$\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }
+
+\paragraph{Connected Lie group} is of special importance in physics.
+However, the books description obfuscate the mathematical description
+of this structure. I will update this note later to remedy such
+% TODO update this part.
+discussion. The message I understand is that the representation is
+tightly bound to the Lie algebra. An important example is that when
+$$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
+$$ [t_b,t_c] = 0$$
+then
+$$ U(T(\theta)) = \exp(it_a \theta^a) $$
+
+\subsubsection{2.3 Quantum Lorentz Transformations}
+\label{sec:2.3_Quantum_Lorentz_Transformations}
+\textbf{Note}: although the title suggests "quantum", this part is
+mostly classical.
+
+Starting with the invariance of interval:
+\begin{align}
+    \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
+    \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
+\end{align}
+or equivalently % TODO why equivalently?
+\begin{align}
+    \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+    \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
+        \frac{\partial x'^\nu}{\partial x^\sigma}
+        =
+    \eta_{\rho\sigma}
+\end{align}
+It claims that any coordinate transformation satisfying 
+\ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
+must be linear.
+
+Such linear Lorentz transformations satisfy:
+\begin{align}
+    T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
+        T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
+\end{align}
+where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
+transformations.
+
+The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
+equations that relate it with $\eta_{\mu\nu}$.
+
+Note that:
+\[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
+And:
+\begin{equation}
+    \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
+    (\Lambda^{-1})\indices{^\rho_\nu} = 
+        \Lambda\indices{_\nu^\rho} = 
+        \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
+\end{equation}
+
+The only part about quantum mechanics here, is that the operators
+corresponding to the Lorentz transformations, have the property that:
+\begin{equation}
+    U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
+        U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
+\end{equation}
+where $a$ represents the translation.
+
+The group of Lorentz transformations is very important. There is:
+    %\text{sssssss} & B
+\[
+    \xymatrix{ 
+    \text{Poincar\'e Group}  \\
+    \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
+    \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
     }
-\tableofcontents
+\]
+The important \textit{proper orthochronous Lorentz group} consists
+of those $\Lambda$ with $\det \Lambda = 1$ and 
+$\Lambda\indices{^0_0} \geq 1$.
 
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
-    \textbf{Thermal electrics}
+We have also $ \mathscr{P}$, the space inversion matrix. And
+\(\mathscr{T}\), the time-reversal matrix. The definition for
+both can be easily written.
 
-    \subsection{By Lang. Chen}
-    \label{sec:c.l}
-    Grow thin films.
-    \begin{itemize}
-	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
-	\item 
-	orbital contral of electrons -> 
-	orbitronics -> Control of Spin orbital coupling.
-	\item
-	Multiferroics -> multiple order parameters, and the interaction
-	between them. E.g. $BiFeO_3$.
-	\item
-	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
-	symmetries simultaneous broken.
-	\item
-	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
-	exactly in theoretical physics?
-	\item
-	$H_2S$: 200K superconductor?
-	\item
-	The Double Exchange effect of oxygem -> Half-metal, phase transition.
-    \end{itemize}
+A important rule is that all homogeneous Lorentz transformations can
+are generated by 
+\(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
+However this property is not proved
 
-    \subsection{By Alan}
-    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
-    the keys.
+\paragraph{Digression about tensor notation} It seems that phsysicists
+have not settled down on their notation for tensors. Weinberg using
+the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
+so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
+tangent vector. I see that this notation helps to distinguish the
+type of arguments. This is unnecessary, since the upper and lower
+indices already fulfill this function. Another benefit is that it
+conveies the process of lowering of raising a index.
 
-    \subsection{By Li, Huang}
-    \begin{itemize}
-            \item Computational Physics
-            \item Surface Dynamics
-            \item Structural factor from 2D to 3D.
-            \item Finding Order Amid the Chaos. amorphous -> spatially
-                    resolved distributed function.
-            \item ?: What is genetically algorithm.
-    \end{itemize}
-    \textbf{Computational and theoretical studies of Surface dynamics}
+However, this idea that each slot in tensor indices are distinct
+and can be lowered and raised seperatly, is not even mentioned
+in some modern mathematical physics book.
 
-    \begin{itemize}
-            \item Surface atoms is immersed in a very different environment
-                    compared with the bulk atoms.
-            \item First-principle calculations
-            \item DFT + LDA -> Conser equation
-            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
-                    Conser equation
-            \item Continumm method ?
-    \end{itemize}
+Helpful link:
+\href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
+\href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.
 
-    \subsection{By Junfen, Liu}
-    \begin{itemize}
-            \item electronic transport in mesoscopic systems:
-            \item Spintronics
-            \item Graphene eletronics
-            \item Superconductors etc.
-    \end{itemize}
-    \textbf{Quantum wire conductiing}
-    The conduction channel in quantum wire is quantized, with discrete value
-    of conductance.
-    \begin{itemize}
-            \item $\lambda_F$ Fermi wavelength
-            \item $L_m$ Momuntum relaxation length <-- impurities.
-            \item $L_\phi$ Phase relaxation length <-- memory of phase,
-                    related to energy $\omega = E/\hbar$.
-            \item $L$ Sample length
-    \end{itemize}
-    \begin{itemize}
-            \item Ballistic transport: $L << L_m$ No scattering.
-            \item Diffusive $L>L_m$, scattering, reduced transmission.
-            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
-            \item Classical. (Omitted)
-    \end{itemize}
-    \textbf{Conductance}
-    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
-    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
-    accounting for the back scattering, perhaps the transmission
-    probability.
-    In reality, $G=\sum_{\text{Different channels}}G_i$,
+\subsubsection{2.4 The Poincar\'{e} Algebra}
+\label{sec:2.4_The_Poincare_Algebra}
+\textbf{I am lost in this part.} The general idea seems to develop, in a 
+infinitesimal sense, the property of a Lorentz transformation.
+For a infinitesimal Lorentz transformation:
+\begin{align}
+    U(1+\omega, \epsilon) = 
+        1+ \frac{1}{2} i\omega_{\rho\sigma}J^{\rho\sigma}
+        -i\epsilon_\rho P^\rho + \cdots
+\end{align}
+where $J$ and $P$ are independent of the infinitesimal value
+$\omega$ and $\epsilon$.
 
-    We can turn the $G$ into resisivity: 
-    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
-    $R+T=1$
+Later $P$ is identified as the energy-momentum operator (with
+$P^0$ being the energy operator), and $J^{23}$, $J^{31}$,
+\(J^{12}\) are identified with the angular momentum operator.
+However, the reason for this identification is not provided. 
+% TODO why P is energy momentum, and J is angular momentum
 
-    \paragraph{Resonate Transmission} (Omitted)
+Later, it was eatablished that $J$ and $P$ satisfy:
+\begin{align}
+    i[J^{\mu\nu},J^{\rho\sigma}] &=
+        \eta^{\nu\rho}J^{\mu\sigma} - \eta^{\mu\rho}J^{\nu\sigma}
+        -\eta^{\sigma\mu}J^{\rho\nu} + \eta^{\sigma\nu}J^{\rho\mu}
+    \\
+    i[P^\mu,J^{\rho\sigma} &=
+        \eta^{\mu\rho}P^\sigma - \eta^{\mu\sigma}P^{\rho}
+    \\
+    [P^\mu,P^\rho] &= 0
+\end{align}
+This is called the \textit{Lie Algebra} of the Poincar\'{e}
+group.
+The relation \([P^\mu,P^\rho] = 0\) is particular interesting.
 
-    \paragraph{Spintronics} Use the extra freedom of Spin.
-
-    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)
-
-    GMR: 2007 Nobel prize in Physics.
-
-    Hall Effect (Omitted)
-    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);
-
-    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)
-
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
-    \textbf{Klein Paradox}
-
-    \paragraph{Josephson Junction} A phase difference could conduct
-    electricity in Superconductors.
-
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
-    Requires strong magnetic field: $\approx 10$ Tesla.
-
-    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
-    where $M$ is the magnetic susceptibility.
-    Two-factors: SO coupling. Spin-dependent Hall Effect.
-
-    An excellent illustrations is found in \cite{Arxiv-Xiao}:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/1}
-        \caption{Illustration}
-        \label{fig:Xiao Illustration}
-    \end{figure}
-
-    \subsection{By Kedong Wang}
-    Tunneling current $I\propto V e^{-2kz}$, where 
-    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
-    $I$ is very sensitive to the distance $z$.
-
-    \paragraph{Work function} $\phi$ characterize the obstruction
-    that prevents electron from escaping the sample.
-
-    \subsection{By Mingyuan Hunag}
-    Too boring.
-
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
-    copy operators in Quantum Mechanics.
-
-    \begin{proof}
-    We proove it by contradiction. Let $U$ be the copy operator. By definition,
-    we have
-    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
-    For any $\ket{\psi}$.
-    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
-    \begin{align*}
-        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
-        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
-        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
-    \end{align*}
-    This is a contradiction.
-    \end{proof}
-    \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
-        strong. However, if we assume that the copyer only
-        works for certain states $\ket{\phi}$, then with the knowledge
-        of these certain states, we could in principle create an exact copy
-        of these states. This copy ,in the sense of another instance of the
-        same object, of original state should not be considered to be an
-        copied version of the original state.
-    \end{remark}
-
-\section{Problems in Bernevig's Topological ...}
-
-    \subsection{Chapter 2}
-    \paragraph{Non-Abelian Berry Transport}
-    Derive Berry curvature to the adiabatic transport of a degenerate
-    multiplet of states separated by a gap from the excited states.
-    (Cautious about rotation within degenerate states).
-
-    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$
-
-    Approach:
-    Assuming that the those degenerate states are labeled by $1\cdots N$. 
-    Thus we have naturally:
+With this, the finite translation and a rotation by angle
+$\theta$ are expressed as:
 \begin{align}
-            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
-        \phi = \sum_n A_n \psi_n
+    U(1,a) = \exp(-iP^\mu a_\mu) \\
+    U(\theta,0) = \exp(i \mathbf{J}\cdot \theta)
 \end{align}
 
-    Then we have:
-    \begin{align}
-    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
-	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
-	\sum_n E A_n \psi_n&=i\hbar\sum_n
-		\left(
-		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
-		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
-		\right) \nonumber\\
-	E A_m &=i\hbar
-		\frac{\partial A_m(t)}{\partial t}
-		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
-    \end{align}
-    Put in another form:
-    $$
-    \sum_n \left(\delta^n_m E
-        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
-        =
-    i\hbar \frac{\partial A_m(t)}{\partial t}
-    $$
-    In matrix form:
-    \begin{align}
-            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
-    \end{align}
-    where:
-    \begin{align}
-        E &= \left(
-        \begin{array}{ccc}
-         \cdots   &     &   \\
-              & E &   \\
-             &    & \text{...} \\
-        \end{array}
-        \right) \\
-        P &= (P^m_n) = \left(
-        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
-        A &= \left(\begin{array}{c}
-            A_1(t) \\
-            A_2(t) \\
-            \cdots \\
-        \end{array}\right)
-    \end{align}
+This part ends with a discussion on the low-velocity limit
+of the Lie Algebra obtained above, i.e. the Galilean algebra.
 
-    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
-    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
-    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.
-
-    Notice that
-    \begin{align}
-            0= \frac{\partial}{\partial t} \braket{m|n} &=
-        \braket{\frac{\partial}{\partial t}m|n} +
-        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
-    \end{align}
-    temporary mathematica code:
-
-% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
-%         {y1[x], y2[x]}, x]
-% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
-% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
-% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
-
-\section{Miscellnaneous Notes}
-    \subsection{Super conductor}
-    Mean-field approach to deal with a four operator diagonalization.
-
-    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
-    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:
-
-    	$$ \delta^2 \approx 0 $$
-    i.e.:
-
-    \begin{align}
-    	( (CD)^* - avg ) ( CD - avg ) = 0\\
-    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
-    \end{align}
-    Hence a four operator is reduced into a few of two operators.
-    Such method could be naturally extended to treat the operator
-    $\sum_{i,j} D^*_i C^*_i C_j D_j$.
-
-    A copper pair has the energy of:
-    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$
-
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
-    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
-
-    This will require an additional enegy of $2\Delta$.
-
-    The exact meaning of "equivalent to" is as follows:
-    \begin{align}
-        & \text{break a copper pair} \longrightarrow 
-        \text{scatter two electrons consecutively} 
-        \nonumber\\ & \longrightarrow 
-        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
-    \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
-
-    \subsection{Preface of BSCS}
-        \label{sec:Preface_of_Bosonization_and_Strongly 
-        Correlated_Systems}
-    BSCS: see \cite{BSCS}.
-    Parallism between theories in condensed matter physics and those in
-    particle physics.
-    \begin{itemize}
-            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
-                    (C.M.P.)
-            \item 'inflation' in Cosmology, first order phase transition
-            \item 'cosmic strings', magnetic field vortex lines in type
-                    II superconductors
-            \item Hadron-meson interaction, Ginzburg-Landau theory of
-                    superfluid $He^3$.
-    \end{itemize}
-    Same ideas on different space-time scales, different hierachical
-    'layers'.
-    Strong parallism: \textbf{strongly correlated low dimensional system}
-
-    E.g.:
-
-    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.
-
-    Approaches:
-    \begin{enumerate}
-            \item Exact solutions
-            \item Reformulate complicated interacting models in such a way
-                    that they become weekly interacting. -> Bosonization.
-
-                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
-                    Model of interacting
-
-                    fermions.
-                    (Jordan and Wigner, 1928)
-    \end{enumerate}
-    Bosonization: transformation from fermions to a scalar massless bosonic
-    field.
-
-    \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
-
-    pp. 266.
-
-    \begin{defi}
-        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
-        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
-        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
-    \end{defi}
-
-    pp. 291.
-
-    \begin{thm}[Existence-uniqueness theorem]
-        There exists one, and only one, solution of the initial-value
-        problem
-
-        \begin{align}
-            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
-                \mathbf{x}(t_0) = \mathbf{x}^0 = 
-                \left(
-                \begin{array}{c}
-		            x^0_1\\
-                    x^0_2\\
-                    \cdots
-                \end{array} 
-                    \right)
-        \end{align}
-
-        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
-    \end{thm}
-    \begin{remark}
-        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
-        time $t$. Also notice that the elements of $\mathbf{A}$ are just
-        numbers.
-    \end{remark}
-
-    \begin{thm}
-        The dimension of the space $\mathbf{V}$ of all solutions of the
-        homogeneous linear system of differential equations:
-        \begin{align}
-            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
-        \end{align}
-        is $n$, i.e. the dimension of vector $\mathbf{x}$.
-    \end{thm} 
-    \subsection{ODE by Arnold}
-    sec. 14
-    \begin{defi}
-        \begin{align}
-            \label{eq:e^A}
-            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
-            \text{or}& \nonumber \\
-            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
-        \end{align}
-        where $I$ is the identity matrix.
-    \end{defi}
-    Equivalance of the two definition will be addressed in the Theorem on
-    pp. 165.
-
-    Important theorems:
-    \begin{thm}[pp. 158]
-        The series $e^A$ converges for any $A$ uniformly on each set
-        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
-    \end{thm}
-    \begin{thm}[pp. 160]
-        $$e^{At} = H^t$$
-        where $H^t$ is the translation operator which sends every polynomial
-        $p(x)$ into $p(x+t)$.
-    \end{thm}
-    \begin{thm}[pp. 163]
-        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
-    \end{thm}
-    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
-        Constant Coefficients]
-        The solution of:
-        \begin{align}
-            \label{eq:fund_thm_of_linear_eqs_const_coef}
-            \dot{\mathbf{x}} = A\mathbf{x}
-        \end{align}
-        with initial condition $\phi(0) = \mathbf{x}_0$ is
-        \begin{align}
-            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
-        \end{align}
-    \end{thm}
-
-    Practically solution to
-    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
-    (pp. 173, Sec 17)
-    (Assuming $A$ is diagonalizable.)
-    \begin{itemize}
-        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
-            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
-        \item Expand the initial condition in the new basis.
-            \begin{align}
-                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
-            \end{align}
-        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
-    \end{itemize}
-    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
-
-    \begin{align}
-        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
-            (\eta_b,U_{ac}\dot{\psi}_c
-    \end{align}
-    \subsection{Quantum Statistical Mechanics}
-    \label{sec:Quantum Statistical Mechanics}
-    \begin{defi}[Time Evolution Operator]
-        The time evolution operator $U(t,t_0)$ is defined such that
-        \begin{align}
-            \label{eq:def_time_evo_op}
-            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
-        \end{align}
-    \end{defi}
-    It satisfy the relationship:
-    \begin{align}
-        \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
-    \end{align}
-    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
-    Equations.
-
-    \paragraph{Quantum Macrostates}
-    Macrostates of the system depend on only a few the thermodynamic
-    functions. We can form an ensemble of a large number $\mathcal{N}$ of
-    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
-    The different microstates occur with probability $p_\alpha$.
-    When wen no longer have exact knowledge of the microstate of a
-    system the system is said to be in a \textit{mixed state}.
-    The ensemble average of the quantum mechanical expectation
-    value is given by:
-    \begin{align}
-        \label{eq:quantum_macrostates_ensemble_avg}
-        \bar{\braket{O}} &= 
-            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
-            = \sum_{\alpha,m,n} p_\alpha
-                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
-                \nonumber\\
-            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
-                = \text{tr}(\rho O)
-    \end{align}
-    where we have introduced the density matrix:
-    \begin{defi}[Density Matrix]
-        The density matrix $\rho(t)$ is defined as
-        \begin{align}
-            \label{eq:density_matrix_def}
-        \braket{n|\rho(t)|m} \equiv
-        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
-        \end{align}
-        or
-        \begin{align}
-            \label{eq:density_matrix_def_2}
-            \rho(t) \equiv \sum_\alpha p_\alpha
-                \ket{\psi_\alpha}\bra{\psi_\alpha}
-        \end{align}
-    \end{defi}
-    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
-    P.D.F, since $\rho$ often represents density.
-
-    Density matrix satisfies several good properties:
-    \begin{itemize}
-        \item Normalized
-        \item Hermiticity
-        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
-    \end{itemize}
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
-
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
-
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-\end{thebibliography}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-
-\end{document}
+\subsection{Note}
+\label{sec:Note}
+I will now change to another book: Q.F.T. in a Nutshell by A. Zee.

### 2016-10-26 Draft/sections/misc-math.tex
Updates physics GRE prepare notes.

--- 2016-07-08 draft.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
+From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. 
+By \href{http://math.stackexchange.com/users/1102/aryabhata}{Aryabhata}.
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage{hyperref} % For hyperlink everything.
-\usepackage{CJKutf8} % For Chinese characters
-%\usepackage{ dsfont } % For double struck fonts
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
+I believe this can also be solved using double integrals.
 
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
+It is possible (if I remember correctly) to justify switching the order of integration to give the equality:
 
-\title{Draft}
-\date{\today}
-\author{we.taper}
-\begin{document}
-\maketitle
-\abstract{
-    This is a draft.
-}
-\tableofcontents
+$$\int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dy \Bigg)\, dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
+Notice that
+$$\int_{0}^{\infty} e^{-xy} \sin x\,dy = \frac{\sin x}{x}$$
 
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
-    \textbf{Thermal electrics}
+This leads us to
 
-    \subsection{By Lang. Chen}
-    \label{sec:c.l}
-    Grow thin films.
-    \begin{itemize}
-	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
-	\item 
-	orbital contral of electrons -> 
-	orbitronics -> Control of Spin orbital coupling.
-	\item
-	Multiferroics -> multiple order parameters, and the interaction
-	between them. E.g. $BiFeO_3$.
-	\item
-	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
-	symmetries simultaneous broken.
-	\item
-	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
-	exactly in theoretical physics?
-	\item
-	$H_2S$: 200K superconductor?
-	\item
-	The Double Exchange effect of oxygem -> Half-metal, phase transition.
-    \end{itemize}
+$$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty} \Bigg(\int_{0}^{\infty} e^{-xy} \sin x \,dx \Bigg)\,dy$$
+Now the right hand side can be found easily, using integration by parts.
 
-    \subsection{By Alan}
-    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
-    the keys.
+\begin{align*}
+I &= \int e^{-xy} \sin x \,dx = -e^{-xy}{\cos x} - y \int e^{-xy} \cos x \, dx\\
+&= -e^{-xy}{\cos x} - y \Big(e^{-xy}\sin x + y \int e^{-xy} \sin x \,dx \Big)\\
+&= \frac{-ye^{-xy}\sin x - e^{-xy}\cos x}{1+y^2}.
+\end{align*}
+Thus $$\int_{0}^{\infty} e^{-xy} \sin x \,dx = \frac{1}{1+y^2}$$
+Thus $$\int_{0}^{\infty} \Big(\frac{\sin x}{x} \Big) \,dx = \int_{0}^{\infty}\frac{1}{1+y^2}\,dy = \frac{\pi}{2}.$$
 
-    \subsection{By Li, Huang}
-    \begin{itemize}
-            \item Computational Physics
-            \item Surface Dynamics
-            \item Structural factor from 2D to 3D.
-            \item Finding Order Amid the Chaos. amorphous -> spatially
-                    resolved distributed function.
-            \item ?: What is genetically algorithm.
-    \end{itemize}
-    \textbf{Computational and theoretical studies of Surface dynamics}
+\subsection{Bayes' theorem}
+\label{sec:Bayes-theorem}
+I am quite unfamiliar with this formula, so I decided to make a note
+here for future reference.
 
-    \begin{itemize}
-            \item Surface atoms is immersed in a very different environment
-                    compared with the bulk atoms.
-            \item First-principle calculations
-            \item DFT + LDA -> Conser equation
-            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
-                    Conser equation
-            \item Continumm method ?
-    \end{itemize}
+This formula starts from the definition of conditional probability:
+\begin{align}
+P(A|B)\equiv \frac{P(A\&B)}{P(B)}
+\end{align}
+this definition if quite intuitively pleasing if $P(B)$ is multiplied
+to the left side. Then one easily deduce that:
+\begin{thm}[Bayes' theorem] \begin{align}
+   	P(A|B)=\frac{P(B|A)P(A)}{P(B)}
+   	\end{align} \end{thm}
 
-    \subsection{By Junfen, Liu}
-    \begin{itemize}
-            \item electronic transport in mesoscopic systems:
-            \item Spintronics
-            \item Graphene eletronics
-            \item Superconductors etc.
-    \end{itemize}
-    \textbf{Quantum wire conductiing}
-    The conduction channel in quantum wire is quantized, with discrete value
-    of conductance.
-    \begin{itemize}
-            \item $\lambda_F$ Fermi wavelength
-            \item $L_m$ Momuntum relaxation length <-- impurities.
-            \item $L_\phi$ Phase relaxation length <-- memory of phase,
-                    related to energy $\omega = E/\hbar$.
-            \item $L$ Sample length
-    \end{itemize}
-    \begin{itemize}
-            \item Ballistic transport: $L << L_m$ No scattering.
-            \item Diffusive $L>L_m$, scattering, reduced transmission.
-            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
-            \item Classical. (Omitted)
-    \end{itemize}
-    \textbf{Conductance}
-    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
-    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
-    accounting for the back scattering, perhaps the transmission
-    probability.
-    In reality, $G=\sum_{\text{Different channels}}G_i$,
-
-    We can turn the $G$ into resisivity: 
-    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
-    $R+T=1$
-
-    \paragraph{Resonate Transmission} (Omitted)
-
-    \paragraph{Spintronics} Use the extra freedom of Spin.
-
-    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)
-
-    GMR: 2007 Nobel prize in Physics.
-
-    Hall Effect (Omitted)
-    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);
-
-    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)
-
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
-    \textbf{Klein Paradox}
-
-    \paragraph{Josephson Junction} A phase difference could conduct
-    electricity in Superconductors.
-
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
-    Requires strong magnetic field: $\approx 10$ Tesla.
-
-    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
-    where $M$ is the magnetic susceptibility.
-    Two-factors: SO coupling. Spin-dependent Hall Effect.
-
-    An excellent illustrations is found in \cite{Arxiv-Xiao}:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/1}
-        \caption{Illustration}
-        \label{fig:Xiao Illustration}
-    \end{figure}
-
-    \subsection{By Kedong Wang}
-    Tunneling current $I\propto V e^{-2kz}$, where 
-    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
-    $I$ is very sensitive to the distance $z$.
-
-    \paragraph{Work function} $\phi$ characterize the obstruction
-    that prevents electron from escaping the sample.
-
-    \subsection{By Mingyuan Hunag}
-    Too boring.
-
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
-    copy operators in Quantum Mechanics.
-
-    \begin{proof}
-    We proove it by contradiction. Let $U$ be the copy operator. By definition,
-    we have
-    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
-    For any $\ket{\psi}$.
-    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
-    \begin{align*}
-        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
-        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
-        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
-    \end{align*}
-    This is a contradiction.
-    \end{proof}
-    \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
-        strong. However, if we assume that the copyer only
-        works for certain states $\ket{\phi}$, then with the knowledge
-        of these certain states, we could in principle create an exact copy
-        of these states. This copy ,in the sense of another instance of the
-        same object, of original state should not be considered to be an
-        copied version of the original state.
-    \end{remark}
-
-\section{Problems in Bernevig's Topological ...}
-
-    \subsection{Chapter 2}
-    \paragraph{Non-Abelian Berry Transport}
-    Derive Berry curvature to the adiabatic transport of a degenerate
-    multiplet of states separated by a gap from the excited states.
-    (Cautious about rotation within degenerate states).
-
-    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$
-
-    Approach:
-    Assuming that the those degenerate states are labeled by $1\cdots N$. 
-    Thus we have naturally:
+We have also an extended form. Suppose the event space is partitioned
+into $\{A_i\}$, then we have (also easily proved):
 \begin{align}
-            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
-        \phi = \sum_n A_n \psi_n
+P(A_i|B)=\frac{P(B|A_i)P(A_i)}{\sum_j P(B|A_j)P(A_j)}
 \end{align}
-
-    Then we have:
-    \begin{align}
-    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
-	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
-	\sum_n E A_n \psi_n&=i\hbar\sum_n
-		\left(
-		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
-		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
-		\right) \nonumber\\
-	E A_m &=i\hbar
-		\frac{\partial A_m(t)}{\partial t}
-		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
-    \end{align}
-    Put in another form:
-    $$
-    \sum_n \left(\delta^n_m E
-        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
-        =
-    i\hbar \frac{\partial A_m(t)}{\partial t}
-    $$
-    In matrix form:
-    \begin{align}
-            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
-    \end{align}
-    where:
-    \begin{align}
-        E &= \left(
-        \begin{array}{ccc}
-         \cdots   &     &   \\
-              & E &   \\
-             &    & \text{...} \\
-        \end{array}
-        \right) \\
-        P &= (P^m_n) = \left(
-        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
-        A &= \left(\begin{array}{c}
-            A_1(t) \\
-            A_2(t) \\
-            \cdots \\
-        \end{array}\right)
-    \end{align}
-
-    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
-    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
-    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.
-
-    Notice that
-    \begin{align}
-            0= \frac{\partial}{\partial t} \braket{m|n} &=
-        \braket{\frac{\partial}{\partial t}m|n} +
-        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
-    \end{align}
-    temporary mathematica code:
-
-% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
-%         {y1[x], y2[x]}, x]
-% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
-% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
-% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
-
-\section{Miscellnaneous Notes}
-    \subsection{Super conductor}
-    Mean-field approach to deal with a four operator diagonalization.
-
-    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
-    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:
-
-    	$$ \delta^2 \approx 0 $$
-    i.e.:
-
-    \begin{align}
-    	( (CD)^* - avg ) ( CD - avg ) = 0\\
-    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
-    \end{align}
-    Hence a four operator is reduced into a few of two operators.
-    Such method could be naturally extended to treat the operator
-    $\sum_{i,j} D^*_i C^*_i C_j D_j$.
-
-    A copper pair has the energy of:
-    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$
-
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
-    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
-
-    This will require an additional enegy of $2\Delta$.
-
-    The exact meaning of "equivalent to" is as follows:
-    \begin{align}
-        & \text{break a copper pair} \longrightarrow 
-        \text{scatter two electrons consecutively} 
-        \nonumber\\ & \longrightarrow 
-        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
-    \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
-
-    \subsection{Preface of BSCS}
-        \label{sec:Preface_of_Bosonization_and_Strongly 
-        Correlated_Systems}
-    BSCS: see \cite{BSCS}.
-    Parallism between theories in condensed matter physics and those in
-    particle physics.
-    \begin{itemize}
-            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
-                    (C.M.P.)
-            \item 'inflation' in Cosmology, first order phase transition
-            \item 'cosmic strings', magnetic field vortex lines in type
-                    II superconductors
-            \item Hadron-meson interaction, Ginzburg-Landau theory of
-                    superfluid $He^3$.
-    \end{itemize}
-    Same ideas on different space-time scales, different hierachical
-    'layers'.
-    Strong parallism: \textbf{strongly correlated low dimensional system}
-
-    E.g.:
-
-    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.
-
-    Approaches:
-    \begin{enumerate}
-            \item Exact solutions
-            \item Reformulate complicated interacting models in such a way
-                    that they become weekly interacting. -> Bosonization.
-
-                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
-                    Model of interacting
-
-                    fermions.
-                    (Jordan and Wigner, 1928)
-    \end{enumerate}
-    Bosonization: transformation from fermions to a scalar massless bosonic
-    field.
+Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
 
 \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
+This is a smsall note of \cite{DETA}.
 
@@
 \end{itemize}
-    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
 
+\subsection{Why 0/0 is undefined?}
+If we suppose
+$$ \frac{0}{0}= \triangle $$
+Consider the following derivation:
 \begin{align}
-        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
-            (\eta_b,U_{ac}\dot{\psi}_c
+\frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
+0 \cdot \frac{1}{0} &= \triangle\\
+\Rightarrow \triangle &= 0
 \end{align}
-    \subsection{Quantum Statistical Mechanics}
-    \label{sec:Quantum Statistical Mechanics}
-    \begin{defi}[Time Evolution Operator]
-        The time evolution operator $U(t,t_0)$ is defined such that
-        \begin{align}
-            \label{eq:def_time_evo_op}
-            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
-        \end{align}
-    \end{defi}
-    It satisfy the relationship:
-    \begin{align}
-        \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
-    \end{align}
-    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
-    Equations.
+This is already bad enough. And we are forced to define $\frac{1}{0}$.
+Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
+This is disastrous.
 
-    \paragraph{Quantum Macrostates}
-    Macrostates of the system depend on only a few the thermodynamic
-    functions. We can form an ensemble of a large number $\mathcal{N}$ of
-    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
-    The different microstates occur with probability $p_\alpha$.
-    When wen no longer have exact knowledge of the microstate of a
-    system the system is said to be in a \textit{mixed state}.
-    The ensemble average of the quantum mechanical expectation
-    value is given by:
-    \begin{align}
-        \label{eq:quantum_macrostates_ensemble_avg}
-        \bar{\braket{O}} &= 
-            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
-            = \sum_{\alpha,m,n} p_\alpha
-                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
-                \nonumber\\
-            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
-                = \text{tr}(\rho O)
-    \end{align}
-    where we have introduced the density matrix:
-    \begin{defi}[Density Matrix]
-        The density matrix $\rho(t)$ is defined as
-        \begin{align}
-            \label{eq:density_matrix_def}
-        \braket{n|\rho(t)|m} \equiv
-        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
-        \end{align}
-        or
-        \begin{align}
-            \label{eq:density_matrix_def_2}
-            \rho(t) \equiv \sum_\alpha p_\alpha
-                \ket{\psi_\alpha}\bra{\psi_\alpha}
-        \end{align}
-    \end{defi}
-    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
-    P.D.F, since $\rho$ often represents density.
+Alternatively, we could let
+\begin{enumerate}
+   	\item Let $\frac{1}{0}$ be undefined.
+   	\item Or let $\frac{1}{0} =
+   	\infty$.
+   	\item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
+   	true when $b=0$.
+\end{enumerate}
+The third idea is disastrous for algebraic manipulation. \footnote{
+   	Or more speicifically, it is a disaster for field theory.
+}
+The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
+out to be very useful in both mathematics and physics. Actully, in
+physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
+any nonzero number $a$, where the sign of $\infty$ is determined by 
+the sign of $a$.
+The second idea is okey. But then we are faced with a serious problem.
+We have to define $\triangle \equiv 0 \cdot \infty$
 
-    Density matrix satisfies several good properties:
-    \begin{itemize}
-        \item Normalized
-        \item Hermiticity
-        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
-    \end{itemize}
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
-
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
-
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-\end{thebibliography}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-
-\end{document}
+$\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?

### 2016-10-26 Draft/sections/misc-other.tex
Updates physics GRE prepare notes.

--- 2016-07-10 draft.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\subsection{About Matlab}
+\label{sec:About-Matlab}
+\paragraph{On using $A/B$ or $A\\B$}
+Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
+, abbrevated $A/B$ and $A\\B$, are different and should be used with
+caution. One can check that:
+\begin{center}
+    $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
+    equivalent to $D\backslash A$.
+\end{center}
+Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage{hyperref} % For hyperlink everything.
-\usepackage{CJKutf8} % For Chinese characters
-%\usepackage{ dsfont } % For double struck fonts
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
-
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-\title{Draft}
-\date{\today}
-\author{we.taper}
-\begin{document}
-\maketitle
-\abstract{
-    This is a draft.
-}
-\tableofcontents
-
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
-    \textbf{Thermal electrics}
-
-    \subsection{By Lang. Chen}
-    \label{sec:c.l}
-    Grow thin films.
-    \begin{itemize}
-	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
-	\item 
-	orbital contral of electrons -> 
-	orbitronics -> Control of Spin orbital coupling.
-	\item
-	Multiferroics -> multiple order parameters, and the interaction
-	between them. E.g. $BiFeO_3$.
-	\item
-	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
-	symmetries simultaneous broken.
-	\item
-	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
-	exactly in theoretical physics?
-	\item
-	$H_2S$: 200K superconductor?
-	\item
-	The Double Exchange effect of oxygem -> Half-metal, phase transition.
-    \end{itemize}
-
-    \subsection{By Alan}
-    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
-    the keys.
-
-    \subsection{By Li, Huang}
-    \begin{itemize}
-            \item Computational Physics
-            \item Surface Dynamics
-            \item Structural factor from 2D to 3D.
-            \item Finding Order Amid the Chaos. amorphous -> spatially
-                    resolved distributed function.
-            \item ?: What is genetically algorithm.
-    \end{itemize}
-    \textbf{Computational and theoretical studies of Surface dynamics}
-
-    \begin{itemize}
-            \item Surface atoms is immersed in a very different environment
-                    compared with the bulk atoms.
-            \item First-principle calculations
-            \item DFT + LDA -> Conser equation
-            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
-                    Conser equation
-            \item Continumm method ?
-    \end{itemize}
-
-    \subsection{By Junfen, Liu}
-    \begin{itemize}
-            \item electronic transport in mesoscopic systems:
-            \item Spintronics
-            \item Graphene eletronics
-            \item Superconductors etc.
-    \end{itemize}
-    \textbf{Quantum wire conductiing}
-    The conduction channel in quantum wire is quantized, with discrete value
-    of conductance.
-    \begin{itemize}
-            \item $\lambda_F$ Fermi wavelength
-            \item $L_m$ Momuntum relaxation length <-- impurities.
-            \item $L_\phi$ Phase relaxation length <-- memory of phase,
-                    related to energy $\omega = E/\hbar$.
-            \item $L$ Sample length
-    \end{itemize}
-    \begin{itemize}
-            \item Ballistic transport: $L << L_m$ No scattering.
-            \item Diffusive $L>L_m$, scattering, reduced transmission.
-            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
-            \item Classical. (Omitted)
-    \end{itemize}
-    \textbf{Conductance}
-    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
-    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
-    accounting for the back scattering, perhaps the transmission
-    probability.
-    In reality, $G=\sum_{\text{Different channels}}G_i$,
-
-    We can turn the $G$ into resisivity: 
-    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
-    $R+T=1$
-
-    \paragraph{Resonate Transmission} (Omitted)
-
-    \paragraph{Spintronics} Use the extra freedom of Spin.
-
-    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)
-
-    GMR: 2007 Nobel prize in Physics.
-
-    Hall Effect (Omitted)
-    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);
-
-    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)
-
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
-    \textbf{Klein Paradox}
-
-    \paragraph{Josephson Junction} A phase difference could conduct
-    electricity in Superconductors.
-
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
-    Requires strong magnetic field: $\approx 10$ Tesla.
-
-    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
-    where $M$ is the magnetic susceptibility.
-    Two-factors: SO coupling. Spin-dependent Hall Effect.
-
-    An excellent illustrations is found in \cite{Arxiv-Xiao}:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/1}
-        \caption{Illustration}
-        \label{fig:Xiao Illustration}
-    \end{figure}
-
-    \subsection{By Kedong Wang}
-    Tunneling current $I\propto V e^{-2kz}$, where 
-    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
-    $I$ is very sensitive to the distance $z$.
-
-    \paragraph{Work function} $\phi$ characterize the obstruction
-    that prevents electron from escaping the sample.
-
-    \subsection{By Mingyuan Hunag}
-    Too boring.
-
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
-    copy operators in Quantum Mechanics.
-
-    \begin{proof}
-    We proove it by contradiction. Let $U$ be the copy operator. By definition,
-    we have
-    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
-    For any $\ket{\psi}$.
-    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
-    \begin{align*}
-        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
-        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
-        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
-    \end{align*}
-    This is a contradiction.
-    \end{proof}
-    \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
-        strong. However, if we assume that the copyer only
-        works for certain states $\ket{\phi}$, then with the knowledge
-        of these certain states, we could in principle create an exact copy
-        of these states. This copy ,in the sense of another instance of the
-        same object, of original state should not be considered to be an
-        copied version of the original state.
-    \end{remark}
-
-\section{Problems in Bernevig's Topological ...}
-
-    \subsection{Chapter 2}
-    \paragraph{Non-Abelian Berry Transport}
-    Derive Berry curvature to the adiabatic transport of a degenerate
-    multiplet of states separated by a gap from the excited states.
-    (Cautious about rotation within degenerate states).
-
-    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$
-
-    Approach:
-    Assuming that the those degenerate states are labeled by $1\cdots N$. 
-    Thus we have naturally:
-	\begin{align}
-            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
-        \phi = \sum_n A_n \psi_n
-    \end{align}
-
-    Then we have:
-    \begin{align}
-    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
-	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
-	\sum_n E A_n \psi_n&=i\hbar\sum_n
-		\left(
-		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
-		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
-		\right) \nonumber\\
-	E A_m &=i\hbar
-		\frac{\partial A_m(t)}{\partial t}
-		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
-    \end{align}
-    Put in another form:
-    $$
-    \sum_n \left(\delta^n_m E
-        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
-        =
-    i\hbar \frac{\partial A_m(t)}{\partial t}
-    $$
-    In matrix form:
-    \begin{align}
-            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
-    \end{align}
-    where:
-    \begin{align}
-        E &= \left(
-        \begin{array}{ccc}
-         \cdots   &     &   \\
-              & E &   \\
-             &    & \text{...} \\
-        \end{array}
-        \right) \\
-        P &= (P^m_n) = \left(
-        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
-        A &= \left(\begin{array}{c}
-            A_1(t) \\
-            A_2(t) \\
-            \cdots \\
-        \end{array}\right)
-    \end{align}
-
-    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
-    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
-    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.
-
-    Notice that
-    \begin{align}
-            0= \frac{\partial}{\partial t} \braket{m|n} &=
-        \braket{\frac{\partial}{\partial t}m|n} +
-        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
-    \end{align}
-    temporary mathematica code:
-
-% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
-%         {y1[x], y2[x]}, x]
-% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
-% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
-% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
-
-\section{Miscellnaneous Notes}
-    \subsection{Super conductor}
-    Mean-field approach to deal with a four operator diagonalization.
-
-    Suppose we have: $D^*C^* CD$, then let $\delta = CD - \braket{CD} =
-    CD - avg$. Then if we assume $\braket{CD}\neq 0$, and $\delta \approx 0$. Then we have:
-
-    	$$ \delta^2 \approx 0 $$
-    i.e.:
-
-    \begin{align}
-    	( (CD)^* - avg ) ( CD - avg ) = 0\\
-    	D^*C^*CD = avg*(CD+D^*C^*) - avg^2
-    \end{align}
-    Hence a four operator is reduced into a few of two operators.
-    Such method could be naturally extended to treat the operator
-    $\sum_{i,j} D^*_i C^*_i C_j D_j$.
-
-    A copper pair has the energy of:
-    $$\Delta = \braket{C_{k \uparrow}C_{-k \downarrow} }$$
-
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
-    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
-
-    This will require an additional enegy of $2\Delta$.
-
-    The exact meaning of "equivalent to" is as follows:
-    \begin{align}
-        & \text{break a copper pair} \longrightarrow 
-        \text{scatter two electrons consecutively} 
-        \nonumber\\ & \longrightarrow 
-        \text{create two electron-hole mixed type quasi-particle} \longrightarrow 2\Delta \nonumber
-    \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
-
-    \subsection{Preface of BSCS}
-        \label{sec:Preface_of_Bosonization_and_Strongly 
-        Correlated_Systems}
-    BSCS: see \cite{BSCS}.
-    Parallism between theories in condensed matter physics and those in
-    particle physics.
-    \begin{itemize}
-            \item Anderson-Higgs Phenomenon (Paritcle), Meissner effect
-                    (C.M.P.)
-            \item 'inflation' in Cosmology, first order phase transition
-            \item 'cosmic strings', magnetic field vortex lines in type
-                    II superconductors
-            \item Hadron-meson interaction, Ginzburg-Landau theory of
-                    superfluid $He^3$.
-    \end{itemize}
-    Same ideas on different space-time scales, different hierachical
-    'layers'.
-    Strong parallism: \textbf{strongly correlated low dimensional system}
-
-    E.g.:
-
-    The problem of formation and structure of heavy particles - hadrons and mesons. The corresponding fine structure constant $\alpha_G\approx 1$.
-
-    Approaches:
-    \begin{enumerate}
-            \item Exact solutions
-            \item Reformulate complicated interacting models in such a way
-                    that they become weekly interacting. -> Bosonization.
-
-                    Spin $1/2$ anisotropic Hisenberg chain $\approx$
-                    Model of interacting
-
-                    fermions.
-                    (Jordan and Wigner, 1928)
-    \end{enumerate}
-    Bosonization: transformation from fermions to a scalar massless bosonic
-    field.
-
-    \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
-
-    pp. 266.
-
-    \begin{defi}
-        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
-        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
-        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
-    \end{defi}
-
-    pp. 291.
-
-    \begin{thm}[Existence-uniqueness theorem]
-        There exists one, and only one, solution of the initial-value
-        problem
-
-        \begin{align}
-            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
-                \mathbf{x}(t_0) = \mathbf{x}^0 = 
-                \left(
-                \begin{array}{c}
-		            x^0_1\\
-                    x^0_2\\
-                    \cdots
-                \end{array} 
-                    \right)
-        \end{align}
-
-        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
-    \end{thm}
-    \begin{remark}
-        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
-        time $t$. Also notice that the elements of $\mathbf{A}$ are just
-        numbers.
-    \end{remark}
-
-    \begin{thm}
-        The dimension of the space $\mathbf{V}$ of all solutions of the
-        homogeneous linear system of differential equations:
-        \begin{align}
-            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
-        \end{align}
-        is $n$, i.e. the dimension of vector $\mathbf{x}$.
-    \end{thm} 
-    \subsection{ODE by Arnold}
-    sec. 14
-    \begin{defi}
-        \begin{align}
-            \label{eq:e^A}
-            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
-            \text{or}& \nonumber \\
-            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
-        \end{align}
-        where $I$ is the identity matrix.
-    \end{defi}
-    Equivalance of the two definition will be addressed in the Theorem on
-    pp. 165.
-
-    Important theorems:
-    \begin{thm}[pp. 158]
-        The series $e^A$ converges for any $A$ uniformly on each set
-        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
-    \end{thm}
-    \begin{thm}[pp. 160]
-        $$e^{At} = H^t$$
-        where $H^t$ is the translation operator which sends every polynomial
-        $p(x)$ into $p(x+t)$.
-    \end{thm}
-    \begin{thm}[pp. 163]
-        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
-    \end{thm}
-    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
-        Constant Coefficients]
-        The solution of:
-        \begin{align}
-            \label{eq:fund_thm_of_linear_eqs_const_coef}
-            \dot{\mathbf{x}} = A\mathbf{x}
-        \end{align}
-        with initial condition $\phi(0) = \mathbf{x}_0$ is
-        \begin{align}
-            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
-        \end{align}
-    \end{thm}
-
-    Practically solution to
-    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
-    (pp. 173, Sec 17)
-    (Assuming $A$ is diagonalizable.)
-    \begin{itemize}
-        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
-            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
-        \item Expand the initial condition in the new basis.
-            \begin{align}
-                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
-            \end{align}
-        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
-    \end{itemize}
-    \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
-
-    \begin{align}
-        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
-            (\eta_b,U_{ac}\dot{\psi}_c
-    \end{align}
-    \subsection{Quantum Statistical Mechanics}
-    \label{sec:Quantum Statistical Mechanics}
-    \begin{defi}[Time Evolution Operator]
-        The time evolution operator $U(t,t_0)$ is defined such that
-        \begin{align}
-            \label{eq:def_time_evo_op}
-            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
-        \end{align}
-    \end{defi}
-    It satisfy the relationship:
-    \begin{align}
-        \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
-    \end{align}
-    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
-    Equations.
-
-    \paragraph{Quantum Macrostates}
-    Macrostates of the system depend on only a few the thermodynamic
-    functions. We can form an ensemble of a large number $\mathcal{N}$ of
-    microstates $\{\psi_\alpha\}$, corresponding too a given macrostates.
-    The different microstates occur with probability $p_\alpha$.
-    When wen no longer have exact knowledge of the microstate of a
-    system the system is said to be in a \textit{mixed state}.
-    The ensemble average of the quantum mechanical expectation
-    value is given by:
-    \begin{align}
-        \label{eq:quantum_macrostates_ensemble_avg}
-        \bar{\braket{O}} &= 
-            \sum_\alpha p_\alpha \braket{\psi_\alpha|O|\psi_\alpha}
-            = \sum_{\alpha,m,n} p_\alpha
-                \braket{\psi_\alpha|m}\braket{m|O|n}\braket{n|\psi_\alpha}
-                \nonumber\\
-            &= \sum_{m,n} \braket{n|\rho|m}\braket{m|O|n}
-                = \text{tr}(\rho O)
-    \end{align}
-    where we have introduced the density matrix:
-    \begin{defi}[Density Matrix]
-        The density matrix $\rho(t)$ is defined as
-        \begin{align}
-            \label{eq:density_matrix_def}
-        \braket{n|\rho(t)|m} \equiv
-        \sum_\alpha p_\alpha \braket{n|\psi_\alpha} \braket{\psi_\alpha|m}
-        \end{align}
-        or
-        \begin{align}
-            \label{eq:density_matrix_def_2}
-            \rho(t) \equiv \sum_\alpha p_\alpha
-                \ket{\psi_\alpha}\bra{\psi_\alpha}
-        \end{align}
-    \end{defi}
-    Density matrix is denoted by $\rho(t)$ by analogy of the notation for
-    P.D.F, since $\rho$ often represents density.
-
-    Density matrix satisfies several good properties:
-    \begin{itemize}
-        \item Normalized
-        \item Hermiticity
-        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
-    \end{itemize}
 \subsection{The Mathematical Theory of Communication}
@@
 % TODO having trouble understanding the Theorem 4 on page 55.
-
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
-
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
-
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-\end{thebibliography}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-
-\end{document}

### 2016-10-26 Draft/sections/misc-physics.tex
Updates physics GRE prepare notes.

--- 2016-07-08 draft.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage{hyperref} % For hyperlink everything.
-\usepackage{CJKutf8} % For Chinese characters
-%\usepackage{ dsfont } % For double struck fonts
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
-
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-\title{Draft}
-\date{\today}
-\author{we.taper}
-\begin{document}
-\maketitle
-\abstract{
-    This is a draft.
-}
-\tableofcontents
-
-\section{Lectures on the Frontiers of Physics}
-\textbf{Given by professor of physics in SUSTC}
-    \subsection{By JQ. He.}
-    \textbf{Thermal electrics}
-
-    \subsection{By Lang. Chen}
-    \label{sec:c.l}
-    Grow thin films.
-    \begin{itemize}
-	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
-	\item 
-	orbital contral of electrons -> 
-	orbitronics -> Control of Spin orbital coupling.
-	\item
-	Multiferroics -> multiple order parameters, and the interaction
-	between them. E.g. $BiFeO_3$.
-	\item
-	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
-	symmetries simultaneous broken.
-	\item
-	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
-	exactly in theoretical physics?
-	\item
-	$H_2S$: 200K superconductor?
-	\item
-	The Double Exchange effect of oxygem -> Half-metal, phase transition.
-    \end{itemize}
-
-    \subsection{By Alan}
-    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
-    the keys.
-
-    \subsection{By Li, Huang}
-    \begin{itemize}
-            \item Computational Physics
-            \item Surface Dynamics
-            \item Structural factor from 2D to 3D.
-            \item Finding Order Amid the Chaos. amorphous -> spatially
-                    resolved distributed function.
-            \item ?: What is genetically algorithm.
-    \end{itemize}
-    \textbf{Computational and theoretical studies of Surface dynamics}
-
-    \begin{itemize}
-            \item Surface atoms is immersed in a very different environment
-                    compared with the bulk atoms.
-            \item First-principle calculations
-            \item DFT + LDA -> Conser equation
-            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
-                    Conser equation
-            \item Continumm method ?
-    \end{itemize}
-
-    \subsection{By Junfen, Liu}
-    \begin{itemize}
-            \item electronic transport in mesoscopic systems:
-            \item Spintronics
-            \item Graphene eletronics
-            \item Superconductors etc.
-    \end{itemize}
-    \textbf{Quantum wire conductiing}
-    The conduction channel in quantum wire is quantized, with discrete value
-    of conductance.
-    \begin{itemize}
-            \item $\lambda_F$ Fermi wavelength
-            \item $L_m$ Momuntum relaxation length <-- impurities.
-            \item $L_\phi$ Phase relaxation length <-- memory of phase,
-                    related to energy $\omega = E/\hbar$.
-            \item $L$ Sample length
-    \end{itemize}
-    \begin{itemize}
-            \item Ballistic transport: $L << L_m$ No scattering.
-            \item Diffusive $L>L_m$, scattering, reduced transmission.
-            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
-            \item Classical. (Omitted)
-    \end{itemize}
-    \textbf{Conductance}
-    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
-    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
-    accounting for the back scattering, perhaps the transmission
-    probability.
-    In reality, $G=\sum_{\text{Different channels}}G_i$,
-
-    We can turn the $G$ into resisivity: 
-    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
-    $R+T=1$
-
-    \paragraph{Resonate Transmission} (Omitted)
-
-    \paragraph{Spintronics} Use the extra freedom of Spin.
-
-    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)
-
-    GMR: 2007 Nobel prize in Physics.
-
-    Hall Effect (Omitted)
-    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);
-
-    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)
-
-    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
-    \textbf{Klein Paradox}
-
-    \paragraph{Josephson Junction} A phase difference could conduct
-    electricity in Superconductors.
-
-    \subsection{By Haizhou, Lu}
-    \paragraph{Quantum Anomalous Hall Effect}
-    Requires strong magnetic field: $\approx 10$ Tesla.
-
-    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
-    where $M$ is the magnetic susceptibility.
-    Two-factors: SO coupling. Spin-dependent Hall Effect.
-
-    An excellent illustrations is found in \cite{Arxiv-Xiao}:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/1}
-        \caption{Illustration}
-        \label{fig:Xiao Illustration}
-    \end{figure}
-
-    \subsection{By Kedong Wang}
-    Tunneling current $I\propto V e^{-2kz}$, where 
-    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
-    $I$ is very sensitive to the distance $z$.
-
-    \paragraph{Work function} $\phi$ characterize the obstruction
-    that prevents electron from escaping the sample.
-
-    \subsection{By Mingyuan Hunag}
-    Too boring.
-
-    \subsection{By Wenkang Wong}
-    \paragraph{Non-clone Theorem} We can easily see that there is no universal
-    copy operators in Quantum Mechanics.
-
-    \begin{proof}
-    We proove it by contradiction. Let $U$ be the copy operator. By definition,
-    we have
-    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
-    For any $\ket{\psi}$.
-    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
-    \begin{align*}
-        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
-        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
-        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
-    \end{align*}
-    This is a contradiction.
-    \end{proof}
-    \begin{remark}
-        We assume that the copyer is universal. This might seems to be too
-        strong. However, if we assume that the copyer only
-        works for certain states $\ket{\phi}$, then with the knowledge
-        of these certain states, we could in principle create an exact copy
-        of these states. This copy ,in the sense of another instance of the
-        same object, of original state should not be considered to be an
-        copied version of the original state.
-    \end{remark}
-
-\section{Problems in Bernevig's Topological ...}
-
-    \subsection{Chapter 2}
-    \paragraph{Non-Abelian Berry Transport}
-    Derive Berry curvature to the adiabatic transport of a degenerate
-    multiplet of states separated by a gap from the excited states.
-    (Cautious about rotation within degenerate states).
-
-    Answer: $\gamma_{mn}(t) = i \int_0^t \braket{m(R(t'))|\frac{d}{dt'}|n(R(t'))}dt'$
-
-    Approach:
-    Assuming that the those degenerate states are labeled by $1\cdots N$. 
-    Thus we have naturally:
-	\begin{align}
-            H\phi &=i\hbar\frac{\partial}{\partial t}\phi\text{,  }
-        \phi = \sum_n A_n \psi_n
-    \end{align}
-
-    Then we have:
-    \begin{align}
-    H \sum_n A_n \psi_n &=i\hbar\frac{\partial }{\partial t}
-	  	\sum_n A_n(t) \psi_n(R(t)) \nonumber\\
-	\sum_n E A_n \psi_n&=i\hbar\sum_n
-		\left(
-		\frac{\partial A_n(t)}{\partial t}\psi_n(R(t))+
-		A_n(t)\frac{\partial \psi_n(R(t))}{\partial t}
-		\right) \nonumber\\
-	E A_m &=i\hbar
-		\frac{\partial A_m(t)}{\partial t}
-		+\sum_n A_n(t)\braket{m|\frac{\partial }{\partial t}|n}
-    \end{align}
-    Put in another form:
-    $$
-    \sum_n \left(\delta^n_m E
-        - \braket{m| \frac{\partial}{\partial t}|n} \right) A_n
-        =
-    i\hbar \frac{\partial A_m(t)}{\partial t}
-    $$
-    In matrix form:
-    \begin{align}
-            (E - P) \mathbf{A} = i\hbar \dot{\mathbf{A}}
-    \end{align}
-    where:
-    \begin{align}
-        E &= \left(
-        \begin{array}{ccc}
-         \cdots   &     &   \\
-              & E &   \\
-             &    & \text{...} \\
-        \end{array}
-        \right) \\
-        P &= (P^m_n) = \left(
-        \braket{m| \frac{\partial}{\partial t}|n}\right)\\
-        A &= \left(\begin{array}{c}
-            A_1(t) \\
-            A_2(t) \\
-            \cdots \\
-        \end{array}\right)
-    \end{align}
-
-    Note that $\braket{n| \frac{\partial}{\partial t}|m}^* \neq
-    \braket{m| \frac{\partial}{\partial t} |n}$, thus $P$ may not be
-    Hermitian.Ergo $E-P$ is Hermitian. So it is diagonalizable.
-
-    Notice that
-    \begin{align}
-            0= \frac{\partial}{\partial t} \braket{m|n} &=
-        \braket{\frac{\partial}{\partial t}m|n} +
-        \braket{m|\frac{\partial}{\partial t}n} &&(\text{any }m,n)
-    \end{align}
-    temporary mathematica code:
-
-% In[8]:=DSolve[{y1'[x]+y2'[x]==x,y1'[x]-y2'[x]==0},
-%         {y1[x], y2[x]}, x]
-% In[9]:= DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1+A2[t]*m2, 
-% e1*A2[t]==A2'[t]+A1[t]*m1+A2[t]*m2},{A1[t],A2[t]},t]
-% In[10]:=DSolve[{e1*A1[t]==A1'[t]+A1[t]*m1},{A1[t]},t]
-
-\section{Miscellnaneous Notes}
 \subsection{Super conductor}
@@
 
-    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
+To resist the flow of current carried by Copper Pair, is equivalent to destroying a pair of Copper Pair:
 $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$
@@
 \end{align}
-
-    \subsection{Why 0/0 is undefined?}
-    If we suppose
-    $$ \frac{0}{0}= \triangle $$
-    Consider the following derivation:
-    \begin{align}
-	    \frac{0}{0} \cdot 1 &= \triangle \cdot 1 = \triangle \\
-	    0 \cdot \frac{1}{0} &= \triangle\\
-	    \Rightarrow \triangle &= 0
-    \end{align}
-    This is already bad enough. And we are forced to define $\frac{1}{0}$.
-    Let $\frac{1}{0} = \square$, which literally means $1=0\cdot \square = 0$.
-    This is disastrous.
-
-    Alternatively, we could let
-    \begin{enumerate}
-	    \item Let $\frac{1}{0}$ be undefined.
-	    \item Or let $\frac{1}{0} =
-		    \infty$.
-	    \item Or, let $\frac{a}{b}\cdot c= a\cdot \frac{c}{b}$ be not 
-		    true when $b=0$.
-    \end{enumerate}
-    The third idea is disastrous for algebraic manipulation. \footnote{
-    Or more speicifically, it is a disaster for field theory.
-    }
-    The first idea is not good. Since defining $\frac{1}{0}=\infty$ turns
-    out to be very useful in both mathematics and physics. Actully, in
-    physics it is common practice to set $\frac{a}{0}=\pm\infty$ for
-    any nonzero number $a$, where the sign of $\infty$ is determined by 
-    the sign of $a$.
-    The second idea is okey. But then we are faced with a serious problem.
-    We have to define $\triangle \equiv 0 \cdot \infty$
-
-    $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
 
@@
 
-    \subsection{System of Differential Equations}
-    This is a small note of \cite{DETA}.
-
-    pp. 266.
-
-    \begin{defi}
-        $\mathbf{x(t)}$ is a vector whose elements are $x_i(t)$.
-        $ \frac{d}{d t}$ acts on vector $\mathbf{x}$ element-wise.
-        $\dot{\mathbf{x}}$ is abbrevation for $\frac{d}{d t}\mathbf{x}$
-    \end{defi}
-
-    pp. 291.
-
-    \begin{thm}[Existence-uniqueness theorem]
-        There exists one, and only one, solution of the initial-value
-        problem
-
-        \begin{align}
-            \dot{\mathbf{x}}=\mathbf{A}\mathbf{x}\text{, }&
-                \mathbf{x}(t_0) = \mathbf{x}^0 = 
-                \left(
-                \begin{array}{c}
-		            x^0_1\\
-                    x^0_2\\
-                    \cdots
-                \end{array} 
-                    \right)
-        \end{align}
-
-        Moreover, this solution exists for $-\infty\langle t\langle \infty$.
-    \end{thm}
-    \begin{remark}
-        By this, any non-trivial solution $\mathbf{x}(t)\neq 0$ at any
-        time $t$. Also notice that the elements of $\mathbf{A}$ are just
-        numbers.
-    \end{remark}
-
-    \begin{thm}
-        The dimension of the space $\mathbf{V}$ of all solutions of the
-        homogeneous linear system of differential equations:
-        \begin{align}
-            \frac{d\mathbf{x}}{dt}=\mathbf{Ax}
-        \end{align}
-        is $n$, i.e. the dimension of vector $\mathbf{x}$.
-    \end{thm} 
-    \subsection{ODE by Arnold}
-    sec. 14
-    \begin{defi}
-        \begin{align}
-            \label{eq:e^A}
-            e^A &= I + A + \frac{A^2}{2!} + \frac{A^3}{3!}\\
-            \text{or}& \nonumber \\
-            e^A &= \lim_{n\to \infty}(I+\frac{A}{n})^n
-        \end{align}
-        where $I$ is the identity matrix.
-    \end{defi}
-    Equivalance of the two definition will be addressed in the Theorem on
-    pp. 165.
-
-    Important theorems:
-    \begin{thm}[pp. 158]
-        The series $e^A$ converges for any $A$ uniformly on each set
-        $X=\{A:||A||\leq a\}$, $a\in \mathbb{R}$.
-    \end{thm}
-    \begin{thm}[pp. 160]
-        $$e^{At} = H^t$$
-        where $H^t$ is the translation operator which sends every polynomial
-        $p(x)$ into $p(x+t)$.
-    \end{thm}
-    \begin{thm}[pp. 163]
-        $$\frac{d}{dt} e^{tA} = Ae^{tA}$$
-    \end{thm}
-    \begin{thm}[Fundamental Theorem of the Theory of Linear Equations with
-        Constant Coefficients]
-        The solution of:
-        \begin{align}
-            \label{eq:fund_thm_of_linear_eqs_const_coef}
-            \dot{\mathbf{x}} = A\mathbf{x}
-        \end{align}
-        with initial condition $\phi(0) = \mathbf{x}_0$ is
-        \begin{align}
-            \mathbf{\phi}(t) = e^{tA}\mathbf{x}_0
-        \end{align}
-    \end{thm}
-
-    Practically solution to
-    $$ \dot{\mathbf{x}} = A\mathbf{x}$$
-    (pp. 173, Sec 17)
-    (Assuming $A$ is diagonalizable.)
-    \begin{itemize}
-        \item Find the eigenvectors $\xi_1,\cdots ,\xi_n$ and eigenvalues
-            $\lambda_1,\cdots ,\lambda_n$. Use them as basis.
-        \item Expand the initial condition in the new basis.
-            \begin{align}
-                \mathbf{x}_0=\sum_{k=1}^{n} C_k\xi_k
-            \end{align}
-        \item Then $\phi(t) = \sum_{k=1}^n C_k e^{\lambda_k t}\xi_k$
-    \end{itemize}
 \subsection{Appearance of Gauge Structure in Simple Dynamical Systems}
@@
     \label{eq:def_time_evo_op 2}
-        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
+    i\hbar \partial_t U(t,t_0)= H U(t,t_0)
 \end{align}
@@
 \end{itemize}
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
+The time evolution of density matrix, directly obtained from Schrodinger's
+equation, is
+\begin{align}
+    \label{eq:quantum_macrostates:density_matrix:evolution}
+    i\hbar \frac{\partial}{\partial t}\rho = [H,\rho]
+\end{align}
+\subsection{Special techniques in Electrostatistics}
+\label{sec:Special-techniques-in-Electrostatistics}
 
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
-
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-\end{thebibliography}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-
-\end{document}
+For the book \cite{griffiths-EM}, pp. 120 of section 3.1.6.

### 2016-10-26 GRE Physics Prep/General Physics Formula.tex
Updates physics GRE prepare notes.

@@
 
+\section{General}
+\label{sec:Table}
+
+\begin{table}[H]
+    \centering
+    \caption{Metric Prefix}
+    \begin{tabular}{c c c}
+        tera  & T     & $10^{12}$ \\
+        giga  & G     & $10^{9}$ \\
+        mega  & M     & $10^{6}$ \\
+        kilo  & k     & $10^{3}$ \\
+        centi & c     & $10^{-2}$ \\
+        milli & m     & $10^{-3}$ \\
+        micro & $\mu$ & $10^{-6}$ \\
+        nano  & n     & $10^{-9}$ \\
+        pico  & p     & $10^{-12}$ \\
+    \end{tabular}
+\end{table}
+
+\paragraph{Rotation matrix}
+Active rotation in the counter-clockwise $\theta$:
+\begin{equation}
+    \left(
+    \begin{array}{cc}
+        \cos{\theta} & -\sin{\theta} \\
+        \sin{\theta} & \cos{\theta} \\
+    \end{array}
+    \right)
+\end{equation}
+
 \section{Classical mechanics}
 \label{sec:Classical-mechanics}
+
+\begin{align}
+L &= T- V\\
+\frac{\diff}{\diff t} \left(\frac{\partial L}{\partial \dot{q}}\right)
+    &= \frac{\partial L}{\partial q} \\
+\dot{q} &= \frac{\partial H}{\partial p} \\
+\dot{p} &= -\frac{\partial H}{\partial q}
+\end{align}
 
@@
 \begin{align}
-    & v = \frac{\tau}{\mu} \\
+    & v = \sqrt{\frac{\tau}{\mu}} \\
     & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
@@
 \end{align}
-\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
+\paragraph{Sound (Longitudinal) Wave} (\textbf{pp.466 ch17 of
+\cite{book}})
 \begin{align}
@@
 \end{align}
+
+\textbf{Black Body Radiation}
+Plank's law:
+\begin{equation}
+    I(\mu,T) = \frac{2h\mu^3}{c^2} \frac{1}{e^{\frac{h\mu}{kT}-1}}
+\end{equation}
+Wien's displacement law:
+
+Wien's displacement law shows how the spectrum of black-body radiation
+at any temperature is related to the spectrum at any other
+temperature. If we know the shape of the spectrum at one temperature,
+we can calculate the shape at any other temperature. Spectral
+intensity can be expressed as a function of wavelength or of
+frequency.
+
+A consequence of Wien's displacement law is that the wavelength at
+which the intensity per unit wavelength of the radiation produced by a
+black body is at a maximum, $\lambda_\text{max}$, is a function only of the temperature:
+\begin{equation}
+    \lambda_\text{max}=\frac{b}{T}
+\end{equation}
+where the constant $b$, known as Wien's displacement constant.
 \textbf{Conduction}
@@
 \end{equation}
-
+For electric generator:
+\begin{equation}
+    E_\text{max} = nBA_\text{rea}\omega
+\end{equation}
 \textbf{Circuit Rule}
@@
 
+\begin{align}
+    & X_C = \frac{1}{\omega_d C} \\
+    & X_L = \omega_d L \\
+    & V = I X \\
+    & Z_\text{impedance} = \text{vector sum of all above} \\
+    & Z = \sqrt{R^2+(X_L-X_C)^2}  \text{ for simple RLC circuit}
+\end{align}
+% \begin{itemize}
+%     \item \textbf{Resisitor} $V_R$ is in phase with $I$.
+%     \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
+%     \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
+% \end{itemize}
 \paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})
@@
 
+\section{Optics}
+\label{sec:Optics}
+
 \paragraph{Optics} (\textbf{pp.913 ch33 of \cite{book}})
@@
 \begin{align}
+    & n = \frac{c}{v_\text{medium}} \\
     & \lambda_n = \frac{\lambda}{n} \\
@@
 
+\paragraph{Lenses}
+
+\begin{align}
+    & \frac{1}{s_o} + \frac{1}{s_i} = \frac{1}{f}
+\end{align}
+\begin{table}[H]
+    \centering
+    \begin{tabular}{c c c}
+        Quantity & + & -\\
+        \hline
+        $s_i$ & real & virtual \\
+        \hline
+        $s_o$ & real & virtual \\
+        \hline
+        $f$ & convex & concave \\
+        \hline
+    \end{tabular}
+\end{table}
 \section{Relativity}
@@
     u &= \frac{u'+v}{1+u'v/c^2} \\
-    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}} \\
-    f &= f_0 \sqrt{1-\beta^2} \\
+    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}}\text{ (away)} \\
+    v &= \frac{|\Delta\lambda|}{\lambda_0}c\,( \text{ away, for } v<<c) \\
+    f &= f_0 \sqrt{1-\beta^2} \text{ (perpendicular)}\\
     \vec{p} &= \gamma m \vec{v} \\
@@
 
-\paragraph{Standard Model}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/Hydrogen_spectrum_series.pdf}
+    \caption{Hydrogen spectrum series}
+\end{figure}
+\begin{table}[H]
+    \centering
+    \caption{Three common decay processes}
+    \begin{tabular}{c c}
+        Decay name & Process \\
+        $\alpha$ & Emitting a Helium Nucleus (two protons and two
+        neutrons) \\
+        \hline
+        $\beta$ & $n\to p+e^- \bar{v_e}$ or $p\to n+e^+ +v_e$ \\
+        \hline
+        $\gamma$ & Only photon (light ray) emitted \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\section{Standard Model}
 Read page 1244 of \cite{book}.

### 2016-10-30 Draft/sections/misc-math.tex
New notes in Draft, about a specific function.

@@
 $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
+\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
+\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
+
+Here I prove a simple fact that:
+\begin{thm}
+    Any smooth $f$ function of $\mathbb{R}$. If $f$ satisfy the
+    relation:
+    \begin{equation}
+        f(x+y)=f(x)f(y)
+    \end{equation}
+    for any $x,y\in \mathbb{R}$, and $f(0)\neq 0$. Then:
+    \begin{equation}
+        f(x) = e^{k x}
+    \end{equation}
+    where $k=\dv{f}{x}\left(0\right)$.
+\end{thm}
+\begin{proof}
+    Notice that since $f(0)=f(0+0)=f(0)^2$, and $f(0)\neq 0$, we have
+    $f(0)=1$.
+
+    Consider
+    \begin{align*}
+        \dv{f}{x} = \lim_{\Delta x\to 0} 
+        \frac{f(x+\Delta x)-f(x)}{\Delta x}
+            = \lim_{\Delta x\to 0} 
+            \frac{f(x)\left(f(\Delta x)-1\right)}{\Delta x}
+    \end{align*}
+    Using Taylor expansion about $f(0)$ and notice $f(0)=1$, one will
+    easily get
+    \begin{equation*}
+        \lim_{\Delta x\to 0} 
+            \frac{f(\Delta x)-1}{\Delta x}
+            = f'(0)
+    \end{equation*}
+    Therefore, 
+    \begin{equation*}
+        \dv{f}{x} = f'(0)f(x)
+    \end{equation*}
+    Hence by thoey of differential equations (I don't quite remember
+    the specific theorem), one has $f(x)=e^{f'(0)x}$.
+\end{proof}

### 2016-10-30 Notes of Bernvig's Book/sections/Ch4 TR symmetry/Notes about TR symmetry.tex
Minor Modifications

--- 2016-10-22 Notes of Bernvig's Book/Ch4 TR symmetry/Notes about TR symmetry.tex
@@
 
+        \begin{lemma}
+            For time reversal symmetric electron bands, its Berry
+            phase is always $0$. Hence, the Hall conductance is also
+            zero.
+        \end{lemma}
+        \begin{proof}
+            Consider the Berry field strength:
+            $$F_{ij}(\vb{k}) = \braket{\partial_i n(\vb{k})|\partial_j
+            n(\vb{k})} - (i \leftrightarrow j) $$
+
+            The time reversed state $T\ket{n(\vb{k})}
+            =\ket{n^*(-\vb{k})}$, since $T$ flips $\vb{k}$ and is
+            antiunitary. So in the time reversed state the Berry field
+            strength is:
+            $$F'_{ij}(\vb{k}) = \braket{\partial_i n^*(-\vb{k})|\partial_j
+            n^*(-\vb{k})} - (i \leftrightarrow j) $$
+            Notice that $\braket{n^*|m^*} = \braket{m|n}$, as can be
+            seen if we use the position space wave function. Then we
+            have
+            $$F'_{ij}(\vb{k}) = -F_{ij}(-\vb{k})$$
+            Also, the system is time reversal symmetric, so
+            \begin{align}
+                F_{ij}(\vb{k}) = F'_{ij}(\vb{k}) = -F_{ij}(-\vb{k})
+            \end{align}
+            Hence $F_{ij}$ is an odd function and its integration over
+            the whole BZ is $0$.
+        \end{proof}
+
 \section{Anchor}

### 2016-10-31 Lecture note - Group Theory in Physics/group theory in physics.tex
New lecture note of group theory in physics.

@@
 \usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
 \newtheorem{thm}{Theorem}[section]
@@
 \theoremstyle{definition}
+\newtheorem{defi}{Definition}[section]
 \newtheorem{ex}{Example}[section]
@@
 \newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}
+
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physics-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physics-taper}
 
@@
 
+\section{Skipped Two lectures}
+Due to GRE physics preparation. Concepts that may have been covered:
+
+\begin{itemize}
+    \item Representation of Groups.
+        \begin{itemize}
+            \item Character of representation.
+            \item Equivalence between representation.
+        \end{itemize}
+    \item Transformation of Fields
+    \item Regular Representation.
+\end{itemize}
+
+Now let's me cover these concepts quickly.
+
+\begin{defi}[Representation]
+\nomenclature{Representation}{\nomrefpage.}
+    A representation of a group $G$ is a continuous homomorphism $D$
+    from $G$ to the group of automorphisms of a vector space $V$:
+    \begin{equation}
+        D: G\mapsto \mathrm{Aut}V
+    \end{equation}
+    $V$ is called the \textit{represetation space}, and the
+    \textit{dimension of the representation} is the dimension of $V$.
+\end{defi}
+
+The following is copied from \cite{Ludeling}.
+
+\begin{itemize}
+    \item There is always the representation $D(g) = 1$ for all $g$.
+        If $\mathrm{dim} V = 1$, this is called the \textit{trivial
+        representation} \nomenclature{trivial
+        representation}{\nomrefpage}.
+    \item The matrix groups, i.e. $\mathrm{GL}(n, K)$ and subgroups,
+        naturally have the representation "by themselves", i.e.
+        by$n\times n$ matrices acting on $K_n$ and satisfying the
+        defining constraints (e.g. nonzero determinant). This is
+        loosely called the \textit{fundamental or defining
+        representation}.
+    \item Two representations $D$ and $D'$ are called
+        \textit{equivalent}\nomenclature{equivalent of
+        representation}{\nomrefpage} if they are related by a
+        similarity transformation, i.e. if there is an operator S such
+        that
+        \begin{equation}
+            SD(g)S^{-1} = D'(g)
+        \end{equation}
+        for all $g$. Note that $S$ does not depend on $g$! Two equivalent
+        representation can be thought of as the same representation in
+        different bases. We will normally regard equivalent
+        representations as being equal.
+
+        Note also here $S$ is the transformation of basis. If we know
+        the transformation of vectors $X$, then
+        \begin{equation}
+            X^{-1} D(g)X = D'(g)
+        \end{equation}
+    \item A representation is called
+        \textit{faithful}\nomenclature{faithful
+        representation}{\nomrefpage}if it is injective, i.e.
+        $\mathrm{ker} D = \{e\}$, or in other words, if $D(g_1) \neq
+        D(g_2)$ whenever $g_1 \neq g_2$.
+    \item If $V$ is equipped with a (positive definite) scalar
+        product, D is unitary if it preserves that scalar product, i.e
+        if
+        \begin{equation}
+            \braket{u,v} = \braket{D(g)u,D(g)v}
+        \end{equation}
+        for all $g\in G$. (Here we assume that $V$ is a complex vector
+        space, as that is the most relevant case. Otherwise one could
+        define orthogonal representations etc.)
+\end{itemize}
+
+\section{20161031}
+\label{sec:20161031}
+
+\begin{thm}[Unitary Representation]
+    For finite groups and for compact Lie groups, all representations
+    are equivalent to a unitary representation.
+\end{thm}
+\begin{proof}
+    For $D(g)$, we need to find a $X$ such that $\bar{D}(g)\equiv
+    X^{-1}D(g)X$ is unitary.
+
+    Since
+    \begin{align*}
+        1 = \bar{D}^\dagger \bar{D}
+    \end{align*}
+    One will find 
+    $$ (XX^\dagger)^{-1} = D^\dagger (XX^\dagger)^{-1} D$$
+    Then let
+    \begin{equation}
+        H\equiv \sum_{s\in G} D^\dagger(s) D(s)
+    \end{equation}
+    One can verify that
+    \begin{equation}
+        D^\dagger (g) H D(g) = H
+    \end{equation}
+
+    Now we construct $X$ from $H$. We have
+    \begin{equation}
+        H = (XX^\dagger)^{-1}
+    \end{equation}
+
+    Notice we have $H$ is Hermitian by above equation. Also, $H$ is
+    positive definite (easily seen from the definition of $H$ and 
+    $a^\dagger H a \geq 0$. Also $H$ is of full rank.).
+
+    Then we have $UHU^{-1} = \mathrm{diag}\{\gamma_1,\gamma_2,\cdots\}$
+    and $\gamma_i > 0$. The rest for constructing $X$ should be
+    obvious.
+
+    Another way to prove this is to imbe
+\end{proof}
+
+\begin{thm}
+    For any two equivalent representation, there is always a unitary
+    matrix to relate the two, i.e. exits $Y$ unitary, s.t.
+    $$ \bar{D}(g) = Y^{-1} D(g) Y$$
+\end{thm}
+\begin{proof}
+    Suppose we have two unitary representation $D(g)$ and
+    $\bar{D}(g)$, related by
+    $$ \bar{D}(g) = X^{-1} D(g) X$$
+    where $X$ is not necessarily unitary.
+
+    Let $H\equiv X^\dagger X$, it is easy to prove that $H$ is
+    Hermitian and positive definite. Direct calculation shows that
+    $$ \bar{D}^{-1}(g) H \bar{D}(g) = H$$
+    That is $\bar{D}(g)$ and $H$ commute.
+    Then we construct $Y$ from $H$. Let $V$ be such that
+    \begin{equation}
+        V^{-1} H V = \Gamma
+    \end{equation}
+    where $\Gamma$ is a diagonal matrix of $H$'s eigenvalues.
+    Obviously $V$ has to be unitary. Define $Y$ to be
+    \begin{equation}
+        Y\equiv V \sqrt{\Gamma} V^{-1}
+    \end{equation}
+    By direct calculation, we have
+    $$ (XY)^\dagger (XY) = 1$$
+    One can show that
+    $$[ Y, \bar{D}(g)] = 0$$
+    with laborious calculation. % TODO 
+\end{proof}
+
+\begin{defi}[Reducibility of Representation]
+    \nomenclature{Reducibility of Representation}{\nomrefpage.}
+    A representation $D$ is called \textit{reducible} if $V$ contains an
+    invariant subspace. Otherwise $D$ is called irreducible.
+
+    A representation is called \textit{fully reducible} if $V$ can be
+    written as the direct sum of irreducible invariant subspaces, i.e.
+    $V=V_1\oplus \cdots \oplus V_p$, all the $V_i$ are invariant and the
+    restriction of $D$ to each $V_i$ is irreducible.
+\end{defi}
+
+\begin{ex}$ $
+
+    \begin{itemize}
+        \item The representation of finite group is obviously fully
+            reducible or irreducible.
+        \item The representation of translation group is not fully
+            reducible. For example, for translation we have:
+            $T_a T_b = T_{a+b}$,
+            One can confirm that the following representation obeys
+            the above relationship:
+            $$T_a = \left( \begin{array}{cc}
+                 1 & a \\
+                 0 & 1 \\
+            \end{array} \right)$$
+            but this is obviously not fully reducible.
+    \end{itemize}
+\end{ex}
+
+\begin{defi}[Interwiner]
+\nomenclature{Interwiner}{\nomrefpage.}
+    Given two representations $D_1$ and $D_2$ acting on $V_1$ and
+    $V_2$, an intertwiner between $D_1$ and $D_2$ is a linear operator
+    \begin{equation}
+        F: V_1 \mapsto V_2
+    \end{equation}
+    which "commutes" with $G$ in the sense that
+    \begin{equation}
+        F D_1(g) = D_2(g) F
+    \end{equation}
+    for all $g\in G$.
+\end{defi}
+
+(From pp.30 of \cite{Ludeling})
+
+The existence of an intertwiner has a number of consequences. First,
+$D_1$ and $D_2$ are equivalent exactly if there exists an invertible
+intertwiner. Second, \hl{the kernel and the image of $F$ are invariant
+subspaces}: Assume $v\in \Ker{F}$, i.e. $Fv = 0$. Then
+\begin{equation}
+    FD_1 v = D_2 F v = D_2 0 = 0
+\end{equation}
+so $D_1 v\in \Ker{F}$. On the other hand, let $w_2 = Fw_1$ be an
+arbitrary element of the image of $F$. Then from the definition we have
+\begin{equation}
+    D_2 w_2 = D_2 F w_1 = FD_1 w_1
+\end{equation}
+which is again in the image of $F$. Now if $D_1$ is irreducible, the only invariant subspaces,
+hence the only possible kernels, are $\{0\}$ and $V_1$ itself, so $F$ is either injective or zero.
+Similarly, if $D_2$ is irreducible, F is either surjective or zero. Taking these statements together, we arrive at Schur’s Lemma:
+
+\begin{lemma}[Schur's lemma 1]
+    An intertwiner between two irreducible representations is either
+    an isomorphism, in which case the representations are equivalent,
+    or zero
+\end{lemma}
+
+An important special case is the one where $D_1 = D_2$. In that case,
+we see that $F$ is essentially unique. More precisely, we have the
+following theorem, also often called Schur’s Lemma:
+\begin{lemma}[Schur's lemma 2]
+    If $D$ is an irreducible finite-dimensional representation on a complex
+vector space and there is an endomorphism $F$ of $V$ which satisfies 
+\begin{equation}
+    FD(g) = D(g) F
+\end{equation}
+for all $g\in G$, then F is a multiple of the identity, $F = \lambda
+\id$
+\end{lemma}
+\begin{proof}
+    Note that $F$ has at least one eigenvector $v$ with eigenvalue
+    $\lambda$. (This is where we need $V$ to be a complex vector
+    space: A real matrix might have complex eigenvalues, and hence no
+    real eigenvectors.) Clearly, $F-\lambda\id$ is also an
+    intertwiner, and it is not an isomorphism since it annihilates
+    $v$. Hence, by Schur’s Lemma, it vanishes, thus $F = \lambda\id$.
+\end{proof}
+
+(From the book \cite{book})
+\begin{thm}[Orthogonal Theorem]
+    For finite group $G$, let $D^i(G)$ and $D^j(G)$ be its two
+    irreducible, non-equivalent, and unitary representation. Then, as
+    a vector in group algebra, they have the following orthogonal
+    relationship:
+    \begin{equation}
+        \sum_{R\in G} D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R) =
+        \frac{g}{m_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+    \end{equation}
+    $g$ is the order of the group, and $m_j$ is the
+    dimension of representation $D^j(G)$.
+\end{thm}
+\begin{proof}
+    Let
+    \begin{equation}
+        Y_{\rho\lambda}^{\mu\nu} \equiv
+        \delta_{\rho\lambda}\delta_{\mu\nu}
+    \end{equation}
+    Then let
+    \begin{align*}
+        X^{\mu\nu} = \sum_{R\in G} D^i(R^{-1}) Y^{\mu\nu} D^j(R)
+    \end{align*}
+    One can find by direct calculation
+    \begin{align}
+        X^{\mu\nu}_{\rho\lambda}= \sum_{R\in G}
+        D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R)
+    \end{align}
+    And also through direct calculation, one finds
+    \begin{align*}
+        D^i (s) X^{\mu\nu} = X^{\mu\nu} D^j(s)
+    \end{align*}
+    for any $s\in G$. 
+    Then $X^{\mu\nu}$ is a interwiner. So the case for $i\neq j$ is
+    obvious. When $i=j$, we have:
+    $$ X = \lambda \id$$
+    Now we find the $\lambda$, i.e. the eigenvalue of $X^{\mu\nu}$.
+
+    Now since
+    \begin{align*}
+        X^{\mu\nu}_{\rho\lambda} = \lambda^{\mu\nu}
+        \delta_{\rho\lambda}
+    \end{align*}
+    One can find two fact by direct calculation:
+    \begin{align*}
+        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = m_j \lambda^{\mu\nu} \\
+        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = g \delta^{\mu\nu}
+    \end{align*}
+    Hence $\lambda^{\mu\nu} = \frac{g}{m_j} \delta^{\mu\nu}$.
+\end{proof}
+\begin{remark}
+    For the first orthogonality $\delta_{ij}$, one actually do not
+    required that $D^i$ and $D^j$ is unitary.
+\end{remark}
+\begin{coro}
+    \begin{equation}
+        \sum_{j=1}^{l} m_j^2 \leq g
+    \end{equation}
+    % TODO
+\end{coro}
+\begin{coro}
+    \begin{equation}
+        \sum_{R\in G} \chi^{i*}(R)\chi^j(R) = g \delta_{ij}
+    \end{equation}
+\end{coro}
 \section{Anchor}
@@
 \begin{thebibliography}{1}
-    %\bibitem{book} 
     \bibitem{book} Zhongqi Ma, Group Theory in Physics
     \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
+    \bibitem{Ludeling} Lecture Notes for physics751: Group Theory (for
+    Physicists), by C Ludeling.
+    \href{http://www.th.physik.uni-bonn.de/nilles/people/luedeling/grouptheory/data/grouptheorynotes.pdf}{Link}
 \end{thebibliography}

### 2016-10-31 Lecture note - Group Theory in Physics/group theory in physics.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

--- 2016-09-27 Group Theory in Physics/group theory in physics.tex
@@
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{mathrsfs}
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physics-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physicist-taper}
+
+\makenomenclature
 % Followings are for the special character: differential "d".
@@
 \newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage[unicode]{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-% A list of nomenclatures.
-\usepackage{nomencl}
-\makenomenclature
-
-% For highlighting
-\usepackage{xcolor,soul}
-\newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}
 
@@
 \label{sec:20160919}
-
-He first introduces several common examples of symmetries in our life and
-physics. Omitted, with one exception:
-
-He mentions that there is one more symmetry in the Hydrogen 
-Hamiltonian: the Laplace-Runge-Lenz symmetry. (So its symmetry 
-group is not just $SO(3)$, but two copies of $SO(3)$ that forms a $SO(4)$.
-And using the representation of $SO(4)$, the complete spectrum of
-Hydrogen Hamiltonian is solved. Hence this $SO(4)$ is the largest
-symmetry of Hydrogen Hamiltonian.
-
-    \subsection{Digression about Lenz vector}
-    \label{sec:Digression_about_Lenz_vector}
-    Since the class is too boring, I checked about the Lenz vector via
-    Google and found this Math.SE question \cite{math.se_1_lenz_vector}
-
-    The first answer to that post is:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        1) \textbf{Problem}. The \href{http://en.wikipedia.org/wiki/Kepler_problem}{Kepler Problem} has Hamiltonian
-
-        $$ H~:=~ \frac{p^2}{2m}- \frac{k}{q},  $$
-
-        where $m$ is the 2-body reduced mass. The [Laplace–Runge–Lenz vector](http://en.wikipedia.org/wiki/Laplace%E2%80%93Runge%E2%80%93Lenz_vector) is (up to an irrelevant normalization)
-
-        $$ A^j ~:=~a^j  + km\frac{q^j}{q}, \qquad a^j~:=~({\bf L} \times {\bf p})^j~=~{\bf q}\cdot{\bf p}~p^j- p^2~q^j,\qquad {\bf L}~:=~ {\bf q} \times {\bf p}.$$
-
-        2) \textbf{Action}. The Hamiltonian Lagrangian is
-
-        $$  L_H~:=~ \dot{\bf q}\cdot{\bf p} - H, $$
-
-        and the action is
-
-        $$ S[{\bf q},{\bf p}]~=~ \int {\rm d}t~L_H .$$
-
-        The non-zero fundamental canonical Poisson brackets are
-
-        $$ \{ q^i , p^j\}~=~ \delta^{ij}. $$
-
-        3) \textbf{Inverse Noether's Theorem}. Quite generally in the Hamiltonian formulation, given a constant of motion $Q$, then the infinitesimal variation
-
-        $$\delta~=~ \varepsilon \{Q,\cdot\}$$
-
-        is a global off-shell symmetry of the action $S$ (modulo boundary terms).
-Here $\varepsilon$ is an infinitesimal global parameter, and $X_Q=\{Q,\cdot\}$ is a Hamiltonian vector field with Hamiltonian generator $Q$.
-The full Noether current is (minus) $Q$, see e.g.
-my answer to [this question](http://physics.stackexchange.com/q/8626/2451).
-\hl{(The words \textbf{on-shell}.
-and \textbf{off-shell}.
-refer to whether the equations of motion are satisfied or not.)}
-
-        4) \textbf{Variation}.
-Let us check that the three Laplace–Runge–Lenz components $A^j$ are Hamiltonian generators of three continuous global off-shell symmetries of the action $S$.
-In detail, the infinitesimal variations $\delta= \varepsilon_j \{A^j,\cdot\}$ read
-
-        $$ \delta  q^i ~=~  \varepsilon_j  \{A^j,q^i\}   , \qquad 
-         \{A^j,q^i\} ~ =~ 2 p^i q^j - q^i p^j - {\bf q}\cdot{\bf p}~\delta^{ij}, $$
-        $$ \delta  p^i ~=~  \varepsilon_j  \{A^j,p^i\}   , \qquad  
-        \{A^j,p^i\}~ =~ p^i p^j - p^2~\delta^{ij} +km\left(\frac{\delta^{ij}}{q}- \frac{q^i q^j}{q^3}\right), $$
-        $$ \delta  t ~=~0,$$
-
-        where $\varepsilon_j$ are three infinitesimal parameters.
-
-        5) Notice for later that
-
-        $$ {\bf q}\cdot\delta {\bf q}~=~\varepsilon_j({\bf q}\cdot{\bf p}~q^j - q^2~p^j),  $$
-
-        $$ {\bf p}\cdot\delta {\bf p}
-        ~=~\varepsilon_j km(\frac{p^j}{q}-\frac{{\bf q}\cdot{\bf p}~q^j}{q^3})~=~- \frac{km}{q^3}{\bf q}\cdot\delta {\bf q},  $$
-
-        $$ {\bf q}\cdot\delta {\bf p}~=~\varepsilon_j({\bf q}\cdot{\bf p}~p^j - p^2~q^j )~=~\varepsilon_j a^j,  $$
-
-        $$ {\bf p}\cdot\delta {\bf q}~=~2\varepsilon_j( p^2~q^j - {\bf q}\cdot{\bf p}~p^j)~=~-2\varepsilon_j a^j~.  $$
-
-        6) The Hamiltonian is invariant
-
-        $$ \delta  H ~=~ \frac{1}{m}{\bf p}\cdot\delta {\bf p} + \frac{k}{q^3}{\bf q}\cdot\delta {\bf q}~=~0, $$
-
-        showing that the Laplace–Runge–Lenz vector $A^j$ is classically a constant of motion
-
-        $$\frac{dA^j}{dt} ~\approx~ \{ A^j, H\}+\frac{\partial A^j}{\partial t} ~=~  0.$$
-
-        (We will use the $\approx$ sign to stress that an equation is an on-shell equation.)
-
-        7) The variation of the Hamiltonian Lagrangian $L_H$ is a total time derivative
-
-        $$ \delta L_H~=~ \delta  (\dot{\bf q}\cdot{\bf p})~=~ \dot{\bf q}\cdot\delta {\bf p} - \dot{\bf p}\cdot\delta {\bf q} + \frac{d({\bf p}\cdot\delta {\bf q})}{dt} $$
-        $$  =~ \varepsilon_j\left( \dot{\bf q}\cdot{\bf p}~p^j - p^2~\dot{q}^j +  km\left( \frac{\dot{q}^j}{q} -  \frac{{\bf q} \cdot \dot{\bf q}~q^j}{q^3}\right)\right)    $$
-        $$- \varepsilon_j\left(2 \dot{\bf p}\cdot{\bf p}~q^j - \dot{\bf p}\cdot{\bf q}~p^j- {\bf p}\cdot{\bf q}~\dot{p}^j  \right) - 2\varepsilon_j\frac{da^j}{dt}$$
-        $$ =~\varepsilon_j\frac{df^j}{dt}, \qquad f^j ~:=~ A^j-2a^j, $$
-
-        and hence the action $S$ is invariant off-shell up to boundary terms.
-
-        8) \textbf{Noether current}. The bare \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether current} $j^k$ is
-
-        $$j^k~:=~ \frac{\partial L_H}{\partial \dot{q}^i}  \{A^k,q^i\}+\frac{\partial L_H}{\partial \dot{p}^i}  \{A^k,p^i\}
-        ~=~ p^i\{A^k,q^i\}~=~ -2a^k. $$
-
-        The full Noether current $J^k$ (which takes the total time-derivative into account) becomes (minus) the Laplace–Runge–Lenz vector
-
-        $$ J^k~:=~j^k-f^k~=~ -2a^k-(A^k-2a^k)~=~ -A^k.$$
-
-        $J^k$ is conserved on-shell
-
-        $$\frac{dJ^k}{dt} ~\approx~  0,$$
-
-        due to \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether's first Theorem}. Here $k$ is an index that labels the three symmetries.
-    \end{quote}
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    However, I don't really understand the content inside. I asked professor
-    Ye whether we can find some physics about this conserved quantity, and
-    he answered with no.
-
-    The next answer is also interesting:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        While Kepler second law is simply a statement of the conservation of angular momentum (and as such it holds for all systems described by central forces), \hl{the first and the third laws are special and are linked with the unique form of the newtonian potential $-k/r$.} In particular, \hl{Bertrand theorem assures that *only* the newtonian potential and the harmonic potential $kr^2$ give rise to closed orbits (no precession).} It is natural to think that this must be due to some kind of symmetry of the problem.
-In fact, the particular symmetry of the newtonian potential is described exactly by the conservation of the RL vector (\hl{it can be shown that the RL vector is conserved iff the potential is central and newtonian}).
-This, in turn, is due to a more general symmetry: \hl{if conservation of angular momentum is linked to the group of special orthogonal transformations in 3-dimensional space $SO(3)$, conservation of the RL vector must be linked to a 6-dimensional group of symmetries}, since in this case there are apparently six conserved quantities (3 components of $L$ and 3 components of $\mathcal A$).
-In the case of bound orbits, this group is $SO(4)$, the group of rotations in 4-dimensional space.
-
-        Just to fix the notation, the RL vector is:
-
-        \begin{equation} \mathcal{A}=\textbf{p}\times\textbf{L}-\frac{km}{r}\textbf{x} \end{equation}
-
-        Calculate its total derivative:
-
-        \begin{equation}\frac{d\mathcal{A}}{dt}=-\nabla U\times(\textbf{x}\times\textbf{p})+\textbf{p}\times\frac{d\textbf{L}}{dt}-\frac{k\textbf{p}}{r}+\frac{km(\textbf{p}\cdot \textbf{x})}{r^3}\textbf{x} \end{equation}
-
-        Make use of Levi-Civita symbol to develop the cross terms:
-
-        \begin{equation}\epsilon_{sjk}\epsilon_{sil}=\delta_{ji}\delta_{kl}-\delta_{jl}\delta_{ki}   \end{equation}
-
-        Finally:
-
-        \begin{equation}
-        \frac{d\mathcal{A}}{dt}=\left(\textbf{x}\cdot\nabla U-\frac{k}{r}\right)\textbf{p}+\left[(\textbf{p}\cdot\textbf{x})\frac{k}{r^3}-2\textbf{p}\cdot\nabla U\right]\textbf{x}+(\textbf{p}\cdot\textbf{x})\nabla U
-        \end{equation}
-
-        Now, if the potential $U=U(r)$ is central:
-
-        \begin{equation}
-        (\nabla U)_j=\frac{\partial U}{\partial x_j}=\frac{dU}{dr}\frac{\partial r}{\partial x_j}=\frac{dU}{dr}\frac{x_j}{r}
-        \end{equation}
-
-        so
-
-        \begin{equation} \nabla U=\frac{dU}{dr}\frac{\textbf{x}}{r}\end{equation}
-
-        Substituting back:
-
-        \begin{equation}
-            \hlMath{\frac{d\mathcal A}{dt}=\frac{1}{r}\left(\frac{dU}{dr}-\frac{k}{r^2}\right)[r^2\textbf{p}-(\textbf{x}\cdot\textbf{p})\textbf{x}]}
-        \end{equation}
-
-        Now, you see that if $U$ has \textit{exactly} the newtonian form then the first parenthesis is zero and so the RL vector is conserved.
-
-        Maybe there's some slicker way to see it (Poisson brackets?), but this works anyway.
-    \end{quote}
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    % TODO Study in detail about this example.
-
-    \subsection{Coming back to the course}
-
-After mentioning the Poinc\'{a}re group, he produces to review some
-concepts about linear algebra:
-\begin{enumerate}
-    \item The axioms of linear space, using quantum mechanics
-        as basic example (Omitted).
-    \item Some common concepts of linear space: linear-independence,
-        subspace, direct sum, linear operators, its matrix representation. (Omitted)
-    \item Introducing the complete antisymmetric tensor 
-        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
-        \begin{align}
-            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
-            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
-            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
-            \\
-            &= \sum_{p_1,\cdots,p_n} 
-            \epsilon_{p_1,\cdots,p_n} 
-                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
-                \\
-            \epsilon_{ab}\epsilon_{rs} &=
-                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
-                \\
-            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
-                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
-        \end{align}
-    \item Some special matrices.
-    \item Fact: If $R\Gamma = \Gamma R$, and 
-        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
-        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
-        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
-        On the other hand, if $R_{\mu\nu}\neq 0$, then
-        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
-        This is obviously from:
-        \begin{align*}
-            \sum_j R^{i}_{j}\Gamma^{j}_{k}=\sum_j\Gamma^{i}_{j} R^{j}_k
-            \Longrightarrow
-            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
-        \end{align*}
-        where the first is automatically summed, and the second is not.
-
-    \item A linear functional is closed w.r.t. a vector space. (Omitted)
-    \item ... then this linear functional can be expressed as a
-        matrix w.r.t to a basis of this vector space. (Omitted)
-    \item Invariant subspace. (Omitted)
-    \item Transformation of basis. (Omitted)
-    \item Direct sum of operators:
-
-        Let vector spaces $L=L_1\oplus L_2$, with $L=\braket{e_i}$,
-        $L_1=\braket{e'_1,\cdots e'_n}$,$L_2=\braket{e'_{n+1},\cdots,e'_m}$,
-        $e'_\nu=\sum_\mu e_\mu  S_{\mu\nu}$. 
-        Assume that $L_1,L_2$ are invariant w.r.t $A$, an linear operator. If:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{m} e'_\nu R'_{\nu\mu}
-        \end{align}
-        we have obviously:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{n} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{1\cdots n\}
-                \\
-            A e'_\mu = \sum_{\nu=n}^{m} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{n\cdots m\}
-        \end{align}
-        i.e., $A$'s matrix representation has two diagonal blocks.
-        Using this fact, $A$ after a linear transformation (by $S$),
-        could be written as $R_1\oplus R_2$, where the meaning of $R_1/R_2$
-        is obvious.
-    \item Eigenvalues and the characteristic equation. (Omitted)
-        Some properties:
-        \begin{enumerate}
-            \item Trace = $\sum_i \lambda_i$
-            \item Determinant = $\prod_i \lambda_i$
-            \item Geometric multiplicity $\leq$ Algebraic multiplicity, or
-                $$\mathrm{dim}V_{\lambda_1} \leq n_1$$.
-        \end{enumerate}
-    \item Inner product and orthonormal basis. (Omitted) Here we define
-        matrix $\Omega$ to be, when a basis $\{e_i\}$is given:
-        \begin{defi}[]
-        \nomenclature{}{\nomrefpage.}
-            \begin{align}
-                \Omega_{ij} \equiv \braket{e_i,e_j}
-            \end{align}
-        \end{defi}
-    \item Adjoint operator:
-
-        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
-        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
-        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
-        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
-        $(R^T)^* \Omega = \Omega A$, so:
-        \begin{align}
-            R = \Omega^{-1} A^\dagger \Omega
-        \end{align}
-        where we have used the fact that $\Omega^\dagger=\Omega$.
-
-        Note that $(R^{k}_j)^* \Omega_{ki}$ is not $\Omega^T R^*$.
-        (Be careful and you will find out why.)
-
-        This is very different from my previous naive concept
-        when $\Omega$ is not identity matrix, i.e. when the basis
-        is not orthonormal.
-\end{enumerate}
+\input{sections/20160919}
 
@@
 \label{sec:20160926}
+\input{sections/20160926}
 
-He first introduces some important matrices:
+\section{20161010}
+\label{sec:20161010}
+\input{sections/20161010}
 
-\paragraph{Unitary matrix} Eigenvalues of Unitary matrices has modulus $1$,
-i.e. $|\lambda|=1$. This can be proved directly. Also, Unitary matrices are unitarily diagonalizable. This is a result of the following Spectral Theorem:
-\begin{thm}[Spectral Theorem]
-    A matrix $A$, which is normal (i.e. $A^\dagger A= AA^\dagger$), if and only if it is unitarily diagonalizable.
-\end{thm}
-\begin{proof}
-    If $A$ is normal, then by Schur decomposition, we can write
-    $A=UTU^\dagger$, here $U$ is unitary and $T$ is upper-triangular. 
-    Using the condition of being normal, one can show directly that $T$ 
-    is in fact also normal. Now we show that any triangular matrix that 
-    is normal must be diagonal. Observe that we have 
-    $\braket{e_i,T^\dagger T e_i}=\braket{e_i,TT^\dagger e_i}$, 
-    i.e. $\braket{T^\dagger e_i, T^\dagger e_i}=\braket{T e_i, T e_i}$. 
-    This is sayin g that the norm of the first column of $A^\dagger$ 
-    is equal to the norm of the first column of $A$. Obviously 
-    $A$ has to be diagonal.
+\section{Skipped Two lectures}
+\input{sections/Skipped-Two-Lectures}
 
-    The converse is obvious.
-\end{proof}
-
-Also, unitary matrix's eigenvector corresponding to different eigenvalues 
-are orthogonal. This is a direct result of fact mentioned above.
-
-\paragraph{Hermitian matrices} They have real eigenvalues and orthogonal
-eigenvectors (proof omitted). Also, if $\text{det}(R^\dagger R)\neq 0$,
-then $R^\dagger R >0$, i.e. it is positive-definite.
-
-\textbf{This is wong:} An example is that
-the matrix $\Omega$ introduced in the previous lecture has
-$\text{det}(\Omega^\dagger \Omega)=\text{det}(\Omega)$, hence
-$\text{det}(\Omega)=1$ (it cannot be $0$), hence it is positive definite.
-
-\textbf{Actually} 
-$\text{det}(\Omega^\dagger \Omega)\neq\text{det}(\Omega)$, because
-\begin{align}
-    \sum_\rho \ket{e_\rho}\bra{e_\rho} \neq 1 \text{(unless the basis is
-        orthonormal)}
-    % TODO think about this in depth
-\end{align}
-Therefore we need anthoer argument for $\Omega$ being positive-definite.
-It is provided in page 11 of \cite{book}.
-
-\paragraph{Orthogonal matrix} For an orthogonal matrix over $\mathbb{C}$,
-it is quite troublesome. For example, if $Ra=\lambda a$ and
-$\lambda \neq \pm 1$, then we have $a^T a=0$, which is quite bad because
-this force $a$ to have complex components.
-
-\paragraph{Orthogonal matrix over $\mathbb{R}$} In this case, we have
-similar result. But it is easy to show that for an orthogonal matrix
-$R$ having only real elements, then its eigenvalues $\lambda= \pm 1$.
-
-Then he proceeds to direct product.
-\paragraph{Direct product} and also the Kronecker Product of two
-matrices. Properties (let $T=R\otimes S$):
-\begin{enumerate}
-    \item $\mathrm{dim}T = \mathrm{dim}R \times \mathrm{dim}S$
-    \item $\mathrm{tr}(T)=\mathrm{tr}(R)\mathrm{tr}(S)$
-    \item $\otimes$ commutes with the operation of inverse, transpose,
-        and transpose conjugation.
-    \item \begin{align}
-            \frac{d}{d\alpha} (R(\alpha)\otimes S(\alpha)) =
-            R'(\alpha)\otimes S(\alpha) + R(\alpha)\otimes S'(\alpha)
-    \end{align}
-    \item when the dimentions are the same:
-        \begin{enumerate}
-            \item 
-            $(R_1\otimes S_1)(R_2\otimes S_2) = (R_1R_2)\otimes (S_1S_2)$
-        \end{enumerate}
-\end{enumerate}
-
-Finally we arrived in the group theory.
-\paragraph{Symmetry examples} Dipole transition. 
-$\braket{\phi_f|\hat{P}|\phi_i}$, must happen when the parity of $\phi_i$
-and $\phi_f$ is of opposite parity. (pp.18 of \cite{book})
-
-\paragraph{Group}
-\begin{defi}[Group]
-\nomenclature{Group}{\nomrefpage.}
-    Omitted.
-\end{defi}
-Some basic properties (Omitted).
-\begin{defi}[Abel Group]
-\nomenclature{Abel Group}{\nomrefpage.}
-    Omitted.
-\end{defi}
-\begin{defi}[Cardinality of group $\# A$]
-\nomenclature{Cardinality of group $#$}{\nomrefpage.}
-    Omitted.
-\end{defi}
-
-\paragraph{Multiplication table}
-
-Facts: group of order $1,2,$ and $3$ are unique up to an isomorphism.
-
-\begin{defi}[Cyclic group, generators]
-\nomenclature{Cyclic group, generators}{\nomrefpage.}
-    Omitted.
-\end{defi}
-
-\begin{defi}[$C_N,\bar{C}_N$]
-\nomenclature{$C_N,\bar{C}_N$}{\nomrefpage.}
-    $\bar{C}_N=C_N*\sigma$
-\end{defi}
+\section{20161031}
+\label{sec:20161031}
+\input{sections/20161031}
 \section{Anchor}
 \label{sec:Anchor}
-
 \begin{thebibliography}{1}
-    %\bibitem{book} 
     \bibitem{book} Zhongqi Ma, Group Theory in Physics
     \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
+    \bibitem{Ludeling} Lecture Notes for physics751: Group Theory (for
+    Physicists), by C Ludeling.
+    \href{http://www.th.physik.uni-bonn.de/nilles/people/luedeling/grouptheory/data/grouptheorynotes.pdf}{Link}
 \end{thebibliography}

### 2016-10-31 Lecture note - Group Theory in Physics/sections/20160919.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

--- 2016-09-19 Group Theory in Physics/group theory in physics.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-% Followings are for the special character: differential "d".
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage[unicode]{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-% A list of nomenclatures.
-\usepackage{nomencl}
-\makenomenclature
-
-% For highlighting
-\usepackage{xcolor,soul}
-\newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}
-
-\title{Group Theory in Physics (Course Note)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-This is our course note for the course about group theoy, with its
-application in physics.
-}
-\tableofcontents
-\begin{enumerate}
-    \item Combine group theory with you research.
-    \item Mid-term and final.
-    \item No homework, cause it is already graduate level.
-    \item Professor Fei Ye. (Phone: 88018229, 228 in Research building 2), 
-        T.A. Zhe Zhang. (110 Research building 2).
-\end{enumerate}
-
-\section{20160919}
-\label{sec:20160919}
-
 He first introduces several common examples of symmetries in our life and
@@
 \end{enumerate}
-
-\section{Anchor}
-\label{sec:Anchor}
-
-\begin{thebibliography}{1}
-    %\bibitem{book} 
-    \bibitem{book_1} Zhongqi Ma, Group Theory in Physics
-    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
-\end{thebibliography}
-\printnomenclature
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-\end{document}

### 2016-10-31 Lecture note - Group Theory in Physics/sections/20160926.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

--- 2016-09-27 Group Theory in Physics/group theory in physics.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+He first introduces some important matrices:
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-% Followings are for the special character: differential "d".
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage[unicode]{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-% A list of nomenclatures.
-\usepackage{nomencl}
-\makenomenclature
-
-% For highlighting
-\usepackage{xcolor,soul}
-\newcommand{\hlMath}[1]{\colorbox{yellow!80}{$\displaystyle#1$}}
-
-\title{Group Theory in Physics (Course Note)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-This is our course note for the course about group theoy, with its
-application in physics.
-}
-\tableofcontents
-\begin{enumerate}
-    \item Combine group theory with you research.
-    \item Mid-term and final.
-    \item No homework, cause it is already graduate level.
-    \item Professor Fei Ye. (Phone: 88018229, 228 in Research building 2), 
-        T.A. Zhe Zhang. (110 Research building 2).
-\end{enumerate}
-
-\section{20160919}
-\label{sec:20160919}
-
-He first introduces several common examples of symmetries in our life and
-physics. Omitted, with one exception:
-
-He mentions that there is one more symmetry in the Hydrogen 
-Hamiltonian: the Laplace-Runge-Lenz symmetry. (So its symmetry 
-group is not just $SO(3)$, but two copies of $SO(3)$ that forms a $SO(4)$.
-And using the representation of $SO(4)$, the complete spectrum of
-Hydrogen Hamiltonian is solved. Hence this $SO(4)$ is the largest
-symmetry of Hydrogen Hamiltonian.
-
-    \subsection{Digression about Lenz vector}
-    \label{sec:Digression_about_Lenz_vector}
-    Since the class is too boring, I checked about the Lenz vector via
-    Google and found this Math.SE question \cite{math.se_1_lenz_vector}
-
-    The first answer to that post is:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        1) \textbf{Problem}. The \href{http://en.wikipedia.org/wiki/Kepler_problem}{Kepler Problem} has Hamiltonian
-
-        $$ H~:=~ \frac{p^2}{2m}- \frac{k}{q},  $$
-
-        where $m$ is the 2-body reduced mass. The [Laplace–Runge–Lenz vector](http://en.wikipedia.org/wiki/Laplace%E2%80%93Runge%E2%80%93Lenz_vector) is (up to an irrelevant normalization)
-
-        $$ A^j ~:=~a^j  + km\frac{q^j}{q}, \qquad a^j~:=~({\bf L} \times {\bf p})^j~=~{\bf q}\cdot{\bf p}~p^j- p^2~q^j,\qquad {\bf L}~:=~ {\bf q} \times {\bf p}.$$
-
-        2) \textbf{Action}. The Hamiltonian Lagrangian is
-
-        $$  L_H~:=~ \dot{\bf q}\cdot{\bf p} - H, $$
-
-        and the action is
-
-        $$ S[{\bf q},{\bf p}]~=~ \int {\rm d}t~L_H .$$
-
-        The non-zero fundamental canonical Poisson brackets are
-
-        $$ \{ q^i , p^j\}~=~ \delta^{ij}. $$
-
-        3) \textbf{Inverse Noether's Theorem}. Quite generally in the Hamiltonian formulation, given a constant of motion $Q$, then the infinitesimal variation
-
-        $$\delta~=~ \varepsilon \{Q,\cdot\}$$
-
-        is a global off-shell symmetry of the action $S$ (modulo boundary terms).
-Here $\varepsilon$ is an infinitesimal global parameter, and $X_Q=\{Q,\cdot\}$ is a Hamiltonian vector field with Hamiltonian generator $Q$.
-The full Noether current is (minus) $Q$, see e.g.
-my answer to [this question](http://physics.stackexchange.com/q/8626/2451).
-\hl{(The words \textbf{on-shell}.
-and \textbf{off-shell}.
-refer to whether the equations of motion are satisfied or not.)}
-
-        4) \textbf{Variation}.
-Let us check that the three Laplace–Runge–Lenz components $A^j$ are Hamiltonian generators of three continuous global off-shell symmetries of the action $S$.
-In detail, the infinitesimal variations $\delta= \varepsilon_j \{A^j,\cdot\}$ read
-
-        $$ \delta  q^i ~=~  \varepsilon_j  \{A^j,q^i\}   , \qquad 
-         \{A^j,q^i\} ~ =~ 2 p^i q^j - q^i p^j - {\bf q}\cdot{\bf p}~\delta^{ij}, $$
-        $$ \delta  p^i ~=~  \varepsilon_j  \{A^j,p^i\}   , \qquad  
-        \{A^j,p^i\}~ =~ p^i p^j - p^2~\delta^{ij} +km\left(\frac{\delta^{ij}}{q}- \frac{q^i q^j}{q^3}\right), $$
-        $$ \delta  t ~=~0,$$
-
-        where $\varepsilon_j$ are three infinitesimal parameters.
-
-        5) Notice for later that
-
-        $$ {\bf q}\cdot\delta {\bf q}~=~\varepsilon_j({\bf q}\cdot{\bf p}~q^j - q^2~p^j),  $$
-
-        $$ {\bf p}\cdot\delta {\bf p}
-        ~=~\varepsilon_j km(\frac{p^j}{q}-\frac{{\bf q}\cdot{\bf p}~q^j}{q^3})~=~- \frac{km}{q^3}{\bf q}\cdot\delta {\bf q},  $$
-
-        $$ {\bf q}\cdot\delta {\bf p}~=~\varepsilon_j({\bf q}\cdot{\bf p}~p^j - p^2~q^j )~=~\varepsilon_j a^j,  $$
-
-        $$ {\bf p}\cdot\delta {\bf q}~=~2\varepsilon_j( p^2~q^j - {\bf q}\cdot{\bf p}~p^j)~=~-2\varepsilon_j a^j~.  $$
-
-        6) The Hamiltonian is invariant
-
-        $$ \delta  H ~=~ \frac{1}{m}{\bf p}\cdot\delta {\bf p} + \frac{k}{q^3}{\bf q}\cdot\delta {\bf q}~=~0, $$
-
-        showing that the Laplace–Runge–Lenz vector $A^j$ is classically a constant of motion
-
-        $$\frac{dA^j}{dt} ~\approx~ \{ A^j, H\}+\frac{\partial A^j}{\partial t} ~=~  0.$$
-
-        (We will use the $\approx$ sign to stress that an equation is an on-shell equation.)
-
-        7) The variation of the Hamiltonian Lagrangian $L_H$ is a total time derivative
-
-        $$ \delta L_H~=~ \delta  (\dot{\bf q}\cdot{\bf p})~=~ \dot{\bf q}\cdot\delta {\bf p} - \dot{\bf p}\cdot\delta {\bf q} + \frac{d({\bf p}\cdot\delta {\bf q})}{dt} $$
-        $$  =~ \varepsilon_j\left( \dot{\bf q}\cdot{\bf p}~p^j - p^2~\dot{q}^j +  km\left( \frac{\dot{q}^j}{q} -  \frac{{\bf q} \cdot \dot{\bf q}~q^j}{q^3}\right)\right)    $$
-        $$- \varepsilon_j\left(2 \dot{\bf p}\cdot{\bf p}~q^j - \dot{\bf p}\cdot{\bf q}~p^j- {\bf p}\cdot{\bf q}~\dot{p}^j  \right) - 2\varepsilon_j\frac{da^j}{dt}$$
-        $$ =~\varepsilon_j\frac{df^j}{dt}, \qquad f^j ~:=~ A^j-2a^j, $$
-
-        and hence the action $S$ is invariant off-shell up to boundary terms.
-
-        8) \textbf{Noether current}. The bare \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether current} $j^k$ is
-
-        $$j^k~:=~ \frac{\partial L_H}{\partial \dot{q}^i}  \{A^k,q^i\}+\frac{\partial L_H}{\partial \dot{p}^i}  \{A^k,p^i\}
-        ~=~ p^i\{A^k,q^i\}~=~ -2a^k. $$
-
-        The full Noether current $J^k$ (which takes the total time-derivative into account) becomes (minus) the Laplace–Runge–Lenz vector
-
-        $$ J^k~:=~j^k-f^k~=~ -2a^k-(A^k-2a^k)~=~ -A^k.$$
-
-        $J^k$ is conserved on-shell
-
-        $$\frac{dJ^k}{dt} ~\approx~  0,$$
-
-        due to \href{http://en.wikipedia.org/wiki/Noether%27s_theorem}{Noether's first Theorem}. Here $k$ is an index that labels the three symmetries.
-    \end{quote}
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    However, I don't really understand the content inside. I asked professor
-    Ye whether we can find some physics about this conserved quantity, and
-    he answered with no.
-
-    The next answer is also interesting:
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \begin{quote}
-        While Kepler second law is simply a statement of the conservation of angular momentum (and as such it holds for all systems described by central forces), \hl{the first and the third laws are special and are linked with the unique form of the newtonian potential $-k/r$.} In particular, \hl{Bertrand theorem assures that *only* the newtonian potential and the harmonic potential $kr^2$ give rise to closed orbits (no precession).} It is natural to think that this must be due to some kind of symmetry of the problem.
-In fact, the particular symmetry of the newtonian potential is described exactly by the conservation of the RL vector (\hl{it can be shown that the RL vector is conserved iff the potential is central and newtonian}).
-This, in turn, is due to a more general symmetry: \hl{if conservation of angular momentum is linked to the group of special orthogonal transformations in 3-dimensional space $SO(3)$, conservation of the RL vector must be linked to a 6-dimensional group of symmetries}, since in this case there are apparently six conserved quantities (3 components of $L$ and 3 components of $\mathcal A$).
-In the case of bound orbits, this group is $SO(4)$, the group of rotations in 4-dimensional space.
-
-        Just to fix the notation, the RL vector is:
-
-        \begin{equation} \mathcal{A}=\textbf{p}\times\textbf{L}-\frac{km}{r}\textbf{x} \end{equation}
-
-        Calculate its total derivative:
-
-        \begin{equation}\frac{d\mathcal{A}}{dt}=-\nabla U\times(\textbf{x}\times\textbf{p})+\textbf{p}\times\frac{d\textbf{L}}{dt}-\frac{k\textbf{p}}{r}+\frac{km(\textbf{p}\cdot \textbf{x})}{r^3}\textbf{x} \end{equation}
-
-        Make use of Levi-Civita symbol to develop the cross terms:
-
-        \begin{equation}\epsilon_{sjk}\epsilon_{sil}=\delta_{ji}\delta_{kl}-\delta_{jl}\delta_{ki}   \end{equation}
-
-        Finally:
-
-        \begin{equation}
-        \frac{d\mathcal{A}}{dt}=\left(\textbf{x}\cdot\nabla U-\frac{k}{r}\right)\textbf{p}+\left[(\textbf{p}\cdot\textbf{x})\frac{k}{r^3}-2\textbf{p}\cdot\nabla U\right]\textbf{x}+(\textbf{p}\cdot\textbf{x})\nabla U
-        \end{equation}
-
-        Now, if the potential $U=U(r)$ is central:
-
-        \begin{equation}
-        (\nabla U)_j=\frac{\partial U}{\partial x_j}=\frac{dU}{dr}\frac{\partial r}{\partial x_j}=\frac{dU}{dr}\frac{x_j}{r}
-        \end{equation}
-
-        so
-
-        \begin{equation} \nabla U=\frac{dU}{dr}\frac{\textbf{x}}{r}\end{equation}
-
-        Substituting back:
-
-        \begin{equation}
-            \hlMath{\frac{d\mathcal A}{dt}=\frac{1}{r}\left(\frac{dU}{dr}-\frac{k}{r^2}\right)[r^2\textbf{p}-(\textbf{x}\cdot\textbf{p})\textbf{x}]}
-        \end{equation}
-
-        Now, you see that if $U$ has \textit{exactly} the newtonian form then the first parenthesis is zero and so the RL vector is conserved.
-
-        Maybe there's some slicker way to see it (Poisson brackets?), but this works anyway.
-    \end{quote}
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    % TODO Study in detail about this example.
-
-    \subsection{Coming back to the course}
-
-After mentioning the Poinc\'{a}re group, he produces to review some
-concepts about linear algebra:
-\begin{enumerate}
-    \item The axioms of linear space, using quantum mechanics
-        as basic example (Omitted).
-    \item Some common concepts of linear space: linear-independence,
-        subspace, direct sum, linear operators, its matrix representation. (Omitted)
-    \item Introducing the complete antisymmetric tensor 
-        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
-        \begin{align}
-            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
-            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
-            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
-            \\
-            &= \sum_{p_1,\cdots,p_n} 
-            \epsilon_{p_1,\cdots,p_n} 
-                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
-                \\
-            \epsilon_{ab}\epsilon_{rs} &=
-                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
-                \\
-            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
-                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
-        \end{align}
-    \item Some special matrices.
-    \item Fact: If $R\Gamma = \Gamma R$, and 
-        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
-        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
-        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
-        On the other hand, if $R_{\mu\nu}\neq 0$, then
-        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
-        This is obviously from:
-        \begin{align*}
-            \sum_j R^{i}_{j}\Gamma^{j}_{k}=\sum_j\Gamma^{i}_{j} R^{j}_k
-            \Longrightarrow
-            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
-        \end{align*}
-        where the first is automatically summed, and the second is not.
-
-    \item A linear functional is closed w.r.t. a vector space. (Omitted)
-    \item ... then this linear functional can be expressed as a
-        matrix w.r.t to a basis of this vector space. (Omitted)
-    \item Invariant subspace. (Omitted)
-    \item Transformation of basis. (Omitted)
-    \item Direct sum of operators:
-
-        Let vector spaces $L=L_1\oplus L_2$, with $L=\braket{e_i}$,
-        $L_1=\braket{e'_1,\cdots e'_n}$,$L_2=\braket{e'_{n+1},\cdots,e'_m}$,
-        $e'_\nu=\sum_\mu e_\mu  S_{\mu\nu}$. 
-        Assume that $L_1,L_2$ are invariant w.r.t $A$, an linear operator. If:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{m} e'_\nu R'_{\nu\mu}
-        \end{align}
-        we have obviously:
-        \begin{align}
-            A e'_\mu = \sum_{\nu=1}^{n} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{1\cdots n\}
-                \\
-            A e'_\mu = \sum_{\nu=n}^{m} e'_\nu R'_{\nu\mu} \text{for }
-                \mu\in \{n\cdots m\}
-        \end{align}
-        i.e., $A$'s matrix representation has two diagonal blocks.
-        Using this fact, $A$ after a linear transformation (by $S$),
-        could be written as $R_1\oplus R_2$, where the meaning of $R_1/R_2$
-        is obvious.
-    \item Eigenvalues and the characteristic equation. (Omitted)
-        Some properties:
-        \begin{enumerate}
-            \item Trace = $\sum_i \lambda_i$
-            \item Determinant = $\prod_i \lambda_i$
-            \item Geometric multiplicity $\leq$ Algebraic multiplicity, or
-                $$\mathrm{dim}V_{\lambda_1} \leq n_1$$.
-        \end{enumerate}
-    \item Inner product and orthonormal basis. (Omitted) Here we define
-        matrix $\Omega$ to be, when a basis $\{e_i\}$is given:
-        \begin{defi}[]
-        \nomenclature{}{\nomrefpage.}
-            \begin{align}
-                \Omega_{ij} \equiv \braket{e_i,e_j}
-            \end{align}
-        \end{defi}
-    \item Adjoint operator:
-
-        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
-        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
-        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
-        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
-        $(R^T)^* \Omega = \Omega A$, so:
-        \begin{align}
-            R = \Omega^{-1} A^\dagger \Omega
-        \end{align}
-        where we have used the fact that $\Omega^\dagger=\Omega$.
-
-        Note that $(R^{k}_j)^* \Omega_{ki}$ is not $\Omega^T R^*$.
-        (Be careful and you will find out why.)
-
-        This is very different from my previous naive concept
-        when $\Omega$ is not identity matrix, i.e. when the basis
-        is not orthonormal.
-\end{enumerate}
-
-\section{20160926}
-\label{sec:20160926}
-
-He first introduces some important matrices:
+\subsection{Some Important Matrices}
+\label{sec:Some-Important-Matrices}
 
@@
 \begin{thm}[Spectral Theorem]
-    A matrix $A$, which is normal (i.e. $A^\dagger A= AA^\dagger$), if and only if it is unitarily diagonalizable.
+    One matrix $A$ is normal (i.e. $A^\dagger A= AA^\dagger$), if and only if it is unitarily diagonalizable.
 \end{thm}
@@
     i.e. $\braket{T^\dagger e_i, T^\dagger e_i}=\braket{T e_i, T e_i}$. 
-    This is sayin g that the norm of the first column of $A^\dagger$ 
+    This is saying that the norm of the first column of $A^\dagger$ 
     is equal to the norm of the first column of $A$. Obviously 
@@
 
+\subsection{Symmetry and Group}
+\label{sec:Symmetry-and-Group}
+
 Finally we arrived in the group theory.
@@
 \end{defi}
-\section{Anchor}
-\label{sec:Anchor}
-
-\begin{thebibliography}{1}
-    %\bibitem{book} 
-    \bibitem{book} Zhongqi Ma, Group Theory in Physics
-    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
-\end{thebibliography}
-\printnomenclature
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-\end{document}

### 2016-10-31 Lecture note - Group Theory in Physics/sections/20161010.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

\subsection{Common Concepts in Group}
\label{sec:Common-Concepts-in-Group}

Introducing to various groups:$S_4, V_4$, $D_3$, all omited.
(\textbf{pp.22-23 of \cite{book}})

$D_n$ group. See pp. 25-26 of the book \cite{book}.
Note that here the $n$ refers to the $n$-polygon, not that the group is
of order $n$. For the mathematicians, they might be comfortable with
$D_n$ means the dihedral group of order $n$, but is actually the group of
symmetries of $n/2$-polygon.

\begin{defi}[Subgroup]
\nomenclature{Subgroup}{\nomrefpage.}
    Omitted.
\end{defi}
\begin{fact}
    One only has to check the closeness for determining a subgroup, if it
    is of finite order.

    However, for group of infinite order, one has to check the existance
    of unit and inverse elements.
\end{fact}
Examples of subgroup (\textbf{pp.26 of \cite{book}})

Noteworth:$C_6$ has three copies of $D_2$, this can be intuitively 
guessed by the fact that a hexago has three rectanle in it.

\begin{defi}[Coset]
\nomenclature{Coset}{\nomrefpage.}
    Omitted.
\end{defi}
Properties of coset (omitted).

\begin{defi}[Index of subgroup]
\nomenclature{Index of subgroup}{\nomrefpage.}
    Omitted.
\end{defi}

\begin{prop}
    Two elements $R$ and $T$ belongs to the same coset $kH$, if and only
    if $R^{-1}T\in H$.
\end{prop}
\begin{proof}
    Omitted.
\end{proof}
\begin{defi}[Normal/Invariant subgroup]
\nomenclature{Normal/Invariant subgroup}{\nomrefpage.}
    A subgroupNormal/Invariant subgrouproup(also invariant), if and only
    if for any $x\in G$, we have $xH = Hx$.
\end{defi}
\begin{fact}
    If $H$ has index 2, then it must be normal/invariant. This is
    obvious.
\end{fact}
\begin{defi}[Quotient]
\nomenclature{Quotient}{\nomrefpage.}
    Omitted.
\end{defi}
Note that quotient group (a.k.a. factor group) is only defined for a normal subgroup.

\begin{ex}
    $D_3$ (Using the multiplication table). Omitted because it is too
    complex to be typed down here.
\end{ex}

\subsection{Conjugacy classes}
\label{sec:Conjugacy-classes}

\begin{defi}[Conjugate]
\nomenclature{Conjugate}{\nomrefpage.}
    If exists $S\in G$, s.t. $R' = S^{-1}RS$, then we say $R'$ is
    conjugate to $R$.
\end{defi}
see (\textbf{pp.28-30 of \cite{book}})
This is clearly an equivalence relationship. By this we can define
conjugate class, denoted by $C=\{R_1,\cdots\}$, then we have the
characterization $C = \{ s^{-1} R_i s|\forall s\in G\}$, for any
$R_i$. We then have the following facts (all are obvious):
\begin{fact}$ $

    \begin{enumerate}
        \item The unit class formed just by the unit element.
        \item The inverse class formed by just all the inverse element.
            $C^{-1} = \{ R_i^{-1}\}$. If $C=C^{-1}$, then $C$ is called
            self-inverse.
        \item The order of elements in a class is just the same.
        \item For $\forall T,S\in G$, $TS$ and $ST$ are conjugate to each
            other. This means that all elements symmetric on the
            multiplication table is conjugate to each other.
        \item For two elements $R$, $R'$ conjugate to each other, both
            can be expressed by the products of two elements in two
            different way. (Isn't this too obvious to mention.)
        \item Let $G$ be a rotation group. Suppose it has an axis of the
            order of $n$, with its operation denoted as $R$,, we can get
            a new axis by the following steps. (Supose we have another
            rotation $S$),

            \begin{enumerate}
                \item  $S^{-1}$, rotate $m$ back to $n$.
                \item  $R$, rotate about n around $2\pi/n$,
                \item  $S$ rotate $n$ to $m$
            \end{enumerate}

            Result: $S^{-1}RS$ rotate around a new axis $m$ about
            $2\pi/n$. So $R'=S^{-1}RS$ and $R$ is calle the equivalent
            axis.

            Also, if $m=-n$, then they are called polar axis to each
            other.

        \item $C_n$, which is an abel group, every element form a
            conjugate class by itself. Specifically, $e$ and $R^{n/2}$
            are self inverse, if $n$ is even.
    \end{enumerate}
\end{fact}
\begin{prop}
    \label{prop:20161010.conjugate_subgroup}
    For an invariant subgroup, then every conjugate element is also
    inside the same invariant subgroup. This shows that an invariant
    subgroup can be decomposed into a series of sum of conjugate classes.
\end{prop}
\begin{proof}
    If $R\in H$, then we show that $S^{-1}RS\in H$, this is obviously
    since it belongs to $S^{-1}HS$.
\end{proof}

\begin{ex}
    For $D_3: E,D,F,A,B,C$, their orders are respetively
    $1,3,3,2,2,2$. We have the following conjugate classes:
    \begin{enumerate}
        \item $\{ E\}$. Is self inverse.
        \item $\{ D,F\}$. $D$ is conjugate to $F$. We can see
            this physically by looking at rotation from the front
            or the below. This class is also self-inverse.
        \item $\{A,B,C\}$, is clearly a self-inverse conjugate
            class.
    \end{enumerate}
\end{ex}
\begin{ex}[$D_6$]
    Ramiliarize one with the formulae for $D_n$. Hint: use the order of
    elements to find classes of conjugate. Then use the proposition
    \ref{prop:20161010.conjugate_subgroup} to find the subgroups.
    % TODO maybe I can try this when I am free.
\end{ex}

### 2016-10-31 Lecture note - Group Theory in Physics/sections/20161031.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

\subsection{Unitarity of Representation}
\label{sec:Unitarity-of-Representation}

\begin{thm}[Unitary Representation]
    For finite groups and for compact Lie groups, all representations
    are equivalent to a unitary representation.
\end{thm}
\begin{remark}
    Before the formal proof, I remarked that since any finite group
    can be imbeded inside the symmetric group (Cayley's theorem), and
    the symmetric has clearly a unitary representation (perhaps the
    easiest representation one could ever construct besides the
    trivial representation), one could naturally guess whether it is
    possible that any representation could be turned into a unitary
    one.

    As for the compact Lie group case, it is just mentioned in
    \cite{Ludeling} and will not be proved here. It is mentioned in
    page 25 of \cite{Ludeling} that:
    \begin{quote}
        For compact Lie groups, however, there exists a (unique)
        translationally invariant measure, so we can replace
        $\sum_g\to \int \dd g$ and the integral is convergent because
        of compactness. Then the proof directly carries over.
    \end{quote}
\end{remark}
\begin{proof}
    For $D(g)$, we need to find a $X$ such that $\bar{D}(g)\equiv
    X^{-1}D(g)X$ is unitary.

    Since
    \begin{align*}
        1 = \bar{D}^\dagger \bar{D}
    \end{align*}
    One will find 
    $$ (XX^\dagger)^{-1} = D^\dagger (XX^\dagger)^{-1} D$$
    Then let
    \begin{equation}
        H\equiv \sum_{s\in G} D^\dagger(s) D(s)
    \end{equation}
    One can verify that
    \begin{equation}
        D^\dagger (g) H D(g) = H
    \end{equation}

    Now we construct $X$ from $H$. We have
    \begin{equation}
        H = (XX^\dagger)^{-1}
    \end{equation}

    Notice we have $H$ is Hermitian by above equation. Also, $H$ is
    positive definite (easily seen from the definition of $H$ and 
    $a^\dagger H a \geq 0$. Also $H$ is of full rank.).

    Then we have $UHU^{-1} = \mathrm{diag}\{\gamma_1,\gamma_2,\cdots\}$
    and $\gamma_i > 0$. The rest for constructing $X$ should be
    obvious.
\end{proof}
\begin{remark}[Examples of Non-unitary representation]
    It is remard in \cite{Ludeling} that for infinite and non-compact
    groups, the representation are not unitary in general. He gives
    two examples:
    \begin{itemize}
        \item The group $\mathbb{Z}^*$ acting on $\mathbb{C}$ by
            mulplication is certain not equivalent to any unitary
            representation.
        \item Arugment for a representation of non-compact Lie group
            cannot be made unitary by a similarity transformation:
            \begin{quote}
                The group of unitary operators on a finite dimensional
                vector space is isomorphic to $U(n)$ (for complex
                vector spaces, $O(n)$ otherwise), and is hence
                compact. But there cannot be a bijective continuous
                map between a compact and a non-compact space, so
                faithful finite-dimensional representations of
                non-compact groups will be non-unitary. 
            \end{quote}
            But then he mentions something about a perculiar case, the
            Lorentz group, which I do not understand. 
    \end{itemize}
\end{remark}
Anyway, he summarised in the following:
\begin{quote}
   To summarise, for finite groups and for compact Lie groups, all
   representations are equivalent to a unitary one (and we will
   usually take them to be unitary from now on).  For infinite groups
   and non-compact Lie groups, on the other hand, finite-dimensional
   faithful representations are never unitary. Finally, some
   non-compact groups may have representations which are unitary with
   respect to a non-definite scalar product, such as the Lorentz group 
\end{quote}

From class, Ye Fei proved that:
\begin{thm}
    For any two equivalent representation, there is always a unitary
    matrix to relate the two, i.e. exits $Y$ unitary, s.t.
    $$ \bar{D}(g) = Y^{-1} D(g) Y$$
\end{thm}
\begin{proof}
    Suppose we have two unitary representation $D(g)$ and
    $\bar{D}(g)$, related by
    $$ \bar{D}(g) = X^{-1} D(g) X$$
    where $X$ is not necessarily unitary.

    Let $H\equiv X^\dagger X$, it is easy to prove that $H$ is
    Hermitian and positive definite. Direct calculation shows that
    $$ \bar{D}^{-1}(g) H \bar{D}(g) = H$$
    That is $\bar{D}(g)$ and $H$ commute.
    Then we construct $Y$ from $H$. Let $V$ be such that
    \begin{equation}
        V^{-1} H V = \Gamma
    \end{equation}
    where $\Gamma$ is a diagonal matrix of $H$'s eigenvalues.
    Obviously $V$ has to be unitary. Define $\bar{Y}$ to be
    \begin{equation}
        \bar{Y}\equiv V \sqrt{\Gamma} V^{-1}
    \end{equation}
    By direct calculation, we have
    $$ (X\bar{Y})^\dagger (X\bar{Y}) = \id$$
    One can show that
    $$ \bar{Y}^{-1} \bar{D} \bar{Y} = \bar{D}$$
    with laborious calculation. Then one can easily verify that
    $Y\equiv \bar{Y}X$ is the required unitary transformation.
\end{proof}

\begin{defi}[Reducibility of Representation]
    \nomenclature{Reducibility of Representation}{\nomrefpage.}
    A representation $D$ is called \textit{reducible} if $V$ contains an
    invariant subspace. Otherwise $D$ is called irreducible.

    A representation is called \textit{fully reducible} if $V$ can be
    written as the direct sum of irreducible invariant subspaces, i.e.
    $V=V_1\oplus \cdots \oplus V_p$, all the $V_i$ are invariant and the
    restriction of $D$ to each $V_i$ is irreducible.
\end{defi}

\begin{ex}$ $

    \begin{itemize}
        \item The representation of finite group is obviously fully
            reducible or irreducible.
        \item The representation of translation group is not fully
            reducible. For example, for translation we have:
            $T_a T_b = T_{a+b}$,
            One can confirm that the following representation obeys
            the above relationship:
            $$T_a = \left( \begin{array}{cc}
                 1 & a \\
                 0 & 1 \\
            \end{array} \right)$$
            but this is obviously not fully reducible.
    \end{itemize}
\end{ex}

\begin{defi}[Interwiner]
\nomenclature{Interwiner}{\nomrefpage.}
    Given two representations $D_1$ and $D_2$ acting on $V_1$ and
    $V_2$, an intertwiner between $D_1$ and $D_2$ is a linear operator
    \begin{equation}
        F: V_1 \mapsto V_2
    \end{equation}
    which "commutes" with $G$ in the sense that
    \begin{equation}
        F D_1(g) = D_2(g) F
    \end{equation}
    for all $g\in G$.
\end{defi}

(From pp.30 of \cite{Ludeling})

The existence of an intertwiner has a number of consequences. First,
$D_1$ and $D_2$ are equivalent exactly if there exists an invertible
intertwiner. Second, \hl{the kernel and the image of $F$ are invariant
subspaces}: Assume $v\in \Ker{F}$, i.e. $Fv = 0$. Then
\begin{equation}
    FD_1 v = D_2 F v = D_2 0 = 0
\end{equation}
so $D_1 v\in \Ker{F}$. On the other hand, let $w_2 = Fw_1$ be an
arbitrary element of the image of $F$. Then from the definition we have
\begin{equation}
    D_2 w_2 = D_2 F w_1 = FD_1 w_1
\end{equation}
which is again in the image of $F$. Now if $D_1$ is irreducible, the only invariant subspaces,
hence the only possible kernels, are $\{0\}$ and $V_1$ itself, so $F$ is either injective or zero.
Similarly, if $D_2$ is irreducible, F is either surjective or zero. Taking these statements together, we arrive at Schur’s Lemma:

\begin{lemma}[Schur's lemma I]
    An intertwiner between two irreducible representations is either
    an isomorphism, in which case the representations are equivalent,
    or zero
\end{lemma}

An important special case is the one where $D_1 = D_2$. In that case,
we see that $F$ is essentially unique. More precisely, we have the
following theorem, also often called Schur’s Lemma:
\begin{lemma}[Schur's lemma II]
    If $D$ is an irreducible finite-dimensional representation on a complex
vector space and there is an endomorphism $F$ of $V$ which satisfies 
\begin{equation}
    FD(g) = D(g) F
\end{equation}
for all $g\in G$, then F is a multiple of the identity, $F = \lambda
\id$
\end{lemma}
\begin{proof}
    Note that $F$ has at least one eigenvector $v$ with eigenvalue
    $\lambda$. (This is where we need $V$ to be a complex vector
    space: A real matrix might have complex eigenvalues, and hence no
    real eigenvectors.) Clearly, $F-\lambda\id$ is also an
    intertwiner, and it is not an isomorphism since it annihilates
    $v$. Hence, by Schur’s Lemma, it vanishes, thus $F = \lambda\id$.
\end{proof}

(From the book \cite{book})
\begin{thm}[Orthogonal Theorem]
    For finite group $G$, let $D^i(G)$ and $D^j(G)$ be its two
    irreducible, non-equivalent, and unitary representation. Then, as
    a vector in group algebra, they have the following orthogonal
    relationship:
    \begin{equation}
        \sum_{R\in G} D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R) =
        \frac{g}{m_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
    \end{equation}
    $g$ is the order of the group, and $m_j$ is the
    dimension of representation $D^j(G)$.
\end{thm}
\begin{proof}
    Let
    \begin{equation}
        Y_{\rho\lambda}^{\mu\nu} \equiv
        \delta_{\rho\lambda}\delta_{\mu\nu}
    \end{equation}
    Then let
    \begin{align*}
        X^{\mu\nu} = \sum_{R\in G} D^i(R^{-1}) Y^{\mu\nu} D^j(R)
    \end{align*}
    One can find by direct calculation
    \begin{align}
        X^{\mu\nu}_{\rho\lambda}= \sum_{R\in G}
        D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R)
    \end{align}
    And also through direct calculation, one finds
    \begin{align*}
        D^i (s) X^{\mu\nu} = X^{\mu\nu} D^j(s)
    \end{align*}
    for any $s\in G$. 
    Then $X^{\mu\nu}$ is a interwiner. So the case for $i\neq j$ is
    obvious. When $i=j$, we have:
    $$ X = \lambda \id$$
    Now we find the $\lambda$, i.e. the eigenvalue of $X^{\mu\nu}$.

    Now since
    \begin{align*}
        X^{\mu\nu}_{\rho\lambda} = \lambda^{\mu\nu}
        \delta_{\rho\lambda}
    \end{align*}
    One can find two fact by direct calculation:
    \begin{align*}
        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = m_j \lambda^{\mu\nu} \\
        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = g \delta^{\mu\nu}
    \end{align*}
    Hence $\lambda^{\mu\nu} = \frac{g}{m_j} \delta^{\mu\nu}$.
\end{proof}
\begin{remark}
    For the first orthogonality $\delta_{ij}$, one actually do not
    required that $D^i$ and $D^j$ is unitary.
\end{remark}
\begin{coro}
    \begin{equation}
        \sum_{j=1}^{l} m_j^2 \leq g
    \end{equation}
    % TODO
\end{coro}
\begin{coro}
    \begin{equation}
        \sum_{R\in G} \chi^{i*}(R)\chi^j(R) = g \delta_{ij}
    \end{equation}
\end{coro}

### 2016-10-31 Lecture note - Group Theory in Physics/sections/Skipped-Two-Lectures.tex
Incooperate all my preambles into the latex package physicist-taper. Minor modification to lecture notes.

Due to GRE physics preparation. Concepts that may have been covered:

\begin{itemize}
    \item Representation of Groups.
        \begin{itemize}
            \item Character of representation.
            \item Equivalence between representation.
        \end{itemize}
    \item Transformation of Fields
    \item Regular Representation.
\end{itemize}

Now let me cover these concepts quickly.

\begin{defi}[Representation]
\nomenclature{Representation}{\nomrefpage.}
    A representation of a group $G$ is a continuous homomorphism $D$
    from $G$ to the group of automorphisms of a vector space $V$:
    \begin{equation}
        D: G\mapsto \mathrm{Aut}V
    \end{equation}
    $V$ is called the \textit{represetation space}, and the
    \textit{dimension of the representation} is the dimension of $V$.
\end{defi}

The following is copied from \cite{Ludeling}.

\begin{itemize}
    \item There is always the representation $D(g) = 1$ for all $g$.
        If $\mathrm{dim} V = 1$, this is called the \textit{trivial
        representation} \nomenclature{trivial
        representation}{\nomrefpage}.
    \item The matrix groups, i.e. $\mathrm{GL}(n, K)$ and subgroups,
        naturally have the representation "by themselves", i.e.
        by$n\times n$ matrices acting on $K_n$ and satisfying the
        defining constraints (e.g. nonzero determinant). This is
        loosely called the \textit{fundamental or defining
        representation}.
    \item Two representations $D$ and $D'$ are called
        \textit{equivalent}\nomenclature{equivalent of
        representation}{\nomrefpage} if they are related by a
        similarity transformation, i.e. if there is an operator S such
        that
        \begin{equation}
            SD(g)S^{-1} = D'(g)
        \end{equation}
        for all $g$. Note that $S$ does not depend on $g$! Two equivalent
        representation can be thought of as the same representation in
        different bases. We will normally regard equivalent
        representations as being equal.

        Note also here $S$ is the transformation of basis. If we know
        the transformation of vectors $X$, then
        \begin{equation}
            X^{-1} D(g)X = D'(g)
        \end{equation}
    \item A representation is called
        \textit{faithful}\nomenclature{faithful
        representation}{\nomrefpage} if it is injective, i.e.
        $\mathrm{ker} D = \{e\}$, or in other words, if $D(g_1) \neq
        D(g_2)$ whenever $g_1 \neq g_2$.
    \item If $V$ is equipped with a (positive definite) scalar
        product, D is unitary if it preserves that scalar product, i.e
        if
        \begin{equation}
            \braket{u,v} = \braket{D(g)u,D(g)v}
        \end{equation}
        for all $g\in G$. (Here we assume that $V$ is a complex vector
        space, as that is the most relevant case. Otherwise one could
        define orthogonal representations etc.)
\end{itemize}

### 2016-11-01 Lecture note - Group Theory in Physics/sections/20161010.tex
Conjugacy classes and regular representation in Group theory.

@@
 \nomenclature{Normal/Invariant subgroup}{\nomrefpage.}
-    A subgroupNormal/Invariant subgrouproup(also invariant), if and only
-    if for any $x\in G$, we have $xH = Hx$.
+    A subgroup is normal or nnvariant subgrouproup(also invariant), if
+    and only if for any $x\in G$, we have $xH = Hx$.
 \end{defi}
@@
     \label{prop:20161010.conjugate_subgroup}
-    For an invariant subgroup, then every conjugate element is also
-    inside the same invariant subgroup. This shows that an invariant
+    For an normal subgroup, every conjugate element is also
+    inside the same normal subgroup. This indicates that an normal
     subgroup can be decomposed into a series of sum of conjugate classes.

### 2016-11-01 Lecture note - Group Theory in Physics/sections/20161031.tex
Conjugacy classes and regular representation in Group theory.

@@
     Before the formal proof, I remarked that since any finite group
-    can be imbeded inside the symmetric group (Cayley's theorem), and
+    can be embedded inside the symmetric group (Cayley's theorem), and
     the symmetric has clearly a unitary representation (perhaps the
@@
 
-\begin{defi}[Reducibility of Representation]
+\subsection{Reduciblility of Representations}
+\label{sec:Reduciblility-of-Representations}
+
+\begin{defi}[Reducible/Irreducible Representation]
     \nomenclature{Reducibility of Representation}{\nomrefpage.}
@@
         \item The representation of finite group is obviously fully
-            reducible or irreducible.
+            reducible or irreducible. % TODO WHY 
         \item The representation of translation group is not fully

### 2016-11-01 Lecture note - Group Theory in Physics/sections/Skipped-Two-Lectures.tex
Conjugacy classes and regular representation in Group theory.

@@
 \begin{itemize}
+    \item Conjugacy classes
     \item Representation of Groups.
@@
     \item Transformation of Fields
-    \item Regular Representation.
+    \item Group Algebra and Regular Representation.
 \end{itemize}
 
-Now let me cover these concepts quickly.
+\subsection{Conjugacy classes (continued)}
+\label{sec:Conjugacy classes (continued)}
+
+One important group is the symmetric group. It is important because
+that every finite group of order $n$ can be embedded inside the
+symmetric group $S_n$ (Cayley's theorem) \footnote{
+    However, it is hard sometimes to find the smallest possible
+    symmetric group to embed into. For example, $S_3$ has 6 elements
+    and can thus be embedded into $S_6$. But obviously it can be
+    embedded better just into itself $S_3$.
+}.
+
+The conjugacy classes in symemtric is pretty easy to find. What we
+need to know is the following observation (from \cite{Ludeling})
+
+\begin{key}
+    Consider two permutation $\pi$ and $\sigma$:
+    \begin{align}
+        \pi =\left( \begin{array}{ccc}
+             1 & \cdots & n \\
+            \pi(1) & \cdots & \pi(n) \\
+            \end{array} \right) ,\quad\quad
+        \sigma = \left( \begin{array}{ccc}
+             1 & \cdots & n \\
+            \sigma(1) & \cdots & \sigma(n) \\
+            \end{array} \right)
+    \end{align}
+    Then we have by direct calculation:
+    \begin{align}
+        \sigma\pi\sigma^{-1} = \left( \begin{array}{ccc}
+                \sigma(1)      & \cdots & \sigma(n) \\
+                \sigma(\pi(1)) & \cdots & \sigma(\pi(n)) \\
+            \end{array} \right)
+    \end{align}
+    Therefore, the cycle structure of $\pi$ is unchanged under any
+    "conjugacy transformation".
+\end{key}
+What do I mean by cycle structure? Let's see an example. Suppose we
+have a cycle $(123)$:
+\begin{center} \begin{tikzcd}[column sep=small]
+    & 1 \arrow[dr] & \\
+    2\arrow[ru] & & 3\arrow{ll} 
+\end{tikzcd} \end{center}
+Then the conjugated map $\sigma (123) \sigma^{-1}$ will have:
+\begin{center} \begin{tikzcd}[column sep=small]
+    & \sigma(1) \arrow[dr] & \\
+    \sigma(2)\arrow[ru] & & \sigma(3)\arrow{ll} 
+\end{tikzcd} \end{center}
+So it has a cycle of $(\sigma(1)\sigma(2)\sigma(3))$.
+We see that in general, the cycle type is unchanged under conjugacy
+transformation.
+\footnote{ For a permutation, its cycle type is determined by
+    decomposing it into independent cycles. For independent cycles,
+    the cycle type is unique. For example, $(135)(24)$ has a cycle
+    type of $(3,2)$, or $(2,3)$ since the order is irrelevant. But if
+    we decompose it into non-independent cycles, we cannot determine
+    its cycle type. For example, $(135)=(15)(13)$, which is ambiguous
+    if we were to tell the cycle type.
+}
+
+On the other hand, all elements of the same cycle type belong to the
+same conjugacy class. For example, consider two permutations:
+$(i_1 i_2 i_3)(i_4 i_5)$ and $\left(\pi_{i_1}
+\pi_{i_2}\pi_{i_3}\right)\left(\pi_{i_4}\pi_{i_5}\right)$, where $\pi$
+permutes the five numbers $i_1 \cdots i_5$.
+Consider the map:
+\begin{equation}
+    \sigma \equiv \left( \begin{array}{ccc}
+            i_1      & \cdots & i_5 \\
+            \pi_{i_1} & \cdots & \pi_{i_5} \\
+        \end{array} \right)
+\end{equation}
+Then \begin{align*}
+    &\sigma (i_1 i_2 i_3)(i_4 i_5) \sigma^{-1} =  \\
+    &\left( \begin{array}{ccc}
+            i_1      & \cdots & i_5 \\
+            \pi_{i_1} & \cdots & \pi_{i_5} \\
+        \end{array} \right)
+        (i_1 i_2 i_3)(i_4 i_5)
+        \left( \begin{array}{ccc}
+            \pi_{i_1} & \cdots & \pi_{i_5} \\
+            i_1      & \cdots & i_5 \\
+        \end{array} \right) \\
+    & = (\pi_{i_1} \pi_{i_2}\pi_{i_3})(\pi_{i_4}\pi_{i_5})
+\end{align*}
+The proof for the general case is similar. So we have the theorem
+below:
+\begin{thm}[Cycle type determines conjugacy class]
+    Two permutations are conjugate in the symmetric group if and only if they have the same cycle type.
+\end{thm}
+\begin{remark}
+    Since a cycle type is just a set of unordered integer partition of
+    number $n$. The above theorem means that the set of conjugacy
+    classes in the symmetric group on a finite set is in bijection
+    with the set of unordered integer partitions of the size of the
+    set. 
+\end{remark}
+
+\subsection{Group Representation}
+\label{sec:Group-Representation}
 
@@
 
-The following is copied from \cite{Ludeling}.
+Related concepts. (The following is copied from \cite{Ludeling}.)
 
@@
 
-        Note also here $S$ is the transformation of basis. If we know
-        the transformation of vectors $X$, then
+        Note also here $S$ represents a transformation of basis. If we
+        know the transformation of vectors $X$, then
         \begin{equation}
@@
 \end{itemize}
+
+\subsubsection{Regular Representation}
+\label{sec:Regular-Representation}
+
+Now we construce a simple representation for all groups. It utilizes a
+vector space constructed from group itself called Group Algebra.
+
+\begin{defi}[Group algebra/Monoid algebra]
+\nomenclature{$A[G]$ group algebra/monoid algebra}{\nomrefpage.}
+
+    Let $A$ be a commutative ring, $G$ be a monoid, written
+    multiplicatively. Then the monoid ring $A[G]$ consists of those
+    finite formal linear combinations $v$ of the form:
+    \begin{equation}
+        v = \sum_{g\in G} v_g g
+    \end{equation}
+    where $v_g \in A$. The $v_g$ are seen as coefficients and $g$ are
+    seen as the basis vectors that can be multiplied. Soe the addition
+    is defined as:
+    \begin{equation}
+        v+w = \sum_{g\in G} (v_g + w_g) g
+    \end{equation}
+    And the multiplication is
+    \begin{equation}
+        v w = \sum_{g,g'\in G} (v_g w_{g'}) gg'
+    \end{equation}
+    If $G$ is a group then the
+    corresponding $A[G]$ is called a \textit{group algebra}.
+\end{defi}
+A rigorious definition would use the concept of function to define the
+"formal linear combination". Please refer to page 105 (section II.3) of
+\cite{lang-algebra}. 
+\begin{remark}
+    Note that both $A$ and $G$ can be naturally embeded into $A[G]$.
+    This will helps us to define a representation of group $G$ later.
+\end{remark}
+
+\begin{ex}
+    (From page 106 of \cite{lang-algebra}.)
+    Polynomial rings are special cases. In $n$ variables, consider a
+    multiplicative free abelian group of rank $n$. Let $X_l,\cdots
+    X_n$ be generators. Let $G$ be the multiplicative subset
+    consisting of elements $X_1^{v_1},\cdots,X_n^{v_n}$, where
+    $v_i\leq 0$ for all $i$. Then $G$ is a monoid, and it is eas to
+    verify that $A[G]$ is just $A[X_1,\cdots, X_n]$.
+\end{ex}
+
+Here we take $A$ to be $\mathbb{C}$, then we have clearly
+$\mathbb{C}[G]$ a vector space equipped with a bilinear map (the
+product), i.e. an algebra over a field. Its dimension is clear equal
+to the order of $G$. We can also give it an inner product by:
+\begin{equation}
+    \braket{v,w} =\sum_{g\in G} v_g^* w_g
+\end{equation}
+Now we can define the regular representation:
+
+\begin{defi}[Regular Representation]
+\nomenclature{Regular Representation}{\nomrefpage.}
+    A regular representation of a group $G$ is the following
+    endomorphism of $\mathbb{C}[G]$:
+    \begin{equation}
+        D_\text{reg}: v \mapsto g\cdot v
+    \end{equation}
+    where $v\in \mathbb{C}[G]$, $g\in G \hookrightarrow \mathbb{C}[G]$.
+\end{defi}
+
+\begin{remark}
+    This representation can be just seen as a permutation of basis
+    vectors, because:
+    \begin{equation}
+        g\cdot v = \sum_{h\in G} v_h (gh) = \sum_{h'\in G}
+        v_{g^{-1}h'}\, h'
+    \end{equation}
+    Therefore, it is unitary.
+\end{remark}
+
+\begin{remark}
+    This representation is not 
+\end{remark}

### 2016-11-02 Lecture note - Group Theory in Physics/sections/20161031.tex
New notes to the group theory - representation.

@@
 
+\begin{ex}
+    The regular representation mentioned before is reducible. For
+    example, the vector
+    \begin{equation}
+        V = \sum_{g\in G} g
+    \end{equation}
+    spans an invariant subspace of the operator $D_\text{reg}$.
+\end{ex}
+
 \begin{ex}$ $
@@
         \item The representation of finite group is obviously fully
-            reducible or irreducible. % TODO WHY 
+            reducible or irreducible (since a unitary matrix cannot
+            have off diagonal blocks).
         \item The representation of translation group is not fully
@@
 (From the book \cite{book})
-\begin{thm}[Orthogonal Theorem]
+\subsection{Orthogonality Relations and Counting Irreducible
+    Representations}
+\label{sec:Orthogonality-Relations-and-Counting-Irreducible-Representations}
+
+\begin{thm}[Orthogonality Theorem for Representations]
     For finite group $G$, let $D^i(G)$ and $D^j(G)$ be its two
-    irreducible, non-equivalent, and unitary representation. Then, as
-    a vector in group algebra, they have the following orthogonal
+    irreducible representation. Then, as a vector in group algebra,
+    they have the following orthogonal
     relationship:
     \begin{equation}
-        \sum_{R\in G} D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R) =
-        \frac{g}{m_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+        \sum_{h\in G} D^{i}_{\mu\rho}(h^{-1})D^j_{\nu \lambda}(h) =
+        \frac{N}{d_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
     \end{equation}
-    $g$ is the order of the group, and $m_j$ is the
-    dimension of representation $D^j(G)$.
+    $N$ is the order of the group, and $d_j$ is the
+    dimension of representation $D^j(G)$. If in addition, the two
+    representations are unitary, we have
+    \begin{equation}
+        \sum_{h\in G} D^{i*}_{\mu\rho}(h)D^j_{\nu \lambda}(h) =
+        \frac{N}{d_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+    \end{equation}
 \end{thm}
 \begin{proof}
+    \textbf{Note}: The following proof is clumsy and only applies for
+    the unitary case. For a good proof, please refer to page 44 of
+    \cite{Ludeling}.
+
     Let
@@
     \begin{align*}
-        X^{\mu\nu} = \sum_{R\in G} D^i(R^{-1}) Y^{\mu\nu} D^j(R)
+        X^{\mu\nu} = \sum_{h\in G} D^i(h^{-1}) Y^{\mu\nu} D^j(h)
     \end{align*}
@@
     \begin{align}
-        X^{\mu\nu}_{\rho\lambda}= \sum_{R\in G}
-        D^{i*}_{\mu\rho}(R)D^j_{\nu \lambda}(R)
+        X^{\mu\nu}_{\rho\lambda}= \sum_{h\in G}
+        D^{i*}_{\mu\rho}(h)D^j_{\nu \lambda}(h)
     \end{align}
@@
     \begin{align*}
-        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = m_j \lambda^{\mu\nu} \\
-        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = g \delta^{\mu\nu}
+        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = d_j \lambda^{\mu\nu} \\
+        &\sum_\rho X^{\mu\nu}_{\rho\lambda} = N \delta^{\mu\nu}
     \end{align*}
-    Hence $\lambda^{\mu\nu} = \frac{g}{m_j} \delta^{\mu\nu}$.
+    Hence $\lambda^{\mu\nu} = \frac{N}{d_j} \delta^{\mu\nu}$.
+\end{proof}
+The above relation gives us the first clue to the total number of
+irreducible representations by the following corollary. 
+\begin{coro}
+    \begin{equation}
+        \sum_{j} m_j^2 = N = \abs{G}
+    \end{equation}
+    where the index $j$ runs over all possible irreducible
+    representations.
+\end{coro}
+\begin{proof}
+    Define the following vector in group algebra
+    \begin{equation}
+        v^{i}_{\mu\nu} = \sqrt{\frac{d_j}{N}} \sum_{h\in G}
+        \left(D^i(h)\right)_{\mu\nu} h
+    \end{equation}
+    Then by the orthogonality theorem, this vector is orthonomal in
+    vector space/group algebra $\mathbb{C}[G]$. But the dimension of
+    this vector space is $N$, and for each representation $D^i$ we
+    have $d_i^2$ vectors like the one above, which are all orthogonal
+    to each other. Note that orthogonal implies linear independence,
+    hence we have:
+        $$\sum_{j} m_j^2 \leq N $$
+    To make the inequality an equality, it is suffice to prove that
+    such $v^{i}_{\mu\nu}$ forms a basis of the group algebra
+    $\mathbb{C}[G]$. In page 45 to 46 of \cite{Ludeling}, he shows
+    that for any $g\in G\hookrightarrow \mathbb{C}[G]$, one has
+    \begin{align}
+        g = \sum_{h\in G} \left(D_\text{reg}(h)\right)_{ge} h
+        = \sum_{h\in G} \left[ \sum_{j,\mu\nu} c^j_{\mu\nu}
+        \left(D^j(h)\right)_{\mu\nu}\right] h
+    \end{align}
+    where $e$ is the unit in the group. $c$ are some hard to tell
+    constants. To show this, \cite{Ludeling} uses that fact that
+    $D_\text{reg}$ is unitary, so it is completely reducible into
+    irreducible components, which have to be (some of) the $D^i$,
+    i.e. $D_\text{reg}= U(D^{i_1}\oplus D^{i_2}\oplus
+    \cdots)U^\dagger$. The detailed proof is not reproduced here.
+
+    Then, $g$ is a linear combination with
+    coefficients in $\left(D^j(h)\right)_{\mu\nu}$, hence a linear
+    combination of $v^i_{\mu\nu}$. Since $g$ can be any basis in the
+    group algebra, this shows that the $\{v^i_{\mu\nu}\}$ is complete.
 \end{proof}
 \begin{remark}
-    For the first orthogonality $\delta_{ij}$, one actually do not
-    required that $D^i$ and $D^j$ is unitary.
+    The above proof shows in some sense that the regular
+    representation contains all irreducible representation as
+    components. Since all $v^i_{\mu\nu}$ appears in the regular
+    representation.
 \end{remark}
+
+\subsection{Characters}
+\label{sec:Characters}
+\begin{defi}[Character of Representation]
+\nomenclature{Character of Representation}{\nomrefpage.}
+    Given a representation $D$ of $G$ over vector space on field $K$,
+    the character $\chi: G\to K$ is
+    defined as the trace
+    \begin{equation}
+        \chi(g) = \Tr D(g)
+    \end{equation}
+\end{defi}
+\begin{remark}
+    Since trace is invariant under similarity transformation (remember
+    that $\Tr AB = \Tr BA$), trace can be used to distinguishes
+    between non-equivalent representations. Hence it is called the
+    character of that representation.
+\end{remark}
+Using the orthogonality relation in
+Section~\ref{sec:Orthogonality-Relations-and-Counting-Irreducible-Representations}
+it is esay to see we have
 \begin{coro}
     \begin{equation}
-        \sum_{j=1}^{l} m_j^2 \leq g
+        \sum_{h\in G} \chi^{i}(h^{-1})\chi^j(h) = N \delta_{ij}
     \end{equation}
-    % TODO
+    Or when the representations are unitary:
+    \begin{equation}
+        \sum_{h\in G} \chi^{i*}(h)\chi^j(h) = N \delta_{ij}
+    \end{equation}
+    Here again $N = \abs{G}$.
 \end{coro}
-\begin{coro}
-    \begin{equation}
-        \sum_{R\in G} \chi^{i*}(R)\chi^j(R) = g \delta_{ij}
-    \end{equation}
-\end{coro}

### 2016-11-02 Notes of various papers/Kitaev. Periodic table for topological insulators and superconductors/notes.tex
New notes to the group theory - representation.

--- 2016-10-22 Notes of Bernvig's Book/Ch4 TR symmetry/Notes about TR symmetry.tex
@@
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{bbm} % for numbers within mathbb
-\usepackage{mathrsfs} % For \mathscr{ABC}
-% Followings are for the special character: differential "d".
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage[unicode]{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\newtheorem{fact}{Fact}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-\newtheorem{argument}{Argument}[section]
-
-% A list of nomenclatures.
-\usepackage{nomencl}
-\makenomenclature
-
-% For drawing diagrams with arrows
-\usepackage[all]{xy}
-
 % My own physics package
@@
 % prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physics-taper".
+% "physics" loaded in package "physicist-taper".
 \usepackage[log-declarations=false]{xparse}
-\usepackage{physics-taper}
+\usepackage{physicist-taper}
 
-\title{Notes about Spin and TR Symmetry}
+\makenomenclature
+
+\title{Notes about Periodic table for topological insulators and superconductors}
 \date{\today}
@@
 \abstract{
-This is a note about TR symmetry, with its application in the theory of
-condensed matter physics. The two reference book are the classic by
-Sakurai \cite{sakurai}, and the other by Bernevig \cite{bernevig}.
-It contains a summary of treatment of Spin (actually, rotation) in
-quantum mechanics, which is needed to discuss the TR symmetry operator.
+As title suggests.
 }
 \tableofcontents
+From the start: for \textbf{Gapped free-fermion} system, he mentions
+the classification hitherto available. See
+Table~\ref{tab:classification}.
+\begin{table}[ht]
+    \centering
+    \caption{Classification}
+    \label{tab:classification}
+    \vspace{+0.5pt}
+    \rowcolors{1}{white}{lightgrey}
+    \tabulinesep=1.2mm
+    \begin{tabu}{  X[l] X[l] X[l] X[l] }
+        \textit{Symmetry} & \textit{Spatial Dimension} &
+        \textit{Result} & \textit{Other Keywords} \\
+        \hline
+        T & 0 & An intger: the number of particle-occupied Kramers
+        doublet states & \\
+        T & 1 & None & \\
+        T & 2 & $\mathbb{Z}_2$ & \\
+        T & 3 & $\mathbb{Z}_2$ & $3D$ crystals have additional
+        $3\mathbb{Z}_2$ invariant$ \Rightarrow$ "weak topological
+        insulators \\
+        Q(?) & 2 & Characterized by $\mu$ in units of $e^2/h$ & TKNN \\
+        Q(?) & even  d & Topological invariant ($k$-th Chern number) \\
+        Q(?) & 0 &  number of single-particle states with negative
+energy ($E< E_F = 0$), which are filled with electrons. \\
+        T\& Q \\
+        No T \& No Q & 0 & $\mathbb{Z}_2$ \\
+        No T \& No Q & 1 &$\mathbb{Z}_2$ &"majorana chain"  \\
+        No T \& No Q & 2 & Topological number is integer. & Even-odd
+        effects. \\
+    \bottomrule
+    \end{tabu}
+\end{table}
 
-\section{Review of Spin theory}
-\label{sec:Review-of-Spin-theory}
-Outline:
-\begin{enumerate}
-    \item The representation of infinitesimal operator.
-    \item From traditional rotational operators to commutation
-        relationship
-    \item From commutators to their eigenvalues.
-    \item Summarize some further results regarding the matrix
-        representation of those operators.
-\end{enumerate}
-
-\subsection{The representation of transformation}
-\label{sec:The-representation-of-transformation}
-
-To find an operator for a physical transformation, we naturally encounters
-the theory of representation of groups. Why groups? See the following
-notes for an bird view. (The note is an excerpt from my notes about
-Quantum Field Theory by Weinberg, which is still in its infancy because
-the book is so hard to read)
+\paragraph{Robustness in classification}
 \begin{quote}
-    The set of all symmetries transformations obviously can have a group
-    structure. By giving each symmetry transformation a unitary or
-    antiunitary operator, a representation of such group is obtained.
-    However, such a representation can be projective (projective as in
-    projective geometry, or $\mathbb{CP}^n$), since operators acts on ket
-    spaces, which is already projective (i.e. within a freedom of phase). 
+    ..., the topological numbers are insensitive to disorder and can even
+    be defined without the spectral gap assumption, provided the
+    eigenstates are localized.
 \end{quote}
 
-Here I outlined one general procedure to obtain such representation from
-infinitesimal transformations. This procedure is discussed in chapter 1
-and 2 of \cite{sakurai}.
-% TODO update more specific location inside that book.
-We first needs two thing to characterize a tranformation: a Hermitian
-operator $G$ and an infinitesimal change $\varepsilon$. I am not sure about
-how to choose $G$, but I think the choice for $\varepsilon$ should be
-% TODO how to choose G, and what is G
-clear. Here are three typical examples.
-
-For displacement in $x$ direction:
-\begin{align}
-    G \rightarrow \frac{p_x}{\hbar},\, \varepsilon \rightarrow \diff x
-\end{align}
-For an infinitesimal time evolution:
-\begin{align}
-    G \rightarrow \frac{H}{\hbar},\, \varepsilon \rightarrow \diff t
-\end{align}
-For infinitesimal rotation around $k$ th axis:
-\begin{align}
-    G \rightarrow \frac{J_k}{\hbar},\, \varepsilon \rightarrow \diff \phi
-    \label{eq:revSpin.repreTrans.angulalMomGen}
-\end{align}
-Or more general (let the rotation be characterized by $\mathbf{J}\cdot
-\hat{\mathbf{n}}$, where $\hat{\mathbf{n}}$ is a unit vector), we have:
-\begin{align}
-    G \rightarrow \frac{\mathbf{J}\cdot \hat{\mathbf{n}} }{\hbar},\,
-    \varepsilon \rightarrow \diff \phi
-\end{align}
-
-Here $\mathbf{J}=(J_x,J_y,J_z)$ is defined such that the substitution
-\ref{eq:revSpin.repreTrans.angulalMomGen} indeed produces a rotation.
-What do we mean by "indeed" here? This will be explained in section
-\ref{sec:From-classical-mechanic-to-commutators}.
-\label{page:question-def_of_J}
-
-Then the operator corresponding to the infinitesimal transformation is
-\begin{align}
-    U_\varepsilon= 1-i\, G\varepsilon
-\end{align}
-And for a finite transformation (let $\Delta$ denotes the finite
-transformation):
-\begin{align}
-    \lim_{N\to \infty}\left[ 1-iG\frac{\Delta}{N}\right]^N =
-    \exp(-iG\Delta)
-\end{align}
-For example, in the case of rotation we have (using $\mathscr{D}$ to
-denote the operator):
-\begin{align}
-    \mathscr{D}(\hat{\mathbf{n}},\diff \phi) =
-    1-i\frac{\mathbf{J}\cdot\hat{\mathbf{n}}}{\hbar}\diff\phi
-    \\
-    \mathscr{D}(z,\phi)=\exp(\frac{-iJ_z \phi}{\hbar})
-    \label{eq:revSpin.repreTrans.repreFiniteRot}
-\end{align}
-
-Note that, here $G$ is regarded as a generator of physical transformation:
-\begin{table}[H]
-    \centering
-    \caption{Generators}
-    \begin{tabular}{|c|c|}
-    \hline
-    Generator                     & Physically generated transformation \\
-    \hline
-    Momentum $p_x$                & Translation $\diff x$ \\
-    \hline
-    Energy $H$                    & Time evolution: $\diff t$ \\
-    \hline
-    Angular momentum $J_x$ & Rotation about $x$ axis \\
-    \hline
-    \end{tabular}
-\end{table}
-\subsection{From classical mechanics to commutators in quantum mechanics}
-\label{sec:From-classical-mechanic-to-commutators}
-
-This part is discussed in secion 3.1 of \cite{sakurai}.
-
-The commutation relationship is obtained by considering infinitesimal
-transformation. In general, classical rotation can be decomposed into
-rotation about three axes. We can use linear transformation to express
-them. For example, rotation about $z$ axis is:
-\begin{align}
-    R_z(\phi) = \left( \begin{array}{ccc}
-         \cos (\phi ) & -\sin (\phi ) & 0 \\
-         \sin (\phi ) & \cos (\phi ) & 0 \\
-         0 & 0 & 1 \\ \end{array} \right)
-\end{align}
-Put it into infinitesimal amount, one has:
-\begin{align} 
-    R_z(\varepsilon)=\left( \begin{array}{ccc}
-     1-\frac{\varepsilon ^2}{2} & -\varepsilon               & 0 \\
-     \varepsilon                & 1-\frac{\varepsilon ^2}{2} & 0 \\
-     0                          & 0                          & 1 \\
-\end{array} \right) \end{align}
-Similar procedure could be done for other axes (see equation 3.1.4 and
-3.1.5 in \cite{sakurai}). By calculation one finds that
-$$ R_x(\varepsilon)R_y(\varepsilon)=R_y(\varepsilon)R_x(\varepsilon)$$
-if terms higher than $\varepsilon$ is ignored. This means that
-infinitesimal rotation $\diff \mathbf{\omega}$ can be safely considered as
-vectors.
-
-However if only terms of order equal and lower than $\varepsilon^2$ is kept
-(note especially that $\varepsilon^4$ is ignored), one finds:
-\begin{align}
-    \label{eq:revSpin.fromCM2QM.classicalRotComu}
-    R_x(\varepsilon)R_y(\varepsilon)-R_y(\varepsilon)R_x(\varepsilon)=
-    R_z(\varepsilon^2)-\mathbb{I}
-\end{align}
-
-Expand equation \ref{eq:revSpin.repreTrans.repreFiniteRot} in orders of
-$\phi$ and keep only terms with order $leq \phi^2$, we have:
-$$
-\mathscr{D}(x,\varepsilon)=
-1-\frac{iJ_x \varepsilon}{\hbar}-\frac{J_x^2 \varepsilon^2}{2\hbar^2}
-$$
-and so on for other axes.
-
-Plug these results into the classical commutation relationship
-\ref{eq:revSpin.fromCM2QM.classicalRotComu}, and with some calculation,
-one will find:
-\begin{align}
-    \label{eq:revSpin.fromCM2QM.comuOfAngularM}
-    [J_i,J_j]=i\hbar \varepsilon_{ijk}J_k
-\end{align}
-here $\varepsilon_{ijk}$ is the Levi-Civita notation in $3$ dimension.
-This relation also ensures that the operator $\mathbf{J}$ we defined
-indeed corresponds to a physical rotation, which answers the question is
-mentioned in page \pageref{page:question-def_of_J}.
-
-\subsection{From commutators to eigenvalues}
-\label{sec:From-commutators-to-eigenvalues}
-Now one may use the commutation relation
-\ref{eq:revSpin.fromCM2QM.comuOfAngularM} to get the eigenvalues of these
-operators. The procedure is quite standard and can be found in section 3.5
-of \cite{sakurai}. There the author defines the ladder operators:
-\begin{defi}[Ladder operator]
-\nomenclature{Ladder operator}{\nomrefpage.}
-    \begin{align}
-        J_{\pm}\equiv J_x \pm i J_y
-    \end{align}
-\end{defi}
-Then he derives the cummutation relationship:
-\begin{align}
-    [\mathbf{J}^2,J_k] &= 0\\
-    [J_+,J_-] &=2\hbar J_z \\
-    [J_z,J_\pm] &= \pm \hbar J_\pm \\
-    [\mathbf{J}^2,J_\pm] &=0 \\
-\end{align}
-Chossing the $z$ direction as eigenstate. Denote the simultaneous
-eigenstates of $\mathbf{J}^2$ and $J_z$ as $\ket{j,m}$, such that:
-\begin{align}
-    \mathbf{J}^2\ket{j,m} &= j(j+1)\hbar^2 \ket{j,m} \\
-    J_z \ket{j,m} &= m \hbar\ket{j,m}
-\end{align}
-(such a strange choice is conventional in the case of spin).
-
-As usual, one finds that
-\begin{itemize}
-    \item For $J_z$, $J_\pm$ will pull up/lower its eigenvalue for
-        eigenstate in units of $\hbar$.
-    \item For $\mathbf{J}^2$, $J_\pm$ will not alter its eigenvectors,
-        since it commutes with $\mathbf{J}^2$.
-\end{itemize} 
-By above relationships, one can derive the following facts (for
-convenience let $a$ be the eigenvalue for $\mathbf{J}^2$, and $b$ be the
-eigenvalue for $J_z$.):
-\begin{itemize}
-    \item $a\geq b^2$, i.e $b$ is bounded by $a$. More specifically,
-    \item $a=b_{\text{max}}(b_{\text{max}}+\hbar)$.
-    \item Also, $-b_{\text{max}}\leq b \leq b_{\text{max}}$.
-    \item Using $b_{\text{max}}=b_{\text{min}}+n\hbar$ ($n$ is some
-        integer), one gets
-    \item $b_{\text{max}}= \frac{n\hbar}{2}$. This, by identifying
-        $j=\frac{n}{2}$, one has
-\end{itemize}
-\begin{align}
-    a &= j(j+1)\hbar^2 \\
-    b &= m\hbar\\
-    (m &= -j, -j+1,\cdots, j-1,j;\, j=\frac{n}{2}) \nonumber
-\end{align}
-\subsection{Getting the matrix of rotation operators}
-\label{sec:Using-Euler-angles-to-get-matrix-of-rotation-operators}
-
-Simply by commutation relationships above, one can easy get:
-\begin{align}
-    \bra{j',m'}\mathbf{J}^2\ket{j,m} &= 
-        j(j+1)\hbar^2 \delta_{j'j}\delta_{m'm} \\
-    \bra{j',m'}J_z\ket{j,m} &= 
-        m\hbar \delta_{j'j}\delta_{m'm} \\
-    \bra{j',m'}J_\pm\ket{j,m} &= 
-        \sqrt{(j\mp m)(j\pm m+1)} \hbar \delta_{j'j}\delta_{m',m\pm 1}
-        \label{eq:revSpin.getMatRot.J_pm}
-\end{align}
-
-To get matrix element for
-$\exp(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar})$, one needs to
-use Euler angles.
-
-    \subsubsection{Eulerian Angles}
-    \label{sec:Eulerian-Angles}
-    The Euler angles is discussed in section 3.3 of \cite{sakurai}.
-    However, Sakurai's usage in his book \cite{sakurai} is a bit different
-    from the usual one. But the following graph taken from that section
-    should explains all:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=1.2\linewidth]{pics/{fig3.4in-Sakurai-Euler-angles}.png}
-        \caption{Euler Angles (fig 3.4 in that book)}
-        \label{fig:fig3.4-Sakurai-Euler-angles}
-    \end{figure}
-
-    One can find that a Euler rotaion characterized by
-    $(\alpha,\beta,\gamma)$ could be decomposed into:
-    \begin{align}
-        R(\alpha,\beta,\gamma)=R_z(\alpha)R_y(\beta)R_z(\gamma)
-    \end{align}
-
-    \subsubsection{Using Euler angles to get matrix for rotation operator}
-    \label{sec:Using Euler angles to get matrix for rotation operator}
-
-    As the title suggests, in section 3.5 of \cite{sakurai}, we have
-    $$
-    \exp\left(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar}\right)
-    =
-    \exp\left(\frac{-i J_z\alpha}{\hbar}\right)
-    \exp\left(\frac{-i J_y\beta}{\hbar}\right)
-    \exp\left(\frac{-i J_z\gamma}{\hbar}\right)
-    $$,
-    define 
-    \begin{align}
-        \nomenclature{
-            Wigner function $\mathscr{D}^{(j)_{m'm}}$}{\nomrefpage.}
-        \mathscr{D}^{(j)}_{m'm}\equiv
-        \bra{j,m'}
-            \exp\left(\frac{-i J_z\alpha}{\hbar}\right)
-            \exp\left(\frac{-i J_y\beta}{\hbar}\right)
-            \exp\left(\frac{-i J_z\gamma}{\hbar}\right)
-        \ket{j,m}
-    \end{align}
-    This $\mathscr{D}$ is sometimes called the \textbf{Wigner function}.
-    Note that we have implicitly assumed that the rotation in 
-    $\exp\left(\frac{-i\mathbf{J}\cdot\hat{\mathbf{n}}\phi}{\hbar}\right)$
-    does not alter the eigenstate of length $\mathbf{J}^2$. This is
-    physically satisfying, and can also be proved (equation 3.5.43 in
-    \cite{sakurai}).
-
-    % TODO I thin we should distinguish of two concepts of rotation:
-    % J and exp(-iJ/h).
-
-    Since we have diagonalize using the eigenstate of $J_z$, we have:
-    \begin{align}
-        \mathscr{D}^{(j)}_{m'm} =
-            e^{-i(m'\alpha+m\gamma)}\bra{j,m'}
-                \exp\left(\frac{-i J_y\beta}{\hbar}\right)
-            \ket{j,m}
-    \end{align}
-    The remaining part can only be calculated case by case. Denote it as 
-    $d^{(j)}_{m'm}$\nomenclature{ $d^{(j)}_{m'm}$}{\nomrefpage.}, i.e.:
-    \begin{align}
-        d^{(j)}_{m'm}\equiv \bra{j,m'}
-                \exp\left(\frac{-i J_y\beta}{\hbar}\right)
-            \ket{j,m}
-    \end{align}
-
-    Detailed calculation could start from equation
-    \ref{eq:revSpin.getMatRot.J_pm}.
-    In case of $j=\frac{1}{2}$, as is familiar for use, it is:
-    \begin{align}
-        d^{\frac{1}{2}}=\left( \begin{array}{cc}
-            \cos \left(\frac{\beta }{2}\right) 
-                & -\sin \left(\frac{\beta}{2}\right) \\
-            \sin \left(\frac{\beta }{2}\right) 
-                & \cos \left(\frac{\beta}{2}\right) \\
-            \end{array} \right)
-    \end{align}
-    Footnote \footnote{This can also be obtained using the Pauli matrices,
-    which can be found in my miscellaneous notes.}
-
-    \subsubsection{Pauli matrices in half-spin: about \texorpdfstring{$e^{-i\pi S_y/\hbar}$}{}}
-    \label{sec:About-exp(-i*pi-S_y/hbar)}
-
-    Since everyone is familiar with the Pauli matrices in spin $1/2$
-    system, I here only shows a useful result. This result is related to
-    equation (4.4.65) in \cite{sakurai}.
-
-    Since 
-    $$S_y=\frac{\hbar}{2}\sigma_y=\frac{\hbar}{2}
-        \left( \begin{array}{cc}
-         0 & -i \\
-         i & 0 \\
-        \end{array} \right)$$
-    It is easy to check that $\sigma_y^2 = \mathbb{I}$. So:
-    \begin{align*}
-        e^{-i\phi S_y/\hbar}=
-        e^{-i\frac{\phi}{2}\sigma_y}&=\sum_{n=0}^{\infty}
-         \frac{(-i\frac{\phi}{2})^n(\sigma_y)^n}{n!}\nonumber\\
-         &=\sum_{\text{odd }n}-\frac{i(\frac{\phi}{2})^n}{n!}\sigma_y
-           + \sum_{\text{even }n}\frac{(i\frac{\phi}{2})^n}{n!}\mathbb{I}
-    \end{align*}
-    Using the taylor expansions:
-    \begin{align}
-        \sinh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n+1}}{(2n+1)!}
-        \text{ (odd terms)}\\
-        \cosh{x}&= \sum_{n=0}^{\infty}\frac{x^{2n}}{(2n)!}
-        \text{ (even terms)}
-    \end{align}
-    We see that:
-    \begin{align}
-        e^{-i\phi S_y/\hbar}=e^{-i\frac{\phi}{2}\sigma_y}&=
-         - \sigma_y\sinh{i\frac{\phi}{2}}+ \mathbb{I}\cosh{i\frac{\phi}{2}}
-         \nonumber\\
-         &=
-         -i\sigma_y \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-         &=-i\frac{2}{\hbar}S_y\sin{\frac{\phi}{2}}
-            +\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-         &=\left( \begin{array}{cc}
-            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
-            \sin (\frac{\phi }{2}) & \cos (\frac{\phi }{2}) \\
-         \end{array}\right)
-    \end{align}
-    So
-    $$e^{-i\pi S_y/\hbar} = -i\frac{2S_y}{\hbar}$$
-    By exactly the same argument, or simply by the symmetry
-    ($x\leftrightarrow y$), we
-    have:
-    \begin{align}
-        e^{-i\phi S_x/\hbar}=e^{-i\frac{\phi}{2}\sigma_x}&=
-         -i\sigma_x \sin{\frac{\phi}{2}}+\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-        &=-i\frac{2}{\hbar}S_x\sin{\frac{\phi}{2}}
-            +\mathbb{I}\cos{\frac{\phi}{2}}
-        \\
-        &=\left(\begin{array}{cc}
-            \cos(\frac{\phi }{2}) & -\sin(\frac{\phi }{2}) \\
-            \sin (\frac{\phi }{2}) & \cos(\frac{\phi }{2}) \\
-         \end{array}\right)
-    \end{align}
-    Also, one can easily find that:
-    \begin{align}
-        e^{-i\phi S_z/\hbar}=e^{-i\frac{\phi}{2}\sigma_z}&=
-          \left(\begin{array}{cc}
-              e^{-i\frac{\phi }{2}} & 0 \\
-              0                     & e^{i\frac{\phi }{2}} \\
-         \end{array}\right)
-    \end{align}
-    Also, we have a formula that encompass all the above relationship
-    (proved in page 170, section 3.2 of \cite{sakurai}):
-    \begin{align}
-        \exp(\frac{-i\vec{\sigma}\cdot\hat{\vec{n}}\phi}{2})
-        =
-        \cos(\frac{\phi}{2})\mathbb{I}-i\vec\sigma\cdot\hat{\vec{n}}
-        \sin(\frac{\phi}{2})
-    \end{align}
-    where $\vec\sigma=(\sigma_x,\sigma_y,\sigma_z)$, and 
-    $\hat{\vec{n}}$ is any unit vector.
-
-    \subsubsection{Eigenstate for \texorpdfstring{$\mathbf{S}\cdot
-    \hat{\mathbf{n}}$}{}}
-    \label{sec:Eigenstate_for_Sn}
-    Here is a physical arguemnt to construct an eigenstate for the
-    operator $\mathbf{S}\cdot \hat{\mathbf{n}}$. It mimics what was done
-    in page 172 of \cite{sakurai}. This is certainly correct when
-    $j=\frac{1}{2}$. However, I am not sure about its validity in case of
-    higher spin.
-    % TODO check this!
-
-    Suppose we have a state of the highest eigenvalue for $J_z$, i.e.
-    a state labeled by $\ket{j,j}$, then in principle any state can
-    be obtained from this state after a rotatation and a scale. But since
-    $\ket{\mathbf{n}}$ is unit vector, it can be characterized by two
-    angle: the polar angle $\beta$ and the azimuthal angles $\alpha$.
-    As shown in the following picture:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\linewidth]{pics/{fig3.3in-Sakurai-polar-n-azimuthal}.png}
-        \caption{Polar and azimuthal angle (fig 3.3 in \cite{sakurai})}
-    \end{figure}
-
-    So I think the eigenstate should be:
-    \begin{align}
-        \label{eq:revSpin.getMatRot.Sn.Snket}
-        \ket{\hat{\mathbf{n}};+}= e^{-iS_z \alpha/\hbar}
-        e^{-iS_y \beta/\hbar} \ket{+}
-    \end{align}
-    here $\ket{+}$ denotes the state $\ket{j,j}$. The eigenvalue is of
-    course $j\hbar$.
-
-    This is confirmed when $j=\frac{1}{2}$ in page 171 of \cite{sakurai},
-    but not in other cases.
-
-\section{Review of Symmetry Operator}
-\label{sec:Review-of-Symmetry-Operator}
-
-This part is discussed in section 4.4 of \cite{sakurai}.
-
-Outline:
-\begin{enumerate}
-    \item A note about antilinear operator, and we should treat it with
-        care.
-    \item The invariance of probability and Wigner's theorem
-    \item The values of measurement before and after transformation
-\end{enumerate}
-
-\subsection{A note about antiunitary operator}
-\label{sec:A-note-about-antiunitary-operator}
-Please note that the Dirac bra-ket notation is only convenient when we are
-dealing with unitary operators. When antiunitary operators, or arbitrary
-operators are considered, the situation can get tricky. Here are two
-examples.
-
-    \subsubsection{Formula for base transformation}
-    \label{sec:Formula-for-base-transformation}
-
-    Suppose we transform the basis
-    $\ket{e_i}$ by an operator $\mathcal{O}$, what is the formula for the
-    corresponding basis for the dual space? The requirement of dual basis
-    requires that:
-    $$ \bra{\widetilde{e}_i} = \bra{\widetilde{e}_i}U^{-1}$$
-    But by the "dual-correspondance" in Dirac notation, we expect:
-    $$ \bra{\widetilde{e}_i} = \bra{\widetilde{e}_i}U^{\dagger}$$
-    The two notion coincide only when $U$ is unitary.
-
-    Similarly, consider the operator $\ket{e_i}\bra{e_i}$, if we perform a
-    scale of the basis $\ket{e_i}\to \lambda\ket{e_i}$, then how will the
-    above operator transform? Is it
-    $$ \ket{\lambda e_i}\bra{\lambda e_i}$$
-    or is it:
-    $$ \ket{\lambda^{-1} e_i}\bra{\lambda e_i}$$
-    Of course, when the transformation is unitary, the two notion
-    coincide, because $\lambda^*=\lambda^{-1}$ implies
-    $\lambda=\lambda^{-1}$.
-    \subsubsection{The adjoint of antilinear operator}
-    label{sec:The-adjoint-of-antilinear-operator}
-
-    If we were to define adjoint of an antilinear operator, we might
-    run into troubles with traditional definition. For example, suppose
-    $A$ is antilinear, let us multiply it with $c\mathbbm{1}$, where $c$
-    is just some nonzero constant.
-
-    We have:
-    \begin{align}
-        \braket{\phi|cA \psi} = c\braket{\phi|A\psi}
-    \end{align}
-    on the other hand:
-    \begin{align}
-        &\braket{\phi|cA \psi} = \braket{cA\psi|\phi}^*
-            = \braket{\psi|A^\dagger c^* \phi}^* 
-            =(c\braket{\psi|A^\dagger \phi})^* \nonumber\\
-            =& c^* \braket{A\psi|\phi}^* 
-            = c^* \braket{\phi|A\psi}
-    \end{align}
-    A contracdiction. Then, it was proposed, in the first answer to
-    this Math.SE post\cite{math.SE-adjoint-of-antilinear}, that we define
-    the adjoint operator differently for antilinear operator $A$:
-    \begin{align}
-        \braket{A^\dagger v|w} = \braket{v| Aw}^*
-    \end{align}
-    Then the above discrepancy will not exist anymore (easily confirmed).
-
-    Here I also include the complete answer for reference:
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
+\paragraph{Equivalence of Hamiltonian} 
 \begin{quote}
-        I) First of all, one should never use the [Dirac bra-ket notation](http://en.wikipedia.org/wiki/Bra-ket\_notation) (in its ultimate version where an operator acts to the right on kets and to the left on bras) to consider the definition of [adjointness](http://en.wikipedia.org/wiki/Adjoint\_operator), since the notation was designed to make the adjointness property look like a mathematical triviality, which it is not.
-See also [this](http://physics.stackexchange.com/q/43069/2451) Phys.SE post.
-
-        II) OP's question(v1) about the existence of the adjoint of an [antilinear](http://en.wikipedia.org/wiki/Antilinear\_map) operator is an interesting mathematical question, which is rarely treated in textbooks, because they usually start by assuming that operators are $\mathbb{C}$-linear.
-
-        III) Let us next recall the mathematical definition of the adjoint of a linear operator.
-Let there be a [Hilbert space](http://en.wikipedia.org/wiki/Hilbert\_space) $H$ over a [field](http://en.wikipedia.org/wiki/Field\_\%28mathematics\%29) $\mathbb{F}$, which in principle could be either real or complex numbers, $\mathbb{F}=\mathbb{R}$ or $\mathbb{F}=\mathbb{C}$.
-Of course in quantum mechanics, $\mathbb{F}=\mathbb{C}$.
-In the complex case, we will use the standard physicist's convention that the [inner product/sequilinear form](http://en.wikipedia.org/wiki/Sesquilinear\_form) $\langle \cdot | \cdot \rangle$ is conjugated $\mathbb{C}$-linear in the first entry, and $\mathbb{C}$-linear in the second entry.
-
-        Recall [Riesz' representation theorem](http://en.wikipedia.org/wiki/Riesz\_representation\_theorem): For each continuous $\mathbb{F}$-linear functional $f: H \to \mathbb{F}$ there exists a unique vector $u\in H$ such that
-        $$\text{tag\{1\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
-
-        Let $A:H\to H$ be a continuous$^1$ $\mathbb{F}$-linear operator. Let $v\in H$ be a vector. Consider the continuous $\mathbb{F}$-linear functional
-
-        $$\text{tag\{2\}} f(\cdot)~=~\langle v | A(\cdot) \rangle.$$
-
-        The value $A^{\dagger}v\in H$ of the adjoint operator $A^{\dagger}$ at the vector $v\in H$ is by definition the unique vector $u\in H$, guaranteed by Riesz' representation theorem, such that 
-        $$\text{tag\{3\}} f(\cdot)~=~\langle u | \cdot \rangle.$$
-
-        In other words, 
-        $$\text{tag\{4\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\langle v | Aw \rangle. $$
-
-        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an $\mathbb{F}$-linear operator as well.
-
-        IV) Finally, let us return to OP's question and consider the definition of the adjoint of an antilinear operator.
-The definition will rely on the complex version of Riesz' representation theorem.
-Let $H$ be given a complex Hilbert space, and let  $A:H\to H$ be an antilinear continuous operator.
-In this case, the above equations (2) and (4) should be replaced with
-
-        $$\text{tag\{2'\}} f(\cdot)~=~\overline{\langle v | A(\cdot) \rangle},$$
-
-        and
-
-        $$\text{tag\{4'\}} \langle A^{\dagger}v | w \rangle~=~\langle u | w \rangle~=~f(w)=\overline{\langle v | Aw \rangle}, $$
-
-        respectively. Note that $f$ is a $\mathbb{C}$-linear functional.
-
-        It is straightforward to check that the adjoint operator $A^{\dagger}:H\to H$ defined this way becomes an antilinear operator as well.
-
-        --
-
-        $^{1}$We will ignore subtleties with [discontinuous/unbounded operators](http://en.wikipedia.org/wiki/Unbounded\_operator), domains, [selfadjoint extensions](http://en.wikipedia.org/wiki/Extensions\_of\_symmetric\_operators), etc., in this answer.
+    ... Two Hamiltonians belong to the same phase if they can be
+    continuously transformed one to the other while maintaining
+    the energy gap or localization; we will elaborate on that
+    later. 
 \end{quote}
-
-    \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
-
-    \subsubsection{Conclusion}
-    \label{sec:Conclusion}
-    For antilinear operators, we should always working with it acting on
-    the kets. See page 289 in section 4.4 of \cite{sakurai}.
-
-\subsection{Properties of a symmetry operator}
-\label{sec:Property-of-symmetry-operator}
-Consider a symmetry operation acting on states such that:
-\begin{align}
-    \ket{\alpha}\to \ket{\widetilde{\alpha}}\,\,
-    \ket{\beta}\to \ket{\widetilde{\beta}}
-\end{align}
-We require that the probability, the most important thing in quantum
-mechanics, is unchaged:
-\begin{align}
-    |\braket{\widetilde{\beta}|\widetilde{\alpha}}| =
-        |\braket{\beta|\alpha}|
-\end{align}
-Wigner has proved that\footnote{
-Though it was only mentioned in page 289 of \cite{sakurai}.},
-all such symmetry transformations can be characterized either by an unitary
-or an antiunitary operator. Also, any antiunitary operator $\theta$ can be
-expressed as
-\begin{align}
-    \theta = U K
-\end{align}
-where $U$ is unitary, and $K$ is complex conjugation. Three facts about
-$K$:
-\begin{itemize}
-    \item \textit{"acts only on any coefficient that multiplies a ket
-        (and stands on the right of K)."} 
-    \item $K$ also does not act on the base ket, i.e. $K\ket{e}=\ket{e}$.
-    \item $K$'s action depends heavily the base ket. This is obvious from
-        the above two points. Of course, this is not important when every
-        physical state is only projective. However, I still doubt whether
-        this will call additional problem.
-        \footnote{Consider $K\ket{e}=\ket{e}$, but when
-        $\ket{e}=i\ket{e'}$, then $K\ket{e}=-i\ket{e'}=-\ket{e}$.}
-\end{itemize}
-
-\subsection{States and Operators after transformation}
-\label{sec:States-and-Operators-after-transformation}
-Let $U$ be an unitary operator and $A$ be an antiunitary operator. Suppose
-we have $\ket{\alpha}$ and $\ket{\beta}$, and regard both to be
-transformed under $U$ and $A$. Let:
-\begin{align}
-    \ket{\alpha_u}=U\ket{\alpha},\, \ket{\alpha_a}=A\ket{\alpha} \\
-    \ket{\beta_u}=U\ket{\beta},\, \ket{\beta_a}=A\ket{\beta}
-\end{align}
-Then by defintion of unitary and antiunitary, we have:
-\begin{align}
-    \braket{\beta_u|\alpha_u} &=\braket{\beta|\alpha} \\
-    \braket{\beta_a|\alpha_a}^* &=\braket{\beta|\alpha}
-\end{align}
-
-For any operator $\mathcal{O}$, we have, after transformation:
-\begin{align}
-    \mathcal{O}_u &= U\mathcal{O}U^\dagger \\
-    \mathcal{O}_a &= A \mathcal{O}^\dagger A^{-1}
-\end{align}
-The two equation are mean to expresses the following idea:
-\begin{align}
-    \bra{\alpha}\mathcal{O}\ket{\beta} &=
-    \braket{\widetilde{\alpha}|\mathcal{O}_u |\widetilde{\beta}} \\
-    \bra{\alpha}\mathcal{O}\ket{\beta} &=
-    \braket{\widetilde{\beta}|\mathcal{O}_a |\widetilde{\alpha}}
-\end{align}
-
-Proof may be found on page 292 of \cite{sakurai}.
-\section{TR operator}
-
-Finally I can turn to the TR operator. But before the formal discussion of
-time reversal, I should first note that the name \textbf{time reversal} is
-actually a misnomer. As mentioned in page 284, section 4.4 in 
-\cite{sakurai}:
-\begin{quote}
-    What we do in this section can be more appropriately characterized by
-    the term \textbf{reversal of motion}. Indeed, that is the phrase used
-    by E.  Wigner, who formulated time reversal in a very fundamental
-    paper written in 1932.
-\end{quote}
-This section can be found in section 4.4 of \cite{sakurai}.
-
-Outline:
-\begin{enumerate}
-    \item Deduce the property of TR symmetry operator from classical
-        picture.
-    \item The problem of degenracy and how a breaking of TR symmetry lifts
-        this degenracy.
-\end{enumerate}
-
-    \subsection{From classical notion to properties of TR symmetry}
-    \label{sec:From-classical-notion-to-property-of-TR-symmetry}
-    To get the time reversal operator, we can first look at the following
-    equality (let $T$ dentoes the time reversal operator):
-    \begin{align}
-        \left(1-\frac{iH}{\hbar}\delta t\right) T \ket{\alpha}
-        = T\left(1-\frac{iH}{\hbar}(-\delta t)\right)\ket{\alpha}
-        \label{eq:TRoper.fromClas2Quam.phyPic}
-    \end{align}
-    This follows from the following notion: a time reversed state is
-    equivalent to the original state at an earlier time. Recall that
-    $\left(1-\frac{iH}{\hbar}\delta t\right)$ produces an infinitesimal
-    time translation.
-
-    From equality \ref{eq:TRoper.fromClas2Quam.phyPic}, one finds:
-    \begin{align}
-        -iHT = T i H
-    \end{align}
-
-    One can show that \textbf{$T$ must be antilinear}. Because if one
-    assumes that $T$ is linear, one will find that the energy
-    spectrum for time reversal symmetric system will always has symmetric
-    energy spectrum (i.e. with both and symmetric positive and negative
-    energy), which is not true.
-
-    So we have:
-    \begin{itemize}
-        \item $T$ is antiunitary.
-        \item $T H=HT$ for a time reversal symmetric state.
-    \end{itemize}
-
-    Recall that $T= UK$, and $K$ is highly dependent on the basis
-    chosen. So $U$ will depend on the basis too. To get $T$ in a
-    basis $\ket{e_i}$, obviously we only need to consider the result of
-    $K\ket{e_i}$. This however, is hard to determine. However we can argue
-    that in case when the basis has some classical connection, then by the
-    Correspondance Principle we have, for example:
-    \begin{align}
-        T \hat{p} T^{-1}&= -\hat{p} \\
-        T \hat{x} T^{-1}&= \hat{x} \\
-        T \mathbf{J} T^{-1}&= -\mathbf{J}
-    \end{align}
-    with these one can easily find:
-    \begin{align}
-        T \ket{p} &= \ket{-p} \\
-        T \ket{x} &= \ket{x} \\
-        [x_i, p_j]T \ket{} &= i\hbar \delta_{ij} T\ket{}
-    \end{align}
-    where $\ket{}$ stands for any ket. Then clearly, $T$ is just
-    complex conjugation for wave function $\Psi(x)$. But $T$ acts on
-    $\Psi(p)$ will produces $\Psi^*(-p)$. The case for eigenstate of
-    spin is a little complicated, which will be discussed in section
-    \ref{sec:Time-reversal-operator-in-spin-j}.
-
-    \subsection{Properties of TR operator}
-    \label{sec:Properties-of-TR-operator}
-
-    Following is a useful theorem, which is easy to proof (proof can be
-    found on page 294 of \cite{sakurai}):
-    \begin{thm}
-        \label{thm:TRoper.fromCM2QM.TR_nondegen_real}
-        When Hamiltonian is invariant under time reversal and the energy
-        eigenket is nondegenerate; then the corresponding energy
-        eigenfunction is real (or, more generally, a real function times a
-        phase factor independent of $x$)
-    \end{thm}
-    Therefore, a complex eigenfunction almost means a degenrate state, or
-    the system is not invariant under time reversal.
-
-    The next theorem is about $T^2$. Classically, since there is only
-    two directions in time, we expect $T^2=1$. But quantum states are
-    rays, so there is the freedom of phase. Then $T^2 = \phi$ for
-    some $|\phi|^2=1$. But better, we have:
-
-    \begin{lemma}
-        $T^2 = \pm \mathbbm{1}$
-    \end{lemma}
-    \begin{proof}
-        Proof can be found on page 34 of \cite{bernevig}. But the proof is
-        so clever that I want to include it here. First observe that 
-        $U U^\dagger = \mathbbm{1}$, implies that $U^* U^T = \mathbbm{1}$
-        by transposing both sides. Next one use the expression $T=UK$ to
-        expand $T^2$, only to find that $U=\phi U^T$, this means that
-        $\phi^2=1$. Hence $\phi=\pm 1$.
-    \end{proof}
-
-    We then have the useful fact:
-    \begin{fact}
-        For any kets $\ket{\alpha},\ket{\beta}$, we have
-        \begin{align}
-            \pm \braket{\alpha|T\beta} = 
-                \braket{\beta|T\alpha}
-        \end{align}
-        The sign is the same as in $T^2=\pm 1$. Specifically, one has
-        \begin{align}
-            \braket{\alpha |T \alpha} = 0
-        \end{align}
-        when $T^2= -\mathbbm{1}$.
-    \end{fact}
-    \begin{proof}
-        This is simple by using 
-        $\braket{T\alpha|T\beta} = \braket{\beta|\alpha}$, 
-        and replacing $\ket{\alpha}$ with $\ket{T \alpha}$.
-    \end{proof}
-
-    \subsection{Time reversal operator in system with spin 
-    \texorpdfstring{$j$}{}}
-    \label{sec:Time-reversal-operator-in-spin-j}
-    Using my guess \ref{eq:revSpin.getMatRot.Sn.Snket}:
-    \begin{align*}
-        \ket{\hat{\mathbf{n}};+}= e^{-iS_z \alpha/\hbar}
-        e^{-iS_y \beta/\hbar} \ket{+}
-    \end{align*}
-    and by similar argument in that section \ref{sec:Eigenstate_for_Sn},
-    we can argue that the state with opposite direction is
-    \begin{align}
-        \ket{\hat{\mathbf{n}};-}= e^{-iS_z \alpha/\hbar}
-        e^{-iS_y (\beta+\pi)/\hbar} \ket{+}
-    \end{align}
-    Again, I am using notation $\ket{-}$ to denotes $\ket{j,-j}$.
-
-    Since time reversal reverses the angular momentum, I expects:
-    \begin{align}
-        T \ket{\hat{\mathbf{n}};+} = \eta \ket{\hat{\mathbf{n}};-}
-    \end{align}
-    where $\eta$ is just some unnecessay factor.
-
-    With above relationship, one can easily see that:
-    \begin{align}
-        T = \eta e^{-i\pi J_y/\hbar}K
-    \end{align}
-    The proof is trivial for $j=\frac{1}{2}$, but I cannot find a proof
-    for other values of $j$.
-
-    It is also interesting to note that in general:
-    \begin{thm} \begin{align}
-        \label{eq:TRoper.TRoper.square_minus}
-        T^2 &= -1 \text{ if $j$ is a half-integer} \\
-        T^2 &= 1 \text{ if $j$ is an integer}
-        \label{eq:TRoper.TRoper.square_plus}
-    \end{align} \end{thm}
-    However, this can only be proved when $j=\frac{1}{2}$, in which case
-    the proof is also straightforward if we use the formula mentioned in
-    section \ref{sec:About-exp(-i*pi-S_y/hbar)}.
-
-    However, if we imagine a spin $j$ system as composed all just of
-    electrons of spin $\frac{1}{2}$, then we have a strong argument that
-    the above formula is true.
-    \subsection{Kramer's theorem and the lifting of degenracy}
-    \label{sec:Kramers-theorem-and-the-lifting-of-degenracy}
-    When one is concerned with the energy spectrum, one encounters the
-    Kramer's theorem, which says:
-    \begin{thm}[Kramer's theorem]
-        For a system with halt-integer $j$ spin, the degree of degeneracy
-        is at least two.
-    \end{thm}
-    \begin{proof}
-        Let $\ket{n}$ be an energy eigenstate. If the system is time
-        reversal symmetric, i.e. $[H,T]=0$, then $T \ket{n}$ is
-        another energy eigenstate with the same energy. Supposing there is
-        no degeneracy, then we have
-        $$ \ket{n} = e^{i\eta}T\ket{n}$$
-        for some $\eta\in \mathbb{R}$. Apply $T$ on both sides, then
-        we have
-        \begin{align*}
-            e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
-            &= T \ket{n} = e^{i\eta} \ket{n}
-        \end{align*}
-        Clearly this is a contracdiction unless $T^2=1$, which is
-        true only for interger spin system by equation
-        \ref{eq:TRoper.TRoper.square_plus} and
-        \ref{eq:TRoper.TRoper.square_minus}.
-    \end{proof}
-    Another way to show this is presented in page 37 of
-    \cite{bernevig}. That method is too troublesome and basis dependent 
-    \footnote{Borrowing the jargon of mathematicians, not canonical,
-        geometric, or intrinsic.}
-    to be shown here.
-    But it shows an interesting fact that $T^2=-1$, actually
-    implies that $U$, its unitary component mentioned in section
-    \ref{sec:Property-of-symmetry-operator}, is antisymmetric. This is
-    obvious when one juxtapose the following two facts:
-    $$ U (U^*)^T = \mathbbm{1}$$
-    $$ T^2 = UKUK = U U^* = -\mathbbm{1} $$
-
-    By Kramer's theorem, one also says that for system with half-integer
-    spin, one \textit{lift the degenracy by breaking the time reversal
-    symmetry of the system.}
-
-        \subsubsection{Argument against Bernevig's result}
-        \label{sec:Argument again Bernevig's result}
-
-        An additional point by Bernevig is about the transition probability
-        $\bra{T \psi}H\ket{\psi}$ from a state to its time reversed
-        state.
-
-        Here I first mention two points:
-        \begin{enumerate}
-            \item When $T H=HT$, and $T=UK$, one can deduce
-                $UH^* = HU$, or $U^*H=H^*U^*$, i.e.
-                $(U^*)_{mp}H_{pn}=(H^*)_{mp}(U^*)_{pn}$.
-            \item As mentioned before in section
-                \ref{sec:Kramers-theorem-and-the-lifting-of-degenracy},
-                $U$ is antisymmetric, so $U^*$ is antisymmetric too.
-        \end{enumerate}
-
-        Then begin Bernevig's wrong calculation (Summation implied when
-        index is repeated twice):
-        \begin{align}
-            & \braket{T\psi|H|\psi} = (U_{mp}K\psi_p)^*H_{mn}\psi_n 
-            \nonumber\\
-            =& U_{mp}^* \psi_p H_{mn} \psi_n 
-            \nonumber\\
-            =& (U^\dagger)_{pm}\psi_p H_{mn}\psi_n 
-            \label{eq:TRoper.Kramer.bernevig1}
-            \\
-            =& (U^\dagger)_{pm}\psi_p (THT^{-1})_{mn} \psi_n 
-            \nonumber\\       
-            =& (U^\dagger)_{pm}\psi_p \left(U_{mr}KH_{rq}(-U_{qn}K)\right)
-                \psi_n
-            \nonumber\\       
-            =& - (U^\dagger)_{pm}\psi_p \left(U_{mr}H^*_{rq}U^*_{qn}\right)
-                \psi_n
-            \nonumber\\       
-            =& - \psi_p \left((U^\dagger)_{pm}
-                U_{mr}\right)H^*_{rq}U^*_{qn}\psi_n
-            \nonumber\\       
-            =& - \psi_p H^*_{pq}U^*_{qn}\psi_n
-            \nonumber\\       
-            \text{(by point 1)}=& - \psi_p U^*_{pq}H_{qn}\psi_n 
-            \nonumber\\       
-            \text{(by point 2)}=& U^*_{qp}\psi_p H_{qn} \psi_n 
-            \nonumber\\       
-            \text{(by the first line)}=& \braket{T\psi|H|\psi}
-        \end{align}
-        So I see that he just circles back to the origin...
-
-        No I give an argument that statement in page 37 of
-        \cite{bernevig} cannot be true.
-        \begin{argument}
-            Suppose we can prove that $\braket{T \psi|H|\psi}=0$.
-            Then $\braket{\psi|HT |\psi}=0$, notice that $H=T
-            HT^{-1}$, and $T^{2}=-1$, one can see that
-            $\braket{\psi|H|\psi}=0$. Such is too strong an result. For
-            example, if $\ket{\psi}$ is any eigenket of $H$, then our
-            argument shows that its eigenvalue is zero. Does this means
-            that $H$ is just the trivial operator $0$? Of course not!
-            Therefore the Bernevig's result is wrong.
-        \end{argument}
-
-    \subsection{Time reversal symmetry in crystal}
-    \label{sec:Time-reversal-symmetry-in-crystal}
-
-        \subsubsection{Time reversal symmetry in spinless crystal}
-        \label{sec:Time-reversal-symmetry-in-spinless-}
-        Since there is not spin, time reversal symmetry does not alter a
-        creation/annihilation of a particle. Then:
-        \begin{align}
-            Tc_j T^{-1} = c_j
-        \end{align}
-        Then, in the fourier expansion of $c_j$:
-        \begin{align}
-            c_j = \sum_k e^{ikR_j} c_k
-        \end{align}
-        Since $T$ acting on the left, will change $e^{ikR_j}$ into
-        $e^{-ikR_j}$, then naturally:
-        \begin{align}
-            Tc_k T^{-1} = c_{-k}
-        \end{align}
-        Then, for a time reversal symmetric system, let 
-        $H = \sum_k h(k)c_k^\dagger c_k$. Since $T H T^{-1}=H$,
-        $T$ has to flip the sign of $k$ again, so:
-        \begin{align}
-            T h(k) T^{-1} = h(-k) \,\text{(For TR symmetric
-            state)}
-            \label{eq:TRoper.trInCry.trInSpinless.hk}
-        \end{align}
-
-        \begin{remark}[Implications for crystal systems]
-            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
-            $\phi(k)$ and $T\phi(k)$ corresponding to two eigenstate in
-            $k$ and $-k$. But since $\bra{\alpha}\ket{T\alpha}$ is not
-            necessarily $0$ for $T^2= \mathbbm{1}$, We cannot prove
-            that we have a double generacy because the two candidate
-            $h(k)$ and $h(-k)$ might be the same wave function.
-        \end{remark}
-
-        Another important implication is that
-        \begin{thm}
-            Hall Conductance vanishes for Spinless time
-            symmetric system.  
-        \end{thm}
-        \begin{proof}
-            Recall we have:
-            \begin{align}
-                \sigma_{ij} = \int \frac{\diff k_x\diff k_y}{(2\pi)^2}
-                \sum_{a=1}^{m} (-i) F_{jk}^a(\vb{k})
-                = \frac{1}{(2\pi)^2} \sum_{a=1}^m \gamma_a
-            \end{align}
-            i.e., The Hall conductivity is an integral over the filled
-            bands of the Berry curvature. (See (3.79) of\cite{bernevig})
-
-            Here 
-            $$F_{ij}(\vb{k}) = -i \left( \braket{\partial_i
-            u(k)|\partial_j u(k)} - (i\leftrightarrow j) \right)$$
-            is the Berry field strength.
-            For system with TR symmetry, we have
-            $$ u(k) = T u(-k)$$
-            (Note that $T$ flips the sign of $k$) Since $T$ is
-            antiunitary, we have $ u(-k) = u(k)^*$. Therefore
-            $\braket{\partial_i u(-k)|\partial_j u(-k)} = 
-              \braket{\partial_j u(k)|\partial_i u(k)}$
-            So:
-            \begin{equation}
-                F_{ij}(\vb{-k}) = - F_{ij}(\vb{k})
-            \end{equation}
-            Therefore $F_{ij}$ is a odd function. So its integration
-            over the whole BZ is zero, i.e. $\sigma_{ij}$ is zero.
-        \end{proof}
 
@@
 \label{sec:Anchor}
+
 \begin{thebibliography}{1}
-    \bibitem{sakurai} Modern Quantum Mechanics. J.J. Sakurai.
-    \bibitem{bernevig} Introduction to Topological Insulators. Bernevig.
-    \bibitem{math.SE-adjoint-of-antilinear}\href{http://physics.stackexchange.com/questions/45227/existence-of-adjoint-of-an-antilinear-operator-time-reversal}{Existence of adjoint of an antilinear operator, time reversal}
+    \bibitem{kitaev-Periodic} Alexei Kitaev. Periodic table for
+    topological insulators and superconductors.
+
 \end{thebibliography}

### 2016-11-06 Lecture note - Group Theory in Physics/sections/20161031.tex
Finding components in representation (Group theory in physics).

@@
     \begin{equation}
-        \sum_{j} m_j^2 = N = \abs{G}
+        \sum_{j} d_j^2 = N = \abs{G}
     \end{equation}
@@
     hence we have:
-        $$\sum_{j} m_j^2 \leq N $$
+        $$\sum_{j} d_j^2 \leq N $$
     To make the inequality an equality, it is suffice to prove that
@@
 \end{coro}
+
+Let the conjugacy classes be labeled by $K_a$, $a=1,\cdots,k$. $k$ is
+the number of conjugacy classes. Let $n_a$ be the number of group
+elements in each conjugacy class $K_a$. Consider one thing:
+\begin{itemize}
+    \item Characters is invariant within each conjugacy classes
+\end{itemize}
+One can derive (pp. 47 of \cite{Ludeling})
+\begin{equation}
+    \sum_a n_a \chi^{i,a}(\chi^{j,a})^* = N\delta^{ij}
+    \label{eq:20161031-nxx-is-Ndelte}
+\end{equation}
+here $\chi^{i,a}$ menas the character in the $i$'s irreducible
+representation of the group element in $a$'s conjugacy class.
+Then the vectors (labeled by each irreducible representation $i$)
+\begin{equation}
+    \frac{1}{\sqrt{N}}
+    (\sqrt{n_1}\chi^{i,1},\cdots,\sqrt{n_k}\chi^{i,k})
+\end{equation}
+are orthonomal. Notice that given a $k$-dimensional space, we in
+effect show cases $r$ linear independence vectors. Therefore we must
+have 
+\begin{equation}
+    r \leq k
+\end{equation}
+
+    \subsubsection{Finding Components of Representations}
+    \label{sec:Finding-Components-of-Representations}
+    \begin{remark}
+        It's easy to see that if $D=aD^1\oplus bD^2$, one has $\chi =
+        a\chi^1 + b\chi^2$.
+    \end{remark}
+    Now we consider the coefficients in the general case. Suppose a
+    representation $D$ has:
+    \begin{equation}
+        D = \oplus a^i D^i
+    \end{equation}
+    where the sum is taken over all irreducible representations
+    $D^i$. We have:
+    \begin{equation}
+        X = \sum_{i} a^i \chi^i
+    \end{equation}
+    It is calculated (page 47 to 48 of \cite{Ludeling}) using equation
+    \ref{eq:20161031-nxx-is-Ndelte},
+    that
+    \begin{equation}
+        \sum_a n_a \chi^{i,a*}X^a = N a^i
+    \end{equation}
+    so
+    \begin{equation}
+        a^i = \frac{1}{N} \sum_a n_a(\chi^{i,a})^* X^a
+        \label{eq:20161031-components-formula}
+    \end{equation}
+    From now on, we always denote the class of identity by $K_1$, and
+    the corresponding character in that representation by
+    $\chi^{i,1}$. Clearly $\chi^{i,1}\equiv d_i$.
+    \begin{ex}
+        If $D$ is the regular representation. It is easy to see that
+        \begin{equation}
+            X_\text{reg}(g) = N \delta_{g,e}
+        \end{equation}
+        where $e$ is the unit element in the group.
+        Then
+        \begin{equation}
+            a^i = \frac{1}{N}\sum_a n_a (\chi^{i,a})^* X^a_\text{reg}
+            = \frac{1}{N} (\chi^{i,1})^* X^1_\text{reg} = 
+            \frac{1}{N} d_i N = d_i
+        \end{equation}
+    \end{ex}
+    \begin{remark}[Criterion for irreduciblility]
+        The above result gives us one way to assess the level of
+        irreduciblility of a representation. Direct calculation shows
+        (with the help of equation
+        \ref{eq:20161031-components-formula})
+        \begin{equation}
+            \sum_a n_a (X^a)^* X^a = N \sum_i (a^i)^2
+        \end{equation}
+        So for a irreducible representation $X$, we have $\sum_a n_a
+        (X^a)^* X^a= N$. For other representations, we have $\sum_a
+        n_a (X^a)^* X^a= N/2N/3N/\cdots$. In this way one somehow
+        measures qualitatively how complex this representation is.
+    \end{remark}

### 2016-11-07 Lecture note - Group Theory in Physics/sections/20161031.tex
Update notes about group theory. (Substantial modification is required actually for this notes).

@@
 \begin{equation}
+    \label{eq:20161031-r_leq_k}
     r \leq k
@@
     \begin{equation}
+        \label{eq:20161031-X_components}
         X = \sum_{i} a^i \chi^i
@@
         \begin{equation}
+            \label{eq:20161031-X-characters}
             X_\text{reg}(g) = N \delta_{g,e}
@@
         \begin{equation}
+            \label{eq:20161031-X_components_reg}
             a^i = \frac{1}{N}\sum_a n_a (\chi^{i,a})^* X^a_\text{reg}
@@
     \end{remark}
+
+    It is also very easy to use the idea of equation
+    \ref{eq:20161031-X_components} to the following result:
+    \begin{thm}
+        Two representations are equivalent if and only if they have
+        the same character function.
+    \end{thm}
+    \subsubsection{Conjugacy Classes and Representations}
+    \label{sec:Conjugacy-Classes-and-Representations}
+
+    Now we proves an refined version of inequality
+    \ref{eq:20161031-r_leq_k}:
+    \begin{thm}
+        For a group $G$, we have
+        \begin{equation}
+            r=k
+        \end{equation}
+        Here $r$ is the number of different irreducible
+        representations of $G$, $k$ is the number of different conjugacy
+        classes of $G$.
+    \end{thm}
+    \begin{ex}
+        It is interesting for symmetric group. Because we have known
+        from remark \ref{rmk:20161010-conjugacy_class_in_Sn} that the
+        number of symmetric group's conjugacy class is an
+        combinatorical problem. So its number of irreducible
+        representation is also a combinatorical number.
+    \end{ex}
+    \begin{proof}
+        To prove the theorem, we somehow reverse the logic. We want to
+        show that there are $k$ vectors, labled by conjugacy classes,
+        in a $r$-dimensional vector space. These $k$ vectors forms
+        someting resembles 
+        $\sum_i \chi^{i,a}\chi^{i,b}\approx \delta^{ab}$.
+
+        We first look at the regular representation. The previous
+        section shows (by equation \ref{eq:20161031-X_components},
+        \ref{eq:20161031-X-characters}, and
+        \ref{eq:20161031-X_components_reg}):
+        \begin{equation}
+            \sum_{i\in\text{ I.R.}} \chi^{i,1}\chi^{i,a} = N
+            \delta_{a,e}
+        \end{equation}
+        Here $i$ denotes different irreducible representations, $a$
+        for conjugacy classes. The delta function is $1$ only when $a$
+        is the unit conjugacy class.
+
+        This shows that character of the identity, considered as a
+        $r$-component vector in the space of representation, is
+        orthogonal to the other characters. We have to extend this to
+        all classes.
+
+        Now consider the class vectors:
+        \begin{defi}[Class vector $\mathcal{K}_a$]
+        \nomenclature{Class vector $\mathcal{K}_a$}{\nomrefpage.}
+            \begin{equation}
+                \mathcal{K}_a = \sum_{g\in K_a} g
+            \end{equation}
+            where $a$ represents the conjugacy class labeled
+            by $K_a$.
+        \end{defi}
+        It has the following property: it is invariant under
+        conjugation
+        \begin{equation}
+            h\mathcal{K}_a h^{-1} = \mathcal{K}_a
+        \end{equation}
+        since a conjugacy are those elements that can be related by a
+        conjugation. From this, we have obviouisly
+        \begin{equation}
+            g\mathcal{K}_a \mathcal{K}_b g^{-1} = \mathcal{K}_a
+            \mathcal{K}_b
+        \end{equation}
+        Thus $\mathcal{K}_a \mathcal{K}_b$ is also a set related to
+        each other 
+    \end{proof}
+% 1. 自共轭 iff 特征 实数
+% 2. 非自共轭 至少一个群元 复数 -》 成对出现
+% 3. 实表示 是 自共轭
+% 4. 特征 实数 不一定 实表示 (so 有 自共轭 但非 实的表示)
+% 5. thm 5 on pp. 68.

### 2016-11-07 Lecture note - Group Theory in Physics/sections/Skipped-Two-Lectures.tex
New notes to the group theory - representation.
New A.Q.M Notes. About trace in Q.M.
Update notes about group theory. (Substantial modification is required actually for this notes).

@@
         \begin{itemize}
-            \item Character of representation.
+            \item Character of representation. (Notes for this part is
+                delayed to be contained in the next lecture's note).
             \item Equivalence between representation.
@@
 \begin{remark}
+    \label{rmk:20161010-conjugacy_class_in_Sn}
     Since a cycle type is just a set of unordered integer partition of
@@
 
-        Note also here $S$ represents a transformation of basis. If we
-        know the transformation of vectors $X$, then
+        Note also here $S$ represents a transformation of vector. If we
+        know the transformation of basis $X$, then
         \begin{equation}
@@
 \end{remark}
-
-\begin{remark}
-    This representation is not 
-\end{remark}

### 2016-11-08 Draft/sections/misc-math.tex
Minor updates to physicist-taper.sty. Adding some pitfalls to math in Draft.

@@
 \end{proof}
+
+\subsection{Common Pitfalls}
+\label{sec:Common Pitfalls}
+    \subsubsection{Tensors}
+    \label{sec:Tensors}
+
+    The $k$-th component $\psi_k$ of the transpose of $(A\phi)^i = A^i_k
+    \phi^k$ is still $A^i_k \phi^k$, although we have to be careful about
+    the position of the index.
+
+    \subsubsection{Transpose}
+    \label{sec:Transpose}
+
+    In matrix theory, if we ahave the following structure:
+    $$\braket{x,y} := x y$$
+    here $x,y$ are regarded as two column vectors in vector space $V$.
+    Then the transpose of a linear transformation $A:V\to V$ is defined
+    as
+    \begin{defi}[Transpose]
+    \nomenclature{Transpose}{\nomrefpage.}
+        $\tensor[^t]{A}{}:V^* \to V^*$ is such that:
+        \begin{equation}
+            \braket{x,Ay} = \braket{\tensor[^t]{A}{}x,y}
+        \end{equation}
+        for any $x,y\in V$.
+    \end{defi}
+
+    In my notation, it maps $x^n\to A^m_n x^m$, or $x_n\to A^m_n x_m$.
+    (My notation is non-standard, but I think it expresses the idea).

### 2016-11-09 General Physics Formula/General Physics Formula.tex
New notes in Draft, about a specific function.
Some micellaneous useful physical ponts.

--- 2016-10-26 GRE Physics Prep/General Physics Formula.tex
@@
 This is a collection of important formulae in Fundamentals of Physics
-Extended Version by Halliday and Resnick.
+Extended Version by Halliday and Resnick, and some other formulae from
+other sources. Although this was initially intended to be preparation
+for GRE physics exam, I found such a review quite useful and will
+continue to update this document whenever I found something useful.
 }
@@
 
-\paragraph{Rotation matrix}
-Active rotation in the counter-clockwise $\theta$:
-\begin{equation}
-    \left(
-    \begin{array}{cc}
-        \cos{\theta} & -\sin{\theta} \\
-        \sin{\theta} & \cos{\theta} \\
-    \end{array}
-    \right)
-\end{equation}
+\include{sections/math}
 
@@
 \end{align}
+
+\textbf{RC Circuit}
+\begin{align}
+    Q = Q_0 e^{-t/(RC)}
+\end{align}
 Predicting RLC current (\textbf{pp.843 of \cite{book}})
@@
 \end{align}
-% \begin{itemize}
-%     \item \textbf{Resisitor} $V_R$ is in phase with $I$.
-%     \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
-%     \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
-% \end{itemize}
+\begin{itemize}
+    \item \textbf{Resisitor} $V_R$ is in phase with $I$.
+    \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
+    \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
+\end{itemize}
 \paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})
 
+\begin{defi}[Permittivity = Dielectric Constant]
+\nomenclature{Permittivity = Dielectric Constant}{$\varepsilon$, \nomrefpage.}
+    $\varepsilon$
+\end{defi}
+\begin{defi}[Permeability]
+\nomenclature{Permeability}{$\mu$, \nomrefpage.}
+    $\mu$
+\end{defi}
 \begin{align}
@@
 
+\paragraph{de Broglie Waves}
+(\href{https://en.wikipedia.org/wiki/Matter_wave}{Wikipedia - Matter
+Wave})
+\begin{align}
+    \lambda &= \frac{h}{p} \\
+    p &= \frac{h}{\lambda} = \hbar\frac{2\pi}{\lambda} = \hbar k \\
+    p &= \frac{hf}{c} \\
+    f &= \frac{E}{h} \\
+    E &= hf = \hbar2\pi f = \hbar\omega
+\end{align}
 \paragraph{Photon} (\textbf{pp.1077 ch38 of \cite{book}})

### 2016-11-10 Notes of various papers/Classification of topological quantum matter with symmetries. Rev.M.P/doubts.tex
New notes for the review paper about topological classifications, inside are some unclear points about that paper.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\makenomenclature

\title{Notes for Classification of topological quantum matter with
symmetries}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
As title suggests.
}
\tableofcontents
\paragraph{Asks}
\begin{enumerate}
    \item Page 6. Why the scalar in Schur's lemma becomes of unit lenght.
    \item page 9. What does it mean by:
        \begin{quote}
            Note that unitary symmetries, which commute with the
            Hamiltonian, allow us to bring the Hamiltonian into a
            block diagonal form.
        \end{quote}
    \item page 9, table I. When he talks about \textit{codimension},
        what is the dimension of the whole space? ($3$? $3+1$?).
        Similar problem also exists in page 10.
        Note, he mentions codimension of gaples modes on page 11. He
        asserts that codimension $1$ means $1$ dimension less than the
        bulk. But it should be strange to compare the dimension of
        defects with the dimension of the bulk.

        Possibly related
        resources:\href{http://www.virginia.edu/bohr/mse209/chapter4.htm}
        {Online notes about Imperfection}:
        \begin{itemize}
            \item $0$D (zero dimension) – point defects: vacancies and
                interstitials. Impurities.
            \item 1D – linear defects: dislocations (edge, screw,
                mixed) 
            \item 2D – grain boundaries, surfaces.  
            \item 3D – extended defects: pores, cracks.
        \end{itemize}

        Note: it is finally defined on page 12. that is:
        codimension of defect $d_c:= d_\text{bulk} - d_\text{defect}$.
    \item page 6, what does it mean by saying \textit{"unitary
        symmetry"}.
    \item page 10, what is a \textit{"quantum phase diagram"}.
    \item page 11, what does he says, \textit{"Topological properties of
        adiabatic cycles can also be discussed in a similar manner."}.
        Does this mean that all previous classification does not
        concern the adiabatic cycles? What is \textit{"adiabatic
        cycles"} exactly in his language?
    \item page 12, "disinclination" is what kind of defect? Any books
        on crystall defects?
    \item page 12, is the \textit{"mass gap"} a massive gap or a gap
        composed of mass?
    \item page 12, about the $D$: if $d_c=1$ (line defect in a
        $2d$-bulk), then $D=0$. So a line is wrapped by a point?
        also, on fig. 2, the ($D=2,d=1$) gives a $d_\text{defect}=-1$!
        Judging from this graph, a $d_\text{defect}=-1$ means a
        temporal defect. Is this true?
\end{enumerate}

\paragraph{Doubts}
\begin{enumerate}
    \item page 10. Amazingly, he says, \textit{"all TIs and TSCs in
        the ten AZ symmetry classes are stable against disorder, and
        hence the assumption of translation invariance is not at all
        necessary"}.  How can translational invariance be ignored?
    \item 
\end{enumerate}
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    %\bibitem{book} 
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-11-10 Notes of various papers/Classification of topological quantum matter with symmetries. Rev.M.P/doubts.tex
New notes from reading that paper.

@@
         cycles"} exactly in his language?
+
+        Note: "adiabatic cycle" may refer to a cycle in phase space
+        (most likely argumented by time $t$ parameter). "Adiabatic"
+        describes the process to be adiabatical, i.e. vary very
+        slowly. The detailed criterion is on page 12, just above
+        equation 3.6:
+        \begin{equation}
+            \xi \abs{\Delta_r H(k,r)}<<\varepsilon_g
+        \end{equation}
     \item page 12, "disinclination" is what kind of defect? Any books
@@
 
+\paragraph{Ask friends}
+\begin{enumerate}
+    \item page 13. What is a homotopy type?
+\end{enumerate}
 \paragraph{Doubts}
@@
         necessary"}.  How can translational invariance be ignored?
-    \item 
+    \item page 12, he mentions:
+        \begin{quote}
+            As in the case of gapped TIs and TSCs, we are interested
+            in the highest dimension strong topologies of the defect
+            that do not involve lower dimensional cycles
+        \end{quote}
+        I don't get what "strong topologies" and "lower dimensional
+        cycles" mean.
+    \item page 13 right column, again he mentioned the strong topology
+        and compactify the space into a $S^{d+D}$. I don't get why:
+        \begin{quote}
+            Physically this means the defect band theory are assumed
+            to have trivial winding around those low-dimensional
+            cycles.
+        \end{quote}
+
+    \item page 13, What does this mean:
+        \begin{quote}
+            It deformation retracts from the defect complement of
+            spacetime.
+        \end{quote}
+
+\end{enumerate}
+
+\paragraph{Revisit}
+\begin{enumerate}
+    \item page 12, bottom. How this procedure of relating real and
+        complex classification is done?
 \end{enumerate}

### 2016-11-12 Lecture note - Group Theory in Physics/sections/20161031.tex
Finished a proof of "irreducible repre" = "conjugacy class".

@@
             \delta_{a,e}
+            \label{eq:20161031-x1xa-Ndelta}
         \end{equation}
@@
             h\mathcal{K}_a h^{-1} = \mathcal{K}_a
+            \label{eq:20161031-hKh-K}
         \end{equation}
-        since a conjugacy are those elements that can be related by a
+        since a conjugacy class are those elements that can be related by a
         conjugation. From this, we have obviouisly
@@
         \end{equation}
-        Thus $\mathcal{K}_a \mathcal{K}_b$ is also a set related to
-        each other 
+        Thus $\mathcal{K}_a \mathcal{K}_b$ is also a vector whose
+        components are related to
+        each other with conjating like relations. It is then a linear
+        combination of class vectors:
+        \begin{equation}
+            \label{eq:20161031-algebra-like-relation}
+            \mathcal{K}_a\mathcal{K}_b = \sum_c c_{abc} \mathcal{K}_c
+        \end{equation}
+        where $c_{abc}$ are coefficients.
+        (it is mentioned that such a form will make those classes an
+        algebra, named class algebra\nomenclature{class
+        algebra}{\nomrefpage}, but now I will not talk on that.
+
+        Now, consider the class vectors $\mathcal{K}_a$ in certain
+        irreducible representation $\mu$:
+        \begin{equation}
+            D^a_{(\mu)} := \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)
+        \end{equation}
+        It commutes with all $D_{(\mu)}(h)$, $h\in G$, since
+        $$D_{(\mu)}(h) \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)
+        D_{(\mu)}(h^{-1})= \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)$$
+        Then by Schur's lemma, $D^a_{(\mu)}= \lambda^a_\mu
+        \id$.
+        Take the trace of $D^a_{(\mu)}$, one will easily find:
+        \begin{equation}
+            \label{eq:20161031-lambda-is}
+            \lambda^a_\mu = \frac{n_a\chi^a_{\mu}}{\chi^1_\mu}
+        \end{equation}
+        Meanwhile, by the algebra like relation
+        \ref{eq:20161031-algebra-like-relation}, one finds:
+        \begin{equation}
+            \lambda^a_\mu \lambda^b_\mu = \sum_c c_{abc} \lambda^c_\mu
+        \end{equation}
+        combine this with the expression for $\lambda$:
+        \ref{eq:20161031-lambda-is}, one has:
+        \begin{equation}
+            n_a n_b \chi^a_\mu \chi^b_\mu = \chi^1_\mu\sum_c
+            c_{abc}n_c\chi^c_\mu
+        \end{equation}
+        Now, one can see this pattern and I would not expatiate on
+        it. The only remaining elements are equation
+        \ref{eq:20161031-x1xa-Ndelta} and the fact that
+        \begin{equation}
+            c_{abe} = \delta_{b,a^{-1}} n_a
+        \end{equation}
+        where $e$ is the unit element in group $G$, and $a^{-1}$ is
+        the inverse class of $a$. This is like saying that only the
+        product of $a$ with its inverse class can have unit elements.
+        With these one can easily calculate and get
+        \begin{equation}
+            \sum_{\mu \in \text{I.R.}} \chi^{a*}_\mu\chi^b_\mu = 
+            \frac{|G|}{n_a} \delta^{ab}
+        \end{equation}
+        So we have:
+        \begin{equation}
+            \sqrt{\frac{n_a}{|G|}}(\chi^a_1,\chi^a_2,\cdots,\chi^a_r)
+        \end{equation}
+        a series of $k$ orthonomal $r$-dimensional vectors. Hence
+        \begin{equation}
+            k\leq r
+        \end{equation}
+        Then, together with previous result, we have:
+        \begin{equation}
+            r = k
+        \end{equation}
     \end{proof}

### 2016-11-12 Lecture note - Group Theory in Physics/sections/20161031.tex
Finished another proof for "conjugacy class"="irrep" in group representation theory.

@@
         \frac{N}{d_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+        \label{eq:20161031-ortho-dd-1}
     \end{equation}
@@
         \frac{N}{d_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+        \label{eq:20161031-ortho-dd-2}
     \end{equation}
@@
             \frac{|G|}{n_a} \delta^{ab}
+            \label{eq:20161031-ortho-character}
         \end{equation}
@@
     \end{proof}
+    Another proof provided by the book \cite{book}.
+    \begin{defi}[Group function]
+    \nomenclature{Group function}{\nomrefpage.}
+        A $\mathbb{C}$-linear function $F:\mathbb{C}[G]\to
+        \mathbb{C}$ is called a group function.
+    \end{defi}
+    He first shows that:
+    \begin{thm}
+        The matrix elements of unitary irreducible representations of
+        finite groups may form an complete orthogonal basis of group
+        algebra. Any group function can be expanded in terms of them.
+    \end{thm}
+    \begin{proof}
+        Let $D^j_{\mu\nu}(g)$, where $g\in G$, $j$ labels irreducible
+        representations, $\mu\nu$ labels matrix element, be one such
+        element. Then we have, for any function $F:G\to \mathbb{C}$,
+        \begin{align}
+            F(h) &= \sum_{j,\mu\nu} C^j_{\mu\nu} D^j_{\mu\nu}(h) \\
+            C^j_{\mu\nu} &= \frac{d_j}{|G|}
+            \sum_{h\in G} D^j_{\mu\nu}(h)^* F(h)
+            \label{eq:20161031-cjmv}
+        \end{align}
+        This can be easily get using the orthonomal relationship.
+        Also notes that we have $\sum_j d^2_j = |G| =
+        \operatorname{Dim}(\mathbb{C}[G])$, confirming that the
+        dimension of basis agree with the dimension of group algebra.
+    \end{proof}
+    \begin{defi}[Class function]
+    \nomenclature{Class function}{\nomrefpage.}
+        A class function is a group function $f$, whose satisfies:
+        \begin{equation}
+            f(s g s^{-1}) = f(g)
+        \end{equation}
+        for any $s,g\in G$.
+    \end{defi}
+    Similarly, we have:
+    \begin{thm}
+        The character $\chi^j(g)$ ,where $j$ labels irreducible
+        representation, $g\in G$, of unitary irreducible representations of
+        finite groups may form an complete orthogonal basis of class
+        functions.
+    \end{thm}
+    \begin{proof}
+        This is easy if one realize that, since $f(sgs^{-1}=f(g)$ for
+        any $s,g\in G$, one has
+        \begin{equation}
+            f(g) = \frac{1}{|G|} \sum_{s\in G} f(s g s^{-1})
+        \end{equation}
+        The rest is to use result mentioned in proving the group
+        function basis above. One finally get:
+        \begin{equation}
+            f(g) = \sum_j \left(\frac{1}{d_j}\sum_\mu
+            C^j_{\mu\mu}\right) \chi^j(g)
+        \end{equation}
+        where $C^j_{\mu\mu}$ is defined in equation
+        \ref{eq:20161031-cjmv}.
+        Or we can write it in another way:
+        \begin{align}
+            F(g) &= \sum_j C_j \chi^j(g) \\
+            C_j &= \frac{1}{|G|} \sum_{h\in G}\chi^j(h)^* F(h)
+        \end{align}
+        the formula for $C_j$ is also easily found by simply
+        calculating $\sum_{h\in G}\chi^j(h)^* F(h)$.
+    \end{proof}
+    Note that the above result is enough to show that the number of
+    irreducible representations is the same as the dimension of
+    class functions (consider it as a vector space).
+
+    The book \cite{book} also rephrase it in page 63, as:
+    \begin{quote}
+        Define two matrices $U_{m,n}$ and $V_{m,n}$, whose elements
+        are defined by:
+    \begin{align}
+        U_{g,j\mu\nu} &:= \sqrt{\frac{d_j}{|G|}} D^j_{\mu\nu}(g) \\
+        V_{a,j} &:= \sqrt{\frac{n_a}{|G|}} \chi^j_a
+    \end{align}
+    The two matrices are unitary. This is true by equation
+    \ref{eq:20161031-ortho-dd-2} and equation
+    \ref{eq:20161031-ortho-character}. Note here $g\in G$, $j$ labels
+    different unitary irreducible representations, $\mu,\nu$ labels
+    the matrix element in that representation, $a$ labels conjugacy
+    classes. The labels $j\mu\nu$ together form the second index of
+    matrix $U_{m,n}$. For convenience, I type all the orthonomal
+    relationship together:
+    \begin{align}
+        &\text{Equation \ref{eq:20161031-ortho-dd-2}:} \nonumber \\
+        & \sum_{h\in G} D^{i*}_{\mu\rho}(h)D^j_{\nu \lambda}(h) =
+        \frac{N}{d_j} \delta_{ij} \delta_{\mu\nu}\delta_{\rho\lambda}
+        \\
+        &\text{Equation \ref{eq:20161031-ortho-character}:} \nonumber \\
+        & \sum_{\mu \in \text{I.R.}} \chi^{a*}_\mu\chi^b_\mu = 
+            \frac{|G|}{n_a} \delta^{ab} 
+    \end{align}
+
+    \end{quote}
+
 % 1. 自共轭 iff 特征 实数

### 2016-11-12 Lecture note - Group Theory in Physics/sections/point-group.tex
Finished another proof for "conjugacy class"="irrep" in group representation theory.

\begin{defi}[Point group]
\nomenclature{Point group}{\nomrefpage.}
    A group is called a point group if it contains of rotations
    that leaves a common point unchanged.
\end{defi}
\begin{defi}[Proper point group]
\nomenclature{Proper point group}{\nomrefpage.}
    A point group is called proper if its elements keep the orientation of the
    volumn element.
\end{defi}
\begin{defi}[Improper point group]
\nomenclature{Improper point group}{\nomrefpage.}
    Improper point group is a point group that contains both improper
    and proper rotations.
\end{defi}
\begin{defi}[Spatial inversion $\sigma$]
\nomenclature{Spatial inversion $\sigma$}{\nomrefpage.}

\end{defi}
\begin{remark}
    Let $G$ be a improper point group.
    An improper rotation in it can been seen as the direct product of a
    proper rotation and a spatial inversion $\sigma$. (Note that
    $\sigma$ commutes with any rotation, and $\sigma^2=\id$.)
    Therefore, a improper point group will always contain some proper
    rotation by $\sigma^2=\id$, and of course, the $e$ is always
    proper. Also, the subset of proper rotation will form a subgroup
    $H$. And such division will make $G/H \cong \mathbb{Z}_2$.
\end{remark}
However, a improper point group does not necessarily contains
$\sigma$. For example, assuming a proper point group has a subgroup
$H$ of index $2$, then multiply every elements of the coset by
$\sigma$ will gives us a group denoted $\sigma H$. Then $H\otimes
\sigma H$ gives us a improper point group that does not contain
$\sigma$.

\begin{defi}[P-type I-type improper point group]
\nomenclature{P-type I-type improper point group}{\nomrefpage.}
    A P-type improper point group is the improper point group that
    does not contain $\sigma$, spatial inversion. On the other hand,
    if it does contain $\sigma$, it is called an I-type improper point
    group.
\end{defi}

### 2016-11-13 Lecture note - Group Theory in Physics/sections/20161010.tex
Finished a proof of "irreducible repre" = "conjugacy class".
Adding point group discussion. Introducing the dihedral and rotation group.

@@
 $R_i$. We then have the following facts (all are obvious):
-\begin{fact}$ $
-
-    \begin{enumerate}
-        \item The unit class formed just by the unit element.
-        \item The inverse class formed by just all the inverse element.
-            $C^{-1} = \{ R_i^{-1}\}$. If $C=C^{-1}$, then $C$ is called
-            self-inverse.
-        \item The order of elements in a class is just the same.
-        \item For $\forall T,S\in G$, $TS$ and $ST$ are conjugate to each
-            other. This means that all elements symmetric on the
-            multiplication table is conjugate to each other.
-        \item For two elements $R$, $R'$ conjugate to each other, both
-            can be expressed by the products of two elements in two
-            different way. (Isn't this too obvious to mention.)
-        \item Let $G$ be a rotation group. Suppose it has an axis of the
-            order of $n$, with its operation denoted as $R$,, we can get
-            a new axis by the following steps. (Supose we have another
+\begin{fact}
+The unit class formed just by the unit element.
+\end{fact}
+\begin{fact}
+    The inverse class formed by just all the inverse element.  $C^{-1}
+    = \{ R_i^{-1}\}$. If $C\cap C^{-1}\neq\varnothing$, then
+    $C=C^{-1}$, $C$ is called self-inverse\nomenclature{self-inverse
+    class}{\nomrefpage}.
+\end{fact}
+\begin{fact}
+    The order of elements in a class is just the same.
+\end{fact}
+\begin{fact}
+    For $\forall T,S\in G$, $TS$ and $ST$ are conjugate to each other.
+    This means that all elements symmetric on the multiplication table is
+    conjugate to each other.
+\end{fact}
+\begin{fact}
+    For two elements $R$, $R'$ conjugate to each other, both can be
+    expressed by the products of two elements in two different way. (Isn't
+    this too obvious to mention.)
+\end{fact}
+\begin{fact}
+    \label{fact:20161010-srs}
+    Let $G$ be a rotation group. Suppose it has an axis of the
+    order of $n$, with its operation denoted as $R$,, we can get a
+    new axis by the following steps. (Supose we have another
     rotation $S$),
-
     \begin{enumerate}
@@
     other.
+\end{fact}
+\begin{fact}
+    $C_n$, which is an abel group, every element form a conjugate
+    class by itself. Specifically, $e$ and $R^{n/2}$ are self inverse,
+    if $n$ is even.
+\end{fact}
 
-        \item $C_n$, which is an abel group, every element form a
-            conjugate class by itself. Specifically, $e$ and $R^{n/2}$
-            are self inverse, if $n$ is even.
-    \end{enumerate}
-\end{fact}
 \begin{prop}

### 2016-11-13 Lecture note - Group Theory in Physics/sections/20161107.tex
Adding point group discussion. Introducing the dihedral and rotation group.

\subsection{Finding Representation}
\label{sec:Finding-Representation}
One important work in group theory is to find all its irreducible
representations. The book \cite{book} suggests we first find the
characters of irreducible representations, and list them in a
character table, and then find the matrix of those irreducible
representations.

He also notes that, a unfaithful representation of a group is
equivalent to a faithful representation of a certain quotient group.
Since quotient group is less complex than the original group, finding
irreducible representation of normal subgroups is very useful for
analysing a group.

\begin{fact}
    Also, a the direct product of two irreducible representations is also
    a representation. If the dimension of one of the representation is
    $1$, then their product is still a irreducible representation.
\end{fact}
\subsection{Self-conjugate representation and Real Representation}
\label{sec:Self-conjugate-representation-and-Real-Representation}

It's easy to see that for any representation $D$, conjugating ever
matrix $D(g)^*$ will give another representation. We define
\begin{defi}[Conjugate Representation]
\nomenclature{Conjugate Representation}{\nomrefpage.}
    The conjugate representation of a given representation $D$ is obtained
    by complex conjugate all its matrices $D(g)^*,\,g\in G$.
\end{defi}
\begin{defi}[Self-conjugate Representation]
\nomenclature{Self-conjugate Representation}{\nomrefpage.}
    A representation $D$ is called self-conjugate if and only if it is
    equivalent (but not necessarily equal) to its conjugate
    representation $D^*$.
\end{defi}
\begin{fact}
    The character of a self-conjugate representation is a real
    function. Since (assume $XD(g)X^{-1}=D^*(g)$):
    $$
        \Tr(XD(g)X^{-1}) = \Tr(X^{-1}XD(g)) = \Tr(D(g)) = \Tr(D^*(g))
        = \Tr(D(g))^*
    $$
\end{fact}

We have a similar concept of real representation:
\begin{defi}[Real representation]
\nomenclature{Real representation}{\nomrefpage.}
    A representation $D$ is called real if and only if it is
    equivalent to a representation $D^\text{real}$, such that for any
    $g\in G$, the matrix $D^\text{real}(g)$ is real.
\end{defi}

Observe that a real representation is obviously self-conjugate, but a
self-conjugate representation is not necessarily real. We have two
indicator for its exact classifications.

Firstly,
\begin{thm}
    Let $D$ be a unitary irreducible representation of a finite group.
    Let $D^*$ be its conjugate representation. Assume that $D$ is
    self-conjugate. Let $X$ be the matrix that relates the two. Then
    $X$ is either symmetric or anti-symmetric. $X$ is symmetric if and
    only if $D$ is real. $X$ is anti-symmetric if and only if $D$ is
    self-conjugate but is not real.
\end{thm}

Secondly, 
\begin{thm}
    for any irreducible representation $D$ of finite group:
    \begin{align}
        \frac{1}{|G|}\sum_{g\in G} \chi(g^2) = \begin{cases}
            1, & \text{$D$ is real} \\
            -1, & \text{$D$ is self-conjugate but is not real} \\
            0, & \text{$D$ is not self-conjugate}
        \end{cases}
    \end{align}
\end{thm}

The proof of these two facts are presented in page 68 of \cite{book}.
Note that there is more general version of the second fact, called
\textit{Frobenius–Schur indicator}, see
\href{https://en.wikipedia.org/wiki/Frobenius%E2%80%93Schur_indicator}
{Wikipedia page}.

\subsection{Subduced Representation}
\label{sec:Subduced-Representation}
\marginpar{To be finished.}
Let $G$ be a group. Let $\mathcal{C}_a$ denotes it conjugacy classes.
Let $D^j$ be its irreducible representations, with dimension $m_j$,
character $\chi^j_a$. Assume it has a subgroup $H=\{T_1=E,
T_2,\cdots,T_h\}$, where $h=|H|$. Let $n=|G|/h$ be its index. Denotes
its coset by $R_rH$. With $R_1:=E$, any element in $G$ can be denotes
as $R_r T_t$ (assume $R_r$ is chosen). Let $\bar{\mathcal{C}}_\beta$
denotes conjugacy classes of the subgroup $H$, with character
$\bar{\chi}^k_\beta$, dimension $\bar{m}_k$.

% \begin{thm}[Frobenius Theorem]
%     % TODO
% \end{thm}
% \begin{proof}
%     Assume that $D^j(T_t)$ can be decomposed into:
%     \begin{align}
%         X^{-1}D^j(T_t)X &= \oplus_k a_{jk}\bar{D}^k(T_t) \\
%         m_j = \sum_k a_{jk} \bar{m}_k
%     \end{align}
%     It is easy to prove that
%     \begin{equation}
%         a_{jk} = \frac{1}{|H|} \sum_{T_t\in H} \bar{\chi}^k(T_t)^*
%         \chi^j(Tt) 
%         = \frac{1}{|H|} \sum_\beta \bar{n}_\beta
%         (\bar{\chi}^k_\beta)^* \chi^j_\beta
%     \end{equation}
%     (Notice that, since character is invariant in conjugate class, we
%     can also label the conjugacy class of $\chi^j_\alpha$ with
%     $\beta$, where $\beta$ labels the conjugacy of subgroup.)
% \end{proof}

### 2016-11-13 Lecture note - Group Theory in Physics/sections/point-group.tex
Adding point group discussion. Introducing the dihedral and rotation group.

@@
+Here I collect the result related to point group in physical space.
 \begin{defi}[Point group]
@@
 
-\begin{defi}[P-type I-type improper point group]
-\nomenclature{P-type I-type improper point group}{\nomrefpage.}
+\begin{defi}[P-type and I-type improper point group]
+\nomenclature{P-type and I-type improper point group}{\nomrefpage.}
     A P-type improper point group is the improper point group that
@@
 \end{defi}
+
+\subsection{Rotation \texorpdfstring{$C_n$}{}}
+\label{sec:C_n}
+$C_n$ is isomorphic to $\mathbb{Z}_n$, here the $C$ emphasize that it
+represent the group generated by the rotation of $2\pi/n$. This group
+is abelian.
+
+\paragraph{Conjugacy Classes} Obvious each element form a conjugacy
+class on its only. Moreover, when $n$ is even, the conjugacy class of
+rotation $\pi$ is self-conjugate.
+
+\paragraph{Invariant Subgroup} When $n$ is prime, there is no
+nontrivial invariant subgroup. When $n$ can be factorized as $n_1n_2$,
+both not equals $1$, then $C_n$ is the product of $C_m$ and $C_n$,
+both are invariant subgroup.
+
+\paragraph{Irreducible representation} Since it has $n$ elements and
+$n$ conjugacy classes, with $\sum_{j=1}^n d_j^2 = n$, each irreducible
+representation is $1$-dimensional. Let $R$ denotes the generator of
+rotation by $2\pi/n$, then by calculating $D^j(R)^n=D^j(1)$, one can
+easily find that for each irreducible representation $j$:
+\begin{equation}
+    D^j(R) = \exp(-i2\pi j/N)
+\end{equation}
+where $j=0,1,\cdots, n$. Since $R$ is its generator, the rest of the
+representation is determined. Hence we have all the irreducible
+representations of $C_n$. The table of characters may be found on page
+65 of \cite{book}.
+
+Note that since all representations are $1$-dimensional, their
+products will keep being irreducible. So having two set of irreducible
+representations of $C_n$ and $C_m$, will give us all the irreducible
+representations of $C_{nm}$.
+\subsection{Dihedral Group}
+\label{sec:Dihedral-Group}
+\begin{defi}[Dihedral Group $D_n$]
+\nomenclature{Dihedral Group $D_n$}{\nomrefpage.}
+    Dihedral group $D_n$ is the symmetric group of regular $n$-gons.
+\end{defi}
+
+\paragraph{Conjugacy Class}
+There is some important difference between the case when $n$ is odd
+and when $n$ is even. When $n$ is odd, the $2$-fold axis are all
+linked with the vortices of the $n$-polygon. On the contrary, when $n$
+is even, there is two different $2$-fold axis. The first $n/2$ axises
+are those linked with the vortices, the second $n/2$ axises are those
+cut through the opposite edges.
+
+Note that by fact \ref{fact:20161010-srs} one can see that such
+difference will note make the two classes in even $n$ the same
+conjugacy class. On the contrary, by the same fact
+\ref{fact:20161010-srs} one sees that those $2$-fold axises are in the
+same conjugacy class when $n$ is odd.
+
+Also denotes one $2\pi/n$ rotation around the $N$-fold axis by $T$,
+then by this very same fact \ref{fact:20161010-srs}, $T$ and $T^{-1}$
+lies in the same conjugacy class, related by a reflection around a
+$2$-fold axis. This is obvious a self-conjugate class. (Note that,
+when only $2\pi/n$ rotation is considered, they form an abelian group
+and each rotation forms a conjugacy class.) Similarly for the
+conjugacy class $\{T^m, T^{-m}\}$, where $m$ is an integer.
+
+In summary, this discussion shows that the self-conjugate classes in $D_n$
+are:
+\begin{fact}
+    When $n$ is odd (Let $n=2n'+1$): The identity class, the class of
+    all $2$-fold axis. The class of $\{ T^m, T^{-m}\}$, where
+    $m=1,2,\cdots, n'$. (Why $m\leq n'$, think about the case when
+    $n=5,n'=2$.). In total $n'+2=\frac{n+3}{2}$ conjugacy
+    classes/irreducible representations. All conjugacy classes are
+    self-conjugate.
+\end{fact}
+\begin{fact}
+    When $n$ is even (Let $n=2n'$): The identity class, the two
+    classes of all $2$-fold axis, as discussed before. The class of
+    $\{ T^m, T^{-m}\}$, where $m=1,2,\cdots, n'$. In total
+    $n'+3=\frac{n+6}{2}$. All conjugacy classes are self-conjugate.
+\end{fact}
+
+\paragraph{Invariant Subgroups}
+By the distinction between edge and vortices type of $2$-fold axises
+discussed before, one can see that the difference in invariant
+subgroup when $n$ is odd or even. More Specifically, when $n=5$ is odd,
+$D_5$ has only $C_5$ as a notrivial subgroup. But when
+$n=6$ is even, it has $C_6$ (then $C_2$ and $C_3$), two copies of
+$D_3$ (each formed by edge and vortex type of $2$-fold axis).

### 2016-11-13 Lecture note - Group Theory in Physics/sections/point-group.tex
Almost finised the Irreps if D_n and C_n. (representation, group theory)

@@
 
-\paragraph{Irreducible representation} Since it has $n$ elements and
-$n$ conjugacy classes, with $\sum_{j=1}^n d_j^2 = n$, each irreducible
-representation is $1$-dimensional. Let $R$ denotes the generator of
-rotation by $2\pi/n$, then by calculating $D^j(R)^n=D^j(1)$, one can
-easily find that for each irreducible representation $j$:
+\paragraph{Irreducible representation} (\textbf{pp.64-65 of \cite{book}})
+
+Since it has $n$ elements and $n$ conjugacy classes, with
+$\sum_{j=1}^n d_j^2 = n$, each irreducible representation is
+$1$-dimensional. Let $R$ denotes the generator of rotation by
+$2\pi/n$, then by calculating $D^j(R)^n=D^j(1)$, one can easily find
+that for each irreducible representation $j$:
 \begin{equation}
@@
 representations of $C_n$ and $C_m$, will give us all the irreducible
-representations of $C_{nm}$.
-\subsection{Dihedral Group}
+representations of $C_{nm}$. For example:
+% TODO pdf scan of C_6.
+
+\subsection{Dihedral Group \texorpdfstring{$D_n$}{}}
 \label{sec:Dihedral-Group}
@@
 \nomenclature{Dihedral Group $D_n$}{\nomrefpage.}
-    Dihedral group $D_n$ is the symmetric group of regular $n$-gons.
+    Dihedral group $D_n$ is the symmetric group of regular $n$-gons
+    for $n\geq 3$. For $n=1/2$, it is usually not defined. I found that
+    in book \cite{book}, $D_2$ is isomorphic to Klein Group, $D_1$ is
+    of course the trivial group.
 \end{defi}
 
-\paragraph{Conjugacy Class}
+But we can have another more mathematical definition of Dihedral
+group:
+\marginpar{To be added}
+\paragraph{Conjugacy Classes}
 There is some important difference between the case when $n$ is odd
@@
     all $2$-fold axis. The class of $\{ T^m, T^{-m}\}$, where
-    $m=1,2,\cdots, n'$. (Why $m\leq n'$, think about the case when
+    $m=1,2,\cdots, n'$. (Why $m\leq n'$? Think about the case when
     $n=5,n'=2$.). In total $n'+2=\frac{n+3}{2}$ conjugacy
@@
     When $n$ is even (Let $n=2n'$): The identity class, the two
-    classes of all $2$-fold axis, as discussed before. The class of
+    classes of all $2$-fold axis, as discussed above. The class of
     $\{ T^m, T^{-m}\}$, where $m=1,2,\cdots, n'$. In total
@@
 
-\paragraph{Invariant Subgroups}
+\paragraph{Invariant Subgroups} (\textbf{pp.30 of \cite{book}})
 By the distinction between edge and vortices type of $2$-fold axises
-discussed before, one can see that the difference in invariant
-subgroup when $n$ is odd or even. More Specifically, when $n=5$ is odd,
+discussed before, one can see that there is difference in invariant
+subgroup when $n$ is odd or even. For example, when $n=5$ is odd,
 $D_5$ has only $C_5$ as a notrivial subgroup. But when
@@
 $D_3$ (each formed by edge and vortex type of $2$-fold axis).
+
+More generally, there importnat subgroup of index for $D_n$. When $n$
+is odd (let $n'2n'+1$), there are one subgroup of index $2$, i.e.
+$C_n'$. When $n$ is even (let $n'=n/2$), there are three invariant
+subgroup of index $2$: $C_n'$, $D_n$, and $D_n'$. Denote $n$ $2$-fold
+axis as $S_j$, rotation around $n$-fold axis by $2\pi/n$ as $T$,
+then:
+\begin{align}
+    D_n &= \{E, T^2,T^4,\cdots,T^{2n-2},S_0,S_2,\cdots,S_{2n-2}\} \\
+    D_n' &= \{E, T^2,T^4,\cdots,T^{2n-2},S_1,S_3,\cdots,S_{2n-1}\}
+\end{align}
+Note that this list is not complete. For example, $D_6$ contains other
+nontrivial invariant subgroups, listed in page 30 of \cite{book}.
+
+\paragraph{Character Table} (\textbf{pp.66 of \cite{book}})
+
+For $D_2$, it is isomorphic to the group
+$\{1,\sigma,\tau,\sigma\tau\}$, where $\sigma$ is spatial inversion,
+$\tau$ is time-reversal. Notice that this group is abelian, so it
+obvious has $4$ irreducible representations. It is easy to get its
+character table, which may be found on page 66, table 3.6 of
+\cite{book}.
+
+For $D_3$, it is non-abelian. As discussed previously, it has $3$
+conjugacy classes, so it has 3 irreducible representations. Notice
+that $D_3/C_3 \cong C_2$, so it inherets the two simple irreducible
+representations of $C_2$. This gives two lines in the character
+table. Also, $6-1^2-1^2=2^2$, so we have one $2$-dimensional
+irreducible representation left.  Next, by fact
+\ref{fact:character-of-identity}, we can determine one element in the
+character for $2$-dimensional irreducible representation. The rest two
+empty blanks can be filled using the orthogonal relations for the
+character table.
+%TODO Add the scanned example.
+
+For general $D_n$, see the part for irreducible representations.
+
+\paragraph{Irreducible representation} (\textbf{pp.71-74 of \cite{book}})
+
+The general procedure is to use the invariant subgroup of index $2$
+mentioned above to get the $1$-dimensional representations. And use
+the relation $\sum_j m_j^2 = |D_n|$ and $\sum_j 1 = $ number of
+conjugacy class to "guess" the dimensional of remaining irreducible
+representations. Finally use subgroup $C_n$ to construct those
+representations (induced representation) and reduce these into
+irreducible ones. But how to reduce them into irreducible one is
+actually the most difficult part, in my opinion.
+
+For odd $n$, let $n=2n'+1$. We have:
+\begin{align}
+    \sum_{j=1}{n'+2} m_j^2 = 4n'+2
+\end{align}
+
+There is two $1$-dimensional irreducible representations, formed using
+the invariant subgroup $C_{2n'+1}$. Since $4n'+2 = 2^2 n'+2$, one
+guesses that the remaining ones are $n$ $2$-dimensional irreducible
+representation. They are constructed (construction process could be
+found in \cite{book}) to be (notice $D_{2n'+1}$ is generated by
+$T_{2n'+1}$, the rotation $2\pi/(2n'+1)$, and $C'_2$, any one of the
+$2$-fold reflection):
+\begin{align}
+    \bar{D}^{E_j}(C_{2n'+1}) &=\left( \begin{array}{cc}
+    \cos(\frac{2j\pi}{2n'+1}) & -\sin(\frac{2j\pi}{2n'+1}) \\
+    \sin(\frac{2j\pi}{2n'+1}) & \cos(\frac{2j\pi}{2n'+1}) \\
+        \end{array} \right) \\
+    \bar{D}^{E_j}(C'_{2}) &= \left( \begin{array}{cc}
+                 1 & 0 \\
+                 0 & -1 \\ 
+                 \end{array} \right)
+\end{align}
+where $j=1,2,\cdots,n$.
+
+The case for even $n$ is simialr (let $n'=n/2$). Except that here one
+as three invariant subgroup of index $2$ (see dicusson about invariant
+subgroup above). So it has three $1$-dimensional irreducible
+representations, and $n-1$ $2$-dimensional irreducible representations.
+
+When $n$ is odd, let $n=2n'$. (TBD)
+
+%TODO Finish it.

### 2016-11-14 Lecture note - Group Theory in Physics/sections/20161107.tex
Almost finised the Irreps if D_n and C_n. (representation, group theory)
Finished all proof of recent classes' contents, just need to add my own scanned notes.

@@
 \label{sec:Finding-Representation}
+% TODO Polish the arragement of this section.
 One important work in group theory is to find all its irreducible
@@
 \end{fact}
+\begin{fact}
+    \label{fact:character-of-identity}
+    Another helpful point is that, for all irreducible
+    representations, the identity element is always mapped to the
+    identity matrix. So the character for this unit class is just the
+    dimension of the representation.
+\end{fact}
 \subsection{Self-conjugate representation and Real Representation}
@@
 \end{defi}
-\begin{fact}
-    The character of a self-conjugate representation is a real
+Note that the character of a self-conjugate representation is a real
 function. Since (assume $XD(g)X^{-1}=D^*(g)$):
@@
 $$
-\end{fact}
+In fact, we have
+\begin{thm}
+    A represents is self-conjugate if and only if its character is
+    real-valued.
+\end{thm}
+\begin{proof}
+    If it is self-conjugate, clearly it is real-valued. On the other
+    hand, if the character is real-valued, then by
+    \begin{equation}
+        \chi_{D^*(g)} = \Tr(D^*(g)) = \Tr(D(g))^* = \chi^*_{D(g)}
+        = \chi_{D(g)}
+    \end{equation}
+    The conjugate representation has the same character, hence is
+    equivalent to original representation by theorem \ref{thm:20161031-character-determine-rep}
+\end{proof}
+
+Fun fact. Since all representation of finite group are equivalent to a
+unitary one, if for en element $g\in G$ its character $\chi(g)$ is
+complex, then its inverse $g^{-1}$ has character $\chi(g)^*$.
+Therefore, for a representation which is not self-conjugate, its
+character will has complex value existing in pairs, unless $g=g^{-1}$.
 
@@
 \label{sec:Subduced-Representation}
-\marginpar{To be finished.}
+\marginpar{To be finished.} %TODO
 Let $G$ be a group. Let $\mathcal{C}_a$ denotes it conjugacy classes.

### 2016-11-14 Lecture note - Group Theory in Physics/sections/point-group.tex
Finished all proof of recent classes' contents, just need to add my own scanned notes.

@@
 But we can have another more mathematical definition of Dihedral
-group:
-\marginpar{To be added}
-\paragraph{Conjugacy Classes}
+group. To introduce that definition, let me first explain some facts
+and discuss a little bit about its conjugacy classes.
+
 There is some important difference between the case when $n$ is odd
@@
 linked with the vortices of the $n$-polygon. On the contrary, when $n$
-is even, there is two different $2$-fold axis. The first $n/2$ axises
-are those linked with the vortices, the second $n/2$ axises are those
-cut through the opposite edges.
+is even, there is two different $2$-fold axis. The first $n/2$
+$2$-fold axises are those linked with the vortices, the second $n/2$
+$2$-fold axises are those cutting through the opposite edges.
 
+\paragraph{Conjugacy Classes}
 Note that by fact \ref{fact:20161010-srs} one can see that such
-difference will note make the two classes in even $n$ the same
-conjugacy class. On the contrary, by the same fact
-\ref{fact:20161010-srs} one sees that those $2$-fold axises are in the
-same conjugacy class when $n$ is odd.
+difference mentioned will make the two classes of $2$-fold axises in
+even $n$ each form their own conjugacy class. On the contrary, by the
+same fact \ref{fact:20161010-srs} one sees that when $n$ is odd, all
+the $2$-fold axises are in the same conjugacy class. Note that a
+reflection is its own inverse, so in either cases ($n$ odd or even),
+we have found self-conjugate classes.
 
-Also denotes one $2\pi/n$ rotation around the $N$-fold axis by $T$,
-then by this very same fact \ref{fact:20161010-srs}, $T$ and $T^{-1}$
-lies in the same conjugacy class, related by a reflection around a
-$2$-fold axis. This is obvious a self-conjugate class. (Note that,
-when only $2\pi/n$ rotation is considered, they form an abelian group
-and each rotation forms a conjugacy class.) Similarly for the
-conjugacy class $\{T^m, T^{-m}\}$, where $m$ is an integer.
+The next conjugacy classes are about rotation. Denotes one $2\pi/n$
+rotation around the $N$-fold axis by $T$, then by this very same fact
+\ref{fact:20161010-srs}, $T$ and $T^{-1}$ lies in the same conjugacy
+class, related by a reflection around a $2$-fold axis. This is obvious
+a self-conjugate class. (Note that, when only $2\pi/n$ rotation is
+considered, they form an abelian group and each rotation forms a
+conjugacy class.) Similarly for the conjugacy class $\{T^m, T^{-m}\}$,
+where $m$ is an integer.
 
-In summary, this discussion shows that the self-conjugate classes in $D_n$
+In summary, this discussion shows that the conjugacy classes (all are
+self-conjugate) in $D_n$
 are:
@@
     $n'+3=\frac{n+6}{2}$. All conjugacy classes are self-conjugate.
+\end{fact}
+
+\paragraph{Formal definition or $D_n$} Having discussed about
+conjugacy classes, one sees that $D_n$ can be defined by generators.
+Clearly, when $n$ is odd, $D_n$ is generated by one rotation $2\pi/n$
+and one reflection (denoted $C'_2$ in the book \cite{book}). When $n$
+is even, one might thinks that we have three generators, i.e. the
+rotation by $2\pi/n$, one reflection about vortex $C'_2$, and one
+reflection about middle of edges $C''_2$. But actually it only needs
+two. The reflection about middle of edges can be produced by the
+rotation and the reflection about vortex, or vice versa. See this
+note for example:
+
+% TODO Add scanned notes.
+
+So all in all, $D_n$ can be generated by just two elements. They are:
+\begin{fact}
+\label{fact:point-group-formal-def-dn}
+\begin{align}
+    D_n &\equiv \braket{R,S|R^n=1,S^2=1,SRS^{-1}=R^{-1}} \\
+        &\equiv \braket{R,S|R^n=1,S^2=1,(SR)^2=1}
+\end{align}
+Here the first line symbolizes that rotation $R$ and $R^{-1}$ are in
+the same conjugacy class. The second is more beautiful and symbolizes
+that a roto-reflection is idempotent.
 \end{fact}
@@
 
+I present only vague discussion below. For details, please to ...
+actually I don't know which book. The textbook \cite{book} is too
+vague too. Perhaps I should find some more detailed books.
+% TODO Add better books.
+
 For odd $n$, let $n=2n'+1$. We have:
@@
 \begin{align}
-    \bar{D}^{E_j}(C_{2n'+1}) &=\left( \begin{array}{cc}
-    \cos(\frac{2j\pi}{2n'+1}) & -\sin(\frac{2j\pi}{2n'+1}) \\
-    \sin(\frac{2j\pi}{2n'+1}) & \cos(\frac{2j\pi}{2n'+1}) \\
+    \bar{D}^{E_j}(C_{n}) &=\left( \begin{array}{cc}
+    \cos(\frac{2j\pi}{n}) & -\sin(\frac{2j\pi}{n}) \\
+    \sin(\frac{2j\pi}{n}) & \cos(\frac{2j\pi}{n}) \\
         \end{array} \right) \\
@@
 
-The case for even $n$ is simialr (let $n'=n/2$). Except that here one
-as three invariant subgroup of index $2$ (see dicusson about invariant
-subgroup above). So it has three $1$-dimensional irreducible
-representations, and $n-1$ $2$-dimensional irreducible representations.
-
-When $n$ is odd, let $n=2n'$. (TBD)
-
-%TODO Finish it.
+The case for even $n$ is simialr (let $n'=n/2$). Except that now it
+has three invariant subgroup of index $2$ (see dicusson about invariant
+subgroup above). So it has $2+2+2-2=4$ $1$-dimensional irreducible
+representations ($-2$ for the repeated identity representation), and
+$n'-1$ $2$-dimensional irreducible representations.
+(we have $\sum_{j=1}^{n'+3}m_j^2 = 4n' = (n-1)2^2 + 4\cdot 1$.)
+The result is exactly the same as in the the add $n$ case, and this is
+why I did not write $2n'+1$ but use $n$ in the above equations.

### 2016-11-14 Lecture note - Group Theory in Physics/sections/point-group.tex
Add a useful formula for reflection and rotation.

@@
 
-\paragraph{Conjugacy Classes}
+\subsubsection{Conjugacy Classes}
 Note that by fact \ref{fact:20161010-srs} one can see that such
@@
 
-\paragraph{Formal definition or $D_n$} Having discussed about
-conjugacy classes, one sees that $D_n$ can be defined by generators.
-Clearly, when $n$ is odd, $D_n$ is generated by one rotation $2\pi/n$
-and one reflection (denoted $C'_2$ in the book \cite{book}). When $n$
-is even, one might thinks that we have three generators, i.e. the
-rotation by $2\pi/n$, one reflection about vortex $C'_2$, and one
-reflection about middle of edges $C''_2$. But actually it only needs
-two. The reflection about middle of edges can be produced by the
-rotation and the reflection about vortex, or vice versa. See this
-note for example:
+\subsubsection{Formal definition of \texorpdfstring{$D_n$}{}}
+
+Having discussed about conjugacy classes, one sees that $D_n$ can be
+defined by generators.  Clearly, when $n$ is odd, $D_n$ is generated
+by one rotation $2\pi/n$ and one reflection (denoted $C'_2$ in the
+book \cite{book}). When $n$ is even, one might thinks that we have
+three generators, i.e. the rotation by $2\pi/n$, one reflection about
+vortex $C'_2$, and one reflection about middle of edges $C''_2$. But
+actually it only needs two. The reflection about middle of edges can
+be produced by the rotation and the reflection about vortex, or vice
+versa. See this note for example:
 
@@
 
-\paragraph{Invariant Subgroups} (\textbf{pp.30 of \cite{book}})
+Observe that by this definition, it's easy to prove that
+\begin{align}
+    SR &= R^{-1}S \\
+    SR^{-1} &= RS
+\end{align}
+which are all physically intuitive. A more sophisticated law is
+also physically easy to see
+\begin{fact}
+    \begin{equation}
+        S_m R^n = R^{-n}S_m
+    \end{equation}
+\end{fact}
+But I here give a mathematical derivation of the above formula:
+\begin{proof}
+    Assume $n$ is add.
+
+    Pick a reference point in the $n$-polygon, label its vortex as $0$. Then
+    let $S_0= S$ be the reflection about this vortex axis. Then label
+    all the remaining vortex $2$-fold axises in the same direction as
+    $R$ as $1,2,\cdots,n-1$. Obviously we have:
+    \begin{align}
+        S_1 &= RS_0 R^{-1} = RSR^{-1} \nonumber\\
+        S_2 &= RS_1 R^{-1} = R^2 S R^{-2} \nonumber\\
+        \cdots & \nonumber \\
+        S_{m} &= R^{m} S R^{m}
+    \end{align}
+    where $m=1,2,\cdots,n-1$. Then
+    \begin{align*}
+        S_m R^n &= R^m S R^{-m} R^n \\
+          &= R^m S R^n R^{-m}\\
+          &= R^m R^{-n} S R^{-m} \\
+          &= R^{-n} S_m
+    \end{align*}
+
+    When $n$ is odd, the proof is the same, except that now $S_{2m}$ is a
+    vortex reflection, and $S_{2m+1}$ is an edge reflection
+    ($m=0,1,\cdots (n/2-1)$). Notice that $S_1= RS_0 = RS$, we easily
+    see
+    \begin{align}
+        S_{2m} &= R^m S R^{-m} \\
+        S_{2m+1} &= R^{m+1} S R^{-m}
+    \end{align}
+    and the rest of the proof is the same.
+\end{proof}
+
+\subsubsection{Invariant Subgroups} (\textbf{pp.30 of \cite{book}})
 By the distinction between edge and vortices type of $2$-fold axises
@@
 
-\paragraph{Character Table} (\textbf{pp.66 of \cite{book}})
+\subsubsection{Character Table} (\textbf{pp.66 of \cite{book}})
 
@@
 
-\paragraph{Irreducible representation} (\textbf{pp.71-74 of \cite{book}})
+\subsubsection{Irreducible representation}
+
+(\textbf{pp.71-74 of \cite{book}})
 

### 2016-11-15 Lecture note - Group Theory in Physics/group theory in physics.tex
Conjugacy classes and regular representation in Group theory.
Finished another proof for "conjugacy class"="irrep" in group representation theory.
Adding point group discussion. Introducing the dihedral and rotation group.
New notes for algebraic theory of representation.

@@
 \tableofcontents
+\paragraph{Information about the class}
 \begin{enumerate}
-    \item Combine group theory with you research.
-    \item Mid-term and final.
+    \item Final project: Combine group theory with you research.
+    \item Mid-term and final exam.
     \item No homework, cause it is already graduate level.
@@
 \input{sections/20161031}
+
+\section{20161107}
+\label{sec:20161107}
+\input{sections/20161107}
+
+\section{Point Group}
+\label{sec:Point-Group}
+\input{sections/point-group}
+
+\section{Representationas and Semisimplicity}
+\label{sec:Representationas-and-Semisimplicity}
+
+Now I digress to read chapter 18 of the book \cite{lang-algebra}.
+
+Let $R$ be a commutative ring and $G$ a group. Let $E$ be a
+$R$-module.
+
+For convenience, given a representation $\rho:G\to \Aut_R(E)$, let
+$\sigma\ni G$, $x\in E$, we write $\sigma x$ instead of
+$\rho(\sigma)x$.
+
+An $R$-module $E$, together with a representation $\rho$, will be
+called a \textbf{$G$-module}\nomenclature{$G$-module}{\nomrefpage} or
+\textbf{$G$-space}\nomenclature{$G$-space}{\nomrefpage}, or also a
+\textbf{$(G,R)$-module}\nomenclature{$(G,R)$-module}{\nomrefpage}.
+
+If $E$, $F$ are $G$-modules, we define a
+\textbf{$G$-homomorphism}\nomenclature{$G$-homomorphism}{\nomrefpage}
+$f:E\to F$ as a $R$-linear map such that $f(\sigma x) = \sigma f(x)$
+for all $x\in G$ and $\sigma\in G$.
+
+We make $R$ into a $G$-module by making $G$ act trivially on $R$, i.e.
+we have a trivial representation on $R$, itself regarded as a
+$R$-module.
+
 \section{Anchor}
@@
     \href{http://www.th.physik.uni-bonn.de/nilles/people/luedeling/grouptheory/data/grouptheorynotes.pdf}{Link}
+    \bibitem{lang-algebra} Serge Lang. Algebra. Revised 3rd. Springer.
 \end{thebibliography}

### 2016-11-15 Lecture note - Group Theory in Physics/sections/point-group.tex
New notes for algebraic theory of representation.

@@
 the relation $\sum_j m_j^2 = |D_n|$ and $\sum_j 1 = $ number of
-conjugacy class to "guess" the dimensional of remaining irreducible
+conjugacy class to get the dimensional of remaining irreducible
 representations. Finally use subgroup $C_n$ to construct those
@@
 actually I don't know which book. The textbook \cite{book} is too
-vague too. Perhaps I should find some more detailed books.
+concise. Perhaps I should find some more detailed books.
 % TODO Add better books.
@@
 the invariant subgroup $C_{2n'+1}$. Since $4n'+2 = 2^2 n'+2$, one
-guesses that the remaining ones are $n$ $2$-dimensional irreducible
-representation. They are constructed (construction process could be
-found in \cite{book}) to be (notice $D_{2n'+1}$ is generated by
-$T_{2n'+1}$, the rotation $2\pi/(2n'+1)$, and $C'_2$, any one of the
-$2$-fold reflection):
+guesses\footnote{Actually, the remaing ones can satisfy our condition
+    only if they are $2$-dimensional. A $1$-dimensional would means an
+    additional invarian subgroup of index $2$, which is not true. A
+    $3$-dimensional would demand an additional $1$-dimensional
+    representation to balance and get a even number. So
+$2$-dimensional is the only possibility.}, that the remaining ones are
+$n$ $2$-dimensional irreducible representations. They are constructed
+(construction process could be found in \cite{book}) to be (notice
+$D_{2n'+1}$ is generated by $T_{2n'+1}$, the rotation
+$2\pi/(2n'+1)$, and $C'_2$, any one of the $2$-fold reflection):
 \begin{align}

### 2016-11-15 Latex packages/latex examples.tex
Minor modification to C.V. Create a new latex example file. Begin reading lang's representaton theory for group theory in physics.

--- 2016-11-10 Notes of various papers/Classification of topological quantum matter with symmetries. Rev.M.P/doubts.tex
@@
 
-\title{Notes for Classification of topological quantum matter with
-symmetries}
+\title{Examples}
 \date{\today}
@@
 \abstract{
-As title suggests.
+Nothing here.
 }
 \tableofcontents
-\paragraph{Asks}
-\begin{enumerate}
-    \item Page 6. Why the scalar in Schur's lemma becomes of unit lenght.
-    \item page 9. What does it mean by:
-        \begin{quote}
-            Note that unitary symmetries, which commute with the
-            Hamiltonian, allow us to bring the Hamiltonian into a
-            block diagonal form.
-        \end{quote}
-    \item page 9, table I. When he talks about \textit{codimension},
-        what is the dimension of the whole space? ($3$? $3+1$?).
-        Similar problem also exists in page 10.
-        Note, he mentions codimension of gaples modes on page 11. He
-        asserts that codimension $1$ means $1$ dimension less than the
-        bulk. But it should be strange to compare the dimension of
-        defects with the dimension of the bulk.
+\begin{center}
+    Bad diagrams
+\end{center}
+$$
+    \begin{tikzcd}[column sep=small]
+        E \ar[dr,"f"]\ar[rr,"\rho"]\ar[drr, phantom, "\#", very near
+        start] & & F\ar[dl,"\rho'"] \\
+        & G &  \,
+    \end{tikzcd}
+    \begin{tikzcd}[column sep=small]
+        E \ar[dr,"f"]\ar[rr,"\rho"]\ar[drr, phantom, "\#"] & & F\ar[dl,"\rho'"] \\
+        & G &  \,
+    \end{tikzcd}
+$$
+\begin{center}
+    A good diagram
+\end{center}
+$$
+    \begin{tikzcd}[column sep=small]
+        E \ar[dr,"f"]\ar[rr,"\rho"] &
+        \ar[d,phantom, "\#", near start] & F\ar[dl,"\rho'"] \\
+        & G &  \,
+    \end{tikzcd}
+$$
 
-        Possibly related
-        resources:\href{http://www.virginia.edu/bohr/mse209/chapter4.htm}
-        {Online notes about Imperfection}:
-        \begin{itemize}
-            \item $0$D (zero dimension) – point defects: vacancies and
-                interstitials. Impurities.
-            \item 1D – linear defects: dislocations (edge, screw,
-                mixed) 
-            \item 2D – grain boundaries, surfaces.  
-            \item 3D – extended defects: pores, cracks.
-        \end{itemize}
-
-        Note: it is finally defined on page 12. that is:
-        codimension of defect $d_c:= d_\text{bulk} - d_\text{defect}$.
-    \item page 6, what does it mean by saying \textit{"unitary
-        symmetry"}.
-    \item page 10, what is a \textit{"quantum phase diagram"}.
-    \item page 11, what does he says, \textit{"Topological properties of
-        adiabatic cycles can also be discussed in a similar manner."}.
-        Does this mean that all previous classification does not
-        concern the adiabatic cycles? What is \textit{"adiabatic
-        cycles"} exactly in his language?
-    \item page 12, "disinclination" is what kind of defect? Any books
-        on crystall defects?
-    \item page 12, is the \textit{"mass gap"} a massive gap or a gap
-        composed of mass?
-    \item page 12, about the $D$: if $d_c=1$ (line defect in a
-        $2d$-bulk), then $D=0$. So a line is wrapped by a point?
-        also, on fig. 2, the ($D=2,d=1$) gives a $d_\text{defect}=-1$!
-        Judging from this graph, a $d_\text{defect}=-1$ means a
-        temporal defect. Is this true?
-\end{enumerate}
-
-\paragraph{Doubts}
-\begin{enumerate}
-    \item page 10. Amazingly, he says, \textit{"all TIs and TSCs in
-        the ten AZ symmetry classes are stable against disorder, and
-        hence the assumption of translation invariance is not at all
-        necessary"}.  How can translational invariance be ignored?
-    \item 
-\end{enumerate}
 \section{Anchor}

### 2016-11-15 Lecture note - Group Theory in Physics/sections/s-lang.tex
Minor modification to C.V. Create a new latex example file. Begin reading lang's representaton theory for group theory in physics.

\section{Representationas and Semisimplicity}
\label{sec:Representationas-and-Semisimplicity}

Now I digress to read chapter 18 of the book \cite{lang-algebra}.

Let $R$ be a commutative ring and $G$ a group. Let $E$ be a
$R$-module.

For convenience, given a representation $\rho:G\to \Aut_R(E)$, let
$\sigma\ni G$, $x\in E$, we write $\sigma x$ instead of
$\rho(\sigma)x$.

An $R$-module $E$, together with a representation $\rho$, will be
called a \textbf{$G$-module}\nomenclature{$G$-module}{\nomrefpage} or
\textbf{$G$-space}\nomenclature{$G$-space}{\nomrefpage}, or also a
\textbf{$(G,R)$-module}\nomenclature{$(G,R)$-module}{\nomrefpage}.

If $E$, $F$ are $G$-modules, we define a
\textbf{$G$-homomorphism}\nomenclature{$G$-homomorphism}{\nomrefpage}
$f:E\to F$ as a $R$-linear map such that $f(\sigma x) = \sigma f(x)$
for all $x\in G$ and $\sigma\in G$.

\begin{equation}
    \begin{tikzcd}[column sep=small]
        E \ar[rr,"f"] &
        \ar[d,phantom, "\#", near start] & F \\
        & G\ar[ul,"\rho"]\ar[ur,"\rho'"] &  \,
    \end{tikzcd}
\end{equation}

We make $R$ into a $G$-module by making $G$ act trivially on $R$, i.e.
we have a trivial representation on $R$, itself regarded as a
$R$-module.

\begin{key}
Now the we discuss a systematically way to construct a new
representation from a given one. More specifically, we want to make
$\Hom_R(E,F)$ into a $G$-module, i.e. construct a representation from
$G$ to $\Hom_R(E,F)$.

First, we define the action of $G$ on $\Hom_R(E,F)$ by (let $f\in
\Hom_R(E,F)$, $f: E\to F$).
\begin{equation}
    ([\sigma] f) (x) = \sigma (f(\sigma^{-1}x))
\end{equation}
We verify that this is an operation/action of $G$ on $\Hom_R(E,F)$:
\begin{align*}
    ([e] f) (x) &= e (f(e^{-1}x)) = f(x) \\
    ([a] [b] f )(x) &= [a] bf(b^{-1}x) = ab f(b^{-1}a^{1}x) =
    abf((ab)^{-1}x) \\
    &= ([ab] f)(x)
\end{align*}
\end{key}

\begin{fact}
\label{fact:g-hom-sg-g}
For convenience we write $([\sigma]f)(x)$ simply as $[\sigma]f(x)$.
Also, 
\begin{align*}
    f(\sigma x)=\sigma f(x) \Leftrightarrow [\sigma]f(x) = \sigma
    f(\sigma^{-1}x) = \sigma\sigma^{-1}f(x) = f(x)
\end{align*}
So $f$ is a $G$-homomorphism if and only if $[\sigma]f=f$ for all
$\sigma\in G$.
\end{fact}
\begin{remark}
    This is the first time I understand why $\sigma^{-1}$ is so
    important. Without it, we don't have the beautiful fact above.
\end{remark}
\begin{defi}[Dual representation $\rho^\vee$]
\nomenclature{Dual representation $\rho^\vee$}{\nomrefpage.}
When $F=R$ (so with trivial action), then $\Hom_R(E,F)=E^\vee$ is the
dual module. If we have $\rho:G\to \Aut_R(E)$, a representation of $G$
on $E$, then the action we just defined gives the dual
representation (also called \nomen{contragredient} in the literature).
\end{defi}
More specifically, $\sigma$ acts trivially on $R$, so
\begin{align}
    \rho^\vee: & G\to \Aut_R(E^\vee)  \\
               & \sigma \mapsto [\sigma] f = f(\sigma^{-1}x) \nonumber
\end{align}

Suppose now that the modules $E$,$F$ are free and finite dimensional
over $R$ (recall that a module is free when it has a basis). Let
$\rho$ be a representation of $G$ on $E$, $M$ be the matrix of
$\rho(\sigma)$ with respect to a basis, $M^\vee$ be the matrix of
$\rho^\vee (\sigma)$ with respect to the dual basis. Then
\begin{align*}
    [\sigma] f: x &\mapsto f(\sigma^{-1} x) \\
    x^i &\mapsto \sum_{ij} f_i(M^{-1})^i_j x^j \\
    \Longrightarrow [\sigma]: f &\mapsto f\sigma^{-1} \\
    f_j &\mapsto \sum_i f_i(M^{-1})^i_j \\
    \left(\begin{array}{c}
        f_1 \\
        f_2 \\
        \cdots 
\end{array}\right) &\mapsto (M^{-1})^T  \left(\begin{array}{c}
        f_1 \\
        f_2 \\
        \cdots 
\end{array}\right) 
\end{align*}
Hence
\begin{equation}
    M^\vee = (M^{-1})^T
\end{equation}

Next we discuss the tensor product instead of Hom. Let $E$,$E'$ be
$(G,R)$-modules. We form their tensor product $E\otimes E'$, taken over
$R$. then we define an action of $G$ on $E\otimes E'$ by (let
$\sigma\in G$):
\begin{equation}
    \sigma (x\otimes x') := \sigma x \otimes \sigma x'
\end{equation}

\begin{fact}
\label{fact:Ev-F--Hom-G}
Suppose that $E$, $F$ are free and finite dimensional over $R$. Then
the $R$-isomorphism
\begin{align}
    E^\vee \otimes F &\overset{g}{\cong} \Hom_R(E,F) \\
    f_i \otimes x^j &\overset{g}{\cong} A^j_i = (f_i x^j)
    \label{eq:fx-g-aji}
\end{align}
is a $G$-isomorphism.
\end{fact}
\begin{proof} 
In this proof, we will use Einstein summation
convention. We see that
\begin{align}
    \sigma (f_i\otimes x^j) = (\sigma^\vee f_i )\otimes (\sigma x^j) =
    f_k (M_E^{-1})^k_i \otimes (M_F)^j_l x^l 
\end{align}
So
\begin{align}
    g(\sigma (f_i\otimes x^j)) = g(f_k (M_E^{-1})^k_i \otimes 
    (M_F)^j_l x^l) = (M^{-1}_E)^k_i A_k^l (M_F)^j_l
\end{align}
Meanwhile, for $h\in \Hom_R(E,F)$,
\begin{align}
    [\sigma] h: x &\mapsto \sigma h(\sigma^{-1} x) \\
    x^i &\mapsto \sigma h^i_k (M_E^{-1})^k_j x^j \\
    &= (M_F)^i_l h^l_k (M_E^{-1})^k_j x^j
\end{align}
So $G$ acts on $h\in \Hom_R(E,F)$ is
\begin{align}
    [\sigma]: h^i_j &\mapsto  (M_F)^i_l h^l_k (M_E^{-1})^k_j
\end{align}
So, consider $g(f_i\otimes x^j)\in \Hom_R(E,F)$, we have
\begin{align*}
    [\sigma] [g (f_i\otimes x^j)] = [\sigma] A^j_i = (M_F)^j_l A^l_k
    (M_E^{-1})^k_i
\end{align*}
Hence
\begin{equation}
    \label{eq:g-iso-sggs}
    g(\sigma (f_i\otimes x^j )) = [\sigma] [g(f_i\otimes x^j)]
\end{equation}
\end{proof}

Whether $E$ is free or not, we define the \nomen{$G$-invariant
submodule of $E$} to be \nomen{$\operatorname{inv}_G(E)$}$=
R$-submodule of elements $x\in E$ such that $\sigma x=x$ for all
$\sigma\in G$. If $E,F$ are free, we have an $R$-isomorphism
\begin{equation}
    \operatorname{inv}_G (E^\vee\otimes F) \cong \Hom_G(E,F)
\end{equation}
\begin{proof}
    I give only a finite dimensional proof (for no proof is provided
    in Lang's book \cite{lang-algebra}. In finite dimensional case,
    this fact is closely related to the fact \ref{fact:Ev-F--Hom-G}:
    \begin{equation*}
        E^\vee \otimes F \overset{g}{\cong} \Hom_R(E,F)
    \end{equation*}

    Let me use the notation used before. The isomorphism is actually
    the $g$ defnied for equation \ref{eq:fx-g-aji}.

    On one hand, for $f_i\otimes x^j \in \operatorname{inv}_G
    (E^\vee\otimes F)$, denote $g(f_i\otimes x^j)$ by $A^j_i$. Then
    $g(\sigma (f_i\otimes x^j)) = g(f_i\otimes x^j) = A^j_i$ for any
    $\sigma\in G$. By equation \ref{eq:g-iso-sggs}, we have
    $[\sigma]A^j_i = A^j_i$, hence by fact \ref{fact:g-hom-sg-g}
    (notice that $A^j_i\in \Hom_R(E,F)$), $A^j_i\in \Hom_G(E,F)$.  The
    converse is similar.

    I think that for infinite dimensional cases, we might replace
    $\sum$ with $\int$ and use the same logic here.
\end{proof}

### 2016-11-16 Lecture note - Group Theory in Physics/serge lang/s-lang.tex
Split Lang's representation theory away from lecture notes. Noting about section 18.1 of Lang's representation of finite groups.

--- 2016-11-15 Lecture note - Group Theory in Physics/sections/s-lang.tex
@@
+% The entire content of this work (including the source code
+% for TeX files and the generated PDF documents) by 
+% Hongxiang Chen (nicknamed we.taper, or just Taper) is
+% licensed under a 
+% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
+% International License (Link to the complete license text:
+% http://creativecommons.org/licenses/by-nc-sa/4.0/).
+\documentclass{article}
+
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physicist-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physicist-taper}
+
+\makenomenclature
+
+% Show the keys for labels, replace options with "final" when done
+% with editing.
+\usepackage[draft,notref]{showkeys}
+
+\title{Representation theory of Finite Groups}
+\date{\today}
+\author{Taper}
+
+\begin{document}
+
+\maketitle
+\abstract{
+A note for correspoding chapter in S. Lang's book.
+}
+\tableofcontents
+
 \section{Representationas and Semisimplicity}
@@
 \end{proof}
+
+\begin{defi}[Sum $\rho\oplus \rho'$]
+\nomenclature{Sum $\rho\oplus \rho'$}{\nomrefpage.}
+If $\rho: G\to \Aut_R(E)$, $\rho':G\to \Aut_R(E')$ are two
+representation of $G$, we define their sum $\rho\oplus \rho'$ to be
+the representation on the direct sum $E\oplus E'$, with $\sigma\in G$
+acting componentwise.
+\end{defi}
+
+Give $G$, observe the $G$-isomorphism classes of representations have
+an additive monoid structure under the above direct sum, and also have
+an associative multiplicative structure under the tensor product. With
+the notation of representations, we denote this product by
+\nomen{$\rho\otimes \rho'$}. This product is distributive with respect
+to the addition (i.e. direct sum), by their definition.
+
+\begin{defi}[Trace $\Tr_G$]
+\nomenclature{Trace $\Tr_G$}{\nomrefpage.}
+    If $G$ is a finite group, and $E$ is a $G$-module, then we can
+    define the trace $\Tr_G:E\to E$ which is an $R$-homomorphism,
+    namely
+    \begin{equation}
+        \Tr_G(x) = \sum_{\sigma\in G} \sigma x
+    \end{equation}
+\end{defi}
+\begin{fact}
+$\Tr_G$ belongs to $ \operatorname{inv}_G (E)$, i.e. is
+fixed under the operation of any $\sigma\in G$:
+\begin{align*}
+    \tau \Tr_G(x) = \sum_{\sigma\in G} \tau \sigma x =
+    \sum_{\sigma'\in G} \sigma' x
+\end{align*}
+\end{fact}
+Let $E,F$ be twn $G$-modules, and $f:E\to F$ is an $R$-homomorphism of
+$G$-modules, then we can easily extend this definition to define
+\nomen{$\Tr_G(f)$} by
+\begin{align}
+    \Tr_G(f)&:E\to F \\
+    \Tr_G(f) &= \sum_{\sigma\in G} [\sigma] f \nonumber
+\end{align}
+Also, $\Tr_G(f)$ is invariant under any $\sigma\in G$, so it is a
+$G$-homomorphism, i.e.  $\Tr_G(f)\in \Hom_G(E,F)$.
+
+\begin{prop}
+    Let $G$ be a finite group and let $E,E',F,F'$ be $G$-modules, let
+    \begin{equation*}
+        E'\overset{\phi}{\to} E\overset{f}{\to} 
+            F \overset{\psi}{\to} F'
+    \end{equation*}
+    be $R$-homomorphism, and asume that $\phi,\psi$ are
+    $G$-homomorphisms. Then 
+    \begin{equation}
+        \Tr_G(\psi\circ f\circ\phi) = \psi\circ\Tr_G(f)\circ\phi
+    \end{equation}
+\end{prop}
+\begin{proof}
+    Proof is provided on the book \cite{lang-algebra}. The essential
+    point is that
+    \begin{equation}
+        [\sigma] (\psi\circ f\circ\phi) = \sigma \psi \sigma^{-1}
+        \sigma f \sigma^{-1} \sigma \phi \sigma^{-1} =
+        [\sigma]\psi\circ [\sigma]f\circ [\sigma]\phi 
+    \end{equation}
+\end{proof}
+
+\begin{thm}[Maschke]
+    Let $G$ be a finite group of order $n$, and let $k$ be a field
+    whose characteristic does not divide $n$. then the group ring
+    $k[G]$ is semisimple.
+\end{thm}
+Recall the an object is called \nomen{semisimple} if it is the direct
+sum of simple objects. A \nomen{simple} object is some ireducible
+building blocks, without being too simple to be simple. \footnote{
+    As remarked in nLab
+    (\href{https://ncatlab.org/nlab/show/too+simple+to+be+simple}{link}),
+    There is a general principle in mathematics that "A trivial object
+    is too simple to be simple". For example, $1$ is not a prime
+number.} A \nomen{simple ring} is a nonzero ring who has no two-sided ideals
+other than the zero ideal and itself.\footnote{ I did not find the
+    definition for a simple ring on Lang's book \cite{lang-algebra}.
+Rather, I found it online.}
+
+The proof of this theorem is provided in page 666, section 18.1 of
+\cite{lang-algebra}. I do not understand it. So I do not put it down
+here.
+
+\section{Anchor}
+\label{sec:Anchor}
+
+\begin{thebibliography}{1}
+    \bibitem{book} Zhongqi Ma, Group Theory in Physics
+    \bibitem{Ludeling} Lecture Notes for physics751: Group Theory (for
+    Physicists), by C Ludeling.
+    \href{http://www.th.physik.uni-bonn.de/nilles/people/luedeling/grouptheory/data/grouptheorynotes.pdf}{Link}
+    \bibitem{lang-algebra} Serge Lang. Algebra. Revised 3rd. Springer.
+\end{thebibliography}
+\printnomenclature
+\section{License}
+The entire content of this work (including the source code
+for TeX files and the generated PDF documents) by 
+Hongxiang Chen (nicknamed we.taper, or just Taper) is
+licensed under a 
+\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
+Commons Attribution-NonCommercial-ShareAlike 4.0 International 
+License}. Permissions beyond the scope of this 
+license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
+\end{document}

### 2016-11-16 Basic Topology Notes/Basic Topology.tex
Initiate notea on basic topology.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\makenomenclature

% Show the keys for labels, replace options with "final" when done
% with editing.
\usepackage[draft,notref]{showkeys}

\title{Notes of Basic Topolgy}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    A note of Basic Topology, based on \textit{Basic Topology} by M.A.
    Armstrong.
}
\tableofcontents
There are several parts that I will skipped for convenience. Those
include chapter 1 - Introduction, chapter 2 - Continuity, chapter 3 -
Compactness and Connectedness, and chapter 4 - Identification Spaces.
Below is some especially confusing part that I would like to note:

\section{Special Notes}
\label{sec:Special-Notes}
\paragraph{Basic facts about maps}
Assuming domain $f=X$, codomain $f=Y$.
\begin{align}
    f(U\cup V) &= f(U)\cup f(V) \\
    f(U\cap V) &= f(U)\cap f(V) \\
    f(U^c) &\supseteq f(U)^c,\,\text{i.e. } f(U)^c \subseteq f(U^c) \\
    f^{-1}(U\cup V) &= f^{-1}(U)\cup f^{-1}(V) \\
    f^{-1}(U\cap V) &= f^{-1}(U)\cap f^{-1}(V) \\
    f^{-1}(U^c) &= [f^{-1}(U)]^c
\end{align}
\paragraph{Smallest the Largest Topolgy}
The set of all possible topolgies on $X$ is partially ordered by
inclusion. For a certain characteristics $\mathcal{C}$, it is possible
to have the smallest or the largest one.

The \nomen{smallest topolgy} $\mathcal{T}_\text{min}$ is the one such
that, for any $\mathcal{T}'$ satisfying $\mathcal{C}$,
$\mathcal{T}_\text{min}\subseteq \mathcal{T}'$. The \nomen{largest
topolgy} $\mathcal{T}_\text{max}$ is the one such that, for any
$\mathcal{T}'$ satisfying $\mathcal{C}$, $\mathcal{T}'\subseteq
\mathcal{T}_\text{max}$.

For example, assuming we have
\begin{equation}
    f: X\to Y
\end{equation}
where $f$ is any function.

If $X$ has topolgy $\mathcal{T}_X$, we ask then what kind of topolgy on
$Y$ will make $f$ a continuous function. First, all $f^{-1}(V)$, with
$V\in \mathcal{T}_Y$ should be open in $X$. So, the easiest choice is to
make $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$, this is the
smallest topolgy.  Also, any set $V\in Y$ such that $f^{-1}(V)\notin
\mathcal{T}_X$ should not be in $\mathcal{T}_Y$. Then the largest
topolgy is $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in
\mathcal{T}_X\}$.

If $Y$ has topolgy $\mathcal{T}_Y$, we also ask what kind of topolgy
on $X$ will make $f$ a continuous function. First, all $V\in
\mathcal{T}_Y$, their preimage $f^{-1}(V)$ must be in $\mathcal{T}_X$.
So the smallest topolgy is
$\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$.
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    \bibitem{book} M.A. Armstrong. Basic Topology. 2ed.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-11-17 Basic Topology Notes/Basic Topology.tex
About identification topology (glueing spaces) - Basic Topology.

@@
 \label{sec:Special-Notes}
+\paragraph{About map} In book \cite{book}, a map is defined as a
+continuous function (page 32), which is confusing. In this note, I
+will not use this convention and will always states continuity
+clearly.
+
 \paragraph{Basic facts about maps}
@@
     f(U\cup V) &= f(U)\cup f(V) \\
-    f(U\cap V) &= f(U)\cap f(V) \\
+    f(U\cap V) &\subseteq f(U)\cap f(V) \\
     f(U^c) &\supseteq f(U)^c,\,\text{i.e. } f(U)^c \subseteq f(U^c) \\
@@
 \mathcal{T}_\text{max}$.
-
+Synonyms of these two words are:
+\begin{itemize}
+    \item Larger: stronger, finer.
+    \item Smaller: weaker, coarser.
+\end{itemize}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.65\linewidth]{pics/comparing-topologies-and-coffee.jpg}
+    \caption{Comparing topologies and coffee (Credit:
+    \href{http://www.math3ma.com/the-back-pocket/2016/8/26/comparing-topologies}{math3ma})}
+\end{figure}
 For example, assuming we have
@@
 So the smallest topolgy is
-$\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$.
+$\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$. Than
+what about the largest topolgy? We consider, what kind of sets cannot
+be inside $\mathcal{T}_X$. First, can $(f^{-1}(V))^c=f^{-1}(V^c)$ be
+in $\mathcal{T}_X$? Yes. Since unless the space is connected, there
+can be sets being both open and closed (other than $X$ and
+$\varnothing$). Any other restrictions? No that I can think of. So,
+the largest topolgy $\mathcal{T}_{X,\text{max}}=2^X$, the set of all
+subsets of $X$. (The notation \nomen{$2^X$} is taken from the page 4
+of book \cite{Singer.Thorpe}.
+
+A summary:
+\begin{table}[H]
+    \centering
+    \caption{Largest and Smallest Topolgies}
+    \begin{tabular}{c l l}
+        $X\overset{f}{\to}Y$ & Smallest  &Largest \\
+        \hline
+        Given $\mathcal{T}_X$ & $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$        & $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in \mathcal{T}_X\}$\\
+        Given $\mathcal{T}_Y$ & $\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$ & $\mathcal{T}_{X,\text{max}}=2^X$ \\
+        No constraint & $\{\varnothing,X\}$ & $2^X$ \\
+        \hline
+    \end{tabular}
+\end{table}
+\paragraph{Facts about subspace/induced topolgy}
+Let $Y$ be a subspace of a topological space $X$ wit induced topolgy.
+\begin{fact}
+    A set $H\subseteq Y$ is open in $Y$ if and only if $H=F\cap Y$
+    for some open set $F$ in $X$.
+\end{fact}
+\begin{fact}
+    A set $H\subseteq Y$ is closed in $Y$ if and only if $H=F\cap Y$
+    for some closed set $F$ in $X$.
+\end{fact}
+\begin{fact}
+    A set $H$ is open/closed in $X$ $\Rightarrow$ $H$ is open/closed
+    in $Y$. But the converse may not be true. The converse statement
+    depends on whether $Y$ is open or closed in $X$.
+\end{fact}
+\section{Collection of Theorems in Chapter 4}
+\label{sec:Collection-of-Theorems-in-Chapter-4}
+\begin{defi}[Identification Topology]
+\nomenclature{Identification Topology}{\nomrefpage.}
+Let $X$ be a topological space and let $\mathscr{P}$ be a family of
+disjoint nonempty subsets of $X$ such that $\cup \mathscr{P}=X$. Such
+a family is usually called a partition of $X$. Let $Y$ be a new space
+whose points are the members of $\mathscr{P}$. Let $\pi:X\to Y$ sends
+each point of $X$ to the subset of $\mathscr{P}$. Define a topolgy
+$\mathcal{T}_Y$ on $Y$ to be the largest topolgy such that the $\pi$
+is continuous. This $\mathcal{T}_Y$ is called the idetification topolgy.
+And $Y$ is called the \nomen{identification space}.
+\end{defi}
+\begin{center} \begin{tikzcd}[]
+    X\ar[r]\ar[rd] & Y\ar[d,equal] \\
+    & \mathscr{P}
+\end{tikzcd} \end{center}
+\begin{thm}
+    Let $Y$ be an idetification space defined as above and let $Z$ be
+    an arbitrary topological space. A function $f:Y\to Z$ is
+    continuous if and ony if the composition $f\circ \pi:X\to Z$ is
+    continuous.
+\end{thm}
+\begin{center} \begin{tikzcd}[]
+    X\ar[r,"\pi"]\ar[rd]\ar[rr,"f\circ\pi",bend left=30] & Y\ar[d,equal]\ar[r,"f"] & Z \\
+    & \mathscr{P}
+\end{tikzcd} \end{center}
+\begin{defi}[Identification Map]
+\nomenclature{Identification Map}{\nomrefpage.}
+    Let $f:X\to Y$ be an onto continuous map and suppose that the topolgy on $Y$
+    is the largest for which $f$ is continuous. Then we call $f$ an
+    identification map.
+\end{defi}
+The naming "identification map" is because:
+\begin{thm}
+    Any function $f:X\to Y$ gives rise to a partition of $X$ whose
+    members are the subsets $\{f^{-1}(y)\}$, where $y\in Y$. Let $Y_*$
+    denote the identification space associated with this partition,
+    and $\pi:X\to Y_*$ the usual continuous map. 
+    $$ \begin{tikzcd}[]
+        X\ar[r,"f"]\ar[d,"\pi"] & Y \\
+        \{f^{-1}(y)\} \ar[r,equal] & Y_*
+    \end{tikzcd} $$
+    If $f$ is an identification map, then:
+    \begin{enumerate}
+        \item the spaces $Y$ and $Y_*$ are homeomorphic;
+        \item a function $g:Y\to Z$ is continuous if and only if the
+            composition $g\circ f:X\to Z$ is continuous.
+    \end{enumerate}
+    $$ \begin{tikzcd}[]
+        X\ar[r,"f"]\ar[d,"\pi"]\ar[rr,"g\circ f",bend left] 
+            & Y\ar[d,equal,"~"]\ar[r,"g"] & Z \\
+        \{f^{-1}(y)\} \ar[r,equal] & Y_*
+    \end{tikzcd} $$
+\end{thm}
+\begin{thm}
+    Let $f:X\to Y$ be an onto continuous map. If $f$ maps open sets of
+    $X$ to open sets of $Y$, or closed sets to closed sets, then $f$
+    is an identification map, i.e. $\mathcal{T}_y$ is the largest
+    topolgy such that $f$ is continuous.
+\end{thm}
+\begin{coro}
+    \label{coro:idmap-coro}
+    Let $f:X\to Y$ be an onto continuous map. If $X$ is compact and
+    $Y$ is Hausdorff, then $f$ is an identification map.
+\end{coro}
+
+\begin{defi}[Torus]
+\nomenclature{Torus}{\nomrefpage.}
+Torus is the uTorusquare $[0,1]\times[0,1]$, with 1. opposite edge
+identified, 2. four edge points identified.
+\end{defi}
+\begin{remark}
+    The identification map and corollary \ref{coro:idmap-coro} can be
+    used to show that torus is homeomorphic to two copies of
+    circles:$S^1\times S^1$. This is mentioned in page 68 of
+    \cite{book}.
+\end{remark}
+\begin{defi}[Cone $CX$]
+\nomenclature{Cone $CX$}{\nomrefpage.}
+    The cone of any space $CX$ is formed from $X\times I$, where $I$ is
+    the unit interval $[0,1]$, with certain identification. The
+    identification shrinks all points in one surface into one point.
+    This is discussed in page 68 of \cite{book}.
+\end{defi}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\linewidth]{pics/{Cone-of-a-circle}.pdf}
+    \caption{Cone of a Circle (Wikipedia)}
+\end{figure}
+\begin{remark}
+    There is another definition of cone $CX$ when $X$ in imbeded into
+    $\mathbb{E}^n$, may be found on page 68 of \cite{book}. Cone
+    constructed in this way is called a geometric cone. It is made up
+    of all straight line segments that join $v=(0,0,\cdots,1)\in
+    \mathbb{E}^{n+1}$ to some point of $X$.
+\end{remark}
+\begin{lemma}
+    The geometric cone on $X$ is homeomorphic to $CX$.
+\end{lemma}
+\begin{defi}[Quotient Space]
+\nomenclature{Quotient Space}{\nomrefpage.}
+    Let $X$ be a topological space, $A$ be its subspace. Then $X/A$
+    menas the $X$ with subspace $A$ identified to a point.
+    \begin{enumerate}
+        \item the set $A$.
+        \item the individual points of $X\setminus A$.
+    \end{enumerate}
+\end{defi}
+\begin{remark}
+    In this notation, $CX$ becomes $(X\times I)/(X\times\{1\})$.
+\end{remark}
+\begin{fact}
+    \begin{equation}
+        B^n/S^{n-1} \cong S^n
+    \end{equation}
+    where $\cong$ menas homeomorphic. This is proved on page 69.
+    Intuitively, this is like wrap a lower dimension ball surround the
+    higher dimension ball.
+\end{fact}
+
+\begin{defi}[$f\cup g$]
+\nomenclature{$f\cup g$}{\nomrefpage.}
+    Let $X,Y$ $f\cup g$ subsets of a topological space and give each of
+    $X,Y$, and$X\cup Y$ the induced topolgy. If $f:X\to Z$ and
+    $g:Y\to Z$ are functions which agree on the intersection of $X$
+    and $Y$, we can define
+    \begin{align}
+        f\cup g &: X\cup Y \to Z  \\
+        (f\cup g)(x) &= f(x),\, x\in X \nonumber \\
+        (f\cup g)(x) &= g(x),\, x\in Y \nonumber
+    \end{align}
+    We say that $f\cup g$ are formed by 'glueing together' the
+    functions $f$ and $g$.
+\end{defi}
+\begin{lemma}[Glueing lemma (closed)]
+    If $X$ and $Y$ are closed in $X\cup Y$, and if both $f$ and $g$
+    are continuous, then $f\cup g$ are continuous.
+\end{lemma}
+Similarly, 
+\begin{lemma}[Glueing lemma (open)]
+    If $X$ and $Y$ are open in $X\cup Y$, and if both $f$ and $g$
+    are continuous, then $f\cup g$ are continuous.
+\end{lemma}
+
+These two lemmas are seen as a special case of the following theorem,
+explained in page 70.
+
+Define \nomen{$X+Y$} to be the disjoint union of spaces $X,Y$. Define
+$j:X+Y \to X\cup Y$ which restrict to either $X$ or $Y$ is just the
+inclusion in $X\cup Y$.
+\begin{thm}
+    If $j$ is an identification map, and if both $f:X\to Z$ and
+    $g:X\to Z$ are continuous, then $f\cup g:X\cup Y\to Z$ is
+    continuous.
+\end{thm}
+$$ \begin{tikzcd}[]
+    X+Y \ar[r,"j"] & X\cup Y\ar[r,"f\cup g"] & Z \\
+    X\ar[rru,"f"] & Y\ar[ru,"g",bend right]
+\end{tikzcd}$$
+
+This can be generalized as follows. Let $X_\alpha,\alpha\in A$ be a
+family of subsets of a topological space and give each $X_\alpha$ and
+the union $\cup X_\alpha$, the induced topolgy. Let $Z$ be a space and
+suppose we are given maps $f_\alpha:X_\alpha\to Z$, one for each
+$\alpha$ in $A$, such that if $\alpha,\beta\in A$,
+$$ 
+\eval{f_\alpha}_{X_\alpha\cap X_\beta} = \eval{f_\beta}_{X_\alpha\cap X_\beta}
+$$
+Define function $F:\cup X_\alpha\to Z$ by glueing together $f_\alpha$.
+Let $\oplus X_\alpha$ be the disjoint unin of spaces $X_\alpha$. Let
+$j:\oplus X_\alpha \to \cup X_\alpha$ be similarly defined.
+\begin{thm}
+    If $j$ is an identification map, and if each $f_\alpha$
+    is continuous, then $F$ is continuous.
+\end{thm}
+\textbf{Note}: When $j$ is the identification map, then $\cup
+X_\alpha$ has the identification topolgy instead of the subspace
+topology. The two will be quite different, as discussed on page 70 to
+71 of \cite{book}.
+
+\begin{defi}[Projective space $P^n$]
+\nomenclature{Projective space}{\nomrefpage.}
+    A discussion of real $P^n$ may be found on page 71.
+\end{defi}
+
+\paragraph{\nomen{Attaching maps} and $X\cup_f Y$} Let:
+\begin{equation}
+    Y \supseteq A \overset{f}{\to} X
+\end{equation}
+where $X,Y$ are topological spaces, $f$ is continuous. We identify the
+disjoint union $X+Y$ using $f$, partitioning them into:
+\begin{enumerate}
+    \item pairs of points $\{a,f(a)\}$ where $a\in A$;
+    \item individual points of $Y\setminus A$;
+    \item individual points of $X\setminus \Im(f)$.
+\end{enumerate}
+The result identification space is denoted $X\cup_f Y$, and $f$ is
+called the attaching map. This process can also be viewed as:
+\begin{equation}
+    X\cup_f Y = (X\amalg Y)/\{f(A)~A\}
+\end{equation}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/Attaching-Space.jpg}
+    \caption{Attaching Space (credit:
+        \href{https://ncatlab.org/nlab/show/Top}{nLab}}
+\end{figure}
+\begin{ex}
+    $P^2$ can be seen as attaching a closed disc $D$ to the boundary
+    of $M$, a Mobius strip, as discussed in page 72 of \cite{book}.
+    Geometrically, this simply shrinks the boundary of $M$ into a
+    point. And an ant travelling around this point can point out the
+    direction just as in $P^2$.
+\end{ex}
+
 \section{Anchor}
@@
     \bibitem{book} M.A. Armstrong. Basic Topology. 2ed.
+    \bibitem{Singer.Thorpe} I.M. Singer, J.A. Thorpe. Lecture Notes on
+    Elementary Topology and Geometry. UTM.
 \end{thebibliography}

### 2016-11-17 Lecture note - Group Theory in Physics/serge lang/s-lang.tex
Read a bit about characters in S. Lang's language. I should learn more about modules to understand the idea of simple module and simple ring.

@@
 \begin{equation}
+    \label{eq:M-dual-M-1T}
     M^\vee = (M^{-1})^T
@@
 
+\section{Characters}
+\label{sec:Characters}
+Assuming in this section that, $G$: a finite group. $k$: a field of
+characteristic not dividing $|G|$. $E,F$: finite dimensional $k$-spaces.
+$n=|G|$.
+
+\begin{defi}[Character $\chi$]
+\nomenclature{Character $\chi$}{\nomrefpage.}
+    The character $\chi$ of a representation $\rho:k[G]\to \End_k(E)$
+    is defined as
+    \begin{align}
+        \chi: k[G] &\to k \\
+        \alpha &\mapsto \Tr(\rho(\alpha))
+    \end{align}
+    We sometimes write it as $\chi_\rho$ or $\chi_E$.
+\end{defi}
+The \nomen{trivial character} is sometimes denoted as \nomen{$\chi_0$}
+or \nomen{$1_G$}.
+
+\begin{remark}
+By the $k$-linearity of trace function, we observe that characters are
+determined by its values on $G$.
+\end{remark}
+
+\begin{defi}[Isomorphic Representations]
+\nomenclature{Isomorphic Representations}{\nomrefpage.}
+    Two representations $\rho,\phi$ of $G$ on spaces $E,F$ are
+    isomorphic if and only if  there is a $G$-isomorphism between $E$
+    and $F$.
+\end{defi}
+\begin{equation} \begin{tikzcd}[column sep=small]
+    & G\ar[dl,"\rho" left=3]\ar[dr,"\phi"] &  \, \\
+        E \ar[rr,"\rho" below=3] &
+            \ar[u,phantom, "\#"] 
+                & F
+\end{tikzcd} \end{equation}
+\begin{align}
+    f(\rho(\sigma)) &= \phi(\sigma) f, \, \forall \sigma\in G
+\end{align}
+In matrix notation, 
+\begin{equation}
+    F \rho_\sigma = \phi_\sigma F,\, \forall\sigma\in G
+\end{equation}
+\textbf{Note}: In everything that follows, we are interested only in
+isomorphism classes of representations.
+
+If $E,F$ are $G$-spaces, then their direct sum $E\oplus F$ is also a
+$G$-space, the operation of $G$ being componentwise. If $x\oplus y\in
+E\oplus F$ with $x\in E,\,y\in F$, then $\sigma(x\oplus y)=\sigma
+x\oplus \sigma y$.
+
+Similarly, the tensor product $E\otimes_k F=E\otimes F$ is a
+$G$-space, the operation $G$ being given by $\sigma(x\otimes y)=\sigma
+x\otimes \sigma y$.
+
+\begin{prop}
+    \label{prop:character-ring}
+    If $e,F$ are $G$-spaces, then
+    \begin{align}
+        \chi_E +\chi_F &= \chi_{E\oplus F} \\
+        \chi_E\chi_F   &= \chi_{E\otimes F}
+    \end{align}
+    If $\chi^\vee$ denotes the character of the dual representation on
+    $E^\vee$, then
+    \begin{align}
+        \chi^\vee(\sigma) = \chi(\sigma^{-1})
+    \end{align}
+    In particular, when $k=\mathbb{C}$, then
+    \begin{equation}
+        \chi^\vee(\sigma) = \overline{\chi(\sigma)}
+    \end{equation}
+\end{prop}
+\begin{proof}
+    The first relation is obvious.
+
+    The second relation holds from the following observation,
+    \begin{align*}
+        \sigma(v_i \otimes w_j) = \sigma v_i \otimes \sigma w_j =
+        A_{i\nu} v_v \otimes B_{j\mu} w_\mu
+    \end{align*}
+    So its character is
+    \begin{equation*}
+        \chi_{E\otimes F}(\sigma) = A_{ii} B_{jj} =
+        \chi_E(\sigma)\chi_F(\sigma)
+    \end{equation*}
+    The third relation follows from that the matrix of dual
+    representation is the matrix $(M^{-1})^T$, see equation
+    \ref{eq:M-dual-M-1T}.
+
+    The last relation will be proved in corollary % TODO
+\end{proof}
+
+We now extend the definition of \nomen{character} to a function of
+$G$, which can be written in a linear combination of characters of
+representations with arbitrary integer coefficients. Then, the
+previous characters are very special. Such characters associated with
+representations will be called \nomen{effective characters}. Note
+that everything we have defined of course depends on the field $k$,
+and we shall add \textbf{over} $\mathbf{k}$ to ouirexpressions if we
+need to specify the field $k$.
+
+\begin{remark}
+    By proposition \ref{prop:character-ring}, all the characters form
+    a ring structure.
+\end{remark}
+
+By a \nomen{simple} or \nomen{irreducible character} of $G$ one means
+the character of a simple representation, i.e., the character
+associated with a simple $k[G]$-module.
+
 \section{Anchor}
@@
 \end{thebibliography}
-\printnomenclature
 \section{License}
@@
 license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
+
+\printnomenclature
 \end{document}

### 2016-11-18 Latex packages/latex examples.tex
Read a bit about characters in S. Lang's language. I should learn more about modules to understand the idea of simple module and simple ring.
Fix some issue about latex package "physicist-taper". Add some crude simple notes about the classification paper.

@@
 \tableofcontents
+\section{Nomenclature}
+
+\nomenclature{aa}{aaa}
+
+\section{Diagram}
+
 \begin{center}
@@
 \begin{center}
-    A good diagram
+    Good diagrams
 \end{center}
@@
 $$
+$$ \begin{tikzcd}[column sep=small]
+& G &  \, \\
+E \ar[ur,"f"]\ar[rr,"\rho" below=3] &
+\ar[u,phantom, "\#"] 
+& F\ar[ul,"\rho'" right=3]
+\end{tikzcd} $$
 
+\section{Table}
+
+\begin{table}[ht]
+	\centering
+	\caption{Classification}
+	\label{tab:classification}
+	\vspace{+0.5pt}
+	\rowcolors{1}{white}{lightgrey}
+	\tabulinesep=1.2mm
+	\begin{tabu}{  X[l] X[l] X[l] X[l] }
+		\textit{Symmetry} & \textit{Spatial Dimension} &
+		\textit{Result} & \textit{Other Keywords} \\
+		\hline
+		T & 0 & An intger: the number of particle-occupied Kramers
+		doublet states & \\
+		T & 1 & None & \\
+		T & 2 & $\mathbb{Z}_2$ & \\
+		T & 3 & $\mathbb{Z}_2$ & $3D$ crystals have additional
+		$3\mathbb{Z}_2$ invariant$ \Rightarrow$ "weak topological
+		insulators \\
+		Q(?) & 2 & Characterized by $\mu$ in units of $e^2/h$ & TKNN \\
+		Q(?) & even  d & Topological invariant ($k$-th Chern number) \\
+		Q(?) & 0 &  number of single-particle states with negative
+		energy ($E< E_F = 0$), which are filled with electrons. \\
+		T\& Q \\
+		No T \& No Q & 0 & $\mathbb{Z}_2$ \\
+		No T \& No Q & 1 &$\mathbb{Z}_2$ &"majorana chain"  \\
+		No T \& No Q & 2 & Topological number is integer. & Even-odd
+		effects. \\
+		\bottomrule
+	\end{tabu}
+\end{table}
 \section{Anchor}
@@
 \begin{thebibliography}{1}
-    %\bibitem{book} 
+    \bibitem{book}  s
 \end{thebibliography}

### 2016-11-18 Notes of various papers/Classification of topological quantum matter with symmetries. Rev.M.P/notes.tex
Fix some issue about latex package "physicist-taper". Add some crude simple notes about the classification paper.

--- 2016-11-10 Notes of various papers/Classification of topological quantum matter with symmetries. Rev.M.P/doubts.tex
@@
 \tableofcontents
+\section{Doubts}
+\label{sec:Doubts}
+
 \paragraph{Asks}
@@
         temporal defect. Is this true?
+    \item page 42, what is a nodal system, what are nodal points?
 \end{enumerate}
@@
 \end{enumerate}
+\section{Summary}
+\label{sec:Summary}
+
+\subsection{About topological matter}
+\label{sec:About-topological-matter}
+Topological states:
+\begin{itemize}
+    \item Topological insulators cannot be distinguished from
+        ordinary, topologically trivial insulators in terms of their
+        symmetries.
+    \item topological insulators' topological nontriviality cannot be
+        detected by a local order parameter.
+    \item insulating electronic band structures can be categorized in
+        terms of topology.
+    \begin{itemize}
+        \item time-reversal are crucial in makeing a spin-orbit induced
+            topological insulators. $ \Rightarrow$ symmetry-protected
+            topological phases (\nomen{SPT}).
+        \item symmetry-protected topological phase can also arise from
+            spatial symmetry.
+    \end{itemize}
+    \item There is a direct analogy between \nomen{TI}s and
+        \nomen{TSC}s (topological insulators and topological
+        superconductors).
+    \item \nomen{bulk-boundary correspondence} $ \Leftarrow$
+        topological phase transition. (pp. 11).
+    \item \nomen{nodal systems} can exhibit band topology even though
+        their bulk gap closes at certain points in BZ.
+    \item All of the above are understood in terms of non-interacting
+        or mean-field Hamiltonians. Less is known about strongly
+        correlated systems.
+\end{itemize}
+
+\subsection{Features of Tenfold for Gapped System}
+\label{sec:Tenfold-for-Gapped-System}
+\nomen{Topological equivalence}. $l:$ adiabatic path or continuous path in
+phase diagram. Then topological class are characterized by invariance
+of gap under $l$.
+
+\nomen{Trivial class}: The topological classes of state
+characterized by atomic insulators.
+
+\nomen{Weak topological phase}: nontrivial topological phase relies
+on lattice-translational symmetry.
+\nomen{Strong topological phase}: ... that does not rely on
+translational symmetry.
+
+\paragraph{Classfication of Gapless}
+\begin{itemize}
+    \item $2$ complex symmetry classes, $8$ real symmetry classes.
+    \item The presence or absence of weak TIs or TSCs in a given
+        symmetry classes can be deduced from that of strong TIs or
+        TSCs in lower dimension in the same symmetry class. So the
+        classification aims for the strong ones.
+        % TODO expands following in the future.
+    \item \nomen{dimensional shift} (pp. 11).
+    \item \nomen{primary series}, \nomen{first/second decendants},
+        \nomen{even series}:
+        class of items in the periodic table. (pp. 12).
+\end{itemize}
+
+\paragraph{Classfication with defects}
+\begin{itemize}
+    \item \nomen{defect Hamiltonian} $H(k,r)$,$r=(x,t)$. Key: $r$
+        varies slowly ($\xi|\grad_r H(r,k)|\ll \varepsilon_g$). page
+        13.
+    \item Characterization (wrapped by $S^D$)
+        \begin{enumerate}
+            \item $s$: AZ symmetry class
+            \item $d$: bulk dimension
+            \item $d_c$: defect codimension
+            \begin{itemize}
+                \item real AZ class: $s-\delta$ (mod $8$)
+                    ($\delta=d-D$, topological dimension)
+                \item complex AZ classes, similarly
+            \end{itemize}
+        \end{enumerate}
+    \item Relate real and complex: forgetful functor.
+    \item \nomen{bulk-defect correspondence}: guarantees gapless
+        defect excitation.
+\end{itemize}
+\paragraph{Topological Invariants} $ $
+
+\nomen{Base space}:
+\begin{equation}
+\begin{tikzcd}[]
+    (\vb{k},\vb{r})\in \text{BZ}^d\times \mathcal{M}^D
+    \ar[rr, "\text{compactify}"] &\, & S^{d+D}
+\end{tikzcd}
+\end{equation}
+Table 3 in page 13, is a summary of invariants:
+\nomen{s}:= AZ symmetry class. \nomen{Ch}: Chern number.
+\nomen{CS}:Chern-Simons invariant. \nomen{$\nu$}: Winding number.
+\nomen{FK}: Fu-Kane.
+\begin{table}[H]
+    \centering
+    \caption{caption}
+    \label{tab:label}
+    \begin{tabu}{c c c}
+        $\,$ & $s$ even & $s$ odd \\
+        \hline
+        $\mathbb{Z}$ & Ch & $\nu$ \\
+        $\mathbb{Z}_2^{(1)}$ & CS & FK \\
+        $\mathbb{Z}_2^{(2)}$ & FK & CS ($\widetilde{\text{CS}}$) \\
+        \bottomrule
+    \end{tabu}
+\end{table}
+
+\subsection{Chern Number}
+\label{sec:Chern-Number}
+It detects an obstruction in defining a set of bloch wave functions
+smooothly over the base space.
+
+\nomen{Fibres} The fibres of the fibre-bundle on the base space are
+wave functions under adiabatic changes. They may be twisted.
+
+\nomen{Twist}: Think of the M\"obius strip as a twisted fibre bundle.
+A good resource:
+\href{http://math.stackexchange.com/questions/1377855/cylinder-and-m%C3%B6bius-strip-as-fiber-bundles-trivializations-and-cocycles}{Cylinder
+and Möbius strip as fiber bundles}. 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.2\linewidth]{pics/mobius-fibre.png}
+    \caption{M\"obius Strip, 
+        Credit:
+        \href{https://www.quora.com/What-is-a-Fiber-Bundle-in-laymans-terms-What-is-it-used-for}{Quora} }
+\end{figure}
+
+\begin{thm}
+    The set of Bloch functions (i.e. projectors) defines a map from the
+    base space to $U(N_+ +N_-)/U(N_+)\times U(N_-)$. Topological
+    distinct maps of this type can be classified by their homotopy
+    group
+    \begin{equation}
+        \pi_{d+D}[U(N_+ +N_-)/U(N_+)\times U(N_-)]
+    \end{equation}
+\end{thm}
+
+When $N_\pm$ is large enough, and when $d+D$ is even, this group is
+$\mathbb{Z}$, the integer topological invariant is the Chern number.
+
+\subsection{Winding number}
+\label{sec:Winding-number}
+\begin{itemize}
+    \item Can only be defined in the presence of chiral symmetry.
+    \item Relavant space: $U(N), \Rightarrow$
+    \item $Q$ matrix (projector) Can be classified by
+        $\pi_{d+D}[U(N)]$, which is nontrivial when $d+D$ is odd. When
+        $d+D$ is odd, $\pi_{d+D}[U(N)]=\mathbb{Z}$, with maps
+        characterized by the winding number.
+\end{itemize}
+
+\subsection{Chern-Simons invariant}
+\label{sec:Chern-Simons-invariant}
+\begin{itemize}
+    \item Can be defined when $d+D$ is odd.
+    \item Symmetry $\rightarrow$ Quantized/Discrete CS invariant. e.g.
+        \begin{itemize}
+            \item chiral symmetry quantizes CS
+        \end{itemize}
+    \item Not gauge-invariant.
+        \begin{itemize}
+            \item But $W:= \exp{2\pi i \,\text{CS}}$ is gauge-invariant.
+        \end{itemize}
+\end{itemize}
+
+\subsection{Fu-Kane Invariant}
+\label{sec:Fu-Kane-Invariant}
+\begin{itemize}
+    \item Construction requires special attention in the choice of basis
+\end{itemize}
+
+\subsection{K-theory Approach}
+\label{sec:K-theory-Approach}
+\begin{itemize}
+    \item Topological nontrivial phases $\Rightarrow$ have massive
+        Dirac Hamiltonian representatives
+\end{itemize}
 \section{Anchor}
@@
 \begin{thebibliography}{1}
-    %\bibitem{book} 
+    \bibitem{review}
+    \url{http://journals.aps.org/rmp/abstract/10.1103/RevModPhys.88.035005}
 \end{thebibliography}

### 2016-11-18 Basic Topology Notes/Basic Topology.tex
Read a bit about characters in S. Lang's language. I should learn more about modules to understand the idea of simple module and simple ring.
Section 4.3 about topological groups for Basic topology.

@@
 \end{fact}
-\section{Collection of Theorems in Chapter 4}
-\label{sec:Collection-of-Theorems-in-Chapter-4}
+\section{A Brief Note of Chapter 4 - Identification Spaces}
+\label{sec:Brief-Note-Chapter-4}
+\subsection{Identification topology}
+\label{sec:Identification topology}
+
 \begin{defi}[Identification Topology]
@@
 \nomenclature{Torus}{\nomrefpage.}
-Torus is the uTorusquare $[0,1]\times[0,1]$, with 1. opposite edge
-identified, 2. four edge points identified.
+Torus is the unit square $[0,1]\times[0,1]$, with 1. opposite edge
+identified; 2. four edge points identified.
 \end{defi}
@@
 \end{remark}
-\begin{defi}[Cone $CX$]
-\nomenclature{Cone $CX$}{\nomrefpage.}
-    The cone of any space $CX$ is formed from $X\times I$, where $I$ is
-    the unit interval $[0,1]$, with certain identification. The
-    identification shrinks all points in one surface into one point.
-    This is discussed in page 68 of \cite{book}.
+\begin{defi}[Cone $\textrm{CX}$]
+\nomenclature{Cone $\textrm{CX}$}{\nomrefpage.}
+    The cone of any space $\textrm{CX}$ is formed from $X\times I$, where
+    $I$ is the unit interval $[0,1]$, with certain identification. The
+    identification shrinks all points in one surface into one point.  This
+    is discussed in page 68 of \cite{book}.
 \end{defi}
@@
 \begin{remark}
-    There is another definition of cone $CX$ when $X$ in imbeded into
+    There is another definition of cone $\textrm{CX}$ when $X$ in imbeded into
     $\mathbb{E}^n$, may be found on page 68 of \cite{book}. Cone
@@
 \begin{lemma}
-    The geometric cone on $X$ is homeomorphic to $CX$.
+    The geometric cone on $X$ is homeomorphic to $\textrm{CX}$.
 \end{lemma}
@@
 \begin{remark}
-    In this notation, $CX$ becomes $(X\times I)/(X\times\{1\})$.
+    In this notation, $\textrm{CX}$ becomes $(X\times I)/(X\times\{1\})$.
 \end{remark}
@@
 \begin{equation}
-    X\cup_f Y = (X\amalg Y)/\{f(A)~A\}
+    X\cup_f Y = (X\amalg Y)/\{f(A)\sim A\}
 \end{equation}
@@
 \end{ex}
+\begin{remark}
+    It is remarked that properties such as compactness, connectedness,
+    and path-connectedness is inherited in identification. However,
+    Hausdorff-ness is not. An counter example can be found in page 72 of
+    \cite{book}.
+\end{remark}
+
+\subsection{Topological Groups}
+\label{sec:Topological-Groups}
+
+In simple words, \nomen{topological groups} are objects that has both
+a topolgy on it and a group structure in it. And the two structures
+must be compatible. Specifically, the multiplication map $a\cdot b$
+and the inverse map $a\to a^{-1}$ are continuous. Homomorphisms
+between are both group-homomorphisms and topological-homomorphisms
+(continuous maps). Isomorphisms are both group-isomorphisms and
+topolgy-isomorphisms (homeomorphisms). A sub-(topological group) is
+both a subgroup and has subspace topolgy. For convenience of language,
+use \nomen{$\mathcal{TPG}$} denotes the category of topological groups.
+\footnote{This notation is nowhere popular or accepted. I use it to
+only to save space and time.}
+\begin{ex}
+    The $\mathbb{R}$ is a topological group. 
+    The $\mathbb{Z}$ with discrete topology form the sub-(topological
+    group) of $\mathbb{R}$. The quotient $\mathbb{R}/\mathbb{Z}$ forms
+    a topological group. The map $f: \mathbb{R}\to S^1$ induces a
+    homeomorphism $\mathbb{R}/\mathbb{Z} \cong S^1$, which is also a
+    group isomorphisms, i.e. it is a $\mathcal{TPG}$-isomorphism.
+\end{ex}
+\begin{ex}
+    Similarly, $R^n$.
+\end{ex}
+
+\begin{ex}
+    The circle is also one. The group structure is combination of
+    degrees.
+\end{ex}
+\begin{ex}
+    Any group with discrete topology.
+\end{ex}
+\begin{ex}
+    The torus considered as the product of two circles. (Take the
+    producttopology and the product group structure.
+\end{ex}
+\begin{ex}
+    Three sphere $S^3$ considered as the unit sphere in the space of
+    quaterions $\mathbb{H}$.
+
+    Remember this? :
+    $$ \begin{tikzcd}[column sep=small]
+        & i\ar[dr] &  \, \\
+    k \ar[ur] &
+    \ar[u,phantom, "\#"] 
+    & j\ar[ll]
+    \end{tikzcd} $$
+    The unit sphere are unit quaterions, see more
+    \href{https://en.wikipedia.org/wiki/Versor}{Versor}.
+\end{ex}
+\begin{ex}
+    The \nomen{orthogonal group} $\mathrm{O}(n)$, of $n\times n$
+    orthogonal real matrices. It is easy to check that
+    $\mathrm{O}(n-1)$ is a sub-$\mathcal{TPG}$ of $\mathrm{O}(n)$.
+\end{ex}
+
+\begin{defi}[Left translation $L_x$]
+\nomenclature{Left translation $L_x$}{\nomrefpage.}
+    For $x\in G$, the function
+    \begin{align}
+        L_x: G &\to G \\
+          g &\mapsto xg
+    \end{align}
+    is called a left translation by $x$. Similarly we have
+    \nomen{right translation $R_x$}.
+\end{defi}
+\begin{fact}
+    $L_x$ and $R_x$ are homeomorphisms (But not group-isomorphisms).
+\end{fact}
+\begin{remark}
+    This shows that a topological group has a certain homogeneity as a
+    topological space. For if $x,y\in G$, then $L_{yx^{-1}}$ maps $x$
+    to $y$ and is a homeomorphism. Therefore \textit{$G$ exhibits the
+    same topological structure locally near each point}.
+\end{remark}
+\begin{thm}
+    Let $G$ is a topological group, let $K$ be a connected component of $G$
+    which contains the identity element. Then $K$ is a closed normal
+    subgroup of $G$.
+\end{thm}
+\begin{fact}
+    If $G=\mathrm{O}(n)$, then $K=\mathrm{SO}(n)$.
+\end{fact}
+\begin{thm}
+    In a connected topological group, any neighbourhood of the
+    identity element is a set generates the whole group.
+\end{thm}
+The two theorems above is summarised as
+
+\begin{table}[H]
+    \centering
+    \caption{caption}
+    \begin{tabu}{l c l}
+        topology            & $\Rightarrow$ & group/topology \\
+        \hline
+        $e$ + connected     & $\Rightarrow$ & closed \& normal subgroup \\
+        $e$ + neighbourhood & $\Rightarrow$ & generator \\
+        \bottomrule
+    \end{tabu}
+\end{table}
+
+A bit more examples about matrices:
+\begin{ex}
+    \nomen{$\mathbb{M}(n)$} the $n\times n$ matrices, is not a
+    topological group. But its subspace
+    \nomen{$\mathrm{GL(n)}$}, specifically,
+    $\mathrm{GL(n,\mathbb{R})}$ or $\mathrm{GL(n,\mathbb{C})}$, is a
+    topological group. This is demonstrated in page 76, theorem 4.12.
+\end{ex}
+\begin{fact}
+    $\mathrm{GL(n)}$ is not compact. It has two idsjoint nonempty open
+    sets: those with positive and those with negative determinants.
+\end{fact}
+\begin{thm}
+    $\mathrm{O}(n)$ and $\mathrm{SO}(n)$ are closed and compact.
+    $\mathrm{SO}(n)$ is a sub-$\mathcal{TPG}$ of $\mathrm{O}(n)$.
+\end{thm}
+\begin{fact}
+    $\mathrm{SO}(2)\cong S^1$ and $\mathrm{SO}(3)\cong P^3$.
+\end{fact}
+\begin{remark}
+    These two facts established on page 77. The first one can be eaily
+    guess. Since a rotation is obviously determined by a rotation
+    degree on $S^1$. Mathematically we have
+    \begin{equation}
+        \left(\begin{array} {cc}
+            \cos\theta & -\sin\theta \\
+            \sin\theta & \cos\theta 
+        \end{array}\right) \cong e^{i\theta}
+    \end{equation}
+
+    The second one has a physical picture. The $P^3$ lies in
+    $\mathbb{H}$ (TBD). % TODO understand this. Related: Geometric algebra
+    % https://en.wikipedia.org/wiki/Geometric_algebra 
+\end{remark}
 

### 2016-11-19 Basic Topology Notes/Basic Topology.tex
Finished chapter 4.4, orbit space of Basic Topology.

@@
     $\mathrm{SO}(2)\cong S^1$ and $\mathrm{SO}(3)\cong P^3$.
+    Here $\cong$ means isomorphisms of topological groups.
 \end{fact}
@@
 
-    The second one has a physical picture. The $P^3$ lies in
-    $\mathbb{H}$ (TBD). % TODO understand this. Related: Geometric algebra
-    % https://en.wikipedia.org/wiki/Geometric_algebra 
+    The second one is proved mathematical in book \cite{book}. But it
+    has a physical argument. Remember we have the the homogeneous
+    coordinates for $P^3$, such as $[1,\theta_x,\theta_y,\theta_z]$.
+    As indicated in my labels, the three free coordinates $\theta_i$
+    can be regarded as rotation in 3-dimensional space. This rotation
+    preserves the orientation, so it is in $\mathrm{SO}$, not in
+    $\mathrm{O}$. 
 \end{remark}
 
+\subsection{Orbit Space}
+\label{sec:Orbit-Space}
+\begin{defi}[Group Action on Topology Space]
+\nomenclature{Group Action on Topology Space}{\nomrefpage.}
+    A topological group $G$ is said to act as a group of
+    homeomorphisms on a space $X$ if each group element (let $g,h\in G$)
+    induces a homeomorphism of the space in such a way that:
+    \begin{enumerate}
+        \item $(hg)(x) = h(g(x)),\, \forall x\in X$;
+        \item $e(x)=x,\, \forall x\in X$, where $e=gg^{-1}$;
+        \item the function $G\times X\to X$,$(g,x)\mapsto g(x)$ is
+            continusous.
+    \end{enumerate}
+\end{defi}
+
+The subset of $X$, consisting of $g(x)$ for all $g\in G$, is called an
+\nomen{orbit} of $x\in X$, written $O(x)$. Thought, it more convenient to
+write it just as \nomen{$Gx$}, as in textbooks of abstract algebra.
+
+\begin{fact}
+    A common fact in abstract algebra here is: each orbit $Gx$ is
+    disjoint. If two $Gx\cap Gy\neq \varnothing$, then $Gx=Gy$.
+\end{fact}
+
+By above fact, orbits partitions $X$, hence we can form the
+Identification space, with every elements in $X$ identified with their
+brothers in the same orbit. The result is \nomen{orbit space $X/G$}.
+
+\begin{ex}
+    \label{ex:R-over-Z-T}
+    $\mathbb{Z}$ acts on $\mathbb{R}$ by addition $x\mapsto x+n$,
+    $x\in \mathbb{R},\,n\in\mathbb{Z}$. It partitioned $\mathbb{R}$
+    into intervals, for each $x\in X$, $x\sim x+n,\forall n\in
+    \mathbb{Z}$. The orbit space $\mathbb{R}/\mathbb{Z}$ is
+    homeomorphic to $S^1$.
+\end{ex}
+
+An action $G$ on $X$ is called \nomen{transitive}, if and only if the
+orbit space $X/G$ is the trivial point $\{1\}$. Or equivalently, the
+only orbit is the whole space, i.e. $Gx=G,\,\forall x\in G$.
+
+\begin{ex}
+    The orthogonal action $O(n)$ on $S^{n-1}$ is transitive.
+    Physically, this is saying that $\forall x\in S^{n-1}$, it can be
+    rotated into $\forall y\in S^{n-1}$. A mathematical proof is on
+    page 79 of \cite{book}
+\end{ex}
+
+\paragraph{A lot of examples from book \cite{book}}$ $
+
+\begin{ex}
+    Extending example \ref{ex:R-over-Z-T}:
+\begin{equation}
+    \mathbb{E}^2/(\mathbb{Z}\times\mathbb{Z}) = T\text{ (torus)}
+\end{equation}
+    Here $=$ means homeomorphism.
+\end{ex}
+\begin{ex}
+    \begin{equation}
+        S^n/\mathbb{Z}_2 = P^n
+    \end{equation}
+    Here $=$ means homeomorphism.
+\end{ex}
+\begin{ex}[Three ways of $\mathbb{Z}_2$ acting on $T$]
+    The detailed procedure is to be found on page 91 of \cite{book}.
+    Here's a picture to visualize the action:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/3-ways-Z2-on-T.PNG}
+        \caption{$ $}
+    \end{figure}
+    The results are (a) a sphere; (b) a torus; (c) a Klein bottle.
+\end{ex}
+\begin{ex}
+    If $G$ is a topological group, and $H$ is
+    $\mathcal{TPG}$-subgroup. Then, the left cosets of right cosets
+    can be canonically seen as orbits. See more on page 81, example 4.
+\end{ex}
+\begin{ex}
+\begin{align}
+    \mathrm{O}(n)/\mathrm{O}(n-1) &= S^{n-1} \\
+    \mathrm{SO}(n)/\mathrm{SO}(n-1) &= S^{n-1}
+\end{align}
+    Here $=$ means homeomorphism. The first is established
+    mathematically in page 82 of \cite{book}. The second is mentioned
+    there, indicating a similar proof.
+
+    Here I give an argument. Consider a unit vector $y$ in $S^{n-1}$, if
+    we want to rotate another unit vector $e_1$ to $y$, since the
+    action is transitive, we can easily find a $A\in \mathrm{O}(n)$ to
+    do this. But in addition, we can also find that $A\cdot B$, where
+    $B\in \mathrm{O}(n-1)$ rotates the space around $e_1$ (thus
+    leaving $e_1$ un-affected) also do our job. So there is an
+    $\mathrm{O}(n-1)$ redundancy in $\mathrm{O}(n)\to S^{n-1}$.
+    Similar for the second relation.
+\end{ex}
+
+\begin{thm}
+    Let $G$ acts on $X$ and suppose that both $G$ and $X/G$ are
+    connected, then $X$ is connected.
+\end{thm}
+\begin{fact}
+    Using the theorem above, one can deduce that: $\mathrm{SO}(1)$ is
+    connected, $S^{n-1}$ is connected, so $\mathrm{SO}(n)$ is
+    connected.
+\end{fact}
+
+Next, the book \cite{book} (page 82 to 85) introduces several three
+spaces (\nomen{Lens space}, \nomen{irrational flow} on $T$ torus,
+\nomen{fundamental region} or in my word \textit{space filling
+shapes}) and two group \nomen{Euclidean group} (page 84) and
+\nomen{plane-crystallographic group} (page 85). To save time, I leave
+here only some pictures:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/irrational-flow.png}
+    \caption{Irrational Flow on $T$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/space-filling-shapes.png}
+    \caption{Space-filling Shapes}
+\end{figure}
 \section{Anchor}

### 2016-11-19 Algebra/Noetherian Ring.tex
Finding components in representation (Group theory in physics).
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

@@
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage[unicode]{hyperref} % For hyperlink everything.
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physicist-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physicist-taper}
 
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
+\makenomenclature % For an index of symbols.
 
-\usepackage[all]{xy} % For drawing category diagrams
-\usepackage{mathrsfs}
-\usepackage{nomencl} % For a index of symbols.
-\makenomenclature % For a index of symbols.
+% Show the keys for labels, replace options with "final" when done
+% with editing.
+\usepackage[draft,notref]{showkeys}
+
+% For the xymatrices I created before I learn to
+% use tikzcd for diagrams.
+\usepackage[all]{xy}
+
 \title{Noetherian Ring}
@@
     \nomenclature{$M$ Module}{A left module\nomrefpage.}
-Let $A$: ring. $M$ is a nomen left $A$-module if and only if 
+Let $A$: ring. $M$ is a left $A$-module if and only if 
 \begin{enumerate}
@@
 \end{enumerate}
+    This captures the notion of being \textit{linear}.
 \end{defi}
@@
             Let $R$ be the ring of all linear maps of $V$ into itself.
-            Then $V$ is also a module over $R$.
+            Then $V$ is also a module over $R$, since $R$ are just
+            linear maps.
     \end{enumerate}
+\end{ex}
+\begin{ex}
+    One can also pass the module structure $M$ from function whose
+    codomain is $M$. For example, when $M$ is an $A$-module and $S$ is
+    an nonempty set. The set of all maps $\mathrm{Map}(S,M)$ can be
+    made into an $A$-module. Let $a\in A$, $a$ acts on 
+    $f\in \mathrm{Map}(S,M)$ by $(af)(s) := a(f(s))$.
 \end{ex}

### 2016-11-19 Draft/sections/misc-other.tex
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

@@
 \label{sec:About-Matlab}
-\paragraph{On using $A/B$ or $A\\B$}
-Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
-, abbrevated $A/B$ and $A\\B$, are different and should be used with
-caution. One can check that:
+\paragraph{On using $A/B$ or $A\backslash B$}
+Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide} ,
+abbrevated $A/B$ and $A\backslash B$, are different and should be used
+with caution. One can check that:
 \begin{center}

### 2016-11-19 Latex packages/latex examples.tex
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

@@
 \end{table}
+\textbf{Tentative Schedule:}
+\begin{table}[H]
+	\centering
+	\caption{caption}
+	\label{tab:label}
+	%   \begin{tabu}{ *4c }
+	\begin{tabu}{ p{15 pt} X[l] X[l] X[r] }
+		$\#$ & & & Due date \\
+		\hline
+		\multicolumn{3}{p{\getTabuwidth}}{1. Summarise the review paper} & December, 2016 \\
+		\multicolumn{3}{p{\getTabuwidth}}{2. Learn related mathematical tools (homotopy thoery, group
+			cohomology, etc.)} & April, 2017 \\
+		\multicolumn3{p{\getTabuwidth}}{3. Play with toy models such
+			as the $1D$ quantum walk model} &
+		Faburary, 2017 \\
+		\multicolumn3{p{\getTabuwidth}}{4. Possible research topics:} & July, 2017 \\
+		4.1 &  \multicolumn2{p{\getTabuwidth}}{classifying topological materials in new symmetry
+			groups, such as the space groups;} & \multirow{4}{*}{ As above }\\
+		4.2 &  \multicolumn2{p{\getTabuwidth}}{finding new ways to classify in the non-interacting picture;} & \\
+		4.3 &  \multicolumn2{p{\getTabuwidth}}{experiment about the
+			effectiveness of existing;} & \\
+		4.4 &  \multicolumn2{p{\getTabuwidth}}{explorer approaches to the
+			classification in interacting.} & \\
+		\bottomrule
+	\end{tabu}
+\end{table}
 \section{Anchor}

### 2016-11-21 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/notes.tex
Initiate new note about the 1d non-Hermitian quantum walk.

--- 2016-07-27 Algebra/Noetherian Ring.tex
@@
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage[unicode]{hyperref} % For hyperlink everything.
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physicist-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physicist-taper}
 
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
+\makenomenclature % For an index of symbols.
 
-\usepackage[all]{xy} % For drawing category diagrams
-\usepackage{mathrsfs}
-\usepackage{nomencl} % For a index of symbols.
-\makenomenclature % For a index of symbols.
-\title{Noetherian Ring}
+% Show the keys for labels, replace options with "final" when done
+% with editing.
+\usepackage[draft,notref]{showkeys}
+
+\title{Notes of Topological Transition in a Non-Hermitian Quantum Walk}
 \date{\today}
-\author{we.taper}
+\author{Taper}
+
 \begin{document}
+
 \maketitle
 \abstract{
-    About Noetherian Ring.
+As suggested by the title.
 }
 \tableofcontents
+\section{General}
+\label{sec:General}
+This paper discusses in general a model charaterised by the follwoing
+picture
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/setup.PNG}
+    \caption{Setup}
+\end{figure}
+The equation of motion is
+\begin{align}
+    i\hbar \dot{\psi}^L_m = \varepsilon_L\psi^L_m + v\psi^R_m
+    +v'\psi^R_{m+1} \\
+    i\hbar \dot{\psi}^R_m = \tilde{\varepsilon}_R\psi^R_m + v\psi^L_m
+    +v'\psi^L_{m-1}
+\end{align}
+\section{Anchor}
+\label{sec:Anchor}
 
-\section{Module}
-\label{sec:Module}
-(\textbf{pp.117 to 118 of \cite{lang}})
-\begin{defi}[Module]
-    \nomenclature{$M$ Module}{A left module\nomrefpage.}
-Let $A$: ring. $M$ is a nomen left $A$-module if and only if 
-\begin{enumerate}
-    \item $M$ is an abelian group, usually written additively.
-    \item there exists an operation of $A$ on $M$, written as a
-        multiplicative monoid, such that, for any $a,b\in A$, any
-        $x,y \in M$, we have:
-        \begin{align}
-            (a+b) x = ax + bx\\
-            a(x+y) = ax + ay
-        \end{align}
-\end{enumerate}
-\end{defi}
-
-By definition of an operation, we have $1x = x$. Also, it can be easily
-derived that $a(-x) = -ax$, and $0x=0$.
-
-\begin{ex}{Examples of modules}
-    \begin{enumerate}
-        \item $A$ is a module over itself.
-        \item Any commutative group is a $\mathbb{Z}$-module.
-        \item Any left ideal of $A$ is a module over $A$, i.e. a left
-            $A$-module.
-        \item A vector space $V$ over $K$, is basically a $K$-module,
-            with the additional structure of $K$ being a field.
-        \item Let $V$ be a vector space. 
-            Let $R$ be the ring of all linear maps of $V$ into itself.
-            Then $V$ is also a module over $R$.
-    \end{enumerate}
-\end{ex}
-
-\begin{defi}[Submodule]
-\nomenclature{Submodule}{\nomrefpage.}
-    A submodule $M$ is an additive subgroup such that 
-    $AN\subset N$
-\end{defi}
-
-\begin{defi}[factor module]
-\nomenclature{factor module}{\nomrefpage.}
-    Let $M$ be an $A$-module, and $N$ a submodule. 
-    A factor module $M/N$ is the factor group $M/N$ (for the
-    additive group structure) equipped with a module structure.
-    The action of $A$ on $M/N$ is defined by $a(x+N) = ax+N$.
-    This is well defined, since if $y$ is in the same coset as
-    $x$, then $ay$ is in the same coset as $ax$.
-\end{defi}
-(\textbf{pp.119 of \cite{lang}})
-
-\section{Noetherian}
-\label{sec:Noetherian}
-\begin{defi}[Noetherian Module]
-    \nomenclature{Noetherian Module}{\nomrefpage.}
-    Let $A$: a ring. $M$: a left $A$-module. $M$ is called Noetherian
-    if $M$ satisfies any of the following conditions:
-    \begin{enumerate}
-        \item Every submodule of $M$ is finitely generated.
-        \item Every ascending sequences of submodules of $M$
-            \[ M_1 \subset M_2 \subset \cdots \]
-            such that $M_i \neq M_{i+1}$, is fininte.
-        \item Every non-empty set $S$ of submodules of $M$ has a maximal
-            element.
-    \end{enumerate}
-\end{defi}
-
-The equivalence of the above conditions are proved in page 413 to 414 of 
-\cite{lang}.
-
-\begin{defi}[Noetherian Ring]
-\nomenclature{Noetherian Ring}{\nomrefpage.}
-    A ring $A$ is Noetherian if and only if it is Noetherian when
-    viewed as a left module over itself.
-\end{defi}
-(\textbf{pp.415 of \cite{lang}})
-
-The structure of being Noetherian is consistent between a module
-and its submodules, factor modules, in the sense of the 
-following two propositions.
-
-\begin{prop}
-    Let $M$ be a Noetherian $A$-module, then every submodule and
-    every factor module of $M$ is Noetherian.
-\end{prop}
-(\textbf{pp.414 of \cite{lang}})
-
-\begin{prop}
-    Let $M$ be a module, $N$ be a submodule. If $N$ and $M/N$ are
-    Noetherian, then $M$ is Noetherian.
-\end{prop}
-(\textbf{pp.414 of \cite{lang}})
-
-The above statements could be summarized by saying that, given an
-exact sequence:
-\begin{align*}
-    \xymatrix{
-    0\ar[r] & M'\ar[r]^f & M\ar[r]^g & M''\ar[r] & 0
-    }
-\end{align*}
-$M$ is Noetherian if and only if $M'$ and $M''$ are Noetherian.
-This could be seen by two immediate fact of an exact sequence:
-\[
-    M'\cong \text{Im}f, \text{ } M/\text{Ker}g \cong M''
-\]
+\begin{thebibliography}{1}
+    \bibitem{1dwalk} Topological Transition in a Non-Hermitian Quantum
+    Walk,
+    \href{https://arxiv.org/ct?url=http%3A%2F%2Fdx.doi.org%2F10%252E1103%2FPhysRevLett%252E102%252E065703&v=f6968ad6}{arXiv}
+\end{thebibliography}
 \printnomenclature
-
-\section{Anchor}
-% This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-    \bibitem{lang} S. Lang. Algebra. 3rd. Springer.
-\end{thebibliography}
 \section{License}
@@
 license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-
 \end{document}

### 2016-11-22 Lecture note - Group Theory in Physics/sections/20161121.tex
A temporary note for new class - mainly about Wigner- Theorem. Also, some minor modification for my C.V.

Now we consider the classification of wavefunctions using the
symmetric groups we have known. In general, we need a symmetry, its
symmetry group, and the (irreducible) representation matrices.
During the classification, the representation space is the space
spanned by the set of degenerate wave functions $\psi_\rho$
($\rho=1,\cdots,m$), $\mathcal{L}_E=\operatorname{span}\{\psi_\rho\}$.

assuming we have
\begin{equation}
    H\psi_\rho(x) = E\psi_\rho(x)
\end{equation}

The $\psi_\rho$ satisfies orthogonal relations.
Now we do a spatial transformation, and assume this transformation
satisfy the symmetry of the Hamiltonian ($HP_R = P_R H$). Thn we have:
\begin{equation}
    P_R(\psi_\rho(x)) = \psi_\rho(R^{-1} x) = \sum_\lambda \psi_\lambda
    D_{\lambda\rho}(x)
\end{equation}
In this way, we obtain a representations of our symmetry. Usually,
$P_R$ is unitary, and since our basis $\psi_\rho$ is orthonormal, the
matrix $D$ is unitary. Now we want to find those irreducible
representations, so we do:
\begin{align}
    X^{-1} D(R) X = \oplus_j a_j D^j(R)
\end{align}
where $R\in G$, $D^j$ labels those irreducible representations, $X$ is
some matrix that we do not know now.

$a_j$ can be calculated using previous orthogonal relationships. More
specifically, we have
\begin{equation}
    a_j = \frac{1}{|G|} \sum_{R\in G} (\chi^j(R))^* \chi(R)
\end{equation}

Now we are interested in geting $X$. Notice that
\begin{align*}
    X^{-1} D(R) X = \oplus_j a_j D^j(R)
\end{align*}
tells us something about $X$. Let $X=X_{a,b}$. Here $1\leq a \leq m$.
$b$ can be labeled by $j,\mu,\gamma$, i.e. the irreducible
representation it is inside ($j$), did this irreducible representation
repeats more than one time ($\gamma$), which element is it ($\mu$). So
we have the new basis $\Psi$ related to the odd basis $\psi$ as
\begin{align}
    P_R(\Psi^j_{\mu\gamma}(x)) &= \sum_\nu
    \Psi^j_{\nu\gamma}(x)D^j_{\nu\mu}(R) \\
    \Psi^j_{\mu\gamma} &= \sum_{\rho} \psi_\rho X_{\rho,j\mu\gamma} \\
    \psi_\rho &= \sum_{j\mu\gamma} \psi^{j}_{\mu\gamma}
    (X^{-1})_{j\mu\gamma,\rho}
\end{align}

we have the theorem
\begin{thm}[W-E]
    \begin{itemize}
        \item Those belong to different irreducible representations
            are orthogonal
        \item Those belong to the same irreducible representation, but
            in different row are orthogonal
        \item Those belong to the same irreducible representation, the
            same row, has inner product independent of the index
    \end{itemize}
\end{thm}

Let $\psi^j_\mu$ and $\phi^k_\rho$ belong to $D^j_\mu$ and $D^k_\rho$.
Then 
$P_R \psi^j_\mu= \sum_\nu \psi^j_\nu D^j_{\nu\mu}(R)$,
$P_R \phi^k_\rho= \sum_\lambda \psi^k_\lambda D^j_{\lambda\nu}(R)$

Define $X^{jk}_{\rho\mu} := \braket{\phi^k_\rho|\psi^j_\mu}$.

\begin{align}
    \braket{\phi^k_\rho|P_R\psi^j_\mu} = \sum_\nu
    \braket{\phi^k_\rho|\psi^j_\nu} D^j_{\nu\mu}(R) = (X^{jk}
    D^j(R))_{\rho\mu} \\
    \braket{P^{-1}\phi^k_\rho|\psi^j_\mu} = \braket{
    \sum_\lambda\phi^k_\lambda D^k_{\lambda\rho}(R^{-})|\psi^j_\nu}
    \\
    = \sum_\lambda [D^k_{\lambda\rho}(R^{-1})]^*
    \braket{\phi^k_\lambda|\psi^j_\mu} 
    = \sum_\lambda D^k_{\rho\lambda}
    \braket{\phi^k_\lambda|\psi^j_\mu}
    = \sum_\lambda X^{kj}_{j\mu} = (D^k(R)X^{kj})_{\rho\mu}
\end{align}

Comparing two sides, we have
\begin{equation}
    D^k(R) X^{kj} = X^{kj}D^j(R)
\end{equation}
So by Schur lemma, we have when $k\neq j$
\begin{equation}
    X^{kj} = 0
\end{equation}
when $k=j$
\begin{equation}
    X^{jk} = \lambda\id
\end{equation}
the constant $\lambda$ is denoted as $\bra{k}\ket{j}$
so
\begin{equation}
    X^{jk} = \bra{k} \ket{j} \id
\end{equation}
In all
\begin{equation}
    \braket{\phi^k_\rho|\psi^j_\mu} = \delta_{jk} \delta_{\rho\mu}
    \bra{k} \ket{j}
\end{equation}

\subsection{Canonical Degeneracy}
\label{sec:Canonical-Degeneracy}
\begin{defi}[Canonical/Accidential Degeneracy]
\nomenclature{Canonical/Accidential Degeneracy}{\nomrefpage.}
    Assume $H$ has $M$-fold degeneracy, wit corresponding
    representations $D(G)$. If the representation is irreducible, then
    the degeneracy is called canonical, otherwise it is called
    accidential.
\end{defi}

Assume we have $[P_R,H_0]=0$, $[P_R,H_1]=0$. 
\begin{align}
    P_R \psi^j_\mu = \sum_\nu \psi^j_\nu D^j_{\nu\mu}(R)\\
    H_0 \psi^j_\mu = E^j \psi^j_\mu \\
    P_R H_1 \psi^j_\mu = H_1 P_R \psi^j_\mu = H_1 \sum_\nu \psi^j_\nu
    D^j_{\nu\mu}(R) = \sum_\nu (H_1\psi^j_\nu) D^j_{\nu\mu}(R) \\
\end{align}
By theorem
\begin{align}
    \braket{\psi^j_\nu|H_1 \psi^j_\nu} = \bra{j}\ket{j}\id = \Delta
    E^j \delta_{\nu\mu}
\end{align}
So the first order correction does not remove the degeneracy. For the
higher order correction, the case will be the same. Here only an
argument is given. We consider the process $H_0 + \lambda H_1$, from
$\lambda=0$ to $\lambda=1$, in this process, if $\lambda$ varies
adiabatically, then the degenerate function will keep their degeneracy
in the gradually process if the Hamiltonian is good enough.

For \textbf{accidental degeneracy}, for $j\neq i$
\begin{align}
    \braket{\psi^i_\nu|H_1 \psi^i_\mu} = \delta_{\nu\mu} \Delta E^i \\
    \braket{\psi^j_\nu|H_1 \psi^j_\mu} = \delta_{\nu\mu} \Delta E^j \\
\end{align}
In general, $\Delta E^i$ and $\Delta E^j$ is not the same. If they are
the same, then there may be additional symmetry that we have not yet
discovered.

For $j=i$, 
\begin{equation}
P_R \psi^j_{\nu a} = \sum_\nu \psi^j_{\nu a} D^j_{\nu\mu}(R)
\end{equation}
\begin{align}
    \braket{\psi^j_{\mu a} | H_1 |\psi^j_{\nu b}}  = 
\end{align}

Example

### 2016-11-22 Lecture note - Group Theory in Physics/sections/point-group.tex
Adding scanned notes about group "D_n" and "C_n" to group theory notes.
A temporary note for new class - mainly about Wigner- Theorem. Also, some minor modification for my C.V.

@@
 representations of $C_{nm}$. For example:
-% TODO pdf scan of C_6.
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{scans/get-C6-character.pdf}
+    \caption{Get $C_6$ Character table}
+\end{figure}
 \subsection{Dihedral Group \texorpdfstring{$D_n$}{}}
@@
 
-% TODO Add scanned notes.
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{scans/relate-edge-vortex.pdf}
+    \caption{relate-edge-Vortex}
+\end{figure}
 So all in all, $D_n$ can be generated by just two elements. They are:
@@
 character table.
-%TODO Add the scanned example.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{scans/get-D3-character.pdf}
+    \caption{Get $D_3$ Character table}
+\end{figure}
 
@@
 why I did not write $2n'+1$ but use $n$ in the above equations.
+
+\subsection{T-group}
+
+\nomen{$T$ group} is the group of the symmetry of tetrahedrons. It is
+a subgroup of $O$, the symmetry of cubic or octahedron (will % TODO ).
+
+A graph is provided in the page 33 of \cite{book}.  Part of this work
+has been done in the mid-term exam and is not repreated here.
+
+The conjugacy classes:
+$\{E\}$ and $\{3C_2\}$, $\{4C'_2\}$, $\{4C'^2_2\}$.
+
+\paragraph{Character Table}
+It has a subgroup of $D_2$, which can be seen from analysing the
+number of elments in conjugacy classes. $D_2$ is just $C_3$ discussed
+before, and it has three 1D representations. So first three line of
+the character is simple to get.
+
+The remaing representation is $3$-dimensional, so we can again fill
+one element of the character table. The rest can be easily filled by
+the orthogonal relations.
+
+Details on page 66 and 33 of \cite{book}.

### 2016-11-23 Basic Topology Notes/Basic Topology.tex
New basic topology notes. Chapter on fundamental groups and the no fix point theorem.

--- 2016-11-17 Basic Topology Notes/Basic Topology.tex
@@
 \label{sec:Special-Notes}
-\paragraph{About map} In book \cite{book}, a map is defined as a
-continuous function (page 32), which is confusing. In this note, I
-will not use this convention and will always states continuity
-clearly.
+\input{sections/Special-Notes}
 
-\paragraph{Basic facts about maps}
-Assuming domain $f=X$, codomain $f=Y$.
-\begin{align}
-    f(U\cup V) &= f(U)\cup f(V) \\
-    f(U\cap V) &\subseteq f(U)\cap f(V) \\
-    f(U^c) &\supseteq f(U)^c,\,\text{i.e. } f(U)^c \subseteq f(U^c) \\
-    f^{-1}(U\cup V) &= f^{-1}(U)\cup f^{-1}(V) \\
-    f^{-1}(U\cap V) &= f^{-1}(U)\cap f^{-1}(V) \\
-    f^{-1}(U^c) &= [f^{-1}(U)]^c
-\end{align}
-\paragraph{Smallest the Largest Topolgy}
-The set of all possible topolgies on $X$ is partially ordered by
-inclusion. For a certain characteristics $\mathcal{C}$, it is possible
-to have the smallest or the largest one.
+\section{A Brief Note of Chapter 4 - Identification Spaces}
+\label{sec:Brief-Note-Chapter-4}
+\input{sections/Brief-Note-of-Ch-4}
 
-The \nomen{smallest topolgy} $\mathcal{T}_\text{min}$ is the one such
-that, for any $\mathcal{T}'$ satisfying $\mathcal{C}$,
-$\mathcal{T}_\text{min}\subseteq \mathcal{T}'$. The \nomen{largest
-topolgy} $\mathcal{T}_\text{max}$ is the one such that, for any
-$\mathcal{T}'$ satisfying $\mathcal{C}$, $\mathcal{T}'\subseteq
-\mathcal{T}_\text{max}$.
-Synonyms of these two words are:
-\begin{itemize}
-    \item Larger: stronger, finer.
-    \item Smaller: weaker, coarser.
-\end{itemize}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.65\linewidth]{pics/comparing-topologies-and-coffee.jpg}
-    \caption{Comparing topologies and coffee (Credit:
-    \href{http://www.math3ma.com/the-back-pocket/2016/8/26/comparing-topologies}{math3ma})}
-\end{figure}
-For example, assuming we have
-\begin{equation}
-    f: X\to Y
-\end{equation}
-where $f$ is any function.
-
-If $X$ has topolgy $\mathcal{T}_X$, we ask then what kind of topolgy on
-$Y$ will make $f$ a continuous function. First, all $f^{-1}(V)$, with
-$V\in \mathcal{T}_Y$ should be open in $X$. So, the easiest choice is to
-make $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$, this is the
-smallest topolgy.  Also, any set $V\in Y$ such that $f^{-1}(V)\notin
-\mathcal{T}_X$ should not be in $\mathcal{T}_Y$. Then the largest
-topolgy is $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in
-\mathcal{T}_X\}$.
-
-If $Y$ has topolgy $\mathcal{T}_Y$, we also ask what kind of topolgy
-on $X$ will make $f$ a continuous function. First, all $V\in
-\mathcal{T}_Y$, their preimage $f^{-1}(V)$ must be in $\mathcal{T}_X$.
-So the smallest topolgy is
-$\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$. Than
-what about the largest topolgy? We consider, what kind of sets cannot
-be inside $\mathcal{T}_X$. First, can $(f^{-1}(V))^c=f^{-1}(V^c)$ be
-in $\mathcal{T}_X$? Yes. Since unless the space is connected, there
-can be sets being both open and closed (other than $X$ and
-$\varnothing$). Any other restrictions? No that I can think of. So,
-the largest topolgy $\mathcal{T}_{X,\text{max}}=2^X$, the set of all
-subsets of $X$. (The notation \nomen{$2^X$} is taken from the page 4
-of book \cite{Singer.Thorpe}.
-
-A summary:
-\begin{table}[H]
-    \centering
-    \caption{Largest and Smallest Topolgies}
-    \begin{tabular}{c l l}
-        $X\overset{f}{\to}Y$ & Smallest  &Largest \\
-        \hline
-        Given $\mathcal{T}_X$ & $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$        & $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in \mathcal{T}_X\}$\\
-        Given $\mathcal{T}_Y$ & $\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$ & $\mathcal{T}_{X,\text{max}}=2^X$ \\
-        No constraint & $\{\varnothing,X\}$ & $2^X$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\paragraph{Facts about subspace/induced topolgy}
-Let $Y$ be a subspace of a topological space $X$ wit induced topolgy.
-\begin{fact}
-    A set $H\subseteq Y$ is open in $Y$ if and only if $H=F\cap Y$
-    for some open set $F$ in $X$.
-\end{fact}
-\begin{fact}
-    A set $H\subseteq Y$ is closed in $Y$ if and only if $H=F\cap Y$
-    for some closed set $F$ in $X$.
-\end{fact}
-\begin{fact}
-    A set $H$ is open/closed in $X$ $\Rightarrow$ $H$ is open/closed
-    in $Y$. But the converse may not be true. The converse statement
-    depends on whether $Y$ is open or closed in $X$.
-\end{fact}
-\section{Collection of Theorems in Chapter 4}
-\label{sec:Collection-of-Theorems-in-Chapter-4}
-\begin{defi}[Identification Topology]
-\nomenclature{Identification Topology}{\nomrefpage.}
-Let $X$ be a topological space and let $\mathscr{P}$ be a family of
-disjoint nonempty subsets of $X$ such that $\cup \mathscr{P}=X$. Such
-a family is usually called a partition of $X$. Let $Y$ be a new space
-whose points are the members of $\mathscr{P}$. Let $\pi:X\to Y$ sends
-each point of $X$ to the subset of $\mathscr{P}$. Define a topolgy
-$\mathcal{T}_Y$ on $Y$ to be the largest topolgy such that the $\pi$
-is continuous. This $\mathcal{T}_Y$ is called the idetification topolgy.
-And $Y$ is called the \nomen{identification space}.
-\end{defi}
-\begin{center} \begin{tikzcd}[]
-    X\ar[r]\ar[rd] & Y\ar[d,equal] \\
-    & \mathscr{P}
-\end{tikzcd} \end{center}
-\begin{thm}
-    Let $Y$ be an idetification space defined as above and let $Z$ be
-    an arbitrary topological space. A function $f:Y\to Z$ is
-    continuous if and ony if the composition $f\circ \pi:X\to Z$ is
-    continuous.
-\end{thm}
-\begin{center} \begin{tikzcd}[]
-    X\ar[r,"\pi"]\ar[rd]\ar[rr,"f\circ\pi",bend left=30] & Y\ar[d,equal]\ar[r,"f"] & Z \\
-    & \mathscr{P}
-\end{tikzcd} \end{center}
-\begin{defi}[Identification Map]
-\nomenclature{Identification Map}{\nomrefpage.}
-    Let $f:X\to Y$ be an onto continuous map and suppose that the topolgy on $Y$
-    is the largest for which $f$ is continuous. Then we call $f$ an
-    identification map.
-\end{defi}
-The naming "identification map" is because:
-\begin{thm}
-    Any function $f:X\to Y$ gives rise to a partition of $X$ whose
-    members are the subsets $\{f^{-1}(y)\}$, where $y\in Y$. Let $Y_*$
-    denote the identification space associated with this partition,
-    and $\pi:X\to Y_*$ the usual continuous map. 
-    $$ \begin{tikzcd}[]
-        X\ar[r,"f"]\ar[d,"\pi"] & Y \\
-        \{f^{-1}(y)\} \ar[r,equal] & Y_*
-    \end{tikzcd} $$
-    If $f$ is an identification map, then:
-    \begin{enumerate}
-        \item the spaces $Y$ and $Y_*$ are homeomorphic;
-        \item a function $g:Y\to Z$ is continuous if and only if the
-            composition $g\circ f:X\to Z$ is continuous.
-    \end{enumerate}
-    $$ \begin{tikzcd}[]
-        X\ar[r,"f"]\ar[d,"\pi"]\ar[rr,"g\circ f",bend left] 
-            & Y\ar[d,equal,"~"]\ar[r,"g"] & Z \\
-        \{f^{-1}(y)\} \ar[r,equal] & Y_*
-    \end{tikzcd} $$
-\end{thm}
-\begin{thm}
-    Let $f:X\to Y$ be an onto continuous map. If $f$ maps open sets of
-    $X$ to open sets of $Y$, or closed sets to closed sets, then $f$
-    is an identification map, i.e. $\mathcal{T}_y$ is the largest
-    topolgy such that $f$ is continuous.
-\end{thm}
-\begin{coro}
-    \label{coro:idmap-coro}
-    Let $f:X\to Y$ be an onto continuous map. If $X$ is compact and
-    $Y$ is Hausdorff, then $f$ is an identification map.
-\end{coro}
-
-\begin{defi}[Torus]
-\nomenclature{Torus}{\nomrefpage.}
-Torus is the uTorusquare $[0,1]\times[0,1]$, with 1. opposite edge
-identified, 2. four edge points identified.
-\end{defi}
-\begin{remark}
-    The identification map and corollary \ref{coro:idmap-coro} can be
-    used to show that torus is homeomorphic to two copies of
-    circles:$S^1\times S^1$. This is mentioned in page 68 of
-    \cite{book}.
-\end{remark}
-\begin{defi}[Cone $CX$]
-\nomenclature{Cone $CX$}{\nomrefpage.}
-    The cone of any space $CX$ is formed from $X\times I$, where $I$ is
-    the unit interval $[0,1]$, with certain identification. The
-    identification shrinks all points in one surface into one point.
-    This is discussed in page 68 of \cite{book}.
-\end{defi}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.5\linewidth]{pics/{Cone-of-a-circle}.pdf}
-    \caption{Cone of a Circle (Wikipedia)}
-\end{figure}
-\begin{remark}
-    There is another definition of cone $CX$ when $X$ in imbeded into
-    $\mathbb{E}^n$, may be found on page 68 of \cite{book}. Cone
-    constructed in this way is called a geometric cone. It is made up
-    of all straight line segments that join $v=(0,0,\cdots,1)\in
-    \mathbb{E}^{n+1}$ to some point of $X$.
-\end{remark}
-\begin{lemma}
-    The geometric cone on $X$ is homeomorphic to $CX$.
-\end{lemma}
-\begin{defi}[Quotient Space]
-\nomenclature{Quotient Space}{\nomrefpage.}
-    Let $X$ be a topological space, $A$ be its subspace. Then $X/A$
-    menas the $X$ with subspace $A$ identified to a point.
-    \begin{enumerate}
-        \item the set $A$.
-        \item the individual points of $X\setminus A$.
-    \end{enumerate}
-\end{defi}
-\begin{remark}
-    In this notation, $CX$ becomes $(X\times I)/(X\times\{1\})$.
-\end{remark}
-\begin{fact}
-    \begin{equation}
-        B^n/S^{n-1} \cong S^n
-    \end{equation}
-    where $\cong$ menas homeomorphic. This is proved on page 69.
-    Intuitively, this is like wrap a lower dimension ball surround the
-    higher dimension ball.
-\end{fact}
-
-\begin{defi}[$f\cup g$]
-\nomenclature{$f\cup g$}{\nomrefpage.}
-    Let $X,Y$ $f\cup g$ subsets of a topological space and give each of
-    $X,Y$, and$X\cup Y$ the induced topolgy. If $f:X\to Z$ and
-    $g:Y\to Z$ are functions which agree on the intersection of $X$
-    and $Y$, we can define
-    \begin{align}
-        f\cup g &: X\cup Y \to Z  \\
-        (f\cup g)(x) &= f(x),\, x\in X \nonumber \\
-        (f\cup g)(x) &= g(x),\, x\in Y \nonumber
-    \end{align}
-    We say that $f\cup g$ are formed by 'glueing together' the
-    functions $f$ and $g$.
-\end{defi}
-\begin{lemma}[Glueing lemma (closed)]
-    If $X$ and $Y$ are closed in $X\cup Y$, and if both $f$ and $g$
-    are continuous, then $f\cup g$ are continuous.
-\end{lemma}
-Similarly, 
-\begin{lemma}[Glueing lemma (open)]
-    If $X$ and $Y$ are open in $X\cup Y$, and if both $f$ and $g$
-    are continuous, then $f\cup g$ are continuous.
-\end{lemma}
-
-These two lemmas are seen as a special case of the following theorem,
-explained in page 70.
-
-Define \nomen{$X+Y$} to be the disjoint union of spaces $X,Y$. Define
-$j:X+Y \to X\cup Y$ which restrict to either $X$ or $Y$ is just the
-inclusion in $X\cup Y$.
-\begin{thm}
-    If $j$ is an identification map, and if both $f:X\to Z$ and
-    $g:X\to Z$ are continuous, then $f\cup g:X\cup Y\to Z$ is
-    continuous.
-\end{thm}
-$$ \begin{tikzcd}[]
-    X+Y \ar[r,"j"] & X\cup Y\ar[r,"f\cup g"] & Z \\
-    X\ar[rru,"f"] & Y\ar[ru,"g",bend right]
-\end{tikzcd}$$
-
-This can be generalized as follows. Let $X_\alpha,\alpha\in A$ be a
-family of subsets of a topological space and give each $X_\alpha$ and
-the union $\cup X_\alpha$, the induced topolgy. Let $Z$ be a space and
-suppose we are given maps $f_\alpha:X_\alpha\to Z$, one for each
-$\alpha$ in $A$, such that if $\alpha,\beta\in A$,
-$$ 
-\eval{f_\alpha}_{X_\alpha\cap X_\beta} = \eval{f_\beta}_{X_\alpha\cap X_\beta}
-$$
-Define function $F:\cup X_\alpha\to Z$ by glueing together $f_\alpha$.
-Let $\oplus X_\alpha$ be the disjoint unin of spaces $X_\alpha$. Let
-$j:\oplus X_\alpha \to \cup X_\alpha$ be similarly defined.
-\begin{thm}
-    If $j$ is an identification map, and if each $f_\alpha$
-    is continuous, then $F$ is continuous.
-\end{thm}
-\textbf{Note}: When $j$ is the identification map, then $\cup
-X_\alpha$ has the identification topolgy instead of the subspace
-topology. The two will be quite different, as discussed on page 70 to
-71 of \cite{book}.
-
-\begin{defi}[Projective space $P^n$]
-\nomenclature{Projective space}{\nomrefpage.}
-    A discussion of real $P^n$ may be found on page 71.
-\end{defi}
-
-\paragraph{\nomen{Attaching maps} and $X\cup_f Y$} Let:
-\begin{equation}
-    Y \supseteq A \overset{f}{\to} X
-\end{equation}
-where $X,Y$ are topological spaces, $f$ is continuous. We identify the
-disjoint union $X+Y$ using $f$, partitioning them into:
-\begin{enumerate}
-    \item pairs of points $\{a,f(a)\}$ where $a\in A$;
-    \item individual points of $Y\setminus A$;
-    \item individual points of $X\setminus \Im(f)$.
-\end{enumerate}
-The result identification space is denoted $X\cup_f Y$, and $f$ is
-called the attaching map. This process can also be viewed as:
-\begin{equation}
-    X\cup_f Y = (X\amalg Y)/\{f(A)~A\}
-\end{equation}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.6\linewidth]{pics/Attaching-Space.jpg}
-    \caption{Attaching Space (credit:
-        \href{https://ncatlab.org/nlab/show/Top}{nLab}}
-\end{figure}
-\begin{ex}
-    $P^2$ can be seen as attaching a closed disc $D$ to the boundary
-    of $M$, a Mobius strip, as discussed in page 72 of \cite{book}.
-    Geometrically, this simply shrinks the boundary of $M$ into a
-    point. And an ant travelling around this point can point out the
-    direction just as in $P^2$.
-\end{ex}
+\section{Chapter 5 - Fundamental Groups}
+\label{sec:Chapter-5-Fundamental-Groups}
+\input{sections/ch5-fundamental-groups.tex}
 

### 2016-11-23 Basic Topology Notes/sections/Brief-Note-of-Ch-4.tex
New basic topology notes. Chapter on fundamental groups and the no fix point theorem.

\subsection{Identification topology}
\label{sec:Identification topology}

\begin{defi}[Identification Topology]
\nomenclature{Identification Topology}{\nomrefpage.}
Let $X$ be a topological space and let $\mathscr{P}$ be a family of
disjoint nonempty subsets of $X$ such that $\cup \mathscr{P}=X$. Such
a family is usually called a partition of $X$. Let $Y$ be a new space
whose points are the members of $\mathscr{P}$. Let $\pi:X\to Y$ sends
each point of $X$ to the subset of $\mathscr{P}$. Define a topolgy
$\mathcal{T}_Y$ on $Y$ to be the largest topolgy such that the $\pi$
is continuous. This $\mathcal{T}_Y$ is called the idetification topolgy.
And $Y$ is called the \nomen{identification space}.
\end{defi}
\begin{center} \begin{tikzcd}[]
    X\ar[r]\ar[rd] & Y\ar[d,equal] \\
    & \mathscr{P}
\end{tikzcd} \end{center}
\begin{thm}
    Let $Y$ be an idetification space defined as above and let $Z$ be
    an arbitrary topological space. A function $f:Y\to Z$ is
    continuous if and ony if the composition $f\circ \pi:X\to Z$ is
    continuous.
\end{thm}
\begin{center} \begin{tikzcd}[]
    X\ar[r,"\pi"]\ar[rd]\ar[rr,"f\circ\pi",bend left=30] & Y\ar[d,equal]\ar[r,"f"] & Z \\
    & \mathscr{P}
\end{tikzcd} \end{center}
\begin{defi}[Identification Map]
\nomenclature{Identification Map}{\nomrefpage.}
    Let $f:X\to Y$ be an onto continuous map and suppose that the topolgy on $Y$
    is the largest for which $f$ is continuous. Then we call $f$ an
    identification map.
\end{defi}
The naming "identification map" is because:
\begin{thm}
    Any function $f:X\to Y$ gives rise to a partition of $X$ whose
    members are the subsets $\{f^{-1}(y)\}$, where $y\in Y$. Let $Y_*$
    denote the identification space associated with this partition,
    and $\pi:X\to Y_*$ the usual continuous map. 
    $$ \begin{tikzcd}[]
        X\ar[r,"f"]\ar[d,"\pi"] & Y \\
        \{f^{-1}(y)\} \ar[r,equal] & Y_*
    \end{tikzcd} $$
    If $f$ is an identification map, then:
    \begin{enumerate}
        \item the spaces $Y$ and $Y_*$ are homeomorphic;
        \item a function $g:Y\to Z$ is continuous if and only if the
            composition $g\circ f:X\to Z$ is continuous.
    \end{enumerate}
    $$ \begin{tikzcd}[]
        X\ar[r,"f"]\ar[d,"\pi"]\ar[rr,"g\circ f",bend left] 
            & Y\ar[d,equal,"~"]\ar[r,"g"] & Z \\
        \{f^{-1}(y)\} \ar[r,equal] & Y_*
    \end{tikzcd} $$
\end{thm}
\begin{thm}
    Let $f:X\to Y$ be an onto continuous map. If $f$ maps open sets of
    $X$ to open sets of $Y$, or closed sets to closed sets, then $f$
    is an identification map, i.e. $\mathcal{T}_y$ is the largest
    topolgy such that $f$ is continuous.
\end{thm}
\begin{coro}
    \label{coro:idmap-coro}
    Let $f:X\to Y$ be an onto continuous map. If $X$ is compact and
    $Y$ is Hausdorff, then $f$ is an identification map.
\end{coro}

\begin{defi}[Torus]
\nomenclature{Torus}{\nomrefpage.}
Torus is the unit square $[0,1]\times[0,1]$, with 1. opposite edge
identified; 2. four edge points identified.
\end{defi}
\begin{remark}
    The identification map and corollary \ref{coro:idmap-coro} can be
    used to show that torus is homeomorphic to two copies of
    circles:$S^1\times S^1$. This is mentioned in page 68 of
    \cite{book}.
\end{remark}
\begin{defi}[Cone $\textrm{CX}$]
\nomenclature{Cone $\textrm{CX}$}{\nomrefpage.}
    The cone of any space $\textrm{CX}$ is formed from $X\times I$, where
    $I$ is the unit interval $[0,1]$, with certain identification. The
    identification shrinks all points in one surface into one point.  This
    is discussed in page 68 of \cite{book}.
\end{defi}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{pics/{Cone-of-a-circle}.pdf}
    \caption{Cone of a Circle (Wikipedia)}
\end{figure}
\begin{remark}
    There is another definition of cone $\textrm{CX}$ when $X$ in imbeded into
    $\mathbb{E}^n$, may be found on page 68 of \cite{book}. Cone
    constructed in this way is called a geometric cone. It is made up
    of all straight line segments that join $v=(0,0,\cdots,1)\in
    \mathbb{E}^{n+1}$ to some point of $X$.
\end{remark}
\begin{lemma}
    The geometric cone on $X$ is homeomorphic to $\textrm{CX}$.
\end{lemma}
\begin{defi}[Quotient Space]
\nomenclature{Quotient Space}{\nomrefpage.}
    Let $X$ be a topological space, $A$ be its subspace. Then $X/A$
    menas the $X$ with subspace $A$ identified to a point.
    \begin{enumerate}
        \item the set $A$.
        \item the individual points of $X\setminus A$.
    \end{enumerate}
\end{defi}
\begin{remark}
    In this notation, $\textrm{CX}$ becomes $(X\times I)/(X\times\{1\})$.
\end{remark}
\begin{fact}
    \begin{equation}
        B^n/S^{n-1} \cong S^n
    \end{equation}
    where $\cong$ menas homeomorphic. This is proved on page 69.
    Intuitively, this is like wrap a lower dimension ball surround the
    higher dimension ball.
\end{fact}

\begin{defi}[$f\cup g$]
\nomenclature{$f\cup g$}{\nomrefpage.}
    Let $X,Y$ $f\cup g$ subsets of a topological space and give each of
    $X,Y$, and$X\cup Y$ the induced topolgy. If $f:X\to Z$ and
    $g:Y\to Z$ are functions which agree on the intersection of $X$
    and $Y$, we can define
    \begin{align}
        f\cup g &: X\cup Y \to Z  \\
        (f\cup g)(x) &= f(x),\, x\in X \nonumber \\
        (f\cup g)(x) &= g(x),\, x\in Y \nonumber
    \end{align}
    We say that $f\cup g$ are formed by 'glueing together' the
    functions $f$ and $g$.
\end{defi}
\begin{lemma}[Glueing lemma (closed)]
    If $X$ and $Y$ are closed in $X\cup Y$, and if both $f$ and $g$
    are continuous, then $f\cup g$ are continuous.
\end{lemma}
Similarly, 
\begin{lemma}[Glueing lemma (open)]
    If $X$ and $Y$ are open in $X\cup Y$, and if both $f$ and $g$
    are continuous, then $f\cup g$ are continuous.
\end{lemma}

These two lemmas are seen as a special case of the following theorem,
explained in page 70.

Define \nomen{$X+Y$} to be the disjoint union of spaces $X,Y$. Define
$j:X+Y \to X\cup Y$ which restrict to either $X$ or $Y$ is just the
inclusion in $X\cup Y$.
\begin{thm}
    If $j$ is an identification map, and if both $f:X\to Z$ and
    $g:X\to Z$ are continuous, then $f\cup g:X\cup Y\to Z$ is
    continuous.
\end{thm}
$$ \begin{tikzcd}[]
    X+Y \ar[r,"j"] & X\cup Y\ar[r,"f\cup g"] & Z \\
    X\ar[rru,"f"] & Y\ar[ru,"g",bend right]
\end{tikzcd}$$

This can be generalized as follows. Let $X_\alpha,\alpha\in A$ be a
family of subsets of a topological space and give each $X_\alpha$ and
the union $\cup X_\alpha$, the induced topolgy. Let $Z$ be a space and
suppose we are given maps $f_\alpha:X_\alpha\to Z$, one for each
$\alpha$ in $A$, such that if $\alpha,\beta\in A$,
$$ 
\eval{f_\alpha}_{X_\alpha\cap X_\beta} = \eval{f_\beta}_{X_\alpha\cap X_\beta}
$$
Define function $F:\cup X_\alpha\to Z$ by glueing together $f_\alpha$.
Let $\oplus X_\alpha$ be the disjoint unin of spaces $X_\alpha$. Let
$j:\oplus X_\alpha \to \cup X_\alpha$ be similarly defined.
\begin{thm}
    If $j$ is an identification map, and if each $f_\alpha$
    is continuous, then $F$ is continuous.
\end{thm}
\textbf{Note}: When $j$ is the identification map, then $\cup
X_\alpha$ has the identification topolgy instead of the subspace
topology. The two will be quite different, as discussed on page 70 to
71 of \cite{book}.

\begin{defi}[Projective space $P^n$]
\nomenclature{Projective space}{\nomrefpage.}
    A discussion of real $P^n$ may be found on page 71.
\end{defi}

\paragraph{\nomen{Attaching maps} and $X\cup_f Y$} Let:
\begin{equation}
    Y \supseteq A \overset{f}{\to} X
\end{equation}
where $X,Y$ are topological spaces, $f$ is continuous. We identify the
disjoint union $X+Y$ using $f$, partitioning them into:
\begin{enumerate}
    \item pairs of points $\{a,f(a)\}$ where $a\in A$;
    \item individual points of $Y\setminus A$;
    \item individual points of $X\setminus \Im(f)$.
\end{enumerate}
The result identification space is denoted $X\cup_f Y$, and $f$ is
called the attaching map. This process can also be viewed as:
\begin{equation}
    X\cup_f Y = (X\amalg Y)/\{f(A)\sim A\}
\end{equation}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/Attaching-Space.jpg}
    \caption{Attaching Space (credit:
        \href{https://ncatlab.org/nlab/show/Top}{nLab}}
\end{figure}
\begin{ex}
    $P^2$ can be seen as attaching a closed disc $D$ to the boundary
    of $M$, a Mobius strip, as discussed in page 72 of \cite{book}.
    Geometrically, this simply shrinks the boundary of $M$ into a
    point. And an ant travelling around this point can point out the
    direction just as in $P^2$.
\end{ex}
\begin{remark}
    It is remarked that properties such as compactness, connectedness,
    and path-connectedness is inherited in identification. However,
    Hausdorff-ness is not. An counter example can be found in page 72 of
    \cite{book}.
\end{remark}

\subsection{Topological Groups}
\label{sec:Topological-Groups}

In simple words, \nomen{topological groups} are objects that has both
a topolgy on it and a group structure in it. And the two structures
must be compatible. Specifically, the multiplication map $a\cdot b$
and the inverse map $a\to a^{-1}$ are continuous. Homomorphisms
between are both group-homomorphisms and topological-homomorphisms
(continuous maps). Isomorphisms are both group-isomorphisms and
topolgy-isomorphisms (homeomorphisms). A sub-(topological group) is
both a subgroup and has subspace topolgy. For convenience of language,
use \nomen{$\mathcal{TPG}$} denotes the category of topological groups.
\footnote{This notation is nowhere popular or accepted. I use it to
only to save space and time.}
\begin{ex}
    The $\mathbb{R}$ is a topological group. 
    The $\mathbb{Z}$ with discrete topology form the sub-(topological
    group) of $\mathbb{R}$. The quotient $\mathbb{R}/\mathbb{Z}$ forms
    a topological group. The map $f: \mathbb{R}\to S^1$ induces a
    homeomorphism $\mathbb{R}/\mathbb{Z} \cong S^1$, which is also a
    group isomorphisms, i.e. it is a $\mathcal{TPG}$-isomorphism.
\end{ex}
\begin{ex}
    Similarly, $R^n$.
\end{ex}

\begin{ex}
    The circle is also one. The group structure is combination of
    degrees.
\end{ex}
\begin{ex}
    Any group with discrete topology.
\end{ex}
\begin{ex}
    The torus considered as the product of two circles. (Take the
    producttopology and the product group structure.
\end{ex}
\begin{ex}
    Three sphere $S^3$ considered as the unit sphere in the space of
    quaterions $\mathbb{H}$.

    Remember this? :
    $$ \begin{tikzcd}[column sep=small]
        & i\ar[dr] &  \, \\
    k \ar[ur] &
    \ar[u,phantom, "\#"] 
    & j\ar[ll]
    \end{tikzcd} $$
    The unit sphere are unit quaterions, see more
    \href{https://en.wikipedia.org/wiki/Versor}{Versor}.
\end{ex}
\begin{ex}
    The \nomen{orthogonal group} $\mathrm{O}(n)$, of $n\times n$
    orthogonal real matrices. It is easy to check that
    $\mathrm{O}(n-1)$ is a sub-$\mathcal{TPG}$ of $\mathrm{O}(n)$.
\end{ex}

\begin{defi}[Left translation $L_x$]
\nomenclature{Left translation $L_x$}{\nomrefpage.}
    For $x\in G$, the function
    \begin{align}
        L_x: G &\to G \\
          g &\mapsto xg
    \end{align}
    is called a left translation by $x$. Similarly we have
    \nomen{right translation $R_x$}.
\end{defi}
\begin{fact}
    $L_x$ and $R_x$ are homeomorphisms (But not group-isomorphisms).
\end{fact}
\begin{remark}
    This shows that a topological group has a certain homogeneity as a
    topological space. For if $x,y\in G$, then $L_{yx^{-1}}$ maps $x$
    to $y$ and is a homeomorphism. Therefore \textit{$G$ exhibits the
    same topological structure locally near each point}.
\end{remark}
\begin{thm}
    Let $G$ is a topological group, let $K$ be a connected component of $G$
    which contains the identity element. Then $K$ is a closed normal
    subgroup of $G$.
\end{thm}
\begin{fact}
    If $G=\mathrm{O}(n)$, then $K=\mathrm{SO}(n)$.
\end{fact}
\begin{thm}
    In a connected topological group, any neighbourhood of the
    identity element is a set generates the whole group.
\end{thm}
The two theorems above is summarised as

\begin{table}[H]
    \centering
    \caption{caption}
    \begin{tabu}{l c l}
        topology            & $\Rightarrow$ & group/topology \\
        \hline
        $e$ + connected     & $\Rightarrow$ & closed \& normal subgroup \\
        $e$ + neighbourhood & $\Rightarrow$ & generator \\
        \bottomrule
    \end{tabu}
\end{table}

A bit more examples about matrices:
\begin{ex}
    \nomen{$\mathbb{M}(n)$} the $n\times n$ matrices, is not a
    topological group. But its subspace
    \nomen{$\mathrm{GL(n)}$}, specifically,
    $\mathrm{GL(n,\mathbb{R})}$ or $\mathrm{GL(n,\mathbb{C})}$, is a
    topological group. This is demonstrated in page 76, theorem 4.12.
\end{ex}
\begin{fact}
    $\mathrm{GL(n)}$ is not compact. It has two idsjoint nonempty open
    sets: those with positive and those with negative determinants.
\end{fact}
\begin{thm}
    $\mathrm{O}(n)$ and $\mathrm{SO}(n)$ are closed and compact.
    $\mathrm{SO}(n)$ is a sub-$\mathcal{TPG}$ of $\mathrm{O}(n)$.
\end{thm}
\begin{fact}
    $\mathrm{SO}(2)\cong S^1$ and $\mathrm{SO}(3)\cong P^3$.
    Here $\cong$ means isomorphisms of topological groups.
\end{fact}
\begin{remark}
    These two facts established on page 77. The first one can be eaily
    guess. Since a rotation is obviously determined by a rotation
    degree on $S^1$. Mathematically we have
    \begin{equation}
        \left(\begin{array} {cc}
            \cos\theta & -\sin\theta \\
            \sin\theta & \cos\theta 
        \end{array}\right) \cong e^{i\theta}
    \end{equation}

    The second one is proved mathematical in book \cite{book}. But it
    has a physical argument. Remember we have the the homogeneous
    coordinates for $P^3$, such as $[1,\theta_x,\theta_y,\theta_z]$.
    As indicated in my labels, the three free coordinates $\theta_i$
    can be regarded as rotation in 3-dimensional space. This rotation
    preserves the orientation, so it is in $\mathrm{SO}$, not in
    $\mathrm{O}$. 
\end{remark}

\subsection{Orbit Space}
\label{sec:Orbit-Space}
\begin{defi}[Group Action on Topology Space]
\nomenclature{Group Action on Topology Space}{\nomrefpage.}
    A topological group $G$ is said to act as a group of
    homeomorphisms on a space $X$ if each group element (let $g,h\in G$)
    induces a homeomorphism of the space in such a way that:
    \begin{enumerate}
        \item $(hg)(x) = h(g(x)),\, \forall x\in X$;
        \item $e(x)=x,\, \forall x\in X$, where $e=gg^{-1}$;
        \item the function $G\times X\to X$,$(g,x)\mapsto g(x)$ is
            continuous.
    \end{enumerate}
\end{defi}

The subset of $X$, consisting of $g(x)$ for all $g\in G$, is called an
\nomen{orbit} of $x\in X$, written $O(x)$. Thought, it more convenient to
write it just as \nomen{$Gx$}, as in textbooks of abstract algebra.

\begin{fact}
    A common fact in abstract algebra here is: each orbit $Gx$ is
    disjoint. If two $Gx\cap Gy\neq \varnothing$, then $Gx=Gy$.
\end{fact}

By above fact, orbits partitions $X$, hence we can form the
Identification space, with every elements in $X$ identified with their
brothers in the same orbit. The result is \nomen{orbit space $X/G$}.

\begin{ex}
    \label{ex:R-over-Z-T}
    $\mathbb{Z}$ acts on $\mathbb{R}$ by addition $x\mapsto x+n$,
    $x\in \mathbb{R},\,n\in\mathbb{Z}$. It partitioned $\mathbb{R}$
    into intervals, for each $x\in X$, $x\sim x+n,\forall n\in
    \mathbb{Z}$. The orbit space $\mathbb{R}/\mathbb{Z}$ is
    homeomorphic to $S^1$.
\end{ex}

An action $G$ on $X$ is called \nomen{transitive}, if and only if the
orbit space $X/G$ is the trivial point $\{1\}$. Or equivalently, the
only orbit is the whole space, i.e. $Gx=G,\,\forall x\in G$.

\begin{ex}
    The orthogonal action $O(n)$ on $S^{n-1}$ is transitive.
    Physically, this is saying that $\forall x\in S^{n-1}$, it can be
    rotated into $\forall y\in S^{n-1}$. A mathematical proof is on
    page 79 of \cite{book}
\end{ex}

\paragraph{A lot of examples from book \cite{book}}$ $

\begin{ex}
    Extending example \ref{ex:R-over-Z-T}:
\begin{equation}
    \mathbb{E}^2/(\mathbb{Z}\times\mathbb{Z}) = T\text{ (torus)}
\end{equation}
    Here $=$ means homeomorphism.
\end{ex}
\begin{ex}
    \begin{equation}
        S^n/\mathbb{Z}_2 = P^n
    \end{equation}
    Here $=$ means homeomorphism.
\end{ex}
\begin{ex}[Three ways of $\mathbb{Z}_2$ acting on $T$]
    The detailed procedure is to be found on page 91 of \cite{book}.
    Here's a picture to visualize the action:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/3-ways-Z2-on-T.PNG}
        \caption{$ $}
    \end{figure}
    The results are (a) a sphere; (b) a torus; (c) a Klein bottle.
\end{ex}
\begin{ex}
    If $G$ is a topological group, and $H$ is
    $\mathcal{TPG}$-subgroup. Then, the left cosets of right cosets
    can be canonically seen as orbits. See more on page 81, example 4.
\end{ex}
\begin{ex}
\begin{align}
    \mathrm{O}(n)/\mathrm{O}(n-1) &= S^{n-1} \\
    \mathrm{SO}(n)/\mathrm{SO}(n-1) &= S^{n-1}
\end{align}
    Here $=$ means homeomorphism. The first is established
    mathematically in page 82 of \cite{book}. The second is mentioned
    there, indicating a similar proof.

    Here I give an argument. Consider a unit vector $y$ in $S^{n-1}$, if
    we want to rotate another unit vector $e_1$ to $y$, since the
    action is transitive, we can easily find a $A\in \mathrm{O}(n)$ to
    do this. But in addition, we can also find that $A\cdot B$, where
    $B\in \mathrm{O}(n-1)$ rotates the space around $e_1$ (thus
    leaving $e_1$ un-affected) also do our job. So there is an
    $\mathrm{O}(n-1)$ redundancy in $\mathrm{O}(n)\to S^{n-1}$.
    Similar for the second relation.
\end{ex}

\begin{thm}
    Let $G$ acts on $X$ and suppose that both $G$ and $X/G$ are
    connected, then $X$ is connected.
\end{thm}
\begin{fact}
    Using the theorem above, one can deduce that: $\mathrm{SO}(1)$ is
    connected, $S^{n-1}$ is connected, so $\mathrm{SO}(n)$ is
    connected.
\end{fact}

Next, the book \cite{book} (page 82 to 85) introduces several three
spaces (\nomen{Lens space}, \nomen{irrational flow} on $T$ torus,
\nomen{fundamental region} or in my word \textit{space filling
shapes}) and two group \nomen{Euclidean group} (page 84) and
\nomen{plane-crystallographic group} (page 85). To save time, I leave
here only some pictures:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/irrational-flow.png}
    \caption{Irrational Flow on $T$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/space-filling-shapes.png}
    \caption{Space-filling Shapes}
\end{figure}

### 2016-11-23 Basic Topology Notes/sections/Special-Notes.tex
New basic topology notes. Chapter on fundamental groups and the no fix point theorem.

\paragraph{About map} In book \cite{book}, a map is defined as a
continuous function (page 32), which is confusing. In this note, I
will not use this convention and will always states continuity
clearly.

\paragraph{Basic facts about maps}
Assuming domain $f=X$, codomain $f=Y$.
\begin{align}
    f(U\cup V) &= f(U)\cup f(V) \\
    f(U\cap V) &\subseteq f(U)\cap f(V) \\
    f(U^c) &\supseteq f(U)^c,\,\text{i.e. } f(U)^c \subseteq f(U^c) \\
    f^{-1}(U\cup V) &= f^{-1}(U)\cup f^{-1}(V) \\
    f^{-1}(U\cap V) &= f^{-1}(U)\cap f^{-1}(V) \\
    f^{-1}(U^c) &= [f^{-1}(U)]^c
\end{align}
\paragraph{Smallest the Largest Topolgy}
The set of all possible topolgies on $X$ is partially ordered by
inclusion. For a certain characteristics $\mathcal{C}$, it is possible
to have the smallest or the largest one.

The \nomen{smallest topolgy} $\mathcal{T}_\text{min}$ is the one such
that, for any $\mathcal{T}'$ satisfying $\mathcal{C}$,
$\mathcal{T}_\text{min}\subseteq \mathcal{T}'$. The \nomen{largest
topolgy} $\mathcal{T}_\text{max}$ is the one such that, for any
$\mathcal{T}'$ satisfying $\mathcal{C}$, $\mathcal{T}'\subseteq
\mathcal{T}_\text{max}$.
Synonyms of these two words are:
\begin{itemize}
    \item Larger: stronger, finer.
    \item Smaller: weaker, coarser.
\end{itemize}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.65\linewidth]{pics/comparing-topologies-and-coffee.jpg}
    \caption{Comparing topologies and coffee (Credit:
    \href{http://www.math3ma.com/the-back-pocket/2016/8/26/comparing-topologies}{math3ma})}
\end{figure}
For example, assuming we have
\begin{equation}
    f: X\to Y
\end{equation}
where $f$ is any function.

If $X$ has topolgy $\mathcal{T}_X$, we ask then what kind of topolgy on
$Y$ will make $f$ a continuous function. First, all $f^{-1}(V)$, with
$V\in \mathcal{T}_Y$ should be open in $X$. So, the easiest choice is to
make $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$, this is the
smallest topolgy.  Also, any set $V\in Y$ such that $f^{-1}(V)\notin
\mathcal{T}_X$ should not be in $\mathcal{T}_Y$. Then the largest
topolgy is $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in
\mathcal{T}_X\}$.

If $Y$ has topolgy $\mathcal{T}_Y$, we also ask what kind of topolgy
on $X$ will make $f$ a continuous function. First, all $V\in
\mathcal{T}_Y$, their preimage $f^{-1}(V)$ must be in $\mathcal{T}_X$.
So the smallest topolgy is
$\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$. Than
what about the largest topolgy? We consider, what kind of sets cannot
be inside $\mathcal{T}_X$. First, can $(f^{-1}(V))^c=f^{-1}(V^c)$ be
in $\mathcal{T}_X$? Yes. Since unless the space is connected, there
can be sets being both open and closed (other than $X$ and
$\varnothing$). Any other restrictions? No that I can think of. So,
the largest topolgy $\mathcal{T}_{X,\text{max}}=2^X$, the set of all
subsets of $X$. (The notation \nomen{$2^X$} is taken from the page 4
of book \cite{Singer.Thorpe}.

A summary:
\begin{table}[H]
    \centering
    \caption{Largest and Smallest Topolgies}
    \begin{tabular}{c l l}
        $X\overset{f}{\to}Y$ & Smallest  &Largest \\
        \hline
        Given $\mathcal{T}_X$ & $\mathcal{T}_{Y,\text{min}}=\{\varnothing,Y\}$        & $\mathcal{T}_{Y,\text{max}}=\{ V\subset Y| f^{-1}(V)\in \mathcal{T}_X\}$\\
        Given $\mathcal{T}_Y$ & $\mathcal{T}_{X,\text{min}}=\{f^{-1}(V)|V\in\mathcal{T}_Y\}$ & $\mathcal{T}_{X,\text{max}}=2^X$ \\
        No constraint & $\{\varnothing,X\}$ & $2^X$ \\
        \hline
    \end{tabular}
\end{table}
\paragraph{Facts about subspace/induced topolgy}
Let $Y$ be a subspace of a topological space $X$ wit induced topolgy.
\begin{fact}
    A set $H\subseteq Y$ is open in $Y$ if and only if $H=F\cap Y$
    for some open set $F$ in $X$.
\end{fact}
\begin{fact}
    A set $H\subseteq Y$ is closed in $Y$ if and only if $H=F\cap Y$
    for some closed set $F$ in $X$.
\end{fact}
\begin{fact}
    A set $H$ is open/closed in $X$ $\Rightarrow$ $H$ is open/closed
    in $Y$. But the converse may not be true. The converse statement
    depends on whether $Y$ is open or closed in $X$.
\end{fact}

### 2016-11-23 Basic Topology Notes/sections/ch5-fundamental-groups.tex
New basic topology notes. Chapter on fundamental groups and the no fix point theorem.

\subsection{Homotopic maps}
\label{sec:Homotopic-maps}

By a \nomen{loop} we mena a continuous map $\alpha:I\to X$ such that
$\alpha(0)=\alpha(1)$. We can view is also as a continuous map
$\alpha:S^1 \to X$. It is said to be based at the point
$\alpha(0)$. Two loops $\alpha$ and $\beta$ with the same \nomen{base
point} can be multiplied, and their product is defined on page 87.
A visualization is here:
% cd 1 todo

But this product is not sufficient to become a group. At least, the
multiplication is not associative:
% cd 2 todo

But clearly the two result are exactly if we do care how long they
occupy on the interval $I$, if the interval $I$ is considered as a
time parameter. So we define the following homotopy relation between
loops. If we can find a family $\{f_r\}$ of maps, one for each $r\in
[0,1]$, such that $f_0=\alpha$, $f_1=\beta$, then we say that the
loops $\alpha$ and $\beta$ are homotopic. Schematically,
% cd 3 todo

This relation can be generalized to any continuous maps:
\begin{defi}[Homotopic]
\nomenclature{Homotopic}{\nomrefpage.}
    Let $f,g: X \to Y$ be continuous maps. Then $f$ is homotopic to
    $g$ if there exists a map $F:X \times I\to Y$ such that $F(x,O) =
    f(x)$ and $F(x,1) = g(x)$ for alt points $x\in X$.
\end{defi}

The map $F$ is called a \nomen{homotopy} from $f$ to $g$, and we write
\nomen{$f\simeq_F g$}. In addition, if $f$ and $g$ agree on some
$A\subset X$, we may wish to deform $f$ to $g$ without altering the
values of $f$ on $A$. In this case we ask for a homotopy $F$ from $f$
to $g$ with the additional property that 
\begin{equation}
    F(a,t)=f(a) \text{ for all $a\in A$, for all $t\in I$}
\end{equation}
when such a homotopy exists, we say the \nomen{$f$ is homotopic to $g$
relative to $A$} and write \nomen{$f\simeq_F g$ rel $A$}.
% cd 4 todo

When $f$ and $g$ are loops, then the homotopic relation for loops are
just saying that $f\simeq g$ rel $\{0,1\}$.

% fig 5.1 p 88 todo

\begin{ex}
    The author shows on page 88 of \cite{book} that: when $C$ is a
    convex subset of a euclidean space, let $f,g:X\to C$ be continuous
    maps, then $f\simeq_F g$, where $F$ is $F(x,t)=(1-t)f(x)+tg(x)$.
    Note that if $f$ and $g$ agree on a subset $A$ of $X$, then this
    homotopy is a homotopy relative to $A$. This $F$ is called a
    \nomen{straight-line homotopy}.
\end{ex}
\begin{ex}
    Let $f,g:X\to S^n$ be continuous maps. We can take $S^n$ to be the
    unit sphere in $\mathbb{E}^{n+1}$, and think of $f,g$ as
    continuous maps into $\mathbb{E}^{n+1}$, then we may form a
    straight-line homotopy from $f$ to $g$ by:
    \begin{equation}
        F(x,t) = \frac{(1-t)f(x)+tg(x)}{||(1-t)f(x)+tg(x)||}
    \end{equation}
    But why we are  % yes why! TODO
\end{ex}
\begin{ex}
    This is example is best illustrated by pictures:
    % fig 5.2 todo
    Geometrieally, $\alpha$ winds eaeh of the segments
    $[O,\frac{1}{2}]$, $[\frac{1}{2},\frac{3}{4}]$, $[\frac{3}{4}, 1]$
    once round the eirc1e, the first two being wound in an
    anticlockwise direetion, and the third clockwise. The loop $\beta$
    simply winds the whole interval $[0,1]$ once round the circle
    anticlockwise.

    The book\cite{book} gives a homotopy $F$ between $\alpha$ and
    $\beta$ on page 89. But it is best to imagine $\alpha$ and $\beta$
    being metal coils, and this $F$ just describes the process when
    one magically strach and unfold the coil from $\alpha$ to $\beta$.

    Notice that this coil is connected head to tail, so it is
    essential that there is not pole inside the coil in order that one
    can unfold the coil from $\alpha$ to $\beta$.
\end{ex}

I think we already feel this, but the book proves it on page 90, that

\begin{lemma}
    The relation of 'homotopy' is an equivalence relation on the set
    of all maps from $X$ to $Y$.
\end{lemma}

Also
\begin{lemma}
    The relation of 'homotopy relative to a subset $A$ of $X$' is an
    equivalence relation on the set of all maps from $X$ to $Y$ which
    agree with some give map on $A$.
\end{lemma}

The book also mentions that
\begin{lemma}
    Homotopy behaves well with respect to composition of maps
\end{lemma}
which means precisely that:
\begin{itemize}
    \item If $f\simeq_F g$ rel $A$, then $hf\simeq_{hF} hg$ rel $A$.
        $$ \begin{tikzcd}[]
            A\subset X \ar[r,"f",bend left]\ar[r,"g",bend right]
                & Y \ar[r,"h"] & Z
        \end{tikzcd}$$
    \item If $g\simeq_G h$ rel $B$, then $gf\simeq_F hf$ rel $f^{-1}B$
        via the homotopy $F(x,t)=G(f(x),t)$.
        $$ \begin{tikzcd}[]
            X\ar[r,"f"] & Y \ar[r,"g",bend left]\ar[r,"h",bend right]
             & Z \\
            f^{-1}B\ar[u,phantom,"\subset"
            {anchor=south,rotate=90,left=0,near end}]
                &
            B\ar[u,phantom,"\subset" {anchor=south,rotate=90,left=0,near
            end}] & \, 
        \end{tikzcd}$$
\end{itemize}

From this on, I will follow the lecture by professor Li Qin.

\subsection{Review}
\label{sec:Review}
From last lecture, we have shown:
\begin{ex}
    For $n\geq 2$,
    $$ \pi_1 (S^n) = \{e\} $$
\end{ex}
\begin{ex}
    $$ \pi_1 (\mathbb{R}^n) = \{e\}$$
\end{ex}

\begin{thm}
    $$\pi_1 (S^1) = \mathbb{Z} $$
\end{thm}

\begin{proof}
    Given any integer $n\in \mathbb{Z}$, we give a loop by associatng
    each $n$ 
    \begin{align*}
        \pi : \mathbb{R} \to S^1 \\
        t \mapsto e^{2\pi it}
    \end{align*}
    Define 
    \begin{align}
        \gamma_n : [0,1] \to \mathbb{R} \\
        s\mapsto n s
    \end{align}
    Then $\phi_n:= \pi\circ \gamma_n$ has the property that
    $\phi_n(0)=1$, $\phi_n(1)=1$. So we obtain 
    \begin{equation}
        \phi: \mathbb{Z} \to \pi_1  (S^1)
    \end{equation}
    Geometrically, we $\phi_n$ loops around $S^1$ in $n$ turns.

    We need to prove that $\phi$ is a isomorphism. This is done by:
    \begin{enumerate}
        \item Prove that $\phi$ is a homomorphism;
        \item Prove that $\phi$ is bijective.
    \end{enumerate}
    First,
    \begin{align*}
        \gamma_n: s \mapsto n s \\
        \gamma_m: s\mapsto m s\\
    \end{align*}
    We need
    \begin{align*}
        \braket{\pi\circ \gamma_{m+n}} =
        \braket{\pi\circ\gamma_m}\braket{\pi\circ \gamma_n}\\
    \end{align*}
    Define $\sigma:[0,1]\to \mathbb{R}$, $s\mapsto \gamma_n(s)+m$,
    this is a translation of real line. Then $\pi\circ \sigma =
    \pi\circ \gamma_n$. Then
    \begin{align*}
        \braket{\pi\circ\gamma_m}\braket{\pi\circ \gamma_n}
        = \braket{\pi\circ\gamma_m} \braket{\pi\circ\sigma}
        = \braket{\pi\circ(\gamma_m\circ \sigma)}
    \end{align*}
    $\gamma_{m+n}$ has the same domain and codomain of $\gamma_m \circ
    \sigma$, and they obviously share the same start and the same end
    point. Therefore these two path are homotopic relative to
    $\{0,1\}$.
    Therefore
    \begin{equation}
        \braket{\pi\circ \gamma_{m+n}} =
        \braket{\pi\circ(\gamma_m\circ\sigma)}
    \end{equation}
    Or
    \begin{equation}
        \phi_{m+n} = \phi_{m}\phi_n
    \end{equation}

    Second, we need to show that this map is surjective. Notice that
    $\pi:\mathbb{R}\to S^1$, $t\mapsto e^{2\pi i t}$, is like a
    projection of a circulatory path onto a circle $S^1$. This map is
    locally homeomorphic. We can find a cover of $S^1$ as the
    combination of
    \begin{align*}
        U = S^1\setminus \{-1\} \\
        V = S^1\setminus \{1\}
    \end{align*}
    Then $\pi^{-1}(V)$ are the intervals on $\mathbb{R}$ excluding the
    whole integer points. Similarly, $\pi^{-1}(U)$ are those intervals
    on $\mathbb{R}$ excluding those half-integer points. In each of those
    intervals the map $\pi$ is bijective.
    Now we need a lemma:
    \begin{lemma}[Path-lifting lemma]
        \begin{equation}
            \begin{tikzcd}[]
                \, & \mathbb{R}\ar[d,"\pi"] \\
                {[0,1]}\ar[r,"\sigma"]\ar[ru,"f"] & S^1
            \end{tikzcd}
        \end{equation}
        Assuming we have $\pi$ and $\sigma$, both are continuous maps.
        More specifically, $\sigma$ is a path in $S^1$ which begins at the
        point $1$. Then there is a unique path $\tilde\sigma$ in
        $\mathbb{R}$ which begins at $0$ and satisfies $\pi\circ
        \tilde\sigma = \sigma$.
    \end{lemma}
    \begin{proof}
        By Lebesgue lemma, we can divide the interval $[0,1]$ fine enough
        such that each part  is maped to only one of the cover $U$ or $V$.
        We thus break a path % TODO
    \end{proof}
    Note that $\tilde\sigma(0)=0$, $\tilde\sigma(1)$ is an integer.
    Now for any loop $\gamma:[0,1]\to S^1$ based at $1$, we can find a
    lifting $\tilde\gamma:[0,1]\to \mathbb{R}$ such that
    $\tilde\gamma(0)=0$,$\tilde\gamma(1)=n$, and $\gamma = \pi\circ
    \tilde\gamma$. Then $\tilde\gamma \cong \gamma_n$ rel $\{0,1\}$,
    also $\braket{\pi\circ\tilde\gamma}=\braket{\pi\circ\gamma_n}$.
    Hence for any path $\gamma$ we find a $n$ such that
    $\gamma=\phi(n)$. So the map is surjective.

    We need another lemma to prove that it is injective.
    \begin{lemma}[Homotopy-lifting lemma]
        If $F:[0,1]\times[0,1]\to S^1$ is a map such that
        $F(0,t)=F(1,t)=1$ for $0\leq t\leq 1$, then there exists a
        unique $\tilde F: [0,1]\times[0,1]\to \mathbb{R}$ such that
        \begin{align}
            \pi\circ \tilde F = F \\
            \tilde F(0,t) =0,\, 0\leq t\leq 1
        \end{align}
    \end{lemma}
    % TODO Graph here.
    \begin{proof}
        We need the Lebesgue lemma. Let $S^1=U\cup V$ as before.
    \end{proof}
    Now we proof that the map $\phi$ is injective. Suffice to prove
    that $\Ker(\phi)$ is trivial. Suppose $\phi(n)=\pi\circ \gamma_n$
    is homotopic to the constant loop. Then choose a homotopy $F$
    from $\pi\circ\gamma_n$ to the constant loop. By the
    homotopy-lifting lemma we can find $\tilde F: [0,1]\times[0,1]\to
    \mathbb{R}$ such that $\pi\circ \tilde F = F$. Also $\tilde
    F(0,t)=0$.
    % TODO  We can find the vertical bottom is 0 and verticl height is
    % gamma_n. Right line is integers and can only be 0 Hence gamma_n
    % starts at 0 and ends at 0
    One can find that $\gamma_n\cong 0$. This completes the proof of
    injectivity. Hence completes the whole proof.
\end{proof}

We have an application,
\begin{thm}[Brow Fixed Point theorem] % TODO brower? broer?
    A contiuous map $f:B^2\to B^2$ ($B^2:2D$-closed dicks) must have a
fixed point. That is, $\exists x\in B^2$ such that $f(x)=x$.
\end{thm}
\begin{proof}
    Assuming that this theorem is false, that is $\forall x\in B^2$,
    $x\neq f(x)$, then we have a straight path from $f(x)$ to $x$. We can
    extends this path to cuts the boundary of $B^2$ at $h(x)$. This is
    for all $x\in B^2$, hence we have a map $h: B^2 \to S^1$. Also,
    $h|_{S^1}$ is obvious an identity map. But $S^1$ can be included
    inside $B^2$, so we have:
    \begin{equation}
        S^1 \to B^2 \to S^1 % TODO add function labels
    \end{equation}
    Hence we have a series of homomorphism of fundamental groups:
    \begin{equation}
        \pi_1 (S^1) \to \pi_1 (B^2) \to \pi_1(S^1)
    \end{equation}
    and the composite is identity map. But observe that $B^2$ is a
    convex set and hence its fundamental group is trivial. But $S^1$
    has non-trivial fundamental group.
\end{proof}
\begin{remark}
    This theorem can be extended to higher dimensional case. But the
    proof cannot be the same because for higher dimension $\pi_1(S^n)$
    is no longer non-trivial.
\end{remark}

Another application, which we need a theorem to help:
\begin{thm}
    \begin{equation}
        \pi_1 (X\times Y, (x_0,y_0)) = \pi_1 (X,x_0) \otimes \pi_1
        (X,y_0)
    \end{equation}
\end{thm}
\begin{proof}
    We use the projection maps: $P_1$ and $P_2$.
    Then, the map
    \begin{align*}
        (P_1)_*: \pi_1 (X\times Y) \to \pi_1(X) \\
        (P_2)_*: \pi_1 (X\times Y) \to \pi_1(Y)
    \end{align*}
    and their composition formed into
    \begin{align*}
        \braket{\alpha}\mapsto
        (\braket{P_1\circ\alpha},\braket{P_2\circ\alpha})
    \end{align*}
    this map is surjective, injective, and is homomorphism.
    because any %TODO
\end{proof}

\begin{fact}
By this theorem, the two objects $S^2$ and $S^1\times S^1$ is not
homeomorphic, since their fundamental groups are not the same (the
former is trivial and the later is $\mathbb{Z}\times\mathbb{Z}$).
\end{fact}

% TODO homework: pro 13 of page 95.

### 2016-11-23 Latex packages/latex examples.tex
New basic topology notes. Chapter on fundamental groups and the no fix point theorem.

@@
 \author{Taper}
+
+\tikzset{
+	upprright/.style={anchor=south,rotate=90,left=0,near end}
+}
 
@@
 \end{tikzcd} $$
+
+$$ \begin{tikzcd}[]
+X\ar[r,"f"] & Y \ar[r,"g",bend left]\ar[r,"h",bend right]
+& Z \\
+f^{-1}B\ar[u,phantom,"\subset"
+{anchor=south,rotate=90,left=0,near end}]
+&
+B\ar[u,phantom,"\subset" {anchor=south,rotate=90,left=0,near
+      	end}] & \, 
+\end{tikzcd}$$
+
+Or, with something "tikzset" in the preamble, we can
+
+$$ \begin{tikzcd}[]
+	X\ar[r,"f"] & Y \\
+	f^{-1}B\ar[u,phantom,"\subset" upprright]
+		& B\ar[u,phantom,"\subset" {anchor=south,rotate=90,left=0,near
+		end}] 
+\end{tikzcd}$$
 

### 2016-11-25 C.V/modern cv template/Modern CV template.tex
Add modern CV template. But it is too fancy for physics, I think I won't use it.

%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{John}{Doe}
\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(234)~567~890}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\phone[fixed]{+2~(345)~678~901}
\phone[fax]{+3~(456)~789~012}
\email{john@doe.org}                               % optional, remove / comment the line if not wanted
\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{john.doe}                        % optional, remove / comment the line if not wanted
\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[github]{jdoe}                              % optional, remove / comment the line if not wanted
\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}  % arguments 3 to 6 can be left empty
\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Master thesis}
\cvitem{title}{\emph{Title}}
\cvitem{supervisors}{Supervisors}
\cvitem{description}{Short thesis abstract}

\section{Experience}
\subsection{Vocational}
\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline{}%
Detailed achievements:%
\begin{itemize}%
\item Achievement 1;
\item Achievement 2, with sub-achievements:
  \begin{itemize}%
  \item Sub-achievement (a);
  \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
    \begin{itemize}
    \item Sub-sub-achievement i;
    \item Sub-sub-achievement ii;
    \item Sub-sub-achievement iii;
    \end{itemize}
  \item Sub-achievement (c);
  \end{itemize}
\item Achievement 3.
\end{itemize}}
\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
\subsection{Miscellaneous}
\cventry{year--year}{Job title}{Employer}{City}{}{Description}

\section{Languages}
\cvitemwithcomment{Language 1}{Skill level}{Comment}
\cvitemwithcomment{Language 2}{Skill level}{Comment}
\cvitemwithcomment{Language 3}{Skill level}{Comment}

\section{Computer skills}
\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Interests}
\cvitem{hobby 1}{Description}
\cvitem{hobby 2}{Description}
\cvitem{hobby 3}{Description}

\section{Extra 1}
\cvlistitem{Item 1}
\cvlistitem{Item 2}
\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}

\section{Extra 2}
\cvlistdoubleitem{Item 1}{Item 4}
\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

\section{References}
\begin{cvcolumns}
  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
\date{January 01, 1984}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

Albert Einstein discovered that $e=mc^2$ in 1905.

\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}

%% end of file `template.tex'.

### 2016-11-26 Basic Topology Notes/sections/Special-Notes.tex
Adding notes to homotopy types.

@@
 \end{fact}
+
+\subsection{Lebesgue lamme}
+\label{sec:Lebesgue lamme}
+
+This is a very important lemma, which is why I gave it a seperate
+section. It is labeled (3.11) in book \cite{book}.
+\begin{thm}[Lebesgue Lemma]
+    \label{thm:lebesgue-lemma} 
+    Let $X$ be a compact metric space and let $\mathscr{F}$ be an open
+    cover of $X$. Then there exists a real number $\delta>0$ (called
+    the \nomen{Lebesgue number} of $\mathscr{F}$) such that any subset
+    of $X$ of diameter less than $\delta$ is contained in some member
+    of $\mathscr{F}$.
+\end{thm}

### 2016-11-26 Basic Topology Notes/sections/ch5-fundamental-groups.tex
Adding notes to homotopy types.

@@
 
-From this on, I will follow the lecture by professor Li Qin.
+\subsection{Construction of the fundamental group}
+\label{sec:Construction-of-the-fundamental-group}
 
-\subsection{Review}
-\label{sec:Review}
-From last lecture, we have shown:
-\begin{ex}
-    For $n\geq 2$,
-    $$ \pi_1 (S^n) = \{e\} $$
-\end{ex}
-\begin{ex}
-    $$ \pi_1 (\mathbb{R}^n) = \{e\}$$
-\end{ex}
+\begin{thm}
+    The set of homotopy classes of loops in $X$ based at $p\in X$
+    forms a group under the multiplication
+    $\braket{\alpha}\cdot\braket{\beta}=\braket{\alpha\cdot\beta}$.
+    The identity and inverse elements are defined on page 92 and 93 of
+    \cite{book}.
+\end{thm}
+\begin{remark}
+    Notice that the fundamental group dependes heavily on the base
+    point. Especially when the space $X$ is disconnected. A natural
+    intuition is that when the space is path-connected, then any two
+    paths can be connected. If two points can be connected, then two
+    loops based on different points can be connected. That why we have
+    the following.
+\end{remark}
+\begin{thm}
+    If $X$ is a path-connected then $\pi_1(X,p)$ $\pi_1(X,q)$ are
+    isomorphic for any two points $p,q\in X$.
+\end{thm}
+\begin{proof}
+    The proof is on page 94 of \cite{book}.
+\end{proof}
+\begin{defi}[$f_*$]
+\nomenclature{$f_*$}{\nomrefpage.}
+Suppose we have a continuous map $f:X\to Y$, $f$ can induce a map
+($p\in X,q\in Y$ and $q=f(p)$).
+    \begin{align}
+        f_* : \pi_1(X,p) &\to \pi_1(Y,q) \\
+        \braket{\alpha} &\mapsto \braket{f\circ \alpha}
+    \end{align}
+This map is actually a homomorphism.
+\end{defi}
+\begin{fact}
+By construction, we have for
+$$ \begin{tikzcd}[]
+    X\ar[r,"f"] & Y\ar[r,"g"] & Z
+\end{tikzcd}$$
+\begin{align}
+    (g\circ f)_* = g_* \circ f_*
+\end{align}
+\end{fact}
+\begin{fact}
+With a homeomorphism $h:X\to Y$ and the above fact, we see that
+homeomorphic spaces have isomorphic fundamental groups.
+\end{fact}
+\subsection{Sectin 5.3}
+\label{sec:Sectin-5.3}
+This section calculates the following facts:
+\begin{table}[H]
+    \centering
+    \begin{tabular}{c c c}
+        \hline
+        \#&  Space                           & Fundamental group \\
+          \hline
+        1 &  Conves subset of $\mathbb{E}^n$ & \{e\} \\
+        2 &  Circle                          & $\mathbb{Z}$ \\
+        3 & $S^1$                           & $\mathbb{Z}$ \\
+        4 & $S^n,\, n\geq 2$                & \{e\} \\
+        5 & Torus $S^1\times S^1$           & $\Z\times\Z$ \\
+        6 & $P^n,, n\geq 2$                 & $\Z_2$ \\
+        7 & Klein bottle                    & $\{a,b|a^2=b^2\}$ \\
+        8 & Len space $L(p,q)$              & $\Z_p$ \\
+          \hline
+    \end{tabular}
+\end{table}
 
+\paragraph{Convex subset of $\E^n$} is on page 96 of \cite{book}.
+\begin{defi}[simply connected]
+\nomenclature{simply connected}{\nomrefpage.}
+    A path-connected space whose fundamental group is trivial is said
+    to be simply connected.
+\end{defi}
+
+\paragraph{The $n$-sphere $S^n$} is on page 99. To prove it, we
+require a theorem:
+\begin{thm}
+    Let $X$ be a space which can be written as the union of two simply
+    connected open sets $U,V$ in such a way that $U\cap V$ is
+    path-connected. Then $X$ is simply connected.
+\end{thm}
+\begin{proof}
+    Proof is on page 99 of \cite{book}. It requires the Lebesgue lemma
+    \ref{thm:lebesgue-lemma}. A picture illustrating the proof is
+    provided here:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]
+        {pics/n-sphere-is-simply-con.PNG}
+    \end{figure}
+\end{proof}
+Then, the two cover of $S^n$ are simply $U=S^n-\{x\}$ and
+$V=S^n-\{y\}$, where $x,y$ are two distinct points on $S^n$. Since $U$
+and $V$ are homeomorphic to $\E^n$, $S^n$ is simply-connected.
+
+\subsection{Continued Section 5.3}
+\label{sec:Continued-Section-5.3}
+In this section, I will follow the lecture by professor Li Qin.
+We show that
 \begin{thm}
@@
     \begin{lemma}[Path-lifting lemma]
+        \label{thm:path-lifting-lemma-1}
         \begin{equation}
@@
         More specifically, $\sigma$ is a path in $S^1$ which begins at the
-        point $1$. Then there is a unique path $\tilde\sigma$ in
-        $\mathbb{R}$ which begins at $0$ and satisfies $\pi\circ
+        point $1\in S^1$. Then there is a unique path $\tilde\sigma$ in
+        $\mathbb{R}$ which begins at $0\in \R$ and satisfies $\pi\circ
         \tilde\sigma = \sigma$.
@@
     \begin{proof}
-        By Lebesgue lemma, we can divide the interval $[0,1]$ fine enough
-        such that each part  is maped to only one of the cover $U$ or $V$.
-        We thus break a path % TODO
+        The proof is on page 97 to 98 of \cite{book}. The class gives
+        me enough intuition to understand the proof.
+
+        The intuition is that, by Lebesgue lemma, we can divide the
+        interval $[0,1]$ fine enough such that each divided part  is
+        maped to only one of the cover $U$ or $V$.  We thus break a
+        path $\sigma$ into small paths $\sigma_i$. Each $\sigma_i$ can
+        be lifted into a path $\tilde\sigma_i$ in $\R$. But such
+        lifting can be arbitrary because the inverse of $\pi$ is not a
+        good function. To resolve this ambiguity, one requires the
+        first path should starts with $0\in\R$, and the second should
+        be continuously connected to the first, and so is the third,
+        fourth, etc. This fixes the ambiguity and the paths
+        $\tilde\sigma_i$ when connected give the required path
+        $\tilde\sigma$.
     \end{proof}
@@
     Hence for any path $\gamma$ we find a $n$ such that
-    $\gamma=\phi(n)$. So the map is surjective.
+    $\gamma=\phi(n)$. So \textit{the map is surjective}.
 
@@
         $F(0,t)=F(1,t)=1$ for $0\leq t\leq 1$, then there exists a
-        unique $\tilde F: [0,1]\times[0,1]\to \mathbb{R}$ such that
+        unique $\widetilde F: [0,1]\times[0,1]\to \mathbb{R}$ such that
         \begin{align}
-            \pi\circ \tilde F = F \\
-            \tilde F(0,t) =0,\, 0\leq t\leq 1
+            \pi\circ \widetilde F = F \\
+            \widetilde F(0,t) =0,\, 0\leq t\leq 1
         \end{align}
     \end{lemma}
-    % TODO Graph here.
+    % TODO Graph here. DC 1
     \begin{proof}
-        We need the Lebesgue lemma. Let $S^1=U\cup V$ as before.
+        The proof is on page 98 of \cite{book}. The idea is exactly
+        the same as in lemma~\ref{thm:path-lifting-lemma-1}.
     \end{proof}
@@
     from $\pi\circ\gamma_n$ to the constant loop. By the
-    homotopy-lifting lemma we can find $\tilde F: [0,1]\times[0,1]\to
-    \mathbb{R}$ such that $\pi\circ \tilde F = F$. Also $\tilde
-    F(0,t)=0$.
-    % TODO  We can find the vertical bottom is 0 and verticl height is
-    % gamma_n. Right line is integers and can only be 0 Hence gamma_n
-    % starts at 0 and ends at 0
+    homotopy-lifting lemma we can find $\widetilde F: [0,1]\times[0,1]\to
+    \mathbb{R}$ such that $\pi\circ \widetilde F = F$. Also
+    $\widetilde F(0,t)=0$.
+    We can find the vertical bottom is $0$ and verticl top is
+    $\gamma_n$. Right line is integers and can only be $0$ Hence
+    $\gamma_n$ starts at $0$ and ends at $0$.
     One can find that $\gamma_n\cong 0$. This completes the proof of
@@
 We have an application,
-\begin{thm}[Brow Fixed Point theorem] % TODO brower? broer?
+\begin{thm}[Brouwer Fixed Point theorem] % TODO brower? broer?
     A contiuous map $f:B^2\to B^2$ ($B^2:2D$-closed dicks) must have a
@@
     this map is surjective, injective, and is homomorphism.
-    because any %TODO
+    The detail can be found on page page 101 of \cite{book}.
 \end{proof}
@@
 % TODO homework: pro 13 of page 95.
+
+\subsection{Homotopy Type}
+\label{sec:Homotopy-Type}
+
+Notice that a homeomorphic map will make two space have the same
+fundamental group, but two space having the same fundamental group may
+not be homeomorphic. For example, the plane and the $S^2$ both have
+the same $\pi_1=\{e\}$, but the plane is not compact while the
+$2$-sphere is, i.e. they are not homeomorphic.
+
+Notice also that homeomorphic requires $fg^{-1}=\id$, whereas under
+homotopic relation, we may require $fg^{-1}\cong\id$. Therefore we may
+also define a new type of relationship between topological spaces:
+
+\begin{defi}[Homotopy type]
+\nomenclature{Homotopy type}{\nomrefpage.}
+    Two spaces $X$ and $Y$ have the same homotopy type, or they are
+    homotopy equivalent, if there exist maps:
+    $$ \begin{tikzcd}[]
+        X\ar[r,"f",bend left] & Y\ar[l,"g",bend left]
+    \end{tikzcd}$$
+    such that $g\circ f\cong \id_X$, and $f\circ g\cong\id_Y$.
+\end{defi}
+\begin{fact}
+This relationship must be an equivalence relation on topological
+spaces, as confirmed by lemma (5.16) on page 103 of \cite{book}.
+\end{fact}
+
+\begin{defi}[Deformation retraction]
+\nomenclature{Deformation retraction}{\nomrefpage.}
+    Let $A$ be a subspace of $X$. Let a homotopy $G:X\times I\to X$ which
+    is relative to $A$ and for which
+    $$ \begin{cases}
+        G(x,0)=x & \\
+        G(x,1)\in A
+    \end{cases}$$
+    for all $x\in X$. Then $G$ will be called a deformation retraction
+    of $X$ onto $A$.
+\end{defi}
+\begin{remark}
+    If there is a deformation retraction of $X$ onto $A$, then of
+    course $X$ and $A$ have the same homotopy type.
+\end{remark}
+Following is an example of a deformation retraction:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/deformation-retraction.PNG}
+    \caption{Three Deformation Retractions (from \cite{book})}
+\end{figure}
+
+Exmaples from the book:
+\begin{ex}
+    Homeomorphic spaces have the same homotopy type.
+\end{ex}
+\begin{ex}
+    Any convex subset of a euclidean space is homotopy equivalent to a
+    point.
+\end{ex}
+\begin{ex}
+    $\E^n\setminus \{0\}$ has the homotopy type of $S^{n-1}$. This is
+    shown on page 104 of \cite{book}, and is illustrated there by:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/En-0-and-S-n-1.PNG}
+        \caption{$E^n\setminus\{0\}$ and $S^{n-1}$}
+    \end{figure}
+\end{ex}
+
+\begin{thm}
+    If $f\cong_F g:X\to Y$ then $g_*:\pi_1(X,p)\to \pi_1(Y,g(p))$ is
+    equal to the composition
+    \begin{equation} \begin{tikzcd}[]
+        \pi_1(X,p)\ar[r,"f_*"]&\pi_1(Y,f(p))\ar[r,"\gamma_*"]
+            &\pi_1(Y,g(p))
+    \end{tikzcd} \end{equation}
+    where $\gamma$ is the path joining $f(p)$ to $g(p)$ in $Y$ defined
+    by $\gamma(s)=F(p,s)$.
+\end{thm}
+\begin{proof}
+    Proof can be found on page 105 of \cite{book}.
+\end{proof}
+
+\begin{thm}
+    If two path-connected spaces are of the same homotopy type, then
+    they have isomorphic fundamental group.
+\end{thm}
+\begin{proof}
+    Proof can be found on page 106 of \cite{book}. Here's a note using
+    the notation in that book:
+    $$ \begin{tikzcd}[]
+        X\ar[r,"f",bend left] & Y\ar[l,"g",bend left]
+    \end{tikzcd}$$
+    It should be noticed that the continuity allows one to identify the
+    diagram:
+    $$ \begin{tikzcd}[]
+        \pi_1(X,p)\ar[r,"(gf)_*"]\ar[rr,"\id",bend right]
+            &\pi_1(X,gf(p))\ar[r,"\gamma^{-1}_*"]
+            &\pi_1(X,p)
+    \end{tikzcd} $$
+    with the diagram:
+    $$ \begin{tikzcd}[]
+        \pi_1(X)\ar[r,"(gf)_*"]\ar[rr,"\id",bend right]
+            &\pi_1(X)\ar[r,"\gamma^{-1}_*"]
+            &\pi_1(X)
+    \end{tikzcd} $$
+\end{proof}
+
+\begin{fact}
+Using above fact, we can find that the M\"obius strip, the cylinder,
+the punctured plane $\E^2\setminus\{0\}$, and the solid torus, all
+have the homotopy type of a circle $S^1$, and consequiently have $\Z$
+as fundamental group.
+\end{fact}
+\begin{fact}
+    Also, $\E^n\setminus\{0\}$ deformation-retracts onto $S^{n-1}$ and
+    is therefore a simply connected space when $n\geq 3$.
+\end{fact}
+
+\begin{defi}[Contractible]
+\nomenclature{Contractible}{\nomrefpage.}
+    A space $X$ is called contractible if the identity map $\id_X$ is
+    homotopic to the constant map at some point of $X$.
+\end{defi}
+\begin{thm}$ $
+
+    \begin{enumerate}
+        \item A space is contractible if and only if it has the
+            homotopy type of a point.
+        \item A contractible space is simply connected.
+        \item Any two maps into a contractible space are homotopic.
+        \item If $X$ is contractible, then $\id_X$ is homotopic to the
+            constant map at $x$ for any $x\in X$.
+    \end{enumerate}
+\end{thm}
+\begin{ex}
+    Here is a contractible space that is really hard to imagin. It is
+    called the topologist's dunce hat. It is formed by identifying the
+    sides of a triangle in the manner indicated in the following
+    figure:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.4\linewidth]{pics/topo-dunce-hat.PNG}
+        \caption{Topologist's dunce hat}
+        \label{fig:topo-d-hat}
+    \end{figure}
+    You may imagin identify a pair of sides, then identify the
+    identitied edge to the resting side. The direction for identifying
+    is really important.
+    This space is contractible. Despite some hard words said by the
+    book, it is really simple to see on figure~\ref{fig:topo-d-hat}.
+    Draw any loop on it and shrink it. Noticing that all edges are
+    identified, though in some odd direction.
+\end{ex}

### 2016-11-27 Basic Topology Notes/sections/ch5-fundamental-groups.tex
Adding all recent diagrams and pictures for Basic topology note.

@@
 point} can be multiplied, and their product is defined on page 87.
-A visualization is here:
-% cd 1 todo
-
+A visualization of $\alpha\cdot\beta$ is here:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.4\linewidth]{pics/multiply-loops.pdf}
+    \caption{Multiply loops}
+\end{figure}
 But this product is not sufficient to become a group. At least, the
 multiplication is not associative:
-% cd 2 todo
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/multiply-loop-not-associative.pdf}
+    \caption{Multiplication of loop is not associative}
+\end{figure}
 
@@
 loops $\alpha$ and $\beta$ are homotopic. Schematically,
-% cd 3 todo
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/homotopy-for-loops.pdf}
+    \caption{Homotopy for loops}
+\end{figure}
 This relation can be generalized to any continuous maps:
@@
 relative to $A$} and write \nomen{$f\simeq_F g$ rel $A$}.
-% cd 4 todo
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\linewidth]{pics/homotopy-schematic.pdf}
+    \caption{Homotopy Scheme}
+\end{figure}
 
@@
 
-% fig 5.1 p 88 todo
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\linewidth]{pics/homotopy-for-loops-2.PNG}
+    \caption{Homotopy for loops 2 (pp. 88 of \cite{book})}
+\end{figure}
 \begin{ex}
@@
     This is example is best illustrated by pictures:
-    % fig 5.2 todo
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/{loops-to-loops-fig5.2}.PNG}
+        \caption{Loops to loops (pp. 89 of \cite{book})}
+    \end{figure}
     Geometrieally, $\alpha$ winds eaeh of the segments
@@
         \begin{align}
-            \pi\circ \widetilde F = F \\
-            \widetilde F(0,t) =0,\, 0\leq t\leq 1
+            \pi\circ \widetilde F &= F \\
+            \widetilde F(0,t) &=0,\, 0\leq t\leq 1
         \end{align}
     \end{lemma}
-    % TODO Graph here. DC 1
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.5\linewidth]{pics/homotopy-lifting-1.pdf}
+        \caption{Homotopy lifting lemma-1}
+    \end{figure}
     \begin{proof}
@@
     We can find the vertical bottom is $0$ and verticl top is
-    $\gamma_n$. Right line is integers and can only be $0$ Hence
-    $\gamma_n$ starts at $0$ and ends at $0$.
-    One can find that $\gamma_n\cong 0$. This completes the proof of
-    injectivity. Hence completes the whole proof.
+    $\gamma_n$. Right line is integers and can only be $0$. 
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/homotopy-lifting-2.pdf}
+        \caption{Schematic Draft}
+    \end{figure}
+    Hence $\gamma_n$ starts at $0$ and ends at $0$.  One can find that
+    $\gamma_n\cong 0$. This completes the proof of injectivity. Hence
+    completes the whole proof.
 \end{proof}
@@
 We have an application,
-\begin{thm}[Brouwer Fixed Point theorem] % TODO brower? broer?
+\begin{thm}[Brouwer Fixed Point theorem]
     A contiuous map $f:B^2\to B^2$ ($B^2:2D$-closed dicks) must have a
@@
     \begin{equation}
-        S^1 \to B^2 \to S^1 % TODO add function labels
+        S^1 \to B^2 \to S^1
     \end{equation}
@@
     convex set and hence its fundamental group is trivial. But $S^1$
-    has non-trivial fundamental group.
+    has non-trivial fundamental group. It is then impossible to form
+    such a chain of homomorphism whose product is identity map.
+    Contradiction!
 \end{proof}

### 2016-11-27 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/notes.tex
[minor] Adding fancy quote environments to physicist-taper style (Latex package) [minor] Some reading notes of the paper "1d Quantum Walk" (from page 1 to 2)

@@
 \label{sec:General}
+
 This paper discusses in general a model charaterised by the follwoing
@@
 \end{align}
+
+where
+\begin{equation}
+    \tilde\varepsilon_R = \varepsilon_R - i\hbar \gamma/2
+\end{equation}
+
+\subsection{I can get}
+\label{sec:I-can-get}
+
+\begin{equation}
+    \ket{\psi} = \sum_m \ket{\psi_m^L} + \ket{\psi_m^R}
+\end{equation}
+\begin{equation}
+    \frac{\partial }{\partial t}\braket{\psi|\psi}
+    = -\sum_m \gamma \braket{\psi^R_m|\psi^R_m}
+\end{equation}
+(All leakage from "R" site!)
+(draft page 1 to 2)
+
+\colorbox{red}{Strange:}
+\begin{equation}
+    \sum_m P_m = 1
+\end{equation} (draft page 3)
+\subsection{Result}
+\label{sec:Result}
+
+\begin{myquote} \enquote{
+we find that the average displacement
+of the particle during the course of its decay, $\Delta m =\sum_m mP_m$, 
+is exactly quantized as an integer (0 or 1 unit
+cells), where $P_m$ is the probability distribution for decay from
+different sites.
+
+As in the case of
+the quantum Hall conductance, this quantization results
+from an underlying topological structure; in this case it
+is the winding number of the relative phase between two
+components of the Bloch wave function.
+
+Using the topological origin of this phenomenon, we are able to show
+that the quantization is insensitive to parameters and is
+robust against certain types of noise and decoherence.
+
+The topological transition, which is accompanied by the formation of
+a non-decaying dark state, leads to a prediction of threshold-like
+pumping of nuclear polarization, along with strong suppression of
+current due to the divergence of dwell time at the threshold
+} \end{myquote}
+
+\begin{myquote} \enquote{
+our motivation is to provide a simple
+model of nuclear spin pumping in spin-blockaded double
+quantum dots [9, 10, 11] in the presence of competing
+effects of the hyperfine and spin-orbital interactions, as
+in Ref.[11].
+} \end{myquote}
 \section{Anchor}

### 2016-11-28 Basic Topology Notes/sections/ch5-fundamental-groups.tex
[minor] physicist-taper: add some symbols (N,E). [minor] Basic Topology: add the comb space example to homotopy type and stess not necessarily path-connected there. Clearify one todo about straight-line homotopy on S^n

@@
     \end{equation}
-    But why we are  % yes why! TODO
+    Notice that the ball $B^{n+1}$ is a convex set, so the numerator
+    lies inside the ball. When normalized (as in $F(x,t)$), the
+    numerator is a point on the sphere.
 \end{ex}
@@
 \end{fact}
-
+\begin{remark}
+    The topological spaces $X$ and $Y$ are not necessarily
+    path-connected! But we have:
+\end{remark}
+\begin{fact}
+    If $X$ and $Y$ have the same homotopy type then $X$ is
+    path-connected if and only if $Y$ is path-connected. (This is
+    noted in a footnote on page 107 of \cite{book}.)
+\end{fact}
 \begin{defi}[Deformation retraction]
@@
 \begin{thm}
-    If two path-connected spaces are of the same homotopy type, then
+    If two \hl{path-connected} spaces are of the same homotopy type, then
     they have isomorphic fundamental group.
@@
 \begin{fact}
-Using above fact, we can find that the M\"obius strip, the cylinder,
+Using the above fact, we can find that the M\"obius strip, the cylinder,
 the punctured plane $\E^2\setminus\{0\}$, and the solid torus, all
@@
 \begin{ex}
-    Here is a contractible space that is really hard to imagin. It is
+    Here is a contractible space that is really hard to imagine. It is
     called the topologist's dunce hat. It is formed by identifying the
@@
     \end{figure}
-    You may imagin identify a pair of sides, then identify the
+    You may imagine identifying a pair of sides, then identify the
     identitied edge to the resting side. The direction for identifying
@@
 \end{ex}
+
+\begin{remark}
+    An identity function $\id_X$ on a contractible space $X$
+    is homotopic to constant function $\id_p$ on a point $p\in X$. But
+    this homotopy may not keep the point $p$ fixed. That is, we do not
+    necessarily have $\id_X\cong\id_p$~rel $p$.
+
+    An example on page l08 of \cite{book}. In a space called
+    the topologist's comb:
+    \begin{align*}
+        K &= \{\frac{1}{n}|n\in\N\setminus\{0\}\} \\
+        \text{comb space}&=(\{0\} \times [0,1] ) \cup (K \times [0,1]) \cup ([0,1] \times \{0\})
+    \end{align*}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/comb-space.PNG}
+        \caption{Topologist's Comb (from Wikipedia)}
+    \end{figure}
+    We cannot continuously defrom the identity function $\id_X$ to the
+    constant function on $p=(0,1)$. Intuitively, there are infinite
+    points around $p$ that are infinitesimally close to it. But the
+    identity function must shrink from all these infinite points to
+    the base line $[0,1]$ without afftecting the value on $p$. This
+    sounds unlikely.
+
+    Analytically, the argument is provided by
+    \href{http://math.stackexchange.com/users/172604/pedro}{Pedro} in
+    his Math.SE
+    \href{http://math.stackexchange.com/a/952989/184811}{post}:
+
+    \begin{myquote} \enquote{
+        \textbf{Idea:} Take the sequence $x_n=(\frac{1}{n},1)$, it
+        converges to $x_0$. If existed such homotopy $H(x,t)$ then the
+        sequences $H(x_{n},t)$ would still converge to $x_{0}$.
+
+        You have for each neighborhood $U$ of $x_0$ a number
+        $N_{(U,t)}$ and $\epsilon_{(U,t)}$ such that $H(x_n,s)\in U$
+        for $n>N_{(U,t)}$ and $|t-s|<\epsilon_{(U,t)}$.
+
+        Covering the interval $I$ with
+        $(t-\epsilon_{(U,t)},t+\epsilon_{(U,t)})$ and taking a finite
+        subcover you obtain a number $N$ such that $H(x_n,t)\in U$ for
+        any $n>N$ and $t\in[0,1]$.
+
+        Now you can use disconnectedness of a small neighborhood to
+        show that the homotopy can't take the elements of the sequence
+        to $x_0$. 
+    } \end{myquote}
+\end{remark}

### 2016-11-30 Notes of Advanced Quantum Mechanics/Homeworks/161130/HW7_sol 11310075.tex
Add homework 7 for Advanced Quantum Mechanics.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\title{Solution for HW7}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
\begin{CJK}{UTF8}{gbsn}陈鸿翔（11310075）\end{CJK}
}
%\tableofcontents
\section{Prove}
\label{sec:Prove}
$$  [x,p^n] = in\hbar p^{n-1} $$

\begin{proof}
    \begin{align*}
        [x,p^n] &= p[x,p^{n-1}] + [x,p]p^{n-1} 
            = p[x,p^{n-1}]+i\hbar p^{n-1} \\
        &= p[x,p^{n-2}]+ i\hbar p^{n-1} + i\hbar p^{n-1} \\
        &\cdots \\
        &= ni\hbar p^{n-1}
    \end{align*}
\end{proof}
$$ [p,x^n] = -in\hbar x^{n-1} $$
\begin{proof}
\begin{align*}
    [p,x^n] &= x[p,x^{n-1}] + [p,x]x^{n-1} = x[p,x^{n-1}]  -i\hbar x^{n-1}
    \\
    &= x[p,x^{n-1}] -i\hbar x^{n-1} - i\hbar x^{n-1} \\
    &\cdots \\
    &= -in\hbar x^{n-1}
\end{align*}
\end{proof}

$$ [x,f(p)] = i\hbar \frac{\partial f(p)}{\partial p} $$
\begin{proof}
    Any smooth function of $p$ can be taylor-expanded into a series of
    the form $\sum_n c_n p^n$, since the commutator is linear and 
    $[x,p^n]=i\hbar np^{n-1}$, one see the result will be of the form
    $i\hbar \sum_n c_{n} n p^{n-1}$, which is exactly the expansion of
    the taylor expansion of $\frac{\partial f(p)}{\partial p}$. This
    observation concludes the proof.
\end{proof}

$$ [p,g(x)] = -i\hbar \frac{\partial f(x)}{\partial x} $$

\begin{proof}
    The proof is exactly the same of the one above, if one do a
    transformation $x\to p$, $p\to x$, and $i\to -i$.
\end{proof}

\section*{Problem 2}
\label{sec:Problem 2}
\begin{align}
    A=\left( \begin{array}{ccc}
         a & 0 & 0 \\
         0 & -a & 0 \\
         0 & 0 & -a \\
    \end{array} \right), B=\left( \begin{array}{ccc}
                             b & 0 & 0 \\
                             0 & 0 & \text{ib} \\
                             0 & -\text{ib} & 0 \\
                        \end{array} \right)
\end{align}
The eigenvalues of $A$ are obviously $a,-a,-a$. The eigenvalues of $B$
is found by characteristic equations $\mathrm{Det}(B-\lambda \id)=0$ to be
$\{-b,b,b\}$. So $B$'s spectrum is degenerate too.

It can be found that
\begin{equation*}
    AB = \left( \begin{array}{ccc}
         a b & 0 & 0 \\
         0 & 0 & -i a b \\
         0 & i a b & 0 \\
        \end{array} \right), \\
    BA = \left( \begin{array}{ccc}
         a b & 0 & 0 \\
         0 & 0 & -i a b \\
         0 & i a b & 0 \\
        \end{array} \right), \\
\end{equation*}

The eigenvectors of $A$ are easy to guess, they are
just the three natural basis $\{e_1,e_2,e_3\}$.

It is easy to find (by solving $BX=\lambda_i X$) $B$'s eigenvectors:
$$
\begin{pmatrix}
    1\\ 0\\ 0
\end{pmatrix}
\begin{pmatrix}
    0\\ -i\\ 1
\end{pmatrix}
\begin{pmatrix}
    0\\ i\\ 1
\end{pmatrix}
$$
Since both are degenerate, we can linearly combine the degenerate
eigenvectors of $A$ to form that of $B$, but since $A$'s eigenvectors
are natural basis, and in the only non-degenerate case, the two matrix
share the same eigenvector (notice also that those degenerate
eigenvectors of $B$ does not "mess up" with the non-degenerate
eigenvector). So we do not have to do anything and those
$B$'s eigenvectors will also diagolize $A$. They are the required
eigenvectors.
\end{document}

### 2016-12-01 Basic Topology Notes/sections/ch5-fundamental-groups.tex
New Basic Topology Notes: about triangulation technique.

@@
     continuous maps into $\mathbb{E}^{n+1}$, then we may form a
-    straight-line homotopy from $f$ to $g$ by:
+    similar "straight-line homotopy" from $f$ to $g$ by:
     \begin{equation}

### 2016-12-01 Basic Topology Notes/sections/ch6-Triangulation.tex
New Basic Topology Notes: about triangulation technique.

\subsection{Section 6.1 Triangulating Spaces}
\label{sec:Triangulating-Spaces}

He gave to examples first,
\begin{ex}
    A trivial example:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/ch6-scanned-notes-1/ex1.pdf}
    \end{figure}
\end{ex}
\begin{ex}
    A non trivial one. That is, the M\"obius Strip also has the
    homotopy type of a ciclr $S^1$.
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/ch6-scanned-notes-1/ex2.pdf}
    \end{figure}
\end{ex}
But for complicated spaces, its homotopy type will not be so easy to
calculate in with simple imagination. Here we will introduce a new
technique to actually calculate the homotopy type of topological
spaces.

The technique is called Triangulation. The most visual example comes
from the computer vision technology (though I cannot find a picture by
directly Googling triangulation). The idea we wants to stress is that
the Triangulation is like use small patches of triangles to patch and
cover the surface of 3D smooth objects. Increase the overall number of
patches and make each patch get smaller. In the limit of this process
one might get to recover the original image.

\begin{defi}[Simplex of $\dim k$]
\nomenclature{Simplex of $\dim k$}{\nomrefpage.}
    The stanford simplex of $\dim k$ in $R^{k+1}$ is defined as
    follows. Let $v_i=(0,\cdots,0,1,0,\cdots 0)$, where $1$ is in $i+1$
    coordinates. That is:
    $$ v_0=(1,0,\cdots)$$
    $$ v_1=(0,1,0\cdots)$$
    $$\cdots$$
    $$ v_0=(0,\cdots,0,1)$$
    Then the simplex is the smallest convex set containing
    $\{v_0,\cdots,v_k\}$ in $\R^{k+1}$. It is also called a
    \nomen{$k$-simplex}.
\end{defi}
\begin{ex}
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/ch6-scanned-notes-1/ex3.pdf}
    \end{figure}
\end{ex}
\begin{fact}
    Any point in a $k$-simplex is of the form:
    \begin{equation}
        \lambda_0 v_0 + \lambda_1 v_1 + \cdots + \lambda_k v_k
    \end{equation}
    where each $\lambda_i\geq 0$, and $\sum_{i=0}^{k} \lambda_k=1$.
\end{fact}
\begin{ex}
    There is a special point in the $k$-simplex:
    \begin{equation}
        \frac{1}{k+1} \sum_{i=0}^k v_i
    \end{equation}
    When $k=2$, this is just the usual center of gravity of triangle.
\end{ex}

We want to study those space which is the union of a finite collection
of simplexes which fit together nicely in some Euclidean space. These
are called "triangulable spaces". More specifically:
\begin{defi}[faces]
\nomenclature{faces}{\nomrefpage.}
    If $A$ and $B$ are simplexes, and if the vertices of $B$ form a
    subset of vertices of $A$. Then $B$ is called a face of $A$,
    written as \nomen{$B<A$}.
\end{defi}
\begin{defi}[Simplicial Complex]
\nomenclature{Simplicial Complex}{\nomrefpage.}
    A \textbf{finite} collection of simplexes in some Euclidean space
    in $\R^n$ is called a simplicial complex, if
    \begin{enumerate}
        \item whenever a simplex lies in this collection, then so does
            its faces
        \item whenever two simplexes in this collection intersect,
            their intersection is a common face of these two
            simplexes.
    \end{enumerate}
\end{defi}
\begin{ex}
    % ex 4
\end{ex}
\begin{defi}[Topology on simplicial complex]
\nomenclature{Topology on simplicial complex}{\nomrefpage.}
    The topology on a simplicial complex is given by the subspace
    topology of Euclidean space. Let $K$ be a simplicial complex, we
    denote \nomen{$|K|$} as the topology of $K$. This $|K|$ is called
    a \nomen{polyhedron}.
\end{defi}

\begin{defi}[Triangulation and Triangulable]
\nomenclature{Triangulation and Triangulable}{\nomrefpage.}
    A triangulation on a topological space $X$ consists of a
    simplicial complex $K$, and a homeomorphism $h$:
    $$ h:|K|\to X$$
    A space is called triangulable if such simplicial complex $|K|$
    and homeomorphism $h$ exists.
\end{defi}
\begin{fact}
    If $X$ is triangulable, then $X$ is compact and can be made into a
    metric space. (Notice that the simplicial complex is a finite
    collection.)
\end{fact}
\begin{remark}
    Trigulation is in general not unique. For example:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/ch6-scanned-notes-1/rmk2}
    \end{figure}
\end{remark}
\begin{ex}
    Here is a triangulation on the torus:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/ch6-scanned-notes-1/p5.pdf}
    \end{figure}
    Notice that the following diagram is not a triangulation of torus:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/ch6-scanned-notes-1/p52.pdf}
    \end{figure}
\end{ex}
\begin{lemma}
    Let $K$ be a simplicial complex in $\R^{n}$, then
    \begin{enumerate}
        \item $|K|$ is compact.
        \item Each point of $|K|$ lies in the interior of exactly one
            simplex of $K$.
        \item If we take the simplexes of $K$ seperately, and give
            their union the identification topology, we obtain $|K|$.
            Thus we have two equivalent ways to view the topology on
            $K$.
        \item If $|K|$ is connected, then $|K|$ is also
            path-connected.
    \end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}
    \item Obviously.
    \item Since $K$ is connected by simplexes, a point $p$ must
        obviously be contained in some simplex. Also, since on each
        simplex $p$ must be on the interior of it, or interior of its
        components. We only need to prove that the containing simplex
        is unique. Suppose $p$ is the interior of simplexes $A$ and
        $B$. Notice that their intersection must be their faces. The
        only face of $A$ or $B$ containing interior points is $A$ or
        $B$ itself. Hence $A=B$.
    \item By definition of identification topology, we can see that in
        the identified space, a subset $C\subset |K|$, $C$ is closed
        $\Leftrightarrow$ $C\cap |A|$ is closed in $|A|$ for all
        simplexes $A\in K$. The rest of the proof is obvious.
    \item We need only to show that $|K|$ is locally path-connected.
        But any point $p\in K$, $p\in$ interior of some $A$ where
        $A\in K$. That is, we can find a neighbourhood $U$ of $p$, and
        $U$ is contained in $A$ ($U\subset A$). (More specifically, we
        can find $\varepsilon$ such that 
        $B_{\varepsilon}(p)\cup |K| = B_\varepsilon(p)\cup |A|$)
        But a simplex $A$ is obviously locally path-connected. Hence
        $U$ (or $B_\varepsilon(p)$) is path connected, hence $|K|$ is
        path-connected.
\end{enumerate}
\end{proof}

\subsection{Section 6.2 Barycentric Division}
\label{sec:Barycentric-Division}
Now we begin to make the triangulation more and more detailed. We
start from a simplicial complex $K$ and constructing a new simplicial
complex $K_1$, such that
\begin{enumerate}
    \item $|K|=|K_1|$, homeomorphically.
    \item diameter $|K_1|<$ diameter $|K|$.
\end{enumerate}
The general construction method is called Barycentric division,
visualized as:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/ch6-scanned-notes-1/8.pdf}
\end{figure}
We first define a concept
\begin{defi}[$\hat{A}$ Bary center]
\nomenclature{$\hat{A}$ Bary center}{\nomrefpage.}
Let $A$ be a simplex, then the bery center of $A$, denoted $\hat{A}$,
is the point:
\begin{equation}
    \hat{A}:= \frac{1}{k+1}(v_0+\cdots+v_k)
\end{equation}
\end{defi}
Then, the general process is:
The new space $K_2$ is such that
\begin{enumerate}
    \item The vertices of $K_1$ are bary centers of \textbf{ALL}
        simplexes of $K$. Note the the bary center of a $0$-simplex
        is just itself. So in general, $K_1$ has more vortices of
        $K$.
    \item A collection $\hat{A}_0,\cdots,\hat{A}_k$ of such bary
        centers will form a vortex of a $k$-simplex in $K_1$ if and
        only if there is a permutation $\sigma$ of $\{0,1,\cdots,k\}$
        such that
        \begin{equation}
            A_{\sigma{0}}< A_{\sigma{1}} < \cdots < A_{\sigma{k}}
        \end{equation}
\end{enumerate}
\begin{remark}
    The second point above tries to do the following
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.9\linewidth]{pics/ch6-scanned-notes-1/p9.pdf}
    \end{figure}
\end{remark}

### 2016-12-07 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/notes.tex
[major]Finish the first version of this notes. There are two arguments that I donot understand.

@@
 \begin{align}
+    \begin{aligned}
+        \label{eq:eq-of-motion}
     i\hbar \dot{\psi}^L_m = \varepsilon_L\psi^L_m + v\psi^R_m
@@
     +v'\psi^L_{m-1}
+    \end{aligned}
 \end{align}
@@
 \end{equation}
+
+\textbf{Important Note}: Through out the text we use $m$ as an
+abbreviation of $R_m$. So $\psi_m$ means $\psi(R_m)$, $e^{ikm}$ means
+$e^{ikR_m}$, and quite decivingly, $e^{ik}$~actually is $e^{ikR_1}$.
 
@@
 } \end{myquote}
+
+\section{Calculation}
+\label{sec:Calculation}
+
+The system starts with the initial state:
+\begin{equation}
+    \psi^L_m = \delta_{m,0},\quad \psi^R_m = 0
+\end{equation}
+
+It evolves according to the following equation of motion
+\ref{eq:eq-of-motion}:
+\begin{align*}
+    \begin{aligned}
+    i\hbar \dot{\psi}^L_m = \varepsilon_L\psi^L_m + v\psi^R_m
+    +v'\psi^R_{m+1} \\
+    i\hbar \dot{\psi}^R_m = \tilde{\varepsilon}_R\psi^R_m + v\psi^L_m
+    +v'\psi^L_{m-1}
+    \end{aligned}
+\end{align*}
+
+The paper seeks to find the following:
+\begin{align}
+    \braket{\Delta m} &:= \sum_m m P_m \\
+    P_m &:= \sum_0^\infty \gamma\abs{\psi^R_m(t)}^2 \dd t
+    \label{eq:pm-def}
+\end{align}
+The result can be obtained both numerically and analytically. First,
+the author provides an analytical solution.
+
+\subsection{Analytical Solution}
+\label{sec:Analytical-Solution}
+
+\subsubsection{First observation}
+\label{sec:First-observation}
+
+The first thing the author points out is that:
+\begin{equation}
+    \frac{\partial }{\partial t}\abs{\psi}^2
+    = \frac{\partial }{\partial t}  \braket{\psi|\psi} \neq 0
+\end{equation}
+This is caused by one fundamentabl rule of inner product:
+\begin{equation}
+    \frac{\partial }{\partial t}\braket{f|g} = 
+    \braket{\frac{\partial f}{\partial t}|g} +
+    \braket{g| \frac{\partial f}{\partial t}}
+\end{equation}
+The evolution of kets is determined by Schordinger's equation, the
+evolution of bras is determined by conjugating the Schordinger's
+equation. Thus, it is easy to see:
+\begin{equation}
+    \label{eq:pt-norm-1}
+    i\hbar \frac{\partial }{\partial t}\abs{\psi}^2 =
+    i\hbar \frac{\partial }{\partial t}\braket{\psi|\psi} =
+    \bra{\psi} H-H^\dagger \ket{\psi}
+\end{equation}
+Applying the above rules here, we easily find (notice the only
+non-hermitian term in the equation of motion \ref{eq:eq-of-motion} is
+$\tilde\varepsilon_R = \varepsilon_R -i\hbar \gamma/2$, so
+$H-H^\dagger$ is 
+$\tilde\varepsilon_R-\tilde\varepsilon_R^*=-i\hbar\gamma$. This also
+explains why author choose $\gamma/2$ in $\tilde\varepsilon_R$,
+instead of $\gamma$. Thus we have
+\begin{align}
+    \label{eq:pt-norm-2}
+    \frac{\partial }{\partial t}\braket{\psi^R_m|\psi^R_m} = 
+    -\gamma \braket{\psi^R_m|\psi^R_m}
+\end{align}
+For the $L$ sites, the Hamiltonian is hermitian and thus
+\begin{align}
+    \frac{\partial }{\partial t}\braket{\psi^L_m|\psi^L_m} = 0
+\end{align}
+
+Counting them together, we let
+\begin{equation}
+    \ket{\psi} = \sum_m \ket{\psi^R_m} + \ket{\psi^L_m}
+\end{equation}
+and find
+\begin{equation}
+    \frac{\partial }{\partial t}\abs{\psi}^2 =
+    \frac{\partial }{\partial t}\braket{\psi|\psi} =
+    - \sum_m \gamma\braket{\psi^R_m|\psi^R_m}
+\end{equation}
+
+But he the author asserts
+\begin{equation}
+    \sum_m P_m = 1
+\end{equation}
+If we perceive that $P_m$ are probabilities, then the above equation
+seems logical. But if I write down the formula (by eq \ref{eq:pm-def}):
+\begin{equation}
+    \sum_m P_m = \sum_m \int_0^\infty \gamma\braket{\psi^R_m|\psi^R_m}
+    \overset{?}{=}1
+\end{equation}
+Then the result is not so obvious.\label{confusion:1}
+
+\subsubsection{Pass to momentum space}
+\label{sec:Pass-to-momentum-space}
+
+The basic technique is fourier expansion
+\begin{equation}
+    \psi = \frac{1}{2\pi} \oint \dd{k} e^{ikm}\psi^R_m
+\end{equation}
+So the equation of motion \ref{eq:eq-of-motion} become:
+\begin{align*}
+    i\hbar \frac{\partial }{\partial t}\frac{1}{2\pi}
+    \oint \dd{k} e^{ikm} \psi^L_k 
+    =\frac{1}{2\pi} \oint \dd{k}  
+    \left( \varepsilon_L e^{ikm}\psi^L_k
+    + v e^{ikm}\psi^R_k + v' e^{ik(m+1)}\psi^R_k \right)
+\end{align*}
+similar to the other for $\psi^R_m$.  
+The two equations can be simplified to (comparing the terms inside
+integration):
+
+\begin{align}
+    \label{eq:eq-of-motion-in-k}
+    \begin{aligned}
+    i\hbar \dot{\psi}^L_k = \varepsilon_L\psi^L_k + v\psi^R_k
+    +v' e^{ik} \psi^R_k \\
+    i\hbar \dot{\psi}^R_k = \tilde{\varepsilon}_R\psi^R_k + v\psi^L_k
+    +v'e^{-ik}\psi^L_{k}
+    \end{aligned}
+\end{align}
+
+Or in matirx form:
+\begin{equation}
+    \label{eq:eq-of-motion-in-k-mat}
+    i\hbar \frac{\partial }{\partial t}
+        \begin{pmatrix}
+            \psi^L_k \\ \psi^R_k
+        \end{pmatrix}
+        =
+        \begin{pmatrix}
+            \varepsilon_L & A_k \\
+            A_k^* & \tilde\varepsilon_R
+        \end{pmatrix}
+        \begin{pmatrix}
+            \psi^L_k \\ \psi^R_k
+        \end{pmatrix}
+\end{equation}
+where $A_k:=v+v'e^{ik}$, and we have asumed $v,v'\in\R$. This is
+Eq.(4) in the paper, and can be viewed as an Schordinger's equation in
+the momentum space, with $H(k)$ the matrix on the right-hand-side.
+
+By exactly the same technique described from Eq.~\ref{eq:pt-norm-1} to
+Eq.~\ref{eq:pt-norm-2}, we can get:
+\begin{align*}
+    i\hbar\frac{\partial }{\partial t}\braket{\psi^L_k|\psi^L_k} &= 0
+    \\
+    i\hbar\frac{\partial }{\partial t}\braket{\psi^R_k|\psi^R_k} &= 
+        -\gamma\braket{\psi^R_k|\psi^R_k}
+\end{align*}
+
+So (let $p_k(t):=\abs{\psi^L_k(t)}^2+\abs{\psi^R_k(t)}^2$):
+\begin{equation}
+    \frac{\partial }{\partial t}p_k = -\gamma\abs{\psi^R_k(t)}^2
+    \label{eq:pt-pk}
+\end{equation}
+
+Notice
+\begin{equation*}
+    -\frac{i}{2\pi}\oint \dd{k} 
+    \frac{\partial }{\partial k}(e^{ikm})\ket{\psi^R_k}
+    =-i (im) \frac{1}{2\pi}\oint\dd{k} e^{ikm}\ket{\psi^R_k}
+    =m\ket{\psi^R_m}
+\end{equation*}
+
+Then
+\begin{align*}
+    m\ket{\psi^R_m} &= -i \frac{1}{2\pi}\oint\dd{k}
+    \frac{\partial }{\partial k}(e^{ikm})\ket{\psi^R_k}
+    \\
+    &=-i\frac{1}{2\pi}\left(
+        \eval{e^{ikm}\ket{\psi^R_k}}_{\partial\textrm{BZ}}
+        -\oint\dd{k} e^{ikm}\frac{\partial }{\partial k}\ket{\psi^R_k}
+    \right)
+    \\
+    &= i\frac{1}{2\pi}\oint\dd{k}e^{ikm}\frac{\partial }{\partial k}
+    \ket{\psi^R_k}
+\end{align*}
+Hence
+\begin{align}
+    \braket{\Delta m} &= \sum_m m\int_0^\infty
+    \gamma\braket{\psi^R_m|\psi^R_m} 
+    = \sum_m \int_0^\infty \gamma
+    \bra{\psi^R_m} m\ket{\psi^R_m} \dd t
+    \\
+    &= \sum_m \int_0^\infty \gamma
+    \left(\frac{1}{2\pi}\oint\dd{k} e^{-ikm}\bra{\psi^R_k}\right)
+    i\frac{1}{2\pi}\oint\dd{k'}e^{ik'm}\frac{\partial }{\partial k}
+        \ket{\psi^R_k} \\
+    &= \sum_m \int_0^\infty \gamma
+    \frac{i}{(2\pi)^2}\oint\dd{k}\dd{k'} e^{i(k'-k)m}
+    \bra{\psi^R_k}\frac{\partial }{\partial k}\ket{\psi^R_k}
+\end{align}
+Noticing
+\begin{equation}
+    \sum_m e^{i(k'-k)m} = \delta(k'-k)\frac{(2\pi)^d}{v}
+\end{equation}
+where $v$ is the volumn of the primitive cell in real lattice and $d$
+is the dimention of the real lattice.
+So
+\begin{align}
+    \braket{\Delta m}
+    &= \int_0^\infty \frac{i\gamma}{2\pi v}
+    \oint\dd{k} \bra{\psi^R_k}
+        \frac{\partial }{\partial k}\ket{\psi^R_k}
+\end{align}
+This same of Eq.(5) in the paper except a constant $v$.
+\label{confusion:2}.
+
+Next he sets $\ket{\psi^R_k}=u_k(t)e^{i\theta_k(t)}$, where $u$ is the
+length and $\theta$ is the angle, of $\ket{\psi^R_k}$.
+
+The author notes in [18] that the $u_k(t)>0$ for $t>0$, but this is
+obvious from Eq.\ref{eq:pt-pk}, which is translated into
+\begin{equation}
+    \frac{\partial }{\partial t}(u_k)^2 = -\gamma (u_k)^2
+\end{equation}
+Thus $(u_k)^2$ is an exponential function, which is always positive
+unless the initial condition is $0$.
+
+Note
+\begin{equation}
+    \oint\dd{k} u_k\partial_k u_k 
+    = \frac{1}{2}\oint\dd{k}\partial_k (u_k)^2 =
+    \frac{1}{2}\eval{(u_k)^2}_{\textrm{\tiny two points of the same value}} = 0
+\end{equation}
+Then
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/eq7.pdf}
+\end{figure}
+so
+\begin{equation}
+    \braket{\Delta m}=\oint\frac{\dd{k}}{2\pi}\int_0^\infty\dd{t}
+    (\frac{\partial p_k}{\partial t})
+    (\frac{\partial \theta_k(t)}{\partial k})
+\end{equation}
+This is Eq.7 in the paper, except that I have ignored the $\frac{1}{v}$
+difference between my result and the paper's. Then it is straight
+forward to obtain
+\begin{equation}
+    \braket{\Delta m} = \mathcal{I}_0 - \int_0^\infty\dd{t}
+    \oint\frac{\dd{k}}{2\pi} p_k \partial_t (\partial_k \theta_k)
+    \label{eq:m-I0-int}
+\end{equation}
+where
+\begin{equation}
+    \mathcal{I}_0 = \oint\frac{\dd{k}}{2\pi} \left(p_k
+    \eval{\frac{\partial \theta_k}{\partial k}}_{t=0}^\infty\right)
+\end{equation}
+Now the second term in eq.\ref{eq:m-I0-int} can be turned into
+(assuming $\theta_k(t)$ is smooth so that order of differentiation
+does not matter).
+\begin{equation}
+    - \int_0^\infty\dd{t}
+    \oint\frac{\dd{k}}{2\pi} p_k \partial_t (\partial_k \theta_k)
+    =
+    \int_0^\infty\dd{t}
+    \oint\frac{\dd{k}}{2\pi} 
+    \frac{\partial p_k}{\partial k}
+    \frac{\partial \theta_k}{\partial t}
+    \label{eq:to-be-0}
+\end{equation}
+This is eq.(9) in the paper.
+
+\subsubsection{Arguing that the Integration \ref{eq:to-be-0} is zero}
+\label{sec:Argument-1}
+
+Now the author tries to argue that $p_k$ and $\partial_t\theta_k$ are
+even functions of $k$, so that the integration \ref{eq:to-be-0} is $0$.
+I cannot follow his argument
+\label{confusion:3}. But I find another model, which can found on
+\href{https://en.wikipedia.org/wiki/Rabi_cycle}{Wikipedia - Rabi
+Cycle}. The Rabi Cycle model can be applied only when $\gamma=0$, i.e.
+there is no dissipation. But since the formulae above are continues,
+if the integration $p_k$ and $\partial_t\theta_k$ are even, then they
+should be even when $\gamma=0$, unless some very strange singular
+behavior exist.
+
+\paragraph{$\gamma=0$ case using Two-level system model}$ $
+
+Suppose we have a Hermitian Hamiltonian (let
+$\{E_0,W_1,W_2,\Delta\}\subset\R$):
+\begin{equation}
+    H = E_0\id + W_1\sigma_1+W_2\sigma_2+\Delta\sigma_3 
+    = \begin{pmatrix}
+        E_0 + \Delta & W_1-iW_2 \\
+        W_1+iW_2 & E_0 - \Delta
+    \end{pmatrix}
+\end{equation}
+
+Supose the system starts at $\ket{\psi(0)}= \begin{pmatrix}
+    1\\0
+\end{pmatrix}$, then its time evolution will be (Set $\hbar=1$.
+Calculation is done in the Wikipedia page, and is checked myself.):
+\begin{equation}
+    \label{eq:time-evolve-rabi}
+    \ket{\psi(t)} = \cos(\theta/2)e^{-iE_+ t}\ket{E_+} - \sin(\theta/2)
+    e^{-i\phi}e^{-iE_- t}\ket{E_-}
+\end{equation}
+where $\ket{E_+}=e^{i\phi/2} \begin{pmatrix}
+    \cos(\theta/2) \\ e^{-i\phi}\sin{\theta/2}
+\end{pmatrix}$ and $\ket{E_-}= \begin{pmatrix}
+    -e^{i\phi}\sin(\theta/2) \\ \cos(\theta/2)
+\end{pmatrix}$ are orthonormal eigenkets, and
+\begin{align}
+\begin{aligned}
+    &W:= W_1+iW_2,\quad
+    E_{\pm} = E_0\pm \sqrt{\Delta^2+\abs{W}^2}\\
+    &\sin(\theta):= \frac{|W|}{\sqrt{\Delta^2+\abs{W}^2}},\,
+    \cos(\theta):= \frac{\Delta}{\sqrt{\Delta^2+\abs{W}^2}},\,
+\end{aligned}
+\end{align}
+$\phi$ is such that $W=\abs{W}e^{-i\phi}$.
+
+Here for this paper. Let us suppose for the moment $\gamma=0$, then we
+see that $W=A_k^*$, so $W_1 = v+v'\cos{k}$, $W_2=-v'\sin{k}$. 
+Also $E_0$ and $\Delta$ are linear combination of
+$\varepsilon_R$ and $\varepsilon_L$:
+\begin{equation}
+    E_0 =\frac{\varepsilon_R+\varepsilon_L}{2},\quad
+    \Delta =\frac{\varepsilon_R-\varepsilon_L}{2}
+\end{equation}
+The system still starts with
+$\ket{\psi(0)}$ (since $\psi^L_k(0)=1,\,\psi^R_k(0)=0$). The time
+evolved state still follows eq.\ref{eq:time-evolve-rabi}, where the
+dependence on $k$ lies in $\sin(\theta),\cos(\theta),$ and $\phi$.
+Then by definition, $p_k=\abs{\ket{\psi(t)}}^2$, $u_k(t)$ is the second
+component of $\ket{\psi(t)}$.
+
+I was doubtful of the fact that $p_k$ is even in $k$, so I did a
+numerical check (see file
+"{OneD\_quantum\_walk\_test\_even\_functions\_pk\_uk.m}"), and
+unfortunately my guess seems to be wrong. I have given arbitrary
+numbers to time $t$, $v$, $v'$, energies $\varepsilon_R$ and
+$\varepsilon_L$, and the resulted $p_k$ is always even in $k$, the
+resulted $u_k$ is always constantly $0$ in both time variable $t$ and $k$.
+
+This motivates me to calculate it analytically. The results is
+contained in files \\
+"\texttt{Elementary Calculation of Time Evolution in Two-level model.nb}"
+
+and\\
+"\texttt{Elementary Calculation to get pk and uk from Two-Level
+model.nb}".
+
+(their pdf version files are also included)
+
+The result is that I can understand $p_k$ is even in $k$, but I cannot
+see why $\partial_t u_k$ because its calculation involves getting the
+angle of a complex number, which has not good analytical expressions.
+
 \section{Anchor}

### 2016-12-07 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/files/OneD_quantum_walk_test_even_functions_pk_uk.m

@@ -1,0 +1,104 @@
+% Purpose: Do a numerical calculation to test the result
+%          about p_k and u_k when gamme=0, i.e. no dissipation.
+% version: 20161209-1
+% Description:
+% The result is obtained using exact solution using Rabi Cycle (Wikipedia)
+% formulae. The answer may be numerically incorrect because I need to
+% calculate a theta, which is Arcsin(of something) or Arccos(of something 
+% else). Unsurprisingly, the two result does not agree sometimes.
+clear all;
+v=rand()*10;
+v1=rand()*10;
+Er=rand()*10;
+El=rand()*10;
+
+% First test pk in an arbitrary time
+t=rand()*10;
+index=0;
+k_range=-pi:0.05:pi;
+for k= k_range
+    index = index+1;
+    W=conj(v+v1*exp(1i*k));
+    E0= (Er+El)/2;
+    Delta=(Er-El)/2;
+
+    sin_t=abs(W)/sqrt(Delta^2+abs(W)^2);
+    cos_t=Delta/sqrt(Delta^2+abs(W)^2);
+    theta=asin(sin_t);
+    Indication_of_goodness=asin(sin_t)-acos(cos_t);
+    if Indication_of_goodness > 2*pi*1/360
+    	sprintf('Bad result when getting the angle. The angle differ by ... %0.5e',Indication_of_goodness);
+        pause;
+    end;
+    eiphi=conj(W/abs(W));
+    emiphi=W/abs(W);
+    Ep=E0+sqrt(Delta^2+abs(W)^2);
+    Em=E0-sqrt(Delta^2+abs(W)^2);
+
+    ket_Ep=zeros(2,1);
+    ket_Ep(1)=eiphi*cos(theta/2);
+    ket_Ep(1)=sin(theta/2);
+    ket_Em=zeros(2,1);
+    ket_Em(1)=-eiphi*sin(theta/2);
+    ket_Ep(1)=cos(theta/2);
+
+    psi=zeros(2,1);
+    psi(1)=cos(theta/2)*exp(-1i*Ep*t)*ket_Ep(1)- ...
+            sin(theta/2)*emiphi*exp(-1i*Em*t)*ket_Em(1);
+    psi(2)=cos(theta/2)*exp(-1i*Ep*t)*ket_Ep(2)- ...
+            sin(theta/2)*emiphi*exp(-1i*Em*t)*ket_Em(2);
+    pk(index)=psi'*psi;
+end;
[…]

### 2016-12-08 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/notes.tex
[minor]Add a sample output for the numerical test of $p_k$ and $u_k$

@@
 $\varepsilon_L$, and the resulted $p_k$ is always even in $k$, the
-resulted $u_k$ is always constantly $0$ in both time variable $t$ and $k$.
+resulted $u_k$ is always constantly $0$ in both variables $t$ and $k$.
+So $\partial_t u_k$ is trivially even in $k$. Below are to typical
+outputs:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/Sample-output-for-p_k.eps}
+    \caption{Sample output for $p_k$}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/Sample-output-for-u_k.eps}
+    \caption{Sample output for $u_k$}
+\end{figure}
 

### 2016-12-08 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/files/OneD_quantum_walk_test_even_functions_pk_uk.m

@@ -50,6 +50,7 @@ for k= k_range
     pk(index)=psi'*psi;
 end;
 plot(k_range,pk);
+xlabel('k'); ylabel('p_k');
 title('Testing p_k');
 
 % Then test uk in both two dimension (t,k)
@@ -100,5 +101,5 @@ end
 X=transpose(X); Y=transpose(Y);
 figure;
 mesh(X,Y,uk);
-xlabel('t');ylabel('k');
+xlabel('t');ylabel('k');zlabel('u_k');
 title('Test u_k');

### 2016-12-11 Basic Topology Notes/sections/ch6-Triangulation.tex
[major] new note for topology: simplicial approximation theorem

@@
 Then, the general process is:
-The new space $K_2$ is such that
+The new space $K_1$ is such that
 \begin{enumerate}
@@
         simplexes of $K$. Note the the bary center of a $0$-simplex
-        is just itself. So in general, $K_1$ has more vortices of
+        is just itself. So in general, $K_1$ has more vertices of
         $K$.
     \item A collection $\hat{A}_0,\cdots,\hat{A}_k$ of such bary
-        centers will form a vortex of a $k$-simplex in $K_1$ if and
+        centers will form a vertex of a $k$-simplex in $K_1$ if and
         only if there is a permutation $\sigma$ of $\{0,1,\cdots,k\}$
@@
 \end{remark}
+
+Now we give a precise description of how this Bary center division
+will work. We first describe precisely two characteristics of a
+simplicial complex.
+
+\begin{defi}[dimension of a simplicial complex]
+\nomenclature{dimension of a simplicial complex}{\nomrefpage.}
+    The dimension of a simplicial complex $K$ is the maximum of the
+    dimensions of all its simplexes.
+\end{defi}
+\begin{defi}[mesh $\mu(K)$]
+\nomenclature{mesh $\mu(K)$}{\nomrefpage.}
+    The mesh of a simplicial complex $K$ is the maximum of the
+    diameters of all its simplexes.
+\end{defi}
+
+As we expected, the mesh (which carries the intuition of the smallness
+of one simplicial complex) of a simplicial complex will decrease. The
+following lemma confirmed this.
+
+\begin{lemma}
+    The sollection of simplexes described above forms a simplicial
+    complex. If it is denoted by $K^1$, and is called the first
+    barycentric subdivision of $K$, then $K^1$ has the following
+    properties:
+    \begin{enumerate}
+        \item each simplex of $K^1$ is contained in a simplex of $K$;
+        \item Their topology are the same: $|K^1|=|K|$
+        \item If the dimension of $K$ is $n$, then
+            \begin{equation}
+                \mu(K^1)\leq \frac{n}{n+1}\mu(K)
+            \end{equation}
+    \end{enumerate}
+\end{lemma}
+\begin{proof}
+    The proof can be found in page 126 to 127 of \cite{book}. But the
+    proof of the last point is not so clear and is illustrated here:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\linewidth]{pics/ch6-notes-2/explain1.pdf}
+\end{figure}
+\end{proof}
+\begin{remark}
+    Notice that the number $\frac{n}{n+1}<1$, hence after an infinite
+    number of Barycentric subdivision, the mesh (averaged diameter) of
+    a simplicial complex $K^m$ will goes to zero!
+\end{remark}
+\subsection{Section 6.3 Simplicial approximation}
+\label{sec:Simplicial-approximation}
+
+The purpose here is to approximate any continuous map $f:A\to B$ with
+linear map, in a way that is compatible with the triangulations on
+both $A$ and $B$.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.4\linewidth]{pics/ch6-notes-2/exp2.png}
+\end{figure}
+\begin{defi}[Simplicial map]
+\nomenclature{Simplicial map}{\nomrefpage.}
+    Let $K$ and $L$ be simplicial complexes. A continuous map $s:K\to
+    L$ is called simplicial, if it takes simplexes of $K$
+    \textit{linearly} to simplexes of $L$. Specifically, being
+    \textit{linear} means that:
+
+    For $\forall A\in K$, we have $B=s(A)\in L$. Also, if
+    $A=\{v_0,\cdots,v_k\}$, then $B=\{s(v_0),\cdots,s(v_k)\}$.
+    Lastly, if $x=\sum_{i=0}^k \lambda_i v_i$ is a a point in $A$, with
+    $\lambda_i\geq 0$ and $\sum_{i=0}^k\lambda_i=1$, then
+    $$s(x) = \sum_{i=0}^k \lambda_i s(v_i)$$
+
+    In a word, $s$ maps simplexes to simplexes, vertices, to vertices,
+    and points linearly to points.
+\end{defi}
+\begin{remark}
+    It is easy to see that the a simplicial map is uniquely determined
+    by its value on all the vertices. By this, there can only be a
+    finite number of such kind of maps, since there are only a finite
+    number of vertices.
+\end{remark}
+
+Now we want to find such linear maps to approximate a give function
+$f:|K|\to |L|$. Given a point $x\in |K|$, we define the
+\nomen{carrier of $f(x)$} to be the unique simplex of $L$ that contain
+$f(x)$ as its interior point.
+
+\begin{defi}[Simplicial Approximation]
+\nomenclature{Simplicial Approximation}{\nomrefpage.}
+    A simplicial map $s:|K|\to |L|$ is called a simplicial approximation of
+    $f:|K|\to |L|$ if and only if $s(x)\in$ carrier of $f(x)$,
+    $\forall x\in |K|$.
+\end{defi}
+\begin{ex}
+    Trivial examples:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/ch6-notes-2/ex3.png}
+\end{figure}
+\end{ex}
+\begin{ex}
+    Now we show that when simplicial approximation does not exits. The
+    set up is as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/ch6-notes-2/ex4.png}
+    \end{figure}
+    Hence, there is no simplicial approximation of $f$. But, it will
+    be shown below that, if we divide $K$ small enough
+    ($K^1,K^2,\cdots$), we will eventually be able to find a
+    simplicial approximation of $f$ in some $K^n$.
+\end{ex}
+
+\begin{thm}[Simplicial approximation theorem]
+    \label{thm:SAT}
+    Let $f:|K|\to |L|$ be a continuous map between polyhedras formed
+    by simplicial complexes $|K|$ and $|L|$. If $m$ is chosen large
+    enough, then there is a simplicial approximation $s:|K^m|\to|L|$
+    to $f:|K^m|\to|L|$.
+\end{thm}
+The proof will use a lemma. Define the \nomen{open star} $v$ of a
+simplicial complex $K$, as the union of the interiors of those
+simplexes of $K$ having $v$ as a vertex. This union is denoted by
+\nomen{$\operatorname{star}(v,K)$}. An example is:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.0\linewidth]{pics/ch6-notes-2/ex5.png}
+    \caption{Example of star}
+\end{figure}
+So it really feels like a star spreading out from $v$. We have
+
+\begin{lemma}
+    Vertices $v_0,v_1,\cdots,v_k$ of a simplicial complex $K$ are the
+    vertices of a simplex of $K$ if and only if the intersection of
+    their open stars is nonempty, i.e. 
+    $$\cup_0^k \operatorname{star}(v_i,K)\neq\emptyset$$
+\end{lemma}
+\begin{proof}
+    The proof can be found in page 130 of \cite{book}. It is quite
+    trivial.
+\end{proof}
+Then we have the \textbf{proof of theorem \ref{thm:SAT}}:
+\begin{proof}
+    The proof is found in page 130 to 131 of \cite{book}. The idea is
+    that if for each vertex $u$ of $K$, we can find a vertex $v$ of
+    $L$ such that
+    \begin{equation}
+        f(\operatorname{star}(u,K))\subseteq\operatorname{star}(v,L)
+        \label{eq:proof-temp} \tag{*} 
+    \end{equation}
+    Then the simplicial map $s(u)=v$ will be easily verified to be a
+    simplicial approximation of $f$.
+
+    To make such (*) happen, we naturally have to divide $K^m$ small
+    enough. We can achieve such small division is guaranteed by the
+    Lebesgue lemma \ref{lemma:lebesgue-lemma}, since each subdivision
+    makes the averaged diameter smaller.
+\end{proof}

### 2016-12-11 Basic Topology Notes/sections/ch6-Triangulation.tex
[major] Introduces Edge group in topology.

@@
 \end{proof}
+
+\subsection{6.4 The edge group of a complex}
+\label{sec:edge-group}
+
+The definition of edge group is so similar to that of fundamental
+group (actually, edge group is made to simplify computation of
+fundamental group). Therefore, I will not waste too much words here.
+One with reasonable intuition could just skim through this section.
+
+The following excerpt from book \cite{book} best captures the idea:
+
+\begin{myquote} \enquote{
+We calculated the fundamental groups of one or two spaces in Chapter
+5, but our calculations, though efficient for the examples given
+there, were rather \textit{ad hoc}. If we agree to work with triangulable
+spaces, we can be much more systematic. We shall show how to read off
+generators and relationst for the fundamental group from a
+triangulation of the space.
+
+Let $X$ be a path-connected triangulable space, take a specific
+triangulation $h:|K|\to X$, and replace $X$ by $|K|$ (we are at
+liberty to do this since the funda- mental group is a topological
+invariant). Now the advantage of a polyhedron $|K|$ is that the
+elements of its fundamental group can be represented by loops which
+are made up of edges of $K$. Using such 'edge loops' we shall
+construct a group, called the edge group of the complex $|K|$, which
+can be computed and wh ich is isomorphie to the fundamental group of
+$|K|$.
+} \end{myquote}
+
+The edge pathes $v_0,v_1,\cdots,v_k$, edge loops
+$v,v_1,\cdots,v_{k-1},v$ are defined similar to pathes and loops.
+The equivalence relation between edge loops are defined as represented
+by the following drawing:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/ch6-notes-2/edge-group1.png}
+\end{figure}
+
+The equivalence class of edge pathes and edge loops are denoted
+$\{v_0,v_1,\cdots,v_k\}$, and $\{v,v_1,\cdots,v_{k-1},v\}$,
+respectively. The multiplication of edge loops is defined simply as
+\begin{equation}
+    \{v,v_1,\cdots,v\}\{v,w_1,\cdots,v\} =
+    \{v,v_1,\cdots,v,w_1,\cdots,v\}
+\end{equation}
+
+It is trivially verified that such edge loops form a group, called the
+\nomen{edge group based at $v$, $E(K,v)$}. It is also trivially
+verified that such group does not depend on the choice of base point
+$v$, since $|K|$ is path-connected.
+
+\begin{thm}
+    $E(K,v)$ is isomorphie to $\pi_1(|K|,v)$
+\end{thm}
+\begin{proof}
+    The proof can be found on page 133 of \cite{book}. The essential
+    idea is that an edge loop is just a loop. And a loop is just a
+    continuous map $f:I\to |K|$, we can easily use the simplicial
+    approximation $s:I^m\to |K|$ of $f$ (with appropriately $m$), to
+    find a corresponding edge loop.
+
+    The uniqueness of the loop corresponding to an edge loop is found
+    again by treating $L:=I^2$ as a simplicial complex and apprximate
+    again the homotopy $F:L\to |K|$. The resulted $S$ will again gives
+    us a equivalence relation to the constant edge loop. (Note, we
+    have to use the fact the simplicial maps preserves the equivalence
+    relation between edge pathes). The following pictorially
+    produces the proof:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=1\linewidth]{pics/ch6-notes-2/L.png}
+    \end{figure}
+\end{proof}

### 2016-12-15 Basic Topology Notes/sections/ch6-Triangulation.tex
[major] Basic Topology: Get the generators and relations in the Edge group.

@@
 construct a group, called the edge group of the complex $|K|$, which
-can be computed and wh ich is isomorphie to the fundamental group of
+can be computed and wh ich is isomorphic to the fundamental group of
 $|K|$.
@@
 \begin{thm}
-    $E(K,v)$ is isomorphie to $\pi_1(|K|,v)$
+    $E(K,v)$ is isomorphic to $\pi_1(|K|,v)$
 \end{thm}
@@
         \centering
-        \includegraphics[width=1\linewidth]{pics/ch6-notes-2/L.png}
+        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-2/L.png}
     \end{figure}
 \end{proof}
+
+\begin{remark}
+    This theorem already tells us that the Edge group $E(K,v)$ is
+    indepedent on the choice of base point $v$, since our polyhedron
+    $|K|$ is always assumed to be path-connected.
+\end{remark}
+
+Based on this edge group, we will try to calculate more explicitly the
+structure of this group. Here we provide a way to get the generators
+and relations directly from the edge group.
+
+\begin{key}
+    The intuition is that the structure of this group is
+    determined only by those $1$-simplexes, $2$-simplexes, and the
+    equivalence relations between edge pathes. All higher dimensional
+    simplexes are not relevent to this group structure.
+\end{key}
+
+We let \nomen{$L$} the subcomplex of a simplicial complex $K$. This
+subcomplex $L$ is required to contain all the vertices of $K$ and such
+that its polyhedron $|L|$ is path-connected and simply-connected. Can
+we find such a subcomplex? The intuitive answer is yes due to the
+path-connectedness nature of $|K|$. The rigorous answer needs the help
+of a concept \nomen{tree}. A tree $T$ is a one-dimensional subcomplex of
+$K$ whose polyhedron $|T|$ is both path-connected and
+simply-connected. The following lemma affirms that we can find our $L$
+to be exactly the maximal tree in $K$:
+\begin{lemma}
+    A maximal tree contains all the vertices of $K$.
+\end{lemma}
+\begin{proof}
+    We first observe that a tree must exists, unless the dimension of
+    $K$ is $0$ (in which case, there is entirely no need for the
+    following discussions, and the lemma is still true because there is
+    not even a maximal tree!). Let $T$ be a maximal tree in $K$, which
+    means that if $T'$ is a tree and contains $T$, than $T'=T$. 
+    The next step is simply and is expatiated on page 134 of
+    \cite{book}. The idea is to grow a tree by adding more vertices,
+    which is possible because $|K|$ is path-connected and a path can
+    be easily turned into an edge path. Note that add a
+    simply-connected space in this way will keep the space
+    simply-connected, just do not add a vertices twice too creat a
+    loop.
+
+    Obviously one will get a tree which is maximal and contains all
+    the vertices.  Such a process also affirms that the maximal tree
+    will exist (but may not be unique).
+\end{proof}
+
+\begin{ex}
+    Here is the maximal tree of the triangulation of two-torus:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex1-maximal-tree.png}
+    \end{figure}
+\end{ex}
+
+\begin{ex}
+    The maximal tree is usually not unique!
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex2-maxi-tree-not-unique.png}
+    \end{figure}
+\end{ex}
+
+Now since $|L|$ is simply-connected, it will not contribute to the
+edge group. What contributes to the edge group is those edges that are
+not in this $|L|$. This motivates us to define a new group:
+
+\begin{defi}[$G(K,L)$]
+\nomenclature{$G(K,L)$}{\nomrefpage.}
+    Let $L$ be the maximal tree in $K$ (assume $|K|$ is
+    path-connected). Then $G(K,L)$ is defined by generators $g_{ij}$
+    for each \textbf{ordered} pair of vertices $v_i,v_j$ such that
+    $\{v_i,v_j\}$ spans a simplex ($0$-simplex or $1$-simplex) in $K$.
+    Those generators are subject to the following conditions:
+    \begin{enumerate}
+        \item $g_{ij}=1$, the identity element, if and only if
+            $\{v_i,v_j\}$ spans a simplex in $L$.
+        \item $g_{ij}g_{jk}=g_{ik}$ if and only if $\{v_i,v_j,v_k\}$
+            spans a simplex ($0$ or $1$ or $2$ simplex) in $K$.
+    \end{enumerate}
+\end{defi}
+
+\begin{ex}
+    \label{ex:torus-GLKgroup}
+    Again, for torus:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex3-L-in-triangle.png}
+    \end{figure}
+\end{ex}
+\begin{ex}
+    \label{ex:ex4-L-in-two-torus}
+    And for another:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex4-L-in-two-torus.png}
+    \end{figure}
+    Note that this does not gives a triangulation of two-torus! 
+    The reason will be explained later in
+    example~\ref{ex:pi1-two-torus}.
+\end{ex}
+More generally, we have
+\begin{thm}
+    $G(K,L)\cong E(K,v)$, as a group isomorphism.
+\end{thm}
+\begin{proof}
+    The proof in page 135 to 136 of \cite{book} constructs the
+    following homomorphisms:
+
+    $$\begin{tikzcd}[]
+        G(K,L)\ar[r,"\phi",shift left] & 
+            E(K,v)\ar[l,"\theta", shift left]
+    \end{tikzcd}$$
+
+    It is pretty simple to get these two maps and confirms that their
+    composites are identity functions on each space.
+\end{proof}
+
+\begin{remark}
+    We have now the following chain of homomorphisms:
+    $$ \pi_1(|K|,v)\cong E(K,v) \cong G(K,L) $$
+\end{remark}
+\begin{coro}
+    For any path-connected, triangulable space, its fundamental group
+    is finitely presented, i.e., the fundamental group has only a
+    finite number of generators and a finite number of relations.
+\end{coro}
+
+For example, we have demonstrated in example~\ref{ex:torus-GLKgroup}
+that its $G(K,L)\cong \Z_2$, which is just its fundamental group.
+
+In addition, armed with this tool, we can answer an additional
+question. We want to know what is the fundamental group of two torus
+connected together:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/pic-two-torus.png}
+\end{figure}
+
+This can be done using the following theorem:
+
+\begin{thm}[Van Kampen's theorem]
+    Let $J$, $K$ be two simplicial complexes in some Euclidean space
+    which intersect in a common subcomplex, and suppose all $|J|$,
+    $|K|$, $|J\cap K|$ are path-connected. Let $j,k$ be the inclusion
+    maps:
+    $$ \begin{tikzcd}[]
+        \lvert J\cap K\rvert \ar[r,"j",hook] & \lvert J\rvert
+    \end{tikzcd}$$
+    $$ \begin{tikzcd}[]
+        \lvert J\cap K\rvert \ar[r,"k",hook] & \lvert K\rvert
+    \end{tikzcd}$$
+    Take a vertice $v\in J\cap K$ as the base point. The fundamental
+    group $\pi_1(|J\cup K|, v)$ is obtained from the free product
+    $\pi_1(|J|,v)*\pi_1(|K|,v)$ by adding the relations
+    $j_*(z)=k_*(z)$ for all $z\in\pi_1(|J\cap K|,v)$.
+\end{thm}
+\begin{proof}
+    The proof can be found on page 137 to 138 of \cite{book}. Please
+    do read the paragraph just before this theorem to get a picture of
+    the proof.
+
+    Note also that a $2$-simplex cannot possiblly cross the
+    intersection part $J\cap K$. Please check why I mention this when
+    reading the proof on the book \cite{book}.
+\end{proof}
+
+\begin{ex}
+    \label{ex:pi1-two-torus}
+    Here's how to find the fundamental group for two-torus connected:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex-pi1-two-torus.png}
+\end{figure}
+    The result confirms that the triangulation of a two-torus is as
+    simple as in example~\ref{ex:ex4-L-in-two-torus}.
+\end{ex}
+
+\begin{ex}
+    Next we consider the projective space $\R P^2$, the space is
+    homeomorphic to half the sphere $S^2$, with the antipodal points
+    on the boundary identified:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.4\linewidth]{pics/ch6-notes-3/rp2.png}
+    \end{figure}
+    Then it can be regarded as a 2-disc with it boundary attached to
+    the boundary of a M\"obius strip. This construction will tell us
+    that the fundamental group of $\R P^2$ is $\Z_2$.
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/ch6-notes-3/rp2-pi1.png}
+        \caption{Page 139, Fig 6.16 of \cite{book}}
+    \end{figure}
+\end{ex}

### 2016-12-21 Basic Topology Notes/sections/ch8-Simplicial-Homology.tex
[major] Introducing simplicial homology groups.

We first notice that
\begin{equation}
    \pi_1(S^n)=\pi_1(\{*\}) = \{1\}
\end{equation}
for $n\geq 2$. But clearly $S^n$ is not homotopic to the one point
space $\{*\}$, i.e. $S^n$ is not contractible! Therefore, the
fundamental homotopy group does not solve the problem of determine the
homotopy of a space. The homology groups will be an new direction to go.

The details is covered in page 173 of \cite{book}.
Sadly, even if one can computes all the homology groups (or all the
homotopy groups), one cannot determine uniquely the homotopy type of
the space in general, unless one has some additional conditions.
For example, we have the Whitehead's Theorem: Given a continuous map
from $X\to Y$, two "good" topological spaces, if $f$ induces
isomorphisms on all homotopy group $\pi_n(X)\to\pi_n(Y)$, ($n\geq 1$),
and induces bijection on $\pi_0(X)\to\pi_0(Y)$, then $f$ is a
homotopic equivalence. Is there similar good theorem for homology
groups? Perhaps there is, but it is still not good enough for we still
need to find such a $f$.

Anyway, let's proceed to the discussion of simplicial homology.
\textbf{Note}: all the following discussions are based on a given
triangulation $K$ of the space.

\subsection{Section 8.1 - Cycles and boundaries}
\label{sec:Cycles-and-boundaries}

Geometrically, the homology groups aims to encode the information
about $k$-dimensional holes in a space, as holes are important in
determining the homotopy type of a space.

Then we notice that the boundary and bulk relation is also important.
What I mean is in the following picture. The first loop encircles
a part that does not belong to the torus, whereas the second loop
encloses a solid part in the torus. One sees that the first loop is
not nullhomotopic, i.e. it cannot be homotopic contracted to the
trivial loop. On the other hand, loop 2 can. Look more generally, if a
loop is the boundary of simple part (e.g. a simplex), then it is
homotopic to the trivial loop. In this case we physicists can regard
it as the boundary of a good bulk, g simplex. However, if a loop has
empty bulk, i.e. it encloses no simplex, it is not a boundary of
something, then it will be a nontrivial element in the fundamental
group. This is why boundaries are important in our consideration.

% todo torus-p1
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/ch8/torus-p1.png}
\end{figure}

Before discussion, I should make clear that if we only care about
information of holes of certain dimension $q$, then we only have to care
about composition of simplexes of the same dimension $q$ that encloses
certain area (be it empty or not). For example, in fundamental groups,
we only care about holes looks like $S^1$. So in most cases we only
care about series of $1$-simplexes that is connected to form a loop,
as in the case of edge groups. We call these things that we care about
a closed $q$-cycles, to be defined precisely later.  The set of all
closed $q$-cycles are denoted $Z_q$.

Next is how to consider boundaries algebraically. For example, give a
set of vertices, how to seperate the boundary out of this? This is
especially troublesome given that we will have boundaries of different
dimensions. There are the $0$-dimension boundary of endpoints, the
$1$-dimension boundary of lines enclosing area, the $2$-dimension
boundaries called faces.

The boundary operator $\partial$ aims to solve this problem, it gives
a systematic way to obtaining $(d-1)$-dimension boundary from a
$d$-dimension simplex. The simple examples are provided in page 174 to
175 of \cite{book}.

Lastly, as mentioned, closed $q$-cycles that is the boundary of some
solid part may become trivial, they are called $q$-boundaries. Closed
$q$-cycles that are not the boundary a solid part will be nontrivial.
Therefore, we might want to consider a quotient space:
$$ H_q = Z_q/B_q$$

I believe I have done a good job in summarizing the key point, now is
time to read the first section to get some practical ideas.

\subsection{Section 8.2 Homology groups}
\label{sec:Homology-groups}

This section formalize the intuitions from the previous section. It
defines \nomen{oriented simplex}, i.e. simplex denoted by a specific
$\{v_0,v_1,\vdots\}$ in this order. An change of order will change its
orientation. Such change of orientation is denoted by a minus sign,
and we have:
\begin{equation}
    (v_0,v_1,\cdots) = \operatorname{sign}\theta (v_{\theta(0)},
    v_{\theta(1)},\cdots)
\end{equation}
where $\theta$ is any permutation.

Then \nomen{$C_q(K)$} is the free abelian group generated by the oriented
$q$-simplexes of $K$, subject to the relations $\sigma+\tau=0$,
whenever $\sigma$ and $\tau$ are just the same simplex with opposite
orientations. An element of this group is called a \nomen{$q$-chain}.
Note that the rank of $C_q(K)$ is equal to the number of
$q$-simplexes in $K$.

The boundary homomorphism $\partial$ is defined such that
\begin{equation}
    \partial(v_0,\cdots,v_q)=\sum_{i=0}^{q}(-1)^i
    (v_{(0)},\cdots,\hat{v}_{(i)},\cdots,v_{(q)})
\end{equation}

where $(v_{(0)},\cdots,\hat{v}_{(i)},\cdots,v_{(q)})$
is shorthand for the oriented $(q-1)$-simplex obtained by deleting
the vertex $v_i$. It is easy to verify that $\partial^2=0$

In the special case when $q=0$, we define that boundary of a single
vertex is $0$ and that $C_{-1}(K)=0$.

We define the closed chains \nomen{$Z_q(K)$} as
\begin{equation}
    Z_q(K)=\Ker(\partial:C_q(K)\to C_{q-1}(K)).
\end{equation}
And the boundary \nomen{$B_q(K)$} is then
\begin{equation}
    B_q(K)=\Im(\partial:C_{q+1}(K)\to C_{q}(K)).
\end{equation}

$B_q$ will be a subgroup of $Z_q$ because $\partial^2=0$, this allows
us to define the \nomen{$q$-th homology group of $K$} as:
\begin{equation}
    H_q(K)=Z_q(K)/B_q(K)
\end{equation}

The elements of $H_q(K)$ are written $[z]$ for $z\in Z_q$, called the
\nomen{homology class} of $z$. Two $q$-cycles differ by a boundary
will have the same homology class and is called \nomen{homologous
cycles}. We note that $H_q(K)$ is by definition abelian and finitely
generated.

Of course, we need to verify various things in the above statements,
they can be found in the textbook \cite{book}.

\subsection{Section 8.3 Examples}
\label{sec:Section 8.3 Examples}

I only mention two theorems for the present:

\begin{thm}
    $H_0(K)$ is a free abelian group whose rank is the number of
    path-connected components of $|K|$ (or just components, as $|K|$
    is path-connected).
\end{thm}
\begin{proof}
    This is quite obvious.
\end{proof}

\begin{thm}
    If $|K|$ is connected, then $H_1(K)$ is isomorphic to the
    abelianization of its fundamental group $\pi_1(K)$.
\end{thm}
\begin{proof}
    Found on page 182 of \cite{book}.
\end{proof}

### 2016-12-23 Basic Topology Notes/sections/ch6-Triangulation.tex
[major] Introducing simplicial homology groups.
[major] Examples of homology groups, and introduce chain complex.

@@
 \begin{ex}
+    \label{ex:triangu-torus}
     Here is a triangulation on the torus:
@@
 
-\subsection{6.4 The edge group of a complex}
+\subsection{Section 6.4 The edge group of a complex}
 \label{sec:edge-group}
@@
 \begin{ex}
-    Here is the maximal tree of the triangulation of two-torus:
+    Here is the maximal tree of a triangulation:
     \begin{figure}[H]
         \centering
-        \includegraphics[width=0.9\linewidth]{pics/ch6-notes-3/ex1-maximal-tree.png}
+        \includegraphics[width=0.6\linewidth]{pics/ch6-notes-3/ex1-maximal-tree.png}
     \end{figure}
@@
     \label{ex:torus-GLKgroup}
-    Again, for torus:
+    Again, for circle:
     \begin{figure}[H]

### 2016-12-23 Basic Topology Notes/sections/ch8-Simplicial-Homology.tex
[major] Examples of homology groups, and introduce chain complex.

@@
 
-% todo torus-p1
 \begin{figure}[H]
@@
 
-I only mention two theorems for the present:
+I will mention two theorems first:
 
@@
 \end{proof}
+
+The two theorems indicates again that those homology groups are
+independent of the choice of triangulation, and they should be
+topological invariants.
+
+Then I will turn attention to specific examples.
+
+\begin{key}
+    \label{key:2cycle-orientation}
+    Observe that every cycle is actually a closed object. It encircles
+    or encloses an aresa. A closed $1$-cycle is actually a loop. A
+    closed $2$-cycle will always enclose an area, so it is actually a
+    sphere. A closed $2$-cycle will give an orientation on its
+    surface. For example, suppose that we have a closed $2$-cycle
+    $\lambda_i\sigma_i$, and assume that there is no repeated
+    $2$-simple in this collection. For a given $2$-simplex $\sigma_1$
+    in it, there will have to be $3$ simplexes surrounding it to
+    cancal out $\sigma_1$'s edges. These $4$ $2$-simplexes are said to
+    have compatible orientation. If one draw them on a paper, one will
+    see that they are of the same orientation. Continue this argument
+    to include all simplexes and one will see this $2$-cycle actually
+    gives an orientation on its surface.
+\end{key}
+\begin{ex}\textbf{Torus}
+
+    Consider the triangulation of torus as in
+    exmaple~\ref{ex:triangu-torus}.
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/ch8/torus-tri.png}
+    \end{figure}
+
+    The zeroth homology group $H_0(K)$ marks the connected components,
+    hence it is $H_0(K)=\Z$. The first homology group $H_1$ is about
+    those closed loops. Almost all loops are boundaries. But there are
+    two (the green one and the blue one), each of which cannot be a
+    boundary. For example, I managed to make the orientation such that
+    the green one is not cancelled, but this leaves a part of the blue
+    one also un-cancelled. 
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/ch8/torus-tri-1.png}
+    \end{figure}
+
+    This two loops generates the $H_1(K)=\Z\cross\Z$, and are also the
+    nontrivial objects in its fundamental group (a coindence,
+    $\pi_1(T^2)=H_1(T^2)$).
+
+    The $2$-cycles are easy to find. Because our space torus has no
+    boundary, we have to add more and more $2$-simplexes until the
+    whole space is covered with a $2$-chain. Then in this case, there
+    is only one generator for $Z_2(K)$. Also, there is not
+    $3$-simplex, so the $B_2=0$. Hence $H_2(K)=Z_2(K)=\Z$.
+\end{ex}
+
+\begin{ex} \textbf{Klein bottle $T^2$}
+
+    As for the Klein bottle, I have had a hard time getting and
+    confirming that the following is a triangulation:
+    \footnote{
+        I found two articles talking about minimal triangulations
+        of Klein bottle. They are:
+        \href{https://arxiv.org/abs/math/0407008}{link1}
+        and
+        \href{http://www.sciencedirect.com/science/article/pii/S0095895697999998}{link2}.
+        The pdf files is also included.
+    }
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/ch8/klein-tri.png}
+    \end{figure}
+
+    The $H_0(K)$ is clearly $\Z$.
+
+    The $1$-cycles on this triangulation are hard to analyse. So I
+    will use the fact that its $\pi_1=\braket{a,b|ba=a^{-1}b}$.
+    The commutator is generated by $aba^{-1}b^{-1}=a^2$ and
+    $bab^{-1}a^{-1}=a^{-2}$. So in the abelianization,
+    $[a]=[a^{2n+1}]$, $[a^{2n}]=[1]$. So $[a]$ generates $\Z_2$. The
+    $[b]$ is not affected, so $[b]$ generates $\Z$. It's easy to
+    confirm that $[ab]=[ba]$, i.e. the abelianization group is
+    abelian. All in all, $H_1(K)=\Z\cross\Z_2$.
+
+    The $H_2(K)=0$, since there is no way to orient the Klein in a
+    reasonable way (see key point~\ref{key:2cycle-orientation}).
+\end{ex}
+
+\begin{ex}\textbf{Cone Space}
+
+    Now the book considers a complex $K$ which is a cone, i.e. $K$ is
+    isomorphic to a complex of the form $CL$ where the dimentions of
+    $L$ is $(\dim{K}-1)$.
+
+    It is easy to see that $H_0(K)=\Z$, since cone is always
+    connected.
+    It is shown in page 181 of book\cite{book} that $H_n(K)=0$, for $n\geq
+    1$. This is reasonable because cones are actually contractible, so
+    there is not much interesting information about higher dimensional
+    spheres in cones to be recorded. The book shows this by
+    constructing a map $d:C_q(K)\to C_{q+1}(K)$, such that
+    \begin{equation}
+        \partial d(\sigma) = \sigma-d\partial(\sigma)
+    \end{equation}
+    It's easy to see that this means every closed cycle is a boundary.
+\end{ex}
+
+\begin{ex}\textbf{$(n+1)$-simplexes and $\sum^n\cong S^n$}
+
+    Let $\Delta^{n+1}$ denotes a $(n+1)$-simplex. In this case, we
+    consider it as a simplicial complex with all of its faces. Let
+    $\sum^n$ denotes the simplexes which lies in the boundary of this
+    $(n+1)$-simplex $\Delta^{n+1}$. Notice this is equivalent to say
+    that $\sum^n$ is the all remaing simplex obtained by removing the
+    interior points of $\Delta^{n+1}$. For example, $\sum^1$ is the
+    3 edges and 3 vertices of the triangle. We see that $\sum^n$ is
+    isomorphic to $S^n$.
+
+    Every $\Delta^{n+1}$ can be thought of as a cone (except when
+    $n=-1$, which is too trivial to be discussed here). So the
+    homology classes of $\Delta^{n+1}$ are $H_0(\Delta^{n+1})=\Z$,
+    $H_q(\Delta^{n+1})=0$, $q\geq 1$.
+
+    The homology classes of $\sum^n$ can be calculated using
+    $\Delta^{n+1}$, because they differ by only a single
+    ${n+1}$-simplex, then most of their chains are the same.
+
+    When $n=0$, the case is trivial and $H_0(\sum^0)=\Z\oplus\Z$,
+    $H_q(\sum^0)=0$ for $q\geq 0$.
+
+    When $n\geq 1$, then since $H_q$ does not involve simplexes of
+    dimension higher than $q+1$, we have
+    $H_q(\sum^n)=H_q(\Delta^{n+1})$, for $0\leq q\leq n-1$. Hence
+    $H_0(\sum^n)=\Z$. $H_q(\sum^n)=0$, for $1\leq q \leq n-1$. 
+    By using $H_n(\Delta^{n+1})=0$, it is easy to get
+    $H_n(\sum^n)=\Z$. (book\cite{book} page 182). The rest of the Homology groups
+    will of course be $0$.
+
+    It is interesting to check that $H_n(\sum^n)=\Z$, not $0$ for a
+    one point space. If we are able to show that Homology group is a
+    topological invariant, then we know now Homology groups can be
+    used to distinguish spheres with a point.
+\end{ex}
+
+\subsection{Section 8.4 Simplicial maps}
+\label{sec:Simplicial maps}
+
+Now we extend a simplicial map $K\to L$ to a homomorphism between
+homology groups. This is easily done by first constructing
+$s:C_q(K)\to C_q(L)$, and then confirming $s\partial=\partial s$, or
+just $[s,\partial]=0$. This is a very general procedure and the
+condition will be frequently seen in Homological algebra or
+Cohomological algebra. In face, let me first introduces Homological
+concepts first.
+
+The collection of groups and homomorphisms:
+$$\begin{tikzcd}[]
+    \cdots \ar[r,"\partial"] & C_q(K) \ar[r,"\partial"] &
+    C_{q-1}(K) \ar[r,"\partial"] & \cdots \ar[r,"\partial"] &
+    C_0(K) \ar[r,"\partial"] & 0
+\end{tikzcd}$$
+will be called a \nomen{chain complex} of $K$, written $C(K)$. 
+A \nomen{chain map} $\phi:C(K)\to C(L)$ is a set of group
+homomorphisms $\phi:C_q(K)\to C_q(L)$. Such a map will induce a
+homomorphism of Homology groups when $\phi\partial=\partial\phi$
+(easily proved). This induced homomorphism between Homology groups is
+dentoed $\phi_*$.
+
+In our specific case where $s$ are simplicial maps $K\to L$, it is
+easy to extend it to $s:C_q(K)\to C_q(L)$, since $s$ has already been
+required to map simplexes to simplexes. We only need to pay attention
+when $\sigma$ a generator (i.e. a $q$-simplex) of $C_q(K)$, is mapped
+to a simplex of inferior quaility, i.e. of lower dimension $<q$. Then
+it is nature to define $s(\sigma)=0$ in this case. It is verifed (page
+185 of \cite{book}) that this map is well defined, is a homomorphism,
+and has the property $s\partial=\partial s$. So $s$ induces a
+homomorphism $s_*:H_q(K)\to H_q(L)$.

### 2016-12-27 Basic Topology Notes/sections/ch5-fundamental-groups.tex
[major] new note for topology: simplicial approximation theorem
[major] Talks about stellar subdivision and how homology group are a homotopic invariant.

@@
     Proof is on page 99 of \cite{book}. It requires the Lebesgue lemma
-    \ref{thm:lebesgue-lemma}. A picture illustrating the proof is
+    \ref{lemma:lebesgue-lemma}. A picture illustrating the proof is
     provided here:
@@
 \begin{thm}[Brouwer Fixed Point theorem]
+    \label{thm:brouwer-fixpoint-B2}
     A contiuous map $f:B^2\to B^2$ ($B^2:2D$-closed dicks) must have a
@@
 \begin{ex}
+    \label{ex:Euclidean-space-and-sphere-homotopy}
     $\E^n\setminus \{0\}$ has the homotopy type of $S^{n-1}$. This is

### 2016-12-27 Basic Topology Notes/sections/ch8-Simplicial-Homology.tex
[major] Talks about stellar subdivision and how homology group are a homotopic invariant.

@@
 \subsection{Section 8.4 Simplicial maps}
-\label{sec:Simplicial maps}
+\label{sec:Simplicial-maps}
 
@@
 homomorphism $s_*:H_q(K)\to H_q(L)$.
+
+\subsection{Section 8.5 Stellar Subdivision and Section 8.6 Invariance}
+\label{sec:Stellar-Subdivision-Invariance}
+
+Let me draw a \textbf{general blueprint}. We aims to
+show that simplicial homology groups are actually a topological
+property. The ultimate aim is to prove these theorems
+
+\begin{thm}
+    Any continuous function $f:|K|\to |L|$ induces a homomorphism
+    $f_*:H_q(K)\to H_q(L)$ in for each $q \geq 0$.
+\end{thm}
+
+\begin{thm}
+    If $f$ is the identity map of $|K|$, then each 
+    $f_*:H_q(K)\to H_q(K)$ is the identity homomorphism, and if we
+    have two maps
+    $$ \begin{tikzcd}[]
+        \lvert K\rvert\ar[r,"f"] & \lvert L\rvert\ar[r,"g"] 
+        & \lvert M\rvert
+    \end{tikzcd}$$
+    then $(g\circ f)_* = g_*\circ f_*: H_q(K)\to H_q(M)$
+    for all $q\geq 0$.
+\end{thm}
+
+\begin{thm}
+    If $f,g:|K|\to |L|$ are homotopic maps, then $f_*=g_*:H_q(K)\to
+    H_q(L)$ for all $q$.
+\end{thm}
+
+\begin{coro}
+    If $|K|$ and $|L|$ have the same homotopy type, then $K$ and $L$
+    have isomorphic homology groups.
+\end{coro}
+
+These theorems can be found on page 189 of the book\cite{book}. But
+unfortunately, this course is too limited to talk about their proof in
+detail. So here we provide the general picture. The starting point
+will be of course, approximating a continuous function $f$ with a
+simplicial map $s$. But in doing so, we have to do barycentric
+subdivision on the codomain. So if we can ensure that the homology
+groups are unaltered in barycentric subdivision, then of course
+simplicial maps will preserve homology groups, as we have seen in
+section~\ref{sec:Simplicial-maps}. And it is nature, though it
+requires proof, that the function $f$ approximated by $s$ will also
+have the same property of preserving simplicial maps.
+
+This section (section 8.5) deals with proving that the barycentric
+subdivision does not alter Homology groups. But it uses a simpler
+step. In general, a lot more vertices will be introduced in one
+barycentric subdivision. But we can look at a simper notion first,
+i.e. a \nomen{stellar subdivision}. Stellar meanings relating to
+stars, and a stellar subdivision quite resembles a star's shining
+lines. A first example is given on top of page 186 of \cite{book}.
+Here I reproduced the figure 8.6 in a more "star" like depiction:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{pics/ch8/stellar-subd-ex.pdf}
+\end{figure}
+
+The benefit of stellar subdivision is that one can do a complete
+barycentric subdivision through performing a series of steller subdivision
+in a specific order. Amazingly the book\cite{book} do not provide a
+proof of this, except that it gives an example using figure 8.7 on
+page 186. But the proof should be easy.
+
+I have omitted a precise description of stellar subdivision here,
+because it is best understood along with the process to obtain a
+barycentric subdivision through stellar subdivision. They are found in
+page 186 of \cite{book}. Just keep in mind that $A_0<A_1<\cdots<A_k$,
+for a simplex $\{\hat{A}_0,\hat{A}_1,\cdots,\hat{A}_k\}$ in a
+barycentric subdivision.
+
+Then the book proves that
+\begin{thm}
+    If $K'$ is obtained from $K$ by a single stellar subdivision, then
+    $K'$ and $K$ have isomorphic Homology groups
+\end{thm}
+and hence
+\begin{coro}
+    Barycentric subdivision does not change the Homology groups of a
+    complex
+\end{coro}
+
+The proof can be in page 186 to 188 of \cite{book}. I also omit the
+proof here, but I warn anyone who wish to study the prooves in the
+next section to study the proofs here carefully, because a important
+map (subdivision chain map) will be constructed here.
+
+As an effort to prevent this tacit talk from being a transient memory,
+I will mention several applications.
+
+\begin{remark}
+    First, Homology group is a homotopic property. This means we can
+    calculate the Homology group of a big complex space by shrinking
+    it into a simple space.
+\end{remark}
+
+\begin{key}
+    The Homology groups of $S^n$ are:
+    $$ H_0(S^n)=H_n(S^n)=\Z $$
+    $$ H_q(S^n)=0,\text{for $q\neq 0,n$} $$
+\end{key}
+\begin{thm}
+    $S^m$ is not homotopic to $S^n$ if $m\neq n$.
+\end{thm}
+\begin{proof}
+    Obviously.
+\end{proof}
+
+\begin{thm}
+    Two Euclidean spaces are homeomorphic if and only if they have the
+    same dimension
+\end{thm}
+\begin{proof}
+    As mentioned in
+    example~\ref{ex:Euclidean-space-and-sphere-homotopy}, the 
+    homotype type of $S^{m-1}$ and $\E^{m}\setminus\{0\}$ are the
+    same. If there is a homotopic equivalence from $\E^m\to \E^n$, it
+    would induces homotopic equivalence on $S^m$ and $S^n$. Hence
+    $\E^m$ is homotopic to $\E^n$ if and only if $m=n$.
+\end{proof}
+
+\begin{thm}[Brouwer fixed-point theorem]
+    A map from $B^n$ to itself must leave at least one point fixed.
+\end{thm}
+\begin{proof}
+    The proof is exactly as it is in
+    theorem~\ref{thm:brouwer-fixpoint-B2}, except that we have to use
+    Homology groups instead of the fundamental group to distinguish
+    different spheres.
+\end{proof}

### 2017-01-01 Basic Topology Notes/sections/ch9-DegreeAndLefschetzNumber.tex
[major] Introduce degree of maps between spheres in Basic Topology

Professor Li Qin skipped many parts before. In this chapter, he also
mentioned only important theorems in the first two sections.

The language in this note will be quite loose. Proofs will be omitted,
so will some theorems, as this was how my teacher taught me. I am not
sure if there are more valuable techniques in these sections. Hence
this can be only regarded as a guideline/introduction to the book.
% todo: ask why he mentioned only this few parts

\subsection{Section 9.1 Maps of spheres}
\label{sec:Maps-of-spheres}

In this section, we restrict our attention only on spheres $S^n$. The
goal is investigate the homotopy classes of continuous functions
between spheres. We will see, in the end, that we can obtain some
information by examining the how these continuous functions acting on
a simple triangulation of sphere.

We first define the degree of a continuous function $f:S^n\to S^n$.
Since $H_n(S^n)=\Z$, we define \nomen{$\operatorname{deg}f$} to be the number
$f_*(1)$, in $f_*:H_n(S^n)\to H_n(S^n)$. Or, equivalently, the number
$\lambda$ such that $f([z])=\lambda[z]$, where $[z]$ is the generator
of $H_n(S^n)=\Z$.

Then we discover several facts:
\begin{fact}
    The degree does not depend on the choice of triangulation of
    sphere.
\end{fact}
\begin{fact}
    Homotopic continuous functions have the same degree.
\end{fact}
\begin{fact}
    $\operatorname{deg}(f\circ g)=\operatorname{deg}f\times
    \operatorname{deg}g$
\end{fact}
\begin{fact}
    By above fact, if $f$ is a homeomorphism,
    $\operatorname{deg}f=\pm 1$.
\end{fact}
\begin{fact}
    Obvious, the degree of identity map of $S^n$ is $1$, that of
    constant map is $0$. Hence the identity map is not homotopic to
    the constant map.
\end{fact}

The above facts can be found in page 195 of \cite{book}.

Since degree is triangulation independent, we will now stick to a very
convenient triangulation constructed in page 196 of \cite{book}. It is
the most straightforward one, and is denoted by \nomen{$\Sigma$}
(remember, we have constructed similar things in chapter 8, denoted
$\Sigma^n$). The vertices are $v_i=(0,\cdots,0,1,0,\cdots,0)$, for
$i=1,2,\cdots,n+1$, and the only $1$ is on the $i$-th coordinate.
Similary we have $v_{-i}=0,\cdots,0,-1,0,\cdots,0)$. Whenever
$\abs{i_1}<\abs{i_2}<\cdots<|i_s|$, with $1\leq s \leq n+1$, the
vertices $v_{i_1},v_{i_2},\cdots,v_{i_s}$ spans a simplex in $\Sigma$.
The collection of all such simplexes constitutes the simplicial
complex $\Sigma$. A graphical illustration can be found on page 196 of
\cite{book}.

The degree of a continuous function $f$ can than be easily determined
on this triangulation. But I will only mention that this is
demonstrated in theorem (9.1) on page 196 of \cite{book}.

Then we discover a sequel of facts, each depending on the previous
one:
\begin{fact}
    The antipodal map of $S^n$ has degree $(-1)^{n+1}$
\end{fact}
\begin{fact}
    A continuous function $f:S^n\to S^n$ which has no fixed points
    must have degree $(-1)^{n+1}$.
\end{fact}
\begin{fact}
    If $n$ is even, and if $f:S^n\to S^n$ is homotopic to the
    identity, then $f$ has a fixed point.
\end{fact}

Using this we can derive an interesting theorem:
\begin{thm}[Hairy ball theorem]
    $S^n$ admits a continuous nonvanishing vector field if and only if
    $n$ is odd.
\end{thm}
\begin{proof}
    Let $v$ be a vector field on $S^n$, for each $v(\vb{x})$, it can
    be regarded just as a normal vector in $\E^{n+1}$ since each
    tangent space is locally a $\R^{n+1}$.

    The continuous function:
    $$f(\vb{x}) = \frac{\vb{x}+v(\vb{x})}{||\vb{x}+v(\vb{x})||}$$
    is homotopic (hint, add a parameter $t$ in front of $v(\vb{x})$), 
    to identity map. Hence $f(\vb{x})$ admits a fix point, i.e. there
    is a point $\vb{x}$ such that $v(\vb{x})=0$.
\end{proof}

Notice that in proof above, the function $f(\vb{x})$ actually help us
regard a vector filed as a speed field, a field that moves each point
on the sphere infinitesimally.

%TODO ntoes for the next section.

### 2017-01-02 Basic Topology Notes/sections/ch9-DegreeAndLefschetzNumber.tex
[major] notes about Euler-Poincare lemma, Betti number, and free actions on spheres S^n when n is even.

@@
 
-%TODO ntoes for the next section.
+And yet another theorem left out by the teacher:
+\begin{thm}
+    If $n$ is even, then only $\Z_2$ and the trivial group can act freely on
+    $S^n$.
+\end{thm}
+\begin{proof}
+    Suppose a group $G$, which is not the trivial group, acts freely on $S^n$.
+    Pick two elements $f,g$ of $G\setminus\{1\}$, they must have not fixed
+    points, so they have $(-1)^{n+1}=-1$ degree. This means their composite
+    $f\circ g$ have a degree of $(-1)\times(-1)=1$, whence we see that $f\circ
+    g$ has fixed point. So $f\circ g= 1$. To repeat, $f\circ g=1$ for any
+    $f,g\in G\setminus{1}$. So $G\cong \Z_2$.
+\end{proof}
+\begin{remark}
+    Physically, this means that most reasonable symmetries, acting on $S^{2n}$ (such
+    as a sphere $S^2$, the most common one in physics), are not free. They are
+    subject to certain constraints such that there is always some point fixed
+    when rotating the sphere.
+\end{remark}
+\subsection{Section 9.2 The Eular-Poincar\'e formula}
+\label{sec:The-Eular-Poincare-formula}
+
+Since we have skipped too many sections in the beginning, we lost a historical
+background for this section. Therefore, I will be tacit in this section.
+
+The first chapter of book\cite{book} introduced yet another topological invariant
+to our list: the Euler characteristics. This section proves that the Eular
+characteristics is actually a homotopy invariant.
+
+The \nomen{Eular characteristics $\chi(K)$} of a simplicial complex is by
+definition:
+\begin{equation}
+    \chi(K)=\sum_{q=0}^n (-1)^q \alpha_q
+\end{equation}
+where $n$ is the dimension of the simplicial complex $K$, $\alpha_q$ is the
+number of $q$-simplexes in $K$. This sections defines the number $\beta_q$ as
+the \textbf{$q$th Betti number of $K$}\nomenclature{$q$th Betti number of $K$,
+$\beta_q$}{\nomrefpage}. It is the rank of free abelian part of $H_q(K)$
+\footnote{
+    recall that every finitely generated abelian group is isomorphic to a direct
+    sum of primary cyclic groups (the torsion part) and infinite cyclic groups
+    (the free part). A primary cyclic group is one whose order is a power of a
+    prime. See more at
+    \href{https://en.wikipedia.org/wiki/Finitely_generated_abelian_group}{wikipedia}.
+}. If we allow, in the definition of homology groups, the coefficients being
+rational, we can form $H_q(K,\Q)$, and we have $\beta_q$ is just the dimension
+of $H_q(K,\Q)$ as a vector space over $\Q$ (lemma (9.9) in \cite{book}). Then
+this section will shows:
+\begin{thm}[Euler-Poincar\'e formula]
+\begin{equation}
+    \chi(K)=\sum_{q=0}^n (-1)^q \beta_q
+\end{equation}
+\end{thm}
+and obviously
+\begin{coro}
+    Simplicial complexes whose polyhedra are homotopy equivalent have the same
+    Euler characteristic.
+\end{coro}

### 2017-01-25 Lecture note - Group Theory in Physics/essay/essay.tex
[major] add essay for course Group theory in Physicists

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\usepackage[
    disable
]{todonotes}
\makenomenclature % For an index of symbols.

% Show the keys for labels, replace options with "final" when done
% with editing.
\usepackage[
    %draft,
    final,
    notref
]{showkeys}
\usepackage{CJKutf8}
\title{Wigner theorem and Time reversal}
\date{\today}
\author{Taper}

\begin{document}
\maketitle

\abstract{
    In this article, we use the Wigner theorem to argue the general behavior of
    a symmetry operator, based on which we will discuss how the time-reversal
    operator should act. And finally, we present the time-reversal operator's
    exact form in spins using results from representations of $SU(2)$.
}
\tableofcontents

% Representative operators and quantum mechanical selection rules 3.6
% Todo: this is my original plan. Finish it if I have time.
% Let $G$ be a group. We discuss how it act on quantum mechanical states and how
% this might determine the structure of quantum mechanics.

\section{Introduction}
\label{sec:Introduction}

We note that quantum mechanical states lives in the Hilbert space
$\mathscr{H}$.  Therefore, a
symmetry will transform the vectors in Hilbert space. But a quantum mechanical
state $\ket{\phi}$ is distinguished from a vector $\phi\in\mathscr{H}$, in that
any nonzero multiple of it $\lambda\phi (\forall \lambda\in\C^*)$, the states it
represent is the same $\ket{\phi}=\ket{\lambda\phi}$. Even when we require that
the vector should be unit, we still have a phase freedom $\lambda=e^{i\theta}$.
Therefore, the action
(i.e. representation) of a symmetry on $\mathscr{H}$ is not so easily obtained.
It should respect this freedom of $\lambda$.

To all reasonable symmetries on the Hamiltonian space $\mathscr{H}$, there is a
theorem discussed below. In a simple word the theorems says that any 
representation of a symmetry group on $\mathscr{H}$ is either unitary or
anti-unitary. The operator $U$ obtained from representation is uniquely
determined if we have fixed some $\phi'=U\phi$, where $\phi'$ is the vector after
a symmetry operation has been performed on $\phi$.

\section{Wigner's Theorem on Symmetry}
\label{sec:Wigner-Theorem}

This theorem is proved on appendix D of \cite{sternberg1995group}. Here I will only
present the theorem and explain how we may interpret and use it physically.

\paragraph{Quantum Mechanical State}
In quantum mechanics, we speak of a state as a vector $\phi$ and often ignore
its length. But if we want to formulate quantum mechanics precisely we will need
to specify a state precisely. Therefore we define a a \nomen{quantum mechanical
state} as a projection $P$ onto a one-dimensional subspace of $\mathscr{H}$.
This coincide with physical description because two vectors in $\mathscr{H}$
represent the same state when they are in the same one-dimensional subspace.
Therefore, we have one-to-one relationships between states, one-dimensional
subspaces, and projections. Explicitly, in Dirac notation, $P=\ket{p}\bra{p}$.
Then we have,
\begin{equation}
    \Tr{PQ} = \sum_n \braket{n|p}\braket{p|q}\braket{q|n} = \braket{p|q}
    \sum_n \braket{q|n}\braket{n|p} = \abs{\braket{p|q}}^2
\end{equation}
In this way, the \nomen{transition probability} of two states $P,Q$, will then
be $\Tr(PQ)$, and is denoted by \nomen{$P\cdot Q$}.

\paragraph{Quantum Mechanical Map}
A quantum mechanical map, $T$, is roughly speaking, a map that does not alter
the physical feature of the system. It is the name that the book
\cite{sternberg1995group} gave to symmetry transformations. In quantum mechanics, the
only thing we can measure is of the form $\abs{\braket{p|q}}^2$, i.e. the
probabilities.  Therefore, a quantum mechanical map is, more precisely, a map
from the states of a Hilbert space $\mathscr{H}$ to the states of a Hilbert
space $\mathscr{H}'$.  such that for any two states $P,Q$, the transition
probability $\Tr{PQ}$ is unchanged:
\begin{equation}
    (TP)\cdot(TQ) = P\cdot Q
\end{equation}

\begin{thm}[Wigner's Theorem]
    Given a quantum mechanical map $T$, there exists a map,
    $U$ from vectors of $\mathscr{H}$ to vectors of $\mathscr{H}'$, such that
    \begin{align}
        P_{U\phi} &= TP_{\phi} \\
        U(\xi+\eta)&=U\xi + U\eta,\text{ for any }\xi,\eta\in\mathscr{H} \\
        \braket{U\xi,U\eta} &= \kappa(\braket{\xi,\eta}) \label{eq:conserv-prob}
    \end{align}
    where $\kappa$ is a function that is either identity
    $\kappa(\lambda)=\lambda$ for $\lambda\in\C$, or is complex conjugate
    $\kappa(\lambda)=\bar{\lambda}$ for $\lambda\in\C$. Also, 
    \begin{equation}
        U(\lambda\xi) = \kappa(\lambda) U\xi,\quad \forall\lambda\in\C
    \end{equation}
\end{thm}

\begin{remark}
    When the quantum mechanical map $T$ is bijective and onto, then the map $U$
    is unitary if $\kappa(\lambda)=\lambda$, or anti-unitary if
    $\kappa(\lambda)=\bar{\lambda}$. For a symmetry $T$, this means that we can
    always find a way to represent it in the form of $U$, an unitary or
    anti-unitary operator.
\end{remark}

But of course the theorem tells us nothing about how to construct this operator
$U$. The proof of it in book\cite{sternberg1995group} did give a construction. Some of it
is explained below.

\textbf{Determine} $\mathbf{\kappa}$:

Assume we have three states $P_1,P_2,P_3$, and so we have three vectors
$\phi_1,\phi_2,\phi_3$ of norm $1$ in $\mathscr{H}$, for each state. Define a
function:
\begin{equation}
    \Delta(P_1,P_2,P_3) \equiv 
        \braket{\phi_1|\phi_2}\braket{\phi_2|\phi_3}\braket{\phi_3|\phi_1}
\end{equation}
This function is obviously independent of the choice of the unit vectors
$\phi_i$, i.e. it is independent of the phase of $\phi_i$.

If $\dim\mathscr{H}=1$, then $\kappa$ is not determined. But there is
really nothing interesting to be considered here.

If $\dim\mathscr{H}>1$, then $\kappa$ is determined by the following equality:
\begin{align}
    \kappa(\Delta(P_1,P_2,P_3)) &= 
    \kappa(
        \braket{\phi_1|\phi_2}\braket{\phi_2|\phi_3}\braket{\phi_3|\phi_1}
    ) \\
    &= \braket{U\phi_1|U\phi_2}\braket{U\phi_2|U\phi_3}\braket{U\phi_3|U\phi_1}
\end{align}
where the second line is determined by the action of $T$.

Note that we can pick $P_1,P_2,P_3$ such that
$\Delta(P_1,P_2,P_3)$ is not real. For example, when $\dim\mathscr{H}=2$, then
$\Delta(P_1,P_2,P_3)$ can be made into the form 
$(\sum_{i=1}^2 x_i^*y_i)(\sum_{i=1}^2 y_i^*z_i)(\sum_{i=1}^2 z_i^*x_i)$. It
is simple to make this not real. In general, we choose two orthogonal unit
vectors $\phi,\psi$ (since $\dim\mathscr{H}>1$), and let $\phi_1=\phi$,
$\phi_2=(\phi-\psi)/\sqrt{2}$, $\phi_3=(\phi+(1-i)\psi)/\sqrt{3}$. Then
\begin{align*}
    \Delta(P_1,P_2,P_3) &=
    \braket{\phi|\frac{\phi-\psi}{\sqrt{2}}}
    \braket{\frac{\phi-\psi}{\sqrt{2}}|\frac{\phi+(1-i)\psi}{\sqrt{3}}}
    \braket{\frac{\phi+(1-i)\psi}{\sqrt{3}}|\phi} \\
    &= \frac{1}{\sqrt{2}}\cdot \frac{1}{\sqrt{6}}(1-1+i)\cdot\frac{1}{\sqrt{3}}
    =\frac{i}{6}
\end{align*}

\textbf{Determine} $\mathbf{U}$:

Initially, $U$ has a phase freedom, i.e., for the same map $T$, $U$ is only
determined up to multiplication of a complex scalar of norm $1$. This can be
seen from equation~\ref{eq:conserv-prob}. But we can fix it by choosing a gauge.

Given any unit vector $\phi\in\mathscr{H}$, and any unit vector
$\phi'\in\mathscr{H}$ with
\begin{equation}
    P_{\phi'}=TP_\phi
\end{equation}
we can always choose $U$ such that
\begin{equation}
    U\phi = \phi'
\end{equation}
And having made such a choice, $U$ will be completely determined.

However, the method given in the proof (in \cite{sternberg1995group}) is in most cases
useless. It proceeds in the mathematician's aspect that we can readily say how the
map $T$ acts on Hilbert space $\mathscr{H}$. But in reality, the method is too
mathematical to be useful. The important thing we can get from above discussion
is that $U$ can be uniquely found when we fixed a gauge. Then, we usually fixed
a basis, and argue physically how the $U\phi$ will be. Below is an example.

\section{Time reversal operator}
\label{sec:Time-reversal-operator}

To get the time reversal operator, we can first look at the following
equality (let $T$ denotes the time reversal operator):
\begin{align}
    \left(1-\frac{iH}{\hbar}\delta t\right) T \ket{\alpha}
    = T\left(1-\frac{iH}{\hbar}(-\delta t)\right)\ket{\alpha}
    \label{eq:TRoper.fromClas2Quam.phyPic}
\end{align}
This follows from the following picture: the time evolution of a time reversed
state is equivalent to the original state at an earlier time. Recall that
$\left(1-\frac{iH}{\hbar}\delta t\right)$ produces an infinitesimal time
translation.

From equality \ref{eq:TRoper.fromClas2Quam.phyPic}, one finds:
\begin{align}
    -iHT = T i H
\end{align}

Wigner's theorem shows that $T$ could either unitary or anti-unitary.
Now we show that \textbf{$T$ must be anti-linear}, hence anti-unitary. Because if
one assumes that $T$ is linear, then we have
$$ TH = -HT $$
Then one will find that the energy spectrum for time
reversal symmetric system will always has symmetric energy spectrum (i.e. with
both positive and negative energy), which is not true.

So we have:
\begin{itemize}
    \item $T$ is anti-unitary
    \item $T H=HT$ for a time reversal symmetric state.
\end{itemize}

Now we write $T= UK$, where $K$ is the complex conjugation operator that
acts only on coefficient and have $K\lambda\ket{\phi} =
\bar{\lambda}\ket{\phi}$.
Be careful that it is highly dependent on the basis
chosen. So $U$ will depend on the basis too. To get $T$ in a
basis $\ket{e_i}$, obviously we only need to consider the result of
$U\ket{e_i}$. This however, is hard to determine. However we can argue
that in case when the basis has some classical connection, then by the
Correspondence Principle we have, for example:
\begin{align}
    T \hat{p} T^{-1}&= -\hat{p} \\
    T \hat{x} T^{-1}&= \hat{x} \\
    T \mathbf{J} T^{-1}&= -\mathbf{J}
\end{align}
with these one can easily find:
\begin{align}
    T \ket{p} &= \ket{-p} \\
    T \ket{x} &= \ket{x} \\
    [x_i, p_j]T \ket{} &= i\hbar \delta_{ij} T\ket{}
\end{align}
where $\ket{}$ stands for any ket. Then clearly, $T$ is just complex conjugation
for wave function $\Psi(x)$. But $T$ acts on $\Psi(p)$ will produces
$\Psi^*(-p)$. The case for eigenstate of spin is a little complicated, which
will be discussed in next section.

\section{Time reversal operator in system with spin 
\texorpdfstring{$j$}{}}
\label{sec:Time-reversal-operator-in-spin-j}

Now label a spin state $\ket{j,m}$, where $j$ is the spin quantum number, and
$m$ is the secondary spin quantum number, where $m=-j,-j+1,\cdot,j$.
Since the commutation relation of Pauli matrices $\sigma$ are the same as the
spin operator $J$, we postulate that representations of $SU(2)$ acts on spin produces
rotations in spins. Also, physically we require that a time-reversal is equal to
a $\pi$ rotation around $y$ axis. Therefore, we have
\begin{align}
    T = \eta D(\vb{e_2},\pi)K
\end{align}
where $\eta$ accounts for the undetermined phase of $T$, $D$ is some
representation of $SU(2)$ and $D(\vb{e_2},\pi)$ is the operator of rotation by $\pi$ in
the $y$ axis. $K$ accounts for the complex conjugation.

If the spin is $j$, when we have, by representation theory of $SU(2)$:
\begin{align}
    T_{\nu\mu} = \eta d^j_{\nu\mu} K
\end{align}
where $d^j_{\nu\mu}(\omega)\equiv D^j_{\nu\mu}(\vb{e_2},\omega)$.

Using this we can prove a very useful formula:
\begin{thm} \begin{align}
    \label{eq:TRoper.TRoper.square_minus}
    T^2=
    \begin{cases}
        -1 & \text{ if $j$ is a half-integer} \\
        1 & \text{ if $j$ is an integer}
    \end{cases}
\end{align} \end{thm}
\begin{proof}
    Using group representation theory, this is almost straightforward to prove.
    Notice that rotation among $y$ axis is determined by the the matrix
    $d^j_{\nu\mu}(\omega)\equiv D^j_{\nu\mu}(\vb{e_2},\omega)$. This matrix is
    real and orthogonal. So
    $$T^2=\eta D(\vb{e_2},\pi) K \eta D(\vb{e_2},\pi) K = \eta\eta^* d^j(2\pi)K^2 = d^j(2\pi)$$
    Note also that $d^j_{\nu\mu}(2\pi) = (-1)^{2j}\delta_{\nu\mu}$. Therefore,
    when $j$ is a half integer, $T^2=-1$, and when $j$ is an integer, $T^2=1$.
\end{proof}

This theorem has a important consequence, as will be shown below:

\begin{thm}[Kramer's theorem]
    For a system with halt-integer $j$ spin, the degree of degeneracy for every
    eigenstate is at least two.
\end{thm}
\begin{proof}
    Let $\ket{n}$ be an energy eigenstate. If the system is time
    reversal symmetric, i.e. $[H,T]=0$, then $T \ket{n}$ is
    another energy eigenstate with the same energy. Supposing there is
    no degeneracy, then we have
    $$ \ket{n} = e^{i\eta}T\ket{n}$$
    for some arbitrary $\eta\in \mathbb{R}$. Apply $T$ on both sides, then
    we have
    \begin{align*}
        e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
        &= T \ket{n} = e^{-i\eta} \ket{n}
    \end{align*}
    Clearly this is a contradiction unless $T^2=1$. But we have shown that
    $T^2=-1$ for half-integer spin. Therefore, 
    $$ \ket{n} \neq e^{i\eta}T\ket{n}$$
\end{proof}

\section{Concluding Remark}
\label{sec:Concluding-Remark}

The proof above is amazingly short, embodying the amazingly powerful application
of group representation theory in quantum mechanics. However, it took some trial
and effort to establish the Wigner theorem and the irreducible representations
of $SU(2)$. Hope we can learn more about group representation in the future.
\nocite{ma2007group}

\todo{improve reference in this doc}
\bibliography{cite}
\bibliographystyle{alpha}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-02-14 Algebra/Noetherian Ring.tex
[minor] Error correction.

@@
 
-\title{Noetherian Ring}
+\title{Algebra}
 \date{\today}
@@
 \abstract{
-    A note about Noetherian Ring, majorly from the book \cite{lang}.
+    A note about Abstract Algebra, majorly from the book \cite{lang}.
 }
 \tableofcontents
+
+\section{Commutator}
+\label{sec:Commutator}
+
+A \nomen{commutator} in a group $G$ is a group element of the form
+$xyx^{-1}y^{-1}$ with $x,y\in G$. Let \nomen{$G^c$} denote the
+subgroup of $g$ generated by all its commutators. This is a group
+because $xyx^{-1}y^{-1}aba^{-1}b^{-1}$
 
@@
 
-\section{Noetherian}
+\section{Noetherian Ring}
 \label{sec:Noetherian}
@@
 (\textbf{pp.415 of \cite{lang}})
-\section{Examples}
+    \subsection{Examples}
     \label{sec:Examples}
@@
         \item The ring of formal power series is \textbf{NOT} Noetherian.
-        See this \href{http://math.stackexchange.com/questions/281597/an-example-of-a-non-noetherian-ufd}{post}
+            See this
+            \href{http://math.stackexchange.com/questions/281597/an-example-of-a-non-noetherian-ufd}{post}:
             \begin{quote}
-        The essential point is that the polynomial ring in infinitely many variables is the ascending union of subrings $K[x_1,\ldots,x_n]$, since any polynomial can involve only finitely-many indeterminates.
-Each of these rings is a UFD, and it is easy to see that a polynomial in which $x_N$ does not appear has only factorizations in which $x_N$ does not appear, again because everything takes place inside some polynomial ring in finitely-many variables.
-But the ring is not Noetherian, because the ideal generated by all the indeterminates is certainly not finitely-generated.
+            The essential point is that the polynomial ring in
+            infinitely many variables is the ascending union of
+            subrings $K[x_1,\ldots,x_n]$, since any polynomial can
+            involve only finitely-many indeterminates. Each of these
+            rings is a UFD, and it is easy to see that a polynomial in
+            which $x_N$ does not appear has only factorizations in
+            which $x_N$ does not appear, again because everything
+            takes place inside some polynomial ring in finitely-many
+            variables. But the ring is not Noetherian, because the
+            ideal generated by all the indeterminates is certainly not
+            finitely-generated.
             \end{quote}

### 2017-02-14 Lecture note - Group Theory in Physics/Group theory and Physics Sternberg/sternberg.tex
[major] new notes about classification of finite subgroups of SO(3).

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{Notes of Group Theory and Physics}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    Notes of Group Theory and Physics written by Sternberg \cite{Sternberg1994}.
}
\tableofcontents

\section{The Classification of the finite subgroups of
\texorpdfstring{$\mathrm{SO}(3)$}{} (1.8)}
\label{sec:Classification-of-finite-subgroups-of-SO3}

Previous section established one important formula for this section. Suppose a
group $G$ acts on a set $M$. Define the \nomen{fix point set}
$\operatorname{FP}(a)$ of an element $a\in G$ as the set of all $m\in M$ such
that $am=m$, i.e. left invariant under $a$. Denote \nomen{$G_m$} for $m\in M$ as the
isotropy subgroup of $m$. Then we have
\begin{equation}
    \sum_{a\neq e} \#\operatorname{FP}(a) =
    \sum_{\text{orbits}}\frac{\#G}{\#G_m}(\#G_m-1)
    \label{eq:fp-orbit-formula}
\end{equation}
The proof is on section 1.7 of \cite{Sternberg1994}.

This section classifies all possible finite subgroups of $\mathrm{SO}(3)$. The
classification of finite subgroups of $\mathrm{O}(3)$ is on the next section.
We basically study the action of $G=\mathrm{SO}(3)$ on $M=S^2$, the unit sphere.
The first interesting discovery is
\begin{thm}[(Euler)]
    When the dimension $n$ is odd, any $a\in \mathrm{SO}(n)$ leaves at least one
    non-zero vector invariant, i.e. any $a\in \mathrm{SO}(n)$, $\Ker(a-I)\neq
    \emptyset$, or there is always a $\vb{v}\neq 0$, such that $a\vb{v}=\vb{v}$.
\end{thm}
This implies that any rotation in odd dimensional space is a rotation about some
fixed axis (since $a\vb{v}=\vb{v}$ implies
$(a\vb{p})\vdot\vb{v}=(a\vb{v})\vdot(a\vb{p})=\vb{v}\vdot\vb{p}=0$).

Then the book analyses the formula counting fix point sets and
orbits~\ref{eq:fp-orbit-formula}. Use new symbols for three numbers:
\begin{table}[H]
    \centering
    \label{tab:three-symbols-for-3-numbers}
    \begin{tabular}{c l}
        $n$ & $=$ $\# G$ \\
        $r$ & $=$ $\text{number of orbits of $G$}$ \\
        $n_i$ & $=$ $\# G_m \text{, where $m\in i$th orbit.}$
    \end{tabular}
\end{table}

Then we have
\begin{equation}
    2-\frac{2}{n} = r-\sum_{1}^{r} \frac{1}{n_i}
\end{equation}

This equation can be simplified by considering the practical numerical values of
$n$, $r$ and $n_i$, with $n_i \leq n$. By eliminating case by case, he finally arrived
at five sets of possible values:
\begin{table}[H]
\centering
\label{tab:label}
\caption{Finite rotation groups}
\begin{tabular}{l l l l l l}
    \hline
    $r$ & $(n_1,n_2,n_3)$ & $\# G$ & Schoenflies & Hermann-Mauguin & Note
    \\
    \hline
    \hline
    2 & (n,n,0) & n & $C_n$ & $n$ & Cyclic group \\
    3 & $(2,2,k), k\geq 2$ & $2k$ & $D_k$ & $222$ for $D_2$, $k2$ otherwise & Dihedral group \\
    3 & $(2,3,3)$ & 12  & $T$  & 23& of regular tetrahedron \\
    3 & $(2,3,4)$ & 24 & $O$ & 432 & of regular octahedron \\
    3 & $(2,3,5)$ & 60 & $I$ & not mentioned & of icosahedron \\
    \hline
\end{tabular}
\end{table}
For details about derivation please visit pp. 28 to 31 of \cite{Sternberg1994}.

But we need to exclude some subgroups from the list of crystallographic groups.
The result is that, on the first row, $n$ is restricted to be $1,2,3,4$ and $6$;
on the second row, $k$ is restricted to be $2,3,4$ and $6$. And $I$ is excluded
from the list of crystallographic groups.

The reason is the common one on Solid States classes about possible space-filling
polygons (see pp.31 of \cite{Sternberg1994}). Also, a good proof about possible
rotation angles in three-dimension for a lattice is provided on pp.31 to 32 of
\cite{Sternberg1994}. The key is that the rotation matrix could be
made of integers, and hence its characteristic (trace) should be an integer.

Next the author mentioned the \nomen{atomic hypothesis}, an interesting
historical account of our view on crystals. The essence is that because only
above mentioned angles occurred in rotational symmetries of crystals, we can
presume that a crystal is not a continuum, but is "built up from discrete
subunits in a regular repetitive pattern" (pp.32).

He also mentions the \nomen{law of rational indices} which found a basis for
modern way of labeling different faces of a lattice (the $(100)$ side, etc.).
But this law is too long to be typed here.

In sum, we have only following finite subgroups of $\mathrm{SO}(3)$ that is
interested for crystals:

$$ C_1, C_2, C_3, C_4, C_6, D_2, D_3, D_4, D_6, T, O $$

\bibliography{cite}
\bibliographystyle{alpha}

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-02-15 Lecture note - Group Theory in Physics/Group theory and Physics Sternberg/sternberg.tex
[major] Note of Sternberg's Group Theory and Physics: about the 32 point groups.

@@
 
-\section{The Classification of the finite subgroups of
+\section{Basic definitions and examples (Ch 1)}
+\label{sec:Basic-def-examples}
+
+    \subsection{The Classification of the finite subgroups of
     \texorpdfstring{$\mathrm{SO}(3)$}{} (1.8)}
-\label{sec:Classification-of-finite-subgroups-of-SO3}
+    \label{sec:Classif-subg-SO3}
 
@@
     \centering
-\label{tab:label}
+    \label{tab:Finite-rot-g}
     \caption{Finite rotation groups}
@@
         3 & $(2,3,4)$ & 24 & $O$ & 432 & of regular octahedron \\
-    3 & $(2,3,5)$ & 60 & $I$ & not mentioned & of icosahedron \\
+        3 & $(2,3,5)$ & 60 & $I$ & not mentioned & of icosahedron, of
+        Fullerene\footnotemark\\
         \hline
@@
     \end{table}
+    \footnotetext{See section 1.10 about Fullerene and icosahedron for details.}
     For details about derivation please visit pp. 28 to 31 of \cite{Sternberg1994}.
-
     But we need to exclude some subgroups from the list of crystallographic groups.
@@
 
+    \subsection{Classification of finite subgroups of
+    \texorpdfstring{$\mathrm{O}(3)$}{}}
+    \label{sec:Classif-subg-O3}
+
+    This section based on the work of previous
+    section~\ref{sec:Classif-subg-SO3}. To use the result of those groups of
+    matrices with $\det=1$ in that section, the author first discuss the
+    example of $T_d$ and $O$.
+
+    $T_d$ is the group of all symmetries(including those that does not preserve
+    the chirality, i.e. with $\det=-1$) of tetrahedron. As abstract groups,
+    $T_d$ and $O$ are all isomorphic to $S_4$, the symmetric group of order $4$.
+    Note that in the context of crystal symmetry, the isomorphic class of group is
+    not enough to characterize a behavior. For example, the $C_2$
+    containing $\pi$ rotation is not the same as $\{e,i\}$ where $i$ is
+    the inversion, but they are isomorphic.\footnote{Perhaps representation
+    classes of groups is more precise in describing the behavior.} The link
+    between $T_d$ and $O$ can be seen from the following:
+
+    \begin{myquote} \enquote{
+    we can consider our tetrahedron as situated inside a cube, with its vertices
+    at the diagonally opposite vertices of each face of the cube. For a given
+    cube there are two such tetrahedra, as shown in Fig. 1.13
+    (Figure~\ref{fig:fig1.13} here).
+    One tetrahedron is carried into the other by the inversion, $-I$.
+    } \end{myquote}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\linewidth]{pics/{fig1.13}.png}
+        \caption{Fig 1.13 in \cite{Sternberg1994}, with modification}
+        \label{fig:fig1.13}
+    \end{figure}
+
+    Written mathematically, we have
+    \begin{equation}
+        T_d = S_4 = T\cup T'
+    \end{equation}
+    where $T$ is mentioned in Table~\ref{tab:Finite-rot-g}. And $T'$ contains
+    those matrices with $\det=-1$.
+    \begin{equation}
+        T_d \overset{\phi}{\cong} O
+    \end{equation}
+    where $\phi$ is defined as
+    \begin{align*}
+        A \to A\quad &\text{for }A\in T \\
+        B \to -B\quad &\text{for }B\in T'
+    \end{align*}
+
+    In general case, for a finite subgroup $G$ of $\mathrm{O}(3)$, we have the
+    following. Let $G_+$ denote the subgroup of $G$ with positive determinant.
+    Let $G_-$ denote the set of elements of $G$ with negative determinant. We
+    have two cases.
+
+    Case 1, $-I\in G_-$, then $G_-=(-I)G_+$, and the structure is simple.
+
+    Case 2, $-I\notin G_-$. Then the author defines $G^\vee:=G_+\cup (-I)G_-$,
+    and shows that 
+    \begin{align}
+        G^\vee &= G_+ \cup aG_+ \\
+        G_- &= (-I)aG_+
+    \end{align}
+    where $a$ is some matrix in $G^\vee\setminus G_+$.
+
+    Then,
+    \begin{myquote} \enquote{
+    From the $11$ rotation groups listed at the end of the preceding section, we
+    obtain $11$ non-rotation groups by including $-I$. In addition, we must check for
+    the normat subgroups of index two in each rotation group in order to
+    construct non-rotation groups which do not include $-I$.
+    } \end{myquote}
+
+    The rest of this section carries out this analysis, culminating in the
+    table~ 4 on pp. 40 of \cite{Sternberg1994}. I reproduce the table with some
+    addition in the Table~\ref{tab:point-g-32}.
+
+    \begin{table}[H]
+        \centering
+        \caption{The $32$ point groups}
+        \label{tab:point-g-32}
+        \includegraphics[width=1\linewidth]{pics/table4-32-point-group.png}
+    \end{table}
+
+    The detailed derivation could be found on pp.35 to 39 of
+    \cite{Sternberg1994}. Note that $S^6\neq S_6$, and $S^4\neq S_4$. Here is
+    some explanations for subscripts: 
+    \begin{table}[H]
+    \centering
+    \begin{tabular}{c l}
+        $h$: & there is a horizontal reflection plane. \\
+        $v$: & there is a vertical reflection plane. \\
+        $d$: & there is diagonal vertical planes. \\
+        $m$: & there is a vertical mirror plane (in H-M notation). \\
+        $/m$: & there is a horizontal mirror plane (in H-M notation).
+    \end{tabular}
+    \end{table}
+
+    Note also that the online engine WolframAlpha is a very good source for
+    details about certain groups. For example, this
+    \href{http://m.wolframalpha.com/input/?i=crystallographic+point+group+C4h}{link}
+    is a good description of group $S^4$ (thouhg it is denoted $S_4$ on the
+    webpage). Searching "crystallographic point group C4h" will get one a good
+    \href{http://m.wolframalpha.com/input/?i=crystallographic+point+group+C4h}{description}
+    of $C_{4h}$. One can also found the book reference from that page by
+    clicking the "Source information" link.
+
+    Then the author goes on to mention some historical methods in "determination
+    of the actual symmetry groups of a given substance", "available to 19th
+    century crystallographers". One method is "to attack the crystal with an
+    acid, and to study the etch figures induced on the faces".  Another is to
+    study the "piezoelectricity", or to test the "rotatory optical activity".
+
+    He also gives a helpful graphical display of $32$ point groups in Fig 1.19
+    on \cite{Sternberg1994}(from pp.42 to 44), which is too long to be included
+    here.
 \bibliography{cite}

### 2017-02-17 QFT/Quantum field theory in CMP-Nagaosa-Note/QFT Nagaosa Note.tex
[minor] some notes about Nagaosa's book.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\makenomenclature % For an index of symbols.

\title{Quantum Field Theory in Condensed Matter Physics}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
This is my study notes of various books, listed in the reference.
\nocite{Nagaosa1999}
}
\tableofcontents

\section{Second Quantization}
\label{sec:Second-Quantization}

The \cite{Nagaosa1999} introduces second quantization in a heuristic, non-rigorous
way. It starts from conjecturing that

\begin{itemize}
    \item $N_n\approx \hat{N}_n$,

        $N_n$ represents $N_n$ times repreatance of the experiments done in on a
        single particle. $\hat{N}_n$ represents the results from one experiments
        done on a system of $\hat{N}_n$ non-interacting particles.

        This equality means that we expect these two kinds of experiments to be
        approximately equivalent.
\end{itemize}

With such spirit, we first examine the single-particle state and tries to
promote something to many-body picture. In single particle state, we have
\begin{equation}
    \psi(\vb{r},t) = \sum_n a_n(t) \phi_n(\vb{r})
\end{equation}
as decomposing any wave function into orthonormal basis and concentrate the
dynamics property on the coefficients $a_n(t)$. And we could found
\footnote{Eq (1.2.5) to eq(1.2.10) of \cite{Nagaosa1999}}
\begin{align}
    \frac{\dd a_n(t)}{\dd t} &= 
        \frac{\partial \braket{\hat{H}}}{\partial (i\hbar a^*_n)} \\
    \frac{\dd (i\hbar a_n^*(t))}{\dd t} &= 
        -\frac{\partial \braket{\hat{H}}}{\partial a_n}
\end{align}
where $\braket{H}=\braket{\psi|H|\psi}$. 
These equations are analogous to Hamilton's canonical equations with $a_n
\Leftrightarrow x$, and $i\hbar a^*_n\Leftrightarrow p$. Then propose that we
can promote $a_n$ and $a_n^*$ as operators. The promotion is not analysed but we
can give a quick analogy as:

\begin{itemize}
    \item $N_n\equiv N\abs{a_n}^2$ is promoted to $\hat{N_n}$, which is an
        observable that counts the total number of particles in state $n$.
    \item $\sqrt{N}a_n \rightarrow \hat{A}_n$,
        $\sqrt{N}a^*_n\rightarrow\hat{A}_n^\dagger$. So that
        $\hat{N}_n=\hat{A}_n^\dagger\hat{A}_n$.
\end{itemize}

And 
\begin{equation}
    \begin{cases}
        [\hat{A}_n,\hat{A}_m^\dagger] = \delta_{n,m},
        [\hat{A}_n,\hat{A}_m]=[\hat{A}_n^\dagger,\hat{A}_n^\dagger]=0,& \text{for bosons} \\
        \{\hat{A}_n,\hat{A}_n^\dagger\} = \delta_{n,m},
        \{\hat{A}_n,\hat{A}_m\}=\{\hat{A}_n^\dagger,\hat{A}_n^\dagger\}=0,& \text{for fermions}
    \end{cases}
\end{equation}
and many other usual commutative/anti-commutative relations.

The \textit{wave picture} starts from promoting $\psi$ and $\psi^*$ into
\nomen{field operators}:
\begin{align}
    \hat{\psi}(\vb{r}) &\equiv \sum_n \hat{A}_n \phi_n (\vb{r}) \\
    \hat{\psi}^\dagger(\vb{r}) &\equiv \sum_n \hat{A}_n^\dagger \phi_n^* (\vb{r})
\end{align}
This definition is again analogous to the single particle picture.
Calculation\footnote{Page 15 of \cite{Nagaosa1999}} shows for bosons
\begin{align}
    [\hat{\psi}(\vb{r}),\hat{\psi}^\dagger(\vb{r}')] &= \delta(\vb{r}-\vb{r}') \\
    [\hat{\psi}(\vb{r}),\hat{\psi}(\vb{r}')] &=
        [\hat{\psi}^\dagger(\vb{r}),\hat{\psi}^\dagger(\vb{r}')] = 0
\end{align}
with commutators $[]$ replaced with anti-commutators $\{\}$ for fermions. The
\nomen{particle density operator} is defined as
$n(\vb{r})=\hat{\psi}^\dagger(\vb{r})\hat{\psi}(\vb{r})$. 
and the rest are old things.

The operator new to me is the \nomen{phase operator} $\hat{\theta}_n$ for bosons
\footnote{The phase for fermions is complicated and is delegated to the task of
chapter 5 of \cite{Nagaosa1999}.}. It has the property that:
\begin{align}
    \hat{A}_n^\dagger &= \sqrt{\hat{N}_n} e^{-i\hat{\theta}_n/\hbar} \\
    \hat{A}_n         &= \sqrt{\hat{N}_n} e^{i\hat{\theta}_n/\hbar} \\
    [\hat{N}_n,\hat{\theta}_n] &= i\hbar \label{eq:Ntheta}
\end{align}
It is shonw that equation~\ref{eq:Ntheta} leads to
$[\hat{A}_n,\hat{A}_n^\dagger]=1$. It is shown also that
\begin{align}
    \exp(\frac{i}{\hbar}\hat{\theta}_n) (\hat{N}_n)^m
        \exp(-\frac{i}{\hbar}\hat{\theta}_n) &= (\hat{N}_n+1)^m \\
    \exp(\frac{i}{\hbar}\hat{\theta}_n) \ket{N_n} &\propto \ket{N-1}
    \label{eq:eithetaN}
\end{align}
It is concluded, because of the above equation~\ref{eq:eithetaN} and that there
is not state $\ket{-1}$, the $\hat{\theta}_n$ \textit{is not Hermitian}.
\footnote{See page 17 of \cite{Nagaosa1999}}

\bibliography{cite}
\bibliographystyle{alpha}

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-02-17 Lecture note - Group Theory in Physics/group theory in physics.tex
Minor modification to C.V. Create a new latex example file. Begin reading lang's representaton theory for group theory in physics.
Adding scanned notes about group "D_n" and "C_n" to group theory notes.
Split Lang's representation theory away from lecture notes. Noting about section 18.1 of Lang's representation of finite groups.
A temporary note for new class - mainly about Wigner- Theorem. Also, some minor modification for my C.V.
[minor] Uploading some missing notes about Group theory in Physics.

--- 2016-10-31 Lecture note - Group Theory in Physics/group theory in physics.tex
@@
 
+% Show the keys for labels, replace options with "final" when done
+% with editing.
+\usepackage[draft,notref]{showkeys}
+
+% Resolve pdf version warning
+\pdfoptionpdfminorversion=6
+
 \title{Group Theory in Physics (Course Note)}
@@
 \input{sections/20161031}
+
+\section{20161107}
+\label{sec:20161107}
+\input{sections/20161107}
+
+\section{Point Group}
+\label{sec:Point-Group}
+\input{sections/point-group}
+
+\section{20161121}
+\input{sections/20161121}
+\section{20161128}
+\label{sec:20161128}
+After some work, I realize that it is impractical to follow the
+teacher's class with notes. Therefore I will write here just some
+important formulae, as a preparation for exams.
+
+Pauli matrices
+\begin{align}
+    &\sigma_1 =\begin{pmatrix}
+        0 & 1\\ 1 & 0
+    \end{pmatrix}\\
+    &\sigma_2 = \begin{pmatrix}
+        0& -i \\ i & 0
+    \end{pmatrix} \\
+    &\sigma_3 = \begin{pmatrix}
+    1 & 0 \\ 0 & -1
+    \end{pmatrix}\\
+    &\sigma_a \sigma_b = \delta_{ab} \id + i\sum_c
+    \varepsilon_{abc}\sigma_c \\
+    &\Tr{\sigma_a} =0 \\
+    &\Tr{\sigma_a \sigma_b} =2\delta_{ab} \\
+    &\exp{-i\omega \sigma_2} =\id \cos{\omega}-i\sigma_2\sin{\omega}
+    = \begin{pmatrix}
+        \cos{\omega} & -\sin{\omega} \\
+        \sin{\omega} & \cos{\omega}
+    \end{pmatrix} \\
+    &R(\vec{e_3},\omega)= \exp{-i\omega T_3}= \begin{pmatrix}
+        \cos{\omega} & -\sin{\omega} & 0 \\
+        \sin{\omega} & \cos{\omega} & 0 \\
+        0 & 0 & 1
+    \end{pmatrix},\quad T_3 = \begin{pmatrix}
+        0 & -i & 0 \\
+        i & 0 & 0 \\
+        0 & 0 & 0
+    \end{pmatrix} \\
+    & R(\vec{e}_1,\omega) = \exp{-i\omega T_1} = \begin{pmatrix}
+        1 & 0 & 0 \\
+        0 & \cos{\omega} & -\sin{\omega} \\
+        0 & \sin{\omega} & \cos{\omega} 
+    \end{pmatrix},\, T_1 = \begin{pmatrix}
+        0 & 0 & 0 \\
+        0 & 0 & -i \\
+        0 & i & 0
+    \end{pmatrix}\\
+    & R(\vec{e}_2,\omega) = \exp{-i\omega T_2} = \begin{pmatrix}
+        \cos{\omega} & 0 & \sin{\omega} \\
+        0 & 1 & 0 \\
+    -\sin{\omega} & 0 & \cos{\omega} 
+    \end{pmatrix},\, T_2 = \begin{pmatrix}
+        0 & 0 & i \\
+        0 & 0 & 0 \\
+        -i & 0 & 0
+    \end{pmatrix}\\
+    & (T_a)_{bc}= -i\varepsilon_{abc} \\
+    & S(\phi,\theta) = \begin{pmatrix}
+    \cos{\phi}\cos{\theta} & -\sin{\phi} & \cos{\phi}\sin{\theta} \\
+    \sin{\phi}\cos{\theta} & \cos{\phi} & \sin{\phi}\sin{\theta} \\
+    -\sin{\theta} & 0 & \cos{\theta}
+    \end{pmatrix} \\
+    & S(\phi,\theta) \begin{pmatrix}
+        0 \\ 0 \\ 1
+    \end{pmatrix} = \begin{pmatrix}
+        \cos{\phi}\sin{\theta} \\ \sin{\phi}\sin{\theta} \\ \cos{\theta}
+    \end{pmatrix} = \begin{pmatrix}
+        n_1 \\ n_2 \\ n_3
+    \end{pmatrix}\\
+    & R(\vec{n},\omega) =
+        S(\phi,\theta)R(\vec{e_3},\omega)S(\phi,\theta)^{-1}
+        =\exp{-i\omega\vec{n}\vdot\vec{T}}
+        = \exp{-i\sum_a \omega_a T_a} \\
+    & R(\vec{n},\omega) = R(-\vec{n},2\pi-\omega) \\
+    & S T_3 S^{-1} = \vec{n}\vdot\vec{T}
+\end{align}
+\begin{fact}
+    The character $\chi$ of $SO(3)$ is a function of $\omega$ only. In
+    fact:
+    \begin{equation}
+        \chi(R(\vec{n},\omega)) = 1+2\cos{\omega}
+    \end{equation}
+\end{fact}
+\begin{enumerate}
+    \item $R\in G$, $\# G=g$
+
+        $ R(1):=R(r_1,r_2,\cdot,r_g)$
+    \item $R(r)S(s)=T(t)$,
+
+        $f(r,s)=t$, $f:(Space)\otimes(Space)\to (Space)$.
+
+        $t_j = f_j(r_1,\cdot,r_g,s_1,\cdot,s_g)=f_j(r,s)$
+\end{enumerate}
+
+\begin{align}
+    & P_R\psi(x)=\psi(R^{-1}x) \\
+    & I^{(0)}_j = -i\sum_a 
+        \eval{\frac{\partial (Ax)_a}{\partial \alpha_j}}_{\alpha=0}
+        \frac{\partial }{\partial x_a} \\
+    & P_A\psi(x) = \psi(x)-i\sum_{j=1}^g \alpha_j I^{(0)}_j\psi(x)
+\end{align}
 \section{Anchor}

### 2017-02-21 Draft/sections/misc-math.tex
Add the Zassenhaus formula for exponential of operators.
[major] Notes about a trick to calculate Jacobi matrix (det(A)=1+tr(A)).

@@
     (My notation is non-standard, but I think it expresses the idea).
+
+\subsection{Matrix Operations}
+    \subsubsection{Matrix Exponentials}
+    \label{sec:Matrix-Exponentials}
+    I found these formulae from Wikipedia page:
+    \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
+    \paragraph{The Zassenhaus formula}
+    \begin{align}
+        e^{t(X+Y)} &= e^{tX}~ e^{tY} ~e^{-\frac{t^2}{2} [X,Y]} ~
+        e^{\frac{t^3}{6}(2[Y,[X,Y]]+ [X,[X,Y]] )} \nonumber\\
+        & \times
+          e^{\frac{-t^4}{24}([[[X,Y],X],X] + 3[[[X,Y],X],Y] + 3[[[X,Y],Y],Y]) }
+        \times\cdots
+    \end{align}
+
+    \paragraph{Logarithm of Matrix}
+    The logarithm of  a matrix $A$ is defined when there is a matrix $B$ such that
+    $e^B=A$, then $\ln(A)=B$.
+
+    Using this, we have a formula to calculate the determinant of a some special
+    matrix.
+
+    Let $A = I + B$, and suppose $\det(A)\neq
+    0$. Then, we have:
+    \begin{equation}
+        \det(A) = \exp(\tr(\ln(A)))
+    \end{equation}
+    Since $\exp{\sum_i \ln(\lambda_i)} = \Pi_i \exp(\ln(\lambda_i))=\Pi_i
+    \lambda_i=\det(A)$.
+
+    Next, we recap several series:
+    \begin{align*}
+        \ln(1+x) &= \sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n}x^n \\
+        \exp(x) &= \sum_{n=0}^{\infty} \frac{x^n}{n!}
+    \end{align*}
+    Then we start the calculation:
+    \begin{align*}
+        \ln(I+B) &= \sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n}B^n \\
+        \tr(\ln(I+B)) &= \sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n}\tr(B^n) \\
+        \det(A) &= \exp(\tr(\ln(I+B))) 
+            = \exp(\sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n}\tr(B^n)) \\
+            &\approx 1+ \sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n}\tr(B^n) \\
+            &\approx 1+ \tr(B)
+    \end{align*}
+
+    Therefore, we have, for appropriate matrix $B$:
+    \begin{thm}
+    \begin{equation}
+        \det(A) \equiv \det(I+B) \approx 1+\tr(B)
+    \end{equation}
+    \end{thm}
+
+    A typical situation is that $A$ is the transformation matrix:
+    \begin{equation}
+        A^\mu_\nu = \frac{\partial x'_\mu}{\partial x_\nu} 
+        = \delta^\mu_\nu + \text{(first order matrix $B$)}^\mu_\nu
+    \end{equation}

### 2017-02-21 Condensed Matter Field Theory note/CMF-Atland.tex
[MAJOR] Initiate notes about Condensed Matter Field Theory.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{Condensed Matter Field Theory notes}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
Notes of book \cite{Altland2010a}.
}
\tableofcontents

\section{pp.33 eq.1.43}
\label{sec:Table}

In page 33 of \cite{Altland2010a}, the author derives a difference of action, when we
have a symmetry transformation paraterized by $\omega_a$:

\begin{align}
    x_\mu \to x'_\mu &= x_\mu + \frac{\partial x_\mu}{\omega_a}|_{\omega=0} \omega_a(x) \\
    \phi^i(x) \to \phi'(x') &= \phi^i(x) + \omega_a(x)F^i_a[\phi]
\end{align}

We have:
\begin{align}
    \mathcal{L} &= \mathcal{L}(\phi^i(x),\partial_{x_\mu}\phi^i(x)) \\
    \mathcal{L}' &= \mathcal{L'}(\phi'^i(x'),\partial_{x'_\mu}\phi'^i(x')) \\
    &= \mathcal{L}\left(\phi^i+F^i_a\omega_a, 
                    \left(\delta_{\mu\nu}-\partial_{x_\mu}(\omega_a
                    \partial_{\omega_a}x_\mu)\right)
                    \partial_{x_\nu}(\phi^i+F^i_a\omega_a)
                  \right)
\end{align}
And

\begin{align}
    \Delta S &= \int \dd[m]{x'} \mathcal{L}' - \int \dd[m]{x} \mathcal{L} 
    \label{eq:dS-integrand}\\
    &=
    \int \dd[m]{x}
    \left(1+\partial_{x_\mu}\left(\omega_a \partial_{\omega_a}x_\mu\right) \right) 
    \nonumber\\
    &\times \mathcal{L}\left(
                    \phi^i+F^i_a\omega_a, 
                    \left(\delta_{\mu\nu}-\partial_{x_\mu}\left(\omega_a
                        \partial_{\omega_a}x_\mu\right)\right)
                        \partial_{x_\nu}(\phi^i+F^i_a\omega_a)
                    \right) \nonumber\\
    &- \int \dd[m]{x}  \mathcal{L}(\phi^i(x),\partial_{x_\mu}\phi^i(x))
\end{align}

Then he argues that, "for constant parameters $\omega_a$ the action difference
$\Delta a$ vanishes". Therefore "the leading contribution to the action
difference of a symmetry transformation must be linear in the derivative
$\partial_{x_\mu}\omega_a$".

Then he writes that "A straightforward expansion of the formula above
for $\Delta S$ shows that these terms are given by"

\begin{equation}
    \Delta S = -\int \dd[m]{x} j^a_\mu (x) \partial_{x_\mu}\omega_a
\end{equation}
where $j^a_\mu$ is:
\begin{equation}
    j^a_\mu = \left(
        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
            \partial_{x_\nu}\phi^i
        -\mathcal{L}\delta_{\mu\nu} \right) \frac{\partial x_\nu}{\partial\omega_a}
    - \frac{\partial\mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)} F^i_a
\end{equation}

I am partically confused about how to do the "straightforward expansion". I
guess I should do $\frac{\partial}{\partial (\partial_{x_\mu}\omega_a)}$ to the
integrand inside expression for $\Delta S$, though I don't really understand the
reason. Even so, the integrand contains terms like
$\partial_{x_\mu}\partial_{\omega_a}x_\mu$, which I don't know how to deal with.

\textbf{Solution}. The reality is a bit more complicated. We first do a first
order expasion to get the infinitesimal difference:

\begin{align}
    &\mathcal{L}'-\mathcal{L} \\
    \approx &
    \frac{\partial \mathcal{L}}{\partial\phi^i} F^i_a\omega_a
    +\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
        \left[
        \partial_\mu\left(F^i_a\omega_a\right) 
            - \partial_\mu\left(\omega_a\frac{\partial x_\nu}{\partial\omega_a}\right)
                \partial_\nu\left(\phi^i+F^i_a\omega_a\right)
        \right]
    \nonumber\\
    =&\quad
    \omega_a
    \left[
        \frac{\partial \mathcal{L}}{\partial\phi^i}F^i_a 
        +
        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
        \left(
            \partial_\mu F^i_a 
            - \partial_\mu(\frac{\partial x_\nu}{\partial \omega_a})
            \partial_\nu(\phi^i+F^i_a\omega_a)
        \right)
    \right]
    \label{eq:l-l-omega}
    \\
    +&
    \partial_\mu\omega_a
    \left[
        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
        \left(
            F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
            \partial_\nu(\phi^i+F^i_a\omega_a)
        \right)
    \right]
    \label{eq:l-l-pmu-omega}
\end{align}

We also discover the integrand in Eq.\ref{eq:dS-integrand} to be
\begin{align}
    &\left(1+\partial_\mu(
        \omega_a\frac{\partial x_\mu}{\partial \omega_a})
        \right)\mathcal{L}'-\mathcal{L} 
    \\
    =& 
    \left(
    1+\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})
    \right)
    (\mathcal{L}'-\mathcal{L})
    +
    \left(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})\right)
    \mathcal{L}
    \label{eq:integrand-l-density}
\end{align}
For the first term 
$\left(
    1+\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})
\right) (\mathcal{L}'-\mathcal{L}) $, the $(\mathcal{L}'-\mathcal{L})$ already
has terms of first order of $\omega_a$ and of first order of
$\partial_\nu\omega_a$. For our purpose, the second order terms
($\partial_\nu(F^i_a\omega_a)$) from item \ref{eq:l-l-omega} and item
\ref{eq:l-l-pmu-omega} can be ignored. Also, the item
$(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial
\omega_a}))(\mathcal{L}'-\mathcal{L})$ in eq.\ref{eq:integrand-l-density} can
also be ignored.

Therefore the integrand in Eq.$\ref{eq:dS-integrand}$ becomes

\begin{align}
    & (\mathcal{L}'-\mathcal{L})
    +
    \left(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})\right)
    \mathcal{L} \\
    = & 
    \omega_a
    \left[
        \frac{\partial \mathcal{L}}{\partial\phi^i}F^i_a 
        +
        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
        \left(
            \partial_\mu F^i_a 
            - (\partial_\mu\frac{\partial x_\nu}{\partial \omega_a})
            \partial_\nu(\phi^i+F^i_a\omega_a)
        \right)
        +
        (\partial_\nu \frac{\partial x_\mu}{\partial \omega_a})\mathcal{L}
    \right]
    \\
    +&
    \partial_\mu\omega_a
    \left[
        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
        \left(
            F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
            \partial_\nu(\phi^i+F^i_a\omega_a)
        \right)
        +
        \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L}
    \right]
\end{align}

Therefore, the term we seek, i.e. the coefficient of $\partial_\mu\omega_a$ is
\begin{align}
  & \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
    \left(
        F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
        \partial_\nu(\phi^i+F^i_a\omega_a)
    \right)
    +
    \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L} \\
    =&
    \left(
        \mathcal{L}\delta_{\mu\nu}
        -\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
            \partial_\nu \phi^i
    \right) \frac{\partial x_\nu}{\partial \omega_a}
    +
    \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}F^i_a
\end{align}
which is what we expect in equation 1.43 of \cite{Altland2010a}.

\textbf{Question}: as for why we should ignore the term with $\omega_a$, there
are two posts (
    \href{http://physics.stackexchange.com/questions/122965/derivation-of-the-noether-current}{[1]},
    \href{http://physics.stackexchange.com/questions/99853/on-a-trick-to-derive-the-noether-current}{[2]} )
might be useful for a thought.

\bibliography{cite}{}
\bibliographystyle{alpha}

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-02-28 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Notes about a troublesome calculation in Condensed Matter Field Theory.

@@
 
+\todo{confusion}
+
+I had great doubt about this problem. Though I have posted an answer on
+\href{http://physics.stackexchange.com/questions/122965/derivation-of-the-noether-current}{[1]},
+I don't think that answer is satisfactory.
+
+\section{Eq. 3.5}
+
+It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010a}. Here is my
+notes.
+
+According to the book, Eq.3.3 is turned into (I set $\hbar=1$ occasionally,
+though sometimes I forgot that I have set $\hbar=1$, orz):
+\begin{align}
+    \bra{q_f} 
+    &\int \dd{q_N}\dd{p_N}\ket{q_N}\braket{q_N|p_N}\bra{p_N}
+        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t}\times \nonumber\\
+    &   \int \dd{q_{N-1}}\dd{p_{N-1}}\ket{q_{N-1}}\braket{q_{N-1}|p_{N-1}}\bra{p_{N-1}}
+        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \times
+        \dots \nonumber\\
+    &   \int \dd{q_1}\dd{p_1}\ket{q_1}\braket{q_1|p_1}\bra{p_1}
+        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \ket{q_i}
+\end{align}
+Notice that
+\todo{T has only p, V has only q}
+\begin{align}
+    \braket{q|p} &= \frac{\exp(iqp/\hbar)}{\sqrt{2\pi\hbar}} \\
+    \bra{p_N}e^{-i\hat{T}\Delta t} &= \bra{p_N}e^{-iT(p_N)\Delta t} \\
+    e^{-i\hat{V}\Delta t}\ket{q_{N-1}} &= e^{-iV(q_{N-1})\Delta t}\ket{q_{N-1}} \\
+\end{align}
+Also, 
+\begin{align}
+    &\braket{q_N|p_N}\bra{p_N}e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t}\ket{q_{N-1}} 
+    = \frac{e^{iq_N p_N/\hbar}}{\sqrt{2\pi\hbar}}
+        \bra{p_N}e^{-iT(p_N)\Delta t} e^{-iV(q_{N-1})\Delta t}\ket{q_{N-1}}
+    \nonumber\\
+    =& \frac{e^{iq_N p_N/\hbar}}{\sqrt{2\pi\hbar}}
+        \braket{p_N | q_{N-1}}e^{-iT(p_N)\Delta t} e^{-iV(q_{N-1})\Delta t}
+    = \frac{e^{ip_N (q_N-q_{N-1})/\hbar}}{2\pi\hbar}
+        e^{-i[T(p_N)+V(q_{N-1})]\Delta t} 
+\end{align}
+etc. Now we have to pay special attentiont to the start and end. For the start,
+we have a
+$$ \int \dd{q_N} \braket{q_f | q_N} = \int\dd{q_N}\delta(q_N-q_f) $$
+So every $q_N$ is replaced by $q_f$. For the end, we have
+$$ \braket{q_1|p_1}\bra{p_1}e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \ket{q_i}
+= e^{-i[T(p_1)+V(q_i)]}\frac{e^{ip_1(q_1-q_i)}}{2\pi\hbar}
+$$
+
+Together we have the whole thing into:
+
+\begin{align}
+    \int & \dd{q_1}\cdots\dd{q_{N-1}}\dd{p_1}\dd{p_N} \frac{1}{(2\pi\hbar)^N}
+    \times \nonumber\\
+  & e^{i\left[p_1(q_1-q_i)+\cdots p_N(q_N-q_{N-1})\right]} \times\nonumber\\
+  & e^{-i\left[T(p_1)+\cdots+T(p_N)+V(q_i)+V(q_1)+\cdots+V(q_{N-1})\right]}
+\end{align}
+which is exactly eq.(3.5) in book.
+\section{Eq 9.4}
+
+The Hamiltonian for particle on a ring is claimed to be (Eq. 9.1 of
+\cite{Altland2010a}, pp. 498):
+\begin{equation}
+    H = \frac{1}{2}(-i\partial_\phi -A)^2 = \frac{1}{2}(p-A)^2
+\end{equation}
+
+The book \cite{Altland2010a} claims that 
+\begin{equation}
+    L = \frac{1}{2}\dot{\phi}^2 - iA \dot{\phi}
+\end{equation}
+I am quite confused, especially about the appearance of $\dot{\phi}$. Can any explain
+a bit?
+
+How I tried: Since the inverse of a Legendre transformation is Legendre
+transformation itself, 
+\begin{align}
+    \text{Denote }x &\equiv \frac{\partial H}{\partial p} = p-A,\text{ so,} \\
+    p &= x + A,\quad H = \frac{1}{2}x^2 ,\text{ so,}\\
+    L = x p - H &= x(x+A) - \frac{1}{2}x^2 = \frac{1}{2}x^2 + x A 
+\end{align}
+So my calculation found that the Lagrangian of above Hamiltonian is:
+\begin{equation}
+    L = \frac{1}{2}x^2 + x A
+\end{equation}
+where
+\begin{equation}
+    x = \frac{\partial H}{\partial p}
+\end{equation}
+
 \bibliography{cite}{}

### 2017-02-28 Draft/draft.tex
New notes in Draft, about a specific function.
Minor updates to physicist-taper.sty. Adding some pitfalls to math in Draft.
[minor] Calculate Stirling's formula using saddle point method.

@@
 
-\usepackage{float}  % For H in figures
-\usepackage{amsmath, amssymb} % For math
-\usepackage{bbm} % for numbers with mathbb
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % For bibligraphy
-\usepackage{fancyref} % For lazy reference \fref
-\usepackage[unicode]{hyperref} % For hyperlink everything.
-\usepackage{CJKutf8} % For Chinese characters
-%\usepackage{ dsfont } % For double struck fonts
-\usepackage{braket} 
-\usepackage[T1]{fontenc}
-\usepackage{listings}
+% For drawing category diagrams
+% TODO: Clear the place where I used this obsolete XY-pic package
+\usepackage[all]{xy}
 
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-
-\usepackage{tensor}  % For tensor indices
-\usepackage[all]{xy} % For drawing category diagrams
-\usepackage{mathrsfs}
+% My own physics package
+% The following line load the package xparse with additional option to
+% prevent the annoying warnings, which are caused by the package
+% "physics" loaded in package "physics-taper".
+\usepackage[log-declarations=false]{xparse}
+\usepackage{physicist-taper}
 
@@
 % This is just an anchor for seperating thebibliography from above contents.
-\begin{thebibliography}{1}
-	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
-	\bibitem{BSCS} 
-        Bosonization and Strongly Correlated Systems. Cambridge.
-        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}
+\bibliographystyle{alphaurl}
+\bibliography{cite}
 
-    \bibitem{DETA} Martin Braun. Differential Equations and Their
-    Applications. 4ed. Springer.
-    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
-    \bibitem{griffiths-EM} Introduction to Electrodynamics, 3rd,
-    Griffiths
-\end{thebibliography}
 \section{License}

### 2017-02-28 Draft/sections/misc-math.tex
[minor] Some Corrrections of typo.
[minor] Calculate Stirling's formula using saddle point method.

@@
 $\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
+
+\subsection{Gamma Function and Stirling's formula with Stationary phase
+approximation/Saddle point approximation}
+
+The Gamma Function for $z\in\C$ with a positive real part is
+
+\begin{equation}
+    \Gamma(z+1) = \int_0^\infty \dd{x} x^z e^{-x}
+\end{equation}
+
+It has an approximation formula called the Stirling formula. Here I obtain the
+Stirling formula with the Saddle point approximation, also called Stationary
+phase approximation in pp.108 of \cite{Altland2010}.
+
+Let us further restrict $z$ into $z\in\R$ and $z>0$, the natural logarithm $\ln(z)$ is well
+defined, so we have
+
+\begin{equation}
+    \int_0^\infty \dd{x} x^z e^{-x} = 
+    \int_0^\infty \dd{x} e^{\ln(x^z)} e^{-x} = 
+    \int_0^\infty \dd{x} e^{\ln(x^z)-x} 
+\end{equation}
+
+Let $F(x,z) = -(\ln(x^z)-x)$, then $\frac{dF}{dx}(x_0)=-\frac{z}{x_0}+1=0$ gives the
+saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z>0$
+confirms that this is really a minimum point. Therefore, the integration is
+largely determined by the value around point $x_0=z$. Expanding $F$ around
+$x_0=z$, we have
+\begin{equation}
+    F(x_0 + y)\approx F(x_0=z) + \frac{1}{2z} y^2 
+    = z-\ln(z^z) + \frac{1}{2z}y^2
+\end{equation}
+Therefore
+\begin{align}
+    \int_0^\infty \dd{x} e^{\ln(x^z)-x} &= 
+    \int_0^\infty \dd{x} e^{-F(x,z)} \approx
+    \int_{-z}^\infty \dd{y} e^{-z+\ln(z^z) - \frac{1}{2z}y^2}
+\end{align}
+
+Now as $z\to\infty$, we have
+\begin{align}
+    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
+    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
+    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
+    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
+    = (\frac{z}{e})^z \sqrt{2\pi z}
+\end{align}
+Thus we have
+\begin{equation}
+    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
+    = (\frac{z}{e})^z \sqrt{2\pi z}
+\end{equation}
 \subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
@@
     \label{sec:Matrix-Exponentials}
-    I found these formulae from Wikipedia page:
+    \paragraph{The Zassenhaus formula}
+    I found the formula from Wikipedia page:
     \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
-    \paragraph{The Zassenhaus formula}
     \begin{align}

### 2017-03-01 Draft/sections/misc-math.tex
[minor] Discusses the derivative of dirac function.

@@
 \subsection{Gamma Function and Stirling's formula with Stationary phase
-approximation/Saddle point approximation}
+approximation}
 
@@
 It has an approximation formula called the Stirling formula. Here I obtain the
-Stirling formula with the Saddle point approximation, also called Stationary
-phase approximation in pp.108 of \cite{Altland2010}.
+Stirling formula with the Stationary phase approximation in pp.108 of
+\cite{Altland2010}.
 
-Let us further restrict $z$ into $z\in\R$ and $z>0$, the natural logarithm $\ln(z)$ is well
+Without further restricting $z$ into $\R$, we can use Stationary phase approximation
+to get the result.\footnote{
+    If we have restricted $z\in\R$, then instead of Stationary phase
+approximation, we would be using Saddle point approximation.}
+Note that since $\Re(z)>0$, the natural logarithm $\ln(z)$ is well
 defined, so we have
@@
 Let $F(x,z) = -(\ln(x^z)-x)$, then $\frac{dF}{dx}(x_0)=-\frac{z}{x_0}+1=0$ gives the
-saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z>0$
+saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z$
 confirms that this is really a minimum point. Therefore, the integration is
@@
 \end{equation}
+For $z\in\C$, $\Re(z)>0$.
 \subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
@@
 
+\subsection{Dirac delta function}
+
+It is quite troublesome to deal with this function $\delta(x)$. For example, sometimes I
+have to deal with $\frac{\dd}{\dd{x}}\delta(x)$, or $\delta'(x)$. Here I present an argument, not
+proof, of the result.
+
+I treat $\delta(x)$ not as a function, but as an operator. Therefore, we have to
+use a test function $f(x)$ to see what $\delta'(x)$ really is. Assuming that the
+dirac delta function still follows the rule of \textit{integration by parts}.
+Assuming our test function vanishes, or at least does not go to infinity when
+$x\to\infty$ or $x\to-\infty$. Then
+\begin{align}
+    \int_{-\infty}^\infty \dd{x} \delta'(x) f(x) &=
+    \eval{\delta(x)f(x)}_{-\infty}^\infty - \int\dd{x}\delta(x)\frac{\dd}{\dd x}f(x)
+    = 0 - \dv{f}{x}(0)
+\end{align}
+Therefore, we say that in this situation,
+\begin{equation}
+    \delta'(x) = -\delta(x)\dv{x}
+\end{equation}
+
+But there is one pitfall that confuses me for a long time. Because:
+\begin{align*}
+    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
+    = -\int\dd{x}g(x)\delta(x)
+\end{align*}
+This lures me into believing
+\begin{equation}
+    x\delta'(x) = -\delta(x)
+    \label{eq:xdp--d}
+\end{equation}
+Hence
+\begin{equation}
+    \delta'(x) = -\frac{\delta(x)}{x}
+    \label{eq:dp--dx}
+\end{equation}
+While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
 \subsection{Common Pitfalls}

### 2017-03-01 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] today's notes about Atland's CMP Field theory

@@
 \abstract{
-Notes of book \cite{Altland2010a}.
+Notes of book \cite{Altland2010}, and another book \cite{Greiner1996} for
+information about path integral.
 }
@@
 
+\section{Todo}
+
+\begin{enumerate}
+    \item Understand in what case can the Gaussian integral formula can be
+        applied. In another word, understand the analytical continuation of the
+        Gaussian integral. See for example, buttom of pp.343 of
+        \cite{Greiner1996}.
+        \label{todo:analytical-c}
+    \item Understand the Wick Rotation, cf. pp.356(ch11.5) of
+        \cite{Greiner1996}. This is related to todo \ref{todo:analytical-c}
+    \item Understand how the constant term in the path integral of a Feynman
+        Kernal will(or will not) affect the physics. Understand the mathematical
+        rationale to support this. (cf. buttom of pp.344 of \cite{Greiner1996}.
+    \item I have doubt about the correctness of pp.110 eq 3.28 till pp.111
+        (Construction recipe of the path integral), especially about his
+        argument, the size of the \textit{Planck cell}.
+\end{enumerate}
+
+Bonus objectives:
+\begin{enumerate}
+    \item Find abou the similarity between Path Integral of a free particle and
+        the solution to a classical diffusion equation (cf. pp.112, footnote 1
+        of \cite{Altland2010}).
+    \item Those marked \textit{todo} in \cite{Altland2010}.
+\end{enumerate}
 \section{pp.33 eq.1.43}
@@
 
-In page 33 of \cite{Altland2010a}, the author derives a difference of action, when we
+In page 33 of \cite{Altland2010}, the author derives a difference of action, when we
 have a symmetry transformation paraterized by $\omega_a$:
@@
 \end{align}
-which is what we expect in equation 1.43 of \cite{Altland2010a}.
+which is what we expect in equation 1.43 of \cite{Altland2010}.
 
@@
 
-It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010a}. Here is my
+It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010}. Here is my
 notes.
@@
 The Hamiltonian for particle on a ring is claimed to be (Eq. 9.1 of
-\cite{Altland2010a}, pp. 498):
+\cite{Altland2010}, pp. 498):
 \begin{equation}
@@
 
-The book \cite{Altland2010a} claims that 
+The book \cite{Altland2010} claims that 
 \begin{equation}
@@
 \bibliography{cite}{}
-\bibliographystyle{alpha}
+\bibliographystyle{alphaurl}
 

### 2017-03-04 Draft/sections/misc-math.tex
[minor] Notes about definition of functional derivative, and something trivial about using imaginary time.

@@
 For $z\in\C$, $\Re(z)>0$.
-\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
-\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
+\subsection{Function satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
+\label{sec:Function satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
 
@@
 While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
+\subsection{A beautiful product for sine function}
+
+We have:
+\begin{equation}
+    \sin(x) =  x\prod_{n=1}^\infty \left(1-\frac{x^2}{n^2\pi^2}\right)
+\end{equation}
+Obviously the left and right has the same roots. But the proof of equality needs
+some work. See related links:
+\begin{enumerate}
+    \item  
+        \href{http://math.stackexchange.com/questions/674769/sinx-infinite-product-formula-how-did-euler-prove-it}{Phy.SE:
+        $sin(x)$ infinite product formula: how did Euler prove it?},
+    \item \href{https://en.wikipedia.org/wiki/Basel_problem}{Wikipedia-Basel Problem}.
+\end{enumerate}
+
+This formula is also used in calculating a path integral, see pp.114 of
+\cite{Altland2010}.
+
+\subsection{Functional Derivative}
+
+The following is an answer to a question posted on Physics.StackExchange. It
+contains a good definition of functional derivative and a specific example. The
+link to that post is
+\url{http://physics.stackexchange.com/questions/314638/variational-derivative-of-function-with-respect-to-its-derivative}.
+
+The question asks:
+\begin{myquote} \enquote{
+    What is 
+    $$ \frac{\delta f(t)}{\delta \dot{f}(t)} $$
+    Where $\dot{f}(t)=df/dt$.
+} \end{myquote}
+
+The best answer is:
+\begin{myquote} \enquote{
+    The definition of the functional derivative of a functional $I[g]$ is the
+    distribution $\frac{\delta I}{\delta g}(\tau)$ such that 
+    $$\left\langle \frac{\delta I}{\delta g}, h\right\rangle 
+        := \frac{d}{d\alpha}\bigg\rvert_{\alpha=0} I[g+ \alpha h]$$
+    for every test function $h$. In our case, assuming to deal with functions which
+    suitably vanish before reaching $\pm \infty$,
+    $$I[g] = \int_{-\infty}^t g(x)dx$$
+    so that
+    $$I[\dot{f}]= f(t)$$
+    as requested. Going on with the procedure
+    $$\left\langle \frac{\delta I}{\delta g}, h\right\rangle 
+        = \frac{d}{d\alpha}|_{\alpha=0}  \int_{-\infty}^t(g(\tau)+ \alpha h(\tau)) d\tau 
+        = \int_{-\infty}^t h(\tau) dx 
+        = \int_{-\infty}^{+\infty} \theta(t-\tau)h(\tau) d\tau
+    $$
+    where $\theta(\tau)=1$ for $\tau\geq 0$ and $\theta(\tau)=0$ for $\tau<0$
+    and so 
+$$\frac{\delta f(t)}{\delta \dot{f}}(\tau) = \frac{\delta I}{\delta g}(\tau)= \theta(t-\tau)$$
+} \end{myquote}
+In my opinion, the answer has assumed a inner product 
+$$\left\langle f,g \right\rangle := \int f(t)g(t)\dd{t}$$.
+
 \subsection{Common Pitfalls}

### 2017-03-04 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Sth. trivial about imaginary time. (I don't know why this modification is not included in the previous commit)

@@
 
+\section{About \texorpdfstring{$\dot{q}$}{} and imaginary time}
+
+The $\dot{q}$ in all the path integrals, especially eq.3.6 and eq.3.8, is in
+fact a shorthand for the divided difference $\frac{q_{n+1}-q_n}{\Delta t}$ as in
+pp.99 (the buttom). It is not exactly the same as $\dot{q}$. pp.343 of
+\cite{Greiner1996} also mentioned that in this sense, the Lagrangian in all
+path integrals is not identical with the ordinary Lagrange function. Though, I
+still do not know if this matters at all.
+
+In the most common imaginary time transformation, such as those mentioned in
+pp.106 of \cite{Altland2010}, and pp.358 of \cite{Greiner1996}, we have the
+transformation $t\to -i\tau$. This in effect change all the $\Delta t$ in, e.g.
+eq 3.5 (pp.99) of \cite{Altland2010}, to $-i\Delta\tau$. Therefore, the divided
+difference
+$$ \frac{q_{n+1}-q_n}{\Delta t} \to \frac{q_{n+1}-q_n}{-i \Delta\tau}$$
+Therefore,
+$$ \dot{q} \to i\partial_\tau q $$
+$$ \dot{q}^2 \to -\partial^2_\tau q $$
 \section{Eq. 3.5}

### 2017-03-06 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Add a brief Summary of Quantum double well for Condensed Matter Field Theory.

@@
 \printnomenclature
+\section{A brief Summary of Quantum double well}
+
+The Quantum double well:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/quantum-double-well.png}
+    \caption{Quantum double well}
+    The solid line is the double well potential. The dotted line in
+    the second quarter is to remind us of the single well potential and its sets
+    of eigenvalues. The inverted potential in Euclidean time is shown below the
+    $q$-axis.
+\end{figure}
+The Euclidean path integral is
+\begin{equation}
+    G_E(a,\pm a:\tau)=\int_{q(0)=\pm a,q(\tau)=a} Dq\,
+    \exp(-\frac{1}{\hbar}\int_0^\tau\dd{\tau'}
+        \left(\frac{m}{2}\dot{q}^2+V(q)\right)
+    )
+\end{equation}
+with the imaginary time saddle point equation
+\begin{equation}
+    -m\ddot{q}+V'(q) = 0
+\end{equation}
+
+It is turned into several contributions:
+\begin{equation}
+    A = A_{cl}\times A_{qu}
+\end{equation}
+where $A$ denotes transition amplitude, "cl" for classical, "qu" for quantum.
+
+The classical contribution includes a stationary not moving part $A_{cl,st}$, a
+moving but bouncing back and forth in the inverted potential part $A_{cl,inst}$.
+The moving and bouncing back and forth motion is termed \nomen{instanton}, see
+p.117(\cite{Altland2010}) for details.
+
+The $A_{cl,st}$ is $e^{0}=1$ since the stationary path $q\equiv0$. The
+$A_{cl,inst}$ is calculated in the book (pp.116-117), and the result is:
+\begin{equation}
+    A_{cl,inst,one-trip} = \exp(-\frac{1}{\hbar}S_{inst})
+\end{equation}
+for one bouncing trip. Here $S_{inst}$ is given by eq.3.36 in p.117. Adding them
+together gives:
+\begin{equation}
+    A_{cl,inst} =
+    \sum_{n\text{ even/odd}}^\infty \frac{1}{n!}
+    \left(\tau K e^{-S_{inst}/\hbar}\right)^n
+    =\cosh(\tau Ke^{-S_{inst}/\hbar})\text{ or }\sinh(\tau Ke^{-S_{inst}/\hbar})
+\end{equation}
+
+where $K$ is just some prefactor explained in p.118 and calculated in
+pp.122-123.
+
+The quantum contribution is due to the fluctuation of path around the classical
+path. This part is also divided into two categories. The $A_{qu,st}$ for
+fluctuation around the stationary path is calculated in the section about single
+well green function, spcifically eq.3.31 in p.114. It is approximated in p.119
+to be
+\begin{equation}
+    A_{qu,st,n} = e^{-\omega(\tau_{i+1}-\tau_i)/2}
+\end{equation}
+and adding together gives
+\begin{equation}
+    A_{qu,st}= \prod_i e^{-\omega(\tau_{i+1}-\tau_i)/2} = e^{-\tau\omega}
+\end{equation}
+The rest $A_{qu,inst}$ from fluctuation around instanton is assumed to be
+negligible (p.119).
+
+In summary:
+\begin{table}[H]
+    \centering
+    \begin{tabular}{l c c}
+        Path       & Classical ($0$th order) & Fluctuation ($2$nd order) \\
+        Stationary & $1$                     & $\approx e^{-\omega\tau}$  \\
+        Instanton  & $e^{-\frac{1}{\hbar}S_{\text{inst}}}$, or $\cosh(\tau Ke^{-S_{\text{inst}}/\hbar}) \sinh(\tau Ke^{-S_{\text{inst}}/\hbar})$ & $\approx 1$\\
+    \end{tabular}
+\end{table}
+
 \section{License}

### 2017-03-06 Draft/sections/misc-math.tex
[minor] Notes of a "centered coordinate" which takes 2 variables into 1.

@@
 While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
+
+\textbf{Note}: This, in my opinion, is an argument against completely treating
+$\delta(x)$ as a function.
 \subsection{A beautiful product for sine function}
@@
 
+\subsection{A centered coordinate making two variables into one}
+
+This technique is found in p.126 of \cite{Altland2010}. It should be helpful in
+a much broader context.
+
+The original equation is:
+\begin{equation}
+    \partial^2 \phi = \partial_\phi V(\phi)
+\end{equation}
+with $\partial^2 = \partial^2_\tau + \partial^2_x$. We propose a change of
+coordinate $r\equiv \sqrt{x^2+\tau^2}$. Then after careful calculation, one
+finds:
+\begin{align*}
+    \partial_x &= \pm\frac{\sqrt{r^2-\tau^2}}{r}\partial_r \\
+    \partial^2_x &= 
+        \frac{1}{r^2}\left(\frac{\tau^2}{r}\partial_r +
+        (r^2-\tau^2)\partial^2_r\right) 
+\end{align*}
+and similarly for $\partial_\tau$. They combine into:
+\begin{equation}
+    \partial^2 = 
+        \frac{1}{r^2}\left(\frac{x^2+\tau^2}{r}\partial_r +
+        (r^2-\tau^2+r^2-x^2)\partial^2_r\right)
+    = \frac{1}{r}\partial_r + \partial^2_r
+\end{equation}
+Therefore, we have a new equation:
+\begin{equation}
+    \partial^2_r \phi = - \frac{1}{r}\partial_r\phi + \partial_\phi V(\phi)
+\end{equation}
+with a "friction force" of the form $-\frac{1}{r}\partial_r\phi$.
 \subsection{Common Pitfalls}

### 2017-03-08 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] notes about Quantum Tunneling of fields, esp. my doubts.

@@
 
+\section{Tunneling of Quantum field}
+
+This part is particular hard for me. There are majorly three problems. The first
+and most obvious one, is why do we require a "thin wall" approximation? Why is
+this approximation physical?
+
+The next problem is how is expansion of first order in $f$ will make the
+following equation:
+\begin{equation}
+    m\partial^2_r \phi = -\frac{m}{r}\partial_r \phi +
+    \partial_\phi\left(V(\phi)-f\phi\right)
+\end{equation}
+into a simplified form:
+\begin{equation}
+    m\partial^2_r \phi = \partial_\phi(\phi)
+\end{equation}
+
+The last problem is that, the action in the new coordinate is:
+\begin{equation}
+    \int_0^{r_0}\dd{r} \int_0^{2\pi}\dd{\theta} \left[
+        m(\partial_r\phi)^2+V(\phi)-f\phi\right] r
+\end{equation}
+where I have ignored several constants, and have used the formula:
+\begin{equation}
+    \dd{\tau}\dd{x} = r\dd{r}\dd{\theta}
+\end{equation}
+For the moment ignores $-f\phi r$, the first two terms:
+\begin{equation}
+    \int_0^{2\pi}\dd{\theta} \int_0^{r_0}\dd{r} \left[
+        m(\partial_r\phi)^2 + V(\phi)
+    \right] r
+\end{equation}
+is still one step away from producing a $S_{\text{inst}}$ term:
+\begin{equation}
+    S_{\text{inst}} := \int_0^T \dd{\tau} 
+    \left(\frac{m}{2}(\partial_\tau\phi)^2 + V(\phi)\right)
+\end{equation}
 \section{License}

### 2017-03-09 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Some notes about Spin path integral, boson coherent state, in Condensed matter field theory.

@@
 \end{equation}
+\section{Eq. 3.50}
+
+This equation is actually a lemma in combinatorics, see
+
+\href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula#An_important_lemma}{Wikipedia
+Baker–Campbell–Hausdorff formula}.
+
+It says:
+\begin{align}
+    \mathrm{Ad}_{e^X}Y &\equiv e^X Y e^{-X} = e^{\mathrm{ad}_X}Y  \nonumber\\
+    &\equiv Y + [X,Y] + \frac{1}{2!}[X,[X,Y]] + \frac{1}{3!}[X,[X,[X,Y]]] + \cdots
+\end{align}
+or just
+\begin{equation}
+    \mathrm{Ad}_{e^X} = e^{\mathrm{ad}_X}
+\end{equation}
+
+Here the author uses the notation $[X,\,] Y \equiv \mathrm{ad}_X Y \equiv
+[X,Y]$.
+\section{p.138 Exercise}
+Using eq.3.50 on p.138, it is straightforward to obtain:
+\begin{align*}
+    n_1 &= \cos{\phi}\cos{\theta}\braket{S_1} +
+    \cos{\phi}\sin{\theta}\braket{S_3} -\sin{\phi}\braket{S_2} \\
+    n_2 &= \cos{\phi}\braket{S_2} + \sin{\phi}\cos{\theta}\braket{S_1} +
+    \sin{\theta}\sin{\phi}\braket{S_3} \\
+    n_3 &= \cos{\theta}\braket{S_3} + \sin{\theta}\braket{S_1}
+\end{align*}
+And we have
+\begin{align*}
+    \braket{S_1}&=\braket{\uparrow| S_1 |\uparrow} = 0 \\
+    \braket{S_2}&=\braket{\uparrow| S_2 |\uparrow} = 0 \\
+    \braket{S_3}&=\braket{\uparrow| S_3 |\uparrow} = S
+\end{align*}
+by the representation thoery of $\mathrm{SU}(2)$.
+\section{Eq. 3.52}
+
+\begin{align}
+    \braket{\partial_\tau g|g} 
+    &= \braket{\uparrow|
+        \partial_\tau e^{i\phi\hat{S}_3+i\theta\hat{S}_2}
+        e^{-i\phi\hat{S}_3-i\theta\hat{S}_2}
+        |\uparrow}
+    \nonumber\\
+    &= \braket{\uparrow|
+        e^{i\phi\hat{S}_3+i\theta\hat{S}_2}
+        i (\hat{S}_3\partial_\tau\phi + \hat{S}_2\partial_\tau\theta)
+        e^{-i\phi\hat{S}_3-i\theta\hat{S}_2}
+        |\uparrow }
+    \nonumber\\
+    &= i\left(\partial_\tau\phi\braket{g|\hat{S}_3|g} +
+        \partial_\tau\theta\braket{g|\hat{S}_2|g} \right)
+    \nonumber\\
+    &= i(n_3\partial_\tau\phi + n_2 \partial_\tau\theta)
+    \nonumber\\
+    &= i S(\cos{\theta}\partial_\tau\phi + \sin{\theta}\sin{\phi}\partial_\tau\theta)
+\end{align}
+Then how is $\partial_\tau\theta$ missing in (3.52).
+
+\section{Boson coherent state (p.159)}
+
+The aim is to show:
+\begin{equation}
+    a \exp(\phi a^\dagger) \ket{0} = \phi\exp(\phi a^\dagger)\ket{0}
+\end{equation}
+
+Use $aa^\dagger = 1+ a^\dagger a$. And observe:
+\begin{align*}
+    a(a^\dagger)^n &= (a^\dagger)^{n-1}+ a^\dagger a (a^\dagger)^{n-1} \\
+    &= (a^\dagger)^{n-1}+ (a^\dagger)^{n-1}+ (a^\dagger)^2 a (a^\dagger)^{n-2}
+    \\
+    &= 3(a^\dagger)^{n-1} + (a^\dagger)^3 a (a^\dagger)^{n-3} \\
+    &\cdots \\
+    &= n (a^\dagger)^{n-1} + (a^\dagger)^{n} a
+\end{align*}
+Then (notice $a\ket{0}=0$):
+\begin{align*}
+    \sum_n a \frac{\phi^n (a^\dagger)^n}{n!}\ket{0} 
+    &= \sum_n \phi\, \phi^{n-1} \frac{n(a^\dagger)^{n-1}+(a^\dagger)^n a}{n!}\ket{0}\\
+    &= \sum_n \phi\, \phi^{n-1} \frac{n(a^\dagger)^{n-1}}{n!}\ket{0} \\
+    &= \phi\sum_n \phi^{n} \frac{(a^\dagger)^{n}}{n!}\ket{0} \\
+    &= \phi\exp{\phi a^\dagger}\ket{0}
+\end{align*}
 \section{License}

### 2017-03-09 Draft/sections/misc-math.tex
[minor] About many wonderful formulae in exponential of matrices.

@@
     \label{sec:Matrix-Exponentials}
-    \paragraph{The Zassenhaus formula}
+
+    \paragraph{Baker-Campbell-Hausdorf formula}
     I found the formula from Wikipedia page:
     \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
+
+    \begin{align}
+        Z(X,Y)&=\log(\exp X\exp Y) \nonumber\\
+            &= X + Y + \frac{1}{2}[X,Y] +
+            \frac{1}{12}\left ([X,[X,Y]] +[Y,[Y,X]]\right ) \nonumber\\
+            &\quad
+            - \frac {1}{24}[Y,[X,[X,Y]]] \nonumber\\
+            &\quad
+            - \frac{1}{720}\left([Y,[Y,[Y,[Y,X]]]] + [X,[X,[X,[X,Y]]]] \right)
+            \nonumber \\
+            &\quad +\frac{1}{360}\left([X,[Y,[Y,[Y,X]]]] + [Y,[X,[X,[X,Y]]]]\right)
+            \nonumber\\
+            &\quad
+            + \frac{1}{120}\left([Y,[X,[Y,[X,Y]]]] + [X,[Y,[X,[Y,X]]]]\right)
+            + \cdots
+    \end{align}
+    Also from the same source, we have:
+    \paragraph{The Zassenhaus formula}
     \begin{align}
@@
     \end{align}
+
+    \paragraph{Hadamard's lemma}
+    Again, from the same source, there is a useful formula (sometimes called
+    \textit{Hadamard’s lemma}, see
+    \href{http://www.physicspages.com/2016/11/17/exponentials-of-operators-hadamards-lemma/}{this
+    page}.
+
+    \begin{lemma}
+        Let $G$ be a matrix Lie group, and $g$ its corresponding Lie algebra.
+        Let $\mathrm{ad}_X$ be the linear operator on $g$ defined by
+        $$\mathrm{ad}_X Y=[X,Y]=XY-YX$$
+        for some $X\in g$. Denoted $\mathrm{Ad}_A$ for fixed $A\in G$ the linear
+        transformation of $g$ given by $\mathrm{Ad}_A Y = AYA^{-1}$. We have:
+        \begin{equation}
+            \mathrm{Ad}_{e^X} = e^{\mathrm{ad}_X}
+        \end{equation}
+    \end{lemma}
+    Explicitly,
+    \begin{align}
+        \mathrm{Ad}_{e^X}Y &= e^X Y e^{-X} = e^{\mathrm{ad}_X}Y  \nonumber\\
+        &= Y + [X,Y] + \frac{1}{2!}[X,[X,Y]] + \frac{1}{3!}[X,[X,[X,Y]]] + \cdots
+    \end{align}
+
+    Sometimes the $\mathrm{ad}_X$ is denoted by \nomen{$[X,\,\,]$}, so that
+    $[X,\,] Y=[X,Y]$. For example, this is used in p.138 of \cite{Altland2010}.
 

### 2017-03-16 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] notes, especially about Grassmann calculus.

@@
 \end{align*}
+\section{Something about Grassmann Algebra, Grassmann Calculus}
+
+I believe that there are several important points missing in the book, when he
+talks about Grassmann.
+
+\paragraph{The first} thing is the derivative rule. The differentiation with respect to
+Grassmann numbers should follow some version of \nomen{graded Leibniz rule}. But
+I am not sure about the details for the following reason. Consider the
+traditional graded Leibniz rule:
+\begin{equation}
+    \dd (fg) = (\dd f) g + (-1)^{[f]} f\dd g
+\end{equation}
+where $[f]$ is something defined as the parity, or the degree of f.
+
+Now comes the problem: how to define a grade for something like:
+\begin{align}
+    f &= \eta_1 +\eta_2 + \eta_3 + \eta_1\eta_2 +\eta_1\eta_2\eta_3 \\
+    g &= \eta_1 -\eta_2 -\eta_3 + \eta_1\eta_3 - \eta_1\eta_2\eta_3
+\end{align}
+
+\todo{understand graded Leibniz rule}
+
+By calculation, I found:
+\begin{align}
+    \frac{\partial }{\partial \eta_1}(fg) &= -2\eta_2-2\eta_3-2\eta_2\eta_3 \\
+    (\frac{\partial }{\partial \eta_1}f)g &=
+        \eta_1-\eta_2-\eta_3+\eta_1\eta_3-\eta_1\eta_2-\eta_2\eta_3-\eta_1\eta_2\eta_3
+    \\
+    f( \frac{\partial }{\partial \eta_1}g) &=
+        \eta_1+\eta_2+\eta_3+ \eta_1\eta_3 +\eta_1\eta_2+\eta_2\eta_3
+        +\eta_1\eta_2\eta_3
+\end{align}
+It is easy to see that:
+\begin{equation}
+    \pdv{\eta_1}(fg) \neq (\pdv{\eta_1}f)g \pm f(\pdv{\eta_1} g)
+\end{equation}
+
+A more general calculation gives:
+\begin{align}
+    \pdv{\eta}\left[ (a+\eta b)(c+\eta d) \right] &= bc + (-1)^{[a]} ad \\
+    \left(\pdv{\eta}(a+\eta b)\right) (c+\eta d) &= bc + b\eta d \\
+    (a+\eta b)\left(\pdv{\eta}(c+\eta d)\right) &= ad + \eta bd
+\end{align}
+where $(-1)^{[a]}$ is the number such that $a\eta = (-1)^{[a]}\eta a$. So, there
+is no way to reconcile the above calculations into something like:
+\begin{align*}
+    \pdv{\eta}\left[ (a+\eta b)(c+\eta d) \right] = 
+    \left(\pdv{\eta}(a+\eta b)\right) (c+\eta d)  
+    + (-1)^?  (a+\eta b)\left(\pdv{\eta}(c+\eta d)\right)
+\end{align*}
+
+\paragraph{The second} point is very important. It is about the postulations of
+Grassmann variables. I postulate that (in addition to the postulations in p.162
+of \cite{Altland2010}):
+\begin{enumerate}
+    \item All $\eta_i,\bar{\eta}_i,a_i,a^\dagger_i$ anti-commute with each
+        other. From this we also have $\eta_i^2=0$, etc.
+    \item $\{\dd \eta_i,\dd\eta_j\}=0$ for ($i\neq j$).
+    \item $\int \dd{\eta} (af(\eta) + bg(\eta) )
+        = a\int\dd{\eta}f(\eta) + b\int\dd{\eta}g(\eta) $
+    \item $\{\eta_i,\dd{\eta_j}\}=0$, for $i\neq j$.
+    \item $\{\bar{\eta}_i,\dd{\eta_j}\}=0$, for $\forall i,j$.
+    \item $\pdv{\eta} (af(\eta)) = a\pdv{\eta}f(\eta)$, for $a\in\C$.
+\end{enumerate}
+It is not so simple to tell whether we should have 
+$$[\eta_i,\dd\eta_i]=0 \,\text{?}$$ or
+$$\{\eta_i,\dd\eta_i\}=0\,\text{?}$$
+But we should have 
+$$\{\eta_i,\dd{\eta_j}\}=0 \quad\text{for $i\neq j$} $$
+For if $[\eta_i,\dd{\eta_j}]=0$, then we have a contradiction:
+\begin{align}
+    \int\dd{\eta_j} \eta_i\eta_j &= \eta_i \int\dd{\eta_j}\eta_j = \eta_i
+    \nonumber\\
+    &= -\int\dd{\eta_j}\eta_j \eta_i = -\eta_i\quad \text{contradiction!}
+\end{align}
+And similar argument applies for $\{\bar{\eta}_i,\dd{\eta_j}\}=0$, $\forall
+i,j$.
+
+There is also another point missing. The relations between $\eta$ and
+$\ket{0}\bra{0}$ is ambiguous. It seems that there is no harm in assuming:
+\begin{equation}
+    \eta \ket{0}\bra{0} = \ket{0}\bra{0}\eta
+\end{equation}
+Because, if so, we have:
+\begin{equation}
+    a\ket{\eta}\bra{\eta} = \eta\ket{\eta}\bra{\eta} = \ket{\eta}\bra{\eta}\eta
+\end{equation}
+without conflict with:
+\begin{equation}
+    \bar{\eta}\ket{\eta}\bra{\eta} = \ket{\eta}\bra{\eta}\bar{\eta} =
+    \ket{\eta}\bra{\eta} a^\dagger
+\end{equation}
+
+With above assumptions, I have:
+\begin{thm}
+    Assuming that $a,b,c,d$ either commute or anticommute with $\eta$.
+    \begin{equation}
+        \int\dd{\eta} \left(\pdv{\eta}(a+\eta b) \right)(c+\eta d)
+        = (-1)^s\int\dd{\eta} (a+\eta b) \left(\pdv{\eta}(c+\eta d)\right)
+        \label{eq:inteByPart-grass}
+    \end{equation}
+    where $s$ is such that $b\eta = (-1)^s \eta b$.
+\end{thm}
+This can also be generalized into
+\begin{equation}
+    \int\dd{\eta} \left(\pdv{\eta}f(\eta) \right) g(\eta)
+    = (-1)^s\int\dd{\eta} f(\eta) \left(\pdv{\eta}g(\eta)\right)
+\end{equation}
+where $s$ is some appropriate constant as in eq~\ref{eq:inteByPart-grass}. Here
+we have assumed that any $f(\eta)$, we can decompose it into $f=a+\eta b$, where
+$a$ and $b$ do not contain $\eta$. We also assume $a,b$ either commute or
+anticommute with $\eta$.
+\begin{proof}
+    Direct calculation.
+\end{proof}
+
+\paragraph{Change of variables in integration}
+First we consider a simple example.
+\begin{equation}
+    \int \dd{\phi} a+b\phi = b
+\end{equation}
+Let $v = \lambda \phi$, since
+\begin{equation}
+    \int\dd{v} a+ b\frac{v}{\lambda} = \frac{b}{\lambda}
+\end{equation}
+We naturally require
+\begin{equation}
+    \dd{\phi} = \lambda \dd{v}
+\end{equation}
+For multivariable case, it is easy to guess that:
+\begin{align}
+    \vb{v} &= M\vb{\phi} \\
+    \dd{\phi_1}\dd{\phi_2}\cdots \dd{\phi_N} &= \det(M)\dd{v_1}\dd{v_2}\cdots\dd{v_N}
+\end{align}
+(Took from
+\href{https://en.wikipedia.org/wiki/Berezin_integral#Change_of_Grassmann_variables}{Wikipedia
+Berezin Integral}.)
+
 \section{License}

### 2017-03-16 Grassmann Number notes/Grassmann-Supermanifolds-note.tex
[minor] notes about grassmann calculus for Supermanifold.

--- 2017-03-08 Condensed Matter Field Theory note/CMF-Atland.tex
@@
 
-\title{Condensed Matter Field Theory notes}
+\title{Grassmann Number notes}
 \date{\today}
@@
 \abstract{
-Notes of book \cite{Altland2010}, and another book \cite{Greiner1996} for
-information about path integral.
+    From Supermanifolds \cite{DeWitt1992}.
 }
@@
 
-\section{Todo}
+\section{Inverse of a Supernumber}
 
-\begin{enumerate}
-    \item Understand in what case can the Gaussian integral formula can be
-        applied. In another word, understand the analytical continuation of the
-        Gaussian integral. See for example, buttom of pp.343 of
-        \cite{Greiner1996}.
-        \label{todo:analytical-c}
-    \item Understand the Wick Rotation, cf. pp.356(ch11.5) of
-        \cite{Greiner1996}. This is related to todo \ref{todo:analytical-c}
-    \item Understand how the constant term in the path integral of a Feynman
-        Kernal will(or will not) affect the physics. Understand the mathematical
-        rationale to support this. (cf. buttom of pp.344 of \cite{Greiner1996}.
-    \item I have doubt about the correctness of pp.110 eq 3.28 till pp.111
-        (Construction recipe of the path integral), especially about his
-        argument, the size of the \textit{Planck cell}.
-\end{enumerate}
-
-Bonus objectives:
-\begin{enumerate}
-    \item Find abou the similarity between Path Integral of a free particle and
-        the solution to a classical diffusion equation (cf. pp.112, footnote 1
-        of \cite{Altland2010}).
-    \item Those marked \textit{todo} in \cite{Altland2010}.
-\end{enumerate}
-\section{pp.33 eq.1.43}
-\label{sec:Table}
-
-In page 33 of \cite{Altland2010}, the author derives a difference of action, when we
-have a symmetry transformation paraterized by $\omega_a$:
-
-\begin{align}
-    x_\mu \to x'_\mu &= x_\mu + \frac{\partial x_\mu}{\omega_a}|_{\omega=0} \omega_a(x) \\
-    \phi^i(x) \to \phi'(x') &= \phi^i(x) + \omega_a(x)F^i_a[\phi]
-\end{align}
-
-We have:
-\begin{align}
-    \mathcal{L} &= \mathcal{L}(\phi^i(x),\partial_{x_\mu}\phi^i(x)) \\
-    \mathcal{L}' &= \mathcal{L'}(\phi'^i(x'),\partial_{x'_\mu}\phi'^i(x')) \\
-    &= \mathcal{L}\left(\phi^i+F^i_a\omega_a, 
-                    \left(\delta_{\mu\nu}-\partial_{x_\mu}(\omega_a
-                    \partial_{\omega_a}x_\mu)\right)
-                    \partial_{x_\nu}(\phi^i+F^i_a\omega_a)
-                  \right)
-\end{align}
-And
-
-\begin{align}
-    \Delta S &= \int \dd[m]{x'} \mathcal{L}' - \int \dd[m]{x} \mathcal{L} 
-    \label{eq:dS-integrand}\\
-    &=
-    \int \dd[m]{x}
-    \left(1+\partial_{x_\mu}\left(\omega_a \partial_{\omega_a}x_\mu\right) \right) 
-    \nonumber\\
-    &\times \mathcal{L}\left(
-                    \phi^i+F^i_a\omega_a, 
-                    \left(\delta_{\mu\nu}-\partial_{x_\mu}\left(\omega_a
-                        \partial_{\omega_a}x_\mu\right)\right)
-                        \partial_{x_\nu}(\phi^i+F^i_a\omega_a)
-                    \right) \nonumber\\
-    &- \int \dd[m]{x}  \mathcal{L}(\phi^i(x),\partial_{x_\mu}\phi^i(x))
-\end{align}
-
-Then he argues that, "for constant parameters $\omega_a$ the action difference
-$\Delta a$ vanishes". Therefore "the leading contribution to the action
-difference of a symmetry transformation must be linear in the derivative
-$\partial_{x_\mu}\omega_a$".
-
-Then he writes that "A straightforward expansion of the formula above
-for $\Delta S$ shows that these terms are given by"
-
+Let $z=z_B + z_S$ be a supernumber with $z_B$ its body, $z_S$ its soul.
+If $z_B\neq 0$, then it has a inverse. The inverse can be found via the
+following formal series:
 \begin{equation}
-    \Delta S = -\int \dd[m]{x} j^a_\mu (x) \partial_{x_\mu}\omega_a
+    \frac{1}{a+x} = \frac{1}{a}\frac{1}{1+\frac{x}{a}} =
+    \frac{1}{a}\sum_{n=0}^{\infty}(-\frac{x}{a})^n
 \end{equation}
-where $j^a_\mu$ is:
+Thus,
 \begin{equation}
-    j^a_\mu = \left(
-        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-            \partial_{x_\nu}\phi^i
-        -\mathcal{L}\delta_{\mu\nu} \right) \frac{\partial x_\nu}{\partial\omega_a}
-    - \frac{\partial\mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)} F^i_a
+    z^{-1} = z_B^{-1}\sum_{n=0}^{\infty} (-z_B^{-1}z_S)^n
 \end{equation}
-
-I am partically confused about how to do the "straightforward expansion". I
-guess I should do $\frac{\partial}{\partial (\partial_{x_\mu}\omega_a)}$ to the
-integrand inside expression for $\Delta S$, though I don't really understand the
-reason. Even so, the integrand contains terms like
-$\partial_{x_\mu}\partial_{\omega_a}x_\mu$, which I don't know how to deal with.
-
-\textbf{Solution}. The reality is a bit more complicated. We first do a first
-order expasion to get the infinitesimal difference:
-
-\begin{align}
-    &\mathcal{L}'-\mathcal{L} \\
-    \approx &
-    \frac{\partial \mathcal{L}}{\partial\phi^i} F^i_a\omega_a
-    +\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-        \left[
-        \partial_\mu\left(F^i_a\omega_a\right) 
-            - \partial_\mu\left(\omega_a\frac{\partial x_\nu}{\partial\omega_a}\right)
-                \partial_\nu\left(\phi^i+F^i_a\omega_a\right)
-        \right]
-    \nonumber\\
-    =&\quad
-    \omega_a
-    \left[
-        \frac{\partial \mathcal{L}}{\partial\phi^i}F^i_a 
-        +
-        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-        \left(
-            \partial_\mu F^i_a 
-            - \partial_\mu(\frac{\partial x_\nu}{\partial \omega_a})
-            \partial_\nu(\phi^i+F^i_a\omega_a)
-        \right)
-    \right]
-    \label{eq:l-l-omega}
-    \\
-    +&
-    \partial_\mu\omega_a
-    \left[
-        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-        \left(
-            F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
-            \partial_\nu(\phi^i+F^i_a\omega_a)
-        \right)
-    \right]
-    \label{eq:l-l-pmu-omega}
-\end{align}
-
-We also discover the integrand in Eq.\ref{eq:dS-integrand} to be
-\begin{align}
-    &\left(1+\partial_\mu(
-        \omega_a\frac{\partial x_\mu}{\partial \omega_a})
-        \right)\mathcal{L}'-\mathcal{L} 
-    \\
-    =& 
-    \left(
-    1+\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})
-    \right)
-    (\mathcal{L}'-\mathcal{L})
-    +
-    \left(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})\right)
-    \mathcal{L}
-    \label{eq:integrand-l-density}
-\end{align}
-For the first term 
-$\left(
-    1+\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})
-\right) (\mathcal{L}'-\mathcal{L}) $, the $(\mathcal{L}'-\mathcal{L})$ already
-has terms of first order of $\omega_a$ and of first order of
-$\partial_\nu\omega_a$. For our purpose, the second order terms
-($\partial_\nu(F^i_a\omega_a)$) from item \ref{eq:l-l-omega} and item
-\ref{eq:l-l-pmu-omega} can be ignored. Also, the item
-$(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial
-\omega_a}))(\mathcal{L}'-\mathcal{L})$ in eq.\ref{eq:integrand-l-density} can
-also be ignored.
-
-Therefore the integrand in Eq.$\ref{eq:dS-integrand}$ becomes
-
-\begin{align}
-    & (\mathcal{L}'-\mathcal{L})
-    +
-    \left(\partial_\mu(\omega_a\frac{\partial x_\mu}{\partial \omega_a})\right)
-    \mathcal{L} \\
-    = & 
-    \omega_a
-    \left[
-        \frac{\partial \mathcal{L}}{\partial\phi^i}F^i_a 
-        +
-        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-        \left(
-            \partial_\mu F^i_a 
-            - (\partial_\mu\frac{\partial x_\nu}{\partial \omega_a})
-            \partial_\nu(\phi^i+F^i_a\omega_a)
-        \right)
-        +
-        (\partial_\nu \frac{\partial x_\mu}{\partial \omega_a})\mathcal{L}
-    \right]
-    \\
-    +&
-    \partial_\mu\omega_a
-    \left[
-        \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-        \left(
-            F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
-            \partial_\nu(\phi^i+F^i_a\omega_a)
-        \right)
-        +
-        \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L}
-    \right]
-\end{align}
-
-Therefore, the term we seek, i.e. the coefficient of $\partial_\mu\omega_a$ is
-\begin{align}
-  & \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-    \left(
-        F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
-        \partial_\nu(\phi^i+F^i_a\omega_a)
-    \right)
-    +
-    \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L} \\
-    =&
-    \left(
-        \mathcal{L}\delta_{\mu\nu}
-        -\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
-            \partial_\nu \phi^i
-    \right) \frac{\partial x_\nu}{\partial \omega_a}
-    +
-    \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}F^i_a
-\end{align}
-which is what we expect in equation 1.43 of \cite{Altland2010}.
-
-\textbf{Question}: as for why we should ignore the term with $\omega_a$, there
-are two posts (
-    \href{http://physics.stackexchange.com/questions/122965/derivation-of-the-noether-current}{[1]},
-    \href{http://physics.stackexchange.com/questions/99853/on-a-trick-to-derive-the-noether-current}{[2]} )
-might be useful for a thought.
-
-\todo{confusion}
-
-I had great doubt about this problem. Though I have posted an answer on
-\href{http://physics.stackexchange.com/questions/122965/derivation-of-the-noether-current}{[1]},
-I don't think that answer is satisfactory.
-
-\section{About \texorpdfstring{$\dot{q}$}{} and imaginary time}
-
-The $\dot{q}$ in all the path integrals, especially eq.3.6 and eq.3.8, is in
-fact a shorthand for the divided difference $\frac{q_{n+1}-q_n}{\Delta t}$ as in
-pp.99 (the buttom). It is not exactly the same as $\dot{q}$. pp.343 of
-\cite{Greiner1996} also mentioned that in this sense, the Lagrangian in all
-path integrals is not identical with the ordinary Lagrange function. Though, I
-still do not know if this matters at all.
-
-In the most common imaginary time transformation, such as those mentioned in
-pp.106 of \cite{Altland2010}, and pp.358 of \cite{Greiner1996}, we have the
-transformation $t\to -i\tau$. This in effect change all the $\Delta t$ in, e.g.
-eq 3.5 (pp.99) of \cite{Altland2010}, to $-i\Delta\tau$. Therefore, the divided
-difference
-$$ \frac{q_{n+1}-q_n}{\Delta t} \to \frac{q_{n+1}-q_n}{-i \Delta\tau}$$
-Therefore,
-$$ \dot{q} \to i\partial_\tau q $$
-$$ \dot{q}^2 \to -\partial^2_\tau q $$
-\section{Eq. 3.5}
-
-It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010}. Here is my
-notes.
-
-According to the book, Eq.3.3 is turned into (I set $\hbar=1$ occasionally,
-though sometimes I forgot that I have set $\hbar=1$, orz):
-\begin{align}
-    \bra{q_f} 
-    &\int \dd{q_N}\dd{p_N}\ket{q_N}\braket{q_N|p_N}\bra{p_N}
-        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t}\times \nonumber\\
-    &   \int \dd{q_{N-1}}\dd{p_{N-1}}\ket{q_{N-1}}\braket{q_{N-1}|p_{N-1}}\bra{p_{N-1}}
-        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \times
-        \dots \nonumber\\
-    &   \int \dd{q_1}\dd{p_1}\ket{q_1}\braket{q_1|p_1}\bra{p_1}
-        e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \ket{q_i}
-\end{align}
-Notice that
-\todo{T has only p, V has only q}
-\begin{align}
-    \braket{q|p} &= \frac{\exp(iqp/\hbar)}{\sqrt{2\pi\hbar}} \\
-    \bra{p_N}e^{-i\hat{T}\Delta t} &= \bra{p_N}e^{-iT(p_N)\Delta t} \\
-    e^{-i\hat{V}\Delta t}\ket{q_{N-1}} &= e^{-iV(q_{N-1})\Delta t}\ket{q_{N-1}} \\
-\end{align}
-Also, 
-\begin{align}
-    &\braket{q_N|p_N}\bra{p_N}e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t}\ket{q_{N-1}} 
-    = \frac{e^{iq_N p_N/\hbar}}{\sqrt{2\pi\hbar}}
-        \bra{p_N}e^{-iT(p_N)\Delta t} e^{-iV(q_{N-1})\Delta t}\ket{q_{N-1}}
-    \nonumber\\
-    =& \frac{e^{iq_N p_N/\hbar}}{\sqrt{2\pi\hbar}}
-        \braket{p_N | q_{N-1}}e^{-iT(p_N)\Delta t} e^{-iV(q_{N-1})\Delta t}
-    = \frac{e^{ip_N (q_N-q_{N-1})/\hbar}}{2\pi\hbar}
-        e^{-i[T(p_N)+V(q_{N-1})]\Delta t} 
-\end{align}
-etc. Now we have to pay special attentiont to the start and end. For the start,
-we have a
-$$ \int \dd{q_N} \braket{q_f | q_N} = \int\dd{q_N}\delta(q_N-q_f) $$
-So every $q_N$ is replaced by $q_f$. For the end, we have
-$$ \braket{q_1|p_1}\bra{p_1}e^{-i\hat{T}\Delta t}e^{-i\hat{V}\Delta t} \ket{q_i}
-= e^{-i[T(p_1)+V(q_i)]}\frac{e^{ip_1(q_1-q_i)}}{2\pi\hbar}
-$$
-
-Together we have the whole thing into:
-
-\begin{align}
-    \int & \dd{q_1}\cdots\dd{q_{N-1}}\dd{p_1}\dd{p_N} \frac{1}{(2\pi\hbar)^N}
-    \times \nonumber\\
-  & e^{i\left[p_1(q_1-q_i)+\cdots p_N(q_N-q_{N-1})\right]} \times\nonumber\\
-  & e^{-i\left[T(p_1)+\cdots+T(p_N)+V(q_i)+V(q_1)+\cdots+V(q_{N-1})\right]}
-\end{align}
-which is exactly eq.(3.5) in book.
-\section{Eq 9.4}
-
-The Hamiltonian for particle on a ring is claimed to be (Eq. 9.1 of
-\cite{Altland2010}, pp. 498):
-\begin{equation}
-    H = \frac{1}{2}(-i\partial_\phi -A)^2 = \frac{1}{2}(p-A)^2
-\end{equation}
-
-The book \cite{Altland2010} claims that 
-\begin{equation}
-    L = \frac{1}{2}\dot{\phi}^2 - iA \dot{\phi}
-\end{equation}
-I am quite confused, especially about the appearance of $\dot{\phi}$. Can any explain
-a bit?
-
-How I tried: Since the inverse of a Legendre transformation is Legendre
-transformation itself, 
-\begin{align}
-    \text{Denote }x &\equiv \frac{\partial H}{\partial p} = p-A,\text{ so,} \\
-    p &= x + A,\quad H = \frac{1}{2}x^2 ,\text{ so,}\\
-    L = x p - H &= x(x+A) - \frac{1}{2}x^2 = \frac{1}{2}x^2 + x A 
-\end{align}
-So my calculation found that the Lagrangian of above Hamiltonian is:
-\begin{equation}
-    L = \frac{1}{2}x^2 + x A
-\end{equation}
-where
-\begin{equation}
-    x = \frac{\partial H}{\partial p}
-\end{equation}
-
 \bibliography{cite}{}
 \bibliographystyle{alphaurl}
-
 \printnomenclature
-\section{A brief Summary of Quantum double well}
-
-The Quantum double well:
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.6\linewidth]{pics/quantum-double-well.png}
-    \caption{Quantum double well}
-    The solid line is the double well potential. The dotted line in
-    the second quarter is to remind us of the single well potential and its sets
-    of eigenvalues. The inverted potential in Euclidean time is shown below the
-    $q$-axis.
-\end{figure}
-The Euclidean path integral is
-\begin{equation}
-    G_E(a,\pm a:\tau)=\int_{q(0)=\pm a,q(\tau)=a} Dq\,
-    \exp(-\frac{1}{\hbar}\int_0^\tau\dd{\tau'}
-        \left(\frac{m}{2}\dot{q}^2+V(q)\right)
-    )
-\end{equation}
-with the imaginary time saddle point equation
-\begin{equation}
-    -m\ddot{q}+V'(q) = 0
-\end{equation}
-
-It is turned into several contributions:
-\begin{equation}
-    A = A_{cl}\times A_{qu}
-\end{equation}
-where $A$ denotes transition amplitude, "cl" for classical, "qu" for quantum.
-
-The classical contribution includes a stationary not moving part $A_{cl,st}$, a
-moving but bouncing back and forth in the inverted potential part $A_{cl,inst}$.
-The moving and bouncing back and forth motion is termed \nomen{instanton}, see
-p.117(\cite{Altland2010}) for details.
-
-The $A_{cl,st}$ is $e^{0}=1$ since the stationary path $q\equiv0$. The
-$A_{cl,inst}$ is calculated in the book (pp.116-117), and the result is:
-\begin{equation}
-    A_{cl,inst,one-trip} = \exp(-\frac{1}{\hbar}S_{inst})
-\end{equation}
-for one bouncing trip. Here $S_{inst}$ is given by eq.3.36 in p.117. Adding them
-together gives:
-\begin{equation}
-    A_{cl,inst} =
-    \sum_{n\text{ even/odd}}^\infty \frac{1}{n!}
-    \left(\tau K e^{-S_{inst}/\hbar}\right)^n
-    =\cosh(\tau Ke^{-S_{inst}/\hbar})\text{ or }\sinh(\tau Ke^{-S_{inst}/\hbar})
-\end{equation}
-
-where $K$ is just some prefactor explained in p.118 and calculated in
-pp.122-123.
-
-The quantum contribution is due to the fluctuation of path around the classical
-path. This part is also divided into two categories. The $A_{qu,st}$ for
-fluctuation around the stationary path is calculated in the section about single
-well green function, spcifically eq.3.31 in p.114. It is approximated in p.119
-to be
-\begin{equation}
-    A_{qu,st,n} = e^{-\omega(\tau_{i+1}-\tau_i)/2}
-\end{equation}
-and adding together gives
-\begin{equation}
-    A_{qu,st}= \prod_i e^{-\omega(\tau_{i+1}-\tau_i)/2} = e^{-\tau\omega}
-\end{equation}
-The rest $A_{qu,inst}$ from fluctuation around instanton is assumed to be
-negligible (p.119).
-
-In summary:
-\begin{table}[H]
-    \centering
-    \begin{tabular}{l c c}
-        Path       & Classical ($0$th order) & Fluctuation ($2$nd order) \\
-        Stationary & $1$                     & $\approx e^{-\omega\tau}$  \\
-        Instanton  & $e^{-\frac{1}{\hbar}S_{\text{inst}}}$, or $\cosh(\tau Ke^{-S_{\text{inst}}/\hbar}) \sinh(\tau Ke^{-S_{\text{inst}}/\hbar})$ & $\approx 1$\\
-    \end{tabular}
-\end{table}
-
-\section{Tunneling of Quantum field}
-
-This part is particular hard for me. There are majorly three problems. The first
-and most obvious one, is why do we require a "thin wall" approximation? Why is
-this approximation physical?
-
-The next problem is how is expansion of first order in $f$ will make the
-following equation:
-\begin{equation}
-    m\partial^2_r \phi = -\frac{m}{r}\partial_r \phi +
-    \partial_\phi\left(V(\phi)-f\phi\right)
-\end{equation}
-into a simplified form:
-\begin{equation}
-    m\partial^2_r \phi = \partial_\phi(\phi)
-\end{equation}
-
-The last problem is that, the action in the new coordinate is:
-\begin{equation}
-    \int_0^{r_0}\dd{r} \int_0^{2\pi}\dd{\theta} \left[
-        m(\partial_r\phi)^2+V(\phi)-f\phi\right] r
-\end{equation}
-where I have ignored several constants, and have used the formula:
-\begin{equation}
-    \dd{\tau}\dd{x} = r\dd{r}\dd{\theta}
-\end{equation}
-For the moment ignores $-f\phi r$, the first two terms:
-\begin{equation}
-    \int_0^{2\pi}\dd{\theta} \int_0^{r_0}\dd{r} \left[
-        m(\partial_r\phi)^2 + V(\phi)
-    \right] r
-\end{equation}
-is still one step away from producing a $S_{\text{inst}}$ term:
-\begin{equation}
-    S_{\text{inst}} := \int_0^T \dd{\tau} 
-    \left(\frac{m}{2}(\partial_\tau\phi)^2 + V(\phi)\right)
-\end{equation}
 \section{License}

### 2017-03-24 Conferences OR Schools/Boulder Summer School 2016/BSS 2014 - Notes.tex
[minor] a first draft for bss 2014...

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{BSS 2014 - Notes}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    This is a note for an guide to the video recordings of Boulder
    Summer School (BSS) 2014,
    whose major topic is: \textbf{Modern Aspects of
    Superconductivity}. However, after I worked out some outlines of
    these lectures, I found the Yale's website about BSS, I found
    \href{http://boulderschool.yale.edu/2014/boulder-school-2014-lecture-notes}{here}
    their list of topics. I found nothing relavent to my current
    study. So I quit this note. The Yale's website is a better guide
    (in my opinion) to these videos.
}
\tableofcontents

\section{Introduction to BSS 2014 - Topic: Superconductivity}
\label{sec:intro}

Link:\href{https://www.youtube.com/watch?v=umVzk0r0tPo&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=1}{Introduction in Youtube}.

From 0' ~ 14', introduction about this school, its \textbf{success},
its rules, its people (TAs, etc.), Tips, \textbf{No Alcohol}.

From 14' ~ end' , introduction to content of this school. balabala.

\section{Dessau - ARPES}
\label{sec:Dessau}

    \subsection{Dessau 1}
    \label{sec:Dessau 1}

    Link:
    \href{https://www.youtube.com/watch?v=g-qlJ9S-BKY&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=2}{Dessau 1 in Youtube}, Skipped.

    Dessau (University of Colorado, Boulder. Experimentalist).

    3': \textbf{ARPES for the studies of superconductivity}, this lecture
    will tells us about: what it can measure, and its comparison with
    other spectroscopies.

    5'30'': \textbf{Plan}
    \begin{itemize}
        \item Discussion of technique
        \item Case studies, mostly from p-type cuprates
        \item Focus where ARPES made largest initial impacts.
        \item Early studies using Fermi Liquid theory (failed), Recent ...
        \item Topics: Evolutin of electronic structure from the parent
            Mott state, Fermi surfaces and Fermi arcs, superconducting
            gaps, pseudogaps, self-energy effects.
    \end{itemize}

    \subsection{Dessau 2}
    \label{sec:Dessau 2}
    Link:\href{https://www.youtube.com/watch?v=z0_ncvUxxrg&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=3}{Dessau 2 in Youtube}, Skipped.

    \textbf{Plan}:
    \begin{itemize}
        \item Overview of 2D electronic detection
        \item Studies of gaps (superconducting gaps, pseudogaps)
        \item Mode coupling (dispersion kinks)
    \end{itemize}

    \subsection{Dessau 3}
    \label{sec:Dessau 3}
    Link:\href{https://www.youtube.com/watch?v=DuQLBEBK7SM&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=4}{Dessau 3 in Youtube}, Skipped.

    \textbf{Plan}
    \begin{itemize}
        \item ARPES on n-type cuprate superconductors, esp. "hot spots".
        \item Pseudogaps and SC gaps in p-type cuprates.
        \item Competition between pairing and pair-breaking (electron
            self energies)
            \todo{Maybe I should watch this.}
        \item Linearity, deviation from linearity, ARPES scattering rates,
            and transport.
    \end{itemize}
    \bibliography{cite}{}
    \bibliographystyle{alphaurl}

    \printnomenclature

\section{Martinis - Desig of Superconducting Quantum Computer}
\label{sec:Martinis - Desig of Superconducting Quantum Computer}

    \subsection{Martinis 1}
    \label{sec:Martinis 1}
    Link:\href{https://www.youtube.com/watch?v=CyeIeciAMDU&index=5&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh}{Martinis 1 in Youtube}, Skipped.

    John Martinis, from UC Santa Barbara (UCSB).

    \textbf{How Superconducting gives us a very unique, reasonably
    feasible, way to build a Quantum Computer}.

    \textbf{Outline}
    \begin{itemize}
        \item Exponential computing power (why we build)
        \item Hardware Requirements
        \item Physics of Qubits, review
        \item Error correction, the need for fault-tolerant
            computation.
        \item Surface code theory (error-correction and architecture)
        \item Xmon superconducting qubits, integrated circuits for
            scaling above fidelity threshold.
    \end{itemize}

    \subsection{Martinis 2}
    \label{sec:Martinis 2}
    Link:\href{https://www.youtube.com/watch?v=nNeXqsVegUk&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=6}{Martinis 2 in Youtube}, Skipped.

    (It seems that there is not outline/plan available.)

\section{Q \& A Week 1}
\label{sec:QA Week 1}
Link:\href{https://www.youtube.com/watch?v=hsPTifCGgoE&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=7}{Youtube}, Skipped.

\section{Randeria - Phenomenology of Superconducting}
\label{sec:Randeria}
Links:
\href{https://www.youtube.com/watch?v=bQ8mB9kTcMY&index=8&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh}{Randeria 1},
\href{https://www.youtube.com/watch?v=YTJE6-XZkKY&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=9}{Randeria 2},
\href{https://www.youtube.com/watch?v=i_nlB9_ZFMQ&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=10}{Randeria 3},
\href{https://www.youtube.com/watch?v=6xSWAL54ZhM&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=11}{Randeria 4}.

Skipped.

\section{Sigris - Symmetry Aspects of Unconventional Superconductivity}
\label{sec:Sigris}
\url{https://www.youtube.com/watch?v=YtEF9sm03rg&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=12}

\section{Keimer - Neutron and x-ray scattering studies of superconductors}
\label{sec:Keimer}
\url{https://www.youtube.com/watch?v=V_Ijobdl-DY&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=16}

\section{Kvelson - Simples models of Interacting Electrons}
\label{sec:Kvelson}
\url{https://www.youtube.com/watch?v=k5qZILzmIDA&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=19}
\todo{I should watch this later too!}

\section{Paramekanti - }
\label{sec:Paramekanti}
\url{https://www.youtube.com/watch?v=8g1YAISQhPM&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=24}

\textbf{Plan}
\begin{itemize}
    \item Phase diagram and broad questions
    \item Some basic microscopics
    \item Mott transition - entropy arguments
    \item Mott transport - renormalized mean field theory
    \item Superconductivity
    \item Parton (Slave Boson) description (Lec.2)
    \item Variational Monte Carlo method (Lec.2)
\end{itemize}

\section{Public Lecture - Steven Kivelson from Stanford}
\label{sec:Public Lecture}
\url{https://www.youtube.com/watch?v=bO1_rs12gpY&index=26&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh}

Outreach effort for junior people.

Topic: Emmergence, Macroscopics Quantum Phenomenon and High-T Superconductivity.
\todo{watch this later!}

\section{Q \& A Week 2}
\label{sec:QA Week 2}
\url{https://www.youtube.com/watch?v=j1NgPXq_6QM&list=PL8mMEmoXNBfajJ15HO5G-PZW_0yWGWBdh&index=27}

\section{Todadri - Superconductivity, its friends and its enemies,
near Mott transition}
\label{sec:Todadri}

T. Senthil from MIT.

% \section{License}
% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% \href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
% Commons Attribution-NonCommercial-ShareAlike 4.0 International 
% License}. Permissions beyond the scope of this 
% license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-03-24 Dirac Hamiltonian/dirac_H.tex
[major] Learn Dirac Hamiltonian for Lattice Dirac Model.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{Dirac Hamiltonian}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
This aims for recapitulate important information about Dirac
Hamiltonian as is written in Sakurai's text \cite{Sakurai2011},
chapter 8.\footnote{Be careful that some version of this book is
missing chapter 8... I don't understand why...} This is intended to
learn to help me deal with a Lattice Dirac Hamiltonian.
}
\tableofcontents

The starting point is still the Schrodinger equation:

\begin{equation}
    i\hbar \pdv{t}\ket{\psi(t)} = H\ket{\psi(t)}
\end{equation}

We will be using \textbf{Natural Units} from now on.

\section{Klein-Gorden Equations}
\label{sec:Klien-Gorden Equations}

The Klein-Gorden equation starts with the the relativistic energy (of
a particle with momentum $\vb{p}$ and mass $m$):
\begin{equation}
    E_p = +\sqrt{p^2+m^2}
\end{equation}
The plus sign here hints that we may have a negative energy solution.

We do not quantize this equation directly, because the square root is
hard to represent in operators. Instead, Klein-Gorden equation starts
with $H^2$:
\begin{equation}
    H^2 = p^2 + m^2 \overset{\text{quantized as}}{\to}
    -\grad^2 + m^2
\end{equation}
On the other hand, the Schrodinger equation applying twice gives:
\begin{equation}
    -\pdv[2]{t} = H^2
\end{equation}
Hence we have the Klein-Gorden equation:
\begin{equation}
    \label{eq:kg-eq}
    \left(\pdv[2]{t} - \grad^2 + m^2\right) \psi(x,t) = 0
\end{equation}
It can be simplified in $4$-vector notation as:
\begin{equation}
    \label{eq:kg-eq-4vec}
    \left(\partial_\mu \partial^\mu + m^2\right) \psi(x,t) = 0
\end{equation}
or most succinctly as,
\begin{equation}
    \left(\partial^2 + m^2\right) \psi(x,t) = 0
\end{equation}
The author looked at this equation from three different aspects.

\paragraph{Producing the free particle solution} It is first checked
that the free-particle state:
\begin{equation}
    \psi \propto \exp(-i(Et-\vb{p}\vdot\vb{x})) = e^{-ip^\mu x_\mu}
\end{equation}
is a solution to the Klein-Gorden equation, provided that:
\begin{equation}
    E^2 = \vb{p}^2+m^2
\end{equation}

\paragraph{Probability density} By analogy with non-relativistic case,
the four-vector current is defined as:
\begin{equation}
    j^\mu = \frac{i}{2m}
    [\psi^*\partial^\mu\psi - (\partial^\mu\psi)^*\psi]
\end{equation}
It is easy to show $\partial_\mu j^\mu=0$\footnote{Just note that
normally we have $A^\mu B_\mu = A_\mu B^\mu$}. Then, this is a
conserved current. The time-component of this is the density:
\begin{equation}
    \rho \equiv j^0 = \frac{i}{2m}
    \left[\psi^*\partial_t\psi - (\partial_t\psi)^*\psi\right]
\end{equation}
If one check this equation, one find that $\rho$ is proportionally to
the imaginary of some number which, one has no clear reason to say
whether it is positive or negative. Therefore, the Klein-Gorden
equation leaves one in a bad position to interprate the probability
nature of quantum mechanics (what is a "negative probability"
anyway?).

\paragraph{Coupling to electromagnetic field} The author discusses a
little bit about why, when there is electromagnetic field, we have the
replacement
\begin{equation}
    p\to p+eA
\end{equation}
in page 490, footnote (be careful that the author uses the notation
$e=|e|$, whereas I used the notation $e=-|e|$, i.e. $e$ is just $q$,
the charge).

This coupling effectively gives the replacement:
\begin{equation}
    \partial_\mu \quad\to\quad D_\mu
\end{equation}
where $D_\mu\equiv\partial_\mu - ieA_\mu$.

The Klein-Gorden equation now becomes:
\begin{equation}
    \label{eq:kg-emfield}
    [D_\mu D^\mu+m^2] \psi(x,t) = 0
\end{equation}
This equation revels a connection between $e\to-e$ and
$\psi\to\psi^*$\footnote{You will find this if you complex conjugate
the Klein-Gorden equation.}.

\paragraph{Two component interpretation} The author also mentions a
way to split the equation into two equations. If we define $\phi(x,t)$
and $\chi(x,t)$ as in eq.(8.1.15) in p.491, then it is straightforward
to check that, the Klein-Gorden equation is equivalent to:
\begin{equation}
    iD_t \Upsilon = \left[
    -\frac{1}{2m}\vb{D}^2(\tau_3+i\tau_2)+m\tau_3 \right] \Upsilon
\end{equation}
where $(D_t,\vb{D})=D_\mu$, $\tau_i$ are pauli matrices, and $\Upsilon$ is the
two component wave function:
\begin{equation}
    \Upsilon \equiv \begin{pmatrix}
        \phi(x,t) \\ \chi(x,t)
    \end{pmatrix}
\end{equation}

This formulation enables a mysterious interpretation of negative energy,
negative probability, and particles and antiparticles. For more information,
please look at pp.491~494 of \cite{Sakurai2011}.

\section{Dirac Equation}
\label{sec:Dirac Equation}

The Dirac equation aims to change the Klein-Gorden equation into a first order
PDE. There are two approaches to derive the equation. The first can be found in
section 8.2 of \cite{Sakurai2011}, and section II.1 of \cite{zee2010quantum}.
The second approach is found in page 99 (chapter 2) of \cite{Greiner1997}, and
is prefered in my opinion. After all, they lead to the same equation:

\begin{equation}
    (i\gamma^\mu \partial_\mu - m) \psi(x,t) =0
    \label{eq:dirac-eq}
\end{equation}
Where $\gamma^\mu$ are matrices satisfying:
\begin{equation}
    \frac{1}{2}\{ \gamma^\mu,\gamma^\nu\} = \eta^{\mu\nu}
\end{equation}

In other words, $\gamma^\mu$ is a representation of the Clifford algebra
$\mathrm{Cl}_{1,3}(\R)$. We can cast this equation into another form:
\begin{equation}
    i\pdv{t} ket{\psi} = H \ket{\psi} = \bm{\alpha}\vdot\vb{p}+\beta m
\end{equation}
where $\vb{p}$ is the momentum, $\bm{\alpha}$ and $\beta$ satisfy a similar
relation:
\begin{align}
    \frac{1}{2}\{\alpha_i,\alpha_j\} = \delta_{ij} \\
    \{\alpha_i,\beta\} &= 0 \\
    \alpha_i^2 = \beta^2 &= 0
\end{align}
They are related to $\gamma^\mu$ matrices by:
\begin{equation}
    \alpha_i = \gamma^0 \gamma^i \quad\text{and}\quad
    \beta = \gamma^0
\end{equation}
A detailed formula for $\gamma$ matrices can be found in p.94 of
\cite{zee2010quantum}. A detailed formula for $\alpha_i,\beta$
matrices can be found in p.496 of \cite{Sakurai2011}.

\paragraph{The density problem} The dirac formulation has a appearent advantage.
The current defined by
\begin{equation}
    j^\mu \equiv \bar{\psi}\gamma^\mu\psi
\end{equation}
where
\begin{equation}
    \bar{\psi} \equiv \psi^\dagger \beta
\end{equation}
is conserved. And the probability density $\rho$ is
\begin{equation}
    \rho \equiv j^0 = \psi^\dagger \beta \gamma^0 \psi = \psi^\dagger \psi
\end{equation}
It is positive-definite.

\paragraph{Coupled with a charge} When coupled with electromagnetic
field, and with a the vector potential $\vb{A}=0$, it becomes
\begin{equation}
    H = \bm{\alpha}\vdot\vb{p} + \beta m - e \Phi
\end{equation}
where $\Phi$ is the scalar potential.

\bibliography{cite}{}
\bibliographystyle{alphaurl}

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-03-25 Notes of Bernevig's Book/Notes.tex
[minor] Fixed a typo.

--- 2016-10-21 Notes of Bernvig's Book/Ch2 Berry Phase/Ch2 Berry Phase.tex
@@
 
-\section{Deriving Berry Phase}
-\label{sec:Deriving-Berry-Phase}
-From page 1 to page 2 (equation 2.7), one derives the expression for
-the phase $e^{i\gamma_m}$ using instaneous energy eigenstate for
-$E_m$:
-\begin{align}
-    & H(\vec{R})\ket{n(\vec{R})} = E_m(\vec{R})\ket{n(\vec{R})} \\
-    & \gamma_m = i\int_0^t
-    \braket{
-        m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
-        m\left(\vec{R}(t')\right) \diff t' }
-\end{align}
-Then I writes about different ways to get the $\gamma_m$:
-\begin{align}
-    \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
-    \diff \vec{R}
-\end{align}
-(equation 2.8) 
-Also, one defines
-\begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
-\nomenclature{Berry Connection, Berry Vector Potential
-$\vec{A}$}{\nomrefpage.}
-    \begin{align}
-        \vec{A}_n \equiv i \braket{n|\nabla_{\vec{R}}\, n }
-    \end{align}
-\end{defi}
-Then I proves several facts:
-\begin{fact}
-    \label{fact:gamma_is_real}
-    $  $
-    \begin{center}
-        $\gamma_n$ is real
-    \end{center}
-\end{fact}
-\begin{fact}
-    $ $
-    \begin{center}
-        Berry connection $\vec{A}_n$ is gauge-dependent 
-    \end{center}
-    The dependence is: If 
-    $$\ket{n}\to \ket{n'}= e^{i\xi(\vec{R})}\ket{n}$$
-    then
-    \begin{align}
-        \vec{A}_n \to \vec{A}_n - \nabla_{\vec{R}}\,\xi(\vec{R})
-    \end{align}
-\end{fact}
-Therefore we have
-\begin{fact}
-    $  $
-    \begin{center}
-        $\gamma_n$ is gauge-dependent, unless the path tranverses a
-        closed loop.
-    \end{center}
-    Since 
-    $$ \gamma_n \to \gamma_n - \left(\xi(\vec{R}(T))-
-    \xi(\vec{R}(0)) \right) $$
-    It is unchanged unless the integration curve is a closed loop. In
-    which case
-    $$\xi(\vec{R}(T)) - \xi(\vec{R}(0)) = 2\pi m
-    \overset{\text{mod }2\pi}{=} 0 $$
-\end{fact}
-\begin{ex}
-    There is a simple example on page 3 to show that the Berry phase
-    can be actually detected.
-\end{ex}
-By virtue of fact \ref{fact:gamma_is_real}, we have
+\section{Skipped}
+
+\section{Berry Phase}
+\input{sections/chapter2-berry-phase}
+
+\section{Hall Conductance and Chern Numbers}
+
+This chapter is written in an unbelievably hard to read style. I
+skipped it almost completely. There are a few hand written notes,
+which are not worth even re-read.
+
+\section{Time-Reversal Symmetry}
+
+This chapter contains material important for quantum mechanics in
+general and I had written another note bearing the same name for this
+chapter. Since that note is too big to be contained here, I will left
+here empty and advice one search for "TR Symmetry" in this
+repository for that note.
+
+\section{Magnetic Field on the Square Lattice}
+
 \section{Anchor}

### 2017-03-25 Notes of Bernevig's Book/sections/Ch4 TR symmetry/Notes about TR symmetry.tex
[minor] Fixed a typo.

--- 2016-10-30 Notes of Bernvig's Book/sections/Ch4 TR symmetry/Notes about TR symmetry.tex
@@
     spectrum for time reversal symmetric system will always has symmetric
-    energy spectrum (i.e. with both and symmetric positive and negative
+    energy spectrum (i.e. with both positive and negative
     energy), which is not true.
@@
     basis $\ket{e_i}$, obviously we only need to consider the result of
-    $K\ket{e_i}$. This however, is hard to determine. However we can argue
+    $U\ket{e_i}$. This however, is hard to determine. However we can argue
     that in case when the basis has some classical connection, then by the
@@
             e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
-            &= T \ket{n} = e^{i\eta} \ket{n}
+            &= T \ket{n} = e^{-i\eta} \ket{n}
         \end{align*}

### 2017-03-25 Notes of Bernevig's Book/sections/chapter2-berry-phase.tex
[minor] Fixed a typo.

--- 2016-10-22 Notes of Bernvig's Book/Ch2 Berry Phase/Ch2 Berry Phase.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-\usepackage{float}  % For H in figures
-\usepackage{amsmath} % For math
-\usepackage{amssymb}
-\usepackage{bbm} % for numbers within mathbb
-\usepackage{mathrsfs} % For \mathscr{ABC}
-\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
-                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
-\usepackage{graphicx}   % need for figures
-\usepackage{cite} % need for bibligraphy.
-\usepackage[unicode]{hyperref}  % make every cite a link
-\usepackage{CJKutf8} % For Chinese characters
-\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
-
-% For highlighting
-\usepackage{color,soul}
-
-% Following is for theorems etc environments
-% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
-\usepackage{amsthm}
-\newtheorem{defi}{Definition}[section]
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{prop}{Proposition}[section]
-\newtheorem{coro}{Corollary}[section]
-\newtheorem{fact}{Fact}[section]
-\theoremstyle{definition}
-\newtheorem{ex}{Example}[section]
-\newtheorem{argument}{Argument}[section]
-
-% A list of nomenclatures.
-\usepackage{nomencl}
-\makenomenclature
-
-% For drawing diagrams with arrows
-\usepackage[all]{xy}
-
-% -=---------------- My Own New commands ---------------
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physics-taper}
-% Referenced package: \usepackage{physics}
-
-%  Vector notation ---------------------
-% \DeclareDocumentCommand\vectorbold{ s m }{
-%     \IfBooleanTF{#1}
-%     {\boldsymbol{#2}}
-%     {\mathbf{#2}}
-% } % Vector bold [star for Greek and italic Roman]
-% \DeclareDocumentCommand\vb{}{\vectorbold} % Shorthand for \vectorbold
-% 
-% \DeclareDocumentCommand\vectorunit{ s m }{
-%     \IfBooleanTF{#1}
-%     {\boldsymbol{\hat{#2}}}
-%     {\mathbf{\hat{#2}}}
-% } % Unit vector [star for Greek and italic Roman]
-% \DeclareDocumentCommand\vu{}{\vectorunit} % Shorthand for \vectorunit
-% 
-% \DeclareDocumentCommand\vdot{}{\boldsymbol\cdot} % Vector dot product symbol
-% \DeclareDocumentCommand\cross{}{\boldsymbol\times} % Vector cross product symbol
-% \DeclareDocumentCommand\vnabla{}{\boldsymbol\nabla} % Vector bold \nabla symbol
-% \DeclareDocumentCommand\grad{}{\vnabla} 
-% \DeclareDocumentCommand\dive{}{\vnabla\vdot} 
-% \DeclareDocumentCommand\curl{}{\vnabla\cross}
-% \DeclareDocumentCommand\laplacian{}{\nabla^2} 
-% 
-% % Operators ----------------------------
-% \let\imaginary\Im
-% \RenewDocumentCommand\Im{g}{
-%     \IfNoValueTF{#1}
-%     {\operatorname{Im}}
-%     {\operatorname{Im}\left\{ #1 \right\}}
-% }
-% \let\real\Re
-% \DeclareDocumentCommand\Re{g}{
-%     \IfNoValueTF{#1}
-%     {\operatorname{Re}}
-%     {\operatorname{Re} \left\{ #1 \right\} }
-% }
-\title{Notes of Chapter 2 of Bernevig's Book}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-Since I have already made a written one, this note is only an outline
-of the written script, in the hope of makeing it eaiser to read.
-}
-\tableofcontents
-
-\section{Deriving Berry Phase}
+\subsection{Deriving Berry Phase}
 \label{sec:Deriving-Berry-Phase}
@@
 
-\section{Gauge-independent calculation of Berry Curvature}
+\subsection{Gauge-independent calculation of Berry Curvature}
 \label{sec:Gauge-independent-calculation-of-Berry-Curvature}
@@
 
-\section{Degeneracy and level-crossing}
+\subsection{Degeneracy and level-crossing}
 \label{sec:Degeneracy-and-level-crossing}
@@
 
-    \subsection{Two-level system and Berry connection
+    \subsubsection{Two-level system and Berry connection
     \texorpdfstring{$\vb{A}_n$}{}}
@@
 
-        \subsubsection{Two-level system using Hamiltonian approach}
+        \paragraph{Two-level system using Hamiltonian approach}
         \label{sec:Two-level-system-using-Hamiltonian-approach}
@@
         \end{remark}
-\section{Anchor}
-\label{sec:Anchor}
-
-\begin{thebibliography}{1}
-    \bibitem{book} Bernevig's Topological Insulators and
-    Superconductors
-\end{thebibliography}
-\printnomenclature
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
-\end{document}

### 2017-03-27 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Explorer the Lattice Dirac Model in infinite cylinder B.C.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{TR Invariant T.I.}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    An incomplete note of dissertation by Taylor Hughes
    \cite{Hughes2009}.
}
\tableofcontents
Start with chapter 2.

Questions:
\begin{itemize}
    \item Do we have a precise definition of \textit{topological phase
        transition}?
\end{itemize}

\section{Spectrum of \texorpdfstring{$(2+1)$}-d Lattice Dirac Model}
\label{sec:2+1d-LDirac Model}
\begin{align}
    H_{LD} &= \sum_{m,n}\left\{
        i \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
            - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
        + i \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
            - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
        \right.
        \nonumber\\
        &- \left[
            c^\dagger_{m+1,n}\sigma^z c_{m,n}
            + c^\dagger_{m,n}\sigma^z c_{m+1,n}
            + c^\dagger_{m,n+1}\sigma^z c_{m,n}
            + c^\dagger_{m,n}\sigma^z c_{m,n+1}
        \right]
        \nonumber\\
        & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
        \vphantom{xx}\frac\hbar2
    \right\}
\end{align}

Above is the lattice model (eq.2.19) of \cite{Hughes2009}. Here it
should be noted that $c_{m,n}=(c_{u,m,n}, c_{v,m,n})$ for two degrees
of freedom.

This Hamiltonian is solved here with a infinite cylinder geometry, i.e.
the lattice is infinite in $x$ direction while being periodic in $y$
direction. Because of this special setup, the $p_x$ is still a good
quantum number. Therefore we can do a fourier expansion in $x$
direction:

\begin{equation}
    c_{m,n} = \frac{1}{\sqrt{L_x}} \sum_{p_x} e^{ip_x m} c_{p_x,n}
\end{equation}

The resulted Hamiltonian is

\begin{align}
    \tilde H_{LD} = \sum_{n,p_x}\quad &
    2\sin(p_x) c^\dagger_{p_x,n}\sigma^x c_{p_x,n}
    +i \left[ c^\dagger_{p_x,n+1}\sigma^y c_{p_x,n} - 
        c^\dagger_{p_x,n+1}\sigma^y c_{p_x,n}\right]
    \nonumber\\
    &- \left[ 2\cos(p_x) c^\dagger_{p_x,n}\sigma^z c_{p_x,n}
        c^\dagger_{p_x,n+1}\sigma^z c_{p_x,n}
        + c^\dagger_{p_x,n}\sigma^z c_{p_x,n+1}
    \right]
    \nonumber\\
    &+ (2-m) c^\dagger_{p_x,n}\sigma^z c_{p_x,n}
\end{align}

This Hamiltonian can be solved by acting it on the test wavefunction:
\begin{equation}
    \ket{\psi_{p_x}} = \sum_n \psi_{p_x,n,u} c^\dagger_{p_x,n,u} +
                        \psi_{p_x,n,v} c^\dagger_{p_x,n,v} \ket{0}
\end{equation}

Note, in choosing the test wavefunction, $u$ and $v$ could not be
seperated, because there is still interaction between the two
component in terms like $c^\dagger_{p_x,n}\sigma^x c_{p_x,n}$.
If we calculate $\tilde H_{LD}\ket{\psi_{p_x}} = E_{p_x}
\ket{\psi_{p_x}}$, we would get after careful calculation:

\begin{align}
    & \sum_n
    c^\dagger_{p_x,n} A   \psi_{p_x,n-1}
    + c^\dagger_{p_x,n} B \psi_{p_x,n} 
    + c^\dagger_{p_x,n} C \psi_{p_x,n+1}
    \nonumber\\
    &= E_{p_x} \sum_n c^\dagger_{p_x,n}\psi_{p_x,n}
\end{align}
where
\begin{align}
    c^\dagger_{p_x,n} &= \begin{pmatrix}
        c^\dagger_{p_x,n,u},  c^\dagger_{p_x,n,v}
    \end{pmatrix} \\
    A &= i\sigma^y - \sigma^z \\
    B &= 2\sin(p_x)\sigma^x - 2\cos(p_x)\sigma^z + (2-m)\sigma^z \\
    C &= -i\sigma^y - \sigma^z \\
    \psi_{p_x,n} &= \begin{pmatrix}
        \psi_{p_x,n,u} \\ \psi_{p_x,n,v}
    \end{pmatrix}
\end{align}

Suppose there is $N$ lattice in the $y$ direction. Then the periodic
boundary condition implies that $\psi_{N+1}=\psi_{n=1}$, and
$\psi_{n=0} = \psi_N$.

Therefore, the eigenvalue equation could be turned into a matrix form:
\begin{align}
    H_{\text{disc}} \psi \equiv 
    \begin{pmatrix}
        B   & C &        &   & A \\
        A   & B & C      &   & \\
            & A & B      & C & \\
            &   & \cdots &   & \\
            &   & A      & B & C \\
        C   &   &        & A & B
    \end{pmatrix}
    \begin{pmatrix}
        \psi_{p_x,1} \\
        \psi_{p_x,2} \\
        \cdots \\
        \\
        \\
        \psi_{p_x,N} \\
    \end{pmatrix} =
    E_{p_x}
    \begin{pmatrix}
        \psi_{p_x,1} \\
        \psi_{p_x,2} \\
        \cdots \\
        \\
        \\
        \psi_{p_x,N} \\
    \end{pmatrix}
\end{align}

    \subsection{Numerical result}
    \label{sec:Numerical result}
    \textbf{Note}: Results in this section are contained in the file
    "Lattice Dirac Model (2+1)-d.nb", and the file
    "Dirac\_Lattice\_Model\_21\_d.m".

    Let us take $N=3$ for simplicity. The eigenvalue problem is solve
    using Mathematica, and the $6$ eigenvalues are:
    \begin{equation}
        \begin{pmatrix}
        -\sqrt{m^2+4 m \cos (\text{px})+4}\\
        \sqrt{m^2+4 m \cos (\text{px})+4}\\
        -\sqrt{m^2+4 m \cos (\text{px})-6 m-12 \cos (\text{px})+16}\\
        -\sqrt{m^2+4 m \cos (\text{px})-6 m-12 \cos (\text{px})+16}\\
        \sqrt{m^2+4 m \cos (\text{px})-6 m-12 \cos (\text{px})+16}\\
        \sqrt{m^2+4 m \cos (\text{px})-6 m-12 \cos (\text{px})+16}
        \end{pmatrix}
    \end{equation}

    It is found that at $m=-2$, there is a band crossing at $p_x=0$:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N6m-2.pdf}
        \caption{The Eigenvalue plot for $m=-2$. Plotted as
        $E_{p_x}$v $p_x$ }
    \end{figure}

    Also, at $m=2$, there is a band crossing at $p=\pm\pi$:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N6m2.pdf}
        \caption{The Eigenvalue plot for $m=2$. Plotted as
        $E_{p_x}$v$p_x$ }
    \end{figure}

    Since the paper will be focusing in points around $p_x=0$, I will
    focus in $m=-2$. In this case, I want to find more information
    about the eigenvectors.

    When I looked blindly at the value $(m,p_x)=(-2,0)$, the
    Mathematica gave me two eigenvectors both corresponds to the
    eigenvalue $0$:
    \begin{equation}
        \{0,1,0,1,0,1\},\{1,0,1,0,1,0\}
    \end{equation}
    It led me to believe that there are two spin waves, with made with
    purely spin up waves and another of purely spin down waves. But
    this is not correct.

    It is found later that the matrix $H_\text{disc}$ is singular
    (with determinant $0$) when $(m,p_x)=(-2,0)$. Also, a Matlab
    calculation shows that the eigenvectors of the crossing bands
    actually flunctuate between $\pm 1$ in a way illustrated as below:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/Eigenvector-m.eps}
    \end{figure}

    Also, the Mathematica solved eigenvector also demonstrate a
    drastical change around $m=-2$. For example, one component, when
    plotted against $p_x$ change from:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/mN3.pdf}
        \caption{$m=-3$}
    \end{figure}
    to
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/{mN2.5}.pdf}
        \caption{$m=-2.5$}
    \end{figure}
    and suddenly to
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/mN2.pdf}
        \caption{$m=-2$. There is a discontinuity at $p_x=0$}
    \end{figure}
    Finaly, it becomes smooth again:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/{mN1.5}.pdf}
        \caption{$m=-1.5$}
    \end{figure}
    The details can be explored in the Mathematica notebook.

    Also, the case of $N=4$ is also calculated in Mathematica.
    There are similarly two crossing happening at $(m,p_x)$ equals
    $(-2,0)$ and $(2,\pm\pi)$.

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N8m2.pdf}
        \caption{$m=2$}
    \end{figure}
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N8m-2.pdf}
        \caption{$m=-2$}
    \end{figure}

    Surprisingly, the two bands that cross are have exactly the same
    function dependence on $p_x$ and $m$ for the cases of $N=3$ and
    $N=4$.

    \subsection{Discussion about the Lattice Model}
    \label{sec:DisAboutLatticeModel}
    I notice that equation (2.19) transformed according to (2.20)
    is not exactly equation (2.21), but is:
    \begin{align}
        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
        \nonumber\\
        &
        \left[
            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
        \right] c_{p_x,p_y}
    \end{align}
    This result does not become the continuum Dirac Hamiltonian as
    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
    constants should be modified so that:

    \begin{align}
        H_{LD} &= \sum_{m,n}\left\{
            \frac{i}{2} \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
                - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
            + \frac{i}{2} \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
                - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
            \right.
            \nonumber\\
            &- \frac{1}{2}\left[
                c^\dagger_{m+1,n}\sigma^z c_{m,n}
                + c^\dagger_{m,n}\sigma^z c_{m+1,n}
                + c^\dagger_{m,n+1}\sigma^z c_{m,n}
                + c^\dagger_{m,n}\sigma^z c_{m,n+1}
            \right]
            \nonumber\\
            & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
            \vphantom{\frac12}
        \right\}
    \end{align}

    This affects the numerical analysis effectively by the replacement
    $$\sigma^i \to \frac{1}{2}\sigma^i,\quad
        (2-m) \to 2(2-m) $$

    And the result is similar to previous study, except that the band
    crossing happens at different values of $m$. For example, the
    eigenvalue of original and the modified equation (2.21) are
    plotted in Mathematica notebook "Eq2.21-Demo.nb". Also, the
    solution to the infinite cylinder boundary condition has again two
    band crossings, each at $(m,p_x)$ equals $(0,0)$ and $(2,\pm\pi)$
    (for $N=3$ case).

\bibliography{cite}{}
\bibliographystyle{alphaurl}

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2017-03-27 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/programs/Dirac_Lattice_Model_21_d.m

@@ -1,0 +1,90 @@
+clear all;
+% This File has two purposes. Therefore, it plots two different graphs.
+% Explanations of the two purposes is provided in the end of this
+% file.
+PY = [-pi:0.25:pi];
+M = [-3:0.1:3];
+sigma1 = [0,1;1,0];
+sigma2 = [0,-1i;1i,0];
+sigma3 = [1,0;0,-1];
+A = 1i*sigma2 - sigma3;
+C = -1i * sigma2 - sigma3;
+TheTransferM = zeros(6);
+i = 0;
+for m = M
+    i = i+1; % i for m
+    j = 0;
+    for py = PY
+        j = j+1; % j for py
+
+        B = 2*sin(py)*sigma1 - 2*cos(py)* sigma3 + (2-m)*sigma3;
+        TheTransferM(1:2,1:2) = B;
+        TheTransferM(1:2,3:4) = C;
+        TheTransferM(1:2,5:6) = A;
+        for k = 2:2
+            B = 2*sin(py)*sigma1 - 2*cos(py)* sigma3 + (2-m)*sigma3;
+            TheTransferM(2*k-1:2*k,2*(k-1)-1:2*(k-1)) = A;
+            TheTransferM(2*k-1:2*k,2*(k  )-1:2*(k  )) = B;
+            TheTransferM(2*k-1:2*k,2*(k+1)-1:2*(k+1)) = C;
+        end
+        TheTransferM(5:6,1:2) = C;
+        TheTransferM(5:6,3:4) = A;
+        TheTransferM(5:6,5:6) = B;
+        [~,Eigenvalue]=eig(TheTransferM);
+        D1(i,j) = Eigenvalue(1,1);
+        D2(i,j) = Eigenvalue(2,2);
+        D3(i,j) = Eigenvalue(3,3);
+        D4(i,j) = Eigenvalue(4,4);
+        D5(i,j) = Eigenvalue(5,5);
+        D6(i,j) = Eigenvalue(6,6);
+    end
+    for py = 0
+        B = 2*sin(py)*sigma1 - 2*cos(py)* sigma3 + (2-m)*sigma3;
+        TheTransferM(1:2,1:2) = B;
+        TheTransferM(1:2,3:4) = C;
+        TheTransferM(1:2,5:6) = A;
+        for k = 2:2
+            B = 2*sin(py)*sigma1 - 2*cos(py)* sigma3 + (2-m)*sigma3;
[…]

### 2017-03-29 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Update something about spin-waves in this model...

@@
 of freedom.
+
+\subsection{Numerical Solution in Infinity Cylinder Geometry}
+\label{sec:Numerical Solution in Infinity Cylinder Geometry}
 
@@
 
-    \subsection{Numerical result}
-    \label{sec:Numerical result}
-    \textbf{Note}: Results in this section are contained in the file
+\textbf{Note}: Numerical calculations in this section are contained in the file
 "Lattice Dirac Model (2+1)-d.nb", and the file
@@
     \centering
-        \includegraphics[width=0.6\linewidth]{pics/N6m-2.pdf}
+    \includegraphics[width=0.2\linewidth]{pics/N6m-2.pdf}
     \caption{The Eigenvalue plot for $m=-2$. Plotted as
-        $E_{p_x}$v $p_x$ }
+    $E_{p_x}$-$p_x$ }
 \end{figure}
@@
     \caption{The Eigenvalue plot for $m=2$. Plotted as
-        $E_{p_x}$v$p_x$ }
+    $E_{p_x}$-$p_x$ }
 \end{figure}
 
-    Since the paper will be focusing in points around $p_x=0$, I will
-    focus in $m=-2$. In this case, I want to find more information
+When the band crosses, there will be two eigenvectors, corresponds to
+the two crossed bands, in the form of:
+\begin{align}
+    \psi_{p_x} &= \left(\vphantom{\frac12}\psi(p_x),1,\psi(p_x),1,\psi(p_x),1\right)^T \\
+    \phi_{p_x} &= \left(\vphantom{\frac12}\phi(p_x),1,\phi(p_x),1,\phi(p_x),1\right)^T
+\end{align}
+where $\psi(p_x)$ and $\phi(p_x)$ are functions of $p_x$. A look into
+the plot of $\psi(p_x)$ and $\phi(p_x)$ reveals that they together
+provide the path way for excited particles to transfer from the lower
+band to the upper band.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/upperSpinWaveMN2.pdf}
+    \caption{Plot of $\psi(p_x)$ and $\phi(p_x)$ when $m=-2$}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/upperSpinWaveM2.pdf}
+    \caption{Plot of $\psi(p_x)$ and $\phi(p_x)$ when $m=2$, where I
+    have extended the range s.t. $p_x\in\{-\pi,3\pi\}$ to make the
+    meaning clear.}
+\end{figure}
+
+Therefore, one may predict a pure spin-up wave transfering in the
+point $p_x=0$ when $m=2$, and $p_x=\pm\pi$ when $m=2$.
+
+    \subsection{Why I think the Lattice Model is wrong}
+
+    I notice that equation (2.19) transformed according to (2.20)
+    is not exactly equation (2.21), but is:
+    \begin{align}
+        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
+        \nonumber\\
+        &
+        \left[
+            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
+            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
+        \right] c_{p_x,p_y}
+    \end{align}
+    This result does not become the continuum Dirac Hamiltonian as
+    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
+    constants should be modified so that:
+
+    \begin{align}
+        H_{LD} &= \sum_{m,n}\left\{
+            \frac{i}{2} \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
+                - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
+            + \frac{i}{2} \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
+                - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
+            \right.
+            \nonumber\\
+            &- \frac{1}{2}\left[
+                c^\dagger_{m+1,n}\sigma^z c_{m,n}
+                + c^\dagger_{m,n}\sigma^z c_{m+1,n}
+                + c^\dagger_{m,n+1}\sigma^z c_{m,n}
+                + c^\dagger_{m,n}\sigma^z c_{m,n+1}
+            \right]
+            \nonumber\\
+            & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
+            \vphantom{\frac12}
+        \right\}
+    \end{align}
+
+    This affects the numerical analysis effectively by the replacement
+    $$\sigma^i \to \frac{1}{2}\sigma^i,\quad
+        (2-m) \to 2(2-m) $$
+
+    The calculated result is similar to that in the previous section,
+    except that the band crossing happens at different values of $m$.
+    \footnote{For example, the eigenvalue of original and the modified equation
+    (2.21) are plotted in Mathematica notebook "Eq2.21-Demo.nb". Also,
+    the solution to the infinite cylinder boundary condition has again
+    two band crossings, each at $(m,p_x)$ equals $(0,0)$ and
+    $(2,\pm\pi)$ (for $N=3$ case).}
+    So the essential point is unaltered by the difference in some
+    constants. However, in the correct calculation, the crossing band
+    appears at $m=0$, which represents a massless spin-$\frac{1}{2}$
+    particle. I think this should have some theoretical implications.
+
+\subsection{Calculation Note unrelated to the main-subject}
+
+Since the paper will be focusing in points around $p_x=0$, I focused
+in $m=-2$ at first. In this case, I want to find more information
 about the eigenvectors.
@@
 
-    \subsection{Discussion about the Lattice Model}
-    \label{sec:DisAboutLatticeModel}
-    I notice that equation (2.19) transformed according to (2.20)
-    is not exactly equation (2.21), but is:
-    \begin{align}
-        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
-        \nonumber\\
-        &
-        \left[
-            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
-            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
-        \right] c_{p_x,p_y}
-    \end{align}
-    This result does not become the continuum Dirac Hamiltonian as
-    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
-    constants should be modified so that:
-
-    \begin{align}
-        H_{LD} &= \sum_{m,n}\left\{
-            \frac{i}{2} \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
-                - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
-            + \frac{i}{2} \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
-                - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
-            \right.
-            \nonumber\\
-            &- \frac{1}{2}\left[
-                c^\dagger_{m+1,n}\sigma^z c_{m,n}
-                + c^\dagger_{m,n}\sigma^z c_{m+1,n}
-                + c^\dagger_{m,n+1}\sigma^z c_{m,n}
-                + c^\dagger_{m,n}\sigma^z c_{m,n+1}
-            \right]
-            \nonumber\\
-            & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
-            \vphantom{\frac12}
-        \right\}
-    \end{align}
-
-    This affects the numerical analysis effectively by the replacement
-    $$\sigma^i \to \frac{1}{2}\sigma^i,\quad
-        (2-m) \to 2(2-m) $$
-
-    And the result is similar to previous study, except that the band
-    crossing happens at different values of $m$. For example, the
-    eigenvalue of original and the modified equation (2.21) are
-    plotted in Mathematica notebook "Eq2.21-Demo.nb". Also, the
-    solution to the infinite cylinder boundary condition has again two
-    band crossings, each at $(m,p_x)$ equals $(0,0)$ and $(2,\pm\pi)$
-    (for $N=3$ case).
-
 \bibliography{cite}{}

### 2017-03-29 Draft/sections/misc-physics.tex
Some micellaneous useful physical ponts.
[minor] Why we should Fourier-transform Creation/Annihilation operator like that!

@@
 For the book \cite{griffiths-EM}, pp. 120 of section 3.1.6. 
+\subsection{Fourier transformation of Creation and Annihilation
+Operators}
+\label{sec:Fourier-CreationAnnihilation}
+There is one pitfall when dealing with fourier transformation of creation or
+annihilation operators. Suppose we have (for fermions):
+\begin{equation}
+    c_k = \sum_m e^{-ikm} c_m
+    \label{eq:fourier-ck}
+\end{equation}
+(ignoring all unnecessary normalization factors)
+Then there are two ways to process the fourier transformation of $c^\dagger_m$:
+
+\textbf{First}, we could start with mathematical precision, and define:
+\begin{equation}
+    \mathcal{F}[c^\dagger_m](k) \equiv \sum_m e^{-ikm}c^\dagger_m
+\end{equation}
+\textbf{Second}, we could instead define:
+\begin{equation}
+    c^\dagger_k \equiv \sum_m e^{ikm} c^\dagger_m
+    \label{eq:fourier-cDaggerK}
+\end{equation}
+The second definition is most encountered in physics literature, because it has
+several benefits. The first is that it is intuitively straightforward to proceed
+from eq.\ref{eq:fourier-ck} to eq.\ref{eq:fourier-cDaggerK}. The second point is
+that, the second definition preserves the commutation relationship. It is
+straightforward to get,
+\begin{align}
+    \{c_k,c^\dagger_{k'}\} &= \delta_{k,k'} \\
+    \{c_k,\mathcal{F}[c^\dagger_m](k')\} &= \delta_{k,-k'}
+    \label{eq:anticom-ckfck}
+\end{align}
+This explains what I mean by preserving the commutation relationship.
+And, in the second approach, the inverse fourier transformation is also
+different:
+\begin{align}
+    c_m &= \sum_k e^{ikm} c_k \\
+    c^\dagger_m &= \sum_k e^{-ikm} c^\dagger_k
+\end{align}
+
+Below we make several remarks.
+\begin{remark}
+    It should be noted that, if we start with defining
+    \begin{equation}
+        c^\dagger_k \equiv \sum_m e^{-ikm} c^\dagger_m
+    \end{equation}
+    Then, we would have, instead of eq.\ref{eq:fourier-ck}
+    \begin{equation}
+        c_k \equiv \sum_m e^{ikm} c_m
+    \end{equation}
+\end{remark}
+
+\begin{remark}
+    It should also be noted that, mathematically we have the theorem:
+    \begin{equation}
+        \mathcal{F}[f^*(m)](k) = (\mathcal{F}[f(m)])^*(-k)
+    \end{equation}
+    Although, it deals only with complex conjugation, here we could analogously
+    regard the theorem as if $*$ is $\dagger$. Therefore,
+    \begin{equation}
+        \mathcal{F}[c^\dagger_m](k) = c^\dagger_{-k}
+    \end{equation}
+    which explains eq.\ref{eq:anticom-ckfck} from another aspect.
+\end{remark}
+
+\begin{remark}
+    Lastly, let's don't forget that the same fact hold with bosons operators, with
+    $\{,\}\overset{\text{replaced by}}{\to}[,]$.
+\end{remark}
+
+\subsection{Miscellaneous}
+\label{sec:Miscellaneous}
+
+\paragraph{Transpose in Q.M.}
+
+Transpose is somehow rare in quantum mechanics. Consider a complete
+basis $\ket{n}$. By definition of adjoint (dagger), one has
+\begin{equation}
+    \braket{ An|m }=\braket{n | A^\dagger m}
+\end{equation}
+Also, one has
+\begin{equation}
+    \braket{ An|m } = \braket{ m|An }^*
+\end{equation}
+so
+\begin{equation}
+    \braket{ n|A^\dagger m } = \braket{ m|An }^* = \braket{ m|A|n }^*
+\end{equation}
+By this one sees that the operator $\dagger$ is transpose conjugate.
+Therefore, the transpose of an operator $A$ is an operator
+$\tensor[^t]{A}{}$ such
+\begin{equation}
+    \braket{ n|\tensor[^t]{A}{}|m } = \braket{ m|A|n }
+\end{equation}

### 2017-03-30 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] small modifications to the article to make it more clear.

@@
     \centering
-    \includegraphics[width=0.2\linewidth]{pics/N6m-2.pdf}
+    \includegraphics[width=0.6\linewidth]{pics/N6m-2.pdf}
     \caption{The Eigenvalue plot for $m=-2$. Plotted as
@@
     \caption{Plot of $\psi(p_x)$ and $\phi(p_x)$ when $m=2$, where I
-    have extended the range s.t. $p_x\in\{-\pi,3\pi\}$ to make the
+    have extended the plot range s.t. $p_x\in\{-\pi,3\pi\}$ to make the
     meaning clear.}
@@
 
-Therefore, one may predict a pure spin-up wave transfering in the
-point $p_x=0$ when $m=2$, and $p_x=\pm\pi$ when $m=2$.
+Therefore, I think
+\footnote{If I interpret the two component $u,v$ as one for spin up
+and the other for spin down.} 
+this represents a pure spin-up wave transfering in the point $p_x=0$
+when $m=2$, and $p_x=\pm\pi$ when $m=2$.
 

### 2017-04-09 Conferences OR Schools/Boulder Summer School 2016/classification of topological matter by a. ludwig.tex
[major] (Almost complete) note for Ludwig's lecture introducing to the classification

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

% \newcommand\keydash[]{

\title{Classification lecture by A. Ludwig}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
This presents notes for Ludwig's lecture in BSS-2016. It took a lot of
content directly from Ludwig's handwritten notes. Those notes are
available from
\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{BSS's
website}.

This not serves as majorly an introduction to the classification
framework. It introduces the reason why the classification is done
with anti-unitary symmetries and explains how the three symmetries
(T,C,S) are related to the Ten-fold classes of Hamiltonians.
}

\tableofcontents

\section{Reference suggested}
\label{sec:Reference suggested}

This work is done with A. Ludwig, and his collaborators: Shinsei Ryu,
Andreas Schnyder, Akira Furusaki, Joel Moore.

The most recent review (at that time) is: \cite{LudwigNobelSym}.
Besides, the author also suggested many useful references:
\cite{Schnyder2009},\cite{Schnyder2008},\cite{Ryu2010},
\cite{Ryu2012}, \cite{Kitaev2009a}, \cite{Chiu2013},
\cite{Zirnbauer1996}, \cite{Altland1997}, \cite{Heinzner2005},
\cite{Ryu2015}, \cite{Witten2016}.

\section{General Introduction}
\label{sec:General Introduction}

Before the classification, we should first clarify the objects that we
are going to classify. There are \textit{roughly} two types of
materials that we called topological, according to Ludwig. They are:
\begin{enumerate} % Two class of Topological M
    \item Topological phase with intrinsic topological order.

        For example, the Fractional Quantum Hall state. Typically they
        have:
        \begin{itemize}
            \item Ground state degeneracy on topologically non-trivial
                position space.
            \item Anyonic excitations which may have fractional
                quantum numbers and non-trivial Braiding properties.
        \end{itemize}

    \item Symmetry Protected Topological (SPT) Phases

        (example: The $(2+1)$d $(p+ip)$ superconductor has a small
        symmetry group $\Z_2$ (Fermion parity) protecting its SPT
        phase.)
        \begin{itemize}
            \item which have \textbf{none} of the above properties,
            \item but whose ground state cannot be continuously
                deformed into a direct product state (without crossing
                a quantum phase transition at which the gap closes),
                \todo{quantum phase trans?}
                as long as the symmetry protecting the SPT is
                protected.
        \end{itemize}
\end{enumerate}

The aim of this classification is to classify the $2^{\text{nd}}$
group, that of those SPT phases.

\textbf{About this classification}
\begin{itemize}
    \renewcommand{\labelitemi}{$\rightarrow$}
    \item Topological insulators and topological superconductors
        of non-interacting fermions provide the simplest and first
        examples SPT phases.

        They can be completely classified in any dimension of space.
        There are several approaches to this classification.

    \item More general, interacting fermionic SPT phases is not
        yet fully understood. However, their classification should be
        built upon these "templates" of non-interacting cases.
    \item This simplest and most general classification applies to
        the case when only anti-unitarily realized symmetries are
        required to protect the SPT phase. 
    \item (\textbf{Important Note}: all that we talked about being
        \textit{realized}, are refer to the realization in
        $1$st-quantized Hamiltonian, not in the $2$nd-quantized
        Hamiltonian. For example, as we shall see, charge conjugation
        ($C$) is unitary in the $2$nd-quantized Hamiltonian, but
        anti-unitary in the $1$st-quantized Hamiltonian.
    \item This Ten-fold way, is a framework to characterize all possible
        Hamiltonians (single-particle Hamiltonians). (Ref.
        \cite{Zirnbauer1996},\cite{Altland1997},\cite{Schnyder2009}.)
    \item The unitarily realized symmetries are not required to
        protect our SPT, in the sense which will be explained
        immediately. The reason for not considering those unitarily
        realized symmetry is that their classification will depends on
        the specific symmetry group that implements the symmetry.
        Hence its classification will not be as universal as in the
        case of anti-unitarily realized symmetries.

\end{itemize}

\textbf{Looking further}: For Bosonic SPT, the group cohomology
approach aims to address this issue. For fermionic SPT, there are
generalizations of this approach, named group super-cohomology, which
is currently under exploration.

\begin{key}[Why No Unitarily realized symmetry]
    If the Hamiltonian has a symmetry that is unitarily realized, then
    by Quantum Mechanics this Hamiltonian can be block diagonalized,
    and its blocks will not possess memory of the unitary symmetry,
    i.e. they do not commute with the unitary matrix representation of
    that symmetry. Also, those blocks are responsible for the
    topological properties of the system. \todo{really? How they are
    responsible?}

    Therefore, our classification of symmetry is in fact a
    classification of these block Hamiltonians. And it turns out that
    the classification in terms of anti-unitarily realized symmetry
    does not depend on the specific matrix that represents the
    symmetry. In contrast, the classification in terms of unitarily
    realized symmetry depends on the specific group that implements the
    symmetry.
    \todo{What contrast? Specific matrix v.s. Specific group?}

    It may happen that the Hamiltonian possesses some unitarily
    realized symmetries. But these symmetries do not affect our
    classification since when the Hamiltonian becomes a block-diagonal
    matrix, the blocks has no memory of the unitarily realized
    symmetries, i.e. \textit{unitary symmetries do not give more
    constraints to any of the blocks}.
\end{key}

\paragraph{Specification of above statements}

Suppose we have a non-interacting Hamiltonian in the $2$nd-quantized
Fock space:

\begin{equation}
    \label{eq:H-2nd}
    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
\end{equation}

Where $A,B$ label lattice sites (goes from $1$ to $N$), and possibly
spin indices (then goes from $1$ to $2N$). $H_{AB}$
is the 1st quantized Hamiltonian.\todo{Is it single-particle? Make it
precise!}.

Suppose the Hamiltonian is invariant under a symmetry transformation
$\hat{U}$:

\begin{equation}
    \label{eq:sym-in-2nd-1}
    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
\end{equation}

And it acts on creation and annihilation operators by a matrix $u$:
\begin{align}
    \label{eq:sym-in-2nd-2}
    \hat{\psi}'_A = 
    \hat{U} \hat\psi_A \hat{U}^{-1} &=
    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
    \label{eq:sym-in-2nd-3}
    \hat\psi'^\dagger_A =
    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
    \sum_B  \hat\psi^\dagger_B u_{AB}
\end{align}

(we could think about $ \hat\psi^\dagger_A$ as a row vector, and
$\hat\psi_B$ as a column vector. This helps us remember this rules.)

It is easy to find that preserving of canonical commutation relation
($\{\hat\psi'^\dagger_A,\hat\psi'_B\}=\delta_{A,B}$), implies that the
matrix $u$ is unitary.

Next, when we want to pass from the $2$nd quantized picture to the
first quantized picture, we immediately realized one thing.

\paragraph{The linear problem} Passing from $2$nd quantized to the
1st quantized (i.e. plugging Eq.\ref{eq:sym-in-2nd-1},
Eq.\ref{eq:sym-in-2nd-2}, Eq.\ref{eq:sym-in-2nd-3} into
Eq.\ref{eq:H-2nd}), one is faced with $\hat{U} H_{AB} \hat{U}^{-1}$.
If $\hat{U}$ is unitary, then $H_{AB}$ is unchanged. Otherwise,
$H_{AB}$ becomes $H^*_{AB}$.

\paragraph{The unitary (linear) case and the block form of
Hamiltonian}
Suppose we choose $\hat{U}$ to be unitary, then on the 1st quantized
Hamiltonian will satisfy the usual condition:
\begin{equation}
    u H u^{-1} = H
\end{equation}

In this situation, the Hamiltonian will have a block form. More
precisely, suppose all our symmetry transformations form a group
$G_0$. Denote $\mathcal{V}$ as the $N$-dimensional single-particle
Hilbert space spanned by the single-particle states:
\begin{equation}
    \ket{A} = \hat\psi^\dagger_A \ket{0}, \quad A = 1,\cdots,N
\end{equation}
($\ket{0}$ is the Fock vacuum.)

We have
\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
$\mathcal{V}_\lambda$ associated with the irrep (irreducible
representations, labeled by $\lambda$) of $G_0$.
\begin{equation}
    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
\end{equation}
where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
Denote the dimension of each irrep as $d_\lambda$.

In each vector space $\mathcal{V}_\lambda$, one can choose a
(orthogonal) basis of the form:
\begin{equation}
    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
\end{equation}
where
\begin{itemize}
    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
        $k=1,\cdots,d_\lambda$,
    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
        $\alpha=1,\cdots,m_\lambda$.
\end{itemize}
\end{thm}

Thus, each irrep $\lambda$ defines a block-Hamiltonian matrix of size
$m_\lambda\times m_\lambda$:
\begin{equation}
    H^{(\lambda)}_{\alpha\beta} \equiv 
    \braket{v^{(\lambda)}_\alpha | H | v^{(\lambda)}_\beta}
\end{equation}

\paragraph{The exact aim of this classification}
This classification aims to classify sets of all block Hamiltonians
$H^{(\lambda)}$ when we fix a symmetry group $G_0$ and let the
Hamiltonian runs through all possible single-particle Hamiltonians
that commute with operations (this operation should be unitarily
realized on the single-particle Hamiltonian) of $G_0$.

The result turns out to be independent of the group $G_0$, and of
course independent of its irrep $\lambda$.

\section{The Anti-Unitary Symmetries}
\label{sec:The Anti-Unitary Symmetries}

It turns out that under reasonable assumptions, there are only a
finite number of anti-unitary symmetries. Let us revisit our
definition of symmetry transformation:

\begin{equation*}
    \tag{\ref{eq:sym-in-2nd-1}, revisit}
    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
\end{equation*}

If it acts on creation/annihilation operators by:
\begin{align*}
    \tag{\ref{eq:sym-in-2nd-2}, revisit}
    \hat{\psi}'_A = 
    \hat{U} \hat\psi_A \hat{U}^{-1} &=
    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
    \tag{\ref{eq:sym-in-2nd-3}, revisit}
    \hat\psi'^\dagger_A =
    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
    \sum_B  \hat\psi^\dagger_B u_{BA}
\end{align*}

\paragraph{Case 1} Instead of requiring $\hat{U}$ to be linear (which
would give a unitarily realized symmetry on single-particle
Hamiltonian), we require it to be anti-linear:
\begin{equation}
    \hat{U} i \hat{U}^{-1} = -i
\end{equation}
Then, calculation shows:
\begin{equation}
    u H^* u^\dagger = H
\end{equation}
where $H$ is 1st quantized single-particle Hamiltonian. This symmetry
is called time-reversal symmetry, denoted $\hat{\tau}$, its action on
1st-quantized single-particle Hamiltonian $H$ can be denoted using
\begin{equation}
    T \equiv \eval{\hat{\tau}}_{\text{1st quantized Hilbert space}}
\end{equation}
and by above formula, we have:
\begin{equation}
    T = uK
\end{equation}
where $K$ is complex conjugation. And we have the usual property
$THT^{-1}=H$, where $T^{-1}=u^t K$. ($u^t$ is the transpose of $u$).

\paragraph{Case 2} If instead, we change eq.\ref{eq:sym-in-2nd-2} and
eq.\ref{eq:sym-in-2nd-3} to such that

\begin{align}
    \label{eq:sym-cc-1}
    \hat{\psi}'_A = 
    \hat{U} \hat\psi_A \hat{U}^{-1} &=
    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
    \label{eq:sym-cc-2}
    \hat\psi'^\dagger_A =
    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
    \sum_B  \hat\psi_B u^*_{BA}
\end{align}

(Again, a tip is to remember that $\hat\psi^\dagger_A$ is a row
vector, and $\hat\psi_A$ is a column vector)

In words, we require creation operators transform into annihilation
operators, and annihilation operators transform into creation
operators.

Now proceed again in the same way, we have the choice of linear or
antilinear $\hat{U}$. If $\hat{U}$ is linear, then the condition
$\hat{U}\hat{H}\hat{U}^{-1} = \hat{H}$ leads to the equation:
\begin{equation}
    \label{eq:sym-C-cond}
    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}
(notice in calculation that $\sum_i\hat\psi^\dagger_i \hat\psi_i =
\id$ on 1st-quantized single-particle Hilbert space.)

Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
simplifies into (note that $H^t = H^*$ for Hermitian $H$):
\begin{equation}
    u H^* u^\dagger = -H
\end{equation}

This type of symmetry is called charge-conjugation symmetry. It is
also called particle-hole symmetry in condensed matter physics. Notice
that if we denote this symmetry in 2nd-quantized Hilbert space as
$\hat{C}$, then in 1st-quantized single-particle Hilbert space, we
have
\begin{equation}
    C \equiv \eval{\hat{C}}_{\text{1st-quantized}}, \quad
    \text{and}\, C = uK
\end{equation}
with
\begin{equation}
    C H C^{-1} = -H
\end{equation}
for 1st-quantized single-particle Hamiltonian.

\paragraph{Case 3} If we now require again $\hat{U}$ being
anti-linear, and proceed with similar arguments, we would have, very
similar to eq.\ref{eq:sym-C-cond}, the equality: 
\begin{equation}
    \label{eq:sym-S-cond}
    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}
and since $N>>2$, we have $\tr(H)=0$. Then
\begin{equation}
    u H u^\dagger = -H
\end{equation}
This symmetry will be called the chiral symmetry, denoted $\hat{S}$.
And we have a simple relation for its action on 2nd-quantized
Hamiltonian and the 1st-quantized Hamiltonian:
\begin{equation}
    S \equiv \eval{\hat{S}}_{\text{1st-quantized}},\quad
    \text{and}\,\, S = u
\end{equation}
with
\begin{equation}
    S H S^{-1} = -H
\end{equation}
It is easy to see that $S$ is just a combination of $T$ and $C$
symmetry. This will be noted in the coming section.

\subsection{Summary}
\label{sec:Summary}

There are 3 different symmetries that do not lie in our usual sense of
symmetry, which is unitarily realized and commutes with $H$. They are
summarized here. Also, there is a some other property listed below.
They are proved in this lecture, but are either commonly available in
most textbooks, or easy to prove. So I did not give details of proof
below.
\paragraph{Time-reversal}:
\begin{itemize}
    \item 2nd-quantized: 
        $\hat{\tau}\hat{H}\hat{\tau}^{-1}=\hat{H}$ 
    \item Relation:
    \begin{align}
        \hat{\tau} \hat\psi_A \hat{\tau}^{-1} &=
        \sum_B (u_T^\dagger)_{AB} \hat\psi_B \\
        \hat{\tau} \hat\psi^\dagger_A \hat{\tau}^{-1} &= 
        \sum_B  \hat\psi^\dagger_B (u_T)_{BA} \\
        \hat{\tau}i\hat{\tau}^{-1} &= -i
    \end{align}
    \item 1st-quantized:
        $T=u_T K$, $THT^{-1}=H$
    \item Squared term

        If $T$ commutes with $H$, then $T^2$ also
        commutes with $H$. Calculation shows $T^2= u_Tu_T^* = \pm 1$.
        For fermion system, $T^2=(-1)$. Hence in 2nd-quantized Hilbert
        Space, $\hat{T}^2=(-1)^{\hat{Q}}$, where $\hat{Q}=\sum_A
        \hat\psi^\dagger_A \hat\psi_A$. This is exactly the Fermion
        number parity operator.
\end{itemize}
\paragraph{Charge-conjugation}:
\begin{itemize}
    \item 2nd-quantized: 
        $\hat{C}\hat{H}\hat{C}^{-1}=\hat{H}$ 
    \item Relation:
    \begin{align}
        \hat{C} \hat\psi_A \hat{C}^{-1} &=
        \sum_B (u_C^*)^\dagger_{AB} \hat\psi^\dagger_B \\
        \hat{C} \hat\psi^\dagger_A \hat{C}^{-1} &= 
        \sum_B  \hat\psi_B (u_C^*)_{BA} \\
        \hat{C}i\hat{C}^{-1} &= i
    \end{align}
    \item 1st-quantized:
        $C=u_C K$, $CHC^{-1}=-H$, and $\tr(H)=0$.
    \item Squared term

        If $C$ commutes with $H$, then $C^2$ also
        commutes with $H$. Calculation shows $C^2= u_Cu_C^* = \pm 1$.
        For fermion system, $C^2=(-1)$. Hence in 2nd-quantized Hilbert
        Space, $\hat{C}^2=(-1)^{\hat{Q}}$, where $\hat{Q}=\sum_A
        \hat\psi^\dagger_A \hat\psi_A$. This is exactly the Fermion
        number parity operator.

    \item Action on $\mathcal{F}_q$:

        Consider the $\mathcal{F}_q$, the eigenspace of
        $\hat{Q}=\sum_{A=1}^N \hat\psi^\dagger_A \hat\psi_A$, with
        eigenvalue $q$. Then, direct calculation shows:
        \begin{equation}
            \hat{C}\hat{Q}\hat{C}^{-1} = N -\hat{Q}
        \end{equation}
        Therefore, $\hat{C}$ links $\mathcal{F}_q$ and
        $\mathcal{F}_{N-q}$.
\end{itemize}
\paragraph{Chiral/sub-lattice}:
\begin{itemize}
    \item 2nd-quantized: 
        $\hat{S}\hat{H}\hat{S}^{-1}=\hat{H}$ 
    \item Relation:
    \begin{align}
        \hat{S} \hat\psi_A \hat{S}^{-1} &=
        \sum_B (u_S^*)^\dagger_{AB} \hat\psi^\dagger_B \\
        \hat{S} \hat\psi^\dagger_A \hat{S}^{-1} &= 
        \sum_B  \hat\psi_B (u_S^*)_{BA} \\
        \hat{S}i\hat{S}^{-1} &= -i
    \end{align}
    \item 1st-quantized:
        $S=u_S$, $SHS^{-1}=-H$, and $\tr(H)=0$.
    \item \textbf{Relation between Chiral, Time-reversal, and
        Charge-conjugation}

        We have $\hat{S}=\hat{\tau}\hat{C}$, $u_S = u_T u_C^*$.

    \item Squared term

        If $S$ commutes with $H$, then $S^2$ also
        commutes with $H$. Calculation shows $S^2= u^2_S$. But since
        $u_S=u_Tu_C^*$, we can always make a phase choice of $u_T$ and
        $u_C$ such that $S^2=u^2_S = 1$.

    \item Let $S'\equiv CT$. If $T^2=\epsilon_T\id$,
        $C^2=\epsilon_C\id$, and we adopt the phase choice such that
        $S^2=1$, then it can be shown that $S=\epsilon_C\epsilon_T
        S'$, or
        \begin{equation}
            TC = \epsilon_C\epsilon_T CT
        \end{equation}
\end{itemize}

\subsection{How many anti-unitary symmetries are there?}
\label{sec:How many anti-unitary symmetries are there?}

As we have seen, there are three classes of anti-unitary symmetry
transformations.
Within each class, there is actually one unique anti-unitary symmetry
transformation, module those of unitary ones. To be more specific,
suppose we have two realizations of charge-conjugation symmetry:
\begin{equation}
    C_1 = u_{C,1} K,\quad C_2=u_{C,2}K
\end{equation}
They are clearly related by a unitary matrix
$u_{12}=u_{C,1}u_{C,2}^\dagger$, and ${C_1=u_{12}C_2}$.
Then, if we blindly assume the 1st-quantized Hamiltonian has symmetry
$C_1$:
\begin{equation}
    C_1 H C_1^{-1} = -H
\end{equation}
then, plugging $C_2$ inside gives
\begin{equation}
    C_2 H C_2^{-1} = - u_{12}^\dagger H u_{12}
\end{equation}
Therefore, if we further enlarge the group $G_0$ to include
$u_{12}^\dagger$ (i.e. by requiring that $H$ commutes with
$u_{12}^\dagger$), then with $G'_0=G_0\cup\{u_{12}^\dagger\}$, the
classification will be done and nothing new is actually introduced.
Therefore, there is only one $C$ symmetry to be considered, module the
unitary matrices.

Similar argument applies for $T$. But for $S$, Ludwig specifically
point out that $S$'s expression should always be kept explicit. I am
confused about the reason. \todo{Why $S$ so special?}

\section{Incorporating Superconductors}
\label{sec:Incorporating Superconductors}

We can consider the Bogoliubov-de Gennes (BdG) Hamiltonians of fermionic
excitations inside superconductors in the same way. Except that
\begin{itemize}
    \item The particle-number $\hat{Q}$ is not conserved
    \item There is a built-in charge-conjugation symmetry, to be
        explained later.
\end{itemize}

The BdG Hamiltonian uses Nambu Spinor:
\begin{equation}
    \hat\chi \equiv \begin{pmatrix}
        \hat\chi_1 \\ \cdots \\ \hat\chi_N \\ 
        \hat\chi_{N+1} \\ \cdots \\ \hat\chi_{2N}
    \end{pmatrix}
    =
    \begin{pmatrix}
        \hat\psi_1 \\ \cdots \\ \hat\psi_N \\
        \hat\psi^\dagger_1 \\ \cdots \\ \hat\psi^\dagger_N
    \end{pmatrix}
    =
    \begin{pmatrix}
        \hat\psi \\ (\hat\psi^\dagger)^t
    \end{pmatrix}
\end{equation}

(It seems that the author is ignoring spin here.)
Here, we regard $\hat\psi^\dagger$ as a row vector, and $\hat\psi$ as
a column vector. The BdG Hamiltonian is written as
\todo{Check the spin indices later.}
\begin{equation}
    \label{eq:super-H}
    \hat{H} =
    \frac{1}{2} \hat{\chi^\dagger} H \hat{\chi} 
    =
    \frac{1}{2} \sum_{A,B=1}^{2N} \hat{\chi^\dagger}_A H_{AB} \hat\chi_B
    = \frac{1}{2} \begin{pmatrix}
        \hat\psi^\dagger & \hat\psi^t
    \end{pmatrix} H 
    \begin{pmatrix}
        \hat\psi \\ (\hat\psi^\dagger)^t
    \end{pmatrix}
\end{equation}

The 1st-quantized Hamiltonian $H$ has the of 4 $N\times N$ blocks:
\begin{equation}
    \label{eq:super-H-def}
    H =
    \begin{bmatrix}
        \Xi & \Delta \\
        \Delta^* & -\Xi^t
    \end{bmatrix}
\end{equation}
where $\Xi$ is Hermitian, and $\Delta=-\Delta^t$ due to fermion
statistics. \todo{Why fermion statistics leads to this?}

Writing explicitly, we have:
\begin{equation}
    \hat{H} = \sum_{a,b=1}^N \hat\psi^\dagger_a \Xi_{ab} \hat\psi_b
    + \frac{1}{2} \sum_{a,b=1}^N \left(
        \hat\psi^\dagger_a \Delta_{ab} \hat\psi^\dagger_b
        + \hat\psi_a \Delta^*_{ab} \hat\psi_b
    \right)
\end{equation}

A striking difference is that $\hat\chi$ and $\hat\chi^\dagger$ are
related by a linear transformation, whereas in non-superconducting
case, $\hat\psi^\dagger$ and $\hat\psi$ are linear-independent.
Explicitly, since $\left(\hat\chi^\dagger \right)^t=
\begin{bmatrix}
    \left(\hat\psi^\dagger\right)^t \\ \hat\psi
\end{bmatrix}$, then clearly:
\begin{equation}
    \left(\hat\chi^\dagger \right)^t = \tau_1 \hat\chi
\end{equation}
where $\tau_1$ interchange the components:
\begin{equation}
    \tau_1 = \begin{bmatrix}
        0               & \id_{N\times N} \\
        \id_{N\times N} & 0
    \end{bmatrix}
\end{equation}

Taking the transpose again gives
\begin{equation}
    \label{eq:super-relat-1}
    \hat\chi^\dagger = \hat\chi^t \tau_1
\end{equation}
and then,
\begin{equation}
    \label{eq:super-relat-2}
    \hat\chi = \tau_1 (\hat\chi^\dagger)^t
\end{equation}
\paragraph{The Charge-conjugation Symmetry of Superconductors} There
is one charge-conjugation symmetry associated with the matrix
$\tau_1$. If one plugs eq.\ref{eq:super-relat-1} and
eq.\ref{eq:super-relat-2} into the Hamiltonian (eq.\ref{eq:super-H}),
one will find (note that $\tr(H)=0$ by eq.\ref{eq:super-H-def}, and be
careful about summation index):
\begin{equation}
    \frac{1}{2} \hat\chi^\dagger H \hat\chi
    = \frac{1}{2} \hat\chi^\dagger (-\tau_1 H \tau_1)^t \hat\chi
\end{equation}
Therefore (note that $H^t=H^*,\tau_1^t=\tau_1,\tau_1^2=\id$):
\begin{equation}
    \tau_1 H^* \tau_1 = -H
\end{equation}
Therefore, the BdG Hamiltonian has built-in charge-conjugation
symmetry, realized by $u_C = \tau_1$.

\paragraph{Encompass non-interacting problem and superconducting
problem} The way to put the two different kind of problems together,
is to work with operator $\hat\Psi$/$\hat\Psi^\dagger$ which has first
few components for ordinary annihilation/creation operators, and the
last few components for superconductor Nambu spinors, and with
$H$ consisting of two diagonal blocks for each respective. 
\todo{This sounds silly, perhaps I do not get some more deep reason?}

\section{TO BE CONTINUED}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at 
\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
{[My Email Address(Click)]}.
\bibliography{../../library}{}
\bibliographystyle{alphaurl}
\printnomenclature
\end{document}

### 2017-04-10 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] New calculation in open-boundaries.

@@
 
-    \subsection{Why I think the Lattice Model is wrong}
+    \subsection{Why I think the Lattice Model Hamiltonian is mildly wrong}
+    \label{sec:Why-LatticeM-m-wrong}
 
@@
 
-\subsection{Calculation Note unrelated to the main-subject}
+    \subsection{Calculation Note I (Not related to the main discussion)}
 
@@
 \printnomenclature
+
+\subsection{Numerical Solution with open boundary condition in both
+dimensions}
+\label{sec:nsol-open-bc-inXY}
+
+\textbf{Note 1}: Since the essential point is not altered by the minor
+error in Hamiltonian, as mentioned in
+Section~\ref{sec:Why-LatticeM-m-wrong}. I will continue with the
+Lattice Model Hamiltonian that produce correctly the Dirac Hamiltonian
+in the continuum limit.
+
+\textbf{Note 2}: Calculation in this part is available in the
+Mathematica notebook "\texttt{Lattice Dirac Model (2+1)-d-2.nb}".
+
+When the two sides are of open boundary, the problem is quite simple
+and the Fourier-transformed Hamiltonian is (almost) diagonal in
+momentum space. It is (as calculated in \cite{Hughes2009}, eq.2.21):
+\begin{align}
+    &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
+    \nonumber\\
+    &
+    \left[
+        \sin(p_x)\sigma^x + \sin(p_y)\sigma^y
+        +(2-m-\cos(p_x)-\cos(p_y))\sigma^z
+    \right] c_{p_x,p_y}
+\end{align}
+
+The eigenvalues of the Hamiltonian of the form
+$\vb{a}\vdot\vb{\sigma}$ are:
+\begin{equation}
+    E_1 = \abs{a},\quad E_2 = -\abs{a}
+\end{equation}
+If plotted in $(p_x,p_y)$ plane, we will find several interesting
+crossing happening when $m=0,2,4$:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m0.pdf}
+    \caption{$m=0$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m2.pdf}
+    \caption{$m=2$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m4.pdf}
+    \caption{$m=4$}
+\end{figure}
+
+The eigenvectors are of the form:
+\begin{equation}
+    \begin{pmatrix}
+        \phi, \sin(p_x)+i\cos(p_y)
+    \end{pmatrix},\quad \begin{pmatrix}
+        \psi, \sin(p_x)+i\cos(p_y)
+    \end{pmatrix}
+\end{equation}
+where
+\begin{align}
+    \phi &=  (2-m-\cos(p_x)-\cos(p_y))+E_1 \\
+    \psi &=  (2-m-\cos(p_x)+\cos(p_y))+E_1
+\end{align}
+And the have very interesting behavior from $m=-1$ to $m=6$, they
+gradually contact and exchange the position of each other
+\footnote{You would get more fun if you execute the animation inside
+the Mathematica notebook}:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-mN1.pdf}
+    \caption{$m=-1$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m0.pdf}
+    \caption{$m=0$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m1.pdf}
+    \caption{$m=1$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m2.pdf}
+    \caption{$m=2$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m3.pdf}
+    \caption{$m=3$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m4.pdf}
+    \caption{$m=4$}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m6.pdf}
+    \caption{$m=6$}
+\end{figure}
+
 \section{License}

### 2017-04-10 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] fix a typo.

@@
 \end{align}
-And the have very interesting behavior from $m=-1$ to $m=6$, they
-gradually contact and exchange the position of each other
+And besides crossing each other, they have new interesting behavior as
+$m$ varies. When changing from $m=-1$ to $m=6$, they gradually contact
+and exchange the position of each other
 \footnote{You would get more fun if you execute the animation inside

### 2017-04-12 Short Notes/Revisit TB Model.tex
[minor] Notes about TB-model

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.
\title{A Short Revisit to Tight-binding Model}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\tableofcontents

\textbf{Note}: After reading chapter 7.9 of \cite{Parker2009}, I think
that book provides a much clearer understanding of what tight-binding
model is, and therefore I recommend a first reading of that book,
before go into \cite{Ashcroft1976}.

To me, Tight-binding model is almost synonym of the following
2nd-quantized Hamiltonian:
\begin{equation}
    H = \sum_{i,\sigma} c^\dagger_{i,\sigma} c_{i,\sigma}
    - t \sum_{\braket{i,j},\sigma} 
    \left(c^\dagger_{i,\sigma} c_{j,\sigma} + \text{h.c.}\right)
\end{equation}

But actually there is much more that just this. I here give a short
note about some key points in chapter 10, The Tight-Binding Method, in
\cite{Ashcroft1976}.

The aim of Tight-binding model, is to deal

\begin{myquote} \enquote{
with the case in which the overlap of atomic wave functions is enough
to require corrections to the picture of isolated atoms, but not so
much as to render the atomic description completely irrelevant
} \end{myquote}

For this purpose, we start with a set of states:
\begin{equation}
    \psi_{n}(\vb{r})
\end{equation}
that satisfy two conditions:
% \footnote{
% The section General Formulation in chapter 10 of \cite{Ashcroft1976}
% provides an argument for the first condition. It actually starts with
% assuming $\phi_{n}(\vb{r})$ are eigenstates of atomic Hamiltonian as
% an introduction to the Tight-binding mode.}
\begin{enumerate}
    \item They model a wave function localized at each lattice points.
        Here, they are taken to be the bound levels of atomic
        Hamiltonian which are well localized:
        \begin{equation}
            H_{\text{at}} \psi_n(\vb{r})  = E_n \psi_n(\vb{r})
        \end{equation}
    \item They are orthonormal with respect to each other (which is
        quite reasonable a requirement).
\end{enumerate}

With this states, we test if the following wave function is a good
wavefunction of the system:
\begin{equation}
    \psi_{k} = \sum_R e^{ikR} \phi(r-R)
\end{equation}
where $k$ ranges through the $N$ values in the first Brillouin zone
consistent with the Born-von Karman periodic boundary condition. And
\begin{equation}
    \phi(r) = \sum_n b_n \psi_n(\vb{r})
\end{equation}
Exactly how many $n$ should be summed in the above expression will
depend on the situation (explained below).

It is easy to see that $\psi_{nk}$ satisfy the Bloch condition. So we
could assume that:
\begin{equation}
    H \psi(\vb{r}) = (H_\text{at}+\Delta U(\vb{r}))\psi(\vb{r})
    = \varepsilon(\vb{r})\psi(\vb{r})
\end{equation}

Using the orthonormal condition and some techniques, we have (see
pp.179 to 180 of \cite{Ashcroft1976}):
\begin{align}
    \label{eq:tb-model-eq}
    (\varepsilon(k) - E_m) b_m = & 
    -(\varepsilon(k)-E_m)\sum_n\left(
        \sum_{R\neq 0}\int\psi^*_m(r)\psi_n(r-R)e^{ikR}\dd{r}\right)b_n
    \nonumber\\
    &+ \sum_n \left(\int\psi^*_m(r)\Delta U(r)\psi_n(r)\dd{r}\right) b_n
    \nonumber\\
    &+ \sum_n\left(\sum_{R\neq 0}
        \int\psi^*_m(r)\Delta U(r)\psi_n(r-R)e^{ikR}\dd{r}\right)b_n
\end{align}

Now we argue that the right hand side of this equation should be small
because there are small overlap between those localized $\psi_n$.
Therefore, the left hand side should also be small. Therefore:
\begin{equation}
    \varepsilon(k) \approx E_0,\, b_m\approx 0\text{ unless } E_m\approx E_0
\end{equation}
where $E_0$ is energy of one atomic level. However, the above is only
an approximate analysis. To get more details, we would let $n$ only
summed over those levels with energies either degenerate with or very
close to $E_0$, our anticipated atomic energy level. This would make
\ref{eq:tb-model-eq} for different $m$s into a matrix equation. (see
more at p.181 of \cite{Ashcroft1976}). The solution to this equation
gives us coefficients $b_m$, the wavefunction $\psi_k$, and the energy
$\varepsilon(k)$.

\paragraph{Wannier function} The Tight-binding model is related to
Wannier function, since any Bloch function $\psi_{nk}(r)$ can be
expended
\begin{equation}
    \psi_{nk} = \sum_r f_n(r-R) e^{iRk}
\end{equation}
where
\begin{equation}
    f_n(R,r) = \frac{1}{v_0} \int\dd{k}e^{-iRk}\psi_{nk}(r)
\end{equation}
and $v_0$ is the volume in $k$-space of the first Brillouin zone, and
the integral is taken over the 1st BZ. $f_n$ are the so called Wannier
functions and they could be well localized (see p.188 of
\cite{Ashcroft1976}) and is orthonormal (see problem 3 of chapter 10,
\cite{Ashcroft1976}). Therefore they may be substituted as the atomic
eigenstates $\psi_n(r)$ in the above steps.  \todo{How to proceed
them?} % we don't know the energy, the Bloch wavefunctions. How to do it them?

\bibliography{../Library}{}
\bibliographystyle{alphaurl}

% \begin{thebibliography}{1}
% 	\bibitem{book} 
% \end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at 
\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
{[My Email Address(Click)]}.
\end{document}

### 2017-04-17 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Discuss an edge state at the interface of the 2d dirac model.

@@
 
+\subsection{Edge States}
+\label{sec:Edge States}
+Inspired by lecture by Kane of Topological Insulators (BSS 2016), I
+will analyse the continuum limit of this model at the  point
+$(p_x=0,p_y=0)$, where the energy $E=0$. I also assume that we have placed
+to materials adjacent to each other, on with $m<0$, and the other with
+$m>0$. Therefore, at the interface, we could have $m$ as a function of
+$x$ such that $m(0)=0$.
+
+At this point $x=0$, $\sin(p_x)\to p_x$ , and is replaced by $-i\hbar
+\partial _x$. The Schrodinger equation is H$\psi $=0 After the
+calculation, the equation is (with $\hbar=1$):
+\begin{equation}
+    \left[i\partial_x \sigma^x + i\partial_y \sigma^y +
+    m\sigma^z\right] \psi = 0
+\end{equation}
+However, this coupled PDE is hard to solve. Therefore, I restrict
+their value on $x$, and solve the ODE:
+\begin{align}
+    i\partial_x \psi_2(x) + m\psi_1(x) &= 0 \\
+    i\partial_x \psi_1(x) - m\psi_2(x) &= 0
+\end{align}
+If assuming $m(x)$ is in the form of $m(x)=x$, i.e. positive when
+$x>0$, and negative when $x<0$, then the solution is:
+\begin{align}
+    \psi_1 (x,y) &= e^{\text{Int}(x)} C(y) \\
+    \psi_2 (x,y) &= -i \psi_1(x,y)
+\end{align}
+where $\text{Int}(x)=\int_1^x -m(k)\dd{k}$. $\text{Int}(x)$ has the
+property of goes to $-\infty$ as $x\to \pm\infty$.
+
+If, on the contrary, assuming $m(x)$ is in the form of $m(x)=-x$, i.e. positive when $x<0$, and negative when $x>0$, then the solution is:
+\begin{align}
+    \psi_1 (x,y) &= e^{-\text{Int}(x)} C(y) \\
+    \psi_2 (x,y) &= i \psi_1(x,y)
+\end{align}
+In both cases, the function are exponentially decaying wave in the
+interface at $m(0)=0$.
+
 \section{License}

### 2017-04-19 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Calculate the Edge modes.

@@
 Start with chapter 2.
-
-Questions:
-\begin{itemize}
-    \item Do we have a precise definition of \textit{topological phase
-        transition}?
-\end{itemize}
 
@@
 Note, in choosing the test wavefunction, $u$ and $v$ could not be
-seperated, because there is still interaction between the two
+separated, because there is still interaction between the two
 component in terms like $c^\dagger_{p_x,n}\sigma^x c_{p_x,n}$.
@@
 \begin{align}
+    \label{eq:disc-eigeneq}
     H_{\text{disc}} \psi \equiv 
@@
 
-    \subsection{Why I think the Lattice Model Hamiltonian is mildly wrong}
-    \label{sec:Why-LatticeM-m-wrong}
-
-    I notice that equation (2.19) transformed according to (2.20)
-    is not exactly equation (2.21), but is:
-    \begin{align}
-        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
-        \nonumber\\
-        &
-        \left[
-            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
-            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
-        \right] c_{p_x,p_y}
-    \end{align}
-    This result does not become the continuum Dirac Hamiltonian as
-    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
-    constants should be modified so that:
-
-    \begin{align}
-        H_{LD} &= \sum_{m,n}\left\{
-            \frac{i}{2} \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
-                - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
-            + \frac{i}{2} \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
-                - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
-            \right.
-            \nonumber\\
-            &- \frac{1}{2}\left[
-                c^\dagger_{m+1,n}\sigma^z c_{m,n}
-                + c^\dagger_{m,n}\sigma^z c_{m+1,n}
-                + c^\dagger_{m,n+1}\sigma^z c_{m,n}
-                + c^\dagger_{m,n}\sigma^z c_{m,n+1}
-            \right]
-            \nonumber\\
-            & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
-            \vphantom{\frac12}
-        \right\}
-    \end{align}
-
-    This affects the numerical analysis effectively by the replacement
-    $$\sigma^i \to \frac{1}{2}\sigma^i,\quad
-        (2-m) \to 2(2-m) $$
-
-    The calculated result is similar to that in the previous section,
-    except that the band crossing happens at different values of $m$.
-    \footnote{For example, the eigenvalue of original and the modified equation
-    (2.21) are plotted in Mathematica notebook "Eq2.21-Demo.nb". Also,
-    the solution to the infinite cylinder boundary condition has again
-    two band crossings, each at $(m,p_x)$ equals $(0,0)$ and
-    $(2,\pm\pi)$ (for $N=3$ case).}
-    So the essential point is unaltered by the difference in some
-    constants. However, in the correct calculation, the crossing band
-    appears at $m=0$, which represents a massless spin-$\frac{1}{2}$
-    particle. I think this should have some theoretical implications.
-
-    \subsection{Calculation Note I (Not related to the main discussion)}
+    \subsubsection{Calculation Note I (Not related to the main discussion)}
 
@@
 
-\bibliography{cite}{}
-\bibliographystyle{alphaurl}
+\subsection{Why I Think the Lattice Model Hamiltonian is Mildly Wrong}
+\label{sec:Why-LatticeM-m-wrong}
 
-\printnomenclature
+I notice that equation (2.19) transformed according to (2.20)
+is not exactly equation (2.21), but is:
+\begin{align}
+    &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
+    \nonumber\\
+    &
+    \left[
+        2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
+        +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
+    \right] c_{p_x,p_y}
+\end{align}
+This result does not become the continuum Dirac Hamiltonian as
+$p_x,p_y$ goes to zero. Therefore, I suspect that certain
+constants should be modified so that:
 
-\subsection{Numerical Solution with open boundary condition in both
-dimensions}
-\label{sec:nsol-open-bc-inXY}
+\begin{align}
+    H_{LD} &= \sum_{m,n}\left\{
+        \frac{i}{2} \left[ c^\dagger_{m+1,n}\sigma^x c_{m,n}
+            - c^\dagger_{m,n}\sigma^x c_{m+1,n}\right]
+        + \frac{i}{2} \left[ c^\dagger_{m,n+1}\sigma^y c_{m,n}
+            - c^\dagger_{m,n}\sigma^y c_{m,n+1} \right]
+        \right.
+        \nonumber\\
+        &- \frac{1}{2}\left[
+            c^\dagger_{m+1,n}\sigma^z c_{m,n}
+            + c^\dagger_{m,n}\sigma^z c_{m+1,n}
+            + c^\dagger_{m,n+1}\sigma^z c_{m,n}
+            + c^\dagger_{m,n}\sigma^z c_{m,n+1}
+        \right]
+        \nonumber\\
+        & \left. + (2-m) c^\dagger_{m,n}\sigma^z c_{m,n}
+        \vphantom{\frac12}
+    \right\}
+\end{align}
+
+This affects the numerical analysis effectively by the replacement
+$$\sigma^i \to \frac{1}{2}\sigma^i,\quad
+    (2-m) \to 2(2-m) $$
+
+The calculated result is similar to that in the previous section,
+except that the band crossing happens at different values of $m$.
+\footnote{For example, the eigenvalue of original and the modified equation
+(2.21) are plotted in Mathematica notebook "Eq2.21-Demo.nb". Also,
+the solution to the infinite cylinder boundary condition has again
+two band crossings, each at $(m,p_x)$ equals $(0,0)$ and
+$(2,\pm\pi)$ (for $N=3$ case).}
+So the essential point is unaltered by the difference in some
+constants. However, in the correct calculation, the crossing band
+appears at $m=0$, which represents a massless spin-$\frac{1}{2}$
+particle. I think this should have some theoretical implications.
+
+\subsection{Solution With Translational Invariance in x, and Open
+Boundary in y (Infinite Stripe)}
+
+This amounts to removing the $A$ in top right corner and $C$ in bottom
+left corner of eq.\ref{eq:disc-eigeneq}. The calculation can be found
+in file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite Stripe.nb}.
+However, the solution by Mathematica is analytically intractable and
+not really illuminating. Also plotting all those eigenvectors becomes
+time-consuming when $N$ is large. So I looked for similar things
+inside the book by Bernevig \cite{Bernevig2013}, and found the
+following model.
+
+\subsection{Solution With Translational Invariance (Bloch States) in
+both x and y (Infinite Plane)}
+
+    \subsubsection{Numerical Solution}
+    \label{sec:Numerical Solution}
 
@@
 
-\subsection{Edge States}
+    \subsubsection{Edge States}
     \label{sec:Edge States}
@@
     $(p_x=0,p_y=0)$, where the energy $E=0$. I also assume that we have placed
-to materials adjacent to each other, on with $m<0$, and the other with
-$m>0$. Therefore, at the interface, we could have $m$ as a function of
-$x$ such that $m(0)=0$.
+    to materials adjacent to each other in $x$ direction, on with
+    $m<0$, and the other with $m>0$. Therefore, at the interface, we
+    could have $m$ as a function of $x$ such that $m(0)=0$.
 
     At this point $x=0$, $\sin(p_x)\to p_x$ , and is replaced by $-i\hbar
-\partial _x$. The Schrodinger equation is H$\psi $=0 After the
-calculation, the equation is (with $\hbar=1$):
+    \partial _x$. So we recovered the continuum model:
+    \begin{equation}
+        H = -i\hbar\partial_x \sigma^x 
+        -i\hbar\partial_y \sigma^y -m \sigma^z
+    \end{equation}
+    The Schrodinger equation is $H\psi =E\psi = 0$ for $E\approx 0$
+    around this point. After some calculations, the equation is (with
+    $\hbar=1$):
     \begin{equation}
@@
     \end{equation}
-However, this coupled PDE is hard to solve. Therefore, I restrict
-their value on $x$, and solve the ODE:
+    However, this coupled PDE is hard to solve by Mathematica
+    \footnote{See file \texttt{Lattice Dirac Model
+    (2+1)-d-3-EdgeStates.nb} for my calculations.}. Therefore, I
+    restrict their value on $x$, and solve the ODE:
     \begin{align}
@@
 
+    Paused to think what I have got. I have in essential got a
+    solution separated in $x,y$. Therefore, now I re-solve this edge
+    mode, using technique of separation of variables 
+    \footnote{Actually, I am just mimicking the calculation
+    in section 8.8 of \cite{Bernevig2013}.}.
+
+    Without loss of generality, assume $m(x)$ is like $x$, i.e. it
+    goes to $\pm\infty$ as $x\to\pm\infty$. Then, separate the
+    wavefunction into:
+    \begin{equation}
+        \psi(x,y) = \phi_1(x)\phi_2(y)
+    \end{equation}
+    Assuming we are solving a Schrodinger equation $H\psi=E\psi$, with
+    $E$ being very small.  Now, inspired by previous calculation,
+    write down directly $\phi_1(x)=e^{-\int_0^x m(x')\dd{x'}}$.  Then,
+    the equation decoupled directly into:
+    \begin{equation}
+        \left(
+            -i\sigma_y\partial_y + m(x)\left(i\sigma_x-\sigma_z\right)
+        \right)\psi_2(y) = E\psi_2(y)
+    \end{equation}
+    Since $E$ is small, but $m(x)$ could be very large and is
+    independent of $y$, we should make the term $(i\sigma_x-\sigma_z)$
+    somehow disappear. This matrix is singular and has only eigenvalue
+    $0$. Its eigenvector is $(i,1)^t$. So we assume
+    $\phi_2(y)=\chi(x)(i,1)^t$.
+
+    It turns out that $(i,1)^t$ is also the eigenvector of
+    $\sigma_y$ with eigenvalue $-1$. So the equation becomes quite
+    simple now:
+    \begin{equation}
+        i\partial_y\chi(y) = E\chi(y)
+    \end{equation}
+    The solution is $\chi(y)=e^{-iEy}$, a running wave in the $y$
+    direction!
 \section{License}
@@
 license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
+\bibliography{../../Library}{}
+\bibliographystyle{alphaurl}
+
+\printnomenclature
+
 \end{document}

### 2017-04-19 Dirac Hamiltonian/dirac_H.tex
[minor] Expressions for Gamma matrices in dim=4n

@@
 The second approach is found in page 99 (chapter 2) of \cite{Greiner1997}, and
-is prefered in my opinion. After all, they lead to the same equation:
+is preferred in my opinion. After all, they lead to the same equation:
 
@@
 A detailed formula for $\gamma$ matrices can be found in p.94 of
-\cite{zee2010quantum}. A detailed formula for $\alpha_i,\beta$
+\cite{zee2010quantum} or in the section~\todo{}. A detailed formula for $\alpha_i,\beta$
 matrices can be found in p.496 of \cite{Sakurai2011}.
@@
 
+\section{Gamma matrices}
+\label{sec:Gamma-matrices}
+
+It could be quite easy to find representations of Clifford Algebra in
+any dimension. First I note that the size of the Gamma matrices of
+$4n\times 4n$, i.e., the dimension could/must
+\footnote{I am not sure about this. In this \cite{thePhyStackPage}
+    says it must be $4n$, the \cite{theMathematicaPage} says there
+could be Gamma matrix in odd dimension} be $4n$. So we could have a
+very easy construction by repeatedly using the Pauli matrices. The
+Pauli matrices follow:
+\begin{equation}
+    \{\sigma_i,\sigma_j\} = 2\delta_{ij}
+\end{equation}
+So the following $4\times 4$ matrices are good Gamma matrices:
+\begin{equation}
+    \gamma_{1/2/3} = \begin{pmatrix}
+                         & \sigma_{1/2/3} \\
+        -\sigma_{1/2/3} & \\
+    \end{pmatrix},\quad \gamma_0 = \begin{pmatrix}
+        \id & \\
+           & -\id
+    \end{pmatrix}
+\end{equation}
+Note the minus sign in the $-\id$ of $\gamma_0$ is important to
+produce the correct anticommutation relations.
+
+Next, for higher dimension $8$, we can set:
+\begin{equation}
+    \gamma'_{1/2/3} = \begin{pmatrix}
+                         & \gamma_{1/2/3} \\
+        -\gamma_{1/2/3} & \\
+    \end{pmatrix},\quad \gamma'_0 = \begin{pmatrix}
+        \id & \\
+           & -\id
+    \end{pmatrix}
+\end{equation}
+
+And repeating the above process, we can get the Gamma matrices in any
+$4n$ dimension.
+
 \bibliography{cite}{}
@@
 
+\begin{thebibliography}{1}
+    \bibitem{thePhyStackPage}
+    \url{https://physics.stackexchange.com/questions/53318/dimension-of-dirac-gamma-matrices}
+    \bibitem{theMathematicaPage}
+    \url{http://demonstrations.wolfram.com/DiracMatricesInHigherDimensions/}
+\end{thebibliography}
 \printnomenclature

### 2017-04-21 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Various plots for infinite strip geometry added.

@@
 
-\subsection{Solution With Translational Invariance in x, and Open
-Boundary in y (Infinite Stripe)}
-
-This amounts to removing the $A$ in top right corner and $C$ in bottom
-left corner of eq.\ref{eq:disc-eigeneq}. The calculation can be found
-in file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite Stripe.nb}.
-However, the solution by Mathematica is analytically intractable and
-not really illuminating. Also plotting all those eigenvectors becomes
-time-consuming when $N$ is large. So I looked for similar things
-inside the book by Bernevig \cite{Bernevig2013}, and found the
-following model.
-
 \subsection{Solution With Translational Invariance (Bloch States) in
@@
 
-    \subsubsection{Edge States}
+\subsection{Solution With Translational Invariance in x, and Open
+Boundary in y (Infinite Stripe)}
+
+This amounts to removing the $A$ in top right corner and $C$ in bottom
+left corner of eq.\ref{eq:disc-eigeneq}. 
+\footnote{The calculation can be found
+in file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite Stripe
+(N=3).nb}, and file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite
+Stripe (N=20).nb}.}
+In this case, the crossing bands exists at slightly different value of
+$m$, also, there are few sharp transitions from a closed gap state, to an
+open gap state. For example, when $N=3$, the band crossing happens at
+two range of $m$: from $0.65$ to $1.35$ (shown in
+fig~\ref{fig:InfiniteStrip=3-1.jpg}, and from $2.4$ to $3.75$ (shown
+in fig~\ref{fig:InfiniteStrip=3-2.jpg}). The cases when $N=10$,
+$N=20$, $N=30$ also exhibits similar behavior. They also have almost
+two ranges of values for $m$ when two bands close at one point. Their
+result are plotted are at fig~\ref{fig:InfiniteStrip=10.jpg},
+fig~\ref{fig:InfiniteStrip=20.jpg}, and ... the result for $N=30$ will
+be updated here when my program finishes running.
+
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=3-1}.jpg}
+    \caption{Infinite Strip, $N=3$, closes at $p_x=0$}
+    \label{fig:InfiniteStrip=3-1.jpg}
+\end{figure}
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=3-2}.jpg}
+    \caption{Infinite Strip, $N=3$, closes at $p_x=\pi$}
+    \label{fig:InfiniteStrip=3-2.jpg}
+\end{figure}
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=10}.jpg}
+    \caption{Infinite Strip, $N=10$}
+    \label{fig:InfiniteStrip=10.jpg}
+\end{figure}
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=20}.jpg}
+    \caption{Infinite Strip, $N=20$}
+    \label{fig:InfiniteStrip=20.jpg}
+\end{figure}
+
+As we have seen, the solution by Mathematica is analytically
+intractable as $N$ grows larger. Also it would be too time-consuming
+if I were to plotting those eigenvectors when $N$ is large. So I
+looked for similar things inside the book by Bernevig
+\cite{Bernevig2013}, and found the following model.
+
+    \subsubsection{Edge States Analytically Obtained}
     \label{sec:Edge States}
-    Inspired by lecture by Kane of Topological Insulators (BSS 2016), I
-    will analyse the continuum limit of this model at the  point
-    $(p_x=0,p_y=0)$, where the energy $E=0$. I also assume that we have placed
-    to materials adjacent to each other in $x$ direction, on with
-    $m<0$, and the other with $m>0$. Therefore, at the interface, we
-    could have $m$ as a function of $x$ such that $m(0)=0$.
+    I will analyse the continuum limit of this model at the point
+    $(p_x=0,p_y=0)$, where the energy $E=0$. I also assume that we
+    have placed to materials adjacent to each other in $x$ direction.
+    I will assume that the two materials are in different topological
+    states. For example, if the band cross when $m=0$, then one
+    material will have $m<1$, and the other will have $m>0$.
+    Therefore, at the interface, we could have $m$ as a function of
+    $x$ such that $m(0)=0$.
 
-    At this point $x=0$, $\sin(p_x)\to p_x$ , and is replaced by $-i\hbar
-    \partial _x$. So we recovered the continuum model:
+    This assumption implies that we break translational in both
+    direction. So at this point $p_x=0$, $\sin(p_x)\to p_x$ , and is
+    replaced by $-i\hbar \partial _x$. Similar for $\sin(p_y)$. So we
+    recovered the continuum model:
     \begin{equation}
@@
     \end{equation}
-    The solution is $\chi(y)=e^{-iEy}$, a running wave in the $y$
+    The solution is $\chi(y)=e^{-iEy}$, a free electron in the $y$
     direction!
+
+    \textbf{Remark}: Although I have broken translational symmetry in
+    both direction, I could do almost the same calculation with $p_y$
+    conserved, e.g. in a infinite strip. In that case, I would get a
+    state localized in the interface, and have $p_y=-E$, representing
+    an electron travelling with momentum $-E$ in $y$'s direction.
 \section{License}

### 2017-04-21 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/programs/Dirac_Lattice_Model_21_d.m

@@ -59,7 +59,7 @@ for m = M
         V_mIs0_4(i) = Eigenvector(1,4);
     end
 end
-% Display the whole spectrum in (m,py)
+% Display the whole Energy spectrum in (m,py)
 [mesh_M,mesh_Y] = meshgrid(M,PY);
 figure;
 mesh(mesh_M,mesh_Y,D1');
@@ -73,7 +73,8 @@ hold on;
 mesh(mesh_M,mesh_Y,D5');
 hold on;
 mesh(mesh_M,mesh_Y,D6');
-hold on;
+xlabel('m');
+ylabel('p_y');
 hold off;
 
 % Plot the Eigenvector when py=0

### 2017-04-26 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Try to get the Edge modes and Chern number of Lattice Dirac Ham in Hughes's dissertation.

@@
 \usepackage{physicist-taper}
+\usepackage{menukeys}
 \makenomenclature % For an index of symbols.
@@
 
-This amounts to removing the $A$ in top right corner and $C$ in bottom
-left corner of eq.\ref{eq:disc-eigeneq}. 
-\footnote{The calculation can be found
-in file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite Stripe
-(N=3).nb}, and file \texttt{Lattice Dirac Model (2+1)-d-4-Infinite
-Stripe (N=20).nb}.}
-In this case, the crossing bands exists at slightly different value of
-$m$, also, there are few sharp transitions from a closed gap state, to an
-open gap state. For example, when $N=3$, the band crossing happens at
-two range of $m$: from $0.65$ to $1.35$ (shown in
-fig~\ref{fig:InfiniteStrip=3-1.jpg}, and from $2.4$ to $3.75$ (shown
-in fig~\ref{fig:InfiniteStrip=3-2.jpg}). The cases when $N=10$,
-$N=20$, $N=30$ also exhibits similar behavior. They also have almost
-two ranges of values for $m$ when two bands close at one point. Their
-result are plotted are at fig~\ref{fig:InfiniteStrip=10.jpg},
-fig~\ref{fig:InfiniteStrip=20.jpg}, and ... the result for $N=30$ will
-be updated here when my program finishes running.
+Calculations in this are contained in files: 
+\begin{itemize}
+    \item \menu{Lattice Dirac Model (2+1)-d-4-Infinite Stripe (N=3).nb},
+    \item \menu{Lattice Dirac Model (2+1)-d-4-Infinite Stripe (N=20).nb},
+    \item \menu{Lattice Dirac Model (2+1)-d-4-Infinite Stripe (N=30).nb},
+\end{itemize}
+
+This amounts to removing the $A$ in top right corner and $C$ in bottom left
+corner of eq.\ref{eq:disc-eigeneq}.  In this case, the crossing bands exists at
+slightly different value of $m$, also, there are few sharp transitions from a
+closed gap state, to an open gap state. For example, when $N=3$, the band
+crossing happens at two ranges of $m$: from $0$ to $2$ and from $2$ to $4$
+(shown in Figure~\ref{fig:InfiniteStrip=3.jpg}). The cases when $N=10$, $N=20$,
+$N=30$ also exhibits similar behavior. They also have almost two ranges of
+values for $m$ when two bands close at one point. Their result are plotted are
+at fig~\ref{fig:InfiniteStrip=10.jpg}, fig~\ref{fig:InfiniteStrip=20.jpg}, and
+fig~\ref{fig:InfiniteStrip=30.jpg}.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=3-1}.jpg}
-    \caption{Infinite Strip, $N=3$, closes at $p_x=0$}
-    \label{fig:InfiniteStrip=3-1.jpg}
-\end{figure}
-\begin{figure}[htpb]
-    \centering
-    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=3-2}.jpg}
-    \caption{Infinite Strip, $N=3$, closes at $p_x=\pi$}
-    \label{fig:InfiniteStrip=3-2.jpg}
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=3}.jpg}
+    \caption{Infinite Strip, $N=3$}
+    \label{fig:InfiniteStrip=3.jpg}
 \end{figure}
@@
 \end{figure}
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30}.jpg}
+    \caption{Infinite Strip, $N=30$}
+    \label{fig:InfiniteStrip=30.jpg}
+\end{figure}
 
@@
 
-    \subsubsection{Edge States Analytically Obtained}
+    \subsubsection{Edge States in Continuum Limit}
     \label{sec:Edge States}
@@
 
-    If, on the contrary, assuming $m(x)$ is in the form of $m(x)=-x$, i.e. positive when $x<0$, and negative when $x>0$, then the solution is:
+    If, on the contrary, assuming $m(x)$ is in the form of $m(x)=-x$, i.e.
+    positive when $x<0$, and negative when $x>0$, then the solution is:
     \begin{align}
@@
 
-    \textbf{Remark}: Although I have broken translational symmetry in
-    both direction, I could do almost the same calculation with $p_y$
-    conserved, e.g. in a infinite strip. In that case, I would get a
-    state localized in the interface, and have $p_y=-E$, representing
-    an electron travelling with momentum $-E$ in $y$'s direction.
+    \begin{remark}
+    Although the above calculation breaks translational invariance in both
+    direction, the actual boundary states breaks only one. Nonetheless, I could
+    do almost the same calculation with $p_y$ conserved, e.g. in a infinite
+    strip. In that case, I would get a state localized in the interface, and
+    have $p_y=-E$, representing an electron travelling with momentum $-E$ in
+    $y$'s direction.
+    \end{remark}
+
+    \subsubsection{Edge State in Infinity Strip}
+    The edge state in this infinite strip (translational invariant in $x$, and
+    open boundary in $y$) is difficult is obtain. The eigenvalue equation
+    \ref{eq:disc-eigeneq} gives the following relation:
+    \begin{equation}
+        \label{eq:rec-disc-eigeneq}
+        A \psi_{n-1} + B\psi_n + C\psi_{n+1} = E\psi_n
+    \end{equation}
+    If $A,B,C$ are numbers (or invertible matrices), then we could express
+    $\psi_1$ in turns of $\psi_N$ (assuming $E=0$) and take the limit
+    $\psi_1/\psi_N=0$ or $\infty$. This would hint a boundary state localized in
+    $1$ or $N$.
+
+    But now $A$ and $C$ are singular, this makes the
+    equation~\ref{eq:rec-disc-eigeneq} mostly undetermined. The simplest case is
+    that when $B=0$ (i.e. when $p_x=0$ or $\pm \pi$, and $2-m-\cos(p_x)=0$, thus
+    $m=1$ or $3$),
+    there are four possible eigenstates of eigenvalue $E=0$:
+    \begin{align}
+        &\psi_N = \begin{pmatrix}
+            1 \\ -1
+        \end{pmatrix}\text{ or } \begin{pmatrix}
+            0 \\ 0
+        \end{pmatrix},\,
+        \psi_1 = \begin{pmatrix}
+            1 \\ 1
+        \end{pmatrix}\text{ or } \begin{pmatrix}
+            0 \\ 0
+        \end{pmatrix}\nonumber\\
+        &\psi_{N-1}=\psi_{N-2} = \cdots = \psi_2 = \begin{pmatrix}
+            0 \\ 0
+        \end{pmatrix}
+    \end{align}
+    This shows that it possibly has states localized at the boundary, but this
+    tells us nothing when $m$ is not the prescribed values($1$ and $3$).
+
+    \subsection{Berry Phase}
+    \label{sec:Berry Phase}
+    The easiest case when we can calculate the Berry phase is when we have
+    translational invariance in both $x$ and $y$ direction. The
+    Fourier-transformed Hamiltonian is then diagonal. 
+    \begin{align}
+        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
+        \nonumber\\
+        &\left[ \sin(p_x)\sigma^x + \sin(p_y)\sigma^y
+            +(2-m-\cos(p_x)-\cos(p_y))\sigma^z
+        \right] c_{p_x,p_y}
+    \end{align}
+    The Berry phase for a Hamiltonian of the form
+    $\vec{d}(\vec{k})\vdot\vec{\sigma}$, is equal to $\pm\frac{1}{2}\Omega$,
+    where the sign is determined by the choice of eigenstate, the $\Omega$ is
+    the solid angle traversed by $\vec{d}$ as its parameter $\vec{k}$ varies,
+    Now $\vec{d}=(\sin(p_x),\sin(p_y),2-m-\cos(p_x)-\cos(p_y))$, which is
+    numerical explored\footnote{Details can be found in in file \menu{Attempts
+    at Getting Chern Number.nb}.}.
+
+    The surface of $\vec{d}$ as $p_x,p_y$ varies is somewhat distorted
+    (fig~\ref{fig:BerryPhase/Shape}). Thankfully, it does not change as $m$
+    varies (fig~\ref{fig:BerryPhase/AsMVaries}). Also, it is easy to see that
+    when $m<0$ or $m>4$, the surface does not cut the $xy$ plane, hence in that
+    region the Berry Phase is trivial. The distorted picture is dispatched into
+    4 different pieces in fig~\ref{fig:BerryPhase/attempts}. It could be
+    imagined that the vector $\vec{d}$ goes in the order: red
+    $\to$blue$\to$yellow$\to$green$\to$red. With this and a little bit of
+    imagination, I since the solid angle $\Omega$ when $0<m<2$ and $2<m<4$ are
+    both $4\pi$.
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.5\linewidth]{pics/BerryPhase/Shape.pdf}
+        \caption{Surface formed as $p_x,p_y$ varies}
+        \label{fig:BerryPhase/Shape}
+    \end{figure}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/AsMVaries.pdf}
+        \caption{As $m$ varies, the shape does not change. The blue plane is the
+        $xy$ plane. The center of that surface meets the $xy$-plane when $m=2$.
+        That surface leaves the $xy$-plane when $m<0$ or $m>4$.}
+        \label{fig:BerryPhase/AsMVaries}
+    \end{figure}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/attempts.pdf}
+        \caption{Attempts to determine the Berry phase by dispatching the surface
+        into 4 different patches ($m=2$)}
+        \label{fig:BerryPhase/attempts}
+    \end{figure}
 \section{License}

### 2017-04-27 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Use SS.Qing's formula to get Chern number. And plotted Chern number v.s. different m.

@@
     $\to$blue$\to$yellow$\to$green$\to$red. With this and a little bit of
-    imagination, I since the solid angle $\Omega$ when $0<m<2$ and $2<m<4$ are
+    imagination, I think the solid angle $\Omega$ when $0<m<2$ and $2<m<4$ are
     both $4\pi$.
+
+    Exact value can be found using the formula for solid angle in a
+    parameterized surface. Assuming the surface is parameterized as
+    \begin{equation}
+        \vec{f}(x,y) = (f_1(x,y), f_2(x,y), f_3(x,y))
+    \end{equation}
+    Its solid angle can be calculated by:
+    \begin{equation}
+        \int\dd{x}\dd{y} \frac{\vec{f}(x,y)}{\abs{\vec{f}(x,y)}^3}
+        \partial_x \vec{f}(x,y) \cross \partial_y \vec{f}(x,y)
+    \end{equation}
+    This formula can be understood mathematically
+    \cite{SolidAngleParameterizedSurface}, and calculated physically (see p.216 of
+    \cite{Shen2012}).  The calculated result for different $m$ is plotted in
+    fig~\ref{fig:BerryPhase/SSQFormulaPlot}.
     \begin{figure}[htpb]
@@
     \end{figure}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/SSQFormulaPlot.pdf}
+        \caption{Plot of Chern Number for different $m$.}
+        \label{fig:BerryPhase/SSQFormulaPlot}
+    \end{figure}
 \section{License}
@@
 license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
+
 \bibliography{../../Library}{}
 \bibliographystyle{alphaurl}
-
 \printnomenclature

### 2017-04-28 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Getting edge states numerically.

@@
 
-    But now $A$ and $C$ are singular, this makes the
+    But now $A$ and $C$ are singular, making the
     equation~\ref{eq:rec-disc-eigeneq} mostly undetermined. The simplest case is
     that when $B=0$ (i.e. when $p_x=0$ or $\pm \pi$, and $2-m-\cos(p_x)=0$, thus
-    $m=1$ or $3$),
-    there are four possible eigenstates of eigenvalue $E=0$:
+    $m=1$ or $3$), there are four possible eigenstates of eigenvalue $E=0$:
     \begin{align}
@@
     tells us nothing when $m$ is not the prescribed values($1$ and $3$).
+
+    Numerical calculations can be performed in this case to find eigevectors
+    whose eigevectors are close to zero. The result gives real edge states. For
+    example, when $N=30$, below are a plot of eigevectors, whose eigenvalues
+    $\epsilon$ satisfy $\abs{\epsilon}<0.2$:
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState}.pdf}
+        \caption{Edge states when $N=30$ (amplitudes have not been normalized).}
+        \label{fig:InfiniteStrip/InfiniteStrip=30.EdgeState.pdf}
+    \end{figure}
 
@@
     \end{figure}
+
 \section{License}

### 2017-04-29 Short Notes/Shen's View of Topological Quantum Numbers.tex
[minor] About Laughlin's Argue & Strong/Week T.I.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.
\title{Shen's View on Topological Quantum Numbers}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    A short summary of chapter 4, Topological Invariants, of \cite{Shen2012}.
}
\tableofcontents

The local gauge freedom of phase gives us Berry phase, and the Hall conductance
$\sigma_{xy}$ can be related to this Berry phase as:
\todo{Which bands should be included in calculating the Berry phase.}
\begin{equation}
    \sigma_{xy} = \int_{\mathrm{BZ}} \frac{\dd{\vb k}}{(2\pi)^2}
    \Omega_{k_x,k_y}
\end{equation}
where $\Omega_{k_x,k_y}$ is the Berry curvature. The Berry curvature for each
band is defined as
\begin{equation}
    \Omega^n(\vb k) = \grad_{\vb k} \times
        \braket{ u_n(\vb k) | i \grad_{\vb{k}} | u_n(\vb{k})}
\end{equation}

This Berry phase can also be related to the electric polarization (more exactly,
the $\vb P$ in $D=\epsilon_0 \vb{E} + \vb{P}$), in a solid in which there is no
electric field ($\vb{E}=0$). The connection is:
\begin{equation}
    \Delta P_{\alpha} = e \sum_n \int_0^T\dd{t} 
    \int_{\mathrm{BZ}} \frac{\dd{\vb q}}{(2\pi)^d}\Omega^n_{q_\alpha,t}
\end{equation}
(where $d$ should be the dimension of the solid, though this is not mentioned
in the book.)

The quantization of Hall conductance can be viewed from two perspectives. On one
hand, the Berry phase is proportional to the first Chern number, which is proved
mathematically to be quantized. On the other hand, there is the Laughlin's
argument. The Laughlin's argument does two things. First, it relates the change
of flux $\Delta \phi$ to the change of charge $\Delta Q$ by simple
electrodynamics:
\begin{equation}
    \Delta Q = \sigma_{xy} \Delta \phi
\end{equation}
Second, it argues that the threading of one flux quantum $\hbar/e$ does not change the
\todo{Why do we thread this flux of quantum?}
Hamiltonian, but instead pushes integers numbers of charge transport (just like
a Thouless charge pump):
\begin{equation}
    \Delta Q = n e
\end{equation}
Therefore, $ne = \sigma_{xy} \hbar/e$ leads to $\delta_{xy} = n e^2/\hbar$.

However the $\Z_2$ invariant is a complicated stuff which I do not understand.

Also, the generalization of topological insulator from two dimension to three
dimension is done in section 4.9, which I do not understand. But he defines
clearly the concept of strong and weak topological insulator, and mentions that
a weak topological insulator is topologically equivalent to a two-dimensional
topological insulator, and is not robust against disorder.

\bibliography{../Library}{}
\bibliographystyle{alphaurl}

% \begin{thebibliography}{1}
% 	\bibitem{book} 
% \end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at 
\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
{[My Email Address(Click)]}.
\end{document}

### 2017-05-01 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Improves cal of EdgeStates and ChernNumber.

@@
     Numerical calculations can be performed in this case to find eigevectors
-    whose eigevectors are close to zero. The result gives real edge states. For
-    example, when $N=30$, below are a plot of eigevectors, whose eigenvalues
-    $\epsilon$ satisfy $\abs{\epsilon}<0.2$:
+    whose corresponding eigenvalues are close to zero. The result gives very
+    good showcase of edge states. For example, when $N=30$, we plot its
+    eigevectors (more precisely, the absolute value of each components of its
+    eigenvectors) in Figure~\ref{fig:InfiniteStrip=30.EdgeState}.
+    \footnote{Due to numerical problem, it is troublesome to plot eigenvectors
+        corresponding to one band. But we could plot eigenvectors whose
+        eigenvalues $\epsilon$ satisfy $\abs{\epsilon}<0.5$. This ensures that
+        we select the eigenvectors from the crossing band. Also, for numerical
+        accuracy in Mathematica's function \texttt{Eigensystem}, I used the "FEAST"
+        method, since the ordinary method gave a state not localized at the boundary but
+        at some point close to the boundary.}
+    Also, it can be found in that there are one left-localized state and one right-localized state
+    (figure~\ref{fig:InfiniteStrip=30.EdgeState.LeftRight}).
+
     \begin{figure}[htpb]
@@
         \caption{Edge states when $N=30$ (amplitudes have not been normalized).}
-        \label{fig:InfiniteStrip/InfiniteStrip=30.EdgeState.pdf}
+        \label{fig:InfiniteStrip=30.EdgeState}
     \end{figure}
-
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState.LeftRight}.pdf}
+    \caption{The left-localized and right-localized states. The $(p_x,E_x)$ for
+    two states $1,2$ are $(-0.05,0.0499792)$ and $(0.1,0.0998334)$
+    respectively.}
+    \label{fig:InfiniteStrip=30.EdgeState.LeftRight}
+\end{figure}
     \subsection{Berry Phase}

### 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
[major] Fresh & Error-prone notes for SPEMT.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\usepackage{fontspec}
\setmainfont{Times New Roman}

\makenomenclature % For an index of symbols.

\title{Notes about the Minimal Dimensional Method to Classify
Topological Phases (preliminary)}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
    In this paper, I will review the use of minimal Dirac Hamiltonian method
    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
    mechanism behind the homotopic classification of topological insulators. I
    start with a introduction to the general framework of "Tenfold Way", and
    briefly outline the two approaches to classification of topological
    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
    approach expose the mechanism of homotopic classification of topological
    insulators.
}
% TODO: add ref for Clifford Algebra.
\tableofcontents

\section{Outline}
\label{sec:Outline}

The classification of topological insulators in non-interacting system is in
effect a classification of Hamiltonian matrix. The simple case considered here
is the classification done by considering how the Hamiltonian matrix responses
to those anti-unitary symmetries, when we effectively ignored all unitary
symmetries. Specifically, when we module out any unitary symmetries of the
Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
we only classify topological insulators based on how our Hamiltonian matrix
responses to these anti-unitary symmetries.

There are two classical approaches towards this classification. The first is to
examine the existence of Anderson delocalization at the boundary of the
insulator, because the existence of surface conducting state is the signature of
topological insulators and the Anderson localization is the obstruction that
\todo{Be more specific about this and check some facts.}
surface conducting states must overcome. This approach uses the Nonlinear Sigma
Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
when can a localization-breaking term can be added to NL$\sigma$Ms.

The second approach is to use homotopy theory to classify classes Hamiltonians under
continuous deformation, more specifically, under adiabatical change of
Hamiltonians. This method is most elegant but most mathematical demanding
approach compared with others, because calculating homotopy groups, and homotopy theories in
general are notorious hard. Also, one has to use $K$-theory, because of
something physical is enlarging those distinct classes of Hamiltonian. To be
more specific.

But the key to understand topological insulators, are not necessarily the
Hamiltonian of the whole bulk, but the physics happening when the bulk gap
closes. For example, the Chern number is the integration on a compact manifold
without boundary. Therefore, it should always be zero because of the Stokes theorem,
unless inside this manifold there is somewhere where the formula for Chern
number got "blown up", and it is just this locally "blown up" point that is
responsible for the nonzero Chern number, and for the non-triviality of
topological insulators.

Therefore, we can detect the different types of topological insulators when we
are focused in only the crossing point of the band, or, when we shifted the
energy zero level to the crossing point, in only the low energy physics. We
expect a locally linear crossing energy spectrum around this point, so we expect
$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
opening of this spectrum. One simple model with only first-order derivatives to
describe such a low energy physics is the Dirac Hamiltonian.
\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}

An amazing fact happens, when one consider the gamma matrices in Dirac
Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
relations. Together they are proved to be isomorphic to some Clifford Algebra over
$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
symmetry operators, all become some specific representations of their
corresponding Clifford Algebra. Also, it will be illustrated later that the
minimal matrix dimension of such representation, i.e. the minimal dimension of
the Dirac Hamiltonian, can tell the specific type of this topological
insulator. Therefore, as a whole all the classification work is reduced to the
consideration of minimal matrix dimension of the representation of Clifford
Algebra, in different spatial dimension.
\todo{Cautious, we have two dimensions here: matrix and spatial.}

\paragraph{Structure of this work} This work are divided into several parts.
\begin{enumerate}
    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
        Models Approach and the Homotopy/$K$-theory approach work.
    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
        is derived in this approach.
    \item \textbf{Outlook} outlines the possible direction in classification
        under unitary symmetries, and the problems we faced when interaction is
        turned on.
\end{enumerate}

\section{Ten-fold Way}

The classification of topological phases with different non-unitary symmetries
in non-interacting picture, are in essence, the classification of $N\times N$
matrices by its response to three discrete symmetries: time reversal symmetry
($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
symmetry ($S$). As for those unitary symmetries, one can in principle, block
diagonalize the Hamiltonian
$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
has no memory of the unitary symmetries. Therefore, our classification is
applied to those blocks and still holds.

It will be find that, those $T,C$ are the only two meaningful non-unitary
symmetries of the Single-particle system, and there are in total 10 different
ways in which the Single-particle Hamiltonian could respect the three symmetries
$T,C,S$. Now we explain in detail, about the reason why we care about, and only
care about these three symmetries $T,C,$ and $S$.

\subsection{The symmetries of Single-particle Hamiltonian}
\label{sec:The symmetries of Single-particle Hamiltonian}

According to Wigner's theorem, symmetries of physical system can either be
unitary represented, or anti-unitarily represented. Here we show that in the
case of anti-unitary symmetries, there are only 2 different kinds of them that a
Single-particle Hamiltonian in first-quantized space can have. Actually, there
can be more anti-unitary symmetries than this. But under reasonable assumptions,
we can limit our discussion in only this two types.

The Single-particle Hamiltonian acting on Fock space is
\begin{equation}
    \label{eq:H-2nd}
    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
\end{equation}
where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
are creation and annihilation operators acting on Fock space.

Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
to stress that it acts on Second-quantized Fock space.  A symmetry of the
Hamiltonian, represented as an operator $\hat{U}$, must have:
\begin{equation}
    \label{eq:sym-in-2nd-1}
    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
\end{equation}

We expect $\hat{U}$ to change the creation/annihilation operators in two different
ways. First, it may only permute the creation/annihilation operators:
\begin{subequations}
\label{eq:sym-in-2nd-permute}
\begin{align}
    \label{eq:sym-in-2nd-permute-1}
    \hat{\psi}'_A = 
    \hat{U} \hat\psi_A \hat{U}^{-1} &=
    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
    \label{eq:sym-in-2nd-permute-2}
    \hat\psi'^\dagger_A =
    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
    \sum_B  \hat\psi^\dagger_B u_{AB}
\end{align}
\end{subequations}
Where $u$ is some matrix implementing the permutation.
Or, it may interchange the role of creation/annihilation operators:
\begin{subequations}
\label{eq:sym-cc}
\begin{align}
    \label{eq:sym-cc-1}
    \hat{\psi}'_A = 
    \hat{U} \hat\psi_A \hat{U}^{-1} &=
    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
    \label{eq:sym-cc-2}
    \hat\psi'^\dagger_A =
    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
    \sum_B  \hat\psi_B u^*_{BA}
\end{align}
\end{subequations}
Where $u^*$ is some other matrix implementing the interchange. We write complex
conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
interchange), to conserve the anticommutation relation between
$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
should be a unitary matrix.

Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
symmetry, to be explained below.

\paragraph{Case 1: Unitary Symmetry}

Assume the symmetry just permutes the creation/annihilation operators, as in
equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
relation~\ref{eq:sym-in-2nd-permute} plugged into
equation~\ref{eq:sym-in-2nd-1}, gives
\begin{equation}
    u H u^{-1} = H
\end{equation}
Therefore, in this case the symmetry is unitarily realized in First-quantized
Hamiltonian $H_{AB}$.

\paragraph{Case 2: Anti-unitary T Symmetry}
Assume the symmetry just permutes the creation/annihilation operators, as in
equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
relation~\ref{eq:sym-in-2nd-permute} plugged into
equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
\begin{equation}
    u H^* u^\dagger = H
\end{equation}
Or:
\begin{equation}
    uK H u^t K = uK H (uK)^{-1} = H
\end{equation}
where $K$ is complex conjugation. This symmetry is called Time-reversal
symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
operator $T= uK$.

\paragraph{Case 3: Anti-unitary C Symmetry}
Assume the symmetry just interchange the creation/annihilation operators, as in
equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
\footnote{
Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
\id$ on 1st-quantized single-particle Hilbert space.
}
\begin{equation}
    \label{eq:sym-C-cond}
    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}

Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
\begin{equation}
    u H^* u^\dagger = uK H (uK)^{-1} = -H
\end{equation}
This type of symmetry is called charge-conjugation symmetry. It is
also called particle-hole symmetry in condensed matter physics. It is realized
as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.

\paragraph{Case 4: Unitary S Symmetry}
Assume the symmetry now interchange the creation/annihilation operators, as in
equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
\begin{equation}
    \label{eq:sym-S-cond}
    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}
and since $N>>2$, we have $\tr(H)=0$. Then
\begin{equation}
    u H u^\dagger = -H
\end{equation}
This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
of Hamiltonian under $S$. But there is one exception. When the
Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
whole.

\paragraph{Squaring of $T,C,S$} 
Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
hence it is only a phase as they are unitary.
This can be viewed from two perspectives. First, we expect the system, after
applying twice of symmetry operation $T/C$, should come back to the same state, except
a possible phase difference. Second, $T^2/C^2$ commutes with all
$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
of unitary symmetries (to be explained later), therefore by Schur's lemma, they
must be proportional to a constant, which is a phase.

It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
$e^{i\delta}=\pm1$.

But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
operators), we can always pick a phase such that $S^2$ is some phase we want.
Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
phase for $S^2$.\footnote{This is a bit troublesome. First we denote
$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
$S^2=-\varepsilon_C\varepsilon_T$.}

\paragraph{Why Ten Classes} For the three unitary symmetries under
consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
undetermined (depending on the phase choice\footnote{To be explained later.} we
give for $T$ and $C$). Therefore, there are in total 10 different possible ways
that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
to symbolize that the system does not follow $T$($C$) symmetry. Then
$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
different possible ways. In each way the topological invariants of the
Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
and their properties in different spatial dimensions respect a periodic
structure. For the upper two classes, they are named complex classes and respect
a $2$-fold period. The Lower eight classes are named real classes and respect a
$8$-fold period, which is why we only listed the first $0\to 7$ spatial
dimensions.

\subsection{Dealing with Unitary Symmetries}
\label{sec:Dealing with Unitary Symmetries}

As mentioned, we could module out those unitary symmetries. This statement is
made precise by the following theorem about unitary symmetries of the Hamiltonian.
\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
$\mathcal{V}_\lambda$ associated with the irrep (irreducible
representations, labeled by $\lambda$) of $G_0$.
\begin{equation}
    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
\end{equation}
where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
Denote the dimension of each irrep as $d_\lambda$.

In each vector space $\mathcal{V}_\lambda$, one can choose a
(orthogonal) basis of the form:
\begin{equation}
    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
\end{equation}
where
\begin{itemize}
    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
        $k=1,\cdots,d_\lambda$,
    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
        $\alpha=1,\cdots,m_\lambda$.
\end{itemize}
\end{thm}
Therefore, with all unitary symmetries ignored, we are classifying how
Hamiltonian will be like when it respects, in 10 different ways, the
combinations of $T,C,S$ symmetries.

\paragraph{Differently Realized Anti-unitary Symmetries}
It should be noted that there is still a freedom of unitary matrix that
implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
described in the theorem above, we only have one time-reversal symmetry. Similar
analysis could be done for the $C$ symmetry as well.

\paragraph{Translational Symmetry}

Since we are classifying in the solids, it is natural to expect translational
symmetry to present. Also, the addition of translational symmetry do not alter
our classification, which is based on non-unitary symmetries, but also make this
classification more convenient to be done.

With translational symmetry added,\todo{To be added}
%TODO why still unitary symmetries.

The Hamiltonian in $k$-space that preserve these three discrete symmetries
should follow\footnote{It is easy to anticipate the change $k\to -k$ for
    anti-unitary symmetries, since they change the phase factor when one Fourier
transform the Hamiltonian.}:
\begin{subequations}
\begin{align}
    \label{eq:T-sym-Hk}
    TH(k)T^{-1} &= H(-k) \\
    \label{eq:C-sym-Hk}
    CH(k)C^{-1} &= -H(-k) \\
    \label{eq:S-sym-Hk}
    SH(k)S^{-1} &= -S(k)
\end{align}
\end{subequations}

\subsection{The Tenfold Way}
\label{sec:The Tenfold Way}

\todo{Add the table, and the meaning of each Hamiltonian, and the class
of each evolutionary operators}%

\subsection{The Two Original Approaches}
\label{sec:The Two Original Approaches}
\todo{Add this}

\section{Classification by Dirac Mass Terms}
\label{sec:The Minimal Hamiltonian Approach}

\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
We first note that different topological phases are distinguished by the closing
and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
flatten the energy spectrum to two bands of energy $\pm E$, the transition
(closing of gap) will happen at some point where locally the energy is of a
Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
behavior. Then, a class of topological phases, or more specifically, a class of
Hamiltonian matrix that shares the same topological invariant, can be
\textit{represented} by the Dirac Hamiltonian in this class.

\subsection{Crossing Spectrum and Edge Mode}
\label{sec:Crossing Spectrum and Edge Mode}
Here we show that the crossing spectrum characteristic of topological insulators
can be characterized by a Dirac type Hamiltonian, and with this Dirac
Hamiltonian we could find an Edge mode solution built into it.

\paragraph{Crossing Spectrum and Dirac Hamiltonian}
In some local region around the crossing point, the energy spectrum should look
like:
\begin{equation}
    E = \pm \sqrt{\vb{k}^2 + M^2}
\end{equation}
where $\vb{k}$ is the crystal momentum and $M$ is some constant
responsible for the opening and closing of the gap, or in some cases, a parameter
in which we can control to open of close the gap.

As has been analysed in most Quantum Mechanics textbook\footnote{See for
    example, p.99 of \cite{Greiner1997}. Although their discussion is in
dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
use is:
\begin{equation}
    \label{eq:dirac-H}
    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
\end{equation}
where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
Clifford Algebra anti-commutation relation:
\begin{equation}
    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
\end{equation}

\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
phase. First, it has a gapless state. Due to the anti-commutation relation of
$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
we choose not $\gamma_i^2=-1$, which would give non-sensible result
$H_\text{Dirac}^2= -E^2\id$.}
that the energies of Dirac Hamiltonian are:
\begin{equation}
    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
\end{equation}
Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
gaped to gapless and again to gaped state. This shows that the $M$ is parameter
controlling the quantum phase transition, and the system with $M<0$ or $M>0$
possesses two different quantum phase.

In addition, we can analyse its edge mode. Assuming the two material of
different quantum phases touches each other in the $d$th direction. Then we
should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
broken in that direction. Now the eigenvalue equation is:
\begin{equation}
    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
    = E \Phi
\end{equation}

Past experience teaches us the ansatz (assuming
$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
does not blow up the wavefunction):
\begin{equation}
    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
\end{equation}
which after plugging inside the eigenvalue equation, leads to
\begin{equation}
    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
    = E \phi
\end{equation}
After left multiplication of $\gamma_0$, we have:
\begin{equation}
    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
    = E \gamma_0 \phi
\end{equation}
Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
state to be a surface state, so we choose the $-1$ eigenvectors (denoted
$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
\begin{equation}
    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
\end{equation}
As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
eigenspaces:
\begin{equation}
    \label{eq:H-Dirac-surf}
    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
\end{equation}

% \section{Collection of Calculation}
% \label{sec:Collection of Calculation}
% Here collects the calculations done throughout the whole notes.

\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
\label{sec:Homotopy to Minimal Dirac}

\paragraph{Spectral Flattening} The classification of topological insulators
concerns different classes of Hamiltonian that cannot be adiabatically changed
to each without closing or opening of a gap. Hence, we could in general
adiabatically change our parameters such that the spectrum of Hamiltonian is
simplified into two bands of energy $\pm1$. Under this condition, we have
$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
for generating Clifford Algebras.

\paragraph{Extension Problem with General Examples}
The general theme of homotopy classification of classifying topological
insulators are done by the considering the \textit{extension problem}, i.e.
different ways to extend from a Clifford containing only symmetry operators, to
a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
in $0$-dimension, the empty space is nothing, hence
$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
mentioned earlier, hence the extension problem is from
$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
representations form some mathematical structure called \textit{classifying
space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
operators are maps starting from $T^0=S^0$. So our classified objects are
different classes of maps from $S^0\to C_0$, which is mathematically captured by
the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
making it a candidate for generators of Clifford Algebra. The symmetry condition
$\{H,S\}=0$ tells us now we have a extension problem of
$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
trivial topological insulators. The case for real symmetry classes are not too
complicated and is concisely mentioned in \cite{Morimoto2013}.

However, the method to obtain such classifying spaces are mathematical daunting
and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
since they should capture the essence of topological states.

\paragraph{Extension Problem with Dirac Hamiltonian}
The Dirac Hamiltonian
\begin{equation}
    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
\end{equation}
has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
space having the same homotopy type of some classifying space (again!). For
example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
extension problem concerns different ways to extend the algebra
$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
unitarily non-equivalent mass terms. Detailed examples can be found in section
III.C.1 of \cite{Chiu2016}.

\paragraph{Stable Classification} An unmentioned hypothesis above are that we
are classifying strong topological insulators. They are topological insulators
that robust against disorder\cite{Fu2007}. There is a consensus that in
classification of strong topological insulators, we replace the Brillouin Zone
$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
our classification to be independent of and insensitive to the addition of
irrelevant trivial bands. The first replacement allow us to use homotopy groups,
which classify maps with domain in spheres. The "stable way" allows the use of
$K$-theory (sec.III.C.1 of \cite{Chiu2016}).

\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
with extra mass term:
\begin{equation}
    \label{eq:H-spemt}
    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
    + \sum_{j=1}^D m_j\tilde{\gamma}_j
\end{equation}
Here, the parameter $M$ characterized the domain wall between different phases
of topological insulators. The extra mass term $m_j$ represents a perturbation
caused by disorder. I argue that we can do our classification in the following
way. First, we consider the case when $D=0$, i.e. without perturbation, and we
consider how many different mass terms we could have. Second, we consider adding
an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
a SPEMT can be added, then the system is not robust against perturbation and gap
may be opened by disorder. So it is trivial topological insulator. If a SPEMT
cannot be added, then this system is topological non-trivial.

One best thing about this classification is that it can be done by considering
only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
argument is that, complex gamma matrices are of even dimension (except the
trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
\cite{West1998}.}. Therefore, gamma matrices of different
matrix dimension are built by tensor products of Pauli matrices.\todo{make it
more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
tensor them. One can add more bands of the same type, or add more bands of a
different type in the smaller dimension, or add trivial bands. In all cases, the
triviality of topological insulators can be detected in minimal dimension, since
adding trivial bands can be ignored (insensitive to addition of trivial bands),
and the possible different types of matrices are limited.

However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
topological insulator, we need to increase the matrix dimension to consider
multiple copies of the Dirac Hamiltonian. If the topological state is stable for
an arbitrary copies, then this is a $\Z$ topological insulator. If the
topological state is stable only of an odd number of copies, this is a $\Z_2$
topological insulator.

Another way to view this way of classification, is to look at the surface
Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
see if the surface mode can be gapped, so as to detect the topological
properties of the bulk.

\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
\label{sec:Isomorphism}
As with other classifications, we construct isomorphisms between Dirac matrices
and Clifford Algebras, after which we are faced with an extension problem. The
isomorphism is constructed now.
\subsubsection{Symmetry Constraint}
\label{sec:Symmetry Constraint}
The Hamiltonian with extra mass term is
\begin{equation}
    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
    + \sum_{i=1}^{d} k_i \gamma_i
\end{equation}
The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
conditions on the gamma matrices:
\begin{subequations}
    \label{eq:sym-spemt}
\begin{align}
    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
\end{align}
\end{subequations}
With this, we can establish a isomorphism between "Hamiltonian and Symmetry
Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
examples in action.

\subsubsection{Examples of Constructing Isomorphism}
\label{sec:iso-Examples}
For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
\begin{table}[htpb]
    \centering
    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
    \label{tab:generator-AI}
    $ \begin{tabu}{ c | *4{c} }
        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
        \hline
        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
    \end{tabu} $
\end{table}

Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
$J_3=iT\tilde{\gamma}_0$, we could verify that all
$\{i,T,J_3,J_4\}$ anticommute with each other, and
$J_3^2=J_4^2=1$. So together they generate the algebra
$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
Table~\ref{tab:map-sym-cl}.

Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
\begin{equation}
    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
\end{equation}
We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
\begin{table}[htpb]
    \centering
    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
    \label{tab:generator-AII}
    $ \begin{tabu}{ c | *4{c} }
        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
        \hline
        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
    \end{tabu} $
\end{table}
Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
$K_i^2=-1$, $(K'_1)^2=1$. The following map
\begin{equation}
    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
\end{equation}
has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
\begin{table}[htpb]
    \centering
    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
    \label{tab:map-cl13-2-cl04}
    $ \begin{tabu}{ c | *4{c} }
        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
        \hline
        J_1    & -1      & \{\}    & \{\}    & \{\} \\
        J_2    & ~       & -1      & \{\}    & \{\} \\
        J_3    & ~       & ~       & -1      & \{\} \\
        J_4    & ~       & ~       & ~       & -1
    \end{tabu} $

    where $\{\}$ means anticommute.
\end{table}
Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
consistent with $G_{\mathrm{AII}} \cong
\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.

\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
\label{sec:Complex Classes-iso}
The general steps for constructing the isomorphism is presented here. First, we
need to treat the situation of complex classes and real classes
differently. The complex classes are isomorphic to complex Clifford Algebras,
while the real classes are isomorphic to real Clifford Algebras. The reason for
this distinction is that, in real classes, there are complex conjugate operator
$K$. First, there is not way to represent complex conjugation simply as
multiplication of complex matrices. Second, complex matrices come with a nature
definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
Algebras when dealing with real classes (which is the reason why they are named
real classes).

For complex classes, let $G_\#$ be the group generated by elements
$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
Clifford Algebra:
\begin{align}
    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
    \mathrm{C\ell}_{d+D+1}(\C) \\
    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
    \cong  \mathrm{C\ell}_{d+D+2}(\C)
\end{align}

\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
\label{sec:Real Classes-iso}

For real classes, we need to include $i$, and symmetry operators $T,C$ in our
group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
which is possible as is mentioned earlier. Now we demonstrate the proof of
isomorphism in class $\mathrm{AII}$.

We first note that, given a real vector space $V$, we can complexify a real space in
two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
which does not suit our purpose. The second is to find an almost complex
structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
operators on a real vector space naturally.

Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.

Then we discuss some tips that will useful for later calculation.
\paragraph{Tips}
\begin{enumerate}
    \item Since all generator anticommute, all matrices either commute or
        anticommute. So the Algebra is pretty simple.
    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
        or anticommutation does not depends on the order of the matrices $BC$ or
        $CB$. So one might rearrange them in the order whichever is convenient.
    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
        BA$. However, if $A$ and $B$ has something in common, then the above
        condition breaks. This is like adding an "impurity" in it to change the
        commutation/anticommutation relations.
    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
        candidates for symmetry operator are only a small finite set.
        \label{enum:tips-4}
\end{enumerate}

\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
in real vector space, they commute with $J_1=J$. Then, each gamma matrices
should have an even number of Clifford Algebra generators other than $J_1$
itself. Similarly, antiunitary symmetry operators should have an odd number of
Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
some $J_1$ to make it commute/anticommute with symmetry operators. More
explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
\ref{eq:sym-spemt}, and they give us the inspiration to set:
\begin{equation}
    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
    \sum_{i=1}^d k_i J_2\tilde{J}_i
\end{equation}
Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
And within this algebra, only $J_2$ is a possible candidate for symmetry
operators, which satisfy equations~\ref{eq:sym-spemt} (use
tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
class $\mathrm{AII}$. Therefore, the map:
\begin{align}
    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
\end{align}
is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
$\mathrm{AII}$. The inverse map can be found easily. We first solve some
formality problems. A complex number can be written as a real number by
identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
\begin{equation}
    a+bi \to a \begin{pmatrix}
        1 & \\ & 1
    \end{pmatrix} + b \begin{pmatrix}
         & 1 \\ -1 & 
    \end{pmatrix} = a\id + b J
\end{equation}
Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
\begin{equation}
    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
\end{equation}
The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
\begin{equation}
    K \equiv \sigma_z \otimes \id_{n\times n}
\end{equation}
Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
\begin{equation}
    \{\Gamma_T,\Gamma_C\} = 0
\end{equation}

Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
\begin{align}
    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
    \Gamma_T &\to J_2 \nonumber\\
    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
\end{align}
is the desired inverse map.

\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
The rest is exactly the same as in class $\mathrm{AII}$.

All other classes can be treated similarly, so we do not repeat the calculation
and only list the result in Table~\ref{tab:map-sym-cl}.
\begin{table}[htpb]
    \centering
    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
    Algebra. Also, only one direction of mapping is shown. The inverse map can
    be easily constructed accordingly. The complex class are also added for
    convenience.}
    \label{tab:map-sym-cl}
    \begin{tabular}{c | c c c | l | c }
        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
        \hline 
        D & $0$ & $+$ & $0$ & 
        $\tilde{J}_1\to\Gamma_C$,
        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
        DIII & $-$ & $+$ & $1$ & 
        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
        AII & $-$ & $0$ & $0$ & 
        $J_2\to \Gamma_T$,
        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
        $J_2\tilde{J}_i \to \Gamma_i$
        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
        CII & $-$ & $-$ & $1$ & 
        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
        $J_2\tilde{J}_i \to \Gamma_i$
        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
        C & $0$ & $-$ & $0$ & 
        $J_2\to \Gamma_C$, 
        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
        $J_1J_2J_{i+2}\to \Gamma_i$
        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
        CI & $+$ & $-$ & $1$ & 
        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
        $J_1J_2J_{i+2}\to \Gamma_i$
        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
        AI & $+$ & $0$ & $0$ & 
        $\tilde{J}_1\to \Gamma_T$,
        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
        $\tilde{J}_1J_{i+1} \to \Gamma_i$
        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
        BDI & $+$ & $+$ & $1$ & 
        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
        $\tilde{J}_1J_{i+1} \to \Gamma_i$
        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
        \hline
        A & $0$ & $0$ & $0$ & 
        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
        AIII & $0$ & $0$ & $1$ & 
        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
        \hline
    \end{tabular}
\end{table}
\subsection{Classification in 1-dimension}
\label{sec:Classification in 1-dimension}
Classification of $1$ dimension is the simplest, since the minimal matrix
dimension will mostly be $2$, which means we can use the familiar Pauli matrices
directly.

\paragraph{Class $\mathrm{A}$} We have the extension from
$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
\begin{equation}
    H_A = M \sigma_x + k_x \sigma_y
\end{equation}
Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.

\paragraph{Class $\mathrm{AIII}$} We have the extension from
$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
Pauli matrices. For example:
\begin{equation}
    H_A = M \sigma_x + k_x \sigma_y
\end{equation}
However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
there is not other matrix possible for the extra mass term (this can be viewed
alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
has irreducible representation in dimension $1$ or $4$). So the state is
topologically non-trivial. Now we consider the state with arbitrary copies of it.
\begin{equation}
    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
    S=\sigma_z\otimes\id_n
\end{equation}
where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
linearity of anti-commutator and some basic properties of Kronecker product,
there is no SPEMT term. Hence this is a $\Z$ topological insulator.

The above are for complex classes. For real classes, we have to be careful,
since one generator $J_1$ is taken up by $i$.

\paragraph{Class $\mathrm{AII}$} We have the extension from
$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
This already hints that we will have SPEMT. Explicitly, we could let
\begin{equation}
    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
\end{equation}
with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
this is a trivial insulator.

\paragraph{Class $\mathrm{C}$} We have the extension from
$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
could let
\begin{equation}
    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
\end{equation}
with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
this is a trivial insulator.

\paragraph{Class $\mathrm{CI}$} We have the extension from
$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
could let
\begin{equation}
    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
\end{equation}
with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.

\paragraph{Class $\mathrm{AI}$} We have the extension from
$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
that we have SPEMT. Explicitly, we could let
\begin{equation}
    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
\end{equation}
with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.

\paragraph{Class $\mathrm{CII}$} We have extension from
$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
to
$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
We let:
\begin{equation}
    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
\end{equation}
with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
the remaining choice are acceptable, considering $T$ and $C$.}. Consider
arbitrary copies of it:
\begin{equation}
    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
    k_x\sigma_y\otimes\id_2)\otimes\id_n
\end{equation}
with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
with $C$.}. Therefore, this is a $\Z$ topological insulator.

\paragraph{Class $\mathrm{BDI}$} We have extension from
$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
\begin{equation}
    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
\end{equation}
with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
of it:
\begin{equation}
    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
\end{equation}
with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.

\paragraph{Class $\mathrm{D}$} We let:
\begin{equation}
    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
\end{equation}
with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
it:
\begin{equation}
    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
\end{equation}
with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
Hence, this is a $\Z_2$ topological insulator.

To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
\paragraph{Class $\mathrm{DIII}$} We let:
\begin{equation}
    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
\end{equation}
with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
this does not commute with $T$. Hence, there is no SPEMT. Now consider two
copies of it:
\begin{equation}
    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
\end{equation}
with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
this is a $\Z_2$ topological insulator.

In summary, we have classified topological insulators in $d=1$, summarized in
Table~\ref{tab:ti-d=1}.
\begin{table}[htpb]
    \centering
    \caption{Topological Insulators in $d=1$}
    \label{tab:ti-d=1}
    \begin{tabular}{c | c c c | c }
        Class($\#$) & T & C & S & $d=1$ \\
        \hline 
        A & $0$ & $0$ & $0$ & $0$ \\
        AIII & $0$ & $0$ & $1$ & $\Z$ \\
        \hline
        D & $0$ & $+$ & $0$ & $\Z_2$ \\
        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
        AII & $-$ & $0$ & $0$ & $0$ \\
        CII & $-$ & $-$ & $1$ & $\Z$ \\
        C & $0$ & $-$ & $0$ & $0$ \\
        CI & $+$ & $-$ & $1$ & $0$ \\
        AI & $+$ & $0$ & $0$ & $0$ \\
        BDI & $+$ & $+$ & $1$ & $\Z$ \\
        \hline
    \end{tabular}
\end{table}
\todo{add reflection about the disadvantage of this method (no $2\Z$). And
representation aspect}
\subsection{Classification in Arbitrary Dimension}
\label{sec:Classification in Arbitrary Dimension}
We now show combined with some properties, the classification in $d=1$ can be
generalized to classification in arbitrary dimensions. In $K$-theoretic
classification, the extension problem is not affected when tensored with some
other algebras. Specifically, for complex classes, the extension problem of
$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
This insensitive to tensoring a new algebra, can be understand in SPEMT
background.\todo{understand this~}

Now, let us write $\sim$ to represent the equivalence between two extension
problems.  The Complex Clifford Algebra has a periodicity of $2$:
\begin{equation}
    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
    \mathrm{C\ell}_{2}(\C)
\end{equation}
The Real Clifford Algebra has a periodicity of $8$:
\begin{equation}
    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
\end{equation}
This two relation means, the extension problem will be the same with respect to
a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
classes. Hence the classification of topological insulators need only be done
with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
symmetry classes, i.e.
\begin{subequations}
    \label{eq:cli-periodic}
\begin{align}
    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
\end{align}
\end{subequations}
Another useful property is:
\begin{align}
    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
\end{align}
This property tells us that Clifford Algebra basically depends only on the
difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
example, we have (let $n$ be an arbitrary integer):
$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
derive easily two chains of relation:
\begin{align}
    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
    \nonumber\\
    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
\end{align}
and
\begin{align}
    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
    \nonumber\\
    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
\end{align}
Now we tries to connect the two chains together. We note further that the
Clifford Algebra has the following properties:
\begin{align}
    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
\end{align}
Then:
\begin{align}
    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
\end{align}
Therefore,
$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
connecting the two chains. If we compare this carefully with
Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
prove the dimension-shift feature of classification:
\begin{align}
    \label{eq:cli-Chain1}
    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
\end{align}
We need one more property:
\begin{equation}
    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
\end{equation}
Then
\begin{equation}
    \label{eq:cli-Chain2}
    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
\end{equation}
With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
we see that we need only the result in a dimension, to obtain the whole of
classification in Table~\ref{tab:master-table2}.
\begin{table}
\begin{center}
\begin{tabular}{|c|cccccccc|ccc|}
\hline
\multicolumn{12}{|c|}{
The original classification table} \\ \hline
   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
\hline\hline
  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline

  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
   \\
\hline
\end{tabular}
\caption{The original classification table of topological insulators and
superconductors}
\label{tab:master-table2}
\end{center}
\end{table}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at 
\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
{[My Email Address(Click)]}.

\bibliography{../../library}{}
\bibliographystyle{alphaurl}
% \begin{thebibliography}{1}
% 	\bibitem{book} 
% \end{thebibliography}
\printnomenclature

\end{document}

### 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
[major] Add minimal dimension argument and etc.

@@
 \abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
+    The abstract is left blank due of unforeseeable changes that may happen to
+    this document.
 }
-% TODO: add ref for Clifford Algebra.
 \tableofcontents
@@
 The classification of topological insulators in non-interacting system is in
-effect a classification of Hamiltonian matrix. The simple case considered here
+effect a classification of $N\times N$ Hamiltonian matrix. %sym
+The simple case considered here
 is the classification done by considering how the Hamiltonian matrix responses
@@
 
-There are two classical approaches towards this classification. The first is to
-examine the existence of Anderson delocalization at the boundary of the
-insulator, because the existence of surface conducting state is the signature of
-topological insulators and the Anderson localization is the obstruction that
-\todo{Be more specific about this and check some facts.}
-surface conducting states must overcome. This approach uses the Nonlinear Sigma
-Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
+There are two classical approaches towards this classification. The first
+\cite{Schnyder2008} is to examine the existence of Anderson delocalization at
+the boundary of the insulator. The existence of robust surface conducting state
+is the signature of topological insulators. When some random impurity potentials
+could be present in these surfaces, the Anderson localization is the obstruction
+that surface conducting states must overcome. This approach uses the Nonlinear
+Sigma Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
 when can a localization-breaking term can be added to NL$\sigma$Ms.
 
-The second approach is to use homotopy theory to classify classes Hamiltonians under
-continuous deformation, more specifically, under adiabatical change of
-Hamiltonians. This method is most elegant but most mathematical demanding
-approach compared with others, because calculating homotopy groups, and homotopy theories in
-general are notorious hard. Also, one has to use $K$-theory, because of
-something physical is enlarging those distinct classes of Hamiltonian. To be
-more specific.
+The second approach\cite{Kitaev2009a} is to use see the classification as an
+extension problem of Clifford Algebras. The anti-unitary symmetries already
+possess some behavior similar to generators of Clifford Algebras. And sometimes
+Hamiltonians could be regarded as yet another generator of Clifford
+Algebra\cite{Morimoto2013}. The $K$-theory approach is to put the symmetries in
+the Clifford Algebra first, and consider adding the Hamiltonian that preserve
+such symmetries to the Clifford Algebra. So the problem of classification of
+Hamiltonians becomes a problem of extending the Clifford Algebra.
 
@@
 closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes theorem,
-unless inside this manifold there is somewhere where the formula for Chern
-number got "blown up", and it is just this locally "blown up" point that is
-responsible for the nonzero Chern number, and for the non-triviality of
-topological insulators.
+without boundary. Therefore, it should always be zero because of the Stokes
+theorem, unless inside this manifold there is somewhere where the formula for
+Chern number got "blown up", and it is just this locally "blown up" point
+(caused by the crossing) that is responsible for the nonzero Chern number, and
+for the non-triviality of topological insulators. More generally, we believe
+that there is a bulk-boundary correspondence that the properties of the bulk is
+reflected by the properties in the boundary.
 
@@
 opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
-
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
+describe such a low energy physics is the Dirac Hamiltonian. Also, the
+traditional discussion of Klein-Gordon equation all tells us to look at Dirac
+Hamiltonian.
+
+Using the Dirac Hamiltonian, it is discovered by Dr. Chiu \cite{Chiu2013a} that
+the classification of topological insulators could be brought done into very
+simple applications of classification and representation theory of Clifford
+Algebras, which have been well studied with excellent resources provided online.
+In his classification, he established a isomorphism from $G_{\text{symmetries 
+class}}$, the algebra generated by symmetry operators and Dirac Hamiltonians, to
+some Clifford Algebras. Consequently, the Hamiltonian and symmetry operators,
+all become some specific representations of their corresponding Clifford
+Algebras. Also, it will be argued later that the minimal matrix dimension of
+such representation, i.e. the minimal dimension of the Dirac Hamiltonian, can
+tell the specific type of this topological insulator. Therefore, as a whole all
+the classification work is reduced to the consideration of minimal matrix
+dimension of the representation of Clifford Algebra, in different spatial
+dimension.
+
+This work may be considered as a note to Chiu's dissertation\cite{Chiu2013a}.
+However, I do not guarantee that my interpretation is the same as his as I have
+modified and amended some parts to make the work more, in my opinion, congruous
+and systematic.
 
@@
 \begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
+    \item \textbf{Ten-fold Way} Introduces the result of Ten-fold way: why we
+        care only about anti-unitary symmetries, why there are ten different
+        classes.
+    \item \textbf{Classification by Dirac Mass Hamiltonians} gives comprehensive
+        account of how the Minimal Dirac Hamiltonian approach works, and how the
+        ten-fold way is derived in this approach.
+    \item \textbf{Looking Further} outlines the possible direction in classification
+        under unitary symmetries, and some other results.
 \end{enumerate}
@@
 
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
+We begin our discussion with a background before this classification.  The
+classification of topological phases with different non-unitary symmetries in
+non-interacting picture, are in essence, the classification of $N\times N$
 matrices by its response to three discrete symmetries: time reversal symmetry
@@
 different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
+Hamiltonian respecting these symmetries are tabulated in Figure.1
+in\cite{Ludwig2015}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$,
+etc.), and their properties in different spatial dimensions respect a periodic
+structure. For the class $A$ and class $AII$, they are named complex classes and
+respect a $2$-fold period. For the other eight classes are named real classes
+and respect a $8$-fold period, which is why we only listed the first $0\to 7$
+spatial dimensions in Table~\ref{tab:master-table2}.
 
@@
 
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
+With translational symmetry added, the classification can be made the will yield
+the same result.\footnote{This is still a mystery to me which this is true. The
+    exact reason is related to some isomorphism between certain homotopy groups.
+    Interested reader could see Ludwig's lecture
+\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{here}
+for a clue.}
 
@@
 
+The Tenfold Way, is originally the ten different ways to write down a
+Hamiltonian when there are ten different combinations of symmetries that the 
+system respect.
 \todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
+of each evolutionary operators, if I have time}
 
@@
 classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
+$T^d$ by $S^d$\footnote{The exact reason can be found in Kitaev's
+    classification\cite{Kitaev2009a} or another article \cite{Kennedy2015} which
+discuss it from a different view.}, and we do it in a stable way, i.e., we choose
 our classification to be independent of and insensitive to the addition of
@@
 \cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
+matrix dimension are built by tensor products of Pauli matrices.
+\footnote{Or, the non-trivial irreducible representations (turns out there are
+at most 2) are built by tensoing Pauli matrices.}
+Now, to increase the dimension of the matrix, is equivalent to
 tensor them. One can add more bands of the same type, or add more bands of a
@@
 \label{sec:Classification in 1-dimension}
+
+\subsubsection{Model Systems}
+\label{sec:Model Systems}
 Classification of $1$ dimension is the simplest, since the minimal matrix
@@
 \end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
+where $n$ is some positive integer. Since gamma matrices are basically tensor
+products of Pauli matrices, there is no SPEMT term. Hence this is a $\Z$
+topological insulator.
 
@@
 
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
+In summary, we shown examples of different classes of topological insulators in
+$d=1$, summarized in Table~\ref{tab:ti-d=1}.
 \begin{table}[htpb]
@@
 \end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
+\subsubsection{Irreducible Representation Arguments for Classification}
+\label{sec:Irreducible Representation Arguments for Classification}
+The above examples are only valid in special points of the Brillouin Zone.
+However, in real materials, one will be faced with Hamiltonians of various form:
+\begin{equation}
+    H = m\gamma_0 \pm k_1\gamma_1 \pm k_2\gamma_2 \cdots
+\end{equation}
+Here, we look at this problem from a representation theory point of view. It is
+well known that representation of Clifford Algebras are completely reducible,
+and there are only 1 or 2 nontrivial (dimension $>1$) inequivalent irreducible
+representations of Clifford Algebras (see \ref{sec:Various Properties for
+Clifford Algebras}).  The dimension of the representation of relevant Clifford
+Algebras are listed in Table~\ref{tab:mat-dim-allClass-1d}. There are only three
+types of change occurs in that table:
+
+\paragraph{$\mathbf{n\to n}$ or $\mathbf{n\to n_2}$} Basically, this means that in the same
+dimension we could always have a SPEMT present. So there will never be stable
+edge states.
+
+\paragraph{$\mathbf{n\to 2n}$} This means that, although in the same dimension we have
+always stable edge mode. When we take two copies of the Hamiltonian, i.e., when
+there are two edge modes. There will a new gamma matrix in the doubled-dimension
+acting as a SPEMT to gap out the system. Hence in general, an odd copies of
+the edge mode is stable whereas an even copies of the edge mode is not. Hence
+this is a $\Z_2$ topological insulator.
+
+\paragraph{$\mathbf{n_2\to 2n}$} This is similar to the above $\Z_2$ case. However, since
+we have two inequivalent representations in a single edge mode, we could
+the doubled system could have came from different representations, which could
+not be gapped out by the extra SPEMT in doubled-dimension (otherwise we would
+have two inequivalent representations in the doubled-dimension). Hence, this is
+a $\Z$ topological insulator.
+
+In this way we confirmed the classification in Table~\ref{tab:ti-d=1}.
+
+\begin{table}[htpb]
+    \centering
+    \caption{Matrix dimensions related to the extension problem for different
+    classes in $d=1$. Note that a subscript $2$ as in $2_2$, means that there
+    are two inequivalent representations in the same matrix dimension.}
+    \label{tab:mat-dim-allClass-1d}
+    \begin{tabular}{c | c c c}
+        Name of Class & Extension of $\mathrm{C\ell}$ & Dimension Change &
+        Topological Invariant \\
+        \hline
+        A & $\mathrm{C\ell}_{2}(\C)\to\mathrm{C\ell}_{3}(\C)$ & $2\to2_2$ & $0$
+        \\
+        AIII & $\mathrm{C\ell}_{3}(\C)\to\mathrm{C\ell}_{4}(\C)$ & $2_2\to4$ &
+        $\Z$
+        \\
+        AII & $\mathrm{C\ell}_{1,3}(\R)\to\mathrm{C\ell}_{1,4}(\R)$ & $4\to 4_2$ & $0$
+        \\
+        C & $\mathrm{C\ell}_{1,3}(\R)\to\mathrm{C\ell}_{2,3}(\R)$ & $4\to 4$ & $0$
+        \\
+        CI & $\mathrm{C\ell}_{2,3}(\R)\to\mathrm{C\ell}_{3,3}(\R)$ & $4\to 4$ & $0$
+        \\
+        AI & $\mathrm{C\ell}_{2,2}(\R)\to\mathrm{C\ell}_{3,2}(\R)$ & $2\to 2_2$ & $0$
+        \\
+        CII & $\mathrm{C\ell}_{1,4}(\R)\to\mathrm{C\ell}_{1,5}(\R)$ & $4_2\to 8$
+        & $\Z$
+        \\
+        BDI & $\mathrm{C\ell}_{3,2}(\R)\to\mathrm{C\ell}_{4,2}(\R)$ & $2_2\to 4$ 
+        & $\Z$
+        \\
+        D & $\mathrm{C\ell}_{2,2}(\R)\to\mathrm{C\ell}_{2,3}(\R)$ & $2\to 4$ 
+        & $\Z_2$
+        \\
+        DIII & $\mathrm{C\ell}_{2,3}(\R)\to\mathrm{C\ell}_{2,4}(\R)$ & $4\to 8$ 
+        & $\Z_2$
+        \\
+        \hline
+    \end{tabular}
+\end{table}
 \subsection{Classification in Arbitrary Dimension}
@@
 $\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
+problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{2}(\C)\to
+\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{2}(\C)$ (See for example, sec
 III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
 This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
+background. Because $\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, which only
+multiply the matrix dimension of both sides by a constant $2$. So the pattern of
+$n\to n, n\to n_2$, $n\to 2n$, and $n_2\to 2n$, mentioned in previous section,
+remains unaltered. For real classes, instead of $\mathrm{C\ell}_{2}(\C)$, we
+have $\mathrm{C\ell}_{1,1}(\R)\cong\mathcal{M}(2,\R)$, or
+$\mathrm{C\ell}_{2,2}(\R)\cong\mathrm{C\ell}_{1,1}(\R)\otimes\mathrm{C\ell}_{1,1}(\R)\cong\mathcal{M}(4,\R)$.
+So the reasoning is the same.
 
@@
 \end{equation}
-This two relation means, the extension problem will be the same with respect to
+This two relation means that, the extension problem will be the same with respect to
 a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
@@
 \begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
+    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex class)} \\
+    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real class)}
 \end{align}
@@
 \end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
+With equivalences~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
 we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
+classification of all real classes. Similar fact holds for complex classes:
+\begin{equation}
+    G_{\mathrm{AIII}}(d=d_0) \sim G_{\mathrm{A}}(d=d_0-1)
+\end{equation}
+which is too trivial to be mentioned here.
+
+In a word, our classification for topological insulators in $1$ spatial
+dimension is sufficient to generate the whole Table~\ref{tab:master-table2}.
+This is a remarkable consequence of $K$-theory.
 \begin{table}
@@
 \caption{The original classification table of topological insulators and
-superconductors}
+superconductors. Note that in this document we could not yet differentiate
+between $\Z$ and $2\Z$ topological invariants.}
 \label{tab:master-table2}
@@
 \end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
+
+\section{Looking Further}
+\label{sec:Looking Further}
+There has be great deal of progress made in classification of topological
+insulator and superconductors. We first comment that our discussion could be
+easily generalized to some topological superconductors because they naturally
+admits a matrix like Hamiltonian using Nambu spinors.
+
+Also, our discussion falls short in two respects. First, it cannot distinguish
+between $\Z$ and $2\Z$ cases. Secondly, we do not give explicit formulae for
+calculating topological invariants in different cases. The former problem can be
+addressed in Ludwig's \cite{Schnyder2008}, while the latter requires
+considerable work, and provides different topological invariant in different
+cases (see sec. III.B of \cite{Chiu2016}).
+
+There has been progress made both in incorporating defects into classification,
+as well as incorporating unitary symmetries into the classification. The
+defect's classification has been incorporated beautifully into the same table of
+Tenfold Way. On the other hand, introduction of unitary symmetries gives a more
+fruitful result. For example, introduction of crystal symmetries gives a new
+class of topological insulators, dubbed topological crystalline
+insulators.\cite{Ando2015} the case of reflection symmetry, some new topological
+invariants denoted as $M\Z$, called mirror topological invariants, are needed to
+classify topological matters\cite{Chiu2013}.
+
+Lastly, the discussion of topological states in interaction picture extends to
+the case of symmetry-protected phases (SPTs), of which I am not familiar with.
+For all these new concepts, the review \cite{Chiu2016} is an excellent source of
+information.
+
+\section{Various Properties for Clifford Algebras}
+\label{sec:Various Properties for Clifford Algebras}
+We have used various properties of Clifford Algebras from various sources. Here
+I summarized those properties for the convenience of readers.
+
+\paragraph{Isomorphism Relations}
+The best source of isomorphism between Clifford Algebras is actually the
+Wikipedia page about \textit{Classifications of Clifford Algebras}. For a more
+authoritative account, I am using the book \cite{VazJayme2016}. The results
+used in this document are to be found in chapter 4 of that book.
+
+\paragraph{Representation Theory on Complex Clifford Algebras}
+This paper \cite{West1998} has a good discussion on the irreducible
+representations of complex Clifford Algebras, in p.5, p.12. They can be
+summarized as:
+\begin{thm}
+    Consider $\mathrm{C\ell}_{N}(\C)$. For both $N = 2n$ and $N = 2n + 1$, the
+    dimension d of the irreducible representation is uniquely given by
+    \begin{equation}
+        d = 2^n \text{($N=2n$ or $N=2n+1$)}
+    \end{equation}
+    Moreover, for $N = 2n$, the irreducible space is unique, while for $N = 2n +
+    1$, we have two inequivalent irreducible representations with the same
+    dimension $d$.
+\end{thm}
+
+\paragraph{Representation Theory on Real Clifford Algebra}
+The two papers \cite{Okubo1991a}\cite{Okubo1991} are great in this respect.
+Their result used in this document could be summarized as:
+\begin{thm}
+    Consider $\mathrm{C\ell}_{p,q}(\R)$. For $N=2n$, we have:
+    \begin{align}
+        d= \begin{cases}
+              2^n_1, & \text{for } p-q=0\text{ or }2\text{, mod }8 \\
+              2^{n+1}_1, & \text{for } p-q=4\text{ or }6\text{, mod }8 \\
+          \end{cases}
+    \end{align}
+    For $N=2n+1$, we have:
+    \begin{align}
+        d= \begin{cases}
+              2^n_2, & \text{for } p-q=1\text{, mod }8 \\
+              2^{n+1}_1, & \text{for } p-q=3\text{ or }7\text{, mod }8 \\
+              2^{n+1}_2, & \text{for } p-q=5\text{, mod }8 \\
+          \end{cases}
+    \end{align}
+    Where we have used a subscript $\phantom{1}_1$ to denote that there is only
+    one unique irreducible representation, and a subscript $\phantom{1}_2$ to
+    denote that there are two inequivalent irreducible representations.
+\end{thm}
+Below collects a list of dimensions that I have used in the discussion of
+Table~\ref{tab:mat-dim-allClass-1d}:
+\begin{align*}
+    &
+    \mathrm{C\ell}_{1,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{1,3}(\R)\sim 4^2_1,\,
+    \mathrm{C\ell}_{1,4}(\R)\sim 4^2_2,\, \mathrm{C\ell}_{1,5}(\R)\sim 8^2_1,\,
+    \\&
+    \mathrm{C\ell}_{2,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{2,3}(\R)\sim 4^2_1,\,
+    \mathrm{C\ell}_{3,2}(\R)\sim 2^2_2,\, \mathrm{C\ell}_{2,4}(\R)\sim 8^2_1,\,
+    \\&
+    \mathrm{C\ell}_{3,3}(\R)\sim 4^2_1,\, \mathrm{C\ell}_{4,2}(\R)\sim 4^2_1.
+\end{align*}
+
+\section{Online Version}
+This document may be updated online at
+\href{https://github.com/we-taper/Draft/tree/master/Notes%20of%20various%20papers/Chiu%20Minimal%20Dirac%20Hamiltonian%20Method}{here}.
 

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-2.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-% My own physics package
-% The following line load the package xparse with additional option to
-% prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
-
-\makenomenclature % For an index of symbols.
-
-\title{Notes about the Minimal Dimensional Method to Classify
-Topological Phases (preliminary)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
-}
-% TODO: add ref for Clifford Algebra.
-\tableofcontents
-
-\section{Outline}
-\label{sec:Outline}
-
-The classification of topological insulators in non-interacting system is in
-effect a classification of Hamiltonian matrix. The simple case considered here
-is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
-symmetries. Specifically, when we module out any unitary symmetries of the
-Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
-we only classify topological insulators based on how our Hamiltonian matrix
-responses to these anti-unitary symmetries.
-
-There are two classical approaches towards this classification. The first is to
-examine the existence of Anderson delocalization at the boundary of the
-insulator, because the existence of surface conducting state is the signature of
-topological insulators and the Anderson localization is the obstruction that
-\todo{Be more specific about this and check some facts.}
-surface conducting states must overcome. This approach uses the Nonlinear Sigma
-Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
-when can a localization-breaking term can be added to NL$\sigma$Ms.
-
-The second approach is to use homotopy theory to classify classes Hamiltonians under
-continuous deformation, more specifically, under adiabatical change of
-Hamiltonians. This method is most elegant but most mathematical demanding
-approach compared with others, because calculating homotopy groups, and homotopy theories in
-general are notorious hard. Also, one has to use $K$-theory, because of
-something physical is enlarging those distinct classes of Hamiltonian. To be
-more specific.
-
-But the key to understand topological insulators, are not necessarily the
-Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes theorem,
-unless inside this manifold there is somewhere where the formula for Chern
-number got "blown up", and it is just this locally "blown up" point that is
-responsible for the nonzero Chern number, and for the non-triviality of
-topological insulators.
-
-Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
-energy zero level to the crossing point, in only the low energy physics. We
-expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
-
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
-
-\paragraph{Structure of this work} This work are divided into several parts.
-\begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
-\end{enumerate}
-
 \section{Ten-fold Way}
 
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
+We begin our discussion with a background before this classification.  The
+classification of topological phases with different non-unitary symmetries in
+non-interacting picture, are in essence, the classification of $N\times N$
 matrices by its response to three discrete symmetries: time reversal symmetry
@@
 different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
+Hamiltonian respecting these symmetries are tabulated in Figure.1
+in\cite{Ludwig2016}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$,
+etc.), and their properties in different spatial dimensions respect a periodic
+structure. For the class $A$ and class $AII$, they are named complex classes and
+respect a $2$-fold period. For the other eight classes are named real classes
+and respect a $8$-fold period, which is why we only listed the first $0\to 7$
+spatial dimensions in Table~\ref{tab:master-table2}.
 
@@
 
+\paragraph{The Tenfold Way}
+
+The Tenfold Way, is originally the ten different ways to write down a
+Hamiltonian when there are ten different combinations of symmetries that the 
+system respect. The classes of Hamiltonian (or more precisely, the evolution
+operators $e^{itH}$) are tabulated in Figure.1 of \cite{Ludwig2016}. Ludwig
+classified the topological insulators in each spatial dimension by computing the
+homotopy groups for each dimension. On the other hand, this classification can
+also be done using $K$-theory.
+
 \paragraph{Translational Symmetry}
@@
 Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
+symmetry to present. Also, the addition of translational symmetry not only
+produces the same classification, but also make this classification more
+convenient to be done.
 
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
+With translational symmetry added, the classification can be made the will yield
+the same result.\footnote{This is still a mystery to me which this is true. The
+	exact reason is related to some isomorphism between certain homotopy groups.
+	Interested reader could see Ludwig's lecture
+	\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{here}
+	for a clue.}
 
@@
 \end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
-
-\section{Classification by Dirac Mass Terms}
-\label{sec:The Minimal Hamiltonian Approach}
-
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
-We first note that different topological phases are distinguished by the closing
-and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
-flatten the energy spectrum to two bands of energy $\pm E$, the transition
-(closing of gap) will happen at some point where locally the energy is of a
-Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
-behavior. Then, a class of topological phases, or more specifically, a class of
-Hamiltonian matrix that shares the same topological invariant, can be
-\textit{represented} by the Dirac Hamiltonian in this class.
-
-\subsection{Crossing Spectrum and Edge Mode}
-\label{sec:Crossing Spectrum and Edge Mode}
-Here we show that the crossing spectrum characteristic of topological insulators
-can be characterized by a Dirac type Hamiltonian, and with this Dirac
-Hamiltonian we could find an Edge mode solution built into it.
-
-\paragraph{Crossing Spectrum and Dirac Hamiltonian}
-In some local region around the crossing point, the energy spectrum should look
-like:
-\begin{equation}
-    E = \pm \sqrt{\vb{k}^2 + M^2}
-\end{equation}
-where $\vb{k}$ is the crystal momentum and $M$ is some constant
-responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
-
-As has been analysed in most Quantum Mechanics textbook\footnote{See for
-    example, p.99 of \cite{Greiner1997}. Although their discussion is in
-dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
-relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
-use is:
-\begin{equation}
-    \label{eq:dirac-H}
-    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
-\end{equation}
-where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
-Clifford Algebra anti-commutation relation:
-\begin{equation}
-    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
-\end{equation}
-
-\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
-phase. First, it has a gapless state. Due to the anti-commutation relation of
-$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
-tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
-we choose not $\gamma_i^2=-1$, which would give non-sensible result
-$H_\text{Dirac}^2= -E^2\id$.}
-that the energies of Dirac Hamiltonian are:
-\begin{equation}
-    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
-\end{equation}
-Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
-gaped to gapless and again to gaped state. This shows that the $M$ is parameter
-controlling the quantum phase transition, and the system with $M<0$ or $M>0$
-possesses two different quantum phase.
-
-In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
-should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
-broken in that direction. Now the eigenvalue equation is:
-\begin{equation}
-    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
-    = E \Phi
-\end{equation}
-
-Past experience teaches us the ansatz (assuming
-$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
-does not blow up the wavefunction):
-\begin{equation}
-    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
-\end{equation}
-which after plugging inside the eigenvalue equation, leads to
-\begin{equation}
-    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
-    = E \phi
-\end{equation}
-After left multiplication of $\gamma_0$, we have:
-\begin{equation}
-    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
-    = E \gamma_0 \phi
-\end{equation}
-Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
-$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
-eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
-$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
-state to be a surface state, so we choose the $-1$ eigenvectors (denoted
-$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
-\begin{equation}
-    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
-\end{equation}
-As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
-have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
-eigenspaces:
-\begin{equation}
-    \label{eq:H-Dirac-surf}
-    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
-\end{equation}
-
-% \section{Collection of Calculation}
-% \label{sec:Collection of Calculation}
-% Here collects the calculations done throughout the whole notes.
-
-\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
-\label{sec:Homotopy to Minimal Dirac}
-
-\paragraph{Spectral Flattening} The classification of topological insulators
-concerns different classes of Hamiltonian that cannot be adiabatically changed
-to each without closing or opening of a gap. Hence, we could in general
-adiabatically change our parameters such that the spectrum of Hamiltonian is
-simplified into two bands of energy $\pm1$. Under this condition, we have
-$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
-for generating Clifford Algebras.
-
-\paragraph{Extension Problem with General Examples}
-The general theme of homotopy classification of classifying topological
-insulators are done by the considering the \textit{extension problem}, i.e.
-different ways to extend from a Clifford containing only symmetry operators, to
-a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
-in $0$-dimension, the empty space is nothing, hence
-$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
-Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
-classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
-mentioned earlier, hence the extension problem is from
-$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
-representations form some mathematical structure called \textit{classifying
-space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
-operators are maps starting from $T^0=S^0$. So our classified objects are
-different classes of maps from $S^0\to C_0$, which is mathematically captured by
-the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
-only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
-making it a candidate for generators of Clifford Algebra. The symmetry condition
-$\{H,S\}=0$ tells us now we have a extension problem of
-$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
-$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
-$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
-trivial topological insulators. The case for real symmetry classes are not too
-complicated and is concisely mentioned in \cite{Morimoto2013}.
-
-However, the method to obtain such classifying spaces are mathematical daunting
-and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
-since they should capture the essence of topological states.
-
-\paragraph{Extension Problem with Dirac Hamiltonian}
-The Dirac Hamiltonian
-\begin{equation}
-    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
-\end{equation}
-has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
-parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
-$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
-$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
-space having the same homotopy type of some classifying space (again!). For
-example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
-term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
-$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
-$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
-extension problem concerns different ways to extend the algebra
-$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
-unitarily non-equivalent mass terms. Detailed examples can be found in section
-III.C.1 of \cite{Chiu2016}.
-
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
-\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
-with extra mass term:
-\begin{equation}
-    \label{eq:H-spemt}
-    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
-    + \sum_{j=1}^D m_j\tilde{\gamma}_j
-\end{equation}
-Here, the parameter $M$ characterized the domain wall between different phases
-of topological insulators. The extra mass term $m_j$ represents a perturbation
-caused by disorder. I argue that we can do our classification in the following
-way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
-a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
-
-One best thing about this classification is that it can be done by considering
-only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
-argument is that, complex gamma matrices are of even dimension (except the
-trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
-\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
-\cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
-different type in the smaller dimension, or add trivial bands. In all cases, the
-triviality of topological insulators can be detected in minimal dimension, since
-adding trivial bands can be ignored (insensitive to addition of trivial bands),
-and the possible different types of matrices are limited.
-
-However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
-topological insulator, we need to increase the matrix dimension to consider
-multiple copies of the Dirac Hamiltonian. If the topological state is stable for
-an arbitrary copies, then this is a $\Z$ topological insulator. If the
-topological state is stable only of an odd number of copies, this is a $\Z_2$
-topological insulator.
-
-Another way to view this way of classification, is to look at the surface
-Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
-see if the surface mode can be gapped, so as to detect the topological
-properties of the bulk.
-
-\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
-\label{sec:Isomorphism}
-As with other classifications, we construct isomorphisms between Dirac matrices
-and Clifford Algebras, after which we are faced with an extension problem. The
-isomorphism is constructed now.
-\subsubsection{Symmetry Constraint}
-\label{sec:Symmetry Constraint}
-The Hamiltonian with extra mass term is
-\begin{equation}
-    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
-    + \sum_{i=1}^{d} k_i \gamma_i
-\end{equation}
-The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
-conditions on the gamma matrices:
-\begin{subequations}
-    \label{eq:sym-spemt}
-\begin{align}
-    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
-    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
-    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
-\end{align}
-\end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
-Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
-examples in action.
-
-\subsubsection{Examples of Constructing Isomorphism}
-\label{sec:iso-Examples}
-For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
-    \label{tab:generator-AI}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
-$J_3=iT\tilde{\gamma}_0$, we could verify that all
-$\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
-Table~\ref{tab:map-sym-cl}.
-
-Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
-\begin{equation}
-    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
-\end{equation}
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
-    \label{tab:generator-AII}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
-verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
-Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
-$K_i^2=-1$, $(K'_1)^2=1$. The following map
-\begin{equation}
-    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
-\end{equation}
-has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
-\begin{table}[htpb]
-    \centering
-    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
-    \label{tab:map-cl13-2-cl04}
-    $ \begin{tabu}{ c | *4{c} }
-        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
-        \hline
-        J_1    & -1      & \{\}    & \{\}    & \{\} \\
-        J_2    & ~       & -1      & \{\}    & \{\} \\
-        J_3    & ~       & ~       & -1      & \{\} \\
-        J_4    & ~       & ~       & ~       & -1
-    \end{tabu} $
-
-    where $\{\}$ means anticommute.
-\end{table}
-Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
-consistent with $G_{\mathrm{AII}} \cong
-\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.
-
-\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
-\label{sec:Complex Classes-iso}
-The general steps for constructing the isomorphism is presented here. First, we
-need to treat the situation of complex classes and real classes
-differently. The complex classes are isomorphic to complex Clifford Algebras,
-while the real classes are isomorphic to real Clifford Algebras. The reason for
-this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
-multiplication of complex matrices. Second, complex matrices come with a nature
-definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
-\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
-    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
-we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
-Algebras when dealing with real classes (which is the reason why they are named
-real classes).
-
-For complex classes, let $G_\#$ be the group generated by elements
-$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
-class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
-such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
-Clifford Algebra:
-\begin{align}
-    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
-    \mathrm{C\ell}_{d+D+1}(\C) \\
-    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
-    \cong  \mathrm{C\ell}_{d+D+2}(\C)
-\end{align}
-
-\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
-\label{sec:Real Classes-iso}
-
-For real classes, we need to include $i$, and symmetry operators $T,C$ in our
-group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
-
-We first note that, given a real vector space $V$, we can complexify a real space in
-two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
-which does not suit our purpose. The second is to find an almost complex
-structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
-$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
-way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
-$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
-operators on a real vector space naturally.
-
-Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
-where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
-squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
-naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.
-
-Then we discuss some tips that will useful for later calculation.
-\paragraph{Tips}
-\begin{enumerate}
-    \item Since all generator anticommute, all matrices either commute or
-        anticommute. So the Algebra is pretty simple.
-    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
-        or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
-    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
-        BA$. However, if $A$ and $B$ has something in common, then the above
-        condition breaks. This is like adding an "impurity" in it to change the
-        commutation/anticommutation relations.
-    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
-        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
-        candidates for symmetry operator are only a small finite set.
-        \label{enum:tips-4}
-\end{enumerate}
-
-\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
-construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
-in real vector space, they commute with $J_1=J$. Then, each gamma matrices
-should have an even number of Clifford Algebra generators other than $J_1$
-itself. Similarly, antiunitary symmetry operators should have an odd number of
-Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
-some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
-take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
-\ref{eq:sym-spemt}, and they give us the inspiration to set:
-\begin{equation}
-    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
-    \sum_{i=1}^d k_i J_2\tilde{J}_i
-\end{equation}
-Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
-$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
-And within this algebra, only $J_2$ is a possible candidate for symmetry
-operators, which satisfy equations~\ref{eq:sym-spemt} (use
-tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
-time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
-class $\mathrm{AII}$. Therefore, the map:
-\begin{align}
-    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
-    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
-    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
-\end{align}
-is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
-$\mathrm{AII}$. The inverse map can be found easily. We first solve some
-formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
-\begin{equation}
-    a+bi \to a \begin{pmatrix}
-        1 & \\ & 1
-    \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
-    \end{pmatrix} = a\id + b J
-\end{equation}
-Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
-real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
-$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
-\begin{equation}
-    \{\Gamma_T,\Gamma_C\} = 0
-\end{equation}
-
-Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
-\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
-Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
-\begin{align}
-    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
-    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
-    \Gamma_T &\to J_2 \nonumber\\
-    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
-    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
-\end{align}
-is the desired inverse map.
-
-\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
-more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
-Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
-The rest is exactly the same as in class $\mathrm{AII}$.
-
-All other classes can be treated similarly, so we do not repeat the calculation
-and only list the result in Table~\ref{tab:map-sym-cl}.
-\begin{table}[htpb]
-    \centering
-    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
-    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
-    Algebra. Also, only one direction of mapping is shown. The inverse map can
-    be easily constructed accordingly. The complex class are also added for
-    convenience.}
-    \label{tab:map-sym-cl}
-    \begin{tabular}{c | c c c | l | c }
-        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
-        \hline 
-        D & $0$ & $+$ & $0$ & 
-        $\tilde{J}_1\to\Gamma_C$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
-        DIII & $-$ & $+$ & $1$ & 
-        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
-        AII & $-$ & $0$ & $0$ & 
-        $J_2\to \Gamma_T$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
-        CII & $-$ & $-$ & $1$ & 
-        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
-        C & $0$ & $-$ & $0$ & 
-        $J_2\to \Gamma_C$, 
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
-        CI & $+$ & $-$ & $1$ & 
-        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
-        AI & $+$ & $0$ & $0$ & 
-        $\tilde{J}_1\to \Gamma_T$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
-        BDI & $+$ & $+$ & $1$ & 
-        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
-        \hline
-        A & $0$ & $0$ & $0$ & 
-        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
-        AIII & $0$ & $0$ & $1$ & 
-        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\subsection{Classification in 1-dimension}
-\label{sec:Classification in 1-dimension}
-Classification of $1$ dimension is the simplest, since the minimal matrix
-dimension will mostly be $2$, which means we can use the familiar Pauli matrices
-directly.
-
-\paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.
-
-\paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
-topologically non-trivial. Now we consider the state with arbitrary copies of it.
-\begin{equation}
-    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
-    S=\sigma_z\otimes\id_n
-\end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
-
-The above are for complex classes. For real classes, we have to be careful,
-since one generator $J_1$ is taken up by $i$.
-
-\paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
-$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
-\end{equation}
-with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
-We let:
-\begin{equation}
-    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
-SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
-$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
-the remaining choice are acceptable, considering $T$ and $C$.}. Consider
-arbitrary copies of it:
-\begin{equation}
-    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
-    k_x\sigma_y\otimes\id_2)\otimes\id_n
-\end{equation}
-with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
-$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
-SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
-Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
-with $C$.}. Therefore, this is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
-of it:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
-\end{equation}
-with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
-$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
-$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
-complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{D}$} We let:
-\begin{equation}
-    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
-it:
-\begin{equation}
-    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
-Hence, this is a $\Z_2$ topological insulator.
-
-To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
-But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
-\paragraph{Class $\mathrm{DIII}$} We let:
-\begin{equation}
-    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
-form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
-this does not commute with $T$. Hence, there is no SPEMT. Now consider two
-copies of it:
-\begin{equation}
-    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
-this is a $\Z_2$ topological insulator.
-
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
-\begin{table}[htpb]
-    \centering
-    \caption{Topological Insulators in $d=1$}
-    \label{tab:ti-d=1}
-    \begin{tabular}{c | c c c | c }
-        Class($\#$) & T & C & S & $d=1$ \\
-        \hline 
-        A & $0$ & $0$ & $0$ & $0$ \\
-        AIII & $0$ & $0$ & $1$ & $\Z$ \\
-        \hline
-        D & $0$ & $+$ & $0$ & $\Z_2$ \\
-        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
-        AII & $-$ & $0$ & $0$ & $0$ \\
-        CII & $-$ & $-$ & $1$ & $\Z$ \\
-        C & $0$ & $-$ & $0$ & $0$ \\
-        CI & $+$ & $-$ & $1$ & $0$ \\
-        AI & $+$ & $0$ & $0$ & $0$ \\
-        BDI & $+$ & $+$ & $1$ & $\Z$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
-\subsection{Classification in Arbitrary Dimension}
-\label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
-generalized to classification in arbitrary dimensions. In $K$-theoretic
-classification, the extension problem is not affected when tensored with some
-other algebras. Specifically, for complex classes, the extension problem of
-$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
-III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
-
-Now, let us write $\sim$ to represent the equivalence between two extension
-problems.  The Complex Clifford Algebra has a periodicity of $2$:
-\begin{equation}
-    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
-    \mathrm{C\ell}_{2}(\C)
-\end{equation}
-The Real Clifford Algebra has a periodicity of $8$:
-\begin{equation}
-    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
-\end{equation}
-This two relation means, the extension problem will be the same with respect to
-a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
-classes. Hence the classification of topological insulators need only be done
-with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
-symmetry classes, i.e.
-\begin{subequations}
-    \label{eq:cli-periodic}
-\begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
-\end{align}
-\end{subequations}
-Another useful property is:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
-\end{align}
-This property tells us that Clifford Algebra basically depends only on the
-difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
-example, we have (let $n$ be an arbitrary integer):
-$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
-\begin{align}
-    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
-    \nonumber\\
-    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
-\end{align}
-and
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
-    \nonumber\\
-    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
-    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
-\end{align}
-Now we tries to connect the two chains together. We note further that the
-Clifford Algebra has the following properties:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
-    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
-\end{align}
-Then:
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
-    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
-    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
-    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
-\end{align}
-Therefore,
-$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
-connecting the two chains. If we compare this carefully with
-Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
-prove the dimension-shift feature of classification:
-\begin{align}
-    \label{eq:cli-Chain1}
-    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
-    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
-    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
-    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
-\end{align}
-We need one more property:
-\begin{equation}
-    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
-    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
-\end{equation}
-Then
-\begin{equation}
-    \label{eq:cli-Chain2}
-    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
-\end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|c|cccccccc|ccc|}
-\hline
-\multicolumn{12}{|c|}{
-The original classification table} \\ \hline
-   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
-\hline\hline
-  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
-  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline
-
-  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
-  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
-  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
-  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
-  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
-  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
-  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
-  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
-   \\
-\hline
-\end{tabular}
-\caption{The original classification table of topological insulators and
-superconductors}
-\label{tab:master-table2}
-\end{center}
-\end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
-
-\bibliography{../../library}{}
-\bibliographystyle{alphaurl}
-% \begin{thebibliography}{1}
-% 	\bibitem{book} 
-% \end{thebibliography}
-\printnomenclature
-
-\end{document}

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-3.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-% My own physics package
-% The following line load the package xparse with additional option to
-% prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
-
-\makenomenclature % For an index of symbols.
-
-\title{Notes about the Minimal Dimensional Method to Classify
-Topological Phases (preliminary)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-    The abstract is left blank due of unforeseeable changes that may happen to
-    this document.
-}
-\tableofcontents
-
-\section{Outline}
-\label{sec:Outline}
-
-The classification of topological insulators in non-interacting system is in
-effect a classification of $N\times N$ Hamiltonian matrix. %sym
-The simple case considered here
-is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
-symmetries. Specifically, when we module out any unitary symmetries of the
-Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
-we only classify topological insulators based on how our Hamiltonian matrix
-responses to these anti-unitary symmetries.
-
-There are two classical approaches towards this classification. The first
-\cite{Schnyder2008} is to examine the existence of Anderson delocalization at
-the boundary of the insulator. The existence of robust surface conducting state
-is the signature of topological insulators. When some random impurity potentials
-could be present in these surfaces, the Anderson localization is the obstruction
-that surface conducting states must overcome. This approach uses the Nonlinear
-Sigma Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
-when can a localization-breaking term can be added to NL$\sigma$Ms.
-
-The second approach\cite{Kitaev2009a} is to use see the classification as an
-extension problem of Clifford Algebras. The anti-unitary symmetries already
-possess some behavior similar to generators of Clifford Algebras. And sometimes
-Hamiltonians could be regarded as yet another generator of Clifford
-Algebra\cite{Morimoto2013}. The $K$-theory approach is to put the symmetries in
-the Clifford Algebra first, and consider adding the Hamiltonian that preserve
-such symmetries to the Clifford Algebra. So the problem of classification of
-Hamiltonians becomes a problem of extending the Clifford Algebra.
-
-But the key to understand topological insulators, are not necessarily the
-Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes
-theorem, unless inside this manifold there is somewhere where the formula for
-Chern number got "blown up", and it is just this locally "blown up" point
-(caused by the crossing) that is responsible for the nonzero Chern number, and
-for the non-triviality of topological insulators. More generally, we believe
-that there is a bulk-boundary correspondence that the properties of the bulk is
-reflected by the properties in the boundary.
-
-Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
-energy zero level to the crossing point, in only the low energy physics. We
-expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian. Also, the
-traditional discussion of Klein-Gordon equation all tells us to look at Dirac
-Hamiltonian.
-
-Using the Dirac Hamiltonian, it is discovered by Dr. Chiu \cite{Chiu2013a} that
-the classification of topological insulators could be brought done into very
-simple applications of classification and representation theory of Clifford
-Algebras, which have been well studied with excellent resources provided online.
-In his classification, he established a isomorphism from $G_{\text{symmetries 
-class}}$, the algebra generated by symmetry operators and Dirac Hamiltonians, to
-some Clifford Algebras. Consequently, the Hamiltonian and symmetry operators,
-all become some specific representations of their corresponding Clifford
-Algebras. Also, it will be argued later that the minimal matrix dimension of
-such representation, i.e. the minimal dimension of the Dirac Hamiltonian, can
-tell the specific type of this topological insulator. Therefore, as a whole all
-the classification work is reduced to the consideration of minimal matrix
-dimension of the representation of Clifford Algebra, in different spatial
-dimension.
-
-This work may be considered as a note to Chiu's dissertation\cite{Chiu2013a}.
-However, I do not guarantee that my interpretation is the same as his as I have
-modified and amended some parts to make the work more, in my opinion, congruous
-and systematic.
-
-\paragraph{Structure of this work} This work are divided into several parts.
-\begin{enumerate}
-    \item \textbf{Ten-fold Way} Introduces the result of Ten-fold way: why we
-        care only about anti-unitary symmetries, why there are ten different
-        classes.
-    \item \textbf{Classification by Dirac Mass Hamiltonians} gives comprehensive
-        account of how the Minimal Dirac Hamiltonian approach works, and how the
-        ten-fold way is derived in this approach.
-    \item \textbf{Looking Further} outlines the possible direction in classification
-        under unitary symmetries, and some other results.
-\end{enumerate}
-
-\section{Ten-fold Way}
-
-We begin our discussion with a background before this classification.  The
-classification of topological phases with different non-unitary symmetries in
-non-interacting picture, are in essence, the classification of $N\times N$
-matrices by its response to three discrete symmetries: time reversal symmetry
-($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
-symmetry ($S$). As for those unitary symmetries, one can in principle, block
-diagonalize the Hamiltonian
-$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
-$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
-applied to those blocks and still holds.
-
-It will be find that, those $T,C$ are the only two meaningful non-unitary
-symmetries of the Single-particle system, and there are in total 10 different
-ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
-care about these three symmetries $T,C,$ and $S$.
-
-\subsection{The symmetries of Single-particle Hamiltonian}
-\label{sec:The symmetries of Single-particle Hamiltonian}
-
-According to Wigner's theorem, symmetries of physical system can either be
-unitary represented, or anti-unitarily represented. Here we show that in the
-case of anti-unitary symmetries, there are only 2 different kinds of them that a
-Single-particle Hamiltonian in first-quantized space can have. Actually, there
-can be more anti-unitary symmetries than this. But under reasonable assumptions,
-we can limit our discussion in only this two types.
-
-The Single-particle Hamiltonian acting on Fock space is
-\begin{equation}
-    \label{eq:H-2nd}
-    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
-\end{equation}
-where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
-are creation and annihilation operators acting on Fock space.
-
-Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
-to stress that it acts on Second-quantized Fock space.  A symmetry of the
-Hamiltonian, represented as an operator $\hat{U}$, must have:
-\begin{equation}
-    \label{eq:sym-in-2nd-1}
-    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
-\end{equation}
-
-We expect $\hat{U}$ to change the creation/annihilation operators in two different
-ways. First, it may only permute the creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-in-2nd-permute}
-\begin{align}
-    \label{eq:sym-in-2nd-permute-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
-    \label{eq:sym-in-2nd-permute-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi^\dagger_B u_{AB}
-\end{align}
-\end{subequations}
-Where $u$ is some matrix implementing the permutation.
-Or, it may interchange the role of creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-cc}
-\begin{align}
-    \label{eq:sym-cc-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
-    \label{eq:sym-cc-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi_B u^*_{BA}
-\end{align}
-\end{subequations}
-Where $u^*$ is some other matrix implementing the interchange. We write complex
-conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
-interchange), to conserve the anticommutation relation between
-$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
-should be a unitary matrix.
-
-Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
-conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
-symmetry, to be explained below.
-
-\paragraph{Case 1: Unitary Symmetry}
-
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives
-\begin{equation}
-    u H u^{-1} = H
-\end{equation}
-Therefore, in this case the symmetry is unitarily realized in First-quantized
-Hamiltonian $H_{AB}$.
-
-\paragraph{Case 2: Anti-unitary T Symmetry}
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
-$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
-\begin{equation}
-    u H^* u^\dagger = H
-\end{equation}
-Or:
-\begin{equation}
-    uK H u^t K = uK H (uK)^{-1} = H
-\end{equation}
-where $K$ is complex conjugation. This symmetry is called Time-reversal
-symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
-operator $T= uK$.
-
-\paragraph{Case 3: Anti-unitary C Symmetry}
-Assume the symmetry just interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\footnote{
-Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
-\id$ on 1st-quantized single-particle Hilbert space.
-}
-\begin{equation}
-    \label{eq:sym-C-cond}
-    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-
-Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
-in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
-simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
-\begin{equation}
-    u H^* u^\dagger = uK H (uK)^{-1} = -H
-\end{equation}
-This type of symmetry is called charge-conjugation symmetry. It is
-also called particle-hole symmetry in condensed matter physics. It is realized
-as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.
-
-\paragraph{Case 4: Unitary S Symmetry}
-Assume the symmetry now interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\begin{equation}
-    \label{eq:sym-S-cond}
-    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-and since $N>>2$, we have $\tr(H)=0$. Then
-\begin{equation}
-    u H u^\dagger = -H
-\end{equation}
-This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
-unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
-of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
-easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
-defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
-property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
-of Hamiltonian under $S$. But there is one exception. When the
-Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
-whole.
-
-\paragraph{Squaring of $T,C,S$} 
-Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
-hence it is only a phase as they are unitary.
-This can be viewed from two perspectives. First, we expect the system, after
-applying twice of symmetry operation $T/C$, should come back to the same state, except
-a possible phase difference. Second, $T^2/C^2$ commutes with all
-$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
-of unitary symmetries (to be explained later), therefore by Schur's lemma, they
-must be proportional to a constant, which is a phase.
-
-It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
-then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
-$e^{i\delta}=\pm1$.
-
-But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
-$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
-operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
-phase for $S^2$.\footnote{This is a bit troublesome. First we denote
-$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
-$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
-$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
-\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
-Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
-$S^2=-\varepsilon_C\varepsilon_T$.}
-
-\paragraph{Why Ten Classes} For the three unitary symmetries under
-consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
-$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
-undetermined (depending on the phase choice\footnote{To be explained later.} we
-give for $T$ and $C$). Therefore, there are in total 10 different possible ways
-that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
-to symbolize that the system does not follow $T$($C$) symmetry. Then
-$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
-$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
-different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in Figure.1
-in\cite{Ludwig2015}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$,
-etc.), and their properties in different spatial dimensions respect a periodic
-structure. For the class $A$ and class $AII$, they are named complex classes and
-respect a $2$-fold period. For the other eight classes are named real classes
-and respect a $8$-fold period, which is why we only listed the first $0\to 7$
-spatial dimensions in Table~\ref{tab:master-table2}.
-
-\subsection{Dealing with Unitary Symmetries}
-\label{sec:Dealing with Unitary Symmetries}
-
-As mentioned, we could module out those unitary symmetries. This statement is
-made precise by the following theorem about unitary symmetries of the Hamiltonian.
-\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
-This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
-$\mathcal{V}_\lambda$ associated with the irrep (irreducible
-representations, labeled by $\lambda$) of $G_0$.
-\begin{equation}
-    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
-\end{equation}
-where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
-Denote the dimension of each irrep as $d_\lambda$.
-
-In each vector space $\mathcal{V}_\lambda$, one can choose a
-(orthogonal) basis of the form:
-\begin{equation}
-    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
-\end{equation}
-where
-\begin{itemize}
-    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
-        $k=1,\cdots,d_\lambda$,
-    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
-        $\alpha=1,\cdots,m_\lambda$.
-\end{itemize}
-\end{thm}
-Therefore, with all unitary symmetries ignored, we are classifying how
-Hamiltonian will be like when it respects, in 10 different ways, the
-combinations of $T,C,S$ symmetries.
-
-\paragraph{Differently Realized Anti-unitary Symmetries}
-It should be noted that there is still a freedom of unitary matrix that
-implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
-different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
-obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
-easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
-Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
-symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
-described in the theorem above, we only have one time-reversal symmetry. Similar
-analysis could be done for the $C$ symmetry as well.
-
-\paragraph{Translational Symmetry}
-
-Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
-
-With translational symmetry added, the classification can be made the will yield
-the same result.\footnote{This is still a mystery to me which this is true. The
-    exact reason is related to some isomorphism between certain homotopy groups.
-    Interested reader could see Ludwig's lecture
-\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{here}
-for a clue.}
-
-The Hamiltonian in $k$-space that preserve these three discrete symmetries
-should follow\footnote{It is easy to anticipate the change $k\to -k$ for
-    anti-unitary symmetries, since they change the phase factor when one Fourier
-transform the Hamiltonian.}:
-\begin{subequations}
-\begin{align}
-    \label{eq:T-sym-Hk}
-    TH(k)T^{-1} &= H(-k) \\
-    \label{eq:C-sym-Hk}
-    CH(k)C^{-1} &= -H(-k) \\
-    \label{eq:S-sym-Hk}
-    SH(k)S^{-1} &= -S(k)
-\end{align}
-\end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-The Tenfold Way, is originally the ten different ways to write down a
-Hamiltonian when there are ten different combinations of symmetries that the 
-system respect.
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators, if I have time}
-
 \section{Classification by Dirac Mass Terms}
@@
 isomorphism is constructed now.
+
+A bit of notation note. We use $\mathrm{C\ell}_{p,q}(\R)$ to denote a Clifford
+Algebra over $\R$ with $p$ for $+$ signature and $q$ for $-$ signature. We use
+$\mathrm{C\ell}_{n}(\C)$ to denote a Clifford Algebra over $\C$. We use
+$\mathcal{M}(n,K)$ to denote the algebra of $n\times n$ matrices over $K=\C$ or
+$K=\R$. We use $\id_n$ to denote the $n\times n$ identify matrix.
+
 \subsubsection{Symmetry Constraint}
@@
 which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
+isomorphism in class $\mathrm{AII}$.\footnote{For reader unfamiliar with the
+complexfication of real vector space, and the realification of complex vector
+space, I recommend a quick reading of section 12 \cite{suetin1989linear}.}
 
@@
 formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
+identifying $i$ with $J=-i\sigma_y$ and $1$ with $\id$, the identity matrix:
 \begin{equation}
@@
     \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
+         & -1 \\ 1 & 
     \end{pmatrix} = a\id + b J
@@
 $\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
+as $A+iB = (a_{mn})+i(b_{mn}) \to \id_2\otimes(a_{mn})+J\otimes(b_{mn})$. On
+important matrix is the matrix $J_1$ that we identify $i$ as:
+\begin{equation}
+    J_1 \equiv -i\sigma_y \otimes \id_{n\times n}
+\end{equation}
+The complex conjugate $K$ is then a matrix anticommute with $J_1$.  Then $T\to
+\Gamma_T$, $C\to \Gamma_C$ for some real matrices anticommute with $i\to J_1$.
+We also note that, as mentioned earlier, we make a phase choice of $T$ and $C$
+such that:
 \begin{equation}
@@
 \paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
+$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. We have for example:
 \begin{equation}
@@
 \paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
+$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. We have
+for example:
 \begin{equation}
@@
 \paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
+$\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{1,4}(\R)$.
+Explicitly, we could let
 \begin{equation}
@@
 \paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
+$\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{2,3}(\R)$. Explicitly, we
 could let
@@
 \paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
+$\mathrm{C\ell}_{2,3}(\R)$, to $\mathrm{C\ell}_{3,3}(\R)$. Explicitly, we
 could let
@@
 \paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
+$\mathrm{C\ell}_{2,2}(\R)$ to $\mathrm{C\ell}_{3,2}(\R)$. Explicitly, we could let
 \begin{equation}
@@
 \paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
+$\mathrm{C\ell}_{1,4}(\R)$ to $\mathrm{C\ell}_{1,5}(\R)$.
 We let:
@@
 \paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
+$\mathrm{C\ell}_{3,2}(\R)$ to $\mathrm{C\ell}_{4,2}(\R)$. We let:
 \begin{equation}
@@
 and there are only 1 or 2 nontrivial (dimension $>1$) inequivalent irreducible
-representations of Clifford Algebras (see \ref{sec:Various Properties for
+representations of Clifford Algebras (see Appendix~\ref{sec:Various Properties for
 Clifford Algebras}).  The dimension of the representation of relevant Clifford
@@
 
-\paragraph{$\mathbf{n\to n}$ or $\mathbf{n\to n_2}$} Basically, this means that in the same
-dimension we could always have a SPEMT present. So there will never be stable
-edge states.
-
-\paragraph{$\mathbf{n\to 2n}$} This means that, although in the same dimension we have
-always stable edge mode. When we take two copies of the Hamiltonian, i.e., when
-there are two edge modes. There will a new gamma matrix in the doubled-dimension
-acting as a SPEMT to gap out the system. Hence in general, an odd copies of
-the edge mode is stable whereas an even copies of the edge mode is not. Hence
-this is a $\Z_2$ topological insulator.
-
-\paragraph{$\mathbf{n_2\to 2n}$} This is similar to the above $\Z_2$ case. However, since
-we have two inequivalent representations in a single edge mode, we could
-the doubled system could have came from different representations, which could
-not be gapped out by the extra SPEMT in doubled-dimension (otherwise we would
-have two inequivalent representations in the doubled-dimension). Hence, this is
-a $\Z$ topological insulator.
-
-In this way we confirmed the classification in Table~\ref{tab:ti-d=1}.
+\begin{enumerate}
+    \item $\mathbf{n\to n}$ or $\mathbf{n\to n_2}$ Basically, this means that in
+        the same dimension we could always have a SPEMT present. So there will
+        never be stable edge states.
+    \item 
+    $\mathbf{n\to 2n}$ or $\mathbf{n_2\to 2n}$ In this case, a single copy of
+    Hamiltonian is stable against perturbation. Therefore, we consider two copies of
+    the Hamiltonian and see if the double-size Hamiltonian can be gapped by
+    perturbation. If one denote the one irreducible representation in dimension $n$
+    by $\Gamma$, then we are most importantly faced with two types of double-size
+    Hamiltonian:
+    \begin{equation}
+        H_\mathrm{doubled,1} = (M\tilde{\Gamma}_0 + \sum_i k_i\Gamma_i
+        )\otimes\id_{2\times 2}
+    \end{equation}
+    or
+    \begin{equation}
+        H_\mathrm{doubled,2} = \begin{pmatrix}
+            M\tilde{\Gamma}_0 + \sum_i k_i\Gamma_i & 0 \\
+            0 & \pm M\tilde{\Gamma}_0 + \sum_i \pm k_i\Gamma_i \\
+        \end{pmatrix}
+    \end{equation}
+    Where the sign $\pm$ for $H_\mathrm{doubled,2}$ is such that
+    $H_\mathrm{doubled,2}\neq H_\mathrm{doubled,1}$.  The first Hamiltonian is
+    called two equivalent copies of the original Hamiltonian, whereas the second one
+    is called two inequivalent copies of the original Hamiltonian.\footnote{The
+    exact reason for "equivalent" and "inequivalent" would be found in
+    representation theory or Clifford Algebras, but which is not important for
+    our discussion here.} For the second copy, we could always find a SPEMT to gap
+    the system. For example, for
+    \begin{equation}
+        H_\mathrm{doubled,2} = \begin{pmatrix}
+            M\tilde{\Gamma}_0 + \sum_i k_i\Gamma_i & 0 \\
+            0 & - M\tilde{\Gamma}_0 + \sum_i k_i\Gamma_i \\
+        \end{pmatrix} =
+        M\tilde{\Gamma}_0\otimes\sigma_z + 
+            (\sum_i k_i\Gamma_i)\otimes\id_{2\times 2}
+    \end{equation}
+    it can be gapped by a SPEMT such as $\Gamma_1\otimes \sigma_x$.
+
+    For the first type, the situation is different and it distinguishes the $\Z$
+    and $\Z_2$ topological insulator. We first not that, a SPEMT in this case
+    must be of the form $\Gamma\otimes A_{2\times 2}$, where $\Gamma$
+    anticommutes with $\Gamma_i$ and $\tilde{\Gamma}_0$, $A$ is any $2\times 2$
+    matrix.
+    \begin{enumerate}
+        \item $\mathbf{n\to 2n}$: In this case, there will be a SPEMT to gap
+            the doubled Hamiltonian. So this is a $\Z_2$ topological insulator.
+            To be more specific, assume that we have the extension problem of
+            $\mathrm{C\ell}_{p,q}(\R)\to\mathrm{C\ell}_{p,q+1}(\R)$, where
+            $\mathrm{dim}(\mathrm{C\ell}_{p,q}(\R))=n$,
+            $\mathrm{dim}(\mathrm{C\ell}_{p,q+1}(\R))=2n$. It can be checked in
+            Table~\ref{tab:mat-dim-allClass-1d} that
+            $\mathrm{dim}(\mathrm{C\ell}_{p+1,q}(\R))=n_2$, i.e. an extra
+            $\Gamma_{p+1}$ is present in the same dimension. This extra term
+            form a SPEMT in the doubled Hamiltonian as $\Gamma_{p+1}\otimes
+            i\sigma_y$.
+
+            Similarly, if we have $\mathrm{C\ell}_{p,q}(\R)\to
+            \mathrm{C\ell}_{p+1,q}(\R)$, an extra term $\Gamma_{q+1}$ from
+            $\mathrm{C\ell}_{p,q+1}(\R)$ is present in the same dimension, and
+            it forms a SPEMT in the doubled Hamiltonian as $\Gamma_{q+1}\otimes
+            i\sigma_y$.
+        \item $\mathbf{n_2\to 2n}$: In this case, unfortunately no SPEMT can be
+            found from either $\mathrm{C\ell}_{p+1,q}(\R)$ or
+            $\mathrm{C\ell}_{p,q+1}(\R)$, as can be checked in
+            Table~\ref{tab:mat-dim-allClass-1d} that they all doubled the
+            dimension.
+    \end{enumerate}
+\end{enumerate}
+
+In this way we confirmed the classification in Table~\ref{tab:ti-d=1}. And we
+note that, as long as $p-q \text{mod 8}$ is fixed, all the above discussion will
+be the same. This come as a property of the representation of Clifford Algebras
+(see Appendix~\ref{sec:Various Properties for Clifford Algebras} for details).
+Also, if one is interested in how those model system mentioned before can be
+reflected in the representation of Clifford Algebras, one could see
+Appendix~\ref{sec:a case study} for one example.
 
@@
     \caption{Matrix dimensions related to the extension problem for different
-    classes in $d=1$. Note that a subscript $2$ as in $2_2$, means that there
-    are two inequivalent representations in the same matrix dimension.}
+        classes in $d=1$. Note that a subscript $2$ as in $2_2$, means that
+        there are two inequivalent representations in the same matrix dimension.
+        Note also that since the complexification of a real matrix reduce the
+        dimension by $\frac{1}{2}$, we write only half of the dimension as shown
+    in Appendix~\ref{sec:Various Properties for Clifford Algebras}. }
     \label{tab:mat-dim-allClass-1d}
@@
         CII & $\mathrm{C\ell}_{1,4}(\R)\to\mathrm{C\ell}_{1,5}(\R)$ & $4_2\to 8$
+        with $\mathrm{C\ell}_{2,4}(\R)\sim 8$.
         & $\Z$
@@
         BDI & $\mathrm{C\ell}_{3,2}(\R)\to\mathrm{C\ell}_{4,2}(\R)$ & $2_2\to 4$ 
+        with $\mathrm{C\ell}_{3,3}(\R)\sim 4$.
         & $\Z$
@@
         D & $\mathrm{C\ell}_{2,2}(\R)\to\mathrm{C\ell}_{2,3}(\R)$ & $2\to 4$
+        with $\mathrm{C\ell}_{3,2}(\R)\sim2_2$.
         & $\Z_2$
@@
         DIII & $\mathrm{C\ell}_{2,3}(\R)\to\mathrm{C\ell}_{2,4}(\R)$ & $4\to 8$ 
+        with $\mathrm{C\ell}_{3,3}(\R)\sim 4$.
         & $\Z_2$
@@
 \end{table}
-
-\section{Looking Further}
-\label{sec:Looking Further}
-There has be great deal of progress made in classification of topological
-insulator and superconductors. We first comment that our discussion could be
-easily generalized to some topological superconductors because they naturally
-admits a matrix like Hamiltonian using Nambu spinors.
-
-Also, our discussion falls short in two respects. First, it cannot distinguish
-between $\Z$ and $2\Z$ cases. Secondly, we do not give explicit formulae for
-calculating topological invariants in different cases. The former problem can be
-addressed in Ludwig's \cite{Schnyder2008}, while the latter requires
-considerable work, and provides different topological invariant in different
-cases (see sec. III.B of \cite{Chiu2016}).
-
-There has been progress made both in incorporating defects into classification,
-as well as incorporating unitary symmetries into the classification. The
-defect's classification has been incorporated beautifully into the same table of
-Tenfold Way. On the other hand, introduction of unitary symmetries gives a more
-fruitful result. For example, introduction of crystal symmetries gives a new
-class of topological insulators, dubbed topological crystalline
-insulators.\cite{Ando2015} the case of reflection symmetry, some new topological
-invariants denoted as $M\Z$, called mirror topological invariants, are needed to
-classify topological matters\cite{Chiu2013}.
-
-Lastly, the discussion of topological states in interaction picture extends to
-the case of symmetry-protected phases (SPTs), of which I am not familiar with.
-For all these new concepts, the review \cite{Chiu2016} is an excellent source of
-information.
-
-\section{Various Properties for Clifford Algebras}
-\label{sec:Various Properties for Clifford Algebras}
-We have used various properties of Clifford Algebras from various sources. Here
-I summarized those properties for the convenience of readers.
-
-\paragraph{Isomorphism Relations}
-The best source of isomorphism between Clifford Algebras is actually the
-Wikipedia page about \textit{Classifications of Clifford Algebras}. For a more
-authoritative account, I am using the book \cite{VazJayme2016}. The results
-used in this document are to be found in chapter 4 of that book.
-
-\paragraph{Representation Theory on Complex Clifford Algebras}
-This paper \cite{West1998} has a good discussion on the irreducible
-representations of complex Clifford Algebras, in p.5, p.12. They can be
-summarized as:
-\begin{thm}
-    Consider $\mathrm{C\ell}_{N}(\C)$. For both $N = 2n$ and $N = 2n + 1$, the
-    dimension d of the irreducible representation is uniquely given by
-    \begin{equation}
-        d = 2^n \text{($N=2n$ or $N=2n+1$)}
-    \end{equation}
-    Moreover, for $N = 2n$, the irreducible space is unique, while for $N = 2n +
-    1$, we have two inequivalent irreducible representations with the same
-    dimension $d$.
-\end{thm}
-
-\paragraph{Representation Theory on Real Clifford Algebra}
-The two papers \cite{Okubo1991a}\cite{Okubo1991} are great in this respect.
-Their result used in this document could be summarized as:
-\begin{thm}
-    Consider $\mathrm{C\ell}_{p,q}(\R)$. For $N=2n$, we have:
-    \begin{align}
-        d= \begin{cases}
-              2^n_1, & \text{for } p-q=0\text{ or }2\text{, mod }8 \\
-              2^{n+1}_1, & \text{for } p-q=4\text{ or }6\text{, mod }8 \\
-          \end{cases}
-    \end{align}
-    For $N=2n+1$, we have:
-    \begin{align}
-        d= \begin{cases}
-              2^n_2, & \text{for } p-q=1\text{, mod }8 \\
-              2^{n+1}_1, & \text{for } p-q=3\text{ or }7\text{, mod }8 \\
-              2^{n+1}_2, & \text{for } p-q=5\text{, mod }8 \\
-          \end{cases}
-    \end{align}
-    Where we have used a subscript $\phantom{1}_1$ to denote that there is only
-    one unique irreducible representation, and a subscript $\phantom{1}_2$ to
-    denote that there are two inequivalent irreducible representations.
-\end{thm}
-Below collects a list of dimensions that I have used in the discussion of
-Table~\ref{tab:mat-dim-allClass-1d}:
-\begin{align*}
-    &
-    \mathrm{C\ell}_{1,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{1,3}(\R)\sim 4^2_1,\,
-    \mathrm{C\ell}_{1,4}(\R)\sim 4^2_2,\, \mathrm{C\ell}_{1,5}(\R)\sim 8^2_1,\,
-    \\&
-    \mathrm{C\ell}_{2,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{2,3}(\R)\sim 4^2_1,\,
-    \mathrm{C\ell}_{3,2}(\R)\sim 2^2_2,\, \mathrm{C\ell}_{2,4}(\R)\sim 8^2_1,\,
-    \\&
-    \mathrm{C\ell}_{3,3}(\R)\sim 4^2_1,\, \mathrm{C\ell}_{4,2}(\R)\sim 4^2_1.
-\end{align*}
-
-\section{Online Version}
-This document may be updated online at
-\href{https://github.com/we-taper/Draft/tree/master/Notes%20of%20various%20papers/Chiu%20Minimal%20Dirac%20Hamiltonian%20Method}{here}.
-
-\bibliography{../../library}{}
-\bibliographystyle{alphaurl}
-% \begin{thebibliography}{1}
-% 	\bibitem{book} 
-% \end{thebibliography}
-\printnomenclature
-
-\end{document}

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-4.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\section{Looking Further}
+\label{sec:Looking Further}
+There has be great deal of progress made in classification of topological
+insulator and superconductors. We first comment that our discussion could be
+easily generalized to some topological superconductors because they naturally
+admits a matrix like Hamiltonian using Nambu spinors.
 
-% My own physics package
-% The following line load the package xparse with additional option to
-% prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
+Also, our discussion falls short in two respects. First, it cannot distinguish
+between $\Z$ and $2\Z$ cases. Secondly, we do not give explicit formulae for
+calculating topological invariants in different cases. The former problem can be
+addressed in Ludwig's \cite{Schnyder2008}, while the latter requires
+considerable work, and provides different topological invariant in different
+cases (see sec. III.B of \cite{Chiu2016}).
 
-\makenomenclature % For an index of symbols.
+There has been progress made both in incorporating defects into classification,
+as well as incorporating unitary symmetries into the classification. The
+defect's classification has been incorporated beautifully into the same table of
+Tenfold Way. On the other hand, introduction of unitary symmetries gives a more
+fruitful result. For example, introduction of crystal symmetries gives a new
+class of topological insulators, dubbed topological crystalline
+insulators.\cite{Ando2015} the case of reflection symmetry, some new topological
+invariants denoted as $M\Z$, called mirror topological invariants, are needed to
+classify topological matters\cite{Chiu2013}.
 
-\title{Notes about the Minimal Dimensional Method to Classify
-Topological Phases (preliminary)}
-\date{\today}
-\author{Taper}
+Lastly, the discussion of topological states in interaction picture extends to
+the case of symmetry-protected phases (SPTs), of which I am not familiar with.
+For all these new concepts, the review \cite{Chiu2016} is an excellent source of
+information.
 
-\begin{document}
-
-\maketitle
-\abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
-}
-% TODO: add ref for Clifford Algebra.
-\tableofcontents
-
-\section{Outline}
-\label{sec:Outline}
-
-The classification of topological insulators in non-interacting system is in
-effect a classification of Hamiltonian matrix. The simple case considered here
-is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
-symmetries. Specifically, when we module out any unitary symmetries of the
-Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
-we only classify topological insulators based on how our Hamiltonian matrix
-responses to these anti-unitary symmetries.
-
-There are two classical approaches towards this classification. The first is to
-examine the existence of Anderson delocalization at the boundary of the
-insulator, because the existence of surface conducting state is the signature of
-topological insulators and the Anderson localization is the obstruction that
-\todo{Be more specific about this and check some facts.}
-surface conducting states must overcome. This approach uses the Nonlinear Sigma
-Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
-when can a localization-breaking term can be added to NL$\sigma$Ms.
-
-The second approach is to use homotopy theory to classify classes Hamiltonians under
-continuous deformation, more specifically, under adiabatical change of
-Hamiltonians. This method is most elegant but most mathematical demanding
-approach compared with others, because calculating homotopy groups, and homotopy theories in
-general are notorious hard. Also, one has to use $K$-theory, because of
-something physical is enlarging those distinct classes of Hamiltonian. To be
-more specific.
-
-But the key to understand topological insulators, are not necessarily the
-Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes theorem,
-unless inside this manifold there is somewhere where the formula for Chern
-number got "blown up", and it is just this locally "blown up" point that is
-responsible for the nonzero Chern number, and for the non-triviality of
-topological insulators.
-
-Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
-energy zero level to the crossing point, in only the low energy physics. We
-expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
-
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
-
-\paragraph{Structure of this work} This work are divided into several parts.
-\begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
-\end{enumerate}
-
-\section{Ten-fold Way}
-
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
-matrices by its response to three discrete symmetries: time reversal symmetry
-($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
-symmetry ($S$). As for those unitary symmetries, one can in principle, block
-diagonalize the Hamiltonian
-$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
-$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
-applied to those blocks and still holds.
-
-It will be find that, those $T,C$ are the only two meaningful non-unitary
-symmetries of the Single-particle system, and there are in total 10 different
-ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
-care about these three symmetries $T,C,$ and $S$.
-
-\subsection{The symmetries of Single-particle Hamiltonian}
-\label{sec:The symmetries of Single-particle Hamiltonian}
-
-According to Wigner's theorem, symmetries of physical system can either be
-unitary represented, or anti-unitarily represented. Here we show that in the
-case of anti-unitary symmetries, there are only 2 different kinds of them that a
-Single-particle Hamiltonian in first-quantized space can have. Actually, there
-can be more anti-unitary symmetries than this. But under reasonable assumptions,
-we can limit our discussion in only this two types.
-
-The Single-particle Hamiltonian acting on Fock space is
-\begin{equation}
-    \label{eq:H-2nd}
-    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
-\end{equation}
-where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
-are creation and annihilation operators acting on Fock space.
-
-Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
-to stress that it acts on Second-quantized Fock space.  A symmetry of the
-Hamiltonian, represented as an operator $\hat{U}$, must have:
-\begin{equation}
-    \label{eq:sym-in-2nd-1}
-    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
-\end{equation}
-
-We expect $\hat{U}$ to change the creation/annihilation operators in two different
-ways. First, it may only permute the creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-in-2nd-permute}
-\begin{align}
-    \label{eq:sym-in-2nd-permute-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
-    \label{eq:sym-in-2nd-permute-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi^\dagger_B u_{AB}
-\end{align}
-\end{subequations}
-Where $u$ is some matrix implementing the permutation.
-Or, it may interchange the role of creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-cc}
-\begin{align}
-    \label{eq:sym-cc-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
-    \label{eq:sym-cc-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi_B u^*_{BA}
-\end{align}
-\end{subequations}
-Where $u^*$ is some other matrix implementing the interchange. We write complex
-conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
-interchange), to conserve the anticommutation relation between
-$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
-should be a unitary matrix.
-
-Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
-conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
-symmetry, to be explained below.
-
-\paragraph{Case 1: Unitary Symmetry}
-
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives
-\begin{equation}
-    u H u^{-1} = H
-\end{equation}
-Therefore, in this case the symmetry is unitarily realized in First-quantized
-Hamiltonian $H_{AB}$.
-
-\paragraph{Case 2: Anti-unitary T Symmetry}
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
-$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
-\begin{equation}
-    u H^* u^\dagger = H
-\end{equation}
-Or:
-\begin{equation}
-    uK H u^t K = uK H (uK)^{-1} = H
-\end{equation}
-where $K$ is complex conjugation. This symmetry is called Time-reversal
-symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
-operator $T= uK$.
-
-\paragraph{Case 3: Anti-unitary C Symmetry}
-Assume the symmetry just interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\footnote{
-Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
-\id$ on 1st-quantized single-particle Hilbert space.
-}
-\begin{equation}
-    \label{eq:sym-C-cond}
-    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-
-Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
-in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
-simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
-\begin{equation}
-    u H^* u^\dagger = uK H (uK)^{-1} = -H
-\end{equation}
-This type of symmetry is called charge-conjugation symmetry. It is
-also called particle-hole symmetry in condensed matter physics. It is realized
-as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.
-
-\paragraph{Case 4: Unitary S Symmetry}
-Assume the symmetry now interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\begin{equation}
-    \label{eq:sym-S-cond}
-    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-and since $N>>2$, we have $\tr(H)=0$. Then
-\begin{equation}
-    u H u^\dagger = -H
-\end{equation}
-This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
-unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
-of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
-easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
-defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
-property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
-of Hamiltonian under $S$. But there is one exception. When the
-Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
-whole.
-
-\paragraph{Squaring of $T,C,S$} 
-Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
-hence it is only a phase as they are unitary.
-This can be viewed from two perspectives. First, we expect the system, after
-applying twice of symmetry operation $T/C$, should come back to the same state, except
-a possible phase difference. Second, $T^2/C^2$ commutes with all
-$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
-of unitary symmetries (to be explained later), therefore by Schur's lemma, they
-must be proportional to a constant, which is a phase.
-
-It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
-then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
-$e^{i\delta}=\pm1$.
-
-But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
-$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
-operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
-phase for $S^2$.\footnote{This is a bit troublesome. First we denote
-$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
-$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
-$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
-\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
-Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
-$S^2=-\varepsilon_C\varepsilon_T$.}
-
-\paragraph{Why Ten Classes} For the three unitary symmetries under
-consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
-$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
-undetermined (depending on the phase choice\footnote{To be explained later.} we
-give for $T$ and $C$). Therefore, there are in total 10 different possible ways
-that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
-to symbolize that the system does not follow $T$($C$) symmetry. Then
-$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
-$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
-different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
-
-\subsection{Dealing with Unitary Symmetries}
-\label{sec:Dealing with Unitary Symmetries}
-
-As mentioned, we could module out those unitary symmetries. This statement is
-made precise by the following theorem about unitary symmetries of the Hamiltonian.
-\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
-This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
-$\mathcal{V}_\lambda$ associated with the irrep (irreducible
-representations, labeled by $\lambda$) of $G_0$.
-\begin{equation}
-    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
-\end{equation}
-where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
-Denote the dimension of each irrep as $d_\lambda$.
-
-In each vector space $\mathcal{V}_\lambda$, one can choose a
-(orthogonal) basis of the form:
-\begin{equation}
-    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
-\end{equation}
-where
-\begin{itemize}
-    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
-        $k=1,\cdots,d_\lambda$,
-    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
-        $\alpha=1,\cdots,m_\lambda$.
-\end{itemize}
-\end{thm}
-Therefore, with all unitary symmetries ignored, we are classifying how
-Hamiltonian will be like when it respects, in 10 different ways, the
-combinations of $T,C,S$ symmetries.
-
-\paragraph{Differently Realized Anti-unitary Symmetries}
-It should be noted that there is still a freedom of unitary matrix that
-implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
-different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
-obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
-easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
-Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
-symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
-described in the theorem above, we only have one time-reversal symmetry. Similar
-analysis could be done for the $C$ symmetry as well.
-
-\paragraph{Translational Symmetry}
-
-Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
-
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
-
-The Hamiltonian in $k$-space that preserve these three discrete symmetries
-should follow\footnote{It is easy to anticipate the change $k\to -k$ for
-    anti-unitary symmetries, since they change the phase factor when one Fourier
-transform the Hamiltonian.}:
-\begin{subequations}
-\begin{align}
-    \label{eq:T-sym-Hk}
-    TH(k)T^{-1} &= H(-k) \\
-    \label{eq:C-sym-Hk}
-    CH(k)C^{-1} &= -H(-k) \\
-    \label{eq:S-sym-Hk}
-    SH(k)S^{-1} &= -S(k)
-\end{align}
-\end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
-
-\section{Classification by Dirac Mass Terms}
-\label{sec:The Minimal Hamiltonian Approach}
-
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
-We first note that different topological phases are distinguished by the closing
-and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
-flatten the energy spectrum to two bands of energy $\pm E$, the transition
-(closing of gap) will happen at some point where locally the energy is of a
-Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
-behavior. Then, a class of topological phases, or more specifically, a class of
-Hamiltonian matrix that shares the same topological invariant, can be
-\textit{represented} by the Dirac Hamiltonian in this class.
-
-\subsection{Crossing Spectrum and Edge Mode}
-\label{sec:Crossing Spectrum and Edge Mode}
-Here we show that the crossing spectrum characteristic of topological insulators
-can be characterized by a Dirac type Hamiltonian, and with this Dirac
-Hamiltonian we could find an Edge mode solution built into it.
-
-\paragraph{Crossing Spectrum and Dirac Hamiltonian}
-In some local region around the crossing point, the energy spectrum should look
-like:
-\begin{equation}
-    E = \pm \sqrt{\vb{k}^2 + M^2}
-\end{equation}
-where $\vb{k}$ is the crystal momentum and $M$ is some constant
-responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
-
-As has been analysed in most Quantum Mechanics textbook\footnote{See for
-    example, p.99 of \cite{Greiner1997}. Although their discussion is in
-dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
-relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
-use is:
-\begin{equation}
-    \label{eq:dirac-H}
-    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
-\end{equation}
-where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
-Clifford Algebra anti-commutation relation:
-\begin{equation}
-    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
-\end{equation}
-
-\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
-phase. First, it has a gapless state. Due to the anti-commutation relation of
-$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
-tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
-we choose not $\gamma_i^2=-1$, which would give non-sensible result
-$H_\text{Dirac}^2= -E^2\id$.}
-that the energies of Dirac Hamiltonian are:
-\begin{equation}
-    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
-\end{equation}
-Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
-gaped to gapless and again to gaped state. This shows that the $M$ is parameter
-controlling the quantum phase transition, and the system with $M<0$ or $M>0$
-possesses two different quantum phase.
-
-In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
-should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
-broken in that direction. Now the eigenvalue equation is:
-\begin{equation}
-    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
-    = E \Phi
-\end{equation}
-
-Past experience teaches us the ansatz (assuming
-$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
-does not blow up the wavefunction):
-\begin{equation}
-    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
-\end{equation}
-which after plugging inside the eigenvalue equation, leads to
-\begin{equation}
-    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
-    = E \phi
-\end{equation}
-After left multiplication of $\gamma_0$, we have:
-\begin{equation}
-    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
-    = E \gamma_0 \phi
-\end{equation}
-Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
-$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
-eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
-$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
-state to be a surface state, so we choose the $-1$ eigenvectors (denoted
-$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
-\begin{equation}
-    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
-\end{equation}
-As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
-have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
-eigenspaces:
-\begin{equation}
-    \label{eq:H-Dirac-surf}
-    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
-\end{equation}
-
-% \section{Collection of Calculation}
-% \label{sec:Collection of Calculation}
-% Here collects the calculations done throughout the whole notes.
-
-\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
-\label{sec:Homotopy to Minimal Dirac}
-
-\paragraph{Spectral Flattening} The classification of topological insulators
-concerns different classes of Hamiltonian that cannot be adiabatically changed
-to each without closing or opening of a gap. Hence, we could in general
-adiabatically change our parameters such that the spectrum of Hamiltonian is
-simplified into two bands of energy $\pm1$. Under this condition, we have
-$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
-for generating Clifford Algebras.
-
-\paragraph{Extension Problem with General Examples}
-The general theme of homotopy classification of classifying topological
-insulators are done by the considering the \textit{extension problem}, i.e.
-different ways to extend from a Clifford containing only symmetry operators, to
-a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
-in $0$-dimension, the empty space is nothing, hence
-$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
-Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
-classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
-mentioned earlier, hence the extension problem is from
-$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
-representations form some mathematical structure called \textit{classifying
-space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
-operators are maps starting from $T^0=S^0$. So our classified objects are
-different classes of maps from $S^0\to C_0$, which is mathematically captured by
-the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
-only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
-making it a candidate for generators of Clifford Algebra. The symmetry condition
-$\{H,S\}=0$ tells us now we have a extension problem of
-$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
-$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
-$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
-trivial topological insulators. The case for real symmetry classes are not too
-complicated and is concisely mentioned in \cite{Morimoto2013}.
-
-However, the method to obtain such classifying spaces are mathematical daunting
-and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
-since they should capture the essence of topological states.
-
-\paragraph{Extension Problem with Dirac Hamiltonian}
-The Dirac Hamiltonian
-\begin{equation}
-    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
-\end{equation}
-has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
-parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
-$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
-$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
-space having the same homotopy type of some classifying space (again!). For
-example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
-term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
-$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
-$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
-extension problem concerns different ways to extend the algebra
-$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
-unitarily non-equivalent mass terms. Detailed examples can be found in section
-III.C.1 of \cite{Chiu2016}.
-
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
-\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
-with extra mass term:
-\begin{equation}
-    \label{eq:H-spemt}
-    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
-    + \sum_{j=1}^D m_j\tilde{\gamma}_j
-\end{equation}
-Here, the parameter $M$ characterized the domain wall between different phases
-of topological insulators. The extra mass term $m_j$ represents a perturbation
-caused by disorder. I argue that we can do our classification in the following
-way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
-a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
-
-One best thing about this classification is that it can be done by considering
-only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
-argument is that, complex gamma matrices are of even dimension (except the
-trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
-\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
-\cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
-different type in the smaller dimension, or add trivial bands. In all cases, the
-triviality of topological insulators can be detected in minimal dimension, since
-adding trivial bands can be ignored (insensitive to addition of trivial bands),
-and the possible different types of matrices are limited.
-
-However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
-topological insulator, we need to increase the matrix dimension to consider
-multiple copies of the Dirac Hamiltonian. If the topological state is stable for
-an arbitrary copies, then this is a $\Z$ topological insulator. If the
-topological state is stable only of an odd number of copies, this is a $\Z_2$
-topological insulator.
-
-Another way to view this way of classification, is to look at the surface
-Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
-see if the surface mode can be gapped, so as to detect the topological
-properties of the bulk.
-
-\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
-\label{sec:Isomorphism}
-As with other classifications, we construct isomorphisms between Dirac matrices
-and Clifford Algebras, after which we are faced with an extension problem. The
-isomorphism is constructed now.
-\subsubsection{Symmetry Constraint}
-\label{sec:Symmetry Constraint}
-The Hamiltonian with extra mass term is
-\begin{equation}
-    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
-    + \sum_{i=1}^{d} k_i \gamma_i
-\end{equation}
-The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
-conditions on the gamma matrices:
-\begin{subequations}
-    \label{eq:sym-spemt}
-\begin{align}
-    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
-    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
-    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
-\end{align}
-\end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
-Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
-examples in action.
-
-\subsubsection{Examples of Constructing Isomorphism}
-\label{sec:iso-Examples}
-For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
-    \label{tab:generator-AI}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
-$J_3=iT\tilde{\gamma}_0$, we could verify that all
-$\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
-Table~\ref{tab:map-sym-cl}.
-
-Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
-\begin{equation}
-    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
-\end{equation}
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
-    \label{tab:generator-AII}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
-verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
-Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
-$K_i^2=-1$, $(K'_1)^2=1$. The following map
-\begin{equation}
-    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
-\end{equation}
-has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
-\begin{table}[htpb]
-    \centering
-    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
-    \label{tab:map-cl13-2-cl04}
-    $ \begin{tabu}{ c | *4{c} }
-        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
-        \hline
-        J_1    & -1      & \{\}    & \{\}    & \{\} \\
-        J_2    & ~       & -1      & \{\}    & \{\} \\
-        J_3    & ~       & ~       & -1      & \{\} \\
-        J_4    & ~       & ~       & ~       & -1
-    \end{tabu} $
-
-    where $\{\}$ means anticommute.
-\end{table}
-Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
-consistent with $G_{\mathrm{AII}} \cong
-\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.
-
-\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
-\label{sec:Complex Classes-iso}
-The general steps for constructing the isomorphism is presented here. First, we
-need to treat the situation of complex classes and real classes
-differently. The complex classes are isomorphic to complex Clifford Algebras,
-while the real classes are isomorphic to real Clifford Algebras. The reason for
-this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
-multiplication of complex matrices. Second, complex matrices come with a nature
-definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
-\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
-    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
-we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
-Algebras when dealing with real classes (which is the reason why they are named
-real classes).
-
-For complex classes, let $G_\#$ be the group generated by elements
-$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
-class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
-such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
-Clifford Algebra:
-\begin{align}
-    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
-    \mathrm{C\ell}_{d+D+1}(\C) \\
-    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
-    \cong  \mathrm{C\ell}_{d+D+2}(\C)
-\end{align}
-
-\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
-\label{sec:Real Classes-iso}
-
-For real classes, we need to include $i$, and symmetry operators $T,C$ in our
-group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
-
-We first note that, given a real vector space $V$, we can complexify a real space in
-two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
-which does not suit our purpose. The second is to find an almost complex
-structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
-$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
-way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
-$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
-operators on a real vector space naturally.
-
-Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
-where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
-squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
-naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.
-
-Then we discuss some tips that will useful for later calculation.
-\paragraph{Tips}
-\begin{enumerate}
-    \item Since all generator anticommute, all matrices either commute or
-        anticommute. So the Algebra is pretty simple.
-    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
-        or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
-    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
-        BA$. However, if $A$ and $B$ has something in common, then the above
-        condition breaks. This is like adding an "impurity" in it to change the
-        commutation/anticommutation relations.
-    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
-        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
-        candidates for symmetry operator are only a small finite set.
-        \label{enum:tips-4}
-\end{enumerate}
-
-\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
-construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
-in real vector space, they commute with $J_1=J$. Then, each gamma matrices
-should have an even number of Clifford Algebra generators other than $J_1$
-itself. Similarly, antiunitary symmetry operators should have an odd number of
-Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
-some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
-take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
-\ref{eq:sym-spemt}, and they give us the inspiration to set:
-\begin{equation}
-    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
-    \sum_{i=1}^d k_i J_2\tilde{J}_i
-\end{equation}
-Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
-$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
-And within this algebra, only $J_2$ is a possible candidate for symmetry
-operators, which satisfy equations~\ref{eq:sym-spemt} (use
-tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
-time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
-class $\mathrm{AII}$. Therefore, the map:
-\begin{align}
-    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
-    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
-    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
-\end{align}
-is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
-$\mathrm{AII}$. The inverse map can be found easily. We first solve some
-formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
-\begin{equation}
-    a+bi \to a \begin{pmatrix}
-        1 & \\ & 1
-    \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
-    \end{pmatrix} = a\id + b J
-\end{equation}
-Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
-real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
-$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
-\begin{equation}
-    \{\Gamma_T,\Gamma_C\} = 0
-\end{equation}
-
-Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
-\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
-Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
-\begin{align}
-    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
-    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
-    \Gamma_T &\to J_2 \nonumber\\
-    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
-    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
-\end{align}
-is the desired inverse map.
-
-\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
-more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
-Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
-The rest is exactly the same as in class $\mathrm{AII}$.
-
-All other classes can be treated similarly, so we do not repeat the calculation
-and only list the result in Table~\ref{tab:map-sym-cl}.
-\begin{table}[htpb]
-    \centering
-    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
-    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
-    Algebra. Also, only one direction of mapping is shown. The inverse map can
-    be easily constructed accordingly. The complex class are also added for
-    convenience.}
-    \label{tab:map-sym-cl}
-    \begin{tabular}{c | c c c | l | c }
-        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
-        \hline 
-        D & $0$ & $+$ & $0$ & 
-        $\tilde{J}_1\to\Gamma_C$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
-        DIII & $-$ & $+$ & $1$ & 
-        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
-        AII & $-$ & $0$ & $0$ & 
-        $J_2\to \Gamma_T$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
-        CII & $-$ & $-$ & $1$ & 
-        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
-        C & $0$ & $-$ & $0$ & 
-        $J_2\to \Gamma_C$, 
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
-        CI & $+$ & $-$ & $1$ & 
-        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
-        AI & $+$ & $0$ & $0$ & 
-        $\tilde{J}_1\to \Gamma_T$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
-        BDI & $+$ & $+$ & $1$ & 
-        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
-        \hline
-        A & $0$ & $0$ & $0$ & 
-        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
-        AIII & $0$ & $0$ & $1$ & 
-        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\subsection{Classification in 1-dimension}
-\label{sec:Classification in 1-dimension}
-Classification of $1$ dimension is the simplest, since the minimal matrix
-dimension will mostly be $2$, which means we can use the familiar Pauli matrices
-directly.
-
-\paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.
-
-\paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
-topologically non-trivial. Now we consider the state with arbitrary copies of it.
-\begin{equation}
-    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
-    S=\sigma_z\otimes\id_n
-\end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
-
-The above are for complex classes. For real classes, we have to be careful,
-since one generator $J_1$ is taken up by $i$.
-
-\paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
-$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
-\end{equation}
-with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
-We let:
-\begin{equation}
-    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
-SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
-$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
-the remaining choice are acceptable, considering $T$ and $C$.}. Consider
-arbitrary copies of it:
-\begin{equation}
-    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
-    k_x\sigma_y\otimes\id_2)\otimes\id_n
-\end{equation}
-with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
-$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
-SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
-Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
-with $C$.}. Therefore, this is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
-of it:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
-\end{equation}
-with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
-$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
-$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
-complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{D}$} We let:
-\begin{equation}
-    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
-it:
-\begin{equation}
-    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
-Hence, this is a $\Z_2$ topological insulator.
-
-To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
-But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
-\paragraph{Class $\mathrm{DIII}$} We let:
-\begin{equation}
-    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
-form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
-this does not commute with $T$. Hence, there is no SPEMT. Now consider two
-copies of it:
-\begin{equation}
-    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
-this is a $\Z_2$ topological insulator.
-
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
-\begin{table}[htpb]
-    \centering
-    \caption{Topological Insulators in $d=1$}
-    \label{tab:ti-d=1}
-    \begin{tabular}{c | c c c | c }
-        Class($\#$) & T & C & S & $d=1$ \\
-        \hline 
-        A & $0$ & $0$ & $0$ & $0$ \\
-        AIII & $0$ & $0$ & $1$ & $\Z$ \\
-        \hline
-        D & $0$ & $+$ & $0$ & $\Z_2$ \\
-        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
-        AII & $-$ & $0$ & $0$ & $0$ \\
-        CII & $-$ & $-$ & $1$ & $\Z$ \\
-        C & $0$ & $-$ & $0$ & $0$ \\
-        CI & $+$ & $-$ & $1$ & $0$ \\
-        AI & $+$ & $0$ & $0$ & $0$ \\
-        BDI & $+$ & $+$ & $1$ & $\Z$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
-\subsection{Classification in Arbitrary Dimension}
-\label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
-generalized to classification in arbitrary dimensions. In $K$-theoretic
-classification, the extension problem is not affected when tensored with some
-other algebras. Specifically, for complex classes, the extension problem of
-$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
-III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
-
-Now, let us write $\sim$ to represent the equivalence between two extension
-problems.  The Complex Clifford Algebra has a periodicity of $2$:
-\begin{equation}
-    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
-    \mathrm{C\ell}_{2}(\C)
-\end{equation}
-The Real Clifford Algebra has a periodicity of $8$:
-\begin{equation}
-    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
-\end{equation}
-This two relation means, the extension problem will be the same with respect to
-a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
-classes. Hence the classification of topological insulators need only be done
-with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
-symmetry classes, i.e.
-\begin{subequations}
-    \label{eq:cli-periodic}
-\begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
-\end{align}
-\end{subequations}
-Another useful property is:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
-\end{align}
-This property tells us that Clifford Algebra basically depends only on the
-difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
-example, we have (let $n$ be an arbitrary integer):
-$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
-\begin{align}
-    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
-    \nonumber\\
-    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
-\end{align}
-and
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
-    \nonumber\\
-    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
-    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
-\end{align}
-Now we tries to connect the two chains together. We note further that the
-Clifford Algebra has the following properties:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
-    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
-\end{align}
-Then:
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
-    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
-    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
-    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
-\end{align}
-Therefore,
-$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
-connecting the two chains. If we compare this carefully with
-Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
-prove the dimension-shift feature of classification:
-\begin{align}
-    \label{eq:cli-Chain1}
-    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
-    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
-    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
-    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
-\end{align}
-We need one more property:
-\begin{equation}
-    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
-    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
-\end{equation}
-Then
-\begin{equation}
-    \label{eq:cli-Chain2}
-    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
-\end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|c|cccccccc|ccc|}
-\hline
-\multicolumn{12}{|c|}{
-The original classification table} \\ \hline
-   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
-\hline\hline
-  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
-  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline
-
-  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
-  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
-  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
-  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
-  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
-  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
-  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
-  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
-   \\
-\hline
-\end{tabular}
-\caption{The original classification table of topological insulators and
-superconductors}
-\label{tab:master-table2}
-\end{center}
-\end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
-
-\bibliography{../../library}{}
-\bibliographystyle{alphaurl}
-% \begin{thebibliography}{1}
-% 	\bibitem{book} 
-% \end{thebibliography}
-\printnomenclature
-
-\end{document}
+Note that due to unforeseenable problems, this document may be outdated. The
+latest version may be emailed by request.

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-appA.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
+\section{Various Properties for Clifford Algebras}
+\label{sec:Various Properties for Clifford Algebras}
+We have used various properties of Clifford Algebras from various sources. Here
+I summarized those properties for the convenience of readers.
 
-% My own physics package
-% The following line load the package xparse with additional option to
-% prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
+\paragraph{Isomorphism Relations}
+The best source of isomorphism between Clifford Algebras is actually the
+Wikipedia page about \textit{Classifications of Clifford Algebras}. For a more
+authoritative account, I am using the book \cite{VazJayme2016}. The results
+used in this document are to be found in chapter 4 of that book.
 
-\makenomenclature % For an index of symbols.
+\paragraph{Representation Theory on Complex Clifford Algebras}
+This paper \cite{West1998} has a good discussion on the irreducible
+representations of complex Clifford Algebras, in p.5, p.12. They can be
+summarized as:
+\begin{thm}
+	Consider $\mathrm{C\ell}_{N}(\C)$. For both $N = 2n$ and $N = 2n + 1$, the
+	dimension d of the irreducible representation is uniquely given by
+	\begin{equation}
+	d = 2^n \text{($N=2n$ or $N=2n+1$)}
+	\end{equation}
+	Moreover, for $N = 2n$, the irreducible space is unique, while for $N = 2n +
+	1$, we have two inequivalent irreducible representations with the same
+	dimension $d$.
+\end{thm}
 
-\title{Notes about the Minimal Dimensional Method to Classify
-Topological Phases (preliminary)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
-}
-% TODO: add ref for Clifford Algebra.
-\tableofcontents
-
-\section{Outline}
-\label{sec:Outline}
-
-The classification of topological insulators in non-interacting system is in
-effect a classification of Hamiltonian matrix. The simple case considered here
-is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
-symmetries. Specifically, when we module out any unitary symmetries of the
-Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
-we only classify topological insulators based on how our Hamiltonian matrix
-responses to these anti-unitary symmetries.
-
-There are two classical approaches towards this classification. The first is to
-examine the existence of Anderson delocalization at the boundary of the
-insulator, because the existence of surface conducting state is the signature of
-topological insulators and the Anderson localization is the obstruction that
-\todo{Be more specific about this and check some facts.}
-surface conducting states must overcome. This approach uses the Nonlinear Sigma
-Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
-when can a localization-breaking term can be added to NL$\sigma$Ms.
-
-The second approach is to use homotopy theory to classify classes Hamiltonians under
-continuous deformation, more specifically, under adiabatical change of
-Hamiltonians. This method is most elegant but most mathematical demanding
-approach compared with others, because calculating homotopy groups, and homotopy theories in
-general are notorious hard. Also, one has to use $K$-theory, because of
-something physical is enlarging those distinct classes of Hamiltonian. To be
-more specific.
-
-But the key to understand topological insulators, are not necessarily the
-Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes theorem,
-unless inside this manifold there is somewhere where the formula for Chern
-number got "blown up", and it is just this locally "blown up" point that is
-responsible for the nonzero Chern number, and for the non-triviality of
-topological insulators.
-
-Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
-energy zero level to the crossing point, in only the low energy physics. We
-expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
-
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
-
-\paragraph{Structure of this work} This work are divided into several parts.
-\begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
-\end{enumerate}
-
-\section{Ten-fold Way}
-
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
-matrices by its response to three discrete symmetries: time reversal symmetry
-($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
-symmetry ($S$). As for those unitary symmetries, one can in principle, block
-diagonalize the Hamiltonian
-$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
-$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
-applied to those blocks and still holds.
-
-It will be find that, those $T,C$ are the only two meaningful non-unitary
-symmetries of the Single-particle system, and there are in total 10 different
-ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
-care about these three symmetries $T,C,$ and $S$.
-
-\subsection{The symmetries of Single-particle Hamiltonian}
-\label{sec:The symmetries of Single-particle Hamiltonian}
-
-According to Wigner's theorem, symmetries of physical system can either be
-unitary represented, or anti-unitarily represented. Here we show that in the
-case of anti-unitary symmetries, there are only 2 different kinds of them that a
-Single-particle Hamiltonian in first-quantized space can have. Actually, there
-can be more anti-unitary symmetries than this. But under reasonable assumptions,
-we can limit our discussion in only this two types.
-
-The Single-particle Hamiltonian acting on Fock space is
+\paragraph{Representation Theory on Real Clifford Algebra}
+The two papers \cite{Okubo1991a}\cite{Okubo1991} are great in this respect.
+Their result used in this document could be summarized as:
+\begin{thm}
+    Let $N=p+q$.
+	Consider $\mathrm{C\ell}_{p,q}(\R)$. For $N=2n$, we have:
+	\begin{align}
+	d= \begin{cases}
+	2^n_1, & \text{for } p-q=0\text{ or }2\text{, mod }8 \\
+	2^{n+1}_1, & \text{for } p-q=4\text{ or }6\text{, mod }8 \\
+	\end{cases}
+	\end{align}
+	For $N=2n+1$, we have:
+	\begin{align}
+	d= \begin{cases}
+	2^n_2, & \text{for } p-q=1\text{, mod }8 \\
+	2^{n+1}_1, & \text{for } p-q=3\text{ or }7\text{, mod }8 \\
+	2^{n+1}_2, & \text{for } p-q=5\text{, mod }8 \\
+	\end{cases}
+	\end{align}
+	Where we have used a subscript $1$ to denote that there is only
+	one unique irreducible representation, and a subscript $2$ to
+	denote that there are two inequivalent irreducible representations.
+\end{thm}
+Below collects a list of dimensions that I have used in the discussion of
+Table~\ref{tab:mat-dim-allClass-1d}:
 \begin{equation}
-    \label{eq:H-2nd}
-    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
+    \label{eq:Cl-dimenList}
+    \begin{aligned}
+    &
+    \mathrm{C\ell}_{1,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{1,3}(\R)\sim 4^2_1,\,
+    \mathrm{C\ell}_{1,4}(\R)\sim 4^2_2,\, \mathrm{C\ell}_{1,5}(\R)\sim 8^2_1,\,
+    \\&
+    \mathrm{C\ell}_{2,2}(\R)\sim 2^2_1,\, \mathrm{C\ell}_{2,3}(\R)\sim 4^2_1,\,
+    \mathrm{C\ell}_{3,2}(\R)\sim 2^2_2,\, \mathrm{C\ell}_{2,4}(\R)\sim 8^2_1,\,
+    \\&
+    \mathrm{C\ell}_{3,3}(\R)\sim 4^2_1,\, \mathrm{C\ell}_{4,2}(\R)\sim 4^2_1.
+    \end{aligned}
 \end{equation}
-where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
-are creation and annihilation operators acting on Fock space.
-
-Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
-to stress that it acts on Second-quantized Fock space.  A symmetry of the
-Hamiltonian, represented as an operator $\hat{U}$, must have:
-\begin{equation}
-    \label{eq:sym-in-2nd-1}
-    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
-\end{equation}
-
-We expect $\hat{U}$ to change the creation/annihilation operators in two different
-ways. First, it may only permute the creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-in-2nd-permute}
-\begin{align}
-    \label{eq:sym-in-2nd-permute-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
-    \label{eq:sym-in-2nd-permute-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi^\dagger_B u_{AB}
-\end{align}
-\end{subequations}
-Where $u$ is some matrix implementing the permutation.
-Or, it may interchange the role of creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-cc}
-\begin{align}
-    \label{eq:sym-cc-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
-    \label{eq:sym-cc-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi_B u^*_{BA}
-\end{align}
-\end{subequations}
-Where $u^*$ is some other matrix implementing the interchange. We write complex
-conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
-interchange), to conserve the anticommutation relation between
-$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
-should be a unitary matrix.
-
-Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
-conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
-symmetry, to be explained below.
-
-\paragraph{Case 1: Unitary Symmetry}
-
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives
-\begin{equation}
-    u H u^{-1} = H
-\end{equation}
-Therefore, in this case the symmetry is unitarily realized in First-quantized
-Hamiltonian $H_{AB}$.
-
-\paragraph{Case 2: Anti-unitary T Symmetry}
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
-$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
-\begin{equation}
-    u H^* u^\dagger = H
-\end{equation}
-Or:
-\begin{equation}
-    uK H u^t K = uK H (uK)^{-1} = H
-\end{equation}
-where $K$ is complex conjugation. This symmetry is called Time-reversal
-symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
-operator $T= uK$.
-
-\paragraph{Case 3: Anti-unitary C Symmetry}
-Assume the symmetry just interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\footnote{
-Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
-\id$ on 1st-quantized single-particle Hilbert space.
-}
-\begin{equation}
-    \label{eq:sym-C-cond}
-    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-
-Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
-in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
-simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
-\begin{equation}
-    u H^* u^\dagger = uK H (uK)^{-1} = -H
-\end{equation}
-This type of symmetry is called charge-conjugation symmetry. It is
-also called particle-hole symmetry in condensed matter physics. It is realized
-as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.
-
-\paragraph{Case 4: Unitary S Symmetry}
-Assume the symmetry now interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\begin{equation}
-    \label{eq:sym-S-cond}
-    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-and since $N>>2$, we have $\tr(H)=0$. Then
-\begin{equation}
-    u H u^\dagger = -H
-\end{equation}
-This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
-unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
-of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
-easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
-defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
-property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
-of Hamiltonian under $S$. But there is one exception. When the
-Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
-whole.
-
-\paragraph{Squaring of $T,C,S$} 
-Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
-hence it is only a phase as they are unitary.
-This can be viewed from two perspectives. First, we expect the system, after
-applying twice of symmetry operation $T/C$, should come back to the same state, except
-a possible phase difference. Second, $T^2/C^2$ commutes with all
-$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
-of unitary symmetries (to be explained later), therefore by Schur's lemma, they
-must be proportional to a constant, which is a phase.
-
-It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
-then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
-$e^{i\delta}=\pm1$.
-
-But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
-$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
-operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
-phase for $S^2$.\footnote{This is a bit troublesome. First we denote
-$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
-$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
-$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
-\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
-Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
-$S^2=-\varepsilon_C\varepsilon_T$.}
-
-\paragraph{Why Ten Classes} For the three unitary symmetries under
-consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
-$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
-undetermined (depending on the phase choice\footnote{To be explained later.} we
-give for $T$ and $C$). Therefore, there are in total 10 different possible ways
-that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
-to symbolize that the system does not follow $T$($C$) symmetry. Then
-$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
-$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
-different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
-
-\subsection{Dealing with Unitary Symmetries}
-\label{sec:Dealing with Unitary Symmetries}
-
-As mentioned, we could module out those unitary symmetries. This statement is
-made precise by the following theorem about unitary symmetries of the Hamiltonian.
-\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
-This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
-$\mathcal{V}_\lambda$ associated with the irrep (irreducible
-representations, labeled by $\lambda$) of $G_0$.
-\begin{equation}
-    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
-\end{equation}
-where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
-Denote the dimension of each irrep as $d_\lambda$.
-
-In each vector space $\mathcal{V}_\lambda$, one can choose a
-(orthogonal) basis of the form:
-\begin{equation}
-    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
-\end{equation}
-where
-\begin{itemize}
-    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
-        $k=1,\cdots,d_\lambda$,
-    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
-        $\alpha=1,\cdots,m_\lambda$.
-\end{itemize}
-\end{thm}
-Therefore, with all unitary symmetries ignored, we are classifying how
-Hamiltonian will be like when it respects, in 10 different ways, the
-combinations of $T,C,S$ symmetries.
-
-\paragraph{Differently Realized Anti-unitary Symmetries}
-It should be noted that there is still a freedom of unitary matrix that
-implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
-different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
-obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
-easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
-Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
-symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
-described in the theorem above, we only have one time-reversal symmetry. Similar
-analysis could be done for the $C$ symmetry as well.
-
-\paragraph{Translational Symmetry}
-
-Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
-
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
-
-The Hamiltonian in $k$-space that preserve these three discrete symmetries
-should follow\footnote{It is easy to anticipate the change $k\to -k$ for
-    anti-unitary symmetries, since they change the phase factor when one Fourier
-transform the Hamiltonian.}:
-\begin{subequations}
-\begin{align}
-    \label{eq:T-sym-Hk}
-    TH(k)T^{-1} &= H(-k) \\
-    \label{eq:C-sym-Hk}
-    CH(k)C^{-1} &= -H(-k) \\
-    \label{eq:S-sym-Hk}
-    SH(k)S^{-1} &= -S(k)
-\end{align}
-\end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
-
-\section{Classification by Dirac Mass Terms}
-\label{sec:The Minimal Hamiltonian Approach}
-
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
-We first note that different topological phases are distinguished by the closing
-and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
-flatten the energy spectrum to two bands of energy $\pm E$, the transition
-(closing of gap) will happen at some point where locally the energy is of a
-Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
-behavior. Then, a class of topological phases, or more specifically, a class of
-Hamiltonian matrix that shares the same topological invariant, can be
-\textit{represented} by the Dirac Hamiltonian in this class.
-
-\subsection{Crossing Spectrum and Edge Mode}
-\label{sec:Crossing Spectrum and Edge Mode}
-Here we show that the crossing spectrum characteristic of topological insulators
-can be characterized by a Dirac type Hamiltonian, and with this Dirac
-Hamiltonian we could find an Edge mode solution built into it.
-
-\paragraph{Crossing Spectrum and Dirac Hamiltonian}
-In some local region around the crossing point, the energy spectrum should look
-like:
-\begin{equation}
-    E = \pm \sqrt{\vb{k}^2 + M^2}
-\end{equation}
-where $\vb{k}$ is the crystal momentum and $M$ is some constant
-responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
-
-As has been analysed in most Quantum Mechanics textbook\footnote{See for
-    example, p.99 of \cite{Greiner1997}. Although their discussion is in
-dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
-relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
-use is:
-\begin{equation}
-    \label{eq:dirac-H}
-    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
-\end{equation}
-where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
-Clifford Algebra anti-commutation relation:
-\begin{equation}
-    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
-\end{equation}
-
-\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
-phase. First, it has a gapless state. Due to the anti-commutation relation of
-$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
-tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
-we choose not $\gamma_i^2=-1$, which would give non-sensible result
-$H_\text{Dirac}^2= -E^2\id$.}
-that the energies of Dirac Hamiltonian are:
-\begin{equation}
-    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
-\end{equation}
-Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
-gaped to gapless and again to gaped state. This shows that the $M$ is parameter
-controlling the quantum phase transition, and the system with $M<0$ or $M>0$
-possesses two different quantum phase.
-
-In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
-should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
-broken in that direction. Now the eigenvalue equation is:
-\begin{equation}
-    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
-    = E \Phi
-\end{equation}
-
-Past experience teaches us the ansatz (assuming
-$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
-does not blow up the wavefunction):
-\begin{equation}
-    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
-\end{equation}
-which after plugging inside the eigenvalue equation, leads to
-\begin{equation}
-    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
-    = E \phi
-\end{equation}
-After left multiplication of $\gamma_0$, we have:
-\begin{equation}
-    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
-    = E \gamma_0 \phi
-\end{equation}
-Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
-$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
-eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
-$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
-state to be a surface state, so we choose the $-1$ eigenvectors (denoted
-$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
-\begin{equation}
-    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
-\end{equation}
-As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
-have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
-eigenspaces:
-\begin{equation}
-    \label{eq:H-Dirac-surf}
-    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
-\end{equation}
-
-% \section{Collection of Calculation}
-% \label{sec:Collection of Calculation}
-% Here collects the calculations done throughout the whole notes.
-
-\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
-\label{sec:Homotopy to Minimal Dirac}
-
-\paragraph{Spectral Flattening} The classification of topological insulators
-concerns different classes of Hamiltonian that cannot be adiabatically changed
-to each without closing or opening of a gap. Hence, we could in general
-adiabatically change our parameters such that the spectrum of Hamiltonian is
-simplified into two bands of energy $\pm1$. Under this condition, we have
-$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
-for generating Clifford Algebras.
-
-\paragraph{Extension Problem with General Examples}
-The general theme of homotopy classification of classifying topological
-insulators are done by the considering the \textit{extension problem}, i.e.
-different ways to extend from a Clifford containing only symmetry operators, to
-a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
-in $0$-dimension, the empty space is nothing, hence
-$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
-Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
-classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
-mentioned earlier, hence the extension problem is from
-$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
-representations form some mathematical structure called \textit{classifying
-space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
-operators are maps starting from $T^0=S^0$. So our classified objects are
-different classes of maps from $S^0\to C_0$, which is mathematically captured by
-the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
-only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
-making it a candidate for generators of Clifford Algebra. The symmetry condition
-$\{H,S\}=0$ tells us now we have a extension problem of
-$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
-$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
-$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
-trivial topological insulators. The case for real symmetry classes are not too
-complicated and is concisely mentioned in \cite{Morimoto2013}.
-
-However, the method to obtain such classifying spaces are mathematical daunting
-and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
-since they should capture the essence of topological states.
-
-\paragraph{Extension Problem with Dirac Hamiltonian}
-The Dirac Hamiltonian
-\begin{equation}
-    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
-\end{equation}
-has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
-parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
-$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
-$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
-space having the same homotopy type of some classifying space (again!). For
-example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
-term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
-$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
-$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
-extension problem concerns different ways to extend the algebra
-$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
-unitarily non-equivalent mass terms. Detailed examples can be found in section
-III.C.1 of \cite{Chiu2016}.
-
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
-\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
-with extra mass term:
-\begin{equation}
-    \label{eq:H-spemt}
-    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
-    + \sum_{j=1}^D m_j\tilde{\gamma}_j
-\end{equation}
-Here, the parameter $M$ characterized the domain wall between different phases
-of topological insulators. The extra mass term $m_j$ represents a perturbation
-caused by disorder. I argue that we can do our classification in the following
-way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
-a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
-
-One best thing about this classification is that it can be done by considering
-only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
-argument is that, complex gamma matrices are of even dimension (except the
-trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
-\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
-\cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
-different type in the smaller dimension, or add trivial bands. In all cases, the
-triviality of topological insulators can be detected in minimal dimension, since
-adding trivial bands can be ignored (insensitive to addition of trivial bands),
-and the possible different types of matrices are limited.
-
-However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
-topological insulator, we need to increase the matrix dimension to consider
-multiple copies of the Dirac Hamiltonian. If the topological state is stable for
-an arbitrary copies, then this is a $\Z$ topological insulator. If the
-topological state is stable only of an odd number of copies, this is a $\Z_2$
-topological insulator.
-
-Another way to view this way of classification, is to look at the surface
-Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
-see if the surface mode can be gapped, so as to detect the topological
-properties of the bulk.
-
-\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
-\label{sec:Isomorphism}
-As with other classifications, we construct isomorphisms between Dirac matrices
-and Clifford Algebras, after which we are faced with an extension problem. The
-isomorphism is constructed now.
-\subsubsection{Symmetry Constraint}
-\label{sec:Symmetry Constraint}
-The Hamiltonian with extra mass term is
-\begin{equation}
-    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
-    + \sum_{i=1}^{d} k_i \gamma_i
-\end{equation}
-The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
-conditions on the gamma matrices:
-\begin{subequations}
-    \label{eq:sym-spemt}
-\begin{align}
-    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
-    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
-    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
-\end{align}
-\end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
-Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
-examples in action.
-
-\subsubsection{Examples of Constructing Isomorphism}
-\label{sec:iso-Examples}
-For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
-    \label{tab:generator-AI}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
-$J_3=iT\tilde{\gamma}_0$, we could verify that all
-$\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
-Table~\ref{tab:map-sym-cl}.
-
-Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
-\begin{equation}
-    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
-\end{equation}
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
-    \label{tab:generator-AII}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
-verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
-Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
-$K_i^2=-1$, $(K'_1)^2=1$. The following map
-\begin{equation}
-    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
-\end{equation}
-has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
-\begin{table}[htpb]
-    \centering
-    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
-    \label{tab:map-cl13-2-cl04}
-    $ \begin{tabu}{ c | *4{c} }
-        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
-        \hline
-        J_1    & -1      & \{\}    & \{\}    & \{\} \\
-        J_2    & ~       & -1      & \{\}    & \{\} \\
-        J_3    & ~       & ~       & -1      & \{\} \\
-        J_4    & ~       & ~       & ~       & -1
-    \end{tabu} $
-
-    where $\{\}$ means anticommute.
-\end{table}
-Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
-consistent with $G_{\mathrm{AII}} \cong
-\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.
-
-\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
-\label{sec:Complex Classes-iso}
-The general steps for constructing the isomorphism is presented here. First, we
-need to treat the situation of complex classes and real classes
-differently. The complex classes are isomorphic to complex Clifford Algebras,
-while the real classes are isomorphic to real Clifford Algebras. The reason for
-this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
-multiplication of complex matrices. Second, complex matrices come with a nature
-definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
-\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
-    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
-we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
-Algebras when dealing with real classes (which is the reason why they are named
-real classes).
-
-For complex classes, let $G_\#$ be the group generated by elements
-$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
-class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
-such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
-Clifford Algebra:
-\begin{align}
-    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
-    \mathrm{C\ell}_{d+D+1}(\C) \\
-    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
-    \cong  \mathrm{C\ell}_{d+D+2}(\C)
-\end{align}
-
-\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
-\label{sec:Real Classes-iso}
-
-For real classes, we need to include $i$, and symmetry operators $T,C$ in our
-group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
-
-We first note that, given a real vector space $V$, we can complexify a real space in
-two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
-which does not suit our purpose. The second is to find an almost complex
-structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
-$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
-way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
-$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
-operators on a real vector space naturally.
-
-Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
-where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
-squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
-naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.
-
-Then we discuss some tips that will useful for later calculation.
-\paragraph{Tips}
-\begin{enumerate}
-    \item Since all generator anticommute, all matrices either commute or
-        anticommute. So the Algebra is pretty simple.
-    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
-        or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
-    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
-        BA$. However, if $A$ and $B$ has something in common, then the above
-        condition breaks. This is like adding an "impurity" in it to change the
-        commutation/anticommutation relations.
-    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
-        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
-        candidates for symmetry operator are only a small finite set.
-        \label{enum:tips-4}
-\end{enumerate}
-
-\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
-construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
-in real vector space, they commute with $J_1=J$. Then, each gamma matrices
-should have an even number of Clifford Algebra generators other than $J_1$
-itself. Similarly, antiunitary symmetry operators should have an odd number of
-Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
-some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
-take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
-\ref{eq:sym-spemt}, and they give us the inspiration to set:
-\begin{equation}
-    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
-    \sum_{i=1}^d k_i J_2\tilde{J}_i
-\end{equation}
-Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
-$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
-And within this algebra, only $J_2$ is a possible candidate for symmetry
-operators, which satisfy equations~\ref{eq:sym-spemt} (use
-tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
-time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
-class $\mathrm{AII}$. Therefore, the map:
-\begin{align}
-    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
-    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
-    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
-\end{align}
-is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
-$\mathrm{AII}$. The inverse map can be found easily. We first solve some
-formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
-\begin{equation}
-    a+bi \to a \begin{pmatrix}
-        1 & \\ & 1
-    \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
-    \end{pmatrix} = a\id + b J
-\end{equation}
-Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
-real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
-$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
-\begin{equation}
-    \{\Gamma_T,\Gamma_C\} = 0
-\end{equation}
-
-Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
-\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
-Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
-\begin{align}
-    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
-    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
-    \Gamma_T &\to J_2 \nonumber\\
-    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
-    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
-\end{align}
-is the desired inverse map.
-
-\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
-more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
-Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
-The rest is exactly the same as in class $\mathrm{AII}$.
-
-All other classes can be treated similarly, so we do not repeat the calculation
-and only list the result in Table~\ref{tab:map-sym-cl}.
-\begin{table}[htpb]
-    \centering
-    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
-    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
-    Algebra. Also, only one direction of mapping is shown. The inverse map can
-    be easily constructed accordingly. The complex class are also added for
-    convenience.}
-    \label{tab:map-sym-cl}
-    \begin{tabular}{c | c c c | l | c }
-        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
-        \hline 
-        D & $0$ & $+$ & $0$ & 
-        $\tilde{J}_1\to\Gamma_C$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
-        DIII & $-$ & $+$ & $1$ & 
-        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
-        AII & $-$ & $0$ & $0$ & 
-        $J_2\to \Gamma_T$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
-        CII & $-$ & $-$ & $1$ & 
-        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
-        C & $0$ & $-$ & $0$ & 
-        $J_2\to \Gamma_C$, 
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
-        CI & $+$ & $-$ & $1$ & 
-        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
-        AI & $+$ & $0$ & $0$ & 
-        $\tilde{J}_1\to \Gamma_T$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
-        BDI & $+$ & $+$ & $1$ & 
-        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
-        \hline
-        A & $0$ & $0$ & $0$ & 
-        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
-        AIII & $0$ & $0$ & $1$ & 
-        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\subsection{Classification in 1-dimension}
-\label{sec:Classification in 1-dimension}
-Classification of $1$ dimension is the simplest, since the minimal matrix
-dimension will mostly be $2$, which means we can use the familiar Pauli matrices
-directly.
-
-\paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.
-
-\paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
-topologically non-trivial. Now we consider the state with arbitrary copies of it.
-\begin{equation}
-    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
-    S=\sigma_z\otimes\id_n
-\end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
-
-The above are for complex classes. For real classes, we have to be careful,
-since one generator $J_1$ is taken up by $i$.
-
-\paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
-$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
-\end{equation}
-with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
-We let:
-\begin{equation}
-    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
-SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
-$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
-the remaining choice are acceptable, considering $T$ and $C$.}. Consider
-arbitrary copies of it:
-\begin{equation}
-    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
-    k_x\sigma_y\otimes\id_2)\otimes\id_n
-\end{equation}
-with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
-$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
-SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
-Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
-with $C$.}. Therefore, this is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
-of it:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
-\end{equation}
-with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
-$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
-$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
-complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{D}$} We let:
-\begin{equation}
-    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
-it:
-\begin{equation}
-    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
-Hence, this is a $\Z_2$ topological insulator.
-
-To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
-But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
-\paragraph{Class $\mathrm{DIII}$} We let:
-\begin{equation}
-    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
-form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
-this does not commute with $T$. Hence, there is no SPEMT. Now consider two
-copies of it:
-\begin{equation}
-    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
-this is a $\Z_2$ topological insulator.
-
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
-\begin{table}[htpb]
-    \centering
-    \caption{Topological Insulators in $d=1$}
-    \label{tab:ti-d=1}
-    \begin{tabular}{c | c c c | c }
-        Class($\#$) & T & C & S & $d=1$ \\
-        \hline 
-        A & $0$ & $0$ & $0$ & $0$ \\
-        AIII & $0$ & $0$ & $1$ & $\Z$ \\
-        \hline
-        D & $0$ & $+$ & $0$ & $\Z_2$ \\
-        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
-        AII & $-$ & $0$ & $0$ & $0$ \\
-        CII & $-$ & $-$ & $1$ & $\Z$ \\
-        C & $0$ & $-$ & $0$ & $0$ \\
-        CI & $+$ & $-$ & $1$ & $0$ \\
-        AI & $+$ & $0$ & $0$ & $0$ \\
-        BDI & $+$ & $+$ & $1$ & $\Z$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
-\subsection{Classification in Arbitrary Dimension}
-\label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
-generalized to classification in arbitrary dimensions. In $K$-theoretic
-classification, the extension problem is not affected when tensored with some
-other algebras. Specifically, for complex classes, the extension problem of
-$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
-III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
-
-Now, let us write $\sim$ to represent the equivalence between two extension
-problems.  The Complex Clifford Algebra has a periodicity of $2$:
-\begin{equation}
-    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
-    \mathrm{C\ell}_{2}(\C)
-\end{equation}
-The Real Clifford Algebra has a periodicity of $8$:
-\begin{equation}
-    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
-\end{equation}
-This two relation means, the extension problem will be the same with respect to
-a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
-classes. Hence the classification of topological insulators need only be done
-with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
-symmetry classes, i.e.
-\begin{subequations}
-    \label{eq:cli-periodic}
-\begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
-\end{align}
-\end{subequations}
-Another useful property is:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
-\end{align}
-This property tells us that Clifford Algebra basically depends only on the
-difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
-example, we have (let $n$ be an arbitrary integer):
-$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
-\begin{align}
-    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
-    \nonumber\\
-    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
-\end{align}
-and
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
-    \nonumber\\
-    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
-    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
-\end{align}
-Now we tries to connect the two chains together. We note further that the
-Clifford Algebra has the following properties:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
-    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
-\end{align}
-Then:
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
-    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
-    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
-    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
-\end{align}
-Therefore,
-$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
-connecting the two chains. If we compare this carefully with
-Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
-prove the dimension-shift feature of classification:
-\begin{align}
-    \label{eq:cli-Chain1}
-    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
-    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
-    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
-    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
-\end{align}
-We need one more property:
-\begin{equation}
-    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
-    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
-\end{equation}
-Then
-\begin{equation}
-    \label{eq:cli-Chain2}
-    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
-\end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|c|cccccccc|ccc|}
-\hline
-\multicolumn{12}{|c|}{
-The original classification table} \\ \hline
-   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
-\hline\hline
-  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
-  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline
-
-  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
-  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
-  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
-  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
-  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
-  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
-  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
-  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
-   \\
-\hline
-\end{tabular}
-\caption{The original classification table of topological insulators and
-superconductors}
-\label{tab:master-table2}
-\end{center}
-\end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
-
-\bibliography{../../library}{}
-\bibliographystyle{alphaurl}
-% \begin{thebibliography}{1}
-% 	\bibitem{book} 
-% \end{thebibliography}
-\printnomenclature
-
-\end{document}

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-appB.tex
[major] Solved how to distinguish Z and Z2.

\section{A Case Study of Class \texorpdfstring{$\mathrm{D}$}{} at
\texorpdfstring{$d=1$}{}}
\label{sec:a case study}
Throughout the document we never gave a explicit example of constructing the
actual matrices and symmetry operators from representations of Clifford
Algebras. However, a real example is crucial to understand the mechanism. Here I
provide a calculated example, from which I gained the intuition to distinguish
between a $\Z$ and a $\Z_2$ topological insulator.

Class $\mathrm{D}$ has the extension problem: $\mathrm{C\ell}_{2,2}(\R)\to
\mathrm{C\ell}_{2,3}(\R)$, dimension changes as $2\to 4$. Now we write a simple
irreducible representation of $\mathrm{C\ell}_{2,2}(\R)$ as:
\begin{equation}
    \label{eq:old-realified-J}
    J_1 = -i\sigma_y\otimes \id_2,
    J_2 = \sigma_z\otimes i\sigma_y,
    \tilde{J}_1 = \sigma_x\otimes \id_2,
    \tilde{J}_2 = \sigma_z\otimes \sigma_x
\end{equation}
It can be calculated from Table~\ref{tab:map-sym-cl} (or directly use table A.2
from \cite{Chiu2013a}) that:
\begin{equation}
\begin{aligned}
    \Gamma_C &= \tilde{J}_1,\\
    \tilde{\Gamma}_0 &= \tilde{J}_1 J_2,\\
    \Gamma_1 &=J_1\tilde{J}_1\tilde{J}_2
\end{aligned}
\end{equation}
since our complex structure $J_1= \begin{pmatrix}
    0 & -\id \\ \id & 0
\end{pmatrix}$, the real vector space is spanned by basis $\{e_i, J_1 e_i\}$. So
the complexfication can be done by looking at how each matrix acts on $e_i$. The
process is done manually and the result shows that:
\begin{equation}
\begin{aligned}
    J_1 &\to i \\
    \Gamma_C &\to C = iK \\
    \tilde{\Gamma}_0 &\to \tilde{\gamma}_0 = -\sigma_x \\
    {\Gamma}_1 &\to {\gamma}_1 = -\sigma_y
\end{aligned}
\end{equation}
So our Hamiltonian and symmetry operator in minimal dimension is
\begin{equation}
    H = -(M\sigma_y + k_1\sigma_x), C=iK
\end{equation}
there is certainly no SPEMT. Consider two copies of it:
\begin{equation}
    H = -(M\sigma_y + k_1\sigma_x)\otimes\id_2, C=iK
\end{equation}
There is clearly one SPEMT, $m\sigma_z\otimes\sigma_y$. Let me show how this
SPEMT is reflected in representation of Clifford Algebras. We now have in the
doubled dimension:
\begin{equation}
\begin{aligned}
    \tilde{\gamma}_0 &= -\sigma_y\otimes\id_2 = i(i\sigma_y\otimes\id_2) \\
    \tilde{\gamma}_1 &= \sigma_z\otimes\sigma_y = i\sigma_z\otimes(-i\sigma_y)
    \\
    \gamma_1 &= -\sigma_x\otimes\id_2
\end{aligned}
\end{equation}
These new gamma matrices, together with $i$ and $C=iK$, are realified as
\begin{equation}
\begin{aligned}
    i &\to J_1= -i\sigma_y\otimes \id_4 \\
    C &\to \Gamma_C = \sigma_x\otimes\id_4 \\
    \tilde{\gamma}_0 &\to \tilde{\Gamma}_0 = -i\sigma_y\otimes
    i\sigma_y\otimes\id_2 \\
    \tilde{\gamma}_1 &\to \tilde{\Gamma}_1 = -i\sigma_y\otimes\sigma_z\otimes
    (-i\sigma_y) \\
    \gamma_1 &\to \Gamma_1 = -\id_1\otimes\sigma_x\otimes\id_1
\end{aligned}
\end{equation}
Then, we reverse the process and use Table~\ref{tab:map-sym-cl} to get
\begin{equation}
\begin{aligned}
    \label{eq:new-realified-J}
    J_1 &= -i\sigma_y \otimes\id_4 \\
    J_2 &= \sigma_z\otimes i\sigma_y \otimes \id_2 \\
    J_3 &= -\sigma_z\otimes\sigma_z\otimes i\sigma_y \\
    \tilde{J}_1 &= \sigma_x\otimes\id_4 \\
    \tilde{J}_2 &= \sigma_z\otimes\sigma_x\otimes\id_2
\end{aligned}
\end{equation}
Comparing the old $J$s(\ref{eq:old-realified-J}) and new
$J$s(\ref{eq:new-realified-J}), clearly there is only one more player $J_3$. And
$J_3$ comes from $\sigma_z\otimes\sigma_z$, which is an element extend
$\mathrm{C\ell}_{2,2}(\R)\to \mathrm{C\ell}_{3,2}(\R)$. This the reason why
Class $\mathrm{D}$ in $d=1$ is $\Z_2$, not $\Z$, as mentioned in
Section~\ref{sec:Irreducible Representation Arguments for Classification}.

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/introduction.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
-% The entire content of this work (including the source code
-% for TeX files and the generated PDF documents) by 
-% Hongxiang Chen (nicknamed we.taper, or just Taper) is
-% licensed under a 
-% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
-% International License (Link to the complete license text:
-% http://creativecommons.org/licenses/by-nc-sa/4.0/).
-\documentclass{article}
-
-% My own physics package
-% The following line load the package xparse with additional option to
-% prevent the annoying warnings, which are caused by the package
-% "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
-
-\makenomenclature % For an index of symbols.
-
-\title{Notes about the Minimal Dimensional Method to Classify
-Topological Phases (preliminary)}
-\date{\today}
-\author{Taper}
-
-\begin{document}
-
-\maketitle
-\abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
-}
-% TODO: add ref for Clifford Algebra.
-\tableofcontents
-
 \section{Outline}
@@
 opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
+describe such a low energy physics is the Dirac Hamiltonian. Also, the
+traditional discussion of Klein-Gordon equation all tells us to look at Dirac
+Hamiltonian.
 
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
+Using the Dirac Hamiltonian, it is discovered by Dr. Chiu \cite{Chiu2013a} that
+the classification of topological insulators could be brought done into very
+simple applications of classification and representation theory of Clifford
+Algebras, which have been well studied with excellent resources provided online.
+In his classification, he established a isomorphism from $G_{\text{symmetries 
+class}}$, the algebra generated by symmetry operators and Dirac Hamiltonians, to
+some Clifford Algebras. Consequently, the Hamiltonian and symmetry operators,
+all become some specific representations of their corresponding Clifford
+Algebras. Also, it will be argued later that the minimal matrix dimension of
+such representation, i.e. the minimal dimension of the Dirac Hamiltonian, can
+tell the specific type of this topological insulator. Therefore, as a whole all
+the classification work is reduced to the consideration of minimal matrix
+dimension of the representation of Clifford Algebra, in different spatial
+dimension.
+
+This work may be considered as a note to Chiu's dissertation\cite{Chiu2013a}.
+However, I do not guarantee that my interpretation is the same as his as I have
+modified and amended some parts to make the work more, in my opinion, congruous
+and systematic.
 
@@
 \begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
+    \item \textbf{Ten-fold Way} Introduces the result of Ten-fold way: why we
+        care only about anti-unitary symmetries, why there are ten different
+        classes.
+    \item \textbf{Classification by Dirac Mass Hamiltonians} gives comprehensive
+        account of how the Minimal Dirac Hamiltonian approach works, and how the
+        ten-fold way is derived in this approach.
+    \item \textbf{Looking Further} outlines the possible direction in classification
+        under unitary symmetries, and some other results.
 \end{enumerate}
-
-\section{Ten-fold Way}
-
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
-matrices by its response to three discrete symmetries: time reversal symmetry
-($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
-symmetry ($S$). As for those unitary symmetries, one can in principle, block
-diagonalize the Hamiltonian
-$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
-$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
-applied to those blocks and still holds.
-
-It will be find that, those $T,C$ are the only two meaningful non-unitary
-symmetries of the Single-particle system, and there are in total 10 different
-ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
-care about these three symmetries $T,C,$ and $S$.
-
-\subsection{The symmetries of Single-particle Hamiltonian}
-\label{sec:The symmetries of Single-particle Hamiltonian}
-
-According to Wigner's theorem, symmetries of physical system can either be
-unitary represented, or anti-unitarily represented. Here we show that in the
-case of anti-unitary symmetries, there are only 2 different kinds of them that a
-Single-particle Hamiltonian in first-quantized space can have. Actually, there
-can be more anti-unitary symmetries than this. But under reasonable assumptions,
-we can limit our discussion in only this two types.
-
-The Single-particle Hamiltonian acting on Fock space is
-\begin{equation}
-    \label{eq:H-2nd}
-    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
-\end{equation}
-where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
-are creation and annihilation operators acting on Fock space.
-
-Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
-to stress that it acts on Second-quantized Fock space.  A symmetry of the
-Hamiltonian, represented as an operator $\hat{U}$, must have:
-\begin{equation}
-    \label{eq:sym-in-2nd-1}
-    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
-\end{equation}
-
-We expect $\hat{U}$ to change the creation/annihilation operators in two different
-ways. First, it may only permute the creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-in-2nd-permute}
-\begin{align}
-    \label{eq:sym-in-2nd-permute-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
-    \label{eq:sym-in-2nd-permute-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi^\dagger_B u_{AB}
-\end{align}
-\end{subequations}
-Where $u$ is some matrix implementing the permutation.
-Or, it may interchange the role of creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-cc}
-\begin{align}
-    \label{eq:sym-cc-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
-    \label{eq:sym-cc-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi_B u^*_{BA}
-\end{align}
-\end{subequations}
-Where $u^*$ is some other matrix implementing the interchange. We write complex
-conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
-interchange), to conserve the anticommutation relation between
-$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
-should be a unitary matrix.
-
-Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
-conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
-symmetry, to be explained below.
-
-\paragraph{Case 1: Unitary Symmetry}
-
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives
-\begin{equation}
-    u H u^{-1} = H
-\end{equation}
-Therefore, in this case the symmetry is unitarily realized in First-quantized
-Hamiltonian $H_{AB}$.
-
-\paragraph{Case 2: Anti-unitary T Symmetry}
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
-$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
-\begin{equation}
-    u H^* u^\dagger = H
-\end{equation}
-Or:
-\begin{equation}
-    uK H u^t K = uK H (uK)^{-1} = H
-\end{equation}
-where $K$ is complex conjugation. This symmetry is called Time-reversal
-symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
-operator $T= uK$.
-
-\paragraph{Case 3: Anti-unitary C Symmetry}
-Assume the symmetry just interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\footnote{
-Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
-\id$ on 1st-quantized single-particle Hilbert space.
-}
-\begin{equation}
-    \label{eq:sym-C-cond}
-    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-
-Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
-in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
-simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
-\begin{equation}
-    u H^* u^\dagger = uK H (uK)^{-1} = -H
-\end{equation}
-This type of symmetry is called charge-conjugation symmetry. It is
-also called particle-hole symmetry in condensed matter physics. It is realized
-as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.
-
-\paragraph{Case 4: Unitary S Symmetry}
-Assume the symmetry now interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\begin{equation}
-    \label{eq:sym-S-cond}
-    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-and since $N>>2$, we have $\tr(H)=0$. Then
-\begin{equation}
-    u H u^\dagger = -H
-\end{equation}
-This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
-unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
-of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
-easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
-defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
-property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
-of Hamiltonian under $S$. But there is one exception. When the
-Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
-whole.
-
-\paragraph{Squaring of $T,C,S$} 
-Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
-hence it is only a phase as they are unitary.
-This can be viewed from two perspectives. First, we expect the system, after
-applying twice of symmetry operation $T/C$, should come back to the same state, except
-a possible phase difference. Second, $T^2/C^2$ commutes with all
-$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
-of unitary symmetries (to be explained later), therefore by Schur's lemma, they
-must be proportional to a constant, which is a phase.
-
-It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
-then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
-$e^{i\delta}=\pm1$.
-
-But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
-$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
-operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
-phase for $S^2$.\footnote{This is a bit troublesome. First we denote
-$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
-$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
-$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
-\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
-Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
-$S^2=-\varepsilon_C\varepsilon_T$.}
-
-\paragraph{Why Ten Classes} For the three unitary symmetries under
-consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
-$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
-undetermined (depending on the phase choice\footnote{To be explained later.} we
-give for $T$ and $C$). Therefore, there are in total 10 different possible ways
-that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
-to symbolize that the system does not follow $T$($C$) symmetry. Then
-$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
-$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
-different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
-
-\subsection{Dealing with Unitary Symmetries}
-\label{sec:Dealing with Unitary Symmetries}
-
-As mentioned, we could module out those unitary symmetries. This statement is
-made precise by the following theorem about unitary symmetries of the Hamiltonian.
-\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
-This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
-$\mathcal{V}_\lambda$ associated with the irrep (irreducible
-representations, labeled by $\lambda$) of $G_0$.
-\begin{equation}
-    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
-\end{equation}
-where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
-Denote the dimension of each irrep as $d_\lambda$.
-
-In each vector space $\mathcal{V}_\lambda$, one can choose a
-(orthogonal) basis of the form:
-\begin{equation}
-    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
-\end{equation}
-where
-\begin{itemize}
-    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
-        $k=1,\cdots,d_\lambda$,
-    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
-        $\alpha=1,\cdots,m_\lambda$.
-\end{itemize}
-\end{thm}
-Therefore, with all unitary symmetries ignored, we are classifying how
-Hamiltonian will be like when it respects, in 10 different ways, the
-combinations of $T,C,S$ symmetries.
-
-\paragraph{Differently Realized Anti-unitary Symmetries}
-It should be noted that there is still a freedom of unitary matrix that
-implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
-different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
-obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
-easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
-Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
-symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
-described in the theorem above, we only have one time-reversal symmetry. Similar
-analysis could be done for the $C$ symmetry as well.
-
-\paragraph{Translational Symmetry}
-
-Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
-
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
-
-The Hamiltonian in $k$-space that preserve these three discrete symmetries
-should follow\footnote{It is easy to anticipate the change $k\to -k$ for
-    anti-unitary symmetries, since they change the phase factor when one Fourier
-transform the Hamiltonian.}:
-\begin{subequations}
-\begin{align}
-    \label{eq:T-sym-Hk}
-    TH(k)T^{-1} &= H(-k) \\
-    \label{eq:C-sym-Hk}
-    CH(k)C^{-1} &= -H(-k) \\
-    \label{eq:S-sym-Hk}
-    SH(k)S^{-1} &= -S(k)
-\end{align}
-\end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
-
-\section{Classification by Dirac Mass Terms}
-\label{sec:The Minimal Hamiltonian Approach}
-
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
-We first note that different topological phases are distinguished by the closing
-and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
-flatten the energy spectrum to two bands of energy $\pm E$, the transition
-(closing of gap) will happen at some point where locally the energy is of a
-Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
-behavior. Then, a class of topological phases, or more specifically, a class of
-Hamiltonian matrix that shares the same topological invariant, can be
-\textit{represented} by the Dirac Hamiltonian in this class.
-
-\subsection{Crossing Spectrum and Edge Mode}
-\label{sec:Crossing Spectrum and Edge Mode}
-Here we show that the crossing spectrum characteristic of topological insulators
-can be characterized by a Dirac type Hamiltonian, and with this Dirac
-Hamiltonian we could find an Edge mode solution built into it.
-
-\paragraph{Crossing Spectrum and Dirac Hamiltonian}
-In some local region around the crossing point, the energy spectrum should look
-like:
-\begin{equation}
-    E = \pm \sqrt{\vb{k}^2 + M^2}
-\end{equation}
-where $\vb{k}$ is the crystal momentum and $M$ is some constant
-responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
-
-As has been analysed in most Quantum Mechanics textbook\footnote{See for
-    example, p.99 of \cite{Greiner1997}. Although their discussion is in
-dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
-relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
-use is:
-\begin{equation}
-    \label{eq:dirac-H}
-    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
-\end{equation}
-where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
-Clifford Algebra anti-commutation relation:
-\begin{equation}
-    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
-\end{equation}
-
-\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
-phase. First, it has a gapless state. Due to the anti-commutation relation of
-$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
-tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
-we choose not $\gamma_i^2=-1$, which would give non-sensible result
-$H_\text{Dirac}^2= -E^2\id$.}
-that the energies of Dirac Hamiltonian are:
-\begin{equation}
-    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
-\end{equation}
-Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
-gaped to gapless and again to gaped state. This shows that the $M$ is parameter
-controlling the quantum phase transition, and the system with $M<0$ or $M>0$
-possesses two different quantum phase.
-
-In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
-should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
-broken in that direction. Now the eigenvalue equation is:
-\begin{equation}
-    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
-    = E \Phi
-\end{equation}
-
-Past experience teaches us the ansatz (assuming
-$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
-does not blow up the wavefunction):
-\begin{equation}
-    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
-\end{equation}
-which after plugging inside the eigenvalue equation, leads to
-\begin{equation}
-    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
-    = E \phi
-\end{equation}
-After left multiplication of $\gamma_0$, we have:
-\begin{equation}
-    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
-    = E \gamma_0 \phi
-\end{equation}
-Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
-$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
-eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
-$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
-state to be a surface state, so we choose the $-1$ eigenvectors (denoted
-$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
-\begin{equation}
-    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
-\end{equation}
-As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
-have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
-eigenspaces:
-\begin{equation}
-    \label{eq:H-Dirac-surf}
-    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
-\end{equation}
-
-% \section{Collection of Calculation}
-% \label{sec:Collection of Calculation}
-% Here collects the calculations done throughout the whole notes.
-
-\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
-\label{sec:Homotopy to Minimal Dirac}
-
-\paragraph{Spectral Flattening} The classification of topological insulators
-concerns different classes of Hamiltonian that cannot be adiabatically changed
-to each without closing or opening of a gap. Hence, we could in general
-adiabatically change our parameters such that the spectrum of Hamiltonian is
-simplified into two bands of energy $\pm1$. Under this condition, we have
-$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
-for generating Clifford Algebras.
-
-\paragraph{Extension Problem with General Examples}
-The general theme of homotopy classification of classifying topological
-insulators are done by the considering the \textit{extension problem}, i.e.
-different ways to extend from a Clifford containing only symmetry operators, to
-a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
-in $0$-dimension, the empty space is nothing, hence
-$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
-Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
-classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
-mentioned earlier, hence the extension problem is from
-$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
-representations form some mathematical structure called \textit{classifying
-space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
-operators are maps starting from $T^0=S^0$. So our classified objects are
-different classes of maps from $S^0\to C_0$, which is mathematically captured by
-the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
-only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
-making it a candidate for generators of Clifford Algebra. The symmetry condition
-$\{H,S\}=0$ tells us now we have a extension problem of
-$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
-$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
-$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
-trivial topological insulators. The case for real symmetry classes are not too
-complicated and is concisely mentioned in \cite{Morimoto2013}.
-
-However, the method to obtain such classifying spaces are mathematical daunting
-and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
-since they should capture the essence of topological states.
-
-\paragraph{Extension Problem with Dirac Hamiltonian}
-The Dirac Hamiltonian
-\begin{equation}
-    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
-\end{equation}
-has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
-parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
-$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
-$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
-space having the same homotopy type of some classifying space (again!). For
-example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
-term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
-$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
-$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
-extension problem concerns different ways to extend the algebra
-$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
-unitarily non-equivalent mass terms. Detailed examples can be found in section
-III.C.1 of \cite{Chiu2016}.
-
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
-\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
-with extra mass term:
-\begin{equation}
-    \label{eq:H-spemt}
-    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
-    + \sum_{j=1}^D m_j\tilde{\gamma}_j
-\end{equation}
-Here, the parameter $M$ characterized the domain wall between different phases
-of topological insulators. The extra mass term $m_j$ represents a perturbation
-caused by disorder. I argue that we can do our classification in the following
-way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
-a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
-
-One best thing about this classification is that it can be done by considering
-only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
-argument is that, complex gamma matrices are of even dimension (except the
-trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
-\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
-\cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
-different type in the smaller dimension, or add trivial bands. In all cases, the
-triviality of topological insulators can be detected in minimal dimension, since
-adding trivial bands can be ignored (insensitive to addition of trivial bands),
-and the possible different types of matrices are limited.
-
-However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
-topological insulator, we need to increase the matrix dimension to consider
-multiple copies of the Dirac Hamiltonian. If the topological state is stable for
-an arbitrary copies, then this is a $\Z$ topological insulator. If the
-topological state is stable only of an odd number of copies, this is a $\Z_2$
-topological insulator.
-
-Another way to view this way of classification, is to look at the surface
-Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
-see if the surface mode can be gapped, so as to detect the topological
-properties of the bulk.
-
-\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
-\label{sec:Isomorphism}
-As with other classifications, we construct isomorphisms between Dirac matrices
-and Clifford Algebras, after which we are faced with an extension problem. The
-isomorphism is constructed now.
-\subsubsection{Symmetry Constraint}
-\label{sec:Symmetry Constraint}
-The Hamiltonian with extra mass term is
-\begin{equation}
-    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
-    + \sum_{i=1}^{d} k_i \gamma_i
-\end{equation}
-The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
-conditions on the gamma matrices:
-\begin{subequations}
-    \label{eq:sym-spemt}
-\begin{align}
-    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
-    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
-    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
-\end{align}
-\end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
-Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
-examples in action.
-
-\subsubsection{Examples of Constructing Isomorphism}
-\label{sec:iso-Examples}
-For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
-    \label{tab:generator-AI}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
-$J_3=iT\tilde{\gamma}_0$, we could verify that all
-$\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
-Table~\ref{tab:map-sym-cl}.
-
-Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
-\begin{equation}
-    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
-\end{equation}
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
-    \label{tab:generator-AII}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
-verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
-Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
-$K_i^2=-1$, $(K'_1)^2=1$. The following map
-\begin{equation}
-    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
-\end{equation}
-has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
-\begin{table}[htpb]
-    \centering
-    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
-    \label{tab:map-cl13-2-cl04}
-    $ \begin{tabu}{ c | *4{c} }
-        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
-        \hline
-        J_1    & -1      & \{\}    & \{\}    & \{\} \\
-        J_2    & ~       & -1      & \{\}    & \{\} \\
-        J_3    & ~       & ~       & -1      & \{\} \\
-        J_4    & ~       & ~       & ~       & -1
-    \end{tabu} $
-
-    where $\{\}$ means anticommute.
-\end{table}
-Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
-consistent with $G_{\mathrm{AII}} \cong
-\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.
-
-\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
-\label{sec:Complex Classes-iso}
-The general steps for constructing the isomorphism is presented here. First, we
-need to treat the situation of complex classes and real classes
-differently. The complex classes are isomorphic to complex Clifford Algebras,
-while the real classes are isomorphic to real Clifford Algebras. The reason for
-this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
-multiplication of complex matrices. Second, complex matrices come with a nature
-definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
-\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
-    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
-we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
-Algebras when dealing with real classes (which is the reason why they are named
-real classes).
-
-For complex classes, let $G_\#$ be the group generated by elements
-$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
-class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
-such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
-Clifford Algebra:
-\begin{align}
-    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
-    \mathrm{C\ell}_{d+D+1}(\C) \\
-    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
-    \cong  \mathrm{C\ell}_{d+D+2}(\C)
-\end{align}
-
-\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
-\label{sec:Real Classes-iso}
-
-For real classes, we need to include $i$, and symmetry operators $T,C$ in our
-group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
-
-We first note that, given a real vector space $V$, we can complexify a real space in
-two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
-which does not suit our purpose. The second is to find an almost complex
-structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
-$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
-way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
-$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
-operators on a real vector space naturally.
-
-Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
-where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
-squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
-naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.
-
-Then we discuss some tips that will useful for later calculation.
-\paragraph{Tips}
-\begin{enumerate}
-    \item Since all generator anticommute, all matrices either commute or
-        anticommute. So the Algebra is pretty simple.
-    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
-        or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
-    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
-        BA$. However, if $A$ and $B$ has something in common, then the above
-        condition breaks. This is like adding an "impurity" in it to change the
-        commutation/anticommutation relations.
-    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
-        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
-        candidates for symmetry operator are only a small finite set.
-        \label{enum:tips-4}
-\end{enumerate}
-
-\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
-construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
-in real vector space, they commute with $J_1=J$. Then, each gamma matrices
-should have an even number of Clifford Algebra generators other than $J_1$
-itself. Similarly, antiunitary symmetry operators should have an odd number of
-Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
-some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
-take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
-\ref{eq:sym-spemt}, and they give us the inspiration to set:
-\begin{equation}
-    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
-    \sum_{i=1}^d k_i J_2\tilde{J}_i
-\end{equation}
-Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
-$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
-And within this algebra, only $J_2$ is a possible candidate for symmetry
-operators, which satisfy equations~\ref{eq:sym-spemt} (use
-tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
-time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
-class $\mathrm{AII}$. Therefore, the map:
-\begin{align}
-    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
-    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
-    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
-\end{align}
-is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
-$\mathrm{AII}$. The inverse map can be found easily. We first solve some
-formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
-\begin{equation}
-    a+bi \to a \begin{pmatrix}
-        1 & \\ & 1
-    \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
-    \end{pmatrix} = a\id + b J
-\end{equation}
-Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
-real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
-$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
-\begin{equation}
-    \{\Gamma_T,\Gamma_C\} = 0
-\end{equation}
-
-Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
-\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
-Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
-\begin{align}
-    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
-    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
-    \Gamma_T &\to J_2 \nonumber\\
-    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
-    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
-\end{align}
-is the desired inverse map.
-
-\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
-more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
-Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
-The rest is exactly the same as in class $\mathrm{AII}$.
-
-All other classes can be treated similarly, so we do not repeat the calculation
-and only list the result in Table~\ref{tab:map-sym-cl}.
-\begin{table}[htpb]
-    \centering
-    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
-    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
-    Algebra. Also, only one direction of mapping is shown. The inverse map can
-    be easily constructed accordingly. The complex class are also added for
-    convenience.}
-    \label{tab:map-sym-cl}
-    \begin{tabular}{c | c c c | l | c }
-        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
-        \hline 
-        D & $0$ & $+$ & $0$ & 
-        $\tilde{J}_1\to\Gamma_C$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
-        DIII & $-$ & $+$ & $1$ & 
-        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
-        AII & $-$ & $0$ & $0$ & 
-        $J_2\to \Gamma_T$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
-        CII & $-$ & $-$ & $1$ & 
-        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
-        C & $0$ & $-$ & $0$ & 
-        $J_2\to \Gamma_C$, 
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
-        CI & $+$ & $-$ & $1$ & 
-        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
-        AI & $+$ & $0$ & $0$ & 
-        $\tilde{J}_1\to \Gamma_T$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
-        BDI & $+$ & $+$ & $1$ & 
-        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
-        \hline
-        A & $0$ & $0$ & $0$ & 
-        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
-        AIII & $0$ & $0$ & $1$ & 
-        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\subsection{Classification in 1-dimension}
-\label{sec:Classification in 1-dimension}
-Classification of $1$ dimension is the simplest, since the minimal matrix
-dimension will mostly be $2$, which means we can use the familiar Pauli matrices
-directly.
-
-\paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.
-
-\paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
-topologically non-trivial. Now we consider the state with arbitrary copies of it.
-\begin{equation}
-    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
-    S=\sigma_z\otimes\id_n
-\end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
-
-The above are for complex classes. For real classes, we have to be careful,
-since one generator $J_1$ is taken up by $i$.
-
-\paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
-$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
-\end{equation}
-with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
-We let:
-\begin{equation}
-    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
-SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
-$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
-the remaining choice are acceptable, considering $T$ and $C$.}. Consider
-arbitrary copies of it:
-\begin{equation}
-    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
-    k_x\sigma_y\otimes\id_2)\otimes\id_n
-\end{equation}
-with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
-$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
-SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
-Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
-with $C$.}. Therefore, this is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
-of it:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
-\end{equation}
-with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
-$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
-$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
-complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{D}$} We let:
-\begin{equation}
-    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
-it:
-\begin{equation}
-    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
-Hence, this is a $\Z_2$ topological insulator.
-
-To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
-But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
-\paragraph{Class $\mathrm{DIII}$} We let:
-\begin{equation}
-    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
-form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
-this does not commute with $T$. Hence, there is no SPEMT. Now consider two
-copies of it:
-\begin{equation}
-    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
-this is a $\Z_2$ topological insulator.
-
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
-\begin{table}[htpb]
-    \centering
-    \caption{Topological Insulators in $d=1$}
-    \label{tab:ti-d=1}
-    \begin{tabular}{c | c c c | c }
-        Class($\#$) & T & C & S & $d=1$ \\
-        \hline 
-        A & $0$ & $0$ & $0$ & $0$ \\
-        AIII & $0$ & $0$ & $1$ & $\Z$ \\
-        \hline
-        D & $0$ & $+$ & $0$ & $\Z_2$ \\
-        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
-        AII & $-$ & $0$ & $0$ & $0$ \\
-        CII & $-$ & $-$ & $1$ & $\Z$ \\
-        C & $0$ & $-$ & $0$ & $0$ \\
-        CI & $+$ & $-$ & $1$ & $0$ \\
-        AI & $+$ & $0$ & $0$ & $0$ \\
-        BDI & $+$ & $+$ & $1$ & $\Z$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
-\subsection{Classification in Arbitrary Dimension}
-\label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
-generalized to classification in arbitrary dimensions. In $K$-theoretic
-classification, the extension problem is not affected when tensored with some
-other algebras. Specifically, for complex classes, the extension problem of
-$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
-III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
-
-Now, let us write $\sim$ to represent the equivalence between two extension
-problems.  The Complex Clifford Algebra has a periodicity of $2$:
-\begin{equation}
-    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
-    \mathrm{C\ell}_{2}(\C)
-\end{equation}
-The Real Clifford Algebra has a periodicity of $8$:
-\begin{equation}
-    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
-\end{equation}
-This two relation means, the extension problem will be the same with respect to
-a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
-classes. Hence the classification of topological insulators need only be done
-with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
-symmetry classes, i.e.
-\begin{subequations}
-    \label{eq:cli-periodic}
-\begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
-\end{align}
-\end{subequations}
-Another useful property is:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
-\end{align}
-This property tells us that Clifford Algebra basically depends only on the
-difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
-example, we have (let $n$ be an arbitrary integer):
-$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
-\begin{align}
-    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
-    \nonumber\\
-    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
-\end{align}
-and
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
-    \nonumber\\
-    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
-    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
-\end{align}
-Now we tries to connect the two chains together. We note further that the
-Clifford Algebra has the following properties:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
-    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
-\end{align}
-Then:
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
-    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
-    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
-    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
-\end{align}
-Therefore,
-$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
-connecting the two chains. If we compare this carefully with
-Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
-prove the dimension-shift feature of classification:
-\begin{align}
-    \label{eq:cli-Chain1}
-    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
-    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
-    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
-    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
-\end{align}
-We need one more property:
-\begin{equation}
-    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
-    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
-\end{equation}
-Then
-\begin{equation}
-    \label{eq:cli-Chain2}
-    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
-\end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|c|cccccccc|ccc|}
-\hline
-\multicolumn{12}{|c|}{
-The original classification table} \\ \hline
-   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
-\hline\hline
-  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
-  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline
-
-  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
-  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
-  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
-  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
-  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
-  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
-  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
-  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
-   \\
-\hline
-\end{tabular}
-\caption{The original classification table of topological insulators and
-superconductors}
-\label{tab:master-table2}
-\end{center}
-\end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
-
-\bibliography{../../library}{}
-\bibliographystyle{alphaurl}
-% \begin{thebibliography}{1}
-% 	\bibitem{book} 
-% \end{thebibliography}
-\printnomenclature
-
-\end{document}

### 2017-05-16 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
[major] Solved how to distinguish Z and Z2.

--- 2017-05-13 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chiu.SPEMT.tex
@@
 \abstract{
-    In this paper, I will review the use of minimal Dirac Hamiltonian method
-    (developed by Dr. Chiu in \cite{Chiu2013a}), which accounts for the
-    mechanism behind the homotopic classification of topological insulators. I
-    start with a introduction to the general framework of "Tenfold Way", and
-    briefly outline the two approaches to classification of topological
-    insulators. Then, I will argue step by step how Minimal Dirac Hamiltonian
-    approach expose the mechanism of homotopic classification of topological
-    insulators.
+    \todo{Haha, leave this until later.}
 }
-% TODO: add ref for Clifford Algebra.
 \tableofcontents
 
-\section{Outline}
-\label{sec:Outline}
+\input{chapters/introduction.tex}
+\input{chapters/chap-2.tex}
+\input{chapters/chap-3.tex}
+\input{chapters/chap-4.tex}
 
-The classification of topological insulators in non-interacting system is in
-effect a classification of Hamiltonian matrix. The simple case considered here
-is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
-symmetries. Specifically, when we module out any unitary symmetries of the
-Hamiltonian, the number of meaningful anti-unitary symmetries are limited, and
-we only classify topological insulators based on how our Hamiltonian matrix
-responses to these anti-unitary symmetries.
-
-There are two classical approaches towards this classification. The first is to
-examine the existence of Anderson delocalization at the boundary of the
-insulator, because the existence of surface conducting state is the signature of
-topological insulators and the Anderson localization is the obstruction that
-\todo{Be more specific about this and check some facts.}
-surface conducting states must overcome. This approach uses the Nonlinear Sigma
-Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
-when can a localization-breaking term can be added to NL$\sigma$Ms.
-
-The second approach is to use homotopy theory to classify classes Hamiltonians under
-continuous deformation, more specifically, under adiabatical change of
-Hamiltonians. This method is most elegant but most mathematical demanding
-approach compared with others, because calculating homotopy groups, and homotopy theories in
-general are notorious hard. Also, one has to use $K$-theory, because of
-something physical is enlarging those distinct classes of Hamiltonian. To be
-more specific.
-
-But the key to understand topological insulators, are not necessarily the
-Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
-without boundary. Therefore, it should always be zero because of the Stokes theorem,
-unless inside this manifold there is somewhere where the formula for Chern
-number got "blown up", and it is just this locally "blown up" point that is
-responsible for the nonzero Chern number, and for the non-triviality of
-topological insulators.
-
-Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
-energy zero level to the crossing point, in only the low energy physics. We
-expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian.
-\todo{Argument based on Klein-Gorden equation to get the Dirac Hamiltonian}
-
-An amazing fact happens, when one consider the gamma matrices in Dirac
-Hamiltonian, the anti-unitary symmetry operators, and their anti-commutation
-relations. Together they are proved to be isomorphic to some Clifford Algebra over
-$\R$ or $\C$, depending on the situation. And consequently our Hamiltonian and
-symmetry operators, all become some specific representations of their
-corresponding Clifford Algebra. Also, it will be illustrated later that the
-minimal matrix dimension of such representation, i.e. the minimal dimension of
-the Dirac Hamiltonian, can tell the specific type of this topological
-insulator. Therefore, as a whole all the classification work is reduced to the
-consideration of minimal matrix dimension of the representation of Clifford
-Algebra, in different spatial dimension.
-\todo{Cautious, we have two dimensions here: matrix and spatial.}
-
-\paragraph{Structure of this work} This work are divided into several parts.
-\begin{enumerate}
-    \item \textbf{Ten-fold Way} introduces the result of Ten-fold way. 
-    \item \textbf{Original Approach} gives brief idea of how the Nonlinear Sigma
-        Models Approach and the Homotopy/$K$-theory approach work.
-    \item \textbf{Minimal Dirac Hamiltonian} gives comprehensive account of how
-        the Minimal Dirac Hamiltonian approach works, and how the ten-fold way
-        is derived in this approach.
-    \item \textbf{Outlook} outlines the possible direction in classification
-        under unitary symmetries, and the problems we faced when interaction is
-        turned on.
-\end{enumerate}
-
-\section{Ten-fold Way}
-
-The classification of topological phases with different non-unitary symmetries
-in non-interacting picture, are in essence, the classification of $N\times N$
-matrices by its response to three discrete symmetries: time reversal symmetry
-($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
-symmetry ($S$). As for those unitary symmetries, one can in principle, block
-diagonalize the Hamiltonian
-$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
-$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
-applied to those blocks and still holds.
-
-It will be find that, those $T,C$ are the only two meaningful non-unitary
-symmetries of the Single-particle system, and there are in total 10 different
-ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
-care about these three symmetries $T,C,$ and $S$.
-
-\subsection{The symmetries of Single-particle Hamiltonian}
-\label{sec:The symmetries of Single-particle Hamiltonian}
-
-According to Wigner's theorem, symmetries of physical system can either be
-unitary represented, or anti-unitarily represented. Here we show that in the
-case of anti-unitary symmetries, there are only 2 different kinds of them that a
-Single-particle Hamiltonian in first-quantized space can have. Actually, there
-can be more anti-unitary symmetries than this. But under reasonable assumptions,
-we can limit our discussion in only this two types.
-
-The Single-particle Hamiltonian acting on Fock space is
-\begin{equation}
-    \label{eq:H-2nd}
-    \hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
-\end{equation}
-where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
-are creation and annihilation operators acting on Fock space.
-
-Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
-to stress that it acts on Second-quantized Fock space.  A symmetry of the
-Hamiltonian, represented as an operator $\hat{U}$, must have:
-\begin{equation}
-    \label{eq:sym-in-2nd-1}
-    \hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
-\end{equation}
-
-We expect $\hat{U}$ to change the creation/annihilation operators in two different
-ways. First, it may only permute the creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-in-2nd-permute}
-\begin{align}
-    \label{eq:sym-in-2nd-permute-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^\dagger)_{AB} \hat\psi_B \\
-    \label{eq:sym-in-2nd-permute-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi^\dagger_B u_{AB}
-\end{align}
-\end{subequations}
-Where $u$ is some matrix implementing the permutation.
-Or, it may interchange the role of creation/annihilation operators:
-\begin{subequations}
-\label{eq:sym-cc}
-\begin{align}
-    \label{eq:sym-cc-1}
-    \hat{\psi}'_A = 
-    \hat{U} \hat\psi_A \hat{U}^{-1} &=
-    \sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
-    \label{eq:sym-cc-2}
-    \hat\psi'^\dagger_A =
-    \hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
-    \sum_B  \hat\psi_B u^*_{BA}
-\end{align}
-\end{subequations}
-Where $u^*$ is some other matrix implementing the interchange. We write complex
-conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
-interchange), to conserve the anticommutation relation between
-$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
-should be a unitary matrix.
-
-Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
-conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
-symmetry, to be explained below.
-
-\paragraph{Case 1: Unitary Symmetry}
-
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives
-\begin{equation}
-    u H u^{-1} = H
-\end{equation}
-Therefore, in this case the symmetry is unitarily realized in First-quantized
-Hamiltonian $H_{AB}$.
-
-\paragraph{Case 2: Anti-unitary T Symmetry}
-Assume the symmetry just permutes the creation/annihilation operators, as in
-equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
-Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
-relation~\ref{eq:sym-in-2nd-permute} plugged into
-equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
-$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
-\begin{equation}
-    u H^* u^\dagger = H
-\end{equation}
-Or:
-\begin{equation}
-    uK H u^t K = uK H (uK)^{-1} = H
-\end{equation}
-where $K$ is complex conjugation. This symmetry is called Time-reversal
-symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
-operator $T= uK$.
-
-\paragraph{Case 3: Anti-unitary C Symmetry}
-Assume the symmetry just interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\footnote{
-Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
-\id$ on 1st-quantized single-particle Hilbert space.
-}
-\begin{equation}
-    \label{eq:sym-C-cond}
-    u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-
-Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
-in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
-simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
-\begin{equation}
-    u H^* u^\dagger = uK H (uK)^{-1} = -H
-\end{equation}
-This type of symmetry is called charge-conjugation symmetry. It is
-also called particle-hole symmetry in condensed matter physics. It is realized
-as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.
-
-\paragraph{Case 4: Unitary S Symmetry}
-Assume the symmetry now interchange the creation/annihilation operators, as in
-equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
-Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
-relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
-\begin{equation}
-    \label{eq:sym-S-cond}
-    u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
-\end{equation}
-and since $N>>2$, we have $\tr(H)=0$. Then
-\begin{equation}
-    u H u^\dagger = -H
-\end{equation}
-This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
-unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
-of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
-easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
-defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
-property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
-of Hamiltonian under $S$. But there is one exception. When the
-Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
-whole.
-
-\paragraph{Squaring of $T,C,S$} 
-Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
-hence it is only a phase as they are unitary.
-This can be viewed from two perspectives. First, we expect the system, after
-applying twice of symmetry operation $T/C$, should come back to the same state, except
-a possible phase difference. Second, $T^2/C^2$ commutes with all
-$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
-of unitary symmetries (to be explained later), therefore by Schur's lemma, they
-must be proportional to a constant, which is a phase.
-
-It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
-then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
-$e^{i\delta}=\pm1$.
-
-But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
-$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
-operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
-phase for $S^2$.\footnote{This is a bit troublesome. First we denote
-$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
-$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
-$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
-\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
-Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
-$S^2=-\varepsilon_C\varepsilon_T$.}
-
-\paragraph{Why Ten Classes} For the three unitary symmetries under
-consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
-$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
-undetermined (depending on the phase choice\footnote{To be explained later.} we
-give for $T$ and $C$). Therefore, there are in total 10 different possible ways
-that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
-to symbolize that the system does not follow $T$($C$) symmetry. Then
-$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
-$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
-different possible ways. In each way the topological invariants of the
-Hamiltonian respecting these symmetries are tabulated in figure \todo{add the
-master table}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$, etc.),
-and their properties in different spatial dimensions respect a periodic
-structure. For the upper two classes, they are named complex classes and respect
-a $2$-fold period. The Lower eight classes are named real classes and respect a
-$8$-fold period, which is why we only listed the first $0\to 7$ spatial
-dimensions.
-
-\subsection{Dealing with Unitary Symmetries}
-\label{sec:Dealing with Unitary Symmetries}
-
-As mentioned, we could module out those unitary symmetries. This statement is
-made precise by the following theorem about unitary symmetries of the Hamiltonian.
-\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
-This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
-$\mathcal{V}_\lambda$ associated with the irrep (irreducible
-representations, labeled by $\lambda$) of $G_0$.
-\begin{equation}
-    \mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
-\end{equation}
-where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
-Denote the dimension of each irrep as $d_\lambda$.
-
-In each vector space $\mathcal{V}_\lambda$, one can choose a
-(orthogonal) basis of the form:
-\begin{equation}
-    \ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
-\end{equation}
-where
-\begin{itemize}
-    \item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
-        $k=1,\cdots,d_\lambda$,
-    \item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
-        $\alpha=1,\cdots,m_\lambda$.
-\end{itemize}
-\end{thm}
-Therefore, with all unitary symmetries ignored, we are classifying how
-Hamiltonian will be like when it respects, in 10 different ways, the
-combinations of $T,C,S$ symmetries.
-
-\paragraph{Differently Realized Anti-unitary Symmetries}
-It should be noted that there is still a freedom of unitary matrix that
-implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
-different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
-obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
-easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
-Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
-symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
-described in the theorem above, we only have one time-reversal symmetry. Similar
-analysis could be done for the $C$ symmetry as well.
-
-\paragraph{Translational Symmetry}
-
-Since we are classifying in the solids, it is natural to expect translational
-symmetry to present. Also, the addition of translational symmetry do not alter
-our classification, which is based on non-unitary symmetries, but also make this
-classification more convenient to be done.
-
-With translational symmetry added,\todo{To be added}
-%TODO why still unitary symmetries.
-
-The Hamiltonian in $k$-space that preserve these three discrete symmetries
-should follow\footnote{It is easy to anticipate the change $k\to -k$ for
-    anti-unitary symmetries, since they change the phase factor when one Fourier
-transform the Hamiltonian.}:
-\begin{subequations}
-\begin{align}
-    \label{eq:T-sym-Hk}
-    TH(k)T^{-1} &= H(-k) \\
-    \label{eq:C-sym-Hk}
-    CH(k)C^{-1} &= -H(-k) \\
-    \label{eq:S-sym-Hk}
-    SH(k)S^{-1} &= -S(k)
-\end{align}
-\end{subequations}
-
-\subsection{The Tenfold Way}
-\label{sec:The Tenfold Way}
-
-\todo{Add the table, and the meaning of each Hamiltonian, and the class
-of each evolutionary operators}%
-
-\subsection{The Two Original Approaches}
-\label{sec:The Two Original Approaches}
-\todo{Add this}
-
-\section{Classification by Dirac Mass Terms}
-\label{sec:The Minimal Hamiltonian Approach}
-
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
-We first note that different topological phases are distinguished by the closing
-and then opening of the gap, i.e. a quantum phase transition. If we adiabatically
-flatten the energy spectrum to two bands of energy $\pm E$, the transition
-(closing of gap) will happen at some point where locally the energy is of a
-Dirac cone type. Therefore, the Dirac Hamiltonian captures this transition
-behavior. Then, a class of topological phases, or more specifically, a class of
-Hamiltonian matrix that shares the same topological invariant, can be
-\textit{represented} by the Dirac Hamiltonian in this class.
-
-\subsection{Crossing Spectrum and Edge Mode}
-\label{sec:Crossing Spectrum and Edge Mode}
-Here we show that the crossing spectrum characteristic of topological insulators
-can be characterized by a Dirac type Hamiltonian, and with this Dirac
-Hamiltonian we could find an Edge mode solution built into it.
-
-\paragraph{Crossing Spectrum and Dirac Hamiltonian}
-In some local region around the crossing point, the energy spectrum should look
-like:
-\begin{equation}
-    E = \pm \sqrt{\vb{k}^2 + M^2}
-\end{equation}
-where $\vb{k}$ is the crystal momentum and $M$ is some constant
-responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
-
-As has been analysed in most Quantum Mechanics textbook\footnote{See for
-    example, p.99 of \cite{Greiner1997}. Although their discussion is in
-dimension $d=3$, it is easy to generalize it to any dimension.}, this energy-momentum
-relationship requires a Dirac type Hamiltonian. Then, the Dirac Hamiltonian we
-use is:
-\begin{equation}
-    \label{eq:dirac-H}
-    H_\text{Dirac} = M\gamma_0 + \sum_{i=1}^d k_i\gamma_i
-\end{equation}
-where $d$ is the spatial dimension of the physical system, $\gamma_i$ obeys the
-Clifford Algebra anti-commutation relation:
-\begin{equation}
-    \{\gamma_i,\gamma_j\} = 2\delta_{i,j}\id
-\end{equation}
-
-\paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
-phase. First, it has a gapless state. Due to the anti-commutation relation of
-$\gamma_i$, we can show\footnote{Note that $H_\text{Dirac}^2= E^2\id$, this
-tells us it can only have eigenvalues $E_\pm$. Note that this also explains why
-we choose not $\gamma_i^2=-1$, which would give non-sensible result
-$H_\text{Dirac}^2= -E^2\id$.}
-that the energies of Dirac Hamiltonian are:
-\begin{equation}
-    E_\pm = \pm\sqrt{M^2+\sum_{i=1}^d k^2_i}
-\end{equation}
-Therefore, as $M$ varies from negative to $0$ to positive, the system goes from
-gaped to gapless and again to gaped state. This shows that the $M$ is parameter
-controlling the quantum phase transition, and the system with $M<0$ or $M>0$
-possesses two different quantum phase.
-
-In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
-should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
-broken in that direction. Now the eigenvalue equation is:
-\begin{equation}
-    ( M\gamma_0 + \sum_{i=1}^{d-1} k_i\gamma_i - i\partial_{x_d}\gamma_d ) \Phi
-    = E \Phi
-\end{equation}
-
-Past experience teaches us the ansatz (assuming
-$M(x_d)$ goes to $\pm\infty$ as $x_d\to\pm\infty$, so that the leading term below
-does not blow up the wavefunction):
-\begin{equation}
-    \Phi = e^{-\int_0^{x_d} M(x'_d)\dd{x'_d}} \phi(x_1,\cdots,x_{d-1})
-\end{equation}
-which after plugging inside the eigenvalue equation, leads to
-\begin{equation}
-    \left( M(x_d)(\gamma_0 + i\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i \right) \phi
-    = E \phi
-\end{equation}
-After left multiplication of $\gamma_0$, we have:
-\begin{equation}
-    \left( M(\id + i\gamma_0\gamma_d) + \sum_{i=1}^{d-1} k_i\gamma_i  \right) \phi
-    = E \gamma_0 \phi
-\end{equation}
-Since $i\gamma_0\gamma_d$ squares to $1$, it has eigenvalues $\pm1$. Also,
-$i\gamma_0\gamma_d$ and $\gamma_0$ anticommute, so they share the same
-eigenspaces with $\gamma_0$ mapping all the $+1$ eigenvectors of
-$i\gamma_0\gamma_d$ to the $-1$ eigenvectors and vice versa. Now we want this
-state to be a surface state, so we choose the $-1$ eigenvectors (denoted
-$\phi_-$) of $i\gamma_0\gamma_d$ to kill the bulk term. This leads to:
-\begin{equation}
-    \gamma_0 \sum_{i=1}^{d-1} k_i\gamma_i \phi_- = \gamma_0 E\phi_-
-\end{equation}
-As mentioned, $\gamma_0$ switches the two eigenspaces, so we must necessarily
-have a surface Dirac Hamiltonian, by projecting all those matrices to the $-1$
-eigenspaces:
-\begin{equation}
-    \label{eq:H-Dirac-surf}
-    H_\mathrm{surf} \phi_- = \sum_{i=1}^{d-1} \Gamma_{i-} \phi_- = E \phi_-
-\end{equation}
-
-% \section{Collection of Calculation}
-% \label{sec:Collection of Calculation}
-% Here collects the calculations done throughout the whole notes.
-
-\subsection{From Homotopy Classification to Minimal Dirac Hamiltonian Method}
-\label{sec:Homotopy to Minimal Dirac}
-
-\paragraph{Spectral Flattening} The classification of topological insulators
-concerns different classes of Hamiltonian that cannot be adiabatically changed
-to each without closing or opening of a gap. Hence, we could in general
-adiabatically change our parameters such that the spectrum of Hamiltonian is
-simplified into two bands of energy $\pm1$. Under this condition, we have
-$H^2=1$, which already hints that the Hamiltonian itself is a viable candidate
-for generating Clifford Algebras.
-
-\paragraph{Extension Problem with General Examples}
-The general theme of homotopy classification of classifying topological
-insulators are done by the considering the \textit{extension problem}, i.e.
-different ways to extend from a Clifford containing only symmetry operators, to
-a Clifford Algebra containing Hamiltonians. For example, for class $\mathrm{A}$
-in $0$-dimension, the empty space is nothing, hence
-$\mathrm{C\ell}_{0}(\C)$\footnote{The reason for using different Clifford
-Algebra ($\mathrm{C\ell}(\R)$ or $\mathrm{C\ell}(\C)$ for different symmetry
-classes will be explained in section~\ref{sec:Isomorphism}.}. And $H^2=1$ as
-mentioned earlier, hence the extension problem is from
-$\mathrm{C\ell}_{0}(\C)\to \mathrm{C\ell}_{1}(\C)$, whose possible
-representations form some mathematical structure called \textit{classifying
-space} $C_0$ \cite{Morimoto2013}. And since we are in $0$-dimension, all
-operators are maps starting from $T^0=S^0$. So our classified objects are
-different classes of maps from $S^0\to C_0$, which is mathematically captured by
-the $0$-th homotopy group $\pi_0(C_0)=\Z$. For class $\mathrm{AIII}$ which has
-only chiral symmetry operator $S$, we choose a phase such that $S^2=1$, i.e.
-making it a candidate for generators of Clifford Algebra. The symmetry condition
-$\{H,S\}=0$ tells us now we have a extension problem of
-$\mathrm{C\ell}_{1}(\C)\to \mathrm{C\ell}_{2}(\C)$, whose classifying space is
-$C_1$, and has $\pi_0(C_1)=0$. Therefore, in $0$-dimension, the class
-$\mathrm{A}$ has $\Z$ topological insulators and class $\mathrm{AIII}$ has
-trivial topological insulators. The case for real symmetry classes are not too
-complicated and is concisely mentioned in \cite{Morimoto2013}.
-
-However, the method to obtain such classifying spaces are mathematical daunting
-and requires $K$-theory. We try to simplify it by looking at Dirac Hamiltonians,
-since they should capture the essence of topological states.
-
-\paragraph{Extension Problem with Dirac Hamiltonian}
-The Dirac Hamiltonian
-\begin{equation}
-    H = \vec{k}\vdot \vec{\gamma} + m\tilde{\gamma}_0
-\end{equation}
-has a gap closing and opening mass term $m\tilde{\gamma}_0(r)$, depending on some
-parameter $r$. Suppose that we have a domain wall squeezed by two bulk regions
-$A$ and $B$. Now as the parameter $r$ changes freely from region $A$ to region
-$B$, the symmetry condition will force the matrix $\gamma_0$ to explorer some
-space having the same homotopy type of some classifying space (again!). For
-example, for class $\mathrm{A}$ in $2$-dimension, the Hamiltonian without mass
-term ($k_1\gamma_1 + k_2\gamma_2$) consists of two gamma matrices, generating a
-$\mathrm{C\ell}_{2}(\C)$, whereas adding the mass term, we have
-$\mathrm{C\ell}_{3}(\C)$. Since there is no symmetry in class $\mathrm{A}$, the
-extension problem concerns different ways to extend the algebra
-$\mathrm{C\ell}_{2}(\C)\to \mathrm{C\ell}_{3}(\C)$, which tells us the number of
-unitarily non-equivalent mass terms. Detailed examples can be found in section
-III.C.1 of \cite{Chiu2016}.
-
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\cite{Kennedy2015}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
-\paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
-with extra mass term:
-\begin{equation}
-    \label{eq:H-spemt}
-    H = M\tilde{\gamma}_0 + \sum_{i=1}^{d} k_i \gamma_i 
-    + \sum_{j=1}^D m_j\tilde{\gamma}_j
-\end{equation}
-Here, the parameter $M$ characterized the domain wall between different phases
-of topological insulators. The extra mass term $m_j$ represents a perturbation
-caused by disorder. I argue that we can do our classification in the following
-way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
-a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
-
-One best thing about this classification is that it can be done by considering
-only the minimal matrix dimension of those gamma matrices in Hamiltonian. The
-argument is that, complex gamma matrices are of even dimension (except the
-trivial cases of $\mathrm{C\ell}_{0/1}(\C)$)\footnote{See this post
-\cite{PhysicsStackExchange}, or the p.12 and Theorem in p.5 of this
-\cite{West1998}.}. Therefore, gamma matrices of different
-matrix dimension are built by tensor products of Pauli matrices.\todo{make it
-more rigorous!} Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
-different type in the smaller dimension, or add trivial bands. In all cases, the
-triviality of topological insulators can be detected in minimal dimension, since
-adding trivial bands can be ignored (insensitive to addition of trivial bands),
-and the possible different types of matrices are limited.
-
-However, to distinguish between a $\Z$ topological insulator and a $\Z_2$
-topological insulator, we need to increase the matrix dimension to consider
-multiple copies of the Dirac Hamiltonian. If the topological state is stable for
-an arbitrary copies, then this is a $\Z$ topological insulator. If the
-topological state is stable only of an odd number of copies, this is a $\Z_2$
-topological insulator.
-
-Another way to view this way of classification, is to look at the surface
-Dirac Hamiltonian \ref{eq:H-Dirac-surf}. Then the above mentioned approach is to
-see if the surface mode can be gapped, so as to detect the topological
-properties of the bulk.
-
-\subsection{Isomorphism between Symmetry Classes and Clifford Algebras}
-\label{sec:Isomorphism}
-As with other classifications, we construct isomorphisms between Dirac matrices
-and Clifford Algebras, after which we are faced with an extension problem. The
-isomorphism is constructed now.
-\subsubsection{Symmetry Constraint}
-\label{sec:Symmetry Constraint}
-The Hamiltonian with extra mass term is
-\begin{equation}
-    H = M\tilde{\gamma}_0 + \sum_{j=1}^D m_j\tilde{\gamma}_j
-    + \sum_{i=1}^{d} k_i \gamma_i
-\end{equation}
-The symmetry properties \ref{eq:T-sym-Hk},\ref{eq:C-sym-Hk} give the following
-conditions on the gamma matrices:
-\begin{subequations}
-    \label{eq:sym-spemt}
-\begin{align}
-    & \{T,\gamma_i \} = 0,\, [C,\tilde{\gamma}_j] =0 \\
-    & \{C,\tilde{\gamma}_j \} = 0,\, [C,\gamma_i] =0 \\
-    & \{S,\tilde{\gamma}_j \} = \{S,\gamma_i\} =0
-\end{align}
-\end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
-Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
-examples in action.
-
-\subsubsection{Examples of Constructing Isomorphism}
-\label{sec:iso-Examples}
-For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{AI}$ with $d=1,D=0$}
-    \label{tab:generator-AI}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=1     & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$,
-$J_3=iT\tilde{\gamma}_0$, we could verify that all
-$\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
-Table~\ref{tab:map-sym-cl}.
-
-Another example. For class AII ($T^2=-1$, $C=0,S=0$) in $d=1,D=0$, we have:
-\begin{equation}
-    G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
-\end{equation}
-We have its (anti)commutation relations listed in Table~\ref{tab:generator-AII}.
-\begin{table}[htpb]
-    \centering
-    \caption{Generators in $G_{\mathrm{AII}}$ with $d=1,D=0$}
-    \label{tab:generator-AII}
-    $ \begin{tabu}{ c | *4{c} }
-        ~                & i      & T         & \tilde{\gamma}_0       & \gamma_1 \\
-        \hline
-        i                & i^2=-1 & \{i,T\}=0 & [i,\tilde{\gamma}_0]=0 & [i,\gamma_1]=0 \\
-        T                & ~      & T^2=-1    & [T,\tilde{\gamma}_0]=0 & \{T,\gamma_1\}=0 \\
-        \tilde{\gamma}_0 & ~      & ~         & \tilde{\gamma}_0^2 =1  & \{\tilde{\gamma}_0,\gamma_1\}=0 \\
-        \gamma_1         & ~      & ~         & ~                      & \gamma_1^2=1
-    \end{tabu} $
-\end{table}
-Now with $J_4 = T\tilde{\gamma}_0\gamma_1$, $J_3=iT\tilde{\gamma}_0$, we could
-verify that all $\{i,T,J_3,J_4\}$ anticommute with each other, and
-$J_3^2=J_4^2=-1$. So together they generate the algebra $\mathrm{C\ell}_{0,4}(\R)$.
-Notice that, assume we have $\mathrm{C\ell}_{1,3}(\R)=\{K_1,K_2,K_3,K'_1\}$, and
-$K_i^2=-1$, $(K'_1)^2=1$. The following map
-\begin{equation}
-    J_1 = K_1,\, J_2 = K_2,\, J_3=K_3,\, J_4=K_1K_2K_3K'_1
-\end{equation}
-has the property shown in the table~\ref{tab:map-cl13-2-cl04}.
-\begin{table}[htpb]
-    \centering
-    \caption{Map from $\mathrm{C\ell}_{1,3}(\R)$ to $\mathrm{C\ell}_{0,4}(\R)$.}
-    \label{tab:map-cl13-2-cl04}
-    $ \begin{tabu}{ c | *4{c} }
-        ~      & J_1=K_1 & J_2=K_2 & J_3=K_3 & J_4 = K_1K_2K_3K'_1\\
-        \hline
-        J_1    & -1      & \{\}    & \{\}    & \{\} \\
-        J_2    & ~       & -1      & \{\}    & \{\} \\
-        J_3    & ~       & ~       & -1      & \{\} \\
-        J_4    & ~       & ~       & ~       & -1
-    \end{tabu} $
-
-    where $\{\}$ means anticommute.
-\end{table}
-Therefore, $\mathrm{C\ell}_{0,4}(\R) \cong \mathrm{C\ell}_{1,3}(\R) $, which is
-consistent with $G_{\mathrm{AII}} \cong
-\mathrm{C\ell}_{d,3+D}(\R)$ in Table~\ref{tab:map-sym-cl}.
-
-\subsubsection{Constructing the Isomorphism (Complex Symmetry Classes)}
-\label{sec:Complex Classes-iso}
-The general steps for constructing the isomorphism is presented here. First, we
-need to treat the situation of complex classes and real classes
-differently. The complex classes are isomorphic to complex Clifford Algebras,
-while the real classes are isomorphic to real Clifford Algebras. The reason for
-this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
-multiplication of complex matrices. Second, complex matrices come with a nature
-definition of complex conjugate $\dagger$, whereas $K^\dagger$ is ill-defined
-\footnote{Think about this. $\braket{c \phi |K \psi}$ could have different
-    values depending on whether we move $K$ to the left as $K^\dagger$ first, or
-we move $c$ out of the inner-product first.}. Therefore, we use real Clifford
-Algebras when dealing with real classes (which is the reason why they are named
-real classes).
-
-For complex classes, let $G_\#$ be the group generated by elements
-$\{\gamma_i,\tilde{\gamma}_j,S\}$ ($i=1,\cdots,d$, $j=0,1$) in each symmetry
-class $\#$ (so $S$ exists only in class $\mathrm{AIII}$). We may choose a phase
-such that $S^2=1$, as mentioned earlier. Then obviously $G_\#$ will be a
-Clifford Algebra:
-\begin{align}
-    G_{A} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j\} \cong
-    \mathrm{C\ell}_{d+D+1}(\C) \\
-    G_{\mathrm{AIII}} &= \text{generated by }\{\gamma_i,\tilde{\gamma}_j,S\}
-    \cong  \mathrm{C\ell}_{d+D+2}(\C)
-\end{align}
-
-\subsubsection{Constructing the Isomorphism (Real Symmetry Classes)}
-\label{sec:Real Classes-iso}
-
-For real classes, we need to include $i$, and symmetry operators $T,C$ in our
-group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
-isomorphism in class $\mathrm{AII}$.
-
-We first note that, given a real vector space $V$, we can complexify a real space in
-two ways. The first is trivially taking the tensor product $V\otimes_\R \C$,
-which does not suit our purpose. The second is to find an almost complex
-structure $J$, which is a $\R$-linear map that squares to $-\id$, i.e.
-$J^2=-\id$. With this almost complex structure $J$, then $V$ admits in a natural
-way the structure of a complex vector space $V_\C$\cite{DanielHuybrechts2005}. Also, a
-$\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
-operators on a real vector space naturally.
-
-Let us denote the generators in Clifford Algebra as $J_j$ and $\tilde{J}_i$,
-where $J_j^2=-\tilde{J}_i^2 =-\id$. Since this almost complex structure $J$
-squares to $-\id$ and anticommutes with antiunitary symmetry operators, we
-naturally take it to be the first generator in our Clifford Algebra, $J_1=J$.
-
-Then we discuss some tips that will useful for later calculation.
-\paragraph{Tips}
-\begin{enumerate}
-    \item Since all generator anticommute, all matrices either commute or
-        anticommute. So the Algebra is pretty simple.
-    \item Since $[A,BC] = \pm[A,CB]$ and $\{A,BC\}=\pm\{A,CB\}$, the commutation
-        or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
-    \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
-        BA$. However, if $A$ and $B$ has something in common, then the above
-        condition breaks. This is like adding an "impurity" in it to change the
-        commutation/anticommutation relations.
-    \item The restriction given by $\sum_i k_i \gamma_i$, and $\sum_j m_j
-        \tilde{\gamma}_j$ (will be shown later) are much restrictive that the
-        candidates for symmetry operator are only a small finite set.
-        \label{enum:tips-4}
-\end{enumerate}
-
-\paragraph{Class $\mathrm{AII}$} Now we prove the isomorphism. First, we try to
-construct each gamma matrices in Hamiltonian. All matrices commute with $i$, so
-in real vector space, they commute with $J_1=J$. Then, each gamma matrices
-should have an even number of Clifford Algebra generators other than $J_1$
-itself. Similarly, antiunitary symmetry operators should have an odd number of
-Clifford Algebra generators other than $J_1$. We "dope" the gamma matrices with
-some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
-take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
-\ref{eq:sym-spemt}, and they give us the inspiration to set:
-\begin{equation}
-    H_{\mathrm{AII}} = m J_1J_2J_3 + \sum_{j=1}^D m_jJ_1J_2J_{3+j} +
-    \sum_{i=1}^d k_i J_2\tilde{J}_i
-\end{equation}
-Here $\tilde{\gamma}_j$ are $J_1J_2J_{3+j}$, which square to $1$. $\gamma_i$ are
-$J_2\tilde{J}_i$. The Clifford Algebra is at least $\mathrm{C\ell}_{d,3+D}(\R)$.
-And within this algebra, only $J_2$ is a possible candidate for symmetry
-operators, which satisfy equations~\ref{eq:sym-spemt} (use
-tips~\ref{enum:tips-4} for calculation). $J_2$ is found to be a
-time reversal operator, and $J_2^2=-1$ confirms that this Hamiltonian belongs to
-class $\mathrm{AII}$. Therefore, the map:
-\begin{align}
-    f: \mathrm{C\ell}_{d,3+D}(\R) &\to G_{\mathrm{AII}} \\
-    J_1J_2J_{3+j} &\to \tilde{\gamma}_j,\, (j=0,1,\cdots,D) \nonumber\\
-    J_2 \tilde{J}_i &\to \gamma_i,\, (i=0,1,\cdots,d) \nonumber
-\end{align}
-is a map from Clifford Algebra $\mathrm{C\ell}_{d,3+D}(\R)$ to symmetry class
-$\mathrm{AII}$. The inverse map can be found easily. We first solve some
-formality problems. A complex number can be written as a real number by
-identifying $i$ with $J=i\sigma_y$ and $1$ with $\id$, the identity matrix:
-\begin{equation}
-    a+bi \to a \begin{pmatrix}
-        1 & \\ & 1
-    \end{pmatrix} + b \begin{pmatrix}
-         & 1 \\ -1 & 
-    \end{pmatrix} = a\id + b J
-\end{equation}
-Therefore, all complex matrices $\gamma_i,\tilde{\gamma}_j$ are identified with
-real matrices $\Gamma_i,\tilde{\Gamma}_j$, of twice the size of
-$\gamma_i,\tilde{\gamma}_j$. More explicitly, $(a_{mn}+i b_{mn})$ is identified
-as $A+iB = (a_{mn})+i(b_{mn}) \to (a_{mn})+J_1(b_{mn})$, where
-\begin{equation}
-    J_1 \equiv i\sigma_y \otimes \id_{n\times n}
-\end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$, we define:
-\begin{equation}
-    K \equiv \sigma_z \otimes \id_{n\times n}
-\end{equation}
-Then $T\to \Gamma_T$, $C\to \Gamma_C$ for some real matrices.  We also note
-that, as mentioned earlier, we make a phase choice of $T$ and $C$ such that
-\begin{equation}
-    \{\Gamma_T,\Gamma_C\} = 0
-\end{equation}
-
-Now, we write symbolically $J_1J_2J_{3+j} = J_1 \Gamma_T J_{3+j} =
-\tilde{\Gamma}_j$, then clearly $J_{3+j} = \Gamma_T J_1\tilde{\Gamma}_j$.
-Similarly, $\tilde{J}_i = \Gamma_T\Gamma_i$. So the map:
-\begin{align}
-    f^{-1}: G_{\mathrm{AII}} &\to \mathrm{C\ell}_{d,3+D}(\R) \\
-    i\gamma_y \otimes \id_{n\times n} &\to J_1 \nonumber\\
-    \Gamma_T &\to J_2 \nonumber\\
-    \Gamma_TJ_1\Gamma_j &\to J_{3+j} \nonumber\\
-    \Gamma_T\tilde{\Gamma}_i &\to J_{i} \nonumber
-\end{align}
-is the desired inverse map.
-
-\paragraph{Class $\mathrm{CII}$} The class $\mathrm{CII}$ has only one $C^2=-1$
-more than class $\mathrm{AII}$, therefore, we only need to enlarge the Clifford
-Algebra to include one more $J_{4+D}$, and set it as the $C$ symmetry operator.
-The rest is exactly the same as in class $\mathrm{AII}$.
-
-All other classes can be treated similarly, so we do not repeat the calculation
-and only list the result in Table~\ref{tab:map-sym-cl}.
-\begin{table}[htpb]
-    \centering
-    \caption{Mapping Relations between symmetry classes and Clifford Algebras.
-    Here $J_j^2=-\id,\tilde{J}_i^2=\id$, and they generates the Clifford
-    Algebra. Also, only one direction of mapping is shown. The inverse map can
-    be easily constructed accordingly. The complex class are also added for
-    convenience.}
-    \label{tab:map-sym-cl}
-    \begin{tabular}{c | c c c | l | c }
-        Class($\#$) & T & C & S & Mappings  & $G_\#\cong $ \\
-        \hline 
-        D & $0$ & $+$ & $0$ & 
-        $\tilde{J}_1\to\Gamma_C$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,2+D}(\R)$ \\
-        DIII & $-$ & $+$ & $1$ & 
-        $\tilde{J}_1\to\Gamma_C$, $\tilde{J}_{3+D}\to\Gamma_T$,
-        $\tilde{J}_1J_{2+j}\to \tilde{\Gamma}_j$,
-        $J_1\tilde{J}_1\tilde{J}_{1+i}\to \Gamma_i$ &
-        $\mathrm{C\ell}_{1+d,3+D}(\R)$ \\
-        AII & $-$ & $0$ & $0$ & 
-        $J_2\to \Gamma_T$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,3+D}(\R)$ \\
-        CII & $-$ & $-$ & $1$ & 
-        $J_2\to \Gamma_T$, $J_{4+D}\to \Gamma_C$,
-        $J_1J_2J_{3+j}\to \tilde{\Gamma}_j$,
-        $J_2\tilde{J}_i \to \Gamma_i$
-        & $\mathrm{C\ell}_{d,4+D}(\R)$ \\
-        C & $0$ & $-$ & $0$ & 
-        $J_2\to \Gamma_C$, 
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{1+D,2+d}(\R)$ \\
-        CI & $+$ & $-$ & $1$ & 
-        $J_2\to \Gamma_C$, $\tilde{J}_{2+D}\to \Gamma_T$,
-        $J_2\tilde{J}_{1+j} \to \tilde{\Gamma}_j$,
-        $J_1J_2J_{i+2}\to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,2+d}(\R)$ \\
-        AI & $+$ & $0$ & $0$ & 
-        $\tilde{J}_1\to \Gamma_T$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{2+D,1+d}(\R)$ \\
-        BDI & $+$ & $+$ & $1$ & 
-        $\tilde{J}_1\to \Gamma_T$, $\tilde{J}_{3+D}\to \Gamma_C$,
-        $J_1\tilde{J}_1\tilde{J}_{2+j} \to \tilde{\Gamma}_j$,
-        $\tilde{J}_1J_{i+1} \to \Gamma_i$
-        & $\mathrm{C\ell}_{3+D,1+d}(\R)$ \\
-        \hline
-        A & $0$ & $0$ & $0$ & 
-        & $\mathrm{C\ell}_{d+D+1}(\C)$ \\
-        AIII & $0$ & $0$ & $1$ & 
-        & $\mathrm{C\ell}_{d+D+2}(\C)$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\subsection{Classification in 1-dimension}
-\label{sec:Classification in 1-dimension}
-Classification of $1$ dimension is the simplest, since the minimal matrix
-dimension will mostly be $2$, which means we can use the familiar Pauli matrices
-directly.
-
-\paragraph{Class $\mathrm{A}$} We have the extension from
-$\mathrm{C\ell}_{2}(\C)$ to $\mathrm{C\ell}_{3}(\C)$. Since
-$\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, we have for example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-Obviously, there is an SPEMT $m\sigma_x$. So this phase is trivial.
-
-\paragraph{Class $\mathrm{AIII}$} We have the extension from
-$\mathrm{C\ell}_{3}(\C)$ to $\mathrm{C\ell}_{4}(\C)$. Since
-$\mathrm{C\ell}_{3}(\C)\cong \mathcal{M}(2,\C)\oplus\mathcal{M}(2,\C)$, we use
-Pauli matrices. For example:
-\begin{equation}
-    H_A = M \sigma_x + k_x \sigma_y
-\end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
-topologically non-trivial. Now we consider the state with arbitrary copies of it.
-\begin{equation}
-    H_A = M \sigma_x\otimes \id_n + k_x\sigma_y\otimes\id_n,
-    S=\sigma_z\otimes\id_n
-\end{equation}
-where $n$ is some positive integer. Since any matrix $A$, $A$ could be expressed
-as a linear combination of terms like $B\otimes C$, where $B$ is $2\times 2$
-dimensional\footnote{For example, just take $B= \begin{pmatrix}1 & 0 \\ 0 &
-0\end{pmatrix},\begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix},\begin{pmatrix}0 & 0
-\\ 1 & 0\end{pmatrix},\begin{pmatrix}0 & 0 \\ 0 & 1\end{pmatrix}$.}. Due to the
-linearity of anti-commutator and some basic properties of Kronecker product,
-there is no SPEMT term. Hence this is a $\Z$ topological insulator.
-
-The above are for complex classes. For real classes, we have to be careful,
-since one generator $J_1$ is taken up by $i$.
-
-\paragraph{Class $\mathrm{AII}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathbb{H}$, to
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$.
-This already hints that we will have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_x K$. The SPEMT is $m\sigma_z\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{C}$} We have the extension from
-$\mathrm{C\ell}_{1,3}(\R)\cong\mathcal{M}(2,\R)\otimes\mathrm{H}$, to
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{C}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$. The SPEMT is $m\sigma_x\otimes\sigma_x$. So
-this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CI}$} We have the extension from
-$\mathrm{C\ell}_{2,3}(\R)\cong\mathcal{M}(4,\R)\otimes\C$, to
-$\mathrm{C\ell}_{3,3}(\R)\cong\mathcal{M}(6,\R)$. If one realize that $\C$ is
-realized by $2\times 2$ matrices, then this should have SPEMT. Explicitly, we
-could let
-\begin{equation}
-    H_{\mathrm{CI}} = M\sigma_z\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\sigma_y K$, $T=K$. The SPEMT is again
-$m\sigma_x\otimes\sigma_x$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{AI}$} We have the extension from
-$\mathrm{C\ell}_{2,2}(\R)\cong\mathcal{M}(4,\R)$, to
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$. This hints
-that we have SPEMT. Explicitly, we could let
-\begin{equation}
-    H_{\mathrm{AI}} = M\sigma_x + k_x\sigma_y
-\end{equation}
-with $T=K$. The SPEMT is $m\sigma_z$. So this is a trivial insulator.
-
-\paragraph{Class $\mathrm{CII}$} We have extension from
-$\mathrm{C\ell}_{1,4}(\R)\cong\mathcal{M}(2,\R)\otimes(\mathbb{H}\oplus\mathbb{H})$,
-to
-$\mathrm{C\ell}_{1,5}(\R)\cong\mathcal{M}(2,\R)\otimes\mathcal{M}(2,\mathbb{H})$.
-We let:
-\begin{equation}
-    H_{\mathrm{CII}} = M\sigma_x\otimes\id_2 + k_x\sigma_y\otimes\id_2
-\end{equation}
-with $T=\id_2\otimes\sigma_y K$, $C=\sigma_z\otimes\sigma_y K$. There is no
-SPEMT\footnote{To anticommute with $\sigma_x\otimes\id_2$ and
-$\sigma_y\otimes\id_2$, it must be of the form $\sigma_z\otimes?$. But none of
-the remaining choice are acceptable, considering $T$ and $C$.}. Consider
-arbitrary copies of it:
-\begin{equation}
-    H_{\mathrm{CII}} = (M\sigma_x\otimes\id_2 +
-    k_x\sigma_y\otimes\id_2)\otimes\id_n
-\end{equation}
-with $T=\id_2\otimes\sigma_y\otimes\id_n K$,
-$C=\sigma_z\otimes\sigma_y\otimes\id_n K$. There is still no SPEMT\footnote{The
-SPEMT has to be of the form $\sigma_z\otimes\sigma_\alpha\otimes A_{n\times n}$.
-Commuting with $T$ makes $A$ completely imaginary. But it cannot anticommute
-with $C$.}. Therefore, this is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{BDI}$} We have extension from
-$\mathrm{C\ell}_{3,2}(\R)\cong\mathcal{M}(4,\R)\otimes(\R\oplus\R)$, to
-$\mathrm{C\ell}_{4,2}(\R)\cong\mathcal{M}(8,\R)$. We let:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $T=K$, $C=\sigma_x K$. Obviously, there is no SPEMT. For arbitrary copies
-of it:
-\begin{equation}
-    H_{\mathrm{BDI}} = M\sigma_z\otimes\id_n + k_x \sigma_y\otimes\id
-\end{equation}
-with $T=\id_{n+2}K$, $C=\sigma_x\otimes\id_n K$.  The SPEMT must be of the form
-$\sigma_x\otimes\Delta$ to anticommute with $H_{\mathrm{BDI}}$. But to commute with
-$T$ leads to $\Delta$ being real, and to anticommute with $C$ leads to $\Delta$ being
-complex. Hence there is no SPEMT. This is a $\Z$ topological insulator.
-
-\paragraph{Class $\mathrm{D}$} We let:
-\begin{equation}
-    H_{\mathrm{D}} = M\sigma_z + k_x \sigma_y
-\end{equation}
-with $C=\sigma_x K$. Obviously, there is no SPEMT. Now consider two copies of
-it:
-\begin{equation}
-    H_{\mathrm{D}} = (M\sigma_z + k_x \sigma_y)\otimes\id_2
-\end{equation}
-with $C=\sigma_x\otimes\id_2 K$. There is one SPEMT $m \sigma_z\otimes\sigma_y$.
-Hence, this is a $\Z_2$ topological insulator.
-
-To lighten the notation a bit, we introduce $\tau_i=s_i=\sigma_i$ ($i=0,1,2,3$).
-But $\tau_i$, $s_i$, and $\sigma_i$ all act on the different spaces.
-\paragraph{Class $\mathrm{DIII}$} We let:
-\begin{equation}
-    H_{\mathrm{DIII}} = M \sigma_z s_0 + k_x \sigma_y s_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$. Any SPEMT anticommute with Hamiltonian has the
-form $\sigma_x s_i$. For it to anticommute with $C$, it is $\sigma_x s_y$. But
-this does not commute with $T$. Hence, there is no SPEMT. Now consider two
-copies of it:
-\begin{equation}
-    H_{\mathrm{DIII}} = (M \sigma_z s_0 + k_x \sigma_y s_0)\tau_0
-\end{equation}
-with $C=\sigma_x K$, $T=s_y K$.  There is one SPEMT $m \sigma_xs_x\tau_y$. So
-this is a $\Z_2$ topological insulator.
-
-In summary, we have classified topological insulators in $d=1$, summarized in
-Table~\ref{tab:ti-d=1}.
-\begin{table}[htpb]
-    \centering
-    \caption{Topological Insulators in $d=1$}
-    \label{tab:ti-d=1}
-    \begin{tabular}{c | c c c | c }
-        Class($\#$) & T & C & S & $d=1$ \\
-        \hline 
-        A & $0$ & $0$ & $0$ & $0$ \\
-        AIII & $0$ & $0$ & $1$ & $\Z$ \\
-        \hline
-        D & $0$ & $+$ & $0$ & $\Z_2$ \\
-        DIII & $-$ & $+$ & $1$ & $\Z_2$ \\
-        AII & $-$ & $0$ & $0$ & $0$ \\
-        CII & $-$ & $-$ & $1$ & $\Z$ \\
-        C & $0$ & $-$ & $0$ & $0$ \\
-        CI & $+$ & $-$ & $1$ & $0$ \\
-        AI & $+$ & $0$ & $0$ & $0$ \\
-        BDI & $+$ & $+$ & $1$ & $\Z$ \\
-        \hline
-    \end{tabular}
-\end{table}
-\todo{add reflection about the disadvantage of this method (no $2\Z$). And
-representation aspect}
-\subsection{Classification in Arbitrary Dimension}
-\label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
-generalized to classification in arbitrary dimensions. In $K$-theoretic
-classification, the extension problem is not affected when tensored with some
-other algebras. Specifically, for complex classes, the extension problem of
-$\mathrm{C\ell}_{n}(\C)\to\mathrm{C\ell}_{m}(\C)$ is the same as the extension
-problem of $\mathrm{C\ell}_{n}(\C)\otimes\mathrm{C\ell}_{l}(\C)\to
-\mathrm{C\ell}_{m}(\C)\otimes\mathrm{C\ell}_{l}(\C)$ (See for example, sec
-III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
-background.\todo{understand this~}
-
-Now, let us write $\sim$ to represent the equivalence between two extension
-problems.  The Complex Clifford Algebra has a periodicity of $2$:
-\begin{equation}
-    \mathrm{C\ell}_{n+2}(\C) \cong \mathrm{C\ell}_{n}(\C)\otimes
-    \mathrm{C\ell}_{2}(\C)
-\end{equation}
-The Real Clifford Algebra has a periodicity of $8$:
-\begin{equation}
-    \mathrm{C\ell}_{p+8,q}(\R) = \mathrm{C\ell}_{p,q+8}(\R) =
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(16,\R)
-\end{equation}
-This two relation means, the extension problem will be the same with respect to
-a periodicity of $2$ for complex symmetry classes, and $8$ for real symmetry
-classes. Hence the classification of topological insulators need only be done
-with $d=1,2$ for complex symmetry classes, and $d=0,1,\cdots,7$ for real
-symmetry classes, i.e.
-\begin{subequations}
-    \label{eq:cli-periodic}
-\begin{align}
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 2)) \quad\text{(complex)} \\
-    G_{\#}(d=d_0) &\sim G_{\#}(d=(d_0 \text{mod} 8)) \quad\text{(real)}
-\end{align}
-\end{subequations}
-Another useful property is:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q+1}(\R) &\cong
-    \mathrm{C\ell}_{p,q}(\R)\otimes\mathcal{M}(2,\R)
-\end{align}
-This property tells us that Clifford Algebra basically depends only on the
-difference $p-q$, or combined with previous periodicity, $p-q$ (mod $8$). For
-example, we have (let $n$ be an arbitrary integer):
-$\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
-\begin{align}
-    &\mathrm{C\ell}_{1+(D+n),2+D}(\R) \sim \mathrm{C\ell}_{1+(D+1+n),3+D}(\R)
-    \nonumber\\
-    \sim & \mathrm{C\ell}_{(D+2+n),3+D}(\R) \sim \mathrm{C\ell}_{(D+3+n),4+D}(\R)
-\end{align}
-and
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim \mathrm{C\ell}_{2+D,2+(D+5+n)}(\R)
-    \nonumber\\
-    \sim& \mathrm{C\ell}_{2+D,1+(D+6+n)}(\R) \sim
-    \mathrm{C\ell}_{3+D,1+(D+7+n)}(\R)
-\end{align}
-Now we tries to connect the two chains together. We note further that the
-Clifford Algebra has the following properties:
-\begin{align}
-    \mathrm{C\ell}_{p+1,q}(\R) &\cong \mathrm{C\ell}_{q+1,p}(\R) \\
-    \mathrm{C\ell}_{q,p+2}(\R) &\cong \mathrm{C\ell}_{p,q}(\R) \otimes\mathcal{M}(2,\R)
-\end{align}
-Then:
-\begin{align}
-    &\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R) \cong
-    \mathrm{C\ell}_{D+4+n,1+D}(\R)\otimes\mathcal{M}(2,\R) \nonumber\\
-    \cong& \mathrm{C\ell}_{2+D,D+3+n}(\R)\otimes\mathcal{M}(2,\R)
-    \cong \mathrm{C\ell}_{D+1+n,2+D}(\R)\otimes\mathcal{M}(4,\R)
-\end{align}
-Therefore,
-$\mathrm{C\ell}_{1+D,2+(D+4+n)}(\R)\sim\mathrm{C\ell}_{1+(D+n),2+D}(\R)$,
-connecting the two chains. If we compare this carefully with
-Table~\ref{tab:map-sym-cl}, then we would realize that we actually managed to
-prove the dimension-shift feature of classification:
-\begin{align}
-    \label{eq:cli-Chain1}
-    G_{\mathrm{D}}(d=d_0) &\sim G_{\mathrm{DIII}}(d=d_0+1) \nonumber\\
-    \sim G_{\mathrm{AII}}(d=d_0+2) &\sim G_{\mathrm{CII}}(d=d_0+3) \nonumber\\
-    \sim G_{\mathrm{C}}(d=d_0+4) &\sim G_{\mathrm{CI}}(d=d_0+5) \nonumber\\
-    \sim G_{\mathrm{AI}}(d=d_0+6) &\sim G_{\mathrm{BDI}}(d=d_0+7)
-\end{align}
-We need one more property:
-\begin{equation}
-    \mathrm{C\ell}_{1+d,2+D}(\R)\cong
-    \mathrm{C\ell}_{3+D,d}(\R)=\mathrm{C\ell}_{3+D,1+(d-1)}(\R)
-\end{equation}
-Then
-\begin{equation}
-    \label{eq:cli-Chain2}
-    G_{\mathrm{D}}(d=d_0) \sim G_{\mathrm{BDI}}(d=d_0-1)
-\end{equation}
-With equalvalence~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
-classification in Table~\ref{tab:master-table2}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|c|cccccccc|ccc|}
-\hline
-\multicolumn{12}{|c|}{
-The original classification table} \\ \hline
-   $\mbox{AZ class} \backslash d$  & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & T & C & S  \\
-\hline\hline
-  A & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0             & 0 & 0 & 0    \\
-  AIII & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$ & 0 & $\mathbb{Z}$          & 0 & 0 & 1    \\  \hline
-
-  AI & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$    & $+$ & 0 & 0     \\
-  BDI & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$     & $+$ & $+$ & 1    \\
-  D & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$ & 0     & 0 & $+$ & 0     \\
-  DIII & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0 & $2\mathbb{Z}$  & $-$ & $+$ & 1     \\
-  AII & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0 & 0   & $-$ & 0 & 0     \\
-  CII & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0 & 0   & $-$ & $-$ & 1     \\
-  C & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$ & 0     & 0 & $-$ & 0     \\
-  CI & 0 & 0 & 0 & $2\mathbb{Z}$ & 0 & $\mathbb{Z}_2$ & $\mathbb{Z}_2$ & $\mathbb{Z}$    & $+$ & $-$ & 1
-   \\
-\hline
-\end{tabular}
-\caption{The original classification table of topological insulators and
-superconductors}
-\label{tab:master-table2}
-\end{center}
-\end{table}
-\section{License}
-The entire content of this work (including the source code
-for TeX files and the generated PDF documents) by 
-Hongxiang Chen (nicknamed we.taper, or just Taper) is
-licensed under a 
-\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
-Commons Attribution-NonCommercial-ShareAlike 4.0 International 
-License}. Permissions beyond the scope of this 
-license may be available at 
-\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
-{[My Email Address(Click)]}.
+\begin{appendix}
+\input{chapters/chap-appA.tex}
+\input{chapters/chap-appB.tex}
+\end{appendix}
 

### 2017-07-25 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-2.tex
[minor] Correct minor grammatical mistakes.

@@
 
-We begin our discussion with a background before this classification.  The
+We begin our discussion with a background for this classification.  The
 classification of topological phases with different non-unitary symmetries in
@@
 $H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
-has no memory of the unitary symmetries. Therefore, our classification is
+has no memory of the unitary symmetries. Then, our classification is
 applied to those blocks and still holds.
 
-It will be find that, those $T,C$ are the only two meaningful non-unitary
+It will be found that, those $T,C$ are the only two meaningful non-unitary
 symmetries of the Single-particle system, and there are in total 10 different
 ways in which the Single-particle Hamiltonian could respect the three symmetries
-$T,C,S$. Now we explain in detail, about the reason why we care about, and only
+$T,C$, and $S=TC$. Now we explain in detail, about the reason why we care about, and only
 care about these three symmetries $T,C,$ and $S$.
@@
 operators), we can always pick a phase such that $S^2$ is some phase we want.
-Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick some specific
+Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick another specific
 phase for $S^2$.\footnote{This is a bit troublesome. First we denote
@@
 symmetry to present. Also, the addition of translational symmetry not only
-produces the same classification, but also make this classification more
-convenient to be done.
 
-With translational symmetry added, the classification can be made the will yield
-the same result.\footnote{This is still a mystery to me which this is true. The
+produces the same classification\footnote{This is still a mystery to me which this is true. The
 	exact reason is related to some isomorphism between certain homotopy groups.
@@
 	\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{here}
-	for a clue.}
+	for a clue.}, but also generalize to arbitrary dimensions.
 

### 2017-07-25 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-3.tex
[minor] Correct minor grammatical mistakes.

@@
 
-\paragraph{Dirac Hamiltonian and Topological Property of the Bulk}
+\paragraph{Dirac Hamiltonian and Topological Property of the Boundary}
 We first note that different topological phases are distinguished by the closing
@@
 responsible for the opening and closing of the gap, or in some cases, a parameter
-in which we can control to open of close the gap.
+in which we can control to open or close the gap.
 
@@
 \paragraph{Edge Mode and \texorpdfstring{$M$}{}}
-Now we explain why the Dirac Hamiltonian\ref{eq:dirac-H}  is useful for capturing the topological
+Now we explain why the Dirac Hamiltonian eq.~\ref{eq:dirac-H}  is useful for capturing the topological
 phase. First, it has a gapless state. Due to the anti-commutation relation of
@@
 In addition, we can analyse its edge mode. Assuming the two material of
-different quantum phases touches each other in the $d$th direction. Then we
+different quantum phases touches each other in the $d$th dimension. Then we
 should replace $k_d$ by $-i\partial_{x_d}$, since the translational invariance is
@@
 
-\paragraph{Stable Classification} An unmentioned hypothesis above are that we
-are classifying strong topological insulators. They are topological insulators
-that robust against disorder\cite{Fu2007}. There is a consensus that in
-classification of strong topological insulators, we replace the Brillouin Zone
-$T^d$ by $S^d$\footnote{The exact reason can be found in Kitaev's
-    classification\cite{Kitaev2009a} or another article \cite{Kennedy2015} which
-discuss it from a different view.}, and we do it in a stable way, i.e., we choose
-our classification to be independent of and insensitive to the addition of
-irrelevant trivial bands. The first replacement allow us to use homotopy groups,
-which classify maps with domain in spheres. The "stable way" allows the use of
-$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
-
 \paragraph{The View from SPEMT} Let us consider a modified Dirac Hamiltonian
@@
 way. First, we consider the case when $D=0$, i.e. without perturbation, and we
-consider how many different mass terms we could have. Second, we consider adding
-an extra mass term which respect the symmetry of the Hamiltonian ($D=1$).
-Whether this symmetry preserving extra mass term (SPEMT) can be added or not. If
+consider how many different mass terms we could have. Second, we consider whether we can add
+an extra mass term which respect the symmetry of the Hamiltonian ($D=1$) or not.
+Tthis symmetry preserving extra mass term is denoted as SPEMT. If
 a SPEMT can be added, then the system is not robust against perturbation and gap
-may be opened by disorder. So it is trivial topological insulator. If a SPEMT
-cannot be added, then this system is topological non-trivial.
+may be opened by disorder. So it is not protected by symmetry and is trivial topological insulator. If a SPEMT cannot be added, then this system is topological non-trivial.
 
@@
 matrix dimension are built by tensor products of Pauli matrices.
-\footnote{Or, the non-trivial irreducible representations (turns out there are
+\footnote{Or, the non-trivial irreducible representations (turns out that there are
 at most 2) are built by tensoing Pauli matrices.}
-Now, to increase the dimension of the matrix, is equivalent to
-tensor them. One can add more bands of the same type, or add more bands of a
+Now, increasing the dimension of the matrix, is equivalent to
+tensoring them. One can add more bands of the same type, or add more bands of a
 different type in the smaller dimension, or add trivial bands. In all cases, the
@@
 \end{subequations}
-With this, we can establish a isomorphism between "Hamiltonian and Symmetry
+With this, we can establish an isomorphism between "Hamiltonian and Symmetry
 Operators" and "Clifford Algebra over $\R$ or $\C$".  But let's first see some
@@
 For class AI ($T^2=1$, $C=0,S=0$) in $d=1,D=0$, we define:
-$$ G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\} $$
+\begin{equation}
+	G_{\mathrm{AI}} = \{i, T, \tilde{\gamma_0}, \gamma_1\}
+\end{equation}
 We have its (anti)commutation relations listed in Table~\ref{tab:generator-AI}.
@@
 $J_3^2=J_4^2=1$. So together they generate the algebra
-$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}^g((2,2),\R)$. This will be consistent with the
-isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ in
+$\mathrm{C\ell}_{3,1}(\R) \cong \mathrm{C\ell}_{2,2}(\R)$. This is consistent with the
+isomorphism $G_{\mathrm{AI}} \cong \mathrm{C\ell}_{2+D,1+d}(\R)$ shown later in
 Table~\ref{tab:map-sym-cl}.
@@
 this distinction is that, in real classes, there are complex conjugate operator
-$K$. First, there is not way to represent complex conjugation simply as
+$K$. First, there is no way to represent complex conjugation simply as
 multiplication of complex matrices. Second, complex matrices come with a nature
@@
 group $G_\#$. It turns out that we need to pick a phase such that $\{T,C\}=0$,
-which is possible as is mentioned earlier. Now we demonstrate the proof of
+which is possible as mentioned earlier. Now we demonstrate the proof of
 isomorphism in class $\mathrm{AII}$.\footnote{For reader unfamiliar with the
 complexfication of real vector space, and the realification of complex vector
-space, I recommend a quick reading of section 12 \cite{suetin1989linear}.}
+space, I recommend a quick reading of section 12 of \cite{suetin1989linear}.}
 
@@
 $\R$-linear map $A$ on $V$ is $\C$-linear($\C$-antilinear) if and only if $A$
-commutes (anticommutes) with $J$. Therefore, we map model the antiunitary
+commutes (anticommutes) with $J$. Therefore, we can model the antiunitary
 operators on a real vector space naturally.
@@
 
-Then we discuss some tips that will useful for later calculation.
+Then we discuss some tips that will be useful for later calculation.
 \paragraph{Tips}
@@
         or anticommutation does not depends on the order of the matrices $BC$ or
-        $CB$. So one might rearrange them in the order whichever is convenient.
+        $CB$. So one might rearrange them in these orders whichever is convenient.
     \item For $A=\{J_1,\cdots,J_n\},B=\{K_1,\cdots,K_m\}$, we have $AB=(-1)^{mn}
@@
 some $J_1$ to make it commute/anticommute with symmetry operators. More
-explicitly, bearing in mind that in class $\mathrm{AII}$ has only $T^2=-1$, we
+explicitly, bearing in mind that class $\mathrm{AII}$ has only $T^2=-1$, we
 take a quick look into Hamiltonian \ref{eq:H-spemt} and symmetry conditions
@@
 as $A+iB = (a_{mn})+i(b_{mn}) \to \id_2\otimes(a_{mn})+J\otimes(b_{mn})$. On
-important matrix is the matrix $J_1$ that we identify $i$ as:
+important matrix is the matrix $J_1$ which is identified as $i$, and is equal to:
 \begin{equation}
@@
 \end{equation}
-The complex conjugate $K$ is then a matrix anticommute with $J_1$.  Then $T\to
+The complex conjugate $K$ is then a matrix anticommuting with $J_1$.  Then $T\to
 \Gamma_T$, $C\to \Gamma_C$ for some real matrices anticommute with $i\to J_1$.
@@
 \end{equation}
-However, the symmetry operator $S$ takes rest Pauli matrices $\sigma_z$, and
-there is not other matrix possible for the extra mass term (this can be viewed
-alternatively, from $\mathrm{C\ell}_{4}(\C)\cong \mathcal{M}(4,\C)$, which only
-has irreducible representation in dimension $1$ or $4$). So the state is
+However, the symmetry operator $S$ takes the rest of Pauli matrices $\sigma_z$, and
+there is no other matrix possible for the extra mass term. So the state is
+
 topologically non-trivial. Now we consider the state with arbitrary copies of it.
@@
     exact reason for "equivalent" and "inequivalent" would be found in
-    representation theory or Clifford Algebras, but which is not important for
+    representation theory or Clifford Algebras, but it is not important for
     our discussion here.} For the second copy, we could always find a SPEMT to gap
@@
     \end{equation}
-    it can be gapped by a SPEMT such as $\Gamma_1\otimes \sigma_x$.
+    It can be gapped by a SPEMT such as $\Gamma_1\otimes \sigma_x$.
 
@@
     must be of the form $\Gamma\otimes A_{2\times 2}$, where $\Gamma$
-    anticommutes with $\Gamma_i$ and $\tilde{\Gamma}_0$, $A$ is any $2\times 2$
+    anticommutes with $\Gamma_i$ and $\tilde{\Gamma}_0$, $A$ is some $2\times 2$
     matrix.
@@
             $\mathrm{C\ell}_{p,q+1}(\R)$, as can be checked in
-            Table~\ref{tab:mat-dim-allClass-1d} that they all doubled the
+            Table~\ref{tab:mat-dim-allClass-1d} that they all double the
             dimension.
@@
 \label{sec:Classification in Arbitrary Dimension}
-We now show combined with some properties, the classification in $d=1$ can be
+We now show that, when combined with some properties, the classification in $d=1$ can be
 generalized to classification in arbitrary dimensions. In $K$-theoretic
@@
 III.C.1 of \cite{Chiu2016}). For real classes, similar property holds.
-This insensitive to tensoring a new algebra, can be understand in SPEMT
+This insensitivity to tensoring a new algebra, can be understood in SPEMT
 background. Because $\mathrm{C\ell}_{2}(\C)\cong\mathcal{M}(2,\C)$, which only
@@
 $\mathrm{C\ell}_{p+1,q+1}(\R)\sim\mathrm{C\ell}_{p,q}(\R)$. With this, one can
-derive easily two chains of relation:
+derive two chains of relations:
 \begin{align}
@@
 \end{align}
-Now we tries to connect the two chains together. We note further that the
+Now we try to connect the two chains together. We note further that the
 Clifford Algebra has the following properties:
@@
 With equivalences~\ref{eq:cli-periodic},\ref{eq:cli-Chain1},\ref{eq:cli-Chain2},
-we see that we need only the result in a dimension, to obtain the whole of
+we see that we need only the result in a dimension, to obtain the whole table of
 classification of all real classes. Similar fact holds for complex classes:
@@
 \end{equation}
-which is too trivial to be mentioned here.
+which is obvious.
 

### 2017-07-25 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/chap-4.tex
[minor] Correct minor grammatical mistakes.

@@
 \label{sec:Looking Further}
-There has be great deal of progress made in classification of topological
+There has be a great deal of progress made in classification of topological
 insulator and superconductors. We first comment that our discussion could be
@@
 
-Also, our discussion falls short in two respects. First, it cannot distinguish
+An unmentioned hypothesis above is that we
+are classifying strong topological insulators. They are topological insulators
+that are robust against disorder\cite{Fu2007}. There is a consensus that in
+classification of strong topological insulators, we replace the Brillouin Zone
+$T^d$ by $S^d$\footnote{The exact reason can be found in Kitaev's
+ classification\cite{Kitaev2009a} or another article \cite{Kennedy2015} which
+discuss it from a different view.}, and we do it in a stable way, i.e., we choose
+our classification to be independent of and insensitive to the addition of
+irrelevant trivial bands. The first replacement allow us to use homotopy groups,
+which classify maps with domain in spheres. The "stable way" allows the use of
+$K$-theory (sec.III.C.1 of \cite{Chiu2016}).
+
+However, our discussion falls short in two respects. First, it cannot distinguish
 between $\Z$ and $2\Z$ cases. Secondly, we do not give explicit formulae for
 calculating topological invariants in different cases. The former problem can be
-addressed in Ludwig's \cite{Schnyder2008}, while the latter requires
-considerable work, and provides different topological invariant in different
+addressed in Ludwig's \cite{Schnyder2008}, whereas the latter requires
+considerable work, and requires different topological invariant in different
 cases (see sec. III.B of \cite{Chiu2016}).
@@
 class of topological insulators, dubbed topological crystalline
-insulators.\cite{Ando2015} the case of reflection symmetry, some new topological
+insulators.\cite{Ando2015} In the case of reflection symmetry, some new topological
 invariants denoted as $M\Z$, called mirror topological invariants, are needed to
@@
 Lastly, the discussion of topological states in interaction picture extends to
-the case of symmetry-protected phases (SPTs), of which I am not familiar with.
+the case of symmetry-protected phases (SPTs), with which I am not familiar.
 For all these new concepts, the review \cite{Chiu2016} is an excellent source of
 information.
-
-Note that due to unforeseenable problems, this document may be outdated. The
-latest version may be emailed by request.

### 2017-07-25 Notes of various papers/Chiu Minimal Dirac Hamiltonian Method/chapters/introduction.tex
[minor] Correct minor grammatical mistakes.

@@
 is the classification done by considering how the Hamiltonian matrix responses
-to those anti-unitary symmetries, when we effectively ignored all unitary
+to those anti-unitary symmetries, when we ignored all unitary
 symmetries. Specifically, when we module out any unitary symmetries of the
@@
 that surface conducting states must overcome. This approach uses the Nonlinear
-Sigma Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider the
+Sigma Models (NL$\sigma$Ms) to describe the surface Hamiltonian and consider
 when can a localization-breaking term can be added to NL$\sigma$Ms.
@@
 Hamiltonians could be regarded as yet another generator of Clifford
-Algebra\cite{Morimoto2013}. The $K$-theory approach is to put the symmetries in
+Algebra\cite{Morimoto2013}. The second approach is to put the symmetries in
 the Clifford Algebra first, and consider adding the Hamiltonian that preserve
@@
 Hamiltonian of the whole bulk, but the physics happening when the bulk gap
-closes. For example, the Chern number is the integration on a compact manifold
+closes. For example, the Chern number is the integration on a compact manifold $T^d$
 without boundary. Therefore, it should always be zero because of the Stokes
@@
 Chern number got "blown up", and it is just this locally "blown up" point
-(caused by the crossing) that is responsible for the nonzero Chern number, and
+(caused by the crossing bands) that is responsible for the nonzero Chern number, and
 for the non-triviality of topological insulators. More generally, we believe
@@
 Therefore, we can detect the different types of topological insulators when we
-are focused in only the crossing point of the band, or, when we shifted the
+are focused in only the crossing point of the band, or, if we shifted the
 energy zero level to the crossing point, in only the low energy physics. We
 expect a locally linear crossing energy spectrum around this point, so we expect
-$E=\pm\sqrt{\vb{p}^2+m^2}$, with $m$ being the parameter controlling the closing or
-opening of this spectrum. One simple model with only first-order derivatives to
-describe such a low energy physics is the Dirac Hamiltonian. Also, the
+$E=\pm\sqrt{\vec{k}^2+m^2}$, with $m$ being the parameter controlling the closing or
+opening of this spectrum. One simple Hamiltonian with only first-order derivatives to
+describe such a low energy physics is the Dirac Hamiltonian, as shown by the
 traditional discussion of Klein-Gordon equation all tells us to look at Dirac
@@
 Using the Dirac Hamiltonian, it is discovered by Dr. Chiu \cite{Chiu2013a} that
-the classification of topological insulators could be brought done into very
+the classification of topological insulators could be brought into very
 simple applications of classification and representation theory of Clifford
-Algebras, which have been well studied with excellent resources provided online.
-In his classification, he established a isomorphism from $G_{\text{symmetries 
+Algebras, which have been well studied with excellent resources available online.
+In his classification, he established an isomorphism from $G_{\text{symmetries 
 class}}$, the algebra generated by symmetry operators and Dirac Hamiltonians, to

### 2018-01-07 Helstrom Bound/main.tex
understand Helstrom bound
for quantum state discrimination.

\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

% For drawing quantum circuits
\usepackage{qcircuit}

\title{Quantum Machine Learning}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
Hello world! 
}
\tableofcontents

\section{General Measurement}
\label{sec:General Measurement}
\begin{itemize}
  \item General Measurement in Density Matrices
    \begin{itemize}
      \item Defined by $M_1,\cdots, M_m$, with $\sum_i M^\dagger_i M_i = \id$
        (Kraus representation?)
      \item The transformed state is: $\sum_i M_i \rho M_i^\dagger$.
      \item The probability of seeing the item labeled $j$ is,
        \begin{equation}
          p_j = \Tr(M_j \rho M_j^\dagger) = \Tr(M_j^\dagger M_j \rho)
        \end{equation}
      \item The state collapsed into
        \begin{equation}
          \frac{M_j \rho M_j^\dagger}{p_j} = 
          \frac{M_j \rho M_j^\dagger}{\Tr(M_j \rho M_j^\dagger)}
        \end{equation}
    \end{itemize}
  \item Why it is so similar to the statistical description of ensembles, in
    which:
    \begin{equation}
      Z = \Tr(M_j \rho M_j^\dagger)
    \end{equation}
   \item POVMs in Density Matrices:
     \begin{itemize}
       \item We let $E_i = M_i^\dagger M_i$, then
       \item $\sum_i E_i = \id$, $p_j = \Tr(E_j \rho)$,
       \item We don't have an expression for the collapsed state.
     \end{itemize}
\end{itemize}

\section{Discriminating Two Pure States}
\label{sec:Discriminating Two Pure States}
\begin{itemize}
  \item Given $d$-dim state $\psi$ known to be either $\psi_1$ or $\psi_2$.
    Tell which state $\psi$ is in.
  \item Best strategy:
    \begin{itemize}
      \item Do the POVMs with outcome $\{\ket{v_1},\ket{v_2}\}$ such that
      \item \begin{figure}[H]
            \centering
            \includegraphics[width=0.6\linewidth]{fig/dis-two-pure.pdf}
        \end{figure}
      \item The angle $\theta$ is angle between $\psi_i$. The $v_i$ are
        symmetric about the angle bisector of $\psi_i$.
      \item The best probability of success is
        \begin{equation}
          |\braket{\psi_1|v_i}|^2 
          = \cos^2(\frac{\pi/2-\theta}{2}) = \frac{1}{2} + \frac{1}{2}\sin(\theta)
        \end{equation}
    \end{itemize}
  \item ?: Why is this optimal?
  \item ?: How is the probability of success defined?
\end{itemize}

\section{Discriminating Two Mixed States}
\label{sec:Discriminating Two Mixed States}
Given a mixed state $\rho$ in $\rho_1$ or $\rho_2$.

\textbf{Easy case}: 
\begin{itemize}
  \item Assuming equal \textit{a priori} probability.
  \item Assuming $\rho_1=$ ensemble $\{p_1,\psi_i\}$, and $\rho_2=$
    ensemble $\{q_i,\psi_i\}$ (i.e. produced in the same pool of
    $\psi_i$s.).
  \item Optimal:
    \begin{itemize}
      \item Measure in the same basis $\{\psi_i\}$.
      \item If got $\psi_i$, we believe it is $\rho_1$ or $\rho_2$ according to
        $\text{max}(p_i,q_i)$.
      \item Then the overall success is
        \begin{align*}
          P_\text{success} &=
          \frac{1}{2} \sum_i \text{max}(p_i,q_i) \\
          &= \frac{1}{2} \sum_i \left( \frac{p_i+q_i}{2} + \frac{|p_i-q_i|}{2} \right) \\
          &= \frac{1}{2} + \frac{1}{2} \sum_i \frac{|p_i-q_i|}{2} \\
          &= \frac{1}{2} + \frac{1}{2} d_\text{TV}(\{p_i\},\{q_i\})
        \end{align*}
      \item statistical distance/total variation: $d_\text{TV}(\{p_i\},\{q_i\})
        = \sum_i \frac{|p_i-q_i|}{2}$.
    \end{itemize}
  \item Still the optimal is unproven!
\end{itemize}

% \bibliography{library.bib}{}
% \bibliographystyle{alphaurl}
% \printnomenclature

\end{document}

### 2018-01-08 Programs/Python/excel-2-latex.py
a useful script

@@ -1,0 +1,25 @@
+# assert python 3.5
+# assert pandas installed
+import pandas as pd
+import sys
+
+
+def print_usage(script_name):
+    print("Usage: {} excel_file output_file [sheet_name]".format(script_name))
+
+if __name__ == '__main__':
+    argv = sys.argv
+    sheet_name = 0 # default, read the 0th sheet
+    if len(argv) == 3:
+        filename = argv[1]
+        outfilename = argv[2]
+    elif len(argv) == 4:
+        filename = argv[1]
+        outfilename = argv[2]
+        sheet_name = argv[3]
+    else:
+        script_name = argv[0]
+        print_usage(script_name)
+        exit(0)
+    excel_f = pd.read_excel(io=filename, sheet_name=sheet_name)
+    excel_f.to_latex(outfilename)

### 2018-03-10 Programs/Python/convolution.py
add python script to generate latex figs.

@@ -9,3 +9,20 @@ col = np.convolve(a1,a2,'full') # full: This returns the convolution at each poi
 print(col)
 # which should equal to a Binomial Distribution (n=2,p=0.7)
 print(np.isclose(col,[0.09,0.42,0.49]).all())
+
+# Now for two measurements with different possible outcomes
+p1 = [0.4,0.6]
+p2 = [0.4,0.6]
+
+q1 = [0.6,0.4]
+q2 = [0.6,0.4]
+
+suc = 1/2 * p1[1] + 1/2 * q1[0]
+
+colp = np.convolve(p1,p2,'full')
+colq = np.convolve(q1,q2,'full')
+
+suc_2time = 1/2 * colp[2] + 1/2 * colq[0]
+
+print('suc rate:'+str(suc))
+print('suc_2time:'+str(suc_2time))

### 2018-03-10 Programs/Python/gen_latex.py

@@ -1,0 +1,198 @@
+from pathlib import Path
+import os
+import math
+from collections import namedtuple
+from typing import List
+
+
+class Subfig:
+    """
+    Creates a subfig environment containing many figures added to this package
+    """
+    TEMPLATE = r"""\begin{figure}%
+__ALIGNMENT__
+__SUBFIGS__
+
+\caption{__CAPTION__}
+\label{fig:__LABEL__}
+\end{figure}
+"""
+    SINGLE_FIG = r"""\subfloat[__LIST_ENTRY__][__SUB_CAPTION__]{
+    \label{fig:__SUB_LABEL__}%
+    \includegraphics[__INC_OPTION__]{__FIGPATH__}
+}
+""" # todo width
+    Fig = namedtuple('fig', ['figpath', 'list_entry', 'sub_caption','sub_label','inc_option'])
+
+    def __init__(self, caption, alignment = 'left', label=None):
+        """
+
+        :param caption: The caption for every subfig in this environment
+        """
+        self.caption = caption
+        if label is None: self.label = caption
+        else: self.label = label
+        if alignment == 'left':
+            self.alignment = ''
+        elif alignment == 'center':
+            self.alignment = '\\centering'
+        else:
+            raise ValueError(alignment)
+
+        self.figs = []
+
+    def add_fig(self, figpath: str,
+                sub_caption = '', sub_label = None, list_entry = '',
+                include_option = ''):
+        if Path(figpath).exists(): pass
+        else: print('"' + figpath + '" not found (may not exist)')
+        if sub_label is None:
+            tmp = os.path.basename(figpath)
+            sub_label = ''.join([x if x.isalnum() else '_' for x in tmp ])
+
+        fig = self.Fig(
+            figpath=figpath, list_entry=list_entry, sub_caption=sub_caption,
+            sub_label=sub_label, inc_option=include_option
+        )
+        self.figs.append(fig)
+
+    def _fig_to_latex(self, fig:Fig):
+        tmp = self.SINGLE_FIG.replace('__LIST_ENTRY__',fig.list_entry)
+        tmp = tmp.replace('__SUB_CAPTION__',fig.sub_caption)
+        if fig.sub_label == False:
+            tmp = tmp.replace('\n    \\label{fig:__SUB_LABEL__}%', '')
+        else:
+            tmp = tmp.replace('__SUB_LABEL__', fig.sub_label)
[…]

### 2018-03-10 Notes of various papers/ud-3-ortho-peres/ud-3-ortho.tex

\documentclass{article}

\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\usepackage[sharp]{easylist} % use # symbol to denote a list

\makenomenclature

\title{UD Between 3 Non-ortho}
\date{\today}
\author{Taper}

\begin{document}

\maketitle

\begin{abstract}
This is a note for \href{https://arxiv.org/abs/quant-ph/9804031}{Optimal distinction between non-orthogonal quantum states}.
\end{abstract}

\section{Background}

\begin{easylist}[enumerate]
# Why unambiguous?
## It may happen that we have unlimited supply of data
## But we cannot afford a mistake
### Example: cryptography (?)
### why cryptography? $\to$ {\color{red} don't know!}
# Nonortho for $2$ states: solved by [4-6]
## Chefles investigated $N$ linearly independent states $\to$ partial result
# Here: $3$ states
## uses POVM
## a failure could also give contribution using posterior probabilities
## could be extended to $N$ states $\to$ become tedious
\end{easylist}

\section{Setup}

\begin{easylist}[enumerate]
# $\dim{H} =3$
# Input: $u_1, u_2, u_3$, with \textit{a priori} probability $p_1,p_2,p_3$.
# Aim: maximize expected gain of signal
# Start with 
## something approximately $ v_1=u_2\times u_3$.
## it looks like orthogonal complement
## We will add restriction to $v_i$.
#Finally
## $A_j = k_j \ketbra{v_j}$, where $k_j$ is something we want to maximize.
## $P_j = \braket{u_j, A_j u_j}$, and $P_0 = \sum_{j=1}^3 p_j \braket{u_j, A_0 u_j}$.
## Obviously, the $k_j$ must make $A_0 =\id - \sum_{i=1}^3 A_j$ a valid positive operator
## The restriction is discussed in p.4 to 5, and especially eq (11)
## Most useful condition: $\det(A_0)\geq 0$, finally turn into: eq. (12)
# Result
## Let: $G=\sum_j C_j P_j$ , where $C_j$ is the value of signal for $u_j$.
## Maximal $G$ could be obtained by adjusting $k_j$, and the process is discussed in p.6 to p.7
## Example:
### When $p_j=\frac{1}{3}$, and all $C_j=1$, the optimal result is when $k_1=$ .... And $P_0=0.8386$.
### When $p_j$ = as above, but $C_1=0.8, C_2 = 1.2$ and $C_3=1$, the optimal result is in a different sets of $k_i$, and $P_0 = 0.8626$.
## {\color{red} It feels odd to talk about different values for $C_i$.}

# Why Inconclusive matters?
## The initial entropy is $H_\text{init} = -\sum_{j=1}^3 p_j \ln p_j$ 
## In general, the optimal $A_0$ is a matrix of rank $2$, written as: $A_0 = \lambda_m\ketbra{m} + \lambda_n \ketbra{n}$.
## The probability of $m$'s result is: $P_{mj} = p_j \lambda_m |\braket{m,u_j}|^2$
## Using Bayes' theorem, we could have, the posterior probability for input $u_j$ upon observing output$m$ is
### $Q_{jk} = P_{mj}/\sum_{i=1}^3 P_{mi}$ 
## The entropy of this $H_m = -\sum_{j=1}^3 Q_{jm} \ln Q_{jm}$ is usually $H_m < H_\text{init}$.
## Hence at least some information has been gained
## {\color{red} Is this a meaningful gain? How to make use of this?}
#  $N> 3$ signals
## only sketched, actually many are conjectures.

\end{easylist}
\end{document}

### 2018-06-01 Quantum Computation/rBernsteinVazirani.tex
rBV alg notes.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\title{The Recursive and Non-recursive Bernstein-Vazirani Algorithm}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
Based on notes available at:
% \href{https://courses.cs.washington.edu/courses/cse599d/06wi/lecturenotes7.pdf}
}
\tableofcontents

\section{Notation}
\label{sec:Notation}

A $\vec{x}$ is a vector of $n$ binary numbers. A summation $\sum_{\vec{x}}$ is a
summation over all possible $n$ binary numbers: $\sum_{\vec{x}}=\sum_{x\in
  \{0,1\}^n}$. A dot product between two vectors is $\vec{x}\vdot\vec{y} =
  \sum_{i=0}^{n-1} x_i y_i \text{ mod }2$.

\section{Tricks}
\label{sec:Tricks}

\subsection{Hadamard gate}
\label{sec:Hadamard gate}

The Hadamard gate can be written in the following notation:

\begin{equation}
  H = \frac{1}{\sqrt{2^n}}\sum_{\vec{x},\vec{y}} (-1)^{\vec{x}\vdot\vec{y}}
  \ket{\vec{x}}\bra{\vec{y}}.
\end{equation}

Define $\ket{P_{\vec{x}}}$ as
\begin{equation}
  \ket{P_{\vec{x}}} = \frac{1}{\sqrt{2^n}} \sum_{\vec{y}}
  (-1)^{\vec{x}\vdot\vec{y}} \ket{\vec{y}}.
\end{equation}
One can verify that
\begin{equation}
  \braket{P_{\vec{x}} |P_{\vec{y}}} = \delta_{\vec{x},\vec{y}},\,
  \sum_{\vec{x}}\ketbra{P_{\vec{x}}} = \id.
\end{equation}
And the Hadamard gate could be written as
\begin{equation}
  H = \sum_{\vec{x}} \ket{\vec{x}}\bra{P_{\vec{x}}} 
  = \sum_{\vec{x}} \ket{P_{\vec{x}}} \bra{\vec{x}}.
\end{equation}
Therefore the Hadamard gate transfer between the basis where information is
recorded in qubit register $\ket{\vec{x}}$ and the basis where information is
recorded in the phase $\ket{P_{\vec{x}}}$. A special state which will be used
often is
\begin{equation}
  \ket{P_0} = \frac{1}{\sqrt{2^n}} \sum_{\vec{x}}\ket{\vec{x}}.
\end{equation}

\subsection{Phase kickback}
\label{sec:Phase kick}
For a classical function $f:\{0,1\}^n\to \{0,1\},\, \vec{x}\mapsto f(\vec{x})$,
its analogous quantum gate is $U_f:\ket{\vec{x},y} \mapsto \ket{\vec{x},y\oplus
f(x)}$. Quantum computation can calculate this in a parallel manner as a phase
gate by
\begin{equation}
  U_f \left(\sum_{\vec{x}} \phi(\vec{x})  \ket{\vec{x}}
  \otimes \frac{1}{\sqrt{2}} (\ket{0}-\ket{1}) \right)
  = \sum_{\vec{x}} (-1)^{f(\vec{x})} \phi(\vec{x})\ket{\vec{x}} 
  \otimes \frac{1}{\sqrt{2}} (\ket{0}-\ket{1}),
\end{equation}
where $\phi(\vec{x})$ are some arbitrary non-zero phase. If we ignore the
ancilla qubit, then $U_f$ is acting as a phase $(-1)^{f(\vec{x})}$ on every
$\ket{\vec{x}}$ on ``parallel".

\section{The recursive Bernstein-Vazirani}
\label{sec:The recursive Bernstein-Vazirani}

The recursive Bernstein-Vazirani problem (rBV) of level $k$ asks us to find an n-bit number
$\vec{s}$ through a series of oracles provided. The first oracle provided is
$f:\{0,1\}^{nk}\to \{0,1\},\, \{\vec{x}_1,\cdots, \vec{x}_k\}\mapsto
\vec{x}_k\vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}$, where we need to find
out the $n$ number $\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}$. The following
oracles are 
\begin{equation}
  g_j: \{0,1\}^n\to \{0,1\},\, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \mapsto \vec{x}_j \vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{j-1}},\,
  j=k-1,k-2,\cdots,1.
\end{equation}
The final $g_1$ is slightly different because
$g_1(\vec{s}_{\vec{x}_1})=\vec{s}\vdot\vec{x}_1$. Here we would step by step
find out the numbers $\vec{s}_{\vec{x}_1,\cdots,\vec{x}_j}$, until finally we
have $\vec{s}$. Classically the query complexity is lowered bounded as
$\Omega(n^k)$.

\subsection{A quantum algorithm}
\label{sec:A quantum algorithm}

Define the quantum version of oracles as
\begin{align}
  & f\ket{\vec{x}_1,\cdots,\vec{x}_k} =
  (-1)^{\vec{x}_k\vdot\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \ket{\vec{x}_1,\cdots,\vec{x}_k},\\
  & g_j \ket{\vec{x}_1,\cdots, \vec{x}_j, 
    \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\cdots,\vec{x}_k}\nonumber\\
  & = (-1)^{\vec{x}_j \vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{j-1}}}
    \ket{\vec{x}_1,\cdots, \vec{x}_j, 
    \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\cdots,\vec{x}_k},\nonumber\\
  & \;\text{for } j=k-1,k-2,\cdots ,2,\\
  & g_1 \ket{\vec{x}_1, \vec{s}_{\vec{x}_1}, \vec{x}_3, \cdots,\vec{x}_k} =
  (-1)^{\vec{x}_1 \vdot \vec{s}} \ket{\vec{x}_1, \vec{s}_{\vec{x}_1}, \vec{x}_3, \cdots,\vec{x}_k},
\end{align}
where we have used the phase kickback trick mentioned in section~\ref{sec:Phase
kick} and ignored the ancilla qubits. Notice that all quantum oracles are
meaningless phase gate unless a superposition of basis
$\ket{\vec{x}_1,\cdots,\vec{x}_k}$ are present. In the following, we will always
ensure a superposition of the form 
\[
  \sum_{\vec{x}_1,\cdots,\vec{x}_j} \phi(\vec{x}_1,\cdots,\vec{x}_j,\text{(something)})
  \ket{\vec{x}_1,\cdots,\vec{x}_j,\text{(something)}},
\]
is always present for $g_j$ to act on. Here $\phi$ are still some non-zero phases.

A quantum algorithm to solve rBV problem depends on the following operators
$D_j(j=1,\cdots,k)$, defined recursively by:

\begin{align}
  &D_k = H^{\otimes n}_{k} f, \\
  &D_{k-1} = H^{\otimes n}_{k-1} D^\dagger_k g_{k-1}, \\
  &D_{k-2} = H^{\otimes n}_{k-2} D^\dagger_k D^\dagger_{k-1} g_{k-2}, \\
  &\cdots \\
  &D_1 = H^{\otimes n}_1 D^\dagger_k D^\dagger_{k-1}\cdots D^\dagger_2 g_1.
\end{align}

Here the $H^{\otimes n}_j$ is the $n$ bit Hadamard gate $H^{\otimes n}$ acting
on the $j$th register.

The first operator $D_k$ does the following:
\begin{align}
  & D_k \sum_{\vec{x}_1,\cdots,\vec{x}_k} \ket{\vec{x}_1,\cdots,\vec{x}_k}\nonumber\\ 
  = & H^{\otimes n}_k \sum_{\vec{x}_1,\cdots,\vec{x}_k}
  (-1)^{\vec{x}_k\vdot\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \ket{\vec{x}_1,\cdots,\vec{x}_k} \\
  = & H_k^{\otimes n} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},P_{\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}}
  \\
  = & \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{align}
Notice that if there are some arbitrary non-zero phases
$\phi(\vec{x}_1,\cdots,\vec{x}_k)$ in front of
$\ket{\vec{x}_1,\cdots,\vec{x}_k}$ on the first line, the final result will not
change except from this arbitrary phase. $D_k$ can be understood as the following
diagram:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_k} \arrow[r, bend left, "D_k"] & 
   \arrow[l, bend left, "D^\dagger_k"] 
   \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{tikzcd}
\end{equation}

The second operator $D_{k-1}$ does the following next:
\begin{align}
  & D_{k-1} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
  \\
  =& H^{\otimes n}_{k-1} D^\dagger_k \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}} 
  (-1)^{\vec{x}_{k-1}\vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
  \\
  =& H^{\otimes n}_{k-1} \sum_{\vec{x}_1,\cdots,\vec{x}_{k}}
  (-1)^{\vec{x}_{k-1}\vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \\
  =& H^{\otimes n}_{k-1} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-2}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},
  P_{\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}}},P_0}
  \\
  =& \sum_{\vec{x}_1,\cdots,\vec{x}_{k-2}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-2}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}},P_0}
\end{align}

Similarly, we have the following diagram for $D_{k-1}$:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \arrow[r, "\text{load phase}", "g_{k-1}" below,]
  \dar[bend left, "D_{k-1}"]
  & 
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
  \dar["D^\dagger_k"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}},P_0}
  \uar[bend left, "D^\dagger_{k-1}"]
  &
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}

Similarly for $D_{k-j}$, we use $g_j$ to load the phase 
$(-1)^{\vec{x}_j\vdot \vec{s}_{\cdots}}$, and use $D^\dagger_k\cdots
D^\dagger_{k-j+1}$ to solve the lower level rBV problem, and use Hadamard gate
to unload the phase into basis:

\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \arrow[r, "\text{load phase}", "g_j" below,]
  \dar[bend left, "D_{k-1}"]
  & 
  (-1)^{\cdots} 
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \dar["D^\dagger_k\cdots D^\dagger_{k-j+1}"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j-1}},P_0^{\otimes j}}
  \uar[bend left, "D^\dagger_{k-1}"]
  &
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}

The operators $D^\dagger_k\cdots D^\dagger_{k-j+1}$ solves the lower level
problem by gradually moving the $s$ number to the end:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}}
  \rar["D^\dagger_{k-j+1}"]
  &
  \ket{\cdots,\vec{x}_{k-j+1}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j+1}},P_0^{\otimes j-2}}
  \ar[ld]
  \\
  \cdots \rar["D_k"]
  &
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
\end{tikzcd}
\end{equation}

And finally:
\begin{equation}
  D_1 \sum_{\vec{x}_1}\ket{\vec{x}_1, \vec{s}_{\vec{x}_1}, P_0^{\otimes k-2}} =
  \ket{\vec{s}, P_0^{\otimes k-1}}.
\end{equation}
With a measurement in the computational basis, one can with certainty find the
number $\vec{s}$.

\subsection{Complexity of quantum algorithm}
\label{sec:Complexity of quantum algorithm}
The number of steps taken in $D_k$ is $2$. In $D_{k-2}$ is $2+2=2^2$, in
$D_{k-3}$ is $2+2^2+2=2^3$. In general, in $D_{k-j}$ is
\begin{equation}
  \# D_{k-j} = 2^1 + 2^2 + \cdots + 2^{j-1} + 2 = 2^j
\end{equation}

Hence, the total complexity is:
\begin{equation}
  2 + 2^2 + \cdots + 2^k = 2^{k+1}-2 \approx O(2^k)
\end{equation}

If $k=\log_2 n$, then the quantum complexity is $O(n)$ whereas the classical
complexity is lower bounded as $\Omega(n^{\log_2 n})$.

\end{document}

### 2018-06-01 Quantum Computation/rBernsteinVazirani.tex
update

@@
 \usepackage[log-declarations=false]{xparse}
-\usepackage{physicist-taper}
+\usepackage[final]{physicist-taper}
 
-\title{The Recursive and Non-recursive Bernstein-Vazirani Algorithm}
+\title{The Recursive Bernstein-Vazirani Algorithm}
 \date{\today}
-\author{Taper}
+\author{Hongxiang Chen}
 
@@
 Based on notes available at:
-% \href{https://courses.cs.washington.edu/courses/cse599d/06wi/lecturenotes7.pdf}
+\url{https://courses.cs.washington.edu/courses/cse599d/06wi/lecturenotes7.pdf}
 }
@@
 \]
-is always present for $g_j$ to act on. Here $\phi$ are still some non-zero phases.
+is present for $g_j$ to act on. Here $\phi$ are some non-zero phases.
 
@@
 Here the $H^{\otimes n}_j$ is the $n$ bit Hadamard gate $H^{\otimes n}$ acting
-on the $j$th register.
-
-The first operator $D_k$ does the following:
+on the $j$th register. Each operator $D_{k-j}$ solve the $j$th level rBV
+problem. Specifically, the first operator $D_k$ does the following:
 \begin{align}
@@
 \begin{equation}
-\begin{tikzcd}
+\begin{tikzcd}[row sep=large, column sep = large]
   \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
   \arrow[r, "\text{load phase}", "g_j" below,]
-  \dar[bend left, "D_{k-1}"]
+  \dar[bend left, "D_{k-j}"]
   & 
@@
   \\
-  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j-1}},P_0^{\otimes j}}
-  \uar[bend left, "D^\dagger_{k-1}"]
+  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j-1}},P_0,P_0^{\otimes j-1}}
+  \uar[bend left, "D^\dagger_{k-j}"]
   &
-  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
+  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-j}, \vec{x}_{k-j+1},\cdots,\vec{x}_{k}}
   \lar["\text{unload phase}" above, "H"]
@@
 \begin{tikzcd}
-  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}}
+  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0,P_0^{\otimes j-2}}
   \rar["D^\dagger_{k-j+1}"]
@@
   \ket{\cdots,\vec{x}_{k-j+1}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j+1}},P_0^{\otimes j-2}}
-  \ar[ld]
+  \dar["\cdots"]
   \\
-  \cdots \rar["D_k"]
+  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
   &
-  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
+  \ket{\cdots,\vec{x}_{k-j+1},\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_{k-1}}}
+  \lar["D_k"]
 \end{tikzcd}
@@
 
-And finally:
+And finally we note that:
 \begin{equation}
@@
 With a measurement in the computational basis, one can with certainty find the
-number $\vec{s}$.
+number $\vec{s}$. Therefore, the combined operators $D_1D_2\cdots D_k$ solves
+the $k$th level rBV problem.
 
@@
 \label{sec:Complexity of quantum algorithm}
-The number of steps taken in $D_k$ is $2$. In $D_{k-2}$ is $2+2=2^2$, in
-$D_{k-3}$ is $2+2^2+2=2^3$. In general, in $D_{k-j}$ is
+The number of steps taken in $D_k$ is $2$. In $D_{k-1}$ is $2+2=2^2$, in
+$D_{k-2}$ is $2+2^2+2=2^3$. In general, in $D_{k-j}$ is
 \begin{equation}
-  \# D_{k-j} = 2^1 + 2^2 + \cdots + 2^{j-1} + 2 = 2^j
+  2^1 + 2^2 + \cdots + 2^{j-1} + 2 = 2^{j+1}
 \end{equation}

### 2018-06-01 Quantum Computation/rBernsteinVazirani.tex
update rBV to make it clear.
about the qubit registers

@@
 
-The Hadamard gate can be written in the following notation:
+The Hadamard gate on $n$ qubits $H^{\otimes n}$ can be written in the following notation:
 
 \begin{equation}
-  H = \frac{1}{\sqrt{2^n}}\sum_{\vec{x},\vec{y}} (-1)^{\vec{x}\vdot\vec{y}}
+  H^{\otimes n} = \frac{1}{\sqrt{2^n}}\sum_{\vec{x},\vec{y}} (-1)^{\vec{x}\vdot\vec{y}}
   \ket{\vec{x}}\bra{\vec{y}}.
@@
 \begin{equation}
-  H = \sum_{\vec{x}} \ket{\vec{x}}\bra{P_{\vec{x}}} 
+  H^{\otimes n} = \sum_{\vec{x}} \ket{\vec{x}}\bra{P_{\vec{x}}} 
   = \sum_{\vec{x}} \ket{P_{\vec{x}}} \bra{\vec{x}}.
@@
 Therefore the Hadamard gate transfer between the basis where information is
-recorded in qubit register $\ket{\vec{x}}$ and the basis where information is
-recorded in the phase $\ket{P_{\vec{x}}}$. A special state which will be used
+recorded in qubit register ($\ket{\vec{x}}$) and the basis where information is
+recorded in the phase ($\ket{P_{\vec{x}}}$). A special state which will be used
 often is
@@
 
+Here we present a simple quantum algorithm to the $k$th level rBV problem. The
+quantum register are initialised in the state:
+\begin{equation}
+  \ket{P_0}^{\otimes k}\otimes \ket{-} \otimes \cdots \otimes \ket{-} 
+  = \left(\frac{1}{\sqrt{2^n}}\right)^k
+  \sum_{\vec{x}_1,\cdots,\vec{x}_{k}} \ket{\vec{x}_1,\cdots,\vec{x}_k}
+  \ket{-} \otimes \cdots \otimes \ket{-}.
+\end{equation}
+
+Here the first $k\times n$ qubits are grouped into $k$ qubit registers, each
+having $n$ qubits. The rest of qubits are ancilla qubits prepared in the
+$\ket{-} = (\ket{0}-\ket{1})/\sqrt{2} $ state. Although for simplicity we will
+ignore them in the following calculation, it should be noted that the ancilla
+qubits are important for the phase kickback trick mentioned before. Also for
+simplicity, we will ignore all normalisation constant for for the following
+discussion. Therefore the initial state of qubit register is written as:
+\begin{equation}
+  \sum_{\vec{x}_1,\cdots,\vec{x}_{k}} \ket{\vec{x}_1,\cdots,\vec{x}_k}
+\end{equation}
+
 Define the quantum version of oracles as
@@
   & g_j \ket{\vec{x}_1,\cdots, \vec{x}_j, 
-    \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\cdots,\vec{x}_k}\nonumber\\
+  \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\vec{x}_{j+2},\cdots,\vec{x}_k}\nonumber\\
   & = (-1)^{\vec{x}_j \vdot \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{j-1}}}
     \ket{\vec{x}_1,\cdots, \vec{x}_j, 
-    \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\cdots,\vec{x}_k},\nonumber\\
+    \vec{s}_{\vec{x}_1,\cdots,\vec{x}_j} ,\vec{x}_{j+2},\cdots,\vec{x}_k},\nonumber\\
   & \;\text{for } j=k-1,k-2,\cdots ,2,\\
@@
 
-A quantum algorithm to solve rBV problem depends on the following operators
+A quantum algorithm to solve the rBV problem depends on the following operators
 $D_j(j=1,\cdots,k)$, defined recursively by:
@@
 
-Here the $H^{\otimes n}_j$ is the $n$ bit Hadamard gate $H^{\otimes n}$ acting
+Here the $H^{\otimes n}_j$ is simply the $n$ bit Hadamard gate $H^{\otimes n}$ acting
 on the $j$th register. Each operator $D_{k-j}$ solve the $j$th level rBV
@@
   =& H^{\otimes n}_{k-1} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-2}}
-  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},
+  \ket{\vec{x}_1,\cdots,\vec{x}_{k-2},
   P_{\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}}},P_0}
@@
 \label{sec:Complexity of quantum algorithm}
-The number of steps taken in $D_k$ is $2$. In $D_{k-1}$ is $2+2=2^2$, in
-$D_{k-2}$ is $2+2^2+2=2^3$. In general, in $D_{k-j}$ is
+The number of gates ($n$ bit Hadamard and quantum queries) taken in $D_k$ is
+$2$. In $D_{k-1}$ is $2+2=2^2$, in $D_{k-2}$ is $2+2^2+2=2^3$. In general, in
+$D_{k-j}$ there are
 \begin{equation}
-  2^1 + 2^2 + \cdots + 2^{j-1} + 2 = 2^{j+1}
+  2^1 + 2^2 + \cdots + 2^{j-1} + 2 = 2^{j+1},
 \end{equation}
-
-Hence, the total complexity is:
+$n$ bit Hadamard gates and quantum query gates. Hence, the total complexity is:
 \begin{equation}

### 2018-06-04 Quantum Computation/rBV/rBernsteinVazirani.tex
add html ver converted from latex by lwarp (experimental)

--- 2018-06-01 Quantum Computation/rBernsteinVazirani.tex
@@
 
+% for lwarp package: converting latex to html.
+\usepackage{iftex}
+
+% --- LOAD FONT SELECTION AND ENCODING BEFORE LOADING LWARP ---
+
+\ifPDFTeX
+\usepackage{lmodern}            % pdflatex
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\else
+\usepackage{fontspec}           % XeLaTeX or LuaLaTeX
+\fi
+
+% --- LWARP IS LOADED NEXT ---
+\usepackage[
+%   latexmk,                    % Use latexmk to compile.
+%   mathjax,                    % Use MathJax to display math.
+]{lwarp}
+
+% --- LATEX AND HTML CUSTOMIZATION ---
+\setcounter{tocdepth}{2}        % Include subsections in the \TOC.
+\setcounter{secnumdepth}{2}     % Number down to subsections.
+\setcounter{FileDepth}{-5}       % To place the entire file into one html page
+\booltrue{CombineHigherDepths}  % Combine parts/chapters/sections
+\setcounter{SideTOCDepth}{1}    % Include subsections in the side\TOC
+\HTMLLanguage{en-UK}            % Sets the HTML meta language.
+\CSSFilename{lwarp_formal.css}
+
+% --- OTHER PACKAGES ARE LOADED AFTER LWARP ---
 % My own physics package
@@
 % "physics" loaded in package "physicist-taper".
-\usepackage[log-declarations=false]{xparse}
+% \usepackage[log-declarations=false]{xparse}
 \usepackage[final]{physicist-taper}
+
+% for lwarp to work with tikz
+\tikzset{every picture/.style={ampersand replacement=\&}}
 
@@
 \end{align}
+
 Notice that if there are some arbitrary non-zero phases
@@
 diagram:
+\displaymathother
 \begin{equation}
 \begin{tikzcd}
-  \ket{\cdots,\vec{x}_k} \arrow[r, bend left, "D_k"] & 
+  \ket{\cdots,\vec{x}_k} \arrow[r, bend left, "D_k"] \& 
    \arrow[l, bend left, "D^\dagger_k"] 
@@
 \end{equation}
+\displaymathnormal
 
@@
 Similarly, we have the following diagram for $D_{k-1}$:
+\displaymathnormal
 \begin{equation}
@@
   \dar[bend left, "D_{k-1}"]
-  & 
+  \& 
   (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
@@
   \uar[bend left, "D^\dagger_{k-1}"]
-  &
+  \&
   (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
@@
 \end{equation}
+\displaymathother
 
@@
 
+\displaymathother
 \begin{equation}
@@
   \dar[bend left, "D_{k-j}"]
-  & 
+  \& 
   (-1)^{\cdots} 
@@
   \uar[bend left, "D^\dagger_{k-j}"]
-  &
+  \&
   (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-j}, \vec{x}_{k-j+1},\cdots,\vec{x}_{k}}
@@
 problem by gradually moving the $s$ number to the end:
+\displaymathother
 \begin{equation}
@@
   \rar["D^\dagger_{k-j+1}"]
-  &
+  \&
   \ket{\cdots,\vec{x}_{k-j+1}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j+1}},P_0^{\otimes j-2}}
@@
   \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
-  &
+  \&
   \ket{\cdots,\vec{x}_{k-j+1},\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_{k-1}}}

### 2018-06-05 Quantum Computation/simons_alg/simons.tex
simons alg draft

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\title{Simons's Algorithm}
\date{\today}
\author{Hongxiang Chen}

\begin{document}

\maketitle
\abstract{
  Based on Watrous's notes.
}

\section{Why the probability looks in that way}
\label{sec:Why the probability looks in that way}

We are asked of the probability of finding $n-1$ linear independent vectors
$\vec{y}_1,\cdots,\vec{y}_{n-1}$ in the vectors space of dimension $n$ over
binary numbers satisfying the condition:
\begin{equation}
  \vec{s}\vdot\vec{y_i} = 0, \forall i=1,\cdots,n-1
\end{equation}
We could assume that all vectors satisfying the above condition appear with equal
probability.

Since the binary numbers are quite limited, this is a discrete probability and
we could count this easily. Assuming we have founded $m$ linearly independent
vectors $\vec{y}_1,\cdots,\vec{y}_m$, without loss of generality, we could
assume:
\begin{align}
  \vec{y}_1 &= (1,0,\cdots,0), \\
  \vec{y}_2 &= (0,1,0,\cdots,0), \\
            &\cdots, \nonumber\\
  \vec{y}_m &= (0,\cdots,0,1,0,\cdots,0)
\end{align}

Then over all $2^{n-1}$\footnote{Because the condition $\vec{y}\vdot\vec{s}=0$
reduces the dimension by $1$. Formally, this is the result of Rank–nullity
theorem over the field $\mathbb{Z}_2$.} possible vectors, $2^m$ vectors can be linearly expressed by the
above founded vectors. Therefore, the probability of finding the next linearly
independent vector is $\left(1-\frac{2^m}{2^{n-1}}\right)$. Therefore, overall the probability
of finding $n-1$ linearly independent vectors are:
\begin{equation}
  \prod_{k=1}^{n-2}\left(1-\frac{2^k}{2^{n-1}}\right) = \prod_{k=1}^{n-2}
  \left(1-\frac{1}{2^k}\right)
\end{equation}
This is clearly decreasing number w.r.t $n$, hence in the asymptotic limit the
probability is:
\begin{equation}
  \prod_{k=1}^{\infty}\left(1-\frac{1}{2^k}\right).
\end{equation}
\end{document}

### 2018-07-17 Quantum Computation/cvQNN/cvqnn.tex
notes for cv qnn

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}
\usepackage{fullpage}
% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}
\makenomenclature % For an index of symbols.

\title{CV QNN}
\date{\today}
\author{}

\begin{document}

\maketitle
\abstract{
  Notes of arXiv:1806.06871v1
}
\tableofcontents

\section{Continuous Variable Quantum Neural Networks}

\subsection{General continuous variable quantum computation}

Continuous variable quantum computation operates on another model of quantum computation. The states could be represented in two different ways. For one *qumode*, it can be represented as:

\begin{enumerate}
  \item 
A Fock state, $\ket{n}$, where $n\in \mathbb{N}$. They live in a Hilber
space, called Fock space of countable infinite dimension. Their amplitudes are
probabilities, and the transformations are unitary. It is analogus to (but not
the same as) a state of $n$ bosons \footnote{There seems to be no more degree of freedom when $n$ increases. It is not clear what $\ket{n}$ means physically. TODO: check this.}. For multiple qumodes, the state is represented as $\ket{n_0,n_1,\cdots,n_{i-1}}$.
\item
A phase space vector (not a ket) $(x,p)$ where $x$ and $p$ are both real
numbers. They are expecation value of two conjugate operator $\hat{x}$ and
$\hat{p}$\footnote{In some sense, $x$ and $p$ could be understood as momentum. TODO: Check this.}. Here the amplitudes $F(x,p)$ are not probabilities but quasiprobability distributions. The transformation in this picture are much more diverse, and will be used as to embede arbitrary classical neural networks. For multiple qumodes, the state is represented as two vectors $(\vec{x}, \vec{p})$ put together.
\end{enumerate}

\textbf{Note}:
We note that this infinite-dimensional Fock space cannot be simulated classically. What they do is to cut-off the dimension above a number, so that the Hilbert space is truncted. This creates unnormalised state in simulation. To address this issue, they add a penality in the cost function as:

$$
P(\{\ket{\psi_{x_i}}\}) = 
\sum_i \left( |\braket{\psi_{x_i} | \Pi_H | \psi_{x_i}}| - 1\right)^2
$$

where $\Pi_H$ projects onto the truncted Hilbert space.

\subsection{ General transformation on CV model and embedding classical neural
network}

The general transformation on $N$ qumodes are devided into two categories: the Gaussian gates and non-Gaussian gates.

\textbf{ Gaussian}:
The Gaussian gates could achieves a transformation:

$$ 
(\vec{x}, \vec{p}) \to M (\vec{x}, \vec{p}) + (\vec{\alpha_r}, \vec{\alpha_i})
$$

Here $M$ is a sympletic real matrix of size $2N\times 2N$, $\vec{\alpha_r}$
and $\vec{\alpha_i}$ are real and complex part of a complex vector
$\vec{\alpha}\in \mathbb{C}^{N}$. In essence, most linear transformations
($M$) plus affine transformation (displacement, $\vec{\alpha}$) can be
achieved.

Importantly, $M$ is of size $2N\times 2N$ and has a lot of freedom inside (i.e. its submatrix could be non-sympletic). When we only use the $\vec{x}$ vectors to do quantum computation (i.e. we care only about $\vec{x}$ and avoid computations that mixes $\vec{x}$ and $\vec{p}$), arbitrary real matrix $W$ of size $N\times N$ could be implemented using Gaussian gates. Together with the affine transformation, this means any linear neural network of weight $W$ and bias $\vec{b}$ could be implemented using quantum computations such that (discussed in P.6):

$$
D\circ U_2 \circ S \circ U_1 \ket{\vec{x}} = \ket{W\vec{x} + \vec{b}}
$$

This corresponds to the first part of a layer in Fig.1.

\textbf{Non-Gaussian}: The non-Guassian gates achieves a nonlinear function
\footnote{It is not clear to me what kind of non-linear function could be achieved, TODO check.}:
$$
\Phi \ket{\vec{x}} = \ket{\phi(\vec{x})}
$$

Specifically, the author proposed a gate $V = \exp(i \phi(\hat{x}_i)\otimes \hat{p}_{i'})$, where $\phi(x)$ is a polynomial of a fixed degree, which could approximate any smooth function by Taylor expansion. They used this gate to achieve arbitrary nonlinear transformation:
$$
\ket{x_i} \to \ket{\phi(x_i)}
$$

Together with the Gaussian gates, we have the embedding of arbitrary classical neural network of the form $\Phi(W\vec{x}+\vec{b})$ as a quantum neural networks in Fig.1.

\textbf{ Specific neural networks structure} The paper also discusses how many specific neural network structure could be  implemented as in a quantum neural network. This includes:

\begin{itemize}
  \item \textbf{Convnet}: implemented just as a special matrix to do the convolution
  \item \textbf{RNN}: implemented by reusing the same parameter for the quantum layer. Also, it is very convenient to connect the output of a CV quantum computer back to its input on a optical implementation of CV quantum computer
  \item \textbf{Residual Network}: implemented as a gate $\ket{\vec{x}} \to \ket{\vec{x} + \phi(\vec{x})}$.
\end{itemize}

\subsection{ CV-QNN Experiments}

1. Function fitting
\begin{table}[H]
  \centering
  \caption{Experiments}
  \label{tab:label}
  \extrarowsep=3mm
  \begin{tabu}{X[0.5]|X|X|X|X}
    & Function fitting & Classifying data & Generating image & Auto-encoder 
    \\
    Purpose &
    Produce a circuit which fits the function
    $\ket{x} \overset{\text{circuit}}{\to} \ket{f(x)}$.&
    Classify whether the transaction is genuine or fraud. &
    For $m$ size $N\times N$ images, choose $m$ initial state $\ket{\phi_\alpha}$
    ($\alpha = 1,\cdots m$), find a circuit that transform $\ket{\phi_\alpha}$
    into a specific encoding of matrix into states ($\ket{A_\alpha}$) for each
    image. &
    Find a circuit which encodes all states with at most two phonons
    $\ket{\phi}=\alpha\ket{0} + \beta\ket{1} +\gamma\ket{2}$ into a phase space
    coordinate $(x,p)$.
    \\
    Circuit &
    \includegraphics[width=1.00\linewidth]{A.pdf} &
    \includegraphics[width=1.00\linewidth]{B.pdf} &
    \includegraphics[width=1.00\linewidth]{C.pdf} &
    \includegraphics[width=1.00\linewidth]{D.pdf} 
    \\
    Input &
    $x \overset{\mathcal{D}}{\to} \ket{(\vec{x},0)}$, data encoded as
    phase space coordinate.&
    Data are processed after a classical layer, and then encoded as angles of circuit.&
    Data are quantum states $\ket{\phi_\alpha}$, each one $\alpha$ is supposed
    to generate a distinct image.&
    Before training, the data are processed by classical layer and then input
    into the quantum layer as phase space coordinate. After training, the encoder accepts two angles as
    the input.
    \\
    Output &
    Output a measured value, which is a real number, interpreted as the function evaluated at $x$. &
    Output a measured value, which is the number of photons in each mode. By
    post-selecting on single-photon outputs, the position of this photon will be
    interpreted as the decision.&
    Output a quantum state, which should be as closed as possible to the state:
    $\ket{A_\alpha} \propto \sum_{i,j} \sqrt{a_{ij}^\alpha} \ket{i,j} $. Here
    $\alpha$ labels the different images. $a_{ij}^\alpha$ is the matrix element of
    that image $\alpha$.&
    Output the state $\ket{\psi} = \alpha\ket{0} + \beta\ket{1} +
    \gamma\ket{2}$.
    \\
    Cost function &
    $\sum_i \left[f(x_i) - \braket{\hat{x}} \right]^2$ plus
    regularisation terms. Here $\braket{\hat{x}}$ is the expectation value after
    the quantum circuit.&
    $\sum_{i\in \text{data}} (1-p_i)^2$, $p_i$ is the probability of correct
    detection.&
    $\sum_i |\braket{\psi_i | A_i}|^2$ plus regularisation terms. Requires 
    tomography! &
    $\sum_i \left(|\braket{ i| \psi_i }|^2 -1\right)^2$ plus regularisation terms.
    Requires tomography!
    \\
    Result &
    Fig.5 & Fig.9 & Fig.10 & Fig.11 
  \end{tabu}
\end{table}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at 
\href{http://www.google.com/recaptcha/mailhide/d?k=015LguzBJigi0rpyuJRqLoig==\&c=p1c-M-mm7ZcjUCkTuZZa9eEPHRVk6paN0694iazlQy8=}
{[My Email Address(Click)]}.

\bibliography{cite}{}
\bibliographystyle{alphaurl}
% \begin{thebibliography}{1}
% 	\bibitem{book} 
% \end{thebibliography}
\printnomenclature

\end{document}

### 2018-07-18 Quantum Computation/cvQNN/cvqnn.tex
update and refine the notes

@@
 
-\title{CV QNN}
+\title{Continuous Variable Quantum Neural Networks}
 \date{\today}
-\author{}
+\author{Hongxiang}
 
@@
 
-\section{Continuous Variable Quantum Neural Networks}
+\section{General continuous variable quantum computation}
 
-\subsection{General continuous variable quantum computation}
-
-Continuous variable quantum computation operates on another model of quantum computation. The states could be represented in two different ways. For one *qumode*, it can be represented as:
-
+Continuous variable quantum computation operates on another model of quantum
+computation. A \textit{qumode} is their basic unit of computation. The state of
+a qumode could be represented in two different ways:
 \begin{enumerate}
-  \item 
-A Fock state, $\ket{n}$, where $n\in \mathbb{N}$. They live in a Hilber
-space, called Fock space of countable infinite dimension. Their amplitudes are
-probabilities, and the transformations are unitary. It is analogus to (but not
-the same as) a state of $n$ bosons \footnote{There seems to be no more degree of freedom when $n$ increases.
-It is not clear what $\ket{n}$ means physically.
-TODO: check this.}.
-For multiple qumodes, the state is represented as $\ket{n_0,n_1,\cdots,n_{i-1}}$.
-\item
-A phase space vector (not a ket) $(x,p)$ where $x$ and $p$ are both real
-numbers. They are expecation value of two conjugate operator $\hat{x}$ and
-$\hat{p}$\footnote{In some sense, $x$ and $p$ could be understood as momentum.
-TODO: Check this.}.
-Here the amplitudes $F(x,p)$ are not probabilities but quasiprobability distributions.
-The transformation in this picture are much more diverse, and will be used as to embede arbitrary classical neural networks.
-For multiple qumodes, the state is represented as two vectors $(\vec{x}, \vec{p})$ put together.
+  \item A Fock state, $\ket{n}$, where $n\in \mathbb{N}$. They live in a Hilbert
+    space called Fock space of countable infinite dimension. Their amplitudes
+    squared are probabilities. $n$ represents a state of $n$ bosons
+    \footnote{There seems to be no more degree of freedom when $n$ increases. It
+    is not clear what $\ket{n}$ means physically. TODO: check this.}. For
+    multiple qumodes, the state is represented as
+    $\ket{n_0,n_1,\cdots,n_{i-1}}$.
+  \item A phase space coordinate $(x,p)$ where $x$ and $p$ are both real
+    numbers. They are expectation values of two conjugate operator $\hat{x}$ and
+    $\hat{p}$ satisfy certain commutation relations.\footnote{We can think of
+      $x$ and $p$ as position and momentum. But each of them gives a complete
+      basis $\int \ketbra{x} = \id = \int \ketbra{p}$, so a pair
+      $(\vec{x},\vec{p})$ does not transform as a vector anymore.
+    }. Note that all coordinates $(\vec{x},\vec{p})$ does not form a
+    basis for the Hilbert space. Therefore their amplitudes $F(x,p)$ are not
+    probabilities but quasiprobability distributions. For multiple qumodes, the
+    state is represented by two vectors $(\vec{x}, \vec{p})$.
 \end{enumerate}
@@
 \textbf{Note}: 
-We note that this infinite-dimensional Fock space cannot be simulated classically.
-What they do is to cut-off the dimension above a number, so that the Hilbert space is truncted.
-This creates unnormalised state in simulation.
-To address this issue, they add a penality in the cost function as:
+\begin{enumerate}
+  \item This infinite-dimensional Fock space cannot be simulated classically.
+    What they do is to cut-off the dimension above a number, so that the Hilbert
+    space is truncated. This creates unnormalised state in simulation. To
+    address this issue, they add a penalty as a regularisation term in their
+    cost function as:
 
@@
     \sum_i \left( |\braket{\psi_{x_i} | \Pi_H | \psi_{x_i}}| - 1\right)^2
-$$
+    $$,
 
-where $\Pi_H$ projects onto the truncted Hilbert space.
+    where $\Pi_H$ projects onto the truncated Hilbert space. It is not clear how
+    this penalty term could actually be implemented on their quantum computer.
+  \item The phase-space picture is more convenient to represent the
+    transformations in continuous-variable quantum computation.
+\end{enumerate}
 
@@
 
-The general transformation on $N$ qumodes are devided into two categories: the Gaussian gates and non-Gaussian gates.
+Written in the phase-space picture, the transformations on CV-quantum
+computation can be divided into Gaussian or non-Gaussian gates.
 
 \textbf{ Gaussian}:
-The Gaussian gates could achieves a transformation:
+The Gaussian gates in general transform a ket $\ket{\vec{x},\vec{p}}$ according
+to the following rule:
 
 $$ 
-(\vec{x}, \vec{p}) \to M (\vec{x}, \vec{p}) + (\vec{\alpha_r}, \vec{\alpha_i})
+\begin{pmatrix}
+  \vec{x} \\ \vec{p}
+\end{pmatrix}
+\to 
+M \begin{pmatrix}
+  \vec{x} \\ \vec{p}
+\end{pmatrix}
++ 
+\begin{pmatrix}
+  \vec{\alpha_r}\\ \vec{\alpha_i}
+\end{pmatrix}
 $$
@@
 and $\vec{\alpha_i}$ are real and complex part of a complex vector
-$\vec{\alpha}\in \mathbb{C}^{N}$. In essence, most linear transformations
-($M$) plus affine transformation (displacement, $\vec{\alpha}$) can be
-achieved.
+$\vec{\alpha}\in \mathbb{C}^{N}$.
 
 Importantly, $M$ is of size $2N\times 2N$ and has a lot of freedom inside (i.e.
-its submatrix could be non-sympletic).
-When we only use the $\vec{x}$ vectors to do quantum computation (i.e.
-we care only about $\vec{x}$ and avoid computations that mixes $\vec{x}$ and $\vec{p}$), arbitrary real matrix $W$ of size $N\times N$ could be implemented using Gaussian gates.
-Together with the affine transformation, this means any linear neural network of weight $W$ and bias $\vec{b}$ could be implemented using quantum computations such that (discussed in P.6):
+its submatrix could be non-sympletic). \textbf{When we only use the $\vec{x}$ to
+do quantum computation} (i.e. we care only about $\vec{x}$ and avoid computations
+that mixes $\vec{x}$ and $\vec{p}$), arbitrary real matrix $W$ of size $N\times
+N$ could be implemented using Gaussian gates. Together with the affine
+transformation, this means any linear neural network of weight $W$ and bias
+$\vec{b}$ could be implemented using quantum computations such that (discussed
+in page 6):
 
@@
 
-This corresponds to the first part of a layer in Fig.1.
+\textbf{Non-Gaussian}: The non-Guassian gates achieves a nonlinear function
+\footnote{It is not clear to me what kind of non-linear function could be
+achieved, TODO check.} on the phase space vector $\vec{x}$:
 
-\textbf{Non-Gaussian}: The non-Guassian gates achieves a nonlinear function
-\footnote{It is not clear to me what kind of non-linear function could be achieved, TODO check.}:
 $$
@@
 
-Specifically, the author proposed a gate $V = \exp(i \phi(\hat{x}_i)\otimes \hat{p}_{i'})$, where $\phi(x)$ is a polynomial of a fixed degree, which could approximate any smooth function by Taylor expansion.
-They used this gate to achieve arbitrary nonlinear transformation:
-$$
-\ket{x_i} \to \ket{\phi(x_i)}
-$$
+Specifically, the gate $V = \exp(-i \phi(\hat{x}_i)\otimes \hat{p}_{i'})$ maps
+$\ket{x}\ket{0} \to \ket{x}\ket{x+\phi(x)}$. With a swap gate, they could
+achieve $\ket{x_i} \to \ket{\phi(x_i)}$. Here $\phi(x)$ is a polynomial of a
+fixed degree\footnote{Why use a polynomial function $\phi$? Why not just use any
+function you want?}, so any smooth function could be approximated by their
+Taylor expansion. Sadly, they do not have a decomposition of $V$ in terms of
+elementary CV quantum gates.
 
-Together with the Gaussian gates, we have the embedding of arbitrary classical neural network of the form $\Phi(W\vec{x}+\vec{b})$ as a quantum neural networks in Fig.1.
+Together with the Gaussian gates, they have the embedding of an arbitrary
+classical neural network of the form $\Phi(W\vec{x}+\vec{b})$ as a quantum
+neural networks in their Fig.1. Note that in practice, they use the Kerr gate
+$K(\kappa) = \exp(i\kappa \hat{n}^2)$ as a their nonlinear function.
 
-\textbf{ Specific neural networks structure} The paper also discusses how many specific neural network structure could be  implemented as in a quantum neural network. This includes:
+\subsection{Note about non-linearity}
+\label{sec:Note about non-linearity}
+
+Quantum mechanics is linear, but only in terms of different kets/vectors. Since
+circuit model quantum allows any (nonlinear) function on binary number
+$f(b_1,\cdots,b_n)$ to be represented by a quantum gate
+$U:\ket{b_1,\cdots,b_n}\to \ket{f(b-1,\cdots,b_n)}$, their proposal is not very
+exciting in bring nonlinearity.\footnote{Thank Andrea for pointing this out.}
+However, their model is exciting in that:
+\begin{enumerate}
+  \item Their model naturally acts on real numbers $x$ without the need to
+    encode them into binary strings.
+  \item They divide between linear (Gaussian gate) and nonlinear (non-Gaussian
+    gate) in their quantum neural layer is quite clear and quite resembles the
+    structure of conventional neural network. In out circuit model quantum
+    computation, I have not ever seem something like this.
+\end{enumerate}
+
+I think we have:
+
+\begin{table}[H]
+  \centering
+  \caption{Non-liearity}
+  \begin{tabu}{X[0.5] X X}
+    Input & Encoded as & Linear? \\
+    \hline
+    Classical data & Angles of gates & No, usually the quantum gate are
+    nonlinear w.r.t their parameters \\
+    \hline
+    Classical data & Encoded in the amplitudes of
+    $\sum_{b_1,\cdots,b_n}x_{b_1,\cdots,b_n}\ket{b_1,\cdots,b_n}$ & 
+    In circuit model, this depends on the data encoding layer. But any
+    transformation after are linear except from measurements. 
+    \\
+    % -----
+    & Encoded in basis of either $(\vec{x},\vec{p})$ or $\ket{b_1,\cdots,b_n}$ & 
+    The transformation on them could be nonlinear.
+    \\
+    \hline
+    Quantum data & Encoded as probability amplitudes & Linear except from
+    measurements. \\
+    % ------
+    & Encoded as quasiprobability amplitudes (in CV model) & ???\footnote{Todo:
+  check this.}
+  \end{tabu}
+\end{table}
+
+The general transformation on $N$ qumodes are devided into two categories: the Gaussian gates and non-Gaussian gates.
+
+\section{ CV-QNN models and experiments}
+
+\subsection{Models}
+
+The paper also discusses how many specific neural network structure could be  implemented as in a quantum neural network. This includes:
 
 \begin{itemize}
-  \item \textbf{Convnet}: implemented just as a special matrix to do the convolution
-  \item \textbf{RNN}: implemented by reusing the same parameter for the quantum layer.
-Also, it is very convenient to connect the output of a CV quantum computer back to its input on a optical implementation of CV quantum computer
-  \item \textbf{Residual Network}: implemented as a gate $\ket{\vec{x}} \to \ket{\vec{x} + \phi(\vec{x})}$.
+  \item \textbf{Convnet}: implemented just as a special matrix (of Toeplitz
+    structure) to do the convolution. They have detailed how this matrix could
+    be achieved in terms of the Gaussian matrix $M$ but not decomposition
+    in terms of the elementary CV quantum gates ($R,D,S,BS$) is provided.
+  \item \textbf{RNN}: implemented by reusing the same parameter for the quantum
+    layer. Also, it is very convenient to connect the output of a CV quantum
+    computer back to its input on a optical implementation of CV quantum
+    computer
+  \item \textbf{Residual Network}: implemented using the $V$ gate previously
+    mentioned, which maps $\ket{\vec{x}}\ket{0}~\to~\ket{x}\ket{\vec{x} + \phi(\vec{x})}$.
 \end{itemize}
+
+\subsection{Training algorithm}
+
+They have a very short simple discussion of the training algorithm. They use
+their framework in TensorFlow to do the training and so they can either use the
+build-in automatic differentiation, or numerical difference to do this training.
+Adam seems to be the best choice, but they have not reported the hyperparameters.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\linewidth]{opt.png}
+  \caption{Optimiser}
+\end{figure}
 
@@
 
-1. Function fitting
 \begin{table}[H]
   \centering
-  \caption{Experiments}
-  \label{tab:label}
-  \extrarowsep=3mm
+  \extrarowsep=1.5mm
   \begin{tabu}{X[0.5]|X|X|X|X}
@@
     Classify whether the transaction is genuine or fraud. &
-    For $m$ size $N\times N$ images, choose $m$ initial state $\ket{\phi_\alpha}$
+    For $m$ size $N\times N$ matrices, choose $m$ initial state $\ket{\phi_\alpha}$
     ($\alpha = 1,\cdots m$), find a circuit that transform $\ket{\phi_\alpha}$
-    into a specific encoding of matrix into states ($\ket{A_\alpha}$) for each
+    into a specific quantum encoding of matrix $\ket{A_\alpha}$ for each
     image. &
@@
     $\ket{A_\alpha} \propto \sum_{i,j} \sqrt{a_{ij}^\alpha} \ket{i,j} $. Here
-    $\alpha$ labels the different images. $a_{ij}^\alpha$ is the matrix element of
-    that image $\alpha$.&
-    Output the state $\ket{\psi} = \alpha\ket{0} + \beta\ket{1} +
+    $\alpha$ labels the different matrices. $a_{ij}^\alpha$ is the corresponding
+    matrix element.
+    &
+    Output the state
+
+    $\ket{\psi} = \alpha\ket{0} + \beta\ket{1} +
     \gamma\ket{2}$.
@@
     detection.&
-    $\sum_i |\braket{\psi_i | A_i}|^2$ plus regularisation terms. Requires 
-    tomography! &
+    $\sum_i |\braket{\psi_i | A_i}|^2$ plus regularisation terms. 
+    Requires a CV version of C-SWAP test to get $|\braket{\psi_i |
+    A_i}|$ (not mentioned in the paper).
+    &
     $\sum_i \left(|\braket{ i| \psi_i }|^2 -1\right)^2$ plus regularisation terms.
-    Requires tomography!
+    Requires a CV version of C-SWAP test to get $|\braket{\psi_i |
+    A_i}|$ (not mentioned in the paper).
     \\
-    Result &
+    Result (figure in the paper) &
     Fig.5 & Fig.9 & Fig.10 & Fig.11 
